### 2023-02-14 Outline.qmd
initial commit

---
title: Dissertation Outline
author: Thomas Gorman
date: today
---

## Dissertation Outline

#### Project 1

In Project 1, I programmed a simple projectile launching task to serve as a conceptual replication of an influential paradigm in the visuomotor skill learning literature. Several of the canonical empirical patterns are replicated, with the varied trained participants tending to perform better during testing in both experiments. A major issue with previous research in the cross-disciplinary "benefits of variability" literature is that many previous works do not adequately control for the similarity between training and testing conditions. Such issues arise when both from failures to consider the possibility of non-linear generalization, and from often the unquestioned assumption that participants are acquiring, and then generalizing from prototype or schema-based representations. I introduce a theoretically motivated method of explicitly quantifying the similarity between training experience and testing condition. The resulting similarity quantity can then be used to explicitly control for similarity (by adding it as a covariate to the statistical model). The effect of variability remains significant while controlling for similarity, which I argue is a more rigorous demonstration of the effect of variability on testing performance than what is typically provided with standard methods. I conclude by introducing an extended version of the model that assumes training variation influences the steepness of the generalization gradient. With this flexible similarity mechanism, the group-level effect of variability can then be accounted for within the similarity-based generalization framework.\

#### Project 2

In Project 2, a modified version of the task from Project 1 is used in conjunction with a testing procedure that challenges participants to extrapolate well beyond their training experience. In line with previous research in the function learning literature, participants show evidence of successful extrapolation in our linear task environment. Surprisingly though, the constant training group outperforms the varied training group consistently across numerous variants of the task. Such a pattern is far from unheard of in the vast literature on training variability, and it is therefore remains a worthwhile challenge to evaluate the ability of similarity-based models to account for the observed effects. Additionally, the cognitive process models implemented for project 2 will go beyond the modelling efforts of the previous project in two respects. 1) Extensions that enable the model to produce predictions of participant responses, and 2) fitting and attempting to account for behavior in both training AND testing phases of the experiment.\

https://tegorman13.github.io/DP/

#### Index

### Table of Contents

[**Project 1**](https://tegorman13.github.io/DP/igas_n.html)

-   [Abstract](https://tegorman13.github.io/DP/igas_n.html#abstract)
-   [Introduction](https://tegorman13.github.io/DP/igas_n.html#introduction)
    -   [Similarity and instance-based approaches to transfer of learning](https://tegorman13.github.io/DP/igas_n.html#similarity-and-instance-based-approaches-to-transfer-of-learning)
    -   [The effect of training variability on transfer](https://tegorman13.github.io/DP/igas_n.html#the-effect-of-training-variability-on-transfer)
    -   [Issues with Previous Research](https://tegorman13.github.io/DP/igas_n.html#issues-with-previous-research)
-   [Experiment 1](https://tegorman13.github.io/DP/igas_n.html#experiment-1)
    -   [Methods](https://tegorman13.github.io/DP/igas_n.html#methods)
        -   [Sample Size Estimation](https://tegorman13.github.io/DP/igas_n.html#sample-size-estimation)
        -   [Participants](https://tegorman13.github.io/DP/igas_n.html#participants)
        -   [Task](https://tegorman13.github.io/DP/igas_n.html#task)
    -   [Results](https://tegorman13.github.io/DP/igas_n.html#results)
    -   [Data Processing and Statistical Packages](https://tegorman13.github.io/DP/igas_n.html#data-processing-and-statistical-packages)
    -   [Training Phase](https://tegorman13.github.io/DP/igas_n.html#training-phase)
    -   [Testing Phase](https://tegorman13.github.io/DP/igas_n.html#testing-phase)
    -   [Discussion](https://tegorman13.github.io/DP/igas_n.html#discussion)
-   [Experiment 2](https://tegorman13.github.io/DP/igas_n.html#experiment-2)
    -   [Methods](https://tegorman13.github.io/DP/igas_n.html#methods)
        -   [Participants](https://tegorman13.github.io/DP/igas_n.html#participants)
        -   [Task and Procedure](https://tegorman13.github.io/DP/igas_n.html#task-and-procedure)
    -   [Results](https://tegorman13.github.io/DP/igas_n.html#results)
        -   [Data Processing and Statistical Packages](https://tegorman13.github.io/DP/igas_n.html#data-processing-and-statistical-packages-)
        -   [Training Phase](https://tegorman13.github.io/DP/igas_n.html#training-phase)
        -   [Testing Phase](https://tegorman13.github.io/DP/igas_n.html#testing-phase)
    -   [Discussion](https://tegorman13.github.io/DP/igas_n.html#discussion)
-   [Computational Model](https://tegorman13.github.io/DP/igas_n.html#computational-model)
    -   [Fitting model parameters separately by group](https://tegorman13.github.io/DP/igas_n.html#fitting-model-parameters-separately-by-group)
-   [General Discussion](https://tegorman13.github.io/DP/igas_n.html#general-discussion)
    -   [Limitations](https://tegorman13.github.io/DP/igas_n.html#limitations)
    -   [Conclusion](https://tegorman13.github.io/DP/igas_n.html#conclusion)
-   [References](https://tegorman13.github.io/DP/igas_n.html#references)

[**Project 2**](https://tegorman13.github.io/DP/htw_n.html)

-   [Introduction](https://tegorman13.github.io/DP/htw_n.html#introduction)
-   [Methods](https://tegorman13.github.io/DP/htw_n.html#methods)
    -   [Participants](https://tegorman13.github.io/DP/htw_n.html#participants)
    -   [Task](https://tegorman13.github.io/DP/htw_n.html#task)
    -   [Design](https://tegorman13.github.io/DP/htw_n.html#design)
-   [Results](https://tegorman13.github.io/DP/htw_n.html#results)
    -   [Training](https://tegorman13.github.io/DP/htw_n.html#training)
    -   [Testing](https://tegorman13.github.io/DP/htw_n.html#testing)
-   [Modeling](https://tegorman13.github.io/DP/htw_n.html#modeling)
    -   [ALM & Exam Description](https://tegorman13.github.io/DP/htw_n.html#alm-&-exam-description)
    -   [Model Equations](https://tegorman13.github.io/DP/htw_n.html#model-equations)
    -   [Model Fitting and Comparison](https://tegorman13.github.io/DP/htw_n.html#model-fitting-and-comparison)
-   [References](https://tegorman13.github.io/DP/htw_n.html#references)

[**Project 3**](https://tegorman13.github.io/DP/lbd_n.html)

-   [Overview](https://tegorman13.github.io/DP/lbd_n.html#overview)
-   [Methods](https://tegorman13.github.io/DP/lbd_n.html#methods)
    -   [Dataset and Game Description](https://tegorman13.github.io/DP/lbd_n.html#dataset-and-game-description)
    -   [Split-Test Data](https://tegorman13.github.io/DP/lbd_n.html#split-test-data)
-   [Trial-by-trial influence of variability](https://tegorman13.github.io/DP/lbd_n.html#trial-by-trial-influence-of-variability)
    -   [Randomization](https://tegorman13.github.io/DP/lbd_n.html#randomization)
    -   [Measuring Trial-by-trial variability](https://tegorman13.github.io/DP/lbd_n.html#measuring-trial-by-trial-variability)
-   [Computational Modelling](https://tegorman13.github.io/DP/lbd_n.html#computational-modelling)
    -   [Similarity Between Trials](https://tegorman13.github.io/DP/lbd_n.html#similarity-between-trials)
    -   [Measurement model of learning and performance](https://tegorman13.github.io/DP/lbd_n.html#measurement-model-of-learning-and-performance)
-   [References](https://tegorman13.github.io/DP/lbd_n.html#references)

### 2023-10-07 IGAS.qmd
initial commit again

---
title: IGAS Project
date: last-modified
#page-layout: full
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: false 
---

[Pdf of the journal article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
[Link to online version of journal article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}

```{r echo=FALSE}
knitr::opts_chunk$set(echo=FALSE)
# source('build_toc.R')
# files <- list.files(pattern = '*.Rmd', recursive = F) 
# files = files[!grepl('^_', basename(files)) | grepl('^_index[.]', basename(files))]
# t1 <- render_toc("htw_n.Rmd")
# #cat(t1)
# 
# 
# render_toc("igas_n.Rmd")

library(thematic)
thematic_on(bg="#fcfcfc")
```

# Abstract

Exposing learners to variability during training has been demonstrated to
improve performance in subsequent transfer testing. Such variability benefits
are often accounted for by assuming that learners are developing some general
task schema or structure. However much of this research has neglected to account
for differences in similarity between varied and constant training conditions.
In a between-groups manipulation, we trained participants on a simple projectile
launching task, with either varied or constant conditions. We replicate previous
findings showing a transfer advantage of varied over constant training.
Furthermore, we show that a standard similarity model is insufficient to account
for the benefits of variation, but, if the model is adjusted to assume that
varied learners are tuned towards a broader generalization gradient, then a
similarity-based model is sufficient to explain the observed benefits of
variation. Our results therefore suggest that some variability benefits can be
accommodated within instance-based models without positing the learning of some
schemata or structure.

```{r load, include=FALSE}
source('Functions/IGAS_ProcessFunctions.R')
library(webexercises)
library(kableExtra)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)

#rm(list=ls())
###### data loading and organization #######

# load the processed data from experiment 1 and 2
e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')

options(contrasts = c("contr.sum", "contr.poly"))
defaultContrasts = options()$contrasts
theme_set(theme_classic())

dodge <- position_dodge(width = 0.9)
e2GrpPos <- c("400","500","625","675","800","900")
e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")

e1Pos <- c("610","760","835","910")
e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")

```

# Introduction

The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions  (Barnett & Ceci, 2002; Detterman, 1993). Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations. It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur. The factor of interest to the present investigation is variation during training. Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer. We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity. We first review the relevant concepts and literature.

## Similarity and instance-based approaches to transfer of learning

Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances. Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar (Posner & Keele, 1968).  Prototype models were later challenged by the success of instance-based or exemplar models – which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype (Estes, 1994; Hintzman, 1984; Medin & Schaffer, 1978; Nosofsky, 1986). Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli. As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task. Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.

Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains. In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen. Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations (Palmeri, 1997). That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations. Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning (Cohen & Rosenbaum, 2004; Crump & Logan, 2010; Meigh et al., 2018; Poldrack et al., 1999; Wifall et al., 2017) . Crump and Logan (2010) trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set. Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set. Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.

## The effect of training variability on transfer

While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage. Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work – variability of training examples.

Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions (Czyż, 2021; Soderstrom & Bjork, 2015). Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli (Hahn et al., 2005; Maddox & Filoteo, 2011; Posner & Keele, 1968), complex categorization (Nosofsky et al., 2018), language learning (Jones & Brandt, 2020; Perry et al., 2010; Twomey et al., 2018; Wonnacott et al., 2012) anagram completion (Goode et al., 2008), trajectory extrapolation (Fulvio et al., 2014), task switching (Sabah et al., 2019), associative learning (Lee et al., 2019), visual search (George & Egner, 2021; Gonzalez & Madhavan, 2011; Kelley & Yantis, 2009), voice identity learning (Lavan et al., 2019), simple motor learning (Braun et al., 2009; Kerr & Booth, 1978; Roller et al., 2001; Willey & Liu, 2018), sports training (Green et al., 1995; North et al., 2019), and training on a complex video game (Seow et al., 2019).

Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning. Much of this research has been influenced by the work of Schmidt (1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced. According to Schema Theory, learners possess general motor programs for classes of movements (e.g. throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement. Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class. Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group. Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group. For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations. Both groups are then tested from novel locations.  Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies (Catalano & Kleiner, 1984; Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth, 1978; Wulf, 1991), and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.

Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial. Numerous studies have found null, or in some cases negative effects of training variation (DeLosh et al., 1997; Sinkeviciute et al., 2019; Wrisberg et al., 1987), and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials,  or the type of transfer being measured (Berniker et al., 2014; Braithwaite & Goldstone, 2015; Hahn et al., 2005; Lavan et al., 2019; North et al., 2019; Sadakata & McQueen, 2014; Zaman et al., 2021).

## Issues with Previous Research

Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis (Newell, 2003; Van Rossum, 1990). Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions. For training tasks in which participants have numerous degrees of freedom (e.g. projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g. more unique combinations of x and y velocities). Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations. However, even this level of experimental control may still be insufficient to rule out the effect of similarity on transfer. Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance (Ennis et al., 1988; Ghahramani et al., 1996; Logan, 1988; Nosofsky, 1992; Shepard, 1987; Thoroughman & Taylor, 2005), it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups. Figure 1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.

```{r Toy Model, fig.width=9,fig.height=5.0}
theme_set(theme_classic())
p=2
c<- .0002
simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
                     mutate(plotjitter=ifelse(condit=="varied",0,7),
                            linScale=ifelse(condit=="varied",980,1000),
                            genGauss=exp(-c*(abs((x-train.position)^p))),
                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) %>%
  group_by(x,condit) %>%
  summarise(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
colorVec=c("darkblue","darkred")
plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
                  ylim(c(0,1.05)),
                  #xlim(c(250,950)),
                  scale_x_continuous(breaks=seq(200,1000,by=200)),
                  xlab("Test Stimulus"),
                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
                        legend.position="none"))

ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")

#gridExtra::grid.arrange(ip2,ip1,ncol=2)

gtitle="Figure 1"
title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
captionText=str_wrap("Figure 1. Left panel: Generalization predicted from a simple model that assumes a linear generalization function. A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600. Right panel: if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600. ",200)
capt=ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))

plot_grid(title,NULL,ip1,ip2,capt,NULL,ncol=2,rel_heights=c(.1,1,.15))

```

In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations (Chamberlin & Magill, 1992). Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains (Jamieson et al., 2022; Logan, 2002). As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components (Crump & Logan, 2010; Gandolfo et al., 1996; Meigh et al., 2018; Rosenbaum et al., 1995; van Dam & Ernst, 2015).  However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.

The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws. We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task. We then examine the extent to which this advantage can be explained by an instance-based similarity model.

# Experiment 1

## Methods

### Sample Size Estimation
To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task (Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth, 1978; Wulf, 1991). We then averaged effects across these studies, yielding a Cohens f =.43. The GPower 3.1 software package (Faul et al., 2009) was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition. All experiments reported in the present manuscript exceed this minimum number of participants per condition.

### Participants 
Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18-22 years. A total of 110 Indiana University psychology students participated in Experiment 1. We subsequently excluded 34 participants poor performance at one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g. simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices. A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.

### Task
The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library (de Leeuw, 2015). The stimuli, presented on a black background, consisted of a circular blue ball – controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target. Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant. Likewise, the distance between the center of the target, and the training and testing locations was scaled such that relative distances were preserved regardless of screen size. For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance. Methods Figure 2 displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square. 
Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor. Participants can then “wind up” the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor. If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target. If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory. If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier. If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square. If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.

[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.

```{r Figure 2, echo=FALSE,fig.height=5.8, fig.width=10.1}

#mf <- png::readPNG("Assets/methodsFig1.png")
#ggplot()+annotation_raster(mf,xmin = 0, xmax = 486, ymin = 0, ymax = 196)

gtitle="Figure 2"

title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))

captionText=str_wrap("Figure 2: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier. On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions. Participants were constrained to release the ball within the square. ",150)

capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
  theme(plot.margin = margin(0, 0, 0, 1))
  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
mf <- cowplot::ggdraw()+cowplot::draw_image("Assets/methodsFig1.png",hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))

plot_grid(title,mf,capt,ncol=1,rel_heights = c(.1,1,.1))
#plot_grid(mf,capt,ncol=1,rel_widths=c(1,.01))
# plot_grid(capt,capt,ncol=1)

# capt
# # c2 = ggdraw()+draw_label("testing_text out",x=0,hjust=0,vjust=0,size=11)+ theme(plot.margin = unit(c(0, 0, 0, 0), "pt"))
# # c2
# plot_grid(capt,capt,ncol=1,rel_heights =c(1,.2))

```

## Results

## Data Processing and Statistical Packages

To prepare the data, we first removed trials that were not easily interpretable as performance indicators in our task. Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier. 
The primary measure of performance used in all analyses was the absolute distance away from the center of the target. The absolute distance was calculated on every trial, and then averaged within each subject to yield a single performance score, for each position. A consistent pattern across training and testing phases in both experiments was for participants to perform worse from throwing positions further away from the target – a pattern which we refer to as the difficulty of the positions. However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest. All data processing and statistical analyses were performed in R version 4.03 (R Core Team, 2020). ANOVAs for group comparisons were performed using the rstatix package (Kassambara, 2021).

## Training Phase

Figure 3 below shows aggregate training performance binned into three stages representing the beginning, middle, and end of the training phase. Because the two conditions trained from target distances that were not equally difficult, it was not possible to directly compare performance between conditions in the training phase. Our focus for the training data analysis was instead to establish that participants did improve their performance over the course of training, and to examine whether there was any interaction between training stage and condition. Descriptive statistics for the intermittent testing phase are provided in the supplementary materials.

We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor. The analysis revealed a significant effect of training stage F(2,142)=62.4, p<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,  and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ < .01.

```{r Training1, echo=FALSE,fig.height=5.0, fig.width=7}

exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')

exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')

exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
  group_by(sbjCode,Group,conditType,trainHalf) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')

exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
  group_by(sbjCode,Group,conditType,stage) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')

e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
  facet_wrap(~conditType,ncol=2)+
  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
  ylab("Mean Distance From Center Of Target")+
  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)

gtitle="Figure 3"

title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))

captionText=str_wrap("Training performance for varied and constant participants binned into three stages. Shorter bars indicate better performance (ball landing closer to the center of the target). Error bars indicate standard error of the mean. ",145)

capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
  theme(plot.margin = margin(0, 0, 0, 1))
  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))

```

## Testing Phase 
In Experiment 1, a single constant-trained group was compared against a single varied-trained group. At the transfer phase, all participants were tested from 3 positions: 1) the positions(s) from their own training, 2) the training position(s) of the other group, and 3) a position novel to both groups. Overall, group performance was compared with a mixed type III ANOVA, with condition (varied vs. constant) as a between-subject factor and throwing location as a within-subject variable. The effect of throwing position was strong, F(3,213) = 56.12, p<.001, η2G = .23. The effect of training condition was significant F(1,71)=8.19, p<.01, η2G = .07. There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.

```{r e1Test, echo=FALSE,fig.width=9.5, fig.height = 6.5 }

exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% 
  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()

#manuscript plot
e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)

gtitle="Figure 4"

title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))

captionText=str_wrap("Testing performance for each of the 4 testing positions, compared between training conditions. Positions 610 and 910 were trained on by the varied group, and novel for the constant group. Position 760 was trained on by the constant group, and novel for the varied group. Position 835 was novel for both groups. Shorter bars are indicative of better performance (the ball landing closer to the center of the target). Error bars indicate standard error of the mean. ",130)

capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
  theme(plot.margin = margin(0, 0, 0, 1))
  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
plot_grid(title,e1test1,capt,ncol=1,rel_heights=c(.18,1,.15))

```

\
\

```{r e1Table, echo=FALSE }

exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% 
  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()

test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
 test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
 test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
 test=test[,1:3]

captionText="Table 1. Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis."

kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>%   kable_classic() %>% kableExtra::footnote(general=captionText,general_title = "")

# 
# colnames(test) <- c("Position","Constant","Varied")
# ft1=flextable(test,col_keys = c("Position","Constant","Varied"))
# ft1 <- flextable::set_caption(ft1,captionText)
# ft1

```

## Discussion

In Experiment 1, we found that varied training resulted in superior testing performance than constant training, from both a position novel to both groups, and from the position at which the constant group was trained, which was novel to the varied condition. The superiority of varied training over constant training even at the constant training position is of particular note, given that testing at this position should have been highly similar for participants in the constant condition. It should also be noted, though, that testing at the constant trained position is not exactly identical to training from that position, given that the context of testing is different in several ways from that of training, such as the testing trials from the different positions being intermixed, as well as a simple change in context as a function of time. Such contextual differences will be further considered in the General Discussion.

In addition to the variation of throwing position during training, the participants in the varied condition of Experiment 1 also received training practice from the closest/easiest position, as well as from the furthest/most difficult position that would later be encountered by all participants during testing. The varied condition also had the potential advantage of interpolating both of the novel positions from which they would later be tested. Experiment 2 thus sought to address these issues by comparing a varied condition to multiple constant conditions.

# Experiment 2

In Experiment 2, we sought to replicate our findings from Experiment 1 with a new sample of participants, while also addressing the possibility of the pattern of results in Experiment 1 being explained by some idiosyncrasy of the particular training location of the constant group relative to the varied group. To this end, Experiment 2 employed the same basic procedure as Experiment 1, but was designed with six separate constant groups each trained from one of six different locations (400, 500, 625, 675, 800, or 900), and a varied group trained from two locations (500 and 800). Participants in all seven groups were then tested from each of the 6 unique positions.

## Methods

### Participants 
A total of 306 Indiana University psychology students participated in Experiment 2, which was also conducted online. As was the case in experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18–22-year-old individuals. Using the same procedure as experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task. A total of 208 participants were included in the final analyses with 31 in the varied group and 32, 28, 37, 25, 29, 26 participants in the constant groups training from location 400, 500, 625, 675, 800, and 900, respectively. All participants were compensated with course credit.

### Task and Procedure 
The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target. Additionally, the intermittent testing trials featured in experiment 1 were not utilized in experiment 2, and all training and testing trials were presented with feedback. An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).

The procedure for Experiment 2 was also quite similar to experiment 1. Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group. In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training. Each of the constant groups thus experience one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.

## Results

### Data Processing and Statistical Packages  
After confirming that condition and throwing position did not have any significant interactions, we standardized performance within each position, and then average across position to yield a single performance measure per participant. This standardization did not influence our pattern of results. As in experiment 1, we performed type III ANOVA’s due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.  The statistical software for the primary analyses was the same as for experiment 1. Individual learning rates in the testing phase, compared between groups in the supplementary analyses, were fit using the TEfit package in R (Cochrane, 2020).

### Training Phase 
The different training conditions trained from positions that were not equivalently difficult and are thus not easily amenable to comparison. As previously stated, the primary interest of the training data is confirmation that some learning did occur. Figure 5 depicts the training performance of the varied group alongside that of the aggregate of the six constant groups (5a), and each of the 6 separate constant groups (5b). An ANOVA comparison with training stage (beginning, middle, end) as a within-group factor and group (the varied condition vs. the 6 constant conditions collapsed together) as a between-subject factor revealed no significant effect of group on training performance, F(1,206)=.55,p=.49, $\eta^{2}_G$ <.01, a significant effect of training stage F(2,412)=77.91, p<.001, $\eta^{2}_G$ =.05, and no significant interaction between group and training stage, F(2,412)=.489 p=.61, $\eta^{2}_G$ <.01. We also tested for a difference in training performance between the varied group and the two constant groups that trained matching throwing positions (i.e., the constant groups training from position 500, and position 800). The results of our ANOVA on this limited dataset mirrors that of the full-group analysis, with no significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ <.01, a significant effect of training stage F(2,172)=56.29, p<.001, $\eta^{2}_G$ =.11, and no significant interaction between group and training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ <.01.

```{r,echo=FALSE, include=FALSE }

e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)

exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()

exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()

exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()

exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
  group_by(sbjCode,Group2,conditType,stage) %>% 
  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()

transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()

transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% convert_as_factor(testHalf)

variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))

transfer <- rbind(variedTest,constantTest)
transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% convert_as_factor(novel,extrapolate)

transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()

# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
# novelAll <- novelAll %>% group_by(positionX) %>%
#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()

novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)

constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
variedTest <- transfer %>% filter(condit==7) # only varied testing
variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity

variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant

exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()

exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()

exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()

exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()

exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()

```

```{r e2train, echo=FALSE,fig.height=12.5, fig.width=9}

### New - 3 stage
e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
        plot.title.position = "plot")+
  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")

e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
        plot.title.position = "plot")+
  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")

#plot_grid(e2train1,e2train2,ncol=1)

gtitle="Figure 5"

title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))

captionText=str_wrap("Training performance for the six constant conditions, and the varied condition, binned into three stages. In Figure 5a, the six constant groups are averaged together, as are the two training positions for the varied group. In Figure 5b the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis. Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group. Error bars indicate standard error of the mean. ",130)

capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
  theme(plot.margin = margin(0, 0, 0, 1))
  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
plot_grid(title,e2train1,e2train2,capt,ncol=1,rel_heights=c(.18,1,1,.15))

```

### Testing Phase
In Experiment 2, a single varied condition (trained from two positions, 500 and 800), was compared against six separate constant groups (trained from a single position, 400, 500, 625, 675, 800 or 900). For the testing phase, all participants were tested from all six positions, four of which were novel for the varied condition, and five of which were novel for each of the constant groups. For a general comparison, we took the absolute deviations for each throwing position and computed standardized scores across all participants, and then averaged across throwing position. The six constant groups were then collapsed together allowing us to make a simple comparison between training conditions (constant vs. varied). A type III between-subjects ANOVA was performed, yielding a significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$ =.02. Descriptive statistics for each condition are shown in table 2. Figure 6A visualizes the consistent advantage of the varied condition over the constant groups across the testing positions. Figure 6b shows performance between the varied condition and the individual constant groups.

```{r e2test1, echo=FALSE,fig.height=12.5, fig.width=10.5 }

# manuscript plot
e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
  theme(plot.title=element_text(face="bold",size=9),
        plot.title.position = "plot",
        legend.title.align=.25)+
  ggtitle("A")

e2test2<-exp2.Test7 %>% 
  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
  facet_wrap(~ThrowPosition4)+
  ylab("Mean Distance From Center Of Target")+
  guides(fill=guide_legend(title="Training Condition"))+
  theme(plot.title=element_text(face="bold",size=9),
        plot.title.position = "plot",
        legend.title.align=.25,
        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")

gtitle="Figure 6"

title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))

captionText=str_wrap("Testing phase performance from each of the six testing positions. The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested. Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue). The x axis labels indicate the location(s) from which each group trained. Lower values along the y axis reflect better performance at the task (closer distance to target center). Error bars indicate standard error of the mean. ",140)

capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
  theme(plot.margin = margin(0, 0, 0, 1))
  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
plot_grid(title,e2test1,e2test2,capt,ncol=1,rel_heights=c(.18,1,1,.15))

```

\
\
\

```{r e2table1, echo=FALSE }

tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
 tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
 tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
 tab2=tab2[,1:3]

 captionText="Table 2. Transfer performance from each of the 6 throwing locations from which all participants were tested. Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue). The x axis labels indicate the location(s) from which each group trained. Lower values along the y axis reflect better performance at the task (closer distance to target center). Error bars indicate standard error of the mean. "

kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% kable_classic() %>% footnote(general=captionText,general_title = "")

```

Next, we compared the testing performance of constant and varied groups from only positions that participants had not encountered during training. Constant participants each had 5 novel positions, whereas varied participants tested from 4 novel positions (400,625,675,900). We first standardized performance within in each position, and then averaged across positions. Here again, we found a significant effect of condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ = .02 .

```{r e2table3, echo=FALSE }

sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()

tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")

 tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))

 tab3 = tab3 %>% 
   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
 tab3=tab3[,1:3]

 captionText="Table 3. Testing performance from novel positions. Includes data only from positions that were not encountered during the training stage (e.g. excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups). Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis. "

kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% kable_classic() %>% footnote(general=captionText,general_title = "")
```

Finally, corresponding to the comparison of position 760 from experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained. Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group). Figure 7 displays the particular subset of comparisons utilized for this analysis. Again, we standardized performance within each position before performing the analyses on the aggregated data. In this case, the effect of condition did not reach statistical significance F(1,149)=3.14, p=.079, $\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.

```{r e2test2, echo=FALSE,fig.height=6.0, fig.width=7, warning=FALSE}

sum.variedVsNovelIden <- variedVsNovelIden  %>%
  group_by(sbjCode,conditType,positionX) %>% 
  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()

e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)

gtitle="Figure 7"

title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))

captionText=str_wrap("A comparison of throwing location that are identical to those trained by the constant participants (e.g. constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800). Error bars indicate standard error of the mean. ",145)

capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
  theme(plot.margin = margin(0, 0, 0, 1))
  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
plot_grid(title,e2Test2,capt,ncol=1,rel_heights=c(.18,1,.15))

```

\
\

```{r e2tab3,echo=FALSE, warning=FALSE}

tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")

 tab4=tab4 %>% group_by(Condition) %>% 
   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
 tab4=tab4[,1:3]

 captionText="Table 5. Testing performance from the locations trained by constant participants and novel to varied participants. Locations 500 and 800 are not included as these were trained by the varied participants. Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis. "

kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% kable_classic() %>% footnote(general=captionText,general_title = "")

```

## Discussion 
The results of experiment 2 largely conform to the findings of experiment 1. Participants in both varied and constant conditions improved at the task during the training phase. We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions (Catalano & Kleiner, 1984; Wrisberg et al., 1987), which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing (Soderstrom & Bjork, 2015). However our finding of no difference in training performance between constant and varied groups has been observed in previous work (Chua et al., 2019; Moxley, 1979; Pigott & Shapiro, 1984).

In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions. The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt’s influential Schema Theory (Catalano & Kleiner, 1984; Chua et al., 2019; Goodwin et al., 1998; McCracken & Stelmach, 1977; Moxley, 1979; Newell & Shapiro, 1976; Pigott & Shapiro, 1984; Roller et al., 2001; Schmidt, 1975; Willey & Liu, 2018; Wrisberg et al., 1987; Wulf, 1991). We also join a much smaller set of research to observe this pattern in a computerized task (Seow et al., 2019). One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2. Although this pattern has been observed elsewhere in the literature (Goode et al., 2008; Kerr & Booth, 1978), the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.

# Computational Model
Controlling for the similarity between training and testing
The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations. To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release. For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions. We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target. We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions – thus resulting in six separate similarity scores for each participant. Figure 8a visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions. As illustrated in Figure 8b, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.

(ref:taskSpace) Figure 8a is a visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase. This empirical solution space was compiled from all of the participants in experiment 2. Figure 8b shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.

```{r taskSpace, echo=FALSE,fig.height=9.0, fig.width=10}

library("RColorBrewer")
taskspace <- e2 %>% filter(AbsDistFromCenter<900)
taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")

solSpace <- e2 %>% filter(trialType==11)
#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")

solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)

missSpace <- e2 %>% filter(trialType !=11)
missSpace$Result = "Missed Target"
solSpace$Result <- solSpace$Result

# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
# multiplied velocoties by -1 to make the axes less confusing
ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
  geom_point(aes(colour=Result),alpha=0.6) + 
  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")

fullSpace <- rbind(missSpace,solSpace)

fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")

gtitle="Figure 8"
title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))

captionText=str_wrap("Figure 8A is a visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase. This empirical solution space was compiled from all of the participants in experiment 2. Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.",145)

capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
  theme(plot.margin = margin(0, 0, 0, 1))
  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
plot_grid(title,ss,fs,capt,ncol=1,rel_heights=c(.18,1,1,.15))
```

For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.  The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient. Then, as per an instance-based model of similarity (Logan, 2002; Nosofsky, 1992), these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value. The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.  If c has a large value, then even a small difference between two throws’ velocities greatly decreases the extent of generalization from one to the other. A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities. The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions. The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.

**Equation 1:**
\[ Similarity_{I,J} =  \sum_{i = I}\sum_{j=J} e^{-c\cdot d^p_{i,j}} \]

**Equation 2:** 
$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$

A simple linear regression revealed that these similarity scores were significantly predictive of performance in the transfer stage, t =-15.88, p<.01, $r^2$=.17, such that greater similarity between training throws and solution spaces for each of the test locations resulted in better performance. We then repeated the group comparisons above while including similarity as a covariate in the model. Comparing the varied and constant groups in testing performance from all testing positions yielded a significant effect of similarity, F(1, 205)=85.66, p<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition (varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p<.001, $\eta^{2}_G$ =.18 as well  as for condition F(1,148)=11.55, p<.001, $\eta^{2}_G$ =.07. For all comparisons, the pattern of results was consistent with the initial findings from experiment 2, with the varied group still performing significantly better than the constant group.

## Fitting model parameters separately by group
To directly control for similarity in Experiment 2, we developed a model-based measure of the similarity between training throws and testing conditions. This similarity measure was a significant predictor of testing performance, e.g., participants whose training throws were more similar to throws that resulted in target hits from the testing positions, tended to perform better during the testing phase. Importantly, the similarity measure did not explain away the group-level benefits of varied training, which remained significant in our linear model predicting testing performance after similarity was added to the model. However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group (Hahn et al., 2005; Lamberts, 1994). Relatedly, the influential Bayesian generalization model developed by  Tenenbaum & Griffiths (2001) predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples. Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.  Varied versus constant participants may be expected to learn to generalize their experience to different degrees.  To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization. One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience (Nosofsky & Johansen, 2000; Sakamoto et al., 2006).  If one’s training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.  Conversely, if one’s training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.

To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c,  to varied and constant participants.  To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.

Both models generate distinct similarity values between training and testing locations. Much like the analyses in Experiment 2, these similarity values are regressed against testing performance in models of the form shown below. As was the case previously, testing performance is defined as the mean absolute distance from the center of the target (with a separate score for each participant, from each position).

Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p<.01). Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the c parameter separately between groups (Similarity2c). In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p<.01), with the varied group still performing significantly better. However, in linear model 4 the addition of the Similarity2c predictor results in the effect of training group becoming nonsignificant (p=.40), suggesting that the effect of varied vs. constant training is accounted for by the Similarity2c predictor.
Next, to further establish a difference between the models, we performed nested model comparisons using ANOVA, to see if the addition of the training group parameter led to a significant improvement in model performance. In the first comparison, ANOVA(Linear Model 1, Linear Model 2), the addition of the training group predictor significantly improved the performance of the model (F=22.07, p<.01). However, in the second model comparison, ANOVA (Linear model 3, Linear Model 4) found no improvement in model performance with the addition of the training group predictor (F=1.61, p=.20).

Finally, we sought to confirm that similarity values generated from the adjusted Similarity2c model had more predictive power than those generated from the original Similarity1c model. Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value. When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011). Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.

In summary, our modeling suggests that an instance-based model which assumes equivalent generalization gradients between constant and varied trained participants is unable to account for the extent of benefits of varied over constant training observed at testing. The evidence for this in the comparative model fits is that when a varied/constant dummy-coded variable for condition is explicitly added to the model, the variable adds a significant contribution to the prediction of test performance, with the variable condition yielding better performance than the constant conditions.  However, if the instance-based generalization model is modified to assume that the training groups can differ in the steepness of their generalization gradient, by incorporating a separate generalization parameter for each group, then the instance-based model can account for our experimental results without explicitly taking training group into account.  Henceforth this model will be referred to as the Instance-based Generalization with Adaptive Similarity (IGAS) model.

# General Discussion
Across two experiments, we found evidence in support of the benefits of variability hypothesis in a simple, computerized projectile throwing task. Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase. However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions. We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training (Goode et al., 2008; Green et al., 1995; Kerr & Booth, 1978). In experiment 1 varied participants performed significantly better on this identity comparison. In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c). Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees. Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space. Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition. A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.  The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.  In this fashion, contextually appropriate c values could be empirically learned.  This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.

Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained. Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in Figure 9 we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern. In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model – namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.

```{css}

caption, .caption{
  font-style:italic;
  margin-top:0.5em;
  margin-bottom:0.5em;
  width:100%;
  text-align: left;
}

```

```{r} 
#| Toy Model 2, fig.width=10,fig.height=10.0,
#| fig.cap="Figure 9. A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600. For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is: Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$. For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition. The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions. Thus, the generalization model for the varied condition in the bottom-right panel is of the form: Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$."

#

p=2
c<- .000002

trainingTestingDifference=2000;
cvaried=.00002
cconstant=.0005
simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
                            genGauss=exp(-c*(abs((x-train.position)^p))),
                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
                            ) %>% 
  group_by(x,condit) %>%
  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')

#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))

colorVec=c("darkblue","darkred")
plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
                  ylim(c(0,1.05)),
                  #xlim(c(250,950)),
                  scale_x_continuous(breaks=seq(200,1000,by=200)),
                  xlab("Test Stimulus"),
                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.1),
                  annotate(geom="text",x=455,y=1.01,label="Training",size=3.1),
                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.1),
                  annotate(geom="text",x=657,y=1.01,label="Training",size=3.1),
                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.1),
                  annotate(geom="text",x=855,y=1.01,label="Training",size=3.1),
                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
                        legend.position="none"))

ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
  ggtitle("Added distance due to context context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
  ggtitle("Added distance due to context context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)

gtitle="Figure 9."
title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))

```

As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning (Aha & Goldstone, 1992; Briscoe & Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al., 2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013; Taylor & Ivry, 2013; Thoroughman & Taylor, 2005). Lamberts (1994) showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions. The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability (Hahn et al., 2005; Sakamoto et al., 2006). However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task. Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains. (Censor et al., 2012; Cox et al., 2018; Hills et al., 2010; Jamieson et al., 2022; Law & Gold, 2010; Roark et al., 2021; Rosenbaum et al., 2001; Vigo et al., 2018; Wall et al., 2021; Wu et al., 2020; Yang et al., 2020).

Our modelling approach does differ from category learning implementations of instance-based models in several ways. One such difference is the nature of the training instances that are assumed to be stored. In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g. size/color/shape).  Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw. An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g. movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks. Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work – though as described in the introduction there is some evidence in support of this idea (Chamberlin & Magill, 1992; Crump & Logan, 2010; Hommel, 1998; Meigh et al., 2018; Poldrack et al., 1999).  A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues (Cohen & Rosenbaum, 2004; Rosenbaum et al., 1995). Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances. Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures. A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.

Our findings also have some conceptual overlap with an earlier study on the effects of varied training in a coincident timing task (Catalano & Kleiner, 1984). In this task, participants observe a series of lamps lighting up consecutively, and attempt to time a button press with the onset of the final lamp. The design consisted of four separate constant groups, each training from a single lighting velocity, and a single varied group training with all four of the lighting velocities used by the individual constant groups. Participants were then split into four separate testing conditions, each of which were tested from a single novel lighting velocity of varying distance from the training conditions. The result of primary interest was that all participants performed worse as the distance between training and testing velocity increased – a typical generalization decrement. However, varied participants showed less of a decrement than did constant participants. The authors take this result as evidence that varied training results in a less-steep generalization gradient than does constant training. Although the experimental conclusions of Catalano and Kleiner are similar to our own, our work is novel in that we account for our results with a cognitive model, and without assuming the formation of a schema.  Additionally, the way in which Catalano and Kleiner collapse their separate constant groups together may result in similarity confounds between varied and constant conditions that leaves their study open to methodological criticisms, especially in light of related work which demonstrated that the extent to which varied training may be beneficial can depend on whether the constant group they are compared against trained from similar conditions to those later tested (Wrisberg et al., 1987). Our study alleviates such concerns by explicitly controlling for similarity.

## Limitations
A limitation of this study concerns the ordering of the testing/transfer trials at the conclusion of both experiments. Participants were tested from each separate position (4 in Experiment 1, 6 in Experiment 2) in a random, intermixed order. Because the varied group was trained from two positions that were also randomly ordered, they may have benefited from experience with this type of sequencing, whereas the constant groups had no experience with switching between positions trial to trial. This concern is somewhat ameliorated by the fact that the testing phase performance of the constant groups from their trained position was not significantly worse than their level of performance at the end of the training phase, suggesting that they were not harmed by random ordering of positions during testing. It should also be noted that the computerized task utilized in the present work is relatively simple compared to many of the real-world tasks utilized in prior research. It is thus conceivable that the effect of variability in more complex tasks is distinct from the process put forward in the present work. An important challenge for future work will be to assess the extent to which IGAS can account for generalization in relatively complex tasks with far more degrees of freedom.

It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations (Nosofsky, 1992; Shepard, 1987). Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model. In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g. the relative distance between positions 400 and 500 is equivalent to that between 800 and 900). However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.

## Conclusion
Our experiments demonstrate a reliable benefit of varied training in a simple projectile launching task. Such results were accounted for by an instance-based model that assumes that varied training results in the computation of a broader similarity-based generalization gradient. Instance-based models augmented with this assumption may be a valuable approach towards better understanding skill generalization and transfer.

# References

Aha, D. W., & Goldstone, R. L. (1992). Concept Learning and Flexible Weighting. _In Proceedings of the Fourteenth Annual Conference of the Cognitive Science Society_, 534–539.

Barnett, S. M., & Ceci, S. J. (2002). When and where do we apply what we learn?: A taxonomy for far transfer. _Psychological Bulletin_, _128_(4), 612–637. https://doi.org/10.1037//0033-2909.128.4.612

Berniker, M., Mirzaei, H., & Kording, K. P. (2014). The effects of training breadth on motor generalization. _Journal of Neurophysiology_, _112_(11), 2791–2798. https://doi.org/10.1152/jn.00615.2013

Braithwaite, D. W., & Goldstone, R. L. (2015). Effects of Variation and Prior Knowledge on Abstract Concept Learning. _Cognition and Instruction_, _33_(3), 226–256. https://doi.org/10.1080/07370008.2015.1067215

Braun, D. A., Aertsen, A., Wolpert, D. M., & Mehring, C. (2009). Motor Task Variation Induces Structural Learning. _Current Biology_, _19_(4), 352–357. https://doi.org/10.1016/j.cub.2009.01.036

Briscoe, E., & Feldman, J. (2011). Conceptual complexity and the bias/variance tradeoff. _Cognition_, _118_(1), 2–16. https://doi.org/10.1016/j.cognition.2010.10.004

Catalano, J. F., & Kleiner, B. M. (1984). Distant Transfer in Coincident Timing as a Function of Variability of Practice. _Perceptual and Motor Skills_, _58_(3), 851–856. https://doi.org/10.2466/pms.1984.58.3.851

Censor, N., Sagi, D., & Cohen, L. G. (2012). Common mechanisms of human perceptual and motor learning. _Nature Reviews Neuroscience_, _13_(9), 658–664. https://doi.org/10.1038/nrn3315

Chamberlin, C. J., & Magill, R. A. (1992). A Note on Schema and Exemplar Approaches to Motor Skill Representation in Memory. _Journal of Motor Behavior_, _24_(2), 221–224. https://doi.org/10.1080/00222895.1992.9941617

Chua, L.-K., Dimapilis, M. K., Iwatsuki, T., Abdollahipour, R., Lewthwaite, R., & Wulf, G. (2019). Practice variability promotes an external focus of attention and enhances motor skill learning. _Human Movement Science_, _64_, 307–319. https://doi.org/10.1016/j.humov.2019.02.015

Cochrane, A. (2020). TEfits: Nonlinear regression for time-evolving indices. _Journal of Open Source Software_, _5_(52), 2535. https://doi.org/10.21105/joss.02535

Cohen, R. G., & Rosenbaum, D. A. (2004). Where grasps are made reveals how grasps are planned: Generation and recall of motor plans. _Experimental Brain Research_, _157_(4). https://doi.org/10.1007/s00221-004-1862-9

Cox, G. E., Hemmer, P., Aue, W. R., & Criss, A. H. (2018). Information and processes underlying semantic and episodic memory across tasks, items, and individuals. _Journal of Experimental Psychology: General_, _147_(4), 545–590. https://doi.org/10.1037/xge0000407

Crump, M. J. C., & Logan, G. D. (2010). Episodic contributions to sequential control: Learning from a typist’s touch. _Journal of Experimental Psychology: Human Perception and Performance_, _36_(3), 662–672. https://doi.org/10.1037/a0018390

Czyż, S. H. (2021). Variability of Practice, Information Processing, and Decision Making—How Much Do We Know? _Frontiers in Psychology_, _12_. https://doi.org/10.3389/fpsyg.2021.639131

de Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a Web browser. _Behavior Research Methods_, _47_(1), 1–12. https://doi.org/10.3758/s13428-014-0458-y

DeLosh, E. L., McDaniel, M. A., & Busemeyer, J. R. (1997). Extrapolation: The Sine Qua Non for Abstraction in Function Learning. _Journal of Experimental Psychology: Learning, Memory, and Cognition_, 19.

Detterman, D. K. (1993). The case for the prosecution: Transfer as an epiphenomenon. In _Transfer on trial: Intelligence, cognition, and instruction_ (pp. 1–24). Ablex Publishing.

Ennis, D. M., Palen, J. J., & Mullen, K. (1988). A multidimensional stochastic theory of similarity. _Journal of Mathematical Psychology_, _32_(4), 449–465. https://doi.org/10.1016/0022-2496(88)90023-5

Estes, W. K. (1994). _Classification and Cognition_. Oxford University Press.

Faul, F., Erdfelder, E., Buchner, A., & Lang, A.-G. (2009). Statistical power analyses using G*Power 3.1: Tests for correlation and regression analyses. _Behavior Research Methods_, _41_(4), 1149–1160. https://doi.org/10.3758/BRM.41.4.1149

Fulvio, J. M., Green, C. S., & Schrater, P. R. (2014). Task-Specific Response Strategy Selection on the Basis of Recent Training Experience. _PLOS Computational Biology_, _10_(1), e1003425. https://doi.org/10.1371/journal.pcbi.1003425

Gandolfo, F., Mussa-Ivaldi, F. A., & Bizzi, E. (1996). Motor learning by field approximation. _Proceedings of the National Academy of Sciences_, _93_(9), 3843–3846. https://doi.org/10.1073/pnas.93.9.3843

George, N., & Egner, T. (2021). Stimulus variability and task relevance modulate binding-learning. _Attention, Perception, & Psychophysics_. https://doi.org/10.3758/s13414-021-02338-6

Ghahramani, Z., Wolpert, D. M., & Jordan, M. I. (1996). Generalization to Local Remappings of the Visuomotor Coordinate Transformation. _Journal of Neuroscience_, _16_(21), 7085–7096. https://doi.org/10.1523/JNEUROSCI.16-21-07085.1996

Gonzalez, C., & Madhavan, P. (2011). Diversity during training enhances detection of novel stimuli. _Journal of Cognitive Psychology_, _23_(3), 342–350. https://doi.org/10.1080/20445911.2011.507187

Goode, M. K., Geraci, L., & Roediger, H. L. (2008). Superiority of variable to repeated practice in transfer on anagram solution. _Psychonomic Bulletin & Review_, _15_(3), 662–666. https://doi.org/10.3758/PBR.15.3.662

Goodwin, J. E., Eckerson, J. M., Grimes, C. R., & Gordon, P. M. (1998). Effect of Different Quantities of Variable Practice on Acquisition, Retention, and Transfer of An Applied Motor Skill. _Perceptual and Motor Skills_, _87_(1), 147–151. https://doi.org/10.2466/pms.1998.87.1.147

Green, D. P., Whitehead, J., & Sugden, D. A. (1995). Practice Variability and Transfer of a Racket Skill. _Perceptual and Motor Skills_, _81_(3_suppl), 1275–1281. https://doi.org/10.2466/pms.1995.81.3f.1275

Hahn, U., Bailey, T. M., & Elvin, L. B. C. (2005). Effects of category diversity on learning, memory, and generalization. _Memory & Cognition_, _33_(2), 289–302. https://doi.org/10.3758/BF03195318

Hills, T. T., Todd, P. M., & Goldstone, R. L. (2010). The central executive as a search process: Priming exploration and exploitation across domains. _Journal of Experimental Psychology: General_, _139_(4), 590–609. https://doi.org/10.1037/a0020666

Hintzman, D. L. (1984). MINERVA 2: A simulation model of human memory. _Behavior Research Methods, Instruments, & Computers_, _16_(2), 96–101. https://doi.org/10.3758/BF03202365

Hommel, B. (1998). Event Files: Evidence for Automatic Integration of Stimulus-Response Episodes. _Visual Cognition_, _5_(1–2), 183–216. https://doi.org/10.1080/713756773

Jamieson, R. K., Johns, B. T., Vokey, J. R., & Jones, M. N. (2022). Instance theory as a domain-general framework for cognitive psychology. _Nature Reviews Psychology_, _1_(3), 174–183. https://doi.org/10.1038/s44159-022-00025-3

Jones, S. D., & Brandt, S. (2020). Density and Distinctiveness in Early Word Learning: Evidence From Neural Network Simulations. _Cognitive Science_, _44_(1), e12812. https://osf.io/2qk5j/. https://doi.org/10.1111/cogs.12812

Kassambara, A. (2021). _rstatix: Pipe-Friendly Framework for Basic Statistical Tests_ [R package   version 0.7.0]. https://CRAN.R-project.org/package=rstatix

Kelley, T. A., & Yantis, S. (2009). Learning to attend: Effects of practice on information selection. _Journal of Vision_, _9_(7), 16. https://doi.org/10.1167/9.7.16

Kerr, R., & Booth, B. (1978). Specific and varied practice of motor skill. _Perceptual and Motor Skills_, _46_(2), 395–401.

Lamberts, K. (1994). Flexible Tuning of Similarity in Exemplar-Based Categorization. _Journal of Experimental Psychology: Learning, Memory, and Cognition_, _20_(5), 1003–1021.

Lavan, N., Knight, S., Hazan, V., & McGettigan, C. (2019). The effects of high variability training on voice identity learning. _Cognition_, _193_, 104026. https://doi.org/10.1016/j.cognition.2019.104026

Law, C.-T., & Gold, J. I. (2010). Shared Mechanisms of Perceptual Learning and Decision Making. _Topics in Cognitive Science_, _2_(2), 226–238. https://doi.org/10.1111/j.1756-8765.2009.01044.x

Lee, J. C., Lovibond, P. F., & Hayes, B. K. (2019). Evidential diversity increases generalisation in predictive learning. _Quarterly Journal of Experimental Psychology_, _72_(11), 2647–2657. https://doi.org/10.1177/1747021819857065

Logan, G. D. (1988). Toward an instance theory of automatization. _Psychological Review_, _95_(4), 492–527.

Logan, G. D. (2002). An instance theory of attention and memory. _Psychological Review_, _109_(2), 376–400. https://doi.org/10.1037/0033-295X.109.2.376

Maddox, W. T., & Filoteo, J. V. (2011). Stimulus range and discontinuity effects on information-integration category learning and generalization. _Attention, Perception, & Psychophysics_, _73_(4), 1279–1295. https://doi.org/10.3758/s13414-011-0101-2

Marongelli, E., & Thoroughman, K. (2013). The advantage of flexible neuronal tunings in neural network models for motor learning. _Frontiers in Computational Neuroscience_, _7_, 100. https://doi.org/10.3389/fncom.2013.00100

McCracken, H. D., & Stelmach, G. E. (1977). A Test of the Schema Theory of Discrete Motor Learning. _Journal of Motor Behavior_, _9_(3), 193–201. https://doi.org/10.1080/00222895.1977.10735109

Medin, D. L., & Schaffer, M. M. (1978). Context Theory of Classification Learning. _Psychological Review_, _85_(3), 207.

Meigh, K. M., Shaiman, S., Tompkins, C. A., Abbott, K. V., & Nokes-Malach, T. (2018). What memory representation is acquired during nonword speech production learning? The influence of stimulus features and training modality on nonword encoding. _Cogent Psychology_, _5_(1), 1493714. https://doi.org/10.1080/23311908.2018.1493714

Moxley, S. E. (1979). Schema: The Variability of Practice Hypothesis. _Journal of Motor Behavior_, _11_(1), 65–70. https://doi.org/10.1080/00222895.1979.10735173

Newell, K. M. (2003). Schema Theory (1975): Retrospectives and Prospectives. _Research Quarterly for Exercise and Sport_, _74_(4), 383–388. https://doi.org/10.1080/02701367.2003.10609108

Newell, K. M., & Shapiro, D. C. (1976). Variability of Practice and Transfer of Training: Some Evidence Toward a Schema View of Motor Learning. _Journal of Motor Behavior_, _8_(3), 233–243. https://doi.org/10.1080/00222895.1976.10735077

North, J. S., Bezodis, N. E., Murphy, C. P., Runswick, O. R., Pocock, C., & Roca, A. (2019). The effect of consistent and varied follow-through practice schedules on learning a table tennis backhand. _Journal of Sports Sciences_, _37_(6), 613–620. https://doi.org/10.1080/02640414.2018.1522683

Nosofsky, R. M. (1986). Attention, similarity, and the identification-categorization relationship. _Journal of Experimental Psychology: General_, _115_(1), 39–57.

Nosofsky, R. M. (1992). Similarity scaling and cognitive process models. _Annual Review of Psychology_, _43_(1), 25–53.

Nosofsky, R. M., & Johansen, M. K. (2000). Exemplar-based accounts of “multiple-system” phenomena in perceptual categorization. _Psychonomic Bulletin & Review_, _7_(3), 375–402.

Nosofsky, R. M., Sanders, C. A., Zhu, X., & McDaniel, M. A. (2018). Model-guided search for optimal natural-science-category training exemplars: A work in progress. _Psychonomic Bulletin & Review_, _26_(1), 48–76. https://doi.org/10.3758/s13423-018-1508-8

Op de Beeck, H. P., Wagemans, J., & Vogels, R. (2008). The representation of perceived shape similarity and its role for category learning in monkeys: A modeling study. _Vision Research_, _48_(4), 598–610. https://doi.org/10.1016/j.visres.2007.11.019

Palmeri, T. J. (1997). Exemplar Similarity and the Development of Automaticity. _Journal of Experimental Psychology: Human Learning and Memory_, _23_(2), 324–354.

Perry, L. K., Samuelson, L. K., Malloy, L. M., & Schiffer, R. N. (2010). Learn Locally, Think Globally: Exemplar Variability Supports Higher-Order Generalization and Word Learning. _Psychological Science_, _21_(12), 1894–1902. https://doi.org/10.1177/0956797610389189

Pigott, R. E., & Shapiro, D. C. (1984). Motor Schema: The Structure of the Variability Session. _Research Quarterly for Exercise and Sport_, _55_(1), 41–45. https://doi.org/10.1080/02701367.1984.10605353

Poldrack, R. A., Selco, S. L., Field, J. E., & Cohen, N. J. (1999). The relationship between skill learning and repetition priming: Experimental and computational analyses. _Journal of Experimental Psychology: Learning, Memory, and Cognition_, _25_(1), 208–235. https://doi.org/10.1037/0278-7393.25.1.208

Posner, M. I., & Keele, S. W. (1968). On the genesis of abstract ideas. _Journal of Experimental Psychology_, _77_(3), 353–363.

R Core Team. (2020). _R: A Language and Environment for Statistical Computing_. R: A Language and Environment for Statistical Computing. https://www.R-project.org/

Roark, C. L., Paulon, G., Sarkar, A., & Chandrasekaran, B. (2021). Comparing perceptual category learning across modalities in the same individuals. _Psychonomic Bulletin & Review_, _28_(3), 898–909. https://osf.io/htwdk/. https://doi.org/10.3758/s13423-021-01878-0

Roller, C. A., Cohen, H. S., Kimball, K. T., & Bloomberg, J. J. (2001). Variable practice with lenses improves visuo-motor plasticity. _Cognitive Brain Research_, _12_(2), 341–352. https://doi.org/10.1016/S0926-6410(01)00077-5

Rosenbaum, D. A., Carlson, R. A., & Gilmore, R. O. (2001). Acquisition of Intellectual and Perceptual-Motor Skills. _Annual Review of Psychology_, _52_(1), 453–470. https://doi.org/10.1146/annurev.psych.52.1.453

Rosenbaum, D. A., Loukopoulos, L. D., Meulenbroek, R. G., Vaughan, J., & Engelbrecht, S. E. (1995). Planning reaches by evaluating stored postures. _Psychological Review_, _102_(1), 28.

Sabah, K., Dolk, T., Meiran, N., & Dreisbach, G. (2019). When less is more: Costs and benefits of varied vs. fixed content and structure in short-term task switching training. _Psychological Research_, _83_(7), 1531–1542. https://doi.org/10.1007/s00426-018-1006-7

Sadakata, M., & McQueen, J. M. (2014). Individual aptitude in Mandarin lexical tone perception predicts effectiveness of high-variability training. _Frontiers in Psychology_, _5_, 1318. https://doi.org/10.3389/fpsyg.2014.01318

Sakamoto, Y., Love, B. C., & Jones, M. (2006). Tracking Variability in Learning: Contrasting Statistical and Similarity-Based Accounts. _Proceedings of the 28th Annual Conference of the Cognitive Science Society. Vancouver, Canada: Cognitive Science Society_.

Schmidt, R. A. (1975). A schema theory of discrete motor skill learning. _Psychological Review_, _82_(4), 225–260. https://doi.org/10.1037/h0076770

Seow, R. Y. T., Betts, S., & Anderson, J. R. (2019). Transfer effects of varied practice and adaptation to changes in complex skill acquisition. _Proceedings of the 17th International Conference on Cognitive Modelling_, 222–227.

Shepard, R. N. (1987). Toward a universal law of generalization for psychological science. _Science_, _237_(4820), 1317–1323.

Sinkeviciute, R., Brown, H., Brekelmans, G., & Wonnacott, E. (2019). The role of input variability and learner age in second language vocabulary learning. _Studies in Second Language Acquisition_, _41_(04), 795–820. https://doi.org/10.1017/S0272263119000263

Soderstrom, N. C., & Bjork, R. A. (2015). Learning versus performance: An integrative review. _Perspectives on Psychological Science_, _10_(2), 176–199.

Taylor, J., & Ivry, R. (2013). Context-dependent generalization. _Frontiers in Human Neuroscience_, _7_, 171. https://doi.org/10.3389/fnhum.2013.00171

Thoroughman, K. A., & Taylor, J. A. (2005). Rapid Reshaping of Human Motor Generalization. _Journal of Neuroscience_, _25_(39), 8948–8953. https://doi.org/10.1523/JNEUROSCI.1771-05.2005

Twomey, K. E., Ma, L., & Westermann, G. (2018). All the Right Noises: Background Variability Helps Early Word Learning. _Cognitive Science_, _42_(S2), 413–438. https://doi.org/10.1111/cogs.12539

van Dam, L. C. J., & Ernst, M. O. (2015). Mapping Shape to Visuomotor Mapping: Learning and Generalisation of Sensorimotor Behaviour Based on Contextual Information. _PLOS Computational Biology_, _11_(3), e1004172. https://doi.org/10.1371/journal.pcbi.1004172

Van Rossum, J. H. A. (1990). Schmidt’s schema theory: The empirical base of the variability of practice hypothesis. _Human Movement Science_, _9_(3–5), 387–435. https://doi.org/10.1016/0167-9457(90)90010-B

Vigo, R., Doan, K.-M. C., Doan, C. A., & Pinegar, S. (2018). On the learning difficulty of visual and auditory modal concepts: Evidence for a single processing system. _Cognitive Processing_, _19_(1), 1–16. https://doi.org/10.1007/s10339-017-0840-7

Wall, L., Gunawan, D., Brown, S. D., Tran, M.-N., Kohn, R., & Hawkins, G. E. (2021). Identifying relationships between cognitive processes across tasks, contexts, and time. _Behavior Research Methods_, _53_(1), 78–95. https://doi.org/10.3758/s13428-020-01405-4

Wifall, T., Buss, A. T., Farmer, T. A., Spencer, J. P., & Hazeltine, E. (2017). Reaching into response selection: Stimulus and response similarity influence central operations. _Journal of Experimental Psychology: Human Perception and Performance_, _43_(3), 555–568. https://doi.org/10.1037/xhp0000301

Willey, C. R., & Liu, Z. (2018). Long-term motor learning: Effects of varied and specific practice. _Vision Research_, _152_, 10–16. https://doi.org/10.1016/j.visres.2017.03.012

Wonnacott, E., Boyd, J. K., Thomson, J., & Goldberg, A. E. (2012). Input effects on the acquisition of a novel phrasal construction in 5year olds. _Journal of Memory and Language_, _66_(3), 458–478. https://doi.org/10.1016/j.jml.2011.11.004

Wrisberg, C. A., Winter, T. P., & Kuhlman, J. S. (1987). The Variability of Practice Hypothesis: Further Tests and Methodological Discussion. _Research Quarterly for Exercise and Sport_, _58_(4), 369–374. https://doi.org/10.1080/02701367.1987.10608114

Wu, C. M., Schulz, E., Garvert, M. M., Meder, B., & Schuck, N. W. (2020). Similarities and differences in spatial and non-spatial cognitive maps. _PLOS Computational Biology_, _16_(9). https://github.com/charleywu/cognitivemaps. https://doi.org/10.1101/2020.01.21.914556

Wulf, G. (1991). The effect of type of practice on motor learning in children. _Applied Cognitive Psychology_, _5_(2), 123–134. https://doi.org/10.1002/acp.2350050206

Yang, J., Yan, F.-F., Chen, L., Xi, J., Fan, S., Zhang, P., Lu, Z.-L., & Huang, C.-B. (2020). General learning ability in perceptual learning. _Proceedings of the National Academy of Sciences_, _117_(32), 19092–19100. https://doi.org/10.1073/pnas.2002903117

Zaman, J., Chalkia, A., Zenses, A.-K., Bilgin, A. S., Beckers, T., Vervliet, B., & Boddez, Y. (2021). Perceptual variability: Implications for learning and generalization. _Psychonomic Bulletin & Review_, _28_(1), 1–19. https://doi.org/10.3758/s13423-020-01780-1

### 2023-10-07 Introduction.qmd
initial commit again

---
title: Introduction
---

# Variability and Generalization

## Introduction

The factors that influence how learning generalizes are of great interest to those seeking to understanding the nature of the human learning system, and to those attempting to improve the efficacy of teaching and training programs. Such factors are likely legion, but the present effort will limit itself to two characteristics of the learning input - variability and frequency skew. Variability manipulations control either the number of unique instances learners are trained on, or how dispersed or spread out the instances are. Much less research has examined skew manipulations, which hold the number of instances constant, and instead vary the relative frequencies with which the training items occur. Both factors have been linked to generalization in past research. The present essay with will provide an extensive review and discussion of both topics. The review of the expansive literature on the effect of attempts to include at least some examples from each of the many relevant domains, but much of the work is biased towards the background of the author. Conversely, the literature on skew proved to be far sparser than anticipated, as well as being overrepresented in a region of the language learning literature that is somewhat distant from more conventional cognitive psychology.

## The study of variability

In their most generic form, studies assessing the "benefits of variability" hypothesis assign participants to either a constant or varied group for the training stage of the experiment. Then, subjects in both groups complete an identical testing stage which often consists items/conditions seen during training, and novel items/conditions. If the varied group performs better in the testing stage, this is taken for evidence of the benefits of variability hypothesis. Even in this relatively simple between-groups design, researchers must make a number of crucial decisions which will now be highlighted.

1)  What is varied. Unless the task is unidimensional, there will often be many variables that could be varied or held fixed, and the experiment will need to decide the dimension(s) along which the variation will occur. For instance, in a projectile throwing accuracy task -- researchers might vary the distance from the target, the size of the target, the weight of the projectile. They might also vary a contextual variable not directly relevant to the task, but which will still be encoded by the subject on a trial by trial basis, e.g. the background color.

2)  The amount of variation, relative to the control condition. The simplest comparison would be to compare a constant group who trains with 1 example/condition, against a varied group that trains from 2 examples/conditions. However, it is not uncommon in the literature for the varied condition to train from 3 or 4 conditions. For example, Catalano and Kleiner train varied subjects from 4 different velocities in their coincident timing task, and Goode et al. (2008) have varied subjects' practice with 3 different variants (i.e. different letter scrambles of the same word) of an anagram for a given word, while their constant participants view the same variant 3 different times. Alternatively, rather than a constant vs. varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items (Nosofsky et al. 2018).

3)  Locations of the varied examples within the task-space. For tasks in which the stimuli or conditions exist in some continuous metric space, the experimenter must decide whether the varied instances are relatively close together (e.g. throwing a ball from a distance of 4 feet and 5 feet), or far apart (throwing from 4 feet and 20 feet). Spreading the varied training items further apart may be beneficial in terms of providing a more representative sample of the task space to the learner, however large distances may also result in significant differences in difficulty between the training examples, which can be a common confound in variability studies.

4)  The proximity of the testing conditions to the training conditions of the varied and constant groups. Intuitively, the fairest form of comparison is to include testing conditions that are of an equivalent distance from both the varied and constant groups. However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions (Goode et al., 2008; Kerr & Booth, 1978).

Variability Literature Review

An early and influential work on the influence of variability on category learning is that of Posner and Keele (1968). In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g. a low variability condition), or spread further away from the prototype (the varied-training group). It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were. The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group. The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema. The Posner and Keele study have been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training. It's also referenced as a key influence in the development of Schema Theory of Motor Learning (Richard A. Schmidt, 1975), which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning. However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning. The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later (Palmeri & Nosofsky, 2001), when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis. Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances. One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.

## Motor skill learning

Training variation has also been shown to promote transfer in motor learning. Much of this research has been influenced by the work of Schmidt (1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced. Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw. When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement. Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves). Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group. Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group. For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations. Both groups are then tested from novel locations.

One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of Kerr and Booth (1978). Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task. The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet. Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial. 12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants. Participants were also blind folded for testing and did not receive trial by trial feedback in this stage. However, at the halfway point of the testing stage they were allowed to see the landing location of the 4 beanbags they had thrown, and then completed the final 4 testing throws. In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children. Although this design does not directly assess the hypothesis of varied training producing superior generalization to constant training (since the constant group is not tested from a novel position), it nevertheless offers a compelling example of the merits of varied practice.

On occasion the Kerr and Booth design may be nested within a larger experimental design. One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue (Wrisberg et al., 1987). This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g. the design of Kerr and Booth. However, in this case the varied group did not outperform the constant group. A more recent study attempting a slightly more direct replication of the original Kerr & Booth study (Willey & Liu, 2018), having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet). However this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks). Like Wrisberg et al. (1987), this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.

Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket (Green et al., 1995). Varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket. One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group. Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths. Of course, this finding is less surprising than that of Kerr & Booth, given that varied subjects did have some prior exposure to the constant groups condition. This highlights an issue rarely discussed in the literature, of how much practice from an additional position might be necessary to induce benefits. Experimenters almost uniformly have varied participants train with an equivalent number of trials from each of their conditions

One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation (Goode et al., 2008). All participants trained to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials. Although subjects in all conditions were exposed to the same 40 unique words (i.e. the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training). Two different constant groups were used. Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g. LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group. At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e. the particular permutation of letters) which the varied group had not explicitly seen. However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group. This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters. This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.

Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance. However, despite its appeal this particular contrast is relatively uncommon in the literature. It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky. A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters (Catalano & Kleiner, 1984; Chua et al., 2019; McCracken & Stelmach, 1977; Moxley, 1979; Newell & Shapiro, 1976), or for a single constant group to train from just one of the conditions experienced by the varied participants (Pigott & Shapiro, 1984; Roller et al., 2001; Wrisberg & McLean, 1984; Wrisberg & Mead, 1981). A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition (Wrisberg et al., 1987; Wulf, 1991).

Of particular relevant to the current essay is the early work of Catalano and Kleiner (1984), as theirs was one of the earliest studies to investigate the influence of varied vs. constant training on multiple testing locations of graded distance from the training condition. Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb. The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities. Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph. As is often the case, the varied group performed worse during the training phase. In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.

In the category learning literature, the constant vs. varied comparison is much less suitable. Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars. Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns (Homa & Vosburgh, 1976; Posner & Keele, 1968), where more varied or distorted training examples were often shown to produce superior generalize when categorizing novel exemplars. More recently, researchers have also begun to utilize more realistic stimuli in their experiments. Wahlheim et al. (2012) conducted one such study. In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars. Across four different experiments, which were conducted to address on unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e. higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on. A variability advantage was also found in the relatively complex domain of rock categorization (Nosofsky et al., 2018). For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation). The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions. Moreover, the pattern of results in this study could be nicely accounted for by an extended version of the Generalized Context Model.

The studies described thus far have studied the benefits of variability by exposing participants to a greater or lesser number of distinct examples during training. A distinct sub-literature within the category learning domain has focused much less on benefits derived from varied training, instead emphasizing how increased variability during the learning of a novel category influences how far the category boundary will then be generalized. The general approach is to train participants on examples from two categories, with the examples from one of the categories being more dispersed than the other. Participants are then tested with novel items located within ambiguous regions of the task space which allow the experimenters to assess whether the difference in variability influences how far participants generalize the category boundaries.

Cohen et al. (2001) trained subjects on two categories, one with much more variability than the other. In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another. In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart. Participants were tested on an ambiguous novel instance that was located in between the two trained categories. Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation. Moreover, this effect was at odds of the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.

Further observations consonant with the results of Cohen et al. (2001) have since been observed in numerous investigations (Hahn et al., 2005; Hsu & Grifﬁths, 2010; Perlman et al., 2012; Sakamoto et al., 2008). The results of Sakamoto et al. (2008) are noteworthy. They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability. In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial. They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.

The study by Hahn et al. (2005), is also of particular interest to the present discussion. Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories. During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories. The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category. Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category. Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do. The authors then used the standard GCM framework to compare a variety of similarity-based models to account for their results. Of particular interest are their evaluations of a category response bias parameter, and a similarity scaling parameter. A model fit improvement when the response bias parameter is allowed to vary between the high-variability and low-variability trained groups is taken to suggest a simple bias for responding with one of the trained categories over the other. Alternatively, an improvement in fit due to a separate similarity scaling parameter may reflect the groups being differentially sensitive to the distances between stimuli. No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately. The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items -- accounting for their extended generalization gradients, but also for their poor performance in a recognition condition. Additional model comparisons suggested that this similarity rescaling applied across the entire stimulus space, rather than to the high variability category in particular.

Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts (Braithwaite & Goldstone, 2015). This study trained participants on problems involving the concept of sampling with replacement (SWR). Training consisted of examples that were either highly similar in their semantic context (e.g. all involving people selecting objects) or in which the surface features were varied between examples (e.g. people choosing objects AND objects selected in a sequence). The experimenters also surveyed how much prior knowledge each participant had with SWR. They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples. The authors hypothesized that in order to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training. To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples. Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.

Variability has also been examined within the realm of language learning. A particularly impressive study is that of Perry et al. (2010). In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting. All infants were introduced to three novel objects of the same category, with participants in the tight condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category. Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset. Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing. By the end of the nine weeks, all of the infants had learned the labels of the training objects. The varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category, a pattern consistent with much of the existing literature. More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids. The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.

## Some complications to the influence of variability

### Sequence Effects

A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another. The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing). Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis it was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter (J. B. Shea & Morgan, 1979). In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns. A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training. Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random. There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence. However, the main finding of interest was the advantage random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.

Prior to the influential Shea and Morgan (1979) study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification. It was later observed (Lee et al., 1985) that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules. The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts. One such account, the elaborative processing account (J. B. Shea & Zimny, 1983), draws on the earlier work of Battig (Battig, 1966) and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing. Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training (J. B. Shea & Zimny, 1983), and by manipulating whether subjects are able to perform comparisons during training (Wright et al., 1992). An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory (Lee & Magill, 1985). Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context. A much more recent study (Chua et al., 2019), replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting). The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage. In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g. attending to the target distance), and constant or blocked subjects reported more internal attention (e.g. posture or hand position). The authors argue that the benefits of varied/random training may be mediated by changes in attentional focus, however the claims made in the paper seem to go far beyond what can be justified by the analyses reported -- e.g. the increased external focus could be a simple byproduct of varied training. A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.

Other task and participant effects

Of course, the effects of varied training, and different training sequences, are likely to be far more complex than simply more varied training being better than less, or random training being better than blocked. Null effects of both manipulations have been reported (Magill & Hall, 1990; Van Rossum, 1990 for reviews), and a variety of moderators have emerged. In one of the earlier examples of the complex relationship between study sequence and learning (Del Rey et al., 1982), experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities with either blocked, or random training sequence conditions - resulting in 6 experimental conditions: (athlete vs. non-athlete) x (constant vs. blocked vs. random training). Athlete participants had superior performance during training, regardless of sequence condition, and training performance was superior for all subjects in the constant group, followed by blocked training in the middle, and then random training resulting in the worst training performance. Of greater interest is the pattern of testing results for novel transfer conditions. Among the athlete-participants, transfer performance was best for those who received random training, followed by blocked, and then constant training. Non-athletes showed an almost opposite pattern, with superior performance for those who had constant training. A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training (Guadagnoli et al., 1999). More recently, the same pattern was observed in the concept learning literature (Braithwaite & Goldstone, 2015, expt 1). This study trained participants on a mathematical concept and found that participants who self-reported some prior experience with the concept improved more from pre-test to post-test after training with varied examples, while participants who reported no prior experience showed greater gains following training with highly similar examples.

In addition to the influence of prior experiences described above, ample evidence also suggests that numerous aspects of the experiment may also interact with the influence of variation. One important study examined the impact of the amount of training completed in a force production task (C. H. Shea et al., 1990). This study employed a typical blocked vs. random training procedure, but with the additional manipulation of separate groups receiving 50, 200, or 400 total training trials. For the group that received only 50 training trials retention was best when training had been blocked. However, for the conditions that received 200 or 400 training trials the pattern was reversed, with random training resulting in superior retention than blocked training. These results were taken to suggest that the benefits of randomization may take time to emerge. Another experimental factor shown to interact with training sequence is the complexity of the training task (Albaret & Thon, 1998). In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of 2, 3 or 4 components). On a transfer task 48 hours after the completion of training, only participants trained at the lower levels of task complexity (2 or 3 components) showed superior performance to the blocked condition. The authors suggest that the benefits of random sequencing, thought to arise from more elaborate cognitive processing, or the necessity of continually recalling task information from long term into short term memory, are more likely to be obscured as the complexity of the task forces the blocked participants to also engage in such processes.

A final important influence of particular relevance to the practice-sequence literature concerns the exact structure of "random" sequencing. Although the term random is commonly used for convenience, experimenters do not typically leave the order of training entirely up to chance. Rather, the training sequence is often constrained such that each condition must occur a minimum number of times in each quartile of the training phase, thus resulting in an even distribution the conditions throughout training. While the assurance of the conditions being evenly spread throughout training is consistent across studies, other aspects of the sequence structure are a bit more idiosyncratic. Some researchers report setting a maximum number of consecutive repetitions, e.g. no more than 2 consecutive trials of the same condition (Del Rey et al., 1982; J. B. Shea & Morgan, 1979), or structure the random trials such that the same condition never occurs consecutively (Wulf, 1991). Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition (Chua et al., 2019; Willey & Liu, 2018; Wrisberg et al., 1987), resulting in much more switches than would arise if training was perfectly blocked. The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition. Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing (Pigott & Shapiro, 1984), and basketball shot training study (Landin & Hebert, 1997), and in a replication plus extension of the seminal Shea and Morgan (1979) study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition. Consequences on different study schedules have also been repeatedly observed in the category learning literature (Carvalho & Goldstone, 2014, 2017). This line of research has revealed that the effects of blocking vs. interleaving can depend on the structure of the category being learned, and also that the different schedules can result in the participants requiring different representations. A fruitful line of inquiry in the motor skill learning literature may be to attempt to identify whether structural aspects of the motor task interact with different training sequences in a reliable manner.

Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed). Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty(Bjork & Bjork, 2011; R.A. Schmidt & Bjork, 1992), or optimal challenge points (Guadagnoli & Lee, 2004). They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage. This observation is then used to justify the idea that the most enduring and generalizable learning occurs by training at an optimal level of training difficulty, with difficulty being some function of the experience of the learner, and the cognitive or visuomotor processing demands of the task. It then follows that the factors that tend to make training more difficult (i.e. increased variability or randomization), are more likely to be beneficial when the learner has some experience, or when the processing demands of the task are not too extreme (which may only occur after some experience with the task). Such frameworks may be helpful heuristics in some cases, but they also seem to be overly flexible such that any null result of some intervention might be accounted for by a suboptimal amount of training trials, or by suggesting the training task was too difficult. The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.

### 2023-10-09 IGAS.qmd
update citations

@@
   eval: false 
+editor: 
+  markdown: 
+    wrap: 72
 ---
 
-[Pdf of the journal article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
+[Pdf of the journal
+article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
+[Link to online version of journal
+article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
 
@@
 
-Exposing learners to variability during training has been demonstrated to
-improve performance in subsequent transfer testing. Such variability benefits
-are often accounted for by assuming that learners are developing some general
-task schema or structure. However much of this research has neglected to account
-for differences in similarity between varied and constant training conditions.
-In a between-groups manipulation, we trained participants on a simple projectile
-launching task, with either varied or constant conditions. We replicate previous
+Exposing learners to variability during training has been demonstrated
+to improve performance in subsequent transfer testing. Such variability
+benefits are often accounted for by assuming that learners are
+developing some general task schema or structure. However much of this
+research has neglected to account for differences in similarity between
+varied and constant training conditions. In a between-groups
+manipulation, we trained participants on a simple projectile launching
+task, with either varied or constant conditions. We replicate previous
 findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to account
-for the benefits of variation, but, if the model is adjusted to assume that
-varied learners are tuned towards a broader generalization gradient, then a
-similarity-based model is sufficient to explain the observed benefits of
-variation. Our results therefore suggest that some variability benefits can be
-accommodated within instance-based models without positing the learning of some
-schemata or structure.
+Furthermore, we show that a standard similarity model is insufficient to
+account for the benefits of variation, but, if the model is adjusted to
+assume that varied learners are tuned towards a broader generalization
+gradient, then a similarity-based model is sufficient to explain the
+observed benefits of variation. Our results therefore suggest that some
+variability benefits can be accommodated within instance-based models
+without positing the learning of some schemata or structure.
 
@@
 
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions  (Barnett & Ceci, 2002; Detterman, 1993).
-Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
-The factor of interest to the present investigation is variation during training.
-Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
-We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
-We first review the relevant concepts and literature.
+The past century of research on human learning has produced ample
+evidence that although learners can improve at almost any task, such
+improvements are often specific to the trained task, with unreliable or
+even nonexistent transfer to novel tasks or conditions
+[@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993]. Such
+transfer challenges are of noteworthy practical relevance, given that
+educators, trainers, and rehabilitators typically intend for their
+students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that
+influence transfer, and to develop cognitive models that can predict
+when transfer is likely to occur. The factor of interest to the present
+investigation is variation during training. Our experiments add to the
+longstanding empirical investigation of the controversial relationship
+between training variation, and subsequent transfer. We also offer a
+novel explanation for such results in the form of an instance-based
+model that accounts for the benefits of variation in simple terms of
+psychological similarity. We first review the relevant concepts and
+literature.
 
@@
 
-Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances.
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar (Posner & Keele, 1968).
-Prototype models were later challenged by the success of instance-based or exemplar models – which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype (Estes, 1994; Hintzman, 1984; Medin & Schaffer, 1978; Nosofsky, 1986).
-Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli.
-As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
-In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
-Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations (Palmeri, 1997).
-That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning (Cohen & Rosenbaum, 2004; Crump & Logan, 2010; Meigh et al., 2018; Poldrack et al., 1999; Wifall et al., 2017) .
-Crump and Logan (2010) trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
-Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
+Notions of similarity have long played a central role in many prominent
+models of generalization of learning, as well as in the longstanding
+theoretical issue of whether learners abstract an aggregate, summary
+representation, or if they simply store individual instances. Early
+models of learning often assumed that discrete experiences with some
+task or category were not stored individually in memory, but instead
+promoted the formation of a summary representation, often referred to as
+a prototype or schema, and that exposure to novel examples would then
+prompt the retrieval of whichever preexisting prototype was most similar
+@posnerGenesisAbstractIdeas1968 [Posner & Keele, 1968]. Prototype
+models were later challenged by the success of instance-based or
+exemplar models -- which were shown to provide an account of
+generalization as good or better than prototype models, with the
+advantage of not assuming the explicit construction of an internal
+prototype @estesArrayModelsCategory1986;
+@hintzmanMINERVASimulationModel1984;
+@medinContextTheoryClassification1978;
+@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
+Instance-based models assume that learners encode each experience with a
+task as a separate instance/exemplar/trace, and that each encoded trace
+is in turn compared against novel stimuli. As the number of stored
+instances increases, so does the likelihood that some previously stored
+instance will be retrieved to aid in the performance of a novel task.
+Stored instances are retrieved in the context of novel stimuli or tasks
+if they are sufficiently similar, thus suggesting that the process of
+computing similarity is of central importance to generalization.
+
+Similarity, defined in this literature as a function of psychological
+distance between instances or categories, has provided a successful
+account of generalization across numerous tasks and domains. In an
+influential study demonstrating an ordinal similarity effect,
+experimenters employed a numerosity judgment task in which participants
+quickly report the number of dots flashed on a screen. Performance (in
+terms of response times to new patterns) on novel dot configurations
+varied as an inverse function of their similarity to previously trained
+dot configurations @palmeriExemplarSimilarityDevelopment1997. That is, performance was better on
+novel configurations moderately similar to trained configurations than
+to configurations with low-similarity, and also better on low-similarity
+configurations than to even less similar, unrelated configurations.
+Instance-based approaches have had some success accounting for
+performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999]; @wifallPerceptualSimilarityAffects.@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters
+composing the training words to a pre-specified letter set. Following
+training, typing speed was tested on previously experienced words
+composed of previously experienced letters; novel words composed of
+letters from the trained letter set; and novel words composed of letters
+from an untrained letter set. Consistent with an instance-based account,
+transfer performance was graded such that participants were fastest at
+typing the words they had previously trained on, followed by novel words
+composed of letters they had trained on, and slowest performance for new
+words composed of untrained letters.
 
@@
 
-While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work – variability of training examples.
-
-Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions (Czyż, 2021; Soderstrom & Bjork, 2015).
-Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli (Hahn et al., 2005; Maddox & Filoteo, 2011; Posner & Keele, 1968), complex categorization (Nosofsky et al., 2018), language learning (Jones & Brandt, 2020; Perry et al., 2010; Twomey et al., 2018; Wonnacott et al., 2012) anagram completion (Goode et al., 2008), trajectory extrapolation (Fulvio et al., 2014), task switching (Sabah et al., 2019), associative learning (Lee et al., 2019), visual search (George & Egner, 2021; Gonzalez & Madhavan, 2011; Kelley & Yantis, 2009), voice identity learning (Lavan et al., 2019), simple motor learning (Braun et al., 2009; Kerr & Booth, 1978; Roller et al., 2001; Willey & Liu, 2018), sports training (Green et al., 1995; North et al., 2019), and training on a complex video game (Seow et al., 2019).
-
-Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
-Much of this research has been influenced by the work of Schmidt (1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
-throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies (Catalano & Kleiner, 1984; Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth, 1978; Wulf, 1991), and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation (DeLosh et al., 1997; Sinkeviciute et al., 2019; Wrisberg et al., 1987), and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials,  or the type of transfer being measured (Berniker et al., 2014; Braithwaite & Goldstone, 2015; Hahn et al., 2005; Lavan et al., 2019; North et al., 2019; Sadakata & McQueen, 2014; Zaman et al., 2021).
+While similarity-based models account for transfer by the degree of
+similarity between previous and new experiences, a largely separate body
+of research has focused on improving transfer by manipulating
+characteristics of the initial training stage. Such characteristics have
+included training difficulty, spacing, temporal order, feedback
+schedules, and the primary focus of the current work -- variability of
+training examples.
+
+Research on the effects of varied training typically compares
+participants trained under constant, or minimal variability conditions
+to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015]. Varied training has been shown to influence
+learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968],
+complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory
+extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice
+identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
+sports training  [@greenPracticeVariabilityTransfer1995; @northEffectConsistentVaried2019], and training
+on a complex video game [@seowTransferEffectsVaried2019].
+
+Training variation has received a particularly large amount of attention
+within the domain of visuomotor skill learning. Much of this research
+has been influenced by the work of Schmidt (1975), who proposed a
+schema-based account of motor learning as an attempt to address the
+longstanding problem of how novel movements are produced. According to
+Schema Theory, learners possess general motor programs for classes of
+movements (e.g. throwing a ball with an underhand movement), as well as
+schema rules that determine how a motor program is parameterized or
+scaled for a particular movement. Schema theory predicts that varied
+training results in the formation of a more general schema-rule, which
+can allow for transfer to novel movements within a given movement class.
+Experiments that test this hypothesis are often designed to compare the
+transfer performance of a constant-trained group against that of a
+varied-trained group. Both groups train on the same task, but the varied
+group practices from multiple levels of a task-relevant dimension that
+remains invariant for the constant group. For example, investigators
+might train two groups of participants to throw a projectile at a
+target, with a constant group that throws from a single location, and a
+varied group that throws from multiple locations. Both groups are then
+tested from novel locations. Empirically observed benefits of the
+varied-trained group are then attributed to the variation they received
+during training, a finding observed in numerous studies (Catalano &
+Kleiner, 1984; Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth,
+1978; Wulf, 1991), and the benefits of this variation are typically
+thought to be mediated by the development of a more general schema for
+the throwing motion.
+
+Of course, the relationship between training variability and transfer is
+unlikely to be a simple function wherein increased variation is always
+beneficial. Numerous studies have found null, or in some cases negative
+effects of training variation (DeLosh et al., 1997; Sinkeviciute et al.,
+2019; Wrisberg et al., 1987), and many more have suggested that the
+benefits of variability may depend on additional factors such as prior
+task experience, the order of training trials, or the type of transfer
+being measured (Berniker et al., 2014; Braithwaite & Goldstone, 2015;
+Hahn et al., 2005; Lavan et al., 2019; North et al., 2019; Sadakata &
+McQueen, 2014; Zaman et al., 2021).
 
@@
 
-Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis (Newell, 2003; Van Rossum, 1990).
-Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g.
-projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
-more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance (Ennis et al., 1988; Ghahramani et al., 1996; Logan, 1988; Nosofsky, 1992; Shepard, 1987; Thoroughman & Taylor, 2005), it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
-Figure 1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
+Although the benefits of training variation in visuomotor skill learning
+have been observed many times, null findings have also been repeatedly
+found, leading some researchers to question the veracity of the
+variability of practice hypothesis (Newell, 2003; Van Rossum, 1990).
+Critics have also pointed out that investigations of the effects of
+training variability, of the sort described above, often fail to control
+for the effect of similarity between training and testing conditions.
+For training tasks in which participants have numerous degrees of
+freedom (e.g. projectile throwing tasks where participants control the x
+and y velocity of the projectile), varied groups are likely to
+experience a wider range of the task space over the course of their
+training (e.g. more unique combinations of x and y velocities).
+Experimenters may attempt to account for this possibility by ensuring
+that the training location(s) of the varied and constant groups are an
+equal distance away from the eventual transfer locations, such that
+their training throws are, on average, equally similar to throws that
+would lead to good performance at the transfer locations. However, even
+this level of experimental control may still be insufficient to rule out
+the effect of similarity on transfer. Given that psychological
+similarity is typically best described as either a Gaussian or
+exponentially decaying function of psychological distance (Ennis et al.,
+1988; Ghahramani et al., 1996; Logan, 1988; Nosofsky, 1992; Shepard,
+1987; Thoroughman & Taylor, 2005), it is plausible that a subset of the
+most similar training instances could have a disproportionate impact on
+generalization to transfer conditions, even if the average distance
+between training and transfer conditions is identical between groups.
+Figure 1 demonstrates the consequences of a generalization gradient that
+drops off as a Gaussian function of distance from training, as compared
+to a linear drop-off.
 
@@
 
-In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations (Chamberlin & Magill, 1992).
-Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains (Jamieson et al., 2022; Logan, 2002).
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components (Crump & Logan, 2010; Gandolfo et al., 1996; Meigh et al., 2018; Rosenbaum et al., 1995; van Dam & Ernst, 2015).
-However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
-We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
-We then examine the extent to which this advantage can be explained by an instance-based similarity model.
+In addition to largely overlooking the potential for non-linear
+generalization to confound interpretations of training manipulations,
+the visuomotor skill learning literature also rarely considers
+alternatives to schema representations (Chamberlin & Magill, 1992).
+Although schema-theory remains influential within certain literatures,
+instance or exemplar-based models have accounted for human behavior
+across myriad domains (Jamieson et al., 2022; Logan, 2002). As mentioned
+above, instance based accounts have been shown to perform well on a
+variety of different tasks with motoric components (Crump & Logan, 2010;
+Gandolfo et al., 1996; Meigh et al., 2018; Rosenbaum et al., 1995; van
+Dam & Ernst, 2015). However, such accounts have received little
+attention within the subdomain of visuomotor skill learning focused on
+the benefits of varied training.
+
+The present work examines whether the commonly observed benefits of
+varied training can be accounted for by between-group differences in
+similarity between training and testing throws. We first attempt to
+replicate previous work finding an advantage of varied training over
+constant training in a projectile launching task. We then examine the
+extent to which this advantage can be explained by an instance-based
+similarity model.
 
@@
 ### Sample Size Estimation
-To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task (Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth, 1978; Wulf, 1991).
-We then averaged effects across these studies, yielding a Cohens f =.43.
-The GPower 3.1 software package (Faul et al., 2009) was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
-All experiments reported in the present manuscript exceed this minimum number of participants per condition.
+
+To obtain an independent estimate of effect size, we identified previous
+investigations which included between-subjects contrasts of varied and
+constant conditions following training on an accuracy based projectile
+launching task (Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth,
+1978; Wulf, 1991). We then averaged effects across these studies,
+yielding a Cohens f =.43. The GPower 3.1 software package (Faul et al.,
+2009) was then used to determine that a power of 80% requires a sample
+size of at least 23 participants per condition. All experiments reported
+in the present manuscript exceed this minimum number of participants per
+condition.
 
 ### Participants
-Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18-22 years.
-A total of 110 Indiana University psychology students participated in Experiment 1.
-We subsequently excluded 34 participants poor performance at one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
-simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
-A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.
+
+Participants were recruited from an undergraduate population that is 63%
+female and consists almost entirely of individuals aged 18-22 years. A
+total of 110 Indiana University psychology students participated in
+Experiment 1. We subsequently excluded 34 participants poor performance
+at one of the dependent measures of the task (2.5-3 standard deviations
+worse than the median subject at the task) or for displaying a pattern
+of responses that was clearly indicative of a lack of engagement with
+the task (e.g. simply dropping the ball on each trial rather than
+throwing it at the target), or for reporting that they completed the
+experiment on a phone or tablet device, despite the instructions not to
+use one of these devices. A total of 74 participants were retained for
+the final analyses, 35 in the varied group and 39 in the constant group.
 
 ### Task
-The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library (de Leeuw, 2015).
-The stimuli, presented on a black background, consisted of a circular blue ball – controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
-Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
-Likewise, the distance between the center of the target, and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
-For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
-Methods Figure 2 displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square.
-Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor.
-Participants can then “wind up” the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
-If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target.
-If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
-If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier.
-If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square.
-If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+
+The experimental task was programmed in JavaScript, using packages from
+the Phaser physics engine (https://phaser.io) and the jsPsych library
+(de Leeuw, 2015). The stimuli, presented on a black background,
+consisted of a circular blue ball -- controlled by the participant via
+the mouse or trackpad cursor; a rectangular green target; a red
+rectangular barrier located between the ball and the target; and an
+orange square within which the participant could control the ball before
+releasing it in a throw towards the target. Because the task was
+administered online, the absolute distance between stimuli could vary
+depending on the size of the computer monitor being used, but the
+relative distance between the stimuli was held constant. Likewise, the
+distance between the center of the target, and the training and testing
+locations was scaled such that relative distances were preserved
+regardless of screen size. For the sake of brevity, subsequent mentions
+of this relative distance between stimuli, or the position where the
+ball landed in relation to the center of the target, will be referred to
+simply as distance. Methods Figure 2 displays the layout of the task, as
+it would appear to a participant at the start of a trial, with the ball
+appearing in the center of the orange square. Using a mouse or trackpad,
+participants click down on the ball to take control of the ball,
+connecting the movement of the ball to the movement of the cursor.
+Participants can then "wind up" the ball by dragging it (within the
+confines of the orange square) and then launch the ball by releasing the
+cursor. If the ball does not land on the target, participants are
+presented with feedback in red text at the top right of the screen, on
+how many units away they were from the center of the target. If the ball
+was thrown outside of the boundary of the screen participants are given
+feedback as to how far away from the target center the ball would have
+been if it had continued its trajectory. If the ball strikes the barrier
+(from the side or by landing on top), feedback is presented telling
+participants to avoid hitting the barrier. If participants drag the ball
+outside of the orange square before releasing it, the trial terminates,
+and they are reminded to release the ball within the orange square. If
+the ball lands on the target, feedback is presented in green text,
+confirming that the target was hit, and presenting additional feedback
+on how many units away the ball was from the exact center of the target.
+
+[Link to abbrevaited example of
+task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
 
@@
 
-To prepare the data, we first removed trials that were not easily interpretable as performance indicators in our task.
-Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier.
-The primary measure of performance used in all analyses was the absolute distance away from the center of the target.
-The absolute distance was calculated on every trial, and then averaged within each subject to yield a single performance score, for each position.
-A consistent pattern across training and testing phases in both experiments was for participants to perform worse from throwing positions further away from the target – a pattern which we refer to as the difficulty of the positions.
-However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest.
-All data processing and statistical analyses were performed in R version 4.03 (R Core Team, 2020).
-ANOVAs for group comparisons were performed using the rstatix package (Kassambara, 2021).
+To prepare the data, we first removed trials that were not easily
+interpretable as performance indicators in our task. Removed trials
+included: 1) those in which participants dragged the ball outside of the
+orange starting box without releasing it, 2) trials in which
+participants clicked on the ball, and then immediately released it,
+causing the ball to drop straight down, 3) outlier trials in which the
+ball was thrown more than 2.5 standard deviations further than the
+average throw (calculated separately for each throwing position), and 4)
+trials in which the ball struck the barrier. The primary measure of
+performance used in all analyses was the absolute distance away from the
+center of the target. The absolute distance was calculated on every
+trial, and then averaged within each subject to yield a single
+performance score, for each position. A consistent pattern across
+training and testing phases in both experiments was for participants to
+perform worse from throwing positions further away from the target -- a
+pattern which we refer to as the difficulty of the positions. However,
+there were no interactions between throwing position and training
+conditions, allowing us to collapse across positions in cases where
+contrasts for specific positions were not of interest. All data
+processing and statistical analyses were performed in R version 4.03 (R
+Core Team, 2020). ANOVAs for group comparisons were performed using the
+rstatix package (Kassambara, 2021).
 
@@
 
-Figure 3 below shows aggregate training performance binned into three stages representing the beginning, middle, and end of the training phase.
-Because the two conditions trained from target distances that were not equally difficult, it was not possible to directly compare performance between conditions in the training phase.
-Our focus for the training data analysis was instead to establish that participants did improve their performance over the course of training, and to examine whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor.
-The analysis revealed a significant effect of training stage F(2,142)=62.4, p<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,  and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ < .01.
+Figure 3 below shows aggregate training performance binned into three
+stages representing the beginning, middle, and end of the training
+phase. Because the two conditions trained from target distances that
+were not equally difficult, it was not possible to directly compare
+performance between conditions in the training phase. Our focus for the
+training data analysis was instead to establish that participants did
+improve their performance over the course of training, and to examine
+whether there was any interaction between training stage and condition.
+Descriptive statistics for the intermittent testing phase are provided
+in the supplementary materials.
+
+We performed an ANOVA comparison with stage as a within-group factor and
+condition as between-group factor. The analysis revealed a significant
+effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
+such that performance improved over the course of training There was no
+significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
+and no significant interaction between condition and training stage,
+F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
 
@@
 ## Testing Phase
-In Experiment 1, a single constant-trained group was compared against a single varied-trained group.
-At the transfer phase, all participants were tested from 3 positions: 1) the positions(s) from their own training, 2) the training position(s) of the other group, and 3) a position novel to both groups.
-Overall, group performance was compared with a mixed type III ANOVA, with condition (varied vs.
-constant) as a between-subject factor and throwing location as a within-subject variable.
-The effect of throwing position was strong, F(3,213) = 56.12, p<.001, η2G = .23.
-The effect of training condition was significant F(1,71)=8.19, p<.01, η2G = .07.
-There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.
+
+In Experiment 1, a single constant-trained group was compared against a
+single varied-trained group. At the transfer phase, all participants
+were tested from 3 positions: 1) the positions(s) from their own
+training, 2) the training position(s) of the other group, and 3) a
+position novel to both groups. Overall, group performance was compared
+with a mixed type III ANOVA, with condition (varied vs. constant) as a
+between-subject factor and throwing location as a within-subject
+variable. The effect of throwing position was strong, F(3,213) = 56.12,
+p\<.001, η2G = .23. The effect of training condition was significant
+F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
+between group and position, F(3,213)=1.81, p=.15, η2G = .01.
 
@@
 
-In Experiment 1, we found that varied training resulted in superior testing performance than constant training, from both a position novel to both groups, and from the position at which the constant group was trained, which was novel to the varied condition.
-The superiority of varied training over constant training even at the constant training position is of particular note, given that testing at this position should have been highly similar for participants in the constant condition.
-It should also be noted, though, that testing at the constant trained position is not exactly identical to training from that position, given that the context of testing is different in several ways from that of training, such as the testing trials from the different positions being intermixed, as well as a simple change in context as a function of time.
-Such contextual differences will be further considered in the General Discussion.
-
-In addition to the variation of throwing position during training, the participants in the varied condition of Experiment 1 also received training practice from the closest/easiest position, as well as from the furthest/most difficult position that would later be encountered by all participants during testing.
-The varied condition also had the potential advantage of interpolating both of the novel positions from which they would later be tested.
-Experiment 2 thus sought to address these issues by comparing a varied condition to multiple constant conditions.
+In Experiment 1, we found that varied training resulted in superior
+testing performance than constant training, from both a position novel
+to both groups, and from the position at which the constant group was
+trained, which was novel to the varied condition. The superiority of
+varied training over constant training even at the constant training
+position is of particular note, given that testing at this position
+should have been highly similar for participants in the constant
+condition. It should also be noted, though, that testing at the constant
+trained position is not exactly identical to training from that
+position, given that the context of testing is different in several ways
+from that of training, such as the testing trials from the different
+positions being intermixed, as well as a simple change in context as a
+function of time. Such contextual differences will be further considered
+in the General Discussion.
+
+In addition to the variation of throwing position during training, the
+participants in the varied condition of Experiment 1 also received
+training practice from the closest/easiest position, as well as from the
+furthest/most difficult position that would later be encountered by all
+participants during testing. The varied condition also had the potential
+advantage of interpolating both of the novel positions from which they
+would later be tested. Experiment 2 thus sought to address these issues
+by comparing a varied condition to multiple constant conditions.
 
@@
 
-In Experiment 2, we sought to replicate our findings from Experiment 1 with a new sample of participants, while also addressing the possibility of the pattern of results in Experiment 1 being explained by some idiosyncrasy of the particular training location of the constant group relative to the varied group.
-To this end, Experiment 2 employed the same basic procedure as Experiment 1, but was designed with six separate constant groups each trained from one of six different locations (400, 500, 625, 675, 800, or 900), and a varied group trained from two locations (500 and 800).
-Participants in all seven groups were then tested from each of the 6 unique positions.
+In Experiment 2, we sought to replicate our findings from Experiment 1
+with a new sample of participants, while also addressing the possibility
+of the pattern of results in Experiment 1 being explained by some
+idiosyncrasy of the particular training location of the constant group
+relative to the varied group. To this end, Experiment 2 employed the
+same basic procedure as Experiment 1, but was designed with six separate
+constant groups each trained from one of six different locations (400,
+500, 625, 675, 800, or 900), and a varied group trained from two
+locations (500 and 800). Participants in all seven groups were then
+tested from each of the 6 unique positions.
 
@@
 ### Participants
-A total of 306 Indiana University psychology students participated in Experiment 2, which was also conducted online.
-As was the case in experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18–22-year-old individuals.
-Using the same procedure as experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task.
-A total of 208 participants were included in the final analyses with 31 in the varied group and 32, 28, 37, 25, 29, 26 participants in the constant groups training from location 400, 500, 625, 675, 800, and 900, respectively.
+
+A total of 306 Indiana University psychology students participated in
+Experiment 2, which was also conducted online. As was the case in
+experiment 1, the undergraduate population from which we recruited
+participants was 63% female and primarily composed of 18--22-year-old
+individuals. Using the same procedure as experiment 1, we excluded 98
+participants for exceptionally poor performance at one of the dependent
+measures of the task, or for displaying a pattern of responses
+indicative of a lack of engagement with the task. A total of 208
+participants were included in the final analyses with 31 in the varied
+group and 32, 28, 37, 25, 29, 26 participants in the constant groups
+training from location 400, 500, 625, 675, 800, and 900, respectively.
 All participants were compensated with course credit.
@@
 ### Task and Procedure
-The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target.
-Additionally, the intermittent testing trials featured in experiment 1 were not utilized in experiment 2, and all training and testing trials were presented with feedback.
-An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
+
+The task of Experiment 2 was identical to that of Experiment 1, in all
+but some minor adjustments to the height of the barrier, and the
+relative distance between the barrier and the target. Additionally, the
+intermittent testing trials featured in experiment 1 were not utilized
+in experiment 2, and all training and testing trials were presented with
+feedback. An abbreviated demo of the task used for Experiment 2 can be
+found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
 
 The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group.
-In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training.
-Each of the constant groups thus experience one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
+Participants completed 140 training trials, all of which were from the
+same position for the constant groups and split evenly (70 trials each -
+randomized) for the varied group. In the testing phase, participants
+completed 30 trials from each of the six locations that had been used
+separately across each of the constant groups during training. Each of
+the constant groups thus experience one trained location and five novel
+throwing locations in the testing phase, while the varied group
+experiences 2 previously trained, and 4 novel locations.
 
@@
 ### Data Processing and Statistical Packages
-After confirming that condition and throwing position did not have any significant interactions, we standardized performance within each position, and then average across position to yield a single performance measure per participant.
-This standardization did not influence our pattern of results.
-As in experiment 1, we performed type III ANOVA’s due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.
-The statistical software for the primary analyses was the same as for experiment 1.
-Individual learning rates in the testing phase, compared between groups in the supplementary analyses, were fit using the TEfit package in R (Cochrane, 2020).
+
+After confirming that condition and throwing position did not have any
+significant interactions, we standardized performance within each
+position, and then average across position to yield a single performance
+measure per participant. This standardization did not influence our
+pattern of results. As in experiment 1, we performed type III ANOVA's
+due to our unbalanced design, however the pattern of results presented
+below is not altered if type 1 or type III tests are used instead. The
+statistical software for the primary analyses was the same as for
+experiment 1. Individual learning rates in the testing phase, compared
+between groups in the supplementary analyses, were fit using the TEfit
+package in R (Cochrane, 2020).
 
 ### Training Phase
-The different training conditions trained from positions that were not equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is confirmation that some learning did occur.
-Figure 5 depicts the training performance of the varied group alongside that of the aggregate of the six constant groups (5a), and each of the 6 separate constant groups (5b).
-An ANOVA comparison with training stage (beginning, middle, end) as a within-group factor and group (the varied condition vs.
-the 6 constant conditions collapsed together) as a between-subject factor revealed no significant effect of group on training performance, F(1,206)=.55,p=.49, $\eta^{2}_G$ <.01, a significant effect of training stage F(2,412)=77.91, p<.001, $\eta^{2}_G$ =.05, and no significant interaction between group and training stage, F(2,412)=.489 p=.61, $\eta^{2}_G$ <.01.
-We also tested for a difference in training performance between the varied group and the two constant groups that trained matching throwing positions (i.e., the constant groups training from position 500, and position 800).
-The results of our ANOVA on this limited dataset mirrors that of the full-group analysis, with no significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ <.01, a significant effect of training stage F(2,172)=56.29, p<.001, $\eta^{2}_G$ =.11, and no significant interaction between group and training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ <.01.
+
+The different training conditions trained from positions that were not
+equivalently difficult and are thus not easily amenable to comparison.
+As previously stated, the primary interest of the training data is
+confirmation that some learning did occur. Figure 5 depicts the training
+performance of the varied group alongside that of the aggregate of the
+six constant groups (5a), and each of the 6 separate constant groups
+(5b). An ANOVA comparison with training stage (beginning, middle, end)
+as a within-group factor and group (the varied condition vs. the 6
+constant conditions collapsed together) as a between-subject factor
+revealed no significant effect of group on training performance,
+F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
+stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
+interaction between group and training stage, F(2,412)=.489 p=.61,
+$\eta^{2}_G$ \<.01. We also tested for a difference in training
+performance between the varied group and the two constant groups that
+trained matching throwing positions (i.e., the constant groups training
+from position 500, and position 800). The results of our ANOVA on this
+limited dataset mirrors that of the full-group analysis, with no
+significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
+significant effect of training stage F(2,172)=56.29, p\<.001,
+$\eta^{2}_G$ =.11, and no significant interaction between group and
+training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
 
@@
 ### Testing Phase
-In Experiment 2, a single varied condition (trained from two positions, 500 and 800), was compared against six separate constant groups (trained from a single position, 400, 500, 625, 675, 800 or 900).
-For the testing phase, all participants were tested from all six positions, four of which were novel for the varied condition, and five of which were novel for each of the constant groups.
-For a general comparison, we took the absolute deviations for each throwing position and computed standardized scores across all participants, and then averaged across throwing position.
-The six constant groups were then collapsed together allowing us to make a simple comparison between training conditions (constant vs.
-varied).
-A type III between-subjects ANOVA was performed, yielding a significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$ =.02.
-Descriptive statistics for each condition are shown in table 2.
-Figure 6A visualizes the consistent advantage of the varied condition over the constant groups across the testing positions.
-Figure 6b shows performance between the varied condition and the individual constant groups.
+
+In Experiment 2, a single varied condition (trained from two positions,
+500 and 800), was compared against six separate constant groups (trained
+from a single position, 400, 500, 625, 675, 800 or 900). For the testing
+phase, all participants were tested from all six positions, four of
+which were novel for the varied condition, and five of which were novel
+for each of the constant groups. For a general comparison, we took the
+absolute deviations for each throwing position and computed standardized
+scores across all participants, and then averaged across throwing
+position. The six constant groups were then collapsed together allowing
+us to make a simple comparison between training conditions (constant vs.
+varied). A type III between-subjects ANOVA was performed, yielding a
+significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
+=.02. Descriptive statistics for each condition are shown in table 2.
+Figure 6A visualizes the consistent advantage of the varied condition
+over the constant groups across the testing positions. Figure 6b shows
+performance between the varied condition and the individual constant
+groups.
 
@@
 
-Next, we compared the testing performance of constant and varied groups from only positions that participants had not encountered during training.
-Constant participants each had 5 novel positions, whereas varied participants tested from 4 novel positions (400,625,675,900).
-We first standardized performance within in each position, and then averaged across positions.
-Here again, we found a significant effect of condition (constant vs.
-varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ = .02 .
+Next, we compared the testing performance of constant and varied groups
+from only positions that participants had not encountered during
+training. Constant participants each had 5 novel positions, whereas
+varied participants tested from 4 novel positions (400,625,675,900). We
+first standardized performance within in each position, and then
+averaged across positions. Here again, we found a significant effect of
+condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
+.02 .
 
@@
 
-Finally, corresponding to the comparison of position 760 from experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group).
-Figure 7 displays the particular subset of comparisons utilized for this analysis.
-Again, we standardized performance within each position before performing the analyses on the aggregated data.
-In this case, the effect of condition did not reach statistical significance F(1,149)=3.14, p=.079, $\eta^{2}_G$ = .02.
-Table 4 provides descriptive statistics.
+Finally, corresponding to the comparison of position 760 from experiment
+1, we compared the test performance of the varied group against the
+constant group from only the positions that the constant groups trained.
+Such positions were novel to the varied group (thus this analysis
+omitted two constant groups that trained from positions 500 or 800 as
+those positions were not novel to the varied group). Figure 7 displays
+the particular subset of comparisons utilized for this analysis. Again,
+we standardized performance within each position before performing the
+analyses on the aggregated data. In this case, the effect of condition
+did not reach statistical significance F(1,149)=3.14, p=.079,
+$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
 
@@
 ## Discussion
-The results of experiment 2 largely conform to the findings of experiment 1.
-Participants in both varied and constant conditions improved at the task during the training phase.
-We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions (Catalano & Kleiner, 1984; Wrisberg et al., 1987), which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing (Soderstrom & Bjork, 2015).
-However our finding of no difference in training performance between constant and varied groups has been observed in previous work (Chua et al., 2019; Moxley, 1979; Pigott & Shapiro, 1984).
-
-In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions.
-The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt’s influential Schema Theory (Catalano & Kleiner, 1984; Chua et al., 2019; Goodwin et al., 1998; McCracken & Stelmach, 1977; Moxley, 1979; Newell & Shapiro, 1976; Pigott & Shapiro, 1984; Roller et al., 2001; Schmidt, 1975; Willey & Liu, 2018; Wrisberg et al., 1987; Wulf, 1991).
-We also join a much smaller set of research to observe this pattern in a computerized task (Seow et al., 2019).
-One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
-Although this pattern has been observed elsewhere in the literature (Goode et al., 2008; Kerr & Booth, 1978), the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
+
+The results of experiment 2 largely conform to the findings of
+experiment 1. Participants in both varied and constant conditions
+improved at the task during the training phase. We did not observe the
+common finding of training under varied conditions producing worse
+performance during acquisition than training under constant conditions
+(Catalano & Kleiner, 1984; Wrisberg et al., 1987), which has been
+suggested to relate to the subsequent benefits of varied training in
+retention and generalization testing (Soderstrom & Bjork, 2015). However
+our finding of no difference in training performance between constant
+and varied groups has been observed in previous work (Chua et al., 2019;
+Moxley, 1979; Pigott & Shapiro, 1984).
+
+In the testing phase, our varied group significantly outperformed the
+constant conditions in both a general comparison, and in an analysis
+limited to novel throwing positions. The observed benefit of varied over
+constant training echoes the findings of many previous visuomotor skill
+learning studies that have continued to emerge since the introduction of
+Schmidt's influential Schema Theory (Catalano & Kleiner, 1984; Chua et
+al., 2019; Goodwin et al., 1998; McCracken & Stelmach, 1977; Moxley,
+1979; Newell & Shapiro, 1976; Pigott & Shapiro, 1984; Roller et al.,
+2001; Schmidt, 1975; Willey & Liu, 2018; Wrisberg et al., 1987; Wulf,
+1991). We also join a much smaller set of research to observe this
+pattern in a computerized task (Seow et al., 2019). One departure from
+the experiment 1 findings concerns the pattern wherein the varied group
+outperformed the constant group even from the training position of the
+constant group, which was significant in experiment 1, but did not reach
+significance in experiment 2. Although this pattern has been observed
+elsewhere in the literature (Goode et al., 2008; Kerr & Booth, 1978),
+the overall evidence for this effect appears to be far weaker than for
+the more general benefit of varied training in conditions novel to all
+training groups.
 
 # Computational Model
-Controlling for the similarity between training and testing
-The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations.
-To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release.
-For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions.
-We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target.
-We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions – thus resulting in six separate similarity scores for each participant.
-Figure 8a visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions.
-As illustrated in Figure 8b, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.
-
-(ref:taskSpace) Figure 8a is a visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-Figure 8b shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+
+Controlling for the similarity between training and testing The primary
+goal of Experiment 2 was to examine whether the benefits of variability
+would persist after accounting for individual differences in the
+similarity between trained and tested throwing locations. To this end,
+we modelled each throw as a two-dimensional point in the space of x and
+y velocities applied to the projectile at the moment of release. For
+each participant, we took each individual training throw, and computed
+the similarity between that throw and the entire population of throws
+within the solution space for each of the 6 testing positions. We
+defined the solution space empirically as the set of all combinations of
+x and y throw velocities that resulted in hitting the target. We then
+summed each of the trial-level similarities to produce a single
+similarity for each testing position score relating how the participant
+threw the ball during training and the solutions that would result in
+target hits from each of the six testing positions -- thus resulting in
+six separate similarity scores for each participant. Figure 8a
+visualizes the solution space for each location and illustrates how
+different combinations of x and y velocity result in successfully
+striking the target from different launching positions. As illustrated
+in Figure 8b, the solution throws represent just a small fraction of the
+entire space of velocity combinations used by participants throughout
+the experiment.
+
+(ref:taskSpace) Figure 8a is a visual representation of the combinations
+of throw parameters (x and y velocities applied to the ball at launch),
+which resulted in target hits during the testing phase. This empirical
+solution space was compiled from all of the participants in experiment
+2. Figure 8b shows the solution space within the context of all of the
+throws made throughout the testing phase of the experiment.
 
@@
 
-For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.
-The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient.
-Then, as per an instance-based model of similarity (Logan, 2002; Nosofsky, 1992), these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value.
-The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.
-If c has a large value, then even a small difference between two throws’ velocities greatly decreases the extent of generalization from one to the other.
-A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities.
-The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions.
-The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.
-
-**Equation 1:**
-\[ Similarity_{I,J} =  \sum_{i = I}\sum_{j=J} e^{-c\cdot d^p_{i,j}} \]
+For each individual trial, the Euclidean distance (Equation 1) was
+computed between the velocity components (x and y) of that trial and the
+velocity components of each individual solution throw for each of the 6
+positions from which participants would be tested in the final phase of
+the study. The P parameter in Equation 1 is set equal to 2, reflecting a
+Gaussian similarity gradient. Then, as per an instance-based model of
+similarity (Logan, 2002; Nosofsky, 1992), these distances were
+multiplied by a sensitivity parameter, c, and then exponentiated to
+yield a similarity value. The parameter c controls the rate with which
+similarity-based generalization drops off as the Euclidean distance
+between two throws in x- and y-velocity space increases. If c has a
+large value, then even a small difference between two throws' velocities
+greatly decreases the extent of generalization from one to the other. A
+small value for c produces broad generalization from one throw to
+another despite relatively large differences in their velocities. The
+similarity values for each training individual throw made by a given
+participant were then summed to yield a final similarity score, with a
+separate score computed for each of the 6 testing positions. The final
+similarity score is construable as index of how accurate the throws a
+participant made during the training phase would be for each of the
+testing positions.
+
+**Equation 1:** \[ Similarity\_{I,J} = \sum*{i = I}*\sum{j=J}
+e^{-c^\cdot dp\_{i,j}} \]
 
@@
 
-A simple linear regression revealed that these similarity scores were significantly predictive of performance in the transfer stage, t =-15.88, p<.01, $r^2$=.17, such that greater similarity between training throws and solution spaces for each of the test locations resulted in better performance.
-We then repeated the group comparisons above while including similarity as a covariate in the model.
-Comparing the varied and constant groups in testing performance from all testing positions yielded a significant effect of similarity, F(1, 205)=85.66, p<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition (varied vs.
-constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03.
-The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p<.001, $\eta^{2}_G$ =.18 as well  as for condition F(1,148)=11.55, p<.001, $\eta^{2}_G$ =.07.
-For all comparisons, the pattern of results was consistent with the initial findings from experiment 2, with the varied group still performing significantly better than the constant group.
+A simple linear regression revealed that these similarity scores were
+significantly predictive of performance in the transfer stage, t
+=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
+training throws and solution spaces for each of the test locations
+resulted in better performance. We then repeated the group comparisons
+above while including similarity as a covariate in the model. Comparing
+the varied and constant groups in testing performance from all testing
+positions yielded a significant effect of similarity, F(1, 205)=85.66,
+p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
+(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
+group comparison limited to only novel locations for the varied group
+pit against trained location for the constant group resulted in a
+significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
+=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
+=.07. For all comparisons, the pattern of results was consistent with
+the initial findings from experiment 2, with the varied group still
+performing significantly better than the constant group.
 
 ## Fitting model parameters separately by group
-To directly control for similarity in Experiment 2, we developed a model-based measure of the similarity between training throws and testing conditions.
-This similarity measure was a significant predictor of testing performance, e.g., participants whose training throws were more similar to throws that resulted in target hits from the testing positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level benefits of varied training, which remained significant in our linear model predicting testing performance after similarity was added to the model.
-However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group (Hahn et al., 2005; Lamberts, 1994).
-Relatedly, the influential Bayesian generalization model developed by  Tenenbaum & Griffiths (2001) predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
-Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
-Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
-One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience (Nosofsky & Johansen, 2000; Sakamoto et al., 2006).
-If one’s training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
-Conversely, if one’s training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c,  to varied and constant participants.
-To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
-
-Both models generate distinct similarity values between training and testing locations.
-Much like the analyses in Experiment 2, these similarity values are regressed against testing performance in models of the form shown below.
-As was the case previously, testing performance is defined as the mean absolute distance from the center of the target (with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p<.01).
-Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the c parameter separately between groups (Similarity2c).
-In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p<.01), with the varied group still performing significantly better.
-However, in linear model 4 the addition of the Similarity2c predictor results in the effect of training group becoming nonsignificant (p=.40), suggesting that the effect of varied vs.
-constant training is accounted for by the Similarity2c predictor.
-Next, to further establish a difference between the models, we performed nested model comparisons using ANOVA, to see if the addition of the training group parameter led to a significant improvement in model performance.
-In the first comparison, ANOVA(Linear Model 1, Linear Model 2), the addition of the training group predictor significantly improved the performance of the model (F=22.07, p<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear Model 4) found no improvement in model performance with the addition of the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the adjusted Similarity2c model had more predictive power than those generated from the original Similarity1c model.
-Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
-The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
-Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which assumes equivalent generalization gradients between constant and varied trained participants is unable to account for the extent of benefits of varied over constant training observed at testing.
-The evidence for this in the comparative model fits is that when a varied/constant dummy-coded variable for condition is explicitly added to the model, the variable adds a significant contribution to the prediction of test performance, with the variable condition yielding better performance than the constant conditions.
-However, if the instance-based generalization model is modified to assume that the training groups can differ in the steepness of their generalization gradient, by incorporating a separate generalization parameter for each group, then the instance-based model can account for our experimental results without explicitly taking training group into account.
-Henceforth this model will be referred to as the Instance-based Generalization with Adaptive Similarity (IGAS) model.
+
+To directly control for similarity in Experiment 2, we developed a
+model-based measure of the similarity between training throws and
+testing conditions. This similarity measure was a significant predictor
+of testing performance, e.g., participants whose training throws were
+more similar to throws that resulted in target hits from the testing
+positions, tended to perform better during the testing phase.
+Importantly, the similarity measure did not explain away the group-level
+benefits of varied training, which remained significant in our linear
+model predicting testing performance after similarity was added to the
+model. However, previous research has suggested that participants may
+differ in their level of generalization as a function of prior
+experience, and that such differences in generalization gradients can be
+captured by fitting the generalization parameter of an instance-based
+model separately to each group (Hahn et al., 2005; Lamberts, 1994).
+Relatedly, the influential Bayesian generalization model developed by
+Tenenbaum & Griffiths (2001) predicts that the breadth of generalization
+will increase when a rational agent encounters a wider variety of
+examples. Following these leads, we assume that in addition to learning
+the task itself, participants are also adjusting how generalizable their
+experience should be. Varied versus constant participants may be
+expected to learn to generalize their experience to different degrees.
+To accommodate this difference, the generalization parameter of the
+instance-based model (in the present case, the c parameter) can be
+allowed to vary between the two groups to reflect the tendency of
+learners to adaptively tune the extent of their generalization. One
+specific hypothesis is that people adaptively set a value of c to fit
+the variability of their training experience (Nosofsky & Johansen, 2000;
+Sakamoto et al., 2006). If one's training experience is relatively
+variable, as with the variable training condition, then one might infer
+that future test situations will also be variable, in which case a low
+value of c will allow better generalization because generalization will
+drop off slowly with training-to-testing distance. Conversely, if one's
+training experience has little variability, as found in the constant
+training conditions, then one might adopt a high value of c so that
+generalization falls off rapidly away from the trained positions.
+
+To address this possibility, we compared the original instance-based
+model of similarity fit against a modified model which separately fits
+the generalization parameter, c, to varied and constant participants. To
+perform this parameter fitting, we used the optim function in R, and fit
+the model to find the c value(s) that maximized the correlation between
+similarity and testing performance.
+
+Both models generate distinct similarity values between training and
+testing locations. Much like the analyses in Experiment 2, these
+similarity values are regressed against testing performance in models of
+the form shown below. As was the case previously, testing performance is
+defined as the mean absolute distance from the center of the target
+(with a separate score for each participant, from each position).
+
+Linear models 1 and 3 both show that similarity is a significant
+predictor of testing performance (p\<.01). Of greater interest is the
+difference between linear model 2, in which similarity is computed from
+a single c value fit from all participants (Similarity1c), with linear
+model 4, which fits the c parameter separately between groups
+(Similarity2c). In linear model 2, the effect of training group remains
+significant when controlling for Similarity1c (p\<.01), with the varied
+group still performing significantly better. However, in linear model 4
+the addition of the Similarity2c predictor results in the effect of
+training group becoming nonsignificant (p=.40), suggesting that the
+effect of varied vs. constant training is accounted for by the
+Similarity2c predictor. Next, to further establish a difference between
+the models, we performed nested model comparisons using ANOVA, to see if
+the addition of the training group parameter led to a significant
+improvement in model performance. In the first comparison, ANOVA(Linear
+Model 1, Linear Model 2), the addition of the training group predictor
+significantly improved the performance of the model (F=22.07, p\<.01).
+However, in the second model comparison, ANOVA (Linear model 3, Linear
+Model 4) found no improvement in model performance with the addition of
+the training group predictor (F=1.61, p=.20).
+
+Finally, we sought to confirm that similarity values generated from the
+adjusted Similarity2c model had more predictive power than those
+generated from the original Similarity1c model. Using the BIC function
+in R, we compared BIC values between linear model 1 (BIC=14604.00) and
+linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
+a modest advantage for predicting performance using a similarity measure
+computed with two c values over similarity computed with a single c
+value. When fit with separate c values, the best fitting c parameters
+for the model consistently optimized such that the c value for the
+varied group (c=.00008) was smaller in magnitude than the c value for
+the constant group(c= .00011). Recall that similarity decreases as a
+Gaussian function of distance (equation 1 above), and a smaller value of
+c will result in a more gradual drop-off in similarity as the distance
+between training throws and testing solutions increases.
+
+In summary, our modeling suggests that an instance-based model which
+assumes equivalent generalization gradients between constant and varied
+trained participants is unable to account for the extent of benefits of
+varied over constant training observed at testing. The evidence for this
+in the comparative model fits is that when a varied/constant dummy-coded
+variable for condition is explicitly added to the model, the variable
+adds a significant contribution to the prediction of test performance,
+with the variable condition yielding better performance than the
+constant conditions. However, if the instance-based generalization model
+is modified to assume that the training groups can differ in the
+steepness of their generalization gradient, by incorporating a separate
+generalization parameter for each group, then the instance-based model
+can account for our experimental results without explicitly taking
+training group into account. Henceforth this model will be referred to
+as the Instance-based Generalization with Adaptive Similarity (IGAS)
+model.
 
 # General Discussion
-Across two experiments, we found evidence in support of the benefits of variability hypothesis in a simple, computerized projectile throwing task.
-Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
-However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions.
-We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training (Goode et al., 2008; Green et al., 1995; Kerr & Booth, 1978).
-In experiment 1 varied participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
-Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
-Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
-Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
-A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
-The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
-In this fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained.
-Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in Figure 9 we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern.
-In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model – namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.
+
+Across two experiments, we found evidence in support of the benefits of
+variability hypothesis in a simple, computerized projectile throwing
+task. Generalization was observed in both constant and varied
+participants, in that both groups tended to perform better at novel
+positions in the testing phase than did participants who started with
+those positions in the training phase. However, varied trained
+participants consistently performed better than constant trained
+participants, in terms of both the testing phase in general, and in a
+comparison that only included untrained positions. We also found some
+evidence for the less commonly observed pattern wherein varied-trained
+participants outperform constant-trained participants even from
+conditions identical to the constant group training (Goode et al., 2008;
+Green et al., 1995; Kerr & Booth, 1978). In experiment 1 varied
+participants performed significantly better on this identity comparison.
+In Experiment 2, the comparison was not significant initially, but
+became significant after controlling for the similarity measure that
+incorporates only a single value for the steepness of similarity-based
+generalization (c). Furthermore, we showed that the general pattern of
+results from Experiment 2 could be parsimoniously accommodated by an
+instance-based similarity model, but only with the assumption that
+constant and varied participants generalize their training experience to
+different degrees. Our results thus suggest that the benefits of
+variation cannot be explained by the varied-trained participants simply
+covering a broader range of the task space. Rather, the modeling
+suggests that varied participants also learn to adaptively tune their
+generalization function such that throwing locations generalize more
+broadly to one another than they do in the constant condition. A
+learning system could end up adopting a higher c value in the constant
+than variable training conditions by monitoring the trial-by-trial
+variability of the training items. The c parameter would be adapted
+downwards when adjacent training items are dissimilar to each other and
+adapted upwards when adjacent training items are the same. In this
+fashion, contextually appropriate c values could be empirically learned.
+This learning procedure would capture the insight that if a situation
+has a high amount variability, then the learner should be predisposed
+toward thinking that subsequent test items will also show considerable
+variability, in which case generalization gradients should be broad, as
+is achieved by low values for c.
+
+Also of interest is whether the IGAS model can predict the pattern of
+results wherein the varied condition outperforms the constant condition
+even from the position on which the constant condition trained. Although
+our models were fit using all of the Experiment 2 training and testing
+data, not just that of the identity comparisons, in Figure 9 we
+demonstrate how a simplified version of the IGAS model could in
+principle produce such a pattern. In addition to the assumption of
+differential generalization between varied and constant conditions, our
+simplified model makes explicit an assumption that is incorporated into
+the full IGAS model -- namely that even when being tested from a
+position identical to that which was trained, there are always some
+psychological contextual differences between training and testing
+throws, resulting in a non-zero dissimilarity.
 
@@
 
-As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning (Aha & Goldstone, 1992; Briscoe & Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al., 2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013; Taylor & Ivry, 2013; Thoroughman & Taylor, 2005).
-Lamberts (1994) showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability (Hahn et al., 2005; Sakamoto et al., 2006).
-However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains.
-(Censor et al., 2012; Cox et al., 2018; Hills et al., 2010; Jamieson et al., 2022; Law & Gold, 2010; Roark et al., 2021; Rosenbaum et al., 2001; Vigo et al., 2018; Wall et al., 2021; Wu et al., 2020; Yang et al., 2020).
-
-Our modelling approach does differ from category learning implementations of instance-based models in several ways.
-One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g.
-size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
-movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
-Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work – though as described in the introduction there is some evidence in support of this idea (Chamberlin & Magill, 1992; Crump & Logan, 2010; Hommel, 1998; Meigh et al., 2018; Poldrack et al., 1999).
-A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues (Cohen & Rosenbaum, 2004; Rosenbaum et al., 1995).
-Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
-Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
-A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on the effects of varied training in a coincident timing task (Catalano & Kleiner, 1984).
-In this task, participants observe a series of lamps lighting up consecutively, and attempt to time a button press with the onset of the final lamp.
-The design consisted of four separate constant groups, each training from a single lighting velocity, and a single varied group training with all four of the lighting velocities used by the individual constant groups.
-Participants were then split into four separate testing conditions, each of which were tested from a single novel lighting velocity of varying distance from the training conditions.
-The result of primary interest was that all participants performed worse as the distance between training and testing velocity increased – a typical generalization decrement.
-However, varied participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are similar to our own, our work is novel in that we account for our results with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their separate constant groups together may result in similarity confounds between varied and constant conditions that leaves their study open to methodological criticisms, especially in light of related work which demonstrated that the extent to which varied training may be beneficial can depend on whether the constant group they are compared against trained from similar conditions to those later tested (Wrisberg et al., 1987).
-Our study alleviates such concerns by explicitly controlling for similarity.
+As mentioned above, the idea that learners flexibly adjust their
+generalization gradient based on prior experience does have precedent in
+the domains of category learning (Aha & Goldstone, 1992; Briscoe &
+Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al.,
+2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013;
+Taylor & Ivry, 2013; Thoroughman & Taylor, 2005). Lamberts (1994) showed
+that a simple manipulation of background knowledge during a
+categorization test resulted in participants generalizing their training
+experience more or less broadly, and moreover that such a pattern could
+be captured by allowing the generalization parameter of an
+instance-based similarity model to be fit separately between conditions.
+The flexible generalization parameter has also successfully accounted
+for generalization behavior in cases where participants have been
+trained on categories that differ in their relative variability (Hahn et
+al., 2005; Sakamoto et al., 2006). However, to the best of our
+knowledge, IGAS is the first instance-based similarity model that has
+been put forward to account for the effect of varied training in a
+visuomotor skill task. Although IGAS was inspired by work in the domain
+of category learning, its success in a distinct domain may not be
+surprising in light of the numerous prior observations that at least
+certain aspects of learning and generalization may operate under common
+principles across different tasks and domains. (Censor et al., 2012; Cox
+et al., 2018; Hills et al., 2010; Jamieson et al., 2022; Law & Gold,
+2010; Roark et al., 2021; Rosenbaum et al., 2001; Vigo et al., 2018;
+Wall et al., 2021; Wu et al., 2020; Yang et al., 2020).
+
+Our modelling approach does differ from category learning
+implementations of instance-based models in several ways. One such
+difference is the nature of the training instances that are assumed to
+be stored. In category learning studies, instances are represented as
+points in a multidimensional space of all of the attributes that define
+a category item (e.g. size/color/shape). Rather than defining instances
+in terms of what stimuli learners experience, our approach assumes that
+stored, motor instances reflect how they act, in terms of the velocity
+applied to the ball on each throw. An advantage of many motor learning
+tasks is the relative ease with which task execution variables can be
+directly measured (e.g. movement force, velocity, angle, posture) in
+addition to the decision and response time measures that typically
+exhaust the data generated from more classical cognitive tasks. Of
+course, whether learners actually are storing each individual motor
+instance is a fundamental question beyond the scope of the current work
+-- though as described in the introduction there is some evidence in
+support of this idea (Chamberlin & Magill, 1992; Crump & Logan, 2010;
+Hommel, 1998; Meigh et al., 2018; Poldrack et al., 1999). A particularly
+noteworthy instance-based model of sensory-motor behavior is the
+Knowledge II model of Rosenbaum and colleagues (Cohen & Rosenbaum, 2004;
+Rosenbaum et al., 1995). Knowledge II explicitly defines instances as
+postures (joint combinations), and is thus far more detailed than IGAS
+in regards to the contents of stored instances. Knowledge II also
+differs from IGAS in that learning is accounted for by both the
+retrieval of stored postures, and the generation of novel postures via
+the modification of retrieved postures. A promising avenue for future
+research would be to combine the adaptive similarity mechanism of IGAS
+with the novel instance generation mechanisms of Knowledge II.
+
+Our findings also have some conceptual overlap with an earlier study on
+the effects of varied training in a coincident timing task (Catalano &
+Kleiner, 1984). In this task, participants observe a series of lamps
+lighting up consecutively, and attempt to time a button press with the
+onset of the final lamp. The design consisted of four separate constant
+groups, each training from a single lighting velocity, and a single
+varied group training with all four of the lighting velocities used by
+the individual constant groups. Participants were then split into four
+separate testing conditions, each of which were tested from a single
+novel lighting velocity of varying distance from the training
+conditions. The result of primary interest was that all participants
+performed worse as the distance between training and testing velocity
+increased -- a typical generalization decrement. However, varied
+participants showed less of a decrement than did constant participants.
+The authors take this result as evidence that varied training results in
+a less-steep generalization gradient than does constant training.
+Although the experimental conclusions of Catalano and Kleiner are
+similar to our own, our work is novel in that we account for our results
+with a cognitive model, and without assuming the formation of a schema.
+Additionally, the way in which Catalano and Kleiner collapse their
+separate constant groups together may result in similarity confounds
+between varied and constant conditions that leaves their study open to
+methodological criticisms, especially in light of related work which
+demonstrated that the extent to which varied training may be beneficial
+can depend on whether the constant group they are compared against
+trained from similar conditions to those later tested (Wrisberg et al.,
+1987). Our study alleviates such concerns by explicitly controlling for
+similarity.
 
 ## Limitations
-A limitation of this study concerns the ordering of the testing/transfer trials at the conclusion of both experiments.
-Participants were tested from each separate position (4 in Experiment 1, 6 in Experiment 2) in a random, intermixed order.
-Because the varied group was trained from two positions that were also randomly ordered, they may have benefited from experience with this type of sequencing, whereas the constant groups had no experience with switching between positions trial to trial.
-This concern is somewhat ameliorated by the fact that the testing phase performance of the constant groups from their trained position was not significantly worse than their level of performance at the end of the training phase, suggesting that they were not harmed by random ordering of positions during testing.
-It should also be noted that the computerized task utilized in the present work is relatively simple compared to many of the real-world tasks utilized in prior research.
-It is thus conceivable that the effect of variability in more complex tasks is distinct from the process put forward in the present work.
-An important challenge for future work will be to assess the extent to which IGAS can account for generalization in relatively complex tasks with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations (Nosofsky, 1992; Shepard, 1987).
-Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
-In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
-However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
+
+A limitation of this study concerns the ordering of the testing/transfer
+trials at the conclusion of both experiments. Participants were tested
+from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
+random, intermixed order. Because the varied group was trained from two
+positions that were also randomly ordered, they may have benefited from
+experience with this type of sequencing, whereas the constant groups had
+no experience with switching between positions trial to trial. This
+concern is somewhat ameliorated by the fact that the testing phase
+performance of the constant groups from their trained position was not
+significantly worse than their level of performance at the end of the
+training phase, suggesting that they were not harmed by random ordering
+of positions during testing. It should also be noted that the
+computerized task utilized in the present work is relatively simple
+compared to many of the real-world tasks utilized in prior research. It
+is thus conceivable that the effect of variability in more complex tasks
+is distinct from the process put forward in the present work. An
+important challenge for future work will be to assess the extent to
+which IGAS can account for generalization in relatively complex tasks
+with far more degrees of freedom.
+
+It is common for psychological process models of categorization learning
+to use an approach such as multidimensional scaling so as to transform
+the stimuli from the physical dimensions used in the particular task
+into the psychological dimensions more reflective of the actual human
+representations (Nosofsky, 1992; Shepard, 1987). Such scaling typically
+entails having participants rate the similarity between individual items
+and using these similarity judgements to then compute the psychological
+distances between stimuli, which can then be fed into a subsequent
+model. In the present investigation, there was no such way to scale the
+x and y velocity components in terms of the psychological similarity,
+and thus our modelling does rely on the assumption that the
+psychological distances between the different throwing positions are
+proportional to absolute distances in the metric space of the task (e.g.
+the relative distance between positions 400 and 500 is equivalent to
+that between 800 and 900). However, an advantage of our approach is that
+we are measuring similarity in terms of how participants behave
+(applying a velocity to the ball), rather than the metric features of
+the task stimuli.
 
 ## Conclusion
-Our experiments demonstrate a reliable benefit of varied training in a simple projectile launching task.
-Such results were accounted for by an instance-based model that assumes that varied training results in the computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable approach towards better understanding skill generalization and transfer.
+
+Our experiments demonstrate a reliable benefit of varied training in a
+simple projectile launching task. Such results were accounted for by an
+instance-based model that assumes that varied training results in the
+computation of a broader similarity-based generalization gradient.
+Instance-based models augmented with this assumption may be a valuable
+approach towards better understanding skill generalization and transfer.
 
@@
 
-Aha, D. W., & Goldstone, R. L. (1992). Concept Learning and Flexible Weighting. _In Proceedings of the Fourteenth Annual Conference of the Cognitive Science Society_, 534–539.
-
-Barnett, S. M., & Ceci, S. J. (2002). When and where do we apply what we learn?: A taxonomy for far transfer. _Psychological Bulletin_, _128_(4), 612–637. https://doi.org/10.1037//0033-2909.128.4.612
-
-Berniker, M., Mirzaei, H., & Kording, K. P. (2014). The effects of training breadth on motor generalization. _Journal of Neurophysiology_, _112_(11), 2791–2798. https://doi.org/10.1152/jn.00615.2013
-
-Braithwaite, D.
-W., & Goldstone, R.
-L.
-(2015).
-Effects of Variation and Prior Knowledge on Abstract Concept Learning.
-_Cognition and Instruction_, _33_(3), 226–256.
+Aha, D. W., & Goldstone, R. L. (1992). Concept Learning and Flexible
+Weighting. *In Proceedings of the Fourteenth Annual Conference of the
+Cognitive Science Society*, 534--539.
+
+Barnett, S. M., & Ceci, S. J. (2002). When and where do we apply what we
+learn?: A taxonomy for far transfer. *Psychological Bulletin*, *128*(4),
+612--637. https://doi.org/10.1037//0033-2909.128.4.612
+
+Berniker, M., Mirzaei, H., & Kording, K. P. (2014). The effects of
+training breadth on motor generalization. *Journal of Neurophysiology*,
+*112*(11), 2791--2798. https://doi.org/10.1152/jn.00615.2013
+
+Braithwaite, D. W., & Goldstone, R. L. (2015). Effects of Variation and
+Prior Knowledge on Abstract Concept Learning. *Cognition and
+Instruction*, *33*(3), 226--256.
 https://doi.org/10.1080/07370008.2015.1067215
 
-Braun, D. A., Aertsen, A., Wolpert, D. M., & Mehring, C. (2009). Motor Task Variation Induces Structural Learning. _Current Biology_, _19_(4), 352–357. https://doi.org/10.1016/j.cub.2009.01.036
-
-Briscoe, E., & Feldman, J. (2011). Conceptual complexity and the bias/variance tradeoff. _Cognition_, _118_(1), 2–16. https://doi.org/10.1016/j.cognition.2010.10.004
-
-Catalano, J.
-F., & Kleiner, B.
-M.
-(1984).
-Distant Transfer in Coincident Timing as a Function of Variability of Practice.
-_Perceptual and Motor Skills_, _58_(3), 851–856.
-https://doi.org/10.2466/pms.1984.58.3.851
-
-Censor, N., Sagi, D., & Cohen, L. G. (2012). Common mechanisms of human perceptual and motor learning. _Nature Reviews Neuroscience_, _13_(9), 658–664. https://doi.org/10.1038/nrn3315
-
-Chamberlin, C.
-J., & Magill, R.
-A.
-(1992).
-A Note on Schema and Exemplar Approaches to Motor Skill Representation in Memory.
-_Journal of Motor Behavior_, _24_(2), 221–224.
+Braun, D. A., Aertsen, A., Wolpert, D. M., & Mehring, C. (2009). Motor
+Task Variation Induces Structural Learning. *Current Biology*, *19*(4),
+352--357. https://doi.org/10.1016/j.cub.2009.01.036
+
+Briscoe, E., & Feldman, J. (2011). Conceptual complexity and the
+bias/variance tradeoff. *Cognition*, *118*(1), 2--16.
+https://doi.org/10.1016/j.cognition.2010.10.004
+
+Catalano, J. F., & Kleiner, B. M. (1984). Distant Transfer in Coincident
+Timing as a Function of Variability of Practice. *Perceptual and Motor
+Skills*, *58*(3), 851--856. https://doi.org/10.2466/pms.1984.58.3.851
+
+Censor, N., Sagi, D., & Cohen, L. G. (2012). Common mechanisms of human
+perceptual and motor learning. *Nature Reviews Neuroscience*, *13*(9),
+658--664. https://doi.org/10.1038/nrn3315
+
+Chamberlin, C. J., & Magill, R. A. (1992). A Note on Schema and Exemplar
+Approaches to Motor Skill Representation in Memory. *Journal of Motor
+Behavior*, *24*(2), 221--224.
 https://doi.org/10.1080/00222895.1992.9941617
 
-Chua, L.-K., Dimapilis, M.
-K., Iwatsuki, T., Abdollahipour, R., Lewthwaite, R., & Wulf, G.
-(2019).
-Practice variability promotes an external focus of attention and enhances motor skill learning.
-_Human Movement Science_, _64_, 307–319.
+Chua, L.-K., Dimapilis, M. K., Iwatsuki, T., Abdollahipour, R.,
+Lewthwaite, R., & Wulf, G. (2019). Practice variability promotes an
+external focus of attention and enhances motor skill learning. *Human
+Movement Science*, *64*, 307--319.
 https://doi.org/10.1016/j.humov.2019.02.015
 
-Cochrane, A. (2020). TEfits: Nonlinear regression for time-evolving indices. _Journal of Open Source Software_, _5_(52), 2535. https://doi.org/10.21105/joss.02535
-
-Cohen, R.
-G., & Rosenbaum, D.
-A.
-(2004).
-Where grasps are made reveals how grasps are planned: Generation and recall of motor plans.
-_Experimental Brain Research_, _157_(4).
+Cochrane, A. (2020). TEfits: Nonlinear regression for time-evolving
+indices. *Journal of Open Source Software*, *5*(52), 2535.
+https://doi.org/10.21105/joss.02535
+
+Cohen, R. G., & Rosenbaum, D. A. (2004). Where grasps are made reveals
+how grasps are planned: Generation and recall of motor plans.
+*Experimental Brain Research*, *157*(4).
 https://doi.org/10.1007/s00221-004-1862-9
 
-Cox, G.
-E., Hemmer, P., Aue, W.
-R., & Criss, A.
-H.
-(2018).
-Information and processes underlying semantic and episodic memory across tasks, items, and individuals.
-_Journal of Experimental Psychology: General_, _147_(4), 545–590.
-https://doi.org/10.1037/xge0000407
-
-Crump, M.
-J.
-C., & Logan, G.
-D.
-(2010).
-Episodic contributions to sequential control: Learning from a typist’s touch.
-_Journal of Experimental Psychology: Human Perception and Performance_, _36_(3), 662–672.
-https://doi.org/10.1037/a0018390
-
-Czyż, S. H. (2021). Variability of Practice, Information Processing, and Decision Making—How Much Do We Know? _Frontiers in Psychology_, _12_. https://doi.org/10.3389/fpsyg.2021.639131
-
-de Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating behavioral experiments in a Web browser. _Behavior Research Methods_, _47_(1), 1–12. https://doi.org/10.3758/s13428-014-0458-y
-
-DeLosh, E.
-L., McDaniel, M.
-A., & Busemeyer, J.
-R.
-(1997).
+Cox, G. E., Hemmer, P., Aue, W. R., & Criss, A. H. (2018). Information
+and processes underlying semantic and episodic memory across tasks,
+items, and individuals. *Journal of Experimental Psychology: General*,
+*147*(4), 545--590. https://doi.org/10.1037/xge0000407
+
+Crump, M. J. C., & Logan, G. D. (2010). Episodic contributions to
+sequential control: Learning from a typist's touch. *Journal of
+Experimental Psychology: Human Perception and Performance*, *36*(3),
+662--672. https://doi.org/10.1037/a0018390
+
+Czyż, S. H. (2021). Variability of Practice, Information Processing, and
+Decision Making---How Much Do We Know? *Frontiers in Psychology*, *12*.
+https://doi.org/10.3389/fpsyg.2021.639131
+
+de Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating
+behavioral experiments in a Web browser. *Behavior Research Methods*,
+*47*(1), 1--12. https://doi.org/10.3758/s13428-014-0458-y
+
+DeLosh, E. L., McDaniel, M. A., & Busemeyer, J. R. (1997).
 Extrapolation: The Sine Qua Non for Abstraction in Function Learning.
-_Journal of Experimental Psychology: Learning, Memory, and Cognition_, 19.
-
-Detterman, D. K. (1993). The case for the prosecution: Transfer as an epiphenomenon. In _Transfer on trial: Intelligence, cognition, and instruction_ (pp. 1–24). Ablex Publishing.
-
-Ennis, D.
-M., Palen, J.
-J., & Mullen, K.
-(1988).
-A multidimensional stochastic theory of similarity.
-_Journal of Mathematical Psychology_, _32_(4), 449–465.
-https://doi.org/10.1016/0022-2496(88)90023-5
-
-Estes, W. K. (1994). _Classification and Cognition_. Oxford University Press.
-
-Faul, F., Erdfelder, E., Buchner, A., & Lang, A.-G.
-(2009).
-Statistical power analyses using G*Power 3.1: Tests for correlation and regression analyses.
-_Behavior Research Methods_, _41_(4), 1149–1160.
+*Journal of Experimental Psychology: Learning, Memory, and Cognition*,
+19.
+
+Detterman, D. K. (1993). The case for the prosecution: Transfer as an
+epiphenomenon. In *Transfer on trial: Intelligence, cognition, and
+instruction* (pp. 1--24). Ablex Publishing.
+
+Ennis, D. M., Palen, J. J., & Mullen, K. (1988). A multidimensional
+stochastic theory of similarity. *Journal of Mathematical Psychology*,
+*32*(4), 449--465. https://doi.org/10.1016/0022-2496(88)90023-5
+
+Estes, W. K. (1994). *Classification and Cognition*. Oxford University
+Press.
+
+Faul, F., Erdfelder, E., Buchner, A., & Lang, A.-G. (2009). Statistical
+power analyses using G\*Power 3.1: Tests for correlation and regression
+analyses. *Behavior Research Methods*, *41*(4), 1149--1160.
 https://doi.org/10.3758/BRM.41.4.1149
 
-Fulvio, J.
-M., Green, C.
-S., & Schrater, P.
-R.
-(2014).
-Task-Specific Response Strategy Selection on the Basis of Recent Training Experience.
-_PLOS Computational Biology_, _10_(1), e1003425.
+Fulvio, J. M., Green, C. S., & Schrater, P. R. (2014). Task-Specific
+Response Strategy Selection on the Basis of Recent Training Experience.
+*PLOS Computational Biology*, *10*(1), e1003425.
 https://doi.org/10.1371/journal.pcbi.1003425
 
-Gandolfo, F., Mussa-Ivaldi, F.
-A., & Bizzi, E.
-(1996).
-Motor learning by field approximation.
-_Proceedings of the National Academy of Sciences_, _93_(9), 3843–3846.
-https://doi.org/10.1073/pnas.93.9.3843
-
-George, N., & Egner, T. (2021). Stimulus variability and task relevance modulate binding-learning. _Attention, Perception, & Psychophysics_. https://doi.org/10.3758/s13414-021-02338-6
-
-Ghahramani, Z., Wolpert, D.
-M., & Jordan, M.
-I.
-(1996).
-Generalization to Local Remappings of the Visuomotor Coordinate Transformation.
-_Journal of Neuroscience_, _16_(21), 7085–7096.
+Gandolfo, F., Mussa-Ivaldi, F. A., & Bizzi, E. (1996). Motor learning by
+field approximation. *Proceedings of the National Academy of Sciences*,
+*93*(9), 3843--3846. https://doi.org/10.1073/pnas.93.9.3843
+
+George, N., & Egner, T. (2021). Stimulus variability and task relevance
+modulate binding-learning. *Attention, Perception, & Psychophysics*.
+https://doi.org/10.3758/s13414-021-02338-6
+
+Ghahramani, Z., Wolpert, D. M., & Jordan, M. I. (1996). Generalization
+to Local Remappings of the Visuomotor Coordinate Transformation.
+*Journal of Neuroscience*, *16*(21), 7085--7096.
 https://doi.org/10.1523/JNEUROSCI.16-21-07085.1996
 
-Gonzalez, C., & Madhavan, P. (2011). Diversity during training enhances detection of novel stimuli. _Journal of Cognitive Psychology_, _23_(3), 342–350. https://doi.org/10.1080/20445911.2011.507187
-
-Goode, M.
-K., Geraci, L., & Roediger, H.
-L.
-(2008).
-Superiority of variable to repeated practice in transfer on anagram solution.
-_Psychonomic Bulletin & Review_, _15_(3), 662–666.
+Gonzalez, C., & Madhavan, P. (2011). Diversity during training enhances
+detection of novel stimuli. *Journal of Cognitive Psychology*, *23*(3),
+342--350. https://doi.org/10.1080/20445911.2011.507187
+
+Goode, M. K., Geraci, L., & Roediger, H. L. (2008). Superiority of
+variable to repeated practice in transfer on anagram solution.
+*Psychonomic Bulletin & Review*, *15*(3), 662--666.
 https://doi.org/10.3758/PBR.15.3.662
 
-Goodwin, J.
-E., Eckerson, J.
-M., Grimes, C.
-R., & Gordon, P.
-M.
-(1998).
-Effect of Different Quantities of Variable Practice on Acquisition, Retention, and Transfer of An Applied Motor Skill.
-_Perceptual and Motor Skills_, _87_(1), 147–151.
-https://doi.org/10.2466/pms.1998.87.1.147
-
-Green, D.
-P., Whitehead, J., & Sugden, D.
-A.
-(1995).
-Practice Variability and Transfer of a Racket Skill.
-_Perceptual and Motor Skills_, _81_(3_suppl), 1275–1281.
+Goodwin, J. E., Eckerson, J. M., Grimes, C. R., & Gordon, P. M. (1998).
+Effect of Different Quantities of Variable Practice on Acquisition,
+Retention, and Transfer of An Applied Motor Skill. *Perceptual and Motor
+Skills*, *87*(1), 147--151. https://doi.org/10.2466/pms.1998.87.1.147
+
+Green, D. P., Whitehead, J., & Sugden, D. A. (1995). Practice
+Variability and Transfer of a Racket Skill. *Perceptual and Motor
+Skills*, *81*(3_suppl), 1275--1281.
 https://doi.org/10.2466/pms.1995.81.3f.1275
 
-Hahn, U., Bailey, T. M., & Elvin, L. B. C. (2005). Effects of category diversity on learning, memory, and generalization. _Memory & Cognition_, _33_(2), 289–302. https://doi.org/10.3758/BF03195318
-
-Hills, T.
-T., Todd, P.
-M., & Goldstone, R.
-L.
-(2010).
-The central executive as a search process: Priming exploration and exploitation across domains.
-_Journal of Experimental Psychology: General_, _139_(4), 590–609.
-https://doi.org/10.1037/a0020666
-
-Hintzman, D. L. (1984). MINERVA 2: A simulation model of human memory. _Behavior Research Methods, Instruments, & Computers_, _16_(2), 96–101. https://doi.org/10.3758/BF03202365
-
-Hommel, B. (1998). Event Files: Evidence for Automatic Integration of Stimulus-Response Episodes. _Visual Cognition_, _5_(1–2), 183–216. https://doi.org/10.1080/713756773
-
-Jamieson, R.
-K., Johns, B.
-T., Vokey, J.
-R., & Jones, M.
-N.
-(2022).
+Hahn, U., Bailey, T. M., & Elvin, L. B. C. (2005). Effects of category
+diversity on learning, memory, and generalization. *Memory & Cognition*,
+*33*(2), 289--302. https://doi.org/10.3758/BF03195318
+
+Hills, T. T., Todd, P. M., & Goldstone, R. L. (2010). The central
+executive as a search process: Priming exploration and exploitation
+across domains. *Journal of Experimental Psychology: General*, *139*(4),
+590--609. https://doi.org/10.1037/a0020666
+
+Hintzman, D. L. (1984). MINERVA 2: A simulation model of human memory.
+*Behavior Research Methods, Instruments, & Computers*, *16*(2), 96--101.
+https://doi.org/10.3758/BF03202365
+
+Hommel, B. (1998). Event Files: Evidence for Automatic Integration of
+Stimulus-Response Episodes. *Visual Cognition*, *5*(1--2), 183--216.
+https://doi.org/10.1080/713756773
+
+Jamieson, R. K., Johns, B. T., Vokey, J. R., & Jones, M. N. (2022).
 Instance theory as a domain-general framework for cognitive psychology.
-_Nature Reviews Psychology_, _1_(3), 174–183.
+*Nature Reviews Psychology*, *1*(3), 174--183.
 https://doi.org/10.1038/s44159-022-00025-3
 
-Jones, S.
-D., & Brandt, S.
-(2020).
-Density and Distinctiveness in Early Word Learning: Evidence From Neural Network Simulations.
-_Cognitive Science_, _44_(1), e12812.
-https://osf.io/2qk5j/.
+Jones, S. D., & Brandt, S. (2020). Density and Distinctiveness in Early
+Word Learning: Evidence From Neural Network Simulations. *Cognitive
+Science*, *44*(1), e12812. https://osf.io/2qk5j/.
 https://doi.org/10.1111/cogs.12812
 
-Kassambara, A. (2021). _rstatix: Pipe-Friendly Framework for Basic Statistical Tests_ [R package   version 0.7.0]. https://CRAN.R-project.org/package=rstatix
-
-Kelley, T. A., & Yantis, S. (2009). Learning to attend: Effects of practice on information selection. _Journal of Vision_, _9_(7), 16. https://doi.org/10.1167/9.7.16
-
-Kerr, R., & Booth, B. (1978). Specific and varied practice of motor skill. _Perceptual and Motor Skills_, _46_(2), 395–401.
-
-Lamberts, K. (1994). Flexible Tuning of Similarity in Exemplar-Based Categorization. _Journal of Experimental Psychology: Learning, Memory, and Cognition_, _20_(5), 1003–1021.
-
-Lavan, N., Knight, S., Hazan, V., & McGettigan, C.
-(2019).
-The effects of high variability training on voice identity learning.
-_Cognition_, _193_, 104026.
-https://doi.org/10.1016/j.cognition.2019.104026
-
-Law, C.-T., & Gold, J. I. (2010). Shared Mechanisms of Perceptual Learning and Decision Making. _Topics in Cognitive Science_, _2_(2), 226–238. https://doi.org/10.1111/j.1756-8765.2009.01044.x
-
-Lee, J.
-C., Lovibond, P.
-F., & Hayes, B.
-K.
-(2019).
-Evidential diversity increases generalisation in predictive learning.
-_Quarterly Journal of Experimental Psychology_, _72_(11), 2647–2657.
+Kassambara, A. (2021). *rstatix: Pipe-Friendly Framework for Basic
+Statistical Tests* \[R package   version 0.7.0\].
+https://CRAN.R-project.org/package=rstatix
+
+Kelley, T. A., & Yantis, S. (2009). Learning to attend: Effects of
+practice on information selection. *Journal of Vision*, *9*(7), 16.
+https://doi.org/10.1167/9.7.16
+
+Kerr, R., & Booth, B. (1978). Specific and varied practice of motor
+skill. *Perceptual and Motor Skills*, *46*(2), 395--401.
+
+Lamberts, K. (1994). Flexible Tuning of Similarity in Exemplar-Based
+Categorization. *Journal of Experimental Psychology: Learning, Memory,
+and Cognition*, *20*(5), 1003--1021.
+
+Lavan, N., Knight, S., Hazan, V., & McGettigan, C. (2019). The effects
+of high variability training on voice identity learning. *Cognition*,
+*193*, 104026. https://doi.org/10.1016/j.cognition.2019.104026
+
+Law, C.-T., & Gold, J. I. (2010). Shared Mechanisms of Perceptual
+Learning and Decision Making. *Topics in Cognitive Science*, *2*(2),
+226--238. https://doi.org/10.1111/j.1756-8765.2009.01044.x
+
+Lee, J. C., Lovibond, P. F., & Hayes, B. K. (2019). Evidential diversity
+increases generalisation in predictive learning. *Quarterly Journal of
+Experimental Psychology*, *72*(11), 2647--2657.
 https://doi.org/10.1177/1747021819857065
 
-Logan, G. D. (1988). Toward an instance theory of automatization. _Psychological Review_, _95_(4), 492–527.
-
-Logan, G. D. (2002). An instance theory of attention and memory. _Psychological Review_, _109_(2), 376–400. https://doi.org/10.1037/0033-295X.109.2.376
-
-Maddox, W.
-T., & Filoteo, J.
-V.
-(2011).
-Stimulus range and discontinuity effects on information-integration category learning and generalization.
-_Attention, Perception, & Psychophysics_, _73_(4), 1279–1295.
+Logan, G. D. (1988). Toward an instance theory of automatization.
+*Psychological Review*, *95*(4), 492--527.
+
+Logan, G. D. (2002). An instance theory of attention and memory.
+*Psychological Review*, *109*(2), 376--400.
+https://doi.org/10.1037/0033-295X.109.2.376
+
+Maddox, W. T., & Filoteo, J. V. (2011). Stimulus range and discontinuity
+effects on information-integration category learning and generalization.
+*Attention, Perception, & Psychophysics*, *73*(4), 1279--1295.
 https://doi.org/10.3758/s13414-011-0101-2
 
-Marongelli, E., & Thoroughman, K.
-(2013).
-The advantage of flexible neuronal tunings in neural network models for motor learning.
-_Frontiers in Computational Neuroscience_, _7_, 100.
+Marongelli, E., & Thoroughman, K. (2013). The advantage of flexible
+neuronal tunings in neural network models for motor learning. *Frontiers
+in Computational Neuroscience*, *7*, 100.
 https://doi.org/10.3389/fncom.2013.00100
 
-McCracken, H. D., & Stelmach, G. E. (1977). A Test of the Schema Theory of Discrete Motor Learning. _Journal of Motor Behavior_, _9_(3), 193–201. https://doi.org/10.1080/00222895.1977.10735109
-
-Medin, D. L., & Schaffer, M. M. (1978). Context Theory of Classification Learning. _Psychological Review_, _85_(3), 207.
-
-Meigh, K.
-M., Shaiman, S., Tompkins, C.
-A., Abbott, K.
-V., & Nokes-Malach, T.
-(2018).
-What memory representation is acquired during nonword speech production learning?
-The influence of stimulus features and training modality on nonword encoding.
-_Cogent Psychology_, _5_(1), 1493714.
-https://doi.org/10.1080/23311908.2018.1493714
-
-Moxley, S. E. (1979). Schema: The Variability of Practice Hypothesis. _Journal of Motor Behavior_, _11_(1), 65–70. https://doi.org/10.1080/00222895.1979.10735173
-
-Newell, K. M. (2003). Schema Theory (1975): Retrospectives and Prospectives. _Research Quarterly for Exercise and Sport_, _74_(4), 383–388. https://doi.org/10.1080/02701367.2003.10609108
-
-Newell, K.
-M., & Shapiro, D.
-C.
-(1976).
-Variability of Practice and Transfer of Training: Some Evidence Toward a Schema View of Motor Learning.
-_Journal of Motor Behavior_, _8_(3), 233–243.
+McCracken, H. D., & Stelmach, G. E. (1977). A Test of the Schema Theory
+of Discrete Motor Learning. *Journal of Motor Behavior*, *9*(3),
+193--201. https://doi.org/10.1080/00222895.1977.10735109
+
+Medin, D. L., & Schaffer, M. M. (1978). Context Theory of Classification
+Learning. *Psychological Review*, *85*(3), 207.
+
+Meigh, K. M., Shaiman, S., Tompkins, C. A., Abbott, K. V., &
+Nokes-Malach, T. (2018). What memory representation is acquired during
+nonword speech production learning? The influence of stimulus features
+and training modality on nonword encoding. *Cogent Psychology*, *5*(1),
+1493714. https://doi.org/10.1080/23311908.2018.1493714
+
+Moxley, S. E. (1979). Schema: The Variability of Practice Hypothesis.
+*Journal of Motor Behavior*, *11*(1), 65--70.
+https://doi.org/10.1080/00222895.1979.10735173
+
+Newell, K. M. (2003). Schema Theory (1975): Retrospectives and
+Prospectives. *Research Quarterly for Exercise and Sport*, *74*(4),
+383--388. https://doi.org/10.1080/02701367.2003.10609108
+
+Newell, K. M., & Shapiro, D. C. (1976). Variability of Practice and
+Transfer of Training: Some Evidence Toward a Schema View of Motor
+Learning. *Journal of Motor Behavior*, *8*(3), 233--243.
 https://doi.org/10.1080/00222895.1976.10735077
 
-North, J.
-S., Bezodis, N.
-E., Murphy, C.
-P., Runswick, O.
-R., Pocock, C., & Roca, A.
-(2019).
-The effect of consistent and varied follow-through practice schedules on learning a table tennis backhand.
-_Journal of Sports Sciences_, _37_(6), 613–620.
+North, J. S., Bezodis, N. E., Murphy, C. P., Runswick, O. R., Pocock,
+C., & Roca, A. (2019). The effect of consistent and varied
+follow-through practice schedules on learning a table tennis backhand.
+*Journal of Sports Sciences*, *37*(6), 613--620.
 https://doi.org/10.1080/02640414.2018.1522683
 
-Nosofsky, R. M. (1986). Attention, similarity, and the identification-categorization relationship. _Journal of Experimental Psychology: General_, _115_(1), 39–57.
-
-Nosofsky, R. M. (1992). Similarity scaling and cognitive process models. _Annual Review of Psychology_, _43_(1), 25–53.
-
-Nosofsky, R. M., & Johansen, M. K. (2000). Exemplar-based accounts of “multiple-system” phenomena in perceptual categorization. _Psychonomic Bulletin & Review_, _7_(3), 375–402.
-
-Nosofsky, R.
-M., Sanders, C.
-A., Zhu, X., & McDaniel, M.
-A.
-(2018).
-Model-guided search for optimal natural-science-category training exemplars: A work in progress.
-_Psychonomic Bulletin & Review_, _26_(1), 48–76.
-https://doi.org/10.3758/s13423-018-1508-8
-
-Op de Beeck, H.
-P., Wagemans, J., & Vogels, R.
-(2008).
-The representation of perceived shape similarity and its role for category learning in monkeys: A modeling study.
-_Vision Research_, _48_(4), 598–610.
-https://doi.org/10.1016/j.visres.2007.11.019
-
-Palmeri, T. J. (1997). Exemplar Similarity and the Development of Automaticity. _Journal of Experimental Psychology: Human Learning and Memory_, _23_(2), 324–354.
-
-Perry, L.
-K., Samuelson, L.
-K., Malloy, L.
-M., & Schiffer, R.
-N.
-(2010).
-Learn Locally, Think Globally: Exemplar Variability Supports Higher-Order Generalization and Word Learning.
-_Psychological Science_, _21_(12), 1894–1902.
-https://doi.org/10.1177/0956797610389189
-
-Pigott, R.
-E., & Shapiro, D.
-C.
-(1984).
-Motor Schema: The Structure of the Variability Session.
-_Research Quarterly for Exercise and Sport_, _55_(1), 41–45.
-https://doi.org/10.1080/02701367.1984.10605353
-
-Poldrack, R.
-A., Selco, S.
-L., Field, J.
-E., & Cohen, N.
-J.
-(1999).
-The relationship between skill learning and repetition priming: Experimental and computational analyses.
-_Journal of Experimental Psychology: Learning, Memory, and Cognition_, _25_(1), 208–235.
+Nosofsky, R. M. (1986). Attention, similarity, and the
+identification-categorization relationship. *Journal of Experimental
+Psychology: General*, *115*(1), 39--57.
+
+Nosofsky, R. M. (1992). Similarity scaling and cognitive process models.
+*Annual Review of Psychology*, *43*(1), 25--53.
+
+Nosofsky, R. M., & Johansen, M. K. (2000). Exemplar-based accounts of
+"multiple-system" phenomena in perceptual categorization. *Psychonomic
+Bulletin & Review*, *7*(3), 375--402.
+
+Nosofsky, R. M., Sanders, C. A., Zhu, X., & McDaniel, M. A. (2018).
+Model-guided search for optimal natural-science-category training
+exemplars: A work in progress. *Psychonomic Bulletin & Review*, *26*(1),
+48--76. https://doi.org/10.3758/s13423-018-1508-8
+
+Op de Beeck, H. P., Wagemans, J., & Vogels, R. (2008). The
+representation of perceived shape similarity and its role for category
+learning in monkeys: A modeling study. *Vision Research*, *48*(4),
+598--610. https://doi.org/10.1016/j.visres.2007.11.019
+
+Palmeri, T. J. (1997). Exemplar Similarity and the Development of
+Automaticity. *Journal of Experimental Psychology: Human Learning and
+Memory*, *23*(2), 324--354.
+
+Perry, L. K., Samuelson, L. K., Malloy, L. M., & Schiffer, R. N. (2010).
+Learn Locally, Think Globally: Exemplar Variability Supports
+Higher-Order Generalization and Word Learning. *Psychological Science*,
+*21*(12), 1894--1902. https://doi.org/10.1177/0956797610389189
+
+Pigott, R. E., & Shapiro, D. C. (1984). Motor Schema: The Structure of
+the Variability Session. *Research Quarterly for Exercise and Sport*,
+*55*(1), 41--45. https://doi.org/10.1080/02701367.1984.10605353
+
+Poldrack, R. A., Selco, S. L., Field, J. E., & Cohen, N. J. (1999). The
+relationship between skill learning and repetition priming: Experimental
+and computational analyses. *Journal of Experimental Psychology:
+Learning, Memory, and Cognition*, *25*(1), 208--235.
 https://doi.org/10.1037/0278-7393.25.1.208
 
-Posner, M. I., & Keele, S. W. (1968). On the genesis of abstract ideas. _Journal of Experimental Psychology_, _77_(3), 353–363.
-
-R Core Team. (2020). _R: A Language and Environment for Statistical Computing_. R: A Language and Environment for Statistical Computing. https://www.R-project.org/
-
-Roark, C.
-L., Paulon, G., Sarkar, A., & Chandrasekaran, B.
-(2021).
-Comparing perceptual category learning across modalities in the same individuals.
-_Psychonomic Bulletin & Review_, _28_(3), 898–909.
-https://osf.io/htwdk/.
-https://doi.org/10.3758/s13423-021-01878-0
-
-Roller, C.
-A., Cohen, H.
-S., Kimball, K.
-T., & Bloomberg, J.
-J.
-(2001).
+Posner, M. I., & Keele, S. W. (1968). On the genesis of abstract ideas.
+*Journal of Experimental Psychology*, *77*(3), 353--363.
+
+R Core Team. (2020). *R: A Language and Environment for Statistical
+Computing*. R: A Language and Environment for Statistical Computing.
+https://www.R-project.org/
+
+Roark, C. L., Paulon, G., Sarkar, A., & Chandrasekaran, B. (2021).
+Comparing perceptual category learning across modalities in the same
+individuals. *Psychonomic Bulletin & Review*, *28*(3), 898--909.
+https://osf.io/htwdk/. https://doi.org/10.3758/s13423-021-01878-0
+
+Roller, C. A., Cohen, H. S., Kimball, K. T., & Bloomberg, J. J. (2001).
 Variable practice with lenses improves visuo-motor plasticity.
-_Cognitive Brain Research_, _12_(2), 341–352.
+*Cognitive Brain Research*, *12*(2), 341--352.
 https://doi.org/10.1016/S0926-6410(01)00077-5
 
-Rosenbaum, D.
-A., Carlson, R.
-A., & Gilmore, R.
-O.
-(2001).
-Acquisition of Intellectual and Perceptual-Motor Skills.
-_Annual Review of Psychology_, _52_(1), 453–470.
+Rosenbaum, D. A., Carlson, R. A., & Gilmore, R. O. (2001). Acquisition
+of Intellectual and Perceptual-Motor Skills. *Annual Review of
+Psychology*, *52*(1), 453--470.
 https://doi.org/10.1146/annurev.psych.52.1.453
 
-Rosenbaum, D. A., Loukopoulos, L. D., Meulenbroek, R. G., Vaughan, J., & Engelbrecht, S. E. (1995). Planning reaches by evaluating stored postures. _Psychological Review_, _102_(1), 28.
-
-Sabah, K., Dolk, T., Meiran, N., & Dreisbach, G.
-(2019).
-When less is more: Costs and benefits of varied vs.
-fixed content and structure in short-term task switching training.
-_Psychological Research_, _83_(7), 1531–1542.
-https://doi.org/10.1007/s00426-018-1006-7
-
-Sadakata, M., & McQueen, J.
-M.
-(2014).
-Individual aptitude in Mandarin lexical tone perception predicts effectiveness of high-variability training.
-_Frontiers in Psychology_, _5_, 1318.
+Rosenbaum, D. A., Loukopoulos, L. D., Meulenbroek, R. G., Vaughan, J., &
+Engelbrecht, S. E. (1995). Planning reaches by evaluating stored
+postures. *Psychological Review*, *102*(1), 28.
+
+Sabah, K., Dolk, T., Meiran, N., & Dreisbach, G. (2019). When less is
+more: Costs and benefits of varied vs. fixed content and structure in
+short-term task switching training. *Psychological Research*, *83*(7),
+1531--1542. https://doi.org/10.1007/s00426-018-1006-7
+
+Sadakata, M., & McQueen, J. M. (2014). Individual aptitude in Mandarin
+lexical tone perception predicts effectiveness of high-variability
+training. *Frontiers in Psychology*, *5*, 1318.
 https://doi.org/10.3389/fpsyg.2014.01318
 
-Sakamoto, Y., Love, B.
-C., & Jones, M.
-(2006).
-Tracking Variability in Learning: Contrasting Statistical and Similarity-Based Accounts.
-_Proceedings of the 28th Annual Conference of the Cognitive Science Society.
-Vancouver, Canada: Cognitive Science Society_.
-
-Schmidt, R. A. (1975). A schema theory of discrete motor skill learning. _Psychological Review_, _82_(4), 225–260. https://doi.org/10.1037/h0076770
-
-Seow, R.
-Y.
-T., Betts, S., & Anderson, J.
-R.
-(2019).
-Transfer effects of varied practice and adaptation to changes in complex skill acquisition.
-_Proceedings of the 17th International Conference on Cognitive Modelling_, 222–227.
-
-Shepard, R. N. (1987). Toward a universal law of generalization for psychological science. _Science_, _237_(4820), 1317–1323.
-
-Sinkeviciute, R., Brown, H., Brekelmans, G., & Wonnacott, E.
-(2019).
-The role of input variability and learner age in second language vocabulary learning.
-_Studies in Second Language Acquisition_, _41_(04), 795–820.
+Sakamoto, Y., Love, B. C., & Jones, M. (2006). Tracking Variability in
+Learning: Contrasting Statistical and Similarity-Based Accounts.
+*Proceedings of the 28th Annual Conference of the Cognitive Science
+Society. Vancouver, Canada: Cognitive Science Society*.
+
+Schmidt, R. A. (1975). A schema theory of discrete motor skill learning.
+*Psychological Review*, *82*(4), 225--260.
+https://doi.org/10.1037/h0076770
+
+Seow, R. Y. T., Betts, S., & Anderson, J. R. (2019). Transfer effects of
+varied practice and adaptation to changes in complex skill acquisition.
+*Proceedings of the 17th International Conference on Cognitive
+Modelling*, 222--227.
+
+Shepard, R. N. (1987). Toward a universal law of generalization for
+psychological science. *Science*, *237*(4820), 1317--1323.
+
+Sinkeviciute, R., Brown, H., Brekelmans, G., & Wonnacott, E. (2019). The
+role of input variability and learner age in second language vocabulary
+learning. *Studies in Second Language Acquisition*, *41*(04), 795--820.
 https://doi.org/10.1017/S0272263119000263
 
-Soderstrom, N. C., & Bjork, R. A. (2015). Learning versus performance: An integrative review. _Perspectives on Psychological Science_, _10_(2), 176–199.
-
-Taylor, J., & Ivry, R. (2013). Context-dependent generalization. _Frontiers in Human Neuroscience_, _7_, 171. https://doi.org/10.3389/fnhum.2013.00171
-
-Thoroughman, K. A., & Taylor, J. A. (2005). Rapid Reshaping of Human Motor Generalization. _Journal of Neuroscience_, _25_(39), 8948–8953. https://doi.org/10.1523/JNEUROSCI.1771-05.2005
-
-Twomey, K. E., Ma, L., & Westermann, G. (2018). All the Right Noises: Background Variability Helps Early Word Learning. _Cognitive Science_, _42_(S2), 413–438. https://doi.org/10.1111/cogs.12539
-
-van Dam, L.
-C.
-J., & Ernst, M.
-O.
-(2015).
-Mapping Shape to Visuomotor Mapping: Learning and Generalisation of Sensorimotor Behaviour Based on Contextual Information.
-_PLOS Computational Biology_, _11_(3), e1004172.
+Soderstrom, N. C., & Bjork, R. A. (2015). Learning versus performance:
+An integrative review. *Perspectives on Psychological Science*, *10*(2),
+176--199.
+
+Taylor, J., & Ivry, R. (2013). Context-dependent generalization.
+*Frontiers in Human Neuroscience*, *7*, 171.
+https://doi.org/10.3389/fnhum.2013.00171
+
+Thoroughman, K. A., & Taylor, J. A. (2005). Rapid Reshaping of Human
+Motor Generalization. *Journal of Neuroscience*, *25*(39), 8948--8953.
+https://doi.org/10.1523/JNEUROSCI.1771-05.2005
+
+Twomey, K. E., Ma, L., & Westermann, G. (2018). All the Right Noises:
+Background Variability Helps Early Word Learning. *Cognitive Science*,
+*42*(S2), 413--438. https://doi.org/10.1111/cogs.12539
+
+van Dam, L. C. J., & Ernst, M. O. (2015). Mapping Shape to Visuomotor
+Mapping: Learning and Generalisation of Sensorimotor Behaviour Based on
+Contextual Information. *PLOS Computational Biology*, *11*(3), e1004172.
 https://doi.org/10.1371/journal.pcbi.1004172
 
-Van Rossum, J.
-H.
-A.
-(1990).
-Schmidt’s schema theory: The empirical base of the variability of practice hypothesis.
-_Human Movement Science_, _9_(3–5), 387–435.
-https://doi.org/10.1016/0167-9457(90)90010-B
-
-Vigo, R., Doan, K.-M.
-C., Doan, C.
-A., & Pinegar, S.
-(2018).
-On the learning difficulty of visual and auditory modal concepts: Evidence for a single processing system.
-_Cognitive Processing_, _19_(1), 1–16.
+Van Rossum, J. H. A. (1990). Schmidt's schema theory: The empirical base
+of the variability of practice hypothesis. *Human Movement Science*,
+*9*(3--5), 387--435. https://doi.org/10.1016/0167-9457(90)90010-B
+
+Vigo, R., Doan, K.-M. C., Doan, C. A., & Pinegar, S. (2018). On the
+learning difficulty of visual and auditory modal concepts: Evidence for
+a single processing system. *Cognitive Processing*, *19*(1), 1--16.
 https://doi.org/10.1007/s10339-017-0840-7
 
-Wall, L., Gunawan, D., Brown, S.
-D., Tran, M.-N., Kohn, R., & Hawkins, G.
-E.
-(2021).
-Identifying relationships between cognitive processes across tasks, contexts, and time.
-_Behavior Research Methods_, _53_(1), 78–95.
-https://doi.org/10.3758/s13428-020-01405-4
-
-Wifall, T., Buss, A.
-T., Farmer, T.
-A., Spencer, J.
-P., & Hazeltine, E.
-(2017).
-Reaching into response selection: Stimulus and response similarity influence central operations.
-_Journal of Experimental Psychology: Human Perception and Performance_, _43_(3), 555–568.
+Wall, L., Gunawan, D., Brown, S. D., Tran, M.-N., Kohn, R., & Hawkins,
+G. E. (2021). Identifying relationships between cognitive processes
+across tasks, contexts, and time. *Behavior Research Methods*, *53*(1),
+78--95. https://doi.org/10.3758/s13428-020-01405-4
+
+Wifall, T., Buss, A. T., Farmer, T. A., Spencer, J. P., & Hazeltine, E.
+(2017). Reaching into response selection: Stimulus and response
+similarity influence central operations. *Journal of Experimental
+Psychology: Human Perception and Performance*, *43*(3), 555--568.
 https://doi.org/10.1037/xhp0000301
 
-Willey, C. R., & Liu, Z. (2018). Long-term motor learning: Effects of varied and specific practice. _Vision Research_, _152_, 10–16. https://doi.org/10.1016/j.visres.2017.03.012
-
-Wonnacott, E., Boyd, J.
-K., Thomson, J., & Goldberg, A.
-E.
-(2012).
-Input effects on the acquisition of a novel phrasal construction in 5year olds.
-_Journal of Memory and Language_, _66_(3), 458–478.
+Willey, C. R., & Liu, Z. (2018). Long-term motor learning: Effects of
+varied and specific practice. *Vision Research*, *152*, 10--16.
+https://doi.org/10.1016/j.visres.2017.03.012
+
+Wonnacott, E., Boyd, J. K., Thomson, J., & Goldberg, A. E. (2012). Input
+effects on the acquisition of a novel phrasal construction in 5year
+olds. *Journal of Memory and Language*, *66*(3), 458--478.
 https://doi.org/10.1016/j.jml.2011.11.004
 
-Wrisberg, C.
-A., Winter, T.
-P., & Kuhlman, J.
-S.
-(1987).
-The Variability of Practice Hypothesis: Further Tests and Methodological Discussion.
-_Research Quarterly for Exercise and Sport_, _58_(4), 369–374.
+Wrisberg, C. A., Winter, T. P., & Kuhlman, J. S. (1987). The Variability
+of Practice Hypothesis: Further Tests and Methodological Discussion.
+*Research Quarterly for Exercise and Sport*, *58*(4), 369--374.
 https://doi.org/10.1080/02701367.1987.10608114
 
-Wu, C.
-M., Schulz, E., Garvert, M.
-M., Meder, B., & Schuck, N.
-W.
-(2020).
-Similarities and differences in spatial and non-spatial cognitive maps.
-_PLOS Computational Biology_, _16_(9).
+Wu, C. M., Schulz, E., Garvert, M. M., Meder, B., & Schuck, N. W.
+(2020). Similarities and differences in spatial and non-spatial
+cognitive maps. *PLOS Computational Biology*, *16*(9).
 https://github.com/charleywu/cognitivemaps.
@@
 
-Wulf, G. (1991). The effect of type of practice on motor learning in children. _Applied Cognitive Psychology_, _5_(2), 123–134. https://doi.org/10.1002/acp.2350050206
-
-Yang, J., Yan, F.-F., Chen, L., Xi, J., Fan, S., Zhang, P., Lu, Z.-L., & Huang, C.-B.
-(2020).
-General learning ability in perceptual learning.
-_Proceedings of the National Academy of Sciences_, _117_(32), 19092–19100.
-https://doi.org/10.1073/pnas.2002903117
-
-Zaman, J., Chalkia, A., Zenses, A.-K., Bilgin, A.
-S., Beckers, T., Vervliet, B., & Boddez, Y.
-(2021).
-Perceptual variability: Implications for learning and generalization.
-_Psychonomic Bulletin & Review_, _28_(1), 1–19.
-https://doi.org/10.3758/s13423-020-01780-1
+Wulf, G. (1991). The effect of type of practice on motor learning in
+children. *Applied Cognitive Psychology*, *5*(2), 123--134.
+https://doi.org/10.1002/acp.2350050206
+
+Yang, J., Yan, F.-F., Chen, L., Xi, J., Fan, S., Zhang, P., Lu, Z.-L., &
+Huang, C.-B. (2020). General learning ability in perceptual learning.
+*Proceedings of the National Academy of Sciences*, *117*(32),
+19092--19100. https://doi.org/10.1073/pnas.2002903117
+
+Zaman, J., Chalkia, A., Zenses, A.-K., Bilgin, A. S., Beckers, T.,
+Vervliet, B., & Boddez, Y. (2021). Perceptual variability: Implications
+for learning and generalization. *Psychonomic Bulletin & Review*,
+*28*(1), 1--19. https://doi.org/10.3758/s13423-020-01780-1

### 2023-10-10 IGAS.qmd
update IGAS bibliography

@@
 prompt the retrieval of whichever preexisting prototype was most similar
-@posnerGenesisAbstractIdeas1968 [Posner & Keele, 1968]. Prototype
+[@posnerGenesisAbstractIdeas1968]. Prototype
 models were later challenged by the success of instance-based or
@@
 advantage of not assuming the explicit construction of an internal
-prototype @estesArrayModelsCategory1986;
+prototype [@estesArrayModelsCategory1986;
 @hintzmanMINERVASimulationModel1984;
@@
 Instance-based approaches have had some success accounting for
-performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999]; @wifallPerceptualSimilarityAffects.@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters
-composing the training words to a pre-specified letter set. Following
+performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017; @crumpEpisodicContributionsSequential2010] trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
+Following
 training, typing speed was tested on previously experienced words
@@
 identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
-sports training  [@greenPracticeVariabilityTransfer1995; @northEffectConsistentVaried2019], and training
+sports training  [@greenPracticeVariabilityTransfer1995; @greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
 on a complex video game [@seowTransferEffectsVaried2019].
@@
 within the domain of visuomotor skill learning. Much of this research
-has been influenced by the work of Schmidt (1975), who proposed a
+has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a
 schema-based account of motor learning as an attempt to address the
@@
 varied-trained group are then attributed to the variation they received
-during training, a finding observed in numerous studies (Catalano &
-Kleiner, 1984; Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth,
-1978; Wulf, 1991), and the benefits of this variation are typically
+during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically
 thought to be mediated by the development of a more general schema for
@@
 beneficial. Numerous studies have found null, or in some cases negative
-effects of training variation (DeLosh et al., 1997; Sinkeviciute et al.,
-2019; Wrisberg et al., 1987), and many more have suggested that the
+effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the
 benefits of variability may depend on additional factors such as prior
 task experience, the order of training trials, or the type of transfer
-being measured (Berniker et al., 2014; Braithwaite & Goldstone, 2015;
-Hahn et al., 2005; Lavan et al., 2019; North et al., 2019; Sadakata &
-McQueen, 2014; Zaman et al., 2021).
+being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
 
@@
 found, leading some researchers to question the veracity of the
-variability of practice hypothesis (Newell, 2003; Van Rossum, 1990).
+variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
 Critics have also pointed out that investigations of the effects of
@@
 similarity is typically best described as either a Gaussian or
-exponentially decaying function of psychological distance (Ennis et al.,
-1988; Ghahramani et al., 1996; Logan, 1988; Nosofsky, 1992; Shepard,
-1987; Thoroughman & Taylor, 2005), it is plausible that a subset of the
+exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the
 most similar training instances could have a disproportionate impact on
@@
 the visuomotor skill learning literature also rarely considers
-alternatives to schema representations (Chamberlin & Magill, 1992).
+alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
 Although schema-theory remains influential within certain literatures,
 instance or exemplar-based models have accounted for human behavior
-across myriad domains (Jamieson et al., 2022; Logan, 2002). As mentioned
-above, instance based accounts have been shown to perform well on a
-variety of different tasks with motoric components (Crump & Logan, 2010;
-Gandolfo et al., 1996; Meigh et al., 2018; Rosenbaum et al., 1995; van
-Dam & Ernst, 2015). However, such accounts have received little
+across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a]. As mentioned above, instance based accounts have been shown to perform well on a
+variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
+However, such accounts have received little
 attention within the subdomain of visuomotor skill learning focused on
@@
 constant conditions following training on an accuracy based projectile
-launching task (Chua et al., 2019; Goodwin et al., 1998; Kerr & Booth,
-1978; Wulf, 1991). We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package (Faul et al.,
+launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
+We then averaged effects across these studies,
+yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
 2009) was then used to determine that a power of 80% requires a sample
@@
 Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021).
+rstatix package (Kassambara, 2021)****.
 
@@
 between groups in the supplementary analyses, were fit using the TEfit
-package in R (Cochrane, 2020).
+package in R [@cochraneTEfitsNonlinearRegression2020].
 
@@
 common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions
-(Catalano & Kleiner, 1984; Wrisberg et al., 1987), which has been
+performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
 suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing (Soderstrom & Bjork, 2015). However
+retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
 our finding of no difference in training performance between constant
-and varied groups has been observed in previous work (Chua et al., 2019;
-Moxley, 1979; Pigott & Shapiro, 1984).
+and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
 
@@
 learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory (Catalano & Kleiner, 1984; Chua et
-al., 2019; Goodwin et al., 1998; McCracken & Stelmach, 1977; Moxley,
-1979; Newell & Shapiro, 1976; Pigott & Shapiro, 1984; Roller et al.,
-2001; Schmidt, 1975; Willey & Liu, 2018; Wrisberg et al., 1987; Wulf,
-1991). We also join a much smaller set of research to observe this
-pattern in a computerized task (Seow et al., 2019). One departure from
+Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
+We also join a much smaller set of research to observe this
+pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
 the experiment 1 findings concerns the pattern wherein the varied group
@@
 significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature (Goode et al., 2008; Kerr & Booth, 1978),
+elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
 the overall evidence for this effect appears to be far weaker than for
@@
 Gaussian similarity gradient. Then, as per an instance-based model of
-similarity (Logan, 2002; Nosofsky, 1992), these distances were
+similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
 multiplied by a sensitivity parameter, c, and then exponentiated to
@@
 captured by fitting the generalization parameter of an instance-based
-model separately to each group (Hahn et al., 2005; Lamberts, 1994).
-Relatedly, the influential Bayesian generalization model developed by
-Tenenbaum & Griffiths (2001) predicts that the breadth of generalization
+model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
+Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
 will increase when a rational agent encounters a wider variety of
@@
 specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience (Nosofsky & Johansen, 2000;
-Sakamoto et al., 2006). If one's training experience is relatively
+the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
 variable, as with the variable training condition, then one might infer
@@
 participants outperform constant-trained participants even from
-conditions identical to the constant group training (Goode et al., 2008;
-Green et al., 1995; Kerr & Booth, 1978). In experiment 1 varied
+conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
 participants performed significantly better on this identity comparison.
@@
 generalization gradient based on prior experience does have precedent in
-the domains of category learning (Aha & Goldstone, 1992; Briscoe &
-Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al.,
-2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013;
-Taylor & Ivry, 2013; Thoroughman & Taylor, 2005). Lamberts (1994) showed
+the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
+@lambertsFlexibleTuningSimilarity1994 showed
 that a simple manipulation of background knowledge during a
@@
 for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability (Hahn et
-al., 2005; Sakamoto et al., 2006). However, to the best of our
+trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006]. However, to the best of our
 knowledge, IGAS is the first instance-based similarity model that has
@@
 certain aspects of learning and generalization may operate under common
-principles across different tasks and domains. (Censor et al., 2012; Cox
-et al., 2018; Hills et al., 2010; Jamieson et al., 2022; Law & Gold,
-2010; Roark et al., 2021; Rosenbaum et al., 2001; Vigo et al., 2018;
-Wall et al., 2021; Wu et al., 2020; Yang et al., 2020).
+principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001a; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
 
@@
 -- though as described in the introduction there is some evidence in
-support of this idea (Chamberlin & Magill, 1992; Crump & Logan, 2010;
-Hommel, 1998; Meigh et al., 2018; Poldrack et al., 1999). A particularly
+support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
+A particularly
 noteworthy instance-based model of sensory-motor behavior is the
-Knowledge II model of Rosenbaum and colleagues (Cohen & Rosenbaum, 2004;
-Rosenbaum et al., 1995). Knowledge II explicitly defines instances as
+Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995]. Knowledge II explicitly defines instances as
 postures (joint combinations), and is thus far more detailed than IGAS
@@
 Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task (Catalano &
-Kleiner, 1984). In this task, participants observe a series of lamps
+the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
 lighting up consecutively, and attempt to time a button press with the
@@
 can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested (Wrisberg et al.,
-1987). Our study alleviates such concerns by explicitly controlling for
+trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
 similarity.
@@
 into the psychological dimensions more reflective of the actual human
-representations (Nosofsky, 1992; Shepard, 1987). Such scaling typically
-entails having participants rate the similarity between individual items
+representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
 and using these similarity judgements to then compute the psychological
@@
 
-# References
+## References
 

### 2023-10-10 HTW.qmd

---
title: HTW Project
date: last-modified
page-layout: full
bibliography: "Bib/HTW.bib"
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

```{r}
pacman::p_load(tidyverse,knitr,kableExtra)

```

# Introduction

In project 1, we applied model-based techniques to quantify and control for the
similarity between training and testing experience, which in turn enabled us to
account for the difference between varied and constant training via an extended
version of a similarity based generalization model. In project 2, we will go a
step further, implementing a full process model capable of both 1) producing
novel responses and 2) modeling behavior in both the learning and testing stages
of the experiment. Project 2 also places a greater emphasis on extrapolation performance following
training - as varied training has often been purported to be particularly beneficial in such situations. Extrapolation has long been a focus of the literature on function learning [@brehmerHypothesesRelationsScaled1974;
@carrollFunctionalLearningLearning1963]. Central questions of the function learning literature have included the relative difficulties of learning various functional forms (e.g. linear vs.bilinear vs. quadratic), and the relative
effectiveness of rule-based vs. association-based exemplar models vs. various hybrid models
[@bottNonmonotonicExtrapolationFunction2004;
@deloshExtrapolationSineQua1997; @jonesActiveFunctionLearning2018;
@kalishPopulationLinearExperts2004; @mcdanielConceptualBasisFunction2005;
@mcdanielPredictingTransferPerformance2009]. However the issue of training variation has received surprisingly little attention in this area.

# Methods

## Participants

Data was collected from 647 participants (after exclusions). The results shown
below consider data from subjects in our initial experiment, which consisted of
196 participants (106 constant, 90 varied). The follow-up experiments entailed
minor manipulations: 1) reversing the velocity bands that were trained on vs.
novel during testing; 2) providing ordinal rather than numerical feedback during
training (e.g. correct, too low, too high). The data from these subsequent
experiments are largely consistently with our initial results shown below.

## Task

We developed a novel visuomotor extrapolation task, termed the ["Hit The Wall"
(HTW]{.underline}) task, wherein participants learned to launch a projectile
such that it hit a rectangle at the far end of the screen with an appropriate
amount of force. Although the projectile had both x and y velocity components,
only the x-dimension was relevant for the task.\ 
[Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}

## Design

1)  90 training trials split evenly divided between velocity bands.
    Varied training with 3 velocity bands and Constant training with 1
    band.

2)  No-feedback testing from 3 novel extrapolation bands. 15 trials
    each.

3)  No-feedbacd testing from the 3 bands used during the training phase
    (2 of which were novel for the constant group). 9 trials each.

4)  Feedback testing for each of the 3 extrapolation bands. 10 trials
    each.

```{r design, echo=FALSE, fig.cap="Experiment Procedure"}
DiagrammeR::grViz("digraph {
graph [layout = dot, rankdir = LR]
# define the global styles of the nodes. We can override these in box if we wish
node [shape = rectangle, style = filled, fillcolor = Linen]
data1 [label = <<b>Varied Training</b>  
<br ALIGN = 'LEFT' /> 800-1000
<br/> 1000-1200
<br/>1200-1400>]
data2 [label = <<b>Constant Training</b>  
<br/> 800-1000 >]
Test1 [label = <<b>Testing - No Feedback</b>  
<br ALIGN = 'LEFT' /> 100-300
<br/> 350-550
<br/>600-800>]
Test2 [label = <<b>Test From Train</b>  
<br ALIGN = 'LEFT' /> 800-1000
<br/> 1000-1200
<br/>1200-1400>]
Test3[label = <<b>Testing -Feedback</b>  
<br ALIGN = 'LEFT' /> 100-300
<br/> 350-550
<br/>600-800>]

# edge definitions with the node IDs
{data1 data2}  -> Test1 -> Test2 -> Test3
}
",width=700,height=250)

```

<!-- {.tabset} -->

# Results

## Training

Training performance is shown in Results Figure 2A. All groups show improvement
from each of their training velocity-bands (i.e. decreasing average distance from
target). In the velocity band trained at by both groups (800-1000), the constant
group maintains a superior level of performance from the early through the final
stages of training. This difference is unsurprising given that the constant
group had 3x more practice trials from that band.

```{r Training, echo=FALSE,fig.height=5.0, fig.width=7}
#| eval: false
#fig.cap="\\label{fig:figs}training performance"
nbins=8
t1=dt%>% mutate(Trial.Bin=cut(trial,breaks=nbins,labels=FALSE)) %>%  
  group_by(sbjCode,condit,throwCategory,Trial.Bin) %>% summarise(dist=mean(dist),.groups = 'keep') %>%
   ggplot(aes(Trial.Bin,dist,color=throwCategory,group=throwCategory))+
  lineBars+
  facet_wrap(~condit)+
  scale_x_continuous(breaks=seq(1,nbins))+
  ylab("Mean Distance From Target Velocity")+xlab("Training Block")+
  scale_color_discrete(name="Velocity Band")+
  labs(title="Hit The Wall - Training Performance",
       caption="2A. Training Performance for both groups – binned into 8 blocks." )+
  theme(plot.caption=element_text(hjust=0,face="italic"),
        plot.title=element_text(face="bold"),
        axis.title.x=element_text(face="bold"),
        axis.title.y=element_text(face="bold"))

t1

```

## Testing

For evaluating testing performance, we consider 3 separate metrics. 1)
The average absolute deviation from the correct velocity, 2) The % of
throws in which the wall was hit with the correct velocity and 3) The
average x velocity produced.

Results Figure 2B shows the average velocity produced for all 6 bands
that were tested. At least at the aggregate level, both conditions were
able to differentiate all 6 bands in the correct order, despite only
having received training feedback for 1/6 (constant) or 3/6 (varied)
bands during training. Participants in both groups also had a bias
towards greatly overestimating the correct velocity for band 100-300,
for which both groups had an average of greater than 500.

```{r Testing Vx, fig.height=9, fig.width=10.5 }
#| eval: false

sumStats = dtest %>% group_by(sbjCode,vbLabel,condit,throwCategory) %>%
  summarise(vxMean=mean(vxCapped),vxMedian=median(vxCapped),vxSd=sd(vxCapped),.groups = 'keep') %>%group_by(vbLabel,condit,throwCategory) %>%
  summarise(groupMean=round(mean(vxMean),0),groupMedian=round(mean(vxMedian),0),groupSd=round(mean(vxSd,na.rm=TRUE),0),.groups = 'keep') %>%
  mutate(meanLab=paste0("Mean=",groupMean),medianLab=paste0("Median=",groupMedian),sdLab=paste0("Sd=",groupSd)) %>%
  mutate(sumStatLab=paste0(meanLab,"\n",medianLab,"\n",sdLab))

fig2aCap=str_wrap("Figure 2B: Bands 100-300, 350-550 and 600-800 are novel extrapolations for both groups. Band 800-1000 was a training band for both groups. Bands 1000-1200, and 1200-1400 were trained for the varied group, and novel for the constant group.  Top figure displays mean deviation from correct velocity. Bottom figure displays the average % of trials where participants hit the wall with the correct velocity. Error bars indicate standard error of the mean. " ,width=170)

dtest %>% group_by(sbjCode,vbLabel,condit,throwCategory) %>%
  summarise(vxMean=mean(vxCapped),lowBound=first(bandInt),highBound=first(highBound),
            vbLag=first(vbLag),vbLead=first(vbLead),.groups = 'keep') %>%
  ggplot(aes(x=vbLabel,y=vxMean,fill=throwCategory))+
  geom_half_violin(color=NA)+ # remove border color
  geom_half_boxplot(position=position_nudge(x=-0.05),side="r",outlier.shape = NA,center=TRUE,
                    errorbar.draw = FALSE,width=.25)+
  geom_half_point(transformation = position_jitter(width = 0.05, height = 0.05),size=.3,aes(color=throwCategory))+
  facet_wrap(~condit,scale="free_x")+
  geom_rect(data=vbRect,aes(xmin=vbLag,xmax=vbLead,ymin=lowBound,ymax=highBound,fill=throwCategory),alpha=.3)+
  geom_text(data=sumStats,aes(y=2090,label = sumStatLab),size=2.5)+
  bandLines4+
  #geom_text(data=sumStats,aes(x=throwCategory,y=2100,label = groupMean),size=2, vjust = -0.5)+
  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2))+
  scale_fill_discrete(name="Velocity Band")+
  scale_color_discrete(guide="none")+  # remove extra legend
  theme(legend.position='none',
        plot.title=element_text(face="bold"),
        axis.title.x=element_text(face="bold"),
        axis.title.y=element_text(face="bold"),
        axis.text.x = element_text(size = 7.5))+
  ylab("Mean X Velocity")+xlab("Target Velocity Band") +
   labs(title="2B. Testing Performance (no-feedback) - X-Velocity Per Band",
        caption=fig2aCap)+
  theme(plot.caption=element_text(hjust=0,face="italic"))

```

As is reflected in Results Figure 2C, the constant group performed
significantly better than the varied group at the 3 testing bands of
greatest interest. Both groups tended to perform worse for testing bands
further away from their training conditions. The varied group had a
slight advantage for bands 1000-1200 and 1200-1400, which were repeats
from training for the varied participants, but novel for the constant
participants.

```{r Test Performance,fig.height=8.5,fig.width=10.5}
#| eval: false
gbDev<-dtest %>% group_by(sbjCode,vbLabel,condit,throwCategory) %>% 
  summarise(distMean=mean(distCapped),.groups = 'keep') %>% 
  mutate(meanDevCapped=ifelse(distMean>900,900,distMean)) %>%
  ggplot(aes(x=vbLabel,y=meanDevCapped,fill=condit))+
  stat_summary(geom="bar",fun=mean,position=dodge,alpha=.7)+
   stat_summary(geom="errorbar",fun.data=mean_se,alpha=.8,width=.5,position=dodge)+
 #ggbeeswarm::geom_quasirandom(aes(),dodge.width=.9,alpha=.15,size=.3)+
  scale_y_continuous(breaks=round(seq(0,1000,by=200),2))+
  ylab("Mean Absoulte Distance From Boundary")+xlab("Target Velocity Band") +
scale_fill_discrete(name="Training Condition",labels=c("Constant","Varied"))+scale_color_discrete(guide="none")+
  theme( plot.title=element_text(size=9),
        axis.title.x=element_text(face="bold",size=11),
        axis.title.y=element_text(face="bold",size=11),
        axis.text.x = element_text(size = 7.5),
        legend.position="top")+
  labs(title="")#Testing - Mean Absolute Distance From Boundary
leg=ggpubr::get_legend(gbDev)
gbDev<- gbDev+theme(legend.position='none')

gbHit<-dtest %>% group_by(sbjCode,condit,vbLabel,expMode,testMode) %>% 
  summarise(nHitsTest=sum(dist==0),n=n(),Percent_Hit=nHitsTest/n,.groups = 'keep') %>% 
  ggplot(aes(x=vbLabel,y=Percent_Hit,fill=condit))+
  stat_summary(geom="bar",fun=mean,position=dodge,alpha=.7)+
   stat_summary(geom="errorbar",fun.data=mean_se,alpha=.8,width=.5,position=dodge)+
# ggbeeswarm::geom_quasirandom(aes(),dodge.width=.9,alpha=.15,size=.3)+
  ylab("% of throws with correct velocity")+xlab("Target Velocity Band") + 
  scale_fill_discrete(guide='none')+scale_color_discrete(guide="none")+
  theme( plot.title=element_text(size=9),
        axis.title.x=element_text(face="bold",size=11),
        axis.title.y=element_text(face="bold",size=11),
        axis.text.x = element_text(size = 7.5),
        legend.position="top")+
  labs(title="")#Testing -% of hits

gtitle="2C. Testing Performance"
title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0)+theme(plot.margin = margin(0, 0, 0, 7))
captionText=str_wrap("Figure 2C: Bands 100-300, 350-550 and 600-800 are novel extrapolations for both groups. Band 800-1000 was a training band for both groups. Bands 1000-1200, and 1200-1400 were trained for the varied group, and novel for the constant group.  Right side figure displays mean deviation from correct velocity band (lower values correspond to better performance). Bottom Left displays the average % of trials where participants hit the wall with the correct velocity (higher values correspond got better performance). Error bars indicate standard error of the mean. ",150)
capt=ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))

plot_grid(title,NULL,leg,NULL,gbDev,gbHit,capt,NULL,ncol=2,rel_heights=c(.1,.1,1,.1),rel_widths=c(1,1))

```

# Modeling

In project 1, we applied model-based techniques to quantify and control
for the similarity between training and testing experience, which in
turn enabled us to account for the difference between varied and
constant training via an extended version of a similarity based
generalization model. In project 2, we will go a step further,
implementing a full process model capable of both 1) producing novel
responses and 2) modeling behavior in both the learning and testing
stages of the experiment. For this purpose, we will apply the
associative learning model (ALM) and the EXAM model of function learning
(DeLosh 1997). ALM is a simple connectionist learning model which
closely resembles Kruschke's ALCOVE model (Kruscke 1992), with
modifications to allow for the generation of continuous responses.

## ALM & Exam Description

Delosh et al. (1997) introduced the associative learning model (ALM), a
connectionist model within the popular class of radial-basis networks.
ALM was inspired by, and closely resembles Kruschke's influential ALCOVE
model of categorization (Kruscke 1992).

ALM is a localist neural network model, with each input node corresponding to a
particular stimulus, and each output node corresponding to a particular response
value. The units in the input layer activate as a function of their Gaussian
similarity to the input stimulus. So, for example, an input stimulus of value 55
would induce maximal activation of the input unit tuned to 55. Depending on
thevalue of the generalization parameter, the nearby units (e.g. 54 and 56; 53
and 57) may also activate to some degree. ALM is structured with input and
output nodes that correspond to regions of the stimulus space, and response
space, respectively. The units in the input layer activate as a function of
their similarity to a presented stimulus. As was the case with the
exemplar-based models, similarity in ALM is exponentially decaying function of
distance. The input layer is fully connected to the output layer, and the
activation for any particular output node is simply the weighted sum of the
connection weights between that node and the input activations. The network then
produces a response by taking the weighted average of the output units (recall
that each output unit has a value corresponding to a particular response).
During training, the network receives feedback which activates each output unit
as a function of its distance from the ideal level of activation necessary to
produce the correct response. The connection weights between input and output
units are then updated via the standard delta learning rule, where the magnitude
of weight changes are controlled by a learning rate
parameter.

See Table 2A for a full specification of the equations that define ALM and EXAM.

## Model Equations

```{r ALM_Table }
#| results: 'asis'

text_tbl <- data.frame(
    'Step'=c("Input Activation","Output Activation","Output Probability","Mean Output","Feedback Activation","Update Weights","Extrapolation",""),
    'Equation' = c("$a_i$(X) = $\\frac{e^{-c \\cdot (X-X_i)^2}}{ \\sum_{k=1}^Me^{-c \\cdot (X-X_i)^2}}$", 
                   '$O_j$(X) = $\\sum_{k=1}^Mw_{ji} \\cdot a_i(X)$',
                   '$P[Y_j | X] = \\frac{O_i(X)}{\\sum_{k=1}^Mo_k(X)}$',
                   "$m(x) = \\sum_{j=1}^LY_j \\cdot \\bigg[\\frac{O_j(X)}{\\sum_{k=1}^Lo_k(X)}\\bigg]$",
                   "$f_j(Z)=e^{-c\\cdot(Z-Y_j)^2}$",
                   "$w_{ji}(t+1)=w_{ji}(t)+\\alpha \\cdot {f_i(Z(t))-O_j(X(t))} \\cdot a_i(X(t))$",
                   "$P[X_i|X] = \\frac{a_i(X)}{\\sum_{k=1}^Ma_k(X)}$",
                   "$E[Y|X_i]=m(X_i) + \\bigg[\\frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1} - X_{i-1}} \\bigg] \\cdot[X-X_i]$"),

    'Description'= c(
            "Activation of each input node, $X_i$, is a function of the Gaussian similarity between the node value and stimulus X. ",
            "Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights",
            "Each output node has associated response, $Y_j$. The probability of response $Y_j$ is determined by the ratio of output activations",
            "The response to stimulus x is the weighted average of the response probabilities",
            "After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response  ",
            "Delta rule to update weights. Magnitude of weight changes controlled by learning rate parameter alpha.",
            "Novel test stimulus X activates input nodes associated with trained stimuli",
            "Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)")
)
text_tbl$Step=cell_spec(text_tbl$Step,font_size=12)
text_tbl$Equation=cell_spec(text_tbl$Equation,font_size=18)
almTable=kable(text_tbl, 'html', 
  booktabs=T, escape = F, align='l',
  caption = '<span style = "color:black;"><center><strong>Table 1: ALM & EXAM Equations</strong></center></span>',
  col.names=c("","Equation","Description")) %>%
  kable_styling(position="left",bootstrap_options = c("hover")) %>%
  column_spec(1, bold = F,border_right=T) %>%
  column_spec(2, width = '10cm')%>%
  column_spec(3, width = '15cm') %>%
  pack_rows("ALM Activation & Response",1,4,bold=FALSE,italic=TRUE) %>%
  pack_rows("ALM Learning",5,6,bold=FALSE,italic=TRUE) %>%
  pack_rows("EXAM",7,8,bold=FALSE,italic=TRUE)
  #save_kable(file="almTable.html",self_contained=T)
cat(almTable)

```

## Model Fitting and Comparison

Following the procedure used by McDaniel & Busemeyer (2009), we will
assess the ability of both ALM and EXAM to account for the empirical
data when fitting the models to 1) only the training data, and 2) both
training and testing data. Models will be fit directly to the trial by
trial data of each individual participants, both by minimizing the
root-mean squared deviation (RMSE), and by maximizing log likelihood. Because ALM
has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also
fit the extended EXAM version of the model, which operates identically to ALM during training, 
but includes a linear extrapolation mechanism for generating novel responses during testing.

\
\
\
\
\
\
\

# References 
<div id="refs"></div>

### 2023-10-10 IGAS.qmd

@@
 ## References
-
-Aha, D. W., & Goldstone, R. L. (1992). Concept Learning and Flexible
-Weighting. *In Proceedings of the Fourteenth Annual Conference of the
-Cognitive Science Society*, 534--539.
-
-Barnett, S. M., & Ceci, S. J. (2002). When and where do we apply what we
-learn?: A taxonomy for far transfer. *Psychological Bulletin*, *128*(4),
-612--637. https://doi.org/10.1037//0033-2909.128.4.612
-
-Berniker, M., Mirzaei, H., & Kording, K. P. (2014). The effects of
-training breadth on motor generalization. *Journal of Neurophysiology*,
-*112*(11), 2791--2798. https://doi.org/10.1152/jn.00615.2013
-
-Braithwaite, D. W., & Goldstone, R. L. (2015). Effects of Variation and
-Prior Knowledge on Abstract Concept Learning. *Cognition and
-Instruction*, *33*(3), 226--256.
-https://doi.org/10.1080/07370008.2015.1067215
-
-Braun, D. A., Aertsen, A., Wolpert, D. M., & Mehring, C. (2009). Motor
-Task Variation Induces Structural Learning. *Current Biology*, *19*(4),
-352--357. https://doi.org/10.1016/j.cub.2009.01.036
-
-Briscoe, E., & Feldman, J. (2011). Conceptual complexity and the
-bias/variance tradeoff. *Cognition*, *118*(1), 2--16.
-https://doi.org/10.1016/j.cognition.2010.10.004
-
-Catalano, J. F., & Kleiner, B. M. (1984). Distant Transfer in Coincident
-Timing as a Function of Variability of Practice. *Perceptual and Motor
-Skills*, *58*(3), 851--856. https://doi.org/10.2466/pms.1984.58.3.851
-
-Censor, N., Sagi, D., & Cohen, L. G. (2012). Common mechanisms of human
-perceptual and motor learning. *Nature Reviews Neuroscience*, *13*(9),
-658--664. https://doi.org/10.1038/nrn3315
-
-Chamberlin, C. J., & Magill, R. A. (1992). A Note on Schema and Exemplar
-Approaches to Motor Skill Representation in Memory. *Journal of Motor
-Behavior*, *24*(2), 221--224.
-https://doi.org/10.1080/00222895.1992.9941617
-
-Chua, L.-K., Dimapilis, M. K., Iwatsuki, T., Abdollahipour, R.,
-Lewthwaite, R., & Wulf, G. (2019). Practice variability promotes an
-external focus of attention and enhances motor skill learning. *Human
-Movement Science*, *64*, 307--319.
-https://doi.org/10.1016/j.humov.2019.02.015
-
-Cochrane, A. (2020). TEfits: Nonlinear regression for time-evolving
-indices. *Journal of Open Source Software*, *5*(52), 2535.
-https://doi.org/10.21105/joss.02535
-
-Cohen, R. G., & Rosenbaum, D. A. (2004). Where grasps are made reveals
-how grasps are planned: Generation and recall of motor plans.
-*Experimental Brain Research*, *157*(4).
-https://doi.org/10.1007/s00221-004-1862-9
-
-Cox, G. E., Hemmer, P., Aue, W. R., & Criss, A. H. (2018). Information
-and processes underlying semantic and episodic memory across tasks,
-items, and individuals. *Journal of Experimental Psychology: General*,
-*147*(4), 545--590. https://doi.org/10.1037/xge0000407
-
-Crump, M. J. C., & Logan, G. D. (2010). Episodic contributions to
-sequential control: Learning from a typist's touch. *Journal of
-Experimental Psychology: Human Perception and Performance*, *36*(3),
-662--672. https://doi.org/10.1037/a0018390
-
-Czyż, S. H. (2021). Variability of Practice, Information Processing, and
-Decision Making---How Much Do We Know? *Frontiers in Psychology*, *12*.
-https://doi.org/10.3389/fpsyg.2021.639131
-
-de Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating
-behavioral experiments in a Web browser. *Behavior Research Methods*,
-*47*(1), 1--12. https://doi.org/10.3758/s13428-014-0458-y
-
-DeLosh, E. L., McDaniel, M. A., & Busemeyer, J. R. (1997).
-Extrapolation: The Sine Qua Non for Abstraction in Function Learning.
-*Journal of Experimental Psychology: Learning, Memory, and Cognition*,
-19.
-
-Detterman, D. K. (1993). The case for the prosecution: Transfer as an
-epiphenomenon. In *Transfer on trial: Intelligence, cognition, and
-instruction* (pp. 1--24). Ablex Publishing.
-
-Ennis, D. M., Palen, J. J., & Mullen, K. (1988). A multidimensional
-stochastic theory of similarity. *Journal of Mathematical Psychology*,
-*32*(4), 449--465. https://doi.org/10.1016/0022-2496(88)90023-5
-
-Estes, W. K. (1994). *Classification and Cognition*. Oxford University
-Press.
-
-Faul, F., Erdfelder, E., Buchner, A., & Lang, A.-G. (2009). Statistical
-power analyses using G\*Power 3.1: Tests for correlation and regression
-analyses. *Behavior Research Methods*, *41*(4), 1149--1160.
-https://doi.org/10.3758/BRM.41.4.1149
-
-Fulvio, J. M., Green, C. S., & Schrater, P. R. (2014). Task-Specific
-Response Strategy Selection on the Basis of Recent Training Experience.
-*PLOS Computational Biology*, *10*(1), e1003425.
-https://doi.org/10.1371/journal.pcbi.1003425
-
-Gandolfo, F., Mussa-Ivaldi, F. A., & Bizzi, E. (1996). Motor learning by
-field approximation. *Proceedings of the National Academy of Sciences*,
-*93*(9), 3843--3846. https://doi.org/10.1073/pnas.93.9.3843
-
-George, N., & Egner, T. (2021). Stimulus variability and task relevance
-modulate binding-learning. *Attention, Perception, & Psychophysics*.
-https://doi.org/10.3758/s13414-021-02338-6
-
-Ghahramani, Z., Wolpert, D. M., & Jordan, M. I. (1996). Generalization
-to Local Remappings of the Visuomotor Coordinate Transformation.
-*Journal of Neuroscience*, *16*(21), 7085--7096.
-https://doi.org/10.1523/JNEUROSCI.16-21-07085.1996
-
-Gonzalez, C., & Madhavan, P. (2011). Diversity during training enhances
-detection of novel stimuli. *Journal of Cognitive Psychology*, *23*(3),
-342--350. https://doi.org/10.1080/20445911.2011.507187
-
-Goode, M. K., Geraci, L., & Roediger, H. L. (2008). Superiority of
-variable to repeated practice in transfer on anagram solution.
-*Psychonomic Bulletin & Review*, *15*(3), 662--666.
-https://doi.org/10.3758/PBR.15.3.662
-
-Goodwin, J. E., Eckerson, J. M., Grimes, C. R., & Gordon, P. M. (1998).
-Effect of Different Quantities of Variable Practice on Acquisition,
-Retention, and Transfer of An Applied Motor Skill. *Perceptual and Motor
-Skills*, *87*(1), 147--151. https://doi.org/10.2466/pms.1998.87.1.147
-
-Green, D. P., Whitehead, J., & Sugden, D. A. (1995). Practice
-Variability and Transfer of a Racket Skill. *Perceptual and Motor
-Skills*, *81*(3_suppl), 1275--1281.
-https://doi.org/10.2466/pms.1995.81.3f.1275
-
-Hahn, U., Bailey, T. M., & Elvin, L. B. C. (2005). Effects of category
-diversity on learning, memory, and generalization. *Memory & Cognition*,
-*33*(2), 289--302. https://doi.org/10.3758/BF03195318
-
-Hills, T. T., Todd, P. M., & Goldstone, R. L. (2010). The central
-executive as a search process: Priming exploration and exploitation
-across domains. *Journal of Experimental Psychology: General*, *139*(4),
-590--609. https://doi.org/10.1037/a0020666
-
-Hintzman, D. L. (1984). MINERVA 2: A simulation model of human memory.
-*Behavior Research Methods, Instruments, & Computers*, *16*(2), 96--101.
-https://doi.org/10.3758/BF03202365
-
-Hommel, B. (1998). Event Files: Evidence for Automatic Integration of
-Stimulus-Response Episodes. *Visual Cognition*, *5*(1--2), 183--216.
-https://doi.org/10.1080/713756773
-
-Jamieson, R. K., Johns, B. T., Vokey, J. R., & Jones, M. N. (2022).
-Instance theory as a domain-general framework for cognitive psychology.
-*Nature Reviews Psychology*, *1*(3), 174--183.
-https://doi.org/10.1038/s44159-022-00025-3
-
-Jones, S. D., & Brandt, S. (2020). Density and Distinctiveness in Early
-Word Learning: Evidence From Neural Network Simulations. *Cognitive
-Science*, *44*(1), e12812. https://osf.io/2qk5j/.
-https://doi.org/10.1111/cogs.12812
-
-Kassambara, A. (2021). *rstatix: Pipe-Friendly Framework for Basic
-Statistical Tests* \[R package   version 0.7.0\].
-https://CRAN.R-project.org/package=rstatix
-
-Kelley, T. A., & Yantis, S. (2009). Learning to attend: Effects of
-practice on information selection. *Journal of Vision*, *9*(7), 16.
-https://doi.org/10.1167/9.7.16
-
-Kerr, R., & Booth, B. (1978). Specific and varied practice of motor
-skill. *Perceptual and Motor Skills*, *46*(2), 395--401.
-
-Lamberts, K. (1994). Flexible Tuning of Similarity in Exemplar-Based
-Categorization. *Journal of Experimental Psychology: Learning, Memory,
-and Cognition*, *20*(5), 1003--1021.
-
-Lavan, N., Knight, S., Hazan, V., & McGettigan, C. (2019). The effects
-of high variability training on voice identity learning. *Cognition*,
-*193*, 104026. https://doi.org/10.1016/j.cognition.2019.104026
-
-Law, C.-T., & Gold, J. I. (2010). Shared Mechanisms of Perceptual
-Learning and Decision Making. *Topics in Cognitive Science*, *2*(2),
-226--238. https://doi.org/10.1111/j.1756-8765.2009.01044.x
-
-Lee, J. C., Lovibond, P. F., & Hayes, B. K. (2019). Evidential diversity
-increases generalisation in predictive learning. *Quarterly Journal of
-Experimental Psychology*, *72*(11), 2647--2657.
-https://doi.org/10.1177/1747021819857065
-
-Logan, G. D. (1988). Toward an instance theory of automatization.
-*Psychological Review*, *95*(4), 492--527.
-
-Logan, G. D. (2002). An instance theory of attention and memory.
-*Psychological Review*, *109*(2), 376--400.
-https://doi.org/10.1037/0033-295X.109.2.376
-
-Maddox, W. T., & Filoteo, J. V. (2011). Stimulus range and discontinuity
-effects on information-integration category learning and generalization.
-*Attention, Perception, & Psychophysics*, *73*(4), 1279--1295.
-https://doi.org/10.3758/s13414-011-0101-2
-
-Marongelli, E., & Thoroughman, K. (2013). The advantage of flexible
-neuronal tunings in neural network models for motor learning. *Frontiers
-in Computational Neuroscience*, *7*, 100.
-https://doi.org/10.3389/fncom.2013.00100
-
-McCracken, H. D., & Stelmach, G. E. (1977). A Test of the Schema Theory
-of Discrete Motor Learning. *Journal of Motor Behavior*, *9*(3),
-193--201. https://doi.org/10.1080/00222895.1977.10735109
-
-Medin, D. L., & Schaffer, M. M. (1978). Context Theory of Classification
-Learning. *Psychological Review*, *85*(3), 207.
-
-Meigh, K. M., Shaiman, S., Tompkins, C. A., Abbott, K. V., &
-Nokes-Malach, T. (2018). What memory representation is acquired during
-nonword speech production learning? The influence of stimulus features
-and training modality on nonword encoding. *Cogent Psychology*, *5*(1),
-1493714. https://doi.org/10.1080/23311908.2018.1493714
-
-Moxley, S. E. (1979). Schema: The Variability of Practice Hypothesis.
-*Journal of Motor Behavior*, *11*(1), 65--70.
-https://doi.org/10.1080/00222895.1979.10735173
-
-Newell, K. M. (2003). Schema Theory (1975): Retrospectives and
-Prospectives. *Research Quarterly for Exercise and Sport*, *74*(4),
-383--388. https://doi.org/10.1080/02701367.2003.10609108
-
-Newell, K. M., & Shapiro, D. C. (1976). Variability of Practice and
-Transfer of Training: Some Evidence Toward a Schema View of Motor
-Learning. *Journal of Motor Behavior*, *8*(3), 233--243.
-https://doi.org/10.1080/00222895.1976.10735077
-
-North, J. S., Bezodis, N. E., Murphy, C. P., Runswick, O. R., Pocock,
-C., & Roca, A. (2019). The effect of consistent and varied
-follow-through practice schedules on learning a table tennis backhand.
-*Journal of Sports Sciences*, *37*(6), 613--620.
-https://doi.org/10.1080/02640414.2018.1522683
-
-Nosofsky, R. M. (1986). Attention, similarity, and the
-identification-categorization relationship. *Journal of Experimental
-Psychology: General*, *115*(1), 39--57.
-
-Nosofsky, R. M. (1992). Similarity scaling and cognitive process models.
-*Annual Review of Psychology*, *43*(1), 25--53.
-
-Nosofsky, R. M., & Johansen, M. K. (2000). Exemplar-based accounts of
-"multiple-system" phenomena in perceptual categorization. *Psychonomic
-Bulletin & Review*, *7*(3), 375--402.
-
-Nosofsky, R. M., Sanders, C. A., Zhu, X., & McDaniel, M. A. (2018).
-Model-guided search for optimal natural-science-category training
-exemplars: A work in progress. *Psychonomic Bulletin & Review*, *26*(1),
-48--76. https://doi.org/10.3758/s13423-018-1508-8
-
-Op de Beeck, H. P., Wagemans, J., & Vogels, R. (2008). The
-representation of perceived shape similarity and its role for category
-learning in monkeys: A modeling study. *Vision Research*, *48*(4),
-598--610. https://doi.org/10.1016/j.visres.2007.11.019
-
-Palmeri, T. J. (1997). Exemplar Similarity and the Development of
-Automaticity. *Journal of Experimental Psychology: Human Learning and
-Memory*, *23*(2), 324--354.
-
-Perry, L. K., Samuelson, L. K., Malloy, L. M., & Schiffer, R. N. (2010).
-Learn Locally, Think Globally: Exemplar Variability Supports
-Higher-Order Generalization and Word Learning. *Psychological Science*,
-*21*(12), 1894--1902. https://doi.org/10.1177/0956797610389189
-
-Pigott, R. E., & Shapiro, D. C. (1984). Motor Schema: The Structure of
-the Variability Session. *Research Quarterly for Exercise and Sport*,
-*55*(1), 41--45. https://doi.org/10.1080/02701367.1984.10605353
-
-Poldrack, R. A., Selco, S. L., Field, J. E., & Cohen, N. J. (1999). The
-relationship between skill learning and repetition priming: Experimental
-and computational analyses. *Journal of Experimental Psychology:
-Learning, Memory, and Cognition*, *25*(1), 208--235.
-https://doi.org/10.1037/0278-7393.25.1.208
-
-Posner, M. I., & Keele, S. W. (1968). On the genesis of abstract ideas.
-*Journal of Experimental Psychology*, *77*(3), 353--363.
-
-R Core Team. (2020). *R: A Language and Environment for Statistical
-Computing*. R: A Language and Environment for Statistical Computing.
-https://www.R-project.org/
-
-Roark, C. L., Paulon, G., Sarkar, A., & Chandrasekaran, B. (2021).
-Comparing perceptual category learning across modalities in the same
-individuals. *Psychonomic Bulletin & Review*, *28*(3), 898--909.
-https://osf.io/htwdk/. https://doi.org/10.3758/s13423-021-01878-0
-
-Roller, C. A., Cohen, H. S., Kimball, K. T., & Bloomberg, J. J. (2001).
-Variable practice with lenses improves visuo-motor plasticity.
-*Cognitive Brain Research*, *12*(2), 341--352.
-https://doi.org/10.1016/S0926-6410(01)00077-5
-
-Rosenbaum, D. A., Carlson, R. A., & Gilmore, R. O. (2001). Acquisition
-of Intellectual and Perceptual-Motor Skills. *Annual Review of
-Psychology*, *52*(1), 453--470.
-https://doi.org/10.1146/annurev.psych.52.1.453
-
-Rosenbaum, D. A., Loukopoulos, L. D., Meulenbroek, R. G., Vaughan, J., &
-Engelbrecht, S. E. (1995). Planning reaches by evaluating stored
-postures. *Psychological Review*, *102*(1), 28.
-
-Sabah, K., Dolk, T., Meiran, N., & Dreisbach, G. (2019). When less is
-more: Costs and benefits of varied vs. fixed content and structure in
-short-term task switching training. *Psychological Research*, *83*(7),
-1531--1542. https://doi.org/10.1007/s00426-018-1006-7
-
-Sadakata, M., & McQueen, J. M. (2014). Individual aptitude in Mandarin
-lexical tone perception predicts effectiveness of high-variability
-training. *Frontiers in Psychology*, *5*, 1318.
-https://doi.org/10.3389/fpsyg.2014.01318
-
-Sakamoto, Y., Love, B. C., & Jones, M. (2006). Tracking Variability in
-Learning: Contrasting Statistical and Similarity-Based Accounts.
-*Proceedings of the 28th Annual Conference of the Cognitive Science
-Society. Vancouver, Canada: Cognitive Science Society*.
-
-Schmidt, R. A. (1975). A schema theory of discrete motor skill learning.
-*Psychological Review*, *82*(4), 225--260.
-https://doi.org/10.1037/h0076770
-
-Seow, R. Y. T., Betts, S., & Anderson, J. R. (2019). Transfer effects of
-varied practice and adaptation to changes in complex skill acquisition.
-*Proceedings of the 17th International Conference on Cognitive
-Modelling*, 222--227.
-
-Shepard, R. N. (1987). Toward a universal law of generalization for
-psychological science. *Science*, *237*(4820), 1317--1323.
-
-Sinkeviciute, R., Brown, H., Brekelmans, G., & Wonnacott, E. (2019). The
-role of input variability and learner age in second language vocabulary
-learning. *Studies in Second Language Acquisition*, *41*(04), 795--820.
-https://doi.org/10.1017/S0272263119000263
-
-Soderstrom, N. C., & Bjork, R. A. (2015). Learning versus performance:
-An integrative review. *Perspectives on Psychological Science*, *10*(2),
-176--199.
-
-Taylor, J., & Ivry, R. (2013). Context-dependent generalization.
-*Frontiers in Human Neuroscience*, *7*, 171.
-https://doi.org/10.3389/fnhum.2013.00171
-
-Thoroughman, K. A., & Taylor, J. A. (2005). Rapid Reshaping of Human
-Motor Generalization. *Journal of Neuroscience*, *25*(39), 8948--8953.
-https://doi.org/10.1523/JNEUROSCI.1771-05.2005
-
-Twomey, K. E., Ma, L., & Westermann, G. (2018). All the Right Noises:
-Background Variability Helps Early Word Learning. *Cognitive Science*,
-*42*(S2), 413--438. https://doi.org/10.1111/cogs.12539
-
-van Dam, L. C. J., & Ernst, M. O. (2015). Mapping Shape to Visuomotor
-Mapping: Learning and Generalisation of Sensorimotor Behaviour Based on
-Contextual Information. *PLOS Computational Biology*, *11*(3), e1004172.
-https://doi.org/10.1371/journal.pcbi.1004172
-
-Van Rossum, J. H. A. (1990). Schmidt's schema theory: The empirical base
-of the variability of practice hypothesis. *Human Movement Science*,
-*9*(3--5), 387--435. https://doi.org/10.1016/0167-9457(90)90010-B
-
-Vigo, R., Doan, K.-M. C., Doan, C. A., & Pinegar, S. (2018). On the
-learning difficulty of visual and auditory modal concepts: Evidence for
-a single processing system. *Cognitive Processing*, *19*(1), 1--16.
-https://doi.org/10.1007/s10339-017-0840-7
-
-Wall, L., Gunawan, D., Brown, S. D., Tran, M.-N., Kohn, R., & Hawkins,
-G. E. (2021). Identifying relationships between cognitive processes
-across tasks, contexts, and time. *Behavior Research Methods*, *53*(1),
-78--95. https://doi.org/10.3758/s13428-020-01405-4
-
-Wifall, T., Buss, A. T., Farmer, T. A., Spencer, J. P., & Hazeltine, E.
-(2017). Reaching into response selection: Stimulus and response
-similarity influence central operations. *Journal of Experimental
-Psychology: Human Perception and Performance*, *43*(3), 555--568.
-https://doi.org/10.1037/xhp0000301
-
-Willey, C. R., & Liu, Z. (2018). Long-term motor learning: Effects of
-varied and specific practice. *Vision Research*, *152*, 10--16.
-https://doi.org/10.1016/j.visres.2017.03.012
-
-Wonnacott, E., Boyd, J. K., Thomson, J., & Goldberg, A. E. (2012). Input
-effects on the acquisition of a novel phrasal construction in 5year
-olds. *Journal of Memory and Language*, *66*(3), 458--478.
-https://doi.org/10.1016/j.jml.2011.11.004
-
-Wrisberg, C. A., Winter, T. P., & Kuhlman, J. S. (1987). The Variability
-of Practice Hypothesis: Further Tests and Methodological Discussion.
-*Research Quarterly for Exercise and Sport*, *58*(4), 369--374.
-https://doi.org/10.1080/02701367.1987.10608114
-
-Wu, C. M., Schulz, E., Garvert, M. M., Meder, B., & Schuck, N. W.
-(2020). Similarities and differences in spatial and non-spatial
-cognitive maps. *PLOS Computational Biology*, *16*(9).
-https://github.com/charleywu/cognitivemaps.
-https://doi.org/10.1101/2020.01.21.914556
-
-Wulf, G. (1991). The effect of type of practice on motor learning in
-children. *Applied Cognitive Psychology*, *5*(2), 123--134.
-https://doi.org/10.1002/acp.2350050206
-
-Yang, J., Yan, F.-F., Chen, L., Xi, J., Fan, S., Zhang, P., Lu, Z.-L., &
-Huang, C.-B. (2020). General learning ability in perceptual learning.
-*Proceedings of the National Academy of Sciences*, *117*(32),
-19092--19100. https://doi.org/10.1073/pnas.2002903117
-
-Zaman, J., Chalkia, A., Zenses, A.-K., Bilgin, A. S., Beckers, T.,
-Vervliet, B., & Boddez, Y. (2021). Perceptual variability: Implications
-for learning and generalization. *Psychonomic Bulletin & Review*,
-*28*(1), 1--19. https://doi.org/10.3758/s13423-020-01780-1

### 2023-10-16 IGAS.qmd
small updates and re-render

@@
 ---
-title: IGAS Project
+title: An instance-based model account of the benefits of varied practice in visuomotor skill
 date: last-modified
@@
 advantage of not assuming the explicit construction of an internal
-prototype [@estesArrayModelsCategory1986;
+prototype [@estesClassificationCognition1994;
 @hintzmanMINERVASimulationModel1984;

### 2023-10-16 .vdoc.r

@@ -1,0 +1,1482 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+knitr::opts_chunk$set(echo=FALSE)
+# source('build_toc.R')
+# files <- list.files(pattern = '*.Rmd', recursive = F) 
+# files = files[!grepl('^_', basename(files)) | grepl('^_index[.]', basename(files))]
+# t1 <- render_toc("htw_n.Rmd")
+# #cat(t1)
+# 
+# 
+# render_toc("igas_n.Rmd")
+
+library(thematic)
+thematic_on(bg="#fcfcfc")
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+source('Functions/IGAS_ProcessFunctions.R')
+library(webexercises)
+library(kableExtra)
+library(knitr)
+knitr::opts_chunk$set(echo = FALSE)
+
+#rm(list=ls())
+###### data loading and organization #######
+
+# load the processed data from experiment 1 and 2
+e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
+
+options(contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+theme_set(theme_classic())
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
+                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
+
+e1Pos <- c("610","760","835","910")
[…]

### 2023-10-16 IGAS.qmd
Update IGAS notebook

@@
 
-```{r echo=FALSE}
-knitr::opts_chunk$set(echo=FALSE)
-# source('build_toc.R')
-# files <- list.files(pattern = '*.Rmd', recursive = F) 
-# files = files[!grepl('^_', basename(files)) | grepl('^_index[.]', basename(files))]
-# t1 <- render_toc("htw_n.Rmd")
-# #cat(t1)
-# 
-# 
-# render_toc("igas_n.Rmd")
-
-library(thematic)
-thematic_on(bg="#fcfcfc")
+```{r}
+pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot)
+source('Functions/IGAS_ProcessFunctions.R')
+
+theme_set(theme_classic())
+# load the processed data from experiment 1 and 2
+e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
+
+options(contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+theme_set(theme_classic())
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
+                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
+
+e1Pos <- c("610","760","835","910")
+e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
+e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
 ```
@@
 
-```{r load, include=FALSE}
-source('Functions/IGAS_ProcessFunctions.R')
-library(webexercises)
-library(kableExtra)
-library(knitr)
-knitr::opts_chunk$set(echo = FALSE)
-
-#rm(list=ls())
-###### data loading and organization #######
-
-# load the processed data from experiment 1 and 2
-e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
-
-options(contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
+```{r}
 
@@
 ```{r Toy Model, fig.width=9,fig.height=5.0}
-theme_set(theme_classic())
+#| label: toy-model1
+#| fig.cap:  Left panel: Generalization predicted from a simple model that assumes a linear generalization function.
+A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
+Right panel: if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
+(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
 p=2
@@
                             genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) %>%
+  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
   group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
+  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
 colorVec=c("darkblue","darkred")
@@
                   annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
+                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
                         legend.position="none"))
@@
 
-#gridExtra::grid.arrange(ip2,ip1,ncol=2)
-
-gtitle="Figure 1"
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-captionText=str_wrap("Figure 1.
-Left panel: Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel: if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-",200)
-capt=ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-
-plot_grid(title,NULL,ip1,ip2,capt,NULL,ncol=2,rel_heights=c(.1,1,.15))
+plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
 
@@
 ```{r Figure 2, echo=FALSE,fig.height=5.8, fig.width=10.1}
-
-#mf <- png::readPNG("Assets/methodsFig1.png")
-#ggplot()+annotation_raster(mf,xmin = 0, xmax = 486, ymin = 0, ymax = 196)
-
-gtitle="Figure 2"
-
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))
-
-captionText=str_wrap("Figure 2: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
+#| label: IGAS_Methods
+#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square.
-",150)
-
-capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
-  theme(plot.margin = margin(0, 0, 0, 1))
-  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
+Participants were constrained to release the ball within the square
+
 mf <- cowplot::ggdraw()+cowplot::draw_image("Assets/methodsFig1.png",hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-
-plot_grid(title,mf,capt,ncol=1,rel_heights = c(.1,1,.1))
-#plot_grid(mf,capt,ncol=1,rel_widths=c(1,.01))
-# plot_grid(capt,capt,ncol=1)
-
-# capt
-# # c2 = ggdraw()+draw_label("testing_text out",x=0,hjust=0,vjust=0,size=11)+ theme(plot.margin = unit(c(0, 0, 0, 0), "pt"))
-# # c2
-# plot_grid(capt,capt,ncol=1,rel_heights =c(1,.2))
+plot_grid(mf,ncol=1)
 
@@
 ```{r Training1, echo=FALSE,fig.height=5.0, fig.width=7}
+#| label: IGAS_Training1
+#| fig.cap: Training performance for varied and constant participants binned into three stages.
+Shorter bars indicate better performance (ball landing closer to the center of the target).
+Error bars indicate standard error of the mean.
 
@@
 
-gtitle="Figure 3"
-
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))
-
-captionText=str_wrap("Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-",145)
-
-capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
-  theme(plot.margin = margin(0, 0, 0, 1))
-  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
-plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
+#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
+plot_grid(e1train2,ncol=1)
 
@@
 ```{r e1Test, echo=FALSE,fig.width=9.5, fig.height = 6.5 }
+#| label: IGAS_Testing1
+#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
+Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
+Position 760 was trained on by the constant group, and novel for the varied group.
+Position 835 was novel for both groups.
+Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
+Error bars indicate standard error of the mean.
 
@@
 
-gtitle="Figure 4"
-
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))
-
-captionText=str_wrap("Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-",130)
-
-capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
-  theme(plot.margin = margin(0, 0, 0, 1))
-  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
-plot_grid(title,e1test1,capt,ncol=1,rel_heights=c(.18,1,.15))
+e1test1
 
@@
 ```{r e1Table, echo=FALSE }
+#| label: IGAS_Table1
+#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
 
@@
 
-captionText="Table 1. Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis."
-
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>%   kable_classic() %>% kableExtra::footnote(general=captionText,general_title = "")
-
-# 
-# colnames(test) <- c("Position","Constant","Varied")
-# ft1=flextable(test,col_keys = c("Position","Constant","Varied"))
-# ft1 <- flextable::set_caption(ft1,captionText)
-# ft1
+kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>%   
+  kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
 
@@
 
-```{r e2train, echo=FALSE,fig.height=12.5, fig.width=9}
+```{r}
+#| label: e2train
+#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
+In Figure 5a, the six constant groups are averaged together, as are the two training positions for the varied group.
+In Figure 5b the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
+Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
+Error bars indicate standard error of the mean.
 
@@
 
-gtitle="Figure 5"
-
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))
-
-captionText=str_wrap("Training performance for the six constant conditions, and the varied condition, binned into three stages.
-In Figure 5a, the six constant groups are averaged together, as are the two training positions for the varied group.
-In Figure 5b the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-",130)
-
-capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
-  theme(plot.margin = margin(0, 0, 0, 1))
-  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
-plot_grid(title,e2train1,e2train2,capt,ncol=1,rel_heights=c(.18,1,1,.15))
+e2train1
+e2train2
 
@@
 ```{r e2test1, echo=FALSE,fig.height=12.5, fig.width=10.5 }
+#| label: e2test
+#| fig.cap: Testing phase performance from each of the six testing positions.
+The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
+Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
+The x axis labels indicate the location(s) from which each group trained.
+Lower values along the y axis reflect better performance at the task (closer distance to target center).
+Error bars indicate standard error of the mean.
 
@@
 
-gtitle="Figure 6"
-
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))
-
-captionText=str_wrap("Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
+e2test1
+e2test2
+
+```
+
+\
+\
+\
+
+```{r e2table1, echo=FALSE }
+#| label: e2table1
+#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
 Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
@@
 Error bars indicate standard error of the mean.
-",140)
-
-capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
-  theme(plot.margin = margin(0, 0, 0, 1))
-  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
-plot_grid(title,e2test1,e2test2,capt,ncol=1,rel_heights=c(.18,1,1,.15))
-
-```
-
-\
-\
-\
-
-```{r e2table1, echo=FALSE }
 
@@
 
- captionText="Table 2.
-Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-"
-
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% kable_classic() %>% footnote(general=captionText,general_title = "")
+kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
+  kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 ```{r e2table3, echo=FALSE }
+#| label: e2table2
+#| tbl-cap: Testing performance from novel positions.
+Includes data only from positions that were not encountered during the training stage (e.g.
+excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
+Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
 
@@
 
- captionText="Table 3.
-Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-"
-
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% kable_classic() %>% footnote(general=captionText,general_title = "")
+kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
+  kable_classic() #%>% footnote(general=captionText,general_title = "")
 ```
@@
 ```{r e2test2, echo=FALSE,fig.height=6.0, fig.width=7, warning=FALSE}
+#| label: e2test1
+#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
+constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
+Error bars indicate standard error of the mean.
 
@@
 
-gtitle="Figure 7"
-
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))
-
-captionText=str_wrap("A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-",145)
-
-capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
-  theme(plot.margin = margin(0, 0, 0, 1))
-  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
-plot_grid(title,e2Test2,capt,ncol=1,rel_heights=c(.18,1,.15))
+e2Test2
 
@@
 ```{r e2tab3,echo=FALSE, warning=FALSE}
+#| label: e2tab3
+#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
+Locations 500 and 800 are not included as these were trained by the varied participants.
+Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
 
@@
    mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
+
+tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
  tab4=tab4[,1:3]
 
- captionText="Table 5.
-Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-"
-
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% kable_classic() %>% footnote(general=captionText,general_title = "")
+kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
+  kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 ```{r taskSpace, echo=FALSE,fig.height=9.0, fig.width=10}
-
-library("RColorBrewer")
+#| label: taskSpace
+#| fig.cap: a visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+This empirical solution space was compiled from all of the participants in experiment 2.
+Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+#| 
 taskspace <- e2 %>% filter(AbsDistFromCenter<900)
@@
 
-gtitle="Figure 8"
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',y=Inf, x=0,hjust=0,vjust=5.5,size=11)+theme(plot.margin = margin(0, 0, 0, 0))
-
-captionText=str_wrap("Figure 8A is a visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.",145)
-
-capt<-ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+ 
-  theme(plot.margin = margin(0, 0, 0, 1))
-  #theme(plot.margin = unit(c(0, 0, 0, 1), "cm"))
-plot_grid(title,ss,fs,capt,ncol=1,rel_heights=c(.18,1,1,.15))
+ss
+fs
+
 ```
@@
 ```{r}
-#| Toy Model 2, fig.width=10,fig.height=10.0,
-#| fig.cap="Figure 9.
-A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
+#| label: Toy_Model2
+#| fig.cap=A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
 For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is: Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$.
@@
 The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form: Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$."
+Thus, the generalization model for the varied condition in the bottom-right panel is of the form: Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
 

### 2023-10-16 Functions/IGAS_ProcessFunctions.R

@@ -1,0 +1,368 @@
+packages <- c('ez','plyr','dplyr','sciplot','ggplot2','magrittr','car','psych','tidyr',
+              'Matrix','cluster','emdbook','hexbin','caret','glmnet',
+              'afex','purrr','broom','ggpubr','rstatix','stargazer','data.table','cowplot','magick',
+              'stringr')
+have = packages %in% rownames(installed.packages())
+if ( any(!have) ) {print("installing missing packages"); install.packages(packages[!have]) }
+invisible(lapply(packages, require, character.only = TRUE))
+#install.packages("data.table", type="source", repos="https://Rdatatable.gitlab.io/data.table")
+select <- dplyr::select
+mutate <- dplyr::mutate
+filter <- dplyr::filter
+rename <- dplyr::rename
+summarise <- dplyr::summarise
+#rm(list=ls())
+dodge <- position_dodge(width = 0.9)
+
+
+
+
+
+startCluster <- function(progressVar=100,ncores=NULL)
+{
+  if(is.null(ncores))
+  {
+  ncores=detectCores(all.tests = FALSE, logical = TRUE)
+  }
+  cl       <<- makeSOCKcluster(ncores)
+  pb       <<- txtProgressBar(max = progressVar, style = 3)
+  progress <- function(n){setTxtProgressBar(pb, n)}
+  sopts     <<- list(progress = progress)
+  registerDoSNOW(cl)
+  
+print(paste0("started cluster with ",ncores," cores"))
+}
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+# grab subset of subjects who are >= the cutoff # of strdvs for the given variable. Default central tendency is median. 
+engagementOutlier <- function(sbjWiseData,varName, CT="median", cutoff=2.5,printInfo=TRUE){
+  
+  # compute mean,median, and strdv for given variable
+  meanDv=mean(sbjWiseData[,varName])
+  medDv=median(sbjWiseData[,varName])
+  sdDv=sd(sbjWiseData[,varName])
+  
+  # do subsetting
[…]

### 2023-10-16 IGAS.qmd
fix IGAS issues and re-render

@@
   warning: false
-  eval: false 
+  eval: true
 editor: 
@@
 ```{r}
-pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot)
+pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)
 source('Functions/IGAS_ProcessFunctions.R')
@@
 without positing the learning of some schemata or structure.
-
-```{r}
-
-```
 
@@
 between training and transfer conditions is identical between groups.
-Figure 1 demonstrates the consequences of a generalization gradient that
+@fig-toy-model1 demonstrates the consequences of a generalization gradient that
 drops off as a Gaussian function of distance from training, as compared
@@
 
-```{r Toy Model, fig.width=9,fig.height=5.0}
-#| label: toy-model1
-#| fig.cap:  Left panel: Generalization predicted from a simple model that assumes a linear generalization function.
+```{r}
+#| label: fig-toy-model1
+#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
 A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel: if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
+Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
 (For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
+
 p=2
@@
 ball landed in relation to the center of the target, will be referred to
-simply as distance. Methods Figure 2 displays the layout of the task, as
+simply as distance. @fig-IGAS_Methods displays the layout of the task, as
 it would appear to a participant at the start of a trial, with the ball
@@
 
-```{r Figure 2, echo=FALSE,fig.height=5.8, fig.width=10.1}
-#| label: IGAS_Methods
+```{r}
+#| label: fig-IGAS_Methods
 #| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
@@
 
-Figure 3 below shows aggregate training performance binned into three
+@fig-IGAS_Training1 below shows aggregate training performance binned into three
 stages representing the beginning, middle, and end of the training
@@
 
-```{r Training1, echo=FALSE,fig.height=5.0, fig.width=7}
-#| label: IGAS_Training1
+```{r}
+#| label: fig-IGAS_Training1
 #| fig.cap: Training performance for varied and constant participants binned into three stages.
@@
 
-```{r e1Test, echo=FALSE,fig.width=9.5, fig.height = 6.5 }
-#| label: IGAS_Testing1
+```{r}
+#| label: fig-IGAS_Testing1
 #| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
@@
 
-```{r e1Table, echo=FALSE }
-#| label: IGAS_Table1
+```{r}
+#| label: tbl-IGAS_Table1
 #| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
@@
 As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. Figure 5 depicts the training
+confirmation that some learning did occur. @fig-e2train depicts the training
 performance of the varied group alongside that of the aggregate of the
@@
 
-```{r,echo=FALSE, include=FALSE }
+```{r}
 
@@
 ```{r}
-#| label: e2train
+#| label: fig-e2train
 #| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-In Figure 5a, the six constant groups are averaged together, as are the two training positions for the varied group.
-In Figure 5b the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
+On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
+On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
 Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
@@
 significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
-=.02. Descriptive statistics for each condition are shown in table 2.
-Figure 6A visualizes the consistent advantage of the varied condition
-over the constant groups across the testing positions. Figure 6b shows
+=.02. Descriptive statistics for each condition are shown in table 2. In
+@fig-e2testa visualizes the consistent advantage of the varied condition
+over the constant groups across the testing positions. @fig-e2testa shows
 performance between the varied condition and the individual constant
@@
 
-```{r e2test1, echo=FALSE,fig.height=12.5, fig.width=10.5 }
-#| label: e2test
+```{r}
+#| label: fig-e2testa
 #| fig.cap: Testing phase performance from each of the six testing positions.
@@
 Error bars indicate standard error of the mean.
+#| fig-width: 11
+#| fig-height: 9
 
@@
 
-e2test1
-e2test2
+e2test1 / e2test2
 
@@
 
-```{r e2table1, echo=FALSE }
-#| label: e2table1
+```{r}
+#| label: tbl-e2table1
 #| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
@@
 
-```{r e2table3, echo=FALSE }
-#| label: e2table2
+```{r}
+#| label: tbl-e2table2
 #| tbl-cap: Testing performance from novel positions.
@@
 omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). Figure 7 displays
+those positions were not novel to the varied group). @fig-e2test1 displays
 the particular subset of comparisons utilized for this analysis. Again,
@@
 
-```{r e2test2, echo=FALSE,fig.height=6.0, fig.width=7, warning=FALSE}
-#| label: e2test1
+```{r}
+#| label: fig-e2test1
 #| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
@@
 
-```{r e2tab3,echo=FALSE, warning=FALSE}
-#| label: e2tab3
+```{r}
+#| label: tbl-e2tab3
 #| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
@@
 target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. Figure 8a
+six separate similarity scores for each participant. @fig-taskSpace
 visualizes the solution space for each location and illustrates how
@@
 striking the target from different launching positions. As illustrated
-in Figure 8b, the solution throws represent just a small fraction of the
+in @fig-taskSpace, the solution throws represent just a small fraction of the
 entire space of velocity combinations used by participants throughout
@@
 
-(ref:taskSpace) Figure 8a is a visual representation of the combinations
-of throw parameters (x and y velocities applied to the ball at launch),
-which resulted in target hits during the testing phase. This empirical
-solution space was compiled from all of the participants in experiment
-2. Figure 8b shows the solution space within the context of all of the
-throws made throughout the testing phase of the experiment.
-
-```{r taskSpace, echo=FALSE,fig.height=9.0, fig.width=10}
-#| label: taskSpace
-#| fig.cap: a visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+```{r}
+#| label: fig-taskSpace
+#| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
 This empirical solution space was compiled from all of the participants in experiment 2.
@@
 our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in Figure 9 we
+data, not just that of the identity comparisons, in @fig-Toy_Model2 we
 demonstrate how a simplified version of the IGAS model could in
@@
 
-```{css}
-
-caption, .caption{
-  font-style:italic;
-  margin-top:0.5em;
-  margin-bottom:0.5em;
-  width:100%;
-  text-align: left;
-}
-
-```
-
-```{r}
-#| label: Toy_Model2
-#| fig.cap=A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is: Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$.
+```{r}
+#| label: fig-Toy_Model2
+#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
+For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$.
 For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
 The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form: Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
+Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
 
@@
                   xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.1),
-                  annotate(geom="text",x=455,y=1.01,label="Training",size=3.1),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.1),
-                  annotate(geom="text",x=657,y=1.01,label="Training",size=3.1),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.1),
-                  annotate(geom="text",x=855,y=1.01,label="Training",size=3.1),
+                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
+                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
                   theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
@@
 ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
+  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
 ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
+  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
 # gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)

### 2023-10-16 Manuscript/manuscript.qmd
More complete draft of manuscript pdf

--- 2023-10-16 IGAS.qmd
@@
 ---
-title: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: last-modified
-#page-layout: full
-code-fold: true
-code-tools: true
+title: "Dissertation"
+short-title: "Variability and Generalization"
+date: 10-11-2023
+author:
+- name: Thomas Gorman
+  affiliation: Indiana University
+  url: www.tegorman13.github.io
+  email: tegorman@iu.edu
+  orcid: 0000-0001-5366-5442
+
+abstract: |
+  In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations.
+keywords:
+  - Learning Generalization
+  - Function Learning
+  - Visuomotor learning
+  - Training Variability
+code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
+bibliography: ../Assets/Bib/Dissertation.bib
+link-citations: true
+keep-md: true
 execute: 
@@
   eval: true
-editor: 
-  markdown: 
-    wrap: 72
+  include: false
 ---
 
-[Pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
-
-```{r}
-pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)
-source('Functions/IGAS_ProcessFunctions.R')
-
-theme_set(theme_classic())
+```{r setup}
+here::set_here(path='..')
+source(here::here("Functions", "packages.R"))
+
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
+
+knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
+                      warning = FALSE, message = FALSE, eval=TRUE)
+
+knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+                      fig.width = 6, fig.height = (6 * 0.618),
+                      out.width = "100%", collapse = TRUE)
+# 
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+#
+
+```
+
+```{r}
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+
 # load the processed data from experiment 1 and 2
-e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
 # load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
 
@@
 defaultContrasts = options()$contrasts
-theme_set(theme_classic())
 
@@
 
-# Abstract
+# Project 1
+
+## Abstract
 
@@
 
-# Introduction
+## Introduction
 
@@
 
-## Similarity and instance-based approaches to transfer of learning
+### Similarity and instance-based approaches to transfer of learning
 
@@
 
-## Issues with Previous Research
+### Issues with Previous Research
 
@@
 
-# Experiment 1
-
-## Methods
-
-### Sample Size Estimation
+## Experiment 1
+
+### Methods
+
+#### Sample Size Estimation
 
@@
 
-### Participants
+#### Participants
 
@@
 
-### Task
+#### Task
 
@@
 ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-IGAS_Methods displays the layout of the task, as
+simply as distance. @fig-igasTask displays the layout of the task, as
 it would appear to a participant at the start of a trial, with the ball
@@
 
-```{r}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
+![The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
-
-mf <- cowplot::ggdraw()+cowplot::draw_image("Assets/methodsFig1.png",hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
-
-```
-
-## Results
-
-## Data Processing and Statistical Packages
+Participants were constrained to release the ball within the square](../Assets/methodsFig1.png){#fig-igasTask}
+
+### Results
+
+#### Data Processing and Statistical Packages
 
@@
 
-## Training Phase
-
-@fig-IGAS_Training1 below shows aggregate training performance binned into three
+#### Training Phase
+
+@fig-IGAS-Training1 below shows aggregate training performance binned into three
 stages representing the beginning, middle, and end of the training
@@
 ```{r}
-#| label: fig-IGAS_Training1
+#| label: fig-IGAS-Training1
 #| fig.cap: Training performance for varied and constant participants binned into three stages.
@@
 
-## Testing Phase
+### Testing Phase
 
@@
 ```{r}
-#| label: fig-IGAS_Testing1
+#| label: fig-IGAS-Testing1
 #| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
@@
 ```{r}
-#| label: tbl-IGAS_Table1
+#| label: tbl-IGAS-Table1
 #| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
@@
 
-## Discussion
+### Discussion
 
@@
 
-# Experiment 2
+## Experiment 2
 
@@
 
-### Data Processing and Statistical Packages
+#### Data Processing and Statistical Packages
 
@@
 
-### Training Phase
+#### Training Phase
 
@@
 
-### Testing Phase
+#### Testing Phase
 
@@
 \
-\
-\
 
@@
 \
-\
 
@@
 
-# Computational Model
+### Computational Model
 
@@
 
-## Fitting model parameters separately by group
+#### Fitting model parameters separately by group
 
@@
 
-# General Discussion
+### General Discussion
 
@@
 our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy_Model2 we
+data, not just that of the identity comparisons, in @fig-Toy-Model2 we
 demonstrate how a simplified version of the IGAS model could in
@@
 ```{r}
-#| label: fig-Toy_Model2
+#| label: fig-Toy-Model2
 #| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
@@
 Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
+#| fig.width: 11
+#| fig.height: 10
 
@@
 
-## References
+# Project 2
+
+```{r}
+test <- readRDS(here::here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
+#options(brms.backend="cmdstanr",mc.cores=4)
+e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
+testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+# Introduction
+
+In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations.
+Extrapolation has long been a focus of the literature on function learning [@brehmerHypothesesRelationsScaled1974; @carrollFunctionalLearningLearning1963].
+Central questions of the function learning literature have included the relative difficulties of learning various functional forms (e.g.
+linear vs.bilinear vs.
+quadratic), and the relative effectiveness of rule-based vs.
+association-based exemplar models vs.
+various hybrid models [@bottNonmonotonicExtrapolationFunction2004; @deloshExtrapolationSineQua1997; @jonesActiveFunctionLearning2018; @kalishPopulationLinearExperts2004; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+However the issue of training variation has received surprisingly little attention in this area.
+
+# Methods
+
+## Participants
+
+Data was collected from 647 participants (after exclusions).
+The results shown below consider data from subjects in our initial experiment, which consisted of 196 participants (106 constant, 90 varied).
+The follow-up experiments entailed minor manipulations: 1) reversing the velocity bands that were trained on vs.
+novel during testing; 2) providing ordinal rather than numerical feedback during training (e.g.
+correct, too low, too high).
+The data from these subsequent experiments are largely consistently with our initial results shown below.
+
+## Task
+
+We developed a novel visuomotor extrapolation task, termed the Hit The Wall task, wherein participants learned to launch a projectile such that it hit a rectangle at the far end of the screen with an appropriate amount of force.
+Although the projectile had both x and y velocity components, only the x-dimension was relevant for the task.  [Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}
+
+## Procedure
+Upon arrival at the laboratory, participants were provided with a description of the experiment and signed informed consent forms.
+They were then seated in front of a computer equipped with a mouse and were given instructions on how to perform the "Hit The Wall" (HTW) visuomotor extrapolation task.
+
+The HTW task involved launching projectiles to hit a target displayed on the computer screen.
+Participants completed a total of 90 trials during the training stage.
+In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
+In contrast, participants in the constant training condition encountered only one velocity band (800-1000).
+
+During the training stage, participants in both conditions also completed "no feedback" trials, where they received no information about their performance.
+These trials were randomly interleaved with the regular training trials.
+
+Following the training stage, participants proceeded to the testing stage, which consisted of three phases.
+In the first phase, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
+
+In the second phase of testing, participants completed "no-feedback" testing from the three velocity bands used during the training stage (800-1000, 1000-1200, and 1200-1400).
+In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
+
+The third and final phase of testing involved "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 10 trials.
+Participants received feedback on their performance during this phase.
+
+Throughout the experiment, participants' performance was measured by calculating the distance between the produced x-velocity of the projectiles and the closest edge of the current velocity band.
+Lower distances indicated better performance.
+
+After completing the experiment, participants were debriefed and provided with an opportunity to ask questions about the study.
+
+```{dot}
+//| label: fig-design-e1
+//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
+//| fig-width: 6.0
+//| fig-height: 2.5
+//| fig-responsive: false
+//| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+
+```
+
+## Analyses Strategy
+
+All data processing and statistical analyses were performed in R version 4.31 @rcoreteamLanguageEnvironmentStatistical2020.
+To assess differences between groups, we used Bayesian Mixed Effects Regression.
+Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019a.
+Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
+Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as circumventing convergence issues common to the frequentist analogues of our mixed models.
+For each model, we report the median values of the posterior distribution, and 95% credible intervals.
+
+Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 of which were discarded as warmup chains.
+Rhat values were generally within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
+We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
+
+We compared varied and constant performance across two measures, deviation and discrimination.
+Deviation was quantified as the absolute deviation from the nearest boundary of the velocity band, or set to 0 if the throw velocity fell anywhere inside the target band.
+Thus, when the target band was 600-800, throws of 400, 650, and 1100 would result in deviation values of 200, 0, and 300, respectively.
+Discrimination was measured by fitting a linear model to the testing throws of each subjects, with the lower end of the target velocity band as the predicted variable, and the x velocity produced by the participants as the predictor variable.
+Participants who reliably discriminated between velocity bands tended to have positive slopes with values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
+
+```{r}
+#| label: tbl-e1-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap:
+#|   - "Full datasets"
+#|   - "Intersection of samples with all labels available"
+#| layout-ncol: 1
+#| include: true
+#| echo: false
+
+result <- test_summary_table(test, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+
+result$constant |>kbl(booktabs = TRUE,
+                        linesep = "\\addlinespace[0.5em]",
+                        caption = paste("Summary of Deviation- Constant"))
+# |>
+#   kable_styling(font_size = ifelse(fmt_out == "latex", 8.5, NA))
+
+result$varied |> kbl(booktabs = TRUE,
+                        linesep = "\\addlinespace[0.5em]",
+                        caption = paste("Summary of Deviation- Varied"))
+
+```
+
+## Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e1-test-nf-deviation and @fig-e1-test-dev.
+To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+```{=tex}
+\begin{equation}
+dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
+\end{equation}
+```
+
+```{r}
+#| label: fig-e1-test-dev
+#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
+#| include: true
+test |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target")
+```
+
+```{r}
+#| label: tbl-e1-bmm-dist
+#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+#| tbl-subcap: ["Constant Testing1 - Deviation", "Varied Testing - Deviation"]
+#| include: true
+#| echo: false
+#| eval: true
+modelName <- "e1_testDistBand_RF_5K"
+e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=test,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+GetModelStats(e1_distBMM) |> kbl(booktabs = TRUE,caption = paste("Coefficients"))
+
+e1_distBMM |> 
+  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
+          epred = TRUE, re_formula = NA) |> 
+  pairs() |> gather_emmeans_draws()  |> 
+   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
+   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
+   mutate(across(where(is.numeric), \(x) round(x, 2)),
+          pd=ifelse(value<0,1-pd,pd)) |> kbl(booktabs = TRUE)
+# |> 
+#   kbl(caption="Contrasts")
+
+coef_details <- get_coef_details(e1_distBMM, "conditVaried")
+
+```
+
+The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X).
+Overall, the varied training group showed a larger deviation relative to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]).
+Deviation also depended on target velocity band, with lower bands showing less deviation.
+See @tbl-e1-bmm-dist for full model output.
+
+#### Discrimination between bands
+
+In addition to accuracy/deviation, we also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e1-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants on each testing trial.
+
+```{=tex}
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+```
+
+```{r}
+#| label: fig-e1-test-vx
+#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 9
+#| include: true
+test %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e1-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| layout-ncol: 1
+#| include: true
+
+result <- test_summary_table(test, "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kbl(booktabs = TRUE)
+result$varied |> kbl(booktabs = TRUE)
+
+```
+
+```{r}
+#| label: tbl-e1-bmm-vx
+#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
+#| include: true
+#| eval: true
+e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+GetModelStats(e1_vxBMM ) |> kbl(booktabs=T, caption="Fit to all 6 bands")
+
+cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e1_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
+
+modelName <- "e1_extrap_testVxBand"
+e1_extrap_VxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                  data=test |>
+                    filter(expMode=="test-Nf"),file=paste0(here::here("data/model_cache",modelName)),
+                  iter=5000,chains=4)
+GetModelStats(e1_extrap_VxBMM ) |> kable(booktabs=T, caption="Fit to 3 extrapolation bands")
+
+sc2 <- get_coef_details(e1_extrap_VxBMM, "bandInt")
+intCoef2 <- get_coef_details(e1_extrap_VxBMM, "conditVaried:bandInt")
+
+```
+
+See @tbl-e1-bmm-vx for the full model results.
+The estimated coefficient for training condition ($B$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
+Most relevant to the issue of discrimination is the slope on Velocity Band ($B$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
+Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
+The estimate for the interaction between slope and condition ($B$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition.
+This difference is depicted visually in @fig-e1-bmm-vx.@tbl-e1-slope-quartile shows the average slope coefficients for varied and constant participants separately for each quartile.
+The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination.
+Figure @fig-e1-bmm-bx2 shows the distributions of slope values for each participant, and the compares the probability density of slope coefficients between training conditions.
+@fig-e1-indv-slopes
+
+The second model, which focused solely on extrapolation bands, revealed similar patterns.
+The Velocity Band term ($B$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]) still demonstrates a high degree of discrimination ability.
+However, the posterior distribution for interaction term ($B$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\] ) does across over 0, suggesting that the evidence for decreased discrimination ability for the varied participants is not as strong when considering only the three extrapolation bands.
+
+```{r}
+#| label: fig-e1-bmm-vx
+#| fig-cap: Conditional effect of training condition and Band.
+Ribbons indicate 95% HDI.
+The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
+#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
+#| layout-ncol: 2
+#| include: true
+
+e1_vxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |> 
+  condEffects() +
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(test$vb), 
+                     limits = c(0, 1400))
+
+e1_extrap_VxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600))) |>
+  gather_emmeans_draws() |>
+  condEffects() +
+  scale_x_continuous(breaks = c(100, 350, 600), 
+                     labels = levels(test$vb)[1:3], 
+                     limits = c(0, 1000))
+
+```
+
+```{r}
+#| label: tbl-e1-slope-quartile
+#| tbl-cap: "Slope coefficients by quartile, per condition"
+
+new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")]))) |> 
+  dplyr::arrange(id,bandInt) |> 
+  mutate(condit_dummy = ifelse(condit == "Varied", 1, 0))
+
+indv_coefs <- as_tibble(coef(e1_vxBMM)$id, rownames="id")|> 
+  select(id, starts_with("Est")) |>
+  left_join(e1Sbjs, by=join_by(id) )
+
+fixed_effects <- e1_vxBMM |> 
+  spread_draws(`^b_.*`,regex=TRUE) |> arrange(.chain,.draw,.iteration)
+
+random_effects <- e1_vxBMM |> 
+  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
+  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
+  mutate(id = factor(id,levels=levels(test$id))) |> 
+  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)
+
+ indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
+  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
+  right_join(new_data_grid, by = join_by("id")) |> 
+  mutate(
+    Slope = bandInt_RF+b_bandInt,
+    Intercept= RF_Intercept + b_Intercept,
+    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
+    SlopeInt = Slope + (`b_conditVaried:bandInt`*condit_dummy)
+  )
+
+  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt, Intercept,b_Intercept,b_bandInt) |>
+  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
+    select(id,condit,Intercept,b_Intercept,starts_with("Slope"),b_bandInt, n) |>
+  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()
+
+  indvSlopes |> mutate(Condition=condit) |>  group_by(Condition) |> 
+    reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
+  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
+  group_by(Condition) |>
+  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()
+
+```
+
+```{r}
+#| label: fig-e1-bmm-bx2
+#| fig-cap: Slope distributions between condition
+#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
+#| layout-ncol: 2
+#| fig-height: 9
+#| fig-width: 10
+#| include: true
+
+  indvSlopes |> ggplot(aes(y=rankSlope, x=SlopeInt,fill=condit,color=condit)) + 
+  geom_pointrange(aes(xmin=SlopeInt.lower , xmax=SlopeInt.upper)) + 
+  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)
+
+   ggplot(indvSlopes, aes(x = SlopeInt, color = condit)) + 
+  geom_density() + labs(x="Slope Coefficient",y="Density")
+
+```
+
+```{r}
+#| label: fig-e1-indv-slopes
+#| fig-cap: Subset of Varied and Constant Participants with the smallest and largest estimated slope values.
+Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution.
+Colored points and intervals at each band represent the empirical median and 95% HDI.
+#| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
+#| fig-height: 10
+#| fig-width: 12
+#| include: true
+
+nSbj <- 3
+indvDraws  |> indv_model_plot(indvSlopes, testAvg, SlopeInt,rank_variable=Slope,n_sbj=nSbj,"max")
+indvDraws |> indv_model_plot(indvSlopes, testAvg,SlopeInt, rank_variable=Slope,n_sbj=nSbj,"min")
+
+```
+
+# Experiment 2
+
+```{r setup2b, include=FALSE}
+testE2 <- readRDS(here::here("data/e2_08-21-23.rds")) |> filter(expMode2 == "Test") 
+e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
+testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+@fig-design-e2 illustrates the design of Experiment 2.
+The stages of the experiment (i.e.
+training, testing no-feedback, test with feedback), are identical to that of Experiment 1.
+The only change is that Experiment 2 participants train, and then test, on bands in the reverse order of Experiment 1 (i.e.
+training on the softer bands; and testing on the harder bands).
+
+```{dot}
+//| label: fig-design-e2
+//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
+//| fig-width: 6.0
+//| fig-height: 2.5
+//| fig-responsive: false
+//| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+
+```
+
+## E2 Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e2-test-nf-deviation and @fig-e2-test-dev. 
+To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+\begin{equation}
+dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: tbl-e2-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
+
+result <- test_summary_table(testE2, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kbl()
+result$varied |> kbl()
+# make kable table with smaller font size
+# result$constant |> kbl(caption="Constant Testing - Deviation",booktabs=T,escape=F) |> kable_styling(font_size = 7)
+```
+
+```{r}
+#| label: fig-e2-test-dev
+#| fig-cap: E2. Deviations from target band during testing without feedback stage. 
+testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target")
+```
+
+```{r}
+#| label: tbl-e2-bmm-dist
+#| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+#| eval: true
+
+modelName <- "e2_testDistBand_RF_5K"
+e2_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=testE2,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+mp2 <- GetModelStats(e2_distBMM) |> kable(booktabs=T)
+mp2
+
+e2_distBMM |> 
+  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
+          epred = TRUE, re_formula = NA) |> 
+  pairs() |> gather_emmeans_draws()  |> 
+   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
+   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
+   mutate(across(where(is.numeric), \(x) round(x, 2)),
+          pd=ifelse(value<0,1-pd,pd)) |>
+   kbl(caption="Contrasts")
+
+coef_details <- get_coef_details(e2_distBMM, "conditVaried")
+
+```
+
+The model predicting absolute deviation showed a modest tendency for the varied training group to have lower deviation compared to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]),with 94% of the posterior distribution being less than 0.
+This suggests a potential benefit of training with variation, though the evidence is not definitive.
+
+# Experiment 3
+
+```{r setup3b, include=FALSE}
+testE3 <- readRDS(here::here("data/e3_08-21-23.rds")) |> filter(expMode2 == "Test") 
+e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
+testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+The major manipulation adjustment of experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the earlier experiments.
+Ordinal feedback informs participants whether a throw was too soft, too hard, or fell within the target velocity range.
+Experiment 3 participants were randomly assigned to both a training condition (Constant vs.
+Varied) and a Band Order condition (original order used in Experiment 1, or the Reverse order of Experiment 2).
+
+## Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+Note that these no-feedback testing trials are identical to those of Experiment 1 and 2, as the ordinal feedback only occurs during the training phase, and final testing phase, of Experiment 3.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e3-test-nf-deviation and @fig-e3-test-dev. 
+To model differences in accuracy between groups, we fit Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+```{r}
+#| label: tbl-e3-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
+
+resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+resultOrig$constant |> kbl()
+resultOrig$varied |> kbl()
+
+resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+resultRev$constant |> kbl()
+resultRev$varied |> kbl()
+
+```
+
+```{r}
+#| label: fig-e3-test-dev
+#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
+testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder)
+```
+
+```{r}
+#| label: tbl-e3-bmm-dist
+#| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+#| eval: true
+
+modelName <- "e3_testDistBand_RF_5K"
+e3_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=testE3,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+mp3 <- GetModelStats(e3_distBMM) |> kable(booktabs=T)
+mp3
+
+cd1 <- get_coef_details(e3_distBMM, "conditVaried")
+sc1 <- get_coef_details(e3_distBMM, "bandInt")
+intCoef1 <- get_coef_details(e3_distBMM, "conditVaried:bandInt")
+```
+
+The effect of training condition in Experiment 3 showed a similar pattern to Experiment 2, with the varied group tending to have lower deviation than the constant group (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0.
+
+```{r}
+#| label: fig-e3-bmm-dist
+#| fig-cap: e3. Conditioinal Effect of Training Condition and Band. Ribbon indicated 95% Credible Intervals.
+
+e3_distBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |>
+  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+    ylab("Predicted Deviation") + xlab("Velocity Band")+
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE3$vb), 
+                     limits = c(0, 1400)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+```
+
+#### Discrimination between Velocity Bands
+
+In addition to accuracy/deviation.
+We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e3-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
+
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: fig-e3-test-vx
+#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 14
+#| fig-height: 15
+#| column: screen-inset-right
+# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
+# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
+
+testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
+  facet_wrap(bandOrder~condit,scale="free_x")
+
+```
+
+```{r}
+#| label: tbl-e3-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
+
+resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+resultOrig$constant |> kbl()
+resultOrig$varied |> kbl()
+
+resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+resultRev$constant |> kbl()
+resultRev$varied |> kbl()
+```
+
+```{r}
+#| label: tbl-e3-bmm-vx
+#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+#| eval: true
+e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+mt4 <-GetModelStats(e3_vxBMM ) |> kable(booktabs=T)
+mt4
+
+cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e3_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
+```
+
+See @tbl-e3-bmm-vx for the full model results.
+
+Slope estimates for experiment 3 suggest that participants were capable of distinguishing between velocity bands even when provided only ordinal feedback during training (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
+Unlike the previous two experiments, the posterior distribution for the interaction between condition and band was consistently positive, suggestive of superior discrimination for the varied participants
+β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\].
+
+# Modeling
+
+In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning (DeLosh 1997).
+ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model (Kruscke 1992), with modifications to allow for the generation of continuous responses.
+
+## ALM & Exam Description
+
+@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks.
+ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].
+
+ALM is a localist neural network model, with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
+The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
+So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
+Depending on thevalue of the generalization parameter, the nearby units (e.g.
+54 and 56; 53 and 57) may also activate to some degree.
+ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
+The units in the input layer activate as a function of their similarity to a presented stimulus.
+As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
+The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
+The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
+During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
+The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
+
+See  for a full specification of the equations that define ALM and EXAM.
+
+{{< pagebreak >}}
+
+## Model Table
+### ALM Activation & Response
+| Step | Equation | Description |
+|------|----------|-------------|
+| **ALM Activation & Response**  |           |
+| Input Activation | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$ | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.
+|
+| Output Activation                 | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$ | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.   |
+| Output Probability                | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$ | Each output node has associated response, $Y_j$.
+The probability of response $Y_j$ is determined by the ratio of output activations.
+|
+| Mean Output                       | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$   | The response to stimulus x is the weighted average of the response probabilities. |
+| **ALM Learning**                  |                                                                                                                                                          |
+| Feedback Activation               | $f_j(Z) = e^{-c(Z-Y_j)^2}$                  | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response.
+|
+| Update Weights                    | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$    | Delta rule to update weights.
+Magnitude of weight changes controlled by learning rate parameter alpha.
+|
+| **EXAM**                          |                                                                                                                                                          |
+| Extrapolation                     | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$ | Novel test stimulus X activates input nodes associated with trained stimuli.     |
+|                                   | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)    |
+
+{{< pagebreak >}}
+
+## Model Fitting and Comparison
+
+Following the procedure used by @mcdanielPredictingTransferPerformance2009, we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data.
+Models will be fit directly to the trial by trial data of each individual participants, both by minimizing the root-mean squared deviation (RMSE), and by maximizing log likelihood.
+Because ALM has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also fit the extended EXAM version of the model, which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.
+
+# References

### 2023-10-16 Manuscript/test_igas.qmd
More complete draft of manuscript pdf

--- 2023-10-16 IGAS.qmd
@@
 ---
-title: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: last-modified
-#page-layout: full
-code-fold: true
-code-tools: true
-execute: 
-  warning: false
-  eval: true
-editor: 
-  markdown: 
-    wrap: 72
+title: "HTW"
+short-title: "Variability and Generalization"
+date: 10-11-2023
+bibliography: ../Assets/Bib/Dissertation.bib
+link-citations: true
+keep-md: true
+# execute: 
+#   warning: false
+#   eval: true
+#   include: false
 ---
 
-[Pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
+```{r setup, include=FALSE}
+library(here)
+here::set_here(path='..')
+source(here::here("Functions", "packages.R"))
+# test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
+# testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+#   summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
+
+knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+                      fig.width = 6, fig.height = (6 * 0.618),
+                      out.width = "100%", collapse = TRUE)
+# 
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+#
+
+```
 
 ```{r}
-pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)
-source('Functions/IGAS_ProcessFunctions.R')
-
-theme_set(theme_classic())
+
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+
 # load the processed data from experiment 1 and 2
-e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
 # load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
 
@@
 
-## Training Phase
+#### Training Phase
 
@@
 ```{r}
-#| label: fig-IGAS_Training1
+#| label: fig-igasTraining1
 #| fig.cap: Training performance for varied and constant participants binned into three stages.
@@
 ```{r}
-#| label: tbl-IGAS_Table1
+#| label: tbl-igasTable1
 #| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
@@
 
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>%   
-  kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
+ #kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"))  #%>% kableExtra::kable_styling(position="left") #%>%   
+#   kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
+
+```
+
+### Discussion
 
@@
 
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
+# kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  #%>% kableExtra::kable_styling(position="left") %>% 
+#   #kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
+# kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  #%>% kableExtra::kable_styling(position="left") %>% 
+#   #kable_classic() #%>% footnote(general=captionText,general_title = "")
 ```
@@
 
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
+# kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
+#   kable_classic() #%>% footnote(general=captionText,general_title = "")
+
+```
+
+### Discussion
 
@@
 
-## References
+# References

### 2023-10-16 paper.qmd
More complete draft of manuscript pdf

---
title: Dissertation Manuscript
toc: false
page-layout: full
---

```{=html}
<p class="text-center">
  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="manuscript">
  <iconify-icon inline="" icon="fa6-solid:file-lines"></iconify-icon> &ensp;HTML
  </a>

  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="_blank">
  <iconify-icon inline="" icon="fa6-solid:arrow-up-right-from-square"></iconify-icon> &ensp;HTML <small>(new window)</small>
  </a>

  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/Full_Dissertation-nice.pdf" target="manuscript">
  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;PDF
  </a>

  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/Full_Dissertation-nice.pdf">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
  </a>

</p>

<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
```

### 2023-10-16 Functions/Display_Functions.R

@@ -1,0 +1,630 @@
+
+
+pacman::p_load(ggplot2,wesanderson,glue, ggdist,ggforce,patchwork,gghalves)
+#pacman::p_load(ggplot2,ggpattern,viridis,scales,wesanderson,ggthemer)
+options(dplyr.summarise.inform=FALSE)
+
+select <- dplyr::select
+mutate <- dplyr::mutate
+filter <- dplyr::filter
+map <- purrr::map
+
+#### Bayesian/Brms functions
+
+brms_posterior_checks <- function(brmModel, yvar, gvar, ndraws = 50) {
+  
+  dat <- brmModel$data
+  
+  yvar_name <- deparse(substitute(yvar))
+  gvar_name <- deparse(substitute(gvar))
+  
+  y_data <- dat[[yvar_name]]
+  g_data <- dat[[gvar_name]]
+  
+  msum <- summary(brmModel)
+  pt <- posterior_table(brmModel)
+  timeTab <- rstan::get_elapsed_time(brmModel[["fit"]]) |> 
+    as_tibble(rownames = "chain") |>  mutate(total_seconds = warmup + sample) 
+  
+  print(msum)
+  print(pt)
+  print(timeTab)
+  
+  if (brmModel$family$family == "gaussian") {
+   # print(conditional_effects(brmModel))
+    print(pp_check(brmModel, type = "stat_grouped", group = "vb", ndraws = ndraws))
+  #  print(bayes_R2(brmModel))
+    
+  }
+  print(bayesplot::ppc_dens_overlay_grouped(y_data, posterior_predict(brmModel, ndraws = ndraws), g_data))
+  #fixef(brmModel,summary=TRUE)
+}
+
+
+
+plot_subject_fits <- function(model, subject_code) {
+  pattern <- glue("^r_id\\[{subject_code},.*\\]")
+  plot <- mcmc_areas(model, prob = .5, regex_pars = c(pattern)) +
+    ggtitle(glue("fit for subject #{subject_code}:"))
+  return(plot)
+}
+
+
+
+posterior_table <- function(model){
+  bayestestR::describe_posterior(model,
+                                 verbose=FALSE,
+                                 test=c("p_direction","p_significance"),
+                                 centrality=c("median"),
+                                 dispersion=FALSE)
+  
+}
+
+
[…]

### 2023-10-16 Functions/IGAS_ProcessFunctions.R

@@ -11,6 +11,7 @@ mutate <- dplyr::mutate
 filter <- dplyr::filter
 rename <- dplyr::rename
 summarise <- dplyr::summarise
+summarize <- dplyr::summarise
 #rm(list=ls())
 dodge <- position_dodge(width = 0.9)
 

### 2023-10-16 Functions/Table_Functions.R

@@ -1,0 +1,185 @@
+
+# 
+# create_summary_table <- function(data, DV, mfun = list(mean = mean, sd = sd)) {
+#   # Grouping by required variables and computing statistics specified in mfun
+#   summarization <- data %>%
+#     group_by(vb, bandType, condit) %>%
+#     summarise(across(.data[[DV]], mfun, .names = "{.fn}_{.col}"), .groups = 'drop')
+#   
+#   # Correctly renaming the columns to have clear stat names
+#   cols_to_rename <- grep(paste0("^.*_", DV), names(summarization), value = TRUE)
+#   new_colnames <- sapply(strsplit(cols_to_rename, "_"), `[`, 1)
+#   names(summarization)[names(summarization) %in% cols_to_rename] <- new_colnames
+#   
+#   return(summarization)
+# }
+# 
+# create_summary_table(test, "vx", mfun = list(mean = mean, median = median, sd = sd))
+
+
+test_summary_table <- function(data, DV,dlab, mfun = list(mean = mean, sd = sd)) {
+  # Grouping by required variables and computing statistics specified in mfun
+  summarization <- data %>%
+    group_by(vb, bandType, condit) %>%
+    summarise(across(all_of(DV), mfun, .names = "{.fn}_{.col}"), .groups = 'drop') %>%
+    mutate(across(matches(DV), ~ round(.x, 0)))
+  
+  # Correctly renaming the columns to have clear stat names
+  cols_to_rename <- grep(paste0("^.*_", DV), names(summarization), value = TRUE)
+  new_colnames <- sapply(strsplit(cols_to_rename, "_"), `[`, 1)
+  new_colnames <- sapply(new_colnames, function(name) paste0(toupper(substr(name, 1, 1)), substr(name, 2, nchar(name))))
+  names(summarization)[names(summarization) %in% cols_to_rename] <- new_colnames
+  summarization <- summarization |> rename("Band"=vb, "Band Type"=bandType)
+  
+  # summarization <- summarization %>%
+  #   mutate(across(matches(DV), ~cell_spec(.x, font_size = 4)))
+  
+  # Splitting the table into constant and varied groups
+  constant_table <- summarization %>%
+    filter(condit == "Constant") %>%
+    select(-condit) 
+    # kable(caption = paste("Summary of", dlab, "- Constant")) #|>
[…]

### 2023-10-16 Functions/org_functions.R

@@ -1,0 +1,322 @@
+
+
+#walk(paste0("Functions/", c("Display_Functions.R", "org_functions.R")), ~source(here::here(.)))
+
+
+# options(digits = 2, width = 120,
+#         dplyr.summarise.inform = FALSE,
+#         knitr.kable.NA = "")
+
+
+
+get_coef_details <- function(model, term_name) {
+  broom.mixed::tidy(model) |>
+    filter(term == term_name) |> 
+    select(estimate, conf.low, conf.high) |> 
+    mutate(across(where(is.numeric), \(x) round(x, 2)))
+}
+
+
+
+condEffects <- function(m){
+  m |> ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
+    stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
+    stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+    theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
+    ylab("Predicted X Velocity") + xlab("Band")
+}
+
+
+gen_trials <- function(blocks=3,numinputs=3,shuffle=FALSE) {
+  if (shuffle) {
+    examples <- as.vector(apply(replicate(blocks,seq(1, numinputs)), 2,
+                                sample, numinputs))
+  } else{
+    examples <- as.vector(replicate(blocks, seq(1, numinputs)))
+  }
+}
+
+custom_scale <- function(x) {
+  if (sd(x) == 0) {
+    return(as.vector(rep(0, length(x))))
+  } else {
+    return(as.vector(scale(x)))
+  }
+}
+
+
+
+# ks2 = model_parameters(e1_testDistRF2_0,effects="random",keep="^r_id*") 
+# ks2 <- ks2 %>%
+#   mutate(
+#     id = str_extract(Parameter, "(?<=\\[)\\d+"), # Extract digits after the opening square bracket
+#     vb = str_extract(Parameter, "\\d+M\\d+") %>%
+#       str_remove("vb") %>%
+#       str_replace("M", "-")
+#   )
+
+GetIndvFits <- function(model) {
+ks2 = parameters::model_parameters(model,effects="random",keep="^r_id*") 
+ks2 <- ks2 |>
+  mutate(
+    id = factor(gsub(".*\\[([0-9]+),.*", "\\1", Parameter)),
[…]

### 2023-10-16 Functions/packages.R

@@ -1,0 +1,24 @@
+#### INSTALL AND LOAD PACKAGES ==========================================================
+# install pacman package if not installed -----------------------------------------------
+suppressWarnings(if (!require("pacman")) install.packages("pacman"))
+#remotes::install_github("mattcowgill/ggannotate")
+# load packages and install if not installed --------------------------------------------
+pacman::p_load(tidyverse,tidybayes,brms, lme4, bayesplot,bayestestR,parameters,marginaleffects,
+                emmeans, equatiomatic, here, pacman,  broom,
+               broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt,
+                wesanderson,glue, ggdist,ggforce,patchwork,gghalves,ggh4x,modelsummary,
+                pander,RColorBrewer,
+                install = TRUE,
+                update = FALSE
+               )
+
+# show loaded packages ------------------------------------------------------------------
+# cat("loaded packages\n")
+# print(pacman::p_loaded())
+
+select <- dplyr::select
+mutate <- dplyr::mutate
+filter <- dplyr::filter
+map <- purrr::map
+walk(c(here("Functions/Display_Functions.R"), here("Functions/org_functions.R"), 
+       here("Functions/Table_Functions.R")), source)

### 2023-10-16 Manuscript/.vdoc.r

@@ -1,0 +1,2091 @@
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+here::set_here(path='..')
+source(here::here("Functions", "packages.R"))
+
+
+
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
+
+
+knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
+                      warning = FALSE, message = FALSE, eval=TRUE)
+
+
+
+knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+                      fig.width = 6, fig.height = (6 * 0.618),
+                      out.width = "100%", collapse = TRUE)
+# 
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+# 
+
+#
+#
+#
+#
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+
+# load the processed data from experiment 1 and 2
+
+
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
+
+options(contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
[…]

### 2023-10-16 HTW.qmd
fix image issue

@@
 page-layout: full
-bibliography: "Bib/HTW.bib"
+bibliography: "Assets/Bib/HTW.bib"
 code-fold: true
@@
 ```
-
 # Introduction
@@
 but includes a linear extrapolation mechanism for generating novel responses during testing. 
-
+[@albaretDifferentialEffectsTask1998]
 \

### 2023-10-16 paper.qmd
render again

@@
 
-  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/Full_Dissertation-nice.pdf">
-  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
+   <a class="btn btn-warning btn-sm mb-1" href="/manuscript/manuscript.pdf.md" target="manuscript">
+  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscript-md
   </a>

### 2023-10-16 index.qmd
try again with index

---
title: "Dissertation"
comments: false
date-format: 'MMM YYYY'
format:
  html:
    grid:
      sidebar-width: 250px
      body-width: 1400px
      margin-width: 170px
      gutter-width: 1.5rem
    self-contained: false
---

# An instance-based model account of the benefits of varied practice in visuomotor skill

### 2023-10-16 paper.qmd
fix case on Manuscript links

@@
 <p class="text-center">
-  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="manuscript">
+  <a class="btn btn-success btn-sm mb-1" href="/Manuscript/output/manuscript.html" target="manuscript">
   <iconify-icon inline="" icon="fa6-solid:file-lines"></iconify-icon> &ensp;HTML
@@
 
-  <a class="btn btn-success btn-sm mb-1" href="/manuscript/output/manuscript.html" target="_blank">
+  <a class="btn btn-success btn-sm mb-1" href="/Manuscript/output/manuscript.html" target="_blank">
   <iconify-icon inline="" icon="fa6-solid:arrow-up-right-from-square"></iconify-icon> &ensp;HTML <small>(new window)</small>
@@
 
-  <a class="btn btn-danger btn-sm mb-1" href="/manuscript/output/Full_Dissertation-nice.pdf" target="manuscript">
+  <a class="btn btn-danger btn-sm mb-1" href="/Manuscript/output/Full_Dissertation-nice.pdf" target="manuscript">
   <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;PDF
@@
 
-   <a class="btn btn-warning btn-sm mb-1" href="/manuscript/manuscript.pdf.md" target="manuscript">
+   <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/manuscript.pdf.md" target="manuscript">
   <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscript-md
@@
 
-<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
+<iframe src="/Manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
 ```

### 2023-10-17 HTW.qmd
fix toc, re-render, minor fig issues

@@
 ---
+
+[Link HTW project page](https://tegorman13.github.io/htw/){target="_blank"}
 
@@
 ",width=700,height=250)
+
+```
+
+```{dot}
+//| label: fig-design-e1
+//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
+//| fig-width: 6.0
+//| fig-height: 2.5
+//| fig-responsive: false
+//| column: screen-inset-right
+//| fig-align: left
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
 

### 2023-10-17 IGAS.qmd
fix toc, re-render, minor fig issues

@@
 ---
-title: An instance-based model account of the benefits of varied practice in visuomotor skill
+title: IGAS Project
+subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
 date: last-modified
@@
 code-tools: true
+toc: true
+toc-location: body
+toc-title: Contents
 execute: 

### 2023-10-17 Manuscript/manuscript.qmd
fix image issue
fix toc, re-render, minor fig issues

@@
 ---
-title: "Dissertation"
-short-title: "Variability and Generalization"
-date: 10-11-2023
-author:
-- name: Thomas Gorman
-  affiliation: Indiana University
-  url: www.tegorman13.github.io
-  email: tegorman@iu.edu
-  orcid: 0000-0001-5366-5442
-
-abstract: |
-  In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
-In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations.
-keywords:
-  - Learning Generalization
-  - Function Learning
-  - Visuomotor learning
-  - Training Variability
 code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
@@
 keep-md: true
+toc: false
+toc-depth: 3
+toc-location: body
 execute: 
@@
 ---
+
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/pre_html.qmd >}}
+<!-- Manually insert the table of contents here -->
+
+:::
+
+::: {.content-visible when-format="pdf"}
+{{< include pre_sections/pre_pdf.qmd >}}
+:::
 
@@
         knitr.kable.NA = "")
-#
 
@@
                   annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=450,y=.97,label="Training",size=3.1,fontface="plain"),
                   annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=657,y=.97,label="Training",size=3.1,fontface="plain"),
                   annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=850,y=.97,label="Training",size=3.1,fontface="plain"),
                   theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
@@
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square](../Assets/methodsFig1.png){#fig-igasTask}
+Participants were constrained to release the ball within the square](Assets/methodsFig1.png){#fig-igasTask}
 
@@
 Error bars indicate standard error of the mean.
+#| fig.width: 11
+#| fig.height: 10
 
@@
 
-e2train1
-e2train2
+e2train1 / e2train2
 
@@
 target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace
+six separate similarity scores for each participant. @fig-taskSpace1
 visualizes the solution space for each location and illustrates how
@@
 striking the target from different launching positions. As illustrated
-in @fig-taskSpace, the solution throws represent just a small fraction of the
+in @fig-taskSpace1, the solution throws represent just a small fraction of the
 entire space of velocity combinations used by participants throughout
@@
 ```{r}
-#| label: fig-taskSpace
+#| label: fig-taskSpace1
 #| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
@@
 Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| 
+#| fig.height: 10
+#| fig.width: 11
 taskspace <- e2 %>% filter(AbsDistFromCenter<900)
@@
 
-ss
-fs
+ss / fs
 
@@
 certain aspects of learning and generalization may operate under common
-principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001a; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
+principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
 
@@
 //| fig-responsive: false
-//| column: screen-inset-right
+
 digraph {
@@
 To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019a.
+Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
 Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
@@
 #| echo: false
-#| eval: true
 modelName <- "e1_testDistBand_RF_5K"
@@
 #| include: true
-#| eval: true
 e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
@@
 //| fig-responsive: false
-//| column: screen-inset-right
+//| fig-align: left
 digraph {
@@
 #| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-#| eval: true
 
@@
 #| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-#| eval: true
 
@@
 #| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-#| eval: true
+
 e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),

### 2023-10-17 Manuscript/pre_sections/pre_html.qmd
fix toc, re-render, minor fig issues

<div style="text-align: center; margin-top: 50px; font-size: 24px; font-weight: bold;">
  Variability and Generalization - A Similarity-Based Account
</div>

<div style="text-align: center; margin-top: 300px; font-size: 32px;">
  Thomas E. Gorman
</div>

<!-- Second Page and so on... -->
<div style="text-align: justify; margin-top: 700px;">
  Submitted to the faculty of the University Graduate School in partial fulfillment of the
  requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
  Sciences and the Cognitive Science Program, Indiana University
  Indiana University
</div>

<div style="margin-top: 400px;">
  <!-- Your page numbering if needed -->
</div>

<div style="page-break-before: always;"></div>

<!-- Committee Members Page -->
<div style="text-align: center; margin-top: 300px;">
  Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
  requirements for the degree of Doctor of Philosophy.
</div>

<div style="text-align: center; margin-top: 300px;">
  _____________________________  Robert L. Goldstone<br><br>
  _____________________________  Robert Nosofsky<br><br>
  _____________________________  Peter Todd<br><br>
  _____________________________  Mike Jones
</div>

<div style="page-break-before: always;"></div>

<div style="page-break-before: always;"></div>

<!-- Acknowledgements -->
<div style="text-align: center; font-weight: bold; font-size: 24px;">
  Acknowledgements
</div>

<div style="page-break-before: always;"></div>

## Table of contents
<div id="html-toc"></div>
```{=html}
<script>
<!-- document.addEventListener("DOMContentLoaded", function(){ -->
<!--   var toc = document.getElementById("TOC"); -->
<!--   var placeholder = document.getElementById("toc-placeholder"); -->
<!--   if (toc && placeholder) { -->
<!--     placeholder.appendChild(toc); -->
<!--   } -->
<!-- }); -->
document.addEventListener("DOMContentLoaded", function(){
    var tocDiv = document.getElementById("html-toc");
    var headings = document.querySelectorAll('h1, h2, h3'); // adjust if you need more depth
    var tocList = document.createElement("ul");

    headings.forEach(function(heading) {
        var listItem = document.createElement("li");
        var link = document.createElement("a");
        link.textContent = heading.textContent;
        link.href = "#" + heading.id;
        listItem.appendChild(link);

        if (heading.tagName == "H2") {
            listItem.style.marginLeft = "20px";
        } else if (heading.tagName == "H3") {
            listItem.style.marginLeft = "40px";
        }
        tocList.appendChild(listItem);
    });

    tocDiv.appendChild(tocList);
});

</script>
```

### 2023-10-17 Manuscript/pre_sections/pre_pdf.qmd
fix toc, re-render, minor fig issues

\begin{centering}
\LARGE
{Variability and Generalization - A Similarity-Based Account}

\vspace*{1.5cm}

\LARGE
{Thomas E. Gorman}

\vspace{11.5cm}

\end{centering}

Submitted to the faculty of the University Graduate School in partial fulfillment of the
requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
Sciences and the Cognitive Science Program, Indiana University
Indiana University

\vspace{6cm}

\pagenumbering{gobble}

\newpage

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.
\vspace{4cm}

\
\_____________________________  Robert L. Goldstone
\vspace{2.5cm}
\
\
\_____________________________  Robert Nosofsky
\vspace{2.5cm}
\
\_____________________________  Peter Todd
\vspace{2.5cm}
\
\_____________________________  Mike Jones

\newpage

\begin{centering}

\vspace*{6.5cm}

@2023 \\
\vspace{1cm}

Thomas E. Gorman
\vspace{.2cm}

\vspace{5cm}

\end{centering}

\newpage
\begin{center}
\textbf{Acknowledgements}
\end{center}
\newpage

\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage

### 2023-10-17 Manuscript/test_igas.qmd
fix toc, re-render, minor fig issues

@@
 ---
-title: "HTW"
-short-title: "Variability and Generalization"
-date: 10-11-2023
 bibliography: ../Assets/Bib/Dissertation.bib
@@
 keep-md: true
-# execute: 
-#   warning: false
-#   eval: true
-#   include: false
+toc: false
+execute: 
+  warning: false
+  eval: true
+  include: true
 ---
+
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/pre_html.qmd >}}
+
+:::
+
+::: {.content-visible when-format="pdf"}
+{{< include pre_sections/pre_pdf.qmd >}}
+:::
 
@@
 
-```{r}
+```{r, include=FALSE}
 
@@
 
-## Introduction
+# Project 2
 
-The past century of research on human learning has produced ample
-evidence that although learners can improve at almost any task, such
-improvements are often specific to the trained task, with unreliable or
-even nonexistent transfer to novel tasks or conditions
-[@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993]. Such
-transfer challenges are of noteworthy practical relevance, given that
-educators, trainers, and rehabilitators typically intend for their
-students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that
-influence transfer, and to develop cognitive models that can predict
-when transfer is likely to occur. The factor of interest to the present
-investigation is variation during training. Our experiments add to the
-longstanding empirical investigation of the controversial relationship
-between training variation, and subsequent transfer. We also offer a
-novel explanation for such results in the form of an instance-based
-model that accounts for the benefits of variation in simple terms of
-psychological similarity. We first review the relevant concepts and
-literature.
-
-### Similarity and instance-based approaches to transfer of learning
-
-Notions of similarity have long played a central role in many prominent
-models of generalization of learning, as well as in the longstanding
-theoretical issue of whether learners abstract an aggregate, summary
-representation, or if they simply store individual instances. Early
-models of learning often assumed that discrete experiences with some
-task or category were not stored individually in memory, but instead
-promoted the formation of a summary representation, often referred to as
-a prototype or schema, and that exposure to novel examples would then
-prompt the retrieval of whichever preexisting prototype was most similar
-[@posnerGenesisAbstractIdeas1968]. Prototype
-models were later challenged by the success of instance-based or
-exemplar models -- which were shown to provide an account of
-generalization as good or better than prototype models, with the
-advantage of not assuming the explicit construction of an internal
-prototype [@estesClassificationCognition1994;
-@hintzmanMINERVASimulationModel1984;
-@medinContextTheoryClassification1978;
-@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a
-task as a separate instance/exemplar/trace, and that each encoded trace
-is in turn compared against novel stimuli. As the number of stored
-instances increases, so does the likelihood that some previously stored
-instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks
-if they are sufficiently similar, thus suggesting that the process of
-computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological
-distance between instances or categories, has provided a successful
-account of generalization across numerous tasks and domains. In an
-influential study demonstrating an ordinal similarity effect,
-experimenters employed a numerosity judgment task in which participants
-quickly report the number of dots flashed on a screen. Performance (in
-terms of response times to new patterns) on novel dot configurations
-varied as an inverse function of their similarity to previously trained
-dot configurations @palmeriExemplarSimilarityDevelopment1997. That is, performance was better on
-novel configurations moderately similar to trained configurations than
-to configurations with low-similarity, and also better on low-similarity
-configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for
-performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017; @crumpEpisodicContributionsSequential2010] trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following
-training, typing speed was tested on previously experienced words
-composed of previously experienced letters; novel words composed of
-letters from the trained letter set; and novel words composed of letters
-from an untrained letter set. Consistent with an instance-based account,
-transfer performance was graded such that participants were fastest at
-typing the words they had previously trained on, followed by novel words
-composed of letters they had trained on, and slowest performance for new
-words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of
-similarity between previous and new experiences, a largely separate body
-of research has focused on improving transfer by manipulating
-characteristics of the initial training stage. Such characteristics have
-included training difficulty, spacing, temporal order, feedback
-schedules, and the primary focus of the current work -- variability of
-training examples.
-
-Research on the effects of varied training typically compares
-participants trained under constant, or minimal variability conditions
-to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015]. Varied training has been shown to influence
-learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968],
-complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory
-extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice
-identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
-sports training  [@greenPracticeVariabilityTransfer1995; @greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
-on a complex video game [@seowTransferEffectsVaried2019].
-
-Training variation has received a particularly large amount of attention
-within the domain of visuomotor skill learning. Much of this research
-has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a
-schema-based account of motor learning as an attempt to address the
-longstanding problem of how novel movements are produced. According to
-Schema Theory, learners possess general motor programs for classes of
-movements (e.g. throwing a ball with an underhand movement), as well as
-schema rules that determine how a motor program is parameterized or
-scaled for a particular movement. Schema theory predicts that varied
-training results in the formation of a more general schema-rule, which
-can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the
-transfer performance of a constant-trained group against that of a
-varied-trained group. Both groups train on the same task, but the varied
-group practices from multiple levels of a task-relevant dimension that
-remains invariant for the constant group. For example, investigators
-might train two groups of participants to throw a projectile at a
-target, with a constant group that throws from a single location, and a
-varied group that throws from multiple locations. Both groups are then
-tested from novel locations. Empirically observed benefits of the
-varied-trained group are then attributed to the variation they received
-during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically
-thought to be mediated by the development of a more general schema for
-the throwing motion.
-
-Of course, the relationship between training variability and transfer is
-unlikely to be a simple function wherein increased variation is always
-beneficial. Numerous studies have found null, or in some cases negative
-effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the
-benefits of variability may depend on additional factors such as prior
-task experience, the order of training trials, or the type of transfer
-being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-### Issues with Previous Research
-
-Although the benefits of training variation in visuomotor skill learning
-have been observed many times, null findings have also been repeatedly
-found, leading some researchers to question the veracity of the
-variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of
-training variability, of the sort described above, often fail to control
-for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of
-freedom (e.g. projectile throwing tasks where participants control the x
-and y velocity of the projectile), varied groups are likely to
-experience a wider range of the task space over the course of their
-training (e.g. more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring
-that the training location(s) of the varied and constant groups are an
-equal distance away from the eventual transfer locations, such that
-their training throws are, on average, equally similar to throws that
-would lead to good performance at the transfer locations. However, even
-this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer. Given that psychological
-similarity is typically best described as either a Gaussian or
-exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the
-most similar training instances could have a disproportionate impact on
-generalization to transfer conditions, even if the average distance
-between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that
-drops off as a Gaussian function of distance from training, as compared
-to a linear drop-off.
-
-```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
-
-p=2
-c<- .0002
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
-  group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
-
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
-
-```
-
-In addition to largely overlooking the potential for non-linear
-generalization to confound interpretations of training manipulations,
-the visuomotor skill learning literature also rarely considers
-alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures,
-instance or exemplar-based models have accounted for human behavior
-across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a]. As mentioned above, instance based accounts have been shown to perform well on a
-variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little
-attention within the subdomain of visuomotor skill learning focused on
-the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of
-varied training can be accounted for by between-group differences in
-similarity between training and testing throws. We first attempt to
-replicate previous work finding an advantage of varied training over
-constant training in a projectile launching task. We then examine the
-extent to which this advantage can be explained by an instance-based
-similarity model.
-
-## Experiment 1
-
-### Methods
-
-#### Sample Size Estimation
-
-To obtain an independent estimate of effect size, we identified previous
-investigations which included between-subjects contrasts of varied and
-constant conditions following training on an accuracy based projectile
-launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
-2009) was then used to determine that a power of 80% requires a sample
-size of at least 23 participants per condition. All experiments reported
-in the present manuscript exceed this minimum number of participants per
-condition.
-
-#### Participants
-
-Participants were recruited from an undergraduate population that is 63%
-female and consists almost entirely of individuals aged 18-22 years. A
-total of 110 Indiana University psychology students participated in
-Experiment 1. We subsequently excluded 34 participants poor performance
-at one of the dependent measures of the task (2.5-3 standard deviations
-worse than the median subject at the task) or for displaying a pattern
-of responses that was clearly indicative of a lack of engagement with
-the task (e.g. simply dropping the ball on each trial rather than
-throwing it at the target), or for reporting that they completed the
-experiment on a phone or tablet device, despite the instructions not to
-use one of these devices. A total of 74 participants were retained for
-the final analyses, 35 in the varied group and 39 in the constant group.
-
-#### Task
-
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-igasTask displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-![The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square](../Assets/methodsFig1.png){#fig-igasTask}
-
-### Results
-
-#### Data Processing and Statistical Packages
-
-To prepare the data, we first removed trials that were not easily
-interpretable as performance indicators in our task. Removed trials
-included: 1) those in which participants dragged the ball outside of the
-orange starting box without releasing it, 2) trials in which
-participants clicked on the ball, and then immediately released it,
-causing the ball to drop straight down, 3) outlier trials in which the
-ball was thrown more than 2.5 standard deviations further than the
-average throw (calculated separately for each throwing position), and 4)
-trials in which the ball struck the barrier. The primary measure of
-performance used in all analyses was the absolute distance away from the
-center of the target. The absolute distance was calculated on every
-trial, and then averaged within each subject to yield a single
-performance score, for each position. A consistent pattern across
-training and testing phases in both experiments was for participants to
-perform worse from throwing positions further away from the target -- a
-pattern which we refer to as the difficulty of the positions. However,
-there were no interactions between throwing position and training
-conditions, allowing us to collapse across positions in cases where
-contrasts for specific positions were not of interest. All data
-processing and statistical analyses were performed in R version 4.03 (R
-Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021)****.
-
-#### Training Phase
-
-@fig-IGAS_Training1 below shows aggregate training performance binned into three
-stages representing the beginning, middle, and end of the training
-phase. Because the two conditions trained from target distances that
-were not equally difficult, it was not possible to directly compare
-performance between conditions in the training phase. Our focus for the
-training data analysis was instead to establish that participants did
-improve their performance over the course of training, and to examine
-whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided
-in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and
-condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
-such that performance improved over the course of training There was no
-significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
-and no significant interaction between condition and training stage,
-F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
-
-```{r}
-#| label: fig-igasTraining1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
-
-```
-
-### Testing Phase
-
-In Experiment 1, a single constant-trained group was compared against a
-single varied-trained group. At the transfer phase, all participants
-were tested from 3 positions: 1) the positions(s) from their own
-training, 2) the training position(s) of the other group, and 3) a
-position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs. constant) as a
-between-subject factor and throwing location as a within-subject
-variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\<.001, η2G = .23. The effect of training condition was significant
-F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
-between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS-Testing1
-#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-igasTable1
-#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- test=test[,1:3]
-
- #kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"))  #%>% kableExtra::kable_styling(position="left") #%>%   
-#   kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-### Discussion
-
-In Experiment 1, we found that varied training resulted in superior
-testing performance than constant training, from both a position novel
-to both groups, and from the position at which the constant group was
-trained, which was novel to the varied condition. The superiority of
-varied training over constant training even at the constant training
-position is of particular note, given that testing at this position
-should have been highly similar for participants in the constant
-condition. It should also be noted, though, that testing at the constant
-trained position is not exactly identical to training from that
-position, given that the context of testing is different in several ways
-from that of training, such as the testing trials from the different
-positions being intermixed, as well as a simple change in context as a
-function of time. Such contextual differences will be further considered
-in the General Discussion.
-
-In addition to the variation of throwing position during training, the
-participants in the varied condition of Experiment 1 also received
-training practice from the closest/easiest position, as well as from the
-furthest/most difficult position that would later be encountered by all
-participants during testing. The varied condition also had the potential
-advantage of interpolating both of the novel positions from which they
-would later be tested. Experiment 2 thus sought to address these issues
-by comparing a varied condition to multiple constant conditions.
-
-## Experiment 2
-
-In Experiment 2, we sought to replicate our findings from Experiment 1
-with a new sample of participants, while also addressing the possibility
-of the pattern of results in Experiment 1 being explained by some
-idiosyncrasy of the particular training location of the constant group
-relative to the varied group. To this end, Experiment 2 employed the
-same basic procedure as Experiment 1, but was designed with six separate
-constant groups each trained from one of six different locations (400,
-500, 625, 675, 800, or 900), and a varied group trained from two
-locations (500 and 800). Participants in all seven groups were then
-tested from each of the 6 unique positions.
+## Intro
 
 ## Methods
-
-### Participants
-
-A total of 306 Indiana University psychology students participated in
-Experiment 2, which was also conducted online. As was the case in
-experiment 1, the undergraduate population from which we recruited
-participants was 63% female and primarily composed of 18--22-year-old
-individuals. Using the same procedure as experiment 1, we excluded 98
-participants for exceptionally poor performance at one of the dependent
-measures of the task, or for displaying a pattern of responses
-indicative of a lack of engagement with the task. A total of 208
-participants were included in the final analyses with 31 in the varied
-group and 32, 28, 37, 25, 29, 26 participants in the constant groups
-training from location 400, 500, 625, 675, 800, and 900, respectively.
-All participants were compensated with course credit.
-
-### Task and Procedure
-
-The task of Experiment 2 was identical to that of Experiment 1, in all
-but some minor adjustments to the height of the barrier, and the
-relative distance between the barrier and the target. Additionally, the
-intermittent testing trials featured in experiment 1 were not utilized
-in experiment 2, and all training and testing trials were presented with
-feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
-
-The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the
-same position for the constant groups and split evenly (70 trials each -
-randomized) for the varied group. In the testing phase, participants
-completed 30 trials from each of the six locations that had been used
-separately across each of the constant groups during training. Each of
-the constant groups thus experience one trained location and five novel
-throwing locations in the testing phase, while the varied group
-experiences 2 previously trained, and 4 novel locations.
-
-## Results
-
-#### Data Processing and Statistical Packages
-
-After confirming that condition and throwing position did not have any
-significant interactions, we standardized performance within each
-position, and then average across position to yield a single performance
-measure per participant. This standardization did not influence our
-pattern of results. As in experiment 1, we performed type III ANOVA's
-due to our unbalanced design, however the pattern of results presented
-below is not altered if type 1 or type III tests are used instead. The
-statistical software for the primary analyses was the same as for
-experiment 1. Individual learning rates in the testing phase, compared
-between groups in the supplementary analyses, were fit using the TEfit
-package in R [@cochraneTEfitsNonlinearRegression2020].
-
-#### Training Phase
-
-The different training conditions trained from positions that were not
-equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. @fig-e2train depicts the training
-performance of the varied group alongside that of the aggregate of the
-six constant groups (5a), and each of the 6 separate constant groups
-(5b). An ANOVA comparison with training stage (beginning, middle, end)
-as a within-group factor and group (the varied condition vs. the 6
-constant conditions collapsed together) as a between-subject factor
-revealed no significant effect of group on training performance,
-F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
-stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
-interaction between group and training stage, F(2,412)=.489 p=.61,
-$\eta^{2}_G$ \<.01. We also tested for a difference in training
-performance between the varied group and the two constant groups that
-trained matching throwing positions (i.e., the constant groups training
-from position 500, and position 800). The results of our ANOVA on this
-limited dataset mirrors that of the full-group analysis, with no
-significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
-significant effect of training stage F(2,172)=56.29, p\<.001,
-$\eta^{2}_G$ =.11, and no significant interaction between group and
-training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
-
-```{r}
-
-e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
-
-exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
-
-exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
-
-exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
-
-exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% convert_as_factor(novel,extrapolate)
-
-transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
-
-# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
-# novelAll <- novelAll %>% group_by(positionX) %>%
-#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
-novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
-
-constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
-variedTest <- transfer %>% filter(condit==7) # only varied testing
-variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
-
-variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
-constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
-variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
-
-exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-```
-
-```{r}
-#| label: fig-e2train
-#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
-On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-
-### New - 3 stage
-e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
-  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
-  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
-
-e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
-  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
-
-#plot_grid(e2train1,e2train2,ncol=1)
-
-e2train1
-e2train2
-
-```
-
-#### Testing Phase
-
-In Experiment 2, a single varied condition (trained from two positions,
-500 and 800), was compared against six separate constant groups (trained
-from a single position, 400, 500, 625, 675, 800 or 900). For the testing
-phase, all participants were tested from all six positions, four of
-which were novel for the varied condition, and five of which were novel
-for each of the constant groups. For a general comparison, we took the
-absolute deviations for each throwing position and computed standardized
-scores across all participants, and then averaged across throwing
-position. The six constant groups were then collapsed together allowing
-us to make a simple comparison between training conditions (constant vs.
-varied). A type III between-subjects ANOVA was performed, yielding a
-significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
-=.02. Descriptive statistics for each condition are shown in table 2. In
-@fig-e2testa visualizes the consistent advantage of the varied condition
-over the constant groups across the testing positions. @fig-e2testa shows
-performance between the varied condition and the individual constant
-groups.
-
-```{r}
-#| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 9
-
-# manuscript plot
-e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)+
-  ggtitle("A")
-
-e2test2<-exp2.Test7 %>% 
-  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
-  facet_wrap(~ThrowPosition4)+
-  ylab("Mean Distance From Center Of Target")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
-
-e2test1 / e2test2
-
-```
-
-\
-
-```{r}
-#| label: tbl-e2table1
-#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-
-tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab2=tab2[,1:3]
-
-# kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  #%>% kableExtra::kable_styling(position="left") %>% 
-#   #kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
-.02 .
-
-```{r}
-#| label: tbl-e2table2
-#| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-
-sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
- tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
- tab3 = tab3 %>% 
-   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab3=tab3[,1:3]
-
-# kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  #%>% kableExtra::kable_styling(position="left") %>% 
-#   #kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
-
-Finally, corresponding to the comparison of position 760 from experiment
-1, we compared the test performance of the varied group against the
-constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis
-omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). @fig-e2test1 displays
-the particular subset of comparisons utilized for this analysis. Again,
-we standardized performance within each position before performing the
-analyses on the aggregated data. In this case, the effect of condition
-did not reach statistical significance F(1,149)=3.14, p=.079,
-$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
-
-```{r}
-#| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-
-sum.variedVsNovelIden <- variedVsNovelIden  %>%
-  group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
-
-e2Test2
-
-```
-
-\
-
-```{r}
-#| label: tbl-e2tab3
-#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-
-tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
-tab4=tab4 %>% group_by(Condition) %>% 
-   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab4=tab4[,1:3]
-
-# kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-#   kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-### Discussion
-
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
-
-### Computational Model
-
-Controlling for the similarity between training and testing The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
-
-```{r}
-#| label: fig-taskSpace
-#| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| 
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
-  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
-
-ss
-fs
-
-```
-
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
-
-**Equation 1:** \[ Similarity\_{I,J} = \sum*{i = I}*\sum{j=J}
-e^{-c^\cdot dp\_{i,j}} \]
-
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-
-A simple linear regression revealed that these similarity scores were
-significantly predictive of performance in the transfer stage, t
-=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
-training throws and solution spaces for each of the test locations
-resulted in better performance. We then repeated the group comparisons
-above while including similarity as a covariate in the model. Comparing
-the varied and constant groups in testing performance from all testing
-positions yielded a significant effect of similarity, F(1, 205)=85.66,
-p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
-(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
-group comparison limited to only novel locations for the varied group
-pit against trained location for the constant group resulted in a
-significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
-=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
-=.07. For all comparisons, the pattern of results was consistent with
-the initial findings from experiment 2, with the varied group still
-performing significantly better than the constant group.
-
-#### Fitting model parameters separately by group
-
-To directly control for similarity in Experiment 2, we developed a
-model-based measure of the similarity between training throws and
-testing conditions. This similarity measure was a significant predictor
-of testing performance, e.g., participants whose training throws were
-more similar to throws that resulted in target hits from the testing
-positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level
-benefits of varied training, which remained significant in our linear
-model predicting testing performance after similarity was added to the
-model. However, previous research has suggested that participants may
-differ in their level of generalization as a function of prior
-experience, and that such differences in generalization gradients can be
-captured by fitting the generalization parameter of an instance-based
-model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
-will increase when a rational agent encounters a wider variety of
-examples. Following these leads, we assume that in addition to learning
-the task itself, participants are also adjusting how generalizable their
-experience should be. Varied versus constant participants may be
-expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the
-instance-based model (in the present case, the c parameter) can be
-allowed to vary between the two groups to reflect the tendency of
-learners to adaptively tune the extent of their generalization. One
-specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
-variable, as with the variable training condition, then one might infer
-that future test situations will also be variable, in which case a low
-value of c will allow better generalization because generalization will
-drop off slowly with training-to-testing distance. Conversely, if one's
-training experience has little variability, as found in the constant
-training conditions, then one might adopt a high value of c so that
-generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based
-model of similarity fit against a modified model which separately fits
-the generalization parameter, c, to varied and constant participants. To
-perform this parameter fitting, we used the optim function in R, and fit
-the model to find the c value(s) that maximized the correlation between
-similarity and testing performance.
-
-Both models generate distinct similarity values between training and
-testing locations. Much like the analyses in Experiment 2, these
-similarity values are regressed against testing performance in models of
-the form shown below. As was the case previously, testing performance is
-defined as the mean absolute distance from the center of the target
-(with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\<.01). Of greater interest is the
-difference between linear model 2, in which similarity is computed from
-a single c value fit from all participants (Similarity1c), with linear
-model 4, which fits the c parameter separately between groups
-(Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\<.01), with the varied
-group still performing significantly better. However, in linear model 4
-the addition of the Similarity2c predictor results in the effect of
-training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs. constant training is accounted for by the
-Similarity2c predictor. Next, to further establish a difference between
-the models, we performed nested model comparisons using ANOVA, to see if
-the addition of the training group parameter led to a significant
-improvement in model performance. In the first comparison, ANOVA(Linear
-Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear
-Model 4) found no improvement in model performance with the addition of
-the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the
-adjusted Similarity2c model had more predictive power than those
-generated from the original Similarity1c model. Using the BIC function
-in R, we compared BIC values between linear model 1 (BIC=14604.00) and
-linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
-a modest advantage for predicting performance using a similarity measure
-computed with two c values over similarity computed with a single c
-value. When fit with separate c values, the best fitting c parameters
-for the model consistently optimized such that the c value for the
-varied group (c=.00008) was smaller in magnitude than the c value for
-the constant group(c= .00011). Recall that similarity decreases as a
-Gaussian function of distance (equation 1 above), and a smaller value of
-c will result in a more gradual drop-off in similarity as the distance
-between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which
-assumes equivalent generalization gradients between constant and varied
-trained participants is unable to account for the extent of benefits of
-varied over constant training observed at testing. The evidence for this
-in the comparative model fits is that when a varied/constant dummy-coded
-variable for condition is explicitly added to the model, the variable
-adds a significant contribution to the prediction of test performance,
-with the variable condition yielding better performance than the
-constant conditions. However, if the instance-based generalization model
-is modified to assume that the training groups can differ in the
-steepness of their generalization gradient, by incorporating a separate
-generalization parameter for each group, then the instance-based model
-can account for our experimental results without explicitly taking
-training group into account. Henceforth this model will be referred to
-as the Instance-based Generalization with Adaptive Similarity (IGAS)
-model.
-
-### General Discussion
-
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy_Model2 we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model2
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$.
-For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
-The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
-
-#
-
-p=2
-c<- .000002
-
-trainingTestingDifference=2000;
-cvaried=.00002
-cconstant=.0005
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
-                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
-                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
-                            ) %>% 
-  group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
-
-#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
-
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
-ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
-ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
-ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
-# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
-
-gtitle="Figure 9."
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-
-```
-
-As mentioned above, the idea that learners flexibly adjust their
-generalization gradient based on prior experience does have precedent in
-the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed
-that a simple manipulation of background knowledge during a
-categorization test resulted in participants generalizing their training
-experience more or less broadly, and moreover that such a pattern could
-be captured by allowing the generalization parameter of an
-instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted
-for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006]. However, to the best of our
-knowledge, IGAS is the first instance-based similarity model that has
-been put forward to account for the effect of varied training in a
-visuomotor skill task. Although IGAS was inspired by work in the domain
-of category learning, its success in a distinct domain may not be
-surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common
-principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001a; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning
-implementations of instance-based models in several ways. One such
-difference is the nature of the training instances that are assumed to
-be stored. In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define
-a category item (e.g. size/color/shape). Rather than defining instances
-in terms of what stimuli learners experience, our approach assumes that
-stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw. An advantage of many motor learning
-tasks is the relative ease with which task execution variables can be
-directly measured (e.g. movement force, velocity, angle, posture) in
-addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of
-course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work
--- though as described in the introduction there is some evidence in
-support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly
-noteworthy instance-based model of sensory-motor behavior is the
-Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995]. Knowledge II explicitly defines instances as
-postures (joint combinations), and is thus far more detailed than IGAS
-in regards to the contents of stored instances. Knowledge II also
-differs from IGAS in that learning is accounted for by both the
-retrieval of stored postures, and the generation of novel postures via
-the modification of retrieved postures. A promising avenue for future
-research would be to combine the adaptive similarity mechanism of IGAS
-with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
-lighting up consecutively, and attempt to time a button press with the
-onset of the final lamp. The design consisted of four separate constant
-groups, each training from a single lighting velocity, and a single
-varied group training with all four of the lighting velocities used by
-the individual constant groups. Participants were then split into four
-separate testing conditions, each of which were tested from a single
-novel lighting velocity of varying distance from the training
-conditions. The result of primary interest was that all participants
-performed worse as the distance between training and testing velocity
-increased -- a typical generalization decrement. However, varied
-participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in
-a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are
-similar to our own, our work is novel in that we account for our results
-with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their
-separate constant groups together may result in similarity confounds
-between varied and constant conditions that leaves their study open to
-methodological criticisms, especially in light of related work which
-demonstrated that the extent to which varied training may be beneficial
-can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
-similarity.
-
-## Limitations
-
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
-
-## Conclusion
-
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
-
-# References

### 2023-10-17 index.qmd
fix toc, re-render, minor fig issues

@@
 title: "Dissertation"
+author: Thomas E. Gorman
 comments: false
@@
 ---
-
-# An instance-based model account of the benefits of varied practice in visuomotor skill

### 2023-10-17 paper.qmd
fix toc, re-render, minor fig issues

@@
 
-  <a class="btn btn-danger btn-sm mb-1" href="/Manuscript/output/Full_Dissertation-nice.pdf" target="manuscript">
+  <a class="btn btn-danger btn-sm mb-1" href="/Manuscript/output/TG_Full_Dissertation.pdf" target="manuscript">
   <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;PDF
@@
 
-   <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/manuscript.pdf.md" target="manuscript">
-  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscript-md
+<a class="btn btn-warning btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.pdf">
+  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
   </a>
+
+  <!--  <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/manuscript.pdf.md" target="manuscript"> -->
+  <!-- <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscript-md -->
+  <!-- </a>  -->
 

### 2023-10-17 Manuscript/.vdoc.r

@@ -27,9 +27,64 @@
 #
 #
 #
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+library(here)
 here::set_here(path='..')
 source(here::here("Functions", "packages.R"))
-
+# test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
+# testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+#   summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
 
 
 if (is.null(knitr::pandoc_to())) {
@@ -37,12 +92,6 @@ if (is.null(knitr::pandoc_to())) {
 } else {
   fmt_out <- knitr::pandoc_to()
 }
-
-
-knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
-                      warning = FALSE, message = FALSE, eval=TRUE)
-
-
 
 knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                       fig.width = 6, fig.height = (6 * 0.618),
@@ -57,6 +106,7 @@ options(digits = 3, width = 120,
 #
 #
 #
+
 source(here::here('Functions/IGAS_ProcessFunctions.R'))
 
 e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
@@ -81,1987 +131,6 @@ e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Co
 e1Pos <- c("610","760","835","910")
 e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
 e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
[…]

### 2023-10-17 HTW.qmd
fix html toc

@@
 
-[Link HTW project page](https://tegorman13.github.io/htw/){target="_blank"}
+[Link HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
 
+[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
 ```{r}
@@
     each.
-
-```{r design, echo=FALSE, fig.cap="Experiment Procedure"}
-DiagrammeR::grViz("digraph {
-graph [layout = dot, rankdir = LR]
-# define the global styles of the nodes. We can override these in box if we wish
-node [shape = rectangle, style = filled, fillcolor = Linen]
-data1 [label = <<b>Varied Training</b>  
-<br ALIGN = 'LEFT' /> 800-1000
-<br/> 1000-1200
-<br/>1200-1400>]
-data2 [label = <<b>Constant Training</b>  
-<br/> 800-1000 >]
-Test1 [label = <<b>Testing - No Feedback</b>  
-<br ALIGN = 'LEFT' /> 100-300
-<br/> 350-550
-<br/>600-800>]
-Test2 [label = <<b>Test From Train</b>  
-<br ALIGN = 'LEFT' /> 800-1000
-<br/> 1000-1200
-<br/>1200-1400>]
-Test3[label = <<b>Testing -Feedback</b>  
-<br ALIGN = 'LEFT' /> 100-300
-<br/> 350-550
-<br/>600-800>]
-
-# edge definitions with the node IDs
-{data1 data2}  -> Test1 -> Test2 -> Test3
-}
-",width=700,height=250)
-
-```
 

### 2023-10-17 Manuscript/pre_sections/pre_html.qmd
fix html toc

@@
 <!-- }); -->
+
+<!-- document.addEventListener("DOMContentLoaded", function(){ -->
+<!--     var tocDiv = document.getElementById("html-toc"); -->
+<!--     var headings = document.querySelectorAll('h1, h2, h3'); // adjust if you need more depth -->
+<!--     var tocList = document.createElement("ul"); -->
+
+<!--     headings.forEach(function(heading) { -->
+<!--         var listItem = document.createElement("li"); -->
+<!--         var link = document.createElement("a"); -->
+<!--         link.textContent = heading.textContent; -->
+<!--         link.href = "#" + heading.id; -->
+<!--         listItem.appendChild(link); -->
+
+<!--         if (heading.tagName == "H2") { -->
+<!--             listItem.style.marginLeft = "20px"; -->
+<!--         } else if (heading.tagName == "H3") { -->
+<!--             listItem.style.marginLeft = "40px"; -->
+<!--         } -->
+<!--         tocList.appendChild(listItem); -->
+<!--     }); -->
+
+<!--     tocDiv.appendChild(tocList); -->
+<!-- }); -->
+
 document.addEventListener("DOMContentLoaded", function(){
@@
 
-    headings.forEach(function(heading) {
+    headings.forEach(function(heading, index) {
+        // Create or get the ID for the heading
+        if (!heading.id) {
+            heading.id = heading.textContent.replace(/[^a-z0-9]+/gi, '-').toLowerCase() + "-" + index;
+        }
         var listItem = document.createElement("li");

### 2023-10-17 Manuscript/manuscript.qmd
remove redundancies

@@
 ## Procedure
-Upon arrival at the laboratory, participants were provided with a description of the experiment and signed informed consent forms.
-They were then seated in front of a computer equipped with a mouse and were given instructions on how to perform the "Hit The Wall" (HTW) visuomotor extrapolation task.
 

### 2023-10-17 Introduction.qmd
tune up intro section

@@
 
-The factors that influence how learning generalizes are of great interest to those seeking to understanding the nature of the human learning system, and to those attempting to improve the efficacy of teaching and training programs.
-Such factors are likely legion, but the present effort will limit itself to two characteristics of the learning input - variability and frequency skew.
-Variability manipulations control either the number of unique instances learners are trained on, or how dispersed or spread out the instances are.
-Much less research has examined skew manipulations, which hold the number of instances constant, and instead vary the relative frequencies with which the training items occur.
-Both factors have been linked to generalization in past research.
-The present essay with will provide an extensive review and discussion of both topics.
-The review of the expansive literature on the effect of attempts to include at least some examples from each of the many relevant domains, but much of the work is biased towards the background of the author.
-Conversely, the literature on skew proved to be far sparser than anticipated, as well as being overrepresented in a region of the language learning literature that is somewhat distant from more conventional cognitive psychology.
+The factors that influence the generalization of learning are of considerable interest to both researchers exploring the human learning system and practitioners aiming to enhance the effectiveness of educational and training interventions.
+The present effort will focus specifically on the role of variability in the learning input.
+Variability manipulations typically regulate either the number of distinct instances presented to learners during training, or the dispersion of these instances.
+Such manipulations have been empirically demonstrated to affect subsequent generalization performance.
+This essay will offer an in-depth review of the extant literature on the influence of variability, spanning multiple relevant domains.
 
@@
 
-In their most generic form, studies assessing the "benefits of variability" hypothesis assign participants to either a constant or varied group for the training stage of the experiment.
+Studies investigating the "benefits of variability" hypothesis usually assign participants to either a constant or varied group for the training stage of the experiment.
 Then, subjects in both groups complete an identical testing stage which often consists items/conditions seen during training, and novel items/conditions.
 If the varied group performs better in the testing stage, this is taken for evidence of the benefits of variability hypothesis.
-Even in this relatively simple between-groups design, researchers must make a number of crucial decisions which will now be highlighted.
+Even within this relatively straightforward between-groups design, researchers must navigate several crucial methodological choices, highlighted below:
 
-1)  What is varied.
-Unless the task is unidimensional, there will often be many variables that could be varied or held fixed, and the experiment will need to decide the dimension(s) along which the variation will occur.
+1)  Variables Subject to Variation.
+In multidimensional tasks, researchers have the option to vary numerous variables.
+The experimenters must decide the specific dimension(s) across which variation will occur.
 For instance, in a projectile throwing accuracy task -- researchers might vary the distance from the target, the size of the target, the weight of the projectile.
@@
 
-2)  The amount of variation, relative to the control condition.
+2)  Magnitude of Variation, relative to the control condition.
 The simplest comparison would be to compare a constant group who trains with 1 example/condition, against a varied group that trains from 2 examples/conditions.
 However, it is not uncommon in the literature for the varied condition to train from 3 or 4 conditions.
-For example, Catalano and Kleiner train varied subjects from 4 different velocities in their coincident timing task, and Goode et al.
-(2008) have varied subjects' practice with 3 different variants (i.e.
+For example, @catalanoDistantTransferCoincident1984a train varied subjects from 4 different velocities in their coincident timing task, and [@goodeSuperiorityVariableRepeated2008] have varied subjects' practice with 3 different variants (i.e.
 different letter scrambles of the same word) of an anagram for a given word, while their constant participants view the same variant 3 different times.
 Alternatively, rather than a constant vs.
-varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items (Nosofsky et al.
-2018).
+varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items [@nosofskyModelguidedSearchOptimal2018].
 
-3)  Locations of the varied examples within the task-space.
-For tasks in which the stimuli or conditions exist in some continuous metric space, the experimenter must decide whether the varied instances are relatively close together (e.g.
+3)  Locations within Task-Space.
+For tasks in which the stimuli or conditions fall within a continuous metric space, the experimenter must decide whether the varied instances are relatively close together (e.g.
 throwing a ball from a distance of 4 feet and 5 feet), or far apart (throwing from 4 feet and 20 feet).
@@
 
-4)  The proximity of the testing conditions to the training conditions of the varied and constant groups.
+4)  Proximity of Testing to Training Conditions.
 Intuitively, the fairest form of comparison is to include testing conditions that are of an equivalent distance from both the varied and constant groups.
-However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions (Goode et al., 2008; Kerr & Booth, 1978).
+However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978].
 
-Variability Literature Review
+## Variability Literature Review
 
-An early and influential work on the influence of variability on category learning is that of Posner and Keele (1968).
+An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
 In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
@@
 The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
-The Posner and Keele study have been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of Schema Theory of Motor Learning (Richard A.
-Schmidt, 1975), which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
+The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of Schema Theory of Motor Learning @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
 However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
-The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later (Palmeri & Nosofsky, 2001), when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
+The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
 Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
@@
 
-One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of Kerr and Booth (1978).
+One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
 Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
@@
 12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
-Participants were also blind folded for testing and did not receive trial by trial feedback in this stage.
+Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
 However, at the halfway point of the testing stage they were allowed to see the landing location of the 4 beanbags they had thrown, and then completed the final 4 testing throws.
@@
 On occasion the Kerr and Booth design may be nested within a larger experimental design.
-One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue (Wrisberg et al., 1987).
+One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue [@wrisbergVariabilityPracticeHypothesis1987].
 This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g.
@@
 A more recent study attempting a slightly more direct replication of the original Kerr & Booth study (Willey & Liu, 2018), having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-However this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-Like Wrisberg et al.
-(1987), this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
+However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
 
@@
 
+## Category learning
+
 In the category learning literature, the constant vs.
@@
 Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars.
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns (Homa & Vosburgh, 1976; Posner & Keele, 1968), where more varied or distorted training examples were often shown to produce superior generalize when categorizing novel exemplars.
+Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns (Homa & Vosburgh, 1976; Posner & Keele, 1968), where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
 More recently, researchers have also begun to utilize more realistic stimuli in their experiments.
@@
 In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
-Across four different experiments, which were conducted to address on unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
+Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
 higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
@@
 Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
-Moreover, this effect was at odds of the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.
+Moreover, this effect was at odds with the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.
 
@@
 No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
-The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items -- accounting for their extended generalization gradients, but also for their poor performance in a recognition condition.
+The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
+This model accounted for both the extended generalization gradients of the varied particpants, and also for their poor performance in a recognition condition.
 Additional model comparisons suggested that this similarity rescaling applied across the entire stimulus space, rather than to the high variability category in particular.
@@
 A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another.
-The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
-Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis it was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter (J.
+The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
+Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter (J.
 B.
@@
 There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
-However, the main finding of interest was the advantage random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
+However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
 
@@
 
-Other task and participant effects
+## Other task and participant effects
 
@@
 Null effects of both manipulations have been reported (Magill & Hall, 1990; Van Rossum, 1990 for reviews), and a variety of moderators have emerged.
-In one of the earlier examples of the complex relationship between study sequence and learning (Del Rey et al., 1982), experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities with either blocked, or random training sequence conditions - resulting in 6 experimental conditions: (athlete vs.
+In one of the earlier examples of the complex relationship between study sequence and learning (Del Rey et al., 1982), experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
 non-athlete) x (constant vs.
@@
 Among the athlete-participants, transfer performance was best for those who received random training, followed by blocked, and then constant training.
-Non-athletes showed an almost opposite pattern, with superior performance for those who had constant training.
+Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
 A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training (Guadagnoli et al., 1999).
@@
 Another experimental factor shown to interact with training sequence is the complexity of the training task (Albaret & Thon, 1998).
-In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of 2, 3 or 4 components).
+In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of two, three or four components).
 On a transfer task 48 hours after the completion of training, only participants trained at the lower levels of task complexity (2 or 3 components) showed superior performance to the blocked condition.
@@
 Shea & Morgan, 1979), or structure the random trials such that the same condition never occurs consecutively (Wulf, 1991).
-Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition (Chua et al., 2019; Willey & Liu, 2018; Wrisberg et al., 1987), resulting in much more switches than would arise if training was perfectly blocked.
+Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition [@willeyLongtermMotorLearning2018; @chuaPracticeVariabilityPromotes2019; @wrisbergVariabilityPracticeHypothesis1987], resulting in many more switches than would arise if training was perfectly blocked.
 The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition.

### 2023-10-19 Introduction.qmd
manuscript update

@@
 ---
-title: Introduction
+#title: Introduction
 ---
@@
 The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of Schema Theory of Motor Learning @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
+It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
 However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
@@
 Training variation has also been shown to promote transfer in motor learning.
-Much of this research has been influenced by the work of Schmidt (1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
 Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
@@
 However, in this case the varied group did not outperform the constant group.
-A more recent study attempting a slightly more direct replication of the original Kerr & Booth study (Willey & Liu, 2018), having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
+A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
 However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
@@
 
-Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket (Green et al., 1995).
+Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket [@greenPracticeVariabilityTransfer1995a].
 Varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket.
@@
 
-One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation (Goode et al., 2008).
+One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation [@goodeSuperiorityVariableRepeated2008].
 All participants trained to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
@@
 It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters (Catalano & Kleiner, 1984; Chua et al., 2019; McCracken & Stelmach, 1977; Moxley, 1979; Newell & Shapiro, 1976), or for a single constant group to train from just one of the conditions experienced by the varied participants (Pigott & Shapiro, 1984; Roller et al., 2001; Wrisberg & McLean, 1984; Wrisberg & Mead, 1981).
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition (Wrisberg et al., 1987; Wulf, 1991).
+A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
+@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
+@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
+A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
 
-Of particular relevant to the current essay is the early work of Catalano and Kleiner (1984), as theirs was one of the earliest studies to investigate the influence of varied vs.
+Of particular relevant to the current essay is the early work of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
 constant training on multiple testing locations of graded distance from the training condition.
@@
 Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars.
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns (Homa & Vosburgh, 1976; Posner & Keele, 1968), where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
+Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968], where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
 More recently, researchers have also begun to utilize more realistic stimuli in their experiments.
-Wahlheim et al.
-(2012) conducted one such study.
+@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
 In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
@@
 higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization (Nosofsky et al., 2018).
+A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyTestsExemplarmemoryModel2018].
 For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
@@
 
-Cohen et al.
-(2001) trained subjects on two categories, one with much more variability than the other.
+@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
 In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
@@
 
-Further observations consonant with the results of Cohen et al.
-(2001) have since been observed in numerous investigations (Hahn et al., 2005; Hsu & Grifﬁths, 2010; Perlman et al., 2012; Sakamoto et al., 2008).
-The results of Sakamoto et al.
-(2008) are noteworthy.
+Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
+@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010].
+
+The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
 They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
@@
 
-The study by Hahn et al.
-(2005), is also of particular interest to the present discussion.
+The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present discussion.
 Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
@@
 
-Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts (Braithwaite & Goldstone, 2015).
+Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts [@braithwaiteEffectsVariationPrior2015].
 This study trained participants on problems involving the concept of sampling with replacement (SWR).
@@
 Variability has also been examined within the realm of language learning.
-A particularly impressive study is that of Perry et al.
-(2010).
+A particularly impressive study is that of [@perryLearnLocallyThink2010].
 In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
@@
 
-## Some complications to the influence of variability
+## Complications to the influence of variability
 
@@
 The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
-Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter (J.
-B.
-Shea & Morgan, 1979).
+Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter  [@sheaContextualInterferenceEffects1979].
 In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
@@
 
-Prior to the influential Shea and Morgan (1979) study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
-It was later observed (Lee et al., 1985) that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
+Prior to the influential @sheaContextualInterferenceEffects1979 study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
+It was later observed [@leeInfluencePracticeSchedule1985] that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
 The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts.
-One such account, the elaborative processing account (J.
-B.
-Shea & Zimny, 1983), draws on the earlier work of Battig (Battig, 1966) and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
-Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training (J.
-B.
-Shea & Zimny, 1983), and by manipulating whether subjects are able to perform comparisons during training (Wright et al., 1992).
-An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory (Lee & Magill, 1985).
+One such account, the elaborative processing account [@sheaContextEffectsMemory1983], draws on the earlier work [@battigFacilitationInterference1966] and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
+Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training [@sheaContextEffectsMemory1983], and by manipulating whether subjects are able to perform comparisons during training [@wrightContributionElaborativeProcessing1992].
+An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory [@leeLocusContextualInterference].
 Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context.
-A much more recent study (Chua et al., 2019), replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
+A much more recent study [@chuaPracticeVariabilityPromotes2019], replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
 The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
@@
 Of course, the effects of varied training, and different training sequences, are likely to be far more complex than simply more varied training being better than less, or random training being better than blocked.
-Null effects of both manipulations have been reported (Magill & Hall, 1990; Van Rossum, 1990 for reviews), and a variety of moderators have emerged.
-In one of the earlier examples of the complex relationship between study sequence and learning (Del Rey et al., 1982), experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
+Null effects of both manipulations have been reported [see @magillReviewContextualInterference1990; @vanrossumSchmidtSchemaTheory1990 for reviews], and a variety of moderators have emerged.
+In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
 non-athlete) x (constant vs.
@@
 Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
-A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training (Guadagnoli et al., 1999).
-More recently, the same pattern was observed in the concept learning literature (Braithwaite & Goldstone, 2015, expt 1).
+A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training  [@guadagnoliRelationshipContextualInterference1999].
+More recently, the same pattern was observed in the concept learning literature [@braithwaiteEffectsVariationPrior2015 expt 1.].
 This study trained participants on a mathematical concept and found that participants who self-reported some prior experience with the concept improved more from pre-test to post-test after training with varied examples, while participants who reported no prior experience showed greater gains following training with highly similar examples.
@@
 In addition to the influence of prior experiences described above, ample evidence also suggests that numerous aspects of the experiment may also interact with the influence of variation.
-One important study examined the impact of the amount of training completed in a force production task (C.
-H.
-Shea et al., 1990).
+One important study examined the impact of the amount of training completed in a force production task [@sheaContextualInterferenceContributions1990].
 This study employed a typical blocked vs.
@@
 These results were taken to suggest that the benefits of randomization may take time to emerge.
-Another experimental factor shown to interact with training sequence is the complexity of the training task (Albaret & Thon, 1998).
+Another experimental factor shown to interact with training sequence is the complexity of the training task [@albaretDifferentialEffectsTask1998].
 In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of two, three or four components).
@@
 Some researchers report setting a maximum number of consecutive repetitions, e.g.
-no more than 2 consecutive trials of the same condition (Del Rey et al., 1982; J.
-B.
-Shea & Morgan, 1979), or structure the random trials such that the same condition never occurs consecutively (Wulf, 1991).
+no more than 2 consecutive trials of the same condition [@delreyEffectsContextualInterference1982; @sheaContextualInterferenceEffects1979], or structure the random trials such that the same condition never occurs consecutively [@wulfEffectTypePractice1991].
 Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition [@willeyLongtermMotorLearning2018; @chuaPracticeVariabilityPromotes2019; @wrisbergVariabilityPracticeHypothesis1987], resulting in many more switches than would arise if training was perfectly blocked.
 The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition.
-Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing (Pigott & Shapiro, 1984), and basketball shot training study (Landin & Hebert, 1997), and in a replication plus extension of the seminal Shea and Morgan (1979) study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition.
-Consequences on different study schedules have also been repeatedly observed in the category learning literature (Carvalho & Goldstone, 2014, 2017).
+Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing [@pigottMotorSchemaStructure1984], and basketball shot training study [@landinComparisonThreePractice1997], and in a replication plus extension of the seminal [@sheaContextualInterferenceEffects1979] study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition.
+Consequences on different study schedules have also been repeatedly observed in the category learning literature [@carvalhoSequenceStudyChanges2017; @carvalhoPuttingCategoryLearning2014].
 This line of research has revealed that the effects of blocking vs.
@@
 Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed).
-Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty(Bjork & Bjork, 2011; R.A.
-Schmidt & Bjork, 1992), or optimal challenge points (Guadagnoli & Lee, 2004).
+Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty [@bjorkNewTheoryDisuse1992; @schmidtNewConceptualizationsPractice1992], or optimal challenge points [@guadagnoliChallengePointFramework2004].
 They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage.

### 2023-10-19 Manuscript/manuscript.qmd
tune up intro section
manuscript update

@@
 link-citations: true
-keep-md: true
+# keep-md: true
 toc: false
@@
 {{< include pre_sections/pre_html.qmd >}}
-<!-- Manually insert the table of contents here -->
 
@@
 ::: {.content-visible when-format="pdf"}
+
 {{< include pre_sections/pre_pdf.qmd >}}
+
 :::
+{{< pagebreak >}}
+
+# Abstract
+
+This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
+A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
+Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
+To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
+These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
+
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/toc_html.qmd >}}
+
+:::
+
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/toc_pdf.qmd >}}
+
+:::
+
+{{< pagebreak >}}
+
+# Literature Review
+
+{{< include ../Introduction.qmd >}}
 
@@
 #| tbl-cap: "Testing vx - Empirical Summary"
-#| layout-ncol: 1
 #| include: true

### 2023-10-19 Manuscript/pre_sections/pre_html.qmd
manuscript update

--- 2023-10-17 Manuscript/pre_sections/pre_html.qmd
@@
 <div style="text-align: center; margin-top: 50px; font-size: 24px; font-weight: bold;">
-  Variability and Generalization - A Similarity-Based Account
+  The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach
 </div>
@@
 </div>
+<div style="text-align: center; margin-top: 700px; font-size: 24px;">
+
+</div>
 
 <div style="page-break-before: always;"></div>
-
-## Table of contents
-<div id="html-toc"></div>
-```{=html}
-<script>
-<!-- document.addEventListener("DOMContentLoaded", function(){ -->
-<!--   var toc = document.getElementById("TOC"); -->
-<!--   var placeholder = document.getElementById("toc-placeholder"); -->
-<!--   if (toc && placeholder) { -->
-<!--     placeholder.appendChild(toc); -->
-<!--   } -->
-<!-- }); -->
-document.addEventListener("DOMContentLoaded", function(){
-    var tocDiv = document.getElementById("html-toc");
-    var headings = document.querySelectorAll('h1, h2, h3'); // adjust if you need more depth
-    var tocList = document.createElement("ul");
-
-    headings.forEach(function(heading) {
-        var listItem = document.createElement("li");
-        var link = document.createElement("a");
-        link.textContent = heading.textContent;
-        link.href = "#" + heading.id;
-        listItem.appendChild(link);
-
-        if (heading.tagName == "H2") {
-            listItem.style.marginLeft = "20px";
-        } else if (heading.tagName == "H3") {
-            listItem.style.marginLeft = "40px";
-        }
-        tocList.appendChild(listItem);
-    });
-
-    tocDiv.appendChild(tocList);
-});
-
-</script>
-```

### 2023-10-19 md_extract/remove_links.py

@@ -1,0 +1,23 @@
+import re
+import sys
+
+def remove_links(filename):
+    with open(filename, 'r') as file:
+        lines = file.readlines()
+
+    new_lines = []
+    for line in lines:
+        # Using regex to remove the localhost links
+        new_line = re.sub(r'\[([^\]]+)\]\(http://localhost:[0-9]+/[^)]+\)', r'\1', line)
+        new_lines.append(new_line)
+
+    with open(filename, 'w') as file:
+        file.writelines(new_lines)
+
+if __name__ == "__main__":
+    if len(sys.argv) < 2:
+        print("Please provide the filename as an argument.")
+    else:
+        filename = sys.argv[1]
+        remove_links(filename)
+        print(f"Removed localhost links from {filename}.")

### 2023-10-19 Manuscript/pre_sections/pre_docx.qmd
add docx and md download options

# The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach

## Thomas E. Gorman

Submitted to the faculty of the University Graduate School in partial fulfillment of the
requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
Sciences and the Cognitive Science Program, Indiana University.

---

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.

- Robert L. Goldstone
- Robert Nosofsky
- Peter Todd
- Mike Jones

---

## @2023

### Thomas E. Gorman

---

## Acknowledgements

---

### 2023-10-19 paper.qmd
add docx and md download options

@@
 
-  <a class="btn btn-danger btn-sm mb-1" href="/Manuscript/output/TG_Full_Dissertation.pdf" target="manuscript">
+  <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/output/TG_Full_Dissertation.pdf" target="manuscript">
   <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;PDF
@@
   <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
+  </a>
+
+    <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
+  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;DOCX <small>(download)</small>
+  </a>
+
+  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.html.md">
+  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>
   </a>

### 2023-10-19 paper.qmd
fix md

@@
 
-  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.html.md">
+  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.md">
   <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>

### 2023-10-19 HTW.qmd
fix docx and html. Update htw with embed

@@
 [Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
+
+![htw](https://tegorman13.github.io/htw/paper.html){width="900" height="600"}
+
 ```{r}

### 2023-10-19 Manuscript/pre_sections/pre_html.qmd
fix docx and html. Update htw with embed

@@
 <div style="text-align: center; margin-top: 300px;">
-  _____________________________  Robert L. Goldstone<br><br>
-  _____________________________  Robert Nosofsky<br><br>
-  _____________________________  Peter Todd<br><br>
-  _____________________________  Mike Jones
+  _____________________________  Robert L. Goldstone, PhD<br><br>
+  _____________________________  Robert Nosofsky, PhD<br><br>
+  _____________________________  Peter Todd, PhD<br><br>
+  _____________________________  Mike Jones, PhD
 </div>

### 2023-10-19 paper.qmd
fix docx and html. Update htw with embed

@@
 
-  <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.md">
+  <!-- <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/manuscript.md">
   <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;md <small>(download)</small>
-  </a>
+  </a> -->
 

### 2023-10-20 IGAS.qmd
add links pubs

@@
 
-[Pdf of the journal
+____________________________________________________
+[pdf of the journal
 article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\

### 2023-10-20 .vdoc.r
re-render, bib update

@@ -1,1482 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-knitr::opts_chunk$set(echo=FALSE)
-# source('build_toc.R')
-# files <- list.files(pattern = '*.Rmd', recursive = F) 
-# files = files[!grepl('^_', basename(files)) | grepl('^_index[.]', basename(files))]
-# t1 <- render_toc("htw_n.Rmd")
-# #cat(t1)
-# 
-# 
-# render_toc("igas_n.Rmd")
-
-library(thematic)
-thematic_on(bg="#fcfcfc")
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-source('Functions/IGAS_ProcessFunctions.R')
-library(webexercises)
-library(kableExtra)
-library(knitr)
-knitr::opts_chunk$set(echo = FALSE)
-
-#rm(list=ls())
-###### data loading and organization #######
-
-# load the processed data from experiment 1 and 2
-e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
-
-options(contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
[…]

### 2023-10-26 Manuscript/manuscript.qmd
add docx and md download options
fix package conflicts breaking tables

@@
 :::
+
+::: {.content-visible when-format="docx"}
+{{< include pre_sections/pre_docx.qmd >}}
+:::
+
 {{< pagebreak >}}
@@
   reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
+colorVec=c("darkableue","darkred")
 plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
@@
 
-colorVec=c("darkblue","darkred")
+colorVec=c("darkableue","darkred")
 plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
@@
 
-result$constant |>kbl(booktabs = TRUE,
+result$constant |>kable(booktabs = TRUE,
                         linesep = "\\addlinespace[0.5em]",
@@
 
-result$varied |> kbl(booktabs = TRUE,
+result$varied |> kable(booktabs = TRUE,
                         linesep = "\\addlinespace[0.5em]",
@@
                       iter=5000,chains=4)
-GetModelStats(e1_distBMM) |> kbl(booktabs = TRUE,caption = paste("Coefficients"))
+GetModelStats(e1_distBMM) |> kable(booktabs = TRUE,caption = paste("Coefficients"))
 
@@
    mutate(across(where(is.numeric), \(x) round(x, 2)),
-          pd=ifelse(value<0,1-pd,pd)) |> kbl(booktabs = TRUE)
+          pd=ifelse(value<0,1-pd,pd)) |> kable(booktabs = TRUE)
 # |> 
-#   kbl(caption="Contrasts")
+#   kable(caption="Contrasts")
 
@@
 result <- test_summary_table(test, "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-result$constant |> kbl(booktabs = TRUE)
-result$varied |> kbl(booktabs = TRUE)
+result$constant |> kable(booktabs = TRUE)
+result$varied |> kable(booktabs = TRUE)
 
@@
                         control=list(adapt_delta=0.94, max_treedepth=13))
-GetModelStats(e1_vxBMM ) |> kbl(booktabs=T, caption="Fit to all 6 bands")
+GetModelStats(e1_vxBMM ) |> kable(booktabs=T, caption="Fit to all 6 bands")
 
@@
   group_by(Condition) |>
-  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()
+  summarise(across(starts_with("Q"), list(mean = mean))) |> kable()
 
@@
 result <- test_summary_table(testE2, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-result$constant |> kbl()
-result$varied |> kbl()
+result$constant |> kable()
+result$varied |> kable()
 # make kable table with smaller font size
-# result$constant |> kbl(caption="Constant Testing - Deviation",booktabs=T,escape=F) |> kable_styling(font_size = 7)
+# result$constant |> kable(caption="Constant Testing - Deviation",booktabs=T,escape=F) |> kable_styling(font_size = 7)
 ```
@@
           pd=ifelse(value<0,1-pd,pd)) |>
-   kbl(caption="Contrasts")
+   kable(caption="Contrasts")
 
@@
 This suggests a potential benefit of training with variation, though the evidence is not definitive.
+
+#### Discrimination between Velocity Bands
+
+In addition to accuracy/deviation.
+We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e2-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
+
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: fig-e2-test-vx
+#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 9
+testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e2-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
+#| layout-ncol: 2
+
+result <- test_summary_table(testE2, "vx","X Velocity" ,mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kable()
+result$varied |> kable()
+
+```
+
+```{r}
+#| label: tbl-e2-bmm-vx
+#| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=testE2,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+mt3 <-GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T)
+mt3
+
+cd1 <- get_coef_details(e2_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e2_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
+```
+
+See @tbl-e2-bmm-vx for the full model results.
+
+When examining discrimination ability using the model predicting raw x-velocity, the results were less clear than those of the absolute deviation analysis.
+The slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]) indicates that participants showed good discrimination between bands overall.
+However, the interaction term suggested this effect was not modulated by training condition (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]) Thus, while varied training may provide some advantage for accuracy, both training conditions seem to have similar abilities to discriminate between velocity bands.
+
+```{r}
+#| label: fig-e2-bmm-vx
+#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI.
+
+e2_vxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |>
+  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+  ylab("Predicted X Velocity") + xlab("Band")+
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE2$vb), 
+                     limits = c(0, 1400)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+```
 
@@
 resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-resultOrig$constant |> kbl()
-resultOrig$varied |> kbl()
+resultOrig$constant |> kable()
+resultOrig$varied |> kable()
 
 resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-resultRev$constant |> kbl()
-resultRev$varied |> kbl()
+resultRev$constant |> kable()
+resultRev$varied |> kable()
 
@@
 resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-resultOrig$constant |> kbl()
-resultOrig$varied |> kbl()
+resultOrig$constant |> kable()
+resultOrig$varied |> kable()
 
 resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-resultRev$constant |> kbl()
-resultRev$varied |> kbl()
+resultRev$constant |> kable()
+resultRev$varied |> kable()
 ```

### 2023-10-26 Functions/packages.R

@@ -5,8 +5,8 @@ suppressWarnings(if (!require("pacman")) install.packages("pacman"))
 # load packages and install if not installed --------------------------------------------
 pacman::p_load(tidyverse,tidybayes,brms, lme4, bayesplot,bayestestR,parameters,marginaleffects,
                 emmeans, equatiomatic, here, pacman,  broom,
-               broom.mixed,lme4,emmeans,here,knitr,kableExtra,gt,
-                wesanderson,glue, ggdist,ggforce,patchwork,gghalves,ggh4x,modelsummary,
+               broom.mixed,lme4,emmeans,here,knitr,gt,
+                wesanderson,glue, ggdist,ggforce,patchwork,gghalves,ggh4x,
                 pander,RColorBrewer,
                 install = TRUE,
                 update = FALSE

### 2023-10-26 Manuscript/.vdoc.r

@@ -61,37 +61,17 @@
 #
 #
 #
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-library(here)
 here::set_here(path='..')
 source(here::here("Functions", "packages.R"))
-# test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
-# testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
-#   summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
-
 
 if (is.null(knitr::pandoc_to())) {
   fmt_out <- "interactive"
 } else {
   fmt_out <- knitr::pandoc_to()
 }
+
+knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
+                      warning = FALSE, message = FALSE, eval=TRUE)
 
 knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                       fig.width = 6, fig.height = (6 * 0.618),
@@ -100,19 +80,32 @@ knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
 options(digits = 3, width = 120,
         dplyr.summarise.inform = FALSE,
         knitr.kable.NA = "")
-# 
 
 #
 #
 #
 #
-
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
+#
 source(here::here('Functions/IGAS_ProcessFunctions.R'))
 
 e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
 
 # load the processed data from experiment 1 and 2
-
 
 e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
 
@@ -131,6 +124,2063 @@ e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Co
 e1Pos <- c("610","760","835","910")
[…]

### 2023-10-28 Appendix/E1_Appendix.qmd
add supplementals

### Appendix - Project 2 - Experiment 1

```{r}
# print(getwd())
# here::set_here(path='..')
# print(getwd())
source(here::here("Functions", "packages.R"))

```

```{r}
test <- readRDS(here::here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test")  |>
  select(id,condit,bandInt,vb,vx,dist,sdist,bandType,tOrder)
```

```{r setupAe1, include=FALSE}

e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

modelName <- "e1_testDistBand_RF_5K"
e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)

e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))

```

## E1 Appendix

### Posterior Predictive Distributions

```{r}
#| label: fig-post-pred
#| fig-cap: Posterior Predictive distributions for Deviation and Vx. Posterior Draws in Blue, colored lines are empirical data. 
#| fig-subcap: ["Posterior Predictive Distribution - Deviation", "Posterior Predictive Distribution - X Velocity"]
#| fig-width: 13
#| fig-height: 12

vx_pred <- 
  posterior_predict(e1_vxBMM, ndraws = 500) |> 
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test  |>
        mutate(vx_pred = yrep_iter)
    },
    .id = 'iter'
  ) |>
  mutate(iter = as.numeric(iter))

dist_pred <- 
  posterior_predict(e1_distBMM, ndraws = 500) |> 
  array_branch(margin=1) |> 
   map_dfr( 
    function(yrep_iter) {
      test  |>
        mutate(dist_pred = yrep_iter)
    },
    .id = 'iter'
  ) |>
  mutate(iter = as.numeric(iter))

dist_pred  |>
  filter(iter < 100) %>%
  ggplot(aes(dist_pred, group = iter)) +
  geom_line(alpha = .03, stat = 'density', color = 'blue') +
  geom_density(data = test,
               aes(dist,col=vb),
               inherit.aes = FALSE,
               size = 0.7) + # 1
  facet_grid(condit ~ vb) +
  xlab('Deviation')

vx_pred  |>
  filter(iter < 100) %>%
  ggplot(aes(vx_pred, group = iter)) +
  geom_line(alpha = .03, stat = 'density', color = 'blue') +
  geom_density(data = test,
               aes(vx,col=vb),
               inherit.aes = FALSE,
               size = 0.7) + # 1
  facet_grid(condit ~ vb) +
  xlab('Vx')

```

### Empirical vs. Predicted

```{r}
#| label: fig-empVsPred
#| fig-cap: Bayesian Mixed Model predictions vs. Empirical Predictions - X velocity
#| fig-height: 15
#| fig-width: 12

{
vx_pred  |>
  filter(iter < 100)  |> group_by(id,condit,vb,iter) |>
  summarise(vx_pred=mean(vx_pred)) %>%
  ggplot(aes(x=vb,y=vx_pred,fill=condit)) + 
  geom_flat_violin( position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,
                   trim = FALSE, alpha = .5, colour = NA) +
  # geom_point(aes(x = as.numeric(vb) - 0.15, y = vx_pred, colour = vb),
  #            position = position_jitter(width = 0.05, height = 0),
  #            size = 1, shape = 20) +
  geom_boxplot(aes(x = vb, y = vx_pred, fill = condit),
               outlier.shape = NA,
               alpha = 0.5,
               width = 0.1,
               colour = "black") +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Predicted Vx")  } /
{
vx_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  summarise(vx=mean(vx)) %>%
  ggplot(aes(x=vb,y=vx,fill=condit)) + 
  geom_flat_violin( position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,
                   trim = FALSE,
                   alpha = .5,
                   colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15,col=condit),
             # position = position_jitter(width = 0.05),
             position = position_jitter(width = 0.05, height = 0),
             size = 1,
             shape = 20) +
  geom_boxplot(
               outlier.shape = NA,
               alpha = 0.5,
               width = 0.1,
               colour = "black") +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Vx") }
```

### Different Aggregations

```{r fig.width=14, fig.height=13}
#| label: fig-empirical-vxGrp
#| fig-cap: E1. Distribution of vx at Participant and Trial level
#| fig-width: 13
#| fig-height: 14

epId <- vx_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  summarise(vx=median(vx)) |>
  ggplot(aes(x=vb,y=vx,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = 1, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=vx,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Vx - Subject level averaging")

epTrial <- vx_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  ggplot(aes(x=vb,y=vx,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = .5, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=vx,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Vx - Raw Trial") +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank())

epId + epTrial
```

```{r fig.width=14, fig.height=13}
#| label: fig-empirical-distGrp
#| fig-cap: E1. Distribution of Vx  at Participant and Trial level
#| fig-width: 13
#| fig-height: 14

epId <- dist_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  summarise(dist=median(dist)) |>
  ggplot(aes(x=vb,y=dist,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = 1, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=dist,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Deviation - Subject level averaging")

epTrial <- dist_pred  |>
  filter(iter < 2)  |> group_by(id,condit,vb) |>
  ggplot(aes(x=vb,y=dist,fill=condit)) + 
  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
             position = position_jitter(width = 0.05, height = 0),
             size = .5, shape = 20, alpha=.7) +
  geom_boxplot(aes(x=vb,y=dist,fill=condit),
               outlier.shape = NA,
               alpha = 0.5, width = 0.1) +
  geom_hline(yintercept = 0,
             linetype = 'dashed',
             color = 'red',
             size = 0.4) + 
  coord_flip() + ggtitle("Empirical Deviation - Raw Trial") +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank())

epId + epTrial
```

```{r}
#| label: fig-e1-ame
#| fig-cap: E1. Predicted Means Per Condition and Band, and Average Marginal Effect (Constant - Varied)
#| fig-width: 10
#| fig-height: 10

new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")])))

cSamp <- e1_distBMM  |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> gather_emmeans_draws()  |>
  group_by(contrast, .draw,bandInt) |> summarise(value=mean(.value), n=n())

 ameBand <- cSamp |> ggplot(aes(x=value,y="")) + 
  stat_halfeye() + 
  geom_vline(xintercept=0,alpha=.4)+
  facet_wrap(~bandInt,ncol=1) + labs(x="Marginal Effect (Constant - Varied)", y= NULL)+
  ggtitle("Average Marginal Effect")

bothConditGM <- e1_distBMM %>%
  epred_draws(newdata = new_data_grid,ndraws = 2000, re_formula = NA) |>
  ggplot(aes(x=.epred,y="Mean",fill=condit)) + 
  stat_halfeye() +facet_wrap(~bandInt, ncol = 1) +
  labs(x="Predicted Deviation", y=NULL)+
  ggtitle("Grand Means") +theme(legend.position = "bottom")

(bothConditGM | ameBand) + plot_layout(widths=c(2,1.0))
```

### 2023-10-28 Appendix/IGAS-Supplemental.qmd
add supplementals

---
# title: "R Notebook"
# output: html_notebook
execute: 
  warning: false
  eval: true
---

```{r, include=FALSE, echo=FALSE}
source(here::here('Functions/IGAS_ProcessFunctions.R'))
library(patchwork)
#rm(list=ls())
###### data loading and organization #######

# load the processed data from experiment 1 and 2
e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'

options(contrasts = c("contr.sum", "contr.poly"))
defaultContrasts = options()$contrasts
theme_set(theme_classic())

dodge <- position_dodge(width = 0.9)
e2GrpPos <- c("400","500","625","675","800","900")
e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")

e1Pos <- c("610","760","835","910")
e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")

transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% convert_as_factor(testHalf)
variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
transfer <- rbind(variedTest,constantTest)
transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% convert_as_factor(novel,extrapolate)
transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,
                                  AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()

transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(halfInd=floor(max(testPosIndex)/2)) %>%
    mutate(testHalfSbj = case_when(testPosIndex<halfInd ~"1st-Half",testPosIndex>=halfInd ~"2nd-Half")) %>% convert_as_factor(testHalfSbj)

```

Reviewer #2: This study addresses a question that is important both theoretically and practically. However, the authors need to rule out the following, less interesting alternative. Namely, the results could be due to task practice effect, as follows.

Since there was no pre-training test, and no practice trials (as far as I can tell), and since the task was an online motor task that participants could not rely on their prior motor experience, trying to launch the ball to the target could only be done via trial and error. For the varied training group, they got to practice at two distances. Therefore, they had a better "calibration" in terms of the relationship between launching speed and target distance. This was likely beneficial both in Exp.1 when both transfer distances were interpolations from the two trained distances, and in Exp.2 when two transfer distances were interpolations and two were extrapolations but the latter two were immediately next to the training distances.

In comparison, since the constant group trained at only a single distance, any transfer distance (or at least the first transfer distance tested) was extrapolation even if this transfer distance was shorter than the trained, because the participants did not know beforehand how to shoot the ball to the shortest distance due to the existence of the barrier. If the transfer distance was longer, for sure that was extrapolation.

Regardless, the above analysis suggests that the constant group would always be a step behind the varied group. The number of trials at each transfer distance may not be sufficient for them to catch up the varied group either (whether there was learning during testing should be checked). If such disadvantage for the constant group is indeed due to the lack of tryout opportunities, then the authors should verify whether the same results still hold if all groups were provided opportunities to practice, or if pre-training tests across all distances were offered.

### exponential learning models fit to individual subjects
```{r}

e2TestFits <- readRDS(here::here('data/IGAS-e2TestFits-April4.rds'))
e2TestFits <- e2TestFits %>% mutate(Asymptote.Minus.Start=pAsym-pStart)
exp2.fit2 <- e2TestFits %>% ungroup() %>% group_by(sbjCode,conditType) %>%
  summarise(MeanAsym=mean(pAsym),MeanStart=mean(pStart),
            MeanRate=mean(pRate),
            asymMinusStart=mean(Asymptote.Minus.Start),.groups="keep") %>% 
  ungroup() %>% as.data.frame()

```

### Group comparison of learning rate fits
```{r}
# mr1=e2TestFits %>% anova_test(dv=pRate,between=conditType,wid=sbjCode,within=positionX,type=3);show(mr1)
# mr2=exp2.fit2 %>% anova_test(dv=MeanRate,between=conditType,wid=sbjCode,type=3);show(mr2)

h4<-e2TestFits %>% ggplot(aes(x=positionX,y=pRate,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("Learning rates ")+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+ylab("Inverse Learning Rate")+xlab("Testing Location")
h4

# mr1=e2TestFits %>% filter(converged==TRUE)%>% anova_test(dv=pRate,between=conditType,wid=sbjCode,within=positionX,type=3);show(mr1)
# mr2=exp2.fit2 %>% anova_test(dv=MeanRate,between=conditType,wid=sbjCode,type=3);show(mr2)

h4<-e2TestFits %>%filter(Pval<.4)%>% ggplot(aes(x=positionX,y=pRate,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("Learning rates ")+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+ylab("Inverse Learning Rate")+xlab("Testing Location")
h4

```

### First vs. second half of testing stage
```{r,fig.height=7,fig.width=8}

testSplit <- transfer %>%
  group_by(sbjCode, conditType, positionX, testHalfSbj) %>%
  summarise(
    MeanTargetDistance = mean(AbsDistFromCenter),
    MeanScaledDev =mean(scaledDev,trim=.05),
    .groups = "keep"
  ) %>% 
  as.data.frame()

testSplit2 <- transfer %>%
  group_by(sbjCode, conditType, testHalfSbj) %>%
  summarise(
    MeanTargetDistance = mean(AbsDistFromCenter, trim = .01),
    MeanScaledDev =
      mean(scaledDev, trim = .05),
    .groups = "keep"
  ) %>% as.data.frame()

tsw <- testSplit %>% ungroup() %>% 
  pivot_wider(names_from = testHalfSbj,values_from=c(MeanTargetDistance,MeanScaledDev)) %>%
  mutate(endMinusStart = `MeanTargetDistance_2nd-Half` - `MeanTargetDistance_1st-Half`,
    endMinusStartScaled = `MeanScaledDev_2nd-Half` - `MeanScaledDev_1st-Half`) %>% 
    as.data.frame()

tsw2 <- tsw %>% 
  group_by(sbjCode,conditType) %>% summarise(endMinusStart=mean(endMinusStart),endMinusStartScaled=mean(endMinusStartScaled)) %>% as.data.frame()

# testSplit %>% ggplot(aes(x=testHalfSbj,y=MeanTargetDistance))+
#   geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge)+
#   facet_wrap(~positionX,ncol=2)+
#   stat_summary(aes(x=testHalfSbj,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge)

h1=testSplit %>% filter(testHalfSbj=="1st-Half") %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
 geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
 scale_y_continuous(name="Mean Absolute Deviation From Target",limits=c(0,400))+ 
 ggtitle("Testing Performance - 1st half")+
  ylab("Mean Absolute Deviation From Target")+xlab("Testing Location")+theme(legend.position="none")

h2=testSplit %>% filter(testHalfSbj=="2nd-Half") %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
 geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8) + 
 scale_y_continuous(name="",limits=c(0,400))+ 
 ggtitle("Testing Performance - 2nd half")+
  xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)

#egg::ggarrange(h1,h2,ncol=2)

h3 <- tsw %>% ggplot(aes(x=positionX,y=endMinusStart))+
  geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+
  stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
  ylab("2nd Half Deviation - 1st Half Deviation")+ 
  ggtitle("Improvement Per Testing Location")+
  xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Testing Location"))+theme(legend.position="none")

#ggarrange(h1,h2,h3,h4,ncol=2)

(h1 + h2) / (h3 + h4)

# 
 #testSplit2 %>% anova_test(dv=MeanScaledDev,between=conditType,within = c(testHalfSbj),wid=sbjCode,type=3)
 #testSplit %>% anova_test(dv=MeanTargetDistance,between=conditType,covariate=testHalfSbj,within=(positionX),wid=sbjCode)
# testSplit %>% lmer(MeanTargetDistance ~ conditType*testHalfSbj + (1|sbjCode)+(1+testHalfSbj|positionX),data=.) %>% summary()

# testSplit %>% anova_test(dv=MeanTargetDistance,between=conditType,within=positionX,wid=sbjCode,type=3)
# 
# print("Testing End - Testing Start Comparison")
# tsw %>% anova_test(dv=endMinusStart,between=conditType,within=positionX,wid=sbjCode,type=3)
# tsw2 %>% anova_test(dv=endMinusStartScaled,between=conditType,wid=sbjCode,type=3)
# 
# print("2nd Half of testing only comparison")
# testSplit %>% filter(testHalfSbj=="2nd-Half")%>%  anova_test(dv=MeanTargetDistance,between=conditType,within=(positionX),wid=sbjCode)
# testSplit2 %>% filter(testHalfSbj=="2nd-Half")%>%  anova_test(dv=MeanScaledDev,between=conditType,wid=sbjCode,type=3)
# 
# testSplit2 %>% filter(testHalfSbj=="2nd-Half")%>% group_by(conditType) %>% get_summary_stats(type = "mean_sd")

```

### Group Comparison for asymptote-starting performance
```{r}

# ma1=e2TestFits %>% filter()%>% anova_test(dv=Asymptote.Minus.Start,between=conditType,wid=sbjCode,within=positionX,type=3);show(ma1)
# ma2=exp2.fit2 %>% anova_test(dv=asymMinusStart,between=conditType,wid=sbjCode,type=3);show(ma2)

e2TestFits %>% ggplot(aes(x=conditType,y=Asymptote.Minus.Start,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("e2 testing (asymptote - start performance)  ")
```

### Relative distance and under/overshooting

Reviewer 3
Absolute versus relative distance: From a methodological standpoint, I understand the need to differentiate these two types of distance. However, from a theoretical perspective there may be some issue in differentiating these two concepts. Schema theory relies on relative (or invariant) information to inform the motor program. However, both distances would be important to an instance or exemplar representation. You may want to consider commenting on this issue.

Reviewer 2
For the same reason, the plots showing improvement during training could be due to participants learning the task, rather than fine motor skills. Although task learning and motor learning are impossible to separate cleanly, the common practice in the field is indeed to offer practice trials to reduce the task learning aspects. The authors should address this.

In addition to absolute errors (which is related to variance), the authors should also provide other measures of performance, e.g., the mean of the signed errors, so that readers have a better idea whether there was any meaningful over- or undershooting.

#### experiment 1 training - relative distances
```{r,echo=FALSE,warning=FALSE}

# possible that scaling required loading special package from devtools
exp1Train <- e1 %>% filter(stage!="Transfer",mode==1) %>% group_by(positionX) %>%mutate(scaleDev=scale_this(AbsDistFromCenter)) %>%ungroup() %>% group_by(sbjCode,trainHalf,conditType,devianceDirection,positionX)
exp1Train = exp1Train %>% summarise(MeanTargetDistance=mean(AbsDistFromCenter,trim=.05),scaledDist=mean(scaleDev,trim=.05),meanRelativeDist=mean(relativeDeviance,trim=.05))

# ggplot(data = exp1Train, aes(x=stage, y=scaledDist)) + geom_boxplot(aes(fill=conditType),position=position_dodge(1)) +ggtitle("Training Performance - Experiment 1")

# manuscript plot - original
ggplot(data = exp1Train, aes(x=trainHalf, y=MeanTargetDistance)) + geom_boxplot(aes(fill=conditType),position=position_dodge(1)) +ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.5)+theme_classic() +ggtitle("Experiment 1 Training - Absolute Distance")

exp1Train %>% ggplot(aes(x=trainHalf,y=MeanTargetDistance))+
  geom_bar(aes(group=positionX,fill=positionX),stat="summary",fun=mean,position=dodge)+
  facet_wrap(~devianceDirection,ncol=2)+
  stat_summary(aes(x=trainHalf,group=positionX),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
  ylab("Mean Distance From Center Of Target")+
  xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Throw Location"))+theme(legend.title.align=.25)

ggplot(data = exp1Train, aes(x=trainHalf, y=meanRelativeDist)) + geom_boxplot(aes(fill=conditType),position=position_dodge(1)) +ylab("Mean Relative Distance From Center Of Target") +xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.5)+theme_classic()+ggtitle("Experiment 1 Training - Relative Distance ")+facet_grid(.~devianceDirection)

ggplot(data = exp1Train, aes(x=trainHalf, y=MeanTargetDistance)) + geom_boxplot(aes(fill=conditType),position=position_dodge(1)) +ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.5)+theme_classic() +ggtitle("Experiment 1 Training - Absolute Distance")+facet_grid(.~devianceDirection)

t= e1 %>% filter(stage!="Transfer",mode==1)  %>% group_by(conditType,positionX,devianceDirection) %>% 
  summarise(Mean=round(mean(AbsDistFromCenter),2),sd=round(sd(AbsDistFromCenter),2),msd=paste(Mean,"(",sd,")",sep=""),.groups="keep") %>%
   select(-Mean,-sd) %>% spread(positionX,msd) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)

t= e1 %>% filter(stage!="Transfer",mode==1)  %>% group_by(conditType,positionX) %>% 
  summarise(Mean=round(mean(relativeDeviance),2),sd=round(sd(AbsDistFromCenter),2),msd=paste(Mean,"(",sd,")",sep=""),.groups="keep") %>%
   select(-Mean,-sd) %>% spread(positionX,msd) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)

t= e1 %>% filter(stage=="Transfer",mode==1)  %>% group_by(conditType,positionX) %>% 
  summarise(Mean=round(mean(relativeDeviance),2),sd=round(sd(AbsDistFromCenter),2),msd=paste(Mean,"(",sd,")",sep=""),.groups="keep") %>%
   select(-Mean,-sd) %>% spread(positionX,msd) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)

# f=ftable(xtabs(MeanTargetDistance  ~ conditType+positionX+devianceDirection, data = exp1Train))
# stargazer(f,type="text",summary=FALSE,rownames = FALSE)

```

#### experiment 2 training - relative distances
```{r,echo=FALSE,warning=FALSE}
# possible that scaling required loading special package from devtools
exp2Train <- e2 %>% filter(stage!="Transfer",mode==1) %>% group_by(Group2,sbjCode,conditType,Group) %>%mutate(scaleDev=scale_this(AbsDistFromCenter)) %>%ungroup() %>% group_by(Group2,sbjCode,stage,conditType,devianceDirection)
exp2Train = exp2Train %>% summarise(MeanTargetDistance=mean(AbsDistFromCenter),scaledDist=mean(scaleDev),meanRelativeDist=mean(relativeDeviance,trim=.05))
exp2Train$stage <- factor(exp2Train$stage, levels = c("Beginning", "Middle", "End")) #in case the levels get out of order

#ggplot(data = exp2Train, aes(x=stage, y=scaledDist)) + geom_boxplot(aes(fill=Group2),position=position_dodge(1)) +ggtitle("")

# manuscript plots

par(mfrow=c(1,2))
ggplot(data = exp2Train, aes(x=stage, y=meanRelativeDist)) + geom_boxplot(aes(fill=conditType),position=position_dodge(1)) +ylab("Mean Relative Distance From Center Of Target") +xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Group"))+theme(legend.title.align=.25)+theme_classic()+ggtitle("Experiment 2 Training - Relative Distance")+facet_grid(.~devianceDirection)

ggplot(data = exp2Train, aes(x=stage, y=meanRelativeDist)) + geom_boxplot(aes(fill=Group2),position=position_dodge(1)) +ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+ggtitle("Experiment 2 Training - Relative Distance")+facet_grid(.~devianceDirection)

```

#### Experiment 1 Testing - relative distances
```{r,echo=FALSE,warning=FALSE,fig.width=10,fig.height=7}
exp1Transfer3 <- e1 %>% filter(stage=="Transfer") %>% group_by(conditType2,sbjCode,positionX,ThrowPosition,devianceDirection) %>% summarise(MeanTargetDeviance = mean(AbsDistFromCenter),meanRelativeDist=mean(relativeDeviance))

exp1Transfer3_raw <- e1 %>% filter(stage=="Transfer",mode==1,AbsDistFromCenter<1500,trialType!=44)

#manuscript plot
dodge <- position_dodge(width = 0.9)
e1Pos <- c("610","760","835","910")
e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")

# exp1Transfer3 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)

# exp1Transfer3 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+ggtitle("Experiment 1 Test -Relative Distance")
# 
# 
# 
# exp1Transfer3 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+facet_grid(.~devianceDirection)

exp1Transfer3 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Signed Deviation From Target Center") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+facet_grid(.~devianceDirection)

t= exp1Transfer3  %>% 
  group_by(conditType2,positionX) %>% 
  summarise(Mean.unsigned=round(mean(MeanTargetDeviance),2),
            sd.unsigned=round(sd(MeanTargetDeviance),2),
            msdu=paste(Mean.unsigned,"(",sd.unsigned,")",sep=""),
            Mean.signed=round(mean(meanRelativeDist),2),
            sd.signed=round(sd(meanRelativeDist),2),
            msds=paste(Mean.signed,"(",sd.signed,")",sep=""),
            .groups="keep") %>% ungroup() %>%
   select(-Mean.unsigned,-sd.unsigned,-Mean.signed,-sd.signed) %>% 
  pivot_wider(names_from = positionX,values_from=c(msdu,msds)) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)

t= exp1Transfer3  %>% 
  mutate(Condition=conditType2) %>%
  group_by(Condition,positionX) %>% 
  summarise(Mean.signed=round(mean(meanRelativeDist),2),
            sd.signed=round(sd(meanRelativeDist),2),
            msds=paste(Mean.signed,"(",sd.signed,")",sep=""),
            .groups="keep") %>% ungroup() %>%
   select(-Mean.signed,-sd.signed) %>% 
  pivot_wider(names_from = positionX,values_from=c(msds)) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)

```

#### Experiment 2 Testing - relative distances
```{r,echo=FALSE,warning=FALSE,fig.width=8,fig.height=8}

exp2Transfer3 <- e2 %>% filter(stage=="Transfer") %>% group_by(conditType2,sbjCode,positionX,devianceDirection,Group) %>% summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),meanRelativeDist=mean(relativeDeviance)) %>% ungroup()
exp2Transfer3$ThrowPosition <- exp2Transfer3$positionX

exp2Transfer4 <- e2 %>% filter(stage=="Transfer",mode==1,AbsDistFromCenter<1500,trialType!=44) %>% group_by(Group2,sbjCode,positionX,devianceDirection,Group) %>% summarise(MeanTargetDeviance = mean(AbsDistFromCenter),meanRelativeDist=mean(relativeDeviance))

# exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+ggtitle("Experiment 2 Test - Relative Distance")
# 
# exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Absolute Dist - Split by Over/Under")

exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Signed Deviation From Target Center") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+facet_grid(.~devianceDirection)

# 
# exp2Transfer4 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=Group2,fill=Group2))+geom_bar(stat="summary",position=position_dodge(),fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Position"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Absolute Dist - Split by Over/Under")
# 
# 
# exp2Transfer4 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=Group2,fill=Group2))+geom_bar(stat="summary",position=position_dodge(),fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Position"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Experiment 2 Test - Relative Distance")

# 
# t= exp2Transfer3  %>% 
#   mutate(Condition=conditType2) %>%
#   group_by(Condition,positionX) %>% 
#   summarise(Mean.signed=round(mean(meanRelativeDist),2),
#             sd.signed=round(sd(meanRelativeDist),2),
#             msds=paste(Mean.signed,"(",sd.signed,")",sep=""),
#             .groups="keep") %>% ungroup() %>%
#    select(-Mean.signed,-sd.signed) %>% 
#   pivot_wider(names_from = positionX,values_from=c(msds)) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)
#

```

#### Experimenet 1 - intermittent testing
```{r,fig.width=9}
# first 3 trials - 1 throw from 610, 760 and 910
# interleaved every 20 trials, 2 throws from 610, 760, 910
# 10 full intermittent tests (6 trials each), plus 3 at beginning = 63 total per subject. 
#[1] 0  2  3  5  6  8  9  11 12 14 15 17 18 20 21 23 24 26 27 29 30
# First final testing trial is 264. So 1-263 = training and intermittent testing. 
# 
# intTest.third <- exp1.inter %>% filter(intStage!="int1")%>% group_by(sbjCode,conditType,stage,intStage,positionX) %>%
#   summarise(MeanTargetDistance=mean(AbsDistFromCenter,trim=.05)) %>% group_by(sbjCode,conditType,stage,positionX) %>%
#   summarise(MeanTargetDistance=mean(MeanTargetDistance))
# 
# intTest.third %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
#   geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
#   facet_wrap(~conditType,ncol=2)+
#   stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
#   ylab("Mean Distance From Center Of Target")+
#   xlab("Throw Location")+theme(plot.title = element_text(hjust = 0.5))+
#   guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
# 
# intTest.half %>% anova_test(dv=MeanTargetDistance,between=conditType,within=trainHalf,covariate=positionX,wid=sbjCode)
# intTest.half %>% anova_test(dv=MeanTargetDistance,between=conditType,within=c(trainHalf,positionX),wid=sbjCode)

intTest.half <- readRDS(here::here("data/e1_intTest.rds"))

# intTest.half <- exp1.inter %>%filter(AbsDistFromCenter<1550)%>% 
#   group_by(sbjCode,conditType,trainHalf,positionX) %>%
#   summarise(MeanTargetDistance=mean(AbsDistFromCenter,trim=.01))

intTest.half %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
  geom_bar(aes(group=trainHalf,fill=trainHalf),stat="summary",fun=mean,position=dodge)+
  facet_wrap(~conditType,ncol=2)+
  stat_summary(aes(x=positionX,group=trainHalf),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
  ylab("Mean Distance From Center Of Target")+
  xlab("Intermittent Testing Throw Location")+theme(plot.title = element_text(hjust = 0.5))+
  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)

cnames=c("Condition","610_First Half","760_First Half","910_First Half","610_Second Half","760_Second Half","910_Second Half")
test= intTest.half %>% rename(Condition="conditType") %>% group_by(Condition,trainHalf,positionX) %>% 
  summarise(Mean=round(mean(MeanTargetDistance),2),sd=round(sd(MeanTargetDistance),2)) 
test=test %>% group_by(Condition) %>% mutate(msd=paste(Mean,"(",sd,")",sep="")) %>%
 select(Condition,positionX,trainHalf,msd)%>% pivot_wider(names_from = c(positionX,trainHalf),values_from=c(msd))
test=test %>% as.data.frame()
colnames(test) <- cnames
stargazer(test,type="text",summary=FALSE,rownames=FALSE)

```

### Training plots - Experiment 1
```{r}
#| warning: false

# possible that scaling required loading special package from devtools
exp1Train <- e1 %>% filter(stage!="Transfer",mode==1) %>% group_by(Group,sbjCode) %>%mutate(scaleDev=scale_this(AbsDistFromCenter)) %>%ungroup() %>% group_by(Group,sbjCode,stage,conditType)
exp1Train = exp1Train %>% summarise(MeanTargetDistance=mean(AbsDistFromCenter),scaledDist=mean(scaleDev,trim=.05))
exp1Train$stage <- factor(exp1Train$stage, levels = c("Beginning", "Middle", "End")) #in case the levels get out of order
exp1TrainTrials <- e1 %>% filter(stage!="Transfer",mode==1,trialType!=44) %>% group_by(Group,sbjCode,positionX) %>% mutate(scaleDev=scale_this(AbsDistFromCenter),ind=1,trainIndex=cumsum(ind)) %>%ungroup() %>% group_by(Group,sbjCode,stage,conditType)

# exp1TrainTrials %>% filter(AbsDistFromCenter<1000) %>% ggplot(aes(x=trainIndex,y=AbsDistFromCenter,group=conditType2)) +geom_point()+geom_smooth(method="lm",se=FALSE) +facet_grid(~positionX)

# manuscript plot - original
ggplot(data = exp1Train, aes(x=stage, y=MeanTargetDistance)) + geom_boxplot(aes(fill=conditType),position=position_dodge(1))+stat_summary(fun="mean",aes(group=conditType),position=position_dodge(1))+
ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.5)+theme_classic()

lineplot.CI(data=exp1Train,x.factor=stage,group=conditType,response=scaledDist,xlab="Training Stage",x.leg=2,legend=TRUE,ylab="Distance from Target (scaled)",main="Training Performance - Experiment 1",col=c("red","black"))

lineplot.CI(data=exp1Train,x.factor=stage,group=conditType,response=MeanTargetDistance,xlab="Training Stage",x.leg=2,legend=TRUE,ylab="Distance From Target",main="Training Performance - Experiment 1",col=c("red","blue"))

```

#### Not in manuscript #####

# fit to testing performance averaged across positions
```{r}
e2Fits.AggPos <- readRDS(here::here('data/IGAS-e2Fits.AggPos-April_12.rds'))

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pStart,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("experiment 2 - starting performance per position")

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pAsym,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("e2 testing performance asymptote per position ")

e2Fits.AggPos %>% ggplot(aes(x=Group,y=pRate,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("e2 testing performance asymptote per position ")

#mr1=e2Fits.AggPos %>% anova_test(dv=pRate,between=conditType,wid=sbjCode,type=3);show(mr1)

```

#### statistical tests for starting performance
```{r}

ms1=e2TestFits %>% filter(converged==TRUE) %>% anova_test(dv=pStart,between=conditType,wid=sbjCode,within=positionX,type=3);
ms2=exp2.fit2 %>% anova_test(dv=MeanStart,between=conditType,wid=sbjCode,type=3);
#ms1
ms2

e2TestFits %>% ggplot(aes(x=conditType,y=pStart,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("experiment 2 - starting performance per position")

```

#### statistical tests for asymptote
```{r}

ma1=e2TestFits %>% filter(converged==TRUE)%>% anova_test(dv=pAsym,between=conditType,wid=sbjCode,within=positionX,type=3);
ma2=exp2.fit2 %>% anova_test(dv=MeanAsym,between=conditType,wid=sbjCode,type=3);
ma2

e2TestFits %>% ggplot(aes(x=conditType,y=pAsym,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("e2 testing performance asymptote per position ")

```

### 2023-10-28 HTW.qmd
add supplementals

@@
 page-layout: full
-bibliography: "Assets/Bib/HTW.bib"
+bibliography: "Assets/Bib/Dissertation.bib"
 code-fold: true
 code-tools: true
+toc: true
+toc-location: body
+toc-title: Contents
 execute: 
@@
 
-[Link HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
+_______________________________________________________________________________
+[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
 
@@
 
-![htw](https://tegorman13.github.io/htw/paper.html){width="900" height="600"}
+# Introduction
+
+In project 1, I applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+Project 2 also places a greater emphasis on extrapolation performance following training.
+Although varied training has often been purported to be particularly beneficial for generalization or transfer, few experiments have compared varied and constant training in contexts with unambiguous extrapolation testing.
+
+## Function Learning and Extrapolation
+
+The study of human function learning investigates how people learn relationships between continuous input and output values.
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+
+@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
+Input stimuli and output responses were both lines of varying length.
+The correct output response was related to the length of the input line by a linear, quadratic, or random function.
+Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
+Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
+Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
+Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
+@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
+In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
+Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
+
+The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
+In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
+Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
+All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
+Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
+
+The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
+The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
+The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
+
+The authors also introduced two new function-learning models.
+The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
+ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
+ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
+The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
+When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
+ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
+EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
+Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
 
 ```{r}
-pacman::p_load(tidyverse,knitr,kableExtra)
+#| label: fig-delosh-extrap
+#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
+#| echo: false
+#| fig-width: 10
 
+source(here::here("Functions", "packages.R"))
+source(here::here("Functions","deLosh_data.R"))
+
+extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
+                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
+
+linear_function <- function(x) 2.2 * x + 30
+exponential_function <- function(x) 200 * (1 - exp(-x/25))
+quadratic_function <- function(x) 210 - (x - 50)^2 / 12
+
+linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
+    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
+  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
+
+exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
+  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
+  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
+  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
+  extrapLines +
+  scale_shape_manual(values = c(1)) +
+  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
+  theme(legend.title = element_blank(), legend.position="top") +
+  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
+                                                  linetype = c(0, 1))))
+
+quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
+  geom_point( shape = 1) +
+  stat_function( fun = quadratic_function, geom = "line") +
+  labs(title="Quadratic Function",x="",y="") + extrapLines
+
+linear_plot + exponential_plot + quadratic_plot
 ```
-# Introduction
-
-In project 1, we applied model-based techniques to quantify and control for the
-similarity between training and testing experience, which in turn enabled us to
-account for the difference between varied and constant training via an extended
-version of a similarity based generalization model. In project 2, we will go a
-step further, implementing a full process model capable of both 1) producing
-novel responses and 2) modeling behavior in both the learning and testing stages
-of the experiment. Project 2 also places a greater emphasis on extrapolation performance following
-training - as varied training has often been purported to be particularly beneficial in such situations.
-Extrapolation has long been a focus of the literature on function learning [@brehmerHypothesesRelationsScaled1974;
-@carrollFunctionalLearningLearning1963].
-Central questions of the function learning literature have included the relative difficulties of learning various functional forms (e.g.
-linear vs.bilinear vs.
-quadratic), and the relative
-effectiveness of rule-based vs. association-based exemplar models vs. various hybrid models
-[@bottNonmonotonicExtrapolationFunction2004;
-@deloshExtrapolationSineQua1997; @jonesActiveFunctionLearning2018;
-@kalishPopulationLinearExperts2004; @mcdanielConceptualBasisFunction2005;
-@mcdanielPredictingTransferPerformance2009]. However the issue of training variation has received surprisingly little attention in this area.
 
@@
 
-Data was collected from 647 participants (after exclusions). The results shown
-below consider data from subjects in our initial experiment, which consisted of
-196 participants (106 constant, 90 varied). The follow-up experiments entailed
-minor manipulations: 1) reversing the velocity bands that were trained on vs.
-novel during testing; 2) providing ordinal rather than numerical feedback during
-training (e.g. correct, too low, too high). The data from these subsequent
-experiments are largely consistently with our initial results shown below.
+Data was collected from 647 participants (after exclusions).
+The results shown below consider data from subjects in our initial experiment, which consisted of 196 participants (106 constant, 90 varied).
+The follow-up experiments entailed minor manipulations: 1) reversing the velocity bands that were trained on vs.
+novel during testing; 2) providing ordinal rather than numerical feedback during training (e.g.
+correct, too low, too high).
+The data from these subsequent experiments are largely consistently with our initial results shown below.
 
@@
 
-We developed a novel visuomotor extrapolation task, termed the ["Hit The Wall"
-(HTW]{.underline}) task, wherein participants learned to launch a projectile
-such that it hit a rectangle at the far end of the screen with an appropriate
-amount of force. Although the projectile had both x and y velocity components,
-only the x-dimension was relevant for the task.\ 
-[Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}
+We developed a novel visuomotor extrapolation task, termed the Hit The Wall task, wherein participants learned to launch a projectile such that it hit a rectangle at the far end of the screen with an appropriate amount of force.
+Although the projectile had both x and y velocity components, only the x-dimension was relevant for the task.  [Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}
 
-## Design
+## Procedure
 
-1)  90 training trials split evenly divided between velocity bands.
-    Varied training with 3 velocity bands and Constant training with 1
-    band.
+The HTW task involved launching projectiles to hit a target displayed on the computer screen.
+Participants completed a total of 90 trials during the training stage.
+In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
+In contrast, participants in the constant training condition encountered only one velocity band (800-1000).
 
-2)  No-feedback testing from 3 novel extrapolation bands. 15 trials
-    each.
+During the training stage, participants in both conditions also completed "no feedback" trials, where they received no information about their performance.
+These trials were randomly interleaved with the regular training trials.
 
-3)  No-feedbacd testing from the 3 bands used during the training phase
-    (2 of which were novel for the constant group). 9 trials each.
+Following the training stage, participants proceeded to the testing stage, which consisted of three phases.
+In the first phase, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
 
-4)  Feedback testing for each of the 3 extrapolation bands. 10 trials
-    each.
+In the second phase of testing, participants completed "no-feedback" testing from the three velocity bands used during the training stage (800-1000, 1000-1200, and 1200-1400).
+In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
+
+The third and final phase of testing involved "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 10 trials.
+Participants received feedback on their performance during this phase.
+
+Throughout the experiment, participants' performance was measured by calculating the distance between the produced x-velocity of the projectiles and the closest edge of the current velocity band.
+Lower distances indicated better performance.
+
+After completing the experiment, participants were debriefed and provided with an opportunity to ask questions about the study.
 
@@
 //| column: screen-inset-right
-//| fig-align: left
 digraph {
@@
 
-<!-- {.tabset} -->
+## Analyses Strategy
 
-# Results
+All data processing and statistical analyses were performed in R version 4.31 @rcoreteamLanguageEnvironmentStatistical2020.
+To assess differences between groups, we used Bayesian Mixed Effects Regression.
+Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019a.
+Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
+Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as circumventing convergence issues common to the frequentist analogues of our mixed models.
+For each model, we report the median values of the posterior distribution, and 95% credible intervals.
 
-## Training
+Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 of which were discarded as warmup chains.
+Rhat values were generally within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
+We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
 
-Training performance is shown in Results Figure 2A. All groups show improvement
-from each of their training velocity-bands (i.e. decreasing average distance from
-target). In the velocity band trained at by both groups (800-1000), the constant
-group maintains a superior level of performance from the early through the final
-stages of training. This difference is unsurprising given that the constant
-group had 3x more practice trials from that band.
+We compared varied and constant performance across two measures, deviation and discrimination.
+Deviation was quantified as the absolute deviation from the nearest boundary of the velocity band, or set to 0 if the throw velocity fell anywhere inside the target band.
+Thus, when the target band was 600-800, throws of 400, 650, and 1100 would result in deviation values of 200, 0, and 300, respectively.
+Discrimination was measured by fitting a linear model to the testing throws of each subjects, with the lower end of the target velocity band as the predicted variable, and the x velocity produced by the participants as the predictor variable.
+Participants who reliably discriminated between velocity bands tended to have positive slopes with values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
 
-```{r Training, echo=FALSE,fig.height=5.0, fig.width=7}
-#| eval: false
-#fig.cap="\\label{fig:figs}training performance"
-nbins=8
-t1=dt%>% mutate(Trial.Bin=cut(trial,breaks=nbins,labels=FALSE)) %>%  
-  group_by(sbjCode,condit,throwCategory,Trial.Bin) %>% summarise(dist=mean(dist),.groups = 'keep') %>%
-   ggplot(aes(Trial.Bin,dist,color=throwCategory,group=throwCategory))+
-  lineBars+
-  facet_wrap(~condit)+
-  scale_x_continuous(breaks=seq(1,nbins))+
-  ylab("Mean Distance From Target Velocity")+xlab("Training Block")+
-  scale_color_discrete(name="Velocity Band")+
-  labs(title="Hit The Wall - Training Performance",
-       caption="2A. Training Performance for both groups – binned into 8 blocks." )+
-  theme(plot.caption=element_text(hjust=0,face="italic"),
-        plot.title=element_text(face="bold"),
-        axis.title.x=element_text(face="bold"),
-        axis.title.y=element_text(face="bold"))
+```{r setup, include=FALSE}
 
-t1
+# pacman::p_load(tidyverse,knitr,tidybayes,brms, lme4, bayesplot,bayestestR,parameters,marginaleffects,
+#                 emmeans, equatiomatic, here, pacman,  broom,
+#                broom.mixed,lme4,emmeans,here,
+#                 wesanderson,glue, ggdist,ggforce,patchwork,gghalves,ggh4x,
+#                 install = TRUE,
+#                 update = FALSE
+#                )
+# walk(c(here("Functions/Display_Functions.R"), here("Functions/org_functions.R"), 
+#        here("Functions/Table_Functions.R")), source)
+
+test <- readRDS(here::here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
+#options(brms.backend="cmdstanr",mc.cores=4)
+e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
+testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
+
+knitr::opts_chunk$set(include =TRUE, 
+                      warning = FALSE, message = FALSE, eval=TRUE)
+
+knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+                      fig.width = 6, fig.height = (6 * 0.618),
+                      out.width = "100%", collapse = TRUE)
+# 
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+#
 
@@
 
-## Testing
+```{r}
+#| label: tbl-e1-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap:
+#|   - "Full datasets"
+#|   - "Intersection of samples with all labels available"
 
-For evaluating testing performance, we consider 3 separate metrics. 1)
-The average absolute deviation from the correct velocity, 2) The % of
-throws in which the wall was hit with the correct velocity and 3) The
-average x velocity produced.
+result <- test_summary_table(test, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
 
-Results Figure 2B shows the average velocity produced for all 6 bands
-that were tested. At least at the aggregate level, both conditions were
-able to differentiate all 6 bands in the correct order, despite only
-having received training feedback for 1/6 (constant) or 3/6 (varied)
-bands during training. Participants in both groups also had a bias
-towards greatly overestimating the correct velocity for band 100-300,
-for which both groups had an average of greater than 500.
+result$constant |>kable(booktabs = TRUE,
+                        linesep = "\\addlinespace[0.5em]")
+                        #caption = paste("Summary of Deviation- Constant"))
+# |>
+#   kable_styling(font_size = ifelse(fmt_out == "latex", 8.5, NA))
 
-```{r Testing Vx, fig.height=9, fig.width=10.5 }
-#| eval: false
-
-sumStats = dtest %>% group_by(sbjCode,vbLabel,condit,throwCategory) %>%
-  summarise(vxMean=mean(vxCapped),vxMedian=median(vxCapped),vxSd=sd(vxCapped),.groups = 'keep') %>%group_by(vbLabel,condit,throwCategory) %>%
-  summarise(groupMean=round(mean(vxMean),0),groupMedian=round(mean(vxMedian),0),groupSd=round(mean(vxSd,na.rm=TRUE),0),.groups = 'keep') %>%
-  mutate(meanLab=paste0("Mean=",groupMean),medianLab=paste0("Median=",groupMedian),sdLab=paste0("Sd=",groupSd)) %>%
-  mutate(sumStatLab=paste0(meanLab,"\n",medianLab,"\n",sdLab))
-
-fig2aCap=str_wrap("Figure 2B: Bands 100-300, 350-550 and 600-800 are novel extrapolations for both groups.
-Band 800-1000 was a training band for both groups.
-Bands 1000-1200, and 1200-1400 were trained for the varied group, and novel for the constant group.
-Top figure displays mean deviation from correct velocity.
-Bottom figure displays the average % of trials where participants hit the wall with the correct velocity.
-Error bars indicate standard error of the mean.
-" ,width=170)
-
-dtest %>% group_by(sbjCode,vbLabel,condit,throwCategory) %>%
-  summarise(vxMean=mean(vxCapped),lowBound=first(bandInt),highBound=first(highBound),
-            vbLag=first(vbLag),vbLead=first(vbLead),.groups = 'keep') %>%
-  ggplot(aes(x=vbLabel,y=vxMean,fill=throwCategory))+
-  geom_half_violin(color=NA)+ # remove border color
-  geom_half_boxplot(position=position_nudge(x=-0.05),side="r",outlier.shape = NA,center=TRUE,
-                    errorbar.draw = FALSE,width=.25)+
-  geom_half_point(transformation = position_jitter(width = 0.05, height = 0.05),size=.3,aes(color=throwCategory))+
-  facet_wrap(~condit,scale="free_x")+
-  geom_rect(data=vbRect,aes(xmin=vbLag,xmax=vbLead,ymin=lowBound,ymax=highBound,fill=throwCategory),alpha=.3)+
-  geom_text(data=sumStats,aes(y=2090,label = sumStatLab),size=2.5)+
-  bandLines4+
-  #geom_text(data=sumStats,aes(x=throwCategory,y=2100,label = groupMean),size=2, vjust = -0.5)+
-  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2))+
-  scale_fill_discrete(name="Velocity Band")+
-  scale_color_discrete(guide="none")+  # remove extra legend
-  theme(legend.position='none',
-        plot.title=element_text(face="bold"),
-        axis.title.x=element_text(face="bold"),
-        axis.title.y=element_text(face="bold"),
-        axis.text.x = element_text(size = 7.5))+
-  ylab("Mean X Velocity")+xlab("Target Velocity Band") +
-   labs(title="2B. Testing Performance (no-feedback) - X-Velocity Per Band",
-        caption=fig2aCap)+
-  theme(plot.caption=element_text(hjust=0,face="italic"))
+result$varied |> kable(booktabs = TRUE,
+                        linesep = "\\addlinespace[0.5em]")
+                        #caption = paste("Summary of Deviation- Varied"))
 
@@
 
-As is reflected in Results Figure 2C, the constant group performed
-significantly better than the varied group at the 3 testing bands of
-greatest interest. Both groups tended to perform worse for testing bands
-further away from their training conditions. The varied group had a
-slight advantage for bands 1000-1200 and 1200-1400, which were repeats
-from training for the varied participants, but novel for the constant
-participants.
+## Results
 
-```{r Test Performance,fig.height=8.5,fig.width=10.5}
-#| eval: false
-gbDev<-dtest %>% group_by(sbjCode,vbLabel,condit,throwCategory) %>% 
-  summarise(distMean=mean(distCapped),.groups = 'keep') %>% 
-  mutate(meanDevCapped=ifelse(distMean>900,900,distMean)) %>%
-  ggplot(aes(x=vbLabel,y=meanDevCapped,fill=condit))+
-  stat_summary(geom="bar",fun=mean,position=dodge,alpha=.7)+
-   stat_summary(geom="errorbar",fun.data=mean_se,alpha=.8,width=.5,position=dodge)+
- #ggbeeswarm::geom_quasirandom(aes(),dodge.width=.9,alpha=.15,size=.3)+
-  scale_y_continuous(breaks=round(seq(0,1000,by=200),2))+
-  ylab("Mean Absoulte Distance From Boundary")+xlab("Target Velocity Band") +
-scale_fill_discrete(name="Training Condition",labels=c("Constant","Varied"))+scale_color_discrete(guide="none")+
-  theme( plot.title=element_text(size=9),
-        axis.title.x=element_text(face="bold",size=11),
-        axis.title.y=element_text(face="bold",size=11),
-        axis.text.x = element_text(size = 7.5),
-        legend.position="top")+
-  labs(title="")#Testing - Mean Absolute Distance From Boundary
-leg=ggpubr::get_legend(gbDev)
-gbDev<- gbDev+theme(legend.position='none')
+### Testing Phase - No feedback.
 
-gbHit<-dtest %>% group_by(sbjCode,condit,vbLabel,expMode,testMode) %>% 
-  summarise(nHitsTest=sum(dist==0),n=n(),Percent_Hit=nHitsTest/n,.groups = 'keep') %>% 
-  ggplot(aes(x=vbLabel,y=Percent_Hit,fill=condit))+
-  stat_summary(geom="bar",fun=mean,position=dodge,alpha=.7)+
-   stat_summary(geom="errorbar",fun.data=mean_se,alpha=.8,width=.5,position=dodge)+
-# ggbeeswarm::geom_quasirandom(aes(),dodge.width=.9,alpha=.15,size=.3)+
-  ylab("% of throws with correct velocity")+xlab("Target Velocity Band") + 
-  scale_fill_discrete(guide='none')+scale_color_discrete(guide="none")+
-  theme( plot.title=element_text(size=9),
-        axis.title.x=element_text(face="bold",size=11),
-        axis.title.y=element_text(face="bold",size=11),
-        axis.text.x = element_text(size = 7.5),
-        legend.position="top")+
-  labs(title="")#Testing -% of hits
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
 
-gtitle="2C. Testing Performance"
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0)+theme(plot.margin = margin(0, 0, 0, 7))
-captionText=str_wrap("Figure 2C: Bands 100-300, 350-550 and 600-800 are novel extrapolations for both groups.
-Band 800-1000 was a training band for both groups.
-Bands 1000-1200, and 1200-1400 were trained for the varied group, and novel for the constant group.
-Right side figure displays mean deviation from correct velocity band (lower values correspond to better performance).
-Bottom Left displays the average % of trials where participants hit the wall with the correct velocity (higher values correspond got better performance).
-Error bars indicate standard error of the mean.
-",150)
-capt=ggdraw()+draw_label(captionText,fontface = 'italic',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
+#### Deviation From Target Band
 
-plot_grid(title,NULL,leg,NULL,gbDev,gbHit,capt,NULL,ncol=2,rel_heights=c(.1,.1,1,.1),rel_widths=c(1,1))
+Descriptive summaries testing deviation data are provided in @tbl-e1-test-nf-deviation and @fig-e1-test-dev.
+To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+```{=tex}
+\begin{equation}
+dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
+\end{equation}
+```
+
+```{r}
+#| label: fig-e1-test-dev
+#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
+#| include: true
+test |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target")
+```
+
+```{r}
+#| label: tbl-e1-bmm-dist
+#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+#| tbl-subcap: ["Constant Testing1 - Deviation", "Varied Testing - Deviation"]
+
+modelName <- "e1_testDistBand_RF_5K"
+e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=test,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+GetModelStats(e1_distBMM) |> kable(booktabs = TRUE,caption = paste("Coefficients"))
+
+e1_distBMM |> 
+  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
+          epred = TRUE, re_formula = NA) |> 
+  pairs() |> gather_emmeans_draws()  |> 
+   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
+   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
+   mutate(across(where(is.numeric), \(x) round(x, 2)),
+          pd=ifelse(value<0,1-pd,pd)) |> kable(booktabs = TRUE)
+# |> 
+#   kbl(caption="Contrasts")
+
+coef_details <- get_coef_details(e1_distBMM, "conditVaried")
 
@@
 
+The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X).
+Overall, the varied training group showed a larger deviation relative to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]).
+Deviation also depended on target velocity band, with lower bands showing less deviation.
+See @tbl-e1-bmm-dist for full model output.
+
+#### Discrimination between bands
+
+In addition to accuracy/deviation, we also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e1-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants on each testing trial.
+
+```{=tex}
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+```
+
+```{r}
+#| label: fig-e1-test-vx
+#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 9
+#| include: true
+test %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e1-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant", "Varied"]
+
+result <- test_summary_table(test, "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kable(booktabs = TRUE)
+result$varied |> kable(booktabs = TRUE)
+
+```
+
+```{r}
+#| label: tbl-e1-bmm-vx
+#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
+#| include: true
+#| eval: true
+e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+GetModelStats(e1_vxBMM ) |> kable(booktabs=T, caption="Fit to all 6 bands")
+
+cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e1_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
+
+modelName <- "e1_extrap_testVxBand"
+e1_extrap_VxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                  data=test |>
+                    filter(expMode=="test-Nf"),file=paste0(here::here("data/model_cache",modelName)),
+                  iter=5000,chains=4)
+GetModelStats(e1_extrap_VxBMM ) |> kable(booktabs=T, caption="Fit to 3 extrapolation bands")
+
+sc2 <- get_coef_details(e1_extrap_VxBMM, "bandInt")
+intCoef2 <- get_coef_details(e1_extrap_VxBMM, "conditVaried:bandInt")
+
+```
+
+See @tbl-e1-bmm-vx for the full model results.
+The estimated coefficient for training condition ($B$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
+Most relevant to the issue of discrimination is the slope on Velocity Band ($B$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
+Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
+The estimate for the interaction between slope and condition ($B$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition.
+This difference is depicted visually in @fig-e1-bmm-vx.@tbl-e1-slope-quartile shows the average slope coefficients for varied and constant participants separately for each quartile.
+The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination.
+Figure @fig-e1-bmm-bx2 shows the distributions of slope values for each participant, and the compares the probability density of slope coefficients between training conditions.
+@fig-e1-indv-slopes
+
+The second model, which focused solely on extrapolation bands, revealed similar patterns.
+The Velocity Band term ($B$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]) still demonstrates a high degree of discrimination ability.
+However, the posterior distribution for interaction term ($B$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\] ) does across over 0, suggesting that the evidence for decreased discrimination ability for the varied participants is not as strong when considering only the three extrapolation bands.
+
+```{r}
+#| label: fig-e1-bmm-vx
+#| fig-cap: Conditional effect of training condition and Band.
+Ribbons indicate 95% HDI.
+The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
+#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
+#| layout-ncol: 2
+#| include: true
+
+e1_vxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |> 
+  condEffects() +
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(test$vb), 
+                     limits = c(0, 1400))
+
+e1_extrap_VxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600))) |>
+  gather_emmeans_draws() |>
+  condEffects() +
+  scale_x_continuous(breaks = c(100, 350, 600), 
+                     labels = levels(test$vb)[1:3], 
+                     limits = c(0, 1000))
+
+```
+
+```{r}
+#| label: tbl-e1-slope-quartile
+#| tbl-cap: "Slope coefficients by quartile, per condition"
+
+new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")]))) |> 
+  dplyr::arrange(id,bandInt) |> 
+  mutate(condit_dummy = ifelse(condit == "Varied", 1, 0))
+
+indv_coefs <- as_tibble(coef(e1_vxBMM)$id, rownames="id")|> 
+  select(id, starts_with("Est")) |>
+  left_join(e1Sbjs, by=join_by(id) )
+
+fixed_effects <- e1_vxBMM |> 
+  spread_draws(`^b_.*`,regex=TRUE) |> arrange(.chain,.draw,.iteration)
+
+random_effects <- e1_vxBMM |> 
+  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
+  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
+  mutate(id = factor(id,levels=levels(test$id))) |> 
+  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)
+
+ indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
+  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
+  right_join(new_data_grid, by = join_by("id")) |> 
+  mutate(
+    Slope = bandInt_RF+b_bandInt,
+    Intercept= RF_Intercept + b_Intercept,
+    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
+    SlopeInt = Slope + (`b_conditVaried:bandInt`*condit_dummy)
+  )
+
+  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt, Intercept,b_Intercept,b_bandInt) |>
+  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
+    select(id,condit,Intercept,b_Intercept,starts_with("Slope"),b_bandInt, n) |>
+  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()
+
+  indvSlopes |> mutate(Condition=condit) |>  group_by(Condition) |> 
+    reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
+  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
+  group_by(Condition) |>
+  summarise(across(starts_with("Q"), list(mean = mean))) |> kable()
+
+```
+
+```{r}
+#| label: fig-e1-bmm-bx2
+#| fig-cap: Slope distributions between condition
+#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
+#| layout-ncol: 2
+#| fig-height: 9
+#| fig-width: 10
+#| include: true
+
+  indvSlopes |> ggplot(aes(y=rankSlope, x=SlopeInt,fill=condit,color=condit)) + 
+  geom_pointrange(aes(xmin=SlopeInt.lower , xmax=SlopeInt.upper)) + 
+  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)
+
+   ggplot(indvSlopes, aes(x = SlopeInt, color = condit)) + 
+  geom_density() + labs(x="Slope Coefficient",y="Density")
+
+```
+
+test
+
+```{r}
+#| label: fig-e1-indv-slopes
+#| fig-cap: Subset of Varied and Constant Participants with the smallest and largest estimated slope values.
+Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution.
+Colored points and intervals at each band represent the empirical median and 95% HDI.
+#| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
+#| fig-height: 6
+#| fig-width: 9
+
+nSbj <- 3
+indvDraws  |> indv_model_plot(indvSlopes, testAvg, SlopeInt,rank_variable=Slope,n_sbj=nSbj,"max")
+indvDraws |> indv_model_plot(indvSlopes, testAvg,SlopeInt, rank_variable=Slope,n_sbj=nSbj,"min")
+
+```
+
+# Experiment 2
+
+```{r setup2b, include=FALSE}
+testE2 <- readRDS(here::here("data/e2_08-21-23.rds")) |> filter(expMode2 == "Test") 
+e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
+testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+@fig-design-e2 illustrates the design of Experiment 2.
+The stages of the experiment (i.e.
+training, testing no-feedback, test with feedback), are identical to that of Experiment 1.
+The only change is that Experiment 2 participants train, and then test, on bands in the reverse order of Experiment 1 (i.e.
+training on the softer bands; and testing on the harder bands).
+
+```{dot}
+//| label: fig-design-e2
+//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
+//| fig-width: 6.0
+//| fig-height: 2.5
+//| fig-responsive: false
+//| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+
+```
+
+## E2 Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e2-test-nf-deviation and @fig-e2-test-dev. 
+To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+\begin{equation}
+dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: tbl-e2-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
+
+result <- test_summary_table(testE2, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kable()
+result$varied |> kable()
+# make kable table with smaller font size
+# result$constant |> kbl(caption="Constant Testing - Deviation",booktabs=T,escape=F) |> kable_styling(font_size = 7)
+```
+
+```{r}
+#| label: fig-e2-test-dev
+#| fig-cap: E2. Deviations from target band during testing without feedback stage. 
+testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target")
+```
+
+```{r}
+#| label: tbl-e2-bmm-dist
+#| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+#| tbl-subcap: ["Model fits", "Contrasts"]
+
+modelName <- "e2_testDistBand_RF_5K"
+e2_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=testE2,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+mp2 <- GetModelStats(e2_distBMM) |> kable(booktabs=T)
+mp2
+
+e2_distBMM |> 
+  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
+          epred = TRUE, re_formula = NA) |> 
+  pairs() |> gather_emmeans_draws()  |> 
+   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
+   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
+   mutate(across(where(is.numeric), \(x) round(x, 2)),
+          pd=ifelse(value<0,1-pd,pd)) |>
+   kable()
+
+coef_details <- get_coef_details(e2_distBMM, "conditVaried")
+
+```
+
+The model predicting absolute deviation showed a modest tendency for the varied training group to have lower deviation compared to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]),with 94% of the posterior distribution being less than 0.
+This suggests a potential benefit of training with variation, though the evidence is not definitive.
+
+#### Discrimination between Velocity Bands
+
+In addition to accuracy/deviation.
+We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e2-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
+
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: fig-e2-test-vx
+#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 9
+testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e2-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
+#| layout-ncol: 2
+
+result <- test_summary_table(testE2, "vx","X Velocity" ,mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kable()
+result$varied |> kable()
+
+```
+
+```{r}
+#| label: tbl-e2-bmm-vx
+#| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=testE2,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+mt3 <-GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T)
+mt3
+
+cd1 <- get_coef_details(e2_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e2_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
+```
+
+See @tbl-e2-bmm-vx for the full model results.
+
+When examining discrimination ability using the model predicting raw x-velocity, the results were less clear than those of the absolute deviation analysis.
+The slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]) indicates that participants showed good discrimination between bands overall.
+However, the interaction term suggested this effect was not modulated by training condition (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]) Thus, while varied training may provide some advantage for accuracy, both training conditions seem to have similar abilities to discriminate between velocity bands.
+
+```{r}
+#| label: fig-e2-bmm-vx
+#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI.
+
+e2_vxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |>
+  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+  ylab("Predicted X Velocity") + xlab("Band")+
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE2$vb), 
+                     limits = c(0, 1400)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+```
+
+# Experiment 3
+
+```{r setup3b, include=FALSE}
+testE3 <- readRDS(here::here("data/e3_08-21-23.rds")) |> filter(expMode2 == "Test") 
+e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
+testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+The major manipulation adjustment of experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the earlier experiments.
+Ordinal feedback informs participants whether a throw was too soft, too hard, or fell within the target velocity range.
+Experiment 3 participants were randomly assigned to both a training condition (Constant vs.
+Varied) and a Band Order condition (original order used in Experiment 1, or the Reverse order of Experiment 2).
+
+## Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+Note that these no-feedback testing trials are identical to those of Experiment 1 and 2, as the ordinal feedback only occurs during the training phase, and final testing phase, of Experiment 3.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e3-test-nf-deviation and @fig-e3-test-dev. 
+To model differences in accuracy between groups, we fit Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+```{r}
+#| label: tbl-e3-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
+
+resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+resultOrig$constant |> kable()
+resultOrig$varied |> kable()
+
+resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+resultRev$constant |> kable()
+resultRev$varied |> kable()
+
+```
+
+```{r}
+#| label: fig-e3-test-dev
+#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
+testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder)
+```
+
+```{r}
+#| label: tbl-e3-bmm-dist
+#| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+#| eval: true
+
+modelName <- "e3_testDistBand_RF_5K"
+e3_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=testE3,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+mp3 <- GetModelStats(e3_distBMM) |> kable(booktabs=T)
+mp3
+
+cd1 <- get_coef_details(e3_distBMM, "conditVaried")
+sc1 <- get_coef_details(e3_distBMM, "bandInt")
+intCoef1 <- get_coef_details(e3_distBMM, "conditVaried:bandInt")
+```
+
+The effect of training condition in Experiment 3 showed a similar pattern to Experiment 2, with the varied group tending to have lower deviation than the constant group (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0.
+
+```{r}
+#| label: fig-e3-bmm-dist
+#| fig-cap: e3. Conditioinal Effect of Training Condition and Band. Ribbon indicated 95% Credible Intervals.
+
+e3_distBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |>
+  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+    ylab("Predicted Deviation") + xlab("Velocity Band")+
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE3$vb), 
+                     limits = c(0, 1400)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+```
+
+#### Discrimination between Velocity Bands
+
+In addition to accuracy/deviation.
+We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e3-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
+
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: fig-e3-test-vx
+#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 12
+#| fig-height: 13
+
+# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
+# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
+
+testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
+  facet_wrap(bandOrder~condit,scale="free_x")
+
+# column: screen-inset-right
+
+```
+
+```{r}
+#| label: tbl-e3-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
+
+resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+resultOrig$constant |> kable()
+resultOrig$varied |> kable()
+
+resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+resultRev$constant |> kable()
+resultRev$varied |> kable()
+```
+
+```{r}
+#| label: tbl-e3-bmm-vx
+#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+#| eval: true
+e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+mt4 <-GetModelStats(e3_vxBMM ) |> kable(booktabs=T)
+mt4
+
+cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e3_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
+```
+
+See @tbl-e3-bmm-vx for the full model results.
+
+Slope estimates for experiment 3 suggest that participants were capable of distinguishing between velocity bands even when provided only ordinal feedback during training (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
+Unlike the previous two experiments, the posterior distribution for the interaction between condition and band was consistently positive, suggestive of superior discrimination for the varied participants
+β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\].
+
 # Modeling
 
-In project 1, we applied model-based techniques to quantify and control
-for the similarity between training and testing experience, which in
-turn enabled us to account for the difference between varied and
-constant training via an extended version of a similarity based
-generalization model. In project 2, we will go a step further,
-implementing a full process model capable of both 1) producing novel
-responses and 2) modeling behavior in both the learning and testing
-stages of the experiment. For this purpose, we will apply the
-associative learning model (ALM) and the EXAM model of function learning
-(DeLosh 1997). ALM is a simple connectionist learning model which
-closely resembles Kruschke's ALCOVE model (Kruscke 1992), with
-modifications to allow for the generation of continuous responses.
+In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning (DeLosh 1997).
+ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model (Kruscke 1992), with modifications to allow for the generation of continuous responses.
 
@@
 
-Delosh et al. (1997) introduced the associative learning model (ALM), a
-connectionist model within the popular class of radial-basis networks.
-ALM was inspired by, and closely resembles Kruschke's influential ALCOVE
-model of categorization (Kruscke 1992).
+@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks.
+ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].
 
-ALM is a localist neural network model, with each input node corresponding to a
-particular stimulus, and each output node corresponding to a particular response
-value. The units in the input layer activate as a function of their Gaussian
-similarity to the input stimulus. So, for example, an input stimulus of value 55
-would induce maximal activation of the input unit tuned to 55. Depending on
-thevalue of the generalization parameter, the nearby units (e.g. 54 and 56; 53
-and 57) may also activate to some degree. ALM is structured with input and
-output nodes that correspond to regions of the stimulus space, and response
-space, respectively. The units in the input layer activate as a function of
-their similarity to a presented stimulus. As was the case with the
-exemplar-based models, similarity in ALM is exponentially decaying function of
-distance. The input layer is fully connected to the output layer, and the
-activation for any particular output node is simply the weighted sum of the
-connection weights between that node and the input activations. The network then
-produces a response by taking the weighted average of the output units (recall
-that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit
-as a function of its distance from the ideal level of activation necessary to
-produce the correct response. The connection weights between input and output
-units are then updated via the standard delta learning rule, where the magnitude
-of weight changes are controlled by a learning rate
-parameter.
+ALM is a localist neural network model, with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
+The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
+So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
+Depending on thevalue of the generalization parameter, the nearby units (e.g.
+54 and 56; 53 and 57) may also activate to some degree.
+ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
+The units in the input layer activate as a function of their similarity to a presented stimulus.
+As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
+The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
+The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
+During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
+The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
 
-See Table 2A for a full specification of the equations that define ALM and EXAM.
+See  for a full specification of the equations that define ALM and EXAM.
 
-## Model Equations
+{{< pagebreak >}}
 
-```{r ALM_Table }
-#| results: 'asis'
+## Model Table
+### ALM Activation & Response
+| Step | Equation | Description |
+|------|----------|-------------|
+| **ALM Activation & Response**  |           |
+| Input Activation | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$ | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.
+|
+| Output Activation                 | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$ | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.   |
+| Output Probability                | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$ | Each output node has associated response, $Y_j$.
+The probability of response $Y_j$ is determined by the ratio of output activations.
+|
+| Mean Output                       | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$   | The response to stimulus x is the weighted average of the response probabilities. |
+| **ALM Learning**                  |                                                                                                                                                          |
+| Feedback Activation               | $f_j(Z) = e^{-c(Z-Y_j)^2}$                  | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response.
+|
+| Update Weights                    | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$    | Delta rule to update weights.
+Magnitude of weight changes controlled by learning rate parameter alpha.
+|
+| **EXAM**                          |                                                                                                                                                          |
+| Extrapolation                     | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$ | Novel test stimulus X activates input nodes associated with trained stimuli.     |
+|                                   | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)    |
 
-text_tbl <- data.frame(
-    'Step'=c("Input Activation","Output Activation","Output Probability","Mean Output","Feedback Activation","Update Weights","Extrapolation",""),
-    'Equation' = c("$a_i$(X) = $\\frac{e^{-c \\cdot (X-X_i)^2}}{ \\sum_{k=1}^Me^{-c \\cdot (X-X_i)^2}}$", 
-                   '$O_j$(X) = $\\sum_{k=1}^Mw_{ji} \\cdot a_i(X)$',
-                   '$P[Y_j | X] = \\frac{O_i(X)}{\\sum_{k=1}^Mo_k(X)}$',
-                   "$m(x) = \\sum_{j=1}^LY_j \\cdot \\bigg[\\frac{O_j(X)}{\\sum_{k=1}^Lo_k(X)}\\bigg]$",
-                   "$f_j(Z)=e^{-c\\cdot(Z-Y_j)^2}$",
-                   "$w_{ji}(t+1)=w_{ji}(t)+\\alpha \\cdot {f_i(Z(t))-O_j(X(t))} \\cdot a_i(X(t))$",
-                   "$P[X_i|X] = \\frac{a_i(X)}{\\sum_{k=1}^Ma_k(X)}$",
-                   "$E[Y|X_i]=m(X_i) + \\bigg[\\frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1} - X_{i-1}} \\bigg] \\cdot[X-X_i]$"),
-
-    'Description'= c(
-            "Activation of each input node, $X_i$, is a function of the Gaussian similarity between the node value and stimulus X. ",
-            "Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights",
-            "Each output node has associated response, $Y_j$. The probability of response $Y_j$ is determined by the ratio of output activations",
-            "The response to stimulus x is the weighted average of the response probabilities",
-            "After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response  ",
-            "Delta rule to update weights. Magnitude of weight changes controlled by learning rate parameter alpha.",
-            "Novel test stimulus X activates input nodes associated with trained stimuli",
-            "Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)")
-)
-text_tbl$Step=cell_spec(text_tbl$Step,font_size=12)
-text_tbl$Equation=cell_spec(text_tbl$Equation,font_size=18)
-almTable=kable(text_tbl, 'html', 
-  booktabs=T, escape = F, align='l',
-  caption = '<span style = "color:black;"><center><strong>Table 1: ALM & EXAM Equations</strong></center></span>',
-  col.names=c("","Equation","Description")) %>%
-  kable_styling(position="left",bootstrap_options = c("hover")) %>%
-  column_spec(1, bold = F,border_right=T) %>%
-  column_spec(2, width = '10cm')%>%
-  column_spec(3, width = '15cm') %>%
-  pack_rows("ALM Activation & Response",1,4,bold=FALSE,italic=TRUE) %>%
-  pack_rows("ALM Learning",5,6,bold=FALSE,italic=TRUE) %>%
-  pack_rows("EXAM",7,8,bold=FALSE,italic=TRUE)
-  #save_kable(file="almTable.html",self_contained=T)
-cat(almTable)
-
-```
+{{< pagebreak >}}
 
@@
 
-Following the procedure used by McDaniel & Busemeyer (2009), we will
-assess the ability of both ALM and EXAM to account for the empirical
-data when fitting the models to 1) only the training data, and 2) both
-training and testing data. Models will be fit directly to the trial by
-trial data of each individual participants, both by minimizing the
-root-mean squared deviation (RMSE), and by maximizing log likelihood. Because ALM
-has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also
-fit the extended EXAM version of the model, which operates identically to ALM during training, 
-but includes a linear extrapolation mechanism for generating novel responses during testing. 
-[@albaretDifferentialEffectsTask1998]
-\
-\
-\
-\
-\
-\
-\
+Following the procedure used by @mcdanielPredictingTransferPerformance2009, we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data.
+Models will be fit directly to the trial by trial data of each individual participants, both by minimizing the root-mean squared deviation (RMSE), and by maximizing log likelihood.
+Because ALM has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also fit the extended EXAM version of the model, which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.
 
 # References
+# References 
 <div id="refs"></div>

### 2023-10-28 Manuscript/igas_e1.qmd
add supplementals

--- 2023-10-19 Manuscript/manuscript.qmd
@@
 toc: false
-toc-depth: 3
-toc-location: body
+# toc-depth: 3
+# toc-location: body
 execute: 
@@
 :::
+
+::: {.content-visible when-format="docx"}
+
+{{< include pre_sections/pre_docx.qmd >}}
+
+:::
+
 {{< pagebreak >}}
@@
 These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
+
+{{< pagebreak >}}
 
@@
 
-# Literature Review
-
-{{< include ../Introduction.qmd >}}
-
-```{r setup}
-here::set_here(path='..')
-source(here::here("Functions", "packages.R"))
-
-if (is.null(knitr::pandoc_to())) {
-  fmt_out <- "interactive"
-} else {
-  fmt_out <- knitr::pandoc_to()
-}
-
-knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
-                      warning = FALSE, message = FALSE, eval=TRUE)
-
-knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
-                      fig.width = 6, fig.height = (6 * 0.618),
-                      out.width = "100%", collapse = TRUE)
-# 
-options(digits = 3, width = 120,
-        dplyr.summarise.inform = FALSE,
-        knitr.kable.NA = "")
-
-```
-
-```{r}
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-
-# load the processed data from experiment 1 and 2
-
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-options(contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-```
-
-# Project 1
-
-## Abstract
-
-Exposing learners to variability during training has been demonstrated
-to improve performance in subsequent transfer testing. Such variability
-benefits are often accounted for by assuming that learners are
-developing some general task schema or structure. However much of this
-research has neglected to account for differences in similarity between
-varied and constant training conditions. In a between-groups
-manipulation, we trained participants on a simple projectile launching
-task, with either varied or constant conditions. We replicate previous
-findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to
-account for the benefits of variation, but, if the model is adjusted to
-assume that varied learners are tuned towards a broader generalization
-gradient, then a similarity-based model is sufficient to explain the
-observed benefits of variation. Our results therefore suggest that some
-variability benefits can be accommodated within instance-based models
-without positing the learning of some schemata or structure.
-
-## Introduction
-
-The past century of research on human learning has produced ample
-evidence that although learners can improve at almost any task, such
-improvements are often specific to the trained task, with unreliable or
-even nonexistent transfer to novel tasks or conditions
-[@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993]. Such
-transfer challenges are of noteworthy practical relevance, given that
-educators, trainers, and rehabilitators typically intend for their
-students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that
-influence transfer, and to develop cognitive models that can predict
-when transfer is likely to occur. The factor of interest to the present
-investigation is variation during training. Our experiments add to the
-longstanding empirical investigation of the controversial relationship
-between training variation, and subsequent transfer. We also offer a
-novel explanation for such results in the form of an instance-based
-model that accounts for the benefits of variation in simple terms of
-psychological similarity. We first review the relevant concepts and
-literature.
-
-### Similarity and instance-based approaches to transfer of learning
-
-Notions of similarity have long played a central role in many prominent
-models of generalization of learning, as well as in the longstanding
-theoretical issue of whether learners abstract an aggregate, summary
-representation, or if they simply store individual instances. Early
-models of learning often assumed that discrete experiences with some
-task or category were not stored individually in memory, but instead
-promoted the formation of a summary representation, often referred to as
-a prototype or schema, and that exposure to novel examples would then
-prompt the retrieval of whichever preexisting prototype was most similar
-[@posnerGenesisAbstractIdeas1968]. Prototype
-models were later challenged by the success of instance-based or
-exemplar models -- which were shown to provide an account of
-generalization as good or better than prototype models, with the
-advantage of not assuming the explicit construction of an internal
-prototype [@estesClassificationCognition1994;
-@hintzmanMINERVASimulationModel1984;
-@medinContextTheoryClassification1978;
-@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a
-task as a separate instance/exemplar/trace, and that each encoded trace
-is in turn compared against novel stimuli. As the number of stored
-instances increases, so does the likelihood that some previously stored
-instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks
-if they are sufficiently similar, thus suggesting that the process of
-computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological
-distance between instances or categories, has provided a successful
-account of generalization across numerous tasks and domains. In an
-influential study demonstrating an ordinal similarity effect,
-experimenters employed a numerosity judgment task in which participants
-quickly report the number of dots flashed on a screen. Performance (in
-terms of response times to new patterns) on novel dot configurations
-varied as an inverse function of their similarity to previously trained
-dot configurations @palmeriExemplarSimilarityDevelopment1997. That is, performance was better on
-novel configurations moderately similar to trained configurations than
-to configurations with low-similarity, and also better on low-similarity
-configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for
-performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017; @crumpEpisodicContributionsSequential2010] trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following
-training, typing speed was tested on previously experienced words
-composed of previously experienced letters; novel words composed of
-letters from the trained letter set; and novel words composed of letters
-from an untrained letter set. Consistent with an instance-based account,
-transfer performance was graded such that participants were fastest at
-typing the words they had previously trained on, followed by novel words
-composed of letters they had trained on, and slowest performance for new
-words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of
-similarity between previous and new experiences, a largely separate body
-of research has focused on improving transfer by manipulating
-characteristics of the initial training stage. Such characteristics have
-included training difficulty, spacing, temporal order, feedback
-schedules, and the primary focus of the current work -- variability of
-training examples.
-
-Research on the effects of varied training typically compares
-participants trained under constant, or minimal variability conditions
-to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015]. Varied training has been shown to influence
-learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968],
-complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory
-extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice
-identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
-sports training  [@greenPracticeVariabilityTransfer1995; @greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
-on a complex video game [@seowTransferEffectsVaried2019].
-
-Training variation has received a particularly large amount of attention
-within the domain of visuomotor skill learning. Much of this research
-has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a
-schema-based account of motor learning as an attempt to address the
-longstanding problem of how novel movements are produced. According to
-Schema Theory, learners possess general motor programs for classes of
-movements (e.g. throwing a ball with an underhand movement), as well as
-schema rules that determine how a motor program is parameterized or
-scaled for a particular movement. Schema theory predicts that varied
-training results in the formation of a more general schema-rule, which
-can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the
-transfer performance of a constant-trained group against that of a
-varied-trained group. Both groups train on the same task, but the varied
-group practices from multiple levels of a task-relevant dimension that
-remains invariant for the constant group. For example, investigators
-might train two groups of participants to throw a projectile at a
-target, with a constant group that throws from a single location, and a
-varied group that throws from multiple locations. Both groups are then
-tested from novel locations. Empirically observed benefits of the
-varied-trained group are then attributed to the variation they received
-during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically
-thought to be mediated by the development of a more general schema for
-the throwing motion.
-
-Of course, the relationship between training variability and transfer is
-unlikely to be a simple function wherein increased variation is always
-beneficial. Numerous studies have found null, or in some cases negative
-effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the
-benefits of variability may depend on additional factors such as prior
-task experience, the order of training trials, or the type of transfer
-being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-### Issues with Previous Research
-
-Although the benefits of training variation in visuomotor skill learning
-have been observed many times, null findings have also been repeatedly
-found, leading some researchers to question the veracity of the
-variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of
-training variability, of the sort described above, often fail to control
-for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of
-freedom (e.g. projectile throwing tasks where participants control the x
-and y velocity of the projectile), varied groups are likely to
-experience a wider range of the task space over the course of their
-training (e.g. more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring
-that the training location(s) of the varied and constant groups are an
-equal distance away from the eventual transfer locations, such that
-their training throws are, on average, equally similar to throws that
-would lead to good performance at the transfer locations. However, even
-this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer. Given that psychological
-similarity is typically best described as either a Gaussian or
-exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the
-most similar training instances could have a disproportionate impact on
-generalization to transfer conditions, even if the average distance
-between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that
-drops off as a Gaussian function of distance from training, as compared
-to a linear drop-off.
-
-```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
-
-p=2
-c<- .0002
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
-  group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=.97,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=.97,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
-
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
-
-```
-
-In addition to largely overlooking the potential for non-linear
-generalization to confound interpretations of training manipulations,
-the visuomotor skill learning literature also rarely considers
-alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures,
-instance or exemplar-based models have accounted for human behavior
-across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a]. As mentioned above, instance based accounts have been shown to perform well on a
-variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little
-attention within the subdomain of visuomotor skill learning focused on
-the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of
-varied training can be accounted for by between-group differences in
-similarity between training and testing throws. We first attempt to
-replicate previous work finding an advantage of varied training over
-constant training in a projectile launching task. We then examine the
-extent to which this advantage can be explained by an instance-based
-similarity model.
-
-## Experiment 1
-
-### Methods
-
-#### Sample Size Estimation
-
-To obtain an independent estimate of effect size, we identified previous
-investigations which included between-subjects contrasts of varied and
-constant conditions following training on an accuracy based projectile
-launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
-2009) was then used to determine that a power of 80% requires a sample
-size of at least 23 participants per condition. All experiments reported
-in the present manuscript exceed this minimum number of participants per
-condition.
-
-#### Participants
-
-Participants were recruited from an undergraduate population that is 63%
-female and consists almost entirely of individuals aged 18-22 years. A
-total of 110 Indiana University psychology students participated in
-Experiment 1. We subsequently excluded 34 participants poor performance
-at one of the dependent measures of the task (2.5-3 standard deviations
-worse than the median subject at the task) or for displaying a pattern
-of responses that was clearly indicative of a lack of engagement with
-the task (e.g. simply dropping the ball on each trial rather than
-throwing it at the target), or for reporting that they completed the
-experiment on a phone or tablet device, despite the instructions not to
-use one of these devices. A total of 74 participants were retained for
-the final analyses, 35 in the varied group and 39 in the constant group.
-
-#### Task
-
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-igasTask displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-![The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square](Assets/methodsFig1.png){#fig-igasTask}
-
-### Results
-
-#### Data Processing and Statistical Packages
-
-To prepare the data, we first removed trials that were not easily
-interpretable as performance indicators in our task. Removed trials
-included: 1) those in which participants dragged the ball outside of the
-orange starting box without releasing it, 2) trials in which
-participants clicked on the ball, and then immediately released it,
-causing the ball to drop straight down, 3) outlier trials in which the
-ball was thrown more than 2.5 standard deviations further than the
-average throw (calculated separately for each throwing position), and 4)
-trials in which the ball struck the barrier. The primary measure of
-performance used in all analyses was the absolute distance away from the
-center of the target. The absolute distance was calculated on every
-trial, and then averaged within each subject to yield a single
-performance score, for each position. A consistent pattern across
-training and testing phases in both experiments was for participants to
-perform worse from throwing positions further away from the target -- a
-pattern which we refer to as the difficulty of the positions. However,
-there were no interactions between throwing position and training
-conditions, allowing us to collapse across positions in cases where
-contrasts for specific positions were not of interest. All data
-processing and statistical analyses were performed in R version 4.03 (R
-Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021)****.
-
-#### Training Phase
-
-@fig-IGAS-Training1 below shows aggregate training performance binned into three
-stages representing the beginning, middle, and end of the training
-phase. Because the two conditions trained from target distances that
-were not equally difficult, it was not possible to directly compare
-performance between conditions in the training phase. Our focus for the
-training data analysis was instead to establish that participants did
-improve their performance over the course of training, and to examine
-whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided
-in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and
-condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
-such that performance improved over the course of training There was no
-significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
-and no significant interaction between condition and training stage,
-F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
-
-```{r}
-#| label: fig-IGAS-Training1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
-
-```
-
-### Testing Phase
-
-In Experiment 1, a single constant-trained group was compared against a
-single varied-trained group. At the transfer phase, all participants
-were tested from 3 positions: 1) the positions(s) from their own
-training, 2) the training position(s) of the other group, and 3) a
-position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs. constant) as a
-between-subject factor and throwing location as a within-subject
-variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\<.001, η2G = .23. The effect of training condition was significant
-F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
-between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS-Testing1
-#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-IGAS-Table1
-#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- test=test[,1:3]
-
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>%   
-  kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-### Discussion
-
-In Experiment 1, we found that varied training resulted in superior
-testing performance than constant training, from both a position novel
-to both groups, and from the position at which the constant group was
-trained, which was novel to the varied condition. The superiority of
-varied training over constant training even at the constant training
-position is of particular note, given that testing at this position
-should have been highly similar for participants in the constant
-condition. It should also be noted, though, that testing at the constant
-trained position is not exactly identical to training from that
-position, given that the context of testing is different in several ways
-from that of training, such as the testing trials from the different
-positions being intermixed, as well as a simple change in context as a
-function of time. Such contextual differences will be further considered
-in the General Discussion.
-
-In addition to the variation of throwing position during training, the
-participants in the varied condition of Experiment 1 also received
-training practice from the closest/easiest position, as well as from the
-furthest/most difficult position that would later be encountered by all
-participants during testing. The varied condition also had the potential
-advantage of interpolating both of the novel positions from which they
-would later be tested. Experiment 2 thus sought to address these issues
-by comparing a varied condition to multiple constant conditions.
-
-## Experiment 2
-
-In Experiment 2, we sought to replicate our findings from Experiment 1
-with a new sample of participants, while also addressing the possibility
-of the pattern of results in Experiment 1 being explained by some
-idiosyncrasy of the particular training location of the constant group
-relative to the varied group. To this end, Experiment 2 employed the
-same basic procedure as Experiment 1, but was designed with six separate
-constant groups each trained from one of six different locations (400,
-500, 625, 675, 800, or 900), and a varied group trained from two
-locations (500 and 800). Participants in all seven groups were then
-tested from each of the 6 unique positions.
-
-## Methods
-
-### Participants
-
-A total of 306 Indiana University psychology students participated in
-Experiment 2, which was also conducted online. As was the case in
-experiment 1, the undergraduate population from which we recruited
-participants was 63% female and primarily composed of 18--22-year-old
-individuals. Using the same procedure as experiment 1, we excluded 98
-participants for exceptionally poor performance at one of the dependent
-measures of the task, or for displaying a pattern of responses
-indicative of a lack of engagement with the task. A total of 208
-participants were included in the final analyses with 31 in the varied
-group and 32, 28, 37, 25, 29, 26 participants in the constant groups
-training from location 400, 500, 625, 675, 800, and 900, respectively.
-All participants were compensated with course credit.
-
-### Task and Procedure
-
-The task of Experiment 2 was identical to that of Experiment 1, in all
-but some minor adjustments to the height of the barrier, and the
-relative distance between the barrier and the target. Additionally, the
-intermittent testing trials featured in experiment 1 were not utilized
-in experiment 2, and all training and testing trials were presented with
-feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
-
-The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the
-same position for the constant groups and split evenly (70 trials each -
-randomized) for the varied group. In the testing phase, participants
-completed 30 trials from each of the six locations that had been used
-separately across each of the constant groups during training. Each of
-the constant groups thus experience one trained location and five novel
-throwing locations in the testing phase, while the varied group
-experiences 2 previously trained, and 4 novel locations.
-
-## Results
-
-#### Data Processing and Statistical Packages
-
-After confirming that condition and throwing position did not have any
-significant interactions, we standardized performance within each
-position, and then average across position to yield a single performance
-measure per participant. This standardization did not influence our
-pattern of results. As in experiment 1, we performed type III ANOVA's
-due to our unbalanced design, however the pattern of results presented
-below is not altered if type 1 or type III tests are used instead. The
-statistical software for the primary analyses was the same as for
-experiment 1. Individual learning rates in the testing phase, compared
-between groups in the supplementary analyses, were fit using the TEfit
-package in R [@cochraneTEfitsNonlinearRegression2020].
-
-#### Training Phase
-
-The different training conditions trained from positions that were not
-equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. @fig-e2train depicts the training
-performance of the varied group alongside that of the aggregate of the
-six constant groups (5a), and each of the 6 separate constant groups
-(5b). An ANOVA comparison with training stage (beginning, middle, end)
-as a within-group factor and group (the varied condition vs. the 6
-constant conditions collapsed together) as a between-subject factor
-revealed no significant effect of group on training performance,
-F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
-stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
-interaction between group and training stage, F(2,412)=.489 p=.61,
-$\eta^{2}_G$ \<.01. We also tested for a difference in training
-performance between the varied group and the two constant groups that
-trained matching throwing positions (i.e., the constant groups training
-from position 500, and position 800). The results of our ANOVA on this
-limited dataset mirrors that of the full-group analysis, with no
-significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
-significant effect of training stage F(2,172)=56.29, p\<.001,
-$\eta^{2}_G$ =.11, and no significant interaction between group and
-training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
-
-```{r}
-
-e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
-
-exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
-
-exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
-
-exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
-
-exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% convert_as_factor(novel,extrapolate)
-
-transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
-
-# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
-# novelAll <- novelAll %>% group_by(positionX) %>%
-#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
-novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
-
-constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
-variedTest <- transfer %>% filter(condit==7) # only varied testing
-variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
-
-variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
-constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
-variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
-
-exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-```
-
-```{r}
-#| label: fig-e2train
-#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
-On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-#| fig.width: 11
-#| fig.height: 10
-
-### New - 3 stage
-e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
-  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
-  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
-
-e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
-  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
-
-#plot_grid(e2train1,e2train2,ncol=1)
-
-e2train1 / e2train2
-
-```
-
-#### Testing Phase
-
-In Experiment 2, a single varied condition (trained from two positions,
-500 and 800), was compared against six separate constant groups (trained
-from a single position, 400, 500, 625, 675, 800 or 900). For the testing
-phase, all participants were tested from all six positions, four of
-which were novel for the varied condition, and five of which were novel
-for each of the constant groups. For a general comparison, we took the
-absolute deviations for each throwing position and computed standardized
-scores across all participants, and then averaged across throwing
-position. The six constant groups were then collapsed together allowing
-us to make a simple comparison between training conditions (constant vs.
-varied). A type III between-subjects ANOVA was performed, yielding a
-significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
-=.02. Descriptive statistics for each condition are shown in table 2. In
-@fig-e2testa visualizes the consistent advantage of the varied condition
-over the constant groups across the testing positions. @fig-e2testa shows
-performance between the varied condition and the individual constant
-groups.
-
-```{r}
-#| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 9
-
-# manuscript plot
-e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)+
-  ggtitle("A")
-
-e2test2<-exp2.Test7 %>% 
-  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
-  facet_wrap(~ThrowPosition4)+
-  ylab("Mean Distance From Center Of Target")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
-
-e2test1 / e2test2
-
-```
-
-\
-
-```{r}
-#| label: tbl-e2table1
-#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-
-tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab2=tab2[,1:3]
-
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
-.02 .
-
-```{r}
-#| label: tbl-e2table2
-#| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-
-sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
- tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
- tab3 = tab3 %>% 
-   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab3=tab3[,1:3]
-
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
-
-Finally, corresponding to the comparison of position 760 from experiment
-1, we compared the test performance of the varied group against the
-constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis
-omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). @fig-e2test1 displays
-the particular subset of comparisons utilized for this analysis. Again,
-we standardized performance within each position before performing the
-analyses on the aggregated data. In this case, the effect of condition
-did not reach statistical significance F(1,149)=3.14, p=.079,
-$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
-
-```{r}
-#| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-
-sum.variedVsNovelIden <- variedVsNovelIden  %>%
-  group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
-
-e2Test2
-
-```
-
-\
-
-```{r}
-#| label: tbl-e2tab3
-#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-
-tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
-tab4=tab4 %>% group_by(Condition) %>% 
-   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab4=tab4[,1:3]
-
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-### Discussion
-
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
-
-### Computational Model
-
-Controlling for the similarity between training and testing The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace1
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace1, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
-
-```{r}
-#| label: fig-taskSpace1
-#| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig.height: 10
-#| fig.width: 11
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
-  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
-
-ss / fs
-
-```
-
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
-
-**Equation 1:** \[ Similarity\_{I,J} = \sum*{i = I}*\sum{j=J}
-e^{-c^\cdot dp\_{i,j}} \]
-
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-
-A simple linear regression revealed that these similarity scores were
-significantly predictive of performance in the transfer stage, t
-=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
-training throws and solution spaces for each of the test locations
-resulted in better performance. We then repeated the group comparisons
-above while including similarity as a covariate in the model. Comparing
-the varied and constant groups in testing performance from all testing
-positions yielded a significant effect of similarity, F(1, 205)=85.66,
-p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
-(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
-group comparison limited to only novel locations for the varied group
-pit against trained location for the constant group resulted in a
-significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
-=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
-=.07. For all comparisons, the pattern of results was consistent with
-the initial findings from experiment 2, with the varied group still
-performing significantly better than the constant group.
-
-#### Fitting model parameters separately by group
-
-To directly control for similarity in Experiment 2, we developed a
-model-based measure of the similarity between training throws and
-testing conditions. This similarity measure was a significant predictor
-of testing performance, e.g., participants whose training throws were
-more similar to throws that resulted in target hits from the testing
-positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level
-benefits of varied training, which remained significant in our linear
-model predicting testing performance after similarity was added to the
-model. However, previous research has suggested that participants may
-differ in their level of generalization as a function of prior
-experience, and that such differences in generalization gradients can be
-captured by fitting the generalization parameter of an instance-based
-model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
-will increase when a rational agent encounters a wider variety of
-examples. Following these leads, we assume that in addition to learning
-the task itself, participants are also adjusting how generalizable their
-experience should be. Varied versus constant participants may be
-expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the
-instance-based model (in the present case, the c parameter) can be
-allowed to vary between the two groups to reflect the tendency of
-learners to adaptively tune the extent of their generalization. One
-specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
-variable, as with the variable training condition, then one might infer
-that future test situations will also be variable, in which case a low
-value of c will allow better generalization because generalization will
-drop off slowly with training-to-testing distance. Conversely, if one's
-training experience has little variability, as found in the constant
-training conditions, then one might adopt a high value of c so that
-generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based
-model of similarity fit against a modified model which separately fits
-the generalization parameter, c, to varied and constant participants. To
-perform this parameter fitting, we used the optim function in R, and fit
-the model to find the c value(s) that maximized the correlation between
-similarity and testing performance.
-
-Both models generate distinct similarity values between training and
-testing locations. Much like the analyses in Experiment 2, these
-similarity values are regressed against testing performance in models of
-the form shown below. As was the case previously, testing performance is
-defined as the mean absolute distance from the center of the target
-(with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\<.01). Of greater interest is the
-difference between linear model 2, in which similarity is computed from
-a single c value fit from all participants (Similarity1c), with linear
-model 4, which fits the c parameter separately between groups
-(Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\<.01), with the varied
-group still performing significantly better. However, in linear model 4
-the addition of the Similarity2c predictor results in the effect of
-training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs. constant training is accounted for by the
-Similarity2c predictor. Next, to further establish a difference between
-the models, we performed nested model comparisons using ANOVA, to see if
-the addition of the training group parameter led to a significant
-improvement in model performance. In the first comparison, ANOVA(Linear
-Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear
-Model 4) found no improvement in model performance with the addition of
-the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the
-adjusted Similarity2c model had more predictive power than those
-generated from the original Similarity1c model. Using the BIC function
-in R, we compared BIC values between linear model 1 (BIC=14604.00) and
-linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
-a modest advantage for predicting performance using a similarity measure
-computed with two c values over similarity computed with a single c
-value. When fit with separate c values, the best fitting c parameters
-for the model consistently optimized such that the c value for the
-varied group (c=.00008) was smaller in magnitude than the c value for
-the constant group(c= .00011). Recall that similarity decreases as a
-Gaussian function of distance (equation 1 above), and a smaller value of
-c will result in a more gradual drop-off in similarity as the distance
-between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which
-assumes equivalent generalization gradients between constant and varied
-trained participants is unable to account for the extent of benefits of
-varied over constant training observed at testing. The evidence for this
-in the comparative model fits is that when a varied/constant dummy-coded
-variable for condition is explicitly added to the model, the variable
-adds a significant contribution to the prediction of test performance,
-with the variable condition yielding better performance than the
-constant conditions. However, if the instance-based generalization model
-is modified to assume that the training groups can differ in the
-steepness of their generalization gradient, by incorporating a separate
-generalization parameter for each group, then the instance-based model
-can account for our experimental results without explicitly taking
-training group into account. Henceforth this model will be referred to
-as the Instance-based Generalization with Adaptive Similarity (IGAS)
-model.
-
-### General Discussion
-
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy-Model2 we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model2
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$.
-For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
-The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
-#| fig.width: 11
-#| fig.height: 10
-
-#
-
-p=2
-c<- .000002
-
-trainingTestingDifference=2000;
-cvaried=.00002
-cconstant=.0005
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
-                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
-                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
-                            ) %>% 
-  group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
-
-#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
-
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
-ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
-ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
-ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
-# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
-
-gtitle="Figure 9."
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-
-```
-
-As mentioned above, the idea that learners flexibly adjust their
-generalization gradient based on prior experience does have precedent in
-the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed
-that a simple manipulation of background knowledge during a
-categorization test resulted in participants generalizing their training
-experience more or less broadly, and moreover that such a pattern could
-be captured by allowing the generalization parameter of an
-instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted
-for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006]. However, to the best of our
-knowledge, IGAS is the first instance-based similarity model that has
-been put forward to account for the effect of varied training in a
-visuomotor skill task. Although IGAS was inspired by work in the domain
-of category learning, its success in a distinct domain may not be
-surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common
-principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning
-implementations of instance-based models in several ways. One such
-difference is the nature of the training instances that are assumed to
-be stored. In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define
-a category item (e.g. size/color/shape). Rather than defining instances
-in terms of what stimuli learners experience, our approach assumes that
-stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw. An advantage of many motor learning
-tasks is the relative ease with which task execution variables can be
-directly measured (e.g. movement force, velocity, angle, posture) in
-addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of
-course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work
--- though as described in the introduction there is some evidence in
-support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly
-noteworthy instance-based model of sensory-motor behavior is the
-Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995]. Knowledge II explicitly defines instances as
-postures (joint combinations), and is thus far more detailed than IGAS
-in regards to the contents of stored instances. Knowledge II also
-differs from IGAS in that learning is accounted for by both the
-retrieval of stored postures, and the generation of novel postures via
-the modification of retrieved postures. A promising avenue for future
-research would be to combine the adaptive similarity mechanism of IGAS
-with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
-lighting up consecutively, and attempt to time a button press with the
-onset of the final lamp. The design consisted of four separate constant
-groups, each training from a single lighting velocity, and a single
-varied group training with all four of the lighting velocities used by
-the individual constant groups. Participants were then split into four
-separate testing conditions, each of which were tested from a single
-novel lighting velocity of varying distance from the training
-conditions. The result of primary interest was that all participants
-performed worse as the distance between training and testing velocity
-increased -- a typical generalization decrement. However, varied
-participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in
-a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are
-similar to our own, our work is novel in that we account for our results
-with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their
-separate constant groups together may result in similarity confounds
-between varied and constant conditions that leaves their study open to
-methodological criticisms, especially in light of related work which
-demonstrated that the extent to which varied training may be beneficial
-can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
-similarity.
-
-## Limitations
-
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
-
-## Conclusion
-
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
-
-# Project 2
-
-```{r}
-test <- readRDS(here::here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
-#options(brms.backend="cmdstanr",mc.cores=4)
-e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
-testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
-  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
-```
-
-# Introduction
-
-In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
-In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations.
-Extrapolation has long been a focus of the literature on function learning [@brehmerHypothesesRelationsScaled1974; @carrollFunctionalLearningLearning1963].
-Central questions of the function learning literature have included the relative difficulties of learning various functional forms (e.g.
-linear vs.bilinear vs.
-quadratic), and the relative effectiveness of rule-based vs.
-association-based exemplar models vs.
-various hybrid models [@bottNonmonotonicExtrapolationFunction2004; @deloshExtrapolationSineQua1997; @jonesActiveFunctionLearning2018; @kalishPopulationLinearExperts2004; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
-However the issue of training variation has received surprisingly little attention in this area.
-
-# Methods
-
-## Participants
-
-Data was collected from 647 participants (after exclusions).
-The results shown below consider data from subjects in our initial experiment, which consisted of 196 participants (106 constant, 90 varied).
-The follow-up experiments entailed minor manipulations: 1) reversing the velocity bands that were trained on vs.
-novel during testing; 2) providing ordinal rather than numerical feedback during training (e.g.
-correct, too low, too high).
-The data from these subsequent experiments are largely consistently with our initial results shown below.
-
-## Task
-
-We developed a novel visuomotor extrapolation task, termed the Hit The Wall task, wherein participants learned to launch a projectile such that it hit a rectangle at the far end of the screen with an appropriate amount of force.
-Although the projectile had both x and y velocity components, only the x-dimension was relevant for the task.  [Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}
-
-## Procedure
-
-The HTW task involved launching projectiles to hit a target displayed on the computer screen.
-Participants completed a total of 90 trials during the training stage.
-In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-In contrast, participants in the constant training condition encountered only one velocity band (800-1000).
-
-During the training stage, participants in both conditions also completed "no feedback" trials, where they received no information about their performance.
-These trials were randomly interleaved with the regular training trials.
-
-Following the training stage, participants proceeded to the testing stage, which consisted of three phases.
-In the first phase, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-
-In the second phase of testing, participants completed "no-feedback" testing from the three velocity bands used during the training stage (800-1000, 1000-1200, and 1200-1400).
-In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-
-The third and final phase of testing involved "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 10 trials.
-Participants received feedback on their performance during this phase.
-
-Throughout the experiment, participants' performance was measured by calculating the distance between the produced x-velocity of the projectiles and the closest edge of the current velocity band.
-Lower distances indicated better performance.
-
-After completing the experiment, participants were debriefed and provided with an opportunity to ask questions about the study.
-
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 6.0
-//| fig-height: 2.5
-//| fig-responsive: false
-
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-
-```
-
-## Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.31 @rcoreteamLanguageEnvironmentStatistical2020.
-To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
-Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as circumventing convergence issues common to the frequentist analogues of our mixed models.
-For each model, we report the median values of the posterior distribution, and 95% credible intervals.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 of which were discarded as warmup chains.
-Rhat values were generally within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
-
-We compared varied and constant performance across two measures, deviation and discrimination.
-Deviation was quantified as the absolute deviation from the nearest boundary of the velocity band, or set to 0 if the throw velocity fell anywhere inside the target band.
-Thus, when the target band was 600-800, throws of 400, 650, and 1100 would result in deviation values of 200, 0, and 300, respectively.
-Discrimination was measured by fitting a linear model to the testing throws of each subjects, with the lower end of the target velocity band as the predicted variable, and the x velocity produced by the participants as the predictor variable.
-Participants who reliably discriminated between velocity bands tended to have positive slopes with values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-```{r}
-#| label: tbl-e1-test-nf-deviation
-#| tbl-cap: "Testing Deviation - Empirical Summary"
-#| tbl-subcap:
-#|   - "Full datasets"
-#|   - "Intersection of samples with all labels available"
-#| layout-ncol: 1
-#| include: true
-#| echo: false
-
-result <- test_summary_table(test, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-
-result$constant |>kbl(booktabs = TRUE,
-                        linesep = "\\addlinespace[0.5em]",
-                        caption = paste("Summary of Deviation- Constant"))
-# |>
-#   kable_styling(font_size = ifelse(fmt_out == "latex", 8.5, NA))
-
-result$varied |> kbl(booktabs = TRUE,
-                        linesep = "\\addlinespace[0.5em]",
-                        caption = paste("Summary of Deviation- Varied"))
-
-```
-
-## Results
-
-### Testing Phase - No feedback.
-
-In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
-
-#### Deviation From Target Band
-
-Descriptive summaries testing deviation data are provided in @tbl-e1-test-nf-deviation and @fig-e1-test-dev.
-To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
-The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
-
-```{=tex}
-\begin{equation}
-dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
-\end{equation}
-```
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
-#| include: true
-test |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  labs(x="Band", y="Deviation From Target")
-```
-
-```{r}
-#| label: tbl-e1-bmm-dist
-#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-#| tbl-subcap: ["Constant Testing1 - Deviation", "Varied Testing - Deviation"]
-#| include: true
-#| echo: false
-modelName <- "e1_testDistBand_RF_5K"
-e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
-                      data=test,file=paste0(here::here("data/model_cache",modelName)),
-                      iter=5000,chains=4)
-GetModelStats(e1_distBMM) |> kbl(booktabs = TRUE,caption = paste("Coefficients"))
-
-e1_distBMM |> 
-  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
-          epred = TRUE, re_formula = NA) |> 
-  pairs() |> gather_emmeans_draws()  |> 
-   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
-   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
-   mutate(across(where(is.numeric), \(x) round(x, 2)),
-          pd=ifelse(value<0,1-pd,pd)) |> kbl(booktabs = TRUE)
-# |> 
-#   kbl(caption="Contrasts")
-
-coef_details <- get_coef_details(e1_distBMM, "conditVaried")
-
-```
-
-The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X).
-Overall, the varied training group showed a larger deviation relative to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]).
-Deviation also depended on target velocity band, with lower bands showing less deviation.
-See @tbl-e1-bmm-dist for full model output.
-
-#### Discrimination between bands
-
-In addition to accuracy/deviation, we also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
-responding differently when prompted for band 600-800 than when prompted for band 150-350).
-@tbl-e1-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
-To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants on each testing trial.
-
-```{=tex}
-\begin{equation}
-vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
-\end{equation}
-```
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-#| include: true
-test %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-test-nf-vx
-#| tbl-cap: "Testing vx - Empirical Summary"
-#| include: true
-
-result <- test_summary_table(test, "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-result$constant |> kbl(booktabs = TRUE)
-result$varied |> kbl(booktabs = TRUE)
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
-#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
-#| include: true
-e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-GetModelStats(e1_vxBMM ) |> kbl(booktabs=T, caption="Fit to all 6 bands")
-
-cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e1_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-
-modelName <- "e1_extrap_testVxBand"
-e1_extrap_VxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                  data=test |>
-                    filter(expMode=="test-Nf"),file=paste0(here::here("data/model_cache",modelName)),
-                  iter=5000,chains=4)
-GetModelStats(e1_extrap_VxBMM ) |> kable(booktabs=T, caption="Fit to 3 extrapolation bands")
-
-sc2 <- get_coef_details(e1_extrap_VxBMM, "bandInt")
-intCoef2 <- get_coef_details(e1_extrap_VxBMM, "conditVaried:bandInt")
-
-```
-
-See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($B$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the slope on Velocity Band ($B$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
-Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($B$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition.
-This difference is depicted visually in @fig-e1-bmm-vx.@tbl-e1-slope-quartile shows the average slope coefficients for varied and constant participants separately for each quartile.
-The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination.
-Figure @fig-e1-bmm-bx2 shows the distributions of slope values for each participant, and the compares the probability density of slope coefficients between training conditions.
-@fig-e1-indv-slopes
-
-The second model, which focused solely on extrapolation bands, revealed similar patterns.
-The Velocity Band term ($B$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]) still demonstrates a high degree of discrimination ability.
-However, the posterior distribution for interaction term ($B$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\] ) does across over 0, suggesting that the evidence for decreased discrimination ability for the varied participants is not as strong when considering only the three extrapolation bands.
-
-```{r}
-#| label: fig-e1-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
-#| layout-ncol: 2
-#| include: true
-
-e1_vxBMM |> emmeans( ~condit + bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects() +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(test$vb), 
-                     limits = c(0, 1400))
-
-e1_extrap_VxBMM |> emmeans( ~condit + bandInt, 
-                       at = list(bandInt = c(100, 350, 600))) |>
-  gather_emmeans_draws() |>
-  condEffects() +
-  scale_x_continuous(breaks = c(100, 350, 600), 
-                     labels = levels(test$vb)[1:3], 
-                     limits = c(0, 1000))
-
-```
-
-```{r}
-#| label: tbl-e1-slope-quartile
-#| tbl-cap: "Slope coefficients by quartile, per condition"
-
-new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")]))) |> 
-  dplyr::arrange(id,bandInt) |> 
-  mutate(condit_dummy = ifelse(condit == "Varied", 1, 0))
-
-indv_coefs <- as_tibble(coef(e1_vxBMM)$id, rownames="id")|> 
-  select(id, starts_with("Est")) |>
-  left_join(e1Sbjs, by=join_by(id) )
-
-fixed_effects <- e1_vxBMM |> 
-  spread_draws(`^b_.*`,regex=TRUE) |> arrange(.chain,.draw,.iteration)
-
-random_effects <- e1_vxBMM |> 
-  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
-  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
-  mutate(id = factor(id,levels=levels(test$id))) |> 
-  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)
-
- indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
-  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
-  right_join(new_data_grid, by = join_by("id")) |> 
-  mutate(
-    Slope = bandInt_RF+b_bandInt,
-    Intercept= RF_Intercept + b_Intercept,
-    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
-    SlopeInt = Slope + (`b_conditVaried:bandInt`*condit_dummy)
-  )
-
-  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt, Intercept,b_Intercept,b_bandInt) |>
-  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
-    select(id,condit,Intercept,b_Intercept,starts_with("Slope"),b_bandInt, n) |>
-  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()
-
-  indvSlopes |> mutate(Condition=condit) |>  group_by(Condition) |> 
-    reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
-  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
-  group_by(Condition) |>
-  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()
-
-```
-
-```{r}
-#| label: fig-e1-bmm-bx2
-#| fig-cap: Slope distributions between condition
-#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
-#| layout-ncol: 2
-#| fig-height: 9
-#| fig-width: 10
-#| include: true
-
-  indvSlopes |> ggplot(aes(y=rankSlope, x=SlopeInt,fill=condit,color=condit)) + 
-  geom_pointrange(aes(xmin=SlopeInt.lower , xmax=SlopeInt.upper)) + 
-  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)
-
-   ggplot(indvSlopes, aes(x = SlopeInt, color = condit)) + 
-  geom_density() + labs(x="Slope Coefficient",y="Density")
-
-```
-
-```{r}
-#| label: fig-e1-indv-slopes
-#| fig-cap: Subset of Varied and Constant Participants with the smallest and largest estimated slope values.
-Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution.
-Colored points and intervals at each band represent the empirical median and 95% HDI.
-#| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
-#| fig-height: 10
-#| fig-width: 12
-#| include: true
-
-nSbj <- 3
-indvDraws  |> indv_model_plot(indvSlopes, testAvg, SlopeInt,rank_variable=Slope,n_sbj=nSbj,"max")
-indvDraws |> indv_model_plot(indvSlopes, testAvg,SlopeInt, rank_variable=Slope,n_sbj=nSbj,"min")
-
-```
-
-# Experiment 2
-
-```{r setup2b, include=FALSE}
-testE2 <- readRDS(here::here("data/e2_08-21-23.rds")) |> filter(expMode2 == "Test") 
-e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
-testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
-  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
-```
-
-@fig-design-e2 illustrates the design of Experiment 2.
-The stages of the experiment (i.e.
-training, testing no-feedback, test with feedback), are identical to that of Experiment 1.
-The only change is that Experiment 2 participants train, and then test, on bands in the reverse order of Experiment 1 (i.e.
-training on the softer bands; and testing on the harder bands).
-
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 6.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| fig-align: left
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-
-```
-
-## E2 Results
-
-### Testing Phase - No feedback.
-
-In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
-
-#### Deviation From Target Band
-
-Descriptive summaries testing deviation data are provided in @tbl-e2-test-nf-deviation and @fig-e2-test-dev. 
-To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
-The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
-
-\begin{equation}
-dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
-\end{equation}
-
-```{r}
-#| label: tbl-e2-test-nf-deviation
-#| tbl-cap: "Testing Deviation - Empirical Summary"
-#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
-
-result <- test_summary_table(testE2, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-result$constant |> kbl()
-result$varied |> kbl()
-# make kable table with smaller font size
-# result$constant |> kbl(caption="Constant Testing - Deviation",booktabs=T,escape=F) |> kable_styling(font_size = 7)
-```
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap: E2. Deviations from target band during testing without feedback stage. 
-testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  labs(x="Band", y="Deviation From Target")
-```
-
-```{r}
-#| label: tbl-e2-bmm-dist
-#| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-
-modelName <- "e2_testDistBand_RF_5K"
-e2_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
-                      data=testE2,file=paste0(here::here("data/model_cache",modelName)),
-                      iter=5000,chains=4)
-mp2 <- GetModelStats(e2_distBMM) |> kable(booktabs=T)
-mp2
-
-e2_distBMM |> 
-  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
-          epred = TRUE, re_formula = NA) |> 
-  pairs() |> gather_emmeans_draws()  |> 
-   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
-   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
-   mutate(across(where(is.numeric), \(x) round(x, 2)),
-          pd=ifelse(value<0,1-pd,pd)) |>
-   kbl(caption="Contrasts")
-
-coef_details <- get_coef_details(e2_distBMM, "conditVaried")
-
-```
-
-The model predicting absolute deviation showed a modest tendency for the varied training group to have lower deviation compared to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]),with 94% of the posterior distribution being less than 0.
-This suggests a potential benefit of training with variation, though the evidence is not definitive.
-
-# Experiment 3
-
-```{r setup3b, include=FALSE}
-testE3 <- readRDS(here::here("data/e3_08-21-23.rds")) |> filter(expMode2 == "Test") 
-e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
-testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
-  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
-```
-
-The major manipulation adjustment of experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the earlier experiments.
-Ordinal feedback informs participants whether a throw was too soft, too hard, or fell within the target velocity range.
-Experiment 3 participants were randomly assigned to both a training condition (Constant vs.
-Varied) and a Band Order condition (original order used in Experiment 1, or the Reverse order of Experiment 2).
-
-## Results
-
-### Testing Phase - No feedback.
-
-In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
-Note that these no-feedback testing trials are identical to those of Experiment 1 and 2, as the ordinal feedback only occurs during the training phase, and final testing phase, of Experiment 3.
-
-#### Deviation From Target Band
-
-Descriptive summaries testing deviation data are provided in @tbl-e3-test-nf-deviation and @fig-e3-test-dev. 
-To model differences in accuracy between groups, we fit Bayesian mixed effects regression models to the trial level data from the testing phase.
-The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
-
-```{r}
-#| label: tbl-e3-test-nf-deviation
-#| tbl-cap: "Testing Deviation - Empirical Summary"
-#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
-
-resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-resultOrig$constant |> kbl()
-resultOrig$varied |> kbl()
-
-resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-resultRev$constant |> kbl()
-resultRev$varied |> kbl()
-
-```
-
-```{r}
-#| label: fig-e3-test-dev
-#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
-testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder)
-```
-
-```{r}
-#| label: tbl-e3-bmm-dist
-#| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-
-modelName <- "e3_testDistBand_RF_5K"
-e3_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
-                      data=testE3,file=paste0(here::here("data/model_cache",modelName)),
-                      iter=5000,chains=4)
-mp3 <- GetModelStats(e3_distBMM) |> kable(booktabs=T)
-mp3
-
-cd1 <- get_coef_details(e3_distBMM, "conditVaried")
-sc1 <- get_coef_details(e3_distBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_distBMM, "conditVaried:bandInt")
-```
-
-The effect of training condition in Experiment 3 showed a similar pattern to Experiment 2, with the varied group tending to have lower deviation than the constant group (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0.
-
-```{r}
-#| label: fig-e3-bmm-dist
-#| fig-cap: e3. Conditioinal Effect of Training Condition and Band. Ribbon indicated 95% Credible Intervals.
-
-e3_distBMM |> emmeans( ~condit + bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |>
-  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-    ylab("Predicted Deviation") + xlab("Velocity Band")+
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(0, 1400)) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-```
-
-#### Discrimination between Velocity Bands
-
-In addition to accuracy/deviation.
-We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
-responding differently when prompted for band 600-800 than when prompted for band 150-350).
-@tbl-e3-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
-To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
-
-\begin{equation}
-vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
-\end{equation}
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 14
-#| fig-height: 15
-#| column: screen-inset-right
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-  facet_wrap(bandOrder~condit,scale="free_x")
-
-```
-
-```{r}
-#| label: tbl-e3-test-nf-vx
-#| tbl-cap: "Testing vx - Empirical Summary"
-#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
-
-resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-resultOrig$constant |> kbl()
-resultOrig$varied |> kbl()
-
-resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-resultRev$constant |> kbl()
-resultRev$varied |> kbl()
-```
-
-```{r}
-#| label: tbl-e3-bmm-vx
-#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-mt4 <-GetModelStats(e3_vxBMM ) |> kable(booktabs=T)
-mt4
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-```
-
-See @tbl-e3-bmm-vx for the full model results.
-
-Slope estimates for experiment 3 suggest that participants were capable of distinguishing between velocity bands even when provided only ordinal feedback during training (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
-Unlike the previous two experiments, the posterior distribution for the interaction between condition and band was consistently positive, suggestive of superior discrimination for the varied participants
-β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\].
-
-# Modeling
-
-In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
-In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning (DeLosh 1997).
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model (Kruscke 1992), with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks.
-ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].
-
-ALM is a localist neural network model, with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on thevalue of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-
-See  for a full specification of the equations that define ALM and EXAM.
-
-{{< pagebreak >}}
-
-## Model Table
-### ALM Activation & Response
-| Step | Equation | Description |
-|------|----------|-------------|
-| **ALM Activation & Response**  |           |
-| Input Activation | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$ | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.
-|
-| Output Activation                 | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$ | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.   |
-| Output Probability                | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$ | Each output node has associated response, $Y_j$.
-The probability of response $Y_j$ is determined by the ratio of output activations.
-|
-| Mean Output                       | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$   | The response to stimulus x is the weighted average of the response probabilities. |
-| **ALM Learning**                  |                                                                                                                                                          |
-| Feedback Activation               | $f_j(Z) = e^{-c(Z-Y_j)^2}$                  | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response.
-|
-| Update Weights                    | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$    | Delta rule to update weights.
-Magnitude of weight changes controlled by learning rate parameter alpha.
-|
-| **EXAM**                          |                                                                                                                                                          |
-| Extrapolation                     | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$ | Novel test stimulus X activates input nodes associated with trained stimuli.     |
-|                                   | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)    |
-
-{{< pagebreak >}}
-
-## Model Fitting and Comparison
+## Main body
 
@@
 
+quarto pandoc --citeproc --pdf-engine xelatex -t pdf \
+  --bibliography=../Assets/Bib/Dissertation.bib \
+  --standalone \
+  -f markdown igas_e1.pdf.md \
+  -o refer-test.pdf
+
+quarto render igas_e1.qmd --citeproc --pdf-engine xelatex -t pdf \
+  --bibliography=../Assets/Bib/Dissertation.bib \
+  --standalone \
+  -o refer-test.pdf
+
+# Appendix
+
+{{< include ../Appendix/E1_Appendix.qmd >}}
+
+::: {.content-visible when-format="pdf"}
+
 # References
+
+:::

### 2023-10-28 Manuscript/manuscript.qmd
add supplementals

@@
   reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkableue","darkred")
+colorVec=c("darkblue","darkred")
 plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
@@
 
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>%   
-  kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
+kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
+
+#%>% kableExtra::kable_styling(position="left") 
+# %>%   
+#   kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
 
@@
 
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
+
+#  %>% kableExtra::kable_styling(position="left") %>% 
+#   kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
+
+# %>% kableExtra::kable_styling(position="left") %>% 
+#   kable_classic() #%>% footnote(general=captionText,general_title = "")
 ```
@@
 
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
+
+#  %>% kableExtra::kable_styling(position="left") %>% 
+#   kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 
-colorVec=c("darkableue","darkred")
+colorVec=c("darkblue","darkred")
 plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
@@
 
-In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 1, I applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
 In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations.
-Extrapolation has long been a focus of the literature on function learning [@brehmerHypothesesRelationsScaled1974; @carrollFunctionalLearningLearning1963].
-Central questions of the function learning literature have included the relative difficulties of learning various functional forms (e.g.
-linear vs.bilinear vs.
-quadratic), and the relative effectiveness of rule-based vs.
-association-based exemplar models vs.
-various hybrid models [@bottNonmonotonicExtrapolationFunction2004; @deloshExtrapolationSineQua1997; @jonesActiveFunctionLearning2018; @kalishPopulationLinearExperts2004; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
-However the issue of training variation has received surprisingly little attention in this area.
+Project 2 also places a greater emphasis on extrapolation performance following training.
+Although varied training has often been purported to be particularly beneficial for generalization or transfer, few experiments have compared varied and constant training in contexts with unambiguous extrapolation testing.
+
+## Function Learning and Extrapolation
+
+The study of human function learning investigates how people learn relationships between continuous input and output values.
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+
+@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
+Input stimuli and output responses were both lines of varying length.
+The correct output response was related to the length of the input line by a linear, quadratic, or random function.
+Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
+Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
+Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
+Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
+@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
+In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
+Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
+
+The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
+In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
+Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
+All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
+Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
+
+The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
+The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
+The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
+
+The authors also introduced two new function-learning models.
+The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
+ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
+ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
+The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
+When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
+ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
+EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
+Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
+
+```{r}
+#| label: fig-delosh-extrap
+#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
+#| echo: false
+#| fig-width: 10
+source(here::here("Functions","deLosh_data.R"))
+
+extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
+                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
+
+linear_function <- function(x) 2.2 * x + 30
+exponential_function <- function(x) 200 * (1 - exp(-x/25))
+quadratic_function <- function(x) 210 - (x - 50)^2 / 12
+
+linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
+    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
+  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
+
+exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
+  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
+  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
+  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
+  extrapLines +
+  scale_shape_manual(values = c(1)) +
+  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
+  theme(legend.title = element_blank(), legend.position="top") +
+  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
+                                                  linetype = c(0, 1))))
+
+quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
+  geom_point( shape = 1) +
+  stat_function( fun = quadratic_function, geom = "line") +
+  labs(title="Quadratic Function",x="",y="") + extrapLines
+
+linear_plot + exponential_plot + quadratic_plot
+```
 
@@
 #| include: true
+#| tbl-subcap: ["Constant", "Varied"]
 
@@
 The estimate for the interaction between slope and condition ($B$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition.
-This difference is depicted visually in @fig-e1-bmm-vx.@tbl-e1-slope-quartile shows the average slope coefficients for varied and constant participants separately for each quartile.
+This difference is depicted visually in @fig-e1-bmm-vx.Slope coefficients are broken down by quartile in @tbl-e1-slope-quartile.
 The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination.
@@
 #| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
-#| layout-ncol: 2
-#| include: true
+#| layout-ncol: 1
 
@@
 #| fig-width: 10
-#| include: true
 
@@
 Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution.
-Colored points and intervals at each band represent the empirical median and 95% HDI.
+Black points and intervals at each band represent the estimated median and 95% HDI.
+Blue points are empirical means.
 #| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
-#| fig-height: 10
-#| fig-width: 12
-#| include: true
+#| fig-height: 6
+#| fig-width: 9
 
@@
 #| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
-#| layout-ncol: 2
+#| layout-ncol: 1
 
@@
     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder)
+  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
 ```
@@
 #| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 14
-#| fig-height: 15
-#| column: screen-inset-right
+#| fig-width: 12
+#| fig-height: 13
 # testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
@@
 
+::: {.content-visible when-format="html"}
 # References
+
+::: {#refs}
+:::
+
+:::
+
+## Appendix
+
+### Project 1 Appendix
+
+{{< include ../Appendix/IGAS-Supplemental.qmd >}}
+
+{{< include ../Appendix/E1_Appendix.qmd >}}
+
+::: {.content-visible when-format="pdf"}
+
+# References
+
+:::

### 2023-10-28 Appendix/.vdoc.r

@@ -1,0 +1,539 @@
+#
+#
+#
+#
+#
+#
+#
+#
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+#rm(list=ls())
+###### data loading and organization #######
+
+# load the processed data from experiment 1 and 2
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+
+options(contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+theme_set(theme_classic())
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
+                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
+
+e1Pos <- c("610","760","835","910")
+e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
+e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
+
+
+transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
+transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
+transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
[…]

### 2023-10-28 Functions/Display_Functions.R

@@ -82,6 +82,7 @@ indv_model_plot <- function(combined_df, indv_coefs, testAvg,slopeVar, rank_vari
     scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                        labels = levels(testAvg$vb), 
                        limits = c(0, 1400)) +
+    labs(x="Velocity Band",y="Vx") +
     theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5,size=8.5)) +
     ggh4x::facet_nested_wrap(vars(condit, id),ncol=3)
 }

### 2023-10-28 Functions/packages.R

@@ -20,5 +20,5 @@ select <- dplyr::select
 mutate <- dplyr::mutate
 filter <- dplyr::filter
 map <- purrr::map
-walk(c(here("Functions/Display_Functions.R"), here("Functions/org_functions.R"), 
-       here("Functions/Table_Functions.R")), source)
+walk(c(here::here("Functions/Display_Functions.R"), here::here("Functions/org_functions.R"), 
+       here::here("Functions/Table_Functions.R")), source)

### 2023-10-28 Manuscript/.vdoc.r

@@ -1,2210 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-here::set_here(path='..')
-source(here::here("Functions", "packages.R"))
-
-if (is.null(knitr::pandoc_to())) {
-  fmt_out <- "interactive"
-} else {
-  fmt_out <- knitr::pandoc_to()
-}
-
-knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
-                      warning = FALSE, message = FALSE, eval=TRUE)
-
-knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
-                      fig.width = 6, fig.height = (6 * 0.618),
-                      out.width = "100%", collapse = TRUE)
-# 
-options(digits = 3, width = 120,
-        dplyr.summarise.inform = FALSE,
-        knitr.kable.NA = "")
-
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-#
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-
-# load the processed data from experiment 1 and 2
-
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-options(contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
[…]

### 2023-10-29 Appendix/E1_Appendix.qmd
adjust appendices

@@
-### Appendix - Project 2 - Experiment 1
-
 ```{r}
@@
 
-## E1 Appendix
-
-### Posterior Predictive Distributions
+#### Posterior Predictive Distributions
 
 ```{r}
-#| label: fig-post-pred
-#| fig-cap: Posterior Predictive distributions for Deviation and Vx. Posterior Draws in Blue, colored lines are empirical data. 
-#| fig-subcap: ["Posterior Predictive Distribution - Deviation", "Posterior Predictive Distribution - X Velocity"]
-#| fig-width: 13
-#| fig-height: 12
-
-vx_pred <- 
-  posterior_predict(e1_vxBMM, ndraws = 500) |> 
-  array_branch(margin=1) |> 
-   map_dfr( 
-    function(yrep_iter) {
-      test  |>
-        mutate(vx_pred = yrep_iter)
-    },
-    .id = 'iter'
-  ) |>
-  mutate(iter = as.numeric(iter))
+#| label: fig-post-pred-dist
+#| fig-cap: Posterior Predictive distributions for Absolute Deviance. Posterior Draws in Blue, colored lines are empirical data. 
+#| fig-width: 11
+#| fig-height: 9
 
@@
 
+```
+
+```{r}
+#| label: fig-post-pred-vx
+#| fig-cap: Posterior Predictive distributions for Vx. Posterior Draws in Blue, colored lines are empirical data. 
+#| fig-width: 11
+#| fig-height: 7
+vx_pred <- 
+  posterior_predict(e1_vxBMM, ndraws = 500) |> 
+  array_branch(margin=1) |> 
+   map_dfr( 
+    function(yrep_iter) {
+      test  |>
+        mutate(vx_pred = yrep_iter)
+    },
+    .id = 'iter'
+  ) |>
+  mutate(iter = as.numeric(iter))
+
 vx_pred  |>
@@
 
-### Empirical vs. Predicted
+#### Empirical vs. Predicted
 
@@
 #| fig-cap: Bayesian Mixed Model predictions vs. Empirical Predictions - X velocity
-#| fig-height: 15
-#| fig-width: 12
+#| fig-height: 12
+#| fig-width: 11
 
@@
              size = 0.4) + 
-  coord_flip() + ggtitle("Predicted Vx")  } /
-{
+  coord_flip() + ggtitle("Predicted Vx")  
+} / {
 vx_pred  |>
@@
              size = 0.4) + 
-  coord_flip() + ggtitle("Empirical Vx") }
+  coord_flip() + ggtitle("Empirical Vx") 
+}
 ```
 
-### Different Aggregations
+```{r}
 
-```{r fig.width=14, fig.height=13}
-#| label: fig-empirical-vxGrp
-#| fig-cap: E1. Distribution of vx at Participant and Trial level
-#| fig-width: 13
-#| fig-height: 14
-
-epId <- vx_pred  |>
-  filter(iter < 2)  |> group_by(id,condit,vb) |>
-  summarise(vx=median(vx)) |>
-  ggplot(aes(x=vb,y=vx,fill=condit)) + 
-  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
-                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
-  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
-             position = position_jitter(width = 0.05, height = 0),
-             size = 1, shape = 20, alpha=.7) +
-  geom_boxplot(aes(x=vb,y=vx,fill=condit),
-               outlier.shape = NA,
-               alpha = 0.5, width = 0.1) +
-  geom_hline(yintercept = 0,
-             linetype = 'dashed',
-             color = 'red',
-             size = 0.4) + 
-  coord_flip() + ggtitle("Empirical Vx - Subject level averaging")
-
-epTrial <- vx_pred  |>
-  filter(iter < 2)  |> group_by(id,condit,vb) |>
-  ggplot(aes(x=vb,y=vx,fill=condit)) + 
-  geom_flat_violin(aes(fill=condit), position = position_nudge(x = 0.1, y = 0),
-                   adjust = 1.5,trim = FALSE, alpha = .5, colour = NA) +
-  geom_point(aes(x = as.numeric(vb) - 0.15, col=condit),
-             position = position_jitter(width = 0.05, height = 0),
-             size = .5, shape = 20, alpha=.7) +
-  geom_boxplot(aes(x=vb,y=vx,fill=condit),
-               outlier.shape = NA,
-               alpha = 0.5, width = 0.1) +
-  geom_hline(yintercept = 0,
-             linetype = 'dashed',
-             color = 'red',
-             size = 0.4) + 
-  coord_flip() + ggtitle("Empirical Vx - Raw Trial") +
-   theme(axis.title.y=element_blank(),
-        axis.text.y=element_blank())
-
-epId + epTrial
 ```
 
-```{r fig.width=14, fig.height=13}
-#| label: fig-empirical-distGrp
-#| fig-cap: E1. Distribution of Vx  at Participant and Trial level
-#| fig-width: 13
-#| fig-height: 14
+#### Different Aggregations
+
+```{r}
+#| label: fig-empirical-distGrp1
+#| fig-cap: E1. Distribution of Vx  at Participant level
+#| fig-width: 12
+#| fig-height: 10
 
@@
 
+epId 
+```
+
+```{r}
+#| label: fig-empirical-distGrp2
+#| fig-cap: E1. Distribution of Vx at Trial level
+#| fig-width: 12
+#| fig-height: 10
 epTrial <- dist_pred  |>
@@
 
-epId + epTrial
+epTrial
 ```

### 2023-10-29 Appendix/IGAS-Supplemental.qmd
adjust appendices

@@
 ### First vs. second half of testing stage
-```{r,fig.height=7,fig.width=8}
+```{r}
 
@@
 
-# 
- #testSplit2 %>% anova_test(dv=MeanScaledDev,between=conditType,within = c(testHalfSbj),wid=sbjCode,type=3)
- #testSplit %>% anova_test(dv=MeanTargetDistance,between=conditType,covariate=testHalfSbj,within=(positionX),wid=sbjCode)
-# testSplit %>% lmer(MeanTargetDistance ~ conditType*testHalfSbj + (1|sbjCode)+(1+testHalfSbj|positionX),data=.) %>% summary()
-
-# testSplit %>% anova_test(dv=MeanTargetDistance,between=conditType,within=positionX,wid=sbjCode,type=3)
-# 
-# print("Testing End - Testing Start Comparison")
-# tsw %>% anova_test(dv=endMinusStart,between=conditType,within=positionX,wid=sbjCode,type=3)
-# tsw2 %>% anova_test(dv=endMinusStartScaled,between=conditType,wid=sbjCode,type=3)
-# 
-# print("2nd Half of testing only comparison")
-# testSplit %>% filter(testHalfSbj=="2nd-Half")%>%  anova_test(dv=MeanTargetDistance,between=conditType,within=(positionX),wid=sbjCode)
-# testSplit2 %>% filter(testHalfSbj=="2nd-Half")%>%  anova_test(dv=MeanScaledDev,between=conditType,wid=sbjCode,type=3)
-# 
-# testSplit2 %>% filter(testHalfSbj=="2nd-Half")%>% group_by(conditType) %>% get_summary_stats(type = "mean_sd")
-
 ```
@@
 
-e2TestFits %>% ggplot(aes(x=conditType,y=Asymptote.Minus.Start,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("e2 testing (asymptote - start performance)  ")
+e2TestFits %>% ggplot(aes(x=conditType,y=Asymptote.Minus.Start,fill=conditType))+
+  geom_bar(stat="summary",position=dodge,fun="mean")+ 
+  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
+  facet_grid(~positionX)+ggtitle("e2 testing (asymptote - start performance)") + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
+
 ```
@@
 
-# exp1Transfer3 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)
-
-# exp1Transfer3 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+ggtitle("Experiment 1 Test -Relative Distance")
-# 
-# 
-# 
-# exp1Transfer3 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+facet_grid(.~devianceDirection)
-
 exp1Transfer3 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Signed Deviation From Target Center") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",breaks=e1Pos,labels=e1Labels)+facet_grid(.~devianceDirection)
@@
 
-# exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+ggtitle("Experiment 2 Test - Relative Distance")
-# 
-# exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Absolute Dist - Split by Over/Under")
-
 exp2Transfer3 %>% ggplot(aes(x=ThrowPosition,y=meanRelativeDist,group=conditType2,fill=conditType2))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Signed Deviation From Target Center") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+facet_grid(.~devianceDirection)
-
-# 
-# exp2Transfer4 %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=Group2,fill=Group2))+geom_bar(stat="summary",position=position_dodge(),fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Position"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Absolute Dist - Split by Over/Under")
-# 
-# 
-# exp2Transfer4 %>% ggplot(aes(x=positionX,y=meanRelativeDist,group=Group2,fill=Group2))+geom_bar(stat="summary",position=position_dodge(),fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Position"))+theme(legend.title.align=.25)+theme_classic()+facet_grid(.~devianceDirection)+ggtitle("Experiment 2 Test - Relative Distance")
-
-# 
-# t= exp2Transfer3  %>% 
-#   mutate(Condition=conditType2) %>%
-#   group_by(Condition,positionX) %>% 
-#   summarise(Mean.signed=round(mean(meanRelativeDist),2),
-#             sd.signed=round(sd(meanRelativeDist),2),
-#             msds=paste(Mean.signed,"(",sd.signed,")",sep=""),
-#             .groups="keep") %>% ungroup() %>%
-#    select(-Mean.signed,-sd.signed) %>% 
-#   pivot_wider(names_from = positionX,values_from=c(msds)) %>% as.data.frame() %>%stargazer(.,type="text",summary=FALSE,rownames = FALSE)
-#
 
@@
 #### Experimenet 1 - intermittent testing
-```{r,fig.width=9}
-# first 3 trials - 1 throw from 610, 760 and 910
-# interleaved every 20 trials, 2 throws from 610, 760, 910
-# 10 full intermittent tests (6 trials each), plus 3 at beginning = 63 total per subject. 
-#[1] 0  2  3  5  6  8  9  11 12 14 15 17 18 20 21 23 24 26 27 29 30
-# First final testing trial is 264. So 1-263 = training and intermittent testing. 
-# 
-# intTest.third <- exp1.inter %>% filter(intStage!="int1")%>% group_by(sbjCode,conditType,stage,intStage,positionX) %>%
-#   summarise(MeanTargetDistance=mean(AbsDistFromCenter,trim=.05)) %>% group_by(sbjCode,conditType,stage,positionX) %>%
-#   summarise(MeanTargetDistance=mean(MeanTargetDistance))
-# 
-# intTest.third %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-#   geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-#   facet_wrap(~conditType,ncol=2)+
-#   stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-#   ylab("Mean Distance From Center Of Target")+
-#   xlab("Throw Location")+theme(plot.title = element_text(hjust = 0.5))+
-#   guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-# 
-# intTest.half %>% anova_test(dv=MeanTargetDistance,between=conditType,within=trainHalf,covariate=positionX,wid=sbjCode)
-# intTest.half %>% anova_test(dv=MeanTargetDistance,between=conditType,within=c(trainHalf,positionX),wid=sbjCode)
+```{r}
 
 intTest.half <- readRDS(here::here("data/e1_intTest.rds"))
-
-# intTest.half <- exp1.inter %>%filter(AbsDistFromCenter<1550)%>% 
-#   group_by(sbjCode,conditType,trainHalf,positionX) %>%
-#   summarise(MeanTargetDistance=mean(AbsDistFromCenter,trim=.01))
 
@@
 
-# exp1TrainTrials %>% filter(AbsDistFromCenter<1000) %>% ggplot(aes(x=trainIndex,y=AbsDistFromCenter,group=conditType2)) +geom_point()+geom_smooth(method="lm",se=FALSE) +facet_grid(~positionX)
-
 # manuscript plot - original
@@
 
-# fit to testing performance averaged across positions
+#### fit to testing performance averaged across positions
 ```{r}
@@
 
-e2Fits.AggPos %>% ggplot(aes(x=Group,y=pStart,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("experiment 2 - starting performance per position")
+e2Fits.AggPos %>% ggplot(aes(x=Group,y=pStart,fill=Group))+
+  geom_bar(stat="summary",position=dodge,fun="mean")+ 
+  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
+  ggtitle("experiment 2 - starting performance per position") + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
 
-e2Fits.AggPos %>% ggplot(aes(x=Group,y=pAsym,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("e2 testing performance asymptote per position ")
+e2Fits.AggPos %>% ggplot(aes(x=Group,y=pAsym,fill=Group))+
+  geom_bar(stat="summary",position=dodge,fun="mean")+ 
+  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
+  ggtitle("e2 testing performance asymptote per position ") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
 
-e2Fits.AggPos %>% ggplot(aes(x=Group,y=pRate,fill=Group))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("e2 testing performance asymptote per position ")
+e2Fits.AggPos %>% ggplot(aes(x=Group,y=pRate,fill=Group))+
+  geom_bar(stat="summary",position=dodge,fun="mean")+ 
+  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
+  ggtitle("e2 testing performance asymptote per position ") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
 
@@
 
-e2TestFits %>% ggplot(aes(x=conditType,y=pStart,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("experiment 2 - starting performance per position")
+e2TestFits %>% ggplot(aes(x=conditType,y=pStart,fill=conditType))+
+  geom_bar(stat="summary",position=dodge,fun="mean")+ 
+  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
+  facet_grid(~positionX)+ggtitle("experiment 2 - starting performance per position") + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
 
@@
 
-e2TestFits %>% ggplot(aes(x=conditType,y=pAsym,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+facet_grid(~positionX)+ggtitle("e2 testing performance asymptote per position ")
+e2TestFits %>% ggplot(aes(x=conditType,y=pAsym,fill=conditType))+
+  geom_bar(stat="summary",position=dodge,fun="mean")+ 
+  stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+
+  facet_grid(~positionX)+ggtitle("e2 testing performance asymptote per position ") + 
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
 

### 2023-10-29 Manuscript/igas_e1.tex
adjust appendices

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmathfont[]{Libertinus Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={DarkSlateBlue},
  filecolor={Maroon},
  citecolor={DarkSlateBlue},
  urlcolor={DarkSlateBlue},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}
\begin{centering}
\LARGE
{The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach}

\vspace*{1.5cm}

\LARGE
{Thomas E. Gorman}

\vspace{16.5cm}

\end{centering}

Submitted to the faculty of the University Graduate School in partial
fulfillment of the requirements for the degree Doctor of Philosophy in
the Department of Psychology and Brain Sciences and the Cognitive
Science Program, Indiana University Indiana University

\vspace{6cm}

\pagenumbering{gobble}

\newpage

Accepted by the Graduate Faculty, Indiana University, in partial
fulfillment of the requirements for the degree of Doctor of Philosophy.
\vspace{4cm}

\hfill\break
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Robert L.
Goldstone, PhD \vspace{2.5cm}\\
\strut \\
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Robert
Nosofsky, PhD \vspace{2.5cm}\\
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Peter Todd,
PhD \vspace{2.5cm}\\
\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Mike Jones,
PhD

\newpage

\begin{centering}

\vspace*{6.5cm}

@2023 \\
\vspace{1cm}

Thomas E. Gorman
\vspace{.2cm}

\vspace{5cm}

\end{centering}

\newpage
\begin{center}
\textbf{Acknowledgements}
\end{center}
\newpage

\newpage{}

\section{Abstract}\label{abstract}

This dissertation seeks to explore the cognitive underpinnings that
govern the generalization of learning, focusing specifically on the role
of variability during training in shaping subsequent transfer
performance. A comprehensive review of the existing literature is
presented, emphasizing the methodological complications associated with
disentangling the confounding effects of similarity. Through a series of
experiments involving several novel visuomotor tasks, this work
investigates whether and how variability in training conditions affects
performance in novel tasks. To theoretically account for the empirical
outcomes, I employ both instance-based and connectionist computational
models, both of which incorporate similarity-based mechanisms. These
models serve to account for the extent to which variability influences
the learners' generalization gradient, and also explain how training
variation can produce both beneficial and deleterious outcomes.

\newpage{}

\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage

\newpage{}

\subsection{Main body}\label{main-body}

Following the procedure used by Mcdaniel et al.
(\citeproc{ref-mcdanielPredictingTransferPerformance2009}{2009}), we
will assess the ability of both ALM and EXAM to account for the
empirical data when fitting the models to 1) only the training data, and
2) both training and testing data. Models will be fit directly to the
trial by trial data of each individual participants, both by minimizing
the root-mean squared deviation (RMSE), and by maximizing log
likelihood. Because ALM has been shown to do poorly at accounting for
human patterns extrapolation
(\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al., 1997}), we
will also fit the extended EXAM version of the model, which operates
identically to ALM during training, but includes a linear extrapolation
mechanism for generating novel responses during testing.

quarto pandoc --citeproc --pdf-engine xelatex -t pdf\\
--bibliography=../Assets/Bib/Dissertation.bib\\
--standalone\\
-f markdown igas\_e1.pdf.md\\
-o refer-test.pdf

quarto render igas\_e1.qmd --citeproc --pdf-engine xelatex -t pdf\\
--bibliography=../Assets/Bib/Dissertation.bib\\
--standalone\\
-o refer-test.pdf

\section{Appendix}\label{appendix}

\subsubsection{Appendix - Project 2 - Experiment
1}\label{appendix---project-2---experiment-1}

\subsection{E1 Appendix}\label{e1-appendix}

\subsubsection{Posterior Predictive
Distributions}\label{posterior-predictive-distributions}

\subsubsection{Empirical vs.~Predicted}\label{empirical-vs.-predicted}

\subsubsection{Different Aggregations}\label{different-aggregations}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-deloshExtrapolationSineQua1997}
DeLosh, E. L., McDaniel, M. A., \& Busemeyer, J. R. (1997).
Extrapolation: {The Sine Qua Non} for {Abstraction} in {Function
Learning}. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{23}(4), 19.
\url{https://doi.org/10.1037/0278-7393.23.4.968}

\bibitem[\citeproctext]{ref-mcdanielPredictingTransferPerformance2009}
Mcdaniel, M. A., Dimperio, E., Griego, J. A., \& Busemeyer, J. R.
(2009). Predicting transfer performance: {A} comparison of competing
function learning models. \emph{Journal of Experimental Psychology.
Learning, Memory, and Cognition}, \emph{35}, 173--195.
\url{https://doi.org/10.1037/a0013982}

\end{CSLReferences}

\end{document}

### 2023-10-29 paper.qmd
fix cache issue

@@
 
-<iframe src="/Manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
+<iframe src="/Manuscript/output/TG_Full_Dissertation.pdf" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
 ```

### 2023-10-29 Manuscript/manuscript.qmd
adjust appendices
small fixes; remove prefer-html from docx render

@@
   eval: true
-  include: false
+  include: true
+  #echo: false
 ---
@@
 
+{{< pagebreak >}}
+
 ::: {.content-visible when-format="html"}
@@
 ```{r setup}
+#| echo: false
+#| 
 here::set_here(path='..')
@@
 ```{r}
+#| echo: false
 source(here::here('Functions/IGAS_ProcessFunctions.R'))
@@
 
-**Equation 1:** \[ Similarity\_{I,J} = \sum*{i = I}*\sum{j=J}
-e^{-c^\cdot dp\_{i,j}} \]
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
+(e^{-c^\cdot d^{p}_{i,j}}) $$
 
@@
 
-## Appendix
-
-### Project 1 Appendix
+# Appendix
+
+### Appendix - Project 1
 
@@
 
+{{< pagebreak >}}
+
+### Appendix - Project 2 - Experiment 1
+
 {{< include ../Appendix/E1_Appendix.qmd >}}

### 2023-10-30 IGAS.qmd
add supplementals
adjust appendices
adjust igas toy model figure

@@
 ```{r}
-#| label: fig-Toy_Model2
+#| label: fig-Toy-Model2
 #| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$.
+For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
 For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
 The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
+Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
+#| fig.width: 11
+#| fig.height: 11.5
 
@@
 
-## References
+# References
+
+::: {#refs}
+:::
+
+# Appendix
+
+{{< include Appendix/IGAS-Supplemental.qmd >}}

### 2023-10-30 Manuscript/igas_e1.qmd
adjust igas toy model figure

@@
   eval: true
-  include: false
+  include: true
 ---
@@
 ::: {.content-visible when-format="html"}
-
 {{< include pre_sections/pre_html.qmd >}}
-
 :::
@@
 ::: {.content-visible when-format="pdf"}
-
 {{< include pre_sections/pre_pdf.qmd >}}
-
 :::
@@
 ::: {.content-visible when-format="docx"}
-
 {{< include pre_sections/pre_docx.qmd >}}
-
 :::
@@
 ::: {.content-visible when-format="html"}
-
 {{< include pre_sections/toc_html.qmd >}}
-
 :::
@@
 ::: {.content-visible when-format="pdf"}
+{{< include pre_sections/toc_pdf.qmd >}}
+:::
 
-{{< include pre_sections/toc_pdf.qmd >}}
+```{r}
+pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)
+source('../Functions/IGAS_ProcessFunctions.R')
+```
 
-:::
+$$e^{(c\cdot|x-800|)}$$
+
+$$e^{(c\cdot|x-400|)}$$
+
+$$e^{(c\cdot|x-800|)}$$ + $$e^{(c\cdot|x-400|)}$$
+
+$$e^{(c_{varied}\cdot|x-800|)}$$
+
+$e^{(c_{varied}\cdot|x-800|)}$
+$+e^{(c_{varied}\cdot|x-400|)}$
+$e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$
+
+$e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$,
+
+```{r}
+#| label: fig-Toy-Model2
+#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
+For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
+For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
+The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
+Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
+#| fig.width: 11
+#| fig.height: 11.5
+
+#
+
+p=2
+c<- .000002
+
+trainingTestingDifference=2000;
+cvaried=.00002
+cconstant=.0005
+simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
+                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
+                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
+                            genGauss=exp(-c*(abs((x-train.position)^p))),
+                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
+                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
+                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
+                            ) %>% 
+  group_by(x,condit) %>%
+  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
+
+#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
+
+colorVec=c("darkblue","darkred")
+plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
+                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
+                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
+                  ylim(c(0,1.05)),
+                  #xlim(c(250,950)),
+                  scale_x_continuous(breaks=seq(200,1000,by=200)),
+                  xlab("Test Stimulus"),
+                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
+                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
+                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
+                        legend.position="none"))
+
+ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
+ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
+ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
+  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
+ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
+  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
+# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
+
+gtitle="Figure 9."
+title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
+plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
+
+```
 
@@
 
-quarto pandoc --citeproc --pdf-engine xelatex -t pdf \
-  --bibliography=../Assets/Bib/Dissertation.bib \
-  --standalone \
-  -f markdown igas_e1.pdf.md \
+quarto pandoc --citeproc --pdf-engine xelatex -t pdf\
+--bibliography=../Assets/Bib/Dissertation.bib\
+--standalone\
+-f markdown igas_e1.pdf.md\
 -o refer-test.pdf
 
-quarto render igas_e1.qmd --citeproc --pdf-engine xelatex -t pdf \
-  --bibliography=../Assets/Bib/Dissertation.bib \
-  --standalone \
+quarto render igas_e1.qmd --citeproc --pdf-engine xelatex -t pdf\
+--bibliography=../Assets/Bib/Dissertation.bib\
+--standalone\
 -o refer-test.pdf
@@
 ::: {.content-visible when-format="pdf"}
-
 # References
-
 :::

### 2023-10-30 Manuscript/igas_e1.tex
adjust igas toy model figure

@@
 \fi
+
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{241,243,245}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
+\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
 
@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \KOMAoption{captions}{tableheading}
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{pacman}\SpecialCharTok{::}\FunctionTok{p\_load}\NormalTok{(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)}
+\FunctionTok{source}\NormalTok{(}\StringTok{\textquotesingle{}../Functions/IGAS\_ProcessFunctions.R\textquotesingle{}}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\[e^{(c\cdot|x-800|)}\]
+
+\[e^{(c\cdot|x-400|)}\]
+
+\[e^{(c\cdot|x-800|)}\] + \[e^{(c\cdot|x-400|)}\]
+
+\[e^{(c_{varied}\cdot|x-800|)}\]
+
+\(e^{(c_{varied}\cdot|x-800|)}\) \(+e^{(c_{varied}\cdot|x-400|)}\)
+\(e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}\)
+
+\(e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}\),
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# }
+
+\NormalTok{p}\OtherTok{=}\DecValTok{2}
+\NormalTok{c}\OtherTok{\textless{}{-}}\NormalTok{ .}\DecValTok{000002}
+
+\NormalTok{trainingTestingDifference}\OtherTok{=}\DecValTok{2000}\NormalTok{;}
+\NormalTok{cvaried}\OtherTok{=}\NormalTok{.}\DecValTok{00002}
+\NormalTok{cconstant}\OtherTok{=}\NormalTok{.}\DecValTok{0005}
+\NormalTok{simdat }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\AttributeTok{x=}\FunctionTok{rep}\NormalTok{(}\FunctionTok{seq}\NormalTok{(}\DecValTok{200}\NormalTok{,}\DecValTok{1000}\NormalTok{),}\DecValTok{3}\NormalTok{),}\AttributeTok{condit=}\FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\StringTok{"varied"}\NormalTok{,}\DecValTok{1602}\NormalTok{),}\FunctionTok{rep}\NormalTok{(}\StringTok{"constant"}\NormalTok{,}\DecValTok{801}\NormalTok{)),}
+                     \AttributeTok{train.position=}\FunctionTok{c}\NormalTok{(}\FunctionTok{rep}\NormalTok{(}\DecValTok{400}\NormalTok{,}\DecValTok{801}\NormalTok{),}\FunctionTok{rep}\NormalTok{(}\DecValTok{800}\NormalTok{,}\DecValTok{801}\NormalTok{),}\FunctionTok{rep}\NormalTok{(}\DecValTok{600}\NormalTok{,}\DecValTok{801}\NormalTok{)),}\AttributeTok{c=}\NormalTok{.}\DecValTok{0002}\NormalTok{,}\AttributeTok{p=}\DecValTok{2}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+                     \FunctionTok{mutate}\NormalTok{(}\AttributeTok{c2=}\FunctionTok{ifelse}\NormalTok{(condit}\SpecialCharTok{==}\StringTok{"varied"}\NormalTok{,cvaried,cconstant),}
+                            \AttributeTok{genGauss=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c}\SpecialCharTok{*}\NormalTok{(}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
+                            \AttributeTok{genGaussDist=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c}\SpecialCharTok{*}\NormalTok{(trainingTestingDifference}\SpecialCharTok{+}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
+                            \AttributeTok{genGauss2=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c2}\SpecialCharTok{*}\NormalTok{(}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
+                            \AttributeTok{genGaussDist2=}\FunctionTok{exp}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{c2}\SpecialCharTok{*}\NormalTok{(trainingTestingDifference}\SpecialCharTok{+}\FunctionTok{abs}\NormalTok{((x}\SpecialCharTok{{-}}\NormalTok{train.position)}\SpecialCharTok{\^{}}\NormalTok{p))),}
+\NormalTok{                            ) }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{group\_by}\NormalTok{(x,condit) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{genGauss=}\FunctionTok{mean}\NormalTok{(genGauss),}\AttributeTok{genGauss2=}\FunctionTok{mean}\NormalTok{(genGauss2),}\AttributeTok{genGaussDist=}\FunctionTok{mean}\NormalTok{(genGaussDist),}\AttributeTok{genGaussDist2=}\FunctionTok{mean}\NormalTok{(genGaussDist2),}\AttributeTok{.groups=}\StringTok{\textquotesingle{}keep\textquotesingle{}}\NormalTok{)}
+
+\CommentTok{\#plot(x,exp(c*(trainingTestingDifference+abs(x{-}800)))+exp(c*(trainingTestingDifference+abs(x{-}400)))}
+
+\NormalTok{colorVec}\OtherTok{=}\FunctionTok{c}\NormalTok{(}\StringTok{"darkblue"}\NormalTok{,}\StringTok{"darkred"}\NormalTok{)}
+\NormalTok{plotSpecs }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{(}\FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{alpha=}\NormalTok{.}\DecValTok{7}\NormalTok{),}\FunctionTok{scale\_color\_manual}\NormalTok{(}\AttributeTok{values=}\NormalTok{colorVec),}
+                  \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{alpha=}\NormalTok{.}\DecValTok{55}\NormalTok{,}\AttributeTok{xintercept =} \FunctionTok{c}\NormalTok{(}\DecValTok{400}\NormalTok{,}\DecValTok{800}\NormalTok{),}\AttributeTok{color=}\NormalTok{colorVec[}\DecValTok{2}\NormalTok{]),}
+                  \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{alpha=}\NormalTok{.}\DecValTok{55}\NormalTok{,}\AttributeTok{xintercept =} \FunctionTok{c}\NormalTok{(}\DecValTok{600}\NormalTok{),}\AttributeTok{color=}\NormalTok{colorVec[}\DecValTok{1}\NormalTok{]),}
+                  \FunctionTok{ylim}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{,}\FloatTok{1.05}\NormalTok{)),}
+                  \CommentTok{\#xlim(c(250,950)),}
+                  \FunctionTok{scale\_x\_continuous}\NormalTok{(}\AttributeTok{breaks=}\FunctionTok{seq}\NormalTok{(}\DecValTok{200}\NormalTok{,}\DecValTok{1000}\NormalTok{,}\AttributeTok{by=}\DecValTok{200}\NormalTok{)),}
+                  \FunctionTok{xlab}\NormalTok{(}\StringTok{"Test Stimulus"}\NormalTok{),}
+                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{455}\NormalTok{,}\AttributeTok{y=}\FloatTok{1.05}\NormalTok{,}\AttributeTok{label=}\StringTok{"Varied"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
+                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{455}\NormalTok{,}\AttributeTok{y=}\NormalTok{.}\DecValTok{97}\NormalTok{,}\AttributeTok{label=}\StringTok{"Training"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
+                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{662}\NormalTok{,}\AttributeTok{y=}\FloatTok{1.05}\NormalTok{,}\AttributeTok{label=}\StringTok{"Constant"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
+                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{657}\NormalTok{,}\AttributeTok{y=}\NormalTok{.}\DecValTok{97}\NormalTok{,}\AttributeTok{label=}\StringTok{"Training"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
+                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{855}\NormalTok{,}\AttributeTok{y=}\FloatTok{1.05}\NormalTok{,}\AttributeTok{label=}\StringTok{"Varied"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
+                  \FunctionTok{annotate}\NormalTok{(}\AttributeTok{geom=}\StringTok{"text"}\NormalTok{,}\AttributeTok{x=}\DecValTok{855}\NormalTok{,}\AttributeTok{y=}\NormalTok{.}\DecValTok{97}\NormalTok{,}\AttributeTok{label=}\StringTok{"Training"}\NormalTok{,}\AttributeTok{size=}\FloatTok{3.0}\NormalTok{),}
+                  \FunctionTok{theme}\NormalTok{(}\AttributeTok{panel.border =} \FunctionTok{element\_rect}\NormalTok{(}\AttributeTok{colour =} \StringTok{"black"}\NormalTok{, }\AttributeTok{fill=}\ConstantTok{NA}\NormalTok{, }\AttributeTok{size=}\DecValTok{1}\NormalTok{),}
+                        \AttributeTok{legend.position=}\StringTok{"none"}\NormalTok{))}
+
+\NormalTok{ip1 }\OtherTok{\textless{}{-}}\NormalTok{ simdat  }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGauss,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"Amount of Generalization"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Identical context, 1c"}\NormalTok{)}
+\NormalTok{ip2 }\OtherTok{\textless{}{-}}\NormalTok{ simdat }\SpecialCharTok{\%\textgreater{}\%}  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGauss2,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Identical context, 2c"}\NormalTok{)}
+\NormalTok{ip3 }\OtherTok{\textless{}{-}}\NormalTok{ simdat  }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGaussDist,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{"Amount of Generalization"}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Added distance due to context, 1c"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
+\NormalTok{ip4 }\OtherTok{\textless{}{-}}\NormalTok{ simdat }\SpecialCharTok{\%\textgreater{}\%}  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(x,}\AttributeTok{y=}\NormalTok{genGaussDist2,}\AttributeTok{group=}\NormalTok{condit,}\AttributeTok{col=}\NormalTok{condit))}\SpecialCharTok{+}\NormalTok{plotSpecs}\SpecialCharTok{+}\FunctionTok{ylab}\NormalTok{(}\StringTok{""}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Added distance due to context, 2c"}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
+\CommentTok{\# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)}
+
+\NormalTok{gtitle}\OtherTok{=}\StringTok{"Figure 9."}
+\NormalTok{title }\OtherTok{=} \FunctionTok{ggdraw}\NormalTok{()}\SpecialCharTok{+}\FunctionTok{draw\_label}\NormalTok{(gtitle,}\AttributeTok{fontface =} \StringTok{\textquotesingle{}bold\textquotesingle{}}\NormalTok{,}\AttributeTok{x=}\DecValTok{0}\NormalTok{,}\AttributeTok{hjust=}\DecValTok{0}\NormalTok{,}\AttributeTok{size=}\DecValTok{11}\NormalTok{)}\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{plot.margin =} \FunctionTok{margin}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{))}
+\FunctionTok{plot\_grid}\NormalTok{(title,}\ConstantTok{NULL}\NormalTok{,ip1,ip2,ip3,ip4,}\AttributeTok{ncol=}\DecValTok{2}\NormalTok{,}\AttributeTok{rel\_heights=}\FunctionTok{c}\NormalTok{(.}\DecValTok{1}\NormalTok{,.}\DecValTok{8}\NormalTok{,.}\DecValTok{8}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{igas_e1_files/figure-pdf/fig-Toy-Model2-1.pdf}
+
+}
+
+\caption{\label{fig-Toy-Model2}A simple model depicting the necessity of
+both of two separately fit generalization parameters, c, and a positive
+distance between training and testing contexts, in order for an instance
+model to predict a pattern of varied training from stimuli 400 and 800
+outperforming constant training from position 600 at a test position of
+600. For the top left panel, in which the generalization model assumes a
+single c value (-.008) for both varied and constant conditions, and
+identical contexts across training and testing, the equation which
+generates the varied condition is - Amount of Generalization =
+\(e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}\), whereas the constant
+group generalization is generated from \(2\cdot e^{(c\cdot|x-600|)}\).
+For the top right panel, the c constants in the original equations are
+different for the 2 conditions, with \(c=-.002\) for the varied
+condition, and \(c=-.008\) for the constant condition. The bottom two
+panels are generated from identical equations to those immediately
+above, except for the addition of extra distance (100 units) to reflect
+the assumption of some change in context between training and testing
+conditions. Thus, the generalization model for the varied condition in
+the bottom-right panel is of the form - Amount of Generalization =
+\(e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}\) .}
+
+\end{figure}%
+
 \newpage{}
@@
 
-\subsubsection{Appendix - Project 2 - Experiment
-1}\label{appendix---project-2---experiment-1}
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# print(getwd())}
+\CommentTok{\# here::set\_here(path=\textquotesingle{}..\textquotesingle{})}
+\CommentTok{\# print(getwd())}
+\FunctionTok{source}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"Functions"}\NormalTok{, }\StringTok{"packages.R"}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
 
-\subsection{E1 Appendix}\label{e1-appendix}
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{test }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"data/e1\_08{-}21{-}23.rds"}\NormalTok{)) }\SpecialCharTok{|\textgreater{}} \FunctionTok{filter}\NormalTok{(expMode2 }\SpecialCharTok{==} \StringTok{"Test"}\NormalTok{)  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{select}\NormalTok{(id,condit,bandInt,vb,vx,dist,sdist,bandType,tOrder)}
+\end{Highlighting}
+\end{Shaded}
 
-\subsubsection{Posterior Predictive
+\paragraph{Posterior Predictive
 Distributions}\label{posterior-predictive-distributions}
 
-\subsubsection{Empirical vs.~Predicted}\label{empirical-vs.-predicted}
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{dist\_pred }\OtherTok{\textless{}{-}} 
+  \FunctionTok{posterior\_predict}\NormalTok{(e1\_distBMM, }\AttributeTok{ndraws =} \DecValTok{500}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{array\_branch}\NormalTok{(}\AttributeTok{margin=}\DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+   \FunctionTok{map\_dfr}\NormalTok{( }
+    \ControlFlowTok{function}\NormalTok{(yrep\_iter) \{}
+\NormalTok{      test  }\SpecialCharTok{|\textgreater{}}
+        \FunctionTok{mutate}\NormalTok{(}\AttributeTok{dist\_pred =}\NormalTok{ yrep\_iter)}
+\NormalTok{    \},}
+    \AttributeTok{.id =} \StringTok{\textquotesingle{}iter\textquotesingle{}}
+\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{iter =} \FunctionTok{as.numeric}\NormalTok{(iter))}
 
-\subsubsection{Different Aggregations}\label{different-aggregations}
+\NormalTok{dist\_pred  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{100}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(dist\_pred, }\AttributeTok{group =}\NormalTok{ iter)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{03}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}density\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}blue\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{data =}\NormalTok{ test,}
+               \FunctionTok{aes}\NormalTok{(dist,}\AttributeTok{col=}\NormalTok{vb),}
+               \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{,}
+               \AttributeTok{size =} \FloatTok{0.7}\NormalTok{) }\SpecialCharTok{+} \CommentTok{\# 1}
+  \FunctionTok{facet\_grid}\NormalTok{(condit }\SpecialCharTok{\textasciitilde{}}\NormalTok{ vb) }\SpecialCharTok{+}
+  \FunctionTok{xlab}\NormalTok{(}\StringTok{\textquotesingle{}Deviation\textquotesingle{}}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{igas_e1_files/figure-pdf/fig-post-pred-dist-1.pdf}
+
+}
+
+\caption{\label{fig-post-pred-dist}Posterior Predictive distributions
+for Absolute Deviance. Posterior Draws in Blue, colored lines are
+empirical data.}
+
+\end{figure}%
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{vx\_pred }\OtherTok{\textless{}{-}} 
+  \FunctionTok{posterior\_predict}\NormalTok{(e1\_vxBMM, }\AttributeTok{ndraws =} \DecValTok{500}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{array\_branch}\NormalTok{(}\AttributeTok{margin=}\DecValTok{1}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+   \FunctionTok{map\_dfr}\NormalTok{( }
+    \ControlFlowTok{function}\NormalTok{(yrep\_iter) \{}
+\NormalTok{      test  }\SpecialCharTok{|\textgreater{}}
+        \FunctionTok{mutate}\NormalTok{(}\AttributeTok{vx\_pred =}\NormalTok{ yrep\_iter)}
+\NormalTok{    \},}
+    \AttributeTok{.id =} \StringTok{\textquotesingle{}iter\textquotesingle{}}
+\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{iter =} \FunctionTok{as.numeric}\NormalTok{(iter))}
+
+\NormalTok{vx\_pred  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{100}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(vx\_pred, }\AttributeTok{group =}\NormalTok{ iter)) }\SpecialCharTok{+}
+  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{03}\NormalTok{, }\AttributeTok{stat =} \StringTok{\textquotesingle{}density\textquotesingle{}}\NormalTok{, }\AttributeTok{color =} \StringTok{\textquotesingle{}blue\textquotesingle{}}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_density}\NormalTok{(}\AttributeTok{data =}\NormalTok{ test,}
+               \FunctionTok{aes}\NormalTok{(vx,}\AttributeTok{col=}\NormalTok{vb),}
+               \AttributeTok{inherit.aes =} \ConstantTok{FALSE}\NormalTok{,}
+               \AttributeTok{size =} \FloatTok{0.7}\NormalTok{) }\SpecialCharTok{+} \CommentTok{\# 1}
+  \FunctionTok{facet\_grid}\NormalTok{(condit }\SpecialCharTok{\textasciitilde{}}\NormalTok{ vb) }\SpecialCharTok{+}
+  \FunctionTok{xlab}\NormalTok{(}\StringTok{\textquotesingle{}Vx\textquotesingle{}}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{igas_e1_files/figure-pdf/fig-post-pred-vx-1.pdf}
+
+}
+
+\caption{\label{fig-post-pred-vx}Posterior Predictive distributions for
+Vx. Posterior Draws in Blue, colored lines are empirical data.}
+
+\end{figure}%
+
+\paragraph{Empirical vs.~Predicted}\label{empirical-vs.-predicted}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{\{}
+\NormalTok{vx\_pred  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{100}\NormalTok{)  }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(id,condit,vb,iter) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{vx\_pred=}\FunctionTok{mean}\NormalTok{(vx\_pred)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{vb,}\AttributeTok{y=}\NormalTok{vx\_pred,}\AttributeTok{fill=}\NormalTok{condit)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_flat\_violin}\NormalTok{( }\AttributeTok{position =} \FunctionTok{position\_nudge}\NormalTok{(}\AttributeTok{x =} \FloatTok{0.1}\NormalTok{, }\AttributeTok{y =} \DecValTok{0}\NormalTok{),}
+                   \AttributeTok{adjust =} \FloatTok{1.5}\NormalTok{,}
+                   \AttributeTok{trim =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{5}\NormalTok{, }\AttributeTok{colour =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{+}
+  \CommentTok{\# geom\_point(aes(x = as.numeric(vb) {-} 0.15, y = vx\_pred, colour = vb),}
+  \CommentTok{\#            position = position\_jitter(width = 0.05, height = 0),}
+  \CommentTok{\#            size = 1, shape = 20) +}
+  \FunctionTok{geom\_boxplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ vb, }\AttributeTok{y =}\NormalTok{ vx\_pred, }\AttributeTok{fill =}\NormalTok{ condit),}
+               \AttributeTok{outlier.shape =} \ConstantTok{NA}\NormalTok{,}
+               \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
+               \AttributeTok{width =} \FloatTok{0.1}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{,}
+             \AttributeTok{linetype =} \StringTok{\textquotesingle{}dashed\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{color =} \StringTok{\textquotesingle{}red\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{size =} \FloatTok{0.4}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Predicted Vx"}\NormalTok{)  }
+\NormalTok{\} }\SpecialCharTok{/}\NormalTok{ \{}
+\NormalTok{vx\_pred  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{2}\NormalTok{)  }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(id,condit,vb) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{vx=}\FunctionTok{mean}\NormalTok{(vx)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{vb,}\AttributeTok{y=}\NormalTok{vx,}\AttributeTok{fill=}\NormalTok{condit)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_flat\_violin}\NormalTok{( }\AttributeTok{position =} \FunctionTok{position\_nudge}\NormalTok{(}\AttributeTok{x =} \FloatTok{0.1}\NormalTok{, }\AttributeTok{y =} \DecValTok{0}\NormalTok{),}
+                   \AttributeTok{adjust =} \FloatTok{1.5}\NormalTok{,}
+                   \AttributeTok{trim =} \ConstantTok{FALSE}\NormalTok{,}
+                   \AttributeTok{alpha =}\NormalTok{ .}\DecValTok{5}\NormalTok{,}
+                   \AttributeTok{colour =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_point}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{as.numeric}\NormalTok{(vb) }\SpecialCharTok{{-}} \FloatTok{0.15}\NormalTok{,}\AttributeTok{col=}\NormalTok{condit),}
+             \CommentTok{\# position = position\_jitter(width = 0.05),}
+             \AttributeTok{position =} \FunctionTok{position\_jitter}\NormalTok{(}\AttributeTok{width =} \FloatTok{0.05}\NormalTok{, }\AttributeTok{height =} \DecValTok{0}\NormalTok{),}
+             \AttributeTok{size =} \DecValTok{1}\NormalTok{,}
+             \AttributeTok{shape =} \DecValTok{20}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_boxplot}\NormalTok{(}
+               \AttributeTok{outlier.shape =} \ConstantTok{NA}\NormalTok{,}
+               \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{,}
+               \AttributeTok{width =} \FloatTok{0.1}\NormalTok{,}
+               \AttributeTok{colour =} \StringTok{"black"}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{,}
+             \AttributeTok{linetype =} \StringTok{\textquotesingle{}dashed\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{color =} \StringTok{\textquotesingle{}red\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{size =} \FloatTok{0.4}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Empirical Vx"}\NormalTok{) }
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{igas_e1_files/figure-pdf/fig-empVsPred-1.pdf}
+
+}
+
+\caption{\label{fig-empVsPred}Bayesian Mixed Model predictions
+vs.~Empirical Predictions - X velocity}
+
+\end{figure}%
+
+\paragraph{Different Aggregations}\label{different-aggregations}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epId }\OtherTok{\textless{}{-}}\NormalTok{ dist\_pred  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{2}\NormalTok{)  }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(id,condit,vb) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{summarise}\NormalTok{(}\AttributeTok{dist=}\FunctionTok{median}\NormalTok{(dist)) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{vb,}\AttributeTok{y=}\NormalTok{dist,}\AttributeTok{fill=}\NormalTok{condit)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_flat\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{fill=}\NormalTok{condit), }\AttributeTok{position =} \FunctionTok{position\_nudge}\NormalTok{(}\AttributeTok{x =} \FloatTok{0.1}\NormalTok{, }\AttributeTok{y =} \DecValTok{0}\NormalTok{),}
+                   \AttributeTok{adjust =} \FloatTok{1.5}\NormalTok{,}\AttributeTok{trim =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{5}\NormalTok{, }\AttributeTok{colour =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_point}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{as.numeric}\NormalTok{(vb) }\SpecialCharTok{{-}} \FloatTok{0.15}\NormalTok{, }\AttributeTok{col=}\NormalTok{condit),}
+             \AttributeTok{position =} \FunctionTok{position\_jitter}\NormalTok{(}\AttributeTok{width =} \FloatTok{0.05}\NormalTok{, }\AttributeTok{height =} \DecValTok{0}\NormalTok{),}
+             \AttributeTok{size =} \DecValTok{1}\NormalTok{, }\AttributeTok{shape =} \DecValTok{20}\NormalTok{, }\AttributeTok{alpha=}\NormalTok{.}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_boxplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{vb,}\AttributeTok{y=}\NormalTok{dist,}\AttributeTok{fill=}\NormalTok{condit),}
+               \AttributeTok{outlier.shape =} \ConstantTok{NA}\NormalTok{,}
+               \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{width =} \FloatTok{0.1}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{,}
+             \AttributeTok{linetype =} \StringTok{\textquotesingle{}dashed\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{color =} \StringTok{\textquotesingle{}red\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{size =} \FloatTok{0.4}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Empirical Deviation {-} Subject level averaging"}\NormalTok{) }
+
+\NormalTok{epId }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{igas_e1_files/figure-pdf/fig-empirical-distGrp1-1.pdf}
+
+}
+
+\caption{\label{fig-empirical-distGrp1}E1. Distribution of Vx at
+Participant level}
+
+\end{figure}%
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{epTrial }\OtherTok{\textless{}{-}}\NormalTok{ dist\_pred  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{filter}\NormalTok{(iter }\SpecialCharTok{\textless{}} \DecValTok{2}\NormalTok{)  }\SpecialCharTok{|\textgreater{}} \FunctionTok{group\_by}\NormalTok{(id,condit,vb) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{vb,}\AttributeTok{y=}\NormalTok{dist,}\AttributeTok{fill=}\NormalTok{condit)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_flat\_violin}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{fill=}\NormalTok{condit), }\AttributeTok{position =} \FunctionTok{position\_nudge}\NormalTok{(}\AttributeTok{x =} \FloatTok{0.1}\NormalTok{, }\AttributeTok{y =} \DecValTok{0}\NormalTok{),}
+                   \AttributeTok{adjust =} \FloatTok{1.5}\NormalTok{,}\AttributeTok{trim =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{alpha =}\NormalTok{ .}\DecValTok{5}\NormalTok{, }\AttributeTok{colour =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_point}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{as.numeric}\NormalTok{(vb) }\SpecialCharTok{{-}} \FloatTok{0.15}\NormalTok{, }\AttributeTok{col=}\NormalTok{condit),}
+             \AttributeTok{position =} \FunctionTok{position\_jitter}\NormalTok{(}\AttributeTok{width =} \FloatTok{0.05}\NormalTok{, }\AttributeTok{height =} \DecValTok{0}\NormalTok{),}
+             \AttributeTok{size =}\NormalTok{ .}\DecValTok{5}\NormalTok{, }\AttributeTok{shape =} \DecValTok{20}\NormalTok{, }\AttributeTok{alpha=}\NormalTok{.}\DecValTok{7}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_boxplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{vb,}\AttributeTok{y=}\NormalTok{dist,}\AttributeTok{fill=}\NormalTok{condit),}
+               \AttributeTok{outlier.shape =} \ConstantTok{NA}\NormalTok{,}
+               \AttributeTok{alpha =} \FloatTok{0.5}\NormalTok{, }\AttributeTok{width =} \FloatTok{0.1}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{geom\_hline}\NormalTok{(}\AttributeTok{yintercept =} \DecValTok{0}\NormalTok{,}
+             \AttributeTok{linetype =} \StringTok{\textquotesingle{}dashed\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{color =} \StringTok{\textquotesingle{}red\textquotesingle{}}\NormalTok{,}
+             \AttributeTok{size =} \FloatTok{0.4}\NormalTok{) }\SpecialCharTok{+} 
+  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Empirical Deviation {-} Raw Trial"}\NormalTok{) }\SpecialCharTok{+}
+   \FunctionTok{theme}\NormalTok{(}\AttributeTok{axis.title.y=}\FunctionTok{element\_blank}\NormalTok{(),}
+        \AttributeTok{axis.text.y=}\FunctionTok{element\_blank}\NormalTok{())}
+
+\NormalTok{epTrial}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{igas_e1_files/figure-pdf/fig-empirical-distGrp2-1.pdf}
+
+}
+
+\caption{\label{fig-empirical-distGrp2}E1. Distribution of Vx at Trial
+level}
+
+\end{figure}%
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{new\_data\_grid}\OtherTok{=}\FunctionTok{map\_dfr}\NormalTok{(}\DecValTok{1}\NormalTok{, }\SpecialCharTok{\textasciitilde{}}\FunctionTok{data.frame}\NormalTok{(}\FunctionTok{unique}\NormalTok{(test[,}\FunctionTok{c}\NormalTok{(}\StringTok{"id"}\NormalTok{,}\StringTok{"condit"}\NormalTok{,}\StringTok{"bandInt"}\NormalTok{)])))}
+
+\NormalTok{cSamp }\OtherTok{\textless{}{-}}\NormalTok{ e1\_distBMM  }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{emmeans}\NormalTok{(}\StringTok{"condit"}\NormalTok{,}\AttributeTok{by=}\StringTok{"bandInt"}\NormalTok{,}\AttributeTok{at=}\FunctionTok{list}\NormalTok{(}\AttributeTok{bandInt=}\FunctionTok{c}\NormalTok{(}\DecValTok{100}\NormalTok{,}\DecValTok{350}\NormalTok{,}\DecValTok{600}\NormalTok{,}\DecValTok{800}\NormalTok{,}\DecValTok{1000}\NormalTok{,}\DecValTok{1200}\NormalTok{)),}
+          \AttributeTok{epred =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
+  \FunctionTok{pairs}\NormalTok{() }\SpecialCharTok{|\textgreater{}} \FunctionTok{gather\_emmeans\_draws}\NormalTok{()  }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{group\_by}\NormalTok{(contrast, .draw,bandInt) }\SpecialCharTok{|\textgreater{}} \FunctionTok{summarise}\NormalTok{(}\AttributeTok{value=}\FunctionTok{mean}\NormalTok{(.value), }\AttributeTok{n=}\FunctionTok{n}\NormalTok{())}
+
+\NormalTok{ ameBand }\OtherTok{\textless{}{-}}\NormalTok{ cSamp }\SpecialCharTok{|\textgreater{}} \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{value,}\AttributeTok{y=}\StringTok{""}\NormalTok{)) }\SpecialCharTok{+}
+  \FunctionTok{stat\_halfeye}\NormalTok{() }\SpecialCharTok{+} 
+  \FunctionTok{geom\_vline}\NormalTok{(}\AttributeTok{xintercept=}\DecValTok{0}\NormalTok{,}\AttributeTok{alpha=}\NormalTok{.}\DecValTok{4}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{bandInt,}\AttributeTok{ncol=}\DecValTok{1}\NormalTok{) }\SpecialCharTok{+} \FunctionTok{labs}\NormalTok{(}\AttributeTok{x=}\StringTok{"Marginal Effect (Constant {-} Varied)"}\NormalTok{, }\AttributeTok{y=} \ConstantTok{NULL}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Average Marginal Effect"}\NormalTok{)}
+
+\NormalTok{bothConditGM }\OtherTok{\textless{}{-}}\NormalTok{ e1\_distBMM }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{epred\_draws}\NormalTok{(}\AttributeTok{newdata =}\NormalTok{ new\_data\_grid,}\AttributeTok{ndraws =} \DecValTok{2000}\NormalTok{, }\AttributeTok{re\_formula =} \ConstantTok{NA}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{ggplot}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{.epred,}\AttributeTok{y=}\StringTok{"Mean"}\NormalTok{,}\AttributeTok{fill=}\NormalTok{condit)) }\SpecialCharTok{+}
+  \FunctionTok{stat\_halfeye}\NormalTok{() }\SpecialCharTok{+}\FunctionTok{facet\_wrap}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{bandInt, }\AttributeTok{ncol =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x=}\StringTok{"Predicted Deviation"}\NormalTok{, }\AttributeTok{y=}\ConstantTok{NULL}\NormalTok{)}\SpecialCharTok{+}
+  \FunctionTok{ggtitle}\NormalTok{(}\StringTok{"Grand Means"}\NormalTok{) }\SpecialCharTok{+}\FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position =} \StringTok{"bottom"}\NormalTok{)}
+
+\NormalTok{(bothConditGM }\SpecialCharTok{|}\NormalTok{ ameBand) }\SpecialCharTok{+} \FunctionTok{plot\_layout}\NormalTok{(}\AttributeTok{widths=}\FunctionTok{c}\NormalTok{(}\DecValTok{2}\NormalTok{,}\FloatTok{1.0}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}[H]
+
+\centering{
+
+\includegraphics{igas_e1_files/figure-pdf/fig-e1-ame-1.pdf}
+
+}
+
+\caption{\label{fig-e1-ame}E1. Predicted Means Per Condition and Band,
+and Average Marginal Effect (Constant - Varied)}
+
+\end{figure}%
 

### 2023-10-30 Manuscript/manuscript.qmd
adjust igas toy model figure

@@
 #| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization =  $e^{(c\\cdot|x-800|)}  +e^{(c\\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\\cdot e^{(c\\cdot|x-600|)}$.
+For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
 For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
 The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(cvaried\\cdot|x-800|)}  +e^{(cvaried\\cdot|x-400|)}$.
+Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
 #| fig.width: 11
-#| fig.height: 10
+#| fig.height: 11.5
 

### 2023-10-30 paper.qmd
improve format selection

@@
   <!-- </a>  -->
-
+  <br>
+  <span>Click buttons above to select format or download</span>
 </p>

### 2023-11-01 md_extract/remove_links.py
clean up repo

@@ -7,8 +7,14 @@ def remove_links(filename):
 
     new_lines = []
     for line in lines:
-        # Using regex to remove the localhost links
+        # Using regex to remove localhost links
         new_line = re.sub(r'\[([^\]]+)\]\(http://localhost:[0-9]+/[^)]+\)', r'\1', line)
+        # Using regex to remove links containing "#ref"
+        new_line = re.sub(r'\[([^\]]+)\]\([^)]*#ref[^)]*\)', r'\1', new_line)
+        new_line = re.sub(r'\[([^\]]+)\]\([^)]*#tbl[^)]*\)', r'\1', new_line)
+        new_line = re.sub(r'\[([^\]]+)\]\([^)]*#fig[^)]*\)', r'\1', new_line)
+        # Using regex to remove image links with pattern [![](image_source)](link)
+        new_line = re.sub(r'\[\!\[\]\([^\)]+\)\]\([^\)]+\)', '', new_line)
         new_lines.append(new_line)
 
     with open(filename, 'w') as file:
@@ -20,4 +26,4 @@ if __name__ == "__main__":
     else:
         filename = sys.argv[1]
         remove_links(filename)
-        print(f"Removed localhost links from {filename}.")
+        print(f"Removed localhost links, #ref links, and image links from {filename}.")

### 2023-11-11 Manuscript/igas_e1.qmd
markdown renders

@@
 
-::: {.content-visible when-format="html"}
-{{< include pre_sections/pre_html.qmd >}}
-:::
-
-::: {.content-visible when-format="pdf"}
-{{< include pre_sections/pre_pdf.qmd >}}
-:::
-
-::: {.content-visible when-format="docx"}
-{{< include pre_sections/pre_docx.qmd >}}
-:::
-
-{{< pagebreak >}}
-
 # Abstract
@@
 These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
-
-{{< pagebreak >}}
-
-::: {.content-visible when-format="html"}
-{{< include pre_sections/toc_html.qmd >}}
-:::
-
-::: {.content-visible when-format="pdf"}
-{{< include pre_sections/toc_pdf.qmd >}}
-:::
 
@@
 
+## Model Table
+
+::: {.column-page-inset-right}
+| Step | Equation | Description |
+|------|----------|-------------|
+| **ALM Activation & Response**  |           |
+| Input Activation | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$ | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.
+|
+| Output Activation                 | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$ | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.   |
+| Output Probability                | $$P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$$ | Each output node has associated response, $Y_j$.
+The probability of response $Y_j$ is determined by the ratio of output activations.
+|
+| Mean Output                       | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$   | The response to stimulus x is the weighted average of the response probabilities. |
+| **ALM Learning**                  |                                                                                                                                                          |
+| Feedback Activation               | $f_j(Z) = e^{-c(Z-Y_j)^2}$                  | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response.
+|
+| Update Weights                    | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$    | Delta rule to update weights.
+Magnitude of weight changes controlled by learning rate parameter alpha.
+|
+| **EXAM**                          |                                                                                                                                                          |
+| Extrapolation                     | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$ | Novel test stimulus X activates input nodes associated with trained stimuli.     |
+|                                   | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)    |
+: ALM & EXAM Equations {#tbl-alm-exam}
+
+:::
+
+see @tbl-alm-exam
+
 ## Main body
@@
 
-quarto pandoc --citeproc --pdf-engine xelatex -t pdf\
---bibliography=../Assets/Bib/Dissertation.bib\
---standalone\
--f markdown igas_e1.pdf.md\
--o refer-test.pdf
+## Modeling
 
-quarto render igas_e1.qmd --citeproc --pdf-engine xelatex -t pdf\
---bibliography=../Assets/Bib/Dissertation.bib\
---standalone\
--o refer-test.pdf
+In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning (DeLosh 1997).
+ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model (Kruscke 1992), with modifications to allow for the generation of continuous responses.
+
+## ALM & Exam Description
+
+@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks.
+ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].
+
+ALM is a localist neural network model, with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
+The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
+So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
+Depending on thevalue of the generalization parameter, the nearby units (e.g.
+54 and 56; 53 and 57) may also activate to some degree.
+ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
+The units in the input layer activate as a function of their similarity to a presented stimulus.
+As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
+The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
+The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
+During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
+The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
+
+See  for a full specification of the equations that define ALM and EXAM.
 

### 2023-11-11 Manuscript/manuscript.qmd
markdown renders

@@
 code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
-bibliography: ../Assets/Bib/Dissertation.bib
-link-citations: true
-# keep-md: true
 toc: false
@@
 toc-location: body
-execute: 
-  warning: false
-  eval: true
-  include: true
-  #echo: false
+# execute: 
+#   warning: false
+#   include: true
 ---
@@
 
-::: {.content-visible when-format="pdf"}
+::: {.content-visible unless-format="pdf"}
 
@@
 ```{r setup}
-#| echo: false
+
 #| 
@@
 
-knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
-                      warning = FALSE, message = FALSE, eval=TRUE)
-
-knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
-                      fig.width = 6, fig.height = (6 * 0.618),
-                      out.width = "100%", collapse = TRUE)
+# knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
+#                       warning = FALSE, message = FALSE, eval=TRUE)
+
+# knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+#                       fig.width = 6, fig.height = (6 * 0.618),
+#                       out.width = "100%", collapse = TRUE)
 # 
@@
 ```{r}
-#| echo: false
 source(here::here('Functions/IGAS_ProcessFunctions.R'))
@@
 identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
-sports training  [@greenPracticeVariabilityTransfer1995; @greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
+sports training  [@greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
 on a complex video game [@seowTransferEffectsVaried2019].
@@
 #| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
-#| echo: false
 #| fig-width: 10
@@
 #| layout-ncol: 1
-#| include: true
-#| echo: false
 
@@
 #| fig-cap: E1. Deviations from target band during testing without feedback stage. 
-#| include: true
 test |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
@@
 #| tbl-subcap: ["Constant Testing1 - Deviation", "Varied Testing - Deviation"]
-#| include: true
-#| echo: false
 modelName <- "e1_testDistBand_RF_5K"
@@
 #| fig-height: 9
-#| include: true
+
 test %>% group_by(id,vb,condit) |> plot_distByCondit()
@@
 #| tbl-cap: "Testing vx - Empirical Summary"
-#| include: true
 #| tbl-subcap: ["Constant", "Varied"]
@@
 #| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
-#| include: true
 e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
@@
 
-```{r setup2b, include=FALSE}
+```{r setup2b}
 testE2 <- readRDS(here::here("data/e2_08-21-23.rds")) |> filter(expMode2 == "Test") 
@@
 
-```{r setup3b, include=FALSE}
+```{r setup3b}
 testE3 <- readRDS(here::here("data/e3_08-21-23.rds")) |> filter(expMode2 == "Test") 
@@
 
-::: {.content-visible when-format="html"}
+::: {.content-visible unless-format="pdf"}
 # References

### 2023-11-14 HTW.qmd
adjust appendices
update with htw modelling

@@
 
-# Modeling
+### Computational Modelling
 
-In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
-In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning (DeLosh 1997).
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model (Kruscke 1992), with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks.
-ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].
-
-ALM is a localist neural network model, with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on thevalue of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-
-See  for a full specification of the equations that define ALM and EXAM.
-
-{{< pagebreak >}}
-
-## Model Table
-### ALM Activation & Response
-| Step | Equation | Description |
-|------|----------|-------------|
-| **ALM Activation & Response**  |           |
-| Input Activation | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$ | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.
-|
-| Output Activation                 | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$ | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.   |
-| Output Probability                | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$ | Each output node has associated response, $Y_j$.
-The probability of response $Y_j$ is determined by the ratio of output activations.
-|
-| Mean Output                       | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$   | The response to stimulus x is the weighted average of the response probabilities. |
-| **ALM Learning**                  |                                                                                                                                                          |
-| Feedback Activation               | $f_j(Z) = e^{-c(Z-Y_j)^2}$                  | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response.
-|
-| Update Weights                    | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$    | Delta rule to update weights.
-Magnitude of weight changes controlled by learning rate parameter alpha.
-|
-| **EXAM**                          |                                                                                                                                                          |
-| Extrapolation                     | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$ | Novel test stimulus X activates input nodes associated with trained stimuli.     |
-|                                   | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)    |
-
-{{< pagebreak >}}
-
-## Model Fitting and Comparison
-
-Following the procedure used by @mcdanielPredictingTransferPerformance2009, we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data.
-Models will be fit directly to the trial by trial data of each individual participants, both by minimizing the root-mean squared deviation (RMSE), and by maximizing log likelihood.
-Because ALM has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also fit the extended EXAM version of the model, which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.
+{{< include Sections/htw_exam.qmd >}}
 
 # References
-# References 
 <div id="refs"></div>
+
+# Appendix
+{{< include Appendix/E1_Appendix.qmd >}}

### 2023-11-14 Manuscript/igas_e1.qmd
update with htw modelling

--- 2023-10-28 Manuscript/igas_e1.qmd
@@
 code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
-bibliography: ../Assets/Bib/Dissertation.bib
-link-citations: true
-# keep-md: true
 toc: false
-# toc-depth: 3
-# toc-location: body
-execute: 
-  warning: false
-  eval: true
-  include: false
+toc-depth: 3
+toc-location: body
+# execute: 
+#   warning: false
+#   include: true
 ---
@@
 
-## Main body
+# Literature Review
 
-Following the procedure used by @mcdanielPredictingTransferPerformance2009, we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data.
-Models will be fit directly to the trial by trial data of each individual participants, both by minimizing the root-mean squared deviation (RMSE), and by maximizing log likelihood.
-Because ALM has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also fit the extended EXAM version of the model, which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.
+{{< include ../Introduction.qmd >}}
 
-quarto pandoc --citeproc --pdf-engine xelatex -t pdf \
-  --bibliography=../Assets/Bib/Dissertation.bib \
-  --standalone \
-  -f markdown igas_e1.pdf.md \
-  -o refer-test.pdf
+```{r setup}
 
-quarto render igas_e1.qmd --citeproc --pdf-engine xelatex -t pdf \
-  --bibliography=../Assets/Bib/Dissertation.bib \
-  --standalone \
-  -o refer-test.pdf
+#| 
+here::set_here(path='..')
+source(here::here("Functions", "packages.R"))
 
-# Appendix
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
 
-{{< include ../Appendix/E1_Appendix.qmd >}}
+# knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
+#                       warning = FALSE, message = FALSE, eval=TRUE)
 
-::: {.content-visible when-format="pdf"}
+# knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+#                       fig.width = 6, fig.height = (6 * 0.618),
+#                       out.width = "100%", collapse = TRUE)
+# 
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
 
-# References
+```
 
-:::
+```{r}
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+
+# load the processed data from experiment 1 and 2
+
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
+
+options(contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
+                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
+
+e1Pos <- c("610","760","835","910")
+e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
+e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
+```
+
+# Project 1
+
+## Abstract
+
+Exposing learners to variability during training has been demonstrated
+to improve performance in subsequent transfer testing. Such variability
+benefits are often accounted for by assuming that learners are
+developing some general task schema or structure. However much of this
+research has neglected to account for differences in similarity between
+varied and constant training conditions. In a between-groups
+manipulation, we trained participants on a simple projectile launching
+task, with either varied or constant conditions. We replicate previous
+findings showing a transfer advantage of varied over constant training.
+Furthermore, we show that a standard similarity model is insufficient to
+account for the benefits of variation, but, if the model is adjusted to
+assume that varied learners are tuned towards a broader generalization
+gradient, then a similarity-based model is sufficient to explain the
+observed benefits of variation. Our results therefore suggest that some
+variability benefits can be accommodated within instance-based models
+without positing the learning of some schemata or structure.
+
+## Introduction
+
+The past century of research on human learning has produced ample
+evidence that although learners can improve at almost any task, such
+improvements are often specific to the trained task, with unreliable or
+even nonexistent transfer to novel tasks or conditions
+[@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993]. Such
+transfer challenges are of noteworthy practical relevance, given that
+educators, trainers, and rehabilitators typically intend for their
+students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that
+influence transfer, and to develop cognitive models that can predict
+when transfer is likely to occur. The factor of interest to the present
+investigation is variation during training. Our experiments add to the
+longstanding empirical investigation of the controversial relationship
+between training variation, and subsequent transfer. We also offer a
+novel explanation for such results in the form of an instance-based
+model that accounts for the benefits of variation in simple terms of
+psychological similarity. We first review the relevant concepts and
+literature.
+
+### Similarity and instance-based approaches to transfer of learning
+
+Notions of similarity have long played a central role in many prominent
+models of generalization of learning, as well as in the longstanding
+theoretical issue of whether learners abstract an aggregate, summary
+representation, or if they simply store individual instances. Early
+models of learning often assumed that discrete experiences with some
+task or category were not stored individually in memory, but instead
+promoted the formation of a summary representation, often referred to as
+a prototype or schema, and that exposure to novel examples would then
+prompt the retrieval of whichever preexisting prototype was most similar
+[@posnerGenesisAbstractIdeas1968]. Prototype
+models were later challenged by the success of instance-based or
+exemplar models -- which were shown to provide an account of
+generalization as good or better than prototype models, with the
+advantage of not assuming the explicit construction of an internal
+prototype [@estesClassificationCognition1994;
+@hintzmanMINERVASimulationModel1984;
+@medinContextTheoryClassification1978;
+@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
+Instance-based models assume that learners encode each experience with a
+task as a separate instance/exemplar/trace, and that each encoded trace
+is in turn compared against novel stimuli. As the number of stored
+instances increases, so does the likelihood that some previously stored
+instance will be retrieved to aid in the performance of a novel task.
+Stored instances are retrieved in the context of novel stimuli or tasks
+if they are sufficiently similar, thus suggesting that the process of
+computing similarity is of central importance to generalization.
+
+Similarity, defined in this literature as a function of psychological
+distance between instances or categories, has provided a successful
+account of generalization across numerous tasks and domains. In an
+influential study demonstrating an ordinal similarity effect,
+experimenters employed a numerosity judgment task in which participants
+quickly report the number of dots flashed on a screen. Performance (in
+terms of response times to new patterns) on novel dot configurations
+varied as an inverse function of their similarity to previously trained
+dot configurations @palmeriExemplarSimilarityDevelopment1997. That is, performance was better on
+novel configurations moderately similar to trained configurations than
+to configurations with low-similarity, and also better on low-similarity
+configurations than to even less similar, unrelated configurations.
+Instance-based approaches have had some success accounting for
+performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017; @crumpEpisodicContributionsSequential2010] trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
+Following
+training, typing speed was tested on previously experienced words
+composed of previously experienced letters; novel words composed of
+letters from the trained letter set; and novel words composed of letters
+from an untrained letter set. Consistent with an instance-based account,
+transfer performance was graded such that participants were fastest at
+typing the words they had previously trained on, followed by novel words
+composed of letters they had trained on, and slowest performance for new
+words composed of untrained letters.
+
+## The effect of training variability on transfer
+
+While similarity-based models account for transfer by the degree of
+similarity between previous and new experiences, a largely separate body
+of research has focused on improving transfer by manipulating
+characteristics of the initial training stage. Such characteristics have
+included training difficulty, spacing, temporal order, feedback
+schedules, and the primary focus of the current work -- variability of
+training examples.
+
+Research on the effects of varied training typically compares
+participants trained under constant, or minimal variability conditions
+to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015]. Varied training has been shown to influence
+learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968],
+complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory
+extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice
+identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
+sports training  [@greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
+on a complex video game [@seowTransferEffectsVaried2019].
+
+Training variation has received a particularly large amount of attention
+within the domain of visuomotor skill learning. Much of this research
+has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a
+schema-based account of motor learning as an attempt to address the
+longstanding problem of how novel movements are produced. According to
+Schema Theory, learners possess general motor programs for classes of
+movements (e.g. throwing a ball with an underhand movement), as well as
+schema rules that determine how a motor program is parameterized or
+scaled for a particular movement. Schema theory predicts that varied
+training results in the formation of a more general schema-rule, which
+can allow for transfer to novel movements within a given movement class.
+Experiments that test this hypothesis are often designed to compare the
+transfer performance of a constant-trained group against that of a
+varied-trained group. Both groups train on the same task, but the varied
+group practices from multiple levels of a task-relevant dimension that
+remains invariant for the constant group. For example, investigators
+might train two groups of participants to throw a projectile at a
+target, with a constant group that throws from a single location, and a
+varied group that throws from multiple locations. Both groups are then
+tested from novel locations. Empirically observed benefits of the
+varied-trained group are then attributed to the variation they received
+during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically
+thought to be mediated by the development of a more general schema for
+the throwing motion.
+
+Of course, the relationship between training variability and transfer is
+unlikely to be a simple function wherein increased variation is always
+beneficial. Numerous studies have found null, or in some cases negative
+effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the
+benefits of variability may depend on additional factors such as prior
+task experience, the order of training trials, or the type of transfer
+being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+
+### Issues with Previous Research
+
+Although the benefits of training variation in visuomotor skill learning
+have been observed many times, null findings have also been repeatedly
+found, leading some researchers to question the veracity of the
+variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
+Critics have also pointed out that investigations of the effects of
+training variability, of the sort described above, often fail to control
+for the effect of similarity between training and testing conditions.
+For training tasks in which participants have numerous degrees of
+freedom (e.g. projectile throwing tasks where participants control the x
+and y velocity of the projectile), varied groups are likely to
+experience a wider range of the task space over the course of their
+training (e.g. more unique combinations of x and y velocities).
+Experimenters may attempt to account for this possibility by ensuring
+that the training location(s) of the varied and constant groups are an
+equal distance away from the eventual transfer locations, such that
+their training throws are, on average, equally similar to throws that
+would lead to good performance at the transfer locations. However, even
+this level of experimental control may still be insufficient to rule out
+the effect of similarity on transfer. Given that psychological
+similarity is typically best described as either a Gaussian or
+exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the
+most similar training instances could have a disproportionate impact on
+generalization to transfer conditions, even if the average distance
+between training and transfer conditions is identical between groups.
+@fig-toy-model1 demonstrates the consequences of a generalization gradient that
+drops off as a Gaussian function of distance from training, as compared
+to a linear drop-off.
+
+```{r}
+#| label: fig-toy-model1
+#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
+A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
+Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
+(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
+
+p=2
+c<- .0002
+simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
+                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
+                     mutate(plotjitter=ifelse(condit=="varied",0,7),
+                            linScale=ifelse(condit=="varied",980,1000),
+                            genGauss=exp(-c*(abs((x-train.position)^p))),
+                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
+  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
+  group_by(x,condit) %>%
+  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
+colorVec=c("darkblue","darkred")
+plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
+                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
+                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
+                  ylim(c(0,1.05)),
+                  #xlim(c(250,950)),
+                  scale_x_continuous(breaks=seq(200,1000,by=200)),
+                  xlab("Test Stimulus"),
+                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=450,y=.97,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=657,y=.97,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=850,y=.97,label="Training",size=3.1,fontface="plain"),
+                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
+                        legend.position="none"))
+
+ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
+ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
+
+plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
+
+```
+
+In addition to largely overlooking the potential for non-linear
+generalization to confound interpretations of training manipulations,
+the visuomotor skill learning literature also rarely considers
+alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
+Although schema-theory remains influential within certain literatures,
+instance or exemplar-based models have accounted for human behavior
+across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a]. As mentioned above, instance based accounts have been shown to perform well on a
+variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
+However, such accounts have received little
+attention within the subdomain of visuomotor skill learning focused on
+the benefits of varied training.
+
+The present work examines whether the commonly observed benefits of
+varied training can be accounted for by between-group differences in
+similarity between training and testing throws. We first attempt to
+replicate previous work finding an advantage of varied training over
+constant training in a projectile launching task. We then examine the
+extent to which this advantage can be explained by an instance-based
+similarity model.
+
+## Experiment 1
+
+### Methods
+
+#### Sample Size Estimation
+
+To obtain an independent estimate of effect size, we identified previous
+investigations which included between-subjects contrasts of varied and
+constant conditions following training on an accuracy based projectile
+launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
+We then averaged effects across these studies,
+yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
+2009) was then used to determine that a power of 80% requires a sample
+size of at least 23 participants per condition. All experiments reported
+in the present manuscript exceed this minimum number of participants per
+condition.
+
+#### Participants
+
+Participants were recruited from an undergraduate population that is 63%
+female and consists almost entirely of individuals aged 18-22 years. A
+total of 110 Indiana University psychology students participated in
+Experiment 1. We subsequently excluded 34 participants poor performance
+at one of the dependent measures of the task (2.5-3 standard deviations
+worse than the median subject at the task) or for displaying a pattern
+of responses that was clearly indicative of a lack of engagement with
+the task (e.g. simply dropping the ball on each trial rather than
+throwing it at the target), or for reporting that they completed the
+experiment on a phone or tablet device, despite the instructions not to
+use one of these devices. A total of 74 participants were retained for
+the final analyses, 35 in the varied group and 39 in the constant group.
+
+#### Task
+
+The experimental task was programmed in JavaScript, using packages from
+the Phaser physics engine (https://phaser.io) and the jsPsych library
+(de Leeuw, 2015). The stimuli, presented on a black background,
+consisted of a circular blue ball -- controlled by the participant via
+the mouse or trackpad cursor; a rectangular green target; a red
+rectangular barrier located between the ball and the target; and an
+orange square within which the participant could control the ball before
+releasing it in a throw towards the target. Because the task was
+administered online, the absolute distance between stimuli could vary
+depending on the size of the computer monitor being used, but the
+relative distance between the stimuli was held constant. Likewise, the
+distance between the center of the target, and the training and testing
+locations was scaled such that relative distances were preserved
+regardless of screen size. For the sake of brevity, subsequent mentions
+of this relative distance between stimuli, or the position where the
+ball landed in relation to the center of the target, will be referred to
+simply as distance. @fig-igasTask displays the layout of the task, as
+it would appear to a participant at the start of a trial, with the ball
+appearing in the center of the orange square. Using a mouse or trackpad,
+participants click down on the ball to take control of the ball,
+connecting the movement of the ball to the movement of the cursor.
+Participants can then "wind up" the ball by dragging it (within the
+confines of the orange square) and then launch the ball by releasing the
+cursor. If the ball does not land on the target, participants are
+presented with feedback in red text at the top right of the screen, on
+how many units away they were from the center of the target. If the ball
+was thrown outside of the boundary of the screen participants are given
+feedback as to how far away from the target center the ball would have
+been if it had continued its trajectory. If the ball strikes the barrier
+(from the side or by landing on top), feedback is presented telling
+participants to avoid hitting the barrier. If participants drag the ball
+outside of the orange square before releasing it, the trial terminates,
+and they are reminded to release the ball within the orange square. If
+the ball lands on the target, feedback is presented in green text,
+confirming that the target was hit, and presenting additional feedback
+on how many units away the ball was from the exact center of the target.
+
+[Link to abbrevaited example of
+task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+
+![The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
+On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
+Participants were constrained to release the ball within the square](../Assets/methodsFig1.png){#fig-igasTask}

### 2023-11-14 Manuscript/manuscript.qmd
update with htw modelling

@@
 
-::: {.content-visible unless-format="pdf"}
+::: {.content-visible when-format="pdf"}
 
@@
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square](Assets/methodsFig1.png){#fig-igasTask}
+Participants were constrained to release the ball within the square](../Assets/methodsFig1.png){#fig-igasTask}
 
@@
 
-# Modeling
-
-In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
-In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning (DeLosh 1997).
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model (Kruscke 1992), with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks.
-ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].
-
-ALM is a localist neural network model, with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on thevalue of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-
-See  for a full specification of the equations that define ALM and EXAM.
-
-{{< pagebreak >}}
-
-## Model Table
-### ALM Activation & Response
-| Step | Equation | Description |
-|------|----------|-------------|
-| **ALM Activation & Response**  |           |
-| Input Activation | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$ | Activation of each input node $X_i$, is a function of the Gaussian similarity between the node value and stimulus X.
-|
-| Output Activation                 | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$ | Activation of each Output unit $O_j$ is the weighted sum of the input activations and association weights.   |
-| Output Probability                | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$ | Each output node has associated response, $Y_j$.
-The probability of response $Y_j$ is determined by the ratio of output activations.
-|
-| Mean Output                       | $m(x) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$   | The response to stimulus x is the weighted average of the response probabilities. |
-| **ALM Learning**                  |                                                                                                                                                          |
-| Feedback Activation               | $f_j(Z) = e^{-c(Z-Y_j)^2}$                  | After responding, feedback signal Z is presented, activating each output node via the Gaussian similarity to the ideal response.
-|
-| Update Weights                    | $w_{ji}(t + 1) = w_{ji}(t) + \alpha \cdot (f_j(Z(t)) - O_j(X(t)) \cdot a_i(X(t))$    | Delta rule to update weights.
-Magnitude of weight changes controlled by learning rate parameter alpha.
-|
-| **EXAM**                          |                                                                                                                                                          |
-| Extrapolation                     | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$ | Novel test stimulus X activates input nodes associated with trained stimuli.     |
-|                                   | $E[Y|X_i] = m(X_i) + \frac{m(X_{i+1})-m(X_{i-1})}{X_{i+1}-X_{i-1}} \cdot [X - X_i]$ | Slope value computed from nearest training instances and then added to the response associated with the nearest training instance,m(x)    |
-
-{{< pagebreak >}}
-
-## Model Fitting and Comparison
-
-Following the procedure used by @mcdanielPredictingTransferPerformance2009, we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data.
-Models will be fit directly to the trial by trial data of each individual participants, both by minimizing the root-mean squared deviation (RMSE), and by maximizing log likelihood.
-Because ALM has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also fit the extended EXAM version of the model, which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.
-
-{{< pagebreak >}}
+### Computational Modelling
+
+{{< include ../Sections/htw_exam.qmd >}}
 

### 2023-11-14 Sections/htw_exam.qmd
update with htw modelling

---
# title: EXAM Fits and Predictions
date: last-modified
categories: [Simulation, ALM, EXAM, R]
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

```{r}
# load and view data
pacman::p_load(tidyverse,patchwork,here, pander, latex2exp, flextable)
purrr::walk(here::here(c("Functions/Display_Functions.R", "Functions/alm_core.R","Functions/misc_model_funs.R")),source)

purrr::walk(here::here(c("Functions/Display_Functions.R")),source)

select <- dplyr::select; mutate <- dplyr::mutate

ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))
dsAvg <- ds |> group_by(condit,expMode2,tr, x) |> 
  summarise(y=mean(y),.groups="keep")

vAvg <- dsAvg |> filter(condit=="Varied")
cAvg <- dsAvg |> filter(condit=="Constant")

#i1 <- ds |> filter(id=="3")

input.layer <- c(100,350,600,800,1000,1200)
output.layer <- c(100,350,600,800,1000,1200)

purrr::walk(c("con_group_exam_fits", "var_group_exam_fits", "hybrid_group_exam_fits"), 
            ~ list2env(readRDS(here::here(paste0("data/model_cache/", .x, ".rds"))), 
            envir = .GlobalEnv))

# pluck(ex_te_v, "Fit") |> mutate(w= ifelse(exists("w"), round(w,2),NA))
# pluck(hybrid_te_v, "Fit") |> mutate(w= ifelse(exists("w"), round(w,2), NA))
```

```{r}
#| label: fig-alm-diagram
#| fig.cap: The basic structure of the ALM model. 
 alm_plot()
```

{{< pagebreak >}}

::: column-page-inset-right

|                    | **ALM Response Generation**                                            |                                                                                               |
|------------------|------------------------------|-------------------------|
| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
|                    | **ALM Learning**                                                   |                                                                                               |
| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
|                    | **EXAM Extrapolation**                                             |                                                                                               |
| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                              |
| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                          | ALM response $m(X_i)$ adjusted by slope.                                                      |

: ALM & EXAM Equations {#tbl-alm-exam}
:::

{{< pagebreak >}}

# Modeling

In project 1, I applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model. In project 2, I will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment. For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning (DeLosh 1997). ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model (Kruscke 1992), with modifications to allow for the generation of continuous responses.

## ALM & Exam Description

@deloshExtrapolationSineQua1997 introduced the associative learning model (ALM), a connectionist model within the popular class of radial-basis networks. ALM was inspired by, and closely resembles Kruschke's influential ALCOVE model of categorization [@kruschkeALCOVEExemplarbasedConnectionist1992].

ALM is a localist neural network model, with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value. The units in the input layer activate as a function of their Gaussian similarity to the input stimulus. So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55. Depending on thevalue of the generalization parameter, the nearby units (e.g. 54 and 56; 53 and 57) may also activate to some degree. ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively. The units in the input layer activate as a function of their similarity to a presented stimulus. As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance. The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations. The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response). During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response. The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.

See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM.

## Model Fitting and Comparison

Following the procedure used by @mcdanielPredictingTransferPerformance2009, we will assess the ability of both ALM and EXAM to account for the empirical data when fitting the models to 1) only the training data, and 2) both training and testing data. Models were fit to the aggregated participant data by minimizing the root-mean squared deviation (RMSE). Because ALM has been shown to do poorly at accounting for human patterns extrapolation [@deloshExtrapolationSineQua1997], we will also generate predictions from the EXAM model for the testing stage. EXAM which operates identically to ALM during training, but includes a linear extrapolation mechanism for generating novel responses during testing.

For the hybrid model, predictions are computed by first generating separate predictions from ALM and EXAM, and then combining them using the following equation: $\hat{y} = (1 - w) \cdot alm.pred + w \cdot exam.pred$. For the grid search, the weight parameter is varied from 0 to 1, and the resulting RMSE is recorded.

Each model was fit to the data in 3 different ways. 1) To just the testing data, 2) Both the training and testing data, 3) Only the training data. In all cases, the model only updates its weights during the training phase, and the weights are frozen during the testing phase. In all cases, only the ALM model generates predictions during the training phase. For the testing phase, all 3 models are used to generate predictions.

{{< pagebreak >}}

```{r}
#| echo: false
create_combined_df <- function(model_names, model_data, group) {
  combined_df <- do.call(rbind, Map(function(name, data) {
    model<- ifelse(grepl("Hybrid", name), "Hybrid", ifelse(grepl("EXAM", name), "EXAM", "ALM"))
    fit_method <- gsub(".*(Test Only|Test & Train|Train Only).*", "\\1", name)
    extract_params(model, data, group, fit_method)
  }, model_names, model_data))
  row.names(combined_df) <- NULL
  combined_df
}

# Adjust the extract_params function to accept and include the fit_method parameter
extract_params <- function(model_name, model_data, group, fit_method) {
  params_df <- cbind(Model = model_name, Group = group, Fit_Method = fit_method,
                     pluck(model_data, "Fit"), pluck(model_data, "test") |>
                     summarise(Test_RMSE = round(RMSE(y, pred),0))) |>
                     mutate(across(where(is.numeric), \(x) round(x, 3))) |>
                     mutate(w= ifelse(exists("w"), round(w,2), NA))
  return(params_df)
}

model_classes <- c("ALM", "EXAM", "Hybrid")
model_names <- c("ALM Test Only", "ALM Test & Train", "ALM Train Only", "EXAM Test Only", "EXAM Test & Train", "EXAM Train Only", "Hybrid Test Only", "Hybrid Test & Train", "Hybrid Train Only")

model_data_v <- list(a_te_v, a_tetr_v, a_tr_v, ex_te_v, ex_tetr_v, ex_tr_v, hybrid_te_v, hybrid_tetr_v, hybrid_tr_v)
model_data_c <- list(a_te_c, a_tetr_c, a_tr_c, ex0_te_c, ex0_tetr_c, ex0_tr_c, hybrid_te_c, hybrid_tetr_c, hybrid_tr_c)

combined_params_v <- create_combined_df(model_names, model_data_v, "Varied")
combined_params_c <- create_combined_df(model_names, model_data_c, "Constant")
all_combined_params <- rbind(combined_params_c,combined_params_v)

```

```{r}
#| label: tbl-e1-cogmodel
#| tbl-cap: Fit Parameters and Model RMSE. The Test_RMSE column is the main performance indicator of interest, and represents the RMSE for just the testing data. The Fit_Method column indicates the data used to fit the model. The $w$ parameter determines the balance between the ALM and EXAM response generation processes, and is only included for the hybrid model. A weight of .5 would indicate equal contribution from both models. $w$ values approaching 1 indicate stronger weight for EXAM. 
##| column: body-outset-right

reshaped_df <- all_combined_params %>%
  select(-Value,-Test_RMSE) |>
  rename("Fit Method" = Fit_Method) |>
  pivot_longer(cols=c(c,lr,w),names_to="Parameter") %>%
  unite(Group, Group, Parameter) %>%
  pivot_wider(names_from = Group, values_from = value)

header_df <- data.frame(
  col_keys = c("Model", "Fit Method","Constant_c", "Constant_lr", "Constant_w", "Varied_c", "Varied_lr", "Varied_w"),
  line1 = c("", "", "Constant", "", "", "Varied", "",""),
  line2 = c("Model", "Fit Method", "c", "lr", "w", "c", "lr", "w")
)

ft <- flextable(reshaped_df) %>% 
  set_header_df(
    mapping = header_df,
    key = "col_keys"
  ) %>% add_header_lines(values = " ") %>%
  theme_booktabs() %>% 
  merge_v(part = "header") %>% 
  merge_h(part = "header") %>%
  merge_h(part = "header") %>%
  align(align = "center", part = "all") %>% 
  #autofit() %>% 
  empty_blanks() %>% 
  fix_border_issues() %>% 
  hline(part = "header", i = 2, j=3:5) %>% 
  hline(part = "header", i = 2, j=6:8)

ft

```

### Testing Observations vs. Predictions

```{r}
tvte<- pluck(a_te_v, "test") |> 
  mutate(Fit_Method="Test Only") |>
  rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred))

tvtetr<-pluck(a_tetr_v, "test") |> 
  mutate(Fit_Method="Test & Train") |> 
  rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred))

tvtr<- pluck(a_tr_v, "test")|> 
  mutate(Fit_Method="Train Only") |> 
  rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred))

tcte<- pluck(a_te_c, "test") |> 
  mutate(Fit_Method="Test Only") |> 
  rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred))

tctetr<-pluck(a_tetr_c, "test") |> 
  mutate(Fit_Method="Test & Train") |>  
  rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tetr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_c, "test") |> pull(pred))

tctr<- pluck(a_tr_c, "test")|> 
  mutate(Fit_Method="Train Only") |>  
  rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_c, "test") |> pull(pred))

vPreds <- rbind(tvte,tvtetr, tvtr) |> relocate(Fit_Method,.before=x) |> 
   mutate(across(where(is.numeric), \(x) round(x, 0)))

cPreds <- rbind(tcte,tctetr, tctr) |> relocate(Fit_Method,.before=x) |> 
   mutate(across(where(is.numeric), \(x) round(x, 0)))

allPreds <- rbind(vPreds |> mutate(Group="Varied"), cPreds |> mutate(Group="Constant")) |>
  pivot_longer(cols=c("ALM","EXAM","Hybrid"), names_to="Model",values_to = "Prediction") |> 
  mutate(Error=Observed-Prediction, Abs_Error=((Error)^2)) |> 
  group_by(Group,Fit_Method, Model) #|> summarise(Mean_Error=mean(Error), Abs_Error=mean(Abs_Error))

```

```{r}
#| label: tbl-e1-meanPreds
#| tbl-cap: Model Perforamnce - averaged over all X values/Bands. ME=Mean Average Error, RMSE = Root mean squared error. 
#| warning: false

allPreds |> summarise(Error=mean(Error), Abs_Error=sqrt(mean(Abs_Error))) |> 
  mutate(Fit_Method=factor(Fit_Method, levels=c("Test Only", "Test & Train", "Train Only"))) |>
  tabulator(rows=c("Fit_Method", "Model"), columns=c("Group"), 
             `ME` = as_paragraph(Error), 
            `RMSE` = as_paragraph(Abs_Error)) |> as_flextable()
```

## Varied Testing Predictions
```{r}
#| label: fig-model-preds-varied
#| fig-cap: Varied Group - Mean Model predictions vs. observations
#| fig-height: 12
#| fig-width: 14
##| column: screen-inset-right

####

vte <-  pluck(a_te_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_te_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test Only")

vtetr <-  pluck(a_tetr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tetr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") + 
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test and Train")

vtr <-  pluck(a_tr_v, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex_tr_v, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_v, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Train Only")

 vte/vtetr/vtr

```

```{r fig.height=11, fig.width=11}
#| label: tbl-e1-predsV
#| tbl-cap: Varied group - mean model predictions vs. observations. Extrapolation Bands are bolded. For each Modelling fitting and band combination, the model with the smallest residual is highlighted. Only the lower bound of each velocity band is shown (bands are all 200 units). 
##| column: screen-inset-right

# Create a custom header dataframe
header_df <- data.frame(
  col_keys = c("Fit_Method", "x","Observed" ,"ALM_Predicted", "ALM_Residual", "EXAM_Predicted","EXAM_Residual", "Hybrid_Predicted","Hybrid_Residual"),
  line1 = c("","","", "ALM", "", "EXAM", "", "Hybrid",""),
  line2 = c("Fit Method", "X", "Observed", "Predicted","Residual", "Predicted","Residual", "Predicted","Residual")
)

best_vPreds <- vPreds %>%
  pivot_longer(cols = c(ALM, EXAM, Hybrid), names_to = "Model", values_to = "Predicted") |>
  mutate(Residual=(Observed-Predicted), abs_res =abs(Residual)) |> group_by(Fit_Method,x) |>
  mutate(best=if_else(abs_res==min(abs_res),1,0)) |> select(-abs_res)

long_vPreds <- best_vPreds |> select(-best) |>
  pivot_longer(cols=c(Predicted,Residual), names_to="Model_Perf") |>
  relocate(Model, .after=Fit_Method) |> 
  unite(Model,Model,Model_Perf) |>
  pivot_wider(names_from=Model,values_from=value)

best_wide <- best_vPreds |> select(-Residual,-Predicted,-Observed) |> ungroup() |>
  pivot_wider(names_from=Model,values_from=best) |> select(ALM,EXAM,Hybrid)

best_indexV <- row_indices <- apply(best_wide, 1, function(row) {
 which(row == 1)
})

apply_best_formatting <- function(ft, best_index) {
  for (i in 1:length(best_index)) {
      #ft <- ft %>% surround(i=i,j=best_index[i],border=fp_border_default(color="red",width=1))
      ind = best_index[[i]]
      ind <- ind  %>% map_dbl(~ .x*2+3)
      ft <- ft %>% highlight(i=i,j=ind,color="wheat")
      }
  return(ft)
}

ft <- flextable(long_vPreds) %>% 
  set_header_df(
    mapping = header_df,
    key = "col_keys"
  ) %>% 
  theme_booktabs() %>% 
  merge_v(part = "header") %>% 
  merge_h(part = "header") %>%
  align(align = "center", part = "all") %>% 
  #autofit() %>% 
  empty_blanks() %>% 
  fix_border_issues() %>%
  hline(part = "header", i = 1, j=4:9) %>%
  vline(j=c("Observed","ALM_Residual","EXAM_Residual")) %>%
  hline(part = "body", i=c(6,12)) |> 
  bold(i=long_vPreds$x %in% c(100,350,600), j=2)

  # bold the cell with the lowest residual, based on best_wide df
  # for each row, the cell that should be bolded matches which column in best_wide==1 at that row
ft <- apply_best_formatting(ft, best_indexV)
ft

```

```{r}
#| eval: false
pander(tvte, caption="Varied fit to test only")
pander(tvtetr,caption="Varied fit to train and test")
pander(tvtr,caption="Varied fit to train only")
```

## Constant Testing Predictions
```{r}
#| label: fig-model-preds-constant
#| fig-cap: Constant Group - Mean Model predictions vs. observations
#| fig-height: 12
#| fig-width: 14
##| column: screen-inset-right

####

cte <-  pluck(a_te_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_te_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_te_c, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test Only")

ctetr <-  pluck(a_tetr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tetr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tetr_c, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") + 
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Test and Train")

ctr <-  pluck(a_tr_c, "test") |> rename(ALM=pred,Observed=y) %>% 
  cbind(.,EXAM=pluck(ex0_tr_c, "test") |> pull(pred)) %>%
  cbind(., Hybrid=pluck(hybrid_tr_c, "test") |> pull(pred)) |>  
  pivot_longer(Observed:Hybrid, names_to="Model", values_to = "vx") |> 
  ggplot(aes(x,vx,fill=Model, group=Model)) +geom_bar(position="dodge",stat="identity") +
  scale_fill_manual(values=col_themes$wes2)+
  scale_x_continuous(breaks=sort(unique(ds$x)), labels=sort(unique(ds$x)))+ylim(0,1500) +
  theme(legend.title = element_blank(), legend.position="top") +ggtitle("Fit to Train Only")

cte/ctetr/ctr

```

```{r}
#| label: tbl-e1-predsC
#| tbl-cap: Constant group - mean model predictions vs. observations. The X values of Extrapolation Bands are bolded. For each Modelling fitting and band combination, the model with the smallest residual is highlighted. Only the lower bound of each velocity band is shown (bands are all 200 units). 
##| column: screen-inset-right

best_cPreds <- cPreds %>%
  pivot_longer(cols = c(ALM, EXAM, Hybrid), names_to = "Model", values_to = "Predicted") |>
  mutate(Residual=(Observed-Predicted), abs_res =abs(Residual)) |> group_by(Fit_Method,x) |>
  mutate(best=if_else(abs_res==min(abs_res),1,0)) |> select(-abs_res)

long_cPreds <- best_cPreds |> select(-best) |>
  pivot_longer(cols=c(Predicted,Residual), names_to="Model_Perf") |>
  relocate(Model, .after=Fit_Method) |> 
  unite(Model,Model,Model_Perf) |>
  pivot_wider(names_from=Model,values_from=value)

best_wideC <- best_cPreds |> select(-Residual,-Predicted,-Observed) |> ungroup() |>
  pivot_wider(names_from=Model,values_from=best) |> select(ALM,EXAM,Hybrid)

best_indexC <- row_indices <- apply(best_wideC, 1, function(row) {
 which(row == 1)
})

ft <- flextable(long_cPreds) %>% 
  set_header_df(
    mapping = header_df,
    key = "col_keys"
  ) %>% 
  theme_booktabs() %>% 
  merge_v(part = "header") %>% 
  merge_h(part = "header") %>%
  align(align = "center", part = "all") %>% 
  #autofit() %>% 
  empty_blanks() %>% 
  fix_border_issues() %>%
  hline(part = "header", i = 1, j=4:9) %>%
  vline(j=c("Observed","ALM_Residual","EXAM_Residual")) %>%
  hline(part = "body", i=c(6,12)) |> 
  bold(i=long_cPreds$x %in% c(100,350,600, 1000,1200), j=2)

  # bold the cell with the lowest residual, based on best_wide df
  # for each row, the cell that should be bolded matches which column in best_wide==1 at that row

ft <- apply_best_formatting(ft, best_indexC)
ft

```

```{r}

```

```{r}
#| eval: false
#| include: false
pluck(a_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  learn_curve_plot(tr, vx, Resp,facet_var=x, groupVec=Resp,nbins=8)

pluck(a_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  ungroup() %>%
  gather(key = "variable", value = "y_value", dev, abs_dev, vx) %>%
  group_by(variable) %>%
  group_map(~ learn_curve_plot(.x, x_var = tr, y_var = y_value, color_var = Resp, facet_var = x, groupVec = Resp, nbins = 8, y_label = .y$variable), .keep = TRUE)

list(a_tr_v, a_te_v,a_tetr_v) |> map( ~{pluck(.x, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  ungroup() %>%
  gather(key = "variable", value = "y_value", dev, abs_dev, vx) %>%
  group_by(variable) %>%
  group_map(~ learn_curve_plot(.x, x_var = tr, y_var = y_value, color_var = Resp, facet_var = x, groupVec = Resp, nbins = 8, y_label = .y$variable), .keep = TRUE) })

```

# EXAM fit learning curves
```{r}
#| eval: false
#| include: false
pluck(ex_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  learn_curve_plot(tr, vx, Resp,facet_var=x, groupVec=Resp,nbins=8)

pluck(ex_te_v, "train") |> pivot_longer(y:almResp, names_to="Resp", values_to = "vx") |> 
  mutate(dev=x-vx,abs_dev=abs(x-vx)) |>
  ungroup() %>%
  gather(key = "variable", value = "y_value", dev, abs_dev, vx) %>%
  group_by(variable) %>%
  group_map(~ learn_curve_plot(.x, x_var = tr, y_var = y_value, color_var = Resp, facet_var = x, groupVec = Resp, nbins = 8, y_label = .y$variable), .keep = TRUE)

```

```{r}
#| eval: false
#| include: false

optimize_params_weighted_individual <- function(ds, c_values, lr_values, weight_exam_values, input.layer, output.layer) {
    all_results <- list()

    # Loop through each unique id
    for (individual in unique(ds$id)) {
        indiv_data <- ds[ds$id == individual, ]

        # Run the optimization function for the individual's data
        result <- optimize_params_weighted(indiv_data, c_values, lr_values, weight_exam_values, input.layer, output.layer)

        all_results[[as.character(individual)]] <- result
    }

    all_results
}

dss <- ds |> filter(id %in% c(1,2))

all_results_weighted_hybrid <- readRDS(here::here('data/model_cache/indv_hybrid_fits.rds'))
ma <- map(all_results_weighted_hybrid, "best_params") |> map("c")

data.frame(id=names(ma),c=as.numeric(ma))

ma = cbind(id=names(all_results_weighted_hybrid),map(all_results_weighted_hybrid, "best_params") |> map_dfr(magrittr::extract,c("c","lr","weight_exam")))

ds |> group_by(id,condit) |> distinct(id,condit) |> left_join(ma,by=join_by(id))

map(all_results_weighted_hybrid,"best_params") |> pluck("c")
all_results_weighted_hybrid[["1"]]$b

 map(~ map(.x$best_params, pluck, "c"))

 map_df(~ map_df(.x$train, pluck, "d"), .id = "density")
```

### 2023-11-14 Functions/Display_Functions.R

@@ -9,6 +9,78 @@ mutate <- dplyr::mutate
 filter <- dplyr::filter
 map <- purrr::map
 
+
+
+
+alm_plot <- function (){
+  pacman::p_load(tidyverse,ggplot2,igraph,ggraph) 
+
+inNodes <- c("exp(c * (100 - Stim)^2)", "exp(c * (350 - Stim)^2)", 
+             "exp(c * (600 - Stim)^2)", "exp(c * (800 - Stim)^2)", 
+             "exp(c * (1000 - Stim)^2)", "exp(c * (1200 - Stim)^2)")
+
+outNodes <- c(100,350,600,800,1000,1200) %>% as.integer()
+stim <- "Stim"
+resp <- "Response"
+inFlow <- tibble(expand.grid(from=stim,to=inNodes)) %>% mutate_all(as.character)
+outFlow <- tibble(expand.grid(from=outNodes,to=resp)) %>% mutate_all(as.character)
+
+gd <- tibble(expand.grid(from=inNodes,to=outNodes)) %>% mutate_all(as.character) %>%
+  rbind(inFlow,.) %>% rbind(.,outFlow)
+
+g = graph_from_data_frame(gd,directed=TRUE)
+coords2=layout_as_tree(g)
+colnames(coords2)=c("y","x")
+
+odf <- as_tibble(coords2) %>% 
+  mutate(label=vertex_attr(g,"name"),
+         type=c("stim",rep("Input",length(inNodes)),rep("Output",length(outNodes)),"Resp"),
+         x=x*-1) %>%
+  mutate(y=ifelse(type=="Resp",0,y),
+         # Adjust the width of input nodes
+         xmin=ifelse(type=="Input", x-0.3, x-0.08),
+         xmax=ifelse(type=="Input", x+0.3, x+0.08),
+         ymin=y-.30, ymax=y+.30)
+
+input_y <- odf %>% filter(type == "Input") %>% pull(y)
+output_y <- odf %>% filter(type == "Output") %>% pull(y)
+avg_input_y <- mean(input_y)
+avg_output_y <- mean(output_y)
+y_adjustment <- avg_input_y - avg_output_y
+odf <- odf %>%
+  mutate(y = ifelse(type == "Output", y + y_adjustment, y), 
+         ymax = ifelse(type == "Output", ymax + y_adjustment, ymax),
+         ymin = ifelse(type == "Output", ymin + y_adjustment, ymin))
+
+
+plot_edges = gd %>% mutate(id=row_number()) %>%
[…]

### 2023-11-14 Functions/alm_core.R

@@ -1,0 +1,242 @@
+
+
+wrap_grid <- function(dat, c_values, lr_values, input.layer, output.layer,
+                            predParams=list(pred_dat="test_avg", pred_fun="exam.response", loss_fun="RMSE", loss_data="test_error")) {
+  
+  # Precompute as much as possible outside the loop
+  train_data <- dat[dat$expMode2 == "Train", ]
+  test_data <- dat[dat$expMode2 == "Test", ] 
+  test_avg <- test_data |> group_by(x) |> summarise(y=mean(y))
+  trainVec <- sort(c(0,unique(train_data$x)))
+  
+  pred_dat <- get(predParams$pred_dat)
+  pred_fun <- match.fun(predParams$pred_fun)
+  loss_fun <- match.fun(predParams$loss_fun)
+  
+  # Create a grid dataframe with preallocated space
+  grid <- expand.grid(c = c_values, lr = lr_values, Value = NA_real_)
+  
+  # Use future_map (parallel version of map) to iterate over rows in the grid
+  loop_time <-  system.time({ 
+    results <- future_map_dfr(seq_len(nrow(grid)), function(i) {
+      c <- grid$c[i]
+      lr <- grid$lr[i]
+      train_results <- alm.sim(train_data, c, lr, input.layer, output.layer)
+      weight.mat <- train_results$wm
+      
+      train_error <- loss_fun(train_results$d$x, train_results$d$almResp)
+      test_prediction <- map_dbl(pred_dat$x, ~ pred_fun(.x, c, input.layer, output.layer, weight.mat,  trainVec=trainVec))
+      test_error <- loss_fun(test_prediction, pred_dat$y)
+      
+      error <- eval(parse(text=predParams$loss_data)) 
+      
+      tibble(c = c, lr = lr, Value = error)  # Return a tibble with the results
+    })
+  })# stop timer
+  
+  min_value <- min(results$Value, na.rm = TRUE)
+  
+  # Check if the minimum value occurs more than once
+  if(sum(results$Value == min_value, na.rm = TRUE) > 1 && !is.nan(min_value)) {
+    warning("The minimum value in the grid occurs more than once.")
+  }
+  
+  # Extract the best fit parameters
+  bestFit <- results[which.min(results$Value), ] |>  mutate(across(where(is.numeric), \(x) round(x, 5)))
+  
[…]

### 2023-11-14 Functions/misc_model_funs.R

@@ -1,0 +1,52 @@
+
+
+
+adjust_layer <- function(input.layer, k){
+  if(k == 1) return(input.layer)
+  new.layer <- c()
+  for(i in 1:(length(input.layer) - 1)){
+    new.layer <- c(new.layer, seq(input.layer[i], input.layer[i+1], length.out = k + 1))
+  }
+  new.layer <- unique(new.layer)
+  return(new.layer)
+}
+
+
+### Loss Functions
+
+#  mse <- mean((predictions - test_data$y)^2)
+
+RMSE <- function(x,y){
+ # print("rmseTrial")
+  sqrt(mean((x-y)^2, na.rm=TRUE))
+}
+
+RMSE.blocked <- function(x,y,blocks=6){
+  #print("rmseBlocked")
+  data.table(x=x,y=y,t=seq(1,length(x))) %>% 
+    .[, `:=`(fitBins = cut(t, breaks = ..blocks, labels = c(1:..blocks)))] %>%
+    .[, .(predMean = mean(x), obsMean = mean(y)), keyby = .(fitBins)] %>%
+    .[, RMSE(predMean,obsMean)] %>% as.numeric()
+}
+
+MAE <- function(x, y) {
+  mean(abs(x - y))
+}
+
+MAPE <- function(x, y) {
+  mean(abs((x - y) / y)) * 100
+}
+
+MedAE <- function(x, y) {
+  median(abs(x - y))
+}
+
+HuberLoss <- function(x, y, delta = 1) {
+  error <- x - y
+  abs_error <- abs(error)
+  loss <- ifelse(abs_error <= delta, 0.5 * error^2, delta * (abs_error - 0.5 * delta))
+  mean(loss)
+}
+
+
+

### 2023-11-14 Manuscript/manuscript.qmd
partial fix

@@
 toc-location: body
-# execute: 
-#   warning: false
-#   include: true
+execute: 
+  warning: false
+  include: true
 ---

### 2023-11-14 Manuscript/Appendix/IGAS-Supplemental.qmd
move appendix

--- 2023-10-29 Appendix/IGAS-Supplemental.qmd
@@
 
-```{r, include=FALSE, echo=FALSE}
+```{r, setupP1_A, include=FALSE}
+here::set_here(path='..')
 source(here::here('Functions/IGAS_ProcessFunctions.R'))
@@
 ```{r}
+#| label: fig-igas-a1
 
@@
 
-h4<-e2TestFits %>% ggplot(aes(x=positionX,y=pRate,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("Learning rates ")+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+ylab("Inverse Learning Rate")+xlab("Testing Location")
-h4
+# h4<-e2TestFits %>% ggplot(aes(x=positionX,y=pRate,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ggtitle("Learning rates ")+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+ylab("Inverse Learning Rate")+xlab("Testing Location")
+# h4
 
@@
 ```{r}
+#| fig.height: 8 
+#| fig.width: 10
 
@@
  scale_y_continuous(name="Mean Absolute Deviation From Target",limits=c(0,400))+ 
- ggtitle("Testing Performance - 1st half")+
-  ylab("Mean Absolute Deviation From Target")+xlab("Testing Location")+theme(legend.position="none")
+ ggtitle("Testing - 1st half")+
+  ylab("Mean Absolute Deviation From Target")+xlab("Testing Location")+theme(legend.position="top")
 
 h2=testSplit %>% filter(testHalfSbj=="2nd-Half") %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
- geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8) + 
+ geom_bar(aes(group=conditType,fill=conditType),stat="summary",position=dodge,fun="mean")+
+  stat_summary(aes(x=positionX,group=conditType),fun.data=mean_se,geom="errorbar",position=dodge,width=.8) + 
  scale_y_continuous(name="",limits=c(0,400))+ 
- ggtitle("Testing Performance - 2nd half")+
-  xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+
+ ggtitle("Testing - 2nd half")+
+  xlab("Testing Location")+
+  theme(plot.title = element_text(hjust = 0.5))+
+  theme(legend.position="top") +
   guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
@@
   ylab("2nd Half Deviation - 1st Half Deviation")+ 
-  ggtitle("Improvement Per Testing Location")+
+  ggtitle("Improvement Per Location")+
   xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Testing Location"))+theme(legend.position="none")
+  guides(fill=guide_legend(title="Testing Location")) +theme(legend.position="none")
 
@@
 
-(h1 + h2) / (h3 + h4)
+#(h1 + h2) / (h3)
+
+(h1+h2)/h3
 

### 2024-02-28 Sections/Discussion.qmd
re-render

---
title: General Discussion
date: today
---

test

### 2024-02-28 Sections/IGAS.qmd
re-render

--- 2023-10-30 IGAS.qmd
@@
 ```{r}
-pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)
-source('Functions/IGAS_ProcessFunctions.R')
+pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork,here)
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
 
@@
 # load the processed data from experiment 1 and 2
-e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
 # load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
 
@@
 
-mf <- cowplot::ggdraw()+cowplot::draw_image("Assets/methodsFig1.png",hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
+mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
 plot_grid(mf,ncol=1)

### 2024-02-28 Sections/htw_exam.qmd
partial fix
re-render

@@
 # title: EXAM Fits and Predictions
-date: last-modified
-categories: [Simulation, ALM, EXAM, R]
+# date: last-modified
+# categories: [Simulation, ALM, EXAM, R]
 code-fold: true

### 2024-02-28 Appendix/.vdoc.r

@@ -1,539 +1,0 @@
-#
-#
-#
-#
-#
-#
-#
-#
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-#rm(list=ls())
-###### data loading and organization #######
-
-# load the processed data from experiment 1 and 2
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-
-options(contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
[…]

### 2024-03-24 Sections/IGAS.qmd
changes from awhile ago that weren't pushed. looks like formatting mainly

@@
 
-Exposing learners to variability during training has been demonstrated
-to improve performance in subsequent transfer testing. Such variability
-benefits are often accounted for by assuming that learners are
-developing some general task schema or structure. However much of this
-research has neglected to account for differences in similarity between
-varied and constant training conditions. In a between-groups
-manipulation, we trained participants on a simple projectile launching
-task, with either varied or constant conditions. We replicate previous
-findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to
-account for the benefits of variation, but, if the model is adjusted to
-assume that varied learners are tuned towards a broader generalization
-gradient, then a similarity-based model is sufficient to explain the
-observed benefits of variation. Our results therefore suggest that some
-variability benefits can be accommodated within instance-based models
-without positing the learning of some schemata or structure.
+Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
+Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
+However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
+In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
+We replicate previous findings showing a transfer advantage of varied over constant training.
+Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
+Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
 
@@
 
-The past century of research on human learning has produced ample
-evidence that although learners can improve at almost any task, such
-improvements are often specific to the trained task, with unreliable or
-even nonexistent transfer to novel tasks or conditions
-[@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993]. Such
-transfer challenges are of noteworthy practical relevance, given that
-educators, trainers, and rehabilitators typically intend for their
-students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that
-influence transfer, and to develop cognitive models that can predict
-when transfer is likely to occur. The factor of interest to the present
-investigation is variation during training. Our experiments add to the
-longstanding empirical investigation of the controversial relationship
-between training variation, and subsequent transfer. We also offer a
-novel explanation for such results in the form of an instance-based
-model that accounts for the benefits of variation in simple terms of
-psychological similarity. We first review the relevant concepts and
-literature.
+The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
+Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
+The factor of interest to the present investigation is variation during training.
+Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
+We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
+We first review the relevant concepts and literature.
 
@@
 
-Notions of similarity have long played a central role in many prominent
-models of generalization of learning, as well as in the longstanding
-theoretical issue of whether learners abstract an aggregate, summary
-representation, or if they simply store individual instances. Early
-models of learning often assumed that discrete experiences with some
-task or category were not stored individually in memory, but instead
-promoted the formation of a summary representation, often referred to as
-a prototype or schema, and that exposure to novel examples would then
-prompt the retrieval of whichever preexisting prototype was most similar
-[@posnerGenesisAbstractIdeas1968]. Prototype
-models were later challenged by the success of instance-based or
-exemplar models -- which were shown to provide an account of
-generalization as good or better than prototype models, with the
-advantage of not assuming the explicit construction of an internal
-prototype [@estesClassificationCognition1994;
-@hintzmanMINERVASimulationModel1984;
-@medinContextTheoryClassification1978;
+Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances.
+Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar [@posnerGenesisAbstractIdeas1968].
+Prototype models were later challenged by the success of instance-based or exemplar models -- which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978;
 @nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a
-task as a separate instance/exemplar/trace, and that each encoded trace
-is in turn compared against novel stimuli. As the number of stored
-instances increases, so does the likelihood that some previously stored
-instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks
-if they are sufficiently similar, thus suggesting that the process of
-computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological
-distance between instances or categories, has provided a successful
-account of generalization across numerous tasks and domains. In an
-influential study demonstrating an ordinal similarity effect,
-experimenters employed a numerosity judgment task in which participants
-quickly report the number of dots flashed on a screen. Performance (in
-terms of response times to new patterns) on novel dot configurations
-varied as an inverse function of their similarity to previously trained
-dot configurations @palmeriExemplarSimilarityDevelopment1997. That is, performance was better on
-novel configurations moderately similar to trained configurations than
-to configurations with low-similarity, and also better on low-similarity
-configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for
-performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017; @crumpEpisodicContributionsSequential2010] trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following
-training, typing speed was tested on previously experienced words
-composed of previously experienced letters; novel words composed of
-letters from the trained letter set; and novel words composed of letters
-from an untrained letter set. Consistent with an instance-based account,
-transfer performance was graded such that participants were fastest at
-typing the words they had previously trained on, followed by novel words
-composed of letters they had trained on, and slowest performance for new
-words composed of untrained letters.
+Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli.
+As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
+Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
+
+Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
+In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
+Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
+That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
+Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
+@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
+Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
+Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
 
@@
 
-While similarity-based models account for transfer by the degree of
-similarity between previous and new experiences, a largely separate body
-of research has focused on improving transfer by manipulating
-characteristics of the initial training stage. Such characteristics have
-included training difficulty, spacing, temporal order, feedback
-schedules, and the primary focus of the current work -- variability of
-training examples.
-
-Research on the effects of varied training typically compares
-participants trained under constant, or minimal variability conditions
-to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015]. Varied training has been shown to influence
-learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968],
-complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory
-extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice
-identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
-sports training  [@greenPracticeVariabilityTransfer1995; @greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
-on a complex video game [@seowTransferEffectsVaried2019].
-
-Training variation has received a particularly large amount of attention
-within the domain of visuomotor skill learning. Much of this research
-has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a
-schema-based account of motor learning as an attempt to address the
-longstanding problem of how novel movements are produced. According to
-Schema Theory, learners possess general motor programs for classes of
-movements (e.g. throwing a ball with an underhand movement), as well as
-schema rules that determine how a motor program is parameterized or
-scaled for a particular movement. Schema theory predicts that varied
-training results in the formation of a more general schema-rule, which
-can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the
-transfer performance of a constant-trained group against that of a
-varied-trained group. Both groups train on the same task, but the varied
-group practices from multiple levels of a task-relevant dimension that
-remains invariant for the constant group. For example, investigators
-might train two groups of participants to throw a projectile at a
-target, with a constant group that throws from a single location, and a
-varied group that throws from multiple locations. Both groups are then
-tested from novel locations. Empirically observed benefits of the
-varied-trained group are then attributed to the variation they received
-during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically
-thought to be mediated by the development of a more general schema for
-the throwing motion.
-
-Of course, the relationship between training variability and transfer is
-unlikely to be a simple function wherein increased variation is always
-beneficial. Numerous studies have found null, or in some cases negative
-effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the
-benefits of variability may depend on additional factors such as prior
-task experience, the order of training trials, or the type of transfer
-being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
+Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work -- variability of training examples.
+
+Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
+Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+
+Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
+Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
+throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
+Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
+Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
+Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
+For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
+Both groups are then tested from novel locations.
+Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
 
@@
 
-Although the benefits of training variation in visuomotor skill learning
-have been observed many times, null findings have also been repeatedly
-found, leading some researchers to question the veracity of the
-variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of
-training variability, of the sort described above, often fail to control
-for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of
-freedom (e.g. projectile throwing tasks where participants control the x
-and y velocity of the projectile), varied groups are likely to
-experience a wider range of the task space over the course of their
-training (e.g. more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring
-that the training location(s) of the varied and constant groups are an
-equal distance away from the eventual transfer locations, such that
-their training throws are, on average, equally similar to throws that
-would lead to good performance at the transfer locations. However, even
-this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer. Given that psychological
-similarity is typically best described as either a Gaussian or
-exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the
-most similar training instances could have a disproportionate impact on
-generalization to transfer conditions, even if the average distance
-between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that
-drops off as a Gaussian function of distance from training, as compared
-to a linear drop-off.
+Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
+Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
+For training tasks in which participants have numerous degrees of freedom (e.g.
+projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
+more unique combinations of x and y velocities).
+Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
+However, even this level of experimental control may still be insufficient to rule out
+the effect of similarity on transfer.
+Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
+@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
 
@@
 
-In addition to largely overlooking the potential for non-linear
-generalization to confound interpretations of training manipulations,
-the visuomotor skill learning literature also rarely considers
-alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
+In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
 Although schema-theory remains influential within certain literatures,
 instance or exemplar-based models have accounted for human behavior
-across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a]. As mentioned above, instance based accounts have been shown to perform well on a
-variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little
-attention within the subdomain of visuomotor skill learning focused on
-the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of
-varied training can be accounted for by between-group differences in
-similarity between training and testing throws. We first attempt to
-replicate previous work finding an advantage of varied training over
-constant training in a projectile launching task. We then examine the
-extent to which this advantage can be explained by an instance-based
-similarity model.
+across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
+As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
+However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
+
+The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
+We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
+We then examine the extent to which this advantage can be explained by an instance-based similarity model.
 
@@
 
-As mentioned above, the idea that learners flexibly adjust their
-generalization gradient based on prior experience does have precedent in
-the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed
-that a simple manipulation of background knowledge during a
-categorization test resulted in participants generalizing their training
-experience more or less broadly, and moreover that such a pattern could
-be captured by allowing the generalization parameter of an
-instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted
-for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006]. However, to the best of our
-knowledge, IGAS is the first instance-based similarity model that has
-been put forward to account for the effect of varied training in a
-visuomotor skill task. Although IGAS was inspired by work in the domain
-of category learning, its success in a distinct domain may not be
-surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common
-principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001a; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning
-implementations of instance-based models in several ways. One such
-difference is the nature of the training instances that are assumed to
-be stored. In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define
-a category item (e.g. size/color/shape). Rather than defining instances
-in terms of what stimuli learners experience, our approach assumes that
-stored, motor instances reflect how they act, in terms of the velocity
+As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
+@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
+The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been
+trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
+However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
+Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least
+certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001a; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
+
+Our modelling approach does differ from category learning implementations of instance-based models in several ways.
+One such difference is the nature of the training instances that are assumed to be stored.
+In category learning studies, instances are represented as
+points in a multidimensional space of all of the attributes that define a category item (e.g.
+size/color/shape).
+Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity
 applied to the ball on each throw. An advantage of many motor learning

### 2024-04-02 Sections/HTW.qmd
update htw page

---
title: HTW Project
date: last-modified
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
execute: 
  warning: false
  eval: true
---

_______________________________________________________________________________
[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

_______________________________________________________________________________

# Introduction

A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization. One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022]. The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014]. The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ]. The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.

## Function Learning and Extrapolation

The study of human function learning investigates how people learn relationships between continuous input and output values.  Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].

@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning. Input stimuli and output responses were both lines of varying length. The correct output response was related to the length of the input line by a linear, quadratic, or random function.  Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall. Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function. Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions. Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree. @kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes). In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function. Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.

The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .  In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function. Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials. All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials. Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.

The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning). The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.  The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.

The authors also introduced two new function-learning models. The Associative Learning Model (ALM) and the extrapolation-association model (EXAM). ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992]. ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance. The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism. When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope. ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate. EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants. Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.

### Variability and Function Learning

The influence of variability on function learning tasks has received relatively little attention.  The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant. They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.

In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response. The shapes ranged from very spiky to completely circular at the extreme ends of the space. Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space. Learning was significantly slower in the higher variation group. However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.  The authors accounted for both learning and extrapolation performance with a Bayesian learning model. Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli. However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.

```{r}
#| label: fig-delosh-extrap
#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
#| echo: false
#| fig-width: 10
pacman::p_load(dplyr,ggplot2,patchwork) 
source(here::here("Functions","deLosh_data.R"))
source(here::here("Functions","Display_Functions.R"))

extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))

linear_function <- function(x) 2.2 * x + 30
exponential_function <- function(x) 200 * (1 - exp(-x/25))
quadratic_function <- function(x) 210 - (x - 50)^2 / 12

linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines

exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
  extrapLines +
  scale_shape_manual(values = c(1)) +
  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
  theme(legend.title = element_blank(), legend.position="top") +
  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
                                                  linetype = c(0, 1))))

quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
  geom_point( shape = 1) +
  stat_function( fun = quadratic_function, geom = "line") +
  labs(title="Quadratic Function",x="",y="") + extrapLines

linear_plot + exponential_plot + quadratic_plot
```

## Overview Of Present Study

The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task. To the best of our knowledge, this research is the first to employ the classic constant vs. varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task. Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.

To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM). Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.

## Methods

*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course. Participants were randomly assigned to one of two training conditions: varied training or constant training.

*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library. The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task). The target velocities were given as a range, or band, of acceptable velocity values  (e.g. band 800-1000). During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band. Participants were instructed that only the x velocity component of the ball was relevant to the task. The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.

/
```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
#| label: fig-htw-task
#| fig-cap: The Hit the wall task. Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen. The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback. 
#| eval: true
#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))

```

*Procedure.* All participants completed the task online. Participants were provided with a description of the experiment and indicated informed consent. @fig-design-e1 illustrates the general procedure. Participants completed a total of 90 trials during the training stage. In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400). Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.

Following the training stage, participants proceeded immediately to the testing stage. Participants were tested from all six velocity bands, in two separate stages.  In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials. Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400). In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training. The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).

```{dot}
//| label: fig-design-e1
//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
//| fig-width: 7.0
//| fig-height: 2.5
//| fig-responsive: false
/////| column: screen-inset-right
digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled]

  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1

  subgraph cluster {
    label = "Test Phase \n(Counterbalanced Order)"
    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }

  Test2 -> Test3
}
```

```{r}

pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
  stringr, here,conflicted, patchwork, knitr)
#options(brms.backend="cmdstanr",mc.cores=4)
options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
e1 <- readRDS(here("data/e1_08-21-23.rds")) 
e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
testE1 <- e1 |> filter(expMode2 == "Test")
nbins=5
trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
```

### Analyses Strategy

All data processing and statistical analyses were performed in R version 4.32 @rcoreteamLanguageEnvironmentStatistical2020. To assess differences between groups, we used Bayesian Mixed Effects Regression. Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019. Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level. Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.

Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains. Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots). We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects. For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).

| Group Comparison         | Code                                                        | Data                 |
| ------------------------ | ----------------------------------------------------------- | -------------------- |
| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
\

In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs. extrapolation bands); 3) extent of discrimination between all six testing bands. We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band. Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively. The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity. Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.

### Results

```{r}
#| label: fig-e1-train-dev
#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    facet_wrap(~vb)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
p1
```

```{r}
##| label: tbl-e1-train-dist
##| tbl-cap: "Experiment 1 - Learning curves. "
##| output: asis

bmm_e1_train<- trainE1_max %>% 
  brm(dist ~ condit, 
      file=here("data/model_cache/e1_train_deviation"),
      data = .,
      iter = 2000,
      chains = 4,
      control = list(adapt_delta = .94, max_treedepth = 13))
mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
#   tibble::remove_rownames() |> 
#   mutate(Term = stringr::str_remove(Term, "b_")) |>
#    kable(booktabs = TRUE)

cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
```

::: {#tbl-e1-train-dist}

| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
|:-------------|---------:|--------------:|--------------:|----:|
| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
| conditVaried |    79.64 |         57.92 |        101.63 |   1 |

: **Experiment 1 - End of training performance**. The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups. A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.  {.sm}

:::

\

*Training*. @fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band. To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on. The full model results are shown in Table 1. The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).

```{r}
##| label: tbl-e1-bmm-dist
##| tbl-cap: "E1. Training vs. Extrapolation"
#| 
modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
    data=testE1, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
# posterior_summary(bmtd,variable=r_bandInt_params)
# 
# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
# posterior_summary(bmtd,variable=r_bandInt_params)

# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
#   tibble::remove_rownames() |> 
#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
cdted1 <- get_coef_details(bmtd, "conditVaried")
cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
```

::: {#tbl-e1-bmm-dist}

| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
|:------------------------|-----------:|-----------:|-----------:|-----------:|
| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |

: **Experiment 1 testing accuracy**. Main effects of condition and band type (training vs. extrapolation), and the interaction between the two factors. Larger coefficients  indicate larger deviations from the baselines (Condition=constant & bandType=Trained) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
:::

*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs. constant) and band type (trained vs. extrapolation), with random intercepts for participants and bands. The model results are shown in @tbl-e1-bmm-dist. The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`). The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`). Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.

```{r}
#| label: fig-e1-test-dev
#| fig-cap:  A) Deviations from target band during testing without feedback stage. B) Conditional effect of condition (Constant vs. Varied) and testing band type (training vs. extrapolation) on testing accuracy. Error bars represent 95% credible intervals.

pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}

pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")

p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
p2

```

```{r}
##| label: tbl-e1-bmm-vx
##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))

#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)

cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
sc1 <- get_coef_details(e1_vxBMM, "bandInt")
intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
```

\

::: {#tbl-e1-bmm-vx}

| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:-------------|---------:|--------------:|--------------:|-----:|
| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |

Experiment 1. Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs. Varied) and Velocity Band. Larger coefficients on Band represent greater sensitivity/discrimination.  {.striped .hover .sm}
:::

Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant. See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition. This difference is depicted visually in @fig-e1-test-vx.

```{r}
#| label: fig-e1-test-vx
#| fig-cap: Empirical distribution of velocities producing in testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9

testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()

```

```{r}
#| label: tbl-e1-bmm-vx
#| fig-cap: Experiment 1. Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 9
#| fig-width: 11

pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE1$vb), 
                     limits = c(0, 1400)) + 
  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

fe <- fixef(e1_vxBMM)[,1]
fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]

re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
  rownames_to_column("id") |> 
  left_join(e1Sbjs,by="id") |>
  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )

pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
  geom_density(alpha=.5) + 
  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
   theme(legend.title=element_blank()) + 
  labs(x="Slope Coefficient",y="Density")

pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
     theme(legend.title=element_blank(), 
           axis.text.y = element_text(size=6) ) + 
    labs(x="Estimated Slope", y="Participant")  + 
    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")

p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
p3
```

## E1 Summary

In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task. Our findings that training with variable conditions  rresulted in lower final training performance is consistent with much of the prior researchon the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.

More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.

## Experiment 2

```{r}

walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
e2 <- readRDS(here("data/e2_08-04-23.rds")) 
e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
testE2 <- e2 |> filter(expMode2 == "Test")
nbins=5
trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)

# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
```

### Methods & Procedure

The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2). The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800. Both groups were tested from all six bands. A total of 110 participants completed the experiment (Varied: 55, Constant: 55).

```{dot}
//| label: fig-design-e2
//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
//| fig-width: 8.0
//| fig-height: 2.5
//| fig-responsive: false
//| 
//| 
/////| column: screen-inset-right
digraph {
  graph [layout = dot, rankdir = LR]
  node [shape = rectangle, style = filled]
  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
  data1 -> Test1
  data2 -> Test1
  subgraph cluster {
    label = "Test Phase \n(Counterbalanced Order)"
    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }
  Test2 -> Test3
}
```

### Results

```{r}
#| label: fig-e2-train-dev
#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
#| eval: TRUE
p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    facet_wrap(~vb)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
p1
```

```{r}
bmm_e2_train <- trainE2_max %>% 
  brm(dist ~ condit, 
      file=here("data/model_cache/e2_train_deviation"),
      data = .,
      iter = 2000,
      chains = 4,
      control = list(adapt_delta = .94, max_treedepth = 13))

mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")

cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
#   tibble::remove_rownames() |> 
#   mutate(Term = stringr::str_remove(Term, "b_")) |>
#   kable(escape=F,booktabs=T) 
```

::: {#tbl-e2-train-dist}

| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
|:-------------|---------:|--------------:|--------------:|----:|
| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
| conditVaried |    36.15 |         16.35 |         55.67 |   1 |

: **Experiment 2 - End of training performance**. The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups. A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.  {.sm}

:::

\

*Training*. @fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups. We again compared training performance on the band common to both groups (600-800). The full model results are shown in Table 1. The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
```{r}
modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
    data=testE2, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
#   tibble::remove_rownames() |> 
#   mutate(Term = stringr::str_remove(Term, "b_")) |>
#   kable(booktabs=TRUE)

cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
```

::: {#tbl-e2-bmm-dist}

| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:-----------------------------------|---------:|--------------:|--------------:|-----:|
| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |

: **Experiment 2 testing accuracy**. Main effects of condition and band type (training vs. extrapolation), and the interaction between the two factors. Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
:::
\ \

*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs. Constant) and band type (training vs. extrapolation bands). The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`). However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).

```{r}
#| label: fig-e2-test-dev
#| fig-cap:  A) Deviations from target band during testing without feedback stage. B) Estimated marginal means for the interaction between training condition and band type. Error bars represent 95% confidence intervals.
#| eval: TRUE

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}
pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")

p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
p2
```

```{r}
##| label: tbl-e2-bmm-vx
##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"

e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))

#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")

cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
sc2 <- get_coef_details(e2_vxBMM, "bandInt")
intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
```

::: {#tbl-e2-bmm-vx}

| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:-------------|---------:|--------------:|--------------:|-----:|
| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |

Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
:::

*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant. The full model results are shown in @tbl-e2-bmm-vx. The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands. The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).

```{r}
#| label: fig-e2-test-vx
#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()

```

```{r}
#| label: tbl-e2-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 9
#| fig-width: 11

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
}

pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE2$vb), 
                     limits = c(0, 1400)) + 
scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

fe <- fixef(e2_vxBMM)[,1]
fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]

re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
  rownames_to_column("id") |> 
  left_join(e2Sbjs,by="id") |>
  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )

pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
  geom_density(alpha=.5) + 
  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
   theme(legend.title=element_blank()) + 
  labs(x="Slope Coefficient",y="Density")

pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
      theme(legend.title=element_blank(), 
        axis.text.y = element_text(size=6) ) + 
    labs(x="Estimated Slope", y="Participant")  + 
    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")

p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
p3
```

### Experiment 2 Summary

Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands. Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing. However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.

## Experiment 3

```{r}

e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
    mutate(trainCon=case_when(
    bandOrder=="Original" ~ "800",
    bandOrder=="Reverse" ~ "600",
    TRUE ~ NA_character_
    ), trainCon=as.numeric(trainCon)) 
e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
testE3 <- e3 |> filter(expMode2 == "Test")
nbins=5
trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)

```

### Methods & Procedure

The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments. After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e. within the target velocity range). All other aspects of the task and design are identical to Experiments 1 and 2. We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied). Participants were once again recruited from the online Indiana University Introductory Psychology Course pool. Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.

### Results

```{r}

bmm_e3_train <- trainE3_max %>% 
  brm(dist ~ condit*bandOrder, 
      file=here("data/model_cache/e3_train_deviation"),
      data = .,
      iter = 2000,
      chains = 4,
      control = list(adapt_delta = .94, max_treedepth = 13))

# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
#   tibble::remove_rownames() |> 
#   mutate(Term = stringr::str_remove(Term, "b_")) |>
#   kable(escape=F,booktabs=T)

cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
```

::: {#tbl-e3-train-dist}

| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:------------------------------|---------:|--------------:|--------------:|-----:|
| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |

: **Experiment 3 - End of training performance**. The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups. A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.  {.sm}

:::

*Training*. @fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions). The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`). The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).

```{r}
#| label: fig-e3-train-dev
#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
#| eval: true
p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
p1
```

```{r}
#options(brms.backend="cmdstanr",mc.cores=4)
modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
    data=testE3, file=modelFile,
    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))

# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
#   tibble::remove_rownames() |> 
#   mutate(Term = stringr::str_remove(Term, "b_")) |>
#   kable(booktabs=TRUE)

#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
#wrap_plots(ce_bmtd3)

#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")

cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")

```

::: {#tbl-e3-bmm-dist}
| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
| conditVaried:bandTypeExtrapolation                  |    52.66 |         14.16 |         90.23 | 1.00 |
| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |

: **Experiment 3 testing accuracy**. Main effects of condition and band type (training vs. extrapolation), and the interaction between the two factors. Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
:::

*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage. There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`. However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`. The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group. There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands. No other interactions were significant.

<!-- ::: {#fig-e3-test-condEffect}

![](../Assets/figs/e3_cond_effects_dist.png)

E3. A) Deviations from target band during testing without feedback stage. B) Estimated marginal means for the interaction between training condition and band type. Error bars represent 95% confidence intervals.
::: -->

```{r}
#| label: fig-e3-test-dev
#| fig-cap: Experiment 3 Testing Accuracy. A) Deviations from target band during testing without feedback stage. B) Conditional effect of condition (Constant vs. Varied) and testing band type (training vs. extrapolation) on testing accuracy. Error bars represent 95% confidence intervals.
#| eval: true

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}

pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
    facet_wrap(~bandOrder,ncol=1) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
 facet_wrap(~bandOrder,ncol=1)

p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
p2
```

```{r}
##| label: tbl-e3-bmm-vx
##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"

e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))

# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
# m2 <- fixef(e3_vxBMM)
# mp3 <- m1[, c(1,2,4,5,6)]
# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
#   tibble::remove_rownames() |> 
#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
#   mutate(Term = stringr::str_remove(Term, "b_")) |>
#   kable(escape=F,booktabs=T)

#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))

cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
sc1 <- get_coef_details(e3_vxBMM, "bandInt")
intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")

```

::: {#tbl-e3-bmm-vx}

| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
|:----------------------------------------|---------:|--------------:|--------------:|-----:|
| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |

Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
:::

*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist. For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest. The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`. Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`. However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating that the varied condition showed a greater slope coefficient on the reverse order bands, compared to the constant condition - this is clearly shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 10
##| column: screen-inset-right
# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")

testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
```

```{r}
#| label: fig-e3-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 10
#| fig-width: 11
##| eval: FALSE
# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}

pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |> 
  condEffects(bandInt) +
  facet_wrap(~bandOrder,ncol=1) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE3$vb), 
                     limits = c(0, 1400)) + 
scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
  theme(legend.title=element_blank()) + 
  labs(y="Velcoity", x="Band")

fe <- fixef(e3_vxBMM)[,1]
fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]

re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
  rownames_to_column("id") |> 
  left_join(e3Sbjs,by="id") |>
  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
           fixed_effect_interaction2*(bandOrder=="Reverse") + 
           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
  slope = Estimate + adjust )

pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
  geom_density(alpha=.5) + 
  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
   theme(legend.title=element_blank()) + 
  labs(x="Slope Coefficient",y="Density") +
  facet_wrap(~bandOrder,ncol=1)

pid_slopes3 <- re |>  
    mutate(id=reorder(id,slope)) |>
  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
    theme(legend.title=element_blank(), 
      axis.text.y = element_text(size=6) ) + 
    labs(x="Estimated Slope", y="Participant")  + 
    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")

p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')

#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
p3

```

### Experiment 3 Summary

## Computational Model

```{r}
#| cache: false
pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
#walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
#options(brms.backend="cmdstanr",mc.cores=4)
options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
```

```{r}
#| cache: true
invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
invisible(list2env(load_e1(), envir = .GlobalEnv))
e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
e2_model <- load_e2()
e3_model <- load_e3()
```

```{r}
#| label: fig-alm-diagram
#| fig.cap: The Associative Learning Model (ALM). The diagram illustrates the basic structure of the ALM model as used in the present work. Input nodes are activated as a function of their similarity to the lower-boundary of the target band. The generalization parameter, $c$, determines the degree to which nearby input nodes are activated. The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule. 
alm_plot()
```

# Modeling Approach

The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment. For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997]. ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.

## ALM & Exam Description

ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value. The units in the input layer activate as a function of their Gaussian similarity to the input stimulus. So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55. Depending on the value of the generalization parameter, the nearby units (e.g. 54 and 56; 53 and 57) may also activate to some degree. ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively. The units in the input layer activate as a function of their similarity to a presented stimulus. As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance. The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations. The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response). During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response. The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter. The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units. EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses. Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training. EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points. The slope is then used to extrapolate the response to the novel test stimulus. Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group. We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group. This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).

See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.

::: column-page-inset-right
|                    | **ALM Response Generation**                                        |                                                                                               |
|------------------|-----------------------------|-------------------------|
| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
|                    | **ALM Learning**                                                   |                                                                                               |
| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
|                    | **EXAM Extrapolation**                                             |                                                                                               |
| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |

: ALM & EXAM Equations {#tbl-alm-exam}
:::

## Model Fitting

To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data. Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data. We refer to this fitting manipulations as "Fit Method" in the tables and figures below. It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant. The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters. Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.

::: {.callout}

**{{< fa regular lightbulb >}} Approximate Bayesian Computation**

To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual. ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019]. Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g. many neural network models).

The general ABC procedure is to 1) define a prior distribution over model parameters. 2) sample candidate parameter values, $\theta^*$, from the prior. 3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$. 4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$). 5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$. 6) Repeat until desired number of posterior samples are obtained.

Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data. For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018]. For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands. For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group). After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train). For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.

::: column-page-inset-left
$$
discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
$$ {#eq-discrep-test}

$$
\begin{aligned} \\
discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
\end{aligned}
$$ {#eq-discrep-train}
:::

The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$. The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution. Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution. Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual. The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values. Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected. After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%. In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far. To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
:::

For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution. Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant. Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs. To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.

### Modelling Results

#### Group level Patterns

```{r}
#| label: tbl-htw-modelError-e1
#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands. Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
post_tabs <- abc_tables(post_dat,post_dat_l)
train_tab <- abc_train_tables(pd_train,pd_train_l)

e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))

e1_tab %>%
  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
  summarize(ME = mean(mean_error), .groups = "drop") %>%
  pivot_wider(
    names_from = c(Model, condit),
    values_from = ME,
    names_sep = "_"  # Add this line to specify the separator for column names
  ) %>%
  rename("Fit Method" = Fit_Method) %>%
  gt() %>%
  cols_move_to_start(columns = c(`Task Stage`)) %>%
  cols_label(
    `Task Stage` = "Task Stage"
  ) %>%
  fmt_number(
    columns = starts_with("ALM") | starts_with("EXAM"),
    decimals = 2
  ) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = cell_fill(color = "white"),
     locations = cells_body(columns = everything(), rows = everything())
  ) %>%
  tab_style(
    style = cell_borders(sides = "top", color = "black", weight = px(1)),
    locations = cells_column_labels()
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.font.size = 10, 
    quarto.disable_processing = TRUE
  ) 
```

```{r}
#| label: fig-htw-post-dist
#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters. Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median. Note that the y axes of the plots for the c parameter are scaled logarithmically."
#| fig-height: 6
#| fig-width: 10

c_post <- post_dat_avg %>%
    group_by(id, condit, Model, Fit_Method, rank) %>%
    slice_head(n = 1) |>
    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))

lr_post <- post_dat_avg %>%
    group_by(id, condit, Model, Fit_Method, rank) %>%
    slice_head(n = 1) |>
    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
c_post + lr_post
```

```{r}
#| label: fig-htw-resid-pred
#| fig-cap: "Model residuals for each combination of training condition, fit method, and model. Residuals reflect the difference between observed and predicted values. Lower values indicate better model fit. Note that y axes are scaled differently between facets. A) Residuals predicting each block of the training data. B) Residuals predicting each band during the testing stage. Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
#| fig-height: 14
#| fig-width: 11

train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
  group_by(id,condit,Model,Fit_Method,Block) |>
  summarise(mean_error=mean(mean_error)) |>
  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
  stat_bar + 
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
   scale_x_discrete(guide = "axis_nested") +
  scale_fill_manual(values=c("gray10","gray50","gray92"))+
  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
  theme(legend.position="top")

test_resid <-  post_dat |> 
   group_by(id,condit,x,Model,Fit_Method,bandType) |>
    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
  scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .5), guide = "none") +
  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")

(train_resid / test_resid) +
  #plot_layout(heights=c(1,1.5)) & 
  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
```

The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat. There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences. The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.

We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model. Aggregated residuals are displayed in @fig-htw-resid-pred. The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method . Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms). The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models. It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task. Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories. However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data. All subsequent analyses and discussion will thus focus on the testing stage.

The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots). Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods. The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models. Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.

```{r}
#| label: fig-cm-vx-pat
#| fig-cap: "Empirical data and Model predictions for mean velocity across target bands. Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs. Varied) are separated by columns. Each facet contains the predictions of ALM and EXAM, alongside the observed data."
#| fig-height: 10
#| fig-width: 10

post_dat_l |> 
  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
 summarize(vx=median(val)) |> 
 #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
 ggplot(aes(x=Resp,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar + 
    facet_wrap(~rename_fm(Fit_Method)+condit, ncol=2,strip.position = "top", scales = "free_x") +
        scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .5), guide = "none") +
    theme(panel.spacing = unit(0, "lines"), 
         strip.background = element_blank(),
         strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(10,0,0,0), "pt")) + 
         labs(title="Model Predictions - Experiment 1 Data", y="Vx")
```

```{r}
#| label: fig-ee-e1
#| fig-caption: conditional and marginal effects
#| fig-height: 8
#| fig-width: 10

pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
e1_ee_brm_ae <- brm(data=pdl,
  aerror ~  Model * condit + (1+bandInt|id), 
  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))

bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
  select(1,2,4,5,6) %>%
  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
  tibble::remove_rownames() %>%
  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)

#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))

p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
  ggplot2::xlab("Condition") +ylab("Model Error")
p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
  labs(x="Model",y=NULL)
p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
  scale_color_manual(values=wes_palette("Darjeeling1")) +
  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")

bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")

posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
  select(starts_with("b_")) %>%
  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))

constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
comparison_EXAM <- constant_EXAM - varied_EXAM
summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")

# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)

# full set of Model x condit contrasts
# ALM - EXAM
btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
  pluck("contrasts") |> 
  gather_emmeans_draws() |> 
  group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())

# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()

# Constant - Varied
emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
  group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
# btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()

p_em_1<- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
  pluck("contrasts") |>
  gather_emmeans_draws() |> 
  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")

p_ce_1 / p_em_1
```

To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs. EXAM) and training condition (Constant vs. Varied).

Model errors were significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM.  There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group. To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM. The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).

```{r}
#| label: tbl-htw-modelError-e23
#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands. Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."

post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)

pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

e2_tab <- rbind(post_tabs2$agg_pred_full |>
 mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
 mutate("Task Stage"="Train")) |> 
  mutate(Fit_Method=rename_fm(Fit_Method))

post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)

pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))

e3_tab <- rbind(post_tabs3$agg_pred_full |> 
  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
  mutate(Fit_Method=rename_fm(Fit_Method))

e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
gt_table <- e23_tab %>%
  pivot_wider(
    names_from = c(Exp, Model, condit),
    values_from = mean_error,
    names_glue = "{Exp}_{Model}_{condit}"
  ) %>%
  arrange(Fit_Method, `Task Stage`) %>%
  gt() %>%
  cols_move_to_start(columns = `Task Stage`) %>%
  cols_label(`Task Stage` = "Task Stage") %>%
  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
  tab_spanner_delim(delim = "_") %>%
  tab_style(
    style = list(
      cell_fill(color = "white"),
      cell_borders(sides = "top", color = "black", weight = px(1))
    ),
    locations = cells_body(columns = everything(), rows = everything())
  ) %>%
  tab_options(
    column_labels.font.size = 10,
    heading.title.font.size = 14,
    heading.subtitle.font.size = 12,
    table.font.size = 10,
    quarto.disable_processing = TRUE
  ) 
gt_table
```

```{r}
#| label: fig-cm-vx-pat-e2-e3
#| fig-height: 8
#| fig-width: 10
#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage. Observed data is shown on the right. Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."

rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
 summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
 e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
  stat_bar + 
    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
    scale_color_manual(values = c("black" = "black"), guide = "none") +
  scale_size_manual(values = c("black" = .7), guide = "none") +
    theme(panel.spacing = unit(0, "lines"), 
        #  strip.background = element_blank(),
        #  strip.placement = "outside",
         legend.position = "none",plot.title = element_text(hjust=.50),
         axis.title.x = element_blank(),
         plot.margin = unit(c(20,0,0,0), "pt")) + 
         labs(title="Model Predictions Experiment 2 & 3", y="vx")
```

```{r}
#| label: tbl-htw-ee-e23
#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs. EXAM), Condition (Constant vs. Varied), and the interaction between Model and Condition. The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.  The intercept reflects the baseline of ALM and Constant. The other estimates indicate deviations from the baseline for the EXAM mode and varied condition. Lower values indicate better model fit."

e2_ee_brm_ae <- brm(data=pdl2,
  aerror ~  Model * condit + (1+bandInt|id), 
  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))

bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")

bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
  select(1,2,4,5,6) %>%
  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
  tibble::remove_rownames() %>%
  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)

e3_ee_brm_ae <- brm(data=pdl3,
  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))

bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")

bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
  select(1,2,4,5,6) %>%
  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
  tibble::remove_rownames() %>%
  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)

bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
  relocate(exp, .before=Term)

bct_table <- bct %>%
  mutate(
    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
    pd = round(pd, 2)
  ) %>%
  gt() %>%
  # tab_header(
  #   title = "Bayesian Model Results",
  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
  # ) %>%
  cols_label(
    exp = "Experiment",
    Term = "Term",
    Estimate = "Estimate",
    `95% CrI Lower` = "95% CrI Lower",
    `95% CrI Upper` = "95% CrI Upper",
    pd = "pd"
  ) %>%
  fmt_number(
    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
    decimals = 2
  ) %>%
  fmt_number(
    columns = pd,
    decimals = 2
  ) %>%
  tab_spanner(
    label = "Credible Interval",
    columns = c(`95% CrI Lower`, `95% CrI Upper`)
  ) %>%
  tab_style(
    style = list(
      #cell_fill(color = "lightgray"),
      cell_text(weight = "bold"), 
      cell_fill(color = "white"),
      cell_borders(sides = "top", color = "black", weight = px(1))
    ),
    locations = cells_body(
      columns = c(Estimate, pd),
      rows = Term=="ModelEXAM:conditVaried"
    )
  ) %>%
   tab_row_group(
    label = "Experiment 3",
    rows = exp == "Exp 3"
  ) %>%
  tab_row_group(
    label = "Experiment 2",
    rows = exp == "Exp 2"
  ) %>%
  tab_row_group(
    label = "Experiment 1",
    rows = exp == "Exp 1"
  ) %>%
  tab_options(
    table.font.size = 10,
    heading.title.font.size = 16,
    heading.subtitle.font.size = 14,
    quarto.disable_processing = TRUE
    #row_group.background.color = "gray95"
  )
bct_table

```

*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 . For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix. The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1. The Bayesian regression models predicting model error as a function of Model (ALM vs. EXAM), Condition (Constant vs. Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments. The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments. Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1. Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition. We thus also controleld for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3. There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).

```{r}
#| label: fig-e2_e3_ae
#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs. Varied) on Model Error for Experiment 2 and 3 data. Experiment 3 also includes a control for the order of training vs. testing bands (original order vs. reverse order)."
#| fig-height: 6
#| fig-width: 9

#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
  labs(x="Model",y=NULL)
p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
  scale_color_manual(values=wes_palette("Darjeeling1")) +
  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

 p_e2 <- (p1 + p2+ p3) 
#wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))

p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
                         effects = "Model:condit", 
                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
     points=FALSE,plot=FALSE)$`Model:condit` + 
     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
     theme(legend.position="right") + 
     scale_color_manual(values=wes_palette("Darjeeling1"))

# p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
#   ggplot2::xlab("Condition") +ylab("Model Error")
# p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
#   labs(x="Model",y=NULL)
# p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
#   scale_color_manual(values=wes_palette("Darjeeling1")) +
#   labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")

 #p2 <- (p1 + p2+ p3)
 (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
```

*Computational Model Summary*. Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23). This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant. Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group. It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model. A subset of these participants are shown in @fig-htw-indv-pred.

```{r}
#| label: fig-htw-best-model
#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
#| fig-height: 12
#| fig-width: 11

tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
  filter(Fit_Method=="Test_Train") |>
  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
    mutate(e2=abs(y-pred)) |> 
    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
    group_by(id,condit,Model,Fit_Method,Exp) |> 
    summarise(mean_error=mean(mean_error)) |> 
    arrange(id,condit,Fit_Method) |>
    round_tibble(1)

best_id <- tid1 |> 
  group_by(id,condit,Fit_Method) |> 
  mutate(best=ifelse(mean_error==min(mean_error),1,0))

lowest_error_model <- best_id %>%
  group_by(id, condit,Fit_Method, Exp) %>%
  summarise(Best_Model = Model[which.min(mean_error)],
            Lowest_error = min(mean_error),
            differential = min(mean_error) - max(mean_error)) %>%
  ungroup()

error_difference<- best_id %>%
  select(id, condit, Model,Fit_Method, mean_error) %>%
  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
  mutate(Error_difference = (ALM - EXAM))

full_comparison <- lowest_error_model |> 
  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
  group_by(condit,Fit_Method,Best_Model) |> 
  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
  arrange(Fit_Method,-Error_difference)

full_comparison |> 
  filter(Fit_Method=="Test_Train") |> 
  ungroup() |>
  mutate(id = reorder(id, Error_difference)) %>%
  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
  geom_col() +
  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
  theme(axis.text.y = element_text(size=8)) +
  labs(fill="Best Model",
  x="Mean Model Error Difference (ALM - EXAM)",
  y="Participant")

```

```{r  fig.width=11, fig.height=10}
#| label: fig-htw-indv-pred
#| fig-cap: Model predictions alongside observed data for a subset of individual participants. A) 3 constant and 3 varied participants fit to both the test and training data. B) 3 constant and 3 varied subjects fit to only the trainign data. Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands. 
#| fig-height: 7
#| fig-width: 10

cId_tr <- c(137, 181, 11)
vId_tr <- c(14, 193, 47)
cId_tt <- c(11, 93, 35)
vId_tt <- c(1,14,74)
cId_new <- c(175, 68, 93, 74)
# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")

e1_sbjs <- c(49,68,155, 175,74)
e3_sbjs <-  c(245, 280, 249)
e2_sbjs <- c(197, 157, 312, 334)
cFinal <- c(49, 128,202 )
vFinal <- c(68,70,245)

indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))

testIndv <- indv_post_l |> 
#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
  group_by(id,condit,Fit_Method,Model,Resp) |>
   mutate(flab=paste0("Subject: ",id)) |>
  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
  stat_bar_sd + 
  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
  labs(title="Individual Participant fits from Test & Train Fitting Method",
       y="X Velocity",fill="Target Velocity") +
   guides(fill = guide_legend(nrow = 1)) + 
  theme(legend.position = "bottom",axis.title.x = element_blank())

testIndv 
```

# General Discussion

*Experimental Result Summary*

Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task. In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.

Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training. The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.

Experiment 2 extended these findings by reversing the order of the training and testing bands. Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases. However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.

In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments. Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied). The varied condition showed larger deviations at the end of training, consistent with the previous experiments. Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition. During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands. The reverse order conditions showed smaller deviations compared to the original order conditions. Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.

All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015]. The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group. Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.

Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items. Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions. A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials). These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study. @vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items. However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape. This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.

*Modeling Summary*
EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group. May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule. But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval. The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.

One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.

- why does Constant do better 
    - kind of task that permits for prior knowledge about 0
    - learning - end of training
- what does it suggest that the constant group was disproportionately well explained by the EXAM model?
-

*Limitations*
- amount of training
- constant group always having more experience at nearest position

- constant group having more extrapolation items

- only training and extrapolation - no interpolation items - so harder to make claims about extrapolation specifically, as opposed to generalization in general.

- no mechanism to account for sequence effects in models

- more rigorous model comparison to account for exams greater complexity

- knowledge of function

## Comparison to Project 1

### Differences between the tasks

There are a number of differences between Project 1's Hit The Target (HTT), and Project 2's Hit The Wall (HTW) tasks.

- Task Space Complexity: In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard. Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.

- Perceptual Distinctiveness: HTT offers perceptually distinct varied conditions that directly relate to the task's demands, which may increase the sallience between training positions encounted by the varied group. In contrast, HTW's varied conditions differ only in the numerical values displayed, lacking the same level of perceptual differentiation. Conversely in HTW, the only difference between conditions for the varied group are the numbers displayed at the top of the screen which indicate the current target band(e.g. 800-1000, or 1000-1200)

- In HTW, our primary testing stage of interest has no feedback, whereas in HTT testing always included feedback (the intermittent testing in HTT expt 1 being the only exception). Of course, we do collect testing with feedback data at the end of HTW, but we haven't focused on that data at all in our modelling work thus far. It's also interesting to recall that the gap between varied and constant in HTW does seem to close substantially in the testing-with-feedback stage. The difference between no-feedback and feedback testing might be relevant if the benefits of variation have anything to do with improving subsequent learning (as opposed to subsequent immediate performance), OR if the benefits of constant training rely on having the most useful anchor, having the most useful anchor might be a lot less helpful if you're getting feedback from novel positions and can thus immediately begin to form position-specific anchors for the novelties, rather than relying on a training anchor.

- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments. However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands. This means that in HTT the varied group gets half as much experience on any one position as the constant group, and in HTW they only get 1/3 as much experience in any one position. There are likely myriad ways in which this might impact the success of the varied group regardless of how you think the benefits of variation might be occurring, e.g. maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.

### 2024-04-02 Sections/HTW_old.qmd
update htw page

--- 2023-11-14 HTW.qmd
@@
 page-layout: full
-bibliography: "Assets/Bib/Dissertation.bib"
 code-fold: true
@@
 
-{{< include Sections/htw_exam.qmd >}}
+{{< include htw_exam.qmd >}}
 

### 2024-04-02 Functions/Display_Functions.R

@@ -1,6 +1,7 @@
 
 
-pacman::p_load(ggplot2,wesanderson,glue, ggdist,ggforce,patchwork,gghalves)
+#pacman::p_load(ggplot2,wesanderson,glue, ggdist,ggforce,patchwork,gghalves, ggh4x)
+pacman::p_load(ggplot2,wesanderson,glue)
 #pacman::p_load(ggplot2,ggpattern,viridis,scales,wesanderson,ggthemer)
 options(dplyr.summarise.inform=FALSE)
 
@@ -9,7 +10,32 @@ mutate <- dplyr::mutate
 filter <- dplyr::filter
 map <- purrr::map
 
+# stat_bar <- list(stat_summary(fun=mean, geom="bar", position=position_dodge(), alpha=.75),
+#   stat_summary(fun.data=mean_se, geom="errorbar", position=position_dodge()))
 
+stat_bar <- list(stat_summary(fun=mean, geom="bar", position=position_dodge()),
+                 stat_summary(fun.data=mean_se, geom="errorbar", color="black", position=position_dodge(), linewidth=.5))
+
+  
+
+stat_bar_sd <- list(stat_summary(fun=mean, geom="bar", position=position_dodge()),
+  stat_summary(fun.data=mean_sdl, geom="errorbar",fun.args = list(mult = 1), color="black", position=position_dodge(), linewidth=.5))
+
+
+#### Bayesian/Brms functions
+
+rename_fm <- function(fm) {
+  # Apply case_when to transform fm values
+  transformed_fm <- dplyr::case_when(
+    fm == "Test" ~ "Fit to Test Data",
+    fm == "Train" ~ "Fit to Training Data",
+    fm == "Test_Train" ~ "Fit to Test & Training Data",
+    TRUE ~ "WRONG INPUT"
+  )
+  
+  # Convert the transformed_fm into a factor with levels in the specific order
+  factor(transformed_fm, levels = c("Fit to Test Data", "Fit to Test & Training Data","Fit to Training Data","WRONG INPUT"))
+}
 
 
 alm_plot <- function (){
@@ -81,7 +107,6 @@ g <- ggplot() +
 
 
 
-#### Bayesian/Brms functions
 
 brms_posterior_checks <- function(brmModel, yvar, gvar, ndraws = 50) {
   
@@ -154,7 +179,6 @@ indv_model_plot <- function(combined_df, indv_coefs, testAvg,slopeVar, rank_vari
[…]

### 2024-04-02 Functions/fun_alm.R

@@ -1,0 +1,177 @@
+# Constants
+nz <- .0001
+
+normalize_vector <- function(x) x / (sum(x) + nz)
+
+activation_function <- function(input, layer, c) exp(-c * (layer - input)^2)
+
+alm.response <- function(input = 1, c = 1, input.layer, output.layer, weight.mat, trainVec=NULL) {
+  input.activation <- normalize_vector(activation_function(input, input.layer, c))
+  output.activation <- (weight.mat %*% input.activation)
+  output.probability <- normalize_vector(output.activation)
+  mean.response <- sum(output.layer * output.probability)
+  list(mean.response = mean.response, input.activation = input.activation, output.activation = output.activation)
+}
+
+alm.responseOnly <- function(input = 1, c = 1, input.layer, output.layer, weight.mat, trainVec=NULL) {
+  input.activation <- normalize_vector(activation_function(input, input.layer, c))
+  output.activation <- weight.mat %*% input.activation
+  output.probability <- normalize_vector(output.activation)
+  mean.response <- sum(output.layer * output.probability)
+  return(mean.response)
+}
+ 
+
+alm.update <- function(corResp, c = 1, lr, output.layer, input.activation, output_act, weight.mat) {
+  teacherSignal <- (activation_function(corResp,output.layer, c) - output_act) * lr
+  wChange <- teacherSignal %*% t(input.activation)
+  weight.mat <- weight.mat + wChange
+  return(weight.mat)
+}
+
+
+
+exam.response <- function(input, c, input.layer = INPUT_LAYER_DEFAULT,output.layer = OUTPUT_LAYER_DEFAULT, weight.mat, trainVec) {
+  nearestTrain <- trainVec[which.min(abs(input - trainVec))]
+  aresp <- alm.response(nearestTrain, c, input.layer = input.layer,output.layer,weight.mat)$mean.response
+  
+  xUnder <- ifelse(min(trainVec) == nearestTrain, nearestTrain, trainVec[which(trainVec == nearestTrain) - 1])
+  xOver <- ifelse(max(trainVec) == nearestTrain, nearestTrain, trainVec[which(trainVec == nearestTrain) + 1])
+  
+  mUnder <- alm.response(xUnder, c, input.layer = input.layer, output.layer, weight.mat)$mean.response
[…]

### 2024-04-02 Functions/fun_indv_fit.R

@@ -1,0 +1,628 @@
+
+
+abc_train_tables <- function(pd_train,pt_train_l)
+{
+  block_pred_full <-  pd_train  |> group_by(id,condit,Model,Fit_Method,x,Block) |> 
+    mutate(e2=abs(y-pred)) |> 
+    summarise(y=mean(y), pred=mean(pred), mean_error=mean(e2)) |>
+    group_by(id,condit,Model,Fit_Method,Block) |> 
+    summarise(y=mean(y),pred=mean(pred),mean_error=mean(mean_error)) |> 
+    group_by(condit,Model,Fit_Method,Block) |> 
+    summarise(y=mean(y),pred=mean(pred),mean_error=mean(mean_error)) |> 
+    round_tibble(1) 
+  
+  block_pred_best <-  pd_train  |> group_by(id,condit,Model,Fit_Method,x,Block) |> 
+    filter(rank==1) |>
+    mutate(e2=abs(y-pred)) |> 
+    summarise(y=mean(y), pred=mean(pred), mean_error=mean(e2)) |>
+    group_by(condit,Model,Fit_Method,Block) |> 
+    summarise(mean_error=mean(mean_error)) |> 
+    round_tibble(1)
+  
+  block_pred_full_x <-  pd_train  |> group_by(condit,Model,Fit_Method,x,Block) |> 
+    mutate(e2=abs(y-pred)) |> 
+    summarise(y=mean(y), pred=mean(pred), mean_error=mean(e2)) |>
+    group_by(condit,Model,Fit_Method,Block,x) |> 
+    summarise(y=mean(y),pred=mean(pred),mean_error=mean(mean_error)) |> 
+    round_tibble(1) |>
+    group_by(Fit_Method,condit,Block,x) |>
+    mutate(best=if_else(mean_error==min(mean_error),1,0)) |> ungroup()
+  
+  block_pred_best_x <-  pd_train  |> group_by(condit,Model,Fit_Method,x,Block) |> 
+    filter(rank==1) |>
+    mutate(e2=abs(y-pred)) |> 
+    summarise(y=mean(y), pred=mean(pred), mean_error=mean(e2)) |>
+    group_by(condit,Model,Fit_Method,Block,x) |> 
+    summarise(mean_error=mean(mean_error)) |> 
+    round_tibble(1)
+  
+  # agg_pred_full <-  pd_train  |> group_by(condit,Model,Fit_Method,x) |> 
[…]

### 2024-04-02 Functions/org_functions.R

@@ -7,15 +7,35 @@
 #         dplyr.summarise.inform = FALSE,
 #         knitr.kable.NA = "")
 
-
-
-get_coef_details <- function(model, term_name) {
-  broom.mixed::tidy(model) |>
-    filter(term == term_name) |> 
-    select(estimate, conf.low, conf.high) |> 
-    mutate(across(where(is.numeric), \(x) round(x, 2)))
+round_tibble <- function(tbl, rn) {
+  tbl %>% 
+    mutate(across(where(is.numeric), ~round(., rn)))
 }
 
+strip_list_notation <- function(str) {
+  # Remove 'list(' at the beginning
+  str <- gsub("^list\\(", "", str)
+  # Remove ')' at the end
+  str <- gsub("\\)$", "", str)
+  return(str)
+}
+
+get_coef_details <- function(model, term_name) {
+  term_details <- broom.mixed::tidy(model) %>%
+    filter(term == term_name) %>%
+    select(estimate, conf.low, conf.high) %>%
+    mutate(across(where(is.numeric), ~round(.x, 2)))
+  
+  pd_results <- bayestestR::p_direction(model, effects = "fixed", parameters = term_name)
+  # Directly extract the pd value for the specified term
+  pd_value <- ifelse(!is.null(pd_results$pd), pd_results$pd[1], NA_real_)
+  
+  term_details$pd <- paste0(round(pd_value * 100, 2),"%")  # Ensure it's a percentage and rounded
+  return(term_details)
+}
+
+# bayestestR::p_direction(e1_vxBMM)[, "conditVaried"]
+# bayestestR::p_direction(e1_vxBMM, parameter="conditVaried", effects = "fixed")
 
 
 condEffects <- function(m){
@@ -44,8 +64,6 @@ custom_scale <- function(x) {
   }
 }
 
-
-
 # ks2 = model_parameters(e1_testDistRF2_0,effects="random",keep="^r_id*") 
 # ks2 <- ks2 %>%
 #   mutate(
@@ -65,13 +83,6 @@ ks2 <- ks2 |>
   left_join(select(model$data,id,condit) |> distinct(),by=join_by("id"),keep=FALSE) |>
   select(-Group) |> relocate(id,condit,vb)
 }
-
-
-
-
-
-
-
 
 
 

### 2024-04-02 Functions/prep_model_data.R

@@ -1,0 +1,539 @@
+
+
+
+load_init <- function(){
+  # Load libraries
+pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+               stringr,future,furrr, knitr, reactable, flextable,ggstance, htmltools,ggdist)
+#conflict_prefer_all("dplyr", quiet = TRUE)
+walk(c("flextable","dplyr"), conflict_prefer_all, quiet = TRUE)
+
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+
+}
+
+# Only call load_init if not already loaded
+if (!all(c("dplyr", "purrr", "conflicted", "here") %in% .packages())) {
+    load_init()
+    print("Loaded libraries and functions.")
+}
+#  && exists("dplyr.summarise.inform")
+
+
+
+generate_data <- function(Model, post_samples, data, num_samples = 1, return_dat = "train_data, test_data") {
+  # Filter data for the specific id without invalidating selfref
+  sbj_data <- copy(data[id == post_samples$id[1]])
+  simulation_function <- ifelse(Model == "EXAM", full_sim_exam, full_sim_alm)
+
+  target_data <- switch(return_dat,
+                        "test_data" = copy(sbj_data[expMode2 == "Test"]),
+                        "train_data" = copy(sbj_data[expMode2 == "Train"]),
+                        "train_data, test_data" = copy(sbj_data[expMode2 %in% c("Test", "Train")]))
+  
+  post_samples <- post_samples[order(mean_error)][1:num_samples, .(c, lr, mean_error, rank = .I)]
+
+  simulated_data_list <- lapply(1:nrow(post_samples), function(i) {
+    params <- post_samples[i]
+    sim_data <- simulation_function(sbj_data, params$c, params$lr, input_layer = input_layer, 
+                                    output_layer = output_layer, return_dat = return_dat)
+    sim_data_dt <- data.table(id = sbj_data$id[1], condit = sbj_data$condit[1], 
[…]

### 2024-04-02 Functions/prep_mpar.R

@@ -1,0 +1,124 @@
+
+
+#pacman::p_load(parallel, future, furrr)
+
+tg_m1 <- '10.147.17.202'
+macpro <- '10.147.17.83'
+m1l1 <- '10.147.17.245'
+
+make_spec <- function() {
+
+tg_m1 <- '10.147.17.202'
+m1l1 <- '10.147.17.245'
+m1l2 <- '10.147.17.69'
+m1l3 <- '10.147.17.122'
+m1l4 <- '10.147.17.46'
+m1l5 <- '10.147.17.192'
+m1l6 <- '10.147.17.66'
+m1l7 <- '10.147.17.139'
+m1l8 <- '10.147.17.8'
+m1r1 <- '10.147.17.45'
+m1r2 <- '10.147.17.211'
+tg15 <- '10.147.17.222'
+macpro <- '10.147.17.83'
+m1l8_l <- '10.20.209.187'
+
+# alternative m1l8: 10.20.40.99
+#ips <- c(m1l2,tg_m1)
+
+
+# machineAddresses <- list(
+#   #list(host=tg_m1,user='thomasgorman', ncore=7),
+#   list(host=macpro,user='thomasgorman', ncore=1),
+#   list(host=m1l2,user='thomasgorman', ncore=8),
+#   list(host=m1l4,user='thomasgorman', ncore=8),
+#   list(host=m1l5,user='thomasgorman', ncore=8),
+#    list(host=m1l6,user='thomasgorman', ncore=8),
+#    list(host=m1l7,user='thomasgorman', ncore=8),
+#    list(host=m1r1,user='thomasgorman', ncore=8),
+#   list(host=m1r2,user='thomasgorman', ncore=8)
+# )
+
+# machineAddresses <- list(
+#   list(host=tg_m1,user='thomasgorman', ncore=8),
+#   list(host=m1l1,user='thomasgorman', ncore=8),
+#   list(host=m1l3,user='thomasgorman', ncore=8),
+#   list(host=m1l8,user='thomasgorman', ncore=8)
+# )
+
+# machineAddresses <- list(
+#   list(host=m1l1,user='thomasgorman', ncore=8),
+#   list(host=m1l3,user='thomasgorman', ncore=8),
+#   list(host=m1l8,user='thomasgorman', ncore=8)
+# )
+
+machineAddresses <- list(
+  list(host=tg_m1,user='thomasgorman', ncore=6),
[…]

### 2024-04-02 Sections/HTW.qmd
update htw

@@
 code-tools: true
+cache: true
 toc: true
@@
 #| fig-width: 10
-pacman::p_load(dplyr,ggplot2,patchwork) 
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr)
+#options(brms.backend="cmdstanr",mc.cores=4)
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+
+walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
 source(here::here("Functions","deLosh_data.R"))
@@
 
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr)
-#options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+#   stringr, here,conflicted, patchwork, knitr)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
 e1 <- readRDS(here("data/e1_08-21-23.rds")) 
@@
 ```{r}
-#| cache: false
+####| cache: false
 pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 

### 2024-04-02 Sections/Appendix/IGAS-Supplemental.qmd
some full rendering updates

--- 2024-02-28 Appendix/IGAS-Supplemental.qmd
@@
 ```{r, include=FALSE, echo=FALSE}
+
+packages <- c('ez','plyr','dplyr','sciplot','ggplot2','magrittr','car','psych','tidyr',
+              'Matrix','cluster','emdbook','hexbin','caret','glmnet',
+              'afex','purrr','broom','ggpubr','rstatix','stargazer','data.table','cowplot','magick',
+              'stringr')
+invisible(lapply(packages, require, character.only = TRUE))
 source(here::here('Functions/IGAS_ProcessFunctions.R'))
@@
 transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% convert_as_factor(testHalf)
+  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
 variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
@@
 transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% convert_as_factor(novel,extrapolate)
+transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation")) %>% rstatix::convert_as_factor(novel,extrapolate)
 transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,
@@
 transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(halfInd=floor(max(testPosIndex)/2)) %>%
-    mutate(testHalfSbj = case_when(testPosIndex<halfInd ~"1st-Half",testPosIndex>=halfInd ~"2nd-Half")) %>% convert_as_factor(testHalfSbj)
+    mutate(testHalfSbj = case_when(testPosIndex<halfInd ~"1st-Half",testPosIndex>=halfInd ~"2nd-Half")) %>% rstatix::convert_as_factor(testHalfSbj)
 

### 2024-04-02 Sections/HTW.qmd
some full rendering updates

@@
 #| fig-width: 10
+#| cache: false 
 pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
@@
 #options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
 walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)

### 2024-04-02 Sections/full.qmd
some full rendering updates

--- 2024-04-02 Sections/HTW.qmd
@@
 ---
-title: HTW Project
+title: Full Dissertation
+subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
 date: last-modified
-page-layout: full
+#page-layout: full
 code-fold: true
 code-tools: true
-cache: true
 toc: true
@@
   eval: true
+editor: 
+  markdown: 
+    wrap: 72
 ---
+
+# Variability and Generalization
+
+The factors that influence the generalization of learning are of considerable interest to both researchers exploring the human learning system and practitioners aiming to enhance the effectiveness of educational and training interventions.
+The present effort will focus specifically on the role of variability in the learning input.
+Variability manipulations typically regulate either the number of distinct instances presented to learners during training, or the dispersion of these instances.
+Such manipulations have been empirically demonstrated to affect subsequent generalization performance.
+This essay will offer an in-depth review of the extant literature on the influence of variability, spanning multiple relevant domains.
+
+## The study of variability
+
+Studies investigating the "benefits of variability" hypothesis usually assign participants to either a constant or varied group for the training stage of the experiment.
+Then, subjects in both groups complete an identical testing stage which often consists items/conditions seen during training, and novel items/conditions.
+If the varied group performs better in the testing stage, this is taken for evidence of the benefits of variability hypothesis.
+Even within this relatively straightforward between-groups design, researchers must navigate several crucial methodological choices, highlighted below:
+
+1)  Variables Subject to Variation.
+In multidimensional tasks, researchers have the option to vary numerous variables.
+The experimenters must decide the specific dimension(s) across which variation will occur.
+For instance, in a projectile throwing accuracy task -- researchers might vary the distance from the target, the size of the target, the weight of the projectile.
+They might also vary a contextual variable not directly relevant to the task, but which will still be encoded by the subject on a trial by trial basis, e.g.
+the background color.
+
+2)  Magnitude of Variation, relative to the control condition.
+The simplest comparison would be to compare a constant group who trains with 1 example/condition, against a varied group that trains from 2 examples/conditions.
+However, it is not uncommon in the literature for the varied condition to train from 3 or 4 conditions.
+For example, @catalanoDistantTransferCoincident1984a train varied subjects from 4 different velocities in their coincident timing task, and [@goodeSuperiorityVariableRepeated2008] have varied subjects' practice with 3 different variants (i.e.
+different letter scrambles of the same word) of an anagram for a given word, while their constant participants view the same variant 3 different times.
+Alternatively, rather than a constant vs.
+varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items [@nosofskyModelguidedSearchOptimal2018].
+
+3)  Locations within Task-Space.
+For tasks in which the stimuli or conditions fall within a continuous metric space, the experimenter must decide whether the varied instances are relatively close together (e.g.
+throwing a ball from a distance of 4 feet and 5 feet), or far apart (throwing from 4 feet and 20 feet).
+Spreading the varied training items further apart may be beneficial in terms of providing a more representative sample of the task space to the learner, however large distances may also result in significant differences in difficulty between the training examples, which can be a common confound in variability studies.
+
+4)  Proximity of Testing to Training Conditions.
+Intuitively, the fairest form of comparison is to include testing conditions that are of an equivalent distance from both the varied and constant groups.
+However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978].
+
+## Variability Literature Review
+
+An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
+In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
+a low variability condition), or spread further away from the prototype (the varied-training group).
+It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
+The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
+The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
+The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
+However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
+The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
+Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
+One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
+
+## Motor skill learning
+
+Training variation has also been shown to promote transfer in motor learning.
+Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
+When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
+Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves).
+Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
+Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
+For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
+Both groups are then tested from novel locations.
+
+One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
+Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
+The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
+Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
+12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
+Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
+However, at the halfway point of the testing stage they were allowed to see the landing location of the 4 beanbags they had thrown, and then completed the final 4 testing throws.
+In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
+Although this design does not directly assess the hypothesis of varied training producing superior generalization to constant training (since the constant group is not tested from a novel position), it nevertheless offers a compelling example of the merits of varied practice.
+
+On occasion the Kerr and Booth design may be nested within a larger experimental design.
+One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue [@wrisbergVariabilityPracticeHypothesis1987].
+This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g.
+the design of Kerr and Booth.
+However, in this case the varied group did not outperform the constant group.
+A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
+However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
+
+Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket [@greenPracticeVariabilityTransfer1995a].
+Varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket.
+One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
+Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
+Of course, this finding is less surprising than that of Kerr & Booth, given that varied subjects did have some prior exposure to the constant groups condition.
+This highlights an issue rarely discussed in the literature, of how much practice from an additional position might be necessary to induce benefits.
+Experimenters almost uniformly have varied participants train with an equivalent number of trials from each of their conditions
+
+One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation [@goodeSuperiorityVariableRepeated2008].
+All participants trained to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
+Although subjects in all conditions were exposed to the same 40 unique words (i.e.
+the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training).
+Two different constant groups were used.
+Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
+LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
+At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e.
+the particular permutation of letters) which the varied group had not explicitly seen.
+However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group.
+This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
+This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.
+
+Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
+However, despite its appeal this particular contrast is relatively uncommon in the literature.
+It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
+A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
+@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
+@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
+A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
+
+Of particular relevant to the current essay is the early work of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
+constant training on multiple testing locations of graded distance from the training condition.
+Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
+The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
+Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
+As is often the case, the varied group performed worse during the training phase.
+In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
+
+## Category learning
+
+In the category learning literature, the constant vs.
+varied comparison is much less suitable.
+Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars.
+Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968], where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
+More recently, researchers have also begun to utilize more realistic stimuli in their experiments.
+@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
+In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
+Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
+higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
+A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyTestsExemplarmemoryModel2018].
+For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
+The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
+Moreover, the pattern of results in this study could be nicely accounted for by an extended version of the Generalized Context Model.
+
+The studies described thus far have studied the benefits of variability by exposing participants to a greater or lesser number of distinct examples during training.
+A distinct sub-literature within the category learning domain has focused much less on benefits derived from varied training, instead emphasizing how increased variability during the learning of a novel category influences how far the category boundary will then be generalized.
+The general approach is to train participants on examples from two categories, with the examples from one of the categories being more dispersed than the other.
+Participants are then tested with novel items located within ambiguous regions of the task space which allow the experimenters to assess whether the difference in variability influences how far participants generalize the category boundaries.
+
+@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
+In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
+In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart.
+Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
+Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
+Moreover, this effect was at odds with the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.
+
+Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
+@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010].
+The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
+They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
+In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial.
+They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
+
+The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present discussion.
+Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
+During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories.
+The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category.
+Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category.
+Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
+The authors then used the standard GCM framework to compare a variety of similarity-based models to account for their results.
+Of particular interest are their evaluations of a category response bias parameter, and a similarity scaling parameter.
+A model fit improvement when the response bias parameter is allowed to vary between the high-variability and low-variability trained groups is taken to suggest a simple bias for responding with one of the trained categories over the other.
+Alternatively, an improvement in fit due to a separate similarity scaling parameter may reflect the groups being differentially sensitive to the distances between stimuli.
+No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
+The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
+This model accounted for both the extended generalization gradients of the varied particpants, and also for their poor performance in a recognition condition.
+Additional model comparisons suggested that this similarity rescaling applied across the entire stimulus space, rather than to the high variability category in particular.
+
+Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts [@braithwaiteEffectsVariationPrior2015].
+This study trained participants on problems involving the concept of sampling with replacement (SWR).
+Training consisted of examples that were either highly similar in their semantic context (e.g.
+all involving people selecting objects) or in which the surface features were varied between examples (e.g.
+people choosing objects AND objects selected in a sequence).
+The experimenters also surveyed how much prior knowledge each participant had with SWR.
+They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples.
+The authors hypothesized that in order to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
+To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples.
+Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
+
+Variability has also been examined within the realm of language learning.
+A particularly impressive study is that of [@perryLearnLocallyThink2010].
+In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
+All infants were introduced to three novel objects of the same category, with participants in the tight condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
+Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
+Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
+By the end of the nine weeks, all of the infants had learned the labels of the training objects.
+The varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category, a pattern consistent with much of the existing literature.
+More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
+The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
+
+## Complications to the influence of variability
+
+### Sequence Effects
+
+A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another.
+The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
+Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter  [@sheaContextualInterferenceEffects1979].
+In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
+A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training.
+Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random.
+There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
+However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
+
+Prior to the influential @sheaContextualInterferenceEffects1979 study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
+It was later observed [@leeInfluencePracticeSchedule1985] that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
+The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts.
+One such account, the elaborative processing account [@sheaContextEffectsMemory1983], draws on the earlier work [@battigFacilitationInterference1966] and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
+Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training [@sheaContextEffectsMemory1983], and by manipulating whether subjects are able to perform comparisons during training [@wrightContributionElaborativeProcessing1992].
+An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory [@leeLocusContextualInterference].
+Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context.
+A much more recent study [@chuaPracticeVariabilityPromotes2019], replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
+The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
+In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g.
+attending to the target distance), and constant or blocked subjects reported more internal attention (e.g.
+posture or hand position).
+The authors argue that the benefits of varied/random training may be mediated by changes in attentional focus, however the claims made in the paper seem to go far beyond what can be justified by the analyses reported -- e.g.
+the increased external focus could be a simple byproduct of varied training.
+A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.
+
+## Other task and participant effects
+
+Of course, the effects of varied training, and different training sequences, are likely to be far more complex than simply more varied training being better than less, or random training being better than blocked.
+Null effects of both manipulations have been reported [see @magillReviewContextualInterference1990; @vanrossumSchmidtSchemaTheory1990 for reviews], and a variety of moderators have emerged.
+In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
+non-athlete) x (constant vs.
+blocked vs.
+random training).
+Athlete participants had superior performance during training, regardless of sequence condition, and training performance was superior for all subjects in the constant group, followed by blocked training in the middle, and then random training resulting in the worst training performance.
+Of greater interest is the pattern of testing results for novel transfer conditions.
+Among the athlete-participants, transfer performance was best for those who received random training, followed by blocked, and then constant training.
+Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
+A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training  [@guadagnoliRelationshipContextualInterference1999].
+More recently, the same pattern was observed in the concept learning literature [@braithwaiteEffectsVariationPrior2015 expt 1.].
+This study trained participants on a mathematical concept and found that participants who self-reported some prior experience with the concept improved more from pre-test to post-test after training with varied examples, while participants who reported no prior experience showed greater gains following training with highly similar examples.
+
+In addition to the influence of prior experiences described above, ample evidence also suggests that numerous aspects of the experiment may also interact with the influence of variation.
+One important study examined the impact of the amount of training completed in a force production task [@sheaContextualInterferenceContributions1990].
+This study employed a typical blocked vs.
+random training procedure, but with the additional manipulation of separate groups receiving 50, 200, or 400 total training trials.
+For the group that received only 50 training trials retention was best when training had been blocked.
+However, for the conditions that received 200 or 400 training trials the pattern was reversed, with random training resulting in superior retention than blocked training.
+These results were taken to suggest that the benefits of randomization may take time to emerge.
+Another experimental factor shown to interact with training sequence is the complexity of the training task [@albaretDifferentialEffectsTask1998].
+In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of two, three or four components).
+On a transfer task 48 hours after the completion of training, only participants trained at the lower levels of task complexity (2 or 3 components) showed superior performance to the blocked condition.
+The authors suggest that the benefits of random sequencing, thought to arise from more elaborate cognitive processing, or the necessity of continually recalling task information from long term into short term memory, are more likely to be obscured as the complexity of the task forces the blocked participants to also engage in such processes.
+
+A final important influence of particular relevance to the practice-sequence literature concerns the exact structure of "random" sequencing.
+Although the term random is commonly used for convenience, experimenters do not typically leave the order of training entirely up to chance.
+Rather, the training sequence is often constrained such that each condition must occur a minimum number of times in each quartile of the training phase, thus resulting in an even distribution the conditions throughout training.
+While the assurance of the conditions being evenly spread throughout training is consistent across studies, other aspects of the sequence structure are a bit more idiosyncratic.
+Some researchers report setting a maximum number of consecutive repetitions, e.g.
+no more than 2 consecutive trials of the same condition [@delreyEffectsContextualInterference1982; @sheaContextualInterferenceEffects1979], or structure the random trials such that the same condition never occurs consecutively [@wulfEffectTypePractice1991].
+Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition [@willeyLongtermMotorLearning2018; @chuaPracticeVariabilityPromotes2019; @wrisbergVariabilityPracticeHypothesis1987], resulting in many more switches than would arise if training was perfectly blocked.
+The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition.
+Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing [@pigottMotorSchemaStructure1984], and basketball shot training study [@landinComparisonThreePractice1997], and in a replication plus extension of the seminal [@sheaContextualInterferenceEffects1979] study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition.
+Consequences on different study schedules have also been repeatedly observed in the category learning literature [@carvalhoSequenceStudyChanges2017; @carvalhoPuttingCategoryLearning2014].
+This line of research has revealed that the effects of blocking vs.
+interleaving can depend on the structure of the category being learned, and also that the different schedules can result in the participants requiring different representations.
+A fruitful line of inquiry in the motor skill learning literature may be to attempt to identify whether structural aspects of the motor task interact with different training sequences in a reliable manner.
+
+Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed).
+Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty [@bjorkNewTheoryDisuse1992; @schmidtNewConceptualizationsPractice1992], or optimal challenge points [@guadagnoliChallengePointFramework2004].
+They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage.
+This observation is then used to justify the idea that the most enduring and generalizable learning occurs by training at an optimal level of training difficulty, with difficulty being some function of the experience of the learner, and the cognitive or visuomotor processing demands of the task.
+It then follows that the factors that tend to make training more difficult (i.e.
+increased variability or randomization), are more likely to be beneficial when the learner has some experience, or when the processing demands of the task are not too extreme (which may only occur after some experience with the task).
+Such frameworks may be helpful heuristics in some cases, but they also seem to be overly flexible such that any null result of some intervention might be accounted for by a suboptimal amount of training trials, or by suggesting the training task was too difficult.
+The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.
+
+# Project 1
+
+____________________________________________________
+[pdf of the journal
+article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
+[Link to online version of journal
+article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
+
+```{r}
+
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
+  ggh4x,htmltools,future,furrr,ez)
+#options(brms.backend="cmdstanr",mc.cores=4)
+#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
+walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
+walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+#conflicts_prefer(tidybayes::rstudent_t)
+
+# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+
+#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+#options(brms.backend="cmdstanr",mc.cores=4)
+initial_contrasts <- options("contrasts")$contrasts
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+
+library(tidybayes)
+
+theme_set(theme_classic())
+# load the processed data from experiment 1 and 2
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
+
+# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
+# defaultContrasts = options()$contrasts
+# theme_set(theme_classic())
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
+                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
+
+e1Pos <- c("610","760","835","910")
+e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
+e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
+```
+
+# Abstract
+
+Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
+Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
+However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
+In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
+We replicate previous findings showing a transfer advantage of varied over constant training.
+Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
+Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
+
+# Introduction
+
+The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
+Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
+The factor of interest to the present investigation is variation during training.
+Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
+We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
+We first review the relevant concepts and literature.
+
+## Similarity and instance-based approaches to transfer of learning
+
+Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances.
+Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar [@posnerGenesisAbstractIdeas1968].
+Prototype models were later challenged by the success of instance-based or exemplar models -- which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978;
+@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
+Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli.
+As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
+Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
+
+Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
+In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
+Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
+That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
+Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
+@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
+Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
+Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
+
+## The effect of training variability on transfer
+
+While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
+Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work -- variability of training examples.
+
+Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
+Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+
+Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
+Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
+throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
+Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
+Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
+Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
+For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
+Both groups are then tested from novel locations.
+Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+
+## Issues with Previous Research
+
+Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
+Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
+For training tasks in which participants have numerous degrees of freedom (e.g.
+projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
+more unique combinations of x and y velocities).
+Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
+However, even this level of experimental control may still be insufficient to rule out
+the effect of similarity on transfer.
+Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
+@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
+
+```{r}
+#| label: fig-toy-model1
+#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
+A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
+Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
+(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
+
+p=2
+c<- .0002
+simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
+                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
+                     mutate(plotjitter=ifelse(condit=="varied",0,7),
+                            linScale=ifelse(condit=="varied",980,1000),
+                            genGauss=exp(-c*(abs((x-train.position)^p))),
+                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
+  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
+  group_by(x,condit) %>%
+  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
+colorVec=c("darkblue","darkred")
+plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
+                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
+                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
+                  ylim(c(0,1.05)),
+                  #xlim(c(250,950)),
+                  scale_x_continuous(breaks=seq(200,1000,by=200)),
+                  xlab("Test Stimulus"),
+                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
+                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
+                        legend.position="none"))
+
+ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
+ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
+
+plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
+
+```
+
+In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
+Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
+As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
+However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
+
+The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
+We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
+We then examine the extent to which this advantage can be explained by an instance-based similarity model.
+
+# Experiment 1
+
+## Methods
+
+### Sample Size Estimation
+
+To obtain an independent estimate of effect size, we identified previous
+investigations which included between-subjects contrasts of varied and
+constant conditions following training on an accuracy based projectile
+launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
+We then averaged effects across these studies,
+yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
+2009) was then used to determine that a power of 80% requires a sample
+size of at least 23 participants per condition. All experiments reported
+in the present manuscript exceed this minimum number of participants per
+condition.
+
+### Participants
+
+Participants were recruited from an undergraduate population that is 63%
+female and consists almost entirely of individuals aged 18-22 years. A
+total of 110 Indiana University psychology students participated in
+Experiment 1. We subsequently excluded 34 participants poor performance
+at one of the dependent measures of the task (2.5-3 standard deviations
+worse than the median subject at the task) or for displaying a pattern
+of responses that was clearly indicative of a lack of engagement with
+the task (e.g. simply dropping the ball on each trial rather than
+throwing it at the target), or for reporting that they completed the
+experiment on a phone or tablet device, despite the instructions not to
+use one of these devices. A total of 74 participants were retained for
+the final analyses, 35 in the varied group and 39 in the constant group.
+
+### Task
+
+The experimental task was programmed in JavaScript, using packages from
+the Phaser physics engine (https://phaser.io) and the jsPsych library
+(de Leeuw, 2015). The stimuli, presented on a black background,
+consisted of a circular blue ball -- controlled by the participant via
+the mouse or trackpad cursor; a rectangular green target; a red
+rectangular barrier located between the ball and the target; and an
+orange square within which the participant could control the ball before
+releasing it in a throw towards the target. Because the task was
+administered online, the absolute distance between stimuli could vary
+depending on the size of the computer monitor being used, but the
+relative distance between the stimuli was held constant. Likewise, the
+distance between the center of the target, and the training and testing
+locations was scaled such that relative distances were preserved
+regardless of screen size. For the sake of brevity, subsequent mentions
+of this relative distance between stimuli, or the position where the
+ball landed in relation to the center of the target, will be referred to
+simply as distance. @fig-IGAS_Methods displays the layout of the task, as
+it would appear to a participant at the start of a trial, with the ball
+appearing in the center of the orange square. Using a mouse or trackpad,
+participants click down on the ball to take control of the ball,
+connecting the movement of the ball to the movement of the cursor.
+Participants can then "wind up" the ball by dragging it (within the
+confines of the orange square) and then launch the ball by releasing the
+cursor. If the ball does not land on the target, participants are
+presented with feedback in red text at the top right of the screen, on
+how many units away they were from the center of the target. If the ball
+was thrown outside of the boundary of the screen participants are given
+feedback as to how far away from the target center the ball would have
+been if it had continued its trajectory. If the ball strikes the barrier
+(from the side or by landing on top), feedback is presented telling
+participants to avoid hitting the barrier. If participants drag the ball
+outside of the orange square before releasing it, the trial terminates,
+and they are reminded to release the ball within the orange square. If
+the ball lands on the target, feedback is presented in green text,
+confirming that the target was hit, and presenting additional feedback
+on how many units away the ball was from the exact center of the target.
+
+[Link to abbrevaited example of
+task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+
+```{r}
+#| label: fig-IGAS_Methods
+#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
+On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
+Participants were constrained to release the ball within the square
+
+mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
+plot_grid(mf,ncol=1)
+
+```
+
+## Results
+
+## Data Processing and Statistical Packages
+
+To prepare the data, we first removed trials that were not easily
+interpretable as performance indicators in our task. Removed trials
+included: 1) those in which participants dragged the ball outside of the
+orange starting box without releasing it, 2) trials in which
+participants clicked on the ball, and then immediately released it,
+causing the ball to drop straight down, 3) outlier trials in which the
+ball was thrown more than 2.5 standard deviations further than the
+average throw (calculated separately for each throwing position), and 4)
+trials in which the ball struck the barrier. The primary measure of
+performance used in all analyses was the absolute distance away from the
+center of the target. The absolute distance was calculated on every
+trial, and then averaged within each subject to yield a single
+performance score, for each position. A consistent pattern across
+training and testing phases in both experiments was for participants to
+perform worse from throwing positions further away from the target -- a
+pattern which we refer to as the difficulty of the positions. However,
+there were no interactions between throwing position and training
+conditions, allowing us to collapse across positions in cases where
+contrasts for specific positions were not of interest. All data
+processing and statistical analyses were performed in R version 4.03 (R
+Core Team, 2020). ANOVAs for group comparisons were performed using the
+rstatix package (Kassambara, 2021)****.
+
+## Training Phase
+
+@fig-IGAS_Training1 below shows aggregate training performance binned into three
+stages representing the beginning, middle, and end of the training
+phase. Because the two conditions trained from target distances that
+were not equally difficult, it was not possible to directly compare
+performance between conditions in the training phase. Our focus for the
+training data analysis was instead to establish that participants did
+improve their performance over the course of training, and to examine
+whether there was any interaction between training stage and condition.
+Descriptive statistics for the intermittent testing phase are provided
+in the supplementary materials.
+
+We performed an ANOVA comparison with stage as a within-group factor and
+condition as between-group factor. The analysis revealed a significant
+effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
+such that performance improved over the course of training There was no
+significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
+and no significant interaction between condition and training stage,
+F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
+
+```{r}
+#| label: fig-IGAS_Training1
+#| fig.cap: Training performance for varied and constant participants binned into three stages.
+Shorter bars indicate better performance (ball landing closer to the center of the target).
+Error bars indicate standard error of the mean.
+
+exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
+  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
+  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
+  group_by(sbjCode,Group,conditType,trainHalf) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
+  group_by(sbjCode,Group,conditType,stage) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
+  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
+  facet_wrap(~conditType,ncol=2)+
+  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
+  ylab("Mean Distance From Center Of Target")+
+  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
+  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
+
+#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
+plot_grid(e1train2,ncol=1)
+
+```
+
+## Testing Phase
+
+In Experiment 1, a single constant-trained group was compared against a
+single varied-trained group. At the transfer phase, all participants
+were tested from 3 positions: 1) the positions(s) from their own
+training, 2) the training position(s) of the other group, and 3) a
+position novel to both groups. Overall, group performance was compared
+with a mixed type III ANOVA, with condition (varied vs. constant) as a
+between-subject factor and throwing location as a within-subject
+variable. The effect of throwing position was strong, F(3,213) = 56.12,
+p\<.001, η2G = .23. The effect of training condition was significant
+F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
+between group and position, F(3,213)=1.81, p=.15, η2G = .01.
+
+```{r}
+#| label: fig-IGAS_Testing1
+#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
+Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
+Position 760 was trained on by the constant group, and novel for the varied group.
+Position 835 was novel for both groups.
+Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
+Error bars indicate standard error of the mean.
+
+exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
+  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% 
+  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
+  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
+summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
+
+#manuscript plot
+e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
+  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
+
+e1test1
+
+```
+
+\
+\
+
+```{r}
+#| label: tbl-IGAS_Table1
+#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
+
+exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
+  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% 
+  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
+  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
+summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
+
+test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
+   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
+ test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
+ test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
+ test=test[,1:3]
+
+kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
+
+```
+
+## Discussion
+
+In Experiment 1, we found that varied training resulted in superior
+testing performance than constant training, from both a position novel
+to both groups, and from the position at which the constant group was
+trained, which was novel to the varied condition. The superiority of
+varied training over constant training even at the constant training
+position is of particular note, given that testing at this position
+should have been highly similar for participants in the constant
+condition. It should also be noted, though, that testing at the constant
+trained position is not exactly identical to training from that
+position, given that the context of testing is different in several ways
+from that of training, such as the testing trials from the different
+positions being intermixed, as well as a simple change in context as a
+function of time. Such contextual differences will be further considered
+in the General Discussion.
+
+In addition to the variation of throwing position during training, the
+participants in the varied condition of Experiment 1 also received
+training practice from the closest/easiest position, as well as from the
+furthest/most difficult position that would later be encountered by all
+participants during testing. The varied condition also had the potential
+advantage of interpolating both of the novel positions from which they
+would later be tested. Experiment 2 thus sought to address these issues
+by comparing a varied condition to multiple constant conditions.
+
+# Experiment 2
+
+In Experiment 2, we sought to replicate our findings from Experiment 1
+with a new sample of participants, while also addressing the possibility
+of the pattern of results in Experiment 1 being explained by some
+idiosyncrasy of the particular training location of the constant group
+relative to the varied group. To this end, Experiment 2 employed the
+same basic procedure as Experiment 1, but was designed with six separate
+constant groups each trained from one of six different locations (400,
+500, 625, 675, 800, or 900), and a varied group trained from two
+locations (500 and 800). Participants in all seven groups were then
+tested from each of the 6 unique positions.
+
+## Methods
+
+### Participants
+
+A total of 306 Indiana University psychology students participated in
+Experiment 2, which was also conducted online. As was the case in
+experiment 1, the undergraduate population from which we recruited
+participants was 63% female and primarily composed of 18--22-year-old
+individuals. Using the same procedure as experiment 1, we excluded 98
+participants for exceptionally poor performance at one of the dependent
+measures of the task, or for displaying a pattern of responses
+indicative of a lack of engagement with the task. A total of 208
+participants were included in the final analyses with 31 in the varied
+group and 32, 28, 37, 25, 29, 26 participants in the constant groups
+training from location 400, 500, 625, 675, 800, and 900, respectively.
+All participants were compensated with course credit.
+
+### Task and Procedure
+
+The task of Experiment 2 was identical to that of Experiment 1, in all
+but some minor adjustments to the height of the barrier, and the
+relative distance between the barrier and the target. Additionally, the
+intermittent testing trials featured in experiment 1 were not utilized
+in experiment 2, and all training and testing trials were presented with
+feedback. An abbreviated demo of the task used for Experiment 2 can be
+found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
+
+The procedure for Experiment 2 was also quite similar to experiment 1.
+Participants completed 140 training trials, all of which were from the
+same position for the constant groups and split evenly (70 trials each -
+randomized) for the varied group. In the testing phase, participants
+completed 30 trials from each of the six locations that had been used
+separately across each of the constant groups during training. Each of
+the constant groups thus experience one trained location and five novel
+throwing locations in the testing phase, while the varied group
+experiences 2 previously trained, and 4 novel locations.
+
+## Results
+
+### Data Processing and Statistical Packages
+
+After confirming that condition and throwing position did not have any
+significant interactions, we standardized performance within each
+position, and then average across position to yield a single performance
+measure per participant. This standardization did not influence our
+pattern of results. As in experiment 1, we performed type III ANOVA's
+due to our unbalanced design, however the pattern of results presented
+below is not altered if type 1 or type III tests are used instead. The
+statistical software for the primary analyses was the same as for
+experiment 1. Individual learning rates in the testing phase, compared
+between groups in the supplementary analyses, were fit using the TEfit
+package in R [@cochraneTEfitsNonlinearRegression2020].
+
+### Training Phase
+
+The different training conditions trained from positions that were not
+equivalently difficult and are thus not easily amenable to comparison.
+As previously stated, the primary interest of the training data is
+confirmation that some learning did occur. @fig-e2train depicts the training
+performance of the varied group alongside that of the aggregate of the
+six constant groups (5a), and each of the 6 separate constant groups
+(5b). An ANOVA comparison with training stage (beginning, middle, end)
+as a within-group factor and group (the varied condition vs. the 6
+constant conditions collapsed together) as a between-subject factor
+revealed no significant effect of group on training performance,
+F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
+stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
+interaction between group and training stage, F(2,412)=.489 p=.61,
+$\eta^{2}_G$ \<.01. We also tested for a difference in training
+performance between the varied group and the two constant groups that
+trained matching throwing positions (i.e., the constant groups training
+from position 500, and position 800). The results of our ANOVA on this
+limited dataset mirrors that of the full-group analysis, with no
+significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
+significant effect of training stage F(2,172)=56.29, p\<.001,
+$\eta^{2}_G$ =.11, and no significant interaction between group and
+training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
+
+```{r}
+
+e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
+
+exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
+  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
+
+exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
+  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
+  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
+
+exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
+  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
+
+exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
+  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
+  group_by(sbjCode,Group2,conditType,stage) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
+
+transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
+transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
+
+transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
+  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
+
+variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
+constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
+
+transfer <- rbind(variedTest,constantTest)
+transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
+
+transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
+
+# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
+# novelAll <- novelAll %>% group_by(positionX) %>%
+#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
+
+novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
+novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
+
+constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
+variedTest <- transfer %>% filter(condit==7) # only varied testing
+variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
+
+variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
+constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
+variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
+
+exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
+  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
+
+exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
+  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
+
+exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
+  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
+
+exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
+  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
+
+exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
+  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
+
+```
+
+```{r}
+#| label: fig-e2train
+#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
+On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
+On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
+Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
+Error bars indicate standard error of the mean.
+
+### New - 3 stage
+e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
+  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
+  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
+  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
+  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
+        plot.title.position = "plot")+
+  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
+
+e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
+  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
+  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
+  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
+        plot.title.position = "plot")+
+  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
+
+#plot_grid(e2train1,e2train2,ncol=1)
+
+e2train1
+e2train2
+
+```
+
+### Testing Phase
+
+In Experiment 2, a single varied condition (trained from two positions,
+500 and 800), was compared against six separate constant groups (trained
+from a single position, 400, 500, 625, 675, 800 or 900). For the testing
+phase, all participants were tested from all six positions, four of
+which were novel for the varied condition, and five of which were novel
+for each of the constant groups. For a general comparison, we took the
+absolute deviations for each throwing position and computed standardized
+scores across all participants, and then averaged across throwing
+position. The six constant groups were then collapsed together allowing
+us to make a simple comparison between training conditions (constant vs.
+varied). A type III between-subjects ANOVA was performed, yielding a
+significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
+=.02. Descriptive statistics for each condition are shown in table 2. In
+@fig-e2testa visualizes the consistent advantage of the varied condition
+over the constant groups across the testing positions. @fig-e2testa shows
+performance between the varied condition and the individual constant
+groups.
+
+```{r}
+#| label: fig-e2testa
+#| fig.cap: Testing phase performance from each of the six testing positions.
+The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
+Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
+The x axis labels indicate the location(s) from which each group trained.
+Lower values along the y axis reflect better performance at the task (closer distance to target center).
+Error bars indicate standard error of the mean.
+#| fig-width: 11
+#| fig-height: 9
+
+# manuscript plot
+e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
+  theme(plot.title=element_text(face="bold",size=9),
+        plot.title.position = "plot",
+        legend.title.align=.25)+
+  ggtitle("A")
+
+e2test2<-exp2.Test7 %>% 
+  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
+  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
+  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
+  facet_wrap(~ThrowPosition4)+
+  ylab("Mean Distance From Center Of Target")+
+  guides(fill=guide_legend(title="Training Condition"))+
+  theme(plot.title=element_text(face="bold",size=9),
+        plot.title.position = "plot",
+        legend.title.align=.25,
+        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
+  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
+
+e2test1 / e2test2
+
+```
+
+\
+\
+\
+
+```{r}
+#| label: tbl-e2table1
+#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
+Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
+The x axis labels indicate the location(s) from which each group trained.
+Lower values along the y axis reflect better performance at the task (closer distance to target center).
+Error bars indicate standard error of the mean.
+
+tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
+   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
+ tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
+ tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
+   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
+ tab2=tab2[,1:3]
+
+kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+
+```
+
+Next, we compared the testing performance of constant and varied groups
+from only positions that participants had not encountered during
+training. Constant participants each had 5 novel positions, whereas
+varied participants tested from 4 novel positions (400,625,675,900). We
+first standardized performance within in each position, and then
+averaged across positions. Here again, we found a significant effect of
+condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
+.02 .
+
+```{r}
+#| label: tbl-e2table2
+#| tbl-cap: Testing performance from novel positions.
+Includes data only from positions that were not encountered during the training stage (e.g.
+excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
+Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
+
+sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
+  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
+
+tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
+  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
+
+ tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
+
+ tab3 = tab3 %>% 
+   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
+ tab3=tab3[,1:3]
+
+kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+```
+
+Finally, corresponding to the comparison of position 760 from experiment
+1, we compared the test performance of the varied group against the
+constant group from only the positions that the constant groups trained.
+Such positions were novel to the varied group (thus this analysis
+omitted two constant groups that trained from positions 500 or 800 as
+those positions were not novel to the varied group). @fig-e2test1 displays
+the particular subset of comparisons utilized for this analysis. Again,
+we standardized performance within each position before performing the
+analyses on the aggregated data. In this case, the effect of condition
+did not reach statistical significance F(1,149)=3.14, p=.079,
+$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
+
+```{r}
+#| label: fig-e2test1
+#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
+constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
+Error bars indicate standard error of the mean.
+
+sum.variedVsNovelIden <- variedVsNovelIden  %>%
+  group_by(sbjCode,conditType,positionX) %>% 
+  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
+
+e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
+
+e2Test2
+
+```
+
+\
+\
+
+```{r}
+#| label: tbl-e2tab3
+#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
+Locations 500 and 800 are not included as these were trained by the varied participants.
+Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
+
+tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
+  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
+
+tab4=tab4 %>% group_by(Condition) %>% 
+   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
+
+tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
+ tab4=tab4[,1:3]
+
+kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+
+```
+
+## Discussion
+
+The results of experiment 2 largely conform to the findings of
+experiment 1. Participants in both varied and constant conditions
+improved at the task during the training phase. We did not observe the
+common finding of training under varied conditions producing worse
+performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
+suggested to relate to the subsequent benefits of varied training in
+retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
+our finding of no difference in training performance between constant
+and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
+
+In the testing phase, our varied group significantly outperformed the
+constant conditions in both a general comparison, and in an analysis
+limited to novel throwing positions. The observed benefit of varied over
+constant training echoes the findings of many previous visuomotor skill
+learning studies that have continued to emerge since the introduction of
+Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
+We also join a much smaller set of research to observe this
+pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
+the experiment 1 findings concerns the pattern wherein the varied group
+outperformed the constant group even from the training position of the
+constant group, which was significant in experiment 1, but did not reach
+significance in experiment 2. Although this pattern has been observed
+elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
+the overall evidence for this effect appears to be far weaker than for
+the more general benefit of varied training in conditions novel to all
+training groups.
+
+# Computational Model
+
+Controlling for the similarity between training and testing The primary
+goal of Experiment 2 was to examine whether the benefits of variability
+would persist after accounting for individual differences in the
+similarity between trained and tested throwing locations. To this end,
+we modelled each throw as a two-dimensional point in the space of x and
+y velocities applied to the projectile at the moment of release. For
+each participant, we took each individual training throw, and computed
+the similarity between that throw and the entire population of throws
+within the solution space for each of the 6 testing positions. We
+defined the solution space empirically as the set of all combinations of
+x and y throw velocities that resulted in hitting the target. We then
+summed each of the trial-level similarities to produce a single
+similarity for each testing position score relating how the participant
+threw the ball during training and the solutions that would result in
+target hits from each of the six testing positions -- thus resulting in
+six separate similarity scores for each participant. @fig-taskSpace
+visualizes the solution space for each location and illustrates how
+different combinations of x and y velocity result in successfully
+striking the target from different launching positions. As illustrated
+in @fig-taskSpace, the solution throws represent just a small fraction of the
+entire space of velocity combinations used by participants throughout
+the experiment.
+
+```{r}
+#| label: fig-taskSpace
+#| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+This empirical solution space was compiled from all of the participants in experiment 2.
+Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+#| 
+taskspace <- e2 %>% filter(AbsDistFromCenter<900)
+taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
+
+solSpace <- e2 %>% filter(trialType==11)
+#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
+
+solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
+solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
+solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
+
+missSpace <- e2 %>% filter(trialType !=11)
+missSpace$Result = "Missed Target"
+solSpace$Result <- solSpace$Result
+
+# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
+# multiplied velocoties by -1 to make the axes less confusing
+ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
+  geom_point(aes(colour=Result),alpha=0.6) + 
+  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
+  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
+
+fullSpace <- rbind(missSpace,solSpace)
+
+fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
+  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
+  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
+
+ss
+fs
+
+```
+
+For each individual trial, the Euclidean distance (Equation 1) was
+computed between the velocity components (x and y) of that trial and the
+velocity components of each individual solution throw for each of the 6
+positions from which participants would be tested in the final phase of
+the study. The P parameter in Equation 1 is set equal to 2, reflecting a
+Gaussian similarity gradient. Then, as per an instance-based model of
+similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
+multiplied by a sensitivity parameter, c, and then exponentiated to
+yield a similarity value. The parameter c controls the rate with which
+similarity-based generalization drops off as the Euclidean distance
+between two throws in x- and y-velocity space increases. If c has a
+large value, then even a small difference between two throws' velocities
+greatly decreases the extent of generalization from one to the other. A
+small value for c produces broad generalization from one throw to
+another despite relatively large differences in their velocities. The
+similarity values for each training individual throw made by a given
+participant were then summed to yield a final similarity score, with a
+separate score computed for each of the 6 testing positions. The final
+similarity score is construable as index of how accurate the throws a
+participant made during the training phase would be for each of the
+testing positions.
+
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
+(e^{-c^\cdot d^{p}_{i,j}}) $$
+
+**Equation 2:**
+$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+
+A simple linear regression revealed that these similarity scores were
+significantly predictive of performance in the transfer stage, t
+=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
+training throws and solution spaces for each of the test locations
+resulted in better performance. We then repeated the group comparisons
+above while including similarity as a covariate in the model. Comparing
+the varied and constant groups in testing performance from all testing
+positions yielded a significant effect of similarity, F(1, 205)=85.66,
+p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
+(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
+group comparison limited to only novel locations for the varied group
+pit against trained location for the constant group resulted in a
+significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
+=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
+=.07. For all comparisons, the pattern of results was consistent with
+the initial findings from experiment 2, with the varied group still
+performing significantly better than the constant group.
+
+## Fitting model parameters separately by group
+
+To directly control for similarity in Experiment 2, we developed a
+model-based measure of the similarity between training throws and
+testing conditions. This similarity measure was a significant predictor
+of testing performance, e.g., participants whose training throws were
+more similar to throws that resulted in target hits from the testing
+positions, tended to perform better during the testing phase.
+Importantly, the similarity measure did not explain away the group-level
+benefits of varied training, which remained significant in our linear
+model predicting testing performance after similarity was added to the
+model. However, previous research has suggested that participants may
+differ in their level of generalization as a function of prior
+experience, and that such differences in generalization gradients can be
+captured by fitting the generalization parameter of an instance-based
+model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
+Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
+will increase when a rational agent encounters a wider variety of
+examples. Following these leads, we assume that in addition to learning
+the task itself, participants are also adjusting how generalizable their
+experience should be. Varied versus constant participants may be
+expected to learn to generalize their experience to different degrees.
+To accommodate this difference, the generalization parameter of the
+instance-based model (in the present case, the c parameter) can be
+allowed to vary between the two groups to reflect the tendency of
+learners to adaptively tune the extent of their generalization. One
+specific hypothesis is that people adaptively set a value of c to fit
+the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
+variable, as with the variable training condition, then one might infer
+that future test situations will also be variable, in which case a low
+value of c will allow better generalization because generalization will
+drop off slowly with training-to-testing distance. Conversely, if one's
+training experience has little variability, as found in the constant
+training conditions, then one might adopt a high value of c so that
+generalization falls off rapidly away from the trained positions.
+
+To address this possibility, we compared the original instance-based
+model of similarity fit against a modified model which separately fits
+the generalization parameter, c, to varied and constant participants. To
+perform this parameter fitting, we used the optim function in R, and fit
+the model to find the c value(s) that maximized the correlation between
+similarity and testing performance.
+
+Both models generate distinct similarity values between training and
+testing locations. Much like the analyses in Experiment 2, these
+similarity values are regressed against testing performance in models of
+the form shown below. As was the case previously, testing performance is
+defined as the mean absolute distance from the center of the target
+(with a separate score for each participant, from each position).
+
+Linear models 1 and 3 both show that similarity is a significant
+predictor of testing performance (p\<.01). Of greater interest is the
+difference between linear model 2, in which similarity is computed from
+a single c value fit from all participants (Similarity1c), with linear
+model 4, which fits the c parameter separately between groups
+(Similarity2c). In linear model 2, the effect of training group remains
+significant when controlling for Similarity1c (p\<.01), with the varied
+group still performing significantly better. However, in linear model 4
+the addition of the Similarity2c predictor results in the effect of
+training group becoming nonsignificant (p=.40), suggesting that the
+effect of varied vs. constant training is accounted for by the
+Similarity2c predictor. Next, to further establish a difference between
+the models, we performed nested model comparisons using ANOVA, to see if
+the addition of the training group parameter led to a significant
+improvement in model performance. In the first comparison, ANOVA(Linear
+Model 1, Linear Model 2), the addition of the training group predictor
+significantly improved the performance of the model (F=22.07, p\<.01).
+However, in the second model comparison, ANOVA (Linear model 3, Linear
+Model 4) found no improvement in model performance with the addition of
+the training group predictor (F=1.61, p=.20).
+
+Finally, we sought to confirm that similarity values generated from the
+adjusted Similarity2c model had more predictive power than those
+generated from the original Similarity1c model. Using the BIC function
+in R, we compared BIC values between linear model 1 (BIC=14604.00) and
+linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
+a modest advantage for predicting performance using a similarity measure
+computed with two c values over similarity computed with a single c
+value. When fit with separate c values, the best fitting c parameters
+for the model consistently optimized such that the c value for the
+varied group (c=.00008) was smaller in magnitude than the c value for
+the constant group(c= .00011). Recall that similarity decreases as a
+Gaussian function of distance (equation 1 above), and a smaller value of
+c will result in a more gradual drop-off in similarity as the distance
+between training throws and testing solutions increases.
+
+In summary, our modeling suggests that an instance-based model which
+assumes equivalent generalization gradients between constant and varied
+trained participants is unable to account for the extent of benefits of
+varied over constant training observed at testing. The evidence for this
+in the comparative model fits is that when a varied/constant dummy-coded
+variable for condition is explicitly added to the model, the variable
+adds a significant contribution to the prediction of test performance,
+with the variable condition yielding better performance than the
+constant conditions. However, if the instance-based generalization model
+is modified to assume that the training groups can differ in the
+steepness of their generalization gradient, by incorporating a separate
+generalization parameter for each group, then the instance-based model
+can account for our experimental results without explicitly taking
+training group into account. Henceforth this model will be referred to
+as the Instance-based Generalization with Adaptive Similarity (IGAS)
+model.
+
+# General Discussion
+
+Across two experiments, we found evidence in support of the benefits of
+variability hypothesis in a simple, computerized projectile throwing
+task. Generalization was observed in both constant and varied
+participants, in that both groups tended to perform better at novel
+positions in the testing phase than did participants who started with
+those positions in the training phase. However, varied trained
+participants consistently performed better than constant trained
+participants, in terms of both the testing phase in general, and in a
+comparison that only included untrained positions. We also found some
+evidence for the less commonly observed pattern wherein varied-trained
+participants outperform constant-trained participants even from
+conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
+participants performed significantly better on this identity comparison.
+In Experiment 2, the comparison was not significant initially, but
+became significant after controlling for the similarity measure that
+incorporates only a single value for the steepness of similarity-based
+generalization (c). Furthermore, we showed that the general pattern of
+results from Experiment 2 could be parsimoniously accommodated by an
+instance-based similarity model, but only with the assumption that
+constant and varied participants generalize their training experience to
+different degrees. Our results thus suggest that the benefits of
+variation cannot be explained by the varied-trained participants simply
+covering a broader range of the task space. Rather, the modeling
+suggests that varied participants also learn to adaptively tune their
+generalization function such that throwing locations generalize more
+broadly to one another than they do in the constant condition. A
+learning system could end up adopting a higher c value in the constant
+than variable training conditions by monitoring the trial-by-trial
+variability of the training items. The c parameter would be adapted
+downwards when adjacent training items are dissimilar to each other and
+adapted upwards when adjacent training items are the same. In this
+fashion, contextually appropriate c values could be empirically learned.
+This learning procedure would capture the insight that if a situation
+has a high amount variability, then the learner should be predisposed
+toward thinking that subsequent test items will also show considerable
+variability, in which case generalization gradients should be broad, as
+is achieved by low values for c.
+
+Also of interest is whether the IGAS model can predict the pattern of
+results wherein the varied condition outperforms the constant condition
+even from the position on which the constant condition trained. Although
+our models were fit using all of the Experiment 2 training and testing
+data, not just that of the identity comparisons, in @fig-Toy_Model2 we
+demonstrate how a simplified version of the IGAS model could in
+principle produce such a pattern. In addition to the assumption of
+differential generalization between varied and constant conditions, our
+simplified model makes explicit an assumption that is incorporated into
+the full IGAS model -- namely that even when being tested from a
+position identical to that which was trained, there are always some
+psychological contextual differences between training and testing
+throws, resulting in a non-zero dissimilarity.
+
+```{r}
+#| label: fig-Toy-Model2
+#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
+For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
+For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
+The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
+Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
+#| fig.width: 11
+#| fig.height: 11.5
+
+#
+
+p=2
+c<- .000002
+
+trainingTestingDifference=2000;
+cvaried=.00002
+cconstant=.0005
+simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
+                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
+                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
+                            genGauss=exp(-c*(abs((x-train.position)^p))),
+                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
+                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
+                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
+                            ) %>% 
+  group_by(x,condit) %>%
+  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
+
+#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
+
+colorVec=c("darkblue","darkred")
+plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
+                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
+                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
+                  ylim(c(0,1.05)),
+                  #xlim(c(250,950)),
+                  scale_x_continuous(breaks=seq(200,1000,by=200)),
+                  xlab("Test Stimulus"),
+                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
+                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
+                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
+                        legend.position="none"))
+
+ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
+ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
+ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
+  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
+ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
+  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
+# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
+
+gtitle="Figure 9."
+title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
+plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
+
+```
+
+As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
+@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
+The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been
+trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
+However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
+Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least
+certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001a; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
+
+Our modelling approach does differ from category learning implementations of instance-based models in several ways.
+One such difference is the nature of the training instances that are assumed to be stored.
+In category learning studies, instances are represented as
+points in a multidimensional space of all of the attributes that define a category item (e.g.
+size/color/shape).
+Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity
+applied to the ball on each throw.
+An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
+movement force, velocity, angle, posture) in addition to the decision and response time measures that typically
+exhaust the data generated from more classical cognitive tasks. Of course, whether learners actually are storing each individual motor
+instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in
+support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
+A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
+Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
+Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
+A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
+
+Our findings also have some conceptual overlap with an earlier study on
+the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
+lighting up consecutively, and attempt to time a button press with the
+onset of the final lamp. The design consisted of four separate constant
+groups, each training from a single lighting velocity, and a single
+varied group training with all four of the lighting velocities used by
+the individual constant groups. Participants were then split into four
+separate testing conditions, each of which were tested from a single
+novel lighting velocity of varying distance from the training
+conditions. The result of primary interest was that all participants
+performed worse as the distance between training and testing velocity
+increased -- a typical generalization decrement. However, varied
+participants showed less of a decrement than did constant participants.
+The authors take this result as evidence that varied training results in
+a less-steep generalization gradient than does constant training.
+Although the experimental conclusions of Catalano and Kleiner are
+similar to our own, our work is novel in that we account for our results
+with a cognitive model, and without assuming the formation of a schema.
+Additionally, the way in which Catalano and Kleiner collapse their
+separate constant groups together may result in similarity confounds
+between varied and constant conditions that leaves their study open to
+methodological criticisms, especially in light of related work which
+demonstrated that the extent to which varied training may be beneficial
+can depend on whether the constant group they are compared against
+trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
+similarity.
+
+## Limitations
+
+A limitation of this study concerns the ordering of the testing/transfer
+trials at the conclusion of both experiments. Participants were tested
+from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
+random, intermixed order. Because the varied group was trained from two
+positions that were also randomly ordered, they may have benefited from
+experience with this type of sequencing, whereas the constant groups had
+no experience with switching between positions trial to trial. This
+concern is somewhat ameliorated by the fact that the testing phase
+performance of the constant groups from their trained position was not
+significantly worse than their level of performance at the end of the
+training phase, suggesting that they were not harmed by random ordering
+of positions during testing. It should also be noted that the
+computerized task utilized in the present work is relatively simple
+compared to many of the real-world tasks utilized in prior research. It
+is thus conceivable that the effect of variability in more complex tasks
+is distinct from the process put forward in the present work. An
+important challenge for future work will be to assess the extent to
+which IGAS can account for generalization in relatively complex tasks
+with far more degrees of freedom.
+
+It is common for psychological process models of categorization learning
+to use an approach such as multidimensional scaling so as to transform
+the stimuli from the physical dimensions used in the particular task
+into the psychological dimensions more reflective of the actual human
+representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
+and using these similarity judgements to then compute the psychological
+distances between stimuli, which can then be fed into a subsequent
+model. In the present investigation, there was no such way to scale the
+x and y velocity components in terms of the psychological similarity,
+and thus our modelling does rely on the assumption that the
+psychological distances between the different throwing positions are
+proportional to absolute distances in the metric space of the task (e.g.
+the relative distance between positions 400 and 500 is equivalent to
+that between 800 and 900). However, an advantage of our approach is that
+we are measuring similarity in terms of how participants behave
+(applying a velocity to the ball), rather than the metric features of
+the task stimuli.
+
+## Conclusion
+
+Our experiments demonstrate a reliable benefit of varied training in a
+simple projectile launching task. Such results were accounted for by an
+instance-based model that assumes that varied training results in the
+computation of a broader similarity-based generalization gradient.
+Instance-based models augmented with this assumption may be a valuable
+approach towards better understanding skill generalization and transfer.
+
+# Project 2
 
@@
 #| fig-width: 10
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr)
-#options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+#| cache: false 
+# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+#   stringr, here,conflicted, patchwork, knitr)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+
+#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
 source(here::here("Functions","deLosh_data.R"))
-source(here::here("Functions","Display_Functions.R"))
+#source(here::here("Functions","Display_Functions.R"))
 
@@
 
-walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
 e2 <- readRDS(here("data/e2_08-04-23.rds")) 
@@
 ####| cache: false
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-#walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-#options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-```
-
-```{r}
-#| cache: true
+# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+```
+
+```{r}
+###| cache: true
 invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
@@
 e3_model <- load_e3()
+options(contrasts = initial_contrasts)
+
 ```
@@
 #| fig-width: 10
+###| eval: false
+
+pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
 
@@
 
+# plot_custom_effects <- function(model) {
+#   # Extract posterior samples for fixed effects
+#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
+
+#   # Calculate conditional effects
+#   post_samples <- post_samples %>%
+#     mutate(
+#       ALM_Constant = b_Intercept,
+#       EXAM_Constant = b_Intercept + b_ModelEXAM,
+#       ALM_Varied = b_Intercept + b_conditVaried,
+#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
+#     )
+
+#   # Reshape data for plotting
+#   plot_data <- post_samples %>%
+#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
+#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
+#     separate(Condition, into = c("Model", "Condit"), sep = "_")
+
+#   # Plot conditional effects
+#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
+#     geom_boxplot() +
+#     theme_minimal() +
+#     labs(x = "Model", y = "Estimate", color = "Condition")
+# }
+# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
+
 bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
@@
 # ALM - EXAM
-btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
-  pluck("contrasts") |> 
-  gather_emmeans_draws() |> 
-  group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
+# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
+#   pluck("contrasts") |> 
+#   gather_emmeans_draws() |> 
+#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
 
@@
 # Constant - Varied
-emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
-btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
-  group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
-# btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
-
-p_em_1<- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
+# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
+# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
+#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
+# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
+
+p_em_1 <- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
   pluck("contrasts") |>
@@
   p_e2 <- (p1 + p2+ p3) 
-#wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
+# #wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
 
@@
 
-# p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-#   ggplot2::xlab("Condition") +ylab("Model Error")
-# p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-#   labs(x="Model",y=NULL)
-# p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-#   scale_color_manual(values=wes_palette("Darjeeling1")) +
-#   labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- #p2 <- (p1 + p2+ p3)
+p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
+  ggplot2::xlab("Condition") +ylab("Model Error")
+p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
+  labs(x="Model",y=NULL)
+p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
+  scale_color_manual(values=wes_palette("Darjeeling1")) +
+  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
+
+ p2 <- (p1 + p2+ p3)
  (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
@@
 maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.
+
+# References
+
+::: {#refs}
+:::
+
+# Appendix
+
+{{< include Appendix/IGAS-Supplemental.qmd >}}

### 2024-04-02 Sections/full2.qmd
some full rendering updates

--- 2024-04-02 Sections/HTW.qmd
@@
   eval: true
+editor: 
+  markdown: 
+    wrap: 72
 ---
-
-_______________________________________________________________________________
-[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
-
-[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
-
-_______________________________________________________________________________
-
-# Introduction
-
-A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
-One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ].
-The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
-
-## Function Learning and Extrapolation
-
-The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
-
-@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
-Input stimuli and output responses were both lines of varying length.
-The correct output response was related to the length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
-@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
-Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
-In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
-All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
-
-The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
-The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models.
-The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
-The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
-When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
-
-### Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
-
-```{r}
-#| label: fig-delosh-extrap
-#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
-#| echo: false
-#| fig-width: 10
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr)
-#options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-source(here::here("Functions","deLosh_data.R"))
-source(here::here("Functions","Display_Functions.R"))
-
-extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
-                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
-
-linear_function <- function(x) 2.2 * x + 30
-exponential_function <- function(x) 200 * (1 - exp(-x/25))
-quadratic_function <- function(x) 210 - (x - 50)^2 / 12
-
-linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
-    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
-  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
-
-exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
-  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
-  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
-  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
-  extrapLines +
-  scale_shape_manual(values = c(1)) +
-  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
-  theme(legend.title = element_blank(), legend.position="top") +
-  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
-                                                  linetype = c(0, 1))))
-
-quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
-  geom_point( shape = 1) +
-  stat_function( fun = quadratic_function, geom = "line") +
-  labs(title="Quadratic Function",x="",y="") + extrapLines
-
-linear_plot + exponential_plot + quadratic_plot
-```
-
-## Overview Of Present Study
-
-The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
-To the best of our knowledge, this research is the first to employ the classic constant vs.
-varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
-Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
-
-To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
-Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.
-
-## Methods
-
-*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
-Participants were randomly assigned to one of two training conditions: varied training or constant training.
-
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
-band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
-Participants were instructed that only the x velocity component of the ball was relevant to the task.
-The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
-
-/
-```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
-#| label: fig-htw-task
-#| fig-cap: The Hit the wall task.
-Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
-The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
-#| eval: true
-#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
-knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
-
-```
-
-*Procedure.* All participants completed the task online.
-Participants were provided with a description of the experiment and indicated informed consent.
-@fig-design-e1 illustrates the general procedure.
-Participants completed a total of 90 trials during the training stage.
-In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
-
-Following the training stage, participants proceeded immediately to the testing stage.
-Participants were tested from all six velocity bands, in two separate stages.
-In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
-In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
-A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
-
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
-//| fig-responsive: false
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-```
 
@@
 
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e1 <- readRDS(here("data/e1_08-21-23.rds")) 
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-testE1 <- e1 |> filter(expMode2 == "Test")
-nbins=5
-trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
-trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,
+  gt,ggh4x,ggdist,htmltools,future,furrr)
+#options(brms.backend="cmdstanr",mc.cores=4)
+#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
+#walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
+conflicts_prefer(tidybayes::rstudent_t)
+walk(c("dplyr","here","brms","bayestestR"), conflict_prefer_all, quiet = TRUE)
+
+walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+
+# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+
+#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
+#source(here::here('Functions/IGAS_ProcessFunctions.R'))
+#options(brms.backend="cmdstanr",mc.cores=4)
+initial_contrasts <- options("contrasts")$contrasts
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+
+theme_set(theme_classic())
+
+library(tidybayes)
+
+# load the processed data from experiment 1 and 2
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
+
+# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
+# defaultContrasts = options()$contrasts
+# theme_set(theme_classic())
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
+                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
+
+e1Pos <- c("610","760","835","910")
+e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
+e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
 ```
 
-### Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.32 @rcoreteamLanguageEnvironmentStatistical2020.
-To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
-Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
-Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
-For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
-
-| Group Comparison         | Code                                                        | Data                 |
-| ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
-\
-
-In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
-extrapolation bands); 3) extent of discrimination between all six testing bands.
-We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
-Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
-The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
-Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-### Results
-
-```{r}
-#| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-##| label: tbl-e1-train-dist
-##| tbl-cap: "Experiment 1 - Learning curves. "
-##| output: asis
-
-bmm_e1_train<- trainE1_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e1_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#    kable(booktabs = TRUE)
-
-cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
-```
-
-::: {#tbl-e1-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
-| conditVaried |    79.64 |         57.92 |        101.63 |   1 |
-
-: **Experiment 1 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band.
-To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on.
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
-
-```{r}
-##| label: tbl-e1-bmm-dist
-##| tbl-cap: "E1. Training vs. Extrapolation"
-#| 
-modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
-bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE1, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-# 
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-
-# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
-cdted1 <- get_coef_details(bmtd, "conditVaried")
-cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
-cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e1-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:------------------------|-----------:|-----------:|-----------:|-----------:|
-| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
-| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
-| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
-| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |
-
-: **Experiment 1 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficients  indicate larger deviations from the baselines (Condition=constant & bandType=Trained) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
-constant) and band type (trained vs.
-extrapolation), with random intercepts for participants and bands.
-The model results are shown in @tbl-e1-bmm-dist.
-The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`).
-The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`).
-Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% credible intervals.
-
-pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-
-```
-
-```{r}
-##| label: tbl-e1-bmm-vx
-##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)
-
-cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e1_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-```
-
-\
-
-::: {#tbl-e1-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
-| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
-| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
-| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |
-
-Experiment 1.
-Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
-Varied) and Velocity Band.
-Larger coefficients on Band represent greater sensitivity/discrimination.
-{.striped .hover .sm}
-:::
-
-Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
-Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
-This difference is depicted visually in @fig-e1-test-vx.
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: Empirical distribution of velocities producing in testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-
-testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
-#| fig-cap: Experiment 1.
-Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE1$vb), 
-                     limits = c(0, 1400)) + 
-  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e1_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e1Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-     theme(legend.title=element_blank(), 
-           axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-## E1 Summary
-
-In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions  rresulted in lower final training performance is consistent with much of the prior researchon the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
-
-More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.
-
-## Experiment 2
-
-```{r}
-
-walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e2 <- readRDS(here("data/e2_08-04-23.rds")) 
-e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
-testE2 <- e2 |> filter(expMode2 == "Test")
-nbins=5
-trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
-
-# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
-```
-
-### Methods & Procedure
-
-The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
-The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800.
-Both groups were tested from all six bands.
-A total of 110 participants completed the experiment (Varied: 55, Constant: 55).
-
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 8.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| 
-//| 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
-
-### Results
-
-```{r}
-#| label: fig-e2-train-dev
-#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-#| eval: TRUE
-p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-bmm_e2_train <- trainE2_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e2_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
-# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T) 
-```
-
-::: {#tbl-e2-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
-| conditVaried |    36.15 |         16.35 |         55.67 |   1 |
-
-: **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups.
-We again compared training performance on the band common to both groups (600-800).
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
-```{r}
-modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
-bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE2, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
-cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
-cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e2-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-----------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
-| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
-| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
-| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |
-
-: **Experiment 2 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-\ \
-
-*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
-Constant) and band type (training vs.
-extrapolation bands).
-The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`).
-However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-#| eval: TRUE
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e2-bmm-vx
-##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
-
-cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
-sc2 <- get_coef_details(e2_vxBMM, "bandInt")
-intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
-```
-
-::: {#tbl-e2-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
-| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
-| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
-| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
-
-Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-The full model results are shown in @tbl-e2-bmm-vx.
-The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
-The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).
-
-```{r}
-#| label: fig-e2-test-vx
-#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e2-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-}
-
-pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE2$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e2_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e2Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-      theme(legend.title=element_blank(), 
-        axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-### Experiment 2 Summary
-
-Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands.
-Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.
-
-## Experiment 3
-
-```{r}
-
-e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
-    mutate(trainCon=case_when(
-    bandOrder=="Original" ~ "800",
-    bandOrder=="Reverse" ~ "600",
-    TRUE ~ NA_character_
-    ), trainCon=as.numeric(trainCon)) 
-e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
-testE3 <- e3 |> filter(expMode2 == "Test")
-nbins=5
-trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
-
-```
-
-### Methods & Procedure
-
-The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
-After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.
-within the target velocity range).
-All other aspects of the task and design are identical to Experiments 1 and 2.
-We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied).
-Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
-Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.
-
-### Results
-
-```{r}
-
-bmm_e3_train <- trainE3_max %>% 
-  brm(dist ~ condit*bandOrder, 
-      file=here("data/model_cache/e3_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
-cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
-cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
-```
-
-::: {#tbl-e3-train-dist}
-
-| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
-| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
-| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
-| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |
-
-: **Experiment 3 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-*Training*.
-@fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions).
-The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`).
-The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).
-
-```{r}
-#| label: fig-e3-train-dev
-#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
-#| eval: true
-p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
-p1
-```
-
-```{r}
-#options(brms.backend="cmdstanr",mc.cores=4)
-modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
-bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
-    data=testE3, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
-#wrap_plots(ce_bmtd3)
-
-#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")
-
-cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
-cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
-cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
-cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
-cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
-cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
-cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")
-
-```
-
-::: {#tbl-e3-bmm-dist}
-| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
-| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
-| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
-| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
-| conditVaried:bandTypeExtrapolation                  |    52.66 |         14.16 |         90.23 | 1.00 |
-| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
-| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
-| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |
-
-: **Experiment 3 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
-There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
-However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`.
-The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group.
-There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands.
-No other interactions were significant.
-
-<!-- ::: {#fig-e3-test-condEffect}
-
-![](../Assets/figs/e3_cond_effects_dist.png)
-
-E3.
-A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-::: -->
-
-```{r}
-#| label: fig-e3-test-dev
-#| fig-cap: Experiment 3 Testing Accuracy.
-A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% confidence intervals.
-#| eval: true
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-    facet_wrap(~bandOrder,ncol=1) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
- facet_wrap(~bandOrder,ncol=1)
-
-p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e3-bmm-vx
-##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
-# m2 <- fixef(e3_vxBMM)
-# mp3 <- m1[, c(1,2,4,5,6)]
-# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
-# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
-coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")
-
-```
-
-::: {#tbl-e3-bmm-vx}
-
-| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
-| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
-| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
-| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |
-
-Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist.
-For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
-The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
-Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
-However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating that the varied condition showed a greater slope coefficient on the reverse order bands, compared to the constant condition - this is clearly shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 10
-##| column: screen-inset-right
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-```
-
-```{r}
-#| label: fig-e3-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 10
-#| fig-width: 11
-##| eval: FALSE
-# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  facet_wrap(~bandOrder,ncol=1) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e3_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
-fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
-fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
-
-re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e3Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
-           fixed_effect_interaction2*(bandOrder=="Reverse") + 
-           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
-  slope = Estimate + adjust )
-
-pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density") +
-  facet_wrap(~bandOrder,ncol=1)
-
-pid_slopes3 <- re |>  
-    mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-    theme(legend.title=element_blank(), 
-      axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
-
-p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
-
-#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
-p3
-
-```
-
-### Experiment 3 Summary
+# Project 2
 
@@
 ####| cache: false
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-#walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-#options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
 ```
@@
 ```{r}
-#| cache: true
+###| cache: true
 invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
@@
 e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-e2_model <- load_e2()
-e3_model <- load_e3()
+options(contrasts = initial_contrasts)
+# e2_model <- load_e2()
+# e3_model <- load_e3()
 ```
-
-```{r}
-#| label: fig-alm-diagram
-#| fig.cap: The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model as used in the present work.
-Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
-The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
-The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule.
-alm_plot()
-```
-
-# Modeling Approach
-
-The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997].
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
-EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
-Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
-EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
-The slope is then used to extrapolate the response to the novel test stimulus.
-Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
-We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
-This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
-
-See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
-
-::: column-page-inset-right
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-|                    | **EXAM Extrapolation**                                             |                                                                                               |
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
-| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |
-
-: ALM & EXAM Equations {#tbl-alm-exam}
-:::
-
-## Model Fitting
-
-To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
-We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant.
-The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
-Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.
-
-::: {.callout}
-
-**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
-
-To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
-ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
-Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g.
-many neural network models).
-
-The general ABC procedure is to 1) define a prior distribution over model parameters.
-2) sample candidate parameter values, $\theta^*$, from the prior.
-3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
-4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
-5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
-6) Repeat until desired number of posterior samples are obtained.
-
-Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
-For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
-For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
-For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
-After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
-For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
 
@@
 
-#### Group level Patterns
-
-```{r}
-#| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-post_tabs <- abc_tables(post_dat,post_dat_l)
-train_tab <- abc_train_tables(pd_train,pd_train_l)
-
-e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
-
-e1_tab %>%
-  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
-  summarize(ME = mean(mean_error), .groups = "drop") %>%
-  pivot_wider(
-    names_from = c(Model, condit),
-    values_from = ME,
-    names_sep = "_"  # Add this line to specify the separator for column names
-  ) %>%
-  rename("Fit Method" = Fit_Method) %>%
-  gt() %>%
-  cols_move_to_start(columns = c(`Task Stage`)) %>%
-  cols_label(
-    `Task Stage` = "Task Stage"
-  ) %>%
-  fmt_number(
-    columns = starts_with("ALM") | starts_with("EXAM"),
-    decimals = 2
-  ) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = cell_fill(color = "white"),
-     locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_style(
-    style = cell_borders(sides = "top", color = "black", weight = px(1)),
-    locations = cells_column_labels()
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10, 
-    quarto.disable_processing = TRUE
-  ) 
-```
-
-```{r}
-#| label: fig-htw-post-dist
-#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters.
-Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y axes of the plots for the c parameter are scaled logarithmically."
-#| fig-height: 6
-#| fig-width: 10
-
-c_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
-  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
-
-lr_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
-  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
-c_post + lr_post
-```
-
-```{r}
-#| label: fig-htw-resid-pred
-#| fig-cap: "Model residuals for each combination of training condition, fit method, and model.
-Residuals reflect the difference between observed and predicted values.
-Lower values indicate better model fit.
-Note that y axes are scaled differently between facets.
-A) Residuals predicting each block of the training data.
-B) Residuals predicting each band during the testing stage.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-#| fig-height: 14
-#| fig-width: 11
-
-train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
-  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
-  group_by(id,condit,Model,Fit_Method,Block) |>
-  summarise(mean_error=mean(mean_error)) |>
-  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
-  stat_bar + 
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
-   scale_x_discrete(guide = "axis_nested") +
-  scale_fill_manual(values=c("gray10","gray50","gray92"))+
-  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
-  theme(legend.position="top")
-
-test_resid <-  post_dat |> 
-   group_by(id,condit,x,Model,Fit_Method,bandType) |>
-    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
-  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
-  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
-  scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
-  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")
-
-(train_resid / test_resid) +
-  #plot_layout(heights=c(1,1.5)) & 
-  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
-```
-
-The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat.
-There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences.
-The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
-
-We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model.
-Aggregated residuals are displayed in @fig-htw-resid-pred.
-The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method .
-Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms).
-The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models.
-It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task.
-Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories.
-However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data.
-All subsequent analyses and discussion will thus focus on the testing stage.
-
-The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots).
-Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
-The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models.
-Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.
-
 ```{r}
@@
 ```{r}
-#| label: fig-ee-e1
-#| fig-caption: conditional and marginal effects
-#| fig-height: 8
-#| fig-width: 10
 
@@
   labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right") 
+```
+
+```{r}
+#| label: fig-ee-e1b
+#| fig-caption: conditional and marginal effects
+#| fig-height: 8
+#| fig-width: 10
 
@@
 
+```{r}
+#| label: fig-ee-e1
+#| fig-caption: conditional and marginal effects
+#| fig-height: 8
+#| fig-width: 10
+###| eval: false
+pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
+  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
+
+# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
+e1_ee_brm_ae <- brm(data=pdl,
+  aerror ~  Model * condit + (1+bandInt|id), 
+  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
+  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
+
+bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
+  select(1,2,4,5,6) %>%
+  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
+  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
+  tibble::remove_rownames() %>%
+  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
+
+#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
+
+p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
+  ggplot2::xlab("Condition") +ylab("Model Error")
+p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
+  labs(x="Model",y=NULL)
+p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
+  scale_color_manual(values=wes_palette("Darjeeling1")) +
+  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
+
+p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+
+# plot_custom_effects <- function(model) {
+#   # Extract posterior samples for fixed effects
+#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
+
+#   # Calculate conditional effects
+#   post_samples <- post_samples %>%
+#     mutate(
+#       ALM_Constant = b_Intercept,
+#       EXAM_Constant = b_Intercept + b_ModelEXAM,
+#       ALM_Varied = b_Intercept + b_conditVaried,
+#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
+#     )
+
+#   # Reshape data for plotting
+#   plot_data <- post_samples %>%
+#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
+#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
+#     separate(Condition, into = c("Model", "Condit"), sep = "_")
+
+#   # Plot conditional effects
+#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
+#     geom_boxplot() +
+#     theme_minimal() +
+#     labs(x = "Model", y = "Estimate", color = "Condition")
+# }
+# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
+
+bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
+bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
+bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")
+
+posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
+  select(starts_with("b_")) %>%
+  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))
+
+constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
+varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
+comparison_EXAM <- constant_EXAM - varied_EXAM
+summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
+
+# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
+# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)
+
+# full set of Model x condit contrasts
+# ALM - EXAM
+# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
+#   pluck("contrasts") |> 
+#   gather_emmeans_draws() |> 
+#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
+
+# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()
+
+# Constant - Varied
+# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
+# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
+#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
+# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
+
+# p_em_1<- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
+#   pluck("contrasts") |>
+#   gather_emmeans_draws() |> 
+#   group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
+#   filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
+#   ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")
+
+# p_ce_1 / p_em_1
+```
+
 To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
@@
 The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
-
-```{r}
-#| label: tbl-htw-modelError-e23
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-
-post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
-train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
-
-pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e2_tab <- rbind(post_tabs2$agg_pred_full |>
- mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
- mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
-train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
-
-pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e3_tab <- rbind(post_tabs3$agg_pred_full |> 
-  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
-gt_table <- e23_tab %>%
-  pivot_wider(
-    names_from = c(Exp, Model, condit),
-    values_from = mean_error,
-    names_glue = "{Exp}_{Model}_{condit}"
-  ) %>%
-  arrange(Fit_Method, `Task Stage`) %>%
-  gt() %>%
-  cols_move_to_start(columns = `Task Stage`) %>%
-  cols_label(`Task Stage` = "Task Stage") %>%
-  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = list(
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
-  ) 
-gt_table
-```
-
-```{r}
-#| label: fig-cm-vx-pat-e2-e3
-#| fig-height: 8
-#| fig-width: 10
-#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage.
-Observed data is shown on the right.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-
-rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
- e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
-  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
-  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
-  stat_bar + 
-    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
-    scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .7), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-        #  strip.background = element_blank(),
-        #  strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(20,0,0,0), "pt")) + 
-         labs(title="Model Predictions Experiment 2 & 3", y="vx")
-```
-
-```{r}
-#| label: tbl-htw-ee-e23
-#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and the interaction between Model and Condition.
-The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
-The intercept reflects the baseline of ALM and Constant.
-The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
-Lower values indicate better model fit."
-
-e2_ee_brm_ae <- brm(data=pdl2,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
-bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
-bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
-
-bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
-
-e3_ee_brm_ae <- brm(data=pdl3,
-  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
-bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
-bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
-bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
-
-bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
-               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
-  relocate(exp, .before=Term)
-
-bct_table <- bct %>%
-  mutate(
-    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
-    pd = round(pd, 2)
-  ) %>%
-  gt() %>%
-  # tab_header(
-  #   title = "Bayesian Model Results",
-  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
-  # ) %>%
-  cols_label(
-    exp = "Experiment",
-    Term = "Term",
-    Estimate = "Estimate",
-    `95% CrI Lower` = "95% CrI Lower",
-    `95% CrI Upper` = "95% CrI Upper",
-    pd = "pd"
-  ) %>%
-  fmt_number(
-    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
-    decimals = 2
-  ) %>%
-  fmt_number(
-    columns = pd,
-    decimals = 2
-  ) %>%
-  tab_spanner(
-    label = "Credible Interval",
-    columns = c(`95% CrI Lower`, `95% CrI Upper`)
-  ) %>%
-  tab_style(
-    style = list(
-      #cell_fill(color = "lightgray"),
-      cell_text(weight = "bold"), 
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(
-      columns = c(Estimate, pd),
-      rows = Term=="ModelEXAM:conditVaried"
-    )
-  ) %>%
-   tab_row_group(
-    label = "Experiment 3",
-    rows = exp == "Exp 3"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 2",
-    rows = exp == "Exp 2"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 1",
-    rows = exp == "Exp 1"
-  ) %>%
-  tab_options(
-    table.font.size = 10,
-    heading.title.font.size = 16,
-    heading.subtitle.font.size = 14,
-    quarto.disable_processing = TRUE
-    #row_group.background.color = "gray95"
-  )
-bct_table
-
-```
-
-*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
-For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
-The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
-The Bayesian regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
-The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
-Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
-Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
-We thus also controleld for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
-There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
-
-```{r}
-#| label: fig-e2_e3_ae
-#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied) on Model Error for Experiment 2 and 3 data.
-Experiment 3 also includes a control for the order of training vs.
-testing bands (original order vs.
-reverse order)."
-#| fig-height: 6
-#| fig-width: 9
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
-p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- p_e2 <- (p1 + p2+ p3) 
-#wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
-                         effects = "Model:condit", 
-                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
-     points=FALSE,plot=FALSE)$`Model:condit` + 
-     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
-     theme(legend.position="right") + 
-     scale_color_manual(values=wes_palette("Darjeeling1"))
-
-# p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-#   ggplot2::xlab("Condition") +ylab("Model Error")
-# p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-#   labs(x="Model",y=NULL)
-# p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-#   scale_color_manual(values=wes_palette("Darjeeling1")) +
-#   labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- #p2 <- (p1 + p2+ p3)
- (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-```
-
-*Computational Model Summary*.
-Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23).
-This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group.
-It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model.
-A subset of these participants are shown in @fig-htw-indv-pred.
-
-```{r}
-#| label: fig-htw-best-model
-#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
-#| fig-height: 12
-#| fig-width: 11
-
-tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
-  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
-  filter(Fit_Method=="Test_Train") |>
-  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
-    mutate(e2=abs(y-pred)) |> 
-    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
-    group_by(id,condit,Model,Fit_Method,Exp) |> 
-    summarise(mean_error=mean(mean_error)) |> 
-    arrange(id,condit,Fit_Method) |>
-    round_tibble(1)
-
-best_id <- tid1 |> 
-  group_by(id,condit,Fit_Method) |> 
-  mutate(best=ifelse(mean_error==min(mean_error),1,0))
-
-lowest_error_model <- best_id %>%
-  group_by(id, condit,Fit_Method, Exp) %>%
-  summarise(Best_Model = Model[which.min(mean_error)],
-            Lowest_error = min(mean_error),
-            differential = min(mean_error) - max(mean_error)) %>%
-  ungroup()
-
-error_difference<- best_id %>%
-  select(id, condit, Model,Fit_Method, mean_error) %>%
-  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
-  mutate(Error_difference = (ALM - EXAM))
-
-full_comparison <- lowest_error_model |> 
-  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
-  group_by(condit,Fit_Method,Best_Model) |> 
-  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
-  arrange(Fit_Method,-Error_difference)
-
-full_comparison |> 
-  filter(Fit_Method=="Test_Train") |> 
-  ungroup() |>
-  mutate(id = reorder(id, Error_difference)) %>%
-  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
-  geom_col() +
-  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
-  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
-  theme(axis.text.y = element_text(size=8)) +
-  labs(fill="Best Model",
-  x="Mean Model Error Difference (ALM - EXAM)",
-  y="Participant")
-
-```
-
-```{r  fig.width=11, fig.height=10}
-#| label: fig-htw-indv-pred
-#| fig-cap: Model predictions alongside observed data for a subset of individual participants.
-A) 3 constant and 3 varied participants fit to both the test and training data.
-B) 3 constant and 3 varied subjects fit to only the trainign data.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands.
-#| fig-height: 7
-#| fig-width: 10
-
-cId_tr <- c(137, 181, 11)
-vId_tr <- c(14, 193, 47)
-cId_tt <- c(11, 93, 35)
-vId_tt <- c(1,14,74)
-cId_new <- c(175, 68, 93, 74)
-# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")
-
-e1_sbjs <- c(49,68,155, 175,74)
-e3_sbjs <-  c(245, 280, 249)
-e2_sbjs <- c(197, 157, 312, 334)
-cFinal <- c(49, 128,202 )
-vFinal <- c(68,70,245)
-
-indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
-  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
-  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))
-
-testIndv <- indv_post_l |> 
-#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
-   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
-  group_by(id,condit,Fit_Method,Model,Resp) |>
-   mutate(flab=paste0("Subject: ",id)) |>
-  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar_sd + 
-  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
-  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
-  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
-  labs(title="Individual Participant fits from Test & Train Fitting Method",
-       y="X Velocity",fill="Target Velocity") +
-   guides(fill = guide_legend(nrow = 1)) + 
-  theme(legend.position = "bottom",axis.title.x = element_blank())
-
-testIndv 
-```
-
-# General Discussion
-
-*Experimental Result Summary*
-
-Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
-In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-
-Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
-The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.
-
-Experiment 2 extended these findings by reversing the order of the training and testing bands.
-Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases.
-However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.
-
-In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments.
-Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied).
-The varied condition showed larger deviations at the end of training, consistent with the previous experiments.
-Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition.
-During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands.
-The reverse order conditions showed smaller deviations compared to the original order conditions.
-Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.
-
-All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015].
-The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group.
-Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.
-
-Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
-Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
-A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
-These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study.
-@vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
-However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
-
-*Modeling Summary*
-EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group.
-May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule.
-But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval.
-The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-
-One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
-
-- why does Constant do better 
-    - kind of task that permits for prior knowledge about 0
-    - learning - end of training
-- what does it suggest that the constant group was disproportionately well explained by the EXAM model?
--
-
-*Limitations*
-- amount of training
-- constant group always having more experience at nearest position
-
-- constant group having more extrapolation items
-
-- only training and extrapolation - no interpolation items - so harder to make claims about extrapolation specifically, as opposed to generalization in general.
-
-- no mechanism to account for sequence effects in models
-
-- more rigorous model comparison to account for exams greater complexity
-
-- knowledge of function
-
-## Comparison to Project 1
-
-### Differences between the tasks
-
-There are a number of differences between Project 1's Hit The Target (HTT), and Project 2's Hit The Wall (HTW) tasks.
-
-- Task Space Complexity: In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard.
-Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.
-
-- Perceptual Distinctiveness: HTT offers perceptually distinct varied conditions that directly relate to the task's demands, which may increase the sallience between training positions encounted by the varied group.
-In contrast, HTW's varied conditions differ only in the numerical values displayed, lacking the same level of perceptual differentiation.
-Conversely in HTW, the only difference between conditions for the varied group are the numbers displayed at the top of the screen which indicate the current target band(e.g.
-800-1000, or 1000-1200)
-
-- In HTW, our primary testing stage of interest has no feedback, whereas in HTT testing always included feedback (the intermittent testing in HTT expt 1 being the only exception).
-Of course, we do collect testing with feedback data at the end of HTW, but we haven't focused on that data at all in our modelling work thus far.
-It's also interesting to recall that the gap between varied and constant in HTW does seem to close substantially in the testing-with-feedback stage.
-The difference between no-feedback and feedback testing might be relevant if the benefits of variation have anything to do with improving subsequent learning (as opposed to subsequent immediate performance), OR if the benefits of constant training rely on having the most useful anchor, having the most useful anchor might be a lot less helpful if you're getting feedback from novel positions and can thus immediately begin to form position-specific anchors for the novelties, rather than relying on a training anchor.
-
-- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments.
-However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands.
-This means that in HTT the varied group gets half as much experience on any one position as the constant group, and in HTW they only get 1/3 as much experience in any one position.
-There are likely myriad ways in which this might impact the success of the varied group regardless of how you think the benefits of variation might be occurring, e.g.
-maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.

### 2024-04-02 Functions/IGAS_ProcessFunctions.R

@@ -1,17 +1,17 @@
-packages <- c('ez','plyr','dplyr','sciplot','ggplot2','magrittr','car','psych','tidyr',
-              'Matrix','cluster','emdbook','hexbin','caret','glmnet',
-              'afex','purrr','broom','ggpubr','rstatix','stargazer','data.table','cowplot','magick',
-              'stringr')
-have = packages %in% rownames(installed.packages())
-if ( any(!have) ) {print("installing missing packages"); install.packages(packages[!have]) }
-invisible(lapply(packages, require, character.only = TRUE))
-#install.packages("data.table", type="source", repos="https://Rdatatable.gitlab.io/data.table")
-select <- dplyr::select
-mutate <- dplyr::mutate
-filter <- dplyr::filter
-rename <- dplyr::rename
-summarise <- dplyr::summarise
-summarize <- dplyr::summarise
+# packages <- c('ez','plyr','dplyr','sciplot','ggplot2','magrittr','car','psych','tidyr',
+#               'Matrix','cluster','emdbook','hexbin','caret','glmnet',
+#               'afex','purrr','broom','ggpubr','rstatix','stargazer','data.table','cowplot','magick',
+#               'stringr')
+# have = packages %in% rownames(installed.packages())
+# if ( any(!have) ) {print("installing missing packages"); install.packages(packages[!have]) }
+# invisible(lapply(packages, require, character.only = TRUE))
+# #install.packages("data.table", type="source", repos="https://Rdatatable.gitlab.io/data.table")
+# select <- dplyr::select
+# mutate <- dplyr::mutate
+# filter <- dplyr::filter
+# rename <- dplyr::rename
+# summarise <- dplyr::summarise
+# summarize <- dplyr::summarise
 #rm(list=ls())
 dodge <- position_dodge(width = 0.9)
 
@@ -19,20 +19,20 @@ dodge <- position_dodge(width = 0.9)
 
 
 
-startCluster <- function(progressVar=100,ncores=NULL)
-{
-  if(is.null(ncores))
-  {
-  ncores=detectCores(all.tests = FALSE, logical = TRUE)
-  }
-  cl       <<- makeSOCKcluster(ncores)
-  pb       <<- txtProgressBar(max = progressVar, style = 3)
-  progress <- function(n){setTxtProgressBar(pb, n)}
-  sopts     <<- list(progress = progress)
-  registerDoSNOW(cl)
[…]

### 2024-04-03 Sections/IGAS.qmd
copy some of the data files over
render full

@@
 In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures,
-instance or exemplar-based models have accounted for human behavior
-across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
+Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
 As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
@@
 #| label: fig-taskSpace
-#| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
 This empirical solution space was compiled from all of the participants in experiment 2.
-Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+#| fig-width: 11
+#| fig-height: 9
 #| 
@@
 
-ss
-fs
+library(patchwork)
+ss/fs
 
@@
 Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001a; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
+certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
 
@@
 Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw. An advantage of many motor learning
-tasks is the relative ease with which task execution variables can be
-directly measured (e.g. movement force, velocity, angle, posture) in
-addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of
-course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work
--- though as described in the introduction there is some evidence in
+applied to the ball on each throw.
+An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
+movement force, velocity, angle, posture) in addition to the decision and response time measures that typically
+exhaust the data generated from more classical cognitive tasks. Of course, whether learners actually are storing each individual motor
+instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in
 support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly
-noteworthy instance-based model of sensory-motor behavior is the
-Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995]. Knowledge II explicitly defines instances as
-postures (joint combinations), and is thus far more detailed than IGAS
-in regards to the contents of stored instances. Knowledge II also
-differs from IGAS in that learning is accounted for by both the
-retrieval of stored postures, and the generation of novel postures via
-the modification of retrieved postures. A promising avenue for future
-research would be to combine the adaptive similarity mechanism of IGAS
-with the novel instance generation mechanisms of Knowledge II.
+A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
+Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
+Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
+A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
 

### 2024-04-03 Functions/IGAS_ProcessFunctions.R

@@ -1,17 +1,17 @@
-# packages <- c('ez','plyr','dplyr','sciplot','ggplot2','magrittr','car','psych','tidyr',
-#               'Matrix','cluster','emdbook','hexbin','caret','glmnet',
-#               'afex','purrr','broom','ggpubr','rstatix','stargazer','data.table','cowplot','magick',
-#               'stringr')
-# have = packages %in% rownames(installed.packages())
-# if ( any(!have) ) {print("installing missing packages"); install.packages(packages[!have]) }
-# invisible(lapply(packages, require, character.only = TRUE))
-# #install.packages("data.table", type="source", repos="https://Rdatatable.gitlab.io/data.table")
-# select <- dplyr::select
-# mutate <- dplyr::mutate
-# filter <- dplyr::filter
-# rename <- dplyr::rename
-# summarise <- dplyr::summarise
-# summarize <- dplyr::summarise
+packages <- c('ez','plyr','dplyr','sciplot','ggplot2','magrittr','car','psych','tidyr',
+              'Matrix','cluster','emdbook','hexbin','caret','glmnet',
+              'afex','purrr','broom','ggpubr','rstatix','stargazer','data.table','cowplot','magick',
+              'stringr')
+have = packages %in% rownames(installed.packages())
+if ( any(!have) ) {print("installing missing packages"); install.packages(packages[!have]) }
+invisible(lapply(packages, require, character.only = TRUE))
+#install.packages("data.table", type="source", repos="https://Rdatatable.gitlab.io/data.table")
+select <- dplyr::select
+mutate <- dplyr::mutate
+filter <- dplyr::filter
+rename <- dplyr::rename
+summarise <- dplyr::summarise
+summarize <- dplyr::summarise
 #rm(list=ls())
 dodge <- position_dodge(width = 0.9)
 

### 2024-04-04 Sections/Discussion.qmd
update full dissertation page

@@
 
-test
+## Comparison to Project 1
+
+### Differences between the tasks
+
+There are a number of differences between Project 1's Hit The Target (HTT), and Project 2's Hit The Wall (HTW) tasks.
+
+- Task Space Complexity: In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard.
+Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.
+
+- Perceptual Distinctiveness: HTT offers perceptually distinct varied conditions that directly relate to the task's demands, which may increase the sallience between training positions encounted by the varied group.
+In contrast, HTW's varied conditions differ only in the numerical values displayed, lacking the same level of perceptual differentiation.
+Conversely in HTW, the only difference between conditions for the varied group are the numbers displayed at the top of the screen which indicate the current target band(e.g.
+800-1000, or 1000-1200)
+
+- In HTW, our primary testing stage of interest has no feedback, whereas in HTT testing always included feedback (the intermittent testing in HTT expt 1 being the only exception).
+Of course, we do collect testing with feedback data at the end of HTW, but we haven't focused on that data at all in our modelling work thus far.
+It's also interesting to recall that the gap between varied and constant in HTW does seem to close substantially in the testing-with-feedback stage.
+The difference between no-feedback and feedback testing might be relevant if the benefits of variation have anything to do with improving subsequent learning (as opposed to subsequent immediate performance), OR if the benefits of constant training rely on having the most useful anchor, having the most useful anchor might be a lot less helpful if you're getting feedback from novel positions and can thus immediately begin to form position-specific anchors for the novelties, rather than relying on a training anchor.
+
+- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments.
+However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands.
+This means that in HTT the varied group gets half as much experience on any one position as the constant group, and in HTW they only get 1/3 as much experience in any one position.
+There are likely myriad ways in which this might impact the success of the varied group regardless of how you think the benefits of variation might be occurring, e.g.
+maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.

### 2024-04-04 Sections/full.qmd
update full dissertation page

@@
   eval: true
+format:
+  html: default
+  hugo-md:
+    echo: false
+    html-math-method: mathjax
+    output-file: diss_full_hugo.md
+  gfm:
+    echo: true
+    output-file: diss_full_gfm.md
 editor: 
@@
     wrap: 72
+prefer-html: true
 ---
@@
 The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-
 One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
 
-- why does Constant do better 
-    - kind of task that permits for prior knowledge about 0
-    - learning - end of training
-- what does it suggest that the constant group was disproportionately well explained by the EXAM model?
--
-
 *Limitations*
-- amount of training
-- constant group always having more experience at nearest position
-
-- constant group having more extrapolation items
-
-- only training and extrapolation - no interpolation items - so harder to make claims about extrapolation specifically, as opposed to generalization in general.
-
-- no mechanism to account for sequence effects in models
-
-- more rigorous model comparison to account for exams greater complexity
-
-- knowledge of function
+
+While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
+First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
+Such a difference may be an unavoidable consequence of varied vs.
+constant design which match the total number of training trials between the two groups.
+However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
+Another limitation is that the testing stage did not include any interpolation items, i.e.
+the participants tested only from the training bands they experienced during training, or from extrapolation bands.
+The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
+Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
+Finally, the task employed in the present study consisted of only a linear, positive function.
+Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
+It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
 

### 2024-04-04 Sections/HTW.qmd
update

@@
 
-- why does Constant do better 
-    - kind of task that permits for prior knowledge about 0
-    - learning - end of training
-- what does it suggest that the constant group was disproportionately well explained by the EXAM model?
--
-
 *Limitations*
-- amount of training
-- constant group always having more experience at nearest position
-
-- constant group having more extrapolation items
-
-- only training and extrapolation - no interpolation items - so harder to make claims about extrapolation specifically, as opposed to generalization in general.
-
-- no mechanism to account for sequence effects in models
-
-- more rigorous model comparison to account for exams greater complexity
-
-- knowledge of function
-
-## Comparison to Project 1
-
-### Differences between the tasks
-
-There are a number of differences between Project 1's Hit The Target (HTT), and Project 2's Hit The Wall (HTW) tasks.
-
-- Task Space Complexity: In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard.
-Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.
-
-- Perceptual Distinctiveness: HTT offers perceptually distinct varied conditions that directly relate to the task's demands, which may increase the sallience between training positions encounted by the varied group.
-In contrast, HTW's varied conditions differ only in the numerical values displayed, lacking the same level of perceptual differentiation.
-Conversely in HTW, the only difference between conditions for the varied group are the numbers displayed at the top of the screen which indicate the current target band(e.g.
-800-1000, or 1000-1200)
-
-- In HTW, our primary testing stage of interest has no feedback, whereas in HTT testing always included feedback (the intermittent testing in HTT expt 1 being the only exception).
-Of course, we do collect testing with feedback data at the end of HTW, but we haven't focused on that data at all in our modelling work thus far.
-It's also interesting to recall that the gap between varied and constant in HTW does seem to close substantially in the testing-with-feedback stage.
-The difference between no-feedback and feedback testing might be relevant if the benefits of variation have anything to do with improving subsequent learning (as opposed to subsequent immediate performance), OR if the benefits of constant training rely on having the most useful anchor, having the most useful anchor might be a lot less helpful if you're getting feedback from novel positions and can thus immediately begin to form position-specific anchors for the novelties, rather than relying on a training anchor.
-
-- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments.
-However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands.
-This means that in HTT the varied group gets half as much experience on any one position as the constant group, and in HTW they only get 1/3 as much experience in any one position.
-There are likely myriad ways in which this might impact the success of the varied group regardless of how you think the benefits of variation might be occurring, e.g.
-maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.
+
+While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
+First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
+Such a difference may be an unavoidable consequence of varied vs.
+constant design which match the total number of training trials between the two groups.
+However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
+Another limitation is that the testing stage did not include any interpolation items, i.e.
+the participants tested only from the training bands they experienced during training, or from extrapolation bands.
+The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
+Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
+Finally, the task employed in the present study consisted of only a linear, positive function.
+Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
+It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.

### 2024-04-04 Sections/full.qmd
redo

@@
 subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: last-modified
+date: 04/04/24
 #page-layout: full

### 2024-04-04 Sections/full.qmd
re-render full with pdf attempt

@@
     output-file: diss_full_gfm.md
+  hikmah-manuscript-pdf:
+    echo: false
+    output-file: "hikmah-e1.pdf"
+    mainfont: "Linux Libertine O"
+    mainfontoptions:
+      - "Numbers=Proportional"
+      - "Numbers=OldStyle"
+    mathfont: "Libertinus Math"
 editor: 

### 2024-04-04 Sections/IGAS.qmd
fix igas crossrefs; add callout styling

@@
 Error bars indicate standard error of the mean.
+#| fig-width: 11
+#| fig-height: 8
 
@@
 
-e2train1
-e2train2
+e2train1/e2train2
 
@@
 
-library(patchwork)
 ss/fs
@@
 our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy_Model2 we
+data, not just that of the identity comparisons, in @fig-Toy-Model-dis we
 demonstrate how a simplified version of the IGAS model could in
@@
 ```{r}
-#| label: fig-Toy-Model2
+#| label: fig-Toy-Model-dis
 #| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
@@
 #| fig.width: 11
-#| fig.height: 11.5
-
-#
+#| fig.height: 11.0
 
@@
 
-gtitle="Figure 9."
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-
+#gtitle="Figure 9."
+#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
+#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
+p1 <- (ip1+ip2) / (ip3+ip4)
+
+p1
 ```

### 2024-04-04 Sections/full.qmd
fix igas crossrefs; add callout styling

--- 2024-04-04 Sections/full.qmd
@@
     echo: false
+    output: asis
     html-math-method: mathjax
@@
 
-gtitle="Figure 9."
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
+#gtitle="Figure 9."
+#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
+#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
+p1 <- (ip1+ip2) / (ip3+ip4)
+
+p1
 

### 2024-04-04 Sections/full.tex
fixes

--- 2024-04-04 Sections/full.qmd
@@
----
-title: Full Dissertation
-subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: 04/04/24
-#page-layout: full
-code-fold: true
-code-tools: true
-toc: true
-toc-location: body
-toc-title: Contents
-execute: 
-  warning: false
-  eval: true
-format:
-  html: default
-  hugo-md:
-    echo: false
-    html-math-method: mathjax
-    output-file: diss_full_hugo.md
-  gfm:
-    echo: true
-    output-file: diss_full_gfm.md
-editor: 
-  markdown: 
-    wrap: 72
-prefer-html: true
----
-
-# Variability and Generalization
-
-The factors that influence the generalization of learning are of considerable interest to both researchers exploring the human learning system and practitioners aiming to enhance the effectiveness of educational and training interventions.
-The present effort will focus specifically on the role of variability in the learning input.
-Variability manipulations typically regulate either the number of distinct instances presented to learners during training, or the dispersion of these instances.
-Such manipulations have been empirically demonstrated to affect subsequent generalization performance.
-This essay will offer an in-depth review of the extant literature on the influence of variability, spanning multiple relevant domains.
-
-## The study of variability
-
-Studies investigating the "benefits of variability" hypothesis usually assign participants to either a constant or varied group for the training stage of the experiment.
-Then, subjects in both groups complete an identical testing stage which often consists items/conditions seen during training, and novel items/conditions.
-If the varied group performs better in the testing stage, this is taken for evidence of the benefits of variability hypothesis.
-Even within this relatively straightforward between-groups design, researchers must navigate several crucial methodological choices, highlighted below:
-
-1)  Variables Subject to Variation.
-In multidimensional tasks, researchers have the option to vary numerous variables.
-The experimenters must decide the specific dimension(s) across which variation will occur.
-For instance, in a projectile throwing accuracy task -- researchers might vary the distance from the target, the size of the target, the weight of the projectile.
-They might also vary a contextual variable not directly relevant to the task, but which will still be encoded by the subject on a trial by trial basis, e.g.
-the background color.
-
-2)  Magnitude of Variation, relative to the control condition.
-The simplest comparison would be to compare a constant group who trains with 1 example/condition, against a varied group that trains from 2 examples/conditions.
-However, it is not uncommon in the literature for the varied condition to train from 3 or 4 conditions.
-For example, @catalanoDistantTransferCoincident1984a train varied subjects from 4 different velocities in their coincident timing task, and [@goodeSuperiorityVariableRepeated2008] have varied subjects' practice with 3 different variants (i.e.
-different letter scrambles of the same word) of an anagram for a given word, while their constant participants view the same variant 3 different times.
-Alternatively, rather than a constant vs.
-varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items [@nosofskyModelguidedSearchOptimal2018].
-
-3)  Locations within Task-Space.
-For tasks in which the stimuli or conditions fall within a continuous metric space, the experimenter must decide whether the varied instances are relatively close together (e.g.
-throwing a ball from a distance of 4 feet and 5 feet), or far apart (throwing from 4 feet and 20 feet).
-Spreading the varied training items further apart may be beneficial in terms of providing a more representative sample of the task space to the learner, however large distances may also result in significant differences in difficulty between the training examples, which can be a common confound in variability studies.
-
-4)  Proximity of Testing to Training Conditions.
-Intuitively, the fairest form of comparison is to include testing conditions that are of an equivalent distance from both the varied and constant groups.
-However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978].
-
-## Variability Literature Review
-
-An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
-In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
-a low variability condition), or spread further away from the prototype (the varied-training group).
-It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
-The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
-The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
-The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
-However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
-The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
-Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
-One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
-
-## Motor skill learning
-
-Training variation has also been shown to promote transfer in motor learning.
-Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
-When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves).
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  12pt,
+  letterpaper,
+]{article}
+
+\usepackage{amsmath,amssymb}
+\usepackage{setspace}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+  \setmainfont[Numbers=Proportional,Numbers=OldStyle]{Linux Libertine O}
+  \setmathfont[]{Libertinus Math}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage{xcolor}
+\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+
+% -----------------------
+% CUSTOM PREAMBLE STUFF
+% -----------------------
+
+% -----------------
+% Typography tweaks
+% -----------------
+% Indent size
+\setlength{\parindent}{0.5in}
+\setlength{\leftmargin}{0.5in}
+
+% Fix widows and orphans
+\usepackage[all,defaultlines=2]{nowidow}
+
+% List things
+\usepackage{enumitem}
+% Same document-level indentation for ordered and ordered lists
+\setlist[1]{labelindent=\parindent}
+\setlist[itemize]{leftmargin=*}
+\setlist[enumerate]{leftmargin=*}
+
+% Wrap definition list terms
+% https://tex.stackexchange.com/a/9763/11851
+\setlist[description]{style=unboxed}
+
+% For better TOCs
+\usepackage{tocloft}
+
+% Remove left margin in lists inside longtables
+% https://tex.stackexchange.com/a/378190/11851
+\AtBeginEnvironment{longtable}{\setlist[itemize]{nosep, wide=0pt, leftmargin=*, before=\vspace*{-\baselineskip}, after=\vspace*{-\baselineskip}}}
+
+% For fancy ORCID links
+\usepackage{orcidlink}
+
+% Indent all first paragraphs because APA wants that
+\usepackage{indentfirst}
+
+% -----------------
+% Title block stuff
+% -----------------
+
+% Abstract
+\usepackage{abstract}
+\renewcommand{\abstractnamefont}{\normalfont\normalsize\bfseries}
+\renewcommand{\abstracttextfont}{\normalsize}
+\setlength{\absleftindent}{\parindent}
+\setlength{\absrightindent}{\parindent}
+
+% Keywords
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}}#1}
+
+% Title
+\usepackage{titling}
+\setlength{\droptitle}{2\baselineskip}
+\pretitle{\begin{center}\normalfont\normalsize\bfseries}
+\posttitle{\par\end{center}\vspace{2\baselineskip}}
+
+% ------------------
+% Section headings
+% ------------------
+\usepackage{titlesec}
+\titleformat*{\section}{\center\normalsize\bfseries}
+\titleformat*{\subsection}{\normalsize\bfseries}
+\titleformat*{\subsubsection}{\normalsize\bfseries\itshape}
+\titleformat{\paragraph}[runin]{\bfseries}{\theparagraph.}{3pt}{\space}[.]
+\titleformat{\subparagraph}[runin]{\bfseries\itshape}{\thesubparagraph.}{3pt}{\space}[.]
+
+% \titlespacing{<command>}{<left>}{<before-sep>}{<after-sep>}
+% Starred version removes indentation in following paragraph
+\titlespacing*{\section}{0em}{2em}{0em}
+\titlespacing*{\subsection}{0em}{1em}{0em}
+\titlespacing*{\subsubsection}{0em}{0em}{0em}
+\titlespacing*{\paragraph}{\parindent}{1ex}{1em}
+\titlespacing*{\subparagraph}{\parindent}{1ex}{1em}
+
+% -----------
+% Footnotes
+% -----------
+% NB: footmisc has to come after biblatex because of conflicts
+\usepackage[bottom]{footmisc}
+\renewcommand*{\footnotelayout}{\footnotesize}
+
+\addtolength{\skip\footins}{12pt}  % vertical space between rule and main text
+\setlength{\footnotesep}{16pt}  % vertical space between footnotes
+
+% ----------
+% Captions
+% ----------
+\usepackage[font=normalsize]{caption}
+
+% ---------------------------
+% END CUSTOM PREAMBLE STUFF
+% ---------------------------
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\usepackage{caption}
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
+\definecolor{quarto-callout-color}{HTML}{909090}
+\definecolor{quarto-callout-note-color}{HTML}{0758E5}
+\definecolor{quarto-callout-important-color}{HTML}{CC1914}
+\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
+\definecolor{quarto-callout-tip-color}{HTML}{00A047}
+\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
+\definecolor{quarto-callout-color-frame}{HTML}{acacac}
+\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
+\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
+\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
+\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
+\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
+\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage{bookmark}
+
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Full Dissertation},
+  colorlinks=true,
+  linkcolor={DarkSlateBlue},
+  filecolor={Maroon},
+  citecolor={DarkSlateBlue},
+  urlcolor={DarkSlateBlue},
+  pdfcreator={LaTeX via pandoc}}
+
+% -----------------------
+% END-OF-PREAMBLE STUFF
+% -----------------------
+
+% For patching commands like \subtitle
+\usepackage{etoolbox}
+
+% -----------------
+% Running headers
+% -----------------
+
+\usepackage{fancyhdr}
+\setlength{\headheight}{0.25in}
+\renewcommand{\headrulewidth}{0pt}  % Remove lines
+\renewcommand{\footrulewidth}{0pt}
+
+% SHORT TITLE           Page #
+\fancypagestyle{normal}{
+  \fancyhf{}
+  \lhead{\uppercase{ Full Dissertation }}
+  \rhead{\thepage}
+}
+
+% Running head: SHORT TITLE        Page #
+\fancypagestyle{title}{
+  \fancyhf{}
+  \lhead{Running head: \uppercase{ Full Dissertation }}
+  \rhead{}
+}
+
+% Use regular heading style
+\pagestyle{normal}
+
+% ----------
+% BibLaTeX
+% ----------
+\usepackage[style=apa,backend=biber]{biblatex}
+
+\setlength\bibitemsep{0pt}  % No space between bib entries
+\setlength\bibhang{\parindent}  % Match document indentation
+
+% Fix biblatex's odd preference for using In: by default.
+\renewbibmacro{in:}{%
+  \ifentrytype{article}{}{%
+  \printtext{\bibstring{}\intitlepunct}}}
+
+\addbibresource{../Assets/Bib/Dissertation.bib}
+
+% Start bibliography on new page
+\pretocmd{\printbibliography}{\clearpage}{}{}
+
+% ---------------------- 
+% Title block elements
+% ---------------------- 
+\usepackage{authblk}
+\renewcommand*{\Authsep}{, }
+\renewcommand*{\Authand}{ and }
+\renewcommand*{\Authands}{, and }
+\renewcommand*{\Affilfont}{\normalsize}
+\renewcommand*{\Authfont}{\normalsize}
+
+\title{Full Dissertation:}
+
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par #1 \par}{}{}
+}
+\makeatother
+\subtitle{An instance-based model account of the benefits of varied
+practice in visuomotor skill}
+
+\date{}
+
+% Typeset URLs in the same font as their parent environment
+%
+% This has to come at the end of the preamble, after any biblatex stuff because 
+% some biblatex styles (like APA) define their own \urlstyle{}
+\usepackage{url}
+\urlstyle{same}
+
+% ---------------------------
+% END END-OF-PREAMBLE STUFF
+% ---------------------------
+\begin{document}
+% ---------------
+% TITLE SECTION
+% ---------------
+
+\begin{titlepage}
+\center
+
+% Don't include a newpage before \maketitle
+{\let\newpage\relax\maketitle}
+
+% Needs to come after \maketitle
+\thispagestyle{title}
+
+\vspace{0.25in}
+
+\vspace{0.5in}
+
+\begin{center}
+
+\textbf{Author note}
+
+\end{center}
+
+\vfill  % Fill the rest of the page with whitespace
+
+\end{titlepage}
+
+\doublespacing
+
+\begin{center}
+\singlespacing
+\textbf{Full Dissertation:\\An instance-based model account of the
+benefits of varied practice in visuomotor skill}
+\end{center}
+
+% -------------------
+% END TITLE SECTION
+% -------------------
+
+\renewcommand*\contentsname{Contents}
+{
+\hypersetup{linkcolor=}
+\setcounter{tocdepth}{3}
+\tableofcontents
+}
+\setstretch{2}
+\section{Variability and
+Generalization}\label{variability-and-generalization}
+
+The factors that influence the generalization of learning are of
+considerable interest to both researchers exploring the human learning
+system and practitioners aiming to enhance the effectiveness of
+educational and training interventions. The present effort will focus
+specifically on the role of variability in the learning input.
+Variability manipulations typically regulate either the number of
+distinct instances presented to learners during training, or the
+dispersion of these instances. Such manipulations have been empirically
+demonstrated to affect subsequent generalization performance. This essay
+will offer an in-depth review of the extant literature on the influence
+of variability, spanning multiple relevant domains.
+
+\subsection{The study of variability}\label{the-study-of-variability}
+
+Studies investigating the ``benefits of variability'' hypothesis usually
+assign participants to either a constant or varied group for the
+training stage of the experiment. Then, subjects in both groups complete
+an identical testing stage which often consists items/conditions seen
+during training, and novel items/conditions. If the varied group
+performs better in the testing stage, this is taken for evidence of the
+benefits of variability hypothesis. Even within this relatively
+straightforward between-groups design, researchers must navigate several
+crucial methodological choices, highlighted below:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\item
+  Variables Subject to Variation. In multidimensional tasks, researchers
+  have the option to vary numerous variables. The experimenters must
+  decide the specific dimension(s) across which variation will occur.
+  For instance, in a projectile throwing accuracy task -- researchers
+  might vary the distance from the target, the size of the target, the
+  weight of the projectile. They might also vary a contextual variable
+  not directly relevant to the task, but which will still be encoded by
+  the subject on a trial by trial basis, e.g.~the background color.
+\item
+  Magnitude of Variation, relative to the control condition. The
+  simplest comparison would be to compare a constant group who trains
+  with 1 example/condition, against a varied group that trains from 2
+  examples/conditions. However, it is not uncommon in the literature for
+  the varied condition to train from 3 or 4 conditions. For example,
+  \textcite{catalanoDistantTransferCoincident1984a} train varied
+  subjects from 4 different velocities in their coincident timing task,
+  and \autocite{goodeSuperiorityVariableRepeated2008} have varied
+  subjects' practice with 3 different variants (i.e.~different letter
+  scrambles of the same word) of an anagram for a given word, while
+  their constant participants view the same variant 3 different times.
+  Alternatively, rather than a constant vs.~varied comparison, subjects
+  in all conditions might experience a variety of training items, but
+  with one group experiencing a greater number of unique items
+  \autocite{nosofskyModelguidedSearchOptimal2018}.
+\item
+  Locations within Task-Space. For tasks in which the stimuli or
+  conditions fall within a continuous metric space, the experimenter
+  must decide whether the varied instances are relatively close together
+  (e.g.~throwing a ball from a distance of 4 feet and 5 feet), or far
+  apart (throwing from 4 feet and 20 feet). Spreading the varied
+  training items further apart may be beneficial in terms of providing a
+  more representative sample of the task space to the learner, however
+  large distances may also result in significant differences in
+  difficulty between the training examples, which can be a common
+  confound in variability studies.
+\item
+  Proximity of Testing to Training Conditions. Intuitively, the fairest
+  form of comparison is to include testing conditions that are of an
+  equivalent distance from both the varied and constant groups. However
+  researchers might also attempt to demonstrate the benefits of
+  variation as being sufficiently powerful to outperform constant
+  training, even in cases where the constant group trained from a closer
+  proximity to the testing conditions, or whose training conditions are
+  identical to the testing conditions
+  \autocite{goodeSuperiorityVariableRepeated2008,kerrSpecificVariedPractice1978}.
+\end{enumerate}
+
+\subsection{Variability Literature
+Review}\label{variability-literature-review}
+
+An early and influential work on the influence of variability on
+category learning is that of \textcite{posnerGenesisAbstractIdeas1968}.
+In an ambitious attempt to address the question of how category
+information is represented, the authors trained participants to
+categorize artificial dot patterns, manipulating whether learners were
+exposed to examples clustered close to the category prototypes (e.g.~a
+low variability condition), or spread further away from the prototype
+(the varied-training group). It should be noted that both groups in this
+study were trained with the same number of unique instances and the
+manipulated difference was how spread out the instances were. The
+authors claim based on prior experiments using the same stimuli, that
+the training stimuli for the varied group were at least as far away from
+the testing stimuli as the training stimuli of the less-varied group.
+The authors interpreted their findings as evidence for the extraction of
+an abstraction or schema that is extracted and stored, and then over
+time becomes more likely to be the reference point from which
+generalization occurs, given that specific instances are thought to
+decay at a faster rate than prototypes or schema. The Posner and Keele
+study has been extremely influential and continues to be cited in
+contemporary research as clear evidence that schema abstraction
+underlies the benefits of varied training. It's also referenced as a key
+influence in the development of ``Schema Theory of Motor Learning''
+\autocite{schmidtSchemaTheoryDiscrete1975}, which in turn influenced
+decades of investigations on the potential benefits of varied training
+in motor skill learning. However, the classic Posner \& Keele study
+despite being far more carefully designed than many subsequent studies,
+and despite being a relative rarity in explicitly discussing and
+attempting to control for potential confounds of similarity between
+groups, may nevertheless be emblematic of a common issue in many
+investigations of the effects of varied training on learning. The
+problem with Posner \& Keele's conclusion was demonstrated clearly
+almost 3 decades later \autocite{palmeriCentralTendenciesExtreme2001},
+when researchers conducting a near replication of the original study
+also collected similarity judgements following training and performed
+multidimensional scaling analysis. Rather than being in the middle of
+the training stimuli as was the case in the physical stimuli space, the
+psychological representation of the prototype was shown reside at an
+extreme point, and generalization patterns by participants that would
+have seemed to warrant the learning of a prototype were then easily
+accounted for with only the assumption that the participants encoded
+instances. One of the primary concerns of the present paper is that many
+of the studies which purport to explain the benefits of variation via
+prototypes, schemas, or other abstractions, are often overlooking the
+potential of instance based similarity accounts.
+
+\subsection{Motor skill learning}\label{motor-skill-learning}
+
+Training variation has also been shown to promote transfer in motor
+learning. Much of this research has been influenced by the work of
+\autocite{schmidtSchemaTheoryDiscrete1975}, who proposed a schema-based
+account of motor learning as an attempt to address the longstanding
+problem of how novel movements are produced. Schema theory presumes a
+priori that learners possess general motor programs for classes of
+movements, such as an underhand throw. When called up for use, such
+programs must be parameterized, as well as schema rules that determine
+how a motor program is parameterized or scaled for a particular
+movement. Schema theory predicts that varied training results in the
+formation of a more general schema-rule, which can allow for transfer to
+novel movements within a given movement class, such as an underhand
+throw (though it is agnostic to the development of the movement classes
+themselves). Experiments that test this hypothesis are often designed to
+compare the transfer performance of a constant-trained group against
+that of a varied-trained group. Both groups train on the same task, but
+the varied group practices with multiple instances along some
+task-relevant dimension that remains invariant for the constant group.
+For example, investigators might train two groups of participants to
+throw a projectile at a target, with a constant group that throws from a
+single location, and a varied group that throws from multiple locations.
 Both groups are then tested from novel locations.
 
-One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
-Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
-The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
-Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
-12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
-Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
-However, at the halfway point of the testing stage they were allowed to see the landing location of the 4 beanbags they had thrown, and then completed the final 4 testing throws.
-In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-Although this design does not directly assess the hypothesis of varied training producing superior generalization to constant training (since the constant group is not tested from a novel position), it nevertheless offers a compelling example of the merits of varied practice.
-
-On occasion the Kerr and Booth design may be nested within a larger experimental design.
-One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue [@wrisbergVariabilityPracticeHypothesis1987].
-This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g.
-the design of Kerr and Booth.
-However, in this case the varied group did not outperform the constant group.
-A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
-
-Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket [@greenPracticeVariabilityTransfer1995a].
-Varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket.
-One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
-Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-Of course, this finding is less surprising than that of Kerr & Booth, given that varied subjects did have some prior exposure to the constant groups condition.
-This highlights an issue rarely discussed in the literature, of how much practice from an additional position might be necessary to induce benefits.
-Experimenters almost uniformly have varied participants train with an equivalent number of trials from each of their conditions
-
-One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation [@goodeSuperiorityVariableRepeated2008].
-All participants trained to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
-Although subjects in all conditions were exposed to the same 40 unique words (i.e.
-the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training).
-Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
-LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
-At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e.
-the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group.
-This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
-This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.
-
-Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
-It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
-
-Of particular relevant to the current essay is the early work of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
-constant training on multiple testing locations of graded distance from the training condition.
-Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
-The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
-Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
-As is often the case, the varied group performed worse during the training phase.
-In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
-
-## Category learning
-
-In the category learning literature, the constant vs.
-varied comparison is much less suitable.
-Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars.
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968], where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
-More recently, researchers have also begun to utilize more realistic stimuli in their experiments.
-@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
-In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
-Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
-higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyTestsExemplarmemoryModel2018].
-For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
-The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
-Moreover, the pattern of results in this study could be nicely accounted for by an extended version of the Generalized Context Model.
-
-The studies described thus far have studied the benefits of variability by exposing participants to a greater or lesser number of distinct examples during training.
-A distinct sub-literature within the category learning domain has focused much less on benefits derived from varied training, instead emphasizing how increased variability during the learning of a novel category influences how far the category boundary will then be generalized.
-The general approach is to train participants on examples from two categories, with the examples from one of the categories being more dispersed than the other.
-Participants are then tested with novel items located within ambiguous regions of the task space which allow the experimenters to assess whether the difference in variability influences how far participants generalize the category boundaries.
-
-@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
-In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
-In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart.
-Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
-Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
-Moreover, this effect was at odds with the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.
-
-Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010].
-The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
-They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
-In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial.
-They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
-
-The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present discussion.
-Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
-During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories.
-The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category.
-Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category.
-Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
-The authors then used the standard GCM framework to compare a variety of similarity-based models to account for their results.
-Of particular interest are their evaluations of a category response bias parameter, and a similarity scaling parameter.
-A model fit improvement when the response bias parameter is allowed to vary between the high-variability and low-variability trained groups is taken to suggest a simple bias for responding with one of the trained categories over the other.
-Alternatively, an improvement in fit due to a separate similarity scaling parameter may reflect the groups being differentially sensitive to the distances between stimuli.
-No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
-The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied particpants, and also for their poor performance in a recognition condition.
-Additional model comparisons suggested that this similarity rescaling applied across the entire stimulus space, rather than to the high variability category in particular.
-
-Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts [@braithwaiteEffectsVariationPrior2015].
-This study trained participants on problems involving the concept of sampling with replacement (SWR).
-Training consisted of examples that were either highly similar in their semantic context (e.g.
-all involving people selecting objects) or in which the surface features were varied between examples (e.g.
-people choosing objects AND objects selected in a sequence).
-The experimenters also surveyed how much prior knowledge each participant had with SWR.
-They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples.
-The authors hypothesized that in order to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
-To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples.
-Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
-
-Variability has also been examined within the realm of language learning.
-A particularly impressive study is that of [@perryLearnLocallyThink2010].
-In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
-All infants were introduced to three novel objects of the same category, with participants in the tight condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
-Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
-Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels of the training objects.
-The varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category, a pattern consistent with much of the existing literature.
-More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
-The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
-
-## Complications to the influence of variability
-
-### Sequence Effects
-
-A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another.
-The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
-Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter  [@sheaContextualInterferenceEffects1979].
-In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
-A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training.
-Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random.
-There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
-However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
-
-Prior to the influential @sheaContextualInterferenceEffects1979 study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
-It was later observed [@leeInfluencePracticeSchedule1985] that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
-The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts.
-One such account, the elaborative processing account [@sheaContextEffectsMemory1983], draws on the earlier work [@battigFacilitationInterference1966] and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
-Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training [@sheaContextEffectsMemory1983], and by manipulating whether subjects are able to perform comparisons during training [@wrightContributionElaborativeProcessing1992].
-An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory [@leeLocusContextualInterference].
-Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context.
-A much more recent study [@chuaPracticeVariabilityPromotes2019], replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
-The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
-In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g.
-attending to the target distance), and constant or blocked subjects reported more internal attention (e.g.
-posture or hand position).
-The authors argue that the benefits of varied/random training may be mediated by changes in attentional focus, however the claims made in the paper seem to go far beyond what can be justified by the analyses reported -- e.g.
-the increased external focus could be a simple byproduct of varied training.
-A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.
-
-## Other task and participant effects
-
-Of course, the effects of varied training, and different training sequences, are likely to be far more complex than simply more varied training being better than less, or random training being better than blocked.
-Null effects of both manipulations have been reported [see @magillReviewContextualInterference1990; @vanrossumSchmidtSchemaTheory1990 for reviews], and a variety of moderators have emerged.
-In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
-non-athlete) x (constant vs.
-blocked vs.
-random training).
-Athlete participants had superior performance during training, regardless of sequence condition, and training performance was superior for all subjects in the constant group, followed by blocked training in the middle, and then random training resulting in the worst training performance.
-Of greater interest is the pattern of testing results for novel transfer conditions.
-Among the athlete-participants, transfer performance was best for those who received random training, followed by blocked, and then constant training.
-Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
-A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training  [@guadagnoliRelationshipContextualInterference1999].
-More recently, the same pattern was observed in the concept learning literature [@braithwaiteEffectsVariationPrior2015 expt 1.].
-This study trained participants on a mathematical concept and found that participants who self-reported some prior experience with the concept improved more from pre-test to post-test after training with varied examples, while participants who reported no prior experience showed greater gains following training with highly similar examples.
-
-In addition to the influence of prior experiences described above, ample evidence also suggests that numerous aspects of the experiment may also interact with the influence of variation.
-One important study examined the impact of the amount of training completed in a force production task [@sheaContextualInterferenceContributions1990].
-This study employed a typical blocked vs.
-random training procedure, but with the additional manipulation of separate groups receiving 50, 200, or 400 total training trials.
-For the group that received only 50 training trials retention was best when training had been blocked.
-However, for the conditions that received 200 or 400 training trials the pattern was reversed, with random training resulting in superior retention than blocked training.
-These results were taken to suggest that the benefits of randomization may take time to emerge.
-Another experimental factor shown to interact with training sequence is the complexity of the training task [@albaretDifferentialEffectsTask1998].
-In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of two, three or four components).
-On a transfer task 48 hours after the completion of training, only participants trained at the lower levels of task complexity (2 or 3 components) showed superior performance to the blocked condition.
-The authors suggest that the benefits of random sequencing, thought to arise from more elaborate cognitive processing, or the necessity of continually recalling task information from long term into short term memory, are more likely to be obscured as the complexity of the task forces the blocked participants to also engage in such processes.
-
-A final important influence of particular relevance to the practice-sequence literature concerns the exact structure of "random" sequencing.
-Although the term random is commonly used for convenience, experimenters do not typically leave the order of training entirely up to chance.
-Rather, the training sequence is often constrained such that each condition must occur a minimum number of times in each quartile of the training phase, thus resulting in an even distribution the conditions throughout training.
-While the assurance of the conditions being evenly spread throughout training is consistent across studies, other aspects of the sequence structure are a bit more idiosyncratic.
-Some researchers report setting a maximum number of consecutive repetitions, e.g.
-no more than 2 consecutive trials of the same condition [@delreyEffectsContextualInterference1982; @sheaContextualInterferenceEffects1979], or structure the random trials such that the same condition never occurs consecutively [@wulfEffectTypePractice1991].
-Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition [@willeyLongtermMotorLearning2018; @chuaPracticeVariabilityPromotes2019; @wrisbergVariabilityPracticeHypothesis1987], resulting in many more switches than would arise if training was perfectly blocked.
-The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition.
-Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing [@pigottMotorSchemaStructure1984], and basketball shot training study [@landinComparisonThreePractice1997], and in a replication plus extension of the seminal [@sheaContextualInterferenceEffects1979] study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition.
-Consequences on different study schedules have also been repeatedly observed in the category learning literature [@carvalhoSequenceStudyChanges2017; @carvalhoPuttingCategoryLearning2014].
-This line of research has revealed that the effects of blocking vs.
-interleaving can depend on the structure of the category being learned, and also that the different schedules can result in the participants requiring different representations.
-A fruitful line of inquiry in the motor skill learning literature may be to attempt to identify whether structural aspects of the motor task interact with different training sequences in a reliable manner.
-
-Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed).
-Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty [@bjorkNewTheoryDisuse1992; @schmidtNewConceptualizationsPractice1992], or optimal challenge points [@guadagnoliChallengePointFramework2004].
-They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage.
-This observation is then used to justify the idea that the most enduring and generalizable learning occurs by training at an optimal level of training difficulty, with difficulty being some function of the experience of the learner, and the cognitive or visuomotor processing demands of the task.
-It then follows that the factors that tend to make training more difficult (i.e.
-increased variability or randomization), are more likely to be beneficial when the learner has some experience, or when the processing demands of the task are not too extreme (which may only occur after some experience with the task).
-Such frameworks may be helpful heuristics in some cases, but they also seem to be overly flexible such that any null result of some intervention might be accounted for by a suboptimal amount of training trials, or by suggesting the training task was too difficult.
-The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.
-
-# Project 1
-
-____________________________________________________
-[pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
-
-```{r}
-
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
-  ggh4x,htmltools,future,furrr,ez)
-#options(brms.backend="cmdstanr",mc.cores=4)
-#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
-walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-#conflicts_prefer(tidybayes::rstudent_t)
-
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-#options(brms.backend="cmdstanr",mc.cores=4)
-initial_contrasts <- options("contrasts")$contrasts
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-
-library(tidybayes)
-
-theme_set(theme_classic())
-# load the processed data from experiment 1 and 2
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
-# defaultContrasts = options()$contrasts
-# theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-```
-
-# Abstract
-
-Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
-Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
-However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
-In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
-We replicate previous findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
-Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
-
-# Introduction
-
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
-The factor of interest to the present investigation is variation during training.
-Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
-We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
-We first review the relevant concepts and literature.
-
-## Similarity and instance-based approaches to transfer of learning
-
-Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances.
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar [@posnerGenesisAbstractIdeas1968].
-Prototype models were later challenged by the success of instance-based or exemplar models -- which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978;
-@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli.
-As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
-In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
-Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
-That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
-@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
-Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work -- variability of training examples.
-
-Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
-Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
-
-Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
-throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-## Issues with Previous Research
-
-Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g.
-projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
-more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
-
-```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
-
-p=2
-c<- .0002
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
-  group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
-
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
-
-```
-
-In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
-We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
-We then examine the extent to which this advantage can be explained by an instance-based similarity model.
-
-# Experiment 1
-
-## Methods
-
-### Sample Size Estimation
+One of the earliest, and still often cited investigations of Schmidt's
+benefits of variability hypothesis was the work of
+\textcite{kerrSpecificVariedPractice1978}. Two groups of children, aged
+8 and 12, were assigned to either constant or varied training of a bean
+bag throwing task. The constant group practiced throwing a bean-bag at a
+small target placed 3 feet in front of them, and the varied group
+practiced throwing from a distance of both 2 feet and 4 feet.
+Participants were blindfolded and unable to see the target while making
+each throw but would receive feedback by looking at where the beanbag
+had landed in between each training trial. 12 weeks later, all of the
+children were given a final test from a distance of 3 feet which was
+novel for the varied participants and repeated for the constant
+participants. Participants were also blindfolded for testing and did not
+receive trial by trial feedback in this stage. However, at the halfway
+point of the testing stage they were allowed to see the landing location
+of the 4 beanbags they had thrown, and then completed the final 4
+testing throws. In both age groups, participants performed significantly
+better in the varied condition than the constant condition, though the
+effect was larger for the younger, 8-year-old children. Although this
+design does not directly assess the hypothesis of varied training
+producing superior generalization to constant training (since the
+constant group is not tested from a novel position), it nevertheless
+offers a compelling example of the merits of varied practice.
+
+On occasion the Kerr and Booth design may be nested within a larger
+experimental design. One such study that used a movement timing task,
+wherein subjects had to move their hand from a starting location, to a
+target location, attempting to arrive at the target location at specific
+time following the onset of a cue
+\autocite{wrisbergVariabilityPracticeHypothesis1987}. This study
+utilized 4 different constant groups, and 3 varied groups, with one of
+the constant groups training under conditions identical to the testing
+conditions, and which were not trained on by any of the varied groups,
+e.g.~the design of Kerr and Booth. However, in this case the varied
+group did not outperform the constant group. A more recent study
+attempting a slightly more direct replication of the original Kerr \&
+Booth study \autocite{willeyLongtermMotorLearning2018}, having subjects
+throw beanbags at a target, with the varied group training from
+positions (5 and 9 feet) on either side of the constant group (7 feet).
+However, this study diverged from the original in that the participants
+were adults; they faced away from the target and threw the beanbag
+backwards over their bodies; they alternated using their right and left
+hands every 6 trials; and underwent a relatively extreme amount of
+training (20 sessions with 60 practice trials each, spread out over 5-7
+weeks). Like \textcite{wrisbergVariabilityPracticeHypothesis1987}, this
+study did not find a varied advantage from the constant training
+position, though the varied group did perform better at distances novel
+to both groups.
+
+Some support for the Kerr and Booth findings was found with a relatively
+less common experimental task of training participants in hitting a
+projectile at a target with the use of a racket
+\autocite{greenPracticeVariabilityTransfer1995a}. Varied participants
+trained with tennis, squash, badminton, and short-tennis rackets were
+compared against constant subjects trained with only a tennis racket.
+One of the testing conditions had subjects repeat the use of the tennis
+racket, which had been used on all 128 training trials for the constant
+group, and only 32 training trials for the varied group. Nevertheless,
+the varied group outperformed the constant group when using the tennis
+racket at testing, and also performed better in conditions with several
+novel racket lengths. Of course, this finding is less surprising than
+that of Kerr \& Booth, given that varied subjects did have some prior
+exposure to the constant groups condition. This highlights an issue
+rarely discussed in the literature, of how much practice from an
+additional position might be necessary to induce benefits. Experimenters
+almost uniformly have varied participants train with an equivalent
+number of trials from each of their conditions
+
+One of the few studies that has replicated the surprising result of
+varied outperforming constant, from the constant training condition, did
+so in the relatively distant domain of verbal manipulation
+\autocite{goodeSuperiorityVariableRepeated2008}. All participants
+trained to solve anagrams of 40 different words ranging in length from 5
+to 11 letters, with an anagram of each word repeated 3 times throughout
+training, for a total of 120 training trials. Although subjects in all
+conditions were exposed to the same 40 unique words (i.e.~the solution
+to an anagram), participants in the varied group saw 3 different
+arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for
+the solution word FLOOD, whereas constant subjects would train on three
+repetitions of LDOOF (spread evenly across training). Two different
+constant groups were used. Both constant groups trained with three
+repetitions of the same word scramble, but for constant group A, the
+testing phase consisted of the identical letter arrangement to that seen
+during training (e.g.~LDOOF), whereas for constant group B, the testing
+phase consisted of a arrangement they had not seen during training, thus
+presenting them with a testing situation similar situation to the varied
+group. At the testing stage, the varied group outperformed both constant
+groups, a particularly impressive result, given that constant group A
+had 3 prior exposures to the word arrangement (i.e.~the particular
+permutation of letters) which the varied group had not explicitly seen.
+However varied subjects in this study did not exhibit the typical
+decrement in the training phase typical of other varied manipulations in
+the literature, and actually achieved higher levels of anagram solving
+accuracy by the end of training than either of the constant groups --
+solving 2 more anagrams on average than the constant group. This might
+suggest that for tasks of this nature where the learner can simply get
+stuck with a particular word scramble, repeated exposure to the
+identical scramble might be less helpful towards finding the solution
+than being given a different arrangement of the same letters. This
+contention is supported by the fact that constant group A, who was
+tested on the identical arrangement as they experienced during training,
+performed no better at testing than did constant group B, who had
+trained on a different arrangement of the same word solution -- further
+suggesting that there may not have been a strong identity advantage in
+this task.
+
+Pitting varied against constant practice against each other on the home
+turf of the constant group provides a compelling argument for the
+benefits of varied training, as well as an interesting challenge for
+theoretical accounts that posit generalization to occur as some function
+of distance. However, despite its appeal this particular contrast is
+relatively uncommon in the literature. It is unclear whether this may be
+cause for concern over publication bias, or just researchers feeling the
+design is too risky. A far more common design is to have separate
+constant groups that each train exclusively from each of the conditions
+that the varied group encounters
+\autocite{catalanoDistantTransferCoincident1984a,chuaPracticeVariabilityPromotes2019,newellVariabilityPracticeTransfer1976,moxleySchemaVariabilityPractice1979,mccrackenTestSchemaTheory1977},
+or for a single constant group to train from just one of the conditions
+experienced by the varied participants
+\autocite{pigottMotorSchemaStructure1984,rollerVariablePracticeLenses2001,wrisbergTrainingProductionNovel1984,wrisbergDevelopingCoincidentTiming1983}.
+A less common contrast places the constant group training in a region of
+the task space outside of the range of examples experienced by the
+varied group, but distinct from the transfer condition
+\autocite{wrisbergVariabilityPracticeHypothesis1987,wulfVariabilityPracticeImplicit1997}.
+
+Of particular relevant to the current essay is the early work of
+\textcite{catalanoDistantTransferCoincident1984a}, as theirs was one of
+the earliest studies to investigate the influence of varied vs.~constant
+training on multiple testing locations of graded distance from the
+training condition. Participants were trained on coincident timing task,
+in which subjects observe a series of lightbulbs turning on sequentially
+at a consistent rate and attempt to time a button response with the
+onset of the final bulb. The constant groups trained with a single
+velocity of either 5,7,9, or 11 mph, while the varied group trained from
+all 4 of these velocities. Participants were then assigned to one of
+four possible generalization conditions, all of which fell outside of
+the range of the varied training conditions -- 1, 3, 13 or 15 mph. As is
+often the case, the varied group performed worse during the training
+phase. In the testing phase, the general pattern was for all
+participants to perform worse as the testing conditions became further
+away from the training conditions, but since the drop off in performance
+as a function of distance was far less steep for the varied group, the
+authors suggested that varied training induced a decremented
+generalization gradient, such that the varied participants were less
+affected by the change between training and testing conditions.
+
+\subsection{Category learning}\label{category-learning}
+
+In the category learning literature, the constant vs.~varied comparison
+is much less suitable. Instead, researchers tend to compare a condition
+with many repetitions of a few items against condition with fewer
+repetitions of a wider array of exemplars. Much of the earlier work in
+this sub-area trained subjects on artificial categories, such as dot
+patterns
+\autocite{homaCategoryBreadthAbstraction1976,posnerGenesisAbstractIdeas1968},
+where more varied or distorted training examples were often shown to
+produce superior generalization when categorizing novel exemplars. More
+recently, researchers have also begun to utilize more realistic stimuli
+in their experiments.
+\textcite{wahlheimMetacognitiveJudgmentsRepetition2012} conducted one
+such study. In a within-participants design, participants were trained
+on bird categories with either high repetitions of a few exemplars, or
+few repetitions of many exemplars. Across four different experiments,
+which were conducted to address an unrelated question on metacognitive
+judgements, the researchers consistently found that participants
+generalized better to novel species following training with more unique
+exemplars (i.e.~higher variability), while high repetition training
+produced significantly better performance categorizing the specific
+species they had trained on. A variability advantage was also found in
+the relatively complex domain of rock categorization
+\autocite{nosofskyTestsExemplarmemoryModel2018}. For 10 different rock
+categories, participants were trained with either many repetitions of 3
+unique examples of each category, or few repetitions of 9 unique
+examples, with an equal number of total training trials in each group
+(the design also included 2 other conditions less amenable to
+considering the impact of variation). The high-variability group,
+trained with 9 unique examples, showed significantly better
+generalization performance than the other conditions. Moreover, the
+pattern of results in this study could be nicely accounted for by an
+extended version of the Generalized Context Model.
+
+The studies described thus far have studied the benefits of variability
+by exposing participants to a greater or lesser number of distinct
+examples during training. A distinct sub-literature within the category
+learning domain has focused much less on benefits derived from varied
+training, instead emphasizing how increased variability during the
+learning of a novel category influences how far the category boundary
+will then be generalized. The general approach is to train participants
+on examples from two categories, with the examples from one of the
+categories being more dispersed than the other. Participants are then
+tested with novel items located within ambiguous regions of the task
+space which allow the experimenters to assess whether the difference in
+variability influences how far participants generalize the category
+boundaries.
+
+\textcite{cohenCategoryVariabilityExemplar2001} trained subjects on two
+categories, one with much more variability than the other. In experiment
+1, a low variability category composed of 1 instance was compared
+against a high-variability category of 2 instances in one condition, and
+7 instances in another. In experiment 2 both categories were composed of
+3 instances, but for the low-variability group the instances were
+clustered close to each other, whereas the high-variability groups
+instances were spread much further apart. Participants were tested on an
+ambiguous novel instance that was located in between the two trained
+categories. Both experiments provided evidence that participants were
+much more likely to categorize the novel middle stimulus into a category
+with greater variation. Moreover, this effect was at odds with the
+predications of the baseline version of the GCM, thus providing some
+evidence that training variation may at least sometimes induce effects
+that cannot be entirely accounted for by exemplar-similarity accounts.
+
+Further observations consonant with the results of
+\textcite{cohenCategoryVariabilityExemplar2001} have since been observed
+in numerous investigations
+\autocite{hahnEffectsCategoryDiversity2005,perlmanFurtherAttemptsClarify2012,sakamotoPuttingPsychologyBack2008,hsuEffectsGenerativeDiscriminative2010}.
+The results of \textcite{sakamotoPuttingPsychologyBack2008} are
+noteworthy. They first reproduced the basic finding of participants
+being more likely to categorize an unknown middle stimulus into a
+training category with higher variability. In a second experiment, they
+held the variability between the two training categories constant and
+instead manipulated the training sequence, such that the examples of one
+category appeared in an ordered fashion, with very small changes from
+one example to the other (the stimuli were lines that varied only in
+length), whereas examples in the alternate category were shown in a
+random order and thus included larger jumps in the stimulus space from
+trial to trial. They found that the middle stimulus was more likely to
+be categorized into the category that had been learned with a random
+sequence, which was attributed to an increased perception of variability
+which resulted from the larger trial to trial discrepancies.
+
+The work of \textcite{hahnEffectsCategoryDiversity2005}, is also of
+particular interest to the present discussion. Their experimental design
+was similar to previous studies, but they included a larger set of
+testing items which were used to assess generalization both between the
+two training categories as well as novel items located in the outer
+edges of the training categories. During generalization testing,
+participants were given the option to respond with ``neither'', in
+addition to responses to the two training categories. The ``neither''
+response was included to test how far away in the stimulus space
+participants would continue to categorize novel items as belonging to a
+trained category. Consistent with prior findings, high-variability
+training resulted in an increased probability of categorizing items in
+between the training categories as belong to the high variability
+category. Additionally, participants trained with higher variability
+also extended the category boundary further out into the periphery than
+participants trained with a lower variability category were willing to
+do. The authors then used the standard GCM framework to compare a
+variety of similarity-based models to account for their results. Of
+particular interest are their evaluations of a category response bias
+parameter, and a similarity scaling parameter. A model fit improvement
+when the response bias parameter is allowed to vary between the
+high-variability and low-variability trained groups is taken to suggest
+a simple bias for responding with one of the trained categories over the
+other. Alternatively, an improvement in fit due to a separate similarity
+scaling parameter may reflect the groups being differentially sensitive
+to the distances between stimuli. No improvement in model fit was found
+by allowing the response-bias parameter to differ between groups,
+however the model performance did improvement significantly when the
+similarity scaling parameter was fit separately. The best fitting
+similarity-scaling parameters were such that the high-variability group
+was less sensitive to the distances between stimuli, resulting in
+greater similarity values between their training items and testing
+items. This model accounted for both the extended generalization
+gradients of the varied particpants, and also for their poor performance
+in a recognition condition. Additional model comparisons suggested that
+this similarity rescaling applied across the entire stimulus space,
+rather than to the high variability category in particular.
+
+Variability effects have also been examined in the higher-level domain
+of how learners acquire novel concepts, and then instantiate (rather
+than merely recognize) that concept in untrained contexts
+\autocite{braithwaiteEffectsVariationPrior2015}. This study trained
+participants on problems involving the concept of sampling with
+replacement (SWR). Training consisted of examples that were either
+highly similar in their semantic context (e.g.~all involving people
+selecting objects) or in which the surface features were varied between
+examples (e.g.~people choosing objects AND objects selected in a
+sequence). The experimenters also surveyed how much prior knowledge each
+participant had with SWR. They found that whether variation was
+beneficial depended on the prior knowledge of the participants -- such
+that participants with some prior knowledge benefited from varied
+training, whereas participants with minimal prior knowledge performed
+better after training with similar examples. The authors hypothesized
+that in order to benefit from varied examples, participants must be able
+to detect the structure common to the diverse examples, and that
+participants with prior knowledge are more likely to be sensitive to
+such structure, and thus to benefit from varied training. To test this
+hypothesis more directly, the authors conducted a 2nd experiment,
+wherein they controlled prior knowledge by exposing some subjects to a
+short graphical or verbal pre-training lesson, designed to increase
+sensitivity to the training examples. Consistent with their hypothesis,
+participants exposed to the structural sensitivity pre-training
+benefited more from varied training than the controls participants who
+benefited more from training with similar examples.
+
+Variability has also been examined within the realm of language
+learning. A particularly impressive study is that of
+\autocite{perryLearnLocallyThink2010}. In nine training sessions spread
+out over nine weeks infants were trained on object labels in a
+naturalistic play setting. All infants were introduced to three novel
+objects of the same category, with participants in the tight condition
+being exposed to three similar exemplars of the category, and
+participants in the varied condition being exposed to three dissimilar
+objects of the same category. Importantly, the similarity of the objects
+was carefully controlled for by having a separate group of adult
+subjects provide pairwise similarity judgements of the category objects
+prior to the study onset. Multidimensional scaling was then performed to
+obtain the coordinates of the objects psychological space, and out of
+the 10 objects for each category, the 3 most similar objects were
+selected for the tight group and the three least similar objects for the
+varied group, with the leftover four objects being retained for testing.
+By the end of the nine weeks, all of the infants had learned the labels
+of the training objects. The varied group demonstrated superior ability
+to correctly generalize the object labels to untrained exemplars of the
+same category, a pattern consistent with much of the existing
+literature. More interesting was the superior performance of the varied
+group on a higher order generalization task -- such that they were able
+to appropriately generalize the bias they had learned during training
+for attending to the shape of objects to novel solid objects, but not to
+non-solids. The tight training group, on the other hand, tended to
+overgeneralize the shape bias, leading the researchers to suggest that
+the varied training induced a more context-sensitive understanding of
+when to apply their knowledge.
+
+\subsection{Complications to the influence of
+variability}\label{complications-to-the-influence-of-variability}
+
+\subsubsection{Sequence Effects}\label{sequence-effects}
+
+A necessary consequence of varied training is that participants will
+have the experience of switching from one task condition to another. The
+number of switches can vary greatly, with the two extremes being varied
+participants completing all of their training trials in one before
+switching to the next condition (blocked sequencing), or if they
+alternate between conditions on a trial by trial basis
+(random/intermixed/interleaved sequencing). Not long after the initial
+influx of schema-theory inspired studies testing the benefits of
+variability hypothesis was shown that the influence of varied training
+might interact with the type of training sequence chosen by the
+experimenter \autocite{sheaContextualInterferenceEffects1979}. In this
+seminal study, both groups of training subjects trained with the same
+number of trials of three separate movement patterns. A blocked group
+that completed all of their trials with one sequence before beginning
+the next sequence, and a random group that trained with all three
+movement patterns interspersed throughout the course of training.
+Participants were also randomly assigned to retention testing under
+either blocked or random sequence conditions, thus resulting in all four
+training-testing combinations of blocked-blocked; blocked-random;
+random-blocked; random-random. There was some effect of sequence
+context, such that both groups performed better when the testing
+sequence matched their training sequence. However, the main finding of
+interest was the advantage of random-training, which resulted in
+superior testing performance than blocked training regardless of whether
+the testing stage had a blocked or random sequence, an effect observed
+both immediately after training, and in a follow up test ten days after
+the end of training.
+
+Prior to the influential
+\textcite{sheaContextualInterferenceEffects1979} study, studies
+investigating the benefits of variability hypothesis had utilized both
+blocked and random training schedules, often without comment or
+justification. It was later observed
+\autocite{leeInfluencePracticeSchedule1985} that positive evidence for
+benefits of varied training seemed more likely to occur for studies that
+utilized random schedules. The theoretical basis of such studies was
+invariably an appeal to Schmidt's schema theory; however schema theory
+made no clear predictions of an effect of study sequence on retention or
+generalization, thus prompting the need for alternate accounts. One such
+account, the elaborative processing account
+\autocite{sheaContextEffectsMemory1983}, draws on the earlier work
+\autocite{battigFacilitationInterference1966} and argues that randomly
+sequencing conditions during training promotes comparison and
+contrastive processes between those conditions, which result in a deeper
+understanding of the training task than could arise via blocked
+sequencing. Supporting evidence for elaborative processing comes in the
+form of random-sequence trained subjects self-reporting more nuanced
+mental representations of movement patterns following training
+\autocite{sheaContextEffectsMemory1983}, and by manipulating whether
+subjects are able to perform comparisons during training
+\autocite{wrightContributionElaborativeProcessing1992}. An alternative,
+though not incompatible account suggests that the benefits of
+random-sequencing are a result of such sequences forcing the learner to
+continually reconstruct the relevant motor task in working memory
+\autocite{leeLocusContextualInterference}. Blocked training, on the
+other hand, allows the learner to maintain the same motor task in short
+term memory without decay for much of the training which facilitates
+training performance, but hinders ability to retrieve the appropriate
+motor memory in a later testing context. A much more recent study
+\autocite{chuaPracticeVariabilityPromotes2019}, replicates the standard
+findings of an advantage of varied training over constant training (expt
+1, bean-bag throwing task), and of random training over blocked training
+(expt 2 \& 3, bean-bag throwing \& golf putting). The novelty of this
+study is that the experimenters queried subjects about their attentional
+focus throughout the training stage. In all three experiments varied or
+random trained-subjects reported significantly greater external
+attention (e.g.~attending to the target distance), and constant or
+blocked subjects reported more internal attention (e.g.~posture or hand
+position). The authors argue that the benefits of varied/random training
+may be mediated by changes in attentional focus, however the claims made
+in the paper seem to go far beyond what can be justified by the analyses
+reported -- e.g.~the increased external focus could be a simple
+byproduct of varied training. A stronger form of evidence that was not
+provided may have been to use multiple regression analyses to show that
+the testing advantage of the varied/random groups over the
+constant/blocked groups could be accounted for by the differences in
+self-reported attentional focus.
+
+\subsection{Other task and participant
+effects}\label{other-task-and-participant-effects}
+
+Of course, the effects of varied training, and different training
+sequences, are likely to be far more complex than simply more varied
+training being better than less, or random training being better than
+blocked. Null effects of both manipulations have been reported
+\autocites[see][]{magillReviewContextualInterference1990}[ for
+reviews]{vanrossumSchmidtSchemaTheory1990}, and a variety of moderators
+have emerged. In one of the earlier examples of the complex relationship
+between study sequence and learning
+\autocite{delreyEffectsContextualInterference1982}, experimenters
+recruited participants who self-reported either large amounts, or very
+little experience with athletic actives, and then trained participants
+on a coincident timing task under with either a single constant training
+velocity, or with four training velocities under either blocked, or
+random training sequence conditions - resulting in six experimental
+conditions: (athlete vs.~non-athlete) x (constant vs.~blocked vs.~random
+training). Athlete participants had superior performance during
+training, regardless of sequence condition, and training performance was
+superior for all subjects in the constant group, followed by blocked
+training in the middle, and then random training resulting in the worst
+training performance. Of greater interest is the pattern of testing
+results for novel transfer conditions. Among the athlete-participants,
+transfer performance was best for those who received random training,
+followed by blocked, and then constant training. Non-athletes showed the
+opposite pattern, with superior performance for those who had constant
+training. A similar pattern was later observed in a golf-putting
+training study, wherein participants who had some prior golf experience
+benefited most from random-sequenced training, and participants with no
+golf experience benefited most from blocked training
+\autocite{guadagnoliRelationshipContextualInterference1999}. More
+recently, the same pattern was observed in the concept learning
+literature \autocite[ expt 1.]{braithwaiteEffectsVariationPrior2015}.
+This study trained participants on a mathematical concept and found that
+participants who self-reported some prior experience with the concept
+improved more from pre-test to post-test after training with varied
+examples, while participants who reported no prior experience showed
+greater gains following training with highly similar examples.
+
+In addition to the influence of prior experiences described above, ample
+evidence also suggests that numerous aspects of the experiment may also
+interact with the influence of variation. One important study examined
+the impact of the amount of training completed in a force production
+task \autocite{sheaContextualInterferenceContributions1990}. This study
+employed a typical blocked vs.~random training procedure, but with the
+additional manipulation of separate groups receiving 50, 200, or 400
+total training trials. For the group that received only 50 training
+trials retention was best when training had been blocked. However, for
+the conditions that received 200 or 400 training trials the pattern was
+reversed, with random training resulting in superior retention than
+blocked training. These results were taken to suggest that the benefits
+of randomization may take time to emerge. Another experimental factor
+shown to interact with training sequence is the complexity of the
+training task \autocite{albaretDifferentialEffectsTask1998}. In addition
+to random or blocked training, participants in this study were assigned
+to train on a drawing task at one of three different levels of
+complexity (reproducing from memory shapes composed of two, three or
+four components). On a transfer task 48 hours after the completion of
+training, only participants trained at the lower levels of task
+complexity (2 or 3 components) showed superior performance to the
+blocked condition. The authors suggest that the benefits of random
+sequencing, thought to arise from more elaborate cognitive processing,
+or the necessity of continually recalling task information from long
+term into short term memory, are more likely to be obscured as the
+complexity of the task forces the blocked participants to also engage in
+such processes.
+
+A final important influence of particular relevance to the
+practice-sequence literature concerns the exact structure of ``random''
+sequencing. Although the term random is commonly used for convenience,
+experimenters do not typically leave the order of training entirely up
+to chance. Rather, the training sequence is often constrained such that
+each condition must occur a minimum number of times in each quartile of
+the training phase, thus resulting in an even distribution the
+conditions throughout training. While the assurance of the conditions
+being evenly spread throughout training is consistent across studies,
+other aspects of the sequence structure are a bit more idiosyncratic.
+Some researchers report setting a maximum number of consecutive
+repetitions, e.g.~no more than 2 consecutive trials of the same
+condition
+\autocite{delreyEffectsContextualInterference1982,sheaContextualInterferenceEffects1979},
+or structure the random trials such that the same condition never occurs
+consecutively \autocite{wulfEffectTypePractice1991}. Also common is to
+structure experiments such that random condition really consists of many
+small blocks, where participants do a few trials of one condition
+consecutively and then switch to another condition
+\autocite{willeyLongtermMotorLearning2018,chuaPracticeVariabilityPromotes2019,wrisbergVariabilityPracticeHypothesis1987},
+resulting in many more switches than would arise if training was
+perfectly blocked. The question of whether such differences in the
+structure of random sequencing are consequential has been addressed
+experimentally a few times, in all cases consisting of a 1) a no-repeat
+random condition; 2) a blocked random condition (typically 3 or 4
+repeats before a switch); and 3) a standard fully-blocked condition.
+Blocked-random training resulted in better performance than either
+repeat-random, or fully - blocked training in both a bean-bag throwing
+\autocite{pigottMotorSchemaStructure1984}, and basketball shot training
+study \autocite{landinComparisonThreePractice1997}, and in a replication
+plus extension of the seminal
+\autocite{sheaContextualInterferenceEffects1979} study, blocked-random
+training was equally effective as no-repeat random training, with both
+random structures leading to better performance than the fully-blocked
+training condition. Consequences on different study schedules have also
+been repeatedly observed in the category learning literature
+\autocite{carvalhoSequenceStudyChanges2017,carvalhoPuttingCategoryLearning2014}.
+This line of research has revealed that the effects of blocking
+vs.~interleaving can depend on the structure of the category being
+learned, and also that the different schedules can result in the
+participants requiring different representations. A fruitful line of
+inquiry in the motor skill learning literature may be to attempt to
+identify whether structural aspects of the motor task interact with
+different training sequences in a reliable manner.
+
+Numerous researchers have attempted to provide coherent frameworks to
+account for the full range of influences of training variation and
+sequencing described above (along with many other effects not
+discussed). Such accounts are generally quite similar, invoking ideas of
+desirable levels of difficulty
+\autocite{bjorkNewTheoryDisuse1992,schmidtNewConceptualizationsPractice1992},
+or optimal challenge points
+\autocite{guadagnoliChallengePointFramework2004}. They tend to start by
+describing the dissociation between acquisition performance (performance
+during training) and testing performance (delayed retention and/or
+transfer), most strikingly observed as varied/random training
+participants performing worse than their constant/blocked counterparts
+during the training stage of the study, but then outperforming the
+constant/blocked comparisons at a later retention or transfer stage.
+This observation is then used to justify the idea that the most enduring
+and generalizable learning occurs by training at an optimal level of
+training difficulty, with difficulty being some function of the
+experience of the learner, and the cognitive or visuomotor processing
+demands of the task. It then follows that the factors that tend to make
+training more difficult (i.e.~increased variability or randomization),
+are more likely to be beneficial when the learner has some experience,
+or when the processing demands of the task are not too extreme (which
+may only occur after some experience with the task). Such frameworks may
+be helpful heuristics in some cases, but they also seem to be overly
+flexible such that any null result of some intervention might be
+accounted for by a suboptimal amount of training trials, or by
+suggesting the training task was too difficult. The development of
+computational models that can account for how changes in the parameters
+of the motor-skill task scale with difficulty, would be a great step
+forward.
+
+\section{Project 1}\label{project-1}
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+\href{Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf}{pdf
+of the journal article}\\
+\href{https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299}{Link
+to online version of journal article}
+
+\section{Abstract}\label{abstract}
+
+Exposing learners to variability during training has been demonstrated
+to improve performance in subsequent transfer testing. Such variability
+benefits are often accounted for by assuming that learners are
+developing some general task schema or structure. However much of this
+research has neglected to account for differences in similarity between
+varied and constant training conditions. In a between-groups
+manipulation, we trained participants on a simple projectile launching
+task, with either varied or constant conditions. We replicate previous
+findings showing a transfer advantage of varied over constant training.
+Furthermore, we show that a standard similarity model is insufficient to
+account for the benefits of variation, but, if the model is adjusted to
+assume that varied learners are tuned towards a broader generalization
+gradient, then a similarity-based model is sufficient to explain the
+observed benefits of variation. Our results therefore suggest that some
+variability benefits can be accommodated within instance-based models
+without positing the learning of some schemata or structure.
+
+\section{Introduction}\label{introduction}
+
+The past century of research on human learning has produced ample
+evidence that although learners can improve at almost any task, such
+improvements are often specific to the trained task, with unreliable or
+even nonexistent transfer to novel tasks or conditions
+\autocite{barnettWhenWhereWe2002,dettermanCaseProsecutionTransfer1993}.
+Such transfer challenges are of noteworthy practical relevance, given
+that educators, trainers, and rehabilitators typically intend for their
+students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that
+influence transfer, and to develop cognitive models that can predict
+when transfer is likely to occur. The factor of interest to the present
+investigation is variation during training. Our experiments add to the
+longstanding empirical investigation of the controversial relationship
+between training variation, and subsequent transfer. We also offer a
+novel explanation for such results in the form of an instance-based
+model that accounts for the benefits of variation in simple terms of
+psychological similarity. We first review the relevant concepts and
+literature.
+
+\subsection{Similarity and instance-based approaches to transfer of
+learning}\label{similarity-and-instance-based-approaches-to-transfer-of-learning}
+
+Notions of similarity have long played a central role in many prominent
+models of generalization of learning, as well as in the longstanding
+theoretical issue of whether learners abstract an aggregate, summary
+representation, or if they simply store individual instances. Early
+models of learning often assumed that discrete experiences with some
+task or category were not stored individually in memory, but instead
+promoted the formation of a summary representation, often referred to as
+a prototype or schema, and that exposure to novel examples would then
+prompt the retrieval of whichever preexisting prototype was most similar
+\autocite{posnerGenesisAbstractIdeas1968}. Prototype models were later
+challenged by the success of instance-based or exemplar models -- which
+were shown to provide an account of generalization as good or better
+than prototype models, with the advantage of not assuming the explicit
+construction of an internal prototype
+\autocites{estesClassificationCognition1994,hintzmanMINERVASimulationModel1984,medinContextTheoryClassification1978}[
+]{nosofskyAttentionSimilarityIdentificationcategorization1986}.
+Instance-based models assume that learners encode each experience with a
+task as a separate instance/exemplar/trace, and that each encoded trace
+is in turn compared against novel stimuli. As the number of stored
+instances increases, so does the likelihood that some previously stored
+instance will be retrieved to aid in the performance of a novel task.
+Stored instances are retrieved in the context of novel stimuli or tasks
+if they are sufficiently similar, thus suggesting that the process of
+computing similarity is of central importance to generalization.
+
+Similarity, defined in this literature as a function of psychological
+distance between instances or categories, has provided a successful
+account of generalization across numerous tasks and domains. In an
+influential study demonstrating an ordinal similarity effect,
+experimenters employed a numerosity judgment task in which participants
+quickly report the number of dots flashed on a screen. Performance (in
+terms of response times to new patterns) on novel dot configurations
+varied as an inverse function of their similarity to previously trained
+dot configurations \textcite{palmeriExemplarSimilarityDevelopment1997}.
+That is, performance was better on novel configurations moderately
+similar to trained configurations than to configurations with
+low-similarity, and also better on low-similarity configurations than to
+even less similar, unrelated configurations. Instance-based approaches
+have had some success accounting for performance in certain sub-domains
+of motor learning
+\autocite{cohenWhereGraspsAre2004,crumpEpisodicContributionsSequential2010,meighWhatMemoryRepresentation2018,poldrackRelationshipSkillLearning1999,wifallReachingResponseSelection2017}.
+\textcite{crumpEpisodicContributionsSequential2010} trained participants
+to type words on an unfamiliar keyboard, while constraining the letters
+composing the training words to a pre-specified letter set. Following
+training, typing speed was tested on previously experienced words
+composed of previously experienced letters; novel words composed of
+letters from the trained letter set; and novel words composed of letters
+from an untrained letter set. Consistent with an instance-based account,
+transfer performance was graded such that participants were fastest at
+typing the words they had previously trained on, followed by novel words
+composed of letters they had trained on, and slowest performance for new
+words composed of untrained letters.
+
+\subsection{The effect of training variability on
+transfer}\label{the-effect-of-training-variability-on-transfer}
+
+While similarity-based models account for transfer by the degree of
+similarity between previous and new experiences, a largely separate body
+of research has focused on improving transfer by manipulating
+characteristics of the initial training stage. Such characteristics have
+included training difficulty, spacing, temporal order, feedback
+schedules, and the primary focus of the current work -- variability of
+training examples.
+
+Research on the effects of varied training typically compares
+participants trained under constant, or minimal variability conditions
+to those trained from a variety of examples or conditions
+\autocite{czyzVariabilityPracticeInformation2021,soderstromLearningPerformanceIntegrative2015}.
+Varied training has been shown to influence learning in myriad domains
+including categorization of simple stimuli
+\autocite{hahnEffectsCategoryDiversity2005,maddoxStimulusRangeDiscontinuity2011,posnerGenesisAbstractIdeas1968},
+complex categorization \autocite{nosofskyModelguidedSearchOptimal2018},
+language learning
+\autocite{jonesDensityDistinctivenessEarly2020,perryLearnLocallyThink2010,twomeyAllRightNoises2018,wonnacottInputEffectsAcquisition2012},
+anagram completion \autocite{goodeSuperiorityVariableRepeated2008},
+trajectory extrapolation
+\autocite{fulvioTaskSpecificResponseStrategy2014}, task switching
+\autocite{sabahWhenLessMore2019}, associative learning
+\autocite{leeEvidentialDiversityIncreases2019}, visual search
+\autocite{georgeStimulusVariabilityTask2021,gonzalezDiversityTrainingEnhances2011,kelleyLearningAttendEffects2009},
+voice identity learning \autocite{lavanEffectsHighVariability2019},
+simple motor learning
+\autocite{braunMotorTaskVariation2009,kerrSpecificVariedPractice1978,rollerVariablePracticeLenses2001,willeyLimitedGeneralizationVaried2018},
+sports training
+\autocite{greenPracticeVariabilityTransfer1995a,northEffectConsistentVaried2019},
+and training on a complex video game
+\autocite{seowTransferEffectsVaried2019}.
+
+Training variation has received a particularly large amount of attention
+within the domain of visuomotor skill learning. Much of this research
+has been influenced by the work of
+\textcite{schmidtSchemaTheoryDiscrete1975}, who proposed a schema-based
+account of motor learning as an attempt to address the longstanding
+problem of how novel movements are produced. According to Schema Theory,
+learners possess general motor programs for classes of movements
+(e.g.~throwing a ball with an underhand movement), as well as schema
+rules that determine how a motor program is parameterized or scaled for
+a particular movement. Schema theory predicts that varied training
+results in the formation of a more general schema-rule, which can allow
+for transfer to novel movements within a given movement class.
+Experiments that test this hypothesis are often designed to compare the
+transfer performance of a constant-trained group against that of a
+varied-trained group. Both groups train on the same task, but the varied
+group practices from multiple levels of a task-relevant dimension that
+remains invariant for the constant group. For example, investigators
+might train two groups of participants to throw a projectile at a
+target, with a constant group that throws from a single location, and a
+varied group that throws from multiple locations. Both groups are then
+tested from novel locations. Empirically observed benefits of the
+varied-trained group are then attributed to the variation they received
+during training, a finding observed in numerous studies
+\autocite{catalanoDistantTransferCoincident1984a,chuaPracticeVariabilityPromotes2019,goodwinEffectDifferentQuantities1998,kerrSpecificVariedPractice1978,wulfEffectTypePractice1991},
+and the benefits of this variation are typically thought to be mediated
+by the development of a more general schema for the throwing motion.
+
+Of course, the relationship between training variability and transfer is
+unlikely to be a simple function wherein increased variation is always
+beneficial. Numerous studies have found null, or in some cases negative
+effects of training variation
+\autocite{deloshExtrapolationSineQua1997,sinkeviciuteRoleInputVariability2019,wrisbergVariabilityPracticeHypothesis1987},
+and many more have suggested that the benefits of variability may depend
+on additional factors such as prior task experience, the order of
+training trials, or the type of transfer being measured
+\autocite{bernikerEffectsTrainingBreadth2014,braithwaiteEffectsVariationPrior2015,hahnEffectsCategoryDiversity2005,lavanEffectsHighVariability2019,northEffectConsistentVaried2019,sadakataIndividualAptitudeMandarin2014,zamanPerceptualVariabilityImplications2021}.
+
+\subsection{Issues with Previous
+Research}\label{issues-with-previous-research}
+
+Although the benefits of training variation in visuomotor skill learning
+have been observed many times, null findings have also been repeatedly
+found, leading some researchers to question the veracity of the
+variability of practice hypothesis
+\autocite{newellSchemaTheory19752003,vanrossumSchmidtSchemaTheory1990}.
+Critics have also pointed out that investigations of the effects of
+training variability, of the sort described above, often fail to control
+for the effect of similarity between training and testing conditions.
+For training tasks in which participants have numerous degrees of
+freedom (e.g.~projectile throwing tasks where participants control the x
+and y velocity of the projectile), varied groups are likely to
+experience a wider range of the task space over the course of their
+training (e.g.~more unique combinations of x and y velocities).
+Experimenters may attempt to account for this possibility by ensuring
+that the training location(s) of the varied and constant groups are an
+equal distance away from the eventual transfer locations, such that
+their training throws are, on average, equally similar to throws that
+would lead to good performance at the transfer locations. However, even
+this level of experimental control may still be insufficient to rule out
+the effect of similarity on transfer. Given that psychological
+similarity is typically best described as either a Gaussian or
+exponentially decaying function of psychological distance
+\autocites{ennisMultidimensionalStochasticTheory1988,ghahramaniGeneralizationLocalRemappings1996,loganInstanceTheoryAutomatization1988,nosofskySimilarityScalingCognitive1992,shepardUniversalLawGeneralization1987}[
+]{thoroughmanRapidReshapingHuman2005}, it is plausible that a subset of
+the most similar training instances could have a disproportionate impact
+on generalization to transfer conditions, even if the average distance
+between training and transfer conditions is identical between groups.
+Figure~\ref{fig-toy-model1} demonstrates the consequences of a
+generalization gradient that drops off as a Gaussian function of
+distance from training, as compared to a linear drop-off.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-toy-model1-1.pdf}
+
+}
+
+\caption{\label{fig-toy-model1}Left panel- Generalization predicted from
+a simple model that assumes a linear generalization function. A varied
+group (red vertical lines indicate the 2 training locations) trained
+from positions 400 and 800, and a constant group (blue vertical line),
+trained from position 600. Right panel- if a Gaussian generalization
+function is assumed, then varied training (400, 800) is predicted to
+result in better generalization to positions close to 400 and 800 than
+does constant training at 600. (For interpretation of the references to
+color in this figure legend, the reader is referred to the web version
+of this article.)}
+
+\end{figure}%
+
+In addition to largely overlooking the potential for non-linear
+generalization to confound interpretations of training manipulations,
+the visuomotor skill learning literature also rarely considers
+alternatives to schema representations
+\autocite{chamberlinMemoryRepresentationMotor1992}. Although
+schema-theory remains influential within certain literatures, instance
+or exemplar-based models have accounted for human behavior across myriad
+domains
+\autocite{jamiesonInstanceTheoryDomaingeneral2022,loganInstanceTheoryAttention2002a}.
+As mentioned above, instance based accounts have been shown to perform
+well on a variety of different tasks with motoric components
+\autocite{crumpEpisodicContributionsSequential2010,gandolfoMotorLearningField1996a,meighWhatMemoryRepresentation2018,rosenbaumPlanningReachesEvaluating1995,vandamMappingShapeVisuomotor2015}.
+However, such accounts have received little attention within the
+subdomain of visuomotor skill learning focused on the benefits of varied
+training.
+
+The present work examines whether the commonly observed benefits of
+varied training can be accounted for by between-group differences in
+similarity between training and testing throws. We first attempt to
+replicate previous work finding an advantage of varied training over
+constant training in a projectile launching task. We then examine the
+extent to which this advantage can be explained by an instance-based
+similarity model.
+
+\section{Experiment 1}\label{experiment-1}
+
+\subsection{Methods}\label{methods}
+
+\subsubsection{Sample Size Estimation}\label{sample-size-estimation}
 
@@
 constant conditions following training on an accuracy based projectile
-launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
-2009) was then used to determine that a power of 80% requires a sample
-size of at least 23 participants per condition. All experiments reported
-in the present manuscript exceed this minimum number of participants per
-condition.
-
-### Participants
-
-Participants were recruited from an undergraduate population that is 63%
-female and consists almost entirely of individuals aged 18-22 years. A
-total of 110 Indiana University psychology students participated in
-Experiment 1. We subsequently excluded 34 participants poor performance
-at one of the dependent measures of the task (2.5-3 standard deviations
-worse than the median subject at the task) or for displaying a pattern
-of responses that was clearly indicative of a lack of engagement with
-the task (e.g. simply dropping the ball on each trial rather than
-throwing it at the target), or for reporting that they completed the
-experiment on a phone or tablet device, despite the instructions not to
-use one of these devices. A total of 74 participants were retained for
-the final analyses, 35 in the varied group and 39 in the constant group.
-
-### Task
+launching task
+\autocite{chuaPracticeVariabilityPromotes2019,goodwinEffectDifferentQuantities1998,kerrSpecificVariedPractice1978,wulfEffectTypePractice1991}.
+We then averaged effects across these studies, yielding a Cohens f =.43.
+The GPower 3.1 software package
+\autocite{faulStatisticalPowerAnalyses2009}, 2009) was then used to
+determine that a power of 80\% requires a sample size of at least 23
+participants per condition. All experiments reported in the present
+manuscript exceed this minimum number of participants per condition.
+
+\subsubsection{Participants}\label{participants}
+
+Participants were recruited from an undergraduate population that is
+63\% female and consists almost entirely of individuals aged 18-22
+years. A total of 110 Indiana University psychology students
+participated in Experiment 1. We subsequently excluded 34 participants
+poor performance at one of the dependent measures of the task (2.5-3
+standard deviations worse than the median subject at the task) or for
+displaying a pattern of responses that was clearly indicative of a lack
+of engagement with the task (e.g.~simply dropping the ball on each trial
+rather than throwing it at the target), or for reporting that they
+completed the experiment on a phone or tablet device, despite the
+instructions not to use one of these devices. A total of 74 participants
+were retained for the final analyses, 35 in the varied group and 39 in
+the constant group.
+
+\subsubsection{Task}\label{task}
 
@@
 ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-IGAS_Methods displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-```{r}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
-
-mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
-
-```
-
-## Results
-
-## Data Processing and Statistical Packages
+simply as distance. Figure~\ref{fig-IGAS_Methods} displays the layout of
+the task, as it would appear to a participant at the start of a trial,
+with the ball appearing in the center of the orange square. Using a
+mouse or trackpad, participants click down on the ball to take control
+of the ball, connecting the movement of the ball to the movement of the
+cursor. Participants can then ``wind up'' the ball by dragging it
+(within the confines of the orange square) and then launch the ball by
+releasing the cursor. If the ball does not land on the target,
+participants are presented with feedback in red text at the top right of
+the screen, on how many units away they were from the center of the
+target. If the ball was thrown outside of the boundary of the screen
+participants are given feedback as to how far away from the target
+center the ball would have been if it had continued its trajectory. If
+the ball strikes the barrier (from the side or by landing on top),
+feedback is presented telling participants to avoid hitting the barrier.
+If participants drag the ball outside of the orange square before
+releasing it, the trial terminates, and they are reminded to release the
+ball within the orange square. If the ball lands on the target, feedback
+is presented in green text, confirming that the target was hit, and
+presenting additional feedback on how many units away the ball was from
+the exact center of the target.
+
+\href{https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html}{Link to
+abbrevaited example of task}.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-IGAS_Methods-1.pdf}
+
+}
+
+\caption{\label{fig-IGAS_Methods}The stimuli of the task consisted of a
+blue ball, which the participants would launch at the green target,
+while avoiding the red barrier. On each trial, the ball would appear in
+the center of the orange square, with the position of the orange square
+varying between experimental conditions. Participants were constrained
+to release the ball within the square}
+
+\end{figure}%
+
+\subsection{Results}\label{results}
+
+\subsection{Data Processing and Statistical
+Packages}\label{data-processing-and-statistical-packages}
 
@@
 
-## Training Phase
-
-@fig-IGAS_Training1 below shows aggregate training performance binned into three
-stages representing the beginning, middle, and end of the training
-phase. Because the two conditions trained from target distances that
-were not equally difficult, it was not possible to directly compare
-performance between conditions in the training phase. Our focus for the
-training data analysis was instead to establish that participants did
-improve their performance over the course of training, and to examine
-whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided
-in the supplementary materials.
+\subsection{Training Phase}\label{training-phase}
+
+Figure~\ref{fig-IGAS_Training1} below shows aggregate training
+performance binned into three stages representing the beginning, middle,
+and end of the training phase. Because the two conditions trained from
+target distances that were not equally difficult, it was not possible to
+directly compare performance between conditions in the training phase.
+Our focus for the training data analysis was instead to establish that
+participants did improve their performance over the course of training,
+and to examine whether there was any interaction between training stage
+and condition. Descriptive statistics for the intermittent testing phase
+are provided in the supplementary materials.
 
@@
 condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
-such that performance improved over the course of training There was no
-significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
-and no significant interaction between condition and training stage,
-F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
-
-```{r}
-#| label: fig-IGAS_Training1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
-
-```
-
-## Testing Phase
+effect of training stage F(2,142)=62.4, p\textless.001, \(\eta^{2}_G\) =
+.17, such that performance improved over the course of training There
+was no significant effect of condition F(1,71)=1.42, p=.24,
+\(\eta^{2}_G\) = .02, and no significant interaction between condition
+and training stage, F(2,142)=.10, p=.91, \(\eta^{2}_G\) \textless{} .01.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-IGAS_Training1-1.pdf}
+
+}
+
+\caption{\label{fig-IGAS_Training1}Training performance for varied and
+constant participants binned into three stages. Shorter bars indicate
+better performance (ball landing closer to the center of the target).
+Error bars indicate standard error of the mean.}
+
+\end{figure}%
+
+\subsection{Testing Phase}\label{testing-phase}
 
@@
 position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs. constant) as a
+with a mixed type III ANOVA, with condition (varied vs.~constant) as a
 between-subject factor and throwing location as a within-subject
 variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\<.001, η2G = .23. The effect of training condition was significant
-F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
-between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS_Testing1
-#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-IGAS_Table1
-#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- test=test[,1:3]
-
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
+p\textless.001, η2G = .23. The effect of training condition was
+significant F(1,71)=8.19, p\textless.01, η2G = .07. There was no
+significant interaction between group and position, F(3,213)=1.81,
+p=.15, η2G = .01.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-IGAS_Testing1-1.pdf}
+
+}
+
+\caption{\label{fig-IGAS_Testing1}Testing performance for each of the 4
+testing positions, compared between training conditions. Positions 610
+and 910 were trained on by the varied group, and novel for the constant
+group. Position 760 was trained on by the constant group, and novel for
+the varied group. Position 835 was novel for both groups. Shorter bars
+are indicative of better performance (the ball landing closer to the
+center of the target). Error bars indicate standard error of the mean.}
+
+\end{figure}%
+
+\hfill\break
+\hfill\break
+
+\begin{table}
+
+\caption{\label{tbl-IGAS_Table1}}
+
+\centering{
+
+\captionsetup{labelsep=none}
+
+\begin{tabular}{lll}
+\toprule
+Position & Constant & Varied\\
+\midrule
+610 & 132.48(50.85) & 104.2(38.92)\\
+760 & 207.26(89.19) & 167.12(72.29)\\
+835 & 249.13(105.92) & 197.22(109.71)\\
+910 & 289.36(122.48) & 212.86(113.93)\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table}%
+
+\subsection{Discussion}\label{discussion}
 
@@
 
-# Experiment 2
+\section{Experiment 2}\label{experiment-2}
 
@@
 
-## Methods
-
-### Participants
+\subsection{Methods}\label{methods-1}
+
+\subsubsection{Participants}\label{participants-1}
 
@@
 experiment 1, the undergraduate population from which we recruited
-participants was 63% female and primarily composed of 18--22-year-old
+participants was 63\% female and primarily composed of 18--22-year-old
 individuals. Using the same procedure as experiment 1, we excluded 98
@@
 
-### Task and Procedure
+\subsubsection{Task and Procedure}\label{task-and-procedure}
 
@@
 feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
+found at (https://pcl.sitehost.iu.edu/tg/demos/igas\_expt2\_demo.html).
 
@@
 
-## Results
-
-### Data Processing and Statistical Packages
+\subsection{Results}\label{results-1}
+
+\subsubsection{Data Processing and Statistical
+Packages}\label{data-processing-and-statistical-packages-1}
 
@@
 between groups in the supplementary analyses, were fit using the TEfit
-package in R [@cochraneTEfitsNonlinearRegression2020].
-
-### Training Phase
+package in R \autocite{cochraneTEfitsNonlinearRegression2020}.
+
+\subsubsection{Training Phase}\label{training-phase-1}
 
@@
 As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. @fig-e2train depicts the training
-performance of the varied group alongside that of the aggregate of the
-six constant groups (5a), and each of the 6 separate constant groups
-(5b). An ANOVA comparison with training stage (beginning, middle, end)
-as a within-group factor and group (the varied condition vs. the 6
-constant conditions collapsed together) as a between-subject factor
-revealed no significant effect of group on training performance,
-F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
-stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
-interaction between group and training stage, F(2,412)=.489 p=.61,
-$\eta^{2}_G$ \<.01. We also tested for a difference in training
-performance between the varied group and the two constant groups that
-trained matching throwing positions (i.e., the constant groups training
-from position 500, and position 800). The results of our ANOVA on this
-limited dataset mirrors that of the full-group analysis, with no
-significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
-significant effect of training stage F(2,172)=56.29, p\<.001,
-$\eta^{2}_G$ =.11, and no significant interaction between group and
-training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
-
-```{r}
-
-e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
-
-exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
-
-exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
-
-exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
-
-exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
-
-transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
-
-# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
-# novelAll <- novelAll %>% group_by(positionX) %>%
-#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
-novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
-
-constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
-variedTest <- transfer %>% filter(condit==7) # only varied testing
-variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
-
-variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
-constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
-variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
-
-exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-```
-
-```{r}
-#| label: fig-e2train
-#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
-On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-
-### New - 3 stage
-e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
-  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
-  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
-
-e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
-  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
-
-#plot_grid(e2train1,e2train2,ncol=1)
-
-e2train1
-e2train2
-
-```
-
-### Testing Phase
+confirmation that some learning did occur. \textbf{?@fig-e2train}
+depicts the training performance of the varied group alongside that of
+the aggregate of the six constant groups (5a), and each of the 6
+separate constant groups (5b). An ANOVA comparison with training stage
+(beginning, middle, end) as a within-group factor and group (the varied
+condition vs.~the 6 constant conditions collapsed together) as a
+between-subject factor revealed no significant effect of group on
+training performance, F(1,206)=.55,p=.49, \(\eta^{2}_G\) \textless.01, a
+significant effect of training stage F(2,412)=77.91, p\textless.001,
+\(\eta^{2}_G\) =.05, and no significant interaction between group and
+training stage, F(2,412)=.489 p=.61, \(\eta^{2}_G\) \textless.01. We
+also tested for a difference in training performance between the varied
+group and the two constant groups that trained matching throwing
+positions (i.e., the constant groups training from position 500, and
+position 800). The results of our ANOVA on this limited dataset mirrors
+that of the full-group analysis, with no significant effect of group
+F(1,86)=.48, p=.49, \(\eta^{2}_G\) \textless.01, a significant effect of
+training stage F(2,172)=56.29, p\textless.001, \(\eta^{2}_G\) =.11, and
+no significant interaction between group and training stage,
+F(2,172)=.341 p=.71, \(\eta^{2}_G\) \textless.01.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2train-1.pdf}
+
+}
+
+\caption{\label{fig-e2train-1}Training performance for the six constant
+conditions, and the varied condition, binned into three stages. On the
+left side, the six constant groups are averaged together, as are the two
+training positions for the varied group. On the right side, the six
+constant groups are shown separately, with each set of bars representing
+the beginning, middle, and end of training for a single constant group
+that trained from the position indicated on the x-axis. Figure 5b also
+shows training performance separately for both of the throwing locations
+trained by the varied group. Error bars indicate standard error of the
+mean.}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2train-2.pdf}
+
+}
+
+\caption{\label{fig-e2train-2}Training performance for the six constant
+conditions, and the varied condition, binned into three stages. On the
+left side, the six constant groups are averaged together, as are the two
+training positions for the varied group. On the right side, the six
+constant groups are shown separately, with each set of bars representing
+the beginning, middle, and end of training for a single constant group
+that trained from the position indicated on the x-axis. Figure 5b also
+shows training performance separately for both of the throwing locations
+trained by the varied group. Error bars indicate standard error of the
+mean.}
+
+\end{figure}%
+
+\subsubsection{Testing Phase}\label{testing-phase-1}
 
@@
 varied). A type III between-subjects ANOVA was performed, yielding a
-significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
+significant effect of condition F(1,206)=4.33, p=.039, \(\eta^{2}_G\)
 =.02. Descriptive statistics for each condition are shown in table 2. In
-@fig-e2testa visualizes the consistent advantage of the varied condition
-over the constant groups across the testing positions. @fig-e2testa shows
-performance between the varied condition and the individual constant
-groups.
-
-```{r}
-#| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 9
-
-# manuscript plot
-e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)+
-  ggtitle("A")
-
-e2test2<-exp2.Test7 %>% 
-  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
-  facet_wrap(~ThrowPosition4)+
-  ylab("Mean Distance From Center Of Target")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
-
-e2test1 / e2test2
-
-```
-
-\
-\
-\
-
-```{r}
-#| label: tbl-e2table1
-#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-
-tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab2=tab2[,1:3]
-
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
+Figure~\ref{fig-e2testa} visualizes the consistent advantage of the
+varied condition over the constant groups across the testing positions.
+Figure~\ref{fig-e2testa} shows performance between the varied condition
+and the individual constant groups.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2testa-1.pdf}
+
+}
+
+\caption{\label{fig-e2testa}Testing phase performance from each of the
+six testing positions. The six constant conditions are averaged together
+into a single constant group, compared against the single varied-trained
+group.B) Transfer performance from each of the 6 throwing locations from
+which all participants were tested. Each bar represents performance from
+one of seven distinct training groups (six constant groups in red, one
+varied group in blue). The x axis labels indicate the location(s) from
+which each group trained. Lower values along the y axis reflect better
+performance at the task (closer distance to target center). Error bars
+indicate standard error of the mean.}
+
+\end{figure}%
+
+\hfill\break
+\hfill\break
+\hfill\break
+
+\begin{table}
+
+\caption{\label{tbl-e2table1}Transfer performance from each of the 6
+throwing locations from which all participants were tested. Each bar
+represents performance from one of seven distinct training groups (six
+constant groups in red, one varied group in blue). The x axis labels
+indicate the location(s) from which each group trained. Lower values
+along the y axis reflect better performance at the task (closer distance
+to target center). Error bars indicate standard error of the mean.}
+
+\centering{
+
+\begin{tabular}{lll}
+\toprule
+Position & Constant & Varied\\
+\midrule
+400 & 100.59(46.3) & 83.92(33.76)\\
+500 & 152.28(69.82) & 134.38(61.38)\\
+625 & 211.21(90.95) & 183.51(75.92)\\
+675 & 233.32(93.35) & 206.32(94.64)\\
+800 & 283.24(102.85) & 242.65(89.73)\\
+\addlinespace
+900 & 343.51(114.33) & 289.62(110.07)\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table}%
 
@@
 averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
+condition (constant vs.~varied): F(1,206)=4.30, p=.039, \(\eta^{2}_G\) =
 .02 .
 
-```{r}
-#| label: tbl-e2table2
-#| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-
-sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
- tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
- tab3 = tab3 %>% 
-   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab3=tab3[,1:3]
-
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
+\begin{table}
+
+\caption{\label{tbl-e2table2}Testing performance from novel positions.
+Includes data only from positions that were not encountered during the
+training stage (e.g.~excludes positions 500 and 800 for the varied
+group, and one of the six locations for each of the constant groups).
+Table presents Mean absolute deviations from the center of the target,
+and standard deviations in parenthesis.}
+
+\centering{
+
+\begin{tabular}{lll}
+\toprule
+Position & Constant & Varied\\
+\midrule
+400 & 98.84(45.31) & 83.92(33.76)\\
+500 & 152.12(69.94) & NA\\
+625 & 212.91(92.76) & 183.51(75.92)\\
+675 & 232.9(95.53) & 206.32(94.64)\\
+800 & 285.91(102.81) & NA\\
+\addlinespace
+900 & 346.96(111.35) & 289.62(110.07)\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table}%
 
@@
 omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). @fig-e2test1 displays
-the particular subset of comparisons utilized for this analysis. Again,
-we standardized performance within each position before performing the
-analyses on the aggregated data. In this case, the effect of condition
-did not reach statistical significance F(1,149)=3.14, p=.079,
-$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
-
-```{r}
-#| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-
-sum.variedVsNovelIden <- variedVsNovelIden  %>%
-  group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
-
-e2Test2
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-e2tab3
-#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-
-tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
-tab4=tab4 %>% group_by(Condition) %>% 
-   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab4=tab4[,1:3]
-
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
+those positions were not novel to the varied group).
+Figure~\ref{fig-e2test1} displays the particular subset of comparisons
+utilized for this analysis. Again, we standardized performance within
+each position before performing the analyses on the aggregated data. In
+this case, the effect of condition did not reach statistical
+significance F(1,149)=3.14, p=.079, \(\eta^{2}_G\) = .02. Table 4
+provides descriptive statistics.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2test1-1.pdf}
+
+}
+
+\caption{\label{fig-e2test1}A comparison of throwing location that are
+identical to those trained by the constant participants (e.g.~constant
+participants trained at position 900, tested from position 900), which
+are also novel to the varied-trained participants (thus excluding
+positions 500 and 800). Error bars indicate standard error of the mean.}
+
+\end{figure}%
+
+\hfill\break
+\hfill\break
+
+\begin{table}
+
+\caption{\label{tbl-e2tab3}Testing performance from the locations
+trained by constant participants and novel to varied participants.
+Locations 500 and 800 are not included as these were trained by the
+varied participants. Table presents Mean absolute deviation from the
+center of the target, and standard deviations in parenthesis.}
+
+\centering{
+
+\begin{tabular}{lll}
+\toprule
+Position & Constant & Varied\\
+\midrule
+400 & 108.85(50.63) & 83.92(33.76)\\
+625 & 204.75(84.66) & 183.51(75.92)\\
+675 & 235.75(81.15) & 206.32(94.64)\\
+900 & 323.5(130.9) & 289.62(110.07)\\
+\bottomrule
+\end{tabular}
+
+}
+
+\end{table}%
+
+\subsection{Discussion}\label{discussion-1}
 
@@
 common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
+performance during acquisition than training under constant conditions
+\autocite{catalanoDistantTransferCoincident1984a,wrisbergVariabilityPracticeHypothesis1987},
+which has been suggested to relate to the subsequent benefits of varied
+training in retention and generalization testing
+\autocite{soderstromLearningPerformanceIntegrative2015}. However our
+finding of no difference in training performance between constant and
+varied groups has been observed in previous work
+\autocite{chuaPracticeVariabilityPromotes2019,moxleySchemaVariabilityPractice1979,pigottMotorSchemaStructure1984}.
 
@@
 learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
+Schmidt's influential Schema Theory
+\autocite{catalanoDistantTransferCoincident1984a,chuaPracticeVariabilityPromotes2019,goodwinEffectDifferentQuantities1998,mccrackenTestSchemaTheory1977,moxleySchemaVariabilityPractice1979,newellVariabilityPracticeTransfer1976,pigottMotorSchemaStructure1984,rollerVariablePracticeLenses2001,schmidtSchemaTheoryDiscrete1975,willeyLongtermMotorLearning2018,wrisbergVariabilityPracticeHypothesis1987,wulfEffectTypePractice1991}.
+We also join a much smaller set of research to observe this pattern in a
+computerized task \autocite{seowTransferEffectsVaried2019}. One
+departure from the experiment 1 findings concerns the pattern wherein
+the varied group outperformed the constant group even from the training
+position of the constant group, which was significant in experiment 1,
+but did not reach significance in experiment 2. Although this pattern
+has been observed elsewhere in the literature
+\autocite{goodeSuperiorityVariableRepeated2008,kerrSpecificVariedPractice1978},
 the overall evidence for this effect appears to be far weaker than for
@@
 
-# Computational Model
+\section{Computational Model}\label{computational-model}
 
@@
 target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
-
-```{r}
-#| label: fig-taskSpace
-#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig-width: 11
-#| fig-height: 9
-#| 
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
-  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
-
-library(patchwork)
-ss/fs
-
-```
+six separate similarity scores for each participant.
+Figure~\ref{fig-taskSpace} visualizes the solution space for each
+location and illustrates how different combinations of x and y velocity
+result in successfully striking the target from different launching
+positions. As illustrated in Figure~\ref{fig-taskSpace}, the solution
+throws represent just a small fraction of the entire space of velocity
+combinations used by participants throughout the experiment.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-taskSpace-1.pdf}
+
+}
+
+\caption{\label{fig-taskSpace}A) A visual representation of the
+combinations of throw parameters (x and y velocities applied to the ball
+at launch), which resulted in target hits during the testing phase. This
+empirical solution space was compiled from all of the participants in
+experiment 2. B) shows the solution space within the context of all of
+the throws made throughout the testing phase of the experiment.}
+
+\end{figure}%
 
@@
 Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
-
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
-(e^{-c^\cdot d^{p}_{i,j}}) $$
-
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+similarity
+\autocite{loganInstanceTheoryAttention2002a,nosofskySimilarityScalingCognitive1992},
+these distances were multiplied by a sensitivity parameter, c, and then
+exponentiated to yield a similarity value. The parameter c controls the
+rate with which similarity-based generalization drops off as the
+Euclidean distance between two throws in x- and y-velocity space
+increases. If c has a large value, then even a small difference between
+two throws' velocities greatly decreases the extent of generalization
+from one to the other. A small value for c produces broad generalization
+from one throw to another despite relatively large differences in their
+velocities. The similarity values for each training individual throw
+made by a given participant were then summed to yield a final similarity
+score, with a separate score computed for each of the 6 testing
+positions. The final similarity score is construable as index of how
+accurate the throws a participant made during the training phase would
+be for each of the testing positions.
+
+\textbf{Equation 1:} \[ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
+(e^{-c^\cdot d^{p}_{i,j}}) \]
+
+\textbf{Equation 2:}
+\[ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } \]
 
@@
 significantly predictive of performance in the transfer stage, t
-=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
-training throws and solution spaces for each of the test locations
-resulted in better performance. We then repeated the group comparisons
-above while including similarity as a covariate in the model. Comparing
-the varied and constant groups in testing performance from all testing
-positions yielded a significant effect of similarity, F(1, 205)=85.66,
-p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
-(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
-group comparison limited to only novel locations for the varied group
-pit against trained location for the constant group resulted in a
-significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
-=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
-=.07. For all comparisons, the pattern of results was consistent with
-the initial findings from experiment 2, with the varied group still
-performing significantly better than the constant group.
-
-## Fitting model parameters separately by group
+=-15.88, p\textless.01, \(r^2\)=.17, such that greater similarity
+between training throws and solution spaces for each of the test
+locations resulted in better performance. We then repeated the group
+comparisons above while including similarity as a covariate in the
+model. Comparing the varied and constant groups in testing performance
+from all testing positions yielded a significant effect of similarity,
+F(1, 205)=85.66, p\textless.001, \(\eta^{2}_G\) =.29, and also a
+significant effect of condition (varied vs.~constant), F(1, 205)=6.03,
+p=.015, \(\eta^{2}_G\) =.03. The group comparison limited to only novel
+locations for the varied group pit against trained location for the
+constant group resulted in a significant effect of similarity,
+F(1,148)=31.12, p\textless.001, \(\eta^{2}_G\) =.18 as well as for
+condition F(1,148)=11.55, p\textless.001, \(\eta^{2}_G\) =.07. For all
+comparisons, the pattern of results was consistent with the initial
+findings from experiment 2, with the varied group still performing
+significantly better than the constant group.
+
+\subsection{Fitting model parameters separately by
+group}\label{fitting-model-parameters-separately-by-group}
 
@@
 captured by fitting the generalization parameter of an instance-based
-model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
-will increase when a rational agent encounters a wider variety of
-examples. Following these leads, we assume that in addition to learning
-the task itself, participants are also adjusting how generalizable their
-experience should be. Varied versus constant participants may be
-expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the
-instance-based model (in the present case, the c parameter) can be
-allowed to vary between the two groups to reflect the tendency of
-learners to adaptively tune the extent of their generalization. One
-specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
-variable, as with the variable training condition, then one might infer
-that future test situations will also be variable, in which case a low
-value of c will allow better generalization because generalization will
-drop off slowly with training-to-testing distance. Conversely, if one's
-training experience has little variability, as found in the constant
-training conditions, then one might adopt a high value of c so that
+model separately to each group
+\autocite{hahnEffectsCategoryDiversity2005,lambertsFlexibleTuningSimilarity1994}.
+Relatedly, the influential Bayesian generalization model developed by
+\textcite{tenenbaumGeneralizationSimilarityBayesian2001a} predicts that
+the breadth of generalization will increase when a rational agent
+encounters a wider variety of examples. Following these leads, we assume
+that in addition to learning the task itself, participants are also
+adjusting how generalizable their experience should be. Varied versus
+constant participants may be expected to learn to generalize their
+experience to different degrees. To accommodate this difference, the
+generalization parameter of the instance-based model (in the present
+case, the c parameter) can be allowed to vary between the two groups to
+reflect the tendency of learners to adaptively tune the extent of their
+generalization. One specific hypothesis is that people adaptively set a
+value of c to fit the variability of their training experience
+\autocite{nosofskyExemplarbasedAccountsMultiplesystem2000,sakamotoTrackingVariabilityLearning2006}.
+If one's training experience is relatively variable, as with the
+variable training condition, then one might infer that future test
+situations will also be variable, in which case a low value of c will
+allow better generalization because generalization will drop off slowly
+with training-to-testing distance. Conversely, if one's training
+experience has little variability, as found in the constant training
+conditions, then one might adopt a high value of c so that
 generalization falls off rapidly away from the trained positions.
@@
 Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\<.01). Of greater interest is the
-difference between linear model 2, in which similarity is computed from
-a single c value fit from all participants (Similarity1c), with linear
-model 4, which fits the c parameter separately between groups
+predictor of testing performance (p\textless.01). Of greater interest is
+the difference between linear model 2, in which similarity is computed
+from a single c value fit from all participants (Similarity1c), with
+linear model 4, which fits the c parameter separately between groups
 (Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\<.01), with the varied
-group still performing significantly better. However, in linear model 4
-the addition of the Similarity2c predictor results in the effect of
-training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs. constant training is accounted for by the
+significant when controlling for Similarity1c (p\textless.01), with the
+varied group still performing significantly better. However, in linear
+model 4 the addition of the Similarity2c predictor results in the effect
+of training group becoming nonsignificant (p=.40), suggesting that the
+effect of varied vs.~constant training is accounted for by the
 Similarity2c predictor. Next, to further establish a difference between
@@
 Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear
-Model 4) found no improvement in model performance with the addition of
-the training group predictor (F=1.61, p=.20).
+significantly improved the performance of the model (F=22.07,
+p\textless.01). However, in the second model comparison, ANOVA (Linear
+model 3, Linear Model 4) found no improvement in model performance with
+the addition of the training group predictor (F=1.61, p=.20).
 
@@
 
-# General Discussion
+\section{General Discussion}\label{general-discussion}
 
@@
 participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
+conditions identical to the constant group training
+\autocite{goodeSuperiorityVariableRepeated2008,greenPracticeVariabilityTransfer1995a,kerrSpecificVariedPractice1978}.
+In experiment 1 varied participants performed significantly better on
+this identity comparison. In Experiment 2, the comparison was not
+significant initially, but became significant after controlling for the
+similarity measure that incorporates only a single value for the
+steepness of similarity-based generalization (c). Furthermore, we showed
+that the general pattern of results from Experiment 2 could be
+parsimoniously accommodated by an instance-based similarity model, but
+only with the assumption that constant and varied participants
+generalize their training experience to different degrees. Our results
+thus suggest that the benefits of variation cannot be explained by the
+varied-trained participants simply covering a broader range of the task
+space. Rather, the modeling suggests that varied participants also learn
+to adaptively tune their generalization function such that throwing
+locations generalize more broadly to one another than they do in the
+constant condition. A learning system could end up adopting a higher c
+value in the constant than variable training conditions by monitoring
+the trial-by-trial variability of the training items. The c parameter
+would be adapted downwards when adjacent training items are dissimilar
+to each other and adapted upwards when adjacent training items are the
+same. In this fashion, contextually appropriate c values could be
+empirically learned. This learning procedure would capture the insight
+that if a situation has a high amount variability, then the learner
+should be predisposed toward thinking that subsequent test items will
+also show considerable variability, in which case generalization
+gradients should be broad, as is achieved by low values for c.
 
@@
 our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy_Model2 we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model2
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
-For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
-The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
-#| fig.width: 11
-#| fig.height: 11.5
-
-#
-
-p=2
-c<- .000002
-
-trainingTestingDifference=2000;
-cvaried=.00002
-cconstant=.0005
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
-                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
-                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
-                            ) %>% 
-  group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
-
-#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
-
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
-ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
-ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
-ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
-# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
-
-gtitle="Figure 9."
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-
-```
-
-As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
-However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning implementations of instance-based models in several ways.
-One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define a category item (e.g.
-size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
-movement force, velocity, angle, posture) in addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in
-support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
-Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
-Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
-A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
+data, not just that of the identity comparisons, in
+\textbf{?@fig-Toy\_Model2} we demonstrate how a simplified version of
+the IGAS model could in principle produce such a pattern. In addition to
+the assumption of differential generalization between varied and
+constant conditions, our simplified model makes explicit an assumption
+that is incorporated into the full IGAS model -- namely that even when
+being tested from a position identical to that which was trained, there
+are always some psychological contextual differences between training
+and testing throws, resulting in a non-zero dissimilarity.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-Toy-Model2-1.pdf}
+
+}
+
+\caption{\label{fig-Toy-Model2}A simple model depicting the necessity of
+both of two separately fit generalization parameters, c, and a positive
+distance between training and testing contexts, in order for an instance
+model to predict a pattern of varied training from stimuli 400 and 800
+outperforming constant training from position 600 at a test position of
+600. For the top left panel, in which the generalization model assumes a
+single c value (-.008) for both varied and constant conditions, and
+identical contexts across training and testing, the equation which
+generates the varied condition is - Amount of Generalization =
+\(e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}\), whereas the constant
+group generalization is generated from \(2\cdot e^{(c\cdot|x-600|)}\).
+For the top right panel, the c constants in the original equations are
+different for the 2 conditions, with \(c=-.002\) for the varied
+condition, and \(c=-.008\) for the constant condition. The bottom two
+panels are generated from identical equations to those immediately
+above, except for the addition of extra distance (100 units) to reflect
+the assumption of some change in context between training and testing
+conditions. Thus, the generalization model for the varied condition in
+the bottom-right panel is of the form - Amount of Generalization =
+\(e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}\) .}
+
+\end{figure}%
+
+As mentioned above, the idea that learners flexibly adjust their
+generalization gradient based on prior experience does have precedent in
+the domains of category learning
+\autocite{ahaConceptLearningFlexible1992,briscoeConceptualComplexityBias2011,hahnEffectsCategoryDiversity2005,lambertsFlexibleTuningSimilarity1994,opdebeeckRepresentationPerceivedShape2008},
+and sensorimotor adaptation
+\autocite{marongelliAdvantageFlexibleNeuronal2013,taylorContextdependentGeneralization2013,thoroughmanRapidReshapingHuman2005}.
+\textcite{lambertsFlexibleTuningSimilarity1994} showed that a simple
+manipulation of background knowledge during a categorization test
+resulted in participants generalizing their training experience more or
+less broadly, and moreover that such a pattern could be captured by
+allowing the generalization parameter of an instance-based similarity
+model to be fit separately between conditions. The flexible
+generalization parameter has also successfully accounted for
+generalization behavior in cases where participants have been trained on
+categories that differ in their relative variability
+\autocite{hahnEffectsCategoryDiversity2005,sakamotoTrackingVariabilityLearning2006}.
+However, to the best of our knowledge, IGAS is the first instance-based
+similarity model that has been put forward to account for the effect of
+varied training in a visuomotor skill task. Although IGAS was inspired
+by work in the domain of category learning, its success in a distinct
+domain may not be surprising in light of the numerous prior observations
+that at least certain aspects of learning and generalization may operate
+under common principles across different tasks and domains
+\autocite{censorCommonMechanismsHuman2012,hillsCentralExecutiveSearch2010,jamiesonInstanceTheoryDomaingeneral2022,lawSharedMechanismsPerceptual2010,roarkComparingPerceptualCategory2021,rosenbaumAcquisitionIntellectualPerceptualMotor2001,vigoLearningDifficultyVisual2018,wallIdentifyingRelationshipsCognitive2021,wuSimilaritiesDifferencesSpatial2020,yangGeneralLearningAbility2020}.
+
+Our modelling approach does differ from category learning
+implementations of instance-based models in several ways. One such
+difference is the nature of the training instances that are assumed to
+be stored. In category learning studies, instances are represented as
+points in a multidimensional space of all of the attributes that define
+a category item (e.g.~size/color/shape). Rather than defining instances
+in terms of what stimuli learners experience, our approach assumes that
+stored, motor instances reflect how they act, in terms of the velocity
+applied to the ball on each throw. An advantage of many motor learning
+tasks is the relative ease with which task execution variables can be
+directly measured (e.g.~movement force, velocity, angle, posture) in
+addition to the decision and response time measures that typically
+exhaust the data generated from more classical cognitive tasks. Of
+course, whether learners actually are storing each individual motor
+instance is a fundamental question beyond the scope of the current work
+-- though as described in the introduction there is some evidence in
+support of this idea
+\autocite{chamberlinNoteSchemaExemplar1992,crumpEpisodicContributionsSequential2010,hommelEventFilesEvidence1998,meighWhatMemoryRepresentation2018,poldrackRelationshipSkillLearning1999}.
+A particularly noteworthy instance-based model of sensory-motor behavior
+is the Knowledge II model of Rosenbaum and colleagues
+\autocite{cohenWhereGraspsAre2004,rosenbaumPlanningReachesEvaluating1995}.
+Knowledge II explicitly defines instances as postures (joint
+combinations), and is thus far more detailed than IGAS in regards to the
+contents of stored instances. Knowledge II also differs from IGAS in
+that learning is accounted for by both the retrieval of stored postures,
+and the generation of novel postures via the modification of retrieved
+postures. A promising avenue for future research would be to combine the
+adaptive similarity mechanism of IGAS with the novel instance generation
+mechanisms of Knowledge II.
 
 Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
-lighting up consecutively, and attempt to time a button press with the
-onset of the final lamp. The design consisted of four separate constant
-groups, each training from a single lighting velocity, and a single
-varied group training with all four of the lighting velocities used by
-the individual constant groups. Participants were then split into four
-separate testing conditions, each of which were tested from a single
-novel lighting velocity of varying distance from the training
-conditions. The result of primary interest was that all participants
-performed worse as the distance between training and testing velocity
-increased -- a typical generalization decrement. However, varied
-participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in
-a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are
-similar to our own, our work is novel in that we account for our results
-with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their
-separate constant groups together may result in similarity confounds
-between varied and constant conditions that leaves their study open to
-methodological criticisms, especially in light of related work which
-demonstrated that the extent to which varied training may be beneficial
-can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
-similarity.
-
-## Limitations
+the effects of varied training in a coincident timing task
+\autocite{catalanoDistantTransferCoincident1984a}. In this task,
+participants observe a series of lamps lighting up consecutively, and
+attempt to time a button press with the onset of the final lamp. The
+design consisted of four separate constant groups, each training from a
+single lighting velocity, and a single varied group training with all
+four of the lighting velocities used by the individual constant groups.
+Participants were then split into four separate testing conditions, each
+of which were tested from a single novel lighting velocity of varying
+distance from the training conditions. The result of primary interest
+was that all participants performed worse as the distance between
+training and testing velocity increased -- a typical generalization
+decrement. However, varied participants showed less of a decrement than
+did constant participants. The authors take this result as evidence that
+varied training results in a less-steep generalization gradient than
+does constant training. Although the experimental conclusions of
+Catalano and Kleiner are similar to our own, our work is novel in that
+we account for our results with a cognitive model, and without assuming
+the formation of a schema. Additionally, the way in which Catalano and
+Kleiner collapse their separate constant groups together may result in
+similarity confounds between varied and constant conditions that leaves
+their study open to methodological criticisms, especially in light of
+related work which demonstrated that the extent to which varied training
+may be beneficial can depend on whether the constant group they are
+compared against trained from similar conditions to those later tested
+\autocite{wrisbergVariabilityPracticeHypothesis1987}. Our study
+alleviates such concerns by explicitly controlling for similarity.
+
+\subsection{Limitations}\label{limitations}
 
@@
 into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
-
-## Conclusion
+representations
+\autocite{nosofskySimilarityScalingCognitive1992,shepardUniversalLawGeneralization1987}.
+Such scaling typically entails having participants rate the similarity
+between individual items and using these similarity judgements to then
+compute the psychological distances between stimuli, which can then be
+fed into a subsequent model. In the present investigation, there was no
+such way to scale the x and y velocity components in terms of the
+psychological similarity, and thus our modelling does rely on the
+assumption that the psychological distances between the different
+throwing positions are proportional to absolute distances in the metric
+space of the task (e.g. the relative distance between positions 400 and
+500 is equivalent to that between 800 and 900). However, an advantage of
+our approach is that we are measuring similarity in terms of how
+participants behave (applying a velocity to the ball), rather than the
+metric features of the task stimuli.
+
+\subsection{Conclusion}\label{conclusion}
 
@@
 
-# Project 2
-
-_______________________________________________________________________________
-[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
-
-[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
-
-_______________________________________________________________________________
-
-# Introduction
-
-A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
-One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ].
-The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
-
-## Function Learning and Extrapolation
-
-The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
-
-@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
-Input stimuli and output responses were both lines of varying length.
-The correct output response was related to the length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
-@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
-Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
-In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
-All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
-
-The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
-The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models.
-The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
-The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
-When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
-
-### Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
-
-```{r}
-#| label: fig-delosh-extrap
-#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
-#| echo: false
-#| fig-width: 10
-#| cache: false 
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-source(here::here("Functions","deLosh_data.R"))
-#source(here::here("Functions","Display_Functions.R"))
-
-extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
-                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
-
-linear_function <- function(x) 2.2 * x + 30
-exponential_function <- function(x) 200 * (1 - exp(-x/25))
-quadratic_function <- function(x) 210 - (x - 50)^2 / 12
-
-linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
-    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
-  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
-
-exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
-  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
-  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
-  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
-  extrapLines +
-  scale_shape_manual(values = c(1)) +
-  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
-  theme(legend.title = element_blank(), legend.position="top") +
-  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
-                                                  linetype = c(0, 1))))
-
-quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
-  geom_point( shape = 1) +
-  stat_function( fun = quadratic_function, geom = "line") +
-  labs(title="Quadratic Function",x="",y="") + extrapLines
-
-linear_plot + exponential_plot + quadratic_plot
-```
-
-## Overview Of Present Study
-
-The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
-To the best of our knowledge, this research is the first to employ the classic constant vs.
-varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
-Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
-
-To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
-Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.
-
-## Methods
-
-*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
-Participants were randomly assigned to one of two training conditions: varied training or constant training.
-
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
-band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
-Participants were instructed that only the x velocity component of the ball was relevant to the task.
-The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
+\section{Project 2}\label{project-2}
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+\href{https://tegorman13.github.io/htw/}{Link to HTW project page}\\
+
+\href{https://tegorman13.github.io/htw/paper.html}{Working Draft of HTW
+Manuscript}
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+\section{Introduction}\label{introduction-1}
+
+A longstanding issue across both science and instruction has been to
+understand how various aspects of an educational curriculum or training
+program influence learning acquisition and generalization. One such
+aspect, which has received a great deal of research attention, is the
+variability of examples experienced during training
+\autocite{ravivHowVariabilityShapes2022}. The influence of training
+variation has been studied in numerous domains, including category
+learning
+\autocite{cohenCategoryVariabilityExemplar2001,posnerGenesisAbstractIdeas1968},
+visuomotor learning \autocites{schmidtSchemaTheoryDiscrete1975}[
+]{bernikerEffectsTrainingBreadth2014}, language learning
+\autocite{perryLearnLocallyThink2010}, and education
+\autocite{braithwaiteEffectsVariationPrior2015,guoEffectsExampleVariability2014}.
+The pattern of results is complex, with numerous studies finding both
+beneficial
+\autocite{catalanoDistantTransferCoincident1984a,braunMotorTaskVariation2009,rollerVariablePracticeLenses2001},
+as well as null or negative effects
+\autocites{huHighvariabilityTrainingDoes2024,vanrossumSchmidtSchemaTheory1990}[
+]{brekelmansDoesHighVariability2022}. The present study seeks to
+contribute to the large body of existing research by examining the
+influence of variability in visuomotor function learning - a domain in
+which it has been relatively under-studied.
+
+\subsection{Function Learning and
+Extrapolation}\label{function-learning-and-extrapolation}
+
+The study of human function learning investigates how people learn
+relationships between continuous input and output values. Function
+learning is studied both in tasks where individuals are exposed to a
+sequence of input/output pairs
+\autocite{deloshExtrapolationSineQua1997,mcdanielEffectsSpacedMassed2013},
+or situations where observers are presented with a an incomplete
+scatterplot or line graph and make predictions about regions of the plot
+that don't contain data
+\autocite{ciccioneCanHumansPerform2021a,courrieuQuickApproximationBivariate2012,saidExtrapolationAccuracyUnderestimates2021,schulzCommunicatingCompositionalPatterns2020}.
+
+\textcite{carrollFunctionalLearningLearning1963} conducted the earliest
+work on function learning. Input stimuli and output responses were both
+lines of varying length. The correct output response was related to the
+length of the input line by a linear, quadratic, or random function.
+Participants in the linear and quadratic performed above chance levels
+during extrapolation testing, with those in the linear condition
+performing the best overall. Carroll argued that these results were best
+explained by a ruled based model wherein learners form an abstract
+representation of the underlying function. Subsequent work by
+\textcite{brehmerHypothesesRelationsScaled1974},testing a wider array of
+functional forms, provided further evidence for superior extrapolation
+in tasks with linear functions. Brehmer argued that individuals start
+out with an assumption of a linear function, but given sufficient error
+will progressively test alternative hypothesis with polynomials of
+greater degree. \textcite{kohFunctionLearningInduction1991} employed a
+visuomotor function learning task, wherein participants were trained on
+examples from an unknown function relating the length of an input line
+to the duration of a response (time between keystrokes). In this domain,
+participants performed best when the relation between line length and
+response duration was determined by a power, as opposed to linear
+function. Koh \& Meyer developed the log-polynomial adaptive-regression
+model to account for their results.
+
+The first significant challenge to the rule-based accounts of function
+learning was put forth by \textcite{deloshExtrapolationSineQua1997} . In
+their task, participants learned to associate stimulus magnitudes with
+response magnitudes that were related via either linear, exponential, or
+quadratic function. Participants approached ceiling performance by the
+end of training in each function condition, and were able to correctly
+respond in interpolation testing trials. All three conditions
+demonstrated some capacity for extrapolation, however participants in
+the linear condition tended to underestimate the true function, while
+exponential and quadratic participants reliably overestimated the true
+function on extrapolation trials. Extrapolation and interpolation
+performance are depicted in Figure~\ref{fig-delosh-extrap}.
+
+The authors evaluated both of the rule-based models introduced in
+earlier research (with some modifications enabling trial-by-trial
+learning). The polynomial hypothesis testing model
+\autocite{carrollFunctionalLearningLearning1963,brehmerHypothesesRelationsScaled1974}
+tended to mimic the true function closely in extrapolation, and thus
+offered a poor account of the human data. The log-polynomial adaptive
+regression model \autocite{kohFunctionLearningInduction1991} was able to
+mimic some of the systematic deviations produced by human subjects, but
+also predicted overestimation in cases where underestimation occurred.
+
+The authors also introduced two new function-learning models. The
+Associative Learning Model (ALM) and the extrapolation-association model
+(EXAM). ALM is a two layer connectionist model adapted from the ALCOVE
+model in the category learning literature
+\autocite{kruschkeALCOVEExemplarbasedConnectionist1992}. ALM belongs to
+the general class of radial-basis function neural networks, and can be
+considered a similarity-based model in the sense that the nodes in the
+input layer of the network are activated as a function of distance. The
+EXAM model retains the same similarity based activation and associative
+learning mechanisms as ALM, while being augmented with a linear rule
+response mechanism. When presented with novel stimuli, EXAM will
+retrieve the most similar input-output examples encountered during
+training, and from those examples compute a local slope. ALM was able to
+provide a good account of participant training and interpolation data in
+all three function conditions, however it was unable to extrapolate.
+EXAM, on the other hand, was able to reproduce both the extrapolation
+underestimation, as well as the quadratic and exponential overestimation
+patterns exhibited by the human participants. Subsequent research
+identified some limitations in EXAM's ability to account for cases where
+human participants learn and extrapolate sinusoidal function
+\textcite{bottNonmonotonicExtrapolationFunction2004} or to scenarios
+where different functions apply to different regions of the input space
+\textcite{kalishPopulationLinearExperts2004}, though EXAM has been shown
+to provide a good account of human learning and extrapolation in tasks
+with bi-linear, V shaped input spaces
+\textcite{mcdanielPredictingTransferPerformance2009}.
+
+\subsubsection{Variability and Function
+Learning}\label{variability-and-function-learning}
+
+The influence of variability on function learning tasks has received
+relatively little attention. The study by
+\textcite{deloshExtrapolationSineQua1997} (described in detail above)
+did include a variability manipulation (referred to as density in their
+paper), wherein participants were trained with either either 8, 20, or
+50 unique input-output pairs, with the total number of training trials
+held constant. They found a minimal influence of variability on training
+performance, and no difference between groups in interpolation or
+extrapolation, with all three variability conditions displaying accurate
+interpolation, and linearly biased extrapolation that was well accounted
+for by the EXAM model.
+
+In the domain of visuomotor learning,
+\textcite{vandamMappingShapeVisuomotor2015} employed a task which
+required participants to learn a linear function between the spikiness
+of shape stimuli and the correct horizontal position to make a rapid
+pointing response. The shapes ranged from very spiky to completely
+circular at the extreme ends of the space. Participants trained with
+intermediate shapes from a lower variation (2 shapes) or higher
+variation (5 shapes) condition, with the 2 items of the lower varied
+condition matching the items used on the extreme ends of the higher
+variation training space. Learning was significantly slower in the
+higher variation group. However, the two conditions did not differ when
+tested with novel shapes, with both groups producing extrapolation
+responses of comparable magnitudes to the most similar training item,
+rather than in accordance with the true linear function. The authors
+accounted for both learning and extrapolation performance with a
+Bayesian learning model. Similar to ALM, the bayesian model assumes that
+generalization occurs as a Gaussian function of the distance between
+stimuli. However unlike ALM, the bayesian learning model utilizes more
+elaborate probabilistic stimulus representations, with a separate Kalman
+Filter for each shape stimulus.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-delosh-extrap-1.pdf}
+
+}
+
+\caption{\label{fig-delosh-extrap}Generalization reproduced patterns
+from DeLosh et al.~(1997) Figure 3. Stimulii that fall within the dashed
+lines are interpolations of the training examples.}
+
+\end{figure}%
+
+\subsection{Overview Of Present Study}\label{overview-of-present-study}
+
+The present study investigates the influence of training variability on
+learning, generalization, and extrapolation in a uni-dimensional
+visuomotor function learning task. To the best of our knowledge, this
+research is the first to employ the classic constant vs.~varied training
+manipulation, commonly used in the literature on the benefits of
+variability, in the context of a uni-dimensional function learning task.
+Across three experiments, we compare constant and varied training
+conditions in terms of learning performance, extrapolation accuracy, and
+the ability to reliably discriminate between stimuli.
+
+To account for the empirical results, we will apply a series of
+computational models, including the Associative Learning Model (ALM) and
+the Extrapolation-Association Model (EXAM). Notably, this study is the
+first to employ approximate Bayesian computation (ABC) to fit these
+models to individual subject data, enabling us to thoroughly investigate
+the full range of posterior predictions of each model, and to examine
+the the ability of these influential models of function learning to
+account for both the group level and individual level data.
+
+\subsection{Methods}\label{methods-2}
+
+\emph{Participants} A total of 156 participants were recruited from the
+Indiana University Introductory Psychology Course. Participants were
+randomly assigned to one of two training conditions: varied training or
+constant training.
+
+\emph{Task.} The ``Hit The Wall'' (HTW) visuomotor extrapolation task
+task was programmed in Javascript, making heavy use of the
+\href{https://phaser.io/}{phaser.io} game library. The HTW task involved
+launching a projectile such that it would strike the ``wall'' at target
+speed indicated at the top of the screen (see
+Figure~\ref{fig-htw-task}). The target velocities were given as a range,
+or band, of acceptable velocity values (e.g.~band 800-1000). During the
+training stage, participants received feedback indicating whether they
+had hit the wall within the target velocity band, or how many units
+their throw was above or below from the target band. Participants were
+instructed that only the x velocity component of the ball was relevant
+to the task. The y velocity, or the location at which the ball struck
+the wall, had no influence on the task feedback.
 
 /
-```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
-#| label: fig-htw-task
-#| fig-cap: The Hit the wall task.
-Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
-The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
-#| eval: true
-#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
-knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
-
-```
-
-*Procedure.* All participants completed the task online.
-Participants were provided with a description of the experiment and indicated informed consent.
-@fig-design-e1 illustrates the general procedure.
-Participants completed a total of 90 trials during the training stage.
-In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
-
-Following the training stage, participants proceeded immediately to the testing stage.
-Participants were tested from all six velocity bands, in two separate stages.
-In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
-In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
-A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
-
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
-//| fig-responsive: false
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-```
-
-```{r}
-
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e1 <- readRDS(here("data/e1_08-21-23.rds")) 
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-testE1 <- e1 |> filter(expMode2 == "Test")
-nbins=5
-trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
-trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
-```
-
-### Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.32 @rcoreteamLanguageEnvironmentStatistical2020.
-To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
-Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
-Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
-For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
-
-| Group Comparison         | Code                                                        | Data                 |
-| ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
-\
-
-In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
-extrapolation bands); 3) extent of discrimination between all six testing bands.
-We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
-Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
-The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
-Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-### Results
-
-```{r}
-#| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-##| label: tbl-e1-train-dist
-##| tbl-cap: "Experiment 1 - Learning curves. "
-##| output: asis
-
-bmm_e1_train<- trainE1_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e1_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#    kable(booktabs = TRUE)
-
-cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
-```
-
-::: {#tbl-e1-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
-| conditVaried |    79.64 |         57.92 |        101.63 |   1 |
-
-: **Experiment 1 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band.
-To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on.
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
-
-```{r}
-##| label: tbl-e1-bmm-dist
-##| tbl-cap: "E1. Training vs. Extrapolation"
-#| 
-modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
-bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE1, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-# 
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-
-# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
-cdted1 <- get_coef_details(bmtd, "conditVaried")
-cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
-cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e1-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:------------------------|-----------:|-----------:|-----------:|-----------:|
-| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
-| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
-| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
-| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |
-
-: **Experiment 1 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficients  indicate larger deviations from the baselines (Condition=constant & bandType=Trained) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
-constant) and band type (trained vs.
-extrapolation), with random intercepts for participants and bands.
-The model results are shown in @tbl-e1-bmm-dist.
-The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`).
-The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`).
-Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% credible intervals.
-
-pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-
-```
-
-```{r}
-##| label: tbl-e1-bmm-vx
-##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)
-
-cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e1_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-```
-
-\
-
-::: {#tbl-e1-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
-| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
-| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
-| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |
-
-Experiment 1.
-Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
-Varied) and Velocity Band.
-Larger coefficients on Band represent greater sensitivity/discrimination.
-{.striped .hover .sm}
-:::
-
-Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
-Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
-This difference is depicted visually in @fig-e1-test-vx.
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: Empirical distribution of velocities producing in testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-
-testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
-#| fig-cap: Experiment 1.
-Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE1$vb), 
-                     limits = c(0, 1400)) + 
-  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e1_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e1Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-     theme(legend.title=element_blank(), 
-           axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-## E1 Summary
-
-In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions  rresulted in lower final training performance is consistent with much of the prior researchon the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
-
-More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.
-
-## Experiment 2
-
-```{r}
-
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e2 <- readRDS(here("data/e2_08-04-23.rds")) 
-e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
-testE2 <- e2 |> filter(expMode2 == "Test")
-nbins=5
-trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
-
-# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
-```
-
-### Methods & Procedure
-
-The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
-The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800.
-Both groups were tested from all six bands.
-A total of 110 participants completed the experiment (Varied: 55, Constant: 55).
-
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 8.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| 
-//| 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
-
-### Results
-
-```{r}
-#| label: fig-e2-train-dev
-#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-#| eval: TRUE
-p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-bmm_e2_train <- trainE2_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e2_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
-# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T) 
-```
-
-::: {#tbl-e2-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
-| conditVaried |    36.15 |         16.35 |         55.67 |   1 |
-
-: **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups.
-We again compared training performance on the band common to both groups (600-800).
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
-```{r}
-modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
-bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE2, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
-cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
-cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e2-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-----------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
-| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
-| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
-| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |
-
-: **Experiment 2 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-\ \
-
-*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
-Constant) and band type (training vs.
-extrapolation bands).
-The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`).
-However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-#| eval: TRUE
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e2-bmm-vx
-##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
-
-cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
-sc2 <- get_coef_details(e2_vxBMM, "bandInt")
-intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
-```
-
-::: {#tbl-e2-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
-| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
-| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
-| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
-
-Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-The full model results are shown in @tbl-e2-bmm-vx.
-The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
-The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).
-
-```{r}
-#| label: fig-e2-test-vx
-#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e2-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-}
-
-pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE2$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e2_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e2Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-      theme(legend.title=element_blank(), 
-        axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-### Experiment 2 Summary
-
-Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands.
-Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.
-
-## Experiment 3
-
-```{r}
-
-e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
-    mutate(trainCon=case_when(
-    bandOrder=="Original" ~ "800",
-    bandOrder=="Reverse" ~ "600",
-    TRUE ~ NA_character_
-    ), trainCon=as.numeric(trainCon)) 
-e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
-testE3 <- e3 |> filter(expMode2 == "Test")
-nbins=5
-trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
-
-```
-
-### Methods & Procedure
-
-The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
-After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.
-within the target velocity range).
-All other aspects of the task and design are identical to Experiments 1 and 2.
-We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied).
-Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
-Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.
-
-### Results
-
-```{r}
-
-bmm_e3_train <- trainE3_max %>% 
-  brm(dist ~ condit*bandOrder, 
-      file=here("data/model_cache/e3_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
-cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
-cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
-```
-
-::: {#tbl-e3-train-dist}
-
-| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
-| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
-| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
-| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |
-
-: **Experiment 3 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-*Training*.
-@fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions).
-The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`).
-The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).
-
-```{r}
-#| label: fig-e3-train-dev
-#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
-#| eval: true
-p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
-p1
-```
-
-```{r}
-#options(brms.backend="cmdstanr",mc.cores=4)
-modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
-bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
-    data=testE3, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
-#wrap_plots(ce_bmtd3)
-
-#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")
-
-cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
-cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
-cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
-cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
-cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
-cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
-cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")
-
-```
-
-::: {#tbl-e3-bmm-dist}
-| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
-| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
-| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
-| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
-| conditVaried:bandTypeExtrapolation                  |    52.66 |         14.16 |         90.23 | 1.00 |
-| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
-| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
-| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |
-
-: **Experiment 3 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
-There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
-However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`.
-The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group.
-There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands.
-No other interactions were significant.
-
-<!-- ::: {#fig-e3-test-condEffect}
-
-![](../Assets/figs/e3_cond_effects_dist.png)
-
-E3.
-A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-::: -->
-
-```{r}
-#| label: fig-e3-test-dev
-#| fig-cap: Experiment 3 Testing Accuracy.
-A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% confidence intervals.
-#| eval: true
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-    facet_wrap(~bandOrder,ncol=1) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
- facet_wrap(~bandOrder,ncol=1)
-
-p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e3-bmm-vx
-##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
-# m2 <- fixef(e3_vxBMM)
-# mp3 <- m1[, c(1,2,4,5,6)]
-# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
-# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
-coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")
-
-```
-
-::: {#tbl-e3-bmm-vx}
-
-| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
-| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
-| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
-| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |
-
-Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist.
-For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
-The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
-Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
-However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating that the varied condition showed a greater slope coefficient on the reverse order bands, compared to the constant condition - this is clearly shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 10
-##| column: screen-inset-right
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-```
-
-```{r}
-#| label: fig-e3-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 10
-#| fig-width: 11
-##| eval: FALSE
-# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  facet_wrap(~bandOrder,ncol=1) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e3_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
-fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
-fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
-
-re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e3Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
-           fixed_effect_interaction2*(bandOrder=="Reverse") + 
-           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
-  slope = Estimate + adjust )
-
-pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density") +
-  facet_wrap(~bandOrder,ncol=1)
-
-pid_slopes3 <- re |>  
-    mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-    theme(legend.title=element_blank(), 
-      axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
-
-p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
-
-#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
-p3
-
-```
-
-### Experiment 3 Summary
-
-## Computational Model
-
-```{r}
-####| cache: false
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-```
-
-```{r}
-###| cache: true
-invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
-invisible(list2env(load_e1(), envir = .GlobalEnv))
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-e2_model <- load_e2()
-e3_model <- load_e3()
-options(contrasts = initial_contrasts)
-
-```
-
-```{r}
-#| label: fig-alm-diagram
-#| fig.cap: The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model as used in the present work.
-Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
-The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
-The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule.
-alm_plot()
-```
-
-# Modeling Approach
-
-The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997].
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
-EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
-Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
-EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
-The slope is then used to extrapolate the response to the novel test stimulus.
-Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
-We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
-This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
-
-See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
-
-::: column-page-inset-right
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-|                    | **EXAM Extrapolation**                                             |                                                                                               |
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
-| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |
-
-: ALM & EXAM Equations {#tbl-alm-exam}
-:::
-
-## Model Fitting
-
-To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
-We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant.
-The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
-Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.
-
-::: {.callout}
-
-**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
-
-To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
-ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
-Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g.
-many neural network models).
-
-The general ABC procedure is to 1) define a prior distribution over model parameters.
-2) sample candidate parameter values, $\theta^*$, from the prior.
-3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
-4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
-5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
-6) Repeat until desired number of posterior samples are obtained.
-
-Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
-For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
-For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
-For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
-After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
-For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
-
-::: column-page-inset-left
-$$
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=0.6\textwidth,height=\textheight]{../Assets/figs/htw_task_fig.png}
+
+}
+
+\caption{\label{fig-htw-task}The Hit the wall task. Participants launch
+the blue ball to hit the red wall at the target velocity band indicated
+at the top of the screen. The ball must be released from within the
+orange square - but the location of release, and the location at which
+the ball strikes the wall are both irrelevant to the task feedback.}
+
+\end{figure}%
+
+\emph{Procedure.} All participants completed the task online.
+Participants were provided with a description of the experiment and
+indicated informed consent. Figure~\ref{fig-design-e1} illustrates the
+general procedure. Participants completed a total of 90 trials during
+the training stage. In the varied training condition, participants
+encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
+Participants in the constant training condition trained on only one
+velocity band (800-1000) - the closest band to what would be the novel
+extrapolation bands in the testing stage.
+
+Following the training stage, participants proceeded immediately to the
+testing stage. Participants were tested from all six velocity bands, in
+two separate stages. In the novel extrapolation testing stage,
+participants completed ``no-feedback'' testing from three novel
+extrapolation bands (100-300, 350-550, and 600-800), with each band
+consisting of 15 trials. Participants were also tested from the three
+velocity bands that were trained by the varied condition (800-1000,
+1000-1200, and 1200-1400). In the constant training condition, two of
+these bands were novel, while in the varied training condition, all
+three bands were encountered during training. The order in which
+participants completed the novel-extrapolation and testing-from-3-varied
+bands was counterbalanced across participants. A final training stage
+presented participants with ``feedback'' testing for each of the three
+extrapolation bands (100-300, 350-550, and 600-800).
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=7in,height=2.5in]{full_files/figure-latex/dot-figure-1.png}
+
+}
+
+\caption{\label{fig-design-e1}Experiment 1 Design. Constant and Varied
+participants complete different training conditions.}
+
+\end{figure}%
+
+\subsubsection{Analyses Strategy}\label{analyses-strategy}
+
+All data processing and statistical analyses were performed in R version
+4.32 \textcite{rcoreteamLanguageEnvironmentStatistical2020}. To assess
+differences between groups, we used Bayesian Mixed Effects Regression.
+Model fitting was performed with the brms package in R
+\textcite{burknerBrmsPackageBayesian2017}, and descriptive stats and
+tables were extracted with the BayestestR package
+\textcite{makowskiBayestestRDescribingEffects2019}. Mixed effects
+regression enables us to take advantage of partial pooling,
+simultaneously estimating parameters at the individual and group level.
+Our use of Bayesian, rather than frequentist methods allows us to
+directly quantify the uncertainty in our parameter estimates, as well as
+avoiding convergence issues common to the frequentist analogues of our
+mixed models.
+
+Each model was set to run with 4 chains, 5000 iterations per chain, with
+the first 2500 discarded as warmup chains. Rhat values were within an
+acceptable range, with values \textless=1.02 (see appendix for
+diagnostic plots). We used uninformative priors for the fixed effects of
+the model (condition and velocity band), and weakly informative Student
+T distributions for for the random effects. For each model, we report 1)
+the mean values of the posterior distribution for the parameters of
+interest, 2) the lower and upper credible intervals (CrI), and the
+probability of direction value (pd).
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2330}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.5728}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1942}}@{}}
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Group Comparison
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Code
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Data
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+End of Training Accuracy & \texttt{brm(dist\ \textasciitilde{}\ condit)}
+& Final Training Block \\
+Test Accuracy &
+\texttt{brm(dist\ \textasciitilde{}\ condit\ *\ bandType\ +\ (1\textbar{}id)\ +\ (1\textbar{}bandInt)}
+& All Testing trials \\
+Band Discrimination &
+\texttt{brm(vx\ \textasciitilde{}\ condit\ *\ band\ +(1\ +\ bandInt\textbar{}id)}
+& All Testing Trials \\
+\end{longtable}
+
+\hfill\break
+
+In each experiment we compare varied and constant conditions in terms of
+1) accuracy in the final training block; 2) testing accuracy as a
+function of band type (trained vs.~extrapolation bands); 3) extent of
+discrimination between all six testing bands. We quantified accuracy as
+the absolute deviation between the response velocity and the nearest
+boundary of the target band. Thus, when the target band was velocity
+600-800, throws of 400, 650, and 900 would result in deviation values of
+200, 0, and 100, respectively. The degree of discrimination between
+bands was index by fitting a linear model predicting the response
+velocity as a function of the target velocity. Participants who reliably
+discriminated between velocity bands tended to haves slope values
+\textasciitilde1, while participants who made throws irrespective of the
+current target band would have slopes \textasciitilde0.
+
+\subsubsection{Results}\label{results-2}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e1-train-dev-1.pdf}
+
+}
+
+\caption{\label{fig-e1-train-dev}Experiment 1 Training Stage. Deviations
+from target band across training blocks. Lower values represent greater
+accuracy.}
+
+\end{figure}%
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{\textbf{Experiment 1 - End of training performance}. The
+Intercept represents the average of the baseline (constant condition),
+and the conditVaried coefficient reflects the difference between the
+constant and varied groups. A larger positive estimates indicates a
+greater deviation (lower accuracy) for the varied
+group.}\label{tbl-e1-train-dist}\tabularnewline
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 106.34 & 95.46 & 117.25 & 1 \\
+conditVaried & 79.64 & 57.92 & 101.63 & 1 \\
+\end{longtable}
+
+\hfill\break
+
+\emph{Training}. Figure~\ref{fig-e1-train-dev} displays the average
+deviations across training blocks for the varied group, which trained on
+three velocity bands, and the constant group, which trained on one
+velocity band. To compare the training conditions at the end of
+training, we analyzed performance on the 800-1000 velocity band, which
+both groups trained on. The full model results are shown in Table 1. The
+varied group had a significantly greater deviation than the constant
+group in the final training block, (\(\beta\) = 79.64, 95\% CrI
+{[}57.92, 101.63{]}; pd = 100\%).
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3425}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}@{}}
+\caption{\textbf{Experiment 1 testing accuracy}. Main effects of
+condition and band type (training vs.~extrapolation), and the
+interaction between the two factors. Larger coefficients indicate larger
+deviations from the baselines (Condition=constant \& bandType=Trained) -
+and a positive interaction coefficient indicates disproporionate
+deviation for the varied condition on the extrapolation
+bands}\label{tbl-e1-bmm-dist}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 152.55 & 70.63 & 229.85 & 1.0 \\
+conditVaried & 39.00 & -21.10 & 100.81 & 0.9 \\
+bandTypeExtrapolation & 71.51 & 33.24 & 109.60 & 1.0 \\
+conditVaried:bandTypeExtrapolation & 66.46 & 32.76 & 99.36 & 1.0 \\
+\end{longtable}
+
+\emph{Testing.} To compare accuracy between groups in the testing stage,
+we fit a Bayesian mixed effects model predicting deviation from the
+target band as a function of training condition (varied vs.~constant)
+and band type (trained vs.~extrapolation), with random intercepts for
+participants and bands. The model results are shown in
+Table~\ref{tbl-e1-bmm-dist}. The main effect of training condition was
+not significant (\(\beta\) = 39, 95\% CrI {[}-21.1, 100.81{]}; pd =
+89.93\%). The extrapolation testing items had a significantly greater
+deviation than the training bands (\(\beta\) = 71.51, 95\% CrI {[}33.24,
+109.6{]}; pd = 99.99\%). Most importantly, the interaction between
+training condition and band type was significant (\(\beta\) = 66.46,
+95\% CrI {[}32.76, 99.36{]}; pd = 99.99\%), As shown in
+Figure~\ref{fig-e1-test-dev}, the varied group had disproportionately
+larger deviations compared to the constant group in the extrapolation
+bands.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e1-test-dev-1.pdf}
+
+}
+
+\caption{\label{fig-e1-test-dev}A) Deviations from target band during
+testing without feedback stage. B) Conditional effect of condition
+(Constant vs.~Varied) and testing band type (training vs.~extrapolation)
+on testing accuracy. Error bars represent 95\% credible intervals.}
+
+\end{figure}%
+
+\hfill\break
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{Experiment 1. Bayesian Mixed Model Predicting velocity as a
+function of condition (Constant vs.~Varied) and Velocity Band. Larger
+coefficients on Band represent greater
+sensitivity/discrimination.}\label{tbl-e1-bmm-vx}\tabularnewline
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 408.55 & 327.00 & 490.61 & 1.00 \\
+conditVaried & 164.05 & 45.50 & 278.85 & 1.00 \\
+Band & 0.71 & 0.62 & 0.80 & 1.00 \\
+condit*Band & -0.14 & -0.26 & -0.01 & 0.98 \\
+\end{longtable}
+
+Finally, to assess the ability of both conditions to discriminate
+between velocity bands, we fit a model predicting velocity as a function
+of training condition and velocity band, with random intercepts and
+random slopes for each participant. See Table~\ref{tbl-e1-bmm-vx} for
+the full model results. The estimated coefficient for training condition
+(\(\beta\) = 164.05, 95\% CrI {[}45.5, 278.85{]}, pd = 99.61\%) suggests
+that the varied group tends to produce harder throws than the constant
+group, but is not in and of itself useful for assessing discrimination.
+Most relevant to the issue of discrimination is the coefficient on the
+Band predictor (\(\beta\) = 0.71 95\% CrI {[}0.62, 0.8{]}, pd = 100\%).
+Although the median slope does fall underneath the ideal of value of 1,
+the fact that the 95\% credible interval does not contain 0 provides
+strong evidence that participants exhibited some discrimination between
+bands. The estimate for the interaction between slope and condition
+(\(\beta\) = -0.14, 95\% CrI {[}-0.26, -0.01{]}, pd = 98.39\%), suggests
+that the discrimination was somewhat modulated by training condition,
+with the varied participants showing less sensitivity between bands than
+the constant condition. This difference is depicted visually in
+Figure~\ref{fig-e1-test-vx}.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e1-test-vx-1.pdf}
+
+}
+
+\caption{\label{fig-e1-test-vx}Empirical distribution of velocities
+producing in testing stage. Translucent bands with dash lines indicate
+the correct range for each velocity band.}
+
+\end{figure}%
+
+\begin{table}
+
+\caption{\label{tbl-e1-bmm-vx}}
+
+\centering{
+
+\captionsetup{labelsep=none}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{full_files/figure-pdf/tbl-e1-bmm-vx-1.pdf}
+
+}
+
+\subcaption{Experiment 1. Conditional effect of training condition and
+Band. Ribbons indicate 95\% HDI. The steepness of the lines serves as an
+indicator of how well participants discriminated between velocity
+bands.}
+
+\end{figure}%
+
+}
+
+\end{table}%
+
+\subsection{E1 Summary}\label{e1-summary}
+
+In Experiment 1, we investigated how variability in training influenced
+participants' ability learn and extrapolate in a visuomotor task. Our
+findings that training with variable conditions rresulted in lower final
+training performance is consistent with much of the prior researchon the
+influence of training variability
+\autocite{ravivHowVariabilityShapes2022,soderstromLearningPerformanceIntegrative2015},
+and is particularly unsurprising in the present work, given that the
+constant group received three times the amount of training on the
+velocity band common to the two conditions.
+
+More importantly, the varied training group exhibited significantly
+larger deviations from the target velocity bands during the testing
+phase, particularly for the extrapolation bands that were not
+encountered by either condition during training.
+
+\subsection{Experiment 2}\label{experiment-2-1}
+
+\subsubsection{Methods \& Procedure}\label{methods-procedure}
+
+The task and procedure of Experiment 2 was identical to Experiment 1,
+with the exception that the training and testing bands were reversed
+(see Figure~\ref{fig-design-e2}). The Varied group trained on bands
+100-300, 350-550, 600-800, and the constant group trained on band
+600-800. Both groups were tested from all six bands. A total of 110
+participants completed the experiment (Varied: 55, Constant: 55).
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=8in,height=2.5in]{full_files/figure-latex/dot-figure-2.png}
+
+}
+
+\caption{\label{fig-design-e2}Experiment 2 Design. Constant and Varied
+participants complete different training conditions. The training and
+testing bands are the reverse of Experiment 1.}
+
+\end{figure}%
+
+\subsubsection{Results}\label{results-3}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2-train-dev-1.pdf}
+
+}
+
+\caption{\label{fig-e2-train-dev}Experiment 2 Training Stage. Deviations
+from target band across training blocks. Lower values represent greater
+accuracy.}
+
+\end{figure}%
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{\textbf{Experiment 2 - End of training performance}. The
+Intercept represents the average of the baseline (constant condition),
+and the conditVaried coefficient reflects the difference between the
+constant and varied groups. A larger positive coefficient indicates a
+greater deviation (lower accuracy) for the varied
+group.}\label{tbl-e2-train-dist}\tabularnewline
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 91.01 & 80.67 & 101.26 & 1 \\
+conditVaried & 36.15 & 16.35 & 55.67 & 1 \\
+\end{longtable}
+
+\hfill\break
+
+\emph{Training}. Figure~\ref{fig-e2-train-dev} presents the deviations
+across training blocks for both constant and varied training groups. We
+again compared training performance on the band common to both groups
+(600-800). The full model results are shown in Table 1. The varied group
+had a significantly greater deviation than the constant group in the
+final training block, ( \(\beta\) = 36.15, 95\% CrI {[}16.35, 55.67{]};
+pd = 99.95\%).
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.4390}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1220}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1829}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1829}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0732}}@{}}
+\caption{\textbf{Experiment 2 testing accuracy}. Main effects of
+condition and band type (training vs.~extrapolation), and the
+interaction between the two factors. Larger coefficient estimates
+indicate larger deviations from the baselines (constant \& trained
+bands) - and a positive interaction coefficient indicates
+disproporionate deviation for the varied condition on the extrapolation
+bands}\label{tbl-e2-bmm-dist}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 190.91 & 125.03 & 259.31 & 1.00 \\
+conditVaried & -20.58 & -72.94 & 33.08 & 0.78 \\
+bandTypeExtrapolation & 38.09 & -6.94 & 83.63 & 0.95 \\
+conditVaried:bandTypeExtrapolation & 82.00 & 41.89 & 121.31 & 1.00 \\
+\end{longtable}
+
+~\\
+
+\emph{Testing Accuracy.} The analysis of testing accuracy examined
+deviations from the target band as influenced by training condition
+(Varied vs.~Constant) and band type (training vs.~extrapolation bands).
+The results, summarized in Table~\ref{tbl-e2-bmm-dist}, reveal no
+significant main effect of training condition (\(\beta\) = -20.58, 95\%
+CrI {[}-72.94, 33.08{]}; pd = 77.81\%). However, the interaction between
+training condition and band type was significant (\(\beta\) = 82, 95\%
+CrI {[}41.89, 121.31{]}; pd = 100\%), with the varied group showing
+disproportionately larger deviations compared to the constant group on
+the extrapolation bands (see Figure~\ref{fig-e2-test-dev}).
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2-test-dev-1.pdf}
+
+}
+
+\caption{\label{fig-e2-test-dev}A) Deviations from target band during
+testing without feedback stage. B) Estimated marginal means for the
+interaction between training condition and band type. Error bars
+represent 95\% confidence intervals.}
+
+\end{figure}%
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{Experiment 2. Bayesian Mixed Model Predicting Vx as a function
+of condition (Constant vs.~Varied) and Velocity
+Band}\label{tbl-e2-bmm-vx}\tabularnewline
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 362.64 & 274.85 & 450.02 & 1.00 \\
+conditVaried & -8.56 & -133.97 & 113.98 & 0.55 \\
+Band & 0.71 & 0.58 & 0.84 & 1.00 \\
+condit*Band & -0.06 & -0.24 & 0.13 & 0.73 \\
+\end{longtable}
+
+\emph{Testing Discrimination.} Finally, to assess the ability of both
+conditions to discriminate between velocity bands, we fit a model
+predicting velocity as a function of training condition and velocity
+band, with random intercepts and random slopes for each participant. The
+full model results are shown in Table~\ref{tbl-e2-bmm-vx}. The overall
+slope on target velocity band predictor was significantly positive,
+(\(\beta\) = 0.71, 95\% CrI {[}0.58, 0.84{]}; pd= 100\%), indicating
+that participants exhibited discrimination between bands. The
+interaction between slope and condition was not significant, (\(\beta\)
+= -0.06, 95\% CrI {[}-0.24, 0.13{]}; pd= 72.67\%), suggesting that the
+two conditions did not differ in their ability to discriminate between
+bands (see Figure~\ref{fig-e2-test-vx}).
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2-test-vx-1.pdf}
+
+}
+
+\caption{\label{fig-e2-test-vx}E2 testing x velocities. Translucent
+bands with dash lines indicate the correct range for each velocity
+band.}
+
+\end{figure}%
+
+\begin{table}
+
+\caption{\label{tbl-e2-bmm-vx}}
+
+\centering{
+
+\captionsetup{labelsep=none}
+
+\begin{figure}[H]
+
+{\centering \includegraphics{full_files/figure-pdf/tbl-e2-bmm-vx-1.pdf}
+
+}
+
+\subcaption{Conditional effect of training condition and Band. Ribbons
+indicate 95\% HDI. The steepness of the lines serves as an indicator of
+how well participants discriminated between velocity bands.}
+
+\end{figure}%
+
+}
+
+\end{table}%
+
+\subsubsection{Experiment 2 Summary}\label{experiment-2-summary}
+
+Experiment 2 extended the findings of Experiment 1 by examining the
+effects of training variability on extrapolation performance in a
+visuomotor function learning task, but with reversed training and
+testing bands. Similar to Experiment 1, the Varied group exhibited
+poorer performance during training and testing. However unlike
+experiment 1, the Varied group did not show a significant difference in
+discrimination between bands.
+
+\subsection{Experiment 3}\label{experiment-3}
+
+\subsubsection{Methods \& Procedure}\label{methods-procedure-1}
+
+The major adjustment of Experiment 3 is for participants to receive
+ordinal feedback during training, in contrast to the continuous feedback
+of the prior experiments. After each training throw, participants are
+informed whether a throw was too soft, too hard, or correct (i.e.~within
+the target velocity range). All other aspects of the task and design are
+identical to Experiments 1 and 2. We utilized the order of training and
+testing bands from both of the prior experiments, thus assigning
+participants to both an order condition (Original or Reverse) and a
+training condition (Constant or Varied). Participants were once again
+recruited from the online Indiana University Introductory Psychology
+Course pool. Following exclusions, 195 participants were included in the
+final analysis, n=51 in the Constant-Original condition, n=59 in the
+Constant-Reverse condition, n=39 in the Varied-Original condition, and
+n=46 in the Varied-Reverse condition.
+
+\subsubsection{Results}\label{results-4}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.4026}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1299}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1948}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1948}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0779}}@{}}
+\caption{\textbf{Experiment 3 - End of training performance}. The
+Intercept represents the average of the baseline (constant condition),
+and the conditVaried coefficient reflects the difference between the
+constant and varied groups. A larger positive coefficient indicates a
+greater deviation (lower accuracy) for the varied
+group.}\label{tbl-e3-train-dist}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 121.86 & 109.24 & 134.60 & 1.00 \\
+conditVaried & 64.93 & 36.99 & 90.80 & 1.00 \\
+bandOrderReverse & 1.11 & -16.02 & 18.16 & 0.55 \\
+conditVaried:bandOrderReverse & -77.02 & -114.16 & -39.61 & 1.00 \\
+\end{longtable}
+
+\emph{Training}. Figure~\ref{fig-e3-train-dev} displays the average
+deviations from the target band across training blocks, and
+Table~\ref{tbl-e3-train-dist} shows the results of the Bayesian
+regression model predicting the deviation from the common band at the
+end of training (600-800 for reversed order, and 800-1000 for original
+order conditions). The main effect of training condition is significant,
+with the varied condition showing larger deviations ( \(\beta\) = 64.93,
+95\% CrI {[}36.99, 90.8{]}; pd = 100\%). The main effect of band order
+is not significant \(\beta\) = 1.11, 95\% CrI {[}-16.02, 18.16{]}; pd =
+55.4\%, however the interaction between training condition and band
+order is significant, with the varied condition showing greater accuracy
+in the reverse order condition ( \(\beta\) = -77.02, 95\% CrI
+{[}-114.16, -39.61{]}; pd = 100\%).
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e3-train-dev-1.pdf}
+
+}
+
+\caption{\label{fig-e3-train-dev}E3. Deviations from target band during
+testing without feedback stage.}
+
+\end{figure}%
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.5354}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1010}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1515}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1515}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0606}}@{}}
+\caption{\textbf{Experiment 3 testing accuracy}. Main effects of
+condition and band type (training vs.~extrapolation), and the
+interaction between the two factors. Larger coefficient estimates
+indicate larger deviations from the baselines (constant training;
+trained bands \& original order) - and a positive interaction
+coefficient indicates disproportionate deviation for the varied
+condition on the extrapolation
+bands}\label{tbl-e3-bmm-dist}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 288.65 & 199.45 & 374.07 & 1.00 \\
+conditVaried & -40.19 & -104.68 & 23.13 & 0.89 \\
+bandTypeExtrapolation & -23.35 & -57.28 & 10.35 & 0.92 \\
+bandOrderReverse & -73.72 & -136.69 & -11.07 & 0.99 \\
+conditVaried:bandTypeExtrapolation & 52.66 & 14.16 & 90.23 & 1.00 \\
+conditVaried:bandOrderReverse & -37.48 & -123.28 & 49.37 & 0.80 \\
+bandTypeExtrapolation:bandOrderReverse & 80.69 & 30.01 & 130.93 &
+1.00 \\
+conditVaried:bandTypeExtrapolation:bandOrderReverse & 30.42 & -21.00 &
+81.65 & 0.87 \\
+\end{longtable}
+
+\emph{Testing Accuracy.} Table~\ref{tbl-e3-bmm-dist} presents the
+results of the Bayesian mixed efects model predicting absolute deviation
+from the target band during the testing stage. There was no significant
+main effect of training condition,\(\beta\) = -40.19, 95\% CrI
+{[}-104.68, 23.13{]}; pd = 89.31\%, or band type,\(\beta\) = -23.35,
+95\% CrI {[}-57.28, 10.35{]}; pd = 91.52\%. However the effect of band
+order was significant, with the reverse order condition showing lower
+deviations, \(\beta\) = -73.72, 95\% CrI {[}-136.69, -11.07{]}; pd =
+98.89\%. The interaction between training condition and band type was
+also significant \(\beta\) = 52.66, 95\% CrI {[}14.16, 90.23{]}; pd =
+99.59\%, with the varied condition showing disproprionately large
+deviations on the extrapolation bands compared to the constant group.
+There was also a significant interaction between band type and band
+order, \(\beta\) = 80.69, 95\% CrI {[}30.01, 130.93{]}; pd = 99.89\%,
+such that the reverse order condition showed larger deviations on the
+extrapolation bands. No other interactions were significant.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e3-test-dev-1.pdf}
+
+}
+
+\caption{\label{fig-e3-test-dev}Experiment 3 Testing Accuracy. A)
+Deviations from target band during testing without feedback stage. B)
+Conditional effect of condition (Constant vs.~Varied) and testing band
+type (training vs.~extrapolation) on testing accuracy. Error bars
+represent 95\% confidence intervals.}
+
+\end{figure}%
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.4713}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1149}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1724}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1724}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0690}}@{}}
+\caption{Experiment 3. Bayesian Mixed Model Predicting Vx as a function
+of condition (Constant vs.~Varied) and Velocity
+Band}\label{tbl-e3-bmm-vx}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+Term
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+Estimate
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Lower
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+95\% CrI Upper
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+pd
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Intercept & 601.83 & 504.75 & 699.42 & 1.00 \\
+conditVaried & 12.18 & -134.94 & 162.78 & 0.56 \\
+bandOrderReverse & 13.03 & -123.89 & 144.67 & 0.58 \\
+Band & 0.49 & 0.36 & 0.62 & 1.00 \\
+conditVaried:bandOrderReverse & -338.15 & -541.44 & -132.58 & 1.00 \\
+conditVaried:Band & -0.04 & -0.23 & 0.15 & 0.67 \\
+bandOrderReverse:bandInt & -0.10 & -0.27 & 0.08 & 0.86 \\
+conditVaried:bandOrderReverse:bandInt & 0.42 & 0.17 & 0.70 & 1.00 \\
+\end{longtable}
+
+\emph{Testing Discrimination.} The full results of the discrimination
+model are presented in Table~\ref{tbl-e3-bmm-dist}. For the purposes of
+assessing group differences in discrimination, only the coefficients
+including the band variable are of interest. The baseline effect of band
+represents the slope cofficient for the constant training - original
+order condition, this effect was significant \(\beta\) = 0.49, 95\% CrI
+{[}0.36, 0.62{]}; pd = 100\%. Neither of the two way interactions
+reached significance, \(\beta\) = -0.04, 95\% CrI {[}-0.23, 0.15{]}; pd
+= 66.63\%, \(\beta\) = -0.1, 95\% CrI {[}-0.27, 0.08{]}; pd = 86.35\%.
+However, the three way interaction between training condition, band
+order, and target band was significant, \(\beta\) = 0.42, 95\% CrI
+{[}0.17, 0.7{]}; pd = 99.96\% - indicating that the varied condition
+showed a greater slope coefficient on the reverse order bands, compared
+to the constant condition - this is clearly shown in
+Figure~\ref{fig-e3-test-vx}, where the steepness of the best fitting
+line for the varied-reversed condition is noticably steeper than the
+other conditions.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e3-test-vx-1.pdf}
+
+}
+
+\caption{\label{fig-e3-test-vx}e3 testing x velocities. Translucent
+bands with dash lines indicate the correct range for each velocity
+band.}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e3-bmm-vx-1.pdf}
+
+}
+
+\caption{\label{fig-e3-bmm-vx}Conditional effect of training condition
+and Band. Ribbons indicate 95\% HDI. The steepness of the lines serves
+as an indicator of how well participants discriminated between velocity
+bands.}
+
+\end{figure}%
+
+\subsubsection{Experiment 3 Summary}\label{experiment-3-summary}
+
+\subsection{Computational Model}\label{computational-model-1}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-alm-diagram-1.pdf}
+
+}
+
+\caption{\label{fig-alm-diagram}The Associative Learning Model (ALM).
+The diagram illustrates the basic structure of the ALM model as used in
+the present work. Input nodes are activated as a function of their
+similarity to the lower-boundary of the target band. The generalization
+parameter, \(c\), determines the degree to which nearby input nodes are
+activated. The output nodes are activated as a function of the weighted
+sum of the input nodes - weights are updated via the delta rule.}
+
+\end{figure}%
+
+\section{Modeling Approach}\label{modeling-approach}
+
+The modeling goal is to implement a full process model capable of both
+1) producing novel responses and 2) modeling behavior in both the
+learning and testing stages of the experiment. For this purpose, we will
+apply the associative learning model (ALM) and the EXAM model of
+function learning \autocite{deloshExtrapolationSineQua1997}. ALM is a
+simple connectionist learning model which closely resembles Kruschke's
+ALCOVE model \autocite{kruschkeALCOVEExemplarbasedConnectionist1992},
+with modifications to allow for the generation of continuous responses.
+
+\subsection{ALM \& Exam Description}\label{alm-exam-description}
+
+ALM is a localist neural network model
+\autocite{pageConnectionistModellingPsychology2000a}, with each input
+node corresponding to a particular stimulus, and each output node
+corresponding to a particular response value. The units in the input
+layer activate as a function of their Gaussian similarity to the input
+stimulus. So, for example, an input stimulus of value 55 would induce
+maximal activation of the input unit tuned to 55. Depending on the value
+of the generalization parameter, the nearby units (e.g.~54 and 56; 53
+and 57) may also activate to some degree. ALM is structured with input
+and output nodes that correspond to regions of the stimulus space, and
+response space, respectively. The units in the input layer activate as a
+function of their similarity to a presented stimulus. As was the case
+with the exemplar-based models, similarity in ALM is exponentially
+decaying function of distance. The input layer is fully connected to the
+output layer, and the activation for any particular output node is
+simply the weighted sum of the connection weights between that node and
+the input activations. The network then produces a response by taking
+the weighted average of the output units (recall that each output unit
+has a value corresponding to a particular response). During training,
+the network receives feedback which activates each output unit as a
+function of its distance from the ideal level of activation necessary to
+produce the correct response. The connection weights between input and
+output units are then updated via the standard delta learning rule,
+where the magnitude of weight changes are controlled by a learning rate
+parameter. The EXAM model is an extension of ALM, with the same learning
+rule and representational scheme for input and output units. EXAM
+differs from ALM only in its response rule, as it includes a linear
+extrapolation mechanism for generating novel responses. Although this
+extrapolation rule departs from a strictly similarity-based
+generalization mechanism, EXAM is distinct from pure rule-based models
+in that it remains constrained by the weights learned during training.
+EXAM retrieves the two nearest training inputs, and the ALM responses
+associated with those inputs, and computes the slope between these two
+points. The slope is then used to extrapolate the response to the novel
+test stimulus. Because EXAM requires at least two input-output pairs to
+generate a response, additional assumptions were required in order for
+it to generate resposnes for the constant group. We assumed that
+participants come to the task with prior knowledge of the origin point
+(0,0), which can serve as a reference point necessary for the model to
+generate responses for the constant group. This assumption is motivated
+by previous function learning research
+(\textcite{brownUnderestimationLinearFunction2017}), which through a
+series of manipulations of the y intercept of the underlying function,
+found that participants consistently demonstrated knowledge of, or a
+bias towards, the origin point (see
+\textcite{kwantesWhyPeopleUnderestimate2006} for additional evidence of
+such a bias in function learning tasks).
+
+See Table~\ref{tbl-alm-exam} for a full specification of the equations
+that define ALM and EXAM, and Figure~\ref{fig-alm-diagram} for a visual
+representation of the ALM model.
+
+\begin{figure*}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4028}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3472}}@{}}
+\caption{ALM \& EXAM Equations}\label{tbl-alm-exam}\tabularnewline
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{ALM Response Generation}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{ALM Response Generation}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Input Activation &
+\(a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}\) &
+Input nodes activate as a function of Gaussian similarity to stimulus \\
+Output Activation & \(O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)\) &
+Output unit \(O_j\) activation is the weighted sum of input activations
+and association weights \\
+Output Probability & \(P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}\) &
+The response, \(Y_j\) probabilites computed via Luce's choice rule \\
+Mean Output &
+\(m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}\) &
+Weighted average of probabilities determines response to X \\
+& \textbf{ALM Learning} & \\
+Feedback & \(f_j(Z) = e^{-c(Z-Y_j)^2}\) & feedback signal Z computed as
+similarity between ideal response and observed response \\
+magnitude of error & \(\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)\) & Delta
+rule to update weights. \\
+Update Weights & \(w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}\) & Updates
+scaled by learning rate parameter \(\eta\). \\
+& \textbf{EXAM Extrapolation} & \\
+Instance Retrieval & \(P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}\) &
+Novel test stimulus \(X\) activates input nodes \(X_i\) \\
+Slope Computation & \(S =\) \(\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}\) &
+Slope value, \(S\) computed from nearest training instances \\
+Response & \(E[Y|X_i] = m(X_i) + S \cdot [X - X_i]\) & ALM response
+\(m(X_i)\) adjusted by slope. \\
+\end{longtable}
+
+\end{figure*}%
+
+\subsection{Model Fitting}\label{model-fitting}
+
+To fit ALM and EXAM to our participant data, we employ a similar method
+to \textcite{mcdanielPredictingTransferPerformance2009}, wherein we
+examine the performance of each model after being fit to various subsets
+of the data. Each model was fit to the data in with separate procedures:
+1) fit to maximize predictions of the testing data, 2) fit to maximize
+predictions of both the training and testing data, 3) fit to maximize
+predictions of the just the training data. We refer to this fitting
+manipulations as ``Fit Method'' in the tables and figures below. It
+should be emphasized that for all three fit methods, the ALM and EXAM
+models behave identically - with weights updating only during the
+training phase.Models to were fit separately to the data of each
+individual participant. The free parameters for both models are the
+generalization (\(c\)) and learning rate (\(lr\)) parameters. Parameter
+estimation was performed using approximate bayesian computation (ABC),
+which we describe in detail below.
+
+\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, leftrule=.75mm, colframe=quarto-callout-color-frame, colback=white, left=2mm, breakable, bottomrule=.15mm, arc=.35mm, opacityback=0, rightrule=.15mm]
+
+\textbf{\faIcon{lightbulb} Approximate Bayesian Computation}
+
+To estimate the parameters of ALM and EXAM, we used approximate bayesian
+computation (ABC), enabling us to obtain an estimate of the posterior
+distribution of the generalization and learning rate parameters for each
+individual. ABC belongs to the class of simulation-based inference
+methods \autocite{cranmerFrontierSimulationbasedInference2020}, which
+have begun being used for parameter estimation in cognitive modeling
+relatively recently
+\autocite{turnerTutorialApproximateBayesian2012,turnerBayesianAnalysisSimulationbased2016,kangasraasioParameterInferenceComputational2019}.
+Although they can be applied to any model from which data can be
+simulated, ABC methods are most useful for complex models that lack an
+explicit likelihood function (e.g.~many neural network models).
+
+The general ABC procedure is to 1) define a prior distribution over
+model parameters. 2) sample candidate parameter values, \(\theta^*\),
+from the prior. 3) Use \(\theta^*\) to generate a simulated dataset,
+\(Data_{sim}\). 4) Compute a measure of discrepancy between the
+simulated and observed datasets, \(discrep\)(\(Data_{sim}\),
+\(Data_{obs}\)). 5) Accept \(\theta^*\) if the discrepancy is less than
+the tolerance threshold, \(\epsilon\), otherwise reject \(\theta^*\). 6)
+Repeat until desired number of posterior samples are obtained.
+
+Although simple in the abstract, implementations of ABC require
+researchers to make a number of non-trivial decisions as to i) the
+discrepancy function between observed and simulated data, ii) whether to
+compute the discrepancy between trial level data, or a summary statistic
+of the datasets, iii) the value of the minimum tolerance \(\epsilon\)
+between simulated and observed data. For the present work, we follow the
+guidelines from previously published ABC tutorials
+\autocite{turnerTutorialApproximateBayesian2012,farrellComputationalModelingCognition2018}.
+For the test stage, we summarized datasets with mean velocity of each
+band in the observed dataset as \(V_{obs}^{(k)}\) and in the simulated
+dataset as \(V_{sim}^{(k)}\), where \(k\) represents each of the six
+velocity bands. For computing the discrepancy between datasets in the
+training stage, we aggregated training trials into three equally sized
+blocks (separately for each velocity band in the case of the varied
+group). After obtaining the summary statistics of the simulated and
+observed datasets, the discrepancy was computed as the mean of the
+absolute difference between simulated and observed datasets
+(Equation~\ref{eq-discrep-test} and Equation~\ref{eq-discrep-train}).
+For the models fit to both training and testing data, discrepancies were
+computed for both stages, and then averaged together.
+
+\begin{equation}\phantomsection\label{eq-discrep-test}{
 discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
-$$ {#eq-discrep-test}
-
-$$
+}\end{equation}
+
+\begin{equation}\phantomsection\label{eq-discrep-train}{
 \begin{aligned} \\
@@
 \end{aligned}
-$$ {#eq-discrep-train}
-:::
-
-The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
-The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
-Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
-Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
-The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
-Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
-After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
-In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
-To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
-:::
-
-For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution.
-Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant.
-Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs.
-To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.
-
-### Modelling Results
-
-#### Group level Patterns
-
-```{r}
-#| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-post_tabs <- abc_tables(post_dat,post_dat_l)
-train_tab <- abc_train_tables(pd_train,pd_train_l)
-
-e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
-
-e1_tab %>%
-  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
-  summarize(ME = mean(mean_error), .groups = "drop") %>%
-  pivot_wider(
-    names_from = c(Model, condit),
-    values_from = ME,
-    names_sep = "_"  # Add this line to specify the separator for column names
-  ) %>%
-  rename("Fit Method" = Fit_Method) %>%
-  gt() %>%
-  cols_move_to_start(columns = c(`Task Stage`)) %>%
-  cols_label(
-    `Task Stage` = "Task Stage"
-  ) %>%
-  fmt_number(
-    columns = starts_with("ALM") | starts_with("EXAM"),
-    decimals = 2
-  ) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = cell_fill(color = "white"),
-     locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_style(
-    style = cell_borders(sides = "top", color = "black", weight = px(1)),
-    locations = cells_column_labels()
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10, 
-    quarto.disable_processing = TRUE
-  ) 
-```
-
-```{r}
-#| label: fig-htw-post-dist
-#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters.
-Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y axes of the plots for the c parameter are scaled logarithmically."
-#| fig-height: 6
-#| fig-width: 10
-
-c_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
-  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
-
-lr_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
-  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
-c_post + lr_post
-```
-
-```{r}
-#| label: fig-htw-resid-pred
-#| fig-cap: "Model residuals for each combination of training condition, fit method, and model.
-Residuals reflect the difference between observed and predicted values.
-Lower values indicate better model fit.
-Note that y axes are scaled differently between facets.
-A) Residuals predicting each block of the training data.
-B) Residuals predicting each band during the testing stage.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-#| fig-height: 14
-#| fig-width: 11
-
-train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
-  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
-  group_by(id,condit,Model,Fit_Method,Block) |>
-  summarise(mean_error=mean(mean_error)) |>
-  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
-  stat_bar + 
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
-   scale_x_discrete(guide = "axis_nested") +
-  scale_fill_manual(values=c("gray10","gray50","gray92"))+
-  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
-  theme(legend.position="top")
-
-test_resid <-  post_dat |> 
-   group_by(id,condit,x,Model,Fit_Method,bandType) |>
-    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
-  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
-  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
-  scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
-  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")
-
-(train_resid / test_resid) +
-  #plot_layout(heights=c(1,1.5)) & 
-  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
-```
-
-The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat.
-There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences.
-The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
-
-We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model.
-Aggregated residuals are displayed in @fig-htw-resid-pred.
-The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method .
-Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms).
-The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models.
-It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task.
-Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories.
-However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data.
-All subsequent analyses and discussion will thus focus on the testing stage.
-
-The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots).
-Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
-The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models.
-Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.
-
-```{r}
-#| label: fig-cm-vx-pat
-#| fig-cap: "Empirical data and Model predictions for mean velocity across target bands.
-Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs.
-Varied) are separated by columns.
-Each facet contains the predictions of ALM and EXAM, alongside the observed data."
-#| fig-height: 10
-#| fig-width: 10
-
-post_dat_l |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> 
- #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
- ggplot(aes(x=Resp,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-    facet_wrap(~rename_fm(Fit_Method)+condit, ncol=2,strip.position = "top", scales = "free_x") +
-        scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-         strip.background = element_blank(),
-         strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(10,0,0,0), "pt")) + 
-         labs(title="Model Predictions - Experiment 1 Data", y="Vx")
-```
-
-```{r}
-#| label: fig-ee-e1
-#| fig-caption: conditional and marginal effects
-#| fig-height: 8
-#| fig-width: 10
-###| eval: false
-
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
-  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
-e1_ee_brm_ae <- brm(data=pdl,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-
-# plot_custom_effects <- function(model) {
-#   # Extract posterior samples for fixed effects
-#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
-
-#   # Calculate conditional effects
-#   post_samples <- post_samples %>%
-#     mutate(
-#       ALM_Constant = b_Intercept,
-#       EXAM_Constant = b_Intercept + b_ModelEXAM,
-#       ALM_Varied = b_Intercept + b_conditVaried,
-#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
-#     )
-
-#   # Reshape data for plotting
-#   plot_data <- post_samples %>%
-#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
-#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
-#     separate(Condition, into = c("Model", "Condit"), sep = "_")
-
-#   # Plot conditional effects
-#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
-#     geom_boxplot() +
-#     theme_minimal() +
-#     labs(x = "Model", y = "Estimate", color = "Condition")
-# }
-# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
-
-bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
-bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
-bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")
-
-posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
-  select(starts_with("b_")) %>%
-  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))
-
-constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
-varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
-comparison_EXAM <- constant_EXAM - varied_EXAM
-summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
-
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)
-
-# full set of Model x condit contrasts
-# ALM - EXAM
-# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
-#   pluck("contrasts") |> 
-#   gather_emmeans_draws() |> 
-#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
-
-# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()
-
-# Constant - Varied
-# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
-# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
-#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
-# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
-
-p_em_1 <- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
-  pluck("contrasts") |>
-  gather_emmeans_draws() |> 
-  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
-  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
-  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")
-
-p_ce_1 / p_em_1
-```
-
-To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
-EXAM) and training condition (Constant vs.
-Varied).
-
-Model errors were significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM.
-There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group.
-To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
-The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
-
-```{r}
-#| label: tbl-htw-modelError-e23
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-
-post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
-train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
-
-pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e2_tab <- rbind(post_tabs2$agg_pred_full |>
- mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
- mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
-train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
-
-pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e3_tab <- rbind(post_tabs3$agg_pred_full |> 
-  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
-gt_table <- e23_tab %>%
-  pivot_wider(
-    names_from = c(Exp, Model, condit),
-    values_from = mean_error,
-    names_glue = "{Exp}_{Model}_{condit}"
-  ) %>%
-  arrange(Fit_Method, `Task Stage`) %>%
-  gt() %>%
-  cols_move_to_start(columns = `Task Stage`) %>%
-  cols_label(`Task Stage` = "Task Stage") %>%
-  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = list(
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
-  ) 
-gt_table
-```
-
-```{r}
-#| label: fig-cm-vx-pat-e2-e3
-#| fig-height: 8
-#| fig-width: 10
-#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage.
-Observed data is shown on the right.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-
-rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
- e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
-  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
-  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
-  stat_bar + 
-    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
-    scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .7), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-        #  strip.background = element_blank(),
-        #  strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(20,0,0,0), "pt")) + 
-         labs(title="Model Predictions Experiment 2 & 3", y="vx")
-```
-
-```{r}
-#| label: tbl-htw-ee-e23
-#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and the interaction between Model and Condition.
-The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
-The intercept reflects the baseline of ALM and Constant.
-The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
-Lower values indicate better model fit."
-
-e2_ee_brm_ae <- brm(data=pdl2,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
-bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
-bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
-
-bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
-
-e3_ee_brm_ae <- brm(data=pdl3,
-  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
-bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
-bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
-bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
-
-bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
-               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
-  relocate(exp, .before=Term)
-
-bct_table <- bct %>%
-  mutate(
-    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
-    pd = round(pd, 2)
-  ) %>%
-  gt() %>%
-  # tab_header(
-  #   title = "Bayesian Model Results",
-  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
-  # ) %>%
-  cols_label(
-    exp = "Experiment",
-    Term = "Term",
-    Estimate = "Estimate",
-    `95% CrI Lower` = "95% CrI Lower",
-    `95% CrI Upper` = "95% CrI Upper",
-    pd = "pd"
-  ) %>%
-  fmt_number(
-    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
-    decimals = 2
-  ) %>%
-  fmt_number(
-    columns = pd,
-    decimals = 2
-  ) %>%
-  tab_spanner(
-    label = "Credible Interval",
-    columns = c(`95% CrI Lower`, `95% CrI Upper`)
-  ) %>%
-  tab_style(
-    style = list(
-      #cell_fill(color = "lightgray"),
-      cell_text(weight = "bold"), 
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(
-      columns = c(Estimate, pd),
-      rows = Term=="ModelEXAM:conditVaried"
-    )
-  ) %>%
-   tab_row_group(
-    label = "Experiment 3",
-    rows = exp == "Exp 3"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 2",
-    rows = exp == "Exp 2"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 1",
-    rows = exp == "Exp 1"
-  ) %>%
-  tab_options(
-    table.font.size = 10,
-    heading.title.font.size = 16,
-    heading.subtitle.font.size = 14,
-    quarto.disable_processing = TRUE
-    #row_group.background.color = "gray95"
-  )
-bct_table
-
-```
-
-*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
-For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
-The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
-The Bayesian regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
-The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
-Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
-Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
-We thus also controleld for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
-There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
-
-```{r}
-#| label: fig-e2_e3_ae
-#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied) on Model Error for Experiment 2 and 3 data.
-Experiment 3 also includes a control for the order of training vs.
-testing bands (original order vs.
-reverse order)."
-#| fig-height: 6
-#| fig-width: 9
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
-p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-  p_e2 <- (p1 + p2+ p3) 
-# #wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
-                         effects = "Model:condit", 
-                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
-     points=FALSE,plot=FALSE)$`Model:condit` + 
-     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
-     theme(legend.position="right") + 
-     scale_color_manual(values=wes_palette("Darjeeling1"))
-
-p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- p2 <- (p1 + p2+ p3)
- (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-```
-
-*Computational Model Summary*.
-Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23).
-This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group.
-It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model.
-A subset of these participants are shown in @fig-htw-indv-pred.
-
-```{r}
-#| label: fig-htw-best-model
-#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
-#| fig-height: 12
-#| fig-width: 11
-
-tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
-  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
-  filter(Fit_Method=="Test_Train") |>
-  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
-    mutate(e2=abs(y-pred)) |> 
-    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
-    group_by(id,condit,Model,Fit_Method,Exp) |> 
-    summarise(mean_error=mean(mean_error)) |> 
-    arrange(id,condit,Fit_Method) |>
-    round_tibble(1)
-
-best_id <- tid1 |> 
-  group_by(id,condit,Fit_Method) |> 
-  mutate(best=ifelse(mean_error==min(mean_error),1,0))
-
-lowest_error_model <- best_id %>%
-  group_by(id, condit,Fit_Method, Exp) %>%
-  summarise(Best_Model = Model[which.min(mean_error)],
-            Lowest_error = min(mean_error),
-            differential = min(mean_error) - max(mean_error)) %>%
-  ungroup()
-
-error_difference<- best_id %>%
-  select(id, condit, Model,Fit_Method, mean_error) %>%
-  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
-  mutate(Error_difference = (ALM - EXAM))
-
-full_comparison <- lowest_error_model |> 
-  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
-  group_by(condit,Fit_Method,Best_Model) |> 
-  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
-  arrange(Fit_Method,-Error_difference)
-
-full_comparison |> 
-  filter(Fit_Method=="Test_Train") |> 
-  ungroup() |>
-  mutate(id = reorder(id, Error_difference)) %>%
-  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
-  geom_col() +
-  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
-  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
-  theme(axis.text.y = element_text(size=8)) +
-  labs(fill="Best Model",
-  x="Mean Model Error Difference (ALM - EXAM)",
-  y="Participant")
-
-```
-
-```{r  fig.width=11, fig.height=10}
-#| label: fig-htw-indv-pred
-#| fig-cap: Model predictions alongside observed data for a subset of individual participants.
-A) 3 constant and 3 varied participants fit to both the test and training data.
-B) 3 constant and 3 varied subjects fit to only the trainign data.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands.
-#| fig-height: 7
-#| fig-width: 10
-
-cId_tr <- c(137, 181, 11)
-vId_tr <- c(14, 193, 47)
-cId_tt <- c(11, 93, 35)
-vId_tt <- c(1,14,74)
-cId_new <- c(175, 68, 93, 74)
-# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")
-
-e1_sbjs <- c(49,68,155, 175,74)
-e3_sbjs <-  c(245, 280, 249)
-e2_sbjs <- c(197, 157, 312, 334)
-cFinal <- c(49, 128,202 )
-vFinal <- c(68,70,245)
-
-indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
-  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
-  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))
-
-testIndv <- indv_post_l |> 
-#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
-   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
-  group_by(id,condit,Fit_Method,Model,Resp) |>
-   mutate(flab=paste0("Subject: ",id)) |>
-  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar_sd + 
-  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
-  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
-  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
-  labs(title="Individual Participant fits from Test & Train Fitting Method",
-       y="X Velocity",fill="Target Velocity") +
-   guides(fill = guide_legend(nrow = 1)) + 
-  theme(legend.position = "bottom",axis.title.x = element_blank())
-
-testIndv 
-```
-
-# General Discussion
-
-*Experimental Result Summary*
-
-Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
-In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-
-Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
-The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.
-
-Experiment 2 extended these findings by reversing the order of the training and testing bands.
-Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases.
-However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.
-
-In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments.
-Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied).
-The varied condition showed larger deviations at the end of training, consistent with the previous experiments.
-Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition.
-During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands.
-The reverse order conditions showed smaller deviations compared to the original order conditions.
-Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.
-
-All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015].
-The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group.
-Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.
-
-Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
-Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
-A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
-These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study.
-@vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
-However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
-
-*Modeling Summary*
-EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group.
-May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule.
-But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval.
-The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
-
-*Limitations*
-
-While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
-First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
-Such a difference may be an unavoidable consequence of varied vs.
-constant design which match the total number of training trials between the two groups.
-However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
-Another limitation is that the testing stage did not include any interpolation items, i.e.
-the participants tested only from the training bands they experienced during training, or from extrapolation bands.
-The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
-Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
-Finally, the task employed in the present study consisted of only a linear, positive function.
-Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
-It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
-
-## Comparison to Project 1
-
-### Differences between the tasks
-
-There are a number of differences between Project 1's Hit The Target (HTT), and Project 2's Hit The Wall (HTW) tasks.
-
-- Task Space Complexity: In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard.
-Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.
-
-- Perceptual Distinctiveness: HTT offers perceptually distinct varied conditions that directly relate to the task's demands, which may increase the sallience between training positions encounted by the varied group.
-In contrast, HTW's varied conditions differ only in the numerical values displayed, lacking the same level of perceptual differentiation.
-Conversely in HTW, the only difference between conditions for the varied group are the numbers displayed at the top of the screen which indicate the current target band(e.g.
-800-1000, or 1000-1200)
-
-- In HTW, our primary testing stage of interest has no feedback, whereas in HTT testing always included feedback (the intermittent testing in HTT expt 1 being the only exception).
-Of course, we do collect testing with feedback data at the end of HTW, but we haven't focused on that data at all in our modelling work thus far.
-It's also interesting to recall that the gap between varied and constant in HTW does seem to close substantially in the testing-with-feedback stage.
-The difference between no-feedback and feedback testing might be relevant if the benefits of variation have anything to do with improving subsequent learning (as opposed to subsequent immediate performance), OR if the benefits of constant training rely on having the most useful anchor, having the most useful anchor might be a lot less helpful if you're getting feedback from novel positions and can thus immediately begin to form position-specific anchors for the novelties, rather than relying on a training anchor.
-
-- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments.
-However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands.
-This means that in HTT the varied group gets half as much experience on any one position as the constant group, and in HTW they only get 1/3 as much experience in any one position.
-There are likely myriad ways in which this might impact the success of the varied group regardless of how you think the benefits of variation might be occurring, e.g.
-maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.
-
-# References
-
-::: {#refs}
-:::
-
-# Appendix
-
-{{< include Appendix/IGAS-Supplemental.qmd >}}
+}\end{equation}
+
+The final component of our ABC implementation is the determination of an
+appropriate value of \(\epsilon\). The setting of \(\epsilon\) exerts
+strong influence on the approximated posterior distribution. Smaller
+values of \(\epsilon\) increase the rejection rate, and improve the
+fidelity of the approximated posterior, while larger values result in an
+ABC sampler that simply reproduces the prior distribution. Because the
+individual participants in our dataset differed substantially in terms
+of the noisiness of their data, we employed an adaptive tolerance
+setting strategy to tailor \(\epsilon\) to each individual. The initial
+value of \(\epsilon\) was set to the overall standard deviation of each
+individuals velocity values. Thus, sampled parameter values that
+generated simulated data within a standard deviation of the observed
+data were accepted, while worse performing parameters were rejected.
+After every 300 samples the tolerance was allowed to increase only if
+the current acceptance rate of the algorithm was less than 1\%. In such
+cases, the tolerance was shifted towards the average discrepancy of the
+5 best samples obtained thus far. To ensure the acceptance rate did not
+become overly permissive, \(\epsilon\) was also allowed to decrease
+every time a sample was accepted into the posterior.
+
+\end{tcolorbox}
+
+For each of the 156 participants from Experiment 1, the ABC algorithm
+was run until 200 samples of parameters were accepted into the posterior
+distribution. Obtaining this number of posterior samples required an
+average of 205,000 simulation runs per participant. Fitting each
+combination of participant, Model (EXAM \& ALM), and fitting method
+(Test only, Train only, Test \& Train) required a total of 192 million
+simulation runs. To facilitate these intensive computational demands, we
+used the Future Package in R
+\autocite{bengtssonUnifyingFrameworkParallel2021}, allowing us to
+parallelize computations across a cluster of ten M1 iMacs, each with 8
+cores.
+
+\subsubsection{Modelling Results}\label{modelling-results}
+
+\paragraph{Group level Patterns}\label{group-level-patterns}
+
+\begin{longtable}{lcrrrr}
+
+\caption{\label{tbl-htw-modelError-e1}Models errors predicting empirical
+data - aggregated over all participants, posterior parameter values, and
+velocity bands. Note that Fit Method refers to the subset of the data
+that the model was trained on, while Task Stage refers to the subset of
+the data that the model was evaluated on.}
+
+\tabularnewline
+
+\toprule
+ &  & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} \\ 
+\cmidrule(lr){3-4} \cmidrule(lr){5-6}
+Task Stage & Fit Method & Constant & Varied & Constant & Varied \\ 
+\midrule\addlinespace[2.5pt]
+\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{Fit to Test Data} & \cellcolor[HTML]{FFFFFF}{$199.93$} & \cellcolor[HTML]{FFFFFF}{$103.36$} & \cellcolor[HTML]{FFFFFF}{$104.01$} & \cellcolor[HTML]{FFFFFF}{$85.68$} \\
+\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{Fit to Test \& Training Data} & \cellcolor[HTML]{FFFFFF}{$216.97$} & \cellcolor[HTML]{FFFFFF}{$170.28$} & \cellcolor[HTML]{FFFFFF}{$127.94$} & \cellcolor[HTML]{FFFFFF}{$144.86$} \\
+\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{Fit to Training Data} & \cellcolor[HTML]{FFFFFF}{$467.73$} & \cellcolor[HTML]{FFFFFF}{$291.38$} & \cellcolor[HTML]{FFFFFF}{$273.30$} & \cellcolor[HTML]{FFFFFF}{$297.91$} \\
+\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{Fit to Test Data} & \cellcolor[HTML]{FFFFFF}{$297.82$} & \cellcolor[HTML]{FFFFFF}{$2,016.01$} & \cellcolor[HTML]{FFFFFF}{$53.90$} & \cellcolor[HTML]{FFFFFF}{$184.00$} \\
+\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{Fit to Test \& Training Data} & \cellcolor[HTML]{FFFFFF}{$57.40$} & \cellcolor[HTML]{FFFFFF}{$132.32$} & \cellcolor[HTML]{FFFFFF}{$42.92$} & \cellcolor[HTML]{FFFFFF}{$127.90$} \\
+\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{Fit to Training Data} & \cellcolor[HTML]{FFFFFF}{$51.77$} & \cellcolor[HTML]{FFFFFF}{$103.48$} & \cellcolor[HTML]{FFFFFF}{$51.43$} & \cellcolor[HTML]{FFFFFF}{$107.03$} \\
+\bottomrule
+
+\end{longtable}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-htw-post-dist-1.pdf}
+
+}
+
+\caption{\label{fig-htw-post-dist}Posterior Distributions of \(c\) and
+\(lr\) parameters. Points represent median values, thicker intervals
+represent 66\% credible intervals and thin intervals represent 95\%
+credible intervals around the median. Note that the y axes of the plots
+for the c parameter are scaled logarithmically.}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-htw-resid-pred-1.pdf}
+
+}
+
+\caption{\label{fig-htw-resid-pred}Model residuals for each combination
+of training condition, fit method, and model. Residuals reflect the
+difference between observed and predicted values. Lower values indicate
+better model fit. Note that y axes are scaled differently between
+facets. A) Residuals predicting each block of the training data. B)
+Residuals predicting each band during the testing stage. Bolded bars
+indicate bands that were trained, non-bold bars indicate extrapolation
+bands.}
+
+\end{figure}%
+
+The posterior distributions of the \(c\) and \(lr\) parameters are shown
+Figure~\ref{fig-htw-post-dist}, and model predictions are shown
+alongside the empirical data in Figure~\ref{fig-cm-vx-pat}. There were
+substantial individual differences in the posteriors of both parameters,
+with the within-group individual differences generally swamped any
+between-group or between-model differences. The magnitude of these
+individual differences remains even if we consider only the single best
+parameter set for each subject.
+
+We used the posterior distribution of \(c\) and \(lr\) parameters to
+generate a posterior predictive distribution of the observed data for
+each participant, which then allows us to compare the empirical data to
+the full range of predictions from each model. Aggregated residuals are
+displayed in Figure~\ref{fig-htw-resid-pred}. The pattern of training
+stage residual errors are unsurprising across the combinations of models
+and fitting method . Differences in training performance between ALM and
+EXAM are generally minor (the two models have identical learning
+mechanisms). The differences in the magnitude of residuals across the
+three fitting methods are also straightforward, with massive errors for
+the `fit to Test Only' model, and the smallest errors for the `fit to
+train only' models. It is also noteworthy that the residual errors are
+generally larger for the first block of training, which is likely due to
+the initial values of the ALM weights being unconstrained by whatever
+initial biases participants tend to bring to the task. Future work may
+explore the ability of the models to capture more fine grained aspects
+of the learning trajectories. However for the present purposes, our
+primary interest is in the ability of ALM and EXAM to account for the
+testing patterns while being constrained, or not constrained, by the
+training data. All subsequent analyses and discussion will thus focus on
+the testing stage.
+
+The residuals of the model predictions for the testing stage
+(Figure~\ref{fig-htw-resid-pred}) also show an unsurprising pattern
+across fitting methods - with models fit only to the test data showing
+the best performance, followed by models fit to both training and test
+data, and with models fit only to the training data showing the worst
+performance (note that y axes are scaled different between plots).
+Although EXAM tends to perform better for both Constant and Varied
+participants (see also Figure~\ref{fig-ee-e1}), the relative advantage
+of EXAM is generally larger for the Constant group - a pattern
+consistent across all three fitting methods. The primary predictive
+difference between ALM and EXAM is made clear in
+Figure~\ref{fig-cm-vx-pat}, which directly compares the observed data
+against the posterior predictive distributions for both models.
+Regardless of how the models are fit, only EXAM can capture the pattern
+where participants are able to discriminate all 6 target bands.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-cm-vx-pat-1.pdf}
+
+}
+
+\caption{\label{fig-cm-vx-pat}Empirical data and Model predictions for
+mean velocity across target bands. Fitting methods (Test Only, Test \&
+Train, Train Only) - are separated across rows, and Training Condition
+(Constant vs.~Varied) are separated by columns. Each facet contains the
+predictions of ALM and EXAM, alongside the observed data.}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\captionsetup{labelsep=none}\includegraphics{full_files/figure-pdf/fig-ee-e1-1.pdf}
+
+}
+
+\caption{\label{fig-ee-e1}}
+
+\end{figure}%
+
+To quantitatively assess whether the differences in performance between
+models, we fit a bayesian regressions predicting the errors of the
+posterior predictions of each models as a function of the Model (ALM
+vs.~EXAM) and training condition (Constant vs.~Varied).
+
+Model errors were significantly lower for EXAM (\(\beta\) = -37.54, 95\%
+CrI {[}-60.4, -14.17{]}, pd = 99.85\%) than ALM. There was also a
+significant interaction between Model and Condition (\(\beta\) = 60.42,
+95\% CrI {[}36.17, 83.85{]}, pd = 100\%), indicating that the advantage
+of EXAM over ALM was significantly greater for the constant group. To
+assess whether EXAM predicts constant performance significantly better
+for Constant than for Varied subjects, we calculated the difference in
+model error between the Constant and Varied conditions specifically for
+EXAM. The results indicated that the model error for EXAM was
+significantly lower in the Constant condition compared to the Varied
+condition, with a mean difference of -22.88 (95\% CrI {[}-46.02,
+-0.97{]}, pd = 0.98).
+
+\begin{longtable}{lrrrrrrrr}
+
+\caption{\label{tbl-htw-modelError-e23}Models errors predicting
+empirical data - aggregated over all participants, posterior parameter
+values, and velocity bands. Note that Fit Method refers to the subset of
+the data that the model was trained on, while Task Stage refers to the
+subset of the data that the model was evaluated on.}
+
+\tabularnewline
+
+\toprule
+ & \multicolumn{4}{c}{E2} & \multicolumn{4}{c}{E3} \\ 
+\cmidrule(lr){2-5} \cmidrule(lr){6-9}
+ & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} \\ 
+\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
+Task Stage & Constant & Varied & Constant & Varied & Constant & Varied & Constant & Varied \\ 
+\midrule\addlinespace[2.5pt]
+\multicolumn{9}{l}{Fit to Test Data} \\ 
+\midrule\addlinespace[2.5pt]
+\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{$239.7$} & \cellcolor[HTML]{FFFFFF}{$129.8$} & \cellcolor[HTML]{FFFFFF}{$99.7$} & \cellcolor[HTML]{FFFFFF}{$88.2$} & \cellcolor[HTML]{FFFFFF}{$170.1$} & \cellcolor[HTML]{FFFFFF}{$106.1$} & \cellcolor[HTML]{FFFFFF}{$92.3$} & \cellcolor[HTML]{FFFFFF}{$72.8$} \\
+\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{$53.1$} & \cellcolor[HTML]{FFFFFF}{$527.1$} & \cellcolor[HTML]{FFFFFF}{$108.1$} & \cellcolor[HTML]{FFFFFF}{$169.3$} & \cellcolor[HTML]{FFFFFF}{$70.9$} & \cellcolor[HTML]{FFFFFF}{$543.5$} & \cellcolor[HTML]{FFFFFF}{$157.8$} & \cellcolor[HTML]{FFFFFF}{$212.7$} \\
+\midrule\addlinespace[2.5pt]
+\multicolumn{9}{l}{Fit to Test \& Training Data} \\ 
+\midrule\addlinespace[2.5pt]
+\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{$266.0$} & \cellcolor[HTML]{FFFFFF}{$208.2$} & \cellcolor[HTML]{FFFFFF}{$125.1$} & \cellcolor[HTML]{FFFFFF}{$126.4$} & \cellcolor[HTML]{FFFFFF}{$197.7$} & \cellcolor[HTML]{FFFFFF}{$189.5$} & \cellcolor[HTML]{FFFFFF}{$130.0$} & \cellcolor[HTML]{FFFFFF}{$128.5$} \\
+\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{$40.0$} & \cellcolor[HTML]{FFFFFF}{$35.4$} & \cellcolor[HTML]{FFFFFF}{$30.4$} & \cellcolor[HTML]{FFFFFF}{$23.6$} & \cellcolor[HTML]{FFFFFF}{$49.1$} & \cellcolor[HTML]{FFFFFF}{$85.6$} & \cellcolor[HTML]{FFFFFF}{$49.2$} & \cellcolor[HTML]{FFFFFF}{$78.4$} \\
+\midrule\addlinespace[2.5pt]
+\multicolumn{9}{l}{Fit to Training Data} \\ 
+\midrule\addlinespace[2.5pt]
+\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{$357.4$} & \cellcolor[HTML]{FFFFFF}{$295.9$} & \cellcolor[HTML]{FFFFFF}{$305.1$} & \cellcolor[HTML]{FFFFFF}{$234.5$} & \cellcolor[HTML]{FFFFFF}{$415.0$} & \cellcolor[HTML]{FFFFFF}{$298.8$} & \cellcolor[HTML]{FFFFFF}{$295.5$} & \cellcolor[HTML]{FFFFFF}{$243.7$} \\
+\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{$42.5$} & \cellcolor[HTML]{FFFFFF}{$23.0$} & \cellcolor[HTML]{FFFFFF}{$43.2$} & \cellcolor[HTML]{FFFFFF}{$22.6$} & \cellcolor[HTML]{FFFFFF}{$51.4$} & \cellcolor[HTML]{FFFFFF}{$63.8$} & \cellcolor[HTML]{FFFFFF}{$51.8$} & \cellcolor[HTML]{FFFFFF}{$65.3$} \\
+\bottomrule
+
+\end{longtable}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-cm-vx-pat-e2-e3-1.pdf}
+
+}
+
+\caption{\label{fig-cm-vx-pat-e2-e3}Empirical data and Model predictions
+from Experiment 2 and 3 for the testing stage. Observed data is shown on
+the right. Bolded bars indicate bands that were trained, non-bold bars
+indicate extrapolation bands.}
+
+\end{figure}%
+
+\begin{longtable}{llrrrr}
+
+\caption{\label{tbl-htw-ee-e23}Results of Bayesian Regression models
+predicting model error as a function of Model (ALM vs.~EXAM), Condition
+(Constant vs.~Varied), and the interaction between Model and Condition.
+The values represent the estimate coefficient for each term, with 95\%
+credible intervals in brackets. The intercept reflects the baseline of
+ALM and Constant. The other estimates indicate deviations from the
+baseline for the EXAM mode and varied condition. Lower values indicate
+better model fit.}
+
+\tabularnewline
+
+\toprule
+ &  &  & \multicolumn{2}{c}{Credible Interval} &  \\ 
+\cmidrule(lr){4-5}
+Experiment & Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\ 
+\midrule\addlinespace[2.5pt]
+\multicolumn{6}{l}{Experiment 1} \\ 
+\midrule\addlinespace[2.5pt]
+Exp 1 & Intercept & $176.30$ & $156.86$ & $194.59$ & $1.00$ \\ 
+Exp 1 & ModelEXAM & $-88.44$ & $-104.51$ & $-71.81$ & $1.00$ \\ 
+Exp 1 & conditVaried & $-37.54$ & $-60.40$ & $-14.17$ & $1.00$ \\ 
+Exp 1 & ModelEXAM:conditVaried & \cellcolor[HTML]{FFFFFF}{\textbf{$60.42$}} & $36.17$ & $83.85$ & \cellcolor[HTML]{FFFFFF}{\textbf{$1.00$}} \\ 
+\midrule\addlinespace[2.5pt]
+\multicolumn{6}{l}{Experiment 2} \\ 
+\midrule\addlinespace[2.5pt]
+Exp 2 & Intercept & $245.87$ & $226.18$ & $264.52$ & $1.00$ \\ 
+Exp 2 & ModelEXAM & $-137.73$ & $-160.20$ & $-115.48$ & $1.00$ \\ 
+Exp 2 & conditVaried & $-86.39$ & $-113.52$ & $-59.31$ & $1.00$ \\ 
+Exp 2 & ModelEXAM:conditVaried & \cellcolor[HTML]{FFFFFF}{\textbf{$56.87$}} & $25.26$ & $88.04$ & \cellcolor[HTML]{FFFFFF}{\textbf{$1.00$}} \\ 
+\midrule\addlinespace[2.5pt]
+\multicolumn{6}{l}{Experiment 3} \\ 
+\midrule\addlinespace[2.5pt]
+Exp 3 & Intercept & $164.83$ & $140.05$ & $189.44$ & $1.00$ \\ 
+Exp 3 & ModelEXAM & $-65.66$ & $-85.97$ & $-46.02$ & $1.00$ \\ 
+Exp 3 & conditVaried & $-40.61$ & $-75.90$ & $-3.02$ & $0.98$ \\ 
+Exp 3 & bandOrderReverse & $25.47$ & $-9.34$ & $58.68$ & $0.93$ \\ 
+Exp 3 & ModelEXAM:conditVaried & \cellcolor[HTML]{FFFFFF}{\textbf{$41.90$}} & $11.20$ & $72.54$ & \cellcolor[HTML]{FFFFFF}{\textbf{$0.99$}} \\ 
+Exp 3 & ModelEXAM:bandOrderReverse & $-7.32$ & $-34.53$ & $21.05$ & $0.70$ \\ 
+Exp 3 & conditVaried:bandOrderReverse & $30.82$ & $-19.57$ & $83.56$ & $0.88$ \\ 
+Exp 3 & ModelEXAM:conditVaried:bandOrderReverse & $-60.60$ & $-101.80$ & $-18.66$ & $1.00$ \\ 
+\bottomrule
+
+\end{longtable}
+
+\emph{Model Fits to Experiment 2 and 3.} Data from Experiments 2 and 3
+were fit to ALM and EXAM in the same manner as Experiment1 . For
+brevity, we only plot and discuss the results of the ``fit to training
+and testing data'' models - results from the other fitting methods can
+be found in the appendix. The model fitting results for Experiments 2
+and 3 closely mirrored those observed in Experiment 1. The Bayesian
+regression models predicting model error as a function of Model (ALM
+vs.~EXAM), Condition (Constant vs.~Varied), and their interaction (see
+Table~\ref{tbl-htw-ee-e23}) revealed a consistent main effect of Model
+across all three experiments. The negative coefficients for the
+ModelEXAM term (Exp 2: \(\beta\) = -86.39, 95\% CrI -113.52, -59.31, pd
+= 100\%; Exp 3: \(\beta\) = -40.61, 95\% CrI -75.9, -3.02, pd = 98.17\%)
+indicate that EXAM outperformed ALM in both experiments. Furthermore,
+the interaction between Model and Condition was significant in both
+Experiment 2 (\(\beta\) = 56.87, 95\% CrI 25.26, 88.04, pd = 99.98\%)
+and Experiment 3 (\(\beta\) = 41.9, 95\% CrI 11.2, 72.54, pd = 99.35\%),
+suggesting that the superiority of EXAM over ALM was more pronounced for
+the Constant group compared to the Varied group, as was the case in
+Experiment 1. Recall that Experiment 3 included participants in both the
+original and reverse order conditions - and that this manipulation
+interacted with the effect of training condition. We thus also
+controleld for band order in our Bayesian Regression assessing the
+relative performance of EXAM and ALM in Experiment 3. There was a
+significant three way interaction between Model, Training Condition, and
+Band Order (\(\beta\) = -60.6, 95\% CrI -101.8, -18.66, pd = 99.83\%),
+indicating that the relative advantage of EXAM over ALM was only more
+pronounced in the original order condition, and not the reverse order
+condition (see Figure~\ref{fig-e2_e3_ae}).
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-e2_e3_ae-1.pdf}
+
+}
+
+\caption{\label{fig-e2_e3_ae}Conditional effects of Model (ALM vs EXAM)
+and Condition (Constant vs.~Varied) on Model Error for Experiment 2 and
+3 data. Experiment 3 also includes a control for the order of training
+vs.~testing bands (original order vs.~reverse order).}
+
+\end{figure}%
+
+\emph{Computational Model Summary}. Across the model fits to all three
+experiments, we found greater support for EXAM over ALM (negative
+coefficients on the ModelEXAM term in Table~\ref{tbl-htw-ee-e23}), and
+moreover that the constant participants were disproportionately well
+described by EXAM in comparison to ALM (positive coefficients on
+ModelEXAM:conditVaried terms in Table~\ref{tbl-htw-ee-e23}). This
+pattern is also clearly depicted in Figure~\ref{fig-htw-best-model},
+which plots the difference in model errors between ALM and EXAM for each
+individual participant. Both varied and constant conditions have a
+greater proportion of subjects better fit by EXAM (positive error
+differences), with the magnitude of EXAM's advantage visibly greater for
+the constant group. It also bears mention that numerous participants
+were better fit by ALM, or did not show a clear preference for either
+model. A subset of these participants are shown in
+Figure~\ref{fig-htw-indv-pred}.
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-htw-best-model-1.pdf}
+
+}
+
+\caption{\label{fig-htw-best-model}Difference in model errors for each
+participant, with models fit to both train and test data. Positive
+values favor EXAM, while negative values favor ALM.}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics{full_files/figure-pdf/fig-htw-indv-pred-1.pdf}
+
+}
+
+\caption{\label{fig-htw-indv-pred}Model predictions alongside observed
+data for a subset of individual participants. A) 3 constant and 3 varied
+participants fit to both the test and training data. B) 3 constant and 3
+varied subjects fit to only the trainign data. Bolded bars indicate
+bands that were trained, non-bold bars indicate extrapolation bands.}
+
+\end{figure}%
+
+\section{General Discussion}\label{general-discussion-1}
+
+\emph{Experimental Result Summary}
+
+Across three experiments, we investigated the impact of training
+variability on learning and extrapolation in a visuomotor function
+learning task. In Experiment 1, participants in the varied training
+condition, who experienced a wider range of velocity bands during
+training, showed lower accuracy at the end of training compared to those
+in the constant training condition.
+
+Crucially, during the testing phase, the varied group exhibited
+significantly larger deviations from the target velocity bands,
+particularly for the extrapolation bands that were not encountered
+during training. The varied group also showed less discrimination
+between velocity bands, as evidenced by shallower slopes when predicting
+response velocity from target velocity band.
+
+Experiment 2 extended these findings by reversing the order of the
+training and testing bands. Similar to Experiment 1, the varied group
+demonstrated poorer performance during both training and testing phases.
+However, unlike Experiment 1, the varied group did not show a
+significant difference in discrimination between bands compared to the
+constant group.
+
+In Experiment 3, we provided only ordinal feedback during training, in
+contrast to the continuous feedback provided in the previous
+experiments. Participants were assigned to both an order condition
+(original or reverse) and a training condition (constant or varied). The
+varied condition showed larger deviations at the end of training,
+consistent with the previous experiments. Interestingly, there was a
+significant interaction between training condition and band order, with
+the varied condition showing greater accuracy in the reverse order
+condition. During testing, the varied group once again exhibited larger
+deviations, particularly for the extrapolation bands. The reverse order
+conditions showed smaller deviations compared to the original order
+conditions. Discrimination between velocity bands was poorer for the
+varied group in the original order condition, but not in the reverse
+order condition.
+
+All three of our experiments yielded evidence that varied training
+conditions produced less learning by the end of training, a pattern
+consistent with much of the previous research on the influence of
+training variability
+\autocite{catalanoDistantTransferCoincident1984a,wrisbergVariabilityPracticeHypothesis1987,soderstromLearningPerformanceIntegrative2015}.
+The sole exception to this pattern was the reverse order condition in
+Experiment 3, where the varied group was not significantly worse than
+the constant group. Neither the varied condition trained with the same
+reverse-order items in Experiment 2, nor the original-order varied
+condition trained with ordinal feedback in Experiment 3 were able to
+match the performance of their complementary constant groups by the end
+of training, suggesting that the relative success of the ordinal-reverse
+ordered varied group cannot be attributed to item or feedback effects
+alone.
+
+Our findings also diverge from the two previous studies to cleanly
+manipulate the variability of training items in a function learning task
+\autocite{deloshExtrapolationSineQua1997,vandamMappingShapeVisuomotor2015},
+although the varied training condition of
+\textcite{vandamMappingShapeVisuomotor2015} also exhibited less
+learning, neither of these previous studies observed any difference
+between training conditions in extrapolation to novel items. Like
+\textcite{deloshExtrapolationSineQua1997} , our participants exhibited
+above chance extrapolation/discrimination of novel items, however they
+observed no difference between any of their three training conditions. A
+noteworthy difference difference between our studies is that
+\textcite{deloshExtrapolationSineQua1997} trained participants with
+either 8, 20, or 50 unique items (all receiving the same total number of
+training trials). These larger sets of unique items, combined with the
+fact that participants achieved near ceiling level performance by the
+end of training - may have made it more difficult to observe any
+between-group differences of training variation in their study.
+\textcite{vandamMappingShapeVisuomotor2015} 's variability manipulation
+was more similar to our own, as they trained participants with either 2
+or 5 unique items. However, although the mapping between their input
+stimuli and motor responses was technically linear, the input dimension
+was more complex than our own, as it was defined by the degree of
+``spikiness'' of the input shape. This entirely arbitrary mapping also
+would have preculded any sense of a ``0'' point, which may partially
+explain why neither of their training conditions were able to
+extrapolate linearly in the manner observed in the current study or in
+\textcite{deloshExtrapolationSineQua1997}.
+
+\emph{Modeling Summary} EXAM is the best model for both groups, but EXAM
+does relatively good at accounting for the constant group. May have
+seemed counterintuitive, if one assumed that multiple, varied, examples
+were necessary to extract a rule. But, EXAM is not a conventional rule
+model - it doesn't require explictly abstract of a rule, but rather the
+rule-based response occurs during retrieval. The constant groups
+formation of a single, accurate, input-output association, in
+combination with the usefulness of the zero point, may have been
+sufficient for EXAM, and the constant group, to perform well. One
+concern may have been that the assumption of participants making use of
+the zero point turned the extrapolation problem into an interpolation
+problem - however this concern is ameliorated by the consistency of the
+results across both the original and reverse order conditions.
+
+\emph{Limitations}
+
+While the present study provides valuable insights into the influence of
+training variability on visuomotor function learning and extrapolation,
+there are several limitations that should be flagged. First, although
+the constant training group never had experience from a velocity band
+closer to the extrapolation bands than the varied group, they always had
+a three times more trials with the nearest velocity band. Such a
+difference may be an unavoidable consequence of varied vs.~constant
+design which match the total number of training trials between the two
+groups. However in order to more carefully tease apart the influence of
+variability from the influence of frequency/repetition effects, future
+research could explore alternative designs that maintain the variability
+manipulation while equating the amount of training on the nearest
+examples across conditions, such as by increasing the total number of
+trials for the varied group. Another limitation is that the testing
+stage did not include any interpolation items, i.e.~the participants
+tested only from the training bands they experienced during training, or
+from extrapolation bands. The absence of interpolation testing makes it
+more difficult to distinguish between the effects of training
+variability on extrapolation specifically, as opposed to generalization
+more broadly. Of course, the nature of the constant training condition
+makes interpolation teseting impossible to implement, however future
+studies might compare a training regimes that each include at least 2
+distinct items, but still differ in total amount of variability
+experienced, which would then allow groups to be compared in terms of
+both interpolation and extrapolation testing. Finally, the task employed
+in the present study consisted of only a linear, positive function.
+Previous work in human function learning has repeatedly shown that such
+functions are among the easiest to learn, but that humans are
+nonetheless capable of learning negative, non-linear, or discontinuous
+functions
+\autocite{deloshExtrapolationSineQua1997,mcdanielPredictingTransferPerformance2009,kalishLearningExtrapolatingPeriodic2013,busemeyerLearningFunctionalRelations1997}.
+It thus remains an open question as to whether the influence of training
+variability might interact with various components of the to-be-learned
+function.
+
+\subsection{Comparison to Project 1}\label{comparison-to-project-1}
+
+\subsubsection{Differences between the
+tasks}\label{differences-between-the-tasks}
+
+There are a number of differences between Project 1's Hit The Target
+(HTT), and Project 2's Hit The Wall (HTW) tasks.
+
+\begin{itemize}
+\item
+  Task Space Complexity: In~HTW,~the task space is also almost perfectly
+  smooth, at least for the continuous feedback subjects, if they throw
+  100 units too hard, they'll be told that they were 100 units too hard.
+  Whereas in HTT, ~it was possible to produce xy velocity combinations
+  that were technically closer to the empirical solution space than
+  other throws, but which resulted in worse feedback due to striking the
+  barrier.
+\item
+  Perceptual Distinctiveness: HTT offers perceptually distinct varied
+  conditions that directly relate to the task's demands, which may
+  increase the sallience between training positions encounted by the
+  varied group. In contrast, HTW's varied conditions differ only in the
+  numerical values displayed, lacking the same level of perceptual
+  differentiation. Conversely in~HTW, the only difference between
+  conditions for the varied group are the numbers displayed at the top
+  of the screen which indicate the current target band(e.g.~800-1000, or
+  1000-1200)
+\item
+  In~HTW, our primary testing stage of interest has no feedback, whereas
+  in HTT testing always included feedback (the intermittent testing in
+  HTT expt 1 being the only exception). Of course, we do collect testing
+  with feedback data at the end of~HTW, but we haven't focused on that
+  data at all in our modelling work thus far. It's also interesting to
+  recall that the gap between varied and constant in~HTW~does seem to
+  close substantially in the testing-with-feedback stage. The difference
+  between no-feedback and feedback testing might be relevant if the
+  benefits of variation have anything to do with improving subsequent
+  learning (as opposed to subsequent immediate performance), OR if the
+  benefits of constant training rely on having the most useful anchor,
+  having the most useful anchor might be a lot less helpful if you're
+  getting feedback from novel positions and can thus immediately begin
+  to form position-specific anchors for the novelties, rather than
+  relying on a training anchor.~
+\item
+  HTW~and HTT both have a similar amount of training trials
+  (\textasciitilde200), and thus the constant groups acquire a similar
+  amount of experience with their single position/velocity in both
+  experiments. However, the varied conditions in both HTT
+  experiments~train on 2 positions, whereas the varied group
+  in~HTW~trains on 3 velocity bands. This means that in HTT the varied
+  group gets half as much experience on any one position as the constant
+  group, and in~HTW~they only get 1/3 as much experience in any one
+  position. There are likely myriad ways in which this might impact the
+  success of the varied group regardless of how you think the benefits
+  of variation might be occurring, e.g.~maybe they also need to develop
+  a coherent anchor, maybe they need more experience in order to extract
+  a function, or more experience in order to properly learn to tune
+  their c parameter.~
+\end{itemize}
+
+\section{References}\label{references}
+
+%bib-loc-124C8010
+
+\section{Appendix}\label{appendix}
+
+Reviewer \#2: This study addresses a question that is important both
+theoretically and practically. However, the authors need to rule out the
+following, less interesting alternative. Namely, the results could be
+due to task practice effect, as follows.
+
+Since there was no pre-training test, and no practice trials (as far as
+I can tell), and since the task was an online motor task that
+participants could not rely on their prior motor experience, trying to
+launch the ball to the target could only be done via trial and error.
+For the varied training group, they got to practice at two distances.
+Therefore, they had a better ``calibration'' in terms of the
+relationship between launching speed and target distance. This was
+likely beneficial both in Exp.1 when both transfer distances were
+interpolations from the two trained distances, and in Exp.2 when two
+transfer distances were interpolations and two were extrapolations but
+the latter two were immediately next to the training distances.
+
+In comparison, since the constant group trained at only a single
+distance, any transfer distance (or at least the first transfer distance
+tested) was extrapolation even if this transfer distance was shorter
+than the trained, because the participants did not know beforehand how
+to shoot the ball to the shortest distance due to the existence of the
+barrier. If the transfer distance was longer, for sure that was
+extrapolation.
+
+Regardless, the above analysis suggests that the constant group would
+always be a step behind the varied group. The number of trials at each
+transfer distance may not be sufficient for them to catch up the varied
+group either (whether there was learning during testing should be
+checked). If such disadvantage for the constant group is indeed due to
+the lack of tryout opportunities, then the authors should verify whether
+the same results still hold if all groups were provided opportunities to
+practice, or if pre-training tests across all distances were offered.
+
+\subsubsection{exponential learning models fit to individual
+subjects}\label{exponential-learning-models-fit-to-individual-subjects}
+
+\subsubsection{Group comparison of learning rate
+fits}\label{group-comparison-of-learning-rate-fits}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-60-1.pdf}
+
+\subsubsection{First vs.~second half of testing
+stage}\label{first-vs.-second-half-of-testing-stage}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-61-1.pdf}
+
+\subsubsection{Group Comparison for asymptote-starting
+performance}\label{group-comparison-for-asymptote-starting-performance}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-62-1.pdf}
+
+\subsubsection{Relative distance and
+under/overshooting}\label{relative-distance-and-underovershooting}
+
+Reviewer 3 Absolute versus relative distance: From a methodological
+standpoint, I understand the need to differentiate these two types of
+distance. However, from a theoretical perspective there may be some
+issue in differentiating these two concepts. Schema theory relies on
+relative (or invariant) information to inform the motor program.
+However, both distances would be important to an instance or exemplar
+representation. You may want to consider commenting on this issue.
+
+Reviewer 2 For the same reason, the plots showing improvement during
+training could be due to participants learning the task, rather than
+fine motor skills. Although task learning and motor learning are
+impossible to separate cleanly, the common practice in the field is
+indeed to offer practice trials to reduce the task learning aspects. The
+authors should address this.
+
+In addition to absolute errors (which is related to variance), the
+authors should also provide other measures of performance, e.g., the
+mean of the signed errors, so that readers have a better idea whether
+there was any meaningful over- or undershooting.
+
+\paragraph{experiment 1 training - relative
+distances}\label{experiment-1-training---relative-distances}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-63-1.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-63-2.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-63-3.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-63-4.pdf}
+
+\begin{verbatim}
+
+=========================================================================
+conditType devianceDirection      610            760            910      
+-------------------------------------------------------------------------
+constant       Overshoot                    311.84(307.92)               
+constant      Undershoot                    188.05(163.62)               
+varied         Overshoot     211.69(234.97)                360.14(322.01)
+varied        Undershoot     107.35(81.21)                 244.85(196.47)
+-------------------------------------------------------------------------
+\end{verbatim}
+
+\begin{verbatim}
+
+======================================================
+conditType      610           760            910      
+------------------------------------------------------
+constant                 121.03(269.17)               
+varied     39.91(178.12)                150.53(290.04)
+------------------------------------------------------
+\end{verbatim}
+
+\begin{verbatim}
+
+====================================================================
+conditType     610           760            835            910      
+--------------------------------------------------------------------
+constant   7.13(124.02) 107.02(218.49) 142.42(252.34) 122.92(282.58)
+varied     3.19(96.67)   92.1(173.9)   103.84(214.4)  108.12(234.59)
+--------------------------------------------------------------------
+\end{verbatim}
+
+\paragraph{experiment 2 training - relative
+distances}\label{experiment-2-training---relative-distances}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-64-1.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-64-2.pdf}
+
+\paragraph{Experiment 1 Testing - relative
+distances}\label{experiment-1-testing---relative-distances}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-65-1.pdf}
+
+\begin{verbatim}
+
+====================================================================================================================================
+conditType2         msdu_610       msdu_760       msdu_835       msdu_910      msds_610      msds_760      msds_835      msds_910   
+------------------------------------------------------------------------------------------------------------------------------------
+Constant Training 136.27(84.29) 191.65(112.65) 219.46(139.91) 276.75(153.09) 25.28(158.98) 50.82(217.48) 73.14(250.93) 50.76(313.77)
+Varied Training   105.12(51.39)  149.37(93.4)  180.54(129.52) 198.64(137.84) 13.85(116.87) 50.59(169.59) 50.52(217.39) 49.94(237.71)
+------------------------------------------------------------------------------------------------------------------------------------
+\end{verbatim}
+
+\begin{verbatim}
+
+=========================================================================
+Condition              610           760           835           910     
+-------------------------------------------------------------------------
+Constant Training 25.28(158.98) 50.82(217.48) 73.14(250.93) 50.76(313.77)
+Varied Training   13.85(116.87) 50.59(169.59) 50.52(217.39) 49.94(237.71)
+-------------------------------------------------------------------------
+\end{verbatim}
+
+\paragraph{Experiment 2 Testing - relative
+distances}\label{experiment-2-testing---relative-distances}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-66-1.pdf}
+
+\paragraph{Experimenet 1 - intermittent
+testing}\label{experimenet-1---intermittent-testing}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-67-1.pdf}
+
+\begin{verbatim}
+
+======================================================================================================
+Condition 610_First Half 760_First Half 910_First Half 610_Second Half 760_Second Half 910_Second Half
+------------------------------------------------------------------------------------------------------
+constant  206.64(82.08)  286.51(121.07) 406.93(145.2)   187.2(55.24)    238.21(95.16)  313.27(114.86) 
+varied    195.68(78.58)  278.9(105.37)  318.53(134.81)  177.79(70.82)  224.98(108.04)   276.86(110.5) 
+------------------------------------------------------------------------------------------------------
+\end{verbatim}
+
+\subsubsection{Training plots - Experiment
+1}\label{training-plots---experiment-1}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-68-1.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-68-2.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-68-3.pdf}
+
+\paragraph{Not in manuscript}\label{not-in-manuscript}
+
+\paragraph{fit to testing performance averaged across
+positions}\label{fit-to-testing-performance-averaged-across-positions}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-69-1.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-69-2.pdf}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-69-3.pdf}
+
+\paragraph{statistical tests for starting
+performance}\label{statistical-tests-for-starting-performance}
+
+\begin{verbatim}
+ANOVA Table (type III tests)
+
+      Effect DFn DFd F     p p<.05   ges
+1 conditType   1 206 3 0.083       0.015
+\end{verbatim}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-70-1.pdf}
+
+\paragraph{statistical tests for
+asymptote}\label{statistical-tests-for-asymptote}
+
+\begin{verbatim}
+ANOVA Table (type III tests)
+
+      Effect DFn DFd   F     p p<.05   ges
+1 conditType   1 206 3.4 0.067       0.016
+\end{verbatim}
+
+\includegraphics{full_files/figure-pdf/unnamed-chunk-71-1.pdf}
+
+\printbibliography[title=References]
+
+\end{document}

### 2024-04-04 Sections/Discussion.qmd
6 more datasets

@@
 
-## Comparison to Project 1
+Optional: - emphasize that both tasks involve extrapolation - it's just emphasized more in Project 2, and project 2 is designed to more closely mirror tasks used in the function learning literature.
+
+## Project comparison
+
+To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
+
+Task Structure - hitting target vs. hitting wall with correct force
+
+Feedback - relation between feedback and correction - usefulness of feedback was part of what makes HTW different from HTT.
+And in general in visuomotor learning tasks, feedback usually is not quite as precise as it is in HTW.
+- consistency of HTW finding across continuous vs.
+ordinal makes it seem like this wasn't the sole determinative factor.
+
+Form of Variation - varied vs.
+constant in both Projects.
+- varied group in HTT trained on 2 positions, whereas the varied group in HTW trained on 3 velocity bands.
+- In HTT - distinct positions, in HTW - distinct numbers.
 
@@
 
-- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments.
+-   HTW and HTT both have a similar amount of training trials (\~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments.
 However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands.
@@
 maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.
+
+------------------------------------------------------------------------
+
+\ \ \ \ \
+
+## General Discussion
+
+To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
+
+### Empirical Results Summary
+
+Across two projects, we investigated the influence of training variability on learning and generalization in visuomotor tasks.
+In Project 1 (HTT), we consistently found that varied training led to superior performance relative to constant training, even when testing at positions that were identical to the constant group's training.
+In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing.
+This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
+
+### Differences between the two Projects
+
+Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
+
+In HTT, the salient perceptual elements of the task (i.e.
+the launching box, target and barrier) are subject to variation (i.e.
+different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
+Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
+If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
+Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
+the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
+
+The HTT and HTW tasks also differed in terms of general task complexity.
+The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
+Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
+
+::: {#tbl-task-diff}
+
+| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
+| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
+| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
+| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
+Only x velocity is relevant.
+|
+| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
+| Simpler: smooth, linear mapping between velocity and feedback.
+|
+| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
+salient differences in distance between launching box and target.
+| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
+|
+| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
+|
+| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
+| Some potential for learning during no-feedback testing by observing ball trajectory.
+|
+| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
+| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
+|
+| Testing Structure                               | Random interleaving of trained/transfer testing distances.
+| Blocked structure, separately testing trained vs extrapolation testing bands.
+|
+
+Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
+:::
+
+\ \ \ \ \
+
+Rework the section on "Differences between the two Projects" include more speculation on how the perceptual distinctiveness of the task conditions may have memory or attentional consequences that relate to when training variation is useful.
+In particular discussing connections to ideas from instance based, or exemplar-based memory models of learning (e.g.
+works of Gordan Logan; Nosofsky; Crump, Hintzman, Estes etc.)
+
+## Tables
+
+**1h-mis**
+
+::: {#t1h}
+
+| Dimension                               | HTT (IGAS)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              | HTW (ALM & EXAM)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  |
+|----------------------------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
+| Task Complexity                        | In HTT, both x and y velocity dimensions are relevant to the outcome, requiring a parabolic trajectory.
+The task space is more complex, with the possibility of producing xy velocity combinations that are technically closer to the empirical solution space but result in worse feedback due to striking the barrier.
+| In HTW, only the x velocity dimension is relevant to the outcome, with the trajectory not mattering.
+The task space is simpler and smoother, with feedback directly related to the force applied.
+|
+| Dimensionality of Instance-Based Mechanisms | In HTT, the instance-based mechanisms might work well due to the task's multi-dimensional nature, making it easier to retain separate traces.
+| In HTW, instance-based mechanisms might not work as well due to the task's simple, 1-dimensional nature, making it more difficult to retain separate traces.
+|
+| Perceptual Distinctness of Conditions  | In HTT, the different varied conditions are more perceptually distinct and correspond directly to the task at hand (e.g., throwing from 500 vs.
+800).
+| In HTW, the difference between conditions for the varied group is only the number displayed at the top of the screen (e.g., 800-1000 or 1000-1200), which might be less salient.
+|
+| Feedback During Testing                 | In HTT, testing always includes feedback, except for intermittent testing in Experiment 1.
+| In HTW, the primary testing stage of interest has no feedback, with feedback testing occurring at the end but not focused on in the modeling work.
+|
+| Number of Training Positions/Velocities | In HTT, the varied group trains on 2 positions, while the constant group trains on 1 position.
+| In HTW, the varied group trains on 3 velocity bands, while the constant group trains on 1 velocity band.
+|
+| Testing Trial Order                    | In HTT, testing trials are randomly ordered, with participants experiencing trials from their training position and the training position of the other groups.
+| In HTW, no-feedback testing is split into 2 non-overlapping stages, with novel velocity bands encountered in a separate block from the testing of trained positions.
+|
+| Intermittent Testing Trials            | In HTT, intermittent testing trials are included in Experiment 1 with the ball trajectory fully masked.
+| In HTW, there are more no-feedback intermittent testing trials.
+|
+| Episodic Re-activation during Testing  | In HTT, episodic re-activation of training exemplars might occur more frequently due to the randomly ordered testing positions, which include trained positions.
+This could potentially benefit an episodic mechanism.
+| In HTW, the varied subjects are always further away in time and number of trials from re-encountering one of their training locations/bands during testing, which might reduce the potential benefits of episodic re-activation.
+|
+
+:::
+
+\ \ \
+
+**2a**
+
+::: {#t2a}
+
+| Dimension | Project 1 (HTT) | Project 2 (HTW) |
+|-----------|-----------------|-----------------|
+| Task Type | Projectile launching to hit a target | Projectile launching to hit a wall at a specific velocity |
+| Input Dimensions | Two velocity components (x and y), but only x velocity relevant for hitting the target | One velocity component (x) relevant for hitting the wall |
+| Output Dimensions | Distance from the target | Velocity at which the ball hits the wall |
+| Feedback Type | Continuous feedback indicating distance from the target | Continuous feedback indicating deviation from target velocity band (Exp.
+1 and 2); Ordinal feedback (too soft, too hard, or correct) (Exp.
+3) |
+| Generalization Type | Generalization to novel locations | Extrapolation to novel velocity bands |
+| Computational Models | Instance-based Generalization with Adaptive Similarity (IGAS) | Associative Learning Model (ALM) and Extrapolation-Association Model (EXAM) |
+| Model Assumptions | Adaptive tuning of generalization function based on training variability | ALM: Similarity-based generalization; EXAM: Linear extrapolation mechanism |
+| Statistical Analysis | Frequentist null hypothesis testing | Bayesian hierarchical modeling |
+:::
+
+\
+**2b**
+
+::: {#t2b}
+
+| Dimension | HTT (Project 1) | HTW (Project 2) |
+|-----------|-----------------|-----------------|
+| Task Type | Visuomotor Skill Learning | Visuomotor Function Learning |
+| Dependent Variable | Accuracy (Distance from Target) | Accuracy (Distance from Target Band) |
+| Training Manipulation | Constant vs. Varied Throwing Locations | Constant vs. Varied Velocity Bands |
+| Testing | Included both trained and novel throwing locations | Included both trained and novel velocity bands |
+| Modeling Approach | Instance-Based Similarity Model (IGAS) | Associative Learning Model (ALM), Extrapolation-Association Model (EXAM) |
+| Model Fitting | Fit to all participants, allowed generalization parameter to vary between conditions | Fit to individual participants using Approximate Bayesian Computation |
+| Key Findings | Varied training led to superior performance, accounted for by adaptive generalization gradient | Varied training led to poorer performance and less band discrimination, better captured by EXAM than ALM |
+| Novelty | First study to apply an instance-based similarity model to explain benefits of varied training in visuomotor skill learning | First study to investigate effects of training variability in a visuomotor function learning task |
+
+:::
+
+### Outline for "Empirical Results and Modeling Summary" Section
+
+1. **Introduction**
+   - State the section's purpose: to concisely summarize empirical findings and modeling analyses from two projects, HTT and HTW, focusing on the influence of training variability.
+   - Emphasize the integration of empirical data with computational modeling to deepen understanding of learning mechanisms.
+
+2. **Project 1 (HTT) Summary**
+   - **Empirical Results:**
+     - Briefly summarize key findings from Experiments 1 and 2, focusing on training variability's impact on learning and transfer.
+   - **IGAS Model Analysis:**
+     - Describe the Instance-Based Generalization and Adaptation (IGAS) model's role in explaining the empirical results, highlighting how it quantifies the impact of training variability.
+
+3. **Project 2 (HTW) Summary**
+   - **Empirical Results:**
+     - Outline major findings from Experiments 1, 2, and 3, detailing how training variability influenced extrapolation abilities.
+   - **Modeling Results (ALM & EXAM):**
+     - Discuss the application of the Associative Learning Model (ALM) and EXemplar-based Associative Memory (EXAM) model, focusing on their effectiveness in capturing the observed empirical patterns.
+
+4. **Comparative Analysis and Modeling Insights**
+   - Draw connections between empirical findings and model predictions across both projects.
+   - Discuss how modeling provides insights into the cognitive processes underpinning learning and generalization effects observed empirically.
+
+5. **Conclusions**
+   - Highlight the synthesis of empirical and modeling approaches in advancing understanding of training variability's impact.
+   - Suggest directions for future research, incorporating both experimental and computational perspectives.
+
+---
+
+### Empirical Results and Modeling Summary
+
+This summary encapsulates the empirical investigations and computational modeling efforts within the Hit The Target (HTT) and Hit The Wall (HTW) projects, emphasizing the nuanced role of training variability on visuomotor learning and generalization.
+
+**Project 1 (HTT)** explored spatial training variability's effects.
+**Empirical results** from Experiments 1 and 2 consistently showed that varied training enhances transfer performance, despite initial training challenges.
+The **Instance-Based Generalization and Adaptation (IGAS) model** was developed to interpret these results, offering a computational perspective that underscores the importance of specific training experiences in shaping generalization.
+By quantifying similarity across varied training instances, the IGAS model successfully explained why varied training could lead to superior transfer outcomes, validating the hypothesis that broader training experiences foster a more adaptable skill set.
+
+**Project 2 (HTW)** focused on velocity training variability and its influence on function learning tasks.
+**Empirical findings** across three experiments demonstrated varied training's differential effects on extrapolation capabilities, with notable variations depending on the specific conditions and feedback types.
+The **Associative Learning Model (ALM) and EXemplar-based Associative Memory (EXAM) models** were applied to these findings, elucidating the mechanisms behind the observed patterns.
+ALM highlighted the role of associative mechanisms in learning from varied velocity training, while EXAM offered insights into how exemplar-based memory processes might support extrapolation.
+Together, these models provided a comprehensive understanding of how varied training influences learning and extrapolation, showcasing the complexity of underlying cognitive processes.
+
+**Comparative analysis** between HTT and HTW, supported by the IGAS, ALM, and EXAM models, revealed the multifaceted nature of training variability's impact.
+While empirical data underscored the beneficial effects of variability on learning and generalization, the models offered a deeper understanding of the cognitive and memory-related mechanisms at play.
+Specifically, they suggested that the effectiveness of varied training might depend on the task's perceptual features and the cognitive operations required for task performance.
+
+**Conclusions** drawn from both the empirical and modeling efforts highlight the critical role of training variability in enhancing learning outcomes.
+The integration of computational models with empirical data not only validates the observed benefits of varied training but also advances our understanding of the cognitive foundations underlying these effects.
+Future research directions may include refining these models to capture additional nuances of learning processes and exploring their applicability to other learning domains.
+This holistic approach, combining empirical research with computational modeling, promises to yield rich insights into the complexities of learning and generalization.

### 2024-04-04 Sections/full.qmd
6 more datasets

@@
     echo: false
-    output: asis
+    output: false
     html-math-method: mathjax
@@
     echo: false
-    output-file: "hikmah-e1.pdf"
+    output-file: "tg_full_disser.pdf"
     mainfont: "Linux Libertine O"

### 2024-04-04 Sections/full.qmd
re-render with updated gen discussion

@@
 
-# General Discussion
+## Project 2 Discussion
 
@@
 
-## Comparison to Project 1
-
-### Differences between the tasks
-
-There are a number of differences between Project 1's Hit The Target (HTT), and Project 2's Hit The Wall (HTW) tasks.
-
-- Task Space Complexity: In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard.
-Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.
-
-- Perceptual Distinctiveness: HTT offers perceptually distinct varied conditions that directly relate to the task's demands, which may increase the sallience between training positions encounted by the varied group.
-In contrast, HTW's varied conditions differ only in the numerical values displayed, lacking the same level of perceptual differentiation.
-Conversely in HTW, the only difference between conditions for the varied group are the numbers displayed at the top of the screen which indicate the current target band(e.g.
-800-1000, or 1000-1200)
-
-- In HTW, our primary testing stage of interest has no feedback, whereas in HTT testing always included feedback (the intermittent testing in HTT expt 1 being the only exception).
-Of course, we do collect testing with feedback data at the end of HTW, but we haven't focused on that data at all in our modelling work thus far.
-It's also interesting to recall that the gap between varied and constant in HTW does seem to close substantially in the testing-with-feedback stage.
-The difference between no-feedback and feedback testing might be relevant if the benefits of variation have anything to do with improving subsequent learning (as opposed to subsequent immediate performance), OR if the benefits of constant training rely on having the most useful anchor, having the most useful anchor might be a lot less helpful if you're getting feedback from novel positions and can thus immediately begin to form position-specific anchors for the novelties, rather than relying on a training anchor.
-
-- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments.
-However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands.
-This means that in HTT the varied group gets half as much experience on any one position as the constant group, and in HTW they only get 1/3 as much experience in any one position.
-There are likely myriad ways in which this might impact the success of the varied group regardless of how you think the benefits of variation might be occurring, e.g.
-maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.
+## General Discussion
+
+To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
+
+### Empirical Results Summary
+
+Across two projects, we investigated the influence of training variability on learning and generalization in visuomotor tasks.
+In Project 1 (HTT), we consistently found that varied training led to superior performance relative to constant training, even when testing at positions that were identical to the constant group's training.
+In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing.
+This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
+
+### Differences between the two Projects
+
+Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
+
+In HTT, the salient perceptual elements of the task (i.e.
+the launching box, target and barrier) are subject to variation (i.e.
+different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
+Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
+If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
+Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
+the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
+
+The HTT and HTW tasks also differed in terms of general task complexity.
+The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
+Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
+
+::: {#tbl-task-diff}
+
+| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
+| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
+| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
+| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
+Only x velocity is relevant.
+|
+| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
+| Simpler: smooth, linear mapping between velocity and feedback.
+|
+| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
+salient differences in distance between launching box and target.
+| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
+|
+| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
+|
+| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
+| Some potential for learning during no-feedback testing by observing ball trajectory.
+|
+| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
+| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
+|
+| Testing Structure                               | Random interleaving of trained/transfer testing distances.
+| Blocked structure, separately testing trained vs extrapolation testing bands.
+|
+
+Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
+:::
 

### 2024-04-05 Sections/Discussion.qmd
re-render with updated gen discussion
fix minor formatting error in IGAS manuscript

--- 2024-02-28 Sections/Discussion.qmd
@@
 
-test
+Optional: - emphasize that both tasks involve extrapolation - it's just emphasized more in Project 2, and project 2 is designed to more closely mirror tasks used in the function learning literature.
+
+## Project comparison
+
+To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
+
+Task Structure - hitting target vs. hitting wall with correct force
+
+Feedback - relation between feedback and correction - usefulness of feedback was part of what makes HTW different from HTT.
+And in general in visuomotor learning tasks, feedback usually is not quite as precise as it is in HTW.
+- consistency of HTW finding across continuous vs.
+ordinal makes it seem like this wasn't the sole determinative factor.
+
+\ \ \ \ \
+
+## General Discussion
+
+To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
+
+### Summary
+
+Across both projects, we investigated the influence of training variability on learning and generalization in computerized visuomotor skill learning, and function learning tasks.
+In project 1 (HTT), experiments 1 and 2 demonstrated that varied training led to superior testing performance compared to constant training.
+In Experiment 1, the varied group even outperformed the constant group even when testing from the constant groups trained position.
+In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing.
+This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
+
+Both projects also contributed computational modeling componenents.
+
+### Differences between the two Projects
+
+Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
+
+In HTT, the salient perceptual elements of the task (i.e.
+the launching box, target and barrier) are subject to variation (i.e.
+different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
+Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
+If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
+Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
+the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
+
+The HTT and HTW tasks also differed in terms of general task complexity.
+The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
+Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
+*In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard.
+Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.*
+
+::: {#tbl-task-diff}
+
+| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
+| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
+| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
+| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
+Only x velocity is relevant.
+|
+| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
+| Simpler: smooth, linear mapping between velocity and feedback.
+|
+| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
+salient differences in distance between launching box and target.
+| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
+|
+| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
+|
+| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
+| Some potential for learning during no-feedback testing by observing ball trajectory.
+|
+| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
+| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
+|
+| Testing Structure                               | Random interleaving of trained/transfer testing distances.
+| Blocked structure, separately testing trained vs extrapolation testing bands.
+|
+
+Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
+:::
+
+\ \ \ \
+
+Rework the section on "Differences between the two Projects" include more speculation on how the perceptual distinctiveness of the task conditions may have memory or attentional consequences that relate to when training variation is useful.
+In particular discussing connections to ideas from instance based, or exemplar-based memory models of learning (e.g.
+works of Gordan Logan; Nosofsky; Crump, Hintzman, Estes etc.)
+
+### Empirical Results and Modeling Summary
+
+This summary encapsulates the empirical investigations and computational modeling efforts within the Hit The Target (HTT) and Hit The Wall (HTW) projects, emphasizing the nuanced role of training variability on visuomotor learning and generalization.
+
+**Project 1 (HTT)** explored spatial training variability's effects.
+**Empirical results** from Experiments 1 and 2 consistently showed that varied training enhances transfer performance, despite initial training challenges.
+The **Instance-Based Generalization and Adaptation (IGAS) model** was developed to interpret these results, offering a computational perspective that underscores the importance of specific training experiences in shaping generalization.
+By quantifying similarity across varied training instances, the IGAS model successfully explained why varied training could lead to superior transfer outcomes, validating the hypothesis that broader training experiences foster a more adaptable skill set.
+
+**Project 2 (HTW)** focused on velocity training variability and its influence on function learning tasks.
+**Empirical findings** across three experiments demonstrated varied training's differential effects on extrapolation capabilities, with notable variations depending on the specific conditions and feedback types.
+The **Associative Learning Model (ALM) and EXemplar-based Associative Memory (EXAM) models** were applied to these findings, elucidating the mechanisms behind the observed patterns.
+ALM highlighted the role of associative mechanisms in learning from varied velocity training, while EXAM offered insights into how exemplar-based memory processes might support extrapolation.
+Together, these models provided a comprehensive understanding of how varied training influences learning and extrapolation, showcasing the complexity of underlying cognitive processes.
+
+**Comparative analysis** between HTT and HTW, supported by the IGAS, ALM, and EXAM models, revealed the multifaceted nature of training variability's impact.
+While empirical data underscored the beneficial effects of variability on learning and generalization, the models offered a deeper understanding of the cognitive and memory-related mechanisms at play.
+Specifically, they suggested that the effectiveness of varied training might depend on the task's perceptual features and the cognitive operations required for task performance.
+
+**Conclusions** drawn from both the empirical and modeling efforts highlight the critical role of training variability in enhancing learning outcomes.
+The integration of computational models with empirical data not only validates the observed benefits of varied training but also advances our understanding of the cognitive foundations underlying these effects.
+Future research directions may include refining these models to capture additional nuances of learning processes and exploring their applicability to other learning domains.
+This holistic approach, combining empirical research with computational modeling, promises to yield rich insights into the complexities of learning and generalization.

### 2024-04-05 Sections/IGAS.qmd
fix minor formatting error in IGAS manuscript

@@
 
-Controlling for the similarity between training and testing The primary
+*Controlling for the similarity between training and testing.* The primary
 goal of Experiment 2 was to examine whether the benefits of variability

### 2024-04-05 Sections/Discussion.qmd
update with conclusion

@@
 
-Optional: - emphasize that both tasks involve extrapolation - it's just emphasized more in Project 2, and project 2 is designed to more closely mirror tasks used in the function learning literature.
-
-## Project comparison
-
 To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
 
-Task Structure - hitting target vs. hitting wall with correct force
-
-Feedback - relation between feedback and correction - usefulness of feedback was part of what makes HTW different from HTT.
-And in general in visuomotor learning tasks, feedback usually is not quite as precise as it is in HTW.
-- consistency of HTW finding across continuous vs.
-ordinal makes it seem like this wasn't the sole determinative factor.
-
-\ \ \ \ \
-
-## General Discussion
-
-To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
-
-### Summary
+### Empirical and Modeling Summary
 
@@
 In Experiment 1, the varied group even outperformed the constant group even when testing from the constant groups trained position.
-In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing.
+In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of training accuracy, accuracy in extrapolation testing,  and, in a subset of the experiments, the varied group showed a diminished ability to discriminate between bands.
 This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
 
-Both projects also contributed computational modeling componenents.
+Both projects also included computational modeling componenents.
+In Project 1, the IGAS model was introduced as a means of addressing the lack of control for similarity between training and testing conditions common to previous work in the "benefits of variability" literature.
+The IGAS model provides a theoretically motivated method of quantifying the similarity between training experience and testing conditions.
+The resulting similarity metric (i.e.
+our 1c-similarity) is shown to be a significant predictor of testing performance on its own, and when added as a covariate to the statistical model used to compare the constant and varied training groups.
+We then showed the group-level effect of training variability on testing performance can be accounted for with the additional assumption that training variability influences the generalization gradient.
+The contribution of the IGAS model was thus twofold:  1) providing a theoretically justifiable method of quantifying/controlling for similarity between training and testing, and 2) demonstrating the viability of a flexible-similarity based generalization account for the empirically observed benefit of variability in our task.
+Although similar approaches have been employed in other domains, both contributions are novel additions to the large body of research assessing the effect of constant vs.
+varied training manipulations in visuomotor skill tasks.
+
+Although theoretically motivated, the IGAS model of Project 1 is best categorized as a descriptive measurement-model.
+Sufficient to account for group differences, but lacking the machinery necessary to provide a full process-level account of how the empirical quantities of interest are generated.
+In contrast, Project 2 (HTW) implemented a more robust computational modeling approach, implementing and comparing full process models (ALM & EXAM), capable of generating predictions for both the learning and testing stages of the experiment.
+ALM and EXAM have been used as models of function learning, cue judgement, and forecasting behavior in numerous studies over the past 25 years [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @brownUnderestimationLinearFunction2017; @kwantesItemOrderMatters2012; @kelleyComparisonModelsLearning2008; @kaneApplicationsBiasVariance2020; @vonhelversenLearningMultiplecueJudgment2010].
+The present work presents the first application of these models to to the study of training variability in a visuomotor function learning task.
+We fit both models to individual participant data, using a form of simulation-based bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
+EXAM provided the best overall account of the testing data, and the advantage of EXAM over ALM was significantly greater for the constant group.
+Notably, EXAM captured the constant groups' ability to extrapolate linearly to novel velocity bands, despite receiving training from only a single input-output pair.
+This finding suggests that EXAM's linear extrapolation mechanism, combined with the assumption of prior knowledge about the origin point (0, 0), was sufficient to account for the constant groups' accurate extrapolation performance.
+Such findings may offer a preliminary suggestion that experience with a more variable set of training examples  may be detrimental to performance in simple extrapolation tasks.
 
@@
 
-Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
+The HTT and HTW tasks differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
 
@@
 Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
-*In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard.
-Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.*
+In HTW,the relationship between feedback and optimal behavioral adjustment is also almost perfectly smooth, if participants produce a throw that is 100 units too hard, they'll be told that they were 100 units away from the target band.
+Whereas in HTT, the presence of the barrier in introduces irregularities in the task space.
+Even throws close to the solution space might result in failure, creating a less predictable learning environment.
 
@@
 
+### Conclusion
+
+In summary, this dissertation provides a comprehensive examination of the effects of training variability on learning and generalization in visuomotor and function learning tasks.
+The contrasting results obtained from the Hit The Target (HTT) and Hit The Wall (HTW) tasks underscore the complexity inherent to the longstanding pedagogical and scientific goal of identifying training manipulations that consistently benefit learning and generalization.
+Moreover, through the development and application of computational models, we provide novel theoretical accounts for both the beneficial and detrimental effects of training variability observed in our experiments.
+These findings highlight the importance of considering task characteristics when designing experiments intended to assess the influence of training interventions, and demonstrate the value of combining empirical and computational modeling approaches to uncover the cognitive mechanisms that support learning and generalization.
+Future research should continue to investigate the complex interplay between task demands, training manipulations, and individual differences, with the ultimate goal of optimizing educational and training outcomes across a wide range of domains.
+
 \ \ \ \
-
-Rework the section on "Differences between the two Projects" include more speculation on how the perceptual distinctiveness of the task conditions may have memory or attentional consequences that relate to when training variation is useful.
-In particular discussing connections to ideas from instance based, or exemplar-based memory models of learning (e.g.
-works of Gordan Logan; Nosofsky; Crump, Hintzman, Estes etc.)
-
-### Empirical Results and Modeling Summary
-
-This summary encapsulates the empirical investigations and computational modeling efforts within the Hit The Target (HTT) and Hit The Wall (HTW) projects, emphasizing the nuanced role of training variability on visuomotor learning and generalization.
-
-**Project 1 (HTT)** explored spatial training variability's effects.
-**Empirical results** from Experiments 1 and 2 consistently showed that varied training enhances transfer performance, despite initial training challenges.
-The **Instance-Based Generalization and Adaptation (IGAS) model** was developed to interpret these results, offering a computational perspective that underscores the importance of specific training experiences in shaping generalization.
-By quantifying similarity across varied training instances, the IGAS model successfully explained why varied training could lead to superior transfer outcomes, validating the hypothesis that broader training experiences foster a more adaptable skill set.
-
-**Project 2 (HTW)** focused on velocity training variability and its influence on function learning tasks.
-**Empirical findings** across three experiments demonstrated varied training's differential effects on extrapolation capabilities, with notable variations depending on the specific conditions and feedback types.
-The **Associative Learning Model (ALM) and EXemplar-based Associative Memory (EXAM) models** were applied to these findings, elucidating the mechanisms behind the observed patterns.
-ALM highlighted the role of associative mechanisms in learning from varied velocity training, while EXAM offered insights into how exemplar-based memory processes might support extrapolation.
-Together, these models provided a comprehensive understanding of how varied training influences learning and extrapolation, showcasing the complexity of underlying cognitive processes.
-
-**Comparative analysis** between HTT and HTW, supported by the IGAS, ALM, and EXAM models, revealed the multifaceted nature of training variability's impact.
-While empirical data underscored the beneficial effects of variability on learning and generalization, the models offered a deeper understanding of the cognitive and memory-related mechanisms at play.
-Specifically, they suggested that the effectiveness of varied training might depend on the task's perceptual features and the cognitive operations required for task performance.
-
-**Conclusions** drawn from both the empirical and modeling efforts highlight the critical role of training variability in enhancing learning outcomes.
-The integration of computational models with empirical data not only validates the observed benefits of varied training but also advances our understanding of the cognitive foundations underlying these effects.
-Future research directions may include refining these models to capture additional nuances of learning processes and exploring their applicability to other learning domains.
-This holistic approach, combining empirical research with computational modeling, promises to yield rich insights into the complexities of learning and generalization.

### 2024-04-05 Sections/full.qmd
update with conclusion

@@
 
-## General Discussion
+# General Discussion
 
@@
 
-### Empirical Results Summary
-
-Across two projects, we investigated the influence of training variability on learning and generalization in visuomotor tasks.
-In Project 1 (HTT), we consistently found that varied training led to superior performance relative to constant training, even when testing at positions that were identical to the constant group's training.
-In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing.
+### Empirical and Modeling Summary
+
+Across both projects, we investigated the influence of training variability on learning and generalization in computerized visuomotor skill learning, and function learning tasks.
+In project 1 (HTT), experiments 1 and 2 demonstrated that varied training led to superior testing performance compared to constant training.
+In Experiment 1, the varied group even outperformed the constant group even when testing from the constant groups trained position.
+In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of training accuracy, accuracy in extrapolation testing,  and, in a subset of the experiments, the varied group showed a diminished ability to discriminate between bands.
 This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
 
+Both projects also included computational modeling componenents.
+In Project 1, the IGAS model was introduced as a means of addressing the lack of control for similarity between training and testing conditions common to previous work in the "benefits of variability" literature.
+The IGAS model provides a theoretically motivated method of quantifying the similarity between training experience and testing conditions.
+The resulting similarity metric (i.e.
+our 1c-similarity) is shown to be a significant predictor of testing performance on its own, and when added as a covariate to the statistical model used to compare the constant and varied training groups.
+We then showed the group-level effect of training variability on testing performance can be accounted for with the additional assumption that training variability influences the generalization gradient.
+The contribution of the IGAS model was thus twofold:  1) providing a theoretically justifiable method of quantifying/controlling for similarity between training and testing, and 2) demonstrating the viability of a flexible-similarity based generalization account for the empirically observed benefit of variability in our task.
+Although similar approaches have been employed in other domains, both contributions are novel additions to the large body of research assessing the effect of constant vs.
+varied training manipulations in visuomotor skill tasks.
+
+Although theoretically motivated, the IGAS model of Project 1 is best categorized as a descriptive measurement-model.
+Sufficient to account for group differences, but lacking the machinery necessary to provide a full process-level account of how the empirical quantities of interest are generated.
+In contrast, Project 2 (HTW) implemented a more robust computational modeling approach, implementing and comparing full process models (ALM & EXAM), capable of generating predictions for both the learning and testing stages of the experiment.
+ALM and EXAM have been used as models of function learning, cue judgement, and forecasting behavior in numerous studies over the past 25 years [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @brownUnderestimationLinearFunction2017; @kwantesItemOrderMatters2012; @kelleyComparisonModelsLearning2008; @kaneApplicationsBiasVariance2020; @vonhelversenLearningMultiplecueJudgment2010].
+The present work presents the first application of these models to to the study of training variability in a visuomotor function learning task.
+We fit both models to individual participant data, using a form of simulation-based bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
+EXAM provided the best overall account of the testing data, and the advantage of EXAM over ALM was significantly greater for the constant group.
+Notably, EXAM captured the constant groups' ability to extrapolate linearly to novel velocity bands, despite receiving training from only a single input-output pair.
+This finding suggests that EXAM's linear extrapolation mechanism, combined with the assumption of prior knowledge about the origin point (0, 0), was sufficient to account for the constant groups' accurate extrapolation performance.
+Such findings may offer a preliminary suggestion that experience with a more variable set of training examples  may be detrimental to performance in simple extrapolation tasks.
+
 ### Differences between the two Projects
 
-Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
+The HTT and HTW tasks differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
 
@@
 Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
+In HTW,the relationship between feedback and optimal behavioral adjustment is also almost perfectly smooth, if participants produce a throw that is 100 units too hard, they'll be told that they were 100 units away from the target band.
+Whereas in HTT, the presence of the barrier in introduces irregularities in the task space.
+Even throws close to the solution space might result in failure, creating a less predictable learning environment.
 
@@
 
+### Conclusion
+
+In summary, this dissertation provides a comprehensive examination of the effects of training variability on learning and generalization in visuomotor and function learning tasks.
+The contrasting results obtained from the Hit The Target (HTT) and Hit The Wall (HTW) tasks underscore the complexity inherent to the longstanding pedagogical and scientific goal of identifying training manipulations that consistently benefit learning and generalization.
+Moreover, through the development and application of computational models, we provide novel theoretical accounts for both the beneficial and detrimental effects of training variability observed in our experiments.
+These findings highlight the importance of considering task characteristics when designing experiments intended to assess the influence of training interventions, and demonstrate the value of combining empirical and computational modeling approaches to uncover the cognitive mechanisms that support learning and generalization.
+Future research should continue to investigate the complex interplay between task demands, training manipulations, and individual differences, with the ultimate goal of optimizing educational and training outcomes across a wide range of domains.
+
+\ \ \ \
+
 # References

### 2024-04-05 Sections/project_transition.qmd
update with conclusion

In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.

Optional: - emphasize that both tasks involve extrapolation - it's just emphasized more in Project 2, and project 2 is designed to more closely mirror tasks used in the function learning literature.

The HTT and HTW tasks also differed in terms of general task complexity. The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectile's velocity (and to a lesser extent, the position within the launching box at which the ball was released). Conversely, the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output responses are determined by a single input dimension. In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects; if they throw 100 units too hard, they'll be told that they were 100 units too hard. In contrast, in HTT, it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws but resulted in worse feedback due to striking the barrier.

### 2024-04-06 Sections/Appendix/E1_Appendix.qmd
render full in pdf and markdown

--- 2023-10-29 Appendix/E1_Appendix.qmd
@@
 # print(getwd())
-source(here::here("Functions", "packages.R"))
+#source(here::here("Functions", "packages.R"))
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
+  ggh4x,htmltools,future,furrr,ez)
 

### 2024-04-06 Sections/Discussion.qmd
render full in pdf and markdown

@@
 date: today
+format:
+  html: default
+  hugo-md:
+    #echo: false
+    #output: false
+    html-math-method: mathjax
+    output-file: dissc_hugo.md
+    mermaid-format: png
+  gfm:
+    #echo: false
+    output-file: dissc_gfm.md
+    mermaid-format: png
 ---
@@
 \ \ \ \
+
+### test
+
+```{r}
+#| echo: false
+#| include: false 
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+print(out_type)
+
+fmt_out <- knitr::pandoc_to()
+print(fmt_out)
+
+out_type %in% c("html","pdf")
+
+# out_type = "html"
+out_type == "html" || out_type == "pdf" || out_type == "docx"
+
+primary=out_type == "html" || out_type == "pdf" || out_type == "docx"
+
+ifelse(knitr::pandoc_to() %in% c("html","pdf","docx"), TRUE, FALSE)
+
+```
+
+::: {.content-visible unless-format="markdown"}
+```{dot}
+//| label: fig-design-e1
+//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
+//| fig-width: 7.0
+//| fig-height: 2.5
+//| fig-responsive: false
+//| echo: false 
+///| include: !expr "html" || out_type == "pdf" || out_type == "docx"
+
+/////| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+```
+:::

### 2024-04-06 Sections/Introduction.qmd
render full in pdf and markdown

--- 2024-04-04 Sections/full.qmd
@@
 ---
-title: Full Dissertation
-subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: 04/04/24
-#page-layout: full
-code-fold: true
-code-tools: true
-toc: true
-toc-location: body
-toc-title: Contents
-execute: 
-  warning: false
-  eval: true
+#title: Introduction
 format:
@@
     html-math-method: mathjax
-    output-file: diss_full_hugo.md
+    output-file: d_intro_hugo.md
   gfm:
     echo: true
-    output-file: diss_full_gfm.md
-  hikmah-manuscript-pdf:
-    echo: false
-    output-file: "tg_full_disser.pdf"
-    mainfont: "Linux Libertine O"
-    mainfontoptions:
-      - "Numbers=Proportional"
-      - "Numbers=OldStyle"
-    mathfont: "Libertinus Math"
-editor: 
-  markdown: 
-    wrap: 72
-prefer-html: true
+    output-file: d_into_gfm.md
 ---
@@
 The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.
-
-# Project 1
-
-____________________________________________________
-[pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
-
-```{r}
-
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
-  ggh4x,htmltools,future,furrr,ez)
-#options(brms.backend="cmdstanr",mc.cores=4)
-#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
-walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-#conflicts_prefer(tidybayes::rstudent_t)
-
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-#options(brms.backend="cmdstanr",mc.cores=4)
-initial_contrasts <- options("contrasts")$contrasts
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-
-library(tidybayes)
-
-theme_set(theme_classic())
-# load the processed data from experiment 1 and 2
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
-# defaultContrasts = options()$contrasts
-# theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-```
-
-# Abstract
-
-Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
-Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
-However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
-In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
-We replicate previous findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
-Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
-
-# Introduction
-
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
-The factor of interest to the present investigation is variation during training.
-Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
-We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
-We first review the relevant concepts and literature.
-
-## Similarity and instance-based approaches to transfer of learning
-
-Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances.
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar [@posnerGenesisAbstractIdeas1968].
-Prototype models were later challenged by the success of instance-based or exemplar models -- which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978;
-@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli.
-As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
-In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
-Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
-That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
-@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
-Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work -- variability of training examples.
-
-Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
-Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
-
-Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
-throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-## Issues with Previous Research
-
-Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g.
-projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
-more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
-
-```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
-
-p=2
-c<- .0002
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
-  group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
-
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
-
-```
-
-In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
-We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
-We then examine the extent to which this advantage can be explained by an instance-based similarity model.
-
-# Experiment 1
-
-## Methods
-
-### Sample Size Estimation
-
-To obtain an independent estimate of effect size, we identified previous
-investigations which included between-subjects contrasts of varied and
-constant conditions following training on an accuracy based projectile
-launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
-2009) was then used to determine that a power of 80% requires a sample
-size of at least 23 participants per condition. All experiments reported
-in the present manuscript exceed this minimum number of participants per
-condition.
-
-### Participants
-
-Participants were recruited from an undergraduate population that is 63%
-female and consists almost entirely of individuals aged 18-22 years. A
-total of 110 Indiana University psychology students participated in
-Experiment 1. We subsequently excluded 34 participants poor performance
-at one of the dependent measures of the task (2.5-3 standard deviations
-worse than the median subject at the task) or for displaying a pattern
-of responses that was clearly indicative of a lack of engagement with
-the task (e.g. simply dropping the ball on each trial rather than
-throwing it at the target), or for reporting that they completed the
-experiment on a phone or tablet device, despite the instructions not to
-use one of these devices. A total of 74 participants were retained for
-the final analyses, 35 in the varied group and 39 in the constant group.
-
-### Task
-
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-IGAS_Methods displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-```{r}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
-
-mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
-
-```
-
-## Results
-
-## Data Processing and Statistical Packages
-
-To prepare the data, we first removed trials that were not easily
-interpretable as performance indicators in our task. Removed trials
-included: 1) those in which participants dragged the ball outside of the
-orange starting box without releasing it, 2) trials in which
-participants clicked on the ball, and then immediately released it,
-causing the ball to drop straight down, 3) outlier trials in which the
-ball was thrown more than 2.5 standard deviations further than the
-average throw (calculated separately for each throwing position), and 4)
-trials in which the ball struck the barrier. The primary measure of
-performance used in all analyses was the absolute distance away from the
-center of the target. The absolute distance was calculated on every
-trial, and then averaged within each subject to yield a single
-performance score, for each position. A consistent pattern across
-training and testing phases in both experiments was for participants to
-perform worse from throwing positions further away from the target -- a
-pattern which we refer to as the difficulty of the positions. However,
-there were no interactions between throwing position and training
-conditions, allowing us to collapse across positions in cases where
-contrasts for specific positions were not of interest. All data
-processing and statistical analyses were performed in R version 4.03 (R
-Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021)****.
-
-## Training Phase
-
-@fig-IGAS_Training1 below shows aggregate training performance binned into three
-stages representing the beginning, middle, and end of the training
-phase. Because the two conditions trained from target distances that
-were not equally difficult, it was not possible to directly compare
-performance between conditions in the training phase. Our focus for the
-training data analysis was instead to establish that participants did
-improve their performance over the course of training, and to examine
-whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided
-in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and
-condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
-such that performance improved over the course of training There was no
-significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
-and no significant interaction between condition and training stage,
-F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
-
-```{r}
-#| label: fig-IGAS_Training1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
-
-```
-
-## Testing Phase
-
-In Experiment 1, a single constant-trained group was compared against a
-single varied-trained group. At the transfer phase, all participants
-were tested from 3 positions: 1) the positions(s) from their own
-training, 2) the training position(s) of the other group, and 3) a
-position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs. constant) as a
-between-subject factor and throwing location as a within-subject
-variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\<.001, η2G = .23. The effect of training condition was significant
-F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
-between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS_Testing1
-#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-IGAS_Table1
-#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- test=test[,1:3]
-
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
-
-In Experiment 1, we found that varied training resulted in superior
-testing performance than constant training, from both a position novel
-to both groups, and from the position at which the constant group was
-trained, which was novel to the varied condition. The superiority of
-varied training over constant training even at the constant training
-position is of particular note, given that testing at this position
-should have been highly similar for participants in the constant
-condition. It should also be noted, though, that testing at the constant
-trained position is not exactly identical to training from that
-position, given that the context of testing is different in several ways
-from that of training, such as the testing trials from the different
-positions being intermixed, as well as a simple change in context as a
-function of time. Such contextual differences will be further considered
-in the General Discussion.
-
-In addition to the variation of throwing position during training, the
-participants in the varied condition of Experiment 1 also received
-training practice from the closest/easiest position, as well as from the
-furthest/most difficult position that would later be encountered by all
-participants during testing. The varied condition also had the potential
-advantage of interpolating both of the novel positions from which they
-would later be tested. Experiment 2 thus sought to address these issues
-by comparing a varied condition to multiple constant conditions.
-
-# Experiment 2
-
-In Experiment 2, we sought to replicate our findings from Experiment 1
-with a new sample of participants, while also addressing the possibility
-of the pattern of results in Experiment 1 being explained by some
-idiosyncrasy of the particular training location of the constant group
-relative to the varied group. To this end, Experiment 2 employed the
-same basic procedure as Experiment 1, but was designed with six separate
-constant groups each trained from one of six different locations (400,
-500, 625, 675, 800, or 900), and a varied group trained from two
-locations (500 and 800). Participants in all seven groups were then
-tested from each of the 6 unique positions.
-
-## Methods
-
-### Participants
-
-A total of 306 Indiana University psychology students participated in
-Experiment 2, which was also conducted online. As was the case in
-experiment 1, the undergraduate population from which we recruited
-participants was 63% female and primarily composed of 18--22-year-old
-individuals. Using the same procedure as experiment 1, we excluded 98
-participants for exceptionally poor performance at one of the dependent
-measures of the task, or for displaying a pattern of responses
-indicative of a lack of engagement with the task. A total of 208
-participants were included in the final analyses with 31 in the varied
-group and 32, 28, 37, 25, 29, 26 participants in the constant groups
-training from location 400, 500, 625, 675, 800, and 900, respectively.
-All participants were compensated with course credit.
-
-### Task and Procedure
-
-The task of Experiment 2 was identical to that of Experiment 1, in all
-but some minor adjustments to the height of the barrier, and the
-relative distance between the barrier and the target. Additionally, the
-intermittent testing trials featured in experiment 1 were not utilized
-in experiment 2, and all training and testing trials were presented with
-feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
-
-The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the
-same position for the constant groups and split evenly (70 trials each -
-randomized) for the varied group. In the testing phase, participants
-completed 30 trials from each of the six locations that had been used
-separately across each of the constant groups during training. Each of
-the constant groups thus experience one trained location and five novel
-throwing locations in the testing phase, while the varied group
-experiences 2 previously trained, and 4 novel locations.
-
-## Results
-
-### Data Processing and Statistical Packages
-
-After confirming that condition and throwing position did not have any
-significant interactions, we standardized performance within each
-position, and then average across position to yield a single performance
-measure per participant. This standardization did not influence our
-pattern of results. As in experiment 1, we performed type III ANOVA's
-due to our unbalanced design, however the pattern of results presented
-below is not altered if type 1 or type III tests are used instead. The
-statistical software for the primary analyses was the same as for
-experiment 1. Individual learning rates in the testing phase, compared
-between groups in the supplementary analyses, were fit using the TEfit
-package in R [@cochraneTEfitsNonlinearRegression2020].
-
-### Training Phase
-
-The different training conditions trained from positions that were not
-equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. @fig-e2train depicts the training
-performance of the varied group alongside that of the aggregate of the
-six constant groups (5a), and each of the 6 separate constant groups
-(5b). An ANOVA comparison with training stage (beginning, middle, end)
-as a within-group factor and group (the varied condition vs. the 6
-constant conditions collapsed together) as a between-subject factor
-revealed no significant effect of group on training performance,
-F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
-stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
-interaction between group and training stage, F(2,412)=.489 p=.61,
-$\eta^{2}_G$ \<.01. We also tested for a difference in training
-performance between the varied group and the two constant groups that
-trained matching throwing positions (i.e., the constant groups training
-from position 500, and position 800). The results of our ANOVA on this
-limited dataset mirrors that of the full-group analysis, with no
-significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
-significant effect of training stage F(2,172)=56.29, p\<.001,
-$\eta^{2}_G$ =.11, and no significant interaction between group and
-training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
-
-```{r}
-
-e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
-
-exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
-
-exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
-
-exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
-
-exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
-
-transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
-
-# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
-# novelAll <- novelAll %>% group_by(positionX) %>%
-#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
-novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
-
-constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
-variedTest <- transfer %>% filter(condit==7) # only varied testing
-variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
-
-variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
-constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
-variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
-
-exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-```
-
-```{r}
-#| label: fig-e2train
-#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
-On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 8
-
-### New - 3 stage
-e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
-  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
-  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
-
-e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
-  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
-
-#plot_grid(e2train1,e2train2,ncol=1)
-
-e2train1/e2train2
-
-```
-
-### Testing Phase
-
-In Experiment 2, a single varied condition (trained from two positions,
-500 and 800), was compared against six separate constant groups (trained
-from a single position, 400, 500, 625, 675, 800 or 900). For the testing
-phase, all participants were tested from all six positions, four of
-which were novel for the varied condition, and five of which were novel
-for each of the constant groups. For a general comparison, we took the
-absolute deviations for each throwing position and computed standardized
-scores across all participants, and then averaged across throwing
-position. The six constant groups were then collapsed together allowing
-us to make a simple comparison between training conditions (constant vs.
-varied). A type III between-subjects ANOVA was performed, yielding a
-significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
-=.02. Descriptive statistics for each condition are shown in table 2. In
-@fig-e2testa visualizes the consistent advantage of the varied condition
-over the constant groups across the testing positions. @fig-e2testa shows
-performance between the varied condition and the individual constant
-groups.
-
-```{r}
-#| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 9
-
-# manuscript plot
-e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)+
-  ggtitle("A")
-
-e2test2<-exp2.Test7 %>% 
-  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
-  facet_wrap(~ThrowPosition4)+
-  ylab("Mean Distance From Center Of Target")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
-
-e2test1 / e2test2
-
-```
-
-\
-\
-\
-
-```{r}
-#| label: tbl-e2table1
-#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-
-tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab2=tab2[,1:3]
-
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
-.02 .
-
-```{r}
-#| label: tbl-e2table2
-#| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-
-sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
- tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
- tab3 = tab3 %>% 
-   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab3=tab3[,1:3]
-
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
-
-Finally, corresponding to the comparison of position 760 from experiment
-1, we compared the test performance of the varied group against the
-constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis
-omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). @fig-e2test1 displays
-the particular subset of comparisons utilized for this analysis. Again,
-we standardized performance within each position before performing the
-analyses on the aggregated data. In this case, the effect of condition
-did not reach statistical significance F(1,149)=3.14, p=.079,
-$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
-
-```{r}
-#| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-
-sum.variedVsNovelIden <- variedVsNovelIden  %>%
-  group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
-
-e2Test2
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-e2tab3
-#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-
-tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
-tab4=tab4 %>% group_by(Condition) %>% 
-   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab4=tab4[,1:3]
-
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
-
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
-
-# Computational Model
-
-Controlling for the similarity between training and testing The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
-
-```{r}
-#| label: fig-taskSpace
-#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig-width: 11
-#| fig-height: 9
-#| 
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
-  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
-
-library(patchwork)
-ss/fs
-
-```
-
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
-
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
-(e^{-c^\cdot d^{p}_{i,j}}) $$
-
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-
-A simple linear regression revealed that these similarity scores were
-significantly predictive of performance in the transfer stage, t
-=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
-training throws and solution spaces for each of the test locations
-resulted in better performance. We then repeated the group comparisons
-above while including similarity as a covariate in the model. Comparing
-the varied and constant groups in testing performance from all testing
-positions yielded a significant effect of similarity, F(1, 205)=85.66,
-p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
-(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
-group comparison limited to only novel locations for the varied group
-pit against trained location for the constant group resulted in a
-significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
-=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
-=.07. For all comparisons, the pattern of results was consistent with
-the initial findings from experiment 2, with the varied group still
-performing significantly better than the constant group.
-
-## Fitting model parameters separately by group
-
-To directly control for similarity in Experiment 2, we developed a
-model-based measure of the similarity between training throws and
-testing conditions. This similarity measure was a significant predictor
-of testing performance, e.g., participants whose training throws were
-more similar to throws that resulted in target hits from the testing
-positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level
-benefits of varied training, which remained significant in our linear
-model predicting testing performance after similarity was added to the
-model. However, previous research has suggested that participants may
-differ in their level of generalization as a function of prior
-experience, and that such differences in generalization gradients can be
-captured by fitting the generalization parameter of an instance-based
-model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
-will increase when a rational agent encounters a wider variety of
-examples. Following these leads, we assume that in addition to learning
-the task itself, participants are also adjusting how generalizable their
-experience should be. Varied versus constant participants may be
-expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the
-instance-based model (in the present case, the c parameter) can be
-allowed to vary between the two groups to reflect the tendency of
-learners to adaptively tune the extent of their generalization. One
-specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
-variable, as with the variable training condition, then one might infer
-that future test situations will also be variable, in which case a low
-value of c will allow better generalization because generalization will
-drop off slowly with training-to-testing distance. Conversely, if one's
-training experience has little variability, as found in the constant
-training conditions, then one might adopt a high value of c so that
-generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based
-model of similarity fit against a modified model which separately fits
-the generalization parameter, c, to varied and constant participants. To
-perform this parameter fitting, we used the optim function in R, and fit
-the model to find the c value(s) that maximized the correlation between
-similarity and testing performance.
-
-Both models generate distinct similarity values between training and
-testing locations. Much like the analyses in Experiment 2, these
-similarity values are regressed against testing performance in models of
-the form shown below. As was the case previously, testing performance is
-defined as the mean absolute distance from the center of the target
-(with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\<.01). Of greater interest is the
-difference between linear model 2, in which similarity is computed from
-a single c value fit from all participants (Similarity1c), with linear
-model 4, which fits the c parameter separately between groups
-(Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\<.01), with the varied
-group still performing significantly better. However, in linear model 4
-the addition of the Similarity2c predictor results in the effect of
-training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs. constant training is accounted for by the
-Similarity2c predictor. Next, to further establish a difference between
-the models, we performed nested model comparisons using ANOVA, to see if
-the addition of the training group parameter led to a significant
-improvement in model performance. In the first comparison, ANOVA(Linear
-Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear
-Model 4) found no improvement in model performance with the addition of
-the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the
-adjusted Similarity2c model had more predictive power than those
-generated from the original Similarity1c model. Using the BIC function
-in R, we compared BIC values between linear model 1 (BIC=14604.00) and
-linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
-a modest advantage for predicting performance using a similarity measure
-computed with two c values over similarity computed with a single c
-value. When fit with separate c values, the best fitting c parameters
-for the model consistently optimized such that the c value for the
-varied group (c=.00008) was smaller in magnitude than the c value for
-the constant group(c= .00011). Recall that similarity decreases as a
-Gaussian function of distance (equation 1 above), and a smaller value of
-c will result in a more gradual drop-off in similarity as the distance
-between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which
-assumes equivalent generalization gradients between constant and varied
-trained participants is unable to account for the extent of benefits of
-varied over constant training observed at testing. The evidence for this
-in the comparative model fits is that when a varied/constant dummy-coded
-variable for condition is explicitly added to the model, the variable
-adds a significant contribution to the prediction of test performance,
-with the variable condition yielding better performance than the
-constant conditions. However, if the instance-based generalization model
-is modified to assume that the training groups can differ in the
-steepness of their generalization gradient, by incorporating a separate
-generalization parameter for each group, then the instance-based model
-can account for our experimental results without explicitly taking
-training group into account. Henceforth this model will be referred to
-as the Instance-based Generalization with Adaptive Similarity (IGAS)
-model.
-
-# General Discussion
-
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy-Model-dis we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model-dis
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
-For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
-The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
-#| fig.width: 11
-#| fig.height: 11.5
-
-#
-
-p=2
-c<- .000002
-
-trainingTestingDifference=2000;
-cvaried=.00002
-cconstant=.0005
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
-                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
-                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
-                            ) %>% 
-  group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
-
-#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
-
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
-ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
-ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
-ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
-# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
-
-#gtitle="Figure 9."
-#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-p1 <- (ip1+ip2) / (ip3+ip4)
-
-p1
-
-```
-
-As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
-However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning implementations of instance-based models in several ways.
-One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define a category item (e.g.
-size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
-movement force, velocity, angle, posture) in addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in
-support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
-Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
-Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
-A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
-lighting up consecutively, and attempt to time a button press with the
-onset of the final lamp. The design consisted of four separate constant
-groups, each training from a single lighting velocity, and a single
-varied group training with all four of the lighting velocities used by
-the individual constant groups. Participants were then split into four
-separate testing conditions, each of which were tested from a single
-novel lighting velocity of varying distance from the training
-conditions. The result of primary interest was that all participants
-performed worse as the distance between training and testing velocity
-increased -- a typical generalization decrement. However, varied
-participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in
-a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are
-similar to our own, our work is novel in that we account for our results
-with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their
-separate constant groups together may result in similarity confounds
-between varied and constant conditions that leaves their study open to
-methodological criticisms, especially in light of related work which
-demonstrated that the extent to which varied training may be beneficial
-can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
-similarity.
-
-## Limitations
-
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
-
-## Conclusion
-
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
-
-# Project 2
-
-_______________________________________________________________________________
-[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
-
-[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
-
-_______________________________________________________________________________
-
-# Introduction
-
-A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
-One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ].
-The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
-
-## Function Learning and Extrapolation
-
-The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
-
-@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
-Input stimuli and output responses were both lines of varying length.
-The correct output response was related to the length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
-@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
-Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
-In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
-All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
-
-The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
-The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models.
-The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
-The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
-When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
-
-### Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
-
-```{r}
-#| label: fig-delosh-extrap
-#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
-#| echo: false
-#| fig-width: 10
-#| cache: false 
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-source(here::here("Functions","deLosh_data.R"))
-#source(here::here("Functions","Display_Functions.R"))
-
-extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
-                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
-
-linear_function <- function(x) 2.2 * x + 30
-exponential_function <- function(x) 200 * (1 - exp(-x/25))
-quadratic_function <- function(x) 210 - (x - 50)^2 / 12
-
-linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
-    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
-  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
-
-exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
-  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
-  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
-  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
-  extrapLines +
-  scale_shape_manual(values = c(1)) +
-  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
-  theme(legend.title = element_blank(), legend.position="top") +
-  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
-                                                  linetype = c(0, 1))))
-
-quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
-  geom_point( shape = 1) +
-  stat_function( fun = quadratic_function, geom = "line") +
-  labs(title="Quadratic Function",x="",y="") + extrapLines
-
-linear_plot + exponential_plot + quadratic_plot
-```
-
-## Overview Of Present Study
-
-The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
-To the best of our knowledge, this research is the first to employ the classic constant vs.
-varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
-Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
-
-To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
-Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.
-
-## Methods
-
-*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
-Participants were randomly assigned to one of two training conditions: varied training or constant training.
-
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
-band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
-Participants were instructed that only the x velocity component of the ball was relevant to the task.
-The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
-
-/
-```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
-#| label: fig-htw-task
-#| fig-cap: The Hit the wall task.
-Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
-The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
-#| eval: true
-#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
-knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
-
-```
-
-*Procedure.* All participants completed the task online.
-Participants were provided with a description of the experiment and indicated informed consent.
-@fig-design-e1 illustrates the general procedure.
-Participants completed a total of 90 trials during the training stage.
-In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
-
-Following the training stage, participants proceeded immediately to the testing stage.
-Participants were tested from all six velocity bands, in two separate stages.
-In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
-In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
-A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
-
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
-//| fig-responsive: false
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-```
-
-```{r}
-
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e1 <- readRDS(here("data/e1_08-21-23.rds")) 
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-testE1 <- e1 |> filter(expMode2 == "Test")
-nbins=5
-trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
-trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
-```
-
-### Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.32 @rcoreteamLanguageEnvironmentStatistical2020.
-To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
-Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
-Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
-For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
-
-| Group Comparison         | Code                                                        | Data                 |
-| ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
-\
-
-In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
-extrapolation bands); 3) extent of discrimination between all six testing bands.
-We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
-Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
-The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
-Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-### Results
-
-```{r}
-#| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-##| label: tbl-e1-train-dist
-##| tbl-cap: "Experiment 1 - Learning curves. "
-##| output: asis
-
-bmm_e1_train<- trainE1_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e1_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#    kable(booktabs = TRUE)
-
-cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
-```
-
-::: {#tbl-e1-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
-| conditVaried |    79.64 |         57.92 |        101.63 |   1 |
-
-: **Experiment 1 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band.
-To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on.
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
-
-```{r}
-##| label: tbl-e1-bmm-dist
-##| tbl-cap: "E1. Training vs. Extrapolation"
-#| 
-modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
-bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE1, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-# 
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-
-# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
-cdted1 <- get_coef_details(bmtd, "conditVaried")
-cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
-cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e1-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:------------------------|-----------:|-----------:|-----------:|-----------:|
-| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
-| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
-| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
-| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |
-
-: **Experiment 1 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficients  indicate larger deviations from the baselines (Condition=constant & bandType=Trained) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
-constant) and band type (trained vs.
-extrapolation), with random intercepts for participants and bands.
-The model results are shown in @tbl-e1-bmm-dist.
-The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`).
-The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`).
-Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% credible intervals.
-
-pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-
-```
-
-```{r}
-##| label: tbl-e1-bmm-vx
-##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)
-
-cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e1_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-```
-
-\
-
-::: {#tbl-e1-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
-| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
-| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
-| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |
-
-Experiment 1.
-Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
-Varied) and Velocity Band.
-Larger coefficients on Band represent greater sensitivity/discrimination.
-{.striped .hover .sm}
-:::
-
-Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
-Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
-This difference is depicted visually in @fig-e1-test-vx.
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: Empirical distribution of velocities producing in testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-
-testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
-#| fig-cap: Experiment 1.
-Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE1$vb), 
-                     limits = c(0, 1400)) + 
-  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e1_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e1Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-     theme(legend.title=element_blank(), 
-           axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-## E1 Summary
-
-In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions  rresulted in lower final training performance is consistent with much of the prior researchon the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
-
-More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.
-
-## Experiment 2
-
-```{r}
-
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e2 <- readRDS(here("data/e2_08-04-23.rds")) 
-e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
-testE2 <- e2 |> filter(expMode2 == "Test")
-nbins=5
-trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
-
-# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
-```
-
-### Methods & Procedure
-
-The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
-The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800.
-Both groups were tested from all six bands.
-A total of 110 participants completed the experiment (Varied: 55, Constant: 55).
-
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 8.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| 
-//| 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
-
-### Results
-
-```{r}
-#| label: fig-e2-train-dev
-#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-#| eval: TRUE
-p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-bmm_e2_train <- trainE2_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e2_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
-# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T) 
-```
-
-::: {#tbl-e2-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
-| conditVaried |    36.15 |         16.35 |         55.67 |   1 |
-
-: **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups.
-We again compared training performance on the band common to both groups (600-800).
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
-```{r}
-modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
-bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE2, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
-cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
-cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e2-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-----------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
-| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
-| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
-| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |
-
-: **Experiment 2 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-\ \
-
-*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
-Constant) and band type (training vs.
-extrapolation bands).
-The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`).
-However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-#| eval: TRUE
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e2-bmm-vx
-##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
-
-cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
-sc2 <- get_coef_details(e2_vxBMM, "bandInt")
-intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
-```
-
-::: {#tbl-e2-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
-| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
-| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
-| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
-
-Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-The full model results are shown in @tbl-e2-bmm-vx.
-The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
-The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).
-
-```{r}
-#| label: fig-e2-test-vx
-#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e2-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-}
-
-pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE2$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e2_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e2Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-      theme(legend.title=element_blank(), 
-        axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-### Experiment 2 Summary
-
-Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands.
-Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.
-
-## Experiment 3
-
-```{r}
-
-e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
-    mutate(trainCon=case_when(
-    bandOrder=="Original" ~ "800",
-    bandOrder=="Reverse" ~ "600",
-    TRUE ~ NA_character_
-    ), trainCon=as.numeric(trainCon)) 
-e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
-testE3 <- e3 |> filter(expMode2 == "Test")
-nbins=5
-trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
-
-```
-
-### Methods & Procedure
-
-The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
-After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.
-within the target velocity range).
-All other aspects of the task and design are identical to Experiments 1 and 2.
-We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied).
-Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
-Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.
-
-### Results
-
-```{r}
-
-bmm_e3_train <- trainE3_max %>% 
-  brm(dist ~ condit*bandOrder, 
-      file=here("data/model_cache/e3_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
-cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
-cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
-```
-
-::: {#tbl-e3-train-dist}
-
-| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
-| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
-| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
-| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |
-
-: **Experiment 3 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-*Training*.
-@fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions).
-The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`).
-The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).
-
-```{r}
-#| label: fig-e3-train-dev
-#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
-#| eval: true
-p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
-p1
-```
-
-```{r}
-#options(brms.backend="cmdstanr",mc.cores=4)
-modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
-bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
-    data=testE3, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
-#wrap_plots(ce_bmtd3)
-
-#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")
-
-cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
-cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
-cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
-cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
-cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
-cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
-cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")
-
-```
-
-::: {#tbl-e3-bmm-dist}
-| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
-| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
-| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
-| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
-| conditVaried:bandTypeExtrapolation                  |    52.66 |         14.16 |         90.23 | 1.00 |
-| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
-| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
-| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |
-
-: **Experiment 3 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
-There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
-However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`.
-The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group.
-There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands.
-No other interactions were significant.
-
-<!-- ::: {#fig-e3-test-condEffect}
-
-![](../Assets/figs/e3_cond_effects_dist.png)
-
-E3.
-A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-::: -->
-
-```{r}
-#| label: fig-e3-test-dev
-#| fig-cap: Experiment 3 Testing Accuracy.
-A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% confidence intervals.
-#| eval: true
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-    facet_wrap(~bandOrder,ncol=1) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
- facet_wrap(~bandOrder,ncol=1)
-
-p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e3-bmm-vx
-##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
-# m2 <- fixef(e3_vxBMM)
-# mp3 <- m1[, c(1,2,4,5,6)]
-# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
-# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
-coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")
-
-```
-
-::: {#tbl-e3-bmm-vx}
-
-| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
-| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
-| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
-| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |
-
-Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist.
-For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
-The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
-Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
-However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating that the varied condition showed a greater slope coefficient on the reverse order bands, compared to the constant condition - this is clearly shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 10
-##| column: screen-inset-right
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-```
-
-```{r}
-#| label: fig-e3-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 10
-#| fig-width: 11
-##| eval: FALSE
-# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  facet_wrap(~bandOrder,ncol=1) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e3_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
-fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
-fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
-
-re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e3Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
-           fixed_effect_interaction2*(bandOrder=="Reverse") + 
-           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
-  slope = Estimate + adjust )
-
-pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density") +
-  facet_wrap(~bandOrder,ncol=1)
-
-pid_slopes3 <- re |>  
-    mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-    theme(legend.title=element_blank(), 
-      axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
-
-p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
-
-#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
-p3
-
-```
-
-### Experiment 3 Summary
-
-## Computational Model
-
-```{r}
-####| cache: false
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-```
-
-```{r}
-###| cache: true
-invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
-invisible(list2env(load_e1(), envir = .GlobalEnv))
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-e2_model <- load_e2()
-e3_model <- load_e3()
-options(contrasts = initial_contrasts)
-
-```
-
-```{r}
-#| label: fig-alm-diagram
-#| fig.cap: The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model as used in the present work.
-Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
-The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
-The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule.
-alm_plot()
-```
-
-# Modeling Approach
-
-The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997].
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
-EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
-Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
-EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
-The slope is then used to extrapolate the response to the novel test stimulus.
-Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
-We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
-This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
-
-See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
-
-::: column-page-inset-right
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-|                    | **EXAM Extrapolation**                                             |                                                                                               |
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
-| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |
-
-: ALM & EXAM Equations {#tbl-alm-exam}
-:::
-
-## Model Fitting
-
-To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
-We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant.
-The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
-Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.
-
-::: {.callout}
-
-**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
-
-To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
-ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
-Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g.
-many neural network models).
-
-The general ABC procedure is to 1) define a prior distribution over model parameters.
-2) sample candidate parameter values, $\theta^*$, from the prior.
-3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
-4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
-5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
-6) Repeat until desired number of posterior samples are obtained.
-
-Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
-For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
-For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
-For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
-After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
-For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
-
-::: column-page-inset-left
-$$
-discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
-$$ {#eq-discrep-test}
-
-$$
-\begin{aligned} \\
-discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
-discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
-\end{aligned}
-$$ {#eq-discrep-train}
-:::
-
-The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
-The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
-Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
-Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
-The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
-Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
-After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
-In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
-To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
-:::
-
-For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution.
-Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant.
-Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs.
-To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.
-
-### Modelling Results
-
-#### Group level Patterns
-
-```{r}
-#| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-post_tabs <- abc_tables(post_dat,post_dat_l)
-train_tab <- abc_train_tables(pd_train,pd_train_l)
-
-e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
-
-e1_tab %>%
-  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
-  summarize(ME = mean(mean_error), .groups = "drop") %>%
-  pivot_wider(
-    names_from = c(Model, condit),
-    values_from = ME,
-    names_sep = "_"  # Add this line to specify the separator for column names
-  ) %>%
-  rename("Fit Method" = Fit_Method) %>%
-  gt() %>%
-  cols_move_to_start(columns = c(`Task Stage`)) %>%
-  cols_label(
-    `Task Stage` = "Task Stage"
-  ) %>%
-  fmt_number(
-    columns = starts_with("ALM") | starts_with("EXAM"),
-    decimals = 2
-  ) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = cell_fill(color = "white"),
-     locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_style(
-    style = cell_borders(sides = "top", color = "black", weight = px(1)),
-    locations = cells_column_labels()
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10, 
-    quarto.disable_processing = TRUE
-  ) 
-```
-
-```{r}
-#| label: fig-htw-post-dist
-#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters.
-Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y axes of the plots for the c parameter are scaled logarithmically."
-#| fig-height: 6
-#| fig-width: 10
-
-c_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
-  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
-
-lr_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
-  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
-c_post + lr_post
-```
-
-```{r}
-#| label: fig-htw-resid-pred
-#| fig-cap: "Model residuals for each combination of training condition, fit method, and model.
-Residuals reflect the difference between observed and predicted values.
-Lower values indicate better model fit.
-Note that y axes are scaled differently between facets.
-A) Residuals predicting each block of the training data.
-B) Residuals predicting each band during the testing stage.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-#| fig-height: 14
-#| fig-width: 11
-
-train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
-  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
-  group_by(id,condit,Model,Fit_Method,Block) |>
-  summarise(mean_error=mean(mean_error)) |>
-  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
-  stat_bar + 
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
-   scale_x_discrete(guide = "axis_nested") +
-  scale_fill_manual(values=c("gray10","gray50","gray92"))+
-  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
-  theme(legend.position="top")
-
-test_resid <-  post_dat |> 
-   group_by(id,condit,x,Model,Fit_Method,bandType) |>
-    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
-  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
-  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
-  scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
-  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")
-
-(train_resid / test_resid) +
-  #plot_layout(heights=c(1,1.5)) & 
-  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
-```
-
-The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat.
-There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences.
-The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
-
-We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model.
-Aggregated residuals are displayed in @fig-htw-resid-pred.
-The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method .
-Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms).
-The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models.
-It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task.
-Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories.
-However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data.
-All subsequent analyses and discussion will thus focus on the testing stage.
-
-The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots).
-Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
-The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models.
-Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.
-
-```{r}
-#| label: fig-cm-vx-pat
-#| fig-cap: "Empirical data and Model predictions for mean velocity across target bands.
-Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs.
-Varied) are separated by columns.
-Each facet contains the predictions of ALM and EXAM, alongside the observed data."
-#| fig-height: 10
-#| fig-width: 10
-
-post_dat_l |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> 
- #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
- ggplot(aes(x=Resp,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-    facet_wrap(~rename_fm(Fit_Method)+condit, ncol=2,strip.position = "top", scales = "free_x") +
-        scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-         strip.background = element_blank(),
-         strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(10,0,0,0), "pt")) + 
-         labs(title="Model Predictions - Experiment 1 Data", y="Vx")
-```
-
-```{r}
-#| label: fig-ee-e1
-#| fig-caption: conditional and marginal effects
-#| fig-height: 8
-#| fig-width: 10
-###| eval: false
-
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
-  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
-e1_ee_brm_ae <- brm(data=pdl,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-
-# plot_custom_effects <- function(model) {
-#   # Extract posterior samples for fixed effects
-#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
-
-#   # Calculate conditional effects
-#   post_samples <- post_samples %>%
-#     mutate(
-#       ALM_Constant = b_Intercept,
-#       EXAM_Constant = b_Intercept + b_ModelEXAM,
-#       ALM_Varied = b_Intercept + b_conditVaried,
-#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
-#     )
-
-#   # Reshape data for plotting
-#   plot_data <- post_samples %>%
-#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
-#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
-#     separate(Condition, into = c("Model", "Condit"), sep = "_")
-
-#   # Plot conditional effects
-#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
-#     geom_boxplot() +
-#     theme_minimal() +
-#     labs(x = "Model", y = "Estimate", color = "Condition")
-# }
-# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
-
-bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
-bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
-bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")
-
-posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
-  select(starts_with("b_")) %>%
-  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))
-
-constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
-varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
-comparison_EXAM <- constant_EXAM - varied_EXAM
-summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
-
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)
-
-# full set of Model x condit contrasts
-# ALM - EXAM
-# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
-#   pluck("contrasts") |> 
-#   gather_emmeans_draws() |> 
-#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
-
-# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()
-
-# Constant - Varied
-# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
-# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
-#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
-# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
-
-p_em_1 <- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
-  pluck("contrasts") |>
-  gather_emmeans_draws() |> 
-  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
-  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
-  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")
-
-p_ce_1 / p_em_1
-```
-
-To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
-EXAM) and training condition (Constant vs.
-Varied).
-
-Model errors were significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM.
-There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group.
-To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
-The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
-
-```{r}
-#| label: tbl-htw-modelError-e23
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-
-post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
-train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
-
-pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e2_tab <- rbind(post_tabs2$agg_pred_full |>
- mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
- mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
-train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
-
-pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e3_tab <- rbind(post_tabs3$agg_pred_full |> 
-  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
-gt_table <- e23_tab %>%
-  pivot_wider(
-    names_from = c(Exp, Model, condit),
-    values_from = mean_error,
-    names_glue = "{Exp}_{Model}_{condit}"
-  ) %>%
-  arrange(Fit_Method, `Task Stage`) %>%
-  gt() %>%
-  cols_move_to_start(columns = `Task Stage`) %>%
-  cols_label(`Task Stage` = "Task Stage") %>%
-  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = list(
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
-  ) 
-gt_table
-```
-
-```{r}
-#| label: fig-cm-vx-pat-e2-e3
-#| fig-height: 8
-#| fig-width: 10
-#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage.
-Observed data is shown on the right.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-
-rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
- e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
-  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
-  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
-  stat_bar + 
-    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
-    scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .7), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-        #  strip.background = element_blank(),
-        #  strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(20,0,0,0), "pt")) + 
-         labs(title="Model Predictions Experiment 2 & 3", y="vx")
-```
-
-```{r}
-#| label: tbl-htw-ee-e23
-#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and the interaction between Model and Condition.
-The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
-The intercept reflects the baseline of ALM and Constant.
-The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
-Lower values indicate better model fit."
-
-e2_ee_brm_ae <- brm(data=pdl2,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
-bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
-bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
-
-bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
-
-e3_ee_brm_ae <- brm(data=pdl3,
-  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
-bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
-bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
-bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
-
-bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
-               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
-  relocate(exp, .before=Term)
-
-bct_table <- bct %>%
-  mutate(
-    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
-    pd = round(pd, 2)
-  ) %>%
-  gt() %>%
-  # tab_header(
-  #   title = "Bayesian Model Results",
-  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
-  # ) %>%
-  cols_label(
-    exp = "Experiment",
-    Term = "Term",
-    Estimate = "Estimate",
-    `95% CrI Lower` = "95% CrI Lower",
-    `95% CrI Upper` = "95% CrI Upper",
-    pd = "pd"
-  ) %>%
-  fmt_number(
-    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
-    decimals = 2
-  ) %>%
-  fmt_number(
-    columns = pd,
-    decimals = 2
-  ) %>%
-  tab_spanner(
-    label = "Credible Interval",
-    columns = c(`95% CrI Lower`, `95% CrI Upper`)
-  ) %>%
-  tab_style(
-    style = list(
-      #cell_fill(color = "lightgray"),
-      cell_text(weight = "bold"), 
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(
-      columns = c(Estimate, pd),
-      rows = Term=="ModelEXAM:conditVaried"
-    )
-  ) %>%
-   tab_row_group(
-    label = "Experiment 3",
-    rows = exp == "Exp 3"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 2",
-    rows = exp == "Exp 2"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 1",
-    rows = exp == "Exp 1"
-  ) %>%
-  tab_options(
-    table.font.size = 10,
-    heading.title.font.size = 16,
-    heading.subtitle.font.size = 14,
-    quarto.disable_processing = TRUE
-    #row_group.background.color = "gray95"
-  )
-bct_table
-
-```
-
-*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
-For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
-The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
-The Bayesian regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
-The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
-Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
-Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
-We thus also controleld for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
-There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
-
-```{r}
-#| label: fig-e2_e3_ae
-#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied) on Model Error for Experiment 2 and 3 data.
-Experiment 3 also includes a control for the order of training vs.
-testing bands (original order vs.
-reverse order)."
-#| fig-height: 6
-#| fig-width: 9
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
-p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-  p_e2 <- (p1 + p2+ p3) 
-# #wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
-                         effects = "Model:condit", 
-                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
-     points=FALSE,plot=FALSE)$`Model:condit` + 
-     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
-     theme(legend.position="right") + 
-     scale_color_manual(values=wes_palette("Darjeeling1"))
-
-p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- p2 <- (p1 + p2+ p3)
- (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-```
-
-*Computational Model Summary*.
-Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23).
-This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group.
-It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model.
-A subset of these participants are shown in @fig-htw-indv-pred.
-
-```{r}
-#| label: fig-htw-best-model
-#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
-#| fig-height: 12
-#| fig-width: 11
-
-tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
-  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
-  filter(Fit_Method=="Test_Train") |>
-  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
-    mutate(e2=abs(y-pred)) |> 
-    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
-    group_by(id,condit,Model,Fit_Method,Exp) |> 
-    summarise(mean_error=mean(mean_error)) |> 
-    arrange(id,condit,Fit_Method) |>
-    round_tibble(1)
-
-best_id <- tid1 |> 
-  group_by(id,condit,Fit_Method) |> 
-  mutate(best=ifelse(mean_error==min(mean_error),1,0))
-
-lowest_error_model <- best_id %>%
-  group_by(id, condit,Fit_Method, Exp) %>%
-  summarise(Best_Model = Model[which.min(mean_error)],
-            Lowest_error = min(mean_error),
-            differential = min(mean_error) - max(mean_error)) %>%
-  ungroup()
-
-error_difference<- best_id %>%
-  select(id, condit, Model,Fit_Method, mean_error) %>%
-  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
-  mutate(Error_difference = (ALM - EXAM))
-
-full_comparison <- lowest_error_model |> 
-  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
-  group_by(condit,Fit_Method,Best_Model) |> 
-  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
-  arrange(Fit_Method,-Error_difference)
-
-full_comparison |> 
-  filter(Fit_Method=="Test_Train") |> 
-  ungroup() |>
-  mutate(id = reorder(id, Error_difference)) %>%
-  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
-  geom_col() +
-  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
-  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
-  theme(axis.text.y = element_text(size=8)) +
-  labs(fill="Best Model",
-  x="Mean Model Error Difference (ALM - EXAM)",
-  y="Participant")
-
-```
-
-```{r  fig.width=11, fig.height=10}
-#| label: fig-htw-indv-pred
-#| fig-cap: Model predictions alongside observed data for a subset of individual participants.
-A) 3 constant and 3 varied participants fit to both the test and training data.
-B) 3 constant and 3 varied subjects fit to only the trainign data.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands.
-#| fig-height: 7
-#| fig-width: 10
-
-cId_tr <- c(137, 181, 11)
-vId_tr <- c(14, 193, 47)
-cId_tt <- c(11, 93, 35)
-vId_tt <- c(1,14,74)
-cId_new <- c(175, 68, 93, 74)
-# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")
-
-e1_sbjs <- c(49,68,155, 175,74)
-e3_sbjs <-  c(245, 280, 249)
-e2_sbjs <- c(197, 157, 312, 334)
-cFinal <- c(49, 128,202 )
-vFinal <- c(68,70,245)
-
-indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
-  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
-  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))
-
-testIndv <- indv_post_l |> 
-#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
-   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
-  group_by(id,condit,Fit_Method,Model,Resp) |>
-   mutate(flab=paste0("Subject: ",id)) |>
-  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar_sd + 
-  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
-  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
-  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
-  labs(title="Individual Participant fits from Test & Train Fitting Method",
-       y="X Velocity",fill="Target Velocity") +
-   guides(fill = guide_legend(nrow = 1)) + 
-  theme(legend.position = "bottom",axis.title.x = element_blank())
-
-testIndv 
-```
-
-## Project 2 Discussion
-
-*Experimental Result Summary*
-
-Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
-In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-
-Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
-The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.
-
-Experiment 2 extended these findings by reversing the order of the training and testing bands.
-Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases.
-However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.
-
-In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments.
-Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied).
-The varied condition showed larger deviations at the end of training, consistent with the previous experiments.
-Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition.
-During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands.
-The reverse order conditions showed smaller deviations compared to the original order conditions.
-Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.
-
-All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015].
-The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group.
-Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.
-
-Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
-Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
-A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
-These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study.
-@vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
-However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
-
-*Modeling Summary*
-EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group.
-May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule.
-But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval.
-The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
-
-*Limitations*
-
-While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
-First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
-Such a difference may be an unavoidable consequence of varied vs.
-constant design which match the total number of training trials between the two groups.
-However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
-Another limitation is that the testing stage did not include any interpolation items, i.e.
-the participants tested only from the training bands they experienced during training, or from extrapolation bands.
-The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
-Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
-Finally, the task employed in the present study consisted of only a linear, positive function.
-Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
-It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
-
-## General Discussion
-
-To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
-
-### Empirical Results Summary
-
-Across two projects, we investigated the influence of training variability on learning and generalization in visuomotor tasks.
-In Project 1 (HTT), we consistently found that varied training led to superior performance relative to constant training, even when testing at positions that were identical to the constant group's training.
-In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing.
-This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
-
-### Differences between the two Projects
-
-Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
-
-In HTT, the salient perceptual elements of the task (i.e.
-the launching box, target and barrier) are subject to variation (i.e.
-different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
-Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
-If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
-Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
-the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
-
-The HTT and HTW tasks also differed in terms of general task complexity.
-The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
-Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
-
-::: {#tbl-task-diff}
-
-| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
-| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
-| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
-| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
-Only x velocity is relevant.
-|
-| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
-| Simpler: smooth, linear mapping between velocity and feedback.
-|
-| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
-salient differences in distance between launching box and target.
-| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
-|
-| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
-|
-| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
-| Some potential for learning during no-feedback testing by observing ball trajectory.
-|
-| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
-| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
-|
-| Testing Structure                               | Random interleaving of trained/transfer testing distances.
-| Blocked structure, separately testing trained vs extrapolation testing bands.
-|
-
-Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
-:::
-
-# References
-
-::: {#refs}
-:::
-
-# Appendix
-
-{{< include Appendix/IGAS-Supplemental.qmd >}}

### 2024-04-06 Sections/full.qmd
turn off external-filter
render full in pdf and markdown

@@
 title: Full Dissertation
-subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
+subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
 date: 04/04/24
-#page-layout: full
+author:
+- name: Thomas Gorman
+  affiliation: Indiana University
+page-layout: full
 code-fold: true
@@
 toc-title: Contents
+cache: true
 execute: 
@@
     echo: false
-    output: false
+    include: false
     html-math-method: mathjax
@@
   gfm:
-    echo: true
+    echo: false
+    output: false
     output-file: diss_full_gfm.md
@@
 It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
+A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979; @mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
 A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
@@
 ```{r}
+#| cache: false
 
@@
 Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
-
 Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
@@
 
-To obtain an independent estimate of effect size, we identified previous
-investigations which included between-subjects contrasts of varied and
-constant conditions following training on an accuracy based projectile
-launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
-2009) was then used to determine that a power of 80% requires a sample
-size of at least 23 participants per condition. All experiments reported
-in the present manuscript exceed this minimum number of participants per
-condition.
+To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
+We then averaged effects across these studies, yielding a Cohens f =.43.
+The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009], 2009) was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
+All experiments reported in the present manuscript exceed this minimum number of participants per condition.
 
@@
 
-Participants were recruited from an undergraduate population that is 63%
-female and consists almost entirely of individuals aged 18-22 years. A
-total of 110 Indiana University psychology students participated in
-Experiment 1. We subsequently excluded 34 participants poor performance
-at one of the dependent measures of the task (2.5-3 standard deviations
-worse than the median subject at the task) or for displaying a pattern
-of responses that was clearly indicative of a lack of engagement with
-the task (e.g. simply dropping the ball on each trial rather than
-throwing it at the target), or for reporting that they completed the
-experiment on a phone or tablet device, despite the instructions not to
-use one of these devices. A total of 74 participants were retained for
-the final analyses, 35 in the varied group and 39 in the constant group.
+Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18-22 years.
+A total of 110 Indiana University psychology students participated in Experiment 1.
+We subsequently excluded 34 participants poor performance at one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
+simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
+A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.
 
@@
 
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-IGAS_Methods displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library (de Leeuw, 2015).
+The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
+Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
+Likewise, the distance between the center of the target, and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
+For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
+@fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square.
+Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor.
+Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
+If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target.
+If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
+If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier.
+If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square.
+If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
+
+[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
 
@@
 
-To prepare the data, we first removed trials that were not easily
-interpretable as performance indicators in our task. Removed trials
-included: 1) those in which participants dragged the ball outside of the
-orange starting box without releasing it, 2) trials in which
-participants clicked on the ball, and then immediately released it,
-causing the ball to drop straight down, 3) outlier trials in which the
-ball was thrown more than 2.5 standard deviations further than the
-average throw (calculated separately for each throwing position), and 4)
-trials in which the ball struck the barrier. The primary measure of
-performance used in all analyses was the absolute distance away from the
-center of the target. The absolute distance was calculated on every
-trial, and then averaged within each subject to yield a single
-performance score, for each position. A consistent pattern across
-training and testing phases in both experiments was for participants to
-perform worse from throwing positions further away from the target -- a
-pattern which we refer to as the difficulty of the positions. However,
-there were no interactions between throwing position and training
-conditions, allowing us to collapse across positions in cases where
-contrasts for specific positions were not of interest. All data
-processing and statistical analyses were performed in R version 4.03 (R
-Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021)****.
+To prepare the data, we first removed trials that were not easily interpretable as performance indicators in our task.
+Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier.
+The primary measure of performance used in all analyses was the absolute distance away from the center of the target.
+The absolute distance was calculated on every trial, and then averaged within each subject to yield a single performance score, for each position.
+A consistent pattern across training and testing phases in both experiments was for participants to perform worse from throwing positions further away from the target -- a pattern which we refer to as the difficulty of the positions.
+However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest.
+All data processing and statistical analyses were performed in R version 4.03 (R Core Team, 2020).
+ANOVAs for group comparisons were performed using the rstatix package (Kassambara, 2021).
 
@@
 
-@fig-IGAS_Training1 below shows aggregate training performance binned into three
-stages representing the beginning, middle, and end of the training
-phase. Because the two conditions trained from target distances that
-were not equally difficult, it was not possible to directly compare
-performance between conditions in the training phase. Our focus for the
-training data analysis was instead to establish that participants did
-improve their performance over the course of training, and to examine
-whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided
-in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and
-condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
-such that performance improved over the course of training There was no
-significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
-and no significant interaction between condition and training stage,
-F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
+@fig-IGAS_Training1 below shows aggregate training performance binned into three stages representing the beginning, middle, and end of the training phase.
+Because the two conditions trained from target distances that were not equally difficult, it was not possible to directly compare performance between conditions in the training phase.
+Our focus for the training data analysis was instead to establish that participants did improve their performance over the course of training, and to examine whether there was any interaction between training stage and condition.
+Descriptive statistics for the intermittent testing phase are provided in the supplementary materials.
+
+We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor.
+The analysis revealed a significant effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02, and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
 
@@
 
-In Experiment 1, a single constant-trained group was compared against a
-single varied-trained group. At the transfer phase, all participants
-were tested from 3 positions: 1) the positions(s) from their own
-training, 2) the training position(s) of the other group, and 3) a
-position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs. constant) as a
-between-subject factor and throwing location as a within-subject
-variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\<.001, η2G = .23. The effect of training condition was significant
-F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
-between group and position, F(3,213)=1.81, p=.15, η2G = .01.
+In Experiment 1, a single constant-trained group was compared against a single varied-trained group.
+At the transfer phase, all participants were tested from 3 positions: 1) the positions(s) from their own training, 2) the training position(s) of the other group, and 3) a position novel to both groups.
+Overall, group performance was compared with a mixed type III ANOVA, with condition (varied vs.
+constant) as a between-subject factor and throwing location as a within-subject variable.
+The effect of throwing position was strong, F(3,213) = 56.12, p\<.001, η2G = .23.
+The effect of training condition was significant F(1,71)=8.19, p\<.01, η2G = .07.
+There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.
 
@@
 
-In Experiment 1, we found that varied training resulted in superior
-testing performance than constant training, from both a position novel
-to both groups, and from the position at which the constant group was
-trained, which was novel to the varied condition. The superiority of
-varied training over constant training even at the constant training
-position is of particular note, given that testing at this position
-should have been highly similar for participants in the constant
-condition. It should also be noted, though, that testing at the constant
-trained position is not exactly identical to training from that
-position, given that the context of testing is different in several ways
-from that of training, such as the testing trials from the different
-positions being intermixed, as well as a simple change in context as a
-function of time. Such contextual differences will be further considered
-in the General Discussion.
-
-In addition to the variation of throwing position during training, the
-participants in the varied condition of Experiment 1 also received
-training practice from the closest/easiest position, as well as from the
-furthest/most difficult position that would later be encountered by all
-participants during testing. The varied condition also had the potential
-advantage of interpolating both of the novel positions from which they
-would later be tested. Experiment 2 thus sought to address these issues
-by comparing a varied condition to multiple constant conditions.
+In Experiment 1, we found that varied training resulted in superior testing performance than constant training, from both a position novel to both groups, and from the position at which the constant group was trained, which was novel to the varied condition.
+The superiority of varied training over constant training even at the constant training position is of particular note, given that testing at this position should have been highly similar for participants in the constant condition.
+It should also be noted, though, that testing at the constant trained position is not exactly identical to training from that position, given that the context of testing is different in several ways from that of training, such as the testing trials from the different positions being intermixed, as well as a simple change in context as a function of time.
+Such contextual differences will be further considered in the General Discussion.
+
+In addition to the variation of throwing position during training, the participants in the varied condition of Experiment 1 also received training practice from the closest/easiest position, as well as from the furthest/most difficult position that would later be encountered by all participants during testing.
+The varied condition also had the potential advantage of interpolating both of the novel positions from which they would later be tested.
+Experiment 2 thus sought to address these issues by comparing a varied condition to multiple constant conditions.
 
@@
 
-In Experiment 2, we sought to replicate our findings from Experiment 1
-with a new sample of participants, while also addressing the possibility
-of the pattern of results in Experiment 1 being explained by some
-idiosyncrasy of the particular training location of the constant group
-relative to the varied group. To this end, Experiment 2 employed the
-same basic procedure as Experiment 1, but was designed with six separate
-constant groups each trained from one of six different locations (400,
-500, 625, 675, 800, or 900), and a varied group trained from two
-locations (500 and 800). Participants in all seven groups were then
-tested from each of the 6 unique positions.
+In Experiment 2, we sought to replicate our findings from Experiment 1 with a new sample of participants, while also addressing the possibility of the pattern of results in Experiment 1 being explained by some idiosyncrasy of the particular training location of the constant group relative to the varied group.
+To this end, Experiment 2 employed the same basic procedure as Experiment 1, but was designed with six separate constant groups each trained from one of six different locations (400, 500, 625, 675, 800, or 900), and a varied group trained from two locations (500 and 800).
+Participants in all seven groups were then tested from each of the 6 unique positions.
 
@@
 
-A total of 306 Indiana University psychology students participated in
-Experiment 2, which was also conducted online. As was the case in
-experiment 1, the undergraduate population from which we recruited
-participants was 63% female and primarily composed of 18--22-year-old
-individuals. Using the same procedure as experiment 1, we excluded 98
-participants for exceptionally poor performance at one of the dependent
-measures of the task, or for displaying a pattern of responses
-indicative of a lack of engagement with the task. A total of 208
-participants were included in the final analyses with 31 in the varied
-group and 32, 28, 37, 25, 29, 26 participants in the constant groups
-training from location 400, 500, 625, 675, 800, and 900, respectively.
+A total of 306 Indiana University psychology students participated in Experiment 2, which was also conducted online.
+As was the case in experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18--22-year-old individuals.
+Using the same procedure as experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task.
+A total of 208 participants were included in the final analyses with 31 in the varied group and 32, 28, 37, 25, 29, 26 participants in the constant groups training from location 400, 500, 625, 675, 800, and 900, respectively.
 All participants were compensated with course credit.
@@
 
-The task of Experiment 2 was identical to that of Experiment 1, in all
-but some minor adjustments to the height of the barrier, and the
-relative distance between the barrier and the target. Additionally, the
-intermittent testing trials featured in experiment 1 were not utilized
-in experiment 2, and all training and testing trials were presented with
-feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
+The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target.
+Additionally, the intermittent testing trials featured in experiment 1 were not utilized in experiment 2, and all training and testing trials were presented with feedback.
+An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
 
 The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the
-same position for the constant groups and split evenly (70 trials each -
-randomized) for the varied group. In the testing phase, participants
-completed 30 trials from each of the six locations that had been used
-separately across each of the constant groups during training. Each of
-the constant groups thus experience one trained location and five novel
-throwing locations in the testing phase, while the varied group
-experiences 2 previously trained, and 4 novel locations.
+Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group.
+In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training.
+Each of the constant groups thus experience one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
 
@@
 
-After confirming that condition and throwing position did not have any
-significant interactions, we standardized performance within each
-position, and then average across position to yield a single performance
-measure per participant. This standardization did not influence our
-pattern of results. As in experiment 1, we performed type III ANOVA's
-due to our unbalanced design, however the pattern of results presented
-below is not altered if type 1 or type III tests are used instead. The
-statistical software for the primary analyses was the same as for
-experiment 1. Individual learning rates in the testing phase, compared
-between groups in the supplementary analyses, were fit using the TEfit
-package in R [@cochraneTEfitsNonlinearRegression2020].
+After confirming that condition and throwing position did not have any significant interactions, we standardized performance within each position, and then average across position to yield a single performance measure per participant.
+This standardization did not influence our pattern of results.
+As in experiment 1, we performed type III ANOVA's due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.
+The statistical software for the primary analyses was the same as for experiment 1.
+Individual learning rates in the testing phase, compared between groups in the supplementary analyses, were fit using the TEfit package in R [@cochraneTEfitsNonlinearRegression2020].
 
@@
 
-The different training conditions trained from positions that were not
-equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. @fig-e2train depicts the training
-performance of the varied group alongside that of the aggregate of the
-six constant groups (5a), and each of the 6 separate constant groups
-(5b). An ANOVA comparison with training stage (beginning, middle, end)
-as a within-group factor and group (the varied condition vs. the 6
-constant conditions collapsed together) as a between-subject factor
-revealed no significant effect of group on training performance,
-F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
-stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
-interaction between group and training stage, F(2,412)=.489 p=.61,
-$\eta^{2}_G$ \<.01. We also tested for a difference in training
-performance between the varied group and the two constant groups that
-trained matching throwing positions (i.e., the constant groups training
-from position 500, and position 800). The results of our ANOVA on this
-limited dataset mirrors that of the full-group analysis, with no
-significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
-significant effect of training stage F(2,172)=56.29, p\<.001,
-$\eta^{2}_G$ =.11, and no significant interaction between group and
-training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
+The different training conditions trained from positions that were not equivalently difficult and are thus not easily amenable to comparison.
+As previously stated, the primary interest of the training data is confirmation that some learning did occur.
+@fig-e2train depicts the training performance of the varied group alongside that of the aggregate of the six constant groups (5a), and each of the 6 separate constant groups (5b).
+An ANOVA comparison with training stage (beginning, middle, end) as a within-group factor and group (the varied condition vs.
+the 6 constant conditions collapsed together) as a between-subject factor revealed no significant effect of group on training performance, F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant interaction between group and training stage, F(2,412)=.489 p=.61, $\eta^{2}_G$ \<.01.
+We also tested for a difference in training performance between the varied group and the two constant groups that trained matching throwing positions (i.e., the constant groups training from position 500, and position 800).
+The results of our ANOVA on this limited dataset mirrors that of the full-group analysis, with no significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a significant effect of training stage F(2,172)=56.29, p\<.001, $\eta^{2}_G$ =.11, and no significant interaction between group and training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
 
@@
 
-In Experiment 2, a single varied condition (trained from two positions,
-500 and 800), was compared against six separate constant groups (trained
-from a single position, 400, 500, 625, 675, 800 or 900). For the testing
-phase, all participants were tested from all six positions, four of
-which were novel for the varied condition, and five of which were novel
-for each of the constant groups. For a general comparison, we took the
-absolute deviations for each throwing position and computed standardized
-scores across all participants, and then averaged across throwing
-position. The six constant groups were then collapsed together allowing
-us to make a simple comparison between training conditions (constant vs.
-varied). A type III between-subjects ANOVA was performed, yielding a
-significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
-=.02. Descriptive statistics for each condition are shown in table 2. In
-@fig-e2testa visualizes the consistent advantage of the varied condition
-over the constant groups across the testing positions. @fig-e2testa shows
-performance between the varied condition and the individual constant
-groups.
+In Experiment 2, a single varied condition (trained from two positions, 500 and 800), was compared against six separate constant groups (trained from a single position, 400, 500, 625, 675, 800 or 900).
+For the testing phase, all participants were tested from all six positions, four of which were novel for the varied condition, and five of which were novel for each of the constant groups.
+For a general comparison, we took the absolute deviations for each throwing position and computed standardized scores across all participants, and then averaged across throwing position.
+The six constant groups were then collapsed together allowing us to make a simple comparison between training conditions (constant vs.
+varied).
+A type III between-subjects ANOVA was performed, yielding a significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$ =.02.
+Descriptive statistics for each condition are shown in table 2.
+In @fig-e2testa visualizes the consistent advantage of the varied condition over the constant groups across the testing positions.
+@fig-e2testa shows performance between the varied condition and the individual constant groups.
 
@@
 
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
-.02 .
+Next, we compared the testing performance of constant and varied groups from only positions that participants had not encountered during training.
+Constant participants each had 5 novel positions, whereas varied participants tested from 4 novel positions (400,625,675,900).
+We first standardized performance within in each position, and then averaged across positions.
+Here again, we found a significant effect of condition (constant vs.
+varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ = .02 .
 
@@
 
-Finally, corresponding to the comparison of position 760 from experiment
-1, we compared the test performance of the varied group against the
-constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis
-omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). @fig-e2test1 displays
-the particular subset of comparisons utilized for this analysis. Again,
-we standardized performance within each position before performing the
-analyses on the aggregated data. In this case, the effect of condition
-did not reach statistical significance F(1,149)=3.14, p=.079,
-$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
+Finally, corresponding to the comparison of position 760 from experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained.
+Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group).
+@fig-e2test1 displays the particular subset of comparisons utilized for this analysis.
+Again, we standardized performance within each position before performing the analyses on the aggregated data.
+In this case, the effect of condition did not reach statistical significance F(1,149)=3.14, p=.079, $\eta^{2}_G$ = .02.
+Table 4 provides descriptive statistics.
 
@@
 
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
+The results of experiment 2 largely conform to the findings of experiment 1.
+Participants in both varied and constant conditions improved at the task during the training phase.
+We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing [@soderstromLearningPerformanceIntegrative2015].
+However our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
+
+In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions.
+The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
+We also join a much smaller set of research to observe this pattern in a computerized task [@seowTransferEffectsVaried2019].
+One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
+Although this pattern has been observed elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
 
@@
 
-*Controlling for the similarity between training and testing.* The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
+*Controlling for the similarity between training and testing.* The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations.
+To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release.
+For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions.
+We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target.
+We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions -- thus resulting in six separate similarity scores for each participant.
+@fig-taskSpace visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions.
+As illustrated in @fig-taskSpace, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.
 
@@
 
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
-
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
-(e^{-c^\cdot d^{p}_{i,j}}) $$
+For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.
+The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient.
+Then, as per an instance-based model of similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value.
+The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.
+If c has a large value, then even a small difference between two throws' velocities greatly decreases the extent of generalization from one to the other.
+A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities.
+The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions.
+The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.
+
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
 
@@
 
-A simple linear regression revealed that these similarity scores were
-significantly predictive of performance in the transfer stage, t
-=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
-training throws and solution spaces for each of the test locations
-resulted in better performance. We then repeated the group comparisons
-above while including similarity as a covariate in the model. Comparing
-the varied and constant groups in testing performance from all testing
-positions yielded a significant effect of similarity, F(1, 205)=85.66,
-p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
-(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
-group comparison limited to only novel locations for the varied group
-pit against trained location for the constant group resulted in a
-significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
-=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
-=.07. For all comparisons, the pattern of results was consistent with
-the initial findings from experiment 2, with the varied group still
-performing significantly better than the constant group.
+A simple linear regression revealed that these similarity scores were significantly predictive of performance in the transfer stage, t =-15.88, p\<.01, $r^2$=.17, such that greater similarity between training throws and solution spaces for each of the test locations resulted in better performance.
+We then repeated the group comparisons above while including similarity as a covariate in the model.
+Comparing the varied and constant groups in testing performance from all testing positions yielded a significant effect of similarity, F(1, 205)=85.66, p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition (varied vs.
+constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03.
+The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$ =.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$ =.07.
+For all comparisons, the pattern of results was consistent with the initial findings from experiment 2, with the varied group still performing significantly better than the constant group.
 
@@
 
-To directly control for similarity in Experiment 2, we developed a
-model-based measure of the similarity between training throws and
-testing conditions. This similarity measure was a significant predictor
-of testing performance, e.g., participants whose training throws were
-more similar to throws that resulted in target hits from the testing
-positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level
-benefits of varied training, which remained significant in our linear
-model predicting testing performance after similarity was added to the
-model. However, previous research has suggested that participants may
-differ in their level of generalization as a function of prior
-experience, and that such differences in generalization gradients can be
-captured by fitting the generalization parameter of an instance-based
-model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
-will increase when a rational agent encounters a wider variety of
-examples. Following these leads, we assume that in addition to learning
-the task itself, participants are also adjusting how generalizable their
-experience should be. Varied versus constant participants may be
-expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the
-instance-based model (in the present case, the c parameter) can be
-allowed to vary between the two groups to reflect the tendency of
-learners to adaptively tune the extent of their generalization. One
-specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
-variable, as with the variable training condition, then one might infer
-that future test situations will also be variable, in which case a low
-value of c will allow better generalization because generalization will
-drop off slowly with training-to-testing distance. Conversely, if one's
-training experience has little variability, as found in the constant
-training conditions, then one might adopt a high value of c so that
-generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based
-model of similarity fit against a modified model which separately fits
-the generalization parameter, c, to varied and constant participants. To
-perform this parameter fitting, we used the optim function in R, and fit
-the model to find the c value(s) that maximized the correlation between
-similarity and testing performance.
-
-Both models generate distinct similarity values between training and
-testing locations. Much like the analyses in Experiment 2, these
-similarity values are regressed against testing performance in models of
-the form shown below. As was the case previously, testing performance is
-defined as the mean absolute distance from the center of the target
-(with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\<.01). Of greater interest is the
-difference between linear model 2, in which similarity is computed from
-a single c value fit from all participants (Similarity1c), with linear
-model 4, which fits the c parameter separately between groups
-(Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\<.01), with the varied
-group still performing significantly better. However, in linear model 4
-the addition of the Similarity2c predictor results in the effect of
-training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs. constant training is accounted for by the
-Similarity2c predictor. Next, to further establish a difference between
-the models, we performed nested model comparisons using ANOVA, to see if
-the addition of the training group parameter led to a significant
-improvement in model performance. In the first comparison, ANOVA(Linear
-Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear
-Model 4) found no improvement in model performance with the addition of
-the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the
-adjusted Similarity2c model had more predictive power than those
-generated from the original Similarity1c model. Using the BIC function
-in R, we compared BIC values between linear model 1 (BIC=14604.00) and
-linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
-a modest advantage for predicting performance using a similarity measure
-computed with two c values over similarity computed with a single c
-value. When fit with separate c values, the best fitting c parameters
-for the model consistently optimized such that the c value for the
-varied group (c=.00008) was smaller in magnitude than the c value for
-the constant group(c= .00011). Recall that similarity decreases as a
-Gaussian function of distance (equation 1 above), and a smaller value of
-c will result in a more gradual drop-off in similarity as the distance
-between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which
-assumes equivalent generalization gradients between constant and varied
-trained participants is unable to account for the extent of benefits of
-varied over constant training observed at testing. The evidence for this
-in the comparative model fits is that when a varied/constant dummy-coded
-variable for condition is explicitly added to the model, the variable
-adds a significant contribution to the prediction of test performance,
-with the variable condition yielding better performance than the
-constant conditions. However, if the instance-based generalization model
-is modified to assume that the training groups can differ in the
-steepness of their generalization gradient, by incorporating a separate
-generalization parameter for each group, then the instance-based model
-can account for our experimental results without explicitly taking
-training group into account. Henceforth this model will be referred to
-as the Instance-based Generalization with Adaptive Similarity (IGAS)
-model.
+To directly control for similarity in Experiment 2, we developed a model-based measure of the similarity between training throws and testing conditions.
+This similarity measure was a significant predictor of testing performance, e.g., participants whose training throws were more similar to throws that resulted in target hits from the testing positions, tended to perform better during the testing phase.
+Importantly, the similarity measure did not explain away the group-level benefits of varied training, which remained significant in our linear model predicting testing performance after similarity was added to the model.
+However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
+Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
+Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
+Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
+To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
+One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
+If one's training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
+Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+
+To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c, to varied and constant participants.
+To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
+
+Both models generate distinct similarity values between training and testing locations.
+Much like the analyses in Experiment 2, these similarity values are regressed against testing performance in models of the form shown below.
+As was the case previously, testing performance is defined as the mean absolute distance from the center of the target (with a separate score for each participant, from each position).
+
+Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p\<.01).
+Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the c parameter separately between groups (Similarity2c).
+In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p\<.01), with the varied group still performing significantly better.
+However, in linear model 4 the addition of the Similarity2c predictor results in the effect of training group becoming nonsignificant (p=.40), suggesting that the effect of varied vs.
+constant training is accounted for by the Similarity2c predictor.
+Next, to further establish a difference between the models, we performed nested model comparisons using ANOVA, to see if the addition of the training group parameter led to a significant improvement in model performance.
+In the first comparison, ANOVA(Linear Model 1, Linear Model 2), the addition of the training group predictor significantly improved the performance of the model (F=22.07, p\<.01).
+However, in the second model comparison, ANOVA (Linear model 3, Linear Model 4) found no improvement in model performance with the addition of the training group predictor (F=1.61, p=.20).
+
+Finally, we sought to confirm that similarity values generated from the adjusted Similarity2c model had more predictive power than those generated from the original Similarity1c model.
+Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
+The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
+When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
+Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
+
+In summary, our modeling suggests that an instance-based model which assumes equivalent generalization gradients between constant and varied trained participants is unable to account for the extent of benefits of varied over constant training observed at testing.
+The evidence for this in the comparative model fits is that when a varied/constant dummy-coded variable for condition is explicitly added to the model, the variable adds a significant contribution to the prediction of test performance, with the variable condition yielding better performance than the constant conditions.
+However, if the instance-based generalization model is modified to assume that the training groups can differ in the steepness of their generalization gradient, by incorporating a separate generalization parameter for each group, then the instance-based model can account for our experimental results without explicitly taking training group into account.
+Henceforth this model will be referred to as the Instance-based Generalization with Adaptive Similarity (IGAS) model.
 
@@
 Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy-Model-dis we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
+variability hypothesis in a simple, computerized projectile throwing task.
+Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
+However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions.
+We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978].
+In experiment 1 varied participants performed significantly better on this identity comparison.
+In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
+Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
+Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
+Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
+A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
+The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
+In this fashion, contextually appropriate c values could be empirically learned.
+This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
+
+Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained.
+Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in @fig-Toy-Model-dis we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern.
+In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model -- namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.
 
@@
 @lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
+The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
 However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
+Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
 
@@
 One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define a category item (e.g.
+In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g.
 size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw.
+Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
 An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
-movement force, velocity, angle, posture) in addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in
-support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
+movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
+Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
 A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
@@
 
-Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
-lighting up consecutively, and attempt to time a button press with the
-onset of the final lamp. The design consisted of four separate constant
-groups, each training from a single lighting velocity, and a single
-varied group training with all four of the lighting velocities used by
-the individual constant groups. Participants were then split into four
-separate testing conditions, each of which were tested from a single
-novel lighting velocity of varying distance from the training
-conditions. The result of primary interest was that all participants
-performed worse as the distance between training and testing velocity
-increased -- a typical generalization decrement. However, varied
-participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in
-a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are
-similar to our own, our work is novel in that we account for our results
-with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their
-separate constant groups together may result in similarity confounds
-between varied and constant conditions that leaves their study open to
-methodological criticisms, especially in light of related work which
-demonstrated that the extent to which varied training may be beneficial
-can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
-similarity.
+Our findings also have some conceptual overlap with an earlier study on the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].
+In this task, participants observe a series of lamps lighting up consecutively, and attempt to time a button press with the onset of the final lamp.
+The design consisted of four separate constant groups, each training from a single lighting velocity, and a single varied group training with all four of the lighting velocities used by the individual constant groups.
+Participants were then split into four separate testing conditions, each of which were tested from a single novel lighting velocity of varying distance from the training conditions.
+The result of primary interest was that all participants performed worse as the distance between training and testing velocity increased -- a typical generalization decrement.
+However, varied participants showed less of a decrement than did constant participants.
+The authors take this result as evidence that varied training results in a less-steep generalization gradient than does constant training.
+Although the experimental conclusions of Catalano and Kleiner are similar to our own, our work is novel in that we account for our results with a cognitive model, and without assuming the formation of a schema.
+Additionally, the way in which Catalano and Kleiner collapse their separate constant groups together may result in similarity confounds between varied and constant conditions that leaves their study open to methodological criticisms, especially in light of related work which demonstrated that the extent to which varied training may be beneficial can depend on whether the constant group they are compared against trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987].
+Our study alleviates such concerns by explicitly controlling for similarity.
 
@@
 
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
-
+A limitation of this study concerns the ordering of the testing/transfer trials at the conclusion of both experiments.
+Participants were tested from each separate position (4 in Experiment 1, 6 in Experiment 2) in a random, intermixed order.
+Because the varied group was trained from two positions that were also randomly ordered, they may have benefited from experience with this type of sequencing, whereas the constant groups had no experience with switching between positions trial to trial.
+This concern is somewhat ameliorated by the fact that the testing phase performance of the constant groups from their trained position was not significantly worse than their level of performance at the end of the training phase, suggesting that they were not harmed by random ordering of positions during testing.
+It should also be noted that the computerized task utilized in the present work is relatively simple compared to many of the real-world tasks utilized in prior research.
+It is thus conceivable that the effect of variability in more complex tasks is distinct from the process put forward in the present work.
+An important challenge for future work will be to assess the extent to which IGAS can account for generalization in relatively complex tasks with far more degrees of freedom.
+
+It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987].
+Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
+In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g.
+the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
+However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
 ## Conclusion
 
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
+Our experiments demonstrate a reliable benefit of varied training in a simple projectile launching task.
+Such results were accounted for by an instance-based model that assumes that varied training results in the computation of a broader similarity-based generalization gradient.
+Instance-based models augmented with this assumption may be a valuable approach towards better understanding skill generalization and transfer.
 
@@
 
+::: {.content-visible unless-format="markdown"}
 ```{dot}
@@
 //| fig-responsive: false
+//| echo: false  
+///| eval: !expr out_type 
 /////| column: screen-inset-right
@@
 ```
+:::
 
@@
 //| fig-responsive: false
-//| 
+//| echo: false 
 //| 
@@
 ```
+
+:::
 
@@
 
-\ \ \ \
-
+\ \
+
+::: {.content-visible unless-format="pdf"}
 # References
@@
 
+:::
+
 # Appendix
 
+::: {.content-visible unless-format="markdown"}
+### Appendix - Project 1
+
 {{< include Appendix/IGAS-Supplemental.qmd >}}
+
+{{< pagebreak >}}
+
+### Appendix - Project 2 - Experiment 1
+
+{{< include Appendix/E1_Appendix.qmd >}}
+:::
+
+::: {.content-visible when-format="pdf"}
+
+# References
+
+:::

### 2024-04-06 Sections/project_transition.qmd
render full in pdf and markdown

@@
 In contrast, in HTT, it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws but resulted in worse feedback due to striking the barrier.
+
+In Project 2, a modified version of the task from Project 1 is used in conjunction with a testing procedure that challenges participants to extrapolate well beyond their training experience.
+In line with previous research in the function learning literature, participants show evidence of successful extrapolation in our linear task environment.
+Surprisingly though, the constant training group outperforms the varied training group consistently across numerous variants of the task.
+Such a pattern is far from unheard of in the vast literature on training variability, and it is therefore remains a worthwhile challenge to evaluate the ability of similarity-based models to account for the observed effects.
+Additionally, the cognitive process models implemented for project 2 will go beyond the modelling efforts of the previous project in two respects.
+1) Extensions that enable the model to produce predictions of participant responses, and 2) fitting and attempting to account for behavior in both training AND testing phases of the experiment.
+
+In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations.
+Extrapolation has long been a focus of the literature on function learning (Brehmer 1974; Carroll 1963).
+Central questions of the function learning literature have included the relative difficulties of learning various functional forms (e.g.
+linear vs.bilinear vs.
+quadratic), and the relative effectiveness of rule-based vs.
+association-based exemplar models vs.
+various hybrid models (Bott and Heit 2004; DeLosh, McDaniel, and Busemeyer 1997; Jones et al.
+2018; Kalish, Lewandowsky, and Kruschke 2004; M.
+A.
+Mcdaniel and Busemeyer 2005; M.
+Mcdaniel et al.
+2009).
+However the issue of training variation has received surprisingly little attention in this area.

### 2024-04-08 Sections/Appendix/E1_Appendix.qmd
tweaks

--- 2023-10-29 Appendix/E1_Appendix.qmd
@@
 # print(getwd())
-source(here::here("Functions", "packages.R"))
+#source(here::here("Functions", "packages.R"))
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
+  ggh4x,htmltools,future,furrr,ez)
+walk(c("dplyr","here"), conflict_prefer_all, quiet = TRUE)
 
+walk(c("Display_Functions", "org_functions", "Table_Functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
 ```

### 2024-04-08 Sections/IGAS.qmd
render full in pdf and markdown
tweaks

@@
 
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
-The factor of interest to the present investigation is variation during training.
-Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
-We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
-We first review the relevant concepts and literature.
-
 ## Similarity and instance-based approaches to transfer of learning
@@
 ## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work -- variability of training examples.
-
-Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
-Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
 
@@
 
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-IGAS_Methods displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library (de Leeuw, 2015).
+The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
+Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
+Likewise, the distance between the center of the target, and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
+For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
+@fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square.
+Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor.
+Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
+If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target.
+If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
+If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier.
+If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square.
+If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
+[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
 
@@
 
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
-.02 .
-
+Next, we compared the testing performance of constant and varied groups from only positions that participants had not encountered during training.
+Constant participants each had 5 novel positions, whereas varied participants tested from 4 novel positions (400,625,675,900).
+We first standardized performance within in each position, and then averaged across positions.
+Here again, we found a significant effect of condition (constant vs.
+varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ = .02 .
 ```{r}
@@
 
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
-
+The results of experiment 2 largely conform to the findings of experiment 1.
+Participants in both varied and constant conditions improved at the task during the training phase.
+We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing [@soderstromLearningPerformanceIntegrative2015].
+However our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
+
+In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions.
+The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
+We also join a much smaller set of research to observe this pattern in a computerized task [@seowTransferEffectsVaried2019].
+One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
+Although this pattern has been observed elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
 # Computational Model
 
-*Controlling for the similarity between training and testing.* The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
+*Controlling for the similarity between training and testing.* The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations.
+To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release.
+For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions.
+We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target.
+We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions -- thus resulting in six separate similarity scores for each participant.
+@fig-taskSpace visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions.
+As illustrated in @fig-taskSpace, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.
 
@@
 
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
+For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.
+The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient.
+Then, as per an instance-based model of similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value.
+The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.
+If c has a large value, then even a small difference between two throws' velocities greatly decreases the extent of generalization from one to the other.
+A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities.
+The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions.
+The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.
 
@@
 
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy-Model-dis we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
+Across two experiments, we found evidence in support of the benefits of variability hypothesis in a simple, computerized projectile throwing task.
+Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
+However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions.
+We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978].
+In experiment 1 varied participants performed significantly better on this identity comparison.
+In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
+Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
+Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
+Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
+A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
+The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
+In this fashion, contextually appropriate c values could be empirically learned.
+This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
+
+Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained.
+Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in @fig-Toy-Model-dis we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern.
+In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model -- namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.
 
@@
 
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
+A limitation of this study concerns the ordering of the testing/transfer trials at the conclusion of both experiments.
+Participants were tested from each separate position (4 in Experiment 1, 6 in Experiment 2) in a random, intermixed order.
+Because the varied group was trained from two positions that were also randomly ordered, they may have benefited from experience with this type of sequencing, whereas the constant groups had no experience with switching between positions trial to trial.
+This concern is somewhat ameliorated by the fact that the testing phase performance of the constant groups from their trained position was not significantly worse than their level of performance at the end of the training phase, suggesting that they were not harmed by random ordering of positions during testing.
+It should also be noted that the computerized task utilized in the present work is relatively simple compared to many of the real-world tasks utilized in prior research.
+It is thus conceivable that the effect of variability in more complex tasks is distinct from the process put forward in the present work.
+An important challenge for future work will be to assess the extent to which IGAS can account for generalization in relatively complex tasks with far more degrees of freedom.
+
+It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987].
+Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
+In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g.
+the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
+However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
 
@@
 
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
+Our experiments add to the longstanding body of research investigating  the effect of training variability on learning and generalization.
+Both experiments demonstrate a reliable benefit of varied training over constant training in a projectile launching task.
+We also introduce the Instance-based Generalization with Adaptive Similarity (IGAS) as a novel explanation for the effect of variability on generalization.
+The key assumption made by IGAS is that the amount of variation encountered during training influences the steepness of the generalization gradient.
+Instance-based models augmented with this assumption may be a valuable approach towards better understanding skill generalization and transfer.
 

### 2024-04-08 Sections/Introduction.qmd
tweaks

@@
 
-# Variability and Generalization
+# Introduction
 
-The factors that influence the generalization of learning are of considerable interest to both researchers exploring the human learning system and practitioners aiming to enhance the effectiveness of educational and training interventions.
-The present effort will focus specifically on the role of variability in the learning input.
-Variability manipulations typically regulate either the number of distinct instances presented to learners during training, or the dispersion of these instances.
-Such manipulations have been empirically demonstrated to affect subsequent generalization performance.
-This essay will offer an in-depth review of the extant literature on the influence of variability, spanning multiple relevant domains.
+The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer or generalization to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
+Such generalization challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that influence generalization, and to develop cognitive models that can predict when generalization is likely to occur.
+Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
 
@@
 
-Studies investigating the "benefits of variability" hypothesis usually assign participants to either a constant or varied group for the training stage of the experiment.
-Then, subjects in both groups complete an identical testing stage which often consists items/conditions seen during training, and novel items/conditions.
-If the varied group performs better in the testing stage, this is taken for evidence of the benefits of variability hypothesis.
-Even within this relatively straightforward between-groups design, researchers must navigate several crucial methodological choices, highlighted below:
+Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
 
-1)  Variables Subject to Variation.
-In multidimensional tasks, researchers have the option to vary numerous variables.
-The experimenters must decide the specific dimension(s) across which variation will occur.
-For instance, in a projectile throwing accuracy task -- researchers might vary the distance from the target, the size of the target, the weight of the projectile.
-They might also vary a contextual variable not directly relevant to the task, but which will still be encoded by the subject on a trial by trial basis, e.g.
-the background color.
-
-2)  Magnitude of Variation, relative to the control condition.
-The simplest comparison would be to compare a constant group who trains with 1 example/condition, against a varied group that trains from 2 examples/conditions.
-However, it is not uncommon in the literature for the varied condition to train from 3 or 4 conditions.
-For example, @catalanoDistantTransferCoincident1984a train varied subjects from 4 different velocities in their coincident timing task, and [@goodeSuperiorityVariableRepeated2008] have varied subjects' practice with 3 different variants (i.e.
-different letter scrambles of the same word) of an anagram for a given word, while their constant participants view the same variant 3 different times.
-Alternatively, rather than a constant vs.
-varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items [@nosofskyModelguidedSearchOptimal2018].
-
-3)  Locations within Task-Space.
-For tasks in which the stimuli or conditions fall within a continuous metric space, the experimenter must decide whether the varied instances are relatively close together (e.g.
-throwing a ball from a distance of 4 feet and 5 feet), or far apart (throwing from 4 feet and 20 feet).
-Spreading the varied training items further apart may be beneficial in terms of providing a more representative sample of the task space to the learner, however large distances may also result in significant differences in difficulty between the training examples, which can be a common confound in variability studies.
-
-4)  Proximity of Testing to Training Conditions.
-Intuitively, the fairest form of comparison is to include testing conditions that are of an equivalent distance from both the varied and constant groups.
-However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978].
+Research on the effects of varied training typically compares a group of participants trained with minimal variability of examples against a group with greater variability [@czyzVariabilityPracticeInformation2021; @ravivHowVariabilityShapes2022].
 
@@
 higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyTestsExemplarmemoryModel2018].
+A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyModelguidedSearchOptimal2019].
 For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
@@
 Null effects of both manipulations have been reported [see @magillReviewContextualInterference1990; @vanrossumSchmidtSchemaTheory1990 for reviews], and a variety of moderators have emerged.
-In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
+In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic activities, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
 non-athlete) x (constant vs.

### 2024-04-08 Sections/hold_temp.qmd
tweaks

--- 2024-04-05 Sections/full.qmd
@@
----
-title: Full Dissertation
-subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: 04/04/24
-#page-layout: full
-code-fold: true
-code-tools: true
-toc: true
-toc-location: body
-toc-title: Contents
-execute: 
-  warning: false
-  eval: true
-format:
-  html: default
-  hugo-md:
-    echo: false
-    output: false
-    html-math-method: mathjax
-    output-file: diss_full_hugo.md
-  gfm:
-    echo: true
-    output-file: diss_full_gfm.md
-  hikmah-manuscript-pdf:
-    echo: false
-    output-file: "tg_full_disser.pdf"
-    mainfont: "Linux Libertine O"
-    mainfontoptions:
-      - "Numbers=Proportional"
-      - "Numbers=OldStyle"
-    mathfont: "Libertinus Math"
-editor: 
-  markdown: 
-    wrap: 72
-prefer-html: true
----
-
-# Variability and Generalization
-
-The factors that influence the generalization of learning are of considerable interest to both researchers exploring the human learning system and practitioners aiming to enhance the effectiveness of educational and training interventions.
-The present effort will focus specifically on the role of variability in the learning input.
-Variability manipulations typically regulate either the number of distinct instances presented to learners during training, or the dispersion of these instances.
-Such manipulations have been empirically demonstrated to affect subsequent generalization performance.
-This essay will offer an in-depth review of the extant literature on the influence of variability, spanning multiple relevant domains.
-
 ## The study of variability
@@
 Then, subjects in both groups complete an identical testing stage which often consists items/conditions seen during training, and novel items/conditions.
+
 If the varied group performs better in the testing stage, this is taken for evidence of the benefits of variability hypothesis.
@@
 However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978].
-
-## Variability Literature Review
-
-An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
-In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
-a low variability condition), or spread further away from the prototype (the varied-training group).
-It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
-The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
-The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
-The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
-However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
-The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
-Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
-One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
-
-## Motor skill learning
-
-Training variation has also been shown to promote transfer in motor learning.
-Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
-When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves).
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-
-One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
-Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
-The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
-Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
-12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
-Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
-However, at the halfway point of the testing stage they were allowed to see the landing location of the 4 beanbags they had thrown, and then completed the final 4 testing throws.
-In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-Although this design does not directly assess the hypothesis of varied training producing superior generalization to constant training (since the constant group is not tested from a novel position), it nevertheless offers a compelling example of the merits of varied practice.
-
-On occasion the Kerr and Booth design may be nested within a larger experimental design.
-One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue [@wrisbergVariabilityPracticeHypothesis1987].
-This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g.
-the design of Kerr and Booth.
-However, in this case the varied group did not outperform the constant group.
-A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
-
-Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket [@greenPracticeVariabilityTransfer1995a].
-Varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket.
-One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
-Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-Of course, this finding is less surprising than that of Kerr & Booth, given that varied subjects did have some prior exposure to the constant groups condition.
-This highlights an issue rarely discussed in the literature, of how much practice from an additional position might be necessary to induce benefits.
-Experimenters almost uniformly have varied participants train with an equivalent number of trials from each of their conditions
-
-One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation [@goodeSuperiorityVariableRepeated2008].
-All participants trained to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
-Although subjects in all conditions were exposed to the same 40 unique words (i.e.
-the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training).
-Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
-LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
-At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e.
-the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group.
-This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
-This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.
-
-Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
-It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
-
-Of particular relevant to the current essay is the early work of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
-constant training on multiple testing locations of graded distance from the training condition.
-Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
-The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
-Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
-As is often the case, the varied group performed worse during the training phase.
-In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
-
-## Category learning
-
-In the category learning literature, the constant vs.
-varied comparison is much less suitable.
-Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars.
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968], where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
-More recently, researchers have also begun to utilize more realistic stimuli in their experiments.
-@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
-In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
-Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
-higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyTestsExemplarmemoryModel2018].
-For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
-The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
-Moreover, the pattern of results in this study could be nicely accounted for by an extended version of the Generalized Context Model.
-
-The studies described thus far have studied the benefits of variability by exposing participants to a greater or lesser number of distinct examples during training.
-A distinct sub-literature within the category learning domain has focused much less on benefits derived from varied training, instead emphasizing how increased variability during the learning of a novel category influences how far the category boundary will then be generalized.
-The general approach is to train participants on examples from two categories, with the examples from one of the categories being more dispersed than the other.
-Participants are then tested with novel items located within ambiguous regions of the task space which allow the experimenters to assess whether the difference in variability influences how far participants generalize the category boundaries.
-
-@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
-In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
-In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart.
-Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
-Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
-Moreover, this effect was at odds with the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.
-
-Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010].
-The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
-They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
-In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial.
-They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
-
-The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present discussion.
-Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
-During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories.
-The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category.
-Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category.
-Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
-The authors then used the standard GCM framework to compare a variety of similarity-based models to account for their results.
-Of particular interest are their evaluations of a category response bias parameter, and a similarity scaling parameter.
-A model fit improvement when the response bias parameter is allowed to vary between the high-variability and low-variability trained groups is taken to suggest a simple bias for responding with one of the trained categories over the other.
-Alternatively, an improvement in fit due to a separate similarity scaling parameter may reflect the groups being differentially sensitive to the distances between stimuli.
-No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
-The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied particpants, and also for their poor performance in a recognition condition.
-Additional model comparisons suggested that this similarity rescaling applied across the entire stimulus space, rather than to the high variability category in particular.
-
-Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts [@braithwaiteEffectsVariationPrior2015].
-This study trained participants on problems involving the concept of sampling with replacement (SWR).
-Training consisted of examples that were either highly similar in their semantic context (e.g.
-all involving people selecting objects) or in which the surface features were varied between examples (e.g.
-people choosing objects AND objects selected in a sequence).
-The experimenters also surveyed how much prior knowledge each participant had with SWR.
-They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples.
-The authors hypothesized that in order to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
-To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples.
-Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
-
-Variability has also been examined within the realm of language learning.
-A particularly impressive study is that of [@perryLearnLocallyThink2010].
-In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
-All infants were introduced to three novel objects of the same category, with participants in the tight condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
-Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
-Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels of the training objects.
-The varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category, a pattern consistent with much of the existing literature.
-More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
-The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
-
-## Complications to the influence of variability
-
-### Sequence Effects
-
-A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another.
-The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
-Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter  [@sheaContextualInterferenceEffects1979].
-In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
-A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training.
-Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random.
-There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
-However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
-
-Prior to the influential @sheaContextualInterferenceEffects1979 study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
-It was later observed [@leeInfluencePracticeSchedule1985] that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
-The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts.
-One such account, the elaborative processing account [@sheaContextEffectsMemory1983], draws on the earlier work [@battigFacilitationInterference1966] and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
-Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training [@sheaContextEffectsMemory1983], and by manipulating whether subjects are able to perform comparisons during training [@wrightContributionElaborativeProcessing1992].
-An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory [@leeLocusContextualInterference].
-Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context.
-A much more recent study [@chuaPracticeVariabilityPromotes2019], replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
-The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
-In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g.
-attending to the target distance), and constant or blocked subjects reported more internal attention (e.g.
-posture or hand position).
-The authors argue that the benefits of varied/random training may be mediated by changes in attentional focus, however the claims made in the paper seem to go far beyond what can be justified by the analyses reported -- e.g.
-the increased external focus could be a simple byproduct of varied training.
-A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.
-
-## Other task and participant effects
-
-Of course, the effects of varied training, and different training sequences, are likely to be far more complex than simply more varied training being better than less, or random training being better than blocked.
-Null effects of both manipulations have been reported [see @magillReviewContextualInterference1990; @vanrossumSchmidtSchemaTheory1990 for reviews], and a variety of moderators have emerged.
-In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
-non-athlete) x (constant vs.
-blocked vs.
-random training).
-Athlete participants had superior performance during training, regardless of sequence condition, and training performance was superior for all subjects in the constant group, followed by blocked training in the middle, and then random training resulting in the worst training performance.
-Of greater interest is the pattern of testing results for novel transfer conditions.
-Among the athlete-participants, transfer performance was best for those who received random training, followed by blocked, and then constant training.
-Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
-A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training  [@guadagnoliRelationshipContextualInterference1999].
-More recently, the same pattern was observed in the concept learning literature [@braithwaiteEffectsVariationPrior2015 expt 1.].
-This study trained participants on a mathematical concept and found that participants who self-reported some prior experience with the concept improved more from pre-test to post-test after training with varied examples, while participants who reported no prior experience showed greater gains following training with highly similar examples.
-
-In addition to the influence of prior experiences described above, ample evidence also suggests that numerous aspects of the experiment may also interact with the influence of variation.
-One important study examined the impact of the amount of training completed in a force production task [@sheaContextualInterferenceContributions1990].
-This study employed a typical blocked vs.
-random training procedure, but with the additional manipulation of separate groups receiving 50, 200, or 400 total training trials.
-For the group that received only 50 training trials retention was best when training had been blocked.
-However, for the conditions that received 200 or 400 training trials the pattern was reversed, with random training resulting in superior retention than blocked training.
-These results were taken to suggest that the benefits of randomization may take time to emerge.
-Another experimental factor shown to interact with training sequence is the complexity of the training task [@albaretDifferentialEffectsTask1998].
-In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of two, three or four components).
-On a transfer task 48 hours after the completion of training, only participants trained at the lower levels of task complexity (2 or 3 components) showed superior performance to the blocked condition.
-The authors suggest that the benefits of random sequencing, thought to arise from more elaborate cognitive processing, or the necessity of continually recalling task information from long term into short term memory, are more likely to be obscured as the complexity of the task forces the blocked participants to also engage in such processes.
-
-A final important influence of particular relevance to the practice-sequence literature concerns the exact structure of "random" sequencing.
-Although the term random is commonly used for convenience, experimenters do not typically leave the order of training entirely up to chance.
-Rather, the training sequence is often constrained such that each condition must occur a minimum number of times in each quartile of the training phase, thus resulting in an even distribution the conditions throughout training.
-While the assurance of the conditions being evenly spread throughout training is consistent across studies, other aspects of the sequence structure are a bit more idiosyncratic.
-Some researchers report setting a maximum number of consecutive repetitions, e.g.
-no more than 2 consecutive trials of the same condition [@delreyEffectsContextualInterference1982; @sheaContextualInterferenceEffects1979], or structure the random trials such that the same condition never occurs consecutively [@wulfEffectTypePractice1991].
-Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition [@willeyLongtermMotorLearning2018; @chuaPracticeVariabilityPromotes2019; @wrisbergVariabilityPracticeHypothesis1987], resulting in many more switches than would arise if training was perfectly blocked.
-The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition.
-Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing [@pigottMotorSchemaStructure1984], and basketball shot training study [@landinComparisonThreePractice1997], and in a replication plus extension of the seminal [@sheaContextualInterferenceEffects1979] study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition.
-Consequences on different study schedules have also been repeatedly observed in the category learning literature [@carvalhoSequenceStudyChanges2017; @carvalhoPuttingCategoryLearning2014].
-This line of research has revealed that the effects of blocking vs.
-interleaving can depend on the structure of the category being learned, and also that the different schedules can result in the participants requiring different representations.
-A fruitful line of inquiry in the motor skill learning literature may be to attempt to identify whether structural aspects of the motor task interact with different training sequences in a reliable manner.
-
-Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed).
-Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty [@bjorkNewTheoryDisuse1992; @schmidtNewConceptualizationsPractice1992], or optimal challenge points [@guadagnoliChallengePointFramework2004].
-They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage.
-This observation is then used to justify the idea that the most enduring and generalizable learning occurs by training at an optimal level of training difficulty, with difficulty being some function of the experience of the learner, and the cognitive or visuomotor processing demands of the task.
-It then follows that the factors that tend to make training more difficult (i.e.
-increased variability or randomization), are more likely to be beneficial when the learner has some experience, or when the processing demands of the task are not too extreme (which may only occur after some experience with the task).
-Such frameworks may be helpful heuristics in some cases, but they also seem to be overly flexible such that any null result of some intervention might be accounted for by a suboptimal amount of training trials, or by suggesting the training task was too difficult.
-The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.
-
-# Project 1
-
-____________________________________________________
-[pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
-
-```{r}
-
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
-  ggh4x,htmltools,future,furrr,ez)
-#options(brms.backend="cmdstanr",mc.cores=4)
-#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
-walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-#conflicts_prefer(tidybayes::rstudent_t)
-
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-#options(brms.backend="cmdstanr",mc.cores=4)
-initial_contrasts <- options("contrasts")$contrasts
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-
-library(tidybayes)
-
-theme_set(theme_classic())
-# load the processed data from experiment 1 and 2
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
-# defaultContrasts = options()$contrasts
-# theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-```
-
-# Abstract
-
-Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
-Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
-However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
-In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
-We replicate previous findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
-Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
-
-# Introduction
-
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
-The factor of interest to the present investigation is variation during training.
-Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
-We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
-We first review the relevant concepts and literature.
-
-## Similarity and instance-based approaches to transfer of learning
-
-Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances.
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar [@posnerGenesisAbstractIdeas1968].
-Prototype models were later challenged by the success of instance-based or exemplar models -- which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978;
-@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli.
-As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
-In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
-Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
-That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
-@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
-Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work -- variability of training examples.
-
-Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
-Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
-
-Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
-throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-## Issues with Previous Research
-
-Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g.
-projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
-more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
-
-```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
-
-p=2
-c<- .0002
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
-  group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
-
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
-
-```
-
-In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
-We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
-We then examine the extent to which this advantage can be explained by an instance-based similarity model.
-
-# Experiment 1
-
-## Methods
-
-### Sample Size Estimation
-
-To obtain an independent estimate of effect size, we identified previous
-investigations which included between-subjects contrasts of varied and
-constant conditions following training on an accuracy based projectile
-launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
-2009) was then used to determine that a power of 80% requires a sample
-size of at least 23 participants per condition. All experiments reported
-in the present manuscript exceed this minimum number of participants per
-condition.
-
-### Participants
-
-Participants were recruited from an undergraduate population that is 63%
-female and consists almost entirely of individuals aged 18-22 years. A
-total of 110 Indiana University psychology students participated in
-Experiment 1. We subsequently excluded 34 participants poor performance
-at one of the dependent measures of the task (2.5-3 standard deviations
-worse than the median subject at the task) or for displaying a pattern
-of responses that was clearly indicative of a lack of engagement with
-the task (e.g. simply dropping the ball on each trial rather than
-throwing it at the target), or for reporting that they completed the
-experiment on a phone or tablet device, despite the instructions not to
-use one of these devices. A total of 74 participants were retained for
-the final analyses, 35 in the varied group and 39 in the constant group.
-
-### Task
-
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-IGAS_Methods displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-```{r}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
-
-mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
-
-```
-
-## Results
-
-## Data Processing and Statistical Packages
-
-To prepare the data, we first removed trials that were not easily
-interpretable as performance indicators in our task. Removed trials
-included: 1) those in which participants dragged the ball outside of the
-orange starting box without releasing it, 2) trials in which
-participants clicked on the ball, and then immediately released it,
-causing the ball to drop straight down, 3) outlier trials in which the
-ball was thrown more than 2.5 standard deviations further than the
-average throw (calculated separately for each throwing position), and 4)
-trials in which the ball struck the barrier. The primary measure of
-performance used in all analyses was the absolute distance away from the
-center of the target. The absolute distance was calculated on every
-trial, and then averaged within each subject to yield a single
-performance score, for each position. A consistent pattern across
-training and testing phases in both experiments was for participants to
-perform worse from throwing positions further away from the target -- a
-pattern which we refer to as the difficulty of the positions. However,
-there were no interactions between throwing position and training
-conditions, allowing us to collapse across positions in cases where
-contrasts for specific positions were not of interest. All data
-processing and statistical analyses were performed in R version 4.03 (R
-Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021)****.
-
-## Training Phase
-
-@fig-IGAS_Training1 below shows aggregate training performance binned into three
-stages representing the beginning, middle, and end of the training
-phase. Because the two conditions trained from target distances that
-were not equally difficult, it was not possible to directly compare
-performance between conditions in the training phase. Our focus for the
-training data analysis was instead to establish that participants did
-improve their performance over the course of training, and to examine
-whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided
-in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and
-condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
-such that performance improved over the course of training There was no
-significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
-and no significant interaction between condition and training stage,
-F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
-
-```{r}
-#| label: fig-IGAS_Training1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
-
-```
-
-## Testing Phase
-
-In Experiment 1, a single constant-trained group was compared against a
-single varied-trained group. At the transfer phase, all participants
-were tested from 3 positions: 1) the positions(s) from their own
-training, 2) the training position(s) of the other group, and 3) a
-position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs. constant) as a
-between-subject factor and throwing location as a within-subject
-variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\<.001, η2G = .23. The effect of training condition was significant
-F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
-between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS_Testing1
-#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-IGAS_Table1
-#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- test=test[,1:3]
-
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
-
-In Experiment 1, we found that varied training resulted in superior
-testing performance than constant training, from both a position novel
-to both groups, and from the position at which the constant group was
-trained, which was novel to the varied condition. The superiority of
-varied training over constant training even at the constant training
-position is of particular note, given that testing at this position
-should have been highly similar for participants in the constant
-condition. It should also be noted, though, that testing at the constant
-trained position is not exactly identical to training from that
-position, given that the context of testing is different in several ways
-from that of training, such as the testing trials from the different
-positions being intermixed, as well as a simple change in context as a
-function of time. Such contextual differences will be further considered
-in the General Discussion.
-
-In addition to the variation of throwing position during training, the
-participants in the varied condition of Experiment 1 also received
-training practice from the closest/easiest position, as well as from the
-furthest/most difficult position that would later be encountered by all
-participants during testing. The varied condition also had the potential
-advantage of interpolating both of the novel positions from which they
-would later be tested. Experiment 2 thus sought to address these issues
-by comparing a varied condition to multiple constant conditions.
-
-# Experiment 2
-
-In Experiment 2, we sought to replicate our findings from Experiment 1
-with a new sample of participants, while also addressing the possibility
-of the pattern of results in Experiment 1 being explained by some
-idiosyncrasy of the particular training location of the constant group
-relative to the varied group. To this end, Experiment 2 employed the
-same basic procedure as Experiment 1, but was designed with six separate
-constant groups each trained from one of six different locations (400,
-500, 625, 675, 800, or 900), and a varied group trained from two
-locations (500 and 800). Participants in all seven groups were then
-tested from each of the 6 unique positions.
-
-## Methods
-
-### Participants
-
-A total of 306 Indiana University psychology students participated in
-Experiment 2, which was also conducted online. As was the case in
-experiment 1, the undergraduate population from which we recruited
-participants was 63% female and primarily composed of 18--22-year-old
-individuals. Using the same procedure as experiment 1, we excluded 98
-participants for exceptionally poor performance at one of the dependent
-measures of the task, or for displaying a pattern of responses
-indicative of a lack of engagement with the task. A total of 208
-participants were included in the final analyses with 31 in the varied
-group and 32, 28, 37, 25, 29, 26 participants in the constant groups
-training from location 400, 500, 625, 675, 800, and 900, respectively.
-All participants were compensated with course credit.
-
-### Task and Procedure
-
-The task of Experiment 2 was identical to that of Experiment 1, in all
-but some minor adjustments to the height of the barrier, and the
-relative distance between the barrier and the target. Additionally, the
-intermittent testing trials featured in experiment 1 were not utilized
-in experiment 2, and all training and testing trials were presented with
-feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
-
-The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the
-same position for the constant groups and split evenly (70 trials each -
-randomized) for the varied group. In the testing phase, participants
-completed 30 trials from each of the six locations that had been used
-separately across each of the constant groups during training. Each of
-the constant groups thus experience one trained location and five novel
-throwing locations in the testing phase, while the varied group
-experiences 2 previously trained, and 4 novel locations.
-
-## Results
-
-### Data Processing and Statistical Packages
-
-After confirming that condition and throwing position did not have any
-significant interactions, we standardized performance within each
-position, and then average across position to yield a single performance
-measure per participant. This standardization did not influence our
-pattern of results. As in experiment 1, we performed type III ANOVA's
-due to our unbalanced design, however the pattern of results presented
-below is not altered if type 1 or type III tests are used instead. The
-statistical software for the primary analyses was the same as for
-experiment 1. Individual learning rates in the testing phase, compared
-between groups in the supplementary analyses, were fit using the TEfit
-package in R [@cochraneTEfitsNonlinearRegression2020].
-
-### Training Phase
-
-The different training conditions trained from positions that were not
-equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. @fig-e2train depicts the training
-performance of the varied group alongside that of the aggregate of the
-six constant groups (5a), and each of the 6 separate constant groups
-(5b). An ANOVA comparison with training stage (beginning, middle, end)
-as a within-group factor and group (the varied condition vs. the 6
-constant conditions collapsed together) as a between-subject factor
-revealed no significant effect of group on training performance,
-F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training
-stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant
-interaction between group and training stage, F(2,412)=.489 p=.61,
-$\eta^{2}_G$ \<.01. We also tested for a difference in training
-performance between the varied group and the two constant groups that
-trained matching throwing positions (i.e., the constant groups training
-from position 500, and position 800). The results of our ANOVA on this
-limited dataset mirrors that of the full-group analysis, with no
-significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a
-significant effect of training stage F(2,172)=56.29, p\<.001,
-$\eta^{2}_G$ =.11, and no significant interaction between group and
-training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
-
-```{r}
-
-e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
-
-exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
-
-exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
-
-exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
-
-exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
-
-transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
-
-# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
-# novelAll <- novelAll %>% group_by(positionX) %>%
-#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
-novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
-
-constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
-variedTest <- transfer %>% filter(condit==7) # only varied testing
-variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
-
-variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
-constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
-variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
-
-exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-```
-
-```{r}
-#| label: fig-e2train
-#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
-On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 8
-
-### New - 3 stage
-e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
-  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
-  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
-
-e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
-  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
-
-#plot_grid(e2train1,e2train2,ncol=1)
-
-e2train1/e2train2
-
-```
-
-### Testing Phase
-
-In Experiment 2, a single varied condition (trained from two positions,
-500 and 800), was compared against six separate constant groups (trained
-from a single position, 400, 500, 625, 675, 800 or 900). For the testing
-phase, all participants were tested from all six positions, four of
-which were novel for the varied condition, and five of which were novel
-for each of the constant groups. For a general comparison, we took the
-absolute deviations for each throwing position and computed standardized
-scores across all participants, and then averaged across throwing
-position. The six constant groups were then collapsed together allowing
-us to make a simple comparison between training conditions (constant vs.
-varied). A type III between-subjects ANOVA was performed, yielding a
-significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$
-=.02. Descriptive statistics for each condition are shown in table 2. In
-@fig-e2testa visualizes the consistent advantage of the varied condition
-over the constant groups across the testing positions. @fig-e2testa shows
-performance between the varied condition and the individual constant
-groups.
-
-```{r}
-#| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 9
-
-# manuscript plot
-e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)+
-  ggtitle("A")
-
-e2test2<-exp2.Test7 %>% 
-  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
-  facet_wrap(~ThrowPosition4)+
-  ylab("Mean Distance From Center Of Target")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
-
-e2test1 / e2test2
-
-```
-
-\
-\
-\
-
-```{r}
-#| label: tbl-e2table1
-#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-
-tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab2=tab2[,1:3]
-
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
-.02 .
-
-```{r}
-#| label: tbl-e2table2
-#| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-
-sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
- tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
- tab3 = tab3 %>% 
-   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab3=tab3[,1:3]
-
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
-
-Finally, corresponding to the comparison of position 760 from experiment
-1, we compared the test performance of the varied group against the
-constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis
-omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). @fig-e2test1 displays
-the particular subset of comparisons utilized for this analysis. Again,
-we standardized performance within each position before performing the
-analyses on the aggregated data. In this case, the effect of condition
-did not reach statistical significance F(1,149)=3.14, p=.079,
-$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
-
-```{r}
-#| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-
-sum.variedVsNovelIden <- variedVsNovelIden  %>%
-  group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
-
-e2Test2
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-e2tab3
-#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-
-tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
-tab4=tab4 %>% group_by(Condition) %>% 
-   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab4=tab4[,1:3]
-
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
-
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
-
-# Computational Model
-
-*Controlling for the similarity between training and testing.* The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
-
-```{r}
-#| label: fig-taskSpace
-#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig-width: 11
-#| fig-height: 9
-#| 
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
-  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
-
-library(patchwork)
-ss/fs
-
-```
-
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
-
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
-(e^{-c^\cdot d^{p}_{i,j}}) $$
-
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-
-A simple linear regression revealed that these similarity scores were
-significantly predictive of performance in the transfer stage, t
-=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
-training throws and solution spaces for each of the test locations
-resulted in better performance. We then repeated the group comparisons
-above while including similarity as a covariate in the model. Comparing
-the varied and constant groups in testing performance from all testing
-positions yielded a significant effect of similarity, F(1, 205)=85.66,
-p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
-(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
-group comparison limited to only novel locations for the varied group
-pit against trained location for the constant group resulted in a
-significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
-=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
-=.07. For all comparisons, the pattern of results was consistent with
-the initial findings from experiment 2, with the varied group still
-performing significantly better than the constant group.
-
-## Fitting model parameters separately by group
-
-To directly control for similarity in Experiment 2, we developed a
-model-based measure of the similarity between training throws and
-testing conditions. This similarity measure was a significant predictor
-of testing performance, e.g., participants whose training throws were
-more similar to throws that resulted in target hits from the testing
-positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level
-benefits of varied training, which remained significant in our linear
-model predicting testing performance after similarity was added to the
-model. However, previous research has suggested that participants may
-differ in their level of generalization as a function of prior
-experience, and that such differences in generalization gradients can be
-captured by fitting the generalization parameter of an instance-based
-model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
-will increase when a rational agent encounters a wider variety of
-examples. Following these leads, we assume that in addition to learning
-the task itself, participants are also adjusting how generalizable their
-experience should be. Varied versus constant participants may be
-expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the
-instance-based model (in the present case, the c parameter) can be
-allowed to vary between the two groups to reflect the tendency of
-learners to adaptively tune the extent of their generalization. One
-specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
-variable, as with the variable training condition, then one might infer
-that future test situations will also be variable, in which case a low
-value of c will allow better generalization because generalization will
-drop off slowly with training-to-testing distance. Conversely, if one's
-training experience has little variability, as found in the constant
-training conditions, then one might adopt a high value of c so that
-generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based
-model of similarity fit against a modified model which separately fits
-the generalization parameter, c, to varied and constant participants. To
-perform this parameter fitting, we used the optim function in R, and fit
-the model to find the c value(s) that maximized the correlation between
-similarity and testing performance.
-
-Both models generate distinct similarity values between training and
-testing locations. Much like the analyses in Experiment 2, these
-similarity values are regressed against testing performance in models of
-the form shown below. As was the case previously, testing performance is
-defined as the mean absolute distance from the center of the target
-(with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\<.01). Of greater interest is the
-difference between linear model 2, in which similarity is computed from
-a single c value fit from all participants (Similarity1c), with linear
-model 4, which fits the c parameter separately between groups
-(Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\<.01), with the varied
-group still performing significantly better. However, in linear model 4
-the addition of the Similarity2c predictor results in the effect of
-training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs. constant training is accounted for by the
-Similarity2c predictor. Next, to further establish a difference between
-the models, we performed nested model comparisons using ANOVA, to see if
-the addition of the training group parameter led to a significant
-improvement in model performance. In the first comparison, ANOVA(Linear
-Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear
-Model 4) found no improvement in model performance with the addition of
-the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the
-adjusted Similarity2c model had more predictive power than those
-generated from the original Similarity1c model. Using the BIC function
-in R, we compared BIC values between linear model 1 (BIC=14604.00) and
-linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
-a modest advantage for predicting performance using a similarity measure
-computed with two c values over similarity computed with a single c
-value. When fit with separate c values, the best fitting c parameters
-for the model consistently optimized such that the c value for the
-varied group (c=.00008) was smaller in magnitude than the c value for
-the constant group(c= .00011). Recall that similarity decreases as a
-Gaussian function of distance (equation 1 above), and a smaller value of
-c will result in a more gradual drop-off in similarity as the distance
-between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which
-assumes equivalent generalization gradients between constant and varied
-trained participants is unable to account for the extent of benefits of
-varied over constant training observed at testing. The evidence for this
-in the comparative model fits is that when a varied/constant dummy-coded
-variable for condition is explicitly added to the model, the variable
-adds a significant contribution to the prediction of test performance,
-with the variable condition yielding better performance than the
-constant conditions. However, if the instance-based generalization model
-is modified to assume that the training groups can differ in the
-steepness of their generalization gradient, by incorporating a separate
-generalization parameter for each group, then the instance-based model
-can account for our experimental results without explicitly taking
-training group into account. Henceforth this model will be referred to
-as the Instance-based Generalization with Adaptive Similarity (IGAS)
-model.
-
-# General Discussion
-
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy-Model-dis we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model-dis
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
-For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
-The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
-#| fig.width: 11
-#| fig.height: 11.5
-
-#
-
-p=2
-c<- .000002
-
-trainingTestingDifference=2000;
-cvaried=.00002
-cconstant=.0005
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
-                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
-                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
-                            ) %>% 
-  group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
-
-#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
-
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
-ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
-ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
-ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
-# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
-
-#gtitle="Figure 9."
-#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-p1 <- (ip1+ip2) / (ip3+ip4)
-
-p1
-
-```
-
-As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
-However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning implementations of instance-based models in several ways.
-One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define a category item (e.g.
-size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
-movement force, velocity, angle, posture) in addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in
-support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
-Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
-Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
-A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
-lighting up consecutively, and attempt to time a button press with the
-onset of the final lamp. The design consisted of four separate constant
-groups, each training from a single lighting velocity, and a single
-varied group training with all four of the lighting velocities used by
-the individual constant groups. Participants were then split into four
-separate testing conditions, each of which were tested from a single
-novel lighting velocity of varying distance from the training
-conditions. The result of primary interest was that all participants
-performed worse as the distance between training and testing velocity
-increased -- a typical generalization decrement. However, varied
-participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in
-a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are
-similar to our own, our work is novel in that we account for our results
-with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their
-separate constant groups together may result in similarity confounds
-between varied and constant conditions that leaves their study open to
-methodological criticisms, especially in light of related work which
-demonstrated that the extent to which varied training may be beneficial
-can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
-similarity.
-
-## Limitations
-
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
-
-## Conclusion
-
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
-
-# Project 2
-
-_______________________________________________________________________________
-[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
-
-[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
-
-_______________________________________________________________________________
-
-# Introduction
-
-A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
-One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ].
-The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
-
-## Function Learning and Extrapolation
-
-The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
-
-@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
-Input stimuli and output responses were both lines of varying length.
-The correct output response was related to the length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
-@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
-Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
-In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
-All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
-
-The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
-The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models.
-The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
-The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
-When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
-
-### Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
-
-```{r}
-#| label: fig-delosh-extrap
-#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
-#| echo: false
-#| fig-width: 10
-#| cache: false 
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-source(here::here("Functions","deLosh_data.R"))
-#source(here::here("Functions","Display_Functions.R"))
-
-extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
-                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
-
-linear_function <- function(x) 2.2 * x + 30
-exponential_function <- function(x) 200 * (1 - exp(-x/25))
-quadratic_function <- function(x) 210 - (x - 50)^2 / 12
-
-linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
-    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
-  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
-
-exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
-  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
-  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
-  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
-  extrapLines +
-  scale_shape_manual(values = c(1)) +
-  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
-  theme(legend.title = element_blank(), legend.position="top") +
-  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
-                                                  linetype = c(0, 1))))
-
-quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
-  geom_point( shape = 1) +
-  stat_function( fun = quadratic_function, geom = "line") +
-  labs(title="Quadratic Function",x="",y="") + extrapLines
-
-linear_plot + exponential_plot + quadratic_plot
-```
-
-## Overview Of Present Study
-
-The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
-To the best of our knowledge, this research is the first to employ the classic constant vs.
-varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
-Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
-
-To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
-Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.
-
-## Methods
-
-*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
-Participants were randomly assigned to one of two training conditions: varied training or constant training.
-
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
-band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
-Participants were instructed that only the x velocity component of the ball was relevant to the task.
-The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
-
-/
-```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
-#| label: fig-htw-task
-#| fig-cap: The Hit the wall task.
-Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
-The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
-#| eval: true
-#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
-knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
-
-```
-
-*Procedure.* All participants completed the task online.
-Participants were provided with a description of the experiment and indicated informed consent.
-@fig-design-e1 illustrates the general procedure.
-Participants completed a total of 90 trials during the training stage.
-In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
-
-Following the training stage, participants proceeded immediately to the testing stage.
-Participants were tested from all six velocity bands, in two separate stages.
-In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
-In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
-A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
-
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
-//| fig-responsive: false
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-```
-
-```{r}
-
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e1 <- readRDS(here("data/e1_08-21-23.rds")) 
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-testE1 <- e1 |> filter(expMode2 == "Test")
-nbins=5
-trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
-trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
-```
-
-### Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.32 @rcoreteamLanguageEnvironmentStatistical2020.
-To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
-Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
-Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
-For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
-
-| Group Comparison         | Code                                                        | Data                 |
-| ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
-\
-
-In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
-extrapolation bands); 3) extent of discrimination between all six testing bands.
-We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
-Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
-The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
-Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-### Results
-
-```{r}
-#| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-##| label: tbl-e1-train-dist
-##| tbl-cap: "Experiment 1 - Learning curves. "
-##| output: asis
-
-bmm_e1_train<- trainE1_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e1_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#    kable(booktabs = TRUE)
-
-cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
-```
-
-::: {#tbl-e1-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
-| conditVaried |    79.64 |         57.92 |        101.63 |   1 |
-
-: **Experiment 1 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band.
-To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on.
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
-
-```{r}
-##| label: tbl-e1-bmm-dist
-##| tbl-cap: "E1. Training vs. Extrapolation"
-#| 
-modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
-bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE1, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-# 
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-
-# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
-cdted1 <- get_coef_details(bmtd, "conditVaried")
-cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
-cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e1-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:------------------------|-----------:|-----------:|-----------:|-----------:|
-| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
-| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
-| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
-| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |
-
-: **Experiment 1 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficients  indicate larger deviations from the baselines (Condition=constant & bandType=Trained) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
-constant) and band type (trained vs.
-extrapolation), with random intercepts for participants and bands.
-The model results are shown in @tbl-e1-bmm-dist.
-The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`).
-The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`).
-Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% credible intervals.
-
-pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-
-```
-
-```{r}
-##| label: tbl-e1-bmm-vx
-##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)
-
-cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e1_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-```
-
-\
-
-::: {#tbl-e1-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
-| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
-| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
-| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |
-
-Experiment 1.
-Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
-Varied) and Velocity Band.
-Larger coefficients on Band represent greater sensitivity/discrimination.
-{.striped .hover .sm}
-:::
-
-Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
-Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
-This difference is depicted visually in @fig-e1-test-vx.
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: Empirical distribution of velocities producing in testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-
-testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
-#| fig-cap: Experiment 1.
-Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE1$vb), 
-                     limits = c(0, 1400)) + 
-  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e1_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e1Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-     theme(legend.title=element_blank(), 
-           axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-## E1 Summary
-
-In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions  rresulted in lower final training performance is consistent with much of the prior researchon the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
-
-More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.
-
-## Experiment 2
-
-```{r}
-
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e2 <- readRDS(here("data/e2_08-04-23.rds")) 
-e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
-testE2 <- e2 |> filter(expMode2 == "Test")
-nbins=5
-trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
-
-# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
-```
-
-### Methods & Procedure
-
-The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
-The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800.
-Both groups were tested from all six bands.
-A total of 110 participants completed the experiment (Varied: 55, Constant: 55).
-
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 8.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| 
-//| 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
-
-### Results
-
-```{r}
-#| label: fig-e2-train-dev
-#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-#| eval: TRUE
-p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-bmm_e2_train <- trainE2_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e2_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
-# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T) 
-```
-
-::: {#tbl-e2-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
-| conditVaried |    36.15 |         16.35 |         55.67 |   1 |
-
-: **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups.
-We again compared training performance on the band common to both groups (600-800).
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
-```{r}
-modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
-bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE2, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
-cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
-cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e2-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-----------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
-| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
-| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
-| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |
-
-: **Experiment 2 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-\ \
-
-*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
-Constant) and band type (training vs.
-extrapolation bands).
-The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`).
-However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-#| eval: TRUE
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e2-bmm-vx
-##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
-
-cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
-sc2 <- get_coef_details(e2_vxBMM, "bandInt")
-intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
-```
-
-::: {#tbl-e2-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
-| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
-| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
-| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
-
-Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-The full model results are shown in @tbl-e2-bmm-vx.
-The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
-The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).
-
-```{r}
-#| label: fig-e2-test-vx
-#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e2-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-}
-
-pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE2$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e2_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e2Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-      theme(legend.title=element_blank(), 
-        axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-### Experiment 2 Summary
-
-Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands.
-Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.
-
-## Experiment 3
-
-```{r}
-
-e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
-    mutate(trainCon=case_when(
-    bandOrder=="Original" ~ "800",
-    bandOrder=="Reverse" ~ "600",
-    TRUE ~ NA_character_
-    ), trainCon=as.numeric(trainCon)) 
-e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
-testE3 <- e3 |> filter(expMode2 == "Test")
-nbins=5
-trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
-
-```
-
-### Methods & Procedure
-
-The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
-After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.
-within the target velocity range).
-All other aspects of the task and design are identical to Experiments 1 and 2.
-We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied).
-Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
-Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.
-
-### Results
-
-```{r}
-
-bmm_e3_train <- trainE3_max %>% 
-  brm(dist ~ condit*bandOrder, 
-      file=here("data/model_cache/e3_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
-cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
-cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
-```
-
-::: {#tbl-e3-train-dist}
-
-| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
-| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
-| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
-| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |
-
-: **Experiment 3 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-*Training*.
-@fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions).
-The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`).
-The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).
-
-```{r}
-#| label: fig-e3-train-dev
-#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
-#| eval: true
-p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
-p1
-```
-
-```{r}
-#options(brms.backend="cmdstanr",mc.cores=4)
-modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
-bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
-    data=testE3, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
-#wrap_plots(ce_bmtd3)
-
-#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")
-
-cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
-cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
-cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
-cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
-cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
-cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
-cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")
-
-```
-
-::: {#tbl-e3-bmm-dist}
-| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
-| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
-| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
-| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
-| conditVaried:bandTypeExtrapolation                  |    52.66 |         14.16 |         90.23 | 1.00 |
-| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
-| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
-| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |
-
-: **Experiment 3 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
-There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
-However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`.
-The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group.
-There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands.
-No other interactions were significant.
-
-<!-- ::: {#fig-e3-test-condEffect}
-
-![](../Assets/figs/e3_cond_effects_dist.png)
-
-E3.
-A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-::: -->
-
-```{r}
-#| label: fig-e3-test-dev
-#| fig-cap: Experiment 3 Testing Accuracy.
-A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% confidence intervals.
-#| eval: true
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-    facet_wrap(~bandOrder,ncol=1) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
- facet_wrap(~bandOrder,ncol=1)
-
-p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e3-bmm-vx
-##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
-# m2 <- fixef(e3_vxBMM)
-# mp3 <- m1[, c(1,2,4,5,6)]
-# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
-# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
-coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")
-
-```
-
-::: {#tbl-e3-bmm-vx}
-
-| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
-| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
-| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
-| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |
-
-Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist.
-For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
-The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
-Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
-However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating that the varied condition showed a greater slope coefficient on the reverse order bands, compared to the constant condition - this is clearly shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 10
-##| column: screen-inset-right
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-```
-
-```{r}
-#| label: fig-e3-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 10
-#| fig-width: 11
-##| eval: FALSE
-# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  facet_wrap(~bandOrder,ncol=1) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e3_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
-fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
-fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
-
-re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e3Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
-           fixed_effect_interaction2*(bandOrder=="Reverse") + 
-           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
-  slope = Estimate + adjust )
-
-pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density") +
-  facet_wrap(~bandOrder,ncol=1)
-
-pid_slopes3 <- re |>  
-    mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-    theme(legend.title=element_blank(), 
-      axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
-
-p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
-
-#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
-p3
-
-```
-
-### Experiment 3 Summary
-
-## Computational Model
-
-```{r}
-####| cache: false
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-```
-
-```{r}
-###| cache: true
-invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
-invisible(list2env(load_e1(), envir = .GlobalEnv))
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-e2_model <- load_e2()
-e3_model <- load_e3()
-options(contrasts = initial_contrasts)
-
-```
-
-```{r}
-#| label: fig-alm-diagram
-#| fig.cap: The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model as used in the present work.
-Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
-The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
-The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule.
-alm_plot()
-```
-
-# Modeling Approach
-
-The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997].
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
-EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
-Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
-EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
-The slope is then used to extrapolate the response to the novel test stimulus.
-Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
-We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
-This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
-
-See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
-
-::: column-page-inset-right
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-|                    | **EXAM Extrapolation**                                             |                                                                                               |
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
-| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |
-
-: ALM & EXAM Equations {#tbl-alm-exam}
-:::
-
-## Model Fitting
-
-To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
-We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant.
-The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
-Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.
-
-::: {.callout}
-
-**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
-
-To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
-ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
-Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g.
-many neural network models).
-
-The general ABC procedure is to 1) define a prior distribution over model parameters.
-2) sample candidate parameter values, $\theta^*$, from the prior.
-3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
-4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
-5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
-6) Repeat until desired number of posterior samples are obtained.
-
-Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
-For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
-For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
-For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
-After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
-For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
-
-::: column-page-inset-left
-$$
-discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
-$$ {#eq-discrep-test}
-
-$$
-\begin{aligned} \\
-discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
-discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
-\end{aligned}
-$$ {#eq-discrep-train}
-:::
-
-The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
-The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
-Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
-Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
-The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
-Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
-After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
-In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
-To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
-:::
-
-For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution.
-Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant.
-Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs.
-To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.
-
-### Modelling Results
-
-#### Group level Patterns
-
-```{r}
-#| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-post_tabs <- abc_tables(post_dat,post_dat_l)
-train_tab <- abc_train_tables(pd_train,pd_train_l)
-
-e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
-
-e1_tab %>%
-  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
-  summarize(ME = mean(mean_error), .groups = "drop") %>%
-  pivot_wider(
-    names_from = c(Model, condit),
-    values_from = ME,
-    names_sep = "_"  # Add this line to specify the separator for column names
-  ) %>%
-  rename("Fit Method" = Fit_Method) %>%
-  gt() %>%
-  cols_move_to_start(columns = c(`Task Stage`)) %>%
-  cols_label(
-    `Task Stage` = "Task Stage"
-  ) %>%
-  fmt_number(
-    columns = starts_with("ALM") | starts_with("EXAM"),
-    decimals = 2
-  ) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = cell_fill(color = "white"),
-     locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_style(
-    style = cell_borders(sides = "top", color = "black", weight = px(1)),
-    locations = cells_column_labels()
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10, 
-    quarto.disable_processing = TRUE
-  ) 
-```
-
-```{r}
-#| label: fig-htw-post-dist
-#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters.
-Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y axes of the plots for the c parameter are scaled logarithmically."
-#| fig-height: 6
-#| fig-width: 10
-
-c_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
-  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
-
-lr_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
-  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
-c_post + lr_post
-```
-
-```{r}
-#| label: fig-htw-resid-pred
-#| fig-cap: "Model residuals for each combination of training condition, fit method, and model.
-Residuals reflect the difference between observed and predicted values.
-Lower values indicate better model fit.
-Note that y axes are scaled differently between facets.
-A) Residuals predicting each block of the training data.
-B) Residuals predicting each band during the testing stage.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-#| fig-height: 14
-#| fig-width: 11
-
-train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
-  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
-  group_by(id,condit,Model,Fit_Method,Block) |>
-  summarise(mean_error=mean(mean_error)) |>
-  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
-  stat_bar + 
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
-   scale_x_discrete(guide = "axis_nested") +
-  scale_fill_manual(values=c("gray10","gray50","gray92"))+
-  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
-  theme(legend.position="top")
-
-test_resid <-  post_dat |> 
-   group_by(id,condit,x,Model,Fit_Method,bandType) |>
-    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
-  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
-  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
-  scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
-  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")
-
-(train_resid / test_resid) +
-  #plot_layout(heights=c(1,1.5)) & 
-  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
-```
-
-The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat.
-There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences.
-The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
-
-We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model.
-Aggregated residuals are displayed in @fig-htw-resid-pred.
-The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method .
-Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms).
-The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models.
-It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task.
-Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories.
-However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data.
-All subsequent analyses and discussion will thus focus on the testing stage.
-
-The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots).
-Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
-The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models.
-Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.
-
-```{r}
-#| label: fig-cm-vx-pat
-#| fig-cap: "Empirical data and Model predictions for mean velocity across target bands.
-Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs.
-Varied) are separated by columns.
-Each facet contains the predictions of ALM and EXAM, alongside the observed data."
-#| fig-height: 10
-#| fig-width: 10
-
-post_dat_l |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> 
- #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
- ggplot(aes(x=Resp,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-    facet_wrap(~rename_fm(Fit_Method)+condit, ncol=2,strip.position = "top", scales = "free_x") +
-        scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-         strip.background = element_blank(),
-         strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(10,0,0,0), "pt")) + 
-         labs(title="Model Predictions - Experiment 1 Data", y="Vx")
-```
-
-```{r}
-#| label: fig-ee-e1
-#| fig-caption: conditional and marginal effects
-#| fig-height: 8
-#| fig-width: 10
-###| eval: false
-
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
-  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
-e1_ee_brm_ae <- brm(data=pdl,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-
-# plot_custom_effects <- function(model) {
-#   # Extract posterior samples for fixed effects
-#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
-
-#   # Calculate conditional effects
-#   post_samples <- post_samples %>%
-#     mutate(
-#       ALM_Constant = b_Intercept,
-#       EXAM_Constant = b_Intercept + b_ModelEXAM,
-#       ALM_Varied = b_Intercept + b_conditVaried,
-#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
-#     )
-
-#   # Reshape data for plotting
-#   plot_data <- post_samples %>%
-#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
-#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
-#     separate(Condition, into = c("Model", "Condit"), sep = "_")
-
-#   # Plot conditional effects
-#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
-#     geom_boxplot() +
-#     theme_minimal() +
-#     labs(x = "Model", y = "Estimate", color = "Condition")
-# }
-# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
-
-bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
-bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
-bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")
-
-posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
-  select(starts_with("b_")) %>%
-  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))
-
-constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
-varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
-comparison_EXAM <- constant_EXAM - varied_EXAM
-summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
-
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)
-
-# full set of Model x condit contrasts
-# ALM - EXAM
-# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
-#   pluck("contrasts") |> 
-#   gather_emmeans_draws() |> 
-#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
-
-# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()
-
-# Constant - Varied
-# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
-# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
-#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
-# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
-
-p_em_1 <- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
-  pluck("contrasts") |>
-  gather_emmeans_draws() |> 
-  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
-  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
-  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")
-
-p_ce_1 / p_em_1
-```
-
-To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
-EXAM) and training condition (Constant vs.
-Varied).
-
-Model errors were significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM.
-There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group.
-To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
-The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
-
-```{r}
-#| label: tbl-htw-modelError-e23
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-
-post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
-train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
-
-pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e2_tab <- rbind(post_tabs2$agg_pred_full |>
- mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
- mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
-train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
-
-pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e3_tab <- rbind(post_tabs3$agg_pred_full |> 
-  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
-gt_table <- e23_tab %>%
-  pivot_wider(
-    names_from = c(Exp, Model, condit),
-    values_from = mean_error,
-    names_glue = "{Exp}_{Model}_{condit}"
-  ) %>%
-  arrange(Fit_Method, `Task Stage`) %>%
-  gt() %>%
-  cols_move_to_start(columns = `Task Stage`) %>%
-  cols_label(`Task Stage` = "Task Stage") %>%
-  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = list(
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
-  ) 
-gt_table
-```
-
-```{r}
-#| label: fig-cm-vx-pat-e2-e3
-#| fig-height: 8
-#| fig-width: 10
-#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage.
-Observed data is shown on the right.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-
-rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
- e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
-  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
-  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
-  stat_bar + 
-    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
-    scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .7), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-        #  strip.background = element_blank(),
-        #  strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(20,0,0,0), "pt")) + 
-         labs(title="Model Predictions Experiment 2 & 3", y="vx")
-```
-
-```{r}
-#| label: tbl-htw-ee-e23
-#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and the interaction between Model and Condition.
-The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
-The intercept reflects the baseline of ALM and Constant.
-The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
-Lower values indicate better model fit."
-
-e2_ee_brm_ae <- brm(data=pdl2,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
-bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
-bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
-
-bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
-
-e3_ee_brm_ae <- brm(data=pdl3,
-  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
-bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
-bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
-bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
-
-bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
-               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
-  relocate(exp, .before=Term)
-
-bct_table <- bct %>%
-  mutate(
-    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
-    pd = round(pd, 2)
-  ) %>%
-  gt() %>%
-  # tab_header(
-  #   title = "Bayesian Model Results",
-  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
-  # ) %>%
-  cols_label(
-    exp = "Experiment",
-    Term = "Term",
-    Estimate = "Estimate",
-    `95% CrI Lower` = "95% CrI Lower",
-    `95% CrI Upper` = "95% CrI Upper",
-    pd = "pd"
-  ) %>%
-  fmt_number(
-    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
-    decimals = 2
-  ) %>%
-  fmt_number(
-    columns = pd,
-    decimals = 2
-  ) %>%
-  tab_spanner(
-    label = "Credible Interval",
-    columns = c(`95% CrI Lower`, `95% CrI Upper`)
-  ) %>%
-  tab_style(
-    style = list(
-      #cell_fill(color = "lightgray"),
-      cell_text(weight = "bold"), 
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(
-      columns = c(Estimate, pd),
-      rows = Term=="ModelEXAM:conditVaried"
-    )
-  ) %>%
-   tab_row_group(
-    label = "Experiment 3",
-    rows = exp == "Exp 3"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 2",
-    rows = exp == "Exp 2"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 1",
-    rows = exp == "Exp 1"
-  ) %>%
-  tab_options(
-    table.font.size = 10,
-    heading.title.font.size = 16,
-    heading.subtitle.font.size = 14,
-    quarto.disable_processing = TRUE
-    #row_group.background.color = "gray95"
-  )
-bct_table
-
-```
-
-*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
-For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
-The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
-The Bayesian regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
-The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
-Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
-Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
-We thus also controleld for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
-There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
-
-```{r}
-#| label: fig-e2_e3_ae
-#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied) on Model Error for Experiment 2 and 3 data.
-Experiment 3 also includes a control for the order of training vs.
-testing bands (original order vs.
-reverse order)."
-#| fig-height: 6
-#| fig-width: 9
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
-p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-  p_e2 <- (p1 + p2+ p3) 
-# #wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
-                         effects = "Model:condit", 
-                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
-     points=FALSE,plot=FALSE)$`Model:condit` + 
-     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
-     theme(legend.position="right") + 
-     scale_color_manual(values=wes_palette("Darjeeling1"))
-
-p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- p2 <- (p1 + p2+ p3)
- (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-```
-
-*Computational Model Summary*.
-Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23).
-This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group.
-It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model.
-A subset of these participants are shown in @fig-htw-indv-pred.
-
-```{r}
-#| label: fig-htw-best-model
-#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
-#| fig-height: 12
-#| fig-width: 11
-
-tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
-  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
-  filter(Fit_Method=="Test_Train") |>
-  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
-    mutate(e2=abs(y-pred)) |> 
-    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
-    group_by(id,condit,Model,Fit_Method,Exp) |> 
-    summarise(mean_error=mean(mean_error)) |> 
-    arrange(id,condit,Fit_Method) |>
-    round_tibble(1)
-
-best_id <- tid1 |> 
-  group_by(id,condit,Fit_Method) |> 
-  mutate(best=ifelse(mean_error==min(mean_error),1,0))
-
-lowest_error_model <- best_id %>%
-  group_by(id, condit,Fit_Method, Exp) %>%
-  summarise(Best_Model = Model[which.min(mean_error)],
-            Lowest_error = min(mean_error),
-            differential = min(mean_error) - max(mean_error)) %>%
-  ungroup()
-
-error_difference<- best_id %>%
-  select(id, condit, Model,Fit_Method, mean_error) %>%
-  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
-  mutate(Error_difference = (ALM - EXAM))
-
-full_comparison <- lowest_error_model |> 
-  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
-  group_by(condit,Fit_Method,Best_Model) |> 
-  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
-  arrange(Fit_Method,-Error_difference)
-
-full_comparison |> 
-  filter(Fit_Method=="Test_Train") |> 
-  ungroup() |>
-  mutate(id = reorder(id, Error_difference)) %>%
-  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
-  geom_col() +
-  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
-  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
-  theme(axis.text.y = element_text(size=8)) +
-  labs(fill="Best Model",
-  x="Mean Model Error Difference (ALM - EXAM)",
-  y="Participant")
-
-```
-
-```{r  fig.width=11, fig.height=10}
-#| label: fig-htw-indv-pred
-#| fig-cap: Model predictions alongside observed data for a subset of individual participants.
-A) 3 constant and 3 varied participants fit to both the test and training data.
-B) 3 constant and 3 varied subjects fit to only the trainign data.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands.
-#| fig-height: 7
-#| fig-width: 10
-
-cId_tr <- c(137, 181, 11)
-vId_tr <- c(14, 193, 47)
-cId_tt <- c(11, 93, 35)
-vId_tt <- c(1,14,74)
-cId_new <- c(175, 68, 93, 74)
-# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")
-
-e1_sbjs <- c(49,68,155, 175,74)
-e3_sbjs <-  c(245, 280, 249)
-e2_sbjs <- c(197, 157, 312, 334)
-cFinal <- c(49, 128,202 )
-vFinal <- c(68,70,245)
-
-indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
-  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
-  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))
-
-testIndv <- indv_post_l |> 
-#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
-   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
-  group_by(id,condit,Fit_Method,Model,Resp) |>
-   mutate(flab=paste0("Subject: ",id)) |>
-  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar_sd + 
-  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
-  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
-  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
-  labs(title="Individual Participant fits from Test & Train Fitting Method",
-       y="X Velocity",fill="Target Velocity") +
-   guides(fill = guide_legend(nrow = 1)) + 
-  theme(legend.position = "bottom",axis.title.x = element_blank())
-
-testIndv 
-```
-
-## Project 2 Discussion
-
-*Experimental Result Summary*
-
-Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
-In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-
-Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
-The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.
-
-Experiment 2 extended these findings by reversing the order of the training and testing bands.
-Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases.
-However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.
-
-In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments.
-Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied).
-The varied condition showed larger deviations at the end of training, consistent with the previous experiments.
-Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition.
-During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands.
-The reverse order conditions showed smaller deviations compared to the original order conditions.
-Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.
-
-All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015].
-The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group.
-Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.
-
-Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
-Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
-A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
-These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study.
-@vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
-However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
-
-*Modeling Summary*
-EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group.
-May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule.
-But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval.
-The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
-
-*Limitations*
-
-While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
-First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
-Such a difference may be an unavoidable consequence of varied vs.
-constant design which match the total number of training trials between the two groups.
-However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
-Another limitation is that the testing stage did not include any interpolation items, i.e.
-the participants tested only from the training bands they experienced during training, or from extrapolation bands.
-The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
-Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
-Finally, the task employed in the present study consisted of only a linear, positive function.
-Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
-It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
-
-## General Discussion
-
-To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
-
-### Empirical Results Summary
-
-Across two projects, we investigated the influence of training variability on learning and generalization in visuomotor tasks.
-In Project 1 (HTT), we consistently found that varied training led to superior performance relative to constant training, even when testing at positions that were identical to the constant group's training.
-In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing.
-This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
-
-### Differences between the two Projects
-
-Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
-
-In HTT, the salient perceptual elements of the task (i.e.
-the launching box, target and barrier) are subject to variation (i.e.
-different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
-Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
-If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
-Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
-the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
-
-The HTT and HTW tasks also differed in terms of general task complexity.
-The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
-Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
-
-::: {#tbl-task-diff}
-
-| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
-| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
-| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
-| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
-Only x velocity is relevant.
-|
-| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
-| Simpler: smooth, linear mapping between velocity and feedback.
-|
-| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
-salient differences in distance between launching box and target.
-| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
-|
-| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
-|
-| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
-| Some potential for learning during no-feedback testing by observing ball trajectory.
-|
-| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
-| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
-|
-| Testing Structure                               | Random interleaving of trained/transfer testing distances.
-| Blocked structure, separately testing trained vs extrapolation testing bands.
-|
-
-Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
-:::
-
-# References
-
-::: {#refs}
-:::
-
-# Appendix
-
-{{< include Appendix/IGAS-Supplemental.qmd >}}

### 2024-04-08 Sections/IGAS.qmd
update

@@
 Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
-throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
 

### 2024-04-08 Sections/Introduction.qmd
update

@@
 Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
 
-Research on the effects of varied training typically compares a group of participants trained with minimal variability of examples against a group with greater variability [@czyzVariabilityPracticeInformation2021; @ravivHowVariabilityShapes2022].
+Research on the effects of varied training typically compares a 'low variability'  group against a 'high variability' group.
+
+Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
+Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
+throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
+Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
+Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
+Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
+For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
+Both groups are then tested from novel locations.
+Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
 

### 2024-04-09 Sections/HTW.qmd
fix igas crossrefs; add callout styling
add e3 summary and tweak some table captions

@@
 [Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
-
 _______________________________________________________________________________
@@
 extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
+The Intercept represents the baseline condition, (constant training;  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
+Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.{.striped .hover .sm}
 :::
@@
 
-Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
+Experiment 3.
+Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs.
+Varied) and Velocity Band.
+The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the linear slope for the baseline condition.
+{.striped .hover .sm}
 :::
@@
 ### Experiment 3 Summary
+
+In Experiment 3, we investigated the effects of training condition (constant vs.
+varied) and band type (training vs.
+extrapolation) on participants' accuracy and discrimination during the testing phase.
+Unlike the previous experiments, participants received ordinal feedback during the training phase.
+Additionally, Experiment 3 included both the original order condition from Experiment 1 and the reverse order condition from Experiment 2.
+The results revealed no significant main effects of training condition on testing accuracy, nor was there a significant difference between groups in band discrimination.
+However, we observed a significant three-way interaction for the discrimination analysis, indicating that the varied condition showed a steeper slope coefficient on the reverse order bands compared to the constant condition.
+This result suggests that varied training enhanced participants' ability to discriminate between velocity bands, but only when the band order was reversed during testing.
 

### 2024-04-09 Sections/full.qmd
add e3 summary and tweak some table captions

@@
 The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
 
@@
 extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant training;  trained bands & original order) - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
+The Intercept represents the baseline condition, (constant training;  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
+Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
+{.striped .hover .sm}
 :::
@@
 
-Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
+Experiment 3.
+Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs.
+Varied) and Velocity Band.
+The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the linear slope for the baseline condition.
+.hover .sm}
 :::

### 2024-04-09 Sections/full.qmd
fix crossref and re-render

@@
 Alternatively, rather than a constant vs.
-varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items [@nosofskyModelguidedSearchOptimal2018].
+varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items [@nosofskyModelguidedSearchOptimal2019].
 
@@
 Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
-Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
 Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
@@
 Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
+
 In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-
 Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.

### 2024-04-09 Sections/IGAS.qmd
generate md of IGAS

@@
 toc-title: Contents
+format:
+  html: default
+  hugo-md:
+    echo: false
+    include: false
+    html-math-method: mathjax
+    output-file: igas_hugo.md
 execute: 

### 2024-04-11 Sections/Introduction.qmd
generate md of IGAS
intro update

--- 2024-04-08 Sections/Introduction.qmd
@@
 Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
 
-Research on the effects of varied training typically compares a group of participants trained with minimal variability of examples against a group with greater variability [@czyzVariabilityPracticeInformation2021; @ravivHowVariabilityShapes2022].
+Research on the effects of varied training typically manipulates variability in one of two ways.
+In the first approach, a high variability group is exposed to a greater number of unique instances during training, while a low variability group receives fewer unique instances with more repetitions.
+Alternatively, both groups may receive the same number of unique instances, but the high variability group's instances are more widely distributed or spread out in the relevant psychological space, while the low variability group's instances are clustered more tightly together.
+Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
+Researchers will usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
+The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
+However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to make it easy to measure how much performance degrades as a function of how far away testing items are from the training items.
 
-## Variability Literature Review
-
-An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
-In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
-a low variability condition), or spread further away from the prototype (the varied-training group).
-It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
-The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
-The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
-The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
-However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
-The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
-Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
-One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
-
-## Motor skill learning
-
-Training variation has also been shown to promote transfer in motor learning.
-Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
-When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves).
+The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
+Much of this research has been influenced by the work of (@schmidtSchemaTheoryDiscrete1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
+an underhand throw).
+When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
+Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer.
 Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
 Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
+For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
+Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
 
@@
 However, in this case the varied group did not outperform the constant group.
-A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
 
@@
 In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
+
+ A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
+However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+
+## Variability Literature Review
+
+An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
+In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
+a low variability condition), or spread further away from the prototype (the varied-training group).
+It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
+The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
+The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
+The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
+However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
+The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
+Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
+One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
+
+## Motor skill learning
+
+Training variation has also been shown to promote transfer in motor learning.
+Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
+When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
+Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves).
+Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
+Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
+For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
+Both groups are then tested from novel locations.
 

### 2024-04-11 Sections/hold_temp.qmd
intro update

@@
 However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978].
+
+## Schmidt
+
+A noteworthy early study that explored the benefits of variability, as postulated by Schmidt, was conducted by Kerr & Booth (1978).
+In their experiment, two groups of children, ages 8 and 12, were tasked with a bean bag throwing exercise.
+The constant training group practiced aiming at a target 3 feet away, while the varied training group practiced from distances of both 2 and 4 feet.
+During this training phase, participants were blindfolded to prevent visual targeting, though they could check where the beanbag landed after each attempt for feedback.
+Twelve weeks later, all participants were tested at the novel distance of 3 feet, which was familiar to the constant group but new to the varied group.
+Again blindfolded, they received feedback only after the first half of their throws during the final test.
+Notably, both age groups exhibited significantly better performance in the varied condition, with a more pronounced effect in the younger cohort.
+Although this study design indirectly supports the hypothesis that varied training promotes better generalization than constant training, it robustly demonstrates the efficacy of varied practice without directly testing novel positions for the constant group.
+
+## Literature Review
+
+An early and influential work on the influence of variability on category learning is that of Posner & Keele (1968).
+In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g. a low variability condition), or spread further away from the prototype (the varied-training group).
+It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
+The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
+The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
+The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" (Schmidt, 1975), which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
+However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
+The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later (Palmeri & Nosofsky, 2001), when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
+Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
+One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.

### 2024-04-11 Sections/Introduction.qmd
intro development

@@
 Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
-However, at the halfway point of the testing stage they were allowed to see the landing location of the 4 beanbags they had thrown, and then completed the final 4 testing throws.
 In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-Although this design does not directly assess the hypothesis of varied training producing superior generalization to constant training (since the constant group is not tested from a novel position), it nevertheless offers a compelling example of the merits of varied practice.
-
-On occasion the Kerr and Booth design may be nested within a larger experimental design.
-One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue [@wrisbergVariabilityPracticeHypothesis1987].
-This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g.
-the design of Kerr and Booth.
-However, in this case the varied group did not outperform the constant group.
-
-Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket [@greenPracticeVariabilityTransfer1995a].
-Varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket.
+This result offers a particularly compelling example of the merits of varied practice, given that the varied group was able to outperform the constant group even from the  home turf location where one may have expected the constatn group to have the strongest advantage.
+A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a].
 One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
 Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-Of course, this finding is less surprising than that of Kerr & Booth, given that varied subjects did have some prior exposure to the constant groups condition.
-This highlights an issue rarely discussed in the literature, of how much practice from an additional position might be necessary to induce benefits.
-Experimenters almost uniformly have varied participants train with an equivalent number of trials from each of their conditions
+However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperfroms the constant group even from the constants group's home turf has not been consistently replicated.
+One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
+This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
+However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
 
-One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation [@goodeSuperiorityVariableRepeated2008].
-All participants trained to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
+Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
+However, despite its appeal this particular contrast is relatively uncommon in the literature.
+It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
+A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
+@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
+@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
+A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
+Of particular relevance to the current work is the early study of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
+constant training on multiple testing locations of graded distance from the training condition.
+Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
+The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
+Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
+As is often the case, the varied group performed worse during the training phase.
+In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
+
+Benefits of varied training have also been observed in many studies outside of the sensorimotor domain.
+@goodeSuperiorityVariableRepeated2008 trained participants to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
 Although subjects in all conditions were exposed to the same 40 unique words (i.e.
@@
 
-Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
-It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
+In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
+typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
 
-Of particular relevant to the current essay is the early work of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
-constant training on multiple testing locations of graded distance from the training condition.
-Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
-The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
-Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
-As is often the case, the varied group performed worse during the training phase.
-In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
-
- A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-## Variability Literature Review
-
-An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
-In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
-a low variability condition), or spread further away from the prototype (the varied-training group).
-It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
-The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
-The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
-The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
-However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
-The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
-Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
-One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
-
-## Motor skill learning
-
-Training variation has also been shown to promote transfer in motor learning.
-Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
-When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves).
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-
-## Category learning
-
-In the category learning literature, the constant vs.
-varied comparison is much less suitable.
-Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars.
 Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968], where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
@@
 The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+
+## Variability Literature Review
+
+An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
+In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
+a low variability condition), or spread further away from the prototype (the varied-training group).
+It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
+The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
+The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
+The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
+However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
+The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
+Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
+One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
+
+## Category learning
 

### 2024-04-11 Sections/hold_temp.qmd
intro development

@@
+Schema theory and typical study design
+
+Kerr & Booth pattern
+Wrisberg - kerr & booth contrasts plus other comparisons
+Green 1995 - partial support of Kerr & Booth - varied group gets less experience from testing scenario
+Goode analogy study - reps Kerr & Booth
+
+More common designs - lots of citations
+
+catalano 1984 - description
+Wiley 2018 - failed replication of Kerr & Booth
+
+One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue [@wrisbergVariabilityPracticeHypothesis1987].
+This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g.
+the design of Kerr and Booth.
+However, in this case the varied group did not outperform the constant group.
+
 ## The study of variability
@@
 
+Training Condtions - how many, how different, how far apart
+
 ## Schmidt

### 2024-04-11 Sections/Introduction.qmd
finish intro

@@
 ---
-#title: Introduction
+title: Introduction
 format:
@@
     output-file: d_into_gfm.md
+  hikmah-manuscript-pdf:
+    echo: false
+    output-file: "intro_pdf.pdf"
+    mainfont: "Linux Libertine O"
+    mainfontoptions:
+      - "Numbers=Proportional"
+      - "Numbers=OldStyle"
+    mathfont: "Libertinus Math"
 ---
@@
 In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
-typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
+typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
 
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968], where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
-More recently, researchers have also begun to utilize more realistic stimuli in their experiments.
+Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968].
+A seminal study by @posnerGenesisAbstractIdeas1968 trained participants to categorize artificial dot patterns, manipulating whether learners were trained with low variability examples clustered close to the category prototypes (i.e. low distortion training patterns), or higher-variability patterns spread further away from the prototype (i.e.
+high-distortion patterns).
+Participants that received training on more highly-distorted items showed superior generalization to novel high distortion patterns in the subsequent testing phase.
+It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training rathers, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
+This train-until-criterion procedure led to the high-variability condition participants tending to complete a larger number of training trials before switching to the testing stage.
+More recent work [@huHighvariabilityTrainingDoes2024], also used dot pattern categories, but matched the number of training trials across conditions.
+Under this procedure, higher-variability participants tended to reach lower levels of performance by the end of the training stage.
+The results in the testing phase were the opposite of @posnerGenesisAbstractIdeas1968,  with the low-variability training group showing superior generalization to novel high-distortion patterns (as well as generalization to novel patterns of low or medium distortion levels).
+However, whether this discrepancy is solely a result of the different training procedures is unclear, as the studies also differed in the nature of the prototype patterns used.
+@posnerGenesisAbstractIdeas1968  utilized simpler, recognizable prototypes (e.g., a triangle, the letter M, the letter F), while  @huHighvariabilityTrainingDoes2024 employed random prototype patterns.
+
+Recent studies have also begun utilizing more complex or realistic sitmuli when assessing the influence of variability on category learning.
 @wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
@@
 The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
-Moreover, the pattern of results in this study could be nicely accounted for by an extended version of the Generalized Context Model.
 
-The studies described thus far have studied the benefits of variability by exposing participants to a greater or lesser number of distinct examples during training.
-A distinct sub-literature within the category learning domain has focused much less on benefits derived from varied training, instead emphasizing how increased variability during the learning of a novel category influences how far the category boundary will then be generalized.
-The general approach is to train participants on examples from two categories, with the examples from one of the categories being more dispersed than the other.
-Participants are then tested with novel items located within ambiguous regions of the task space which allow the experimenters to assess whether the difference in variability influences how far participants generalize the category boundaries.
-
+A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g.
+the region between the two categories).
+The general approach is to train participants with examples from a high variability category and a low variability category.
+Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
 @cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
@@
 Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
-Moreover, this effect was at odds with the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.
 
 Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010].
+@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; but see @stewartEffectCategoryVariability2002].
 The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
@@
 
-The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present discussion.
+The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present work.
 Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
@@
 Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
-The authors then used the standard GCM framework to compare a variety of similarity-based models to account for their results.
-Of particular interest are their evaluations of a category response bias parameter, and a similarity scaling parameter.
-A model fit improvement when the response bias parameter is allowed to vary between the high-variability and low-variability trained groups is taken to suggest a simple bias for responding with one of the trained categories over the other.
-Alternatively, an improvement in fit due to a separate similarity scaling parameter may reflect the groups being differentially sensitive to the distances between stimuli.
+The author compared a variety of similarity-based models based around the Generalized Context Model [@nosofskyAttentionSimilarityIdentificationcategorization1986] to account for their results, manipulating whether a response-bias or similarity-scaling parameter was fit separately between variability conditions.
 No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
 The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied particpants, and also for their poor performance in a recognition condition.
-Additional model comparisons suggested that this similarity rescaling applied across the entire stimulus space, rather than to the high variability category in particular.
+This model accounted for both the extended generalization gradients of the varied particpants, and also for their poorer performance in a recognition condition.
 
-Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts [@braithwaiteEffectsVariationPrior2015].
-This study trained participants on problems involving the concept of sampling with replacement (SWR).
+Variability has also been examined in the learning of higher-order linguistic categories [@perryLearnLocallyThink2010].
+In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
+All infants were introduced to three novel objects of the same category, with participants in the "tight" condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
+Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
+Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
+By the end of the nine weeks, all of the infants had learned the labels of the training objects.
+In the testing phase, the varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category.
+More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
+The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987; @vanrossumSchmidtSchemaTheory1990], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+
+In an example of a more complex influence of training variation, [@braithwaiteEffectsVariationPrior2015] trained participants on example problems involving the concept of sampling with replacement (SWR).
 Training consisted of examples that were either highly similar in their semantic context (e.g.
@@
 Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
+Interactions between prior experience and the influence of varied training have also been observed in sensorimotor learning [@guadagnoliRelationshipContextualInterference1999;  @delreyEffectsContextualInterference1982].
+@delreyEffectsContextualInterference1982 recruited participants who self-reported either extensive, or very little experience with athletic activities, and then trained participants on a coincident timing task under with either a single constant training velocity, with one of several varied training procedures.
+Unsurprisingly, athlete participants had superior performance during training, regardless of  condition, and training performance was superior for all subjects in the constant group.
+Of greater interest is the pattern of testing results from novel transfer conditions.
+Among the athlete-participants, transfer performance was best for those who received variable training.
+Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
 
-Variability has also been examined within the realm of language learning.
-A particularly impressive study is that of [@perryLearnLocallyThink2010].
-In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
-All infants were introduced to three novel objects of the same category, with participants in the tight condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
-Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
-Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels of the training objects.
-The varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category, a pattern consistent with much of the existing literature.
-More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
-The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
+### The current work
 
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+The overarching purpose of this dissertation is to investigate the effects of training variability on learning and generalization within visuomotor skill learning and function learning.
+Our investigations is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
 
-## Variability Literature Review
+In Project 1, we investigated the influence of varied practice in a simple visuomotor projectile launching task.
+Experiments 1 and 2 compared the performance of constant and varied training groups to assess potential benefits of variability on transfer to novel testing conditions.
+To account for the observed empirical effects, we introduced the Instance-based Generalization with Adaptive Similarity (IGAS) model.
+IGAS provides a novel computational approach for quantifying the similarity between training experiences and transfer conditions, while also allowing for variability to influence the generalization gradient itself.
 
-An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
-In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
-a low variability condition), or spread further away from the prototype (the varied-training group).
-It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
-The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
-The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
-The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
-However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
-The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
-Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
-One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
-
-## Category learning
-
-## Complications to the influence of variability
-
-### Sequence Effects
-
-A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another.
-The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
-Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter  [@sheaContextualInterferenceEffects1979].
-In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
-A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training.
-Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random.
-There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
-However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
-
-Prior to the influential @sheaContextualInterferenceEffects1979 study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
-It was later observed [@leeInfluencePracticeSchedule1985] that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
-The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts.
-One such account, the elaborative processing account [@sheaContextEffectsMemory1983], draws on the earlier work [@battigFacilitationInterference1966] and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
-Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training [@sheaContextEffectsMemory1983], and by manipulating whether subjects are able to perform comparisons during training [@wrightContributionElaborativeProcessing1992].
-An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory [@leeLocusContextualInterference].
-Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context.
-A much more recent study [@chuaPracticeVariabilityPromotes2019], replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
-The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
-In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g.
-attending to the target distance), and constant or blocked subjects reported more internal attention (e.g.
-posture or hand position).
-The authors argue that the benefits of varied/random training may be mediated by changes in attentional focus, however the claims made in the paper seem to go far beyond what can be justified by the analyses reported -- e.g.
-the increased external focus could be a simple byproduct of varied training.
-A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.
-
-## Other task and participant effects
-
-Of course, the effects of varied training, and different training sequences, are likely to be far more complex than simply more varied training being better than less, or random training being better than blocked.
-Null effects of both manipulations have been reported [see @magillReviewContextualInterference1990; @vanrossumSchmidtSchemaTheory1990 for reviews], and a variety of moderators have emerged.
-In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic activities, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
-non-athlete) x (constant vs.
-blocked vs.
-random training).
-Athlete participants had superior performance during training, regardless of sequence condition, and training performance was superior for all subjects in the constant group, followed by blocked training in the middle, and then random training resulting in the worst training performance.
-Of greater interest is the pattern of testing results for novel transfer conditions.
-Among the athlete-participants, transfer performance was best for those who received random training, followed by blocked, and then constant training.
-Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
-A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training  [@guadagnoliRelationshipContextualInterference1999].
-More recently, the same pattern was observed in the concept learning literature [@braithwaiteEffectsVariationPrior2015 expt 1.].
-This study trained participants on a mathematical concept and found that participants who self-reported some prior experience with the concept improved more from pre-test to post-test after training with varied examples, while participants who reported no prior experience showed greater gains following training with highly similar examples.
-
-In addition to the influence of prior experiences described above, ample evidence also suggests that numerous aspects of the experiment may also interact with the influence of variation.
-One important study examined the impact of the amount of training completed in a force production task [@sheaContextualInterferenceContributions1990].
-This study employed a typical blocked vs.
-random training procedure, but with the additional manipulation of separate groups receiving 50, 200, or 400 total training trials.
-For the group that received only 50 training trials retention was best when training had been blocked.
-However, for the conditions that received 200 or 400 training trials the pattern was reversed, with random training resulting in superior retention than blocked training.
-These results were taken to suggest that the benefits of randomization may take time to emerge.
-Another experimental factor shown to interact with training sequence is the complexity of the training task [@albaretDifferentialEffectsTask1998].
-In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of two, three or four components).
-On a transfer task 48 hours after the completion of training, only participants trained at the lower levels of task complexity (2 or 3 components) showed superior performance to the blocked condition.
-The authors suggest that the benefits of random sequencing, thought to arise from more elaborate cognitive processing, or the necessity of continually recalling task information from long term into short term memory, are more likely to be obscured as the complexity of the task forces the blocked participants to also engage in such processes.
-
-A final important influence of particular relevance to the practice-sequence literature concerns the exact structure of "random" sequencing.
-Although the term random is commonly used for convenience, experimenters do not typically leave the order of training entirely up to chance.
-Rather, the training sequence is often constrained such that each condition must occur a minimum number of times in each quartile of the training phase, thus resulting in an even distribution the conditions throughout training.
-While the assurance of the conditions being evenly spread throughout training is consistent across studies, other aspects of the sequence structure are a bit more idiosyncratic.
-Some researchers report setting a maximum number of consecutive repetitions, e.g.
-no more than 2 consecutive trials of the same condition [@delreyEffectsContextualInterference1982; @sheaContextualInterferenceEffects1979], or structure the random trials such that the same condition never occurs consecutively [@wulfEffectTypePractice1991].
-Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition [@willeyLongtermMotorLearning2018; @chuaPracticeVariabilityPromotes2019; @wrisbergVariabilityPracticeHypothesis1987], resulting in many more switches than would arise if training was perfectly blocked.
-The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition.
-Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing [@pigottMotorSchemaStructure1984], and basketball shot training study [@landinComparisonThreePractice1997], and in a replication plus extension of the seminal [@sheaContextualInterferenceEffects1979] study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition.
-Consequences on different study schedules have also been repeatedly observed in the category learning literature [@carvalhoSequenceStudyChanges2017; @carvalhoPuttingCategoryLearning2014].
-This line of research has revealed that the effects of blocking vs.
-interleaving can depend on the structure of the category being learned, and also that the different schedules can result in the participants requiring different representations.
-A fruitful line of inquiry in the motor skill learning literature may be to attempt to identify whether structural aspects of the motor task interact with different training sequences in a reliable manner.
-
-Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed).
-Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty [@bjorkNewTheoryDisuse1992; @schmidtNewConceptualizationsPractice1992], or optimal challenge points [@guadagnoliChallengePointFramework2004].
-They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage.
-This observation is then used to justify the idea that the most enduring and generalizable learning occurs by training at an optimal level of training difficulty, with difficulty being some function of the experience of the learner, and the cognitive or visuomotor processing demands of the task.
-It then follows that the factors that tend to make training more difficult (i.e.
-increased variability or randomization), are more likely to be beneficial when the learner has some experience, or when the processing demands of the task are not too extreme (which may only occur after some experience with the task).
-Such frameworks may be helpful heuristics in some cases, but they also seem to be overly flexible such that any null result of some intervention might be accounted for by a suboptimal amount of training trials, or by suggesting the training task was too difficult.
-The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.
+Project 2 shifted focus to the domain of function learning by employing a visuomotor extrapolation task.
+Across three experiments, we examined how constant and varied training regimes affected learning, discrimination between stimuli, and the ability to extrapolate to novel regions of the function's input space.
+To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.

### 2024-04-11 Sections/full.qmd
finish intro

@@
     echo: false
-    include: false
+    #include: false
     html-math-method: mathjax
@@
 
-# Variability and Generalization
-
-The factors that influence the generalization of learning are of considerable interest to both researchers exploring the human learning system and practitioners aiming to enhance the effectiveness of educational and training interventions.
-The present effort will focus specifically on the role of variability in the learning input.
-Variability manipulations typically regulate either the number of distinct instances presented to learners during training, or the dispersion of these instances.
-Such manipulations have been empirically demonstrated to affect subsequent generalization performance.
-This essay will offer an in-depth review of the extant literature on the influence of variability, spanning multiple relevant domains.
+# Introduction
+
+The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer or generalization to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
+Such generalization challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that influence generalization, and to develop cognitive models that can predict when generalization is likely to occur.
+Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
 
@@
 
-Studies investigating the "benefits of variability" hypothesis usually assign participants to either a constant or varied group for the training stage of the experiment.
-Then, subjects in both groups complete an identical testing stage which often consists items/conditions seen during training, and novel items/conditions.
-If the varied group performs better in the testing stage, this is taken for evidence of the benefits of variability hypothesis.
-Even within this relatively straightforward between-groups design, researchers must navigate several crucial methodological choices, highlighted below:
-
-1)  Variables Subject to Variation.
-In multidimensional tasks, researchers have the option to vary numerous variables.
-The experimenters must decide the specific dimension(s) across which variation will occur.
-For instance, in a projectile throwing accuracy task -- researchers might vary the distance from the target, the size of the target, the weight of the projectile.
-They might also vary a contextual variable not directly relevant to the task, but which will still be encoded by the subject on a trial by trial basis, e.g.
-the background color.
-
-2)  Magnitude of Variation, relative to the control condition.
-The simplest comparison would be to compare a constant group who trains with 1 example/condition, against a varied group that trains from 2 examples/conditions.
-However, it is not uncommon in the literature for the varied condition to train from 3 or 4 conditions.
-For example, @catalanoDistantTransferCoincident1984a train varied subjects from 4 different velocities in their coincident timing task, and [@goodeSuperiorityVariableRepeated2008] have varied subjects' practice with 3 different variants (i.e.
-different letter scrambles of the same word) of an anagram for a given word, while their constant participants view the same variant 3 different times.
-Alternatively, rather than a constant vs.
-varied comparison, subjects in all conditions might experience a variety of training items, but with one group experiencing a greater number of unique items [@nosofskyModelguidedSearchOptimal2019].
-
-3)  Locations within Task-Space.
-For tasks in which the stimuli or conditions fall within a continuous metric space, the experimenter must decide whether the varied instances are relatively close together (e.g.
-throwing a ball from a distance of 4 feet and 5 feet), or far apart (throwing from 4 feet and 20 feet).
-Spreading the varied training items further apart may be beneficial in terms of providing a more representative sample of the task space to the learner, however large distances may also result in significant differences in difficulty between the training examples, which can be a common confound in variability studies.
-
-4)  Proximity of Testing to Training Conditions.
-Intuitively, the fairest form of comparison is to include testing conditions that are of an equivalent distance from both the varied and constant groups.
-However researchers might also attempt to demonstrate the benefits of variation as being sufficiently powerful to outperform constant training, even in cases where the constant group trained from a closer proximity to the testing conditions, or whose training conditions are identical to the testing conditions [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978].
-
-## Variability Literature Review
-
-An early and influential work on the influence of variability on category learning is that of @posnerGenesisAbstractIdeas1968.
-In an ambitious attempt to address the question of how category information is represented, the authors trained participants to categorize artificial dot patterns, manipulating whether learners were exposed to examples clustered close to the category prototypes (e.g.
-a low variability condition), or spread further away from the prototype (the varied-training group).
-It should be noted that both groups in this study were trained with the same number of unique instances and the manipulated difference was how spread out the instances were.
-The authors claim based on prior experiments using the same stimuli, that the training stimuli for the varied group were at least as far away from the testing stimuli as the training stimuli of the less-varied group.
-The authors interpreted their findings as evidence for the extraction of an abstraction or schema that is extracted and stored, and then over time becomes more likely to be the reference point from which generalization occurs, given that specific instances are thought to decay at a faster rate than prototypes or schema.
-The Posner and Keele study has been extremely influential and continues to be cited in contemporary research as clear evidence that schema abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" [@schmidtSchemaTheoryDiscrete1975], which in turn influenced decades of investigations on the potential benefits of varied training in motor skill learning.
-However, the classic Posner & Keele study despite being far more carefully designed than many subsequent studies, and despite being a relative rarity in explicitly discussing and attempting to control for potential confounds of similarity between groups, may nevertheless be emblematic of a common issue in many investigations of the effects of varied training on learning.
-The problem with Posner & Keele's conclusion was demonstrated clearly almost 3 decades later [@palmeriCentralTendenciesExtreme2001], when researchers conducting a near replication of the original study also collected similarity judgements following training and performed multidimensional scaling analysis.
-Rather than being in the middle of the training stimuli as was the case in the physical stimuli space, the psychological representation of the prototype was shown reside at an extreme point, and generalization patterns by participants that would have seemed to warrant the learning of a prototype were then easily accounted for with only the assumption that the participants encoded instances.
-One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
-
-## Motor skill learning
-
-Training variation has also been shown to promote transfer in motor learning.
-Much of this research has been influenced by the work of [@schmidtSchemaTheoryDiscrete1975], who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes a priori that learners possess general motor programs for classes of movements, such as an underhand throw.
-When called up for use, such programs must be parameterized, as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class, such as an underhand throw (though it is agnostic to the development of the movement classes themselves).
+Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
+
+Research on the effects of varied training typically manipulates variability in one of two ways.
+In the first approach, a high variability group is exposed to a greater number of unique instances during training, while a low variability group receives fewer unique instances with more repetitions.
+Alternatively, both groups may receive the same number of unique instances, but the high variability group's instances are more widely distributed or spread out in the relevant psychological space, while the low variability group's instances are clustered more tightly together.
+Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
+Researchers will usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
+The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
+However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to make it easy to measure how much performance degrades as a function of how far away testing items are from the training items.
+
+The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
+Much of this research has been influenced by the work of (@schmidtSchemaTheoryDiscrete1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
+an underhand throw).
+When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
+Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer.
 Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
 Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
+For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
+Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
 
@@
 Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
-However, at the halfway point of the testing stage they were allowed to see the landing location of the 4 beanbags they had thrown, and then completed the final 4 testing throws.
 In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-Although this design does not directly assess the hypothesis of varied training producing superior generalization to constant training (since the constant group is not tested from a novel position), it nevertheless offers a compelling example of the merits of varied practice.
-
-On occasion the Kerr and Booth design may be nested within a larger experimental design.
-One such study that used a movement timing task, wherein subjects had to move their hand from a starting location, to a target location, attempting to arrive at the target location at specific time following the onset of a cue [@wrisbergVariabilityPracticeHypothesis1987].
-This study utilized 4 different constant groups, and 3 varied groups, with one of the constant groups training under conditions identical to the testing conditions, and which were not trained on by any of the varied groups, e.g.
-the design of Kerr and Booth.
-However, in this case the varied group did not outperform the constant group.
-A more recent study attempting a slightly more direct replication of the original Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-However, this study diverged from the original in that the participants were adults; they faced away from the target and threw the beanbag backwards over their bodies; they alternated using their right and left hands every 6 trials; and underwent a relatively extreme amount of training (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-Like @wrisbergVariabilityPracticeHypothesis1987, this study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
-
-Some support for the Kerr and Booth findings was found with a relatively less common experimental task of training participants in hitting a projectile at a target with the use of a racket [@greenPracticeVariabilityTransfer1995a].
-Varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket.
+This result offers a particularly compelling example of the merits of varied practice, given that the varied group was able to outperform the constant group even from the  home turf location where one may have expected the constatn group to have the strongest advantage.
+A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a].
 One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
 Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-Of course, this finding is less surprising than that of Kerr & Booth, given that varied subjects did have some prior exposure to the constant groups condition.
-This highlights an issue rarely discussed in the literature, of how much practice from an additional position might be necessary to induce benefits.
-Experimenters almost uniformly have varied participants train with an equivalent number of trials from each of their conditions
-
-One of the few studies that has replicated the surprising result of varied outperforming constant, from the constant training condition, did so in the relatively distant domain of verbal manipulation [@goodeSuperiorityVariableRepeated2008].
-All participants trained to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
+However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperfroms the constant group even from the constants group's home turf has not been consistently replicated.
+One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
+This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
+However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+
+Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
+However, despite its appeal this particular contrast is relatively uncommon in the literature.
+It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
+A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
+@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
+@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
+A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
+Of particular relevance to the current work is the early study of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
+constant training on multiple testing locations of graded distance from the training condition.
+Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
+The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
+Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
+As is often the case, the varied group performed worse during the training phase.
+In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
+
+Benefits of varied training have also been observed in many studies outside of the sensorimotor domain.
+@goodeSuperiorityVariableRepeated2008 trained participants to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
 Although subjects in all conditions were exposed to the same 40 unique words (i.e.
@@
 
-Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
-It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979; @mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
-
-Of particular relevant to the current essay is the early work of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
-constant training on multiple testing locations of graded distance from the training condition.
-Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
-The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
-Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
-As is often the case, the varied group performed worse during the training phase.
-In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
-
-## Category learning
-
-In the category learning literature, the constant vs.
-varied comparison is much less suitable.
-Instead, researchers tend to compare a condition with many repetitions of a few items against condition with fewer repetitions of a wider array of exemplars.
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968], where more varied or distorted training examples were often shown to produce superior generalization when categorizing novel exemplars.
-More recently, researchers have also begun to utilize more realistic stimuli in their experiments.
+In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
+typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
+
+Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968].
+A seminal study by @posnerGenesisAbstractIdeas1968 trained participants to categorize artificial dot patterns, manipulating whether learners were trained with low variability examples clustered close to the category prototypes (i.e. low distortion training patterns), or higher-variability patterns spread further away from the prototype (i.e.
+high-distortion patterns).
+Participants that received training on more highly-distorted items showed superior generalization to novel high distortion patterns in the subsequent testing phase.
+It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training rathers, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
+This train-until-criterion procedure led to the high-variability condition participants tending to complete a larger number of training trials before switching to the testing stage.
+More recent work [@huHighvariabilityTrainingDoes2024], also used dot pattern categories, but matched the number of training trials across conditions.
+Under this procedure, higher-variability participants tended to reach lower levels of performance by the end of the training stage.
+The results in the testing phase were the opposite of @posnerGenesisAbstractIdeas1968,  with the low-variability training group showing superior generalization to novel high-distortion patterns (as well as generalization to novel patterns of low or medium distortion levels).
+However, whether this discrepancy is solely a result of the different training procedures is unclear, as the studies also differed in the nature of the prototype patterns used.
+@posnerGenesisAbstractIdeas1968  utilized simpler, recognizable prototypes (e.g., a triangle, the letter M, the letter F), while  @huHighvariabilityTrainingDoes2024 employed random prototype patterns.
+
+Recent studies have also begun utilizing more complex or realistic sitmuli when assessing the influence of variability on category learning.
 @wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
@@
 higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyTestsExemplarmemoryModel2018].
+A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyModelguidedSearchOptimal2019].
 For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
 The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
-Moreover, the pattern of results in this study could be nicely accounted for by an extended version of the Generalized Context Model.
-
-The studies described thus far have studied the benefits of variability by exposing participants to a greater or lesser number of distinct examples during training.
-A distinct sub-literature within the category learning domain has focused much less on benefits derived from varied training, instead emphasizing how increased variability during the learning of a novel category influences how far the category boundary will then be generalized.
-The general approach is to train participants on examples from two categories, with the examples from one of the categories being more dispersed than the other.
-Participants are then tested with novel items located within ambiguous regions of the task space which allow the experimenters to assess whether the difference in variability influences how far participants generalize the category boundaries.
-
+
+A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g.
+the region between the two categories).
+The general approach is to train participants with examples from a high variability category and a low variability category.
+Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
 @cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
@@
 Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
-The authors then used the standard GCM framework to compare a variety of similarity-based models to account for their results.
-Of particular interest are their evaluations of a category response bias parameter, and a similarity scaling parameter.
-A model fit improvement when the response bias parameter is allowed to vary between the high-variability and low-variability trained groups is taken to suggest a simple bias for responding with one of the trained categories over the other.
-Alternatively, an improvement in fit due to a separate similarity scaling parameter may reflect the groups being differentially sensitive to the distances between stimuli.
+The author compared a variety of similarity-based models based around the Generalized Context Model [@nosofskyAttentionSimilarityIdentificationcategorization1986] to account for their results, manipulating whether a response-bias or similarity-scaling parameter was fit separately between variability conditions.
 No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
 The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied particpants, and also for their poor performance in a recognition condition.
-Additional model comparisons suggested that this similarity rescaling applied across the entire stimulus space, rather than to the high variability category in particular.
-
-Variability effects have also been examined in the higher-level domain of how learners acquire novel concepts, and then instantiate (rather than merely recognize) that concept in untrained contexts [@braithwaiteEffectsVariationPrior2015].
-This study trained participants on problems involving the concept of sampling with replacement (SWR).
+This model accounted for both the extended generalization gradients of the varied particpants, and also for their poorer performance in a recognition condition.
+
+Variability has also been examined in the learning of higher-order linguistic categories [@perryLearnLocallyThink2010].
+In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
+All infants were introduced to three novel objects of the same category, with participants in the "tight" condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
+Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
+Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
+By the end of the nine weeks, all of the infants had learned the labels of the training objects.
+In the testing phase, the varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category.
+More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
+The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987; @vanrossumSchmidtSchemaTheory1990], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+
+In an example of a more complex influence of training variation, [@braithwaiteEffectsVariationPrior2015] trained participants on example problems involving the concept of sampling with replacement (SWR).
 Training consisted of examples that were either highly similar in their semantic context (e.g.
@@
 Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
-
-Variability has also been examined within the realm of language learning.
-A particularly impressive study is that of [@perryLearnLocallyThink2010].
-In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
-All infants were introduced to three novel objects of the same category, with participants in the tight condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
-Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
-Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels of the training objects.
-The varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category, a pattern consistent with much of the existing literature.
-More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
-The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
-
-## Complications to the influence of variability
-
-### Sequence Effects
-
-A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another.
-The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
-Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter  [@sheaContextualInterferenceEffects1979].
-In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
-A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training.
-Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random.
-There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
-However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
-
-Prior to the influential @sheaContextualInterferenceEffects1979 study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
-It was later observed [@leeInfluencePracticeSchedule1985] that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
-The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts.
-One such account, the elaborative processing account [@sheaContextEffectsMemory1983], draws on the earlier work [@battigFacilitationInterference1966] and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
-Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training [@sheaContextEffectsMemory1983], and by manipulating whether subjects are able to perform comparisons during training [@wrightContributionElaborativeProcessing1992].
-An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory [@leeLocusContextualInterference].
-Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context.
-A much more recent study [@chuaPracticeVariabilityPromotes2019], replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
-The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
-In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g.
-attending to the target distance), and constant or blocked subjects reported more internal attention (e.g.
-posture or hand position).
-The authors argue that the benefits of varied/random training may be mediated by changes in attentional focus, however the claims made in the paper seem to go far beyond what can be justified by the analyses reported -- e.g.
-the increased external focus could be a simple byproduct of varied training.
-A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.
-
-## Other task and participant effects
-
-Of course, the effects of varied training, and different training sequences, are likely to be far more complex than simply more varied training being better than less, or random training being better than blocked.
-Null effects of both manipulations have been reported [see @magillReviewContextualInterference1990; @vanrossumSchmidtSchemaTheory1990 for reviews], and a variety of moderators have emerged.
-In one of the earlier examples of the complex relationship between study sequence and learning [@delreyEffectsContextualInterference1982], experimenters recruited participants who self-reported either large amounts, or very little experience with athletic actives, and then trained participants on a coincident timing task under with either a single constant training velocity, or with four training velocities under either blocked, or random training sequence conditions - resulting in six experimental conditions: (athlete vs.
-non-athlete) x (constant vs.
-blocked vs.
-random training).
-Athlete participants had superior performance during training, regardless of sequence condition, and training performance was superior for all subjects in the constant group, followed by blocked training in the middle, and then random training resulting in the worst training performance.
-Of greater interest is the pattern of testing results for novel transfer conditions.
-Among the athlete-participants, transfer performance was best for those who received random training, followed by blocked, and then constant training.
+Interactions between prior experience and the influence of varied training have also been observed in sensorimotor learning [@guadagnoliRelationshipContextualInterference1999;  @delreyEffectsContextualInterference1982].
+@delreyEffectsContextualInterference1982 recruited participants who self-reported either extensive, or very little experience with athletic activities, and then trained participants on a coincident timing task under with either a single constant training velocity, with one of several varied training procedures.
+Unsurprisingly, athlete participants had superior performance during training, regardless of  condition, and training performance was superior for all subjects in the constant group.
+Of greater interest is the pattern of testing results from novel transfer conditions.
+Among the athlete-participants, transfer performance was best for those who received variable training.
 Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
-A similar pattern was later observed in a golf-putting training study, wherein participants who had some prior golf experience benefited most from random-sequenced training, and participants with no golf experience benefited most from blocked training  [@guadagnoliRelationshipContextualInterference1999].
-More recently, the same pattern was observed in the concept learning literature [@braithwaiteEffectsVariationPrior2015 expt 1.].
-This study trained participants on a mathematical concept and found that participants who self-reported some prior experience with the concept improved more from pre-test to post-test after training with varied examples, while participants who reported no prior experience showed greater gains following training with highly similar examples.
-
-In addition to the influence of prior experiences described above, ample evidence also suggests that numerous aspects of the experiment may also interact with the influence of variation.
-One important study examined the impact of the amount of training completed in a force production task [@sheaContextualInterferenceContributions1990].
-This study employed a typical blocked vs.
-random training procedure, but with the additional manipulation of separate groups receiving 50, 200, or 400 total training trials.
-For the group that received only 50 training trials retention was best when training had been blocked.
-However, for the conditions that received 200 or 400 training trials the pattern was reversed, with random training resulting in superior retention than blocked training.
-These results were taken to suggest that the benefits of randomization may take time to emerge.
-Another experimental factor shown to interact with training sequence is the complexity of the training task [@albaretDifferentialEffectsTask1998].
-In addition to random or blocked training, participants in this study were assigned to train on a drawing task at one of three different levels of complexity (reproducing from memory shapes composed of two, three or four components).
-On a transfer task 48 hours after the completion of training, only participants trained at the lower levels of task complexity (2 or 3 components) showed superior performance to the blocked condition.
-The authors suggest that the benefits of random sequencing, thought to arise from more elaborate cognitive processing, or the necessity of continually recalling task information from long term into short term memory, are more likely to be obscured as the complexity of the task forces the blocked participants to also engage in such processes.
-
-A final important influence of particular relevance to the practice-sequence literature concerns the exact structure of "random" sequencing.
-Although the term random is commonly used for convenience, experimenters do not typically leave the order of training entirely up to chance.
-Rather, the training sequence is often constrained such that each condition must occur a minimum number of times in each quartile of the training phase, thus resulting in an even distribution the conditions throughout training.
-While the assurance of the conditions being evenly spread throughout training is consistent across studies, other aspects of the sequence structure are a bit more idiosyncratic.
-Some researchers report setting a maximum number of consecutive repetitions, e.g.
-no more than 2 consecutive trials of the same condition [@delreyEffectsContextualInterference1982; @sheaContextualInterferenceEffects1979], or structure the random trials such that the same condition never occurs consecutively [@wulfEffectTypePractice1991].
-Also common is to structure experiments such that random condition really consists of many small blocks, where participants do a few trials of one condition consecutively and then switch to another condition [@willeyLongtermMotorLearning2018; @chuaPracticeVariabilityPromotes2019; @wrisbergVariabilityPracticeHypothesis1987], resulting in many more switches than would arise if training was perfectly blocked.
-The question of whether such differences in the structure of random sequencing are consequential has been addressed experimentally a few times, in all cases consisting of a 1) a no-repeat random condition; 2) a blocked random condition (typically 3 or 4 repeats before a switch); and 3) a standard fully-blocked condition.
-Blocked-random training resulted in better performance than either repeat-random, or fully - blocked training in both a bean-bag throwing [@pigottMotorSchemaStructure1984], and basketball shot training study [@landinComparisonThreePractice1997], and in a replication plus extension of the seminal [@sheaContextualInterferenceEffects1979] study, blocked-random training was equally effective as no-repeat random training, with both random structures leading to better performance than the fully-blocked training condition.
-Consequences on different study schedules have also been repeatedly observed in the category learning literature [@carvalhoSequenceStudyChanges2017; @carvalhoPuttingCategoryLearning2014].
-This line of research has revealed that the effects of blocking vs.
-interleaving can depend on the structure of the category being learned, and also that the different schedules can result in the participants requiring different representations.
-A fruitful line of inquiry in the motor skill learning literature may be to attempt to identify whether structural aspects of the motor task interact with different training sequences in a reliable manner.
-
-Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed).
-Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty [@bjorkNewTheoryDisuse1992; @schmidtNewConceptualizationsPractice1992], or optimal challenge points [@guadagnoliChallengePointFramework2004].
-They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage.
-This observation is then used to justify the idea that the most enduring and generalizable learning occurs by training at an optimal level of training difficulty, with difficulty being some function of the experience of the learner, and the cognitive or visuomotor processing demands of the task.
-It then follows that the factors that tend to make training more difficult (i.e.
-increased variability or randomization), are more likely to be beneficial when the learner has some experience, or when the processing demands of the task are not too extreme (which may only occur after some experience with the task).
-Such frameworks may be helpful heuristics in some cases, but they also seem to be overly flexible such that any null result of some intervention might be accounted for by a suboptimal amount of training trials, or by suggesting the training task was too difficult.
-The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.
+
+### The current work
+
+The overarching purpose of this dissertation is to investigate the effects of training variability on learning and generalization within visuomotor skill learning and function learning.
+Our investigations is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
+
+In Project 1, we investigated the influence of varied practice in a simple visuomotor projectile launching task.
+Experiments 1 and 2 compared the performance of constant and varied training groups to assess potential benefits of variability on transfer to novel testing conditions.
+To account for the observed empirical effects, we introduced the Instance-based Generalization with Adaptive Similarity (IGAS) model.
+IGAS provides a novel computational approach for quantifying the similarity between training experiences and transfer conditions, while also allowing for variability to influence the generalization gradient itself.
+
+Project 2 shifted focus to the domain of function learning by employing a visuomotor extrapolation task.
+Across three experiments, we examined how constant and varied training regimes affected learning, discrimination between stimuli, and the ability to extrapolate to novel regions of the function's input space.
+To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.
+
+{{< pagebreak >}}
 
@@
 ____________________________________________________
-[pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
 
@@
 
+{{< pagebreak >}}
+
 # Project 2
-
-_______________________________________________________________________________
-[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
-
-[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
 

### 2024-04-11 Sections/hold_temp.qmd
finish intro

@@
 However, in this case the varied group did not outperform the constant group.
+
+A consequence of varied training is that the trial to trial sequences will tend to to consist of fewer repeats, and more switches between task condition (i.e.
+throwing locations; category exemplars; target velocitys), or in the case where variability is being manipulated by the dispersion of training items, the trial to trial sequences of varied participants will tend to consist of larger jumps in the stimulus space.
+
+ The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one block before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
+
+  [@sheaContextualInterferenceEffects1979].
+In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
+A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training.
+Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random.
+There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
+However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
+A more recent study [@chuaPracticeVariabilityPromotes2019], found a similar pattern of results in both a varied vs.
+constant training manipulation (expt 1, bean-bag throwing task), and of random training vs.
+blocked training manipulation (expt 2 & 3, bean-bag throwing & golf putting).
+The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
+In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g.
+attending to the target distance), and constant or blocked subjects reported more internal attention (e.g.
+posture or hand position).
+The authors argue that the benefits of varied/random training may thusly be mediated by changes in attentional focus.
+
+### Sequence Effects
+
+A necessary consequence of varied training is that participants will have the experience of switching from one task condition to another.
+The number of switches can vary greatly, with the two extremes being varied participants completing all of their training trials in one before switching to the next condition (blocked sequencing), or if they alternate between conditions on a trial by trial basis (random/intermixed/interleaved sequencing).
+Not long after the initial influx of schema-theory inspired studies testing the benefits of variability hypothesis was shown that the influence of varied training might interact with the type of training sequence chosen by the experimenter  [@sheaContextualInterferenceEffects1979].
+In this seminal study, both groups of training subjects trained with the same number of trials of three separate movement patterns.
+A blocked group that completed all of their trials with one sequence before beginning the next sequence, and a random group that trained with all three movement patterns interspersed throughout the course of training.
+Participants were also randomly assigned to retention testing under either blocked or random sequence conditions, thus resulting in all four training-testing combinations of blocked-blocked; blocked-random; random-blocked; random-random.
+There was some effect of sequence context, such that both groups performed better when the testing sequence matched their training sequence.
+However, the main finding of interest was the advantage of random-training, which resulted in superior testing performance than blocked training regardless of whether the testing stage had a blocked or random sequence, an effect observed both immediately after training, and in a follow up test ten days after the end of training.
+
+Prior to the influential @sheaContextualInterferenceEffects1979 study, studies investigating the benefits of variability hypothesis had utilized both blocked and random training schedules, often without comment or justification.
+It was later observed [@leeInfluencePracticeSchedule1985] that positive evidence for benefits of varied training seemed more likely to occur for studies that utilized random schedules.
+The theoretical basis of such studies was invariably an appeal to Schmidt's schema theory; however schema theory made no clear predictions of an effect of study sequence on retention or generalization, thus prompting the need for alternate accounts.
+One such account, the elaborative processing account [@sheaContextEffectsMemory1983], draws on the earlier work [@battigFacilitationInterference1966] and argues that randomly sequencing conditions during training promotes comparison and contrastive processes between those conditions, which result in a deeper understanding of the training task than could arise via blocked sequencing.
+Supporting evidence for elaborative processing comes in the form of random-sequence trained subjects self-reporting more nuanced mental representations of movement patterns following training [@sheaContextEffectsMemory1983], and by manipulating whether subjects are able to perform comparisons during training [@wrightContributionElaborativeProcessing1992].
+An alternative, though not incompatible account suggests that the benefits of random-sequencing are a result of such sequences forcing the learner to continually reconstruct the relevant motor task in working memory [@leeLocusContextualInterference].
+Blocked training, on the other hand, allows the learner to maintain the same motor task in short term memory without decay for much of the training which facilitates training performance, but hinders ability to retrieve the appropriate motor memory in a later testing context.
+A much more recent study [@chuaPracticeVariabilityPromotes2019], replicates the standard findings of an advantage of varied training over constant training (expt 1, bean-bag throwing task), and of random training over blocked training (expt 2 & 3, bean-bag throwing & golf putting).
+The novelty of this study is that the experimenters queried subjects about their attentional focus throughout the training stage.
+In all three experiments varied or random trained-subjects reported significantly greater external attention (e.g.
+attending to the target distance), and constant or blocked subjects reported more internal attention (e.g.
+posture or hand position).
+The authors argue that the benefits of varied/random training may be mediated by changes in attentional focus, however the claims made in the paper seem to go far beyond what can be justified by the analyses reported -- e.g.
+the increased external focus could be a simple byproduct of varied training.
+A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.
 
@@
 
+(note that the studies described above manipulated the variability of the training examples, rather than the variability of the categories)
+
+ Moreover, this effect was at odds with the predications of the baseline version of the GCM, thus providing some evidence that training variation may at least sometimes induce effects that cannot be entirely accounted for by exemplar-similarity accounts.
+
 ## Schmidt
@@
 One of the primary concerns of the present paper is that many of the studies which purport to explain the benefits of variation via prototypes, schemas, or other abstractions, are often overlooking the potential of instance based similarity accounts.
+
+Numerous researchers have attempted to provide coherent frameworks to account for the full range of influences of training variation and sequencing described above (along with many other effects not discussed).
+Such accounts are generally quite similar, invoking ideas of desirable levels of difficulty [@bjorkNewTheoryDisuse1992; @schmidtNewConceptualizationsPractice1992], or optimal challenge points [@guadagnoliChallengePointFramework2004].
+They tend to start by describing the dissociation between acquisition performance (performance during training) and testing performance (delayed retention and/or transfer), most strikingly observed as varied/random training participants performing worse than their constant/blocked counterparts during the training stage of the study, but then outperforming the constant/blocked comparisons at a later retention or transfer stage.
+This observation is then used to justify the idea that the most enduring and generalizable learning occurs by training at an optimal level of training difficulty, with difficulty being some function of the experience of the learner, and the cognitive or visuomotor processing demands of the task.
+It then follows that the factors that tend to make training more difficult (i.e.
+increased variability or randomization), are more likely to be beneficial when the learner has some experience, or when the processing demands of the task are not too extreme (which may only occur after some experience with the task).
+Such frameworks may be helpful heuristics in some cases, but they also seem to be overly flexible such that any null result of some intervention might be accounted for by a suboptimal amount of training trials, or by suggesting the training task was too difficult.
+The development of computational models that can account for how changes in the parameters of the motor-skill task scale with difficulty, would be a great step forward.
+
+; @wulfPrinciplesDerivedStudy2002
+
+Through this combination of controlled experiments and computational modeling, the present work provides an extensive investigation into if, how, and when variability facilitates transfer
+
+Together, these projects contribute to a deeper understanding of the role of training variability in cognitive development, offering insights that could inform educational and training practices across a variety of domains.
+The findings and methodological approaches detailed in this dissertation not only advance theoretical knowledge but also provide practical implications for designing more effective learning environments.
+
+By taking a multi-pronged approach that combines empirical investigations across multiple experimental paradigms with computational modeling, this dissertation provides a comprehensive examination of the complex and sometimes opposing effects of training variability on learning and generalization.
+The contrasting results obtained from the HTT and HTW tasks underscore the importance of considering task characteristics when designing experiments to assess the influence of training manipulations.
+Furthermore, the computational modeling components of this work offer novel theoretical accounts for both the beneficial and detrimental effects of training variability observed in our experiments.
+Collectively, this dissertation highlights the value of integrating empirical and modeling approaches to uncover the cognitive mechanisms that support learning and generalization across a variety of domains.

### 2024-04-12 Sections/Introduction.qmd
adding more citations to intro

@@
 
-Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021],  trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
 See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
@@
 The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
-Much of this research has been influenced by the work of (@schmidtSchemaTheoryDiscrete1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
 Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
@@
 Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; but see @stewartEffectCategoryVariability2002].
+@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; but see @stewartEffectCategoryVariability2002 and @yangCategoryVariabilityEffect2014].
 The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.

### 2024-04-12 Sections/Introduction.tex
adding more citations to intro

--- 2024-04-04 Sections/full.tex
@@
 % ---------------------------
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
-\usepackage{caption}
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
-\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
-\definecolor{quarto-callout-color}{HTML}{909090}
-\definecolor{quarto-callout-note-color}{HTML}{0758E5}
-\definecolor{quarto-callout-important-color}{HTML}{CC1914}
-\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
-\definecolor{quarto-callout-tip-color}{HTML}{00A047}
-\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
-\definecolor{quarto-callout-color-frame}{HTML}{acacac}
-\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
-\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
-\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
-\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
-\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
-\makeatother
 \makeatletter
@@
 \makeatother
-\makeatletter
-\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
-\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
-\makeatother
 \ifLuaTeX
@@
 \hypersetup{
-  pdftitle={Full Dissertation},
+  pdftitle={Introduction},
   colorlinks=true,
@@
   \fancyhf{}
-  \lhead{\uppercase{ Full Dissertation }}
+  \lhead{\uppercase{ Introduction }}
   \rhead{\thepage}
@@
   \fancyhf{}
-  \lhead{Running head: \uppercase{ Full Dissertation }}
+  \lhead{Running head: \uppercase{ Introduction }}
   \rhead{}
@@
 
-\title{Full Dissertation:}
-
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par #1 \par}{}{}
-}
-\makeatother
-\subtitle{An instance-based model account of the benefits of varied
-practice in visuomotor skill}
+\title{Introduction}
 
@@
 \singlespacing
-\textbf{Full Dissertation:\\An instance-based model account of the
-benefits of varied practice in visuomotor skill}
+\textbf{Introduction}
 \end{center}
@@
 
-\renewcommand*\contentsname{Contents}
-{
-\hypersetup{linkcolor=}
-\setcounter{tocdepth}{3}
-\tableofcontents
-}
 \setstretch{2}
-\section{Variability and
-Generalization}\label{variability-and-generalization}
-
-The factors that influence the generalization of learning are of
-considerable interest to both researchers exploring the human learning
-system and practitioners aiming to enhance the effectiveness of
-educational and training interventions. The present effort will focus
-specifically on the role of variability in the learning input.
-Variability manipulations typically regulate either the number of
-distinct instances presented to learners during training, or the
-dispersion of these instances. Such manipulations have been empirically
-demonstrated to affect subsequent generalization performance. This essay
-will offer an in-depth review of the extant literature on the influence
-of variability, spanning multiple relevant domains.
+\section{Introduction}\label{introduction}
+
+The past century of research on human learning has produced ample
+evidence that although learners can improve at almost any task, such
+improvements are often specific to the trained task, with unreliable or
+even nonexistent transfer or generalization to novel tasks or conditions
+\autocite{barnettWhenWhereWe2002,dettermanCaseProsecutionTransfer1993}.
+Such generalization challenges are of noteworthy practical relevance,
+given that educators, trainers, and rehabilitators typically intend for
+their students to be able to apply what they have learned to new
+situations. It is therefore important to better understand the factors
+that influence generalization, and to develop cognitive models that can
+predict when generalization is likely to occur. Such characteristics
+have included training difficulty, spacing, temporal order, feedback
+schedules, and the primary focus of the current work - the variability
+of training examples.
 
@@
 
-Studies investigating the ``benefits of variability'' hypothesis usually
-assign participants to either a constant or varied group for the
-training stage of the experiment. Then, subjects in both groups complete
-an identical testing stage which often consists items/conditions seen
-during training, and novel items/conditions. If the varied group
-performs better in the testing stage, this is taken for evidence of the
-benefits of variability hypothesis. Even within this relatively
-straightforward between-groups design, researchers must navigate several
-crucial methodological choices, highlighted below:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\item
-  Variables Subject to Variation. In multidimensional tasks, researchers
-  have the option to vary numerous variables. The experimenters must
-  decide the specific dimension(s) across which variation will occur.
-  For instance, in a projectile throwing accuracy task -- researchers
-  might vary the distance from the target, the size of the target, the
-  weight of the projectile. They might also vary a contextual variable
-  not directly relevant to the task, but which will still be encoded by
-  the subject on a trial by trial basis, e.g.~the background color.
-\item
-  Magnitude of Variation, relative to the control condition. The
-  simplest comparison would be to compare a constant group who trains
-  with 1 example/condition, against a varied group that trains from 2
-  examples/conditions. However, it is not uncommon in the literature for
-  the varied condition to train from 3 or 4 conditions. For example,
-  \textcite{catalanoDistantTransferCoincident1984a} train varied
-  subjects from 4 different velocities in their coincident timing task,
-  and \autocite{goodeSuperiorityVariableRepeated2008} have varied
-  subjects' practice with 3 different variants (i.e.~different letter
-  scrambles of the same word) of an anagram for a given word, while
-  their constant participants view the same variant 3 different times.
-  Alternatively, rather than a constant vs.~varied comparison, subjects
-  in all conditions might experience a variety of training items, but
-  with one group experiencing a greater number of unique items
-  \autocite{nosofskyModelguidedSearchOptimal2018}.
-\item
-  Locations within Task-Space. For tasks in which the stimuli or
-  conditions fall within a continuous metric space, the experimenter
-  must decide whether the varied instances are relatively close together
-  (e.g.~throwing a ball from a distance of 4 feet and 5 feet), or far
-  apart (throwing from 4 feet and 20 feet). Spreading the varied
-  training items further apart may be beneficial in terms of providing a
-  more representative sample of the task space to the learner, however
-  large distances may also result in significant differences in
-  difficulty between the training examples, which can be a common
-  confound in variability studies.
-\item
-  Proximity of Testing to Training Conditions. Intuitively, the fairest
-  form of comparison is to include testing conditions that are of an
-  equivalent distance from both the varied and constant groups. However
-  researchers might also attempt to demonstrate the benefits of
-  variation as being sufficiently powerful to outperform constant
-  training, even in cases where the constant group trained from a closer
-  proximity to the testing conditions, or whose training conditions are
-  identical to the testing conditions
-  \autocite{goodeSuperiorityVariableRepeated2008,kerrSpecificVariedPractice1978}.
-\end{enumerate}
-
-\subsection{Variability Literature
-Review}\label{variability-literature-review}
-
-An early and influential work on the influence of variability on
-category learning is that of \textcite{posnerGenesisAbstractIdeas1968}.
-In an ambitious attempt to address the question of how category
-information is represented, the authors trained participants to
-categorize artificial dot patterns, manipulating whether learners were
-exposed to examples clustered close to the category prototypes (e.g.~a
-low variability condition), or spread further away from the prototype
-(the varied-training group). It should be noted that both groups in this
-study were trained with the same number of unique instances and the
-manipulated difference was how spread out the instances were. The
-authors claim based on prior experiments using the same stimuli, that
-the training stimuli for the varied group were at least as far away from
-the testing stimuli as the training stimuli of the less-varied group.
-The authors interpreted their findings as evidence for the extraction of
-an abstraction or schema that is extracted and stored, and then over
-time becomes more likely to be the reference point from which
-generalization occurs, given that specific instances are thought to
-decay at a faster rate than prototypes or schema. The Posner and Keele
-study has been extremely influential and continues to be cited in
-contemporary research as clear evidence that schema abstraction
-underlies the benefits of varied training. It's also referenced as a key
-influence in the development of ``Schema Theory of Motor Learning''
-\autocite{schmidtSchemaTheoryDiscrete1975}, which in turn influenced
-decades of investigations on the potential benefits of varied training
-in motor skill learning. However, the classic Posner \& Keele study
-despite being far more carefully designed than many subsequent studies,
-and despite being a relative rarity in explicitly discussing and
-attempting to control for potential confounds of similarity between
-groups, may nevertheless be emblematic of a common issue in many
-investigations of the effects of varied training on learning. The
-problem with Posner \& Keele's conclusion was demonstrated clearly
-almost 3 decades later \autocite{palmeriCentralTendenciesExtreme2001},
-when researchers conducting a near replication of the original study
-also collected similarity judgements following training and performed
-multidimensional scaling analysis. Rather than being in the middle of
-the training stimuli as was the case in the physical stimuli space, the
-psychological representation of the prototype was shown reside at an
-extreme point, and generalization patterns by participants that would
-have seemed to warrant the learning of a prototype were then easily
-accounted for with only the assumption that the participants encoded
-instances. One of the primary concerns of the present paper is that many
-of the studies which purport to explain the benefits of variation via
-prototypes, schemas, or other abstractions, are often overlooking the
-potential of instance based similarity accounts.
-
-\subsection{Motor skill learning}\label{motor-skill-learning}
-
-Training variation has also been shown to promote transfer in motor
-learning. Much of this research has been influenced by the work of
-\autocite{schmidtSchemaTheoryDiscrete1975}, who proposed a schema-based
+Varied training has been shown to influence learning in wide array of
+different tasks and domains, including categorization
+\autocite{hahnEffectsCategoryDiversity2005,maddoxStimulusRangeDiscontinuity2011,posnerGenesisAbstractIdeas1968,nosofskyModelguidedSearchOptimal2019,morgensternOneshotCategorizationNovel2019,plebanekEffectsFrequencyVariability2021},
+language learning
+\autocite{jonesDensityDistinctivenessEarly2020,perryLearnLocallyThink2010,twomeyAllRightNoises2018,wonnacottInputEffectsAcquisition2012,brekelmansDoesHighVariability2022},
+anagram completion \autocite{goodeSuperiorityVariableRepeated2008},
+trajectory extrapolation
+\autocite{fulvioTaskSpecificResponseStrategy2014}, cognitive control
+tasks
+\autocite{sabahWhenLessMore2019,moshon-cohenStimulusVariabilityImproves2024},
+associative learning
+\autocite{leeEvidentialDiversityIncreases2019,reichmannVariabilityAbstractionEvaluative2023,fanStimulusDiversityIncreases2022,pradaExperiencedCategoryVariability2020},
+visual search
+\autocite{georgeStimulusVariabilityTask2021,gonzalezDiversityTrainingEnhances2011,kelleyLearningAttendEffects2009},
+voice identity learning \autocite{lavanEffectsHighVariability2019}, face
+recognition
+\autocite{honigPerceptualSimilarityModulates2022,burtonIdentityVariationRepresentations2016,menonVariationPhotosSame2015},
+the perception of social group heterogeneity
+\autocite{linvilleExemplarAbstractionModels1993,konovalovaInformationSamplingExplanation2020,parkPerceptionVariabilityCategory1987,gershmanStructureLearningPrinciples2023}
+, simple motor learning
+\autocite{braunMotorTaskVariation2009,kerrSpecificVariedPractice1978,rollerVariablePracticeLenses2001,willeyLimitedGeneralizationVaried2018},
+sports training
+\autocite{greenPracticeVariabilityTransfer1995a,northEffectConsistentVaried2019,breslinConstantVariablePractice2012},
+and complex skill learning
+\autocite{seowTransferEffectsVaried2019,huetEducationAttentionExplanation2011,hacquesVisualControlClimbing2022}.
+See \textcite{czyzVariabilityPracticeInformation2021} or
+\textcite{ravivHowVariabilityShapes2022} for more detailed reviews.
+
+Research on the effects of varied training typically manipulates
+variability in one of two ways. In the first approach, a high
+variability group is exposed to a greater number of unique instances
+during training, while a low variability group receives fewer unique
+instances with more repetitions. Alternatively, both groups may receive
+the same number of unique instances, but the high variability group's
+instances are more widely distributed or spread out in the relevant
+psychological space, while the low variability group's instances are
+clustered more tightly together. Researchers then compare the training
+groups in terms of their performance during the training phase, as well
+as their generalization performance during a testing phase. Researchers
+will usually compare the performance of the two groups during both the
+training phase and a subsequent testing phase. The primary theoretical
+interest is often to assess the influence of training variability on
+generalization to novel testing items or conditions. However, the test
+may also include some or all of the items that were used during the
+training stage, allowing for an assessment of whether the variability
+manipulation influenced the learning of the trained items themselves, or
+to make it easy to measure how much performance degrades as a function
+of how far away testing items are from the training items.
+
+The influence of training variation has received a large amount of
+attention in the domain of sensorimotor skill learning. Much of this
+research has been influenced by the work of
+\textcite{schmidtSchemaTheoryDiscrete1975}, who proposed a schema-based
 account of motor learning as an attempt to address the longstanding
-problem of how novel movements are produced. Schema theory presumes a
-priori that learners possess general motor programs for classes of
-movements, such as an underhand throw. When called up for use, such
-programs must be parameterized, as well as schema rules that determine
-how a motor program is parameterized or scaled for a particular
-movement. Schema theory predicts that varied training results in the
-formation of a more general schema-rule, which can allow for transfer to
-novel movements within a given movement class, such as an underhand
-throw (though it is agnostic to the development of the movement classes
-themselves). Experiments that test this hypothesis are often designed to
+problem of how novel movements are produced. Schema theory presumes that
+learners possess general motor programs for a class of movements
+(e.g.~an underhand throw). When called up for use motor programs are
+parameterized by schema rules which determine how the motor program is
+parameterized or scaled to the particular demands of the current task.
+Schema theory predicts that variable training facilitates the formation
+of more robust schemas, which will result in improved generalization or
+transfer. Experiments that test this hypothesis are often designed to
 compare the transfer performance of a constant-trained group against
@@
 task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to
-throw a projectile at a target, with a constant group that throws from a
+For example, studies using a projectile throwing task might assign
+participants to either constant training that practicing throwing from a
 single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
+Following training, both groups are then tested from novel throwing
+locations
+\autocite{pigottMotorSchemaStructure1984,willeyLimitedGeneralizationVaried2018,pachecoLearningSpecificIndividual2018,wulfEffectTypePractice1991}.
 
@@
 participants. Participants were also blindfolded for testing and did not
-receive trial by trial feedback in this stage. However, at the halfway
-point of the testing stage they were allowed to see the landing location
-of the 4 beanbags they had thrown, and then completed the final 4
-testing throws. In both age groups, participants performed significantly
-better in the varied condition than the constant condition, though the
-effect was larger for the younger, 8-year-old children. Although this
-design does not directly assess the hypothesis of varied training
-producing superior generalization to constant training (since the
-constant group is not tested from a novel position), it nevertheless
-offers a compelling example of the merits of varied practice.
-
-On occasion the Kerr and Booth design may be nested within a larger
-experimental design. One such study that used a movement timing task,
-wherein subjects had to move their hand from a starting location, to a
-target location, attempting to arrive at the target location at specific
-time following the onset of a cue
-\autocite{wrisbergVariabilityPracticeHypothesis1987}. This study
-utilized 4 different constant groups, and 3 varied groups, with one of
-the constant groups training under conditions identical to the testing
-conditions, and which were not trained on by any of the varied groups,
-e.g.~the design of Kerr and Booth. However, in this case the varied
-group did not outperform the constant group. A more recent study
-attempting a slightly more direct replication of the original Kerr \&
-Booth study \autocite{willeyLongtermMotorLearning2018}, having subjects
-throw beanbags at a target, with the varied group training from
-positions (5 and 9 feet) on either side of the constant group (7 feet).
-However, this study diverged from the original in that the participants
-were adults; they faced away from the target and threw the beanbag
-backwards over their bodies; they alternated using their right and left
-hands every 6 trials; and underwent a relatively extreme amount of
-training (20 sessions with 60 practice trials each, spread out over 5-7
-weeks). Like \textcite{wrisbergVariabilityPracticeHypothesis1987}, this
-study did not find a varied advantage from the constant training
-position, though the varied group did perform better at distances novel
-to both groups.
-
-Some support for the Kerr and Booth findings was found with a relatively
-less common experimental task of training participants in hitting a
-projectile at a target with the use of a racket
-\autocite{greenPracticeVariabilityTransfer1995a}. Varied participants
-trained with tennis, squash, badminton, and short-tennis rackets were
-compared against constant subjects trained with only a tennis racket.
-One of the testing conditions had subjects repeat the use of the tennis
-racket, which had been used on all 128 training trials for the constant
-group, and only 32 training trials for the varied group. Nevertheless,
-the varied group outperformed the constant group when using the tennis
-racket at testing, and also performed better in conditions with several
-novel racket lengths. Of course, this finding is less surprising than
-that of Kerr \& Booth, given that varied subjects did have some prior
-exposure to the constant groups condition. This highlights an issue
-rarely discussed in the literature, of how much practice from an
-additional position might be necessary to induce benefits. Experimenters
-almost uniformly have varied participants train with an equivalent
-number of trials from each of their conditions
-
-One of the few studies that has replicated the surprising result of
-varied outperforming constant, from the constant training condition, did
-so in the relatively distant domain of verbal manipulation
-\autocite{goodeSuperiorityVariableRepeated2008}. All participants
-trained to solve anagrams of 40 different words ranging in length from 5
-to 11 letters, with an anagram of each word repeated 3 times throughout
+receive trial by trial feedback in this stage. In both age groups,
+participants performed significantly better in the varied condition than
+the constant condition, though the effect was larger for the younger,
+8-year-old children. This result offers a particularly compelling
+example of the merits of varied practice, given that the varied group
+was able to outperform the constant group even from the home turf
+location where one may have expected the constatn group to have the
+strongest advantage. A similar pattern of results was observed in
+another study wherein varied participants trained with tennis, squash,
+badminton, and short-tennis rackets were compared against constant
+subjects trained with only a tennis racket
+\autocite{greenPracticeVariabilityTransfer1995a}. One of the testing
+conditions had subjects repeat the use of the tennis racket, which had
+been used on all 128 training trials for the constant group, and only 32
+training trials for the varied group. Nevertheless, the varied group
+outperformed the constant group when using the tennis racket at testing,
+and also performed better in conditions with several novel racket
+lengths. However, as is the case with many of the patterns commonly
+observed in the ``benefits of variability'' literature, the pattern
+wherein the varied group outperfroms the constant group even from the
+constants group's home turf has not been consistently replicated. One
+recent study attempted a near replication of the Kerr \& Booth study
+\autocite{willeyLongtermMotorLearning2018}, having subjects throw
+beanbags at a target, with the varied group training from positions (5
+and 9 feet) on either side of the constant group (7 feet). This study
+did not find a varied advantage from the constant training position,
+though the varied group did perform better at distances novel to both
+groups. However, this study diverged from the original in that the
+participants were adults; and the amount of training was much greater
+(20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+
+Pitting varied against constant practice against each other on the home
+turf of the constant group provides a compelling argument for the
+benefits of varied training, as well as an interesting challenge for
+theoretical accounts that posit generalization to occur as some function
+of distance. However, despite its appeal this particular contrast is
+relatively uncommon in the literature. It is unclear whether this may be
+cause for concern over publication bias, or just researchers feeling the
+design is too risky. A far more common design is to have separate
+constant groups that each train exclusively from each of the conditions
+that the varied group encounters
+\autocite{catalanoDistantTransferCoincident1984a,chuaPracticeVariabilityPromotes2019,newellVariabilityPracticeTransfer1976,moxleySchemaVariabilityPractice1979,mccrackenTestSchemaTheory1977},
+or for a single constant group to train from just one of the conditions
+experienced by the varied participants
+\autocite{pigottMotorSchemaStructure1984,rollerVariablePracticeLenses2001,wrisbergTrainingProductionNovel1984,wrisbergDevelopingCoincidentTiming1983}.
+A less common contrast places the constant group training in a region of
+the task space outside of the range of examples experienced by the
+varied group, but distinct from the transfer condition
+\autocite{wrisbergVariabilityPracticeHypothesis1987,wulfVariabilityPracticeImplicit1997}.
+Of particular relevance to the current work is the early study of
+\textcite{catalanoDistantTransferCoincident1984a}, as theirs was one of
+the earliest studies to investigate the influence of varied vs.~constant
+training on multiple testing locations of graded distance from the
+training condition. Participants were trained on coincident timing task,
+in which subjects observe a series of lightbulbs turning on sequentially
+at a consistent rate and attempt to time a button response with the
+onset of the final bulb. The constant groups trained with a single
+velocity of either 5,7,9, or 11 mph, while the varied group trained from
+all 4 of these velocities. Participants were then assigned to one of
+four possible generalization conditions, all of which fell outside of
+the range of the varied training conditions -- 1, 3, 13 or 15 mph. As is
+often the case, the varied group performed worse during the training
+phase. In the testing phase, the general pattern was for all
+participants to perform worse as the testing conditions became further
+away from the training conditions, but since the drop off in performance
+as a function of distance was far less steep for the varied group, the
+authors suggested that varied training induced a decremented
+generalization gradient, such that the varied participants were less
+affected by the change between training and testing conditions.
+
+Benefits of varied training have also been observed in many studies
+outside of the sensorimotor domain.
+\textcite{goodeSuperiorityVariableRepeated2008} trained participants to
+solve anagrams of 40 different words ranging in length from 5 to 11
+letters, with an anagram of each word repeated 3 times throughout
 training, for a total of 120 training trials. Although subjects in all
@@
 
-Pitting varied against constant practice against each other on the home
-turf of the constant group provides a compelling argument for the
-benefits of varied training, as well as an interesting challenge for
-theoretical accounts that posit generalization to occur as some function
-of distance. However, despite its appeal this particular contrast is
-relatively uncommon in the literature. It is unclear whether this may be
-cause for concern over publication bias, or just researchers feeling the
-design is too risky. A far more common design is to have separate
-constant groups that each train exclusively from each of the conditions
-that the varied group encounters
-\autocite{catalanoDistantTransferCoincident1984a,chuaPracticeVariabilityPromotes2019,newellVariabilityPracticeTransfer1976,moxleySchemaVariabilityPractice1979,mccrackenTestSchemaTheory1977},
-or for a single constant group to train from just one of the conditions
-experienced by the varied participants
-\autocite{pigottMotorSchemaStructure1984,rollerVariablePracticeLenses2001,wrisbergTrainingProductionNovel1984,wrisbergDevelopingCoincidentTiming1983}.
-A less common contrast places the constant group training in a region of
-the task space outside of the range of examples experienced by the
-varied group, but distinct from the transfer condition
-\autocite{wrisbergVariabilityPracticeHypothesis1987,wulfVariabilityPracticeImplicit1997}.
-
-Of particular relevant to the current essay is the early work of
-\textcite{catalanoDistantTransferCoincident1984a}, as theirs was one of
-the earliest studies to investigate the influence of varied vs.~constant
-training on multiple testing locations of graded distance from the
-training condition. Participants were trained on coincident timing task,
-in which subjects observe a series of lightbulbs turning on sequentially
-at a consistent rate and attempt to time a button response with the
-onset of the final bulb. The constant groups trained with a single
-velocity of either 5,7,9, or 11 mph, while the varied group trained from
-all 4 of these velocities. Participants were then assigned to one of
-four possible generalization conditions, all of which fell outside of
-the range of the varied training conditions -- 1, 3, 13 or 15 mph. As is
-often the case, the varied group performed worse during the training
-phase. In the testing phase, the general pattern was for all
-participants to perform worse as the testing conditions became further
-away from the training conditions, but since the drop off in performance
-as a function of distance was far less steep for the varied group, the
-authors suggested that varied training induced a decremented
-generalization gradient, such that the varied participants were less
-affected by the change between training and testing conditions.
-
-\subsection{Category learning}\label{category-learning}
-
-In the category learning literature, the constant vs.~varied comparison
-is much less suitable. Instead, researchers tend to compare a condition
-with many repetitions of a few items against condition with fewer
-repetitions of a wider array of exemplars. Much of the earlier work in
-this sub-area trained subjects on artificial categories, such as dot
-patterns
-\autocite{homaCategoryBreadthAbstraction1976,posnerGenesisAbstractIdeas1968},
-where more varied or distorted training examples were often shown to
-produce superior generalization when categorizing novel exemplars. More
-recently, researchers have also begun to utilize more realistic stimuli
-in their experiments.
-\textcite{wahlheimMetacognitiveJudgmentsRepetition2012} conducted one
-such study. In a within-participants design, participants were trained
-on bird categories with either high repetitions of a few exemplars, or
-few repetitions of many exemplars. Across four different experiments,
-which were conducted to address an unrelated question on metacognitive
-judgements, the researchers consistently found that participants
-generalized better to novel species following training with more unique
-exemplars (i.e.~higher variability), while high repetition training
-produced significantly better performance categorizing the specific
-species they had trained on. A variability advantage was also found in
-the relatively complex domain of rock categorization
-\autocite{nosofskyTestsExemplarmemoryModel2018}. For 10 different rock
+In the domain of category learning, the constant vs.~varied comparison
+is much less suitable. Instead, researchers will typically employ
+designs where all training groups encounter numerous stimuli, but one
+group experiences a greater number of unique exemplars
+\autocite{wahlheimMetacognitiveJudgmentsRepetition2012,nosofskyModelguidedSearchOptimal2019,doyleMetacognitiveMonitoringCategory2016,hoschPriorExperienceVariability2023,brunsteinPreparingNoveltyDiverse2011},
+or designs where the number of unique training exemplars is held
+constant, but one group trains with items that are more dispersed, or
+spread out across the category space
+\autocite{posnerGenesisAbstractIdeas1968,homaCategoryBreadthAbstraction1976,huHighvariabilityTrainingDoes2024,bowmanTrainingSetCoherence2020,maddoxStimulusRangeDiscontinuity2011}.
+
+Much of the earlier work in this sub-area trained subjects on artificial
+categories, such as dot patterns
+\autocite{homaCategoryBreadthAbstraction1976,posnerGenesisAbstractIdeas1968}.
+A seminal study by \textcite{posnerGenesisAbstractIdeas1968} trained
+participants to categorize artificial dot patterns, manipulating whether
+learners were trained with low variability examples clustered close to
+the category prototypes (i.e.~low distortion training patterns), or
+higher-variability patterns spread further away from the prototype
+(i.e.~high-distortion patterns). Participants that received training on
+more highly-distorted items showed superior generalization to novel high
+distortion patterns in the subsequent testing phase. It should be noted
+that unlike the sensorimotor studies discussed earlier, the
+\textcite{posnerGenesisAbstractIdeas1968} study did not present
+low-varied and high-varied participants with an equal number of training
+rathers, but instead had participants remain in the training stage of
+the experiment until they reached a criterion level of performance. This
+train-until-criterion procedure led to the high-variability condition
+participants tending to complete a larger number of training trials
+before switching to the testing stage. More recent work
+\autocite{huHighvariabilityTrainingDoes2024}, also used dot pattern
+categories, but matched the number of training trials across conditions.
+Under this procedure, higher-variability participants tended to reach
+lower levels of performance by the end of the training stage. The
+results in the testing phase were the opposite of
+\textcite{posnerGenesisAbstractIdeas1968}, with the low-variability
+training group showing superior generalization to novel high-distortion
+patterns (as well as generalization to novel patterns of low or medium
+distortion levels). However, whether this discrepancy is solely a result
+of the different training procedures is unclear, as the studies also
+differed in the nature of the prototype patterns used.
+\textcite{posnerGenesisAbstractIdeas1968} utilized simpler, recognizable
+prototypes (e.g., a triangle, the letter M, the letter F), while
+\textcite{huHighvariabilityTrainingDoes2024} employed random prototype
+patterns.
+
+Recent studies have also begun utilizing more complex or realistic
+sitmuli when assessing the influence of variability on category
+learning. \textcite{wahlheimMetacognitiveJudgmentsRepetition2012}
+conducted one such study. In a within-participants design, participants
+were trained on bird categories with either high repetitions of a few
+exemplars, or few repetitions of many exemplars. Across four different
+experiments, which were conducted to address an unrelated question on
+metacognitive judgements, the researchers consistently found that
+participants generalized better to novel species following training with
+more unique exemplars (i.e.~higher variability), while high repetition
+training produced significantly better performance categorizing the
+specific species they had trained on. A variability advantage was also
+found in the relatively complex domain of rock categorization
+\autocite{nosofskyModelguidedSearchOptimal2019}. For 10 different rock
 categories, participants were trained with either many repetitions of 3
@@
 trained with 9 unique examples, showed significantly better
-generalization performance than the other conditions. Moreover, the
-pattern of results in this study could be nicely accounted for by an
-extended version of the Generalized Context Model.
-
-The studies described thus far have studied the benefits of variability
-by exposing participants to a greater or lesser number of distinct
-examples during training. A distinct sub-literature within the category
-learning domain has focused much less on benefits derived from varied
-training, instead emphasizing how increased variability during the
-learning of a novel category influences how far the category boundary
-will then be generalized. The general approach is to train participants
-on examples from two categories, with the examples from one of the
-categories being more dispersed than the other. Participants are then
-tested with novel items located within ambiguous regions of the task
-space which allow the experimenters to assess whether the difference in
-variability influences how far participants generalize the category
-boundaries.
-
+generalization performance than the other conditions.
+
+A distinct sub-literature within the category learning domain has
+examined how the variability or dispersion of the categories themselves
+influences generalization to ambiguous regions of the category space
+(e.g.~the region between the two categories). The general approach is to
+train participants with examples from a high variability category and a
+low variability category. Participants are then tested with novel items
+located within ambiguous regions of the category space which allow the
+experimenters to assess whether the difference in category variability
+influenced how far participants generalize the category boundaries.
 \textcite{cohenCategoryVariabilityExemplar2001} trained subjects on two
@@
 much more likely to categorize the novel middle stimulus into a category
-with greater variation. Moreover, this effect was at odds with the
-predications of the baseline version of the GCM, thus providing some
-evidence that training variation may at least sometimes induce effects
-that cannot be entirely accounted for by exemplar-similarity accounts.
+with greater variation.
 
@@
 in numerous investigations
-\autocite{hahnEffectsCategoryDiversity2005,perlmanFurtherAttemptsClarify2012,sakamotoPuttingPsychologyBack2008,hsuEffectsGenerativeDiscriminative2010}.
+\autocites{hahnEffectsCategoryDiversity2005,perlmanFurtherAttemptsClarify2012,sakamotoPuttingPsychologyBack2008,hsuEffectsGenerativeDiscriminative2010}[but
+see][ and
+\textcite{yangCategoryVariabilityEffect2014}]{stewartEffectCategoryVariability2002}.
 The results of \textcite{sakamotoPuttingPsychologyBack2008} are
@@
 The work of \textcite{hahnEffectsCategoryDiversity2005}, is also of
-particular interest to the present discussion. Their experimental design
-was similar to previous studies, but they included a larger set of
-testing items which were used to assess generalization both between the
-two training categories as well as novel items located in the outer
-edges of the training categories. During generalization testing,
-participants were given the option to respond with ``neither'', in
-addition to responses to the two training categories. The ``neither''
-response was included to test how far away in the stimulus space
-participants would continue to categorize novel items as belonging to a
-trained category. Consistent with prior findings, high-variability
-training resulted in an increased probability of categorizing items in
-between the training categories as belong to the high variability
-category. Additionally, participants trained with higher variability
-also extended the category boundary further out into the periphery than
-participants trained with a lower variability category were willing to
-do. The authors then used the standard GCM framework to compare a
-variety of similarity-based models to account for their results. Of
-particular interest are their evaluations of a category response bias
-parameter, and a similarity scaling parameter. A model fit improvement
-when the response bias parameter is allowed to vary between the
-high-variability and low-variability trained groups is taken to suggest
-a simple bias for responding with one of the trained categories over the
-other. Alternatively, an improvement in fit due to a separate similarity
-scaling parameter may reflect the groups being differentially sensitive
-to the distances between stimuli. No improvement in model fit was found
-by allowing the response-bias parameter to differ between groups,
-however the model performance did improvement significantly when the
-similarity scaling parameter was fit separately. The best fitting
-similarity-scaling parameters were such that the high-variability group
-was less sensitive to the distances between stimuli, resulting in
-greater similarity values between their training items and testing
-items. This model accounted for both the extended generalization
-gradients of the varied particpants, and also for their poor performance
-in a recognition condition. Additional model comparisons suggested that
-this similarity rescaling applied across the entire stimulus space,
-rather than to the high variability category in particular.
-
-Variability effects have also been examined in the higher-level domain
-of how learners acquire novel concepts, and then instantiate (rather
-than merely recognize) that concept in untrained contexts
-\autocite{braithwaiteEffectsVariationPrior2015}. This study trained
-participants on problems involving the concept of sampling with
-replacement (SWR). Training consisted of examples that were either
-highly similar in their semantic context (e.g.~all involving people
-selecting objects) or in which the surface features were varied between
-examples (e.g.~people choosing objects AND objects selected in a
-sequence). The experimenters also surveyed how much prior knowledge each
-participant had with SWR. They found that whether variation was
-beneficial depended on the prior knowledge of the participants -- such
-that participants with some prior knowledge benefited from varied
-training, whereas participants with minimal prior knowledge performed
-better after training with similar examples. The authors hypothesized
-that in order to benefit from varied examples, participants must be able
-to detect the structure common to the diverse examples, and that
-participants with prior knowledge are more likely to be sensitive to
-such structure, and thus to benefit from varied training. To test this
-hypothesis more directly, the authors conducted a 2nd experiment,
-wherein they controlled prior knowledge by exposing some subjects to a
-short graphical or verbal pre-training lesson, designed to increase
-sensitivity to the training examples. Consistent with their hypothesis,
-participants exposed to the structural sensitivity pre-training
-benefited more from varied training than the controls participants who
-benefited more from training with similar examples.
-
-Variability has also been examined within the realm of language
-learning. A particularly impressive study is that of
-\autocite{perryLearnLocallyThink2010}. In nine training sessions spread
-out over nine weeks infants were trained on object labels in a
-naturalistic play setting. All infants were introduced to three novel
-objects of the same category, with participants in the tight condition
-being exposed to three similar exemplars of the category, and
-participants in the varied condition being exposed to three dissimilar
-objects of the same category. Importantly, the similarity of the objects
-was carefully controlled for by having a separate group of adult
-subjects provide pairwise similarity judgements of the category objects
-prior to the study onset. Multidimensional scaling was then performed to
-obtain the coordinates of the objects psychological space, and out of
-the 10 objects for each category, the 3 most similar objects were
-selected for the tight group and the three least similar objects for the
-varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels
-of the training objects. The varied group demonstrated superior ability
-to correctly generalize the object labels to untrained exemplars of the
-same category, a pattern consistent with much of the existing
-literature. More interesting was the superior performance of the varied
-group on a higher order generalization task -- such that they were able
-to appropriately generalize the bias they had learned during training
-for attending to the shape of objects to novel solid objects, but not to
-non-solids. The tight training group, on the other hand, tended to
-overgeneralize the shape bias, leading the researchers to suggest that
-the varied training induced a more context-sensitive understanding of
-when to apply their knowledge.
-
-\subsection{Complications to the influence of
-variability}\label{complications-to-the-influence-of-variability}
-
-\subsubsection{Sequence Effects}\label{sequence-effects}
-
-A necessary consequence of varied training is that participants will
-have the experience of switching from one task condition to another. The
-number of switches can vary greatly, with the two extremes being varied
-participants completing all of their training trials in one before
-switching to the next condition (blocked sequencing), or if they
-alternate between conditions on a trial by trial basis
-(random/intermixed/interleaved sequencing). Not long after the initial
-influx of schema-theory inspired studies testing the benefits of
-variability hypothesis was shown that the influence of varied training
-might interact with the type of training sequence chosen by the
-experimenter \autocite{sheaContextualInterferenceEffects1979}. In this
-seminal study, both groups of training subjects trained with the same
-number of trials of three separate movement patterns. A blocked group
-that completed all of their trials with one sequence before beginning
-the next sequence, and a random group that trained with all three
-movement patterns interspersed throughout the course of training.
-Participants were also randomly assigned to retention testing under
-either blocked or random sequence conditions, thus resulting in all four
-training-testing combinations of blocked-blocked; blocked-random;
-random-blocked; random-random. There was some effect of sequence
-context, such that both groups performed better when the testing
-sequence matched their training sequence. However, the main finding of
-interest was the advantage of random-training, which resulted in
-superior testing performance than blocked training regardless of whether
-the testing stage had a blocked or random sequence, an effect observed
-both immediately after training, and in a follow up test ten days after
-the end of training.
-
-Prior to the influential
-\textcite{sheaContextualInterferenceEffects1979} study, studies
-investigating the benefits of variability hypothesis had utilized both
-blocked and random training schedules, often without comment or
-justification. It was later observed
-\autocite{leeInfluencePracticeSchedule1985} that positive evidence for
-benefits of varied training seemed more likely to occur for studies that
-utilized random schedules. The theoretical basis of such studies was
-invariably an appeal to Schmidt's schema theory; however schema theory
-made no clear predictions of an effect of study sequence on retention or
-generalization, thus prompting the need for alternate accounts. One such
-account, the elaborative processing account
-\autocite{sheaContextEffectsMemory1983}, draws on the earlier work
-\autocite{battigFacilitationInterference1966} and argues that randomly
-sequencing conditions during training promotes comparison and
-contrastive processes between those conditions, which result in a deeper
-understanding of the training task than could arise via blocked
-sequencing. Supporting evidence for elaborative processing comes in the
-form of random-sequence trained subjects self-reporting more nuanced
-mental representations of movement patterns following training
-\autocite{sheaContextEffectsMemory1983}, and by manipulating whether
-subjects are able to perform comparisons during training
-\autocite{wrightContributionElaborativeProcessing1992}. An alternative,
-though not incompatible account suggests that the benefits of
-random-sequencing are a result of such sequences forcing the learner to
-continually reconstruct the relevant motor task in working memory
-\autocite{leeLocusContextualInterference}. Blocked training, on the
-other hand, allows the learner to maintain the same motor task in short
-term memory without decay for much of the training which facilitates
-training performance, but hinders ability to retrieve the appropriate
-motor memory in a later testing context. A much more recent study
-\autocite{chuaPracticeVariabilityPromotes2019}, replicates the standard
-findings of an advantage of varied training over constant training (expt
-1, bean-bag throwing task), and of random training over blocked training
-(expt 2 \& 3, bean-bag throwing \& golf putting). The novelty of this
-study is that the experimenters queried subjects about their attentional
-focus throughout the training stage. In all three experiments varied or
-random trained-subjects reported significantly greater external
-attention (e.g.~attending to the target distance), and constant or
-blocked subjects reported more internal attention (e.g.~posture or hand
-position). The authors argue that the benefits of varied/random training
-may be mediated by changes in attentional focus, however the claims made
-in the paper seem to go far beyond what can be justified by the analyses
-reported -- e.g.~the increased external focus could be a simple
-byproduct of varied training. A stronger form of evidence that was not
-provided may have been to use multiple regression analyses to show that
-the testing advantage of the varied/random groups over the
-constant/blocked groups could be accounted for by the differences in
-self-reported attentional focus.
-
-\subsection{Other task and participant
-effects}\label{other-task-and-participant-effects}
-
-Of course, the effects of varied training, and different training
-sequences, are likely to be far more complex than simply more varied
-training being better than less, or random training being better than
-blocked. Null effects of both manipulations have been reported
-\autocites[see][]{magillReviewContextualInterference1990}[ for
-reviews]{vanrossumSchmidtSchemaTheory1990}, and a variety of moderators
-have emerged. In one of the earlier examples of the complex relationship
-between study sequence and learning
-\autocite{delreyEffectsContextualInterference1982}, experimenters
-recruited participants who self-reported either large amounts, or very
-little experience with athletic actives, and then trained participants
-on a coincident timing task under with either a single constant training
-velocity, or with four training velocities under either blocked, or
-random training sequence conditions - resulting in six experimental
-conditions: (athlete vs.~non-athlete) x (constant vs.~blocked vs.~random
-training). Athlete participants had superior performance during
-training, regardless of sequence condition, and training performance was
-superior for all subjects in the constant group, followed by blocked
-training in the middle, and then random training resulting in the worst
-training performance. Of greater interest is the pattern of testing
-results for novel transfer conditions. Among the athlete-participants,
-transfer performance was best for those who received random training,
-followed by blocked, and then constant training. Non-athletes showed the
-opposite pattern, with superior performance for those who had constant
-training. A similar pattern was later observed in a golf-putting
-training study, wherein participants who had some prior golf experience
-benefited most from random-sequenced training, and participants with no
-golf experience benefited most from blocked training
-\autocite{guadagnoliRelationshipContextualInterference1999}. More
-recently, the same pattern was observed in the concept learning
-literature \autocite[ expt 1.]{braithwaiteEffectsVariationPrior2015}.
-This study trained participants on a mathematical concept and found that
-participants who self-reported some prior experience with the concept
-improved more from pre-test to post-test after training with varied
-examples, while participants who reported no prior experience showed
-greater gains following training with highly similar examples.
-
-In addition to the influence of prior experiences described above, ample
-evidence also suggests that numerous aspects of the experiment may also
-interact with the influence of variation. One important study examined
-the impact of the amount of training completed in a force production
-task \autocite{sheaContextualInterferenceContributions1990}. This study
-employed a typical blocked vs.~random training procedure, but with the
-additional manipulation of separate groups receiving 50, 200, or 400
-total training trials. For the group that received only 50 training
-trials retention was best when training had been blocked. However, for
-the conditions that received 200 or 400 training trials the pattern was
-reversed, with random training resulting in superior retention than
-blocked training. These results were taken to suggest that the benefits
-of randomization may take time to emerge. Another experimental factor
-shown to interact with training sequence is the complexity of the
-training task \autocite{albaretDifferentialEffectsTask1998}. In addition
-to random or blocked training, participants in this study were assigned
-to train on a drawing task at one of three different levels of
-complexity (reproducing from memory shapes composed of two, three or
-four components). On a transfer task 48 hours after the completion of
-training, only participants trained at the lower levels of task
-complexity (2 or 3 components) showed superior performance to the
-blocked condition. The authors suggest that the benefits of random
-sequencing, thought to arise from more elaborate cognitive processing,
-or the necessity of continually recalling task information from long
-term into short term memory, are more likely to be obscured as the
-complexity of the task forces the blocked participants to also engage in
-such processes.
-
-A final important influence of particular relevance to the
-practice-sequence literature concerns the exact structure of ``random''
-sequencing. Although the term random is commonly used for convenience,
-experimenters do not typically leave the order of training entirely up
-to chance. Rather, the training sequence is often constrained such that
-each condition must occur a minimum number of times in each quartile of
-the training phase, thus resulting in an even distribution the
-conditions throughout training. While the assurance of the conditions
-being evenly spread throughout training is consistent across studies,
-other aspects of the sequence structure are a bit more idiosyncratic.
-Some researchers report setting a maximum number of consecutive
-repetitions, e.g.~no more than 2 consecutive trials of the same
-condition
-\autocite{delreyEffectsContextualInterference1982,sheaContextualInterferenceEffects1979},
-or structure the random trials such that the same condition never occurs
-consecutively \autocite{wulfEffectTypePractice1991}. Also common is to
-structure experiments such that random condition really consists of many
-small blocks, where participants do a few trials of one condition
-consecutively and then switch to another condition
-\autocite{willeyLongtermMotorLearning2018,chuaPracticeVariabilityPromotes2019,wrisbergVariabilityPracticeHypothesis1987},
-resulting in many more switches than would arise if training was
-perfectly blocked. The question of whether such differences in the
-structure of random sequencing are consequential has been addressed
-experimentally a few times, in all cases consisting of a 1) a no-repeat
-random condition; 2) a blocked random condition (typically 3 or 4
-repeats before a switch); and 3) a standard fully-blocked condition.
-Blocked-random training resulted in better performance than either
-repeat-random, or fully - blocked training in both a bean-bag throwing
-\autocite{pigottMotorSchemaStructure1984}, and basketball shot training
-study \autocite{landinComparisonThreePractice1997}, and in a replication
-plus extension of the seminal
-\autocite{sheaContextualInterferenceEffects1979} study, blocked-random
-training was equally effective as no-repeat random training, with both
-random structures leading to better performance than the fully-blocked
-training condition. Consequences on different study schedules have also
-been repeatedly observed in the category learning literature
-\autocite{carvalhoSequenceStudyChanges2017,carvalhoPuttingCategoryLearning2014}.
-This line of research has revealed that the effects of blocking
-vs.~interleaving can depend on the structure of the category being
-learned, and also that the different schedules can result in the
-participants requiring different representations. A fruitful line of
-inquiry in the motor skill learning literature may be to attempt to
-identify whether structural aspects of the motor task interact with
-different training sequences in a reliable manner.
-
-Numerous researchers have attempted to provide coherent frameworks to
-account for the full range of influences of training variation and
-sequencing described above (along with many other effects not
-discussed). Such accounts are generally quite similar, invoking ideas of
-desirable levels of difficulty
-\autocite{bjorkNewTheoryDisuse1992,schmidtNewConceptualizationsPractice1992},
-or optimal challenge points
-\autocite{guadagnoliChallengePointFramework2004}. They tend to start by
-describing the dissociation between acquisition performance (performance
-during training) and testing performance (delayed retention and/or
-transfer), most strikingly observed as varied/random training
-participants performing worse than their constant/blocked counterparts
-during the training stage of the study, but then outperforming the
-constant/blocked comparisons at a later retention or transfer stage.
-This observation is then used to justify the idea that the most enduring
-and generalizable learning occurs by training at an optimal level of
-training difficulty, with difficulty being some function of the
-experience of the learner, and the cognitive or visuomotor processing
-demands of the task. It then follows that the factors that tend to make
-training more difficult (i.e.~increased variability or randomization),
-are more likely to be beneficial when the learner has some experience,
-or when the processing demands of the task are not too extreme (which
-may only occur after some experience with the task). Such frameworks may
-be helpful heuristics in some cases, but they also seem to be overly
-flexible such that any null result of some intervention might be
-accounted for by a suboptimal amount of training trials, or by
-suggesting the training task was too difficult. The development of
-computational models that can account for how changes in the parameters
-of the motor-skill task scale with difficulty, would be a great step
-forward.
-
-\section{Project 1}\label{project-1}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\href{Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf}{pdf
-of the journal article}\\
-\href{https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299}{Link
-to online version of journal article}
-
-\section{Abstract}\label{abstract}
-
-Exposing learners to variability during training has been demonstrated
-to improve performance in subsequent transfer testing. Such variability
-benefits are often accounted for by assuming that learners are
-developing some general task schema or structure. However much of this
-research has neglected to account for differences in similarity between
-varied and constant training conditions. In a between-groups
-manipulation, we trained participants on a simple projectile launching
-task, with either varied or constant conditions. We replicate previous
-findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to
-account for the benefits of variation, but, if the model is adjusted to
-assume that varied learners are tuned towards a broader generalization
-gradient, then a similarity-based model is sufficient to explain the
-observed benefits of variation. Our results therefore suggest that some
-variability benefits can be accommodated within instance-based models
-without positing the learning of some schemata or structure.
-
-\section{Introduction}\label{introduction}
-
-The past century of research on human learning has produced ample
-evidence that although learners can improve at almost any task, such
-improvements are often specific to the trained task, with unreliable or
-even nonexistent transfer to novel tasks or conditions
-\autocite{barnettWhenWhereWe2002,dettermanCaseProsecutionTransfer1993}.
-Such transfer challenges are of noteworthy practical relevance, given
-that educators, trainers, and rehabilitators typically intend for their
-students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that
-influence transfer, and to develop cognitive models that can predict
-when transfer is likely to occur. The factor of interest to the present
-investigation is variation during training. Our experiments add to the
-longstanding empirical investigation of the controversial relationship
-between training variation, and subsequent transfer. We also offer a
-novel explanation for such results in the form of an instance-based
-model that accounts for the benefits of variation in simple terms of
-psychological similarity. We first review the relevant concepts and
-literature.
-
-\subsection{Similarity and instance-based approaches to transfer of
-learning}\label{similarity-and-instance-based-approaches-to-transfer-of-learning}
-
-Notions of similarity have long played a central role in many prominent
-models of generalization of learning, as well as in the longstanding
-theoretical issue of whether learners abstract an aggregate, summary
-representation, or if they simply store individual instances. Early
-models of learning often assumed that discrete experiences with some
-task or category were not stored individually in memory, but instead
-promoted the formation of a summary representation, often referred to as
-a prototype or schema, and that exposure to novel examples would then
-prompt the retrieval of whichever preexisting prototype was most similar
-\autocite{posnerGenesisAbstractIdeas1968}. Prototype models were later
-challenged by the success of instance-based or exemplar models -- which
-were shown to provide an account of generalization as good or better
-than prototype models, with the advantage of not assuming the explicit
-construction of an internal prototype
-\autocites{estesClassificationCognition1994,hintzmanMINERVASimulationModel1984,medinContextTheoryClassification1978}[
-]{nosofskyAttentionSimilarityIdentificationcategorization1986}.
-Instance-based models assume that learners encode each experience with a
-task as a separate instance/exemplar/trace, and that each encoded trace
-is in turn compared against novel stimuli. As the number of stored
-instances increases, so does the likelihood that some previously stored
-instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks
-if they are sufficiently similar, thus suggesting that the process of
-computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological
-distance between instances or categories, has provided a successful
-account of generalization across numerous tasks and domains. In an
-influential study demonstrating an ordinal similarity effect,
-experimenters employed a numerosity judgment task in which participants
-quickly report the number of dots flashed on a screen. Performance (in
-terms of response times to new patterns) on novel dot configurations
-varied as an inverse function of their similarity to previously trained
-dot configurations \textcite{palmeriExemplarSimilarityDevelopment1997}.
-That is, performance was better on novel configurations moderately
-similar to trained configurations than to configurations with
-low-similarity, and also better on low-similarity configurations than to
-even less similar, unrelated configurations. Instance-based approaches
-have had some success accounting for performance in certain sub-domains
-of motor learning
-\autocite{cohenWhereGraspsAre2004,crumpEpisodicContributionsSequential2010,meighWhatMemoryRepresentation2018,poldrackRelationshipSkillLearning1999,wifallReachingResponseSelection2017}.
-\textcite{crumpEpisodicContributionsSequential2010} trained participants
-to type words on an unfamiliar keyboard, while constraining the letters
-composing the training words to a pre-specified letter set. Following
-training, typing speed was tested on previously experienced words
-composed of previously experienced letters; novel words composed of
-letters from the trained letter set; and novel words composed of letters
-from an untrained letter set. Consistent with an instance-based account,
-transfer performance was graded such that participants were fastest at
-typing the words they had previously trained on, followed by novel words
-composed of letters they had trained on, and slowest performance for new
-words composed of untrained letters.
-
-\subsection{The effect of training variability on
-transfer}\label{the-effect-of-training-variability-on-transfer}
-
-While similarity-based models account for transfer by the degree of
-similarity between previous and new experiences, a largely separate body
-of research has focused on improving transfer by manipulating
-characteristics of the initial training stage. Such characteristics have
-included training difficulty, spacing, temporal order, feedback
-schedules, and the primary focus of the current work -- variability of
-training examples.
-
-Research on the effects of varied training typically compares
-participants trained under constant, or minimal variability conditions
-to those trained from a variety of examples or conditions
-\autocite{czyzVariabilityPracticeInformation2021,soderstromLearningPerformanceIntegrative2015}.
-Varied training has been shown to influence learning in myriad domains
-including categorization of simple stimuli
-\autocite{hahnEffectsCategoryDiversity2005,maddoxStimulusRangeDiscontinuity2011,posnerGenesisAbstractIdeas1968},
-complex categorization \autocite{nosofskyModelguidedSearchOptimal2018},
-language learning
-\autocite{jonesDensityDistinctivenessEarly2020,perryLearnLocallyThink2010,twomeyAllRightNoises2018,wonnacottInputEffectsAcquisition2012},
-anagram completion \autocite{goodeSuperiorityVariableRepeated2008},
-trajectory extrapolation
-\autocite{fulvioTaskSpecificResponseStrategy2014}, task switching
-\autocite{sabahWhenLessMore2019}, associative learning
-\autocite{leeEvidentialDiversityIncreases2019}, visual search
-\autocite{georgeStimulusVariabilityTask2021,gonzalezDiversityTrainingEnhances2011,kelleyLearningAttendEffects2009},
-voice identity learning \autocite{lavanEffectsHighVariability2019},
-simple motor learning
-\autocite{braunMotorTaskVariation2009,kerrSpecificVariedPractice1978,rollerVariablePracticeLenses2001,willeyLimitedGeneralizationVaried2018},
-sports training
-\autocite{greenPracticeVariabilityTransfer1995a,northEffectConsistentVaried2019},
-and training on a complex video game
-\autocite{seowTransferEffectsVaried2019}.
-
-Training variation has received a particularly large amount of attention
-within the domain of visuomotor skill learning. Much of this research
-has been influenced by the work of
-\textcite{schmidtSchemaTheoryDiscrete1975}, who proposed a schema-based
-account of motor learning as an attempt to address the longstanding
-problem of how novel movements are produced. According to Schema Theory,
-learners possess general motor programs for classes of movements
-(e.g.~throwing a ball with an underhand movement), as well as schema
-rules that determine how a motor program is parameterized or scaled for
-a particular movement. Schema theory predicts that varied training
-results in the formation of a more general schema-rule, which can allow
-for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the
-transfer performance of a constant-trained group against that of a
-varied-trained group. Both groups train on the same task, but the varied
-group practices from multiple levels of a task-relevant dimension that
-remains invariant for the constant group. For example, investigators
-might train two groups of participants to throw a projectile at a
-target, with a constant group that throws from a single location, and a
-varied group that throws from multiple locations. Both groups are then
-tested from novel locations. Empirically observed benefits of the
-varied-trained group are then attributed to the variation they received
-during training, a finding observed in numerous studies
-\autocite{catalanoDistantTransferCoincident1984a,chuaPracticeVariabilityPromotes2019,goodwinEffectDifferentQuantities1998,kerrSpecificVariedPractice1978,wulfEffectTypePractice1991},
-and the benefits of this variation are typically thought to be mediated
-by the development of a more general schema for the throwing motion.
+particular interest to the present work. Their experimental design was
+similar to previous studies, but they included a larger set of testing
+items which were used to assess generalization both between the two
+training categories as well as novel items located in the outer edges of
+the training categories. During generalization testing, participants
+were given the option to respond with ``neither'', in addition to
+responses to the two training categories. The ``neither'' response was
+included to test how far away in the stimulus space participants would
+continue to categorize novel items as belonging to a trained category.
+Consistent with prior findings, high-variability training resulted in an
+increased probability of categorizing items in between the training
+categories as belong to the high variability category. Additionally,
+participants trained with higher variability also extended the category
+boundary further out into the periphery than participants trained with a
+lower variability category were willing to do. The author compared a
+variety of similarity-based models based around the Generalized Context
+Model
+\autocite{nosofskyAttentionSimilarityIdentificationcategorization1986}
+to account for their results, manipulating whether a response-bias or
+similarity-scaling parameter was fit separately between variability
+conditions. No improvement in model fit was found by allowing the
+response-bias parameter to differ between groups, however the model
+performance did improvement significantly when the similarity scaling
+parameter was fit separately. The best fitting similarity-scaling
+parameters were such that the high-variability group was less sensitive
+to the distances between stimuli, resulting in greater similarity values
+between their training items and testing items. This model accounted for
+both the extended generalization gradients of the varied particpants,
+and also for their poorer performance in a recognition condition.
+
+Variability has also been examined in the learning of higher-order
+linguistic categories \autocite{perryLearnLocallyThink2010}. In nine
+training sessions spread out over nine weeks infants were trained on
+object labels in a naturalistic play setting. All infants were
+introduced to three novel objects of the same category, with
+participants in the ``tight'' condition being exposed to three similar
+exemplars of the category, and participants in the varied condition
+being exposed to three dissimilar objects of the same category.
+Importantly, the similarity of the objects was carefully controlled for
+by having a separate group of adult subjects provide pairwise similarity
+judgements of the category objects prior to the study onset.
+Multidimensional scaling was then performed to obtain the coordinates of
+the objects psychological space, and out of the 10 objects for each
+category, the 3 most similar objects were selected for the tight group
+and the three least similar objects for the varied group, with the
+leftover four objects being retained for testing. By the end of the nine
+weeks, all of the infants had learned the labels of the training
+objects. In the testing phase, the varied group demonstrated superior
+ability to correctly generalize the object labels to untrained exemplars
+of the same category. More interesting was the superior performance of
+the varied group on a higher order generalization task -- such that they
+were able to appropriately generalize the bias they had learned during
+training for attending to the shape of objects to novel solid objects,
+but not to non-solids. The tight training group, on the other hand,
+tended to overgeneralize the shape bias, leading the researchers to
+suggest that the varied training induced a more context-sensitive
+understanding of when to apply their knowledge.
 
@@
 effects of training variation
-\autocite{deloshExtrapolationSineQua1997,sinkeviciuteRoleInputVariability2019,wrisbergVariabilityPracticeHypothesis1987},
+\autocite{deloshExtrapolationSineQua1997,sinkeviciuteRoleInputVariability2019,wrisbergVariabilityPracticeHypothesis1987,vanrossumSchmidtSchemaTheory1990},
 and many more have suggested that the benefits of variability may depend
@@
 
-\subsection{Issues with Previous
-Research}\label{issues-with-previous-research}
-
-Although the benefits of training variation in visuomotor skill learning
-have been observed many times, null findings have also been repeatedly
-found, leading some researchers to question the veracity of the
-variability of practice hypothesis
-\autocite{newellSchemaTheory19752003,vanrossumSchmidtSchemaTheory1990}.
-Critics have also pointed out that investigations of the effects of
-training variability, of the sort described above, often fail to control
-for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of
-freedom (e.g.~projectile throwing tasks where participants control the x
-and y velocity of the projectile), varied groups are likely to
-experience a wider range of the task space over the course of their
-training (e.g.~more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring
-that the training location(s) of the varied and constant groups are an
-equal distance away from the eventual transfer locations, such that
-their training throws are, on average, equally similar to throws that
-would lead to good performance at the transfer locations. However, even
-this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer. Given that psychological
-similarity is typically best described as either a Gaussian or
-exponentially decaying function of psychological distance
-\autocites{ennisMultidimensionalStochasticTheory1988,ghahramaniGeneralizationLocalRemappings1996,loganInstanceTheoryAutomatization1988,nosofskySimilarityScalingCognitive1992,shepardUniversalLawGeneralization1987}[
-]{thoroughmanRapidReshapingHuman2005}, it is plausible that a subset of
-the most similar training instances could have a disproportionate impact
-on generalization to transfer conditions, even if the average distance
-between training and transfer conditions is identical between groups.
-Figure~\ref{fig-toy-model1} demonstrates the consequences of a
-generalization gradient that drops off as a Gaussian function of
-distance from training, as compared to a linear drop-off.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-toy-model1-1.pdf}
-
-}
-
-\caption{\label{fig-toy-model1}Left panel- Generalization predicted from
-a simple model that assumes a linear generalization function. A varied
-group (red vertical lines indicate the 2 training locations) trained
-from positions 400 and 800, and a constant group (blue vertical line),
-trained from position 600. Right panel- if a Gaussian generalization
-function is assumed, then varied training (400, 800) is predicted to
-result in better generalization to positions close to 400 and 800 than
-does constant training at 600. (For interpretation of the references to
-color in this figure legend, the reader is referred to the web version
-of this article.)}
-
-\end{figure}%
-
-In addition to largely overlooking the potential for non-linear
-generalization to confound interpretations of training manipulations,
-the visuomotor skill learning literature also rarely considers
-alternatives to schema representations
-\autocite{chamberlinMemoryRepresentationMotor1992}. Although
-schema-theory remains influential within certain literatures, instance
-or exemplar-based models have accounted for human behavior across myriad
-domains
-\autocite{jamiesonInstanceTheoryDomaingeneral2022,loganInstanceTheoryAttention2002a}.
-As mentioned above, instance based accounts have been shown to perform
-well on a variety of different tasks with motoric components
-\autocite{crumpEpisodicContributionsSequential2010,gandolfoMotorLearningField1996a,meighWhatMemoryRepresentation2018,rosenbaumPlanningReachesEvaluating1995,vandamMappingShapeVisuomotor2015}.
-However, such accounts have received little attention within the
-subdomain of visuomotor skill learning focused on the benefits of varied
-training.
-
-The present work examines whether the commonly observed benefits of
-varied training can be accounted for by between-group differences in
-similarity between training and testing throws. We first attempt to
-replicate previous work finding an advantage of varied training over
-constant training in a projectile launching task. We then examine the
-extent to which this advantage can be explained by an instance-based
-similarity model.
-
-\section{Experiment 1}\label{experiment-1}
-
-\subsection{Methods}\label{methods}
-
-\subsubsection{Sample Size Estimation}\label{sample-size-estimation}
-
-To obtain an independent estimate of effect size, we identified previous
-investigations which included between-subjects contrasts of varied and
-constant conditions following training on an accuracy based projectile
-launching task
-\autocite{chuaPracticeVariabilityPromotes2019,goodwinEffectDifferentQuantities1998,kerrSpecificVariedPractice1978,wulfEffectTypePractice1991}.
-We then averaged effects across these studies, yielding a Cohens f =.43.
-The GPower 3.1 software package
-\autocite{faulStatisticalPowerAnalyses2009}, 2009) was then used to
-determine that a power of 80\% requires a sample size of at least 23
-participants per condition. All experiments reported in the present
-manuscript exceed this minimum number of participants per condition.
-
-\subsubsection{Participants}\label{participants}
-
-Participants were recruited from an undergraduate population that is
-63\% female and consists almost entirely of individuals aged 18-22
-years. A total of 110 Indiana University psychology students
-participated in Experiment 1. We subsequently excluded 34 participants
-poor performance at one of the dependent measures of the task (2.5-3
-standard deviations worse than the median subject at the task) or for
-displaying a pattern of responses that was clearly indicative of a lack
-of engagement with the task (e.g.~simply dropping the ball on each trial
-rather than throwing it at the target), or for reporting that they
-completed the experiment on a phone or tablet device, despite the
-instructions not to use one of these devices. A total of 74 participants
-were retained for the final analyses, 35 in the varied group and 39 in
-the constant group.
-
-\subsubsection{Task}\label{task}
-
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. Figure~\ref{fig-IGAS_Methods} displays the layout of
-the task, as it would appear to a participant at the start of a trial,
-with the ball appearing in the center of the orange square. Using a
-mouse or trackpad, participants click down on the ball to take control
-of the ball, connecting the movement of the ball to the movement of the
-cursor. Participants can then ``wind up'' the ball by dragging it
-(within the confines of the orange square) and then launch the ball by
-releasing the cursor. If the ball does not land on the target,
-participants are presented with feedback in red text at the top right of
-the screen, on how many units away they were from the center of the
-target. If the ball was thrown outside of the boundary of the screen
-participants are given feedback as to how far away from the target
-center the ball would have been if it had continued its trajectory. If
-the ball strikes the barrier (from the side or by landing on top),
-feedback is presented telling participants to avoid hitting the barrier.
-If participants drag the ball outside of the orange square before
-releasing it, the trial terminates, and they are reminded to release the
-ball within the orange square. If the ball lands on the target, feedback
-is presented in green text, confirming that the target was hit, and
-presenting additional feedback on how many units away the ball was from
-the exact center of the target.
-
-\href{https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html}{Link to
-abbrevaited example of task}.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-IGAS_Methods-1.pdf}
-
-}
-
-\caption{\label{fig-IGAS_Methods}The stimuli of the task consisted of a
-blue ball, which the participants would launch at the green target,
-while avoiding the red barrier. On each trial, the ball would appear in
-the center of the orange square, with the position of the orange square
-varying between experimental conditions. Participants were constrained
-to release the ball within the square}
-
-\end{figure}%
-
-\subsection{Results}\label{results}
-
-\subsection{Data Processing and Statistical
-Packages}\label{data-processing-and-statistical-packages}
-
-To prepare the data, we first removed trials that were not easily
-interpretable as performance indicators in our task. Removed trials
-included: 1) those in which participants dragged the ball outside of the
-orange starting box without releasing it, 2) trials in which
-participants clicked on the ball, and then immediately released it,
-causing the ball to drop straight down, 3) outlier trials in which the
-ball was thrown more than 2.5 standard deviations further than the
-average throw (calculated separately for each throwing position), and 4)
-trials in which the ball struck the barrier. The primary measure of
-performance used in all analyses was the absolute distance away from the
-center of the target. The absolute distance was calculated on every
-trial, and then averaged within each subject to yield a single
-performance score, for each position. A consistent pattern across
-training and testing phases in both experiments was for participants to
-perform worse from throwing positions further away from the target -- a
-pattern which we refer to as the difficulty of the positions. However,
-there were no interactions between throwing position and training
-conditions, allowing us to collapse across positions in cases where
-contrasts for specific positions were not of interest. All data
-processing and statistical analyses were performed in R version 4.03 (R
-Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021)****.
-
-\subsection{Training Phase}\label{training-phase}
-
-Figure~\ref{fig-IGAS_Training1} below shows aggregate training
-performance binned into three stages representing the beginning, middle,
-and end of the training phase. Because the two conditions trained from
-target distances that were not equally difficult, it was not possible to
-directly compare performance between conditions in the training phase.
-Our focus for the training data analysis was instead to establish that
-participants did improve their performance over the course of training,
-and to examine whether there was any interaction between training stage
-and condition. Descriptive statistics for the intermittent testing phase
-are provided in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and
-condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\textless.001, \(\eta^{2}_G\) =
-.17, such that performance improved over the course of training There
-was no significant effect of condition F(1,71)=1.42, p=.24,
-\(\eta^{2}_G\) = .02, and no significant interaction between condition
-and training stage, F(2,142)=.10, p=.91, \(\eta^{2}_G\) \textless{} .01.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-IGAS_Training1-1.pdf}
-
-}
-
-\caption{\label{fig-IGAS_Training1}Training performance for varied and
-constant participants binned into three stages. Shorter bars indicate
-better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.}
-
-\end{figure}%
-
-\subsection{Testing Phase}\label{testing-phase}
-
-In Experiment 1, a single constant-trained group was compared against a
-single varied-trained group. At the transfer phase, all participants
-were tested from 3 positions: 1) the positions(s) from their own
-training, 2) the training position(s) of the other group, and 3) a
-position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs.~constant) as a
-between-subject factor and throwing location as a within-subject
-variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\textless.001, η2G = .23. The effect of training condition was
-significant F(1,71)=8.19, p\textless.01, η2G = .07. There was no
-significant interaction between group and position, F(3,213)=1.81,
-p=.15, η2G = .01.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-IGAS_Testing1-1.pdf}
-
-}
-
-\caption{\label{fig-IGAS_Testing1}Testing performance for each of the 4
-testing positions, compared between training conditions. Positions 610
-and 910 were trained on by the varied group, and novel for the constant
-group. Position 760 was trained on by the constant group, and novel for
-the varied group. Position 835 was novel for both groups. Shorter bars
-are indicative of better performance (the ball landing closer to the
-center of the target). Error bars indicate standard error of the mean.}
-
-\end{figure}%
-
-\hfill\break
-\hfill\break
-
-\begin{table}
-
-\caption{\label{tbl-IGAS_Table1}}
-
-\centering{
-
-\captionsetup{labelsep=none}
-
-\begin{tabular}{lll}
-\toprule
-Position & Constant & Varied\\
-\midrule
-610 & 132.48(50.85) & 104.2(38.92)\\
-760 & 207.26(89.19) & 167.12(72.29)\\
-835 & 249.13(105.92) & 197.22(109.71)\\
-910 & 289.36(122.48) & 212.86(113.93)\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{table}%
-
-\subsection{Discussion}\label{discussion}
-
-In Experiment 1, we found that varied training resulted in superior
-testing performance than constant training, from both a position novel
-to both groups, and from the position at which the constant group was
-trained, which was novel to the varied condition. The superiority of
-varied training over constant training even at the constant training
-position is of particular note, given that testing at this position
-should have been highly similar for participants in the constant
-condition. It should also be noted, though, that testing at the constant
-trained position is not exactly identical to training from that
-position, given that the context of testing is different in several ways
-from that of training, such as the testing trials from the different
-positions being intermixed, as well as a simple change in context as a
-function of time. Such contextual differences will be further considered
-in the General Discussion.
-
-In addition to the variation of throwing position during training, the
-participants in the varied condition of Experiment 1 also received
-training practice from the closest/easiest position, as well as from the
-furthest/most difficult position that would later be encountered by all
-participants during testing. The varied condition also had the potential
-advantage of interpolating both of the novel positions from which they
-would later be tested. Experiment 2 thus sought to address these issues
-by comparing a varied condition to multiple constant conditions.
-
-\section{Experiment 2}\label{experiment-2}
-
-In Experiment 2, we sought to replicate our findings from Experiment 1
-with a new sample of participants, while also addressing the possibility
-of the pattern of results in Experiment 1 being explained by some
-idiosyncrasy of the particular training location of the constant group
-relative to the varied group. To this end, Experiment 2 employed the
-same basic procedure as Experiment 1, but was designed with six separate
-constant groups each trained from one of six different locations (400,
-500, 625, 675, 800, or 900), and a varied group trained from two
-locations (500 and 800). Participants in all seven groups were then
-tested from each of the 6 unique positions.
-
-\subsection{Methods}\label{methods-1}
-
-\subsubsection{Participants}\label{participants-1}
-
-A total of 306 Indiana University psychology students participated in
-Experiment 2, which was also conducted online. As was the case in
-experiment 1, the undergraduate population from which we recruited
-participants was 63\% female and primarily composed of 18--22-year-old
-individuals. Using the same procedure as experiment 1, we excluded 98
-participants for exceptionally poor performance at one of the dependent
-measures of the task, or for displaying a pattern of responses
-indicative of a lack of engagement with the task. A total of 208
-participants were included in the final analyses with 31 in the varied
-group and 32, 28, 37, 25, 29, 26 participants in the constant groups
-training from location 400, 500, 625, 675, 800, and 900, respectively.
-All participants were compensated with course credit.
-
-\subsubsection{Task and Procedure}\label{task-and-procedure}
-
-The task of Experiment 2 was identical to that of Experiment 1, in all
-but some minor adjustments to the height of the barrier, and the
-relative distance between the barrier and the target. Additionally, the
-intermittent testing trials featured in experiment 1 were not utilized
-in experiment 2, and all training and testing trials were presented with
-feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas\_expt2\_demo.html).
-
-The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the
-same position for the constant groups and split evenly (70 trials each -
-randomized) for the varied group. In the testing phase, participants
-completed 30 trials from each of the six locations that had been used
-separately across each of the constant groups during training. Each of
-the constant groups thus experience one trained location and five novel
-throwing locations in the testing phase, while the varied group
-experiences 2 previously trained, and 4 novel locations.
-
-\subsection{Results}\label{results-1}
-
-\subsubsection{Data Processing and Statistical
-Packages}\label{data-processing-and-statistical-packages-1}
-
-After confirming that condition and throwing position did not have any
-significant interactions, we standardized performance within each
-position, and then average across position to yield a single performance
-measure per participant. This standardization did not influence our
-pattern of results. As in experiment 1, we performed type III ANOVA's
-due to our unbalanced design, however the pattern of results presented
-below is not altered if type 1 or type III tests are used instead. The
-statistical software for the primary analyses was the same as for
-experiment 1. Individual learning rates in the testing phase, compared
-between groups in the supplementary analyses, were fit using the TEfit
-package in R \autocite{cochraneTEfitsNonlinearRegression2020}.
-
-\subsubsection{Training Phase}\label{training-phase-1}
-
-The different training conditions trained from positions that were not
-equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is
-confirmation that some learning did occur. \textbf{?@fig-e2train}
-depicts the training performance of the varied group alongside that of
-the aggregate of the six constant groups (5a), and each of the 6
-separate constant groups (5b). An ANOVA comparison with training stage
-(beginning, middle, end) as a within-group factor and group (the varied
-condition vs.~the 6 constant conditions collapsed together) as a
-between-subject factor revealed no significant effect of group on
-training performance, F(1,206)=.55,p=.49, \(\eta^{2}_G\) \textless.01, a
-significant effect of training stage F(2,412)=77.91, p\textless.001,
-\(\eta^{2}_G\) =.05, and no significant interaction between group and
-training stage, F(2,412)=.489 p=.61, \(\eta^{2}_G\) \textless.01. We
-also tested for a difference in training performance between the varied
-group and the two constant groups that trained matching throwing
-positions (i.e., the constant groups training from position 500, and
-position 800). The results of our ANOVA on this limited dataset mirrors
-that of the full-group analysis, with no significant effect of group
-F(1,86)=.48, p=.49, \(\eta^{2}_G\) \textless.01, a significant effect of
-training stage F(2,172)=56.29, p\textless.001, \(\eta^{2}_G\) =.11, and
-no significant interaction between group and training stage,
-F(2,172)=.341 p=.71, \(\eta^{2}_G\) \textless.01.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2train-1.pdf}
-
-}
-
-\caption{\label{fig-e2train-1}Training performance for the six constant
-conditions, and the varied condition, binned into three stages. On the
-left side, the six constant groups are averaged together, as are the two
-training positions for the varied group. On the right side, the six
-constant groups are shown separately, with each set of bars representing
-the beginning, middle, and end of training for a single constant group
-that trained from the position indicated on the x-axis. Figure 5b also
-shows training performance separately for both of the throwing locations
-trained by the varied group. Error bars indicate standard error of the
-mean.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2train-2.pdf}
-
-}
-
-\caption{\label{fig-e2train-2}Training performance for the six constant
-conditions, and the varied condition, binned into three stages. On the
-left side, the six constant groups are averaged together, as are the two
-training positions for the varied group. On the right side, the six
-constant groups are shown separately, with each set of bars representing
-the beginning, middle, and end of training for a single constant group
-that trained from the position indicated on the x-axis. Figure 5b also
-shows training performance separately for both of the throwing locations
-trained by the varied group. Error bars indicate standard error of the
-mean.}
-
-\end{figure}%
-
-\subsubsection{Testing Phase}\label{testing-phase-1}
-
-In Experiment 2, a single varied condition (trained from two positions,
-500 and 800), was compared against six separate constant groups (trained
-from a single position, 400, 500, 625, 675, 800 or 900). For the testing
-phase, all participants were tested from all six positions, four of
-which were novel for the varied condition, and five of which were novel
-for each of the constant groups. For a general comparison, we took the
-absolute deviations for each throwing position and computed standardized
-scores across all participants, and then averaged across throwing
-position. The six constant groups were then collapsed together allowing
-us to make a simple comparison between training conditions (constant vs.
-varied). A type III between-subjects ANOVA was performed, yielding a
-significant effect of condition F(1,206)=4.33, p=.039, \(\eta^{2}_G\)
-=.02. Descriptive statistics for each condition are shown in table 2. In
-Figure~\ref{fig-e2testa} visualizes the consistent advantage of the
-varied condition over the constant groups across the testing positions.
-Figure~\ref{fig-e2testa} shows performance between the varied condition
-and the individual constant groups.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2testa-1.pdf}
-
-}
-
-\caption{\label{fig-e2testa}Testing phase performance from each of the
-six testing positions. The six constant conditions are averaged together
-into a single constant group, compared against the single varied-trained
-group.B) Transfer performance from each of the 6 throwing locations from
-which all participants were tested. Each bar represents performance from
-one of seven distinct training groups (six constant groups in red, one
-varied group in blue). The x axis labels indicate the location(s) from
-which each group trained. Lower values along the y axis reflect better
-performance at the task (closer distance to target center). Error bars
-indicate standard error of the mean.}
-
-\end{figure}%
-
-\hfill\break
-\hfill\break
-\hfill\break
-
-\begin{table}
-
-\caption{\label{tbl-e2table1}Transfer performance from each of the 6
-throwing locations from which all participants were tested. Each bar
-represents performance from one of seven distinct training groups (six
-constant groups in red, one varied group in blue). The x axis labels
-indicate the location(s) from which each group trained. Lower values
-along the y axis reflect better performance at the task (closer distance
-to target center). Error bars indicate standard error of the mean.}
-
-\centering{
-
-\begin{tabular}{lll}
-\toprule
-Position & Constant & Varied\\
-\midrule
-400 & 100.59(46.3) & 83.92(33.76)\\
-500 & 152.28(69.82) & 134.38(61.38)\\
-625 & 211.21(90.95) & 183.51(75.92)\\
-675 & 233.32(93.35) & 206.32(94.64)\\
-800 & 283.24(102.85) & 242.65(89.73)\\
-\addlinespace
-900 & 343.51(114.33) & 289.62(110.07)\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{table}%
-
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs.~varied): F(1,206)=4.30, p=.039, \(\eta^{2}_G\) =
-.02 .
-
-\begin{table}
-
-\caption{\label{tbl-e2table2}Testing performance from novel positions.
-Includes data only from positions that were not encountered during the
-training stage (e.g.~excludes positions 500 and 800 for the varied
-group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target,
-and standard deviations in parenthesis.}
-
-\centering{
-
-\begin{tabular}{lll}
-\toprule
-Position & Constant & Varied\\
-\midrule
-400 & 98.84(45.31) & 83.92(33.76)\\
-500 & 152.12(69.94) & NA\\
-625 & 212.91(92.76) & 183.51(75.92)\\
-675 & 232.9(95.53) & 206.32(94.64)\\
-800 & 285.91(102.81) & NA\\
-\addlinespace
-900 & 346.96(111.35) & 289.62(110.07)\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{table}%
-
-Finally, corresponding to the comparison of position 760 from experiment
-1, we compared the test performance of the varied group against the
-constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis
-omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group).
-Figure~\ref{fig-e2test1} displays the particular subset of comparisons
-utilized for this analysis. Again, we standardized performance within
-each position before performing the analyses on the aggregated data. In
-this case, the effect of condition did not reach statistical
-significance F(1,149)=3.14, p=.079, \(\eta^{2}_G\) = .02. Table 4
-provides descriptive statistics.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2test1-1.pdf}
-
-}
-
-\caption{\label{fig-e2test1}A comparison of throwing location that are
-identical to those trained by the constant participants (e.g.~constant
-participants trained at position 900, tested from position 900), which
-are also novel to the varied-trained participants (thus excluding
-positions 500 and 800). Error bars indicate standard error of the mean.}
-
-\end{figure}%
-
-\hfill\break
-\hfill\break
-
-\begin{table}
-
-\caption{\label{tbl-e2tab3}Testing performance from the locations
-trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the
-varied participants. Table presents Mean absolute deviation from the
-center of the target, and standard deviations in parenthesis.}
-
-\centering{
-
-\begin{tabular}{lll}
-\toprule
-Position & Constant & Varied\\
-\midrule
-400 & 108.85(50.63) & 83.92(33.76)\\
-625 & 204.75(84.66) & 183.51(75.92)\\
-675 & 235.75(81.15) & 206.32(94.64)\\
-900 & 323.5(130.9) & 289.62(110.07)\\
-\bottomrule
-\end{tabular}
-
-}
-
-\end{table}%
-
-\subsection{Discussion}\label{discussion-1}
-
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions
-\autocite{catalanoDistantTransferCoincident1984a,wrisbergVariabilityPracticeHypothesis1987},
-which has been suggested to relate to the subsequent benefits of varied
-training in retention and generalization testing
-\autocite{soderstromLearningPerformanceIntegrative2015}. However our
-finding of no difference in training performance between constant and
-varied groups has been observed in previous work
-\autocite{chuaPracticeVariabilityPromotes2019,moxleySchemaVariabilityPractice1979,pigottMotorSchemaStructure1984}.
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory
-\autocite{catalanoDistantTransferCoincident1984a,chuaPracticeVariabilityPromotes2019,goodwinEffectDifferentQuantities1998,mccrackenTestSchemaTheory1977,moxleySchemaVariabilityPractice1979,newellVariabilityPracticeTransfer1976,pigottMotorSchemaStructure1984,rollerVariablePracticeLenses2001,schmidtSchemaTheoryDiscrete1975,willeyLongtermMotorLearning2018,wrisbergVariabilityPracticeHypothesis1987,wulfEffectTypePractice1991}.
-We also join a much smaller set of research to observe this pattern in a
-computerized task \autocite{seowTransferEffectsVaried2019}. One
-departure from the experiment 1 findings concerns the pattern wherein
-the varied group outperformed the constant group even from the training
-position of the constant group, which was significant in experiment 1,
-but did not reach significance in experiment 2. Although this pattern
-has been observed elsewhere in the literature
-\autocite{goodeSuperiorityVariableRepeated2008,kerrSpecificVariedPractice1978},
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
-
-\section{Computational Model}\label{computational-model}
-
-Controlling for the similarity between training and testing The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant.
-Figure~\ref{fig-taskSpace} visualizes the solution space for each
-location and illustrates how different combinations of x and y velocity
-result in successfully striking the target from different launching
-positions. As illustrated in Figure~\ref{fig-taskSpace}, the solution
-throws represent just a small fraction of the entire space of velocity
-combinations used by participants throughout the experiment.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-taskSpace-1.pdf}
-
-}
-
-\caption{\label{fig-taskSpace}A) A visual representation of the
-combinations of throw parameters (x and y velocities applied to the ball
-at launch), which resulted in target hits during the testing phase. This
-empirical solution space was compiled from all of the participants in
-experiment 2. B) shows the solution space within the context of all of
-the throws made throughout the testing phase of the experiment.}
-
-\end{figure}%
-
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity
-\autocite{loganInstanceTheoryAttention2002a,nosofskySimilarityScalingCognitive1992},
-these distances were multiplied by a sensitivity parameter, c, and then
-exponentiated to yield a similarity value. The parameter c controls the
-rate with which similarity-based generalization drops off as the
-Euclidean distance between two throws in x- and y-velocity space
-increases. If c has a large value, then even a small difference between
-two throws' velocities greatly decreases the extent of generalization
-from one to the other. A small value for c produces broad generalization
-from one throw to another despite relatively large differences in their
-velocities. The similarity values for each training individual throw
-made by a given participant were then summed to yield a final similarity
-score, with a separate score computed for each of the 6 testing
-positions. The final similarity score is construable as index of how
-accurate the throws a participant made during the training phase would
-be for each of the testing positions.
-
-\textbf{Equation 1:} \[ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
-(e^{-c^\cdot d^{p}_{i,j}}) \]
-
-\textbf{Equation 2:}
-\[ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } \]
-
-A simple linear regression revealed that these similarity scores were
-significantly predictive of performance in the transfer stage, t
-=-15.88, p\textless.01, \(r^2\)=.17, such that greater similarity
-between training throws and solution spaces for each of the test
-locations resulted in better performance. We then repeated the group
-comparisons above while including similarity as a covariate in the
-model. Comparing the varied and constant groups in testing performance
-from all testing positions yielded a significant effect of similarity,
-F(1, 205)=85.66, p\textless.001, \(\eta^{2}_G\) =.29, and also a
-significant effect of condition (varied vs.~constant), F(1, 205)=6.03,
-p=.015, \(\eta^{2}_G\) =.03. The group comparison limited to only novel
-locations for the varied group pit against trained location for the
-constant group resulted in a significant effect of similarity,
-F(1,148)=31.12, p\textless.001, \(\eta^{2}_G\) =.18 as well as for
-condition F(1,148)=11.55, p\textless.001, \(\eta^{2}_G\) =.07. For all
-comparisons, the pattern of results was consistent with the initial
-findings from experiment 2, with the varied group still performing
-significantly better than the constant group.
-
-\subsection{Fitting model parameters separately by
-group}\label{fitting-model-parameters-separately-by-group}
-
-To directly control for similarity in Experiment 2, we developed a
-model-based measure of the similarity between training throws and
-testing conditions. This similarity measure was a significant predictor
-of testing performance, e.g., participants whose training throws were
-more similar to throws that resulted in target hits from the testing
-positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level
-benefits of varied training, which remained significant in our linear
-model predicting testing performance after similarity was added to the
-model. However, previous research has suggested that participants may
-differ in their level of generalization as a function of prior
-experience, and that such differences in generalization gradients can be
-captured by fitting the generalization parameter of an instance-based
-model separately to each group
-\autocite{hahnEffectsCategoryDiversity2005,lambertsFlexibleTuningSimilarity1994}.
-Relatedly, the influential Bayesian generalization model developed by
-\textcite{tenenbaumGeneralizationSimilarityBayesian2001a} predicts that
-the breadth of generalization will increase when a rational agent
-encounters a wider variety of examples. Following these leads, we assume
-that in addition to learning the task itself, participants are also
-adjusting how generalizable their experience should be. Varied versus
-constant participants may be expected to learn to generalize their
-experience to different degrees. To accommodate this difference, the
-generalization parameter of the instance-based model (in the present
-case, the c parameter) can be allowed to vary between the two groups to
-reflect the tendency of learners to adaptively tune the extent of their
-generalization. One specific hypothesis is that people adaptively set a
-value of c to fit the variability of their training experience
-\autocite{nosofskyExemplarbasedAccountsMultiplesystem2000,sakamotoTrackingVariabilityLearning2006}.
-If one's training experience is relatively variable, as with the
-variable training condition, then one might infer that future test
-situations will also be variable, in which case a low value of c will
-allow better generalization because generalization will drop off slowly
-with training-to-testing distance. Conversely, if one's training
-experience has little variability, as found in the constant training
-conditions, then one might adopt a high value of c so that
-generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based
-model of similarity fit against a modified model which separately fits
-the generalization parameter, c, to varied and constant participants. To
-perform this parameter fitting, we used the optim function in R, and fit
-the model to find the c value(s) that maximized the correlation between
-similarity and testing performance.
-
-Both models generate distinct similarity values between training and
-testing locations. Much like the analyses in Experiment 2, these
-similarity values are regressed against testing performance in models of
-the form shown below. As was the case previously, testing performance is
-defined as the mean absolute distance from the center of the target
-(with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\textless.01). Of greater interest is
-the difference between linear model 2, in which similarity is computed
-from a single c value fit from all participants (Similarity1c), with
-linear model 4, which fits the c parameter separately between groups
-(Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\textless.01), with the
-varied group still performing significantly better. However, in linear
-model 4 the addition of the Similarity2c predictor results in the effect
-of training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs.~constant training is accounted for by the
-Similarity2c predictor. Next, to further establish a difference between
-the models, we performed nested model comparisons using ANOVA, to see if
-the addition of the training group parameter led to a significant
-improvement in model performance. In the first comparison, ANOVA(Linear
-Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07,
-p\textless.01). However, in the second model comparison, ANOVA (Linear
-model 3, Linear Model 4) found no improvement in model performance with
-the addition of the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the
-adjusted Similarity2c model had more predictive power than those
-generated from the original Similarity1c model. Using the BIC function
-in R, we compared BIC values between linear model 1 (BIC=14604.00) and
-linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
-a modest advantage for predicting performance using a similarity measure
-computed with two c values over similarity computed with a single c
-value. When fit with separate c values, the best fitting c parameters
-for the model consistently optimized such that the c value for the
-varied group (c=.00008) was smaller in magnitude than the c value for
-the constant group(c= .00011). Recall that similarity decreases as a
-Gaussian function of distance (equation 1 above), and a smaller value of
-c will result in a more gradual drop-off in similarity as the distance
-between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which
-assumes equivalent generalization gradients between constant and varied
-trained participants is unable to account for the extent of benefits of
-varied over constant training observed at testing. The evidence for this
-in the comparative model fits is that when a varied/constant dummy-coded
-variable for condition is explicitly added to the model, the variable
-adds a significant contribution to the prediction of test performance,
-with the variable condition yielding better performance than the
-constant conditions. However, if the instance-based generalization model
-is modified to assume that the training groups can differ in the
-steepness of their generalization gradient, by incorporating a separate
-generalization parameter for each group, then the instance-based model
-can account for our experimental results without explicitly taking
-training group into account. Henceforth this model will be referred to
-as the Instance-based Generalization with Adaptive Similarity (IGAS)
-model.
-
-\section{General Discussion}\label{general-discussion}
-
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training
-\autocite{goodeSuperiorityVariableRepeated2008,greenPracticeVariabilityTransfer1995a,kerrSpecificVariedPractice1978}.
-In experiment 1 varied participants performed significantly better on
-this identity comparison. In Experiment 2, the comparison was not
-significant initially, but became significant after controlling for the
-similarity measure that incorporates only a single value for the
-steepness of similarity-based generalization (c). Furthermore, we showed
-that the general pattern of results from Experiment 2 could be
-parsimoniously accommodated by an instance-based similarity model, but
-only with the assumption that constant and varied participants
-generalize their training experience to different degrees. Our results
-thus suggest that the benefits of variation cannot be explained by the
-varied-trained participants simply covering a broader range of the task
-space. Rather, the modeling suggests that varied participants also learn
-to adaptively tune their generalization function such that throwing
-locations generalize more broadly to one another than they do in the
-constant condition. A learning system could end up adopting a higher c
-value in the constant than variable training conditions by monitoring
-the trial-by-trial variability of the training items. The c parameter
-would be adapted downwards when adjacent training items are dissimilar
-to each other and adapted upwards when adjacent training items are the
-same. In this fashion, contextually appropriate c values could be
-empirically learned. This learning procedure would capture the insight
-that if a situation has a high amount variability, then the learner
-should be predisposed toward thinking that subsequent test items will
-also show considerable variability, in which case generalization
-gradients should be broad, as is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in
-\textbf{?@fig-Toy\_Model2} we demonstrate how a simplified version of
-the IGAS model could in principle produce such a pattern. In addition to
-the assumption of differential generalization between varied and
-constant conditions, our simplified model makes explicit an assumption
-that is incorporated into the full IGAS model -- namely that even when
-being tested from a position identical to that which was trained, there
-are always some psychological contextual differences between training
-and testing throws, resulting in a non-zero dissimilarity.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-Toy-Model2-1.pdf}
-
-}
-
-\caption{\label{fig-Toy-Model2}A simple model depicting the necessity of
-both of two separately fit generalization parameters, c, and a positive
-distance between training and testing contexts, in order for an instance
-model to predict a pattern of varied training from stimuli 400 and 800
-outperforming constant training from position 600 at a test position of
-600. For the top left panel, in which the generalization model assumes a
-single c value (-.008) for both varied and constant conditions, and
-identical contexts across training and testing, the equation which
-generates the varied condition is - Amount of Generalization =
-\(e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}\), whereas the constant
-group generalization is generated from \(2\cdot e^{(c\cdot|x-600|)}\).
-For the top right panel, the c constants in the original equations are
-different for the 2 conditions, with \(c=-.002\) for the varied
-condition, and \(c=-.008\) for the constant condition. The bottom two
-panels are generated from identical equations to those immediately
-above, except for the addition of extra distance (100 units) to reflect
-the assumption of some change in context between training and testing
-conditions. Thus, the generalization model for the varied condition in
-the bottom-right panel is of the form - Amount of Generalization =
-\(e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}\) .}
-
-\end{figure}%
-
-As mentioned above, the idea that learners flexibly adjust their
-generalization gradient based on prior experience does have precedent in
-the domains of category learning
-\autocite{ahaConceptLearningFlexible1992,briscoeConceptualComplexityBias2011,hahnEffectsCategoryDiversity2005,lambertsFlexibleTuningSimilarity1994,opdebeeckRepresentationPerceivedShape2008},
-and sensorimotor adaptation
-\autocite{marongelliAdvantageFlexibleNeuronal2013,taylorContextdependentGeneralization2013,thoroughmanRapidReshapingHuman2005}.
-\textcite{lambertsFlexibleTuningSimilarity1994} showed that a simple
-manipulation of background knowledge during a categorization test
-resulted in participants generalizing their training experience more or
-less broadly, and moreover that such a pattern could be captured by
-allowing the generalization parameter of an instance-based similarity
-model to be fit separately between conditions. The flexible
-generalization parameter has also successfully accounted for
-generalization behavior in cases where participants have been trained on
-categories that differ in their relative variability
-\autocite{hahnEffectsCategoryDiversity2005,sakamotoTrackingVariabilityLearning2006}.
-However, to the best of our knowledge, IGAS is the first instance-based
-similarity model that has been put forward to account for the effect of
-varied training in a visuomotor skill task. Although IGAS was inspired
-by work in the domain of category learning, its success in a distinct
-domain may not be surprising in light of the numerous prior observations
-that at least certain aspects of learning and generalization may operate
-under common principles across different tasks and domains
-\autocite{censorCommonMechanismsHuman2012,hillsCentralExecutiveSearch2010,jamiesonInstanceTheoryDomaingeneral2022,lawSharedMechanismsPerceptual2010,roarkComparingPerceptualCategory2021,rosenbaumAcquisitionIntellectualPerceptualMotor2001,vigoLearningDifficultyVisual2018,wallIdentifyingRelationshipsCognitive2021,wuSimilaritiesDifferencesSpatial2020,yangGeneralLearningAbility2020}.
-
-Our modelling approach does differ from category learning
-implementations of instance-based models in several ways. One such
-difference is the nature of the training instances that are assumed to
-be stored. In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define
-a category item (e.g.~size/color/shape). Rather than defining instances
-in terms of what stimuli learners experience, our approach assumes that
-stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw. An advantage of many motor learning
-tasks is the relative ease with which task execution variables can be
-directly measured (e.g.~movement force, velocity, angle, posture) in
-addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of
-course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work
--- though as described in the introduction there is some evidence in
-support of this idea
-\autocite{chamberlinNoteSchemaExemplar1992,crumpEpisodicContributionsSequential2010,hommelEventFilesEvidence1998,meighWhatMemoryRepresentation2018,poldrackRelationshipSkillLearning1999}.
-A particularly noteworthy instance-based model of sensory-motor behavior
-is the Knowledge II model of Rosenbaum and colleagues
-\autocite{cohenWhereGraspsAre2004,rosenbaumPlanningReachesEvaluating1995}.
-Knowledge II explicitly defines instances as postures (joint
-combinations), and is thus far more detailed than IGAS in regards to the
-contents of stored instances. Knowledge II also differs from IGAS in
-that learning is accounted for by both the retrieval of stored postures,
-and the generation of novel postures via the modification of retrieved
-postures. A promising avenue for future research would be to combine the
-adaptive similarity mechanism of IGAS with the novel instance generation
-mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task
-\autocite{catalanoDistantTransferCoincident1984a}. In this task,
-participants observe a series of lamps lighting up consecutively, and
-attempt to time a button press with the onset of the final lamp. The
-design consisted of four separate constant groups, each training from a
-single lighting velocity, and a single varied group training with all
-four of the lighting velocities used by the individual constant groups.
-Participants were then split into four separate testing conditions, each
-of which were tested from a single novel lighting velocity of varying
-distance from the training conditions. The result of primary interest
-was that all participants performed worse as the distance between
-training and testing velocity increased -- a typical generalization
-decrement. However, varied participants showed less of a decrement than
-did constant participants. The authors take this result as evidence that
-varied training results in a less-steep generalization gradient than
-does constant training. Although the experimental conclusions of
-Catalano and Kleiner are similar to our own, our work is novel in that
-we account for our results with a cognitive model, and without assuming
-the formation of a schema. Additionally, the way in which Catalano and
-Kleiner collapse their separate constant groups together may result in
-similarity confounds between varied and constant conditions that leaves
-their study open to methodological criticisms, especially in light of
-related work which demonstrated that the extent to which varied training
-may be beneficial can depend on whether the constant group they are
-compared against trained from similar conditions to those later tested
-\autocite{wrisbergVariabilityPracticeHypothesis1987}. Our study
-alleviates such concerns by explicitly controlling for similarity.
-
-\subsection{Limitations}\label{limitations}
-
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations
-\autocite{nosofskySimilarityScalingCognitive1992,shepardUniversalLawGeneralization1987}.
-Such scaling typically entails having participants rate the similarity
-between individual items and using these similarity judgements to then
-compute the psychological distances between stimuli, which can then be
-fed into a subsequent model. In the present investigation, there was no
-such way to scale the x and y velocity components in terms of the
-psychological similarity, and thus our modelling does rely on the
-assumption that the psychological distances between the different
-throwing positions are proportional to absolute distances in the metric
-space of the task (e.g. the relative distance between positions 400 and
-500 is equivalent to that between 800 and 900). However, an advantage of
-our approach is that we are measuring similarity in terms of how
-participants behave (applying a velocity to the ball), rather than the
-metric features of the task stimuli.
-
-\subsection{Conclusion}\label{conclusion}
-
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
-
-\section{Project 2}\label{project-2}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\href{https://tegorman13.github.io/htw/}{Link to HTW project page}\\
-
-\href{https://tegorman13.github.io/htw/paper.html}{Working Draft of HTW
-Manuscript}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\section{Introduction}\label{introduction-1}
-
-A longstanding issue across both science and instruction has been to
-understand how various aspects of an educational curriculum or training
-program influence learning acquisition and generalization. One such
-aspect, which has received a great deal of research attention, is the
-variability of examples experienced during training
-\autocite{ravivHowVariabilityShapes2022}. The influence of training
-variation has been studied in numerous domains, including category
-learning
-\autocite{cohenCategoryVariabilityExemplar2001,posnerGenesisAbstractIdeas1968},
-visuomotor learning \autocites{schmidtSchemaTheoryDiscrete1975}[
-]{bernikerEffectsTrainingBreadth2014}, language learning
-\autocite{perryLearnLocallyThink2010}, and education
-\autocite{braithwaiteEffectsVariationPrior2015,guoEffectsExampleVariability2014}.
-The pattern of results is complex, with numerous studies finding both
-beneficial
-\autocite{catalanoDistantTransferCoincident1984a,braunMotorTaskVariation2009,rollerVariablePracticeLenses2001},
-as well as null or negative effects
-\autocites{huHighvariabilityTrainingDoes2024,vanrossumSchmidtSchemaTheory1990}[
-]{brekelmansDoesHighVariability2022}. The present study seeks to
-contribute to the large body of existing research by examining the
-influence of variability in visuomotor function learning - a domain in
-which it has been relatively under-studied.
-
-\subsection{Function Learning and
-Extrapolation}\label{function-learning-and-extrapolation}
-
-The study of human function learning investigates how people learn
-relationships between continuous input and output values. Function
-learning is studied both in tasks where individuals are exposed to a
-sequence of input/output pairs
-\autocite{deloshExtrapolationSineQua1997,mcdanielEffectsSpacedMassed2013},
-or situations where observers are presented with a an incomplete
-scatterplot or line graph and make predictions about regions of the plot
-that don't contain data
-\autocite{ciccioneCanHumansPerform2021a,courrieuQuickApproximationBivariate2012,saidExtrapolationAccuracyUnderestimates2021,schulzCommunicatingCompositionalPatterns2020}.
-
-\textcite{carrollFunctionalLearningLearning1963} conducted the earliest
-work on function learning. Input stimuli and output responses were both
-lines of varying length. The correct output response was related to the
-length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels
-during extrapolation testing, with those in the linear condition
-performing the best overall. Carroll argued that these results were best
-explained by a ruled based model wherein learners form an abstract
-representation of the underlying function. Subsequent work by
-\textcite{brehmerHypothesesRelationsScaled1974},testing a wider array of
-functional forms, provided further evidence for superior extrapolation
-in tasks with linear functions. Brehmer argued that individuals start
-out with an assumption of a linear function, but given sufficient error
-will progressively test alternative hypothesis with polynomials of
-greater degree. \textcite{kohFunctionLearningInduction1991} employed a
-visuomotor function learning task, wherein participants were trained on
-examples from an unknown function relating the length of an input line
-to the duration of a response (time between keystrokes). In this domain,
-participants performed best when the relation between line length and
-response duration was determined by a power, as opposed to linear
-function. Koh \& Meyer developed the log-polynomial adaptive-regression
-model to account for their results.
-
-The first significant challenge to the rule-based accounts of function
-learning was put forth by \textcite{deloshExtrapolationSineQua1997} . In
-their task, participants learned to associate stimulus magnitudes with
-response magnitudes that were related via either linear, exponential, or
-quadratic function. Participants approached ceiling performance by the
-end of training in each function condition, and were able to correctly
-respond in interpolation testing trials. All three conditions
-demonstrated some capacity for extrapolation, however participants in
-the linear condition tended to underestimate the true function, while
-exponential and quadratic participants reliably overestimated the true
-function on extrapolation trials. Extrapolation and interpolation
-performance are depicted in Figure~\ref{fig-delosh-extrap}.
-
-The authors evaluated both of the rule-based models introduced in
-earlier research (with some modifications enabling trial-by-trial
-learning). The polynomial hypothesis testing model
-\autocite{carrollFunctionalLearningLearning1963,brehmerHypothesesRelationsScaled1974}
-tended to mimic the true function closely in extrapolation, and thus
-offered a poor account of the human data. The log-polynomial adaptive
-regression model \autocite{kohFunctionLearningInduction1991} was able to
-mimic some of the systematic deviations produced by human subjects, but
-also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models. The
-Associative Learning Model (ALM) and the extrapolation-association model
-(EXAM). ALM is a two layer connectionist model adapted from the ALCOVE
-model in the category learning literature
-\autocite{kruschkeALCOVEExemplarbasedConnectionist1992}. ALM belongs to
-the general class of radial-basis function neural networks, and can be
-considered a similarity-based model in the sense that the nodes in the
-input layer of the network are activated as a function of distance. The
-EXAM model retains the same similarity based activation and associative
-learning mechanisms as ALM, while being augmented with a linear rule
-response mechanism. When presented with novel stimuli, EXAM will
-retrieve the most similar input-output examples encountered during
-training, and from those examples compute a local slope. ALM was able to
-provide a good account of participant training and interpolation data in
-all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation
-underestimation, as well as the quadratic and exponential overestimation
-patterns exhibited by the human participants. Subsequent research
-identified some limitations in EXAM's ability to account for cases where
-human participants learn and extrapolate sinusoidal function
-\textcite{bottNonmonotonicExtrapolationFunction2004} or to scenarios
-where different functions apply to different regions of the input space
-\textcite{kalishPopulationLinearExperts2004}, though EXAM has been shown
-to provide a good account of human learning and extrapolation in tasks
-with bi-linear, V shaped input spaces
-\textcite{mcdanielPredictingTransferPerformance2009}.
-
-\subsubsection{Variability and Function
-Learning}\label{variability-and-function-learning}
-
-The influence of variability on function learning tasks has received
-relatively little attention. The study by
-\textcite{deloshExtrapolationSineQua1997} (described in detail above)
-did include a variability manipulation (referred to as density in their
-paper), wherein participants were trained with either either 8, 20, or
-50 unique input-output pairs, with the total number of training trials
-held constant. They found a minimal influence of variability on training
-performance, and no difference between groups in interpolation or
-extrapolation, with all three variability conditions displaying accurate
-interpolation, and linearly biased extrapolation that was well accounted
-for by the EXAM model.
-
-In the domain of visuomotor learning,
-\textcite{vandamMappingShapeVisuomotor2015} employed a task which
-required participants to learn a linear function between the spikiness
-of shape stimuli and the correct horizontal position to make a rapid
-pointing response. The shapes ranged from very spiky to completely
-circular at the extreme ends of the space. Participants trained with
-intermediate shapes from a lower variation (2 shapes) or higher
-variation (5 shapes) condition, with the 2 items of the lower varied
-condition matching the items used on the extreme ends of the higher
-variation training space. Learning was significantly slower in the
-higher variation group. However, the two conditions did not differ when
-tested with novel shapes, with both groups producing extrapolation
-responses of comparable magnitudes to the most similar training item,
-rather than in accordance with the true linear function. The authors
-accounted for both learning and extrapolation performance with a
-Bayesian learning model. Similar to ALM, the bayesian model assumes that
-generalization occurs as a Gaussian function of the distance between
-stimuli. However unlike ALM, the bayesian learning model utilizes more
-elaborate probabilistic stimulus representations, with a separate Kalman
-Filter for each shape stimulus.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-delosh-extrap-1.pdf}
-
-}
-
-\caption{\label{fig-delosh-extrap}Generalization reproduced patterns
-from DeLosh et al.~(1997) Figure 3. Stimulii that fall within the dashed
-lines are interpolations of the training examples.}
-
-\end{figure}%
-
-\subsection{Overview Of Present Study}\label{overview-of-present-study}
-
-The present study investigates the influence of training variability on
-learning, generalization, and extrapolation in a uni-dimensional
-visuomotor function learning task. To the best of our knowledge, this
-research is the first to employ the classic constant vs.~varied training
-manipulation, commonly used in the literature on the benefits of
-variability, in the context of a uni-dimensional function learning task.
-Across three experiments, we compare constant and varied training
-conditions in terms of learning performance, extrapolation accuracy, and
-the ability to reliably discriminate between stimuli.
-
-To account for the empirical results, we will apply a series of
-computational models, including the Associative Learning Model (ALM) and
-the Extrapolation-Association Model (EXAM). Notably, this study is the
-first to employ approximate Bayesian computation (ABC) to fit these
-models to individual subject data, enabling us to thoroughly investigate
-the full range of posterior predictions of each model, and to examine
-the the ability of these influential models of function learning to
-account for both the group level and individual level data.
-
-\subsection{Methods}\label{methods-2}
-
-\emph{Participants} A total of 156 participants were recruited from the
-Indiana University Introductory Psychology Course. Participants were
-randomly assigned to one of two training conditions: varied training or
-constant training.
-
-\emph{Task.} The ``Hit The Wall'' (HTW) visuomotor extrapolation task
-task was programmed in Javascript, making heavy use of the
-\href{https://phaser.io/}{phaser.io} game library. The HTW task involved
-launching a projectile such that it would strike the ``wall'' at target
-speed indicated at the top of the screen (see
-Figure~\ref{fig-htw-task}). The target velocities were given as a range,
-or band, of acceptable velocity values (e.g.~band 800-1000). During the
-training stage, participants received feedback indicating whether they
-had hit the wall within the target velocity band, or how many units
-their throw was above or below from the target band. Participants were
-instructed that only the x velocity component of the ball was relevant
-to the task. The y velocity, or the location at which the ball struck
-the wall, had no influence on the task feedback.
-
-/
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=0.6\textwidth,height=\textheight]{../Assets/figs/htw_task_fig.png}
-
-}
-
-\caption{\label{fig-htw-task}The Hit the wall task. Participants launch
-the blue ball to hit the red wall at the target velocity band indicated
-at the top of the screen. The ball must be released from within the
-orange square - but the location of release, and the location at which
-the ball strikes the wall are both irrelevant to the task feedback.}
-
-\end{figure}%
-
-\emph{Procedure.} All participants completed the task online.
-Participants were provided with a description of the experiment and
-indicated informed consent. Figure~\ref{fig-design-e1} illustrates the
-general procedure. Participants completed a total of 90 trials during
-the training stage. In the varied training condition, participants
-encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-Participants in the constant training condition trained on only one
-velocity band (800-1000) - the closest band to what would be the novel
-extrapolation bands in the testing stage.
-
-Following the training stage, participants proceeded immediately to the
-testing stage. Participants were tested from all six velocity bands, in
-two separate stages. In the novel extrapolation testing stage,
-participants completed ``no-feedback'' testing from three novel
-extrapolation bands (100-300, 350-550, and 600-800), with each band
-consisting of 15 trials. Participants were also tested from the three
-velocity bands that were trained by the varied condition (800-1000,
-1000-1200, and 1200-1400). In the constant training condition, two of
-these bands were novel, while in the varied training condition, all
-three bands were encountered during training. The order in which
-participants completed the novel-extrapolation and testing-from-3-varied
-bands was counterbalanced across participants. A final training stage
-presented participants with ``feedback'' testing for each of the three
-extrapolation bands (100-300, 350-550, and 600-800).
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=7in,height=2.5in]{full_files/figure-latex/dot-figure-1.png}
-
-}
-
-\caption{\label{fig-design-e1}Experiment 1 Design. Constant and Varied
-participants complete different training conditions.}
-
-\end{figure}%
-
-\subsubsection{Analyses Strategy}\label{analyses-strategy}
-
-All data processing and statistical analyses were performed in R version
-4.32 \textcite{rcoreteamLanguageEnvironmentStatistical2020}. To assess
-differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R
-\textcite{burknerBrmsPackageBayesian2017}, and descriptive stats and
-tables were extracted with the BayestestR package
-\textcite{makowskiBayestestRDescribingEffects2019}. Mixed effects
-regression enables us to take advantage of partial pooling,
-simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to
-directly quantify the uncertainty in our parameter estimates, as well as
-avoiding convergence issues common to the frequentist analogues of our
-mixed models.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with
-the first 2500 discarded as warmup chains. Rhat values were within an
-acceptable range, with values \textless=1.02 (see appendix for
-diagnostic plots). We used uninformative priors for the fixed effects of
-the model (condition and velocity band), and weakly informative Student
-T distributions for for the random effects. For each model, we report 1)
-the mean values of the posterior distribution for the parameters of
-interest, 2) the lower and upper credible intervals (CrI), and the
-probability of direction value (pd).
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2330}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.5728}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.1942}}@{}}
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Group Comparison
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Code
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Data
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-End of Training Accuracy & \texttt{brm(dist\ \textasciitilde{}\ condit)}
-& Final Training Block \\
-Test Accuracy &
-\texttt{brm(dist\ \textasciitilde{}\ condit\ *\ bandType\ +\ (1\textbar{}id)\ +\ (1\textbar{}bandInt)}
-& All Testing trials \\
-Band Discrimination &
-\texttt{brm(vx\ \textasciitilde{}\ condit\ *\ band\ +(1\ +\ bandInt\textbar{}id)}
-& All Testing Trials \\
-\end{longtable}
-
-\hfill\break
-
-In each experiment we compare varied and constant conditions in terms of
-1) accuracy in the final training block; 2) testing accuracy as a
-function of band type (trained vs.~extrapolation bands); 3) extent of
-discrimination between all six testing bands. We quantified accuracy as
-the absolute deviation between the response velocity and the nearest
-boundary of the target band. Thus, when the target band was velocity
-600-800, throws of 400, 650, and 900 would result in deviation values of
-200, 0, and 100, respectively. The degree of discrimination between
-bands was index by fitting a linear model predicting the response
-velocity as a function of the target velocity. Participants who reliably
-discriminated between velocity bands tended to haves slope values
-\textasciitilde1, while participants who made throws irrespective of the
-current target band would have slopes \textasciitilde0.
-
-\subsubsection{Results}\label{results-2}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e1-train-dev-1.pdf}
-
-}
-
-\caption{\label{fig-e1-train-dev}Experiment 1 Training Stage. Deviations
-from target band across training blocks. Lower values represent greater
-accuracy.}
-
-\end{figure}%
-
-\begin{longtable}[]{@{}lrrrr@{}}
-\caption{\textbf{Experiment 1 - End of training performance}. The
-Intercept represents the average of the baseline (constant condition),
-and the conditVaried coefficient reflects the difference between the
-constant and varied groups. A larger positive estimates indicates a
-greater deviation (lower accuracy) for the varied
-group.}\label{tbl-e1-train-dist}\tabularnewline
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 106.34 & 95.46 & 117.25 & 1 \\
-conditVaried & 79.64 & 57.92 & 101.63 & 1 \\
-\end{longtable}
-
-\hfill\break
-
-\emph{Training}. Figure~\ref{fig-e1-train-dev} displays the average
-deviations across training blocks for the varied group, which trained on
-three velocity bands, and the constant group, which trained on one
-velocity band. To compare the training conditions at the end of
-training, we analyzed performance on the 800-1000 velocity band, which
-both groups trained on. The full model results are shown in Table 1. The
-varied group had a significantly greater deviation than the constant
-group in the final training block, (\(\beta\) = 79.64, 95\% CrI
-{[}57.92, 101.63{]}; pd = 100\%).
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3425}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}@{}}
-\caption{\textbf{Experiment 1 testing accuracy}. Main effects of
-condition and band type (training vs.~extrapolation), and the
-interaction between the two factors. Larger coefficients indicate larger
-deviations from the baselines (Condition=constant \& bandType=Trained) -
-and a positive interaction coefficient indicates disproporionate
-deviation for the varied condition on the extrapolation
-bands}\label{tbl-e1-bmm-dist}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 152.55 & 70.63 & 229.85 & 1.0 \\
-conditVaried & 39.00 & -21.10 & 100.81 & 0.9 \\
-bandTypeExtrapolation & 71.51 & 33.24 & 109.60 & 1.0 \\
-conditVaried:bandTypeExtrapolation & 66.46 & 32.76 & 99.36 & 1.0 \\
-\end{longtable}
-
-\emph{Testing.} To compare accuracy between groups in the testing stage,
-we fit a Bayesian mixed effects model predicting deviation from the
-target band as a function of training condition (varied vs.~constant)
-and band type (trained vs.~extrapolation), with random intercepts for
-participants and bands. The model results are shown in
-Table~\ref{tbl-e1-bmm-dist}. The main effect of training condition was
-not significant (\(\beta\) = 39, 95\% CrI {[}-21.1, 100.81{]}; pd =
-89.93\%). The extrapolation testing items had a significantly greater
-deviation than the training bands (\(\beta\) = 71.51, 95\% CrI {[}33.24,
-109.6{]}; pd = 99.99\%). Most importantly, the interaction between
-training condition and band type was significant (\(\beta\) = 66.46,
-95\% CrI {[}32.76, 99.36{]}; pd = 99.99\%), As shown in
-Figure~\ref{fig-e1-test-dev}, the varied group had disproportionately
-larger deviations compared to the constant group in the extrapolation
-bands.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e1-test-dev-1.pdf}
-
-}
-
-\caption{\label{fig-e1-test-dev}A) Deviations from target band during
-testing without feedback stage. B) Conditional effect of condition
-(Constant vs.~Varied) and testing band type (training vs.~extrapolation)
-on testing accuracy. Error bars represent 95\% credible intervals.}
-
-\end{figure}%
-
-\hfill\break
-
-\begin{longtable}[]{@{}lrrrr@{}}
-\caption{Experiment 1. Bayesian Mixed Model Predicting velocity as a
-function of condition (Constant vs.~Varied) and Velocity Band. Larger
-coefficients on Band represent greater
-sensitivity/discrimination.}\label{tbl-e1-bmm-vx}\tabularnewline
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 408.55 & 327.00 & 490.61 & 1.00 \\
-conditVaried & 164.05 & 45.50 & 278.85 & 1.00 \\
-Band & 0.71 & 0.62 & 0.80 & 1.00 \\
-condit*Band & -0.14 & -0.26 & -0.01 & 0.98 \\
-\end{longtable}
-
-Finally, to assess the ability of both conditions to discriminate
-between velocity bands, we fit a model predicting velocity as a function
-of training condition and velocity band, with random intercepts and
-random slopes for each participant. See Table~\ref{tbl-e1-bmm-vx} for
-the full model results. The estimated coefficient for training condition
-(\(\beta\) = 164.05, 95\% CrI {[}45.5, 278.85{]}, pd = 99.61\%) suggests
-that the varied group tends to produce harder throws than the constant
-group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the coefficient on the
-Band predictor (\(\beta\) = 0.71 95\% CrI {[}0.62, 0.8{]}, pd = 100\%).
-Although the median slope does fall underneath the ideal of value of 1,
-the fact that the 95\% credible interval does not contain 0 provides
-strong evidence that participants exhibited some discrimination between
-bands. The estimate for the interaction between slope and condition
-(\(\beta\) = -0.14, 95\% CrI {[}-0.26, -0.01{]}, pd = 98.39\%), suggests
-that the discrimination was somewhat modulated by training condition,
-with the varied participants showing less sensitivity between bands than
-the constant condition. This difference is depicted visually in
-Figure~\ref{fig-e1-test-vx}.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e1-test-vx-1.pdf}
-
-}
-
-\caption{\label{fig-e1-test-vx}Empirical distribution of velocities
-producing in testing stage. Translucent bands with dash lines indicate
-the correct range for each velocity band.}
-
-\end{figure}%
-
-\begin{table}
-
-\caption{\label{tbl-e1-bmm-vx}}
-
-\centering{
-
-\captionsetup{labelsep=none}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{full_files/figure-pdf/tbl-e1-bmm-vx-1.pdf}
-
-}
-
-\subcaption{Experiment 1. Conditional effect of training condition and
-Band. Ribbons indicate 95\% HDI. The steepness of the lines serves as an
-indicator of how well participants discriminated between velocity
-bands.}
-
-\end{figure}%
-
-}
-
-\end{table}%
-
-\subsection{E1 Summary}\label{e1-summary}
-
-In Experiment 1, we investigated how variability in training influenced
-participants' ability learn and extrapolate in a visuomotor task. Our
-findings that training with variable conditions rresulted in lower final
-training performance is consistent with much of the prior researchon the
-influence of training variability
-\autocite{ravivHowVariabilityShapes2022,soderstromLearningPerformanceIntegrative2015},
-and is particularly unsurprising in the present work, given that the
-constant group received three times the amount of training on the
-velocity band common to the two conditions.
-
-More importantly, the varied training group exhibited significantly
-larger deviations from the target velocity bands during the testing
-phase, particularly for the extrapolation bands that were not
-encountered by either condition during training.
-
-\subsection{Experiment 2}\label{experiment-2-1}
-
-\subsubsection{Methods \& Procedure}\label{methods-procedure}
-
-The task and procedure of Experiment 2 was identical to Experiment 1,
-with the exception that the training and testing bands were reversed
-(see Figure~\ref{fig-design-e2}). The Varied group trained on bands
-100-300, 350-550, 600-800, and the constant group trained on band
-600-800. Both groups were tested from all six bands. A total of 110
-participants completed the experiment (Varied: 55, Constant: 55).
-
-\begin{figure}
-
-\centering{
-
-\includegraphics[width=8in,height=2.5in]{full_files/figure-latex/dot-figure-2.png}
-
-}
-
-\caption{\label{fig-design-e2}Experiment 2 Design. Constant and Varied
-participants complete different training conditions. The training and
-testing bands are the reverse of Experiment 1.}
-
-\end{figure}%
-
-\subsubsection{Results}\label{results-3}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2-train-dev-1.pdf}
-
-}
-
-\caption{\label{fig-e2-train-dev}Experiment 2 Training Stage. Deviations
-from target band across training blocks. Lower values represent greater
-accuracy.}
-
-\end{figure}%
-
-\begin{longtable}[]{@{}lrrrr@{}}
-\caption{\textbf{Experiment 2 - End of training performance}. The
-Intercept represents the average of the baseline (constant condition),
-and the conditVaried coefficient reflects the difference between the
-constant and varied groups. A larger positive coefficient indicates a
-greater deviation (lower accuracy) for the varied
-group.}\label{tbl-e2-train-dist}\tabularnewline
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 91.01 & 80.67 & 101.26 & 1 \\
-conditVaried & 36.15 & 16.35 & 55.67 & 1 \\
-\end{longtable}
-
-\hfill\break
-
-\emph{Training}. Figure~\ref{fig-e2-train-dev} presents the deviations
-across training blocks for both constant and varied training groups. We
-again compared training performance on the band common to both groups
-(600-800). The full model results are shown in Table 1. The varied group
-had a significantly greater deviation than the constant group in the
-final training block, ( \(\beta\) = 36.15, 95\% CrI {[}16.35, 55.67{]};
-pd = 99.95\%).
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.4390}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1220}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1829}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1829}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0732}}@{}}
-\caption{\textbf{Experiment 2 testing accuracy}. Main effects of
-condition and band type (training vs.~extrapolation), and the
-interaction between the two factors. Larger coefficient estimates
-indicate larger deviations from the baselines (constant \& trained
-bands) - and a positive interaction coefficient indicates
-disproporionate deviation for the varied condition on the extrapolation
-bands}\label{tbl-e2-bmm-dist}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 190.91 & 125.03 & 259.31 & 1.00 \\
-conditVaried & -20.58 & -72.94 & 33.08 & 0.78 \\
-bandTypeExtrapolation & 38.09 & -6.94 & 83.63 & 0.95 \\
-conditVaried:bandTypeExtrapolation & 82.00 & 41.89 & 121.31 & 1.00 \\
-\end{longtable}
-
-~\\
-
-\emph{Testing Accuracy.} The analysis of testing accuracy examined
-deviations from the target band as influenced by training condition
-(Varied vs.~Constant) and band type (training vs.~extrapolation bands).
-The results, summarized in Table~\ref{tbl-e2-bmm-dist}, reveal no
-significant main effect of training condition (\(\beta\) = -20.58, 95\%
-CrI {[}-72.94, 33.08{]}; pd = 77.81\%). However, the interaction between
-training condition and band type was significant (\(\beta\) = 82, 95\%
-CrI {[}41.89, 121.31{]}; pd = 100\%), with the varied group showing
-disproportionately larger deviations compared to the constant group on
-the extrapolation bands (see Figure~\ref{fig-e2-test-dev}).
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2-test-dev-1.pdf}
-
-}
-
-\caption{\label{fig-e2-test-dev}A) Deviations from target band during
-testing without feedback stage. B) Estimated marginal means for the
-interaction between training condition and band type. Error bars
-represent 95\% confidence intervals.}
-
-\end{figure}%
-
-\begin{longtable}[]{@{}lrrrr@{}}
-\caption{Experiment 2. Bayesian Mixed Model Predicting Vx as a function
-of condition (Constant vs.~Varied) and Velocity
-Band}\label{tbl-e2-bmm-vx}\tabularnewline
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 362.64 & 274.85 & 450.02 & 1.00 \\
-conditVaried & -8.56 & -133.97 & 113.98 & 0.55 \\
-Band & 0.71 & 0.58 & 0.84 & 1.00 \\
-condit*Band & -0.06 & -0.24 & 0.13 & 0.73 \\
-\end{longtable}
-
-\emph{Testing Discrimination.} Finally, to assess the ability of both
-conditions to discriminate between velocity bands, we fit a model
-predicting velocity as a function of training condition and velocity
-band, with random intercepts and random slopes for each participant. The
-full model results are shown in Table~\ref{tbl-e2-bmm-vx}. The overall
-slope on target velocity band predictor was significantly positive,
-(\(\beta\) = 0.71, 95\% CrI {[}0.58, 0.84{]}; pd= 100\%), indicating
-that participants exhibited discrimination between bands. The
-interaction between slope and condition was not significant, (\(\beta\)
-= -0.06, 95\% CrI {[}-0.24, 0.13{]}; pd= 72.67\%), suggesting that the
-two conditions did not differ in their ability to discriminate between
-bands (see Figure~\ref{fig-e2-test-vx}).
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2-test-vx-1.pdf}
-
-}
-
-\caption{\label{fig-e2-test-vx}E2 testing x velocities. Translucent
-bands with dash lines indicate the correct range for each velocity
-band.}
-
-\end{figure}%
-
-\begin{table}
-
-\caption{\label{tbl-e2-bmm-vx}}
-
-\centering{
-
-\captionsetup{labelsep=none}
-
-\begin{figure}[H]
-
-{\centering \includegraphics{full_files/figure-pdf/tbl-e2-bmm-vx-1.pdf}
-
-}
-
-\subcaption{Conditional effect of training condition and Band. Ribbons
-indicate 95\% HDI. The steepness of the lines serves as an indicator of
-how well participants discriminated between velocity bands.}
-
-\end{figure}%
-
-}
-
-\end{table}%
-
-\subsubsection{Experiment 2 Summary}\label{experiment-2-summary}
-
-Experiment 2 extended the findings of Experiment 1 by examining the
-effects of training variability on extrapolation performance in a
-visuomotor function learning task, but with reversed training and
-testing bands. Similar to Experiment 1, the Varied group exhibited
-poorer performance during training and testing. However unlike
-experiment 1, the Varied group did not show a significant difference in
-discrimination between bands.
-
-\subsection{Experiment 3}\label{experiment-3}
-
-\subsubsection{Methods \& Procedure}\label{methods-procedure-1}
-
-The major adjustment of Experiment 3 is for participants to receive
-ordinal feedback during training, in contrast to the continuous feedback
-of the prior experiments. After each training throw, participants are
-informed whether a throw was too soft, too hard, or correct (i.e.~within
-the target velocity range). All other aspects of the task and design are
-identical to Experiments 1 and 2. We utilized the order of training and
-testing bands from both of the prior experiments, thus assigning
-participants to both an order condition (Original or Reverse) and a
-training condition (Constant or Varied). Participants were once again
-recruited from the online Indiana University Introductory Psychology
-Course pool. Following exclusions, 195 participants were included in the
-final analysis, n=51 in the Constant-Original condition, n=59 in the
-Constant-Reverse condition, n=39 in the Varied-Original condition, and
-n=46 in the Varied-Reverse condition.
-
-\subsubsection{Results}\label{results-4}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.4026}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1299}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1948}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1948}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0779}}@{}}
-\caption{\textbf{Experiment 3 - End of training performance}. The
-Intercept represents the average of the baseline (constant condition),
-and the conditVaried coefficient reflects the difference between the
-constant and varied groups. A larger positive coefficient indicates a
-greater deviation (lower accuracy) for the varied
-group.}\label{tbl-e3-train-dist}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 121.86 & 109.24 & 134.60 & 1.00 \\
-conditVaried & 64.93 & 36.99 & 90.80 & 1.00 \\
-bandOrderReverse & 1.11 & -16.02 & 18.16 & 0.55 \\
-conditVaried:bandOrderReverse & -77.02 & -114.16 & -39.61 & 1.00 \\
-\end{longtable}
-
-\emph{Training}. Figure~\ref{fig-e3-train-dev} displays the average
-deviations from the target band across training blocks, and
-Table~\ref{tbl-e3-train-dist} shows the results of the Bayesian
-regression model predicting the deviation from the common band at the
-end of training (600-800 for reversed order, and 800-1000 for original
-order conditions). The main effect of training condition is significant,
-with the varied condition showing larger deviations ( \(\beta\) = 64.93,
-95\% CrI {[}36.99, 90.8{]}; pd = 100\%). The main effect of band order
-is not significant \(\beta\) = 1.11, 95\% CrI {[}-16.02, 18.16{]}; pd =
-55.4\%, however the interaction between training condition and band
-order is significant, with the varied condition showing greater accuracy
-in the reverse order condition ( \(\beta\) = -77.02, 95\% CrI
-{[}-114.16, -39.61{]}; pd = 100\%).
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e3-train-dev-1.pdf}
-
-}
-
-\caption{\label{fig-e3-train-dev}E3. Deviations from target band during
-testing without feedback stage.}
-
-\end{figure}%
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.5354}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1010}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1515}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1515}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0606}}@{}}
-\caption{\textbf{Experiment 3 testing accuracy}. Main effects of
-condition and band type (training vs.~extrapolation), and the
-interaction between the two factors. Larger coefficient estimates
-indicate larger deviations from the baselines (constant training;
-trained bands \& original order) - and a positive interaction
-coefficient indicates disproportionate deviation for the varied
-condition on the extrapolation
-bands}\label{tbl-e3-bmm-dist}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 288.65 & 199.45 & 374.07 & 1.00 \\
-conditVaried & -40.19 & -104.68 & 23.13 & 0.89 \\
-bandTypeExtrapolation & -23.35 & -57.28 & 10.35 & 0.92 \\
-bandOrderReverse & -73.72 & -136.69 & -11.07 & 0.99 \\
-conditVaried:bandTypeExtrapolation & 52.66 & 14.16 & 90.23 & 1.00 \\
-conditVaried:bandOrderReverse & -37.48 & -123.28 & 49.37 & 0.80 \\
-bandTypeExtrapolation:bandOrderReverse & 80.69 & 30.01 & 130.93 &
-1.00 \\
-conditVaried:bandTypeExtrapolation:bandOrderReverse & 30.42 & -21.00 &
-81.65 & 0.87 \\
-\end{longtable}
-
-\emph{Testing Accuracy.} Table~\ref{tbl-e3-bmm-dist} presents the
-results of the Bayesian mixed efects model predicting absolute deviation
-from the target band during the testing stage. There was no significant
-main effect of training condition,\(\beta\) = -40.19, 95\% CrI
-{[}-104.68, 23.13{]}; pd = 89.31\%, or band type,\(\beta\) = -23.35,
-95\% CrI {[}-57.28, 10.35{]}; pd = 91.52\%. However the effect of band
-order was significant, with the reverse order condition showing lower
-deviations, \(\beta\) = -73.72, 95\% CrI {[}-136.69, -11.07{]}; pd =
-98.89\%. The interaction between training condition and band type was
-also significant \(\beta\) = 52.66, 95\% CrI {[}14.16, 90.23{]}; pd =
-99.59\%, with the varied condition showing disproprionately large
-deviations on the extrapolation bands compared to the constant group.
-There was also a significant interaction between band type and band
-order, \(\beta\) = 80.69, 95\% CrI {[}30.01, 130.93{]}; pd = 99.89\%,
-such that the reverse order condition showed larger deviations on the
-extrapolation bands. No other interactions were significant.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e3-test-dev-1.pdf}
-
-}
-
-\caption{\label{fig-e3-test-dev}Experiment 3 Testing Accuracy. A)
-Deviations from target band during testing without feedback stage. B)
-Conditional effect of condition (Constant vs.~Varied) and testing band
-type (training vs.~extrapolation) on testing accuracy. Error bars
-represent 95\% confidence intervals.}
-
-\end{figure}%
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.4713}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1149}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1724}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1724}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0690}}@{}}
-\caption{Experiment 3. Bayesian Mixed Model Predicting Vx as a function
-of condition (Constant vs.~Varied) and Velocity
-Band}\label{tbl-e3-bmm-vx}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Term
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-Estimate
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Lower
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-95\% CrI Upper
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-pd
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Intercept & 601.83 & 504.75 & 699.42 & 1.00 \\
-conditVaried & 12.18 & -134.94 & 162.78 & 0.56 \\
-bandOrderReverse & 13.03 & -123.89 & 144.67 & 0.58 \\
-Band & 0.49 & 0.36 & 0.62 & 1.00 \\
-conditVaried:bandOrderReverse & -338.15 & -541.44 & -132.58 & 1.00 \\
-conditVaried:Band & -0.04 & -0.23 & 0.15 & 0.67 \\
-bandOrderReverse:bandInt & -0.10 & -0.27 & 0.08 & 0.86 \\
-conditVaried:bandOrderReverse:bandInt & 0.42 & 0.17 & 0.70 & 1.00 \\
-\end{longtable}
-
-\emph{Testing Discrimination.} The full results of the discrimination
-model are presented in Table~\ref{tbl-e3-bmm-dist}. For the purposes of
-assessing group differences in discrimination, only the coefficients
-including the band variable are of interest. The baseline effect of band
-represents the slope cofficient for the constant training - original
-order condition, this effect was significant \(\beta\) = 0.49, 95\% CrI
-{[}0.36, 0.62{]}; pd = 100\%. Neither of the two way interactions
-reached significance, \(\beta\) = -0.04, 95\% CrI {[}-0.23, 0.15{]}; pd
-= 66.63\%, \(\beta\) = -0.1, 95\% CrI {[}-0.27, 0.08{]}; pd = 86.35\%.
-However, the three way interaction between training condition, band
-order, and target band was significant, \(\beta\) = 0.42, 95\% CrI
-{[}0.17, 0.7{]}; pd = 99.96\% - indicating that the varied condition
-showed a greater slope coefficient on the reverse order bands, compared
-to the constant condition - this is clearly shown in
-Figure~\ref{fig-e3-test-vx}, where the steepness of the best fitting
-line for the varied-reversed condition is noticably steeper than the
-other conditions.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e3-test-vx-1.pdf}
-
-}
-
-\caption{\label{fig-e3-test-vx}e3 testing x velocities. Translucent
-bands with dash lines indicate the correct range for each velocity
-band.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e3-bmm-vx-1.pdf}
-
-}
-
-\caption{\label{fig-e3-bmm-vx}Conditional effect of training condition
-and Band. Ribbons indicate 95\% HDI. The steepness of the lines serves
-as an indicator of how well participants discriminated between velocity
-bands.}
-
-\end{figure}%
-
-\subsubsection{Experiment 3 Summary}\label{experiment-3-summary}
-
-\subsection{Computational Model}\label{computational-model-1}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-alm-diagram-1.pdf}
-
-}
-
-\caption{\label{fig-alm-diagram}The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model as used in
-the present work. Input nodes are activated as a function of their
-similarity to the lower-boundary of the target band. The generalization
-parameter, \(c\), determines the degree to which nearby input nodes are
-activated. The output nodes are activated as a function of the weighted
-sum of the input nodes - weights are updated via the delta rule.}
-
-\end{figure}%
-
-\section{Modeling Approach}\label{modeling-approach}
-
-The modeling goal is to implement a full process model capable of both
-1) producing novel responses and 2) modeling behavior in both the
-learning and testing stages of the experiment. For this purpose, we will
-apply the associative learning model (ALM) and the EXAM model of
-function learning \autocite{deloshExtrapolationSineQua1997}. ALM is a
-simple connectionist learning model which closely resembles Kruschke's
-ALCOVE model \autocite{kruschkeALCOVEExemplarbasedConnectionist1992},
-with modifications to allow for the generation of continuous responses.
-
-\subsection{ALM \& Exam Description}\label{alm-exam-description}
-
-ALM is a localist neural network model
-\autocite{pageConnectionistModellingPsychology2000a}, with each input
-node corresponding to a particular stimulus, and each output node
-corresponding to a particular response value. The units in the input
-layer activate as a function of their Gaussian similarity to the input
-stimulus. So, for example, an input stimulus of value 55 would induce
-maximal activation of the input unit tuned to 55. Depending on the value
-of the generalization parameter, the nearby units (e.g.~54 and 56; 53
-and 57) may also activate to some degree. ALM is structured with input
-and output nodes that correspond to regions of the stimulus space, and
-response space, respectively. The units in the input layer activate as a
-function of their similarity to a presented stimulus. As was the case
-with the exemplar-based models, similarity in ALM is exponentially
-decaying function of distance. The input layer is fully connected to the
-output layer, and the activation for any particular output node is
-simply the weighted sum of the connection weights between that node and
-the input activations. The network then produces a response by taking
-the weighted average of the output units (recall that each output unit
-has a value corresponding to a particular response). During training,
-the network receives feedback which activates each output unit as a
-function of its distance from the ideal level of activation necessary to
-produce the correct response. The connection weights between input and
-output units are then updated via the standard delta learning rule,
-where the magnitude of weight changes are controlled by a learning rate
-parameter. The EXAM model is an extension of ALM, with the same learning
-rule and representational scheme for input and output units. EXAM
-differs from ALM only in its response rule, as it includes a linear
-extrapolation mechanism for generating novel responses. Although this
-extrapolation rule departs from a strictly similarity-based
-generalization mechanism, EXAM is distinct from pure rule-based models
-in that it remains constrained by the weights learned during training.
-EXAM retrieves the two nearest training inputs, and the ALM responses
-associated with those inputs, and computes the slope between these two
-points. The slope is then used to extrapolate the response to the novel
-test stimulus. Because EXAM requires at least two input-output pairs to
-generate a response, additional assumptions were required in order for
-it to generate resposnes for the constant group. We assumed that
-participants come to the task with prior knowledge of the origin point
-(0,0), which can serve as a reference point necessary for the model to
-generate responses for the constant group. This assumption is motivated
-by previous function learning research
-(\textcite{brownUnderestimationLinearFunction2017}), which through a
-series of manipulations of the y intercept of the underlying function,
-found that participants consistently demonstrated knowledge of, or a
-bias towards, the origin point (see
-\textcite{kwantesWhyPeopleUnderestimate2006} for additional evidence of
-such a bias in function learning tasks).
-
-See Table~\ref{tbl-alm-exam} for a full specification of the equations
-that define ALM and EXAM, and Figure~\ref{fig-alm-diagram} for a visual
-representation of the ALM model.
-
-\begin{figure*}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4028}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3472}}@{}}
-\caption{ALM \& EXAM Equations}\label{tbl-alm-exam}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{ALM Response Generation}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{ALM Response Generation}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-Input Activation &
-\(a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}\) &
-Input nodes activate as a function of Gaussian similarity to stimulus \\
-Output Activation & \(O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)\) &
-Output unit \(O_j\) activation is the weighted sum of input activations
-and association weights \\
-Output Probability & \(P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}\) &
-The response, \(Y_j\) probabilites computed via Luce's choice rule \\
-Mean Output &
-\(m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}\) &
-Weighted average of probabilities determines response to X \\
-& \textbf{ALM Learning} & \\
-Feedback & \(f_j(Z) = e^{-c(Z-Y_j)^2}\) & feedback signal Z computed as
-similarity between ideal response and observed response \\
-magnitude of error & \(\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)\) & Delta
-rule to update weights. \\
-Update Weights & \(w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}\) & Updates
-scaled by learning rate parameter \(\eta\). \\
-& \textbf{EXAM Extrapolation} & \\
-Instance Retrieval & \(P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}\) &
-Novel test stimulus \(X\) activates input nodes \(X_i\) \\
-Slope Computation & \(S =\) \(\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}\) &
-Slope value, \(S\) computed from nearest training instances \\
-Response & \(E[Y|X_i] = m(X_i) + S \cdot [X - X_i]\) & ALM response
-\(m(X_i)\) adjusted by slope. \\
-\end{longtable}
-
-\end{figure*}%
-
-\subsection{Model Fitting}\label{model-fitting}
-
-To fit ALM and EXAM to our participant data, we employ a similar method
-to \textcite{mcdanielPredictingTransferPerformance2009}, wherein we
-examine the performance of each model after being fit to various subsets
-of the data. Each model was fit to the data in with separate procedures:
-1) fit to maximize predictions of the testing data, 2) fit to maximize
-predictions of both the training and testing data, 3) fit to maximize
-predictions of the just the training data. We refer to this fitting
-manipulations as ``Fit Method'' in the tables and figures below. It
-should be emphasized that for all three fit methods, the ALM and EXAM
-models behave identically - with weights updating only during the
-training phase.Models to were fit separately to the data of each
-individual participant. The free parameters for both models are the
-generalization (\(c\)) and learning rate (\(lr\)) parameters. Parameter
-estimation was performed using approximate bayesian computation (ABC),
-which we describe in detail below.
-
-\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, leftrule=.75mm, colframe=quarto-callout-color-frame, colback=white, left=2mm, breakable, bottomrule=.15mm, arc=.35mm, opacityback=0, rightrule=.15mm]
-
-\textbf{\faIcon{lightbulb} Approximate Bayesian Computation}
-
-To estimate the parameters of ALM and EXAM, we used approximate bayesian
-computation (ABC), enabling us to obtain an estimate of the posterior
-distribution of the generalization and learning rate parameters for each
-individual. ABC belongs to the class of simulation-based inference
-methods \autocite{cranmerFrontierSimulationbasedInference2020}, which
-have begun being used for parameter estimation in cognitive modeling
-relatively recently
-\autocite{turnerTutorialApproximateBayesian2012,turnerBayesianAnalysisSimulationbased2016,kangasraasioParameterInferenceComputational2019}.
-Although they can be applied to any model from which data can be
-simulated, ABC methods are most useful for complex models that lack an
-explicit likelihood function (e.g.~many neural network models).
-
-The general ABC procedure is to 1) define a prior distribution over
-model parameters. 2) sample candidate parameter values, \(\theta^*\),
-from the prior. 3) Use \(\theta^*\) to generate a simulated dataset,
-\(Data_{sim}\). 4) Compute a measure of discrepancy between the
-simulated and observed datasets, \(discrep\)(\(Data_{sim}\),
-\(Data_{obs}\)). 5) Accept \(\theta^*\) if the discrepancy is less than
-the tolerance threshold, \(\epsilon\), otherwise reject \(\theta^*\). 6)
-Repeat until desired number of posterior samples are obtained.
-
-Although simple in the abstract, implementations of ABC require
-researchers to make a number of non-trivial decisions as to i) the
-discrepancy function between observed and simulated data, ii) whether to
-compute the discrepancy between trial level data, or a summary statistic
-of the datasets, iii) the value of the minimum tolerance \(\epsilon\)
-between simulated and observed data. For the present work, we follow the
-guidelines from previously published ABC tutorials
-\autocite{turnerTutorialApproximateBayesian2012,farrellComputationalModelingCognition2018}.
-For the test stage, we summarized datasets with mean velocity of each
-band in the observed dataset as \(V_{obs}^{(k)}\) and in the simulated
-dataset as \(V_{sim}^{(k)}\), where \(k\) represents each of the six
-velocity bands. For computing the discrepancy between datasets in the
-training stage, we aggregated training trials into three equally sized
-blocks (separately for each velocity band in the case of the varied
-group). After obtaining the summary statistics of the simulated and
-observed datasets, the discrepancy was computed as the mean of the
-absolute difference between simulated and observed datasets
-(Equation~\ref{eq-discrep-test} and Equation~\ref{eq-discrep-train}).
-For the models fit to both training and testing data, discrepancies were
-computed for both stages, and then averaged together.
-
-\begin{equation}\phantomsection\label{eq-discrep-test}{
-discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
-}\end{equation}
-
-\begin{equation}\phantomsection\label{eq-discrep-train}{
-\begin{aligned} \\
-discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
-discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
-\end{aligned}
-}\end{equation}
-
-The final component of our ABC implementation is the determination of an
-appropriate value of \(\epsilon\). The setting of \(\epsilon\) exerts
-strong influence on the approximated posterior distribution. Smaller
-values of \(\epsilon\) increase the rejection rate, and improve the
-fidelity of the approximated posterior, while larger values result in an
-ABC sampler that simply reproduces the prior distribution. Because the
-individual participants in our dataset differed substantially in terms
-of the noisiness of their data, we employed an adaptive tolerance
-setting strategy to tailor \(\epsilon\) to each individual. The initial
-value of \(\epsilon\) was set to the overall standard deviation of each
-individuals velocity values. Thus, sampled parameter values that
-generated simulated data within a standard deviation of the observed
-data were accepted, while worse performing parameters were rejected.
-After every 300 samples the tolerance was allowed to increase only if
-the current acceptance rate of the algorithm was less than 1\%. In such
-cases, the tolerance was shifted towards the average discrepancy of the
-5 best samples obtained thus far. To ensure the acceptance rate did not
-become overly permissive, \(\epsilon\) was also allowed to decrease
-every time a sample was accepted into the posterior.
-
-\end{tcolorbox}
-
-For each of the 156 participants from Experiment 1, the ABC algorithm
-was run until 200 samples of parameters were accepted into the posterior
-distribution. Obtaining this number of posterior samples required an
-average of 205,000 simulation runs per participant. Fitting each
-combination of participant, Model (EXAM \& ALM), and fitting method
-(Test only, Train only, Test \& Train) required a total of 192 million
-simulation runs. To facilitate these intensive computational demands, we
-used the Future Package in R
-\autocite{bengtssonUnifyingFrameworkParallel2021}, allowing us to
-parallelize computations across a cluster of ten M1 iMacs, each with 8
-cores.
-
-\subsubsection{Modelling Results}\label{modelling-results}
-
-\paragraph{Group level Patterns}\label{group-level-patterns}
-
-\begin{longtable}{lcrrrr}
-
-\caption{\label{tbl-htw-modelError-e1}Models errors predicting empirical
-data - aggregated over all participants, posterior parameter values, and
-velocity bands. Note that Fit Method refers to the subset of the data
-that the model was trained on, while Task Stage refers to the subset of
-the data that the model was evaluated on.}
-
-\tabularnewline
-
-\toprule
- &  & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} \\ 
-\cmidrule(lr){3-4} \cmidrule(lr){5-6}
-Task Stage & Fit Method & Constant & Varied & Constant & Varied \\ 
-\midrule\addlinespace[2.5pt]
-\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{Fit to Test Data} & \cellcolor[HTML]{FFFFFF}{$199.93$} & \cellcolor[HTML]{FFFFFF}{$103.36$} & \cellcolor[HTML]{FFFFFF}{$104.01$} & \cellcolor[HTML]{FFFFFF}{$85.68$} \\
-\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{Fit to Test \& Training Data} & \cellcolor[HTML]{FFFFFF}{$216.97$} & \cellcolor[HTML]{FFFFFF}{$170.28$} & \cellcolor[HTML]{FFFFFF}{$127.94$} & \cellcolor[HTML]{FFFFFF}{$144.86$} \\
-\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{Fit to Training Data} & \cellcolor[HTML]{FFFFFF}{$467.73$} & \cellcolor[HTML]{FFFFFF}{$291.38$} & \cellcolor[HTML]{FFFFFF}{$273.30$} & \cellcolor[HTML]{FFFFFF}{$297.91$} \\
-\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{Fit to Test Data} & \cellcolor[HTML]{FFFFFF}{$297.82$} & \cellcolor[HTML]{FFFFFF}{$2,016.01$} & \cellcolor[HTML]{FFFFFF}{$53.90$} & \cellcolor[HTML]{FFFFFF}{$184.00$} \\
-\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{Fit to Test \& Training Data} & \cellcolor[HTML]{FFFFFF}{$57.40$} & \cellcolor[HTML]{FFFFFF}{$132.32$} & \cellcolor[HTML]{FFFFFF}{$42.92$} & \cellcolor[HTML]{FFFFFF}{$127.90$} \\
-\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{Fit to Training Data} & \cellcolor[HTML]{FFFFFF}{$51.77$} & \cellcolor[HTML]{FFFFFF}{$103.48$} & \cellcolor[HTML]{FFFFFF}{$51.43$} & \cellcolor[HTML]{FFFFFF}{$107.03$} \\
-\bottomrule
-
-\end{longtable}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-htw-post-dist-1.pdf}
-
-}
-
-\caption{\label{fig-htw-post-dist}Posterior Distributions of \(c\) and
-\(lr\) parameters. Points represent median values, thicker intervals
-represent 66\% credible intervals and thin intervals represent 95\%
-credible intervals around the median. Note that the y axes of the plots
-for the c parameter are scaled logarithmically.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-htw-resid-pred-1.pdf}
-
-}
-
-\caption{\label{fig-htw-resid-pred}Model residuals for each combination
-of training condition, fit method, and model. Residuals reflect the
-difference between observed and predicted values. Lower values indicate
-better model fit. Note that y axes are scaled differently between
-facets. A) Residuals predicting each block of the training data. B)
-Residuals predicting each band during the testing stage. Bolded bars
-indicate bands that were trained, non-bold bars indicate extrapolation
-bands.}
-
-\end{figure}%
-
-The posterior distributions of the \(c\) and \(lr\) parameters are shown
-Figure~\ref{fig-htw-post-dist}, and model predictions are shown
-alongside the empirical data in Figure~\ref{fig-cm-vx-pat}. There were
-substantial individual differences in the posteriors of both parameters,
-with the within-group individual differences generally swamped any
-between-group or between-model differences. The magnitude of these
-individual differences remains even if we consider only the single best
-parameter set for each subject.
-
-We used the posterior distribution of \(c\) and \(lr\) parameters to
-generate a posterior predictive distribution of the observed data for
-each participant, which then allows us to compare the empirical data to
-the full range of predictions from each model. Aggregated residuals are
-displayed in Figure~\ref{fig-htw-resid-pred}. The pattern of training
-stage residual errors are unsurprising across the combinations of models
-and fitting method . Differences in training performance between ALM and
-EXAM are generally minor (the two models have identical learning
-mechanisms). The differences in the magnitude of residuals across the
-three fitting methods are also straightforward, with massive errors for
-the `fit to Test Only' model, and the smallest errors for the `fit to
-train only' models. It is also noteworthy that the residual errors are
-generally larger for the first block of training, which is likely due to
-the initial values of the ALM weights being unconstrained by whatever
-initial biases participants tend to bring to the task. Future work may
-explore the ability of the models to capture more fine grained aspects
-of the learning trajectories. However for the present purposes, our
-primary interest is in the ability of ALM and EXAM to account for the
-testing patterns while being constrained, or not constrained, by the
-training data. All subsequent analyses and discussion will thus focus on
-the testing stage.
-
-The residuals of the model predictions for the testing stage
-(Figure~\ref{fig-htw-resid-pred}) also show an unsurprising pattern
-across fitting methods - with models fit only to the test data showing
-the best performance, followed by models fit to both training and test
-data, and with models fit only to the training data showing the worst
-performance (note that y axes are scaled different between plots).
-Although EXAM tends to perform better for both Constant and Varied
-participants (see also Figure~\ref{fig-ee-e1}), the relative advantage
-of EXAM is generally larger for the Constant group - a pattern
-consistent across all three fitting methods. The primary predictive
-difference between ALM and EXAM is made clear in
-Figure~\ref{fig-cm-vx-pat}, which directly compares the observed data
-against the posterior predictive distributions for both models.
-Regardless of how the models are fit, only EXAM can capture the pattern
-where participants are able to discriminate all 6 target bands.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-cm-vx-pat-1.pdf}
-
-}
-
-\caption{\label{fig-cm-vx-pat}Empirical data and Model predictions for
-mean velocity across target bands. Fitting methods (Test Only, Test \&
-Train, Train Only) - are separated across rows, and Training Condition
-(Constant vs.~Varied) are separated by columns. Each facet contains the
-predictions of ALM and EXAM, alongside the observed data.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\captionsetup{labelsep=none}\includegraphics{full_files/figure-pdf/fig-ee-e1-1.pdf}
-
-}
-
-\caption{\label{fig-ee-e1}}
-
-\end{figure}%
-
-To quantitatively assess whether the differences in performance between
-models, we fit a bayesian regressions predicting the errors of the
-posterior predictions of each models as a function of the Model (ALM
-vs.~EXAM) and training condition (Constant vs.~Varied).
-
-Model errors were significantly lower for EXAM (\(\beta\) = -37.54, 95\%
-CrI {[}-60.4, -14.17{]}, pd = 99.85\%) than ALM. There was also a
-significant interaction between Model and Condition (\(\beta\) = 60.42,
-95\% CrI {[}36.17, 83.85{]}, pd = 100\%), indicating that the advantage
-of EXAM over ALM was significantly greater for the constant group. To
-assess whether EXAM predicts constant performance significantly better
-for Constant than for Varied subjects, we calculated the difference in
-model error between the Constant and Varied conditions specifically for
-EXAM. The results indicated that the model error for EXAM was
-significantly lower in the Constant condition compared to the Varied
-condition, with a mean difference of -22.88 (95\% CrI {[}-46.02,
--0.97{]}, pd = 0.98).
-
-\begin{longtable}{lrrrrrrrr}
-
-\caption{\label{tbl-htw-modelError-e23}Models errors predicting
-empirical data - aggregated over all participants, posterior parameter
-values, and velocity bands. Note that Fit Method refers to the subset of
-the data that the model was trained on, while Task Stage refers to the
-subset of the data that the model was evaluated on.}
-
-\tabularnewline
-
-\toprule
- & \multicolumn{4}{c}{E2} & \multicolumn{4}{c}{E3} \\ 
-\cmidrule(lr){2-5} \cmidrule(lr){6-9}
- & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} \\ 
-\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
-Task Stage & Constant & Varied & Constant & Varied & Constant & Varied & Constant & Varied \\ 
-\midrule\addlinespace[2.5pt]
-\multicolumn{9}{l}{Fit to Test Data} \\ 
-\midrule\addlinespace[2.5pt]
-\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{$239.7$} & \cellcolor[HTML]{FFFFFF}{$129.8$} & \cellcolor[HTML]{FFFFFF}{$99.7$} & \cellcolor[HTML]{FFFFFF}{$88.2$} & \cellcolor[HTML]{FFFFFF}{$170.1$} & \cellcolor[HTML]{FFFFFF}{$106.1$} & \cellcolor[HTML]{FFFFFF}{$92.3$} & \cellcolor[HTML]{FFFFFF}{$72.8$} \\
-\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{$53.1$} & \cellcolor[HTML]{FFFFFF}{$527.1$} & \cellcolor[HTML]{FFFFFF}{$108.1$} & \cellcolor[HTML]{FFFFFF}{$169.3$} & \cellcolor[HTML]{FFFFFF}{$70.9$} & \cellcolor[HTML]{FFFFFF}{$543.5$} & \cellcolor[HTML]{FFFFFF}{$157.8$} & \cellcolor[HTML]{FFFFFF}{$212.7$} \\
-\midrule\addlinespace[2.5pt]
-\multicolumn{9}{l}{Fit to Test \& Training Data} \\ 
-\midrule\addlinespace[2.5pt]
-\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{$266.0$} & \cellcolor[HTML]{FFFFFF}{$208.2$} & \cellcolor[HTML]{FFFFFF}{$125.1$} & \cellcolor[HTML]{FFFFFF}{$126.4$} & \cellcolor[HTML]{FFFFFF}{$197.7$} & \cellcolor[HTML]{FFFFFF}{$189.5$} & \cellcolor[HTML]{FFFFFF}{$130.0$} & \cellcolor[HTML]{FFFFFF}{$128.5$} \\
-\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{$40.0$} & \cellcolor[HTML]{FFFFFF}{$35.4$} & \cellcolor[HTML]{FFFFFF}{$30.4$} & \cellcolor[HTML]{FFFFFF}{$23.6$} & \cellcolor[HTML]{FFFFFF}{$49.1$} & \cellcolor[HTML]{FFFFFF}{$85.6$} & \cellcolor[HTML]{FFFFFF}{$49.2$} & \cellcolor[HTML]{FFFFFF}{$78.4$} \\
-\midrule\addlinespace[2.5pt]
-\multicolumn{9}{l}{Fit to Training Data} \\ 
-\midrule\addlinespace[2.5pt]
-\cellcolor[HTML]{FFFFFF}{Test} & \cellcolor[HTML]{FFFFFF}{$357.4$} & \cellcolor[HTML]{FFFFFF}{$295.9$} & \cellcolor[HTML]{FFFFFF}{$305.1$} & \cellcolor[HTML]{FFFFFF}{$234.5$} & \cellcolor[HTML]{FFFFFF}{$415.0$} & \cellcolor[HTML]{FFFFFF}{$298.8$} & \cellcolor[HTML]{FFFFFF}{$295.5$} & \cellcolor[HTML]{FFFFFF}{$243.7$} \\
-\cellcolor[HTML]{FFFFFF}{Train} & \cellcolor[HTML]{FFFFFF}{$42.5$} & \cellcolor[HTML]{FFFFFF}{$23.0$} & \cellcolor[HTML]{FFFFFF}{$43.2$} & \cellcolor[HTML]{FFFFFF}{$22.6$} & \cellcolor[HTML]{FFFFFF}{$51.4$} & \cellcolor[HTML]{FFFFFF}{$63.8$} & \cellcolor[HTML]{FFFFFF}{$51.8$} & \cellcolor[HTML]{FFFFFF}{$65.3$} \\
-\bottomrule
-
-\end{longtable}
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-cm-vx-pat-e2-e3-1.pdf}
-
-}
-
-\caption{\label{fig-cm-vx-pat-e2-e3}Empirical data and Model predictions
-from Experiment 2 and 3 for the testing stage. Observed data is shown on
-the right. Bolded bars indicate bands that were trained, non-bold bars
-indicate extrapolation bands.}
-
-\end{figure}%
-
-\begin{longtable}{llrrrr}
-
-\caption{\label{tbl-htw-ee-e23}Results of Bayesian Regression models
-predicting model error as a function of Model (ALM vs.~EXAM), Condition
-(Constant vs.~Varied), and the interaction between Model and Condition.
-The values represent the estimate coefficient for each term, with 95\%
-credible intervals in brackets. The intercept reflects the baseline of
-ALM and Constant. The other estimates indicate deviations from the
-baseline for the EXAM mode and varied condition. Lower values indicate
-better model fit.}
-
-\tabularnewline
-
-\toprule
- &  &  & \multicolumn{2}{c}{Credible Interval} &  \\ 
-\cmidrule(lr){4-5}
-Experiment & Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\ 
-\midrule\addlinespace[2.5pt]
-\multicolumn{6}{l}{Experiment 1} \\ 
-\midrule\addlinespace[2.5pt]
-Exp 1 & Intercept & $176.30$ & $156.86$ & $194.59$ & $1.00$ \\ 
-Exp 1 & ModelEXAM & $-88.44$ & $-104.51$ & $-71.81$ & $1.00$ \\ 
-Exp 1 & conditVaried & $-37.54$ & $-60.40$ & $-14.17$ & $1.00$ \\ 
-Exp 1 & ModelEXAM:conditVaried & \cellcolor[HTML]{FFFFFF}{\textbf{$60.42$}} & $36.17$ & $83.85$ & \cellcolor[HTML]{FFFFFF}{\textbf{$1.00$}} \\ 
-\midrule\addlinespace[2.5pt]
-\multicolumn{6}{l}{Experiment 2} \\ 
-\midrule\addlinespace[2.5pt]
-Exp 2 & Intercept & $245.87$ & $226.18$ & $264.52$ & $1.00$ \\ 
-Exp 2 & ModelEXAM & $-137.73$ & $-160.20$ & $-115.48$ & $1.00$ \\ 
-Exp 2 & conditVaried & $-86.39$ & $-113.52$ & $-59.31$ & $1.00$ \\ 
-Exp 2 & ModelEXAM:conditVaried & \cellcolor[HTML]{FFFFFF}{\textbf{$56.87$}} & $25.26$ & $88.04$ & \cellcolor[HTML]{FFFFFF}{\textbf{$1.00$}} \\ 
-\midrule\addlinespace[2.5pt]
-\multicolumn{6}{l}{Experiment 3} \\ 
-\midrule\addlinespace[2.5pt]
-Exp 3 & Intercept & $164.83$ & $140.05$ & $189.44$ & $1.00$ \\ 
-Exp 3 & ModelEXAM & $-65.66$ & $-85.97$ & $-46.02$ & $1.00$ \\ 
-Exp 3 & conditVaried & $-40.61$ & $-75.90$ & $-3.02$ & $0.98$ \\ 
-Exp 3 & bandOrderReverse & $25.47$ & $-9.34$ & $58.68$ & $0.93$ \\ 
-Exp 3 & ModelEXAM:conditVaried & \cellcolor[HTML]{FFFFFF}{\textbf{$41.90$}} & $11.20$ & $72.54$ & \cellcolor[HTML]{FFFFFF}{\textbf{$0.99$}} \\ 
-Exp 3 & ModelEXAM:bandOrderReverse & $-7.32$ & $-34.53$ & $21.05$ & $0.70$ \\ 
-Exp 3 & conditVaried:bandOrderReverse & $30.82$ & $-19.57$ & $83.56$ & $0.88$ \\ 
-Exp 3 & ModelEXAM:conditVaried:bandOrderReverse & $-60.60$ & $-101.80$ & $-18.66$ & $1.00$ \\ 
-\bottomrule
-
-\end{longtable}
-
-\emph{Model Fits to Experiment 2 and 3.} Data from Experiments 2 and 3
-were fit to ALM and EXAM in the same manner as Experiment1 . For
-brevity, we only plot and discuss the results of the ``fit to training
-and testing data'' models - results from the other fitting methods can
-be found in the appendix. The model fitting results for Experiments 2
-and 3 closely mirrored those observed in Experiment 1. The Bayesian
-regression models predicting model error as a function of Model (ALM
-vs.~EXAM), Condition (Constant vs.~Varied), and their interaction (see
-Table~\ref{tbl-htw-ee-e23}) revealed a consistent main effect of Model
-across all three experiments. The negative coefficients for the
-ModelEXAM term (Exp 2: \(\beta\) = -86.39, 95\% CrI -113.52, -59.31, pd
-= 100\%; Exp 3: \(\beta\) = -40.61, 95\% CrI -75.9, -3.02, pd = 98.17\%)
-indicate that EXAM outperformed ALM in both experiments. Furthermore,
-the interaction between Model and Condition was significant in both
-Experiment 2 (\(\beta\) = 56.87, 95\% CrI 25.26, 88.04, pd = 99.98\%)
-and Experiment 3 (\(\beta\) = 41.9, 95\% CrI 11.2, 72.54, pd = 99.35\%),
-suggesting that the superiority of EXAM over ALM was more pronounced for
-the Constant group compared to the Varied group, as was the case in
-Experiment 1. Recall that Experiment 3 included participants in both the
-original and reverse order conditions - and that this manipulation
-interacted with the effect of training condition. We thus also
-controleld for band order in our Bayesian Regression assessing the
-relative performance of EXAM and ALM in Experiment 3. There was a
-significant three way interaction between Model, Training Condition, and
-Band Order (\(\beta\) = -60.6, 95\% CrI -101.8, -18.66, pd = 99.83\%),
-indicating that the relative advantage of EXAM over ALM was only more
-pronounced in the original order condition, and not the reverse order
-condition (see Figure~\ref{fig-e2_e3_ae}).
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-e2_e3_ae-1.pdf}
-
-}
-
-\caption{\label{fig-e2_e3_ae}Conditional effects of Model (ALM vs EXAM)
-and Condition (Constant vs.~Varied) on Model Error for Experiment 2 and
-3 data. Experiment 3 also includes a control for the order of training
-vs.~testing bands (original order vs.~reverse order).}
-
-\end{figure}%
-
-\emph{Computational Model Summary}. Across the model fits to all three
-experiments, we found greater support for EXAM over ALM (negative
-coefficients on the ModelEXAM term in Table~\ref{tbl-htw-ee-e23}), and
-moreover that the constant participants were disproportionately well
-described by EXAM in comparison to ALM (positive coefficients on
-ModelEXAM:conditVaried terms in Table~\ref{tbl-htw-ee-e23}). This
-pattern is also clearly depicted in Figure~\ref{fig-htw-best-model},
-which plots the difference in model errors between ALM and EXAM for each
-individual participant. Both varied and constant conditions have a
-greater proportion of subjects better fit by EXAM (positive error
-differences), with the magnitude of EXAM's advantage visibly greater for
-the constant group. It also bears mention that numerous participants
-were better fit by ALM, or did not show a clear preference for either
-model. A subset of these participants are shown in
-Figure~\ref{fig-htw-indv-pred}.
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-htw-best-model-1.pdf}
-
-}
-
-\caption{\label{fig-htw-best-model}Difference in model errors for each
-participant, with models fit to both train and test data. Positive
-values favor EXAM, while negative values favor ALM.}
-
-\end{figure}%
-
-\begin{figure}
-
-\centering{
-
-\includegraphics{full_files/figure-pdf/fig-htw-indv-pred-1.pdf}
-
-}
-
-\caption{\label{fig-htw-indv-pred}Model predictions alongside observed
-data for a subset of individual participants. A) 3 constant and 3 varied
-participants fit to both the test and training data. B) 3 constant and 3
-varied subjects fit to only the trainign data. Bolded bars indicate
-bands that were trained, non-bold bars indicate extrapolation bands.}
-
-\end{figure}%
-
-\section{General Discussion}\label{general-discussion-1}
-
-\emph{Experimental Result Summary}
-
-Across three experiments, we investigated the impact of training
-variability on learning and extrapolation in a visuomotor function
-learning task. In Experiment 1, participants in the varied training
-condition, who experienced a wider range of velocity bands during
-training, showed lower accuracy at the end of training compared to those
-in the constant training condition.
-
-Crucially, during the testing phase, the varied group exhibited
-significantly larger deviations from the target velocity bands,
-particularly for the extrapolation bands that were not encountered
-during training. The varied group also showed less discrimination
-between velocity bands, as evidenced by shallower slopes when predicting
-response velocity from target velocity band.
-
-Experiment 2 extended these findings by reversing the order of the
-training and testing bands. Similar to Experiment 1, the varied group
-demonstrated poorer performance during both training and testing phases.
-However, unlike Experiment 1, the varied group did not show a
-significant difference in discrimination between bands compared to the
-constant group.
-
-In Experiment 3, we provided only ordinal feedback during training, in
-contrast to the continuous feedback provided in the previous
-experiments. Participants were assigned to both an order condition
-(original or reverse) and a training condition (constant or varied). The
-varied condition showed larger deviations at the end of training,
-consistent with the previous experiments. Interestingly, there was a
-significant interaction between training condition and band order, with
-the varied condition showing greater accuracy in the reverse order
-condition. During testing, the varied group once again exhibited larger
-deviations, particularly for the extrapolation bands. The reverse order
-conditions showed smaller deviations compared to the original order
-conditions. Discrimination between velocity bands was poorer for the
-varied group in the original order condition, but not in the reverse
-order condition.
-
-All three of our experiments yielded evidence that varied training
-conditions produced less learning by the end of training, a pattern
-consistent with much of the previous research on the influence of
-training variability
-\autocite{catalanoDistantTransferCoincident1984a,wrisbergVariabilityPracticeHypothesis1987,soderstromLearningPerformanceIntegrative2015}.
-The sole exception to this pattern was the reverse order condition in
-Experiment 3, where the varied group was not significantly worse than
-the constant group. Neither the varied condition trained with the same
-reverse-order items in Experiment 2, nor the original-order varied
-condition trained with ordinal feedback in Experiment 3 were able to
-match the performance of their complementary constant groups by the end
-of training, suggesting that the relative success of the ordinal-reverse
-ordered varied group cannot be attributed to item or feedback effects
-alone.
-
-Our findings also diverge from the two previous studies to cleanly
-manipulate the variability of training items in a function learning task
-\autocite{deloshExtrapolationSineQua1997,vandamMappingShapeVisuomotor2015},
-although the varied training condition of
-\textcite{vandamMappingShapeVisuomotor2015} also exhibited less
-learning, neither of these previous studies observed any difference
-between training conditions in extrapolation to novel items. Like
-\textcite{deloshExtrapolationSineQua1997} , our participants exhibited
-above chance extrapolation/discrimination of novel items, however they
-observed no difference between any of their three training conditions. A
-noteworthy difference difference between our studies is that
-\textcite{deloshExtrapolationSineQua1997} trained participants with
-either 8, 20, or 50 unique items (all receiving the same total number of
-training trials). These larger sets of unique items, combined with the
-fact that participants achieved near ceiling level performance by the
-end of training - may have made it more difficult to observe any
-between-group differences of training variation in their study.
-\textcite{vandamMappingShapeVisuomotor2015} 's variability manipulation
-was more similar to our own, as they trained participants with either 2
-or 5 unique items. However, although the mapping between their input
-stimuli and motor responses was technically linear, the input dimension
-was more complex than our own, as it was defined by the degree of
-``spikiness'' of the input shape. This entirely arbitrary mapping also
-would have preculded any sense of a ``0'' point, which may partially
-explain why neither of their training conditions were able to
-extrapolate linearly in the manner observed in the current study or in
-\textcite{deloshExtrapolationSineQua1997}.
-
-\emph{Modeling Summary} EXAM is the best model for both groups, but EXAM
-does relatively good at accounting for the constant group. May have
-seemed counterintuitive, if one assumed that multiple, varied, examples
-were necessary to extract a rule. But, EXAM is not a conventional rule
-model - it doesn't require explictly abstract of a rule, but rather the
-rule-based response occurs during retrieval. The constant groups
-formation of a single, accurate, input-output association, in
-combination with the usefulness of the zero point, may have been
-sufficient for EXAM, and the constant group, to perform well. One
-concern may have been that the assumption of participants making use of
-the zero point turned the extrapolation problem into an interpolation
-problem - however this concern is ameliorated by the consistency of the
-results across both the original and reverse order conditions.
-
-\emph{Limitations}
-
-While the present study provides valuable insights into the influence of
-training variability on visuomotor function learning and extrapolation,
-there are several limitations that should be flagged. First, although
-the constant training group never had experience from a velocity band
-closer to the extrapolation bands than the varied group, they always had
-a three times more trials with the nearest velocity band. Such a
-difference may be an unavoidable consequence of varied vs.~constant
-design which match the total number of training trials between the two
-groups. However in order to more carefully tease apart the influence of
-variability from the influence of frequency/repetition effects, future
-research could explore alternative designs that maintain the variability
-manipulation while equating the amount of training on the nearest
-examples across conditions, such as by increasing the total number of
-trials for the varied group. Another limitation is that the testing
-stage did not include any interpolation items, i.e.~the participants
-tested only from the training bands they experienced during training, or
-from extrapolation bands. The absence of interpolation testing makes it
-more difficult to distinguish between the effects of training
-variability on extrapolation specifically, as opposed to generalization
-more broadly. Of course, the nature of the constant training condition
-makes interpolation teseting impossible to implement, however future
-studies might compare a training regimes that each include at least 2
-distinct items, but still differ in total amount of variability
-experienced, which would then allow groups to be compared in terms of
-both interpolation and extrapolation testing. Finally, the task employed
-in the present study consisted of only a linear, positive function.
-Previous work in human function learning has repeatedly shown that such
-functions are among the easiest to learn, but that humans are
-nonetheless capable of learning negative, non-linear, or discontinuous
-functions
-\autocite{deloshExtrapolationSineQua1997,mcdanielPredictingTransferPerformance2009,kalishLearningExtrapolatingPeriodic2013,busemeyerLearningFunctionalRelations1997}.
-It thus remains an open question as to whether the influence of training
-variability might interact with various components of the to-be-learned
-function.
-
-\subsection{Comparison to Project 1}\label{comparison-to-project-1}
-
-\subsubsection{Differences between the
-tasks}\label{differences-between-the-tasks}
-
-There are a number of differences between Project 1's Hit The Target
-(HTT), and Project 2's Hit The Wall (HTW) tasks.
-
-\begin{itemize}
-\item
-  Task Space Complexity: In~HTW,~the task space is also almost perfectly
-  smooth, at least for the continuous feedback subjects, if they throw
-  100 units too hard, they'll be told that they were 100 units too hard.
-  Whereas in HTT, ~it was possible to produce xy velocity combinations
-  that were technically closer to the empirical solution space than
-  other throws, but which resulted in worse feedback due to striking the
-  barrier.
-\item
-  Perceptual Distinctiveness: HTT offers perceptually distinct varied
-  conditions that directly relate to the task's demands, which may
-  increase the sallience between training positions encounted by the
-  varied group. In contrast, HTW's varied conditions differ only in the
-  numerical values displayed, lacking the same level of perceptual
-  differentiation. Conversely in~HTW, the only difference between
-  conditions for the varied group are the numbers displayed at the top
-  of the screen which indicate the current target band(e.g.~800-1000, or
-  1000-1200)
-\item
-  In~HTW, our primary testing stage of interest has no feedback, whereas
-  in HTT testing always included feedback (the intermittent testing in
-  HTT expt 1 being the only exception). Of course, we do collect testing
-  with feedback data at the end of~HTW, but we haven't focused on that
-  data at all in our modelling work thus far. It's also interesting to
-  recall that the gap between varied and constant in~HTW~does seem to
-  close substantially in the testing-with-feedback stage. The difference
-  between no-feedback and feedback testing might be relevant if the
-  benefits of variation have anything to do with improving subsequent
-  learning (as opposed to subsequent immediate performance), OR if the
-  benefits of constant training rely on having the most useful anchor,
-  having the most useful anchor might be a lot less helpful if you're
-  getting feedback from novel positions and can thus immediately begin
-  to form position-specific anchors for the novelties, rather than
-  relying on a training anchor.~
-\item
-  HTW~and HTT both have a similar amount of training trials
-  (\textasciitilde200), and thus the constant groups acquire a similar
-  amount of experience with their single position/velocity in both
-  experiments. However, the varied conditions in both HTT
-  experiments~train on 2 positions, whereas the varied group
-  in~HTW~trains on 3 velocity bands. This means that in HTT the varied
-  group gets half as much experience on any one position as the constant
-  group, and in~HTW~they only get 1/3 as much experience in any one
-  position. There are likely myriad ways in which this might impact the
-  success of the varied group regardless of how you think the benefits
-  of variation might be occurring, e.g.~maybe they also need to develop
-  a coherent anchor, maybe they need more experience in order to extract
-  a function, or more experience in order to properly learn to tune
-  their c parameter.~
-\end{itemize}
-
-\section{References}\label{references}
-
-%bib-loc-124C8010
-
-\section{Appendix}\label{appendix}
-
-Reviewer \#2: This study addresses a question that is important both
-theoretically and practically. However, the authors need to rule out the
-following, less interesting alternative. Namely, the results could be
-due to task practice effect, as follows.
-
-Since there was no pre-training test, and no practice trials (as far as
-I can tell), and since the task was an online motor task that
-participants could not rely on their prior motor experience, trying to
-launch the ball to the target could only be done via trial and error.
-For the varied training group, they got to practice at two distances.
-Therefore, they had a better ``calibration'' in terms of the
-relationship between launching speed and target distance. This was
-likely beneficial both in Exp.1 when both transfer distances were
-interpolations from the two trained distances, and in Exp.2 when two
-transfer distances were interpolations and two were extrapolations but
-the latter two were immediately next to the training distances.
-
-In comparison, since the constant group trained at only a single
-distance, any transfer distance (or at least the first transfer distance
-tested) was extrapolation even if this transfer distance was shorter
-than the trained, because the participants did not know beforehand how
-to shoot the ball to the shortest distance due to the existence of the
-barrier. If the transfer distance was longer, for sure that was
-extrapolation.
-
-Regardless, the above analysis suggests that the constant group would
-always be a step behind the varied group. The number of trials at each
-transfer distance may not be sufficient for them to catch up the varied
-group either (whether there was learning during testing should be
-checked). If such disadvantage for the constant group is indeed due to
-the lack of tryout opportunities, then the authors should verify whether
-the same results still hold if all groups were provided opportunities to
-practice, or if pre-training tests across all distances were offered.
-
-\subsubsection{exponential learning models fit to individual
-subjects}\label{exponential-learning-models-fit-to-individual-subjects}
-
-\subsubsection{Group comparison of learning rate
-fits}\label{group-comparison-of-learning-rate-fits}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-60-1.pdf}
-
-\subsubsection{First vs.~second half of testing
-stage}\label{first-vs.-second-half-of-testing-stage}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-61-1.pdf}
-
-\subsubsection{Group Comparison for asymptote-starting
-performance}\label{group-comparison-for-asymptote-starting-performance}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-62-1.pdf}
-
-\subsubsection{Relative distance and
-under/overshooting}\label{relative-distance-and-underovershooting}
-
-Reviewer 3 Absolute versus relative distance: From a methodological
-standpoint, I understand the need to differentiate these two types of
-distance. However, from a theoretical perspective there may be some
-issue in differentiating these two concepts. Schema theory relies on
-relative (or invariant) information to inform the motor program.
-However, both distances would be important to an instance or exemplar
-representation. You may want to consider commenting on this issue.
-
-Reviewer 2 For the same reason, the plots showing improvement during
-training could be due to participants learning the task, rather than
-fine motor skills. Although task learning and motor learning are
-impossible to separate cleanly, the common practice in the field is
-indeed to offer practice trials to reduce the task learning aspects. The
-authors should address this.
-
-In addition to absolute errors (which is related to variance), the
-authors should also provide other measures of performance, e.g., the
-mean of the signed errors, so that readers have a better idea whether
-there was any meaningful over- or undershooting.
-
-\paragraph{experiment 1 training - relative
-distances}\label{experiment-1-training---relative-distances}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-63-1.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-63-2.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-63-3.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-63-4.pdf}
-
-\begin{verbatim}
-
-=========================================================================
-conditType devianceDirection      610            760            910      
--------------------------------------------------------------------------
-constant       Overshoot                    311.84(307.92)               
-constant      Undershoot                    188.05(163.62)               
-varied         Overshoot     211.69(234.97)                360.14(322.01)
-varied        Undershoot     107.35(81.21)                 244.85(196.47)
--------------------------------------------------------------------------
-\end{verbatim}
-
-\begin{verbatim}
-
-======================================================
-conditType      610           760            910      
-------------------------------------------------------
-constant                 121.03(269.17)               
-varied     39.91(178.12)                150.53(290.04)
-------------------------------------------------------
-\end{verbatim}
-
-\begin{verbatim}
-
-====================================================================
-conditType     610           760            835            910      
---------------------------------------------------------------------
-constant   7.13(124.02) 107.02(218.49) 142.42(252.34) 122.92(282.58)
-varied     3.19(96.67)   92.1(173.9)   103.84(214.4)  108.12(234.59)
---------------------------------------------------------------------
-\end{verbatim}
-
-\paragraph{experiment 2 training - relative
-distances}\label{experiment-2-training---relative-distances}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-64-1.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-64-2.pdf}
-
-\paragraph{Experiment 1 Testing - relative
-distances}\label{experiment-1-testing---relative-distances}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-65-1.pdf}
-
-\begin{verbatim}
-
-====================================================================================================================================
-conditType2         msdu_610       msdu_760       msdu_835       msdu_910      msds_610      msds_760      msds_835      msds_910   
-------------------------------------------------------------------------------------------------------------------------------------
-Constant Training 136.27(84.29) 191.65(112.65) 219.46(139.91) 276.75(153.09) 25.28(158.98) 50.82(217.48) 73.14(250.93) 50.76(313.77)
-Varied Training   105.12(51.39)  149.37(93.4)  180.54(129.52) 198.64(137.84) 13.85(116.87) 50.59(169.59) 50.52(217.39) 49.94(237.71)
-------------------------------------------------------------------------------------------------------------------------------------
-\end{verbatim}
-
-\begin{verbatim}
-
-=========================================================================
-Condition              610           760           835           910     
--------------------------------------------------------------------------
-Constant Training 25.28(158.98) 50.82(217.48) 73.14(250.93) 50.76(313.77)
-Varied Training   13.85(116.87) 50.59(169.59) 50.52(217.39) 49.94(237.71)
--------------------------------------------------------------------------
-\end{verbatim}
-
-\paragraph{Experiment 2 Testing - relative
-distances}\label{experiment-2-testing---relative-distances}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-66-1.pdf}
-
-\paragraph{Experimenet 1 - intermittent
-testing}\label{experimenet-1---intermittent-testing}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-67-1.pdf}
-
-\begin{verbatim}
-
-======================================================================================================
-Condition 610_First Half 760_First Half 910_First Half 610_Second Half 760_Second Half 910_Second Half
-------------------------------------------------------------------------------------------------------
-constant  206.64(82.08)  286.51(121.07) 406.93(145.2)   187.2(55.24)    238.21(95.16)  313.27(114.86) 
-varied    195.68(78.58)  278.9(105.37)  318.53(134.81)  177.79(70.82)  224.98(108.04)   276.86(110.5) 
-------------------------------------------------------------------------------------------------------
-\end{verbatim}
-
-\subsubsection{Training plots - Experiment
-1}\label{training-plots---experiment-1}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-68-1.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-68-2.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-68-3.pdf}
-
-\paragraph{Not in manuscript}\label{not-in-manuscript}
-
-\paragraph{fit to testing performance averaged across
-positions}\label{fit-to-testing-performance-averaged-across-positions}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-69-1.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-69-2.pdf}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-69-3.pdf}
-
-\paragraph{statistical tests for starting
-performance}\label{statistical-tests-for-starting-performance}
-
-\begin{verbatim}
-ANOVA Table (type III tests)
-
-      Effect DFn DFd F     p p<.05   ges
-1 conditType   1 206 3 0.083       0.015
-\end{verbatim}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-70-1.pdf}
-
-\paragraph{statistical tests for
-asymptote}\label{statistical-tests-for-asymptote}
-
-\begin{verbatim}
-ANOVA Table (type III tests)
-
-      Effect DFn DFd   F     p p<.05   ges
-1 conditType   1 206 3.4 0.067       0.016
-\end{verbatim}
-
-\includegraphics{full_files/figure-pdf/unnamed-chunk-71-1.pdf}
+In an example of a more complex influence of training variation,
+\autocite{braithwaiteEffectsVariationPrior2015} trained participants on
+example problems involving the concept of sampling with replacement
+(SWR). Training consisted of examples that were either highly similar in
+their semantic context (e.g.~all involving people selecting objects) or
+in which the surface features were varied between examples (e.g.~people
+choosing objects AND objects selected in a sequence). The experimenters
+also surveyed how much prior knowledge each participant had with SWR.
+They found that whether variation was beneficial depended on the prior
+knowledge of the participants -- such that participants with some prior
+knowledge benefited from varied training, whereas participants with
+minimal prior knowledge performed better after training with similar
+examples. The authors hypothesized that in order to benefit from varied
+examples, participants must be able to detect the structure common to
+the diverse examples, and that participants with prior knowledge are
+more likely to be sensitive to such structure, and thus to benefit from
+varied training. To test this hypothesis more directly, the authors
+conducted a 2nd experiment, wherein they controlled prior knowledge by
+exposing some subjects to a short graphical or verbal pre-training
+lesson, designed to increase sensitivity to the training examples.
+Consistent with their hypothesis, participants exposed to the structural
+sensitivity pre-training benefited more from varied training than the
+controls participants who benefited more from training with similar
+examples. Interactions between prior experience and the influence of
+varied training have also been observed in sensorimotor learning
+\autocite{guadagnoliRelationshipContextualInterference1999,delreyEffectsContextualInterference1982}.
+\textcite{delreyEffectsContextualInterference1982} recruited
+participants who self-reported either extensive, or very little
+experience with athletic activities, and then trained participants on a
+coincident timing task under with either a single constant training
+velocity, with one of several varied training procedures.
+Unsurprisingly, athlete participants had superior performance during
+training, regardless of condition, and training performance was superior
+for all subjects in the constant group. Of greater interest is the
+pattern of testing results from novel transfer conditions. Among the
+athlete-participants, transfer performance was best for those who
+received variable training. Non-athletes showed the opposite pattern,
+with superior performance for those who had constant training.
+
+\subsubsection{The current work}\label{the-current-work}
+
+The overarching purpose of this dissertation is to investigate the
+effects of training variability on learning and generalization within
+visuomotor skill learning and function learning. Our investigations is
+structured into two main projects, each employing distinct experimental
+paradigms and computational modeling frameworks to elucidate how and
+when variability in training enhances or impedes subsequent
+generalization.
+
+In Project 1, we investigated the influence of varied practice in a
+simple visuomotor projectile launching task. Experiments 1 and 2
+compared the performance of constant and varied training groups to
+assess potential benefits of variability on transfer to novel testing
+conditions. To account for the observed empirical effects, we introduced
+the Instance-based Generalization with Adaptive Similarity (IGAS) model.
+IGAS provides a novel computational approach for quantifying the
+similarity between training experiences and transfer conditions, while
+also allowing for variability to influence the generalization gradient
+itself.
+
+Project 2 shifted focus to the domain of function learning by employing
+a visuomotor extrapolation task. Across three experiments, we examined
+how constant and varied training regimes affected learning,
+discrimination between stimuli, and the ability to extrapolate to novel
+regions of the function's input space. To model human performance in
+this task, we fit the influential Associative Learning Model (ALM) and
+the Extrapolation-Association Model (EXAM) to individual participant
+data using advanced Bayesian parameter estimation techniques.
 

### 2024-04-12 Sections/full.qmd
adding more citations to intro

@@
 
-Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
+Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
 See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
@@
 Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
-
-# Introduction
-
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such transfer challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence transfer, and to develop cognitive models that can predict when transfer is likely to occur.
-The factor of interest to the present investigation is variation during training.
-Our experiments add to the longstanding empirical investigation of the controversial relationship between training variation, and subsequent transfer.
-We also offer a novel explanation for such results in the form of an instance-based model that accounts for the benefits of variation in simple terms of psychological similarity.
-We first review the relevant concepts and literature.
 

### 2024-04-12 Sections/Introduction.qmd
few more citations and language tweak

@@
 
-Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; but see @stewartEffectCategoryVariability2002 and @yangCategoryVariabilityEffect2014].
+Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
+@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002;  @yangCategoryVariabilityEffect2014 and @seitzModelingCategoryVariability2023].
 The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.

### 2024-04-12 Sections/Introduction.tex
update IGAS intro - then re-render everything

@@
 anagram completion \autocite{goodeSuperiorityVariableRepeated2008},
+perceptual learning
+\autocite{manentiVariabilityTrainingUnlocks2023,lovibondStimulusDiscriminabilityInduction2020,robsonSpecificVariedPractice2022a,zamanPerceptualVariabilityImplications2021},
 trajectory extrapolation
@@
 associative learning
-\autocite{leeEvidentialDiversityIncreases2019,reichmannVariabilityAbstractionEvaluative2023,fanStimulusDiversityIncreases2022,pradaExperiencedCategoryVariability2020},
+\autocite{leeEvidentialDiversityIncreases2019,reichmannVariabilityAbstractionEvaluative2023,fanStimulusDiversityIncreases2022,pradaExperiencedCategoryVariability2020,liveseyRevisitingPeakShift2019},
 visual search
@@
 
-Further observations consonant with the results of
-\textcite{cohenCategoryVariabilityExemplar2001} have since been observed
-in numerous investigations
-\autocites{hahnEffectsCategoryDiversity2005,perlmanFurtherAttemptsClarify2012,sakamotoPuttingPsychologyBack2008,hsuEffectsGenerativeDiscriminative2010}[but
-see][ and
-\textcite{yangCategoryVariabilityEffect2014}]{stewartEffectCategoryVariability2002}.
+Further observations of widened generalization following varied training
+have since been observed in numerous investigations
+\autocites{hahnEffectsCategoryDiversity2005,perlmanFurtherAttemptsClarify2012,sakamotoPuttingPsychologyBack2008,hsuEffectsGenerativeDiscriminative2010,hoschPriorExperienceVariability2023}[but
+see][]{stewartEffectCategoryVariability2002}[ and
+\textcite{seitzModelingCategoryVariability2023}]{yangCategoryVariabilityEffect2014}.
 The results of \textcite{sakamotoPuttingPsychologyBack2008} are

### 2024-04-12 Sections/full.qmd
update IGAS intro - then re-render everything

--- 2024-04-12 Sections/full.qmd
@@
 
-Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; but see @stewartEffectCategoryVariability2002 and @yangCategoryVariabilityEffect2014].
+Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
+@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002;  @yangCategoryVariabilityEffect2014; and @seitzModelingCategoryVariability2023].
 The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
@@
 
-Notions of similarity have long played a central role in many prominent models of generalization of learning, as well as in the longstanding theoretical issue of whether learners abstract an aggregate, summary representation, or if they simply store individual instances.
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar [@posnerGenesisAbstractIdeas1968].
-Prototype models were later challenged by the success of instance-based or exemplar models -- which were shown to provide an account of generalization as good or better than prototype models, with the advantage of not assuming the explicit construction of an internal prototype [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978;
-@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli.
+Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar.
+In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimuli.
+Recall that participants are trained on only on distortions of the category prototypes (e.g.
+low, medium or high distortions), never encountering the exact prototypes during the training stage.
+Then, in the testing phase, participants are tested with the prototype patterns, their old training items, and novel low, medium and high distortions.
+The authors found that participants had the highest testing accuracy for the previously unseen prototype patterns, followed by the old training items, and then the novel low, medium and high distortions.
+The authors interpreted this pattern as evidence that participants had acquired prototype representation of the category, as opposed to storing each individual training instance, and that generalization was based on the similarity of the testing items to the learned prototype representations.
+@posnerGenesisAbstractIdeas1968 has been extremely influential,  and continues to be cited in contemporary research as clear evidence that prototype abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
+However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992].
+@palmeriCentralTendenciesExtreme2001 demonstrated the both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
+These authors conducted a near replication of the @posnerGenesisAbstractIdeas1968 study, but also had participants provide similarity judgements of the dot pattern stimuli after completing the training phase.
+A multidimensional scaling analysis of the similarity judgements revelead that the psychological representations of the prototype stimuli were not located in the middle of the training stimuli, but were instead extreme points in the psychological space.
+The authors also demonstrated the generalization patterns of @posnerGenesisAbstractIdeas1968 could be accounted for by an exemplar-based model, without any need to assume the abstraction of a prototype.
+
+Instance-based, or exemplar-based models generally assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978; @nosofskyAttentionSimilarityIdentificationcategorization1986; @jamiesonInstanceTheoryDomaingeneral2022].
 As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
@@
 That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
+Instance-based similarity approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
 @crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
@@
 Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of similarity between previous and new experiences, a largely separate body of research has focused on improving transfer by manipulating characteristics of the initial training stage.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work -- variability of training examples.
-
-Research on the effects of varied training typically compares participants trained under constant, or minimal variability conditions to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015].
-Varied training has been shown to influence learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968], complex categorization [@nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019].
-Training variation has received a particularly large amount of attention within the domain of visuomotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-According to Schema Theory, learners possess general motor programs for classes of movements (e.g.
-throwing a ball with an underhand movement), as well as schema rules that determine how a motor program is parameterized or scaled for a particular movement.
-Schema theory predicts that varied training results in the formation of a more general schema-rule, which can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices from multiple levels of a task-relevant dimension that remains invariant for the constant group.
-For example, investigators might train two groups of participants to throw a projectile at a target, with a constant group that throws from a single location, and a varied group that throws from multiple locations.
-Both groups are then tested from novel locations.
-Empirically observed benefits of the varied-trained group are then attributed to the variation they received during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically thought to be mediated by the development of a more general schema for the throwing motion.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
 
@@
 Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
+However, even this level of experimental control may still be insufficient to rule out the effect of similarity on transfer.
+Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
 @fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.

### 2024-04-12 Sections/HTW.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

@@
 The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
 

### 2024-04-12 Sections/docx_test.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

--- 2024-04-12 Sections/full.qmd
@@
 ---
-title: Full Dissertation
+title: Full Dissertation2
 subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
-date: 04/04/24
+#date: 04/04/24
 author:
@@
   affiliation: Indiana University
-page-layout: full
-code-fold: true
-code-tools: true
-toc: true
-toc-location: body
-toc-title: Contents
-cache: true
+# page-layout: full
+# code-fold: true
+# code-tools: true
+# toc: true
+# toc-location: body
+# toc-title: Contents
+#cache: true
 execute: 
   warning: false
-  eval: true
+  eval: false
 format:
-  html: default
+  #html: default
   hugo-md:
@@
     html-math-method: mathjax
-    output-file: diss_full_hugo.md
+    output-file: diss_full_hugo22.md
   gfm:
@@
     output: false
-    output-file: diss_full_gfm.md
+    output-file: diss_full_gfm22.md
   hikmah-manuscript-pdf:
     echo: false
-    output-file: "tg_full_disser.pdf"
+    output-file: "tg_full_disser22.pdf"
     mainfont: "Linux Libertine O"
@@
     mathfont: "Libertinus Math"
-editor: 
-  markdown: 
-    wrap: 72
+  hikmah-manuscript-docx: 
+    output-file: "manuscript-ms2.docx"
+    echo: false
+    prefer-html: true
+    toc: false
 prefer-html: true
@@
 
-# Introduction
+# Abstract
 
@@
 Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
+
+This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
+A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
+Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
+To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
+These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
 
@@
 
-____________________________________________________
-
 ```{r}
@@
 It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
-However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992].
+However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
 @palmeriCentralTendenciesExtreme2001 demonstrated the both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
@@
 There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS_Testing1
-#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-IGAS_Table1
-#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- test=test[,1:3]
-
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
-
-In Experiment 1, we found that varied training resulted in superior testing performance than constant training, from both a position novel to both groups, and from the position at which the constant group was trained, which was novel to the varied condition.
-The superiority of varied training over constant training even at the constant training position is of particular note, given that testing at this position should have been highly similar for participants in the constant condition.
-It should also be noted, though, that testing at the constant trained position is not exactly identical to training from that position, given that the context of testing is different in several ways from that of training, such as the testing trials from the different positions being intermixed, as well as a simple change in context as a function of time.
-Such contextual differences will be further considered in the General Discussion.
-
-In addition to the variation of throwing position during training, the participants in the varied condition of Experiment 1 also received training practice from the closest/easiest position, as well as from the furthest/most difficult position that would later be encountered by all participants during testing.
-The varied condition also had the potential advantage of interpolating both of the novel positions from which they would later be tested.
-Experiment 2 thus sought to address these issues by comparing a varied condition to multiple constant conditions.
-
-# Experiment 2
-
-In Experiment 2, we sought to replicate our findings from Experiment 1 with a new sample of participants, while also addressing the possibility of the pattern of results in Experiment 1 being explained by some idiosyncrasy of the particular training location of the constant group relative to the varied group.
-To this end, Experiment 2 employed the same basic procedure as Experiment 1, but was designed with six separate constant groups each trained from one of six different locations (400, 500, 625, 675, 800, or 900), and a varied group trained from two locations (500 and 800).
-Participants in all seven groups were then tested from each of the 6 unique positions.
-
-## Methods
-
-### Participants
-
-A total of 306 Indiana University psychology students participated in Experiment 2, which was also conducted online.
-As was the case in experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18--22-year-old individuals.
-Using the same procedure as experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task.
-A total of 208 participants were included in the final analyses with 31 in the varied group and 32, 28, 37, 25, 29, 26 participants in the constant groups training from location 400, 500, 625, 675, 800, and 900, respectively.
-All participants were compensated with course credit.
-
-### Task and Procedure
-
-The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target.
-Additionally, the intermittent testing trials featured in experiment 1 were not utilized in experiment 2, and all training and testing trials were presented with feedback.
-An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
-
-The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group.
-In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training.
-Each of the constant groups thus experience one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
-
-## Results
-
-### Data Processing and Statistical Packages
-
-After confirming that condition and throwing position did not have any significant interactions, we standardized performance within each position, and then average across position to yield a single performance measure per participant.
-This standardization did not influence our pattern of results.
-As in experiment 1, we performed type III ANOVA's due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.
-The statistical software for the primary analyses was the same as for experiment 1.
-Individual learning rates in the testing phase, compared between groups in the supplementary analyses, were fit using the TEfit package in R [@cochraneTEfitsNonlinearRegression2020].
-
-### Training Phase
-
-The different training conditions trained from positions that were not equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is confirmation that some learning did occur.
-@fig-e2train depicts the training performance of the varied group alongside that of the aggregate of the six constant groups (5a), and each of the 6 separate constant groups (5b).
-An ANOVA comparison with training stage (beginning, middle, end) as a within-group factor and group (the varied condition vs.
-the 6 constant conditions collapsed together) as a between-subject factor revealed no significant effect of group on training performance, F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant interaction between group and training stage, F(2,412)=.489 p=.61, $\eta^{2}_G$ \<.01.
-We also tested for a difference in training performance between the varied group and the two constant groups that trained matching throwing positions (i.e., the constant groups training from position 500, and position 800).
-The results of our ANOVA on this limited dataset mirrors that of the full-group analysis, with no significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a significant effect of training stage F(2,172)=56.29, p\<.001, $\eta^{2}_G$ =.11, and no significant interaction between group and training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
-
-```{r}
-
-e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
-
-exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
-
-exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
-
-exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
-
-exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
-
-transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
-
-# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
-# novelAll <- novelAll %>% group_by(positionX) %>%
-#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
-novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
-
-constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
-variedTest <- transfer %>% filter(condit==7) # only varied testing
-variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
-
-variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
-constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
-variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
-
-exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-```
-
-```{r}
-#| label: fig-e2train
-#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
-On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 8
-
-### New - 3 stage
-e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
-  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
-  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
-
-e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
-  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
-
-#plot_grid(e2train1,e2train2,ncol=1)
-
-e2train1/e2train2
-
-```
-
-### Testing Phase
-
-In Experiment 2, a single varied condition (trained from two positions, 500 and 800), was compared against six separate constant groups (trained from a single position, 400, 500, 625, 675, 800 or 900).
-For the testing phase, all participants were tested from all six positions, four of which were novel for the varied condition, and five of which were novel for each of the constant groups.
-For a general comparison, we took the absolute deviations for each throwing position and computed standardized scores across all participants, and then averaged across throwing position.
-The six constant groups were then collapsed together allowing us to make a simple comparison between training conditions (constant vs.
-varied).
-A type III between-subjects ANOVA was performed, yielding a significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$ =.02.
-Descriptive statistics for each condition are shown in table 2.
-In @fig-e2testa visualizes the consistent advantage of the varied condition over the constant groups across the testing positions.
-@fig-e2testa shows performance between the varied condition and the individual constant groups.
-
-```{r}
-#| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 9
-
-# manuscript plot
-e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)+
-  ggtitle("A")
-
-e2test2<-exp2.Test7 %>% 
-  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
-  facet_wrap(~ThrowPosition4)+
-  ylab("Mean Distance From Center Of Target")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
-
-e2test1 / e2test2
-
-```
-
-\
-\
-\
-
-```{r}
-#| label: tbl-e2table1
-#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-
-tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab2=tab2[,1:3]
-
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-Next, we compared the testing performance of constant and varied groups from only positions that participants had not encountered during training.
-Constant participants each had 5 novel positions, whereas varied participants tested from 4 novel positions (400,625,675,900).
-We first standardized performance within in each position, and then averaged across positions.
-Here again, we found a significant effect of condition (constant vs.
-varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ = .02 .
-
-```{r}
-#| label: tbl-e2table2
-#| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-
-sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
- tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
- tab3 = tab3 %>% 
-   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab3=tab3[,1:3]
-
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
-
-Finally, corresponding to the comparison of position 760 from experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group).
-@fig-e2test1 displays the particular subset of comparisons utilized for this analysis.
-Again, we standardized performance within each position before performing the analyses on the aggregated data.
-In this case, the effect of condition did not reach statistical significance F(1,149)=3.14, p=.079, $\eta^{2}_G$ = .02.
-Table 4 provides descriptive statistics.
-
-```{r}
-#| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-
-sum.variedVsNovelIden <- variedVsNovelIden  %>%
-  group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
-
-e2Test2
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-e2tab3
-#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-
-tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
-tab4=tab4 %>% group_by(Condition) %>% 
-   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab4=tab4[,1:3]
-
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
-
-The results of experiment 2 largely conform to the findings of experiment 1.
-Participants in both varied and constant conditions improved at the task during the training phase.
-We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing [@soderstromLearningPerformanceIntegrative2015].
-However our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions.
-The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this pattern in a computerized task [@seowTransferEffectsVaried2019].
-One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
-Although this pattern has been observed elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
-
-# Computational Model
-
-*Controlling for the similarity between training and testing.* The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations.
-To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release.
-For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions.
-We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target.
-We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions -- thus resulting in six separate similarity scores for each participant.
-@fig-taskSpace visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions.
-As illustrated in @fig-taskSpace, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.
-
-```{r}
-#| label: fig-taskSpace
-#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig-width: 11
-#| fig-height: 9
-#| 
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
-  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
-
-library(patchwork)
-ss/fs
-
-```
-
-For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.
-The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient.
-Then, as per an instance-based model of similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value.
-The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.
-If c has a large value, then even a small difference between two throws' velocities greatly decreases the extent of generalization from one to the other.
-A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities.
-The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions.
-The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.
-
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
-
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-
-A simple linear regression revealed that these similarity scores were significantly predictive of performance in the transfer stage, t =-15.88, p\<.01, $r^2$=.17, such that greater similarity between training throws and solution spaces for each of the test locations resulted in better performance.
-We then repeated the group comparisons above while including similarity as a covariate in the model.
-Comparing the varied and constant groups in testing performance from all testing positions yielded a significant effect of similarity, F(1, 205)=85.66, p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition (varied vs.
-constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03.
-The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$ =.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$ =.07.
-For all comparisons, the pattern of results was consistent with the initial findings from experiment 2, with the varied group still performing significantly better than the constant group.
-
-## Fitting model parameters separately by group
-
-To directly control for similarity in Experiment 2, we developed a model-based measure of the similarity between training throws and testing conditions.
-This similarity measure was a significant predictor of testing performance, e.g., participants whose training throws were more similar to throws that resulted in target hits from the testing positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level benefits of varied training, which remained significant in our linear model predicting testing performance after similarity was added to the model.
-However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
-Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
-Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
-One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
-If one's training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
-Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c, to varied and constant participants.
-To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
-
-Both models generate distinct similarity values between training and testing locations.
-Much like the analyses in Experiment 2, these similarity values are regressed against testing performance in models of the form shown below.
-As was the case previously, testing performance is defined as the mean absolute distance from the center of the target (with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p\<.01).
-Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the c parameter separately between groups (Similarity2c).
-In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p\<.01), with the varied group still performing significantly better.
-However, in linear model 4 the addition of the Similarity2c predictor results in the effect of training group becoming nonsignificant (p=.40), suggesting that the effect of varied vs.
-constant training is accounted for by the Similarity2c predictor.
-Next, to further establish a difference between the models, we performed nested model comparisons using ANOVA, to see if the addition of the training group parameter led to a significant improvement in model performance.
-In the first comparison, ANOVA(Linear Model 1, Linear Model 2), the addition of the training group predictor significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear Model 4) found no improvement in model performance with the addition of the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the adjusted Similarity2c model had more predictive power than those generated from the original Similarity1c model.
-Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
-The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
-Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which assumes equivalent generalization gradients between constant and varied trained participants is unable to account for the extent of benefits of varied over constant training observed at testing.
-The evidence for this in the comparative model fits is that when a varied/constant dummy-coded variable for condition is explicitly added to the model, the variable adds a significant contribution to the prediction of test performance, with the variable condition yielding better performance than the constant conditions.
-However, if the instance-based generalization model is modified to assume that the training groups can differ in the steepness of their generalization gradient, by incorporating a separate generalization parameter for each group, then the instance-based model can account for our experimental results without explicitly taking training group into account.
-Henceforth this model will be referred to as the Instance-based Generalization with Adaptive Similarity (IGAS) model.
-
-# General Discussion
-
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing task.
-Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
-However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions.
-We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978].
-In experiment 1 varied participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
-Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
-Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
-Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
-A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
-The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
-In this fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained.
-Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in @fig-Toy-Model-dis we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern.
-In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model -- namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model-dis
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
-For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
-The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
-#| fig.width: 11
-#| fig.height: 11.5
-
-#
-
-p=2
-c<- .000002
-
-trainingTestingDifference=2000;
-cvaried=.00002
-cconstant=.0005
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
-                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
-                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
-                            ) %>% 
-  group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
-
-#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
-
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
-ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
-ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
-ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
-# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
-
-#gtitle="Figure 9."
-#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-p1 <- (ip1+ip2) / (ip3+ip4)
-
-p1
-
-```
-
-As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
-However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning implementations of instance-based models in several ways.
-One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g.
-size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
-movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
-Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
-Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
-Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
-A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].
-In this task, participants observe a series of lamps lighting up consecutively, and attempt to time a button press with the onset of the final lamp.
-The design consisted of four separate constant groups, each training from a single lighting velocity, and a single varied group training with all four of the lighting velocities used by the individual constant groups.
-Participants were then split into four separate testing conditions, each of which were tested from a single novel lighting velocity of varying distance from the training conditions.
-The result of primary interest was that all participants performed worse as the distance between training and testing velocity increased -- a typical generalization decrement.
-However, varied participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are similar to our own, our work is novel in that we account for our results with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their separate constant groups together may result in similarity confounds between varied and constant conditions that leaves their study open to methodological criticisms, especially in light of related work which demonstrated that the extent to which varied training may be beneficial can depend on whether the constant group they are compared against trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987].
-Our study alleviates such concerns by explicitly controlling for similarity.
-
-## Limitations
-
-A limitation of this study concerns the ordering of the testing/transfer trials at the conclusion of both experiments.
-Participants were tested from each separate position (4 in Experiment 1, 6 in Experiment 2) in a random, intermixed order.
-Because the varied group was trained from two positions that were also randomly ordered, they may have benefited from experience with this type of sequencing, whereas the constant groups had no experience with switching between positions trial to trial.
-This concern is somewhat ameliorated by the fact that the testing phase performance of the constant groups from their trained position was not significantly worse than their level of performance at the end of the training phase, suggesting that they were not harmed by random ordering of positions during testing.
-It should also be noted that the computerized task utilized in the present work is relatively simple compared to many of the real-world tasks utilized in prior research.
-It is thus conceivable that the effect of variability in more complex tasks is distinct from the process put forward in the present work.
-An important challenge for future work will be to assess the extent to which IGAS can account for generalization in relatively complex tasks with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987].
-Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
-In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
-However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
-## Conclusion
-
-Our experiments demonstrate a reliable benefit of varied training in a simple projectile launching task.
-Such results were accounted for by an instance-based model that assumes that varied training results in the computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable approach towards better understanding skill generalization and transfer.
-
-{{< pagebreak >}}
-
-# Project 2
-
-_______________________________________________________________________________
-
-# Introduction
-
-A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
-One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ].
-The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
-
-## Function Learning and Extrapolation
-
-The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
-
-@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
-Input stimuli and output responses were both lines of varying length.
-The correct output response was related to the length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
-@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
-Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
-In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
-All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
-
-The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
-The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models.
-The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
-The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
-When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
-
-### Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
-
-```{r}
-#| label: fig-delosh-extrap
-#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
-#| echo: false
-#| fig-width: 10
-#| cache: false 
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-source(here::here("Functions","deLosh_data.R"))
-#source(here::here("Functions","Display_Functions.R"))
-
-extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
-                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
-
-linear_function <- function(x) 2.2 * x + 30
-exponential_function <- function(x) 200 * (1 - exp(-x/25))
-quadratic_function <- function(x) 210 - (x - 50)^2 / 12
-
-linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
-    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
-  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
-
-exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
-  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
-  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
-  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
-  extrapLines +
-  scale_shape_manual(values = c(1)) +
-  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
-  theme(legend.title = element_blank(), legend.position="top") +
-  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
-                                                  linetype = c(0, 1))))
-
-quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
-  geom_point( shape = 1) +
-  stat_function( fun = quadratic_function, geom = "line") +
-  labs(title="Quadratic Function",x="",y="") + extrapLines
-
-linear_plot + exponential_plot + quadratic_plot
-```
-
-## Overview Of Present Study
-
-The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
-To the best of our knowledge, this research is the first to employ the classic constant vs.
-varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
-Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
-
-To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
-Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.
-
-## Methods
-
-*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
-Participants were randomly assigned to one of two training conditions: varied training or constant training.
-
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
-band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
-Participants were instructed that only the x velocity component of the ball was relevant to the task.
-The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
-
-/
-```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
-#| label: fig-htw-task
-#| fig-cap: The Hit the wall task.
-Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
-The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
-#| eval: true
-#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
-knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
-
-```
-
-*Procedure.* All participants completed the task online.
-Participants were provided with a description of the experiment and indicated informed consent.
-@fig-design-e1 illustrates the general procedure.
-Participants completed a total of 90 trials during the training stage.
-In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
-
-Following the training stage, participants proceeded immediately to the testing stage.
-Participants were tested from all six velocity bands, in two separate stages.
-In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
-In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
-A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
-
-::: {.content-visible unless-format="markdown"}
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| echo: false  
-///| eval: !expr out_type 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-```
-:::
-
-```{r}
-
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e1 <- readRDS(here("data/e1_08-21-23.rds")) 
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-testE1 <- e1 |> filter(expMode2 == "Test")
-nbins=5
-trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
-trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
-```
-
-### Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.32 @rcoreteamLanguageEnvironmentStatistical2020.
-To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
-Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
-Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
-For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
-
-| Group Comparison         | Code                                                        | Data                 |
-| ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
-\
-
-In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
-extrapolation bands); 3) extent of discrimination between all six testing bands.
-We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
-Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
-The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
-Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-### Results
-
-```{r}
-#| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-##| label: tbl-e1-train-dist
-##| tbl-cap: "Experiment 1 - Learning curves. "
-##| output: asis
-
-bmm_e1_train<- trainE1_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e1_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#    kable(booktabs = TRUE)
-
-cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
-```
-
-::: {#tbl-e1-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
-| conditVaried |    79.64 |         57.92 |        101.63 |   1 |
-
-: **Experiment 1 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band.
-To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on.
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
-
-```{r}
-##| label: tbl-e1-bmm-dist
-##| tbl-cap: "E1. Training vs. Extrapolation"
-#| 
-modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
-bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE1, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-# 
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-
-# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
-cdted1 <- get_coef_details(bmtd, "conditVaried")
-cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
-cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e1-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:------------------------|-----------:|-----------:|-----------:|-----------:|
-| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
-| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
-| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
-| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |
-
-: **Experiment 1 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficients  indicate larger deviations from the baselines (Condition=constant & bandType=Trained) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-
-*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
-constant) and band type (trained vs.
-extrapolation), with random intercepts for participants and bands.
-The model results are shown in @tbl-e1-bmm-dist.
-The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`).
-The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`).
-Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% credible intervals.
-
-pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-
-```
-
-```{r}
-##| label: tbl-e1-bmm-vx
-##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)
-
-cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e1_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-```
-
-\
-
-::: {#tbl-e1-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
-| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
-| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
-| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |
-
-Experiment 1.
-Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
-Varied) and Velocity Band.
-Larger coefficients on Band represent greater sensitivity/discrimination.
-{.striped .hover .sm}
-:::
-
-Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
-Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
-This difference is depicted visually in @fig-e1-test-vx.
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: Empirical distribution of velocities producing in testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-
-testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
-#| fig-cap: Experiment 1.
-Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE1$vb), 
-                     limits = c(0, 1400)) + 
-  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e1_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e1Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-     theme(legend.title=element_blank(), 
-           axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-## E1 Summary
-
-In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions  rresulted in lower final training performance is consistent with much of the prior researchon the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
-
-More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.
-
-## Experiment 2
-
-```{r}
-
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e2 <- readRDS(here("data/e2_08-04-23.rds")) 
-e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
-testE2 <- e2 |> filter(expMode2 == "Test")
-nbins=5
-trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
-
-# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
-```
-
-### Methods & Procedure
-
-The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
-The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800.
-Both groups were tested from all six bands.
-A total of 110 participants completed the experiment (Varied: 55, Constant: 55).
-
-::: {.content-visible unless-format="markdown"}
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 8.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| echo: false 
-//| 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
-
-:::
-
-### Results
-
-```{r}
-#| label: fig-e2-train-dev
-#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-#| eval: TRUE
-p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-bmm_e2_train <- trainE2_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e2_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
-# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T) 
-```
-
-::: {#tbl-e2-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
-| conditVaried |    36.15 |         16.35 |         55.67 |   1 |
-
-: **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups.
-We again compared training performance on the band common to both groups (600-800).
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
-```{r}
-modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
-bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE2, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
-cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
-cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e2-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-----------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
-| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
-| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
-| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |
-
-: **Experiment 2 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
-:::
-\ \
-
-*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
-Constant) and band type (training vs.
-extrapolation bands).
-The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`).
-However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-#| eval: TRUE
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e2-bmm-vx
-##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
-
-cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
-sc2 <- get_coef_details(e2_vxBMM, "bandInt")
-intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
-```
-
-::: {#tbl-e2-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
-| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
-| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
-| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
-
-Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
-:::
-
-*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-The full model results are shown in @tbl-e2-bmm-vx.
-The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
-The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).
-
-```{r}
-#| label: fig-e2-test-vx
-#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e2-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
-#| fig-width: 11
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-}
-
-pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE2$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e2_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e2Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-      theme(legend.title=element_blank(), 
-        axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-### Experiment 2 Summary
-
-Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands.
-Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.
-
-## Experiment 3
-
-```{r}
-
-e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
-    mutate(trainCon=case_when(
-    bandOrder=="Original" ~ "800",
-    bandOrder=="Reverse" ~ "600",
-    TRUE ~ NA_character_
-    ), trainCon=as.numeric(trainCon)) 
-e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
-testE3 <- e3 |> filter(expMode2 == "Test")
-nbins=5
-trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
-
-```
-
-### Methods & Procedure
-
-The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
-After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.
-within the target velocity range).
-All other aspects of the task and design are identical to Experiments 1 and 2.
-We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied).
-Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
-Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.
-
-### Results
-
-```{r}
-
-bmm_e3_train <- trainE3_max %>% 
-  brm(dist ~ condit*bandOrder, 
-      file=here("data/model_cache/e3_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
-cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
-cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
-```
-
-::: {#tbl-e3-train-dist}
-
-| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
-| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
-| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
-| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |
-
-: **Experiment 3 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
-
-:::
-
-*Training*.
-@fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions).
-The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`).
-The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).
-
-```{r}
-#| label: fig-e3-train-dev
-#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
-#| eval: true
-p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
-p1
-```
-
-```{r}
-#options(brms.backend="cmdstanr",mc.cores=4)
-modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
-bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
-    data=testE3, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
-#wrap_plots(ce_bmtd3)
-
-#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")
-
-cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
-cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
-cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
-cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
-cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
-cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
-cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")
-
-```
-
-::: {#tbl-e3-bmm-dist}
-| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
-| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
-| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
-| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
-| conditVaried:bandTypeExtrapolation                  |    52.66 |         14.16 |         90.23 | 1.00 |
-| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
-| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
-| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |
-
-: **Experiment 3 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-The Intercept represents the baseline condition, (constant training;  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
-Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
-{.striped .hover .sm}
-:::
-
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
-There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
-However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`.
-The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group.
-There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands.
-No other interactions were significant.
-
-<!-- ::: {#fig-e3-test-condEffect}
-
-![](../Assets/figs/e3_cond_effects_dist.png)
-
-E3.
-A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-::: -->
-
-```{r}
-#| label: fig-e3-test-dev
-#| fig-cap: Experiment 3 Testing Accuracy.
-A) Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% confidence intervals.
-#| eval: true
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-    facet_wrap(~bandOrder,ncol=1) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
- facet_wrap(~bandOrder,ncol=1)
-
-p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e3-bmm-vx
-##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
-# m2 <- fixef(e3_vxBMM)
-# mp3 <- m1[, c(1,2,4,5,6)]
-# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
-# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
-coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")
-
-```
-
-::: {#tbl-e3-bmm-vx}
-
-| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
-| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
-| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
-| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |
-
-Experiment 3.
-Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs.
-Varied) and Velocity Band.
-The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the linear slope for the baseline condition.
-.hover .sm}
-:::
-
-*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist.
-For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
-The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
-Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
-However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating that the varied condition showed a greater slope coefficient on the reverse order bands, compared to the constant condition - this is clearly shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 10
-##| column: screen-inset-right
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-```
-
-```{r}
-#| label: fig-e3-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 10
-#| fig-width: 11
-##| eval: FALSE
-# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  facet_wrap(~bandOrder,ncol=1) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e3_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
-fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
-fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
-
-re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e3Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
-           fixed_effect_interaction2*(bandOrder=="Reverse") + 
-           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
-  slope = Estimate + adjust )
-
-pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density") +
-  facet_wrap(~bandOrder,ncol=1)
-
-pid_slopes3 <- re |>  
-    mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-    theme(legend.title=element_blank(), 
-      axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
-
-p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
-
-#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
-p3
-
-```
-
-### Experiment 3 Summary
-
-In Experiment 3, we investigated the effects of training condition (constant vs.
-varied) and band type (training vs.
-extrapolation) on participants' accuracy and discrimination during the testing phase.
-Unlike the previous experiments, participants received ordinal feedback during the training phase.
-Additionally, Experiment 3 included both the original order condition from Experiment 1 and the reverse order condition from Experiment 2.
-The results revealed no significant main effects of training condition on testing accuracy, nor was there a significant difference between groups in band discrimination.
-However, we observed a significant three-way interaction for the discrimination analysis, indicating that the varied condition showed a steeper slope coefficient on the reverse order bands compared to the constant condition.
-This result suggests that varied training enhanced participants' ability to discriminate between velocity bands, but only when the band order was reversed during testing.
-
-## Computational Model
-
-```{r}
-####| cache: false
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-```
-
-```{r}
-###| cache: true
-invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
-invisible(list2env(load_e1(), envir = .GlobalEnv))
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-e2_model <- load_e2()
-e3_model <- load_e3()
-options(contrasts = initial_contrasts)
-
-```
-
-```{r}
-#| label: fig-alm-diagram
-#| fig.cap: The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model as used in the present work.
-Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
-The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
-The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule.
-alm_plot()
-```
-
-# Modeling Approach
-
-The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997].
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.
-
-## ALM & Exam Description
-
-ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
-EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
-Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
-EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
-The slope is then used to extrapolate the response to the novel test stimulus.
-Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
-We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
-This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
-
-See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
-
-::: column-page-inset-right
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-|                    | **EXAM Extrapolation**                                             |                                                                                               |
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
-| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |
-
-: ALM & EXAM Equations {#tbl-alm-exam}
-:::
-
-## Model Fitting
-
-To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
-We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant.
-The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
-Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.
-
-::: {.callout}
-
-**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
-
-To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
-ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
-Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g.
-many neural network models).
-
-The general ABC procedure is to 1) define a prior distribution over model parameters.
-2) sample candidate parameter values, $\theta^*$, from the prior.
-3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
-4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
-5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
-6) Repeat until desired number of posterior samples are obtained.
-
-Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
-For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
-For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
-For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
-After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
-For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
-
-::: column-page-inset-left
-$$
-discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
-$$ {#eq-discrep-test}
-
-$$
-\begin{aligned} \\
-discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
-discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
-\end{aligned}
-$$ {#eq-discrep-train}
-:::
-
-The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
-The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
-Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
-Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
-The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
-Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
-After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
-In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
-To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
-:::
-
-For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution.
-Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant.
-Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs.
-To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.
-
-### Modelling Results
-
-#### Group level Patterns
-
-```{r}
-#| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-post_tabs <- abc_tables(post_dat,post_dat_l)
-train_tab <- abc_train_tables(pd_train,pd_train_l)
-
-e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
-
-e1_tab %>%
-  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
-  summarize(ME = mean(mean_error), .groups = "drop") %>%
-  pivot_wider(
-    names_from = c(Model, condit),
-    values_from = ME,
-    names_sep = "_"  # Add this line to specify the separator for column names
-  ) %>%
-  rename("Fit Method" = Fit_Method) %>%
-  gt() %>%
-  cols_move_to_start(columns = c(`Task Stage`)) %>%
-  cols_label(
-    `Task Stage` = "Task Stage"
-  ) %>%
-  fmt_number(
-    columns = starts_with("ALM") | starts_with("EXAM"),
-    decimals = 2
-  ) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = cell_fill(color = "white"),
-     locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_style(
-    style = cell_borders(sides = "top", color = "black", weight = px(1)),
-    locations = cells_column_labels()
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10, 
-    quarto.disable_processing = TRUE
-  ) 
-```
-
-```{r}
-#| label: fig-htw-post-dist
-#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters.
-Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y axes of the plots for the c parameter are scaled logarithmically."
-#| fig-height: 6
-#| fig-width: 10
-
-c_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
-  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
-
-lr_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
-  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
-c_post + lr_post
-```
-
-```{r}
-#| label: fig-htw-resid-pred
-#| fig-cap: "Model residuals for each combination of training condition, fit method, and model.
-Residuals reflect the difference between observed and predicted values.
-Lower values indicate better model fit.
-Note that y axes are scaled differently between facets.
-A) Residuals predicting each block of the training data.
-B) Residuals predicting each band during the testing stage.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-#| fig-height: 14
-#| fig-width: 11
-
-train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
-  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
-  group_by(id,condit,Model,Fit_Method,Block) |>
-  summarise(mean_error=mean(mean_error)) |>
-  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
-  stat_bar + 
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
-   scale_x_discrete(guide = "axis_nested") +
-  scale_fill_manual(values=c("gray10","gray50","gray92"))+
-  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
-  theme(legend.position="top")
-
-test_resid <-  post_dat |> 
-   group_by(id,condit,x,Model,Fit_Method,bandType) |>
-    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
-  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
-  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
-  scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
-  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")
-
-(train_resid / test_resid) +
-  #plot_layout(heights=c(1,1.5)) & 
-  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
-```
-
-The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat.
-There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences.
-The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
-
-We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model.
-Aggregated residuals are displayed in @fig-htw-resid-pred.
-The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method .
-Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms).
-The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models.
-It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task.
-Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories.
-However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data.
-All subsequent analyses and discussion will thus focus on the testing stage.
-
-The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots).
-Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
-The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models.
-Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.
-
-```{r}
-#| label: fig-cm-vx-pat
-#| fig-cap: "Empirical data and Model predictions for mean velocity across target bands.
-Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs.
-Varied) are separated by columns.
-Each facet contains the predictions of ALM and EXAM, alongside the observed data."
-#| fig-height: 10
-#| fig-width: 10
-
-post_dat_l |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> 
- #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
- ggplot(aes(x=Resp,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-    facet_wrap(~rename_fm(Fit_Method)+condit, ncol=2,strip.position = "top", scales = "free_x") +
-        scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-         strip.background = element_blank(),
-         strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(10,0,0,0), "pt")) + 
-         labs(title="Model Predictions - Experiment 1 Data", y="Vx")
-```
-
-```{r}
-#| label: fig-ee-e1
-#| fig-caption: conditional and marginal effects
-#| fig-height: 8
-#| fig-width: 10
-###| eval: false
-
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
-  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
-e1_ee_brm_ae <- brm(data=pdl,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-
-# plot_custom_effects <- function(model) {
-#   # Extract posterior samples for fixed effects
-#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
-
-#   # Calculate conditional effects
-#   post_samples <- post_samples %>%
-#     mutate(
-#       ALM_Constant = b_Intercept,
-#       EXAM_Constant = b_Intercept + b_ModelEXAM,
-#       ALM_Varied = b_Intercept + b_conditVaried,
-#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
-#     )
-
-#   # Reshape data for plotting
-#   plot_data <- post_samples %>%
-#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
-#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
-#     separate(Condition, into = c("Model", "Condit"), sep = "_")
-
-#   # Plot conditional effects
-#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
-#     geom_boxplot() +
-#     theme_minimal() +
-#     labs(x = "Model", y = "Estimate", color = "Condition")
-# }
-# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
-
-bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
-bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
-bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")
-
-posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
-  select(starts_with("b_")) %>%
-  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))
-
-constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
-varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
-comparison_EXAM <- constant_EXAM - varied_EXAM
-summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
-
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)
-
-# full set of Model x condit contrasts
-# ALM - EXAM
-# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
-#   pluck("contrasts") |> 
-#   gather_emmeans_draws() |> 
-#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
-
-# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()
-
-# Constant - Varied
-# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
-# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
-#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
-# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
-
-p_em_1 <- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
-  pluck("contrasts") |>
-  gather_emmeans_draws() |> 
-  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
-  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
-  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")
-
-p_ce_1 / p_em_1
-```
-
-To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
-EXAM) and training condition (Constant vs.
-Varied).
-
-Model errors were significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM.
-There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group.
-To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
-The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
-
-```{r}
-#| label: tbl-htw-modelError-e23
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-
-post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
-train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
-
-pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e2_tab <- rbind(post_tabs2$agg_pred_full |>
- mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
- mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
-train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
-
-pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e3_tab <- rbind(post_tabs3$agg_pred_full |> 
-  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
-gt_table <- e23_tab %>%
-  pivot_wider(
-    names_from = c(Exp, Model, condit),
-    values_from = mean_error,
-    names_glue = "{Exp}_{Model}_{condit}"
-  ) %>%
-  arrange(Fit_Method, `Task Stage`) %>%
-  gt() %>%
-  cols_move_to_start(columns = `Task Stage`) %>%
-  cols_label(`Task Stage` = "Task Stage") %>%
-  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = list(
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_options(
-    column_labels.font.size = 10,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
-  ) 
-gt_table
-```
-
-```{r}
-#| label: fig-cm-vx-pat-e2-e3
-#| fig-height: 8
-#| fig-width: 10
-#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage.
-Observed data is shown on the right.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-
-rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
- e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
-  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
-  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
-  stat_bar + 
-    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
-    scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .7), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-        #  strip.background = element_blank(),
-        #  strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(20,0,0,0), "pt")) + 
-         labs(title="Model Predictions Experiment 2 & 3", y="vx")
-```
-
-```{r}
-#| label: tbl-htw-ee-e23
-#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and the interaction between Model and Condition.
-The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
-The intercept reflects the baseline of ALM and Constant.
-The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
-Lower values indicate better model fit."
-
-e2_ee_brm_ae <- brm(data=pdl2,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
-bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
-bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
-
-bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
-
-e3_ee_brm_ae <- brm(data=pdl3,
-  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
-bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
-bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
-bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
-
-bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
-               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
-  relocate(exp, .before=Term)
-
-bct_table <- bct %>%
-  mutate(
-    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
-    pd = round(pd, 2)
-  ) %>%
-  gt() %>%
-  # tab_header(
-  #   title = "Bayesian Model Results",
-  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
-  # ) %>%
-  cols_label(
-    exp = "Experiment",
-    Term = "Term",
-    Estimate = "Estimate",
-    `95% CrI Lower` = "95% CrI Lower",
-    `95% CrI Upper` = "95% CrI Upper",
-    pd = "pd"
-  ) %>%
-  fmt_number(
-    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
-    decimals = 2
-  ) %>%
-  fmt_number(
-    columns = pd,
-    decimals = 2
-  ) %>%
-  tab_spanner(
-    label = "Credible Interval",
-    columns = c(`95% CrI Lower`, `95% CrI Upper`)
-  ) %>%
-  tab_style(
-    style = list(
-      #cell_fill(color = "lightgray"),
-      cell_text(weight = "bold"), 
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(
-      columns = c(Estimate, pd),
-      rows = Term=="ModelEXAM:conditVaried"
-    )
-  ) %>%
-   tab_row_group(
-    label = "Experiment 3",
-    rows = exp == "Exp 3"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 2",
-    rows = exp == "Exp 2"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 1",
-    rows = exp == "Exp 1"
-  ) %>%
-  tab_options(
-    table.font.size = 10,
-    heading.title.font.size = 16,
-    heading.subtitle.font.size = 14,
-    quarto.disable_processing = TRUE
-    #row_group.background.color = "gray95"
-  )
-bct_table
-
-```
-
-*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
-For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
-The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
-The Bayesian regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
-The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
-Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
-Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
-We thus also controleld for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
-There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
-
-```{r}
-#| label: fig-e2_e3_ae
-#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied) on Model Error for Experiment 2 and 3 data.
-Experiment 3 also includes a control for the order of training vs.
-testing bands (original order vs.
-reverse order)."
-#| fig-height: 6
-#| fig-width: 9
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
-p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-  p_e2 <- (p1 + p2+ p3) 
-# #wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
-                         effects = "Model:condit", 
-                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
-     points=FALSE,plot=FALSE)$`Model:condit` + 
-     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
-     theme(legend.position="right") + 
-     scale_color_manual(values=wes_palette("Darjeeling1"))
-
-p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- p2 <- (p1 + p2+ p3)
- (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-```
-
-*Computational Model Summary*.
-Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23).
-This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group.
-It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model.
-A subset of these participants are shown in @fig-htw-indv-pred.
-
-```{r}
-#| label: fig-htw-best-model
-#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
-#| fig-height: 12
-#| fig-width: 11
-
-tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
-  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
-  filter(Fit_Method=="Test_Train") |>
-  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
-    mutate(e2=abs(y-pred)) |> 
-    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
-    group_by(id,condit,Model,Fit_Method,Exp) |> 
-    summarise(mean_error=mean(mean_error)) |> 
-    arrange(id,condit,Fit_Method) |>
-    round_tibble(1)
-
-best_id <- tid1 |> 
-  group_by(id,condit,Fit_Method) |> 
-  mutate(best=ifelse(mean_error==min(mean_error),1,0))
-
-lowest_error_model <- best_id %>%
-  group_by(id, condit,Fit_Method, Exp) %>%
-  summarise(Best_Model = Model[which.min(mean_error)],
-            Lowest_error = min(mean_error),
-            differential = min(mean_error) - max(mean_error)) %>%
-  ungroup()
-
-error_difference<- best_id %>%
-  select(id, condit, Model,Fit_Method, mean_error) %>%
-  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
-  mutate(Error_difference = (ALM - EXAM))
-
-full_comparison <- lowest_error_model |> 
-  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
-  group_by(condit,Fit_Method,Best_Model) |> 
-  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
-  arrange(Fit_Method,-Error_difference)
-
-full_comparison |> 
-  filter(Fit_Method=="Test_Train") |> 
-  ungroup() |>
-  mutate(id = reorder(id, Error_difference)) %>%
-  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
-  geom_col() +
-  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
-  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
-  theme(axis.text.y = element_text(size=8)) +
-  labs(fill="Best Model",
-  x="Mean Model Error Difference (ALM - EXAM)",
-  y="Participant")
-
-```
-
-```{r  fig.width=11, fig.height=10}
-#| label: fig-htw-indv-pred
-#| fig-cap: Model predictions alongside observed data for a subset of individual participants.
-A) 3 constant and 3 varied participants fit to both the test and training data.
-B) 3 constant and 3 varied subjects fit to only the trainign data.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands.
-#| fig-height: 7
-#| fig-width: 10
-
-cId_tr <- c(137, 181, 11)
-vId_tr <- c(14, 193, 47)
-cId_tt <- c(11, 93, 35)
-vId_tt <- c(1,14,74)
-cId_new <- c(175, 68, 93, 74)
-# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")
-
-e1_sbjs <- c(49,68,155, 175,74)
-e3_sbjs <-  c(245, 280, 249)
-e2_sbjs <- c(197, 157, 312, 334)
-cFinal <- c(49, 128,202 )
-vFinal <- c(68,70,245)
-
-indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
-  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
-  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))
-
-testIndv <- indv_post_l |> 
-#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
-   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
-  group_by(id,condit,Fit_Method,Model,Resp) |>
-   mutate(flab=paste0("Subject: ",id)) |>
-  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar_sd + 
-  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
-  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
-  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
-  labs(title="Individual Participant fits from Test & Train Fitting Method",
-       y="X Velocity",fill="Target Velocity") +
-   guides(fill = guide_legend(nrow = 1)) + 
-  theme(legend.position = "bottom",axis.title.x = element_blank())
-
-testIndv 
-```
-
-## Project 2 Discussion
-
-*Experimental Result Summary*
-
-Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
-
-In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
-The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.
-
-Experiment 2 extended these findings by reversing the order of the training and testing bands.
-Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases.
-However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.
-
-In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments.
-Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied).
-The varied condition showed larger deviations at the end of training, consistent with the previous experiments.
-Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition.
-During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands.
-The reverse order conditions showed smaller deviations compared to the original order conditions.
-Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.
-
-All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015].
-The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group.
-Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.
-
-Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
-Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
-A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
-These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study.
-@vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
-However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
-
-*Modeling Summary*
-EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group.
-May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule.
-But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval.
-The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
-
-*Limitations*
-
-While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
-First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
-Such a difference may be an unavoidable consequence of varied vs.
-constant design which match the total number of training trials between the two groups.
-However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
-Another limitation is that the testing stage did not include any interpolation items, i.e.
-the participants tested only from the training bands they experienced during training, or from extrapolation bands.
-The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
-Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
-Finally, the task employed in the present study consisted of only a linear, positive function.
-Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
-It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
-
-# General Discussion
-
-To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
-
-### Empirical and Modeling Summary
-
-Across both projects, we investigated the influence of training variability on learning and generalization in computerized visuomotor skill learning, and function learning tasks.
-In project 1 (HTT), experiments 1 and 2 demonstrated that varied training led to superior testing performance compared to constant training.
-In Experiment 1, the varied group even outperformed the constant group even when testing from the constant groups trained position.
-In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of training accuracy, accuracy in extrapolation testing,  and, in a subset of the experiments, the varied group showed a diminished ability to discriminate between bands.
-This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
-
-Both projects also included computational modeling componenents.
-In Project 1, the IGAS model was introduced as a means of addressing the lack of control for similarity between training and testing conditions common to previous work in the "benefits of variability" literature.
-The IGAS model provides a theoretically motivated method of quantifying the similarity between training experience and testing conditions.
-The resulting similarity metric (i.e.
-our 1c-similarity) is shown to be a significant predictor of testing performance on its own, and when added as a covariate to the statistical model used to compare the constant and varied training groups.
-We then showed the group-level effect of training variability on testing performance can be accounted for with the additional assumption that training variability influences the generalization gradient.
-The contribution of the IGAS model was thus twofold:  1) providing a theoretically justifiable method of quantifying/controlling for similarity between training and testing, and 2) demonstrating the viability of a flexible-similarity based generalization account for the empirically observed benefit of variability in our task.
-Although similar approaches have been employed in other domains, both contributions are novel additions to the large body of research assessing the effect of constant vs.
-varied training manipulations in visuomotor skill tasks.
-
-Although theoretically motivated, the IGAS model of Project 1 is best categorized as a descriptive measurement-model.
-Sufficient to account for group differences, but lacking the machinery necessary to provide a full process-level account of how the empirical quantities of interest are generated.
-In contrast, Project 2 (HTW) implemented a more robust computational modeling approach, implementing and comparing full process models (ALM & EXAM), capable of generating predictions for both the learning and testing stages of the experiment.
-ALM and EXAM have been used as models of function learning, cue judgement, and forecasting behavior in numerous studies over the past 25 years [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @brownUnderestimationLinearFunction2017; @kwantesItemOrderMatters2012; @kelleyComparisonModelsLearning2008; @kaneApplicationsBiasVariance2020; @vonhelversenLearningMultiplecueJudgment2010].
-The present work presents the first application of these models to to the study of training variability in a visuomotor function learning task.
-We fit both models to individual participant data, using a form of simulation-based bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
-EXAM provided the best overall account of the testing data, and the advantage of EXAM over ALM was significantly greater for the constant group.
-Notably, EXAM captured the constant groups' ability to extrapolate linearly to novel velocity bands, despite receiving training from only a single input-output pair.
-This finding suggests that EXAM's linear extrapolation mechanism, combined with the assumption of prior knowledge about the origin point (0, 0), was sufficient to account for the constant groups' accurate extrapolation performance.
-Such findings may offer a preliminary suggestion that experience with a more variable set of training examples  may be detrimental to performance in simple extrapolation tasks.
-
-### Differences between the two Projects
-
-The HTT and HTW tasks differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
-
-In HTT, the salient perceptual elements of the task (i.e.
-the launching box, target and barrier) are subject to variation (i.e.
-different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
-Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
-If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
-Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
-the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
-
-The HTT and HTW tasks also differed in terms of general task complexity.
-The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
-Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
-In HTW,the relationship between feedback and optimal behavioral adjustment is also almost perfectly smooth, if participants produce a throw that is 100 units too hard, they'll be told that they were 100 units away from the target band.
-Whereas in HTT, the presence of the barrier in introduces irregularities in the task space.
-Even throws close to the solution space might result in failure, creating a less predictable learning environment.
-
-::: {#tbl-task-diff}
-
-| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
-| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
-| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
-| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
-Only x velocity is relevant.
-|
-| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
-| Simpler: smooth, linear mapping between velocity and feedback.
-|
-| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
-salient differences in distance between launching box and target.
-| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
-|
-| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
-|
-| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
-| Some potential for learning during no-feedback testing by observing ball trajectory.
-|
-| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
-| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
-|
-| Testing Structure                               | Random interleaving of trained/transfer testing distances.
-| Blocked structure, separately testing trained vs extrapolation testing bands.
-|
-
-Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
-:::
-
-### Conclusion
-
-In summary, this dissertation provides a comprehensive examination of the effects of training variability on learning and generalization in visuomotor and function learning tasks.
-The contrasting results obtained from the Hit The Target (HTT) and Hit The Wall (HTW) tasks underscore the complexity inherent to the longstanding pedagogical and scientific goal of identifying training manipulations that consistently benefit learning and generalization.
-Moreover, through the development and application of computational models, we provide novel theoretical accounts for both the beneficial and detrimental effects of training variability observed in our experiments.
-These findings highlight the importance of considering task characteristics when designing experiments intended to assess the influence of training interventions, and demonstrate the value of combining empirical and computational modeling approaches to uncover the cognitive mechanisms that support learning and generalization.
-Future research should continue to investigate the complex interplay between task demands, training manipulations, and individual differences, with the ultimate goal of optimizing educational and training outcomes across a wide range of domains.
-
-\ \
-
-::: {.content-visible unless-format="pdf"}
-# References
-
-::: {#refs}
-:::
-
-:::
-
-# Appendix
-
-::: {.content-visible unless-format="markdown"}
-### Appendix - Project 1
-
-{{< include Appendix/IGAS-Supplemental.qmd >}}
-
-{{< pagebreak >}}
-
-### Appendix - Project 2 - Experiment 1
-
-{{< include Appendix/E1_Appendix.qmd >}}
-:::
-
-::: {.content-visible when-format="pdf"}
-
-# References
-
-:::

### 2024-04-12 Sections/full.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

@@
 subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
-date: 04/04/24
+#date: 04/04/24
 author:
@@
     echo: false
-    #include: false
+    include: true
     html-math-method: mathjax
@@
     mathfont: "Libertinus Math"
-editor: 
-  markdown: 
-    wrap: 72
 prefer-html: true
@@
 It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
-However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992].
-@palmeriCentralTendenciesExtreme2001 demonstrated the both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
+However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
+@palmeriCentralTendenciesExtreme2001 demonstrated both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
 These authors conducted a near replication of the @posnerGenesisAbstractIdeas1968 study, but also had participants provide similarity judgements of the dot pattern stimuli after completing the training phase.
@@
 
-_______________________________________________________________________________
-
 # Introduction
@@
 The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
 
@@
 The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
+A larger positive estimate indicates a greater deviation (lower accuracy) for the varied group.
 {.sm}
@@
 
-::: {.content-visible unless-format="pdf"}
+# Appendix
+
+[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html
+
 # References
-
-::: {#refs}
-:::
-
-:::
-
-# Appendix
-
-::: {.content-visible unless-format="markdown"}
-### Appendix - Project 1
-
-{{< include Appendix/IGAS-Supplemental.qmd >}}
-
-{{< pagebreak >}}
-
-### Appendix - Project 2 - Experiment 1
-
-{{< include Appendix/E1_Appendix.qmd >}}
-:::
-
-::: {.content-visible when-format="pdf"}
-
-# References
-
-:::

### 2024-04-12 Sections/hold_temp.qmd
adding more citations to intro
update/re-render all versions. Took authors note out of hikmah manuscript

@@
 A stronger form of evidence that was not provided may have been to use multiple regression analyses to show that the testing advantage of the varied/random groups over the constant/blocked groups could be accounted for by the differences in self-reported attentional focus.
+
+In North 2019 - biggest effect for varied-random. 
+North, J.
+S., Bezodis, N.
+E., Murphy, C.
+P., Runswick, O.
+R., Pocock, C., & Roca, A.
+(2019).
+The effect of consistent and varied follow-through practice schedules on learning a table tennis backhand.
+Journal of Sports Sciences, 37(6), 613–620.
+https://doi.org/10.1080/02640414.2018.1522683
 
@@
 Collectively, this dissertation highlights the value of integrating empirical and modeling approaches to uncover the cognitive mechanisms that support learning and generalization across a variety of domains.
+
+```{md}
+---
+title: Full Dissertation
+subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
+date: 04/04/24
+author:
+- name: Thomas Gorman
+  affiliation: Indiana University
+page-layout: full
+code-fold: true
+code-tools: true
+toc: true
+toc-location: body
+toc-title: Contents
+cache: true
+execute: 
+  warning: false
+  eval: true
+format:
+  html: default
+  hugo-md:
+    echo: false
+    #include: false
+    html-math-method: mathjax
+    output-file: diss_full_hugo.md
+  gfm:
+    echo: false
+    output: false
+    output-file: diss_full_gfm.md
+  hikmah-manuscript-pdf:
+    echo: false
+    output-file: "tg_full_disser.pdf"
+    mainfont: "Linux Libertine O"
+    mainfontoptions:
+      - "Numbers=Proportional"
+      - "Numbers=OldStyle"
+    mathfont: "Libertinus Math"
+# editor: 
+#   markdown: 
+#     wrap: 72
+prefer-html: true
+---
+
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/pre_html.qmd >}}
+
+:::
+
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/pre_pdf.qmd >}}
+
+:::
+
+::: {.content-visible when-format="docx"}
+{{< include pre_sections/pre_docx.qmd >}}
+:::
+
+{{< pagebreak >}}
+
+::: column-page-inset-right
+
+# Abstract
+
+The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer or generalization to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
+Such generalization challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
+It is therefore important to better understand the factors that influence generalization, and to develop cognitive models that can predict when generalization is likely to occur.
+Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
+
+This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
+A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
+Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
+To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
+These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
+
+{{< pagebreak >}}
+
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/toc_html.qmd >}}
+
+:::
+
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/toc_pdf.qmd >}}
+
+:::
+
+{{< pagebreak >}}
+
+\ \
+
+::: {.content-visible unless-format="pdf"}
+# References
+
+::: {#refs}
+:::
+
+:::
+
+# Appendix
+
+[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html
+
+::: {.content-visible when-format="pdf"}
+
+# References
+
+:::
+
+:::
+
+<!-- ::: {.content-visible unless-format="markdown"}
+### Appendix - Project 1
+
+{{< include Appendix/IGAS-Supplemental.qmd >}}
+
+{{< pagebreak >}}
+
+### Appendix - Project 2 - Experiment 1
+
+{{< include Appendix/E1_Appendix.qmd >}}
+:::
+ -->
+```

### 2024-04-12 Sections/pre_sections/cover.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

---
title: "Dissertation"
short-title: "Variability and Generalization"
date: 10-11-2023
author:
- name: Thomas Gorman
  affiliation: Indiana University
  url: www.tegorman13.github.io
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
---

<style>
  body {
    text-align: center;
  }
</style>

\
\
Thomas Gorman
\
\
\
\
\
\
\
\
\
\
\
\
\
\
\
\
\
\
\

Submitted to the faculty of the University Graduate School in partial fulfillment of the
requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
Sciences and the Cognitive Science Program, Indiana University
Indiana University
Fall 2023

### 2024-04-12 Sections/pre_sections/pre_docx.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

--- 2023-10-19 Manuscript/pre_sections/pre_docx.qmd
@@
 
-Submitted to the faculty of the University Graduate School in partial fulfillment of the
+<!-- Submitted to the faculty of the University Graduate School in partial fulfillment of the
 requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
@@
 
-- Robert L. Goldstone
-- Robert Nosofsky
-- Peter Todd
-- Mike Jones
+- Robert L. Goldstone, PhD
+- Robert Nosofsky, PhD
+- Peter Todd, PhD
+- Mike Jones, PhD -->
 

### 2024-04-12 Sections/pre_sections/pre_html.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

--- 2023-10-19 Manuscript/pre_sections/pre_html.qmd
@@
 <!-- Second Page and so on... -->
-<div style="text-align: justify; margin-top: 700px;">
+<!-- <div style="text-align: justify; margin-top: 700px;">
   Submitted to the faculty of the University Graduate School in partial fulfillment of the
@@
   Indiana University
-</div>
+</div> -->
 
@@
 <!-- Committee Members Page -->
-<div style="text-align: center; margin-top: 300px;">
+<!-- <div style="text-align: center; margin-top: 300px;">
   Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
@@
 
-<div style="page-break-before: always;"></div>
+<div style="page-break-before: always;"></div> -->
 
-<div style="page-break-before: always;"></div>
+<!-- <div style="page-break-before: always;"></div> -->
 
 <!-- Acknowledgements -->
-<div style="text-align: center; font-weight: bold; font-size: 24px;">
+<!-- <div style="text-align: center; font-weight: bold; font-size: 24px;">
   Acknowledgements
@@
 
-</div>
+</div> -->
 

### 2024-04-12 Sections/pre_sections/pre_pdf.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

--- 2023-10-17 Manuscript/pre_sections/pre_pdf.qmd
@@
 \LARGE
-{Variability and Generalization - A Similarity-Based Account}
+{The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach}
 
@@
 
-\vspace{11.5cm}
+\vspace{16.5cm}
 
@@
 
-Submitted to the faculty of the University Graduate School in partial fulfillment of the
+<!-- Submitted to the faculty of the University Graduate School in partial fulfillment of the
 requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
 Sciences and the Cognitive Science Program, Indiana University
-Indiana University
+Indiana University -->
 
@@
 
-\newpage
+<!-- \newpage
 
@@
 \
-\_____________________________  Robert L. Goldstone
+\_____________________________  Robert L. Goldstone, PhD
 \vspace{2.5cm}
@@
 \
-\_____________________________  Robert Nosofsky
+\_____________________________  Robert Nosofsky, PhD
 \vspace{2.5cm}
 \
-\_____________________________  Peter Todd
+\_____________________________  Peter Todd, PhD
 \vspace{2.5cm}
 \
-\_____________________________  Mike Jones
+\_____________________________  Mike Jones, PhD
 
-\newpage
+\newpage -->
 
@@
 
-@2023 \\
+@2024 \\
 \vspace{1cm}
@@
 \newpage
-
-\tableofcontents
-\newpage
-\listoffigures
-\newpage
-\listoftables
-\newpage

### 2024-04-12 Sections/pre_sections/sigs.qmd
update/re-render all versions. Took authors note out of hikmah manuscript

<style>
  body {
    text-align: center;
  }
</style>

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.
\
\
\
\
\
\
\
Doctoral Committee \ \ 
___________________________ Robert L. Goldstone, Ph.D., Co-Chair \ \
___________________________ Robert Nosofsky, Ph.D., Co-Chair \ \
___________________________ Peter Todd, Ph.D.
___________________________ Mike Jones, Ph.D.

\ \ \ \ 
\ \ \ \ 
\ \ \ \

10/20/2023

### 2024-04-12 Sections/hold_temp.qmd
re-render

@@
 ```
+
+Write a complete paragraph for the "Existing Theoretical Frameworks" sections at the end of the Introduction.
+Cite papers like on Bjork, 1994; Soderstrom & Bjork, 2015; Guadagnoli & Lee, 2004, and make the point that while these existing frameworks offer a conceptual framework for understanding the influence of variability, there is currently a dearth of computational modelling approaches being utilized to explain the effects of varied training in the visuomotor learning domain.
+
+### Existing Theoretical Frameworks
+
+Several theoretical frameworks have been proposed to account for the effects of training variability on learning and generalization.
+The contextual interference effect (Battig, 1972; Shea & Morgan, 1979) posits that varied practice leads to greater interference during acquisition but enhanced retention and transfer due to increased contextual discrimination and cognitive effort during learning.
+Similarly, the reconceptualized desirable difficulties framework (Bjork, 1994; Soderstrom & Bjork, 2015) suggests that varied practice introduces desirable difficulties that initially impair performance but promote long-term retention and transfer.
+The challenge point hypothesis (Guadagnoli & Lee, 2004) proposes that optimal learning occurs when the difficulty of the task is matched to the learner's skill level, with varied practice serving to increase task difficulty and facilitate learning for more skilled individuals.
+While these frameworks offer conceptual explanations for the influence of variability, there is currently a paucity of computational modeling approaches that explicitly capture the mechanisms underlying the effects of varied training, particularly in the domain of visuomotor learning.
+Existing computational models have largely focused on category learning (e.g., Nosofsky, 1986) and perceptual learning (e.g., Petrov et al., 2005), with limited attention to the role of variability in visuomotor skill acquisition and generalization.
+Given the importance of understanding the cognitive processes involved in visuomotor learning and transfer, there is a need for computational models that can provide a more precise and quantitative account of how varied practice influences the acquisition and generalization of visuomotor skills.
+
+Existing theoretical frameworks, such as the desirable difficulties framework (Bjork, 1994) and the challenge point framework (Guadagnoli & Lee, 2004), provide valuable conceptual insights into the influence of training variability on learning and generalization.
+These frameworks suggest that introducing appropriate levels of challenge or difficulty during training, such as through increased variability, can enhance long-term retention and transfer (Soderstrom & Bjork, 2015).
+However, while these frameworks offer a high-level understanding of the mechanisms underlying the benefits of varied training, there is currently a scarcity of computational modeling approaches being applied to elucidate the specific cognitive processes and representations involved in the effects of training variability, particularly in the domain of visuomotor learning.
+Computational models, such as connectionist or Bayesian approaches, have the potential to provide a more precise and quantitative account of how variability during training influences the acquisition and generalization of visuomotor skills.
+By specifying the underlying mechanisms and parameters, these models can generate testable predictions and offer a deeper understanding of the cognitive processes that give rise to the observed effects of varied training on visuomotor learning and transfer.
+
+The influence of training variability on learning and generalization has been a topic of considerable interest within cognitive science, particularly in the context of motor learning and skill acquisition.
+Theoretical frameworks such as Bjork's (1994) "desirable difficulties" and Soderstrom and Bjork's (2015) elaboration on the role of varied practice highlight the potential benefits of introducing variability during training to enhance learning outcomes.
+These theories suggest that varying the conditions of practice can improve the adaptability and robustness of learned skills, a principle also supported by Guadagnoli and Lee's (2004) challenge point framework, which posits that optimal learning occurs when the difficulty of practice tasks is appropriately matched to the learner's capabilities.
+While these frameworks provide valuable insights into the mechanisms through which variability might enhance learning, they predominantly focus on general psychological and pedagogical principles.
+Notably, there is a relative scarcity of computational modeling approaches that explicitly address how varied training influences learning processes in the visuomotor domain.
+Such models are crucial for quantitatively testing theories and providing a more detailed mechanistic understanding of how variability affects the acquisition, retention, and generalization of motor skills.
+As such, the current research seeks to fill this gap by developing and applying computational models to empirically investigate the effects of training variability in visuomotor tasks, thereby providing a more nuanced understanding of the conditions under which variability facilitates or impedes learning and transfer.

### 2024-04-14 Sections/HTW.qmd
fix typos

@@
 To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
-Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.
+Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to examine the ability of these influential models of function learning to account for both the group level and individual level data.
 
@@
 Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
+We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for the random effects.
 For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
@@
 In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions  rresulted in lower final training performance is consistent with much of the prior researchon the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
+Our findings that training with variable conditions resulted in lower final training performance are consistent with much of the prior research on the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
 
@@
 To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
+Each model was fit to the data with three separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
 We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant.
+It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models were fit separately to the data of each individual participant.
 The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.

### 2024-04-14 Sections/IGAS.qmd
update IGAS intro - then re-render everything
fix typos

@@
 To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies, yielding a Cohens f =.43.
-The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009], 2009) was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
+We then averaged effects across these studies, yielding a Cohen's f =.43.
+The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009] was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
 All experiments reported in the present manuscript exceed this minimum number of participants per condition.
@@
 
-Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18-22 years.
+Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18 to 22 years.
 A total of 110 Indiana University psychology students participated in Experiment 1.
@@
 Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
-Likewise, the distance between the center of the target, and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
+Likewise, the distance between the center of the target and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
 For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
@@
 However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest.
-All data processing and statistical analyses were performed in R version 4.03 (R Core Team, 2020).
-ANOVAs for group comparisons were performed using the rstatix package (Kassambara, 2021).
+All data processing and statistical analyses were performed in R version 4.32 [@rcoreteamLanguageEnvironmentStatistical2020].
+ANOVAs for group comparisons were performed using the rstatix package [@kassambaraRstatixPipeFriendlyFramework2021a].
 
@@
 We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor.
-The analysis revealed a significant effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02, and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
+The analysis revealed a significant effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training.
+There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02, and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
 
@@
 A total of 306 Indiana University psychology students participated in Experiment 2, which was also conducted online.
-As was the case in experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18--22-year-old individuals.
-Using the same procedure as experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task.
+As was the case in Experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18--22-year-old individuals.
+Using the same procedure as Experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task.
 A total of 208 participants were included in the final analyses with 31 in the varied group and 32, 28, 37, 25, 29, 26 participants in the constant groups training from location 400, 500, 625, 675, 800, and 900, respectively.
@@
 The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target.
-Additionally, the intermittent testing trials featured in experiment 1 were not utilized in experiment 2, and all training and testing trials were presented with feedback.
+Additionally, the intermittent testing trials featured in Experiment 1 were not utilized in Experiment 2.
 An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
 
-The procedure for Experiment 2 was also quite similar to experiment 1.
+The procedure for Experiment 2 was also quite similar to Experiment 1.
 Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group.
 In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training.
-Each of the constant groups thus experience one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
+Each of the constant groups thus experienced one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
 
@@
 This standardization did not influence our pattern of results.
-As in experiment 1, we performed type III ANOVA's due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.
-The statistical software for the primary analyses was the same as for experiment 1.
+As in Experiment 1, we performed type III ANOVAs due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.
+The statistical software for the primary analyses was the same as for Experiment 1.
 Individual learning rates in the testing phase, compared between groups in the supplementary analyses, were fit using the TEfit package in R [@cochraneTEfitsNonlinearRegression2020].
@@
 
-Finally, corresponding to the comparison of position 760 from experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained.
+Finally, corresponding to the comparison of position 760 from Experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained.
 Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group).
@@
 
-The results of experiment 2 largely conform to the findings of experiment 1.
+The results of Experiment 2 largely conform to the findings of Experiment 1.
 Participants in both varied and constant conditions improved at the task during the training phase.
@@
 We also join a much smaller set of research to observe this pattern in a computerized task [@seowTransferEffectsVaried2019].
-One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
+One departure from the Experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in Experiment 1, but did not reach significance in Experiment 2.
 Although this pattern has been observed elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
@@
 The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$ =.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$ =.07.
-For all comparisons, the pattern of results was consistent with the initial findings from experiment 2, with the varied group still performing significantly better than the constant group.
+For all comparisons, the pattern of results was consistent with the initial findings from Experiment 2, with the varied group still performing significantly better than the constant group.
 
@@
 We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978].
-In experiment 1 varied participants performed significantly better on this identity comparison.
+In Experiment 1 varied participants performed significantly better on this identity comparison.
 In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).

### 2024-04-14 Sections/full.qmd
fix typos

@@
 
-Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18-22 years.
+Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18 to 22 years.
 A total of 110 Indiana University psychology students participated in Experiment 1.
-We subsequently excluded 34 participants poor performance at one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
+We subsequently excluded 34 participants for poor performance on one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
 simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
@@
 The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target.
-Additionally, the intermittent testing trials featured in experiment 1 were not utilized in experiment 2, and all training and testing trials were presented with feedback.
+Additionally, the intermittent testing trials featured in experiment 1 were not utilized in Experiment 2.
 An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
 
-The procedure for Experiment 2 was also quite similar to experiment 1.
+The procedure for Experiment 2 was also quite similar to Experiment 1.
 Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group.
 In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training.
-Each of the constant groups thus experience one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
+Each of the constant groups thus experienced one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
 
@@
 #| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
+This empirical solution space was compiled from all of the participants in Experiment 2.
 B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
@@
 One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ].
+The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
+The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022].
 The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
@@
 
-All data processing and statistical analyses were performed in R version 4.32 @rcoreteamLanguageEnvironmentStatistical2020.
+All data processing and statistical analyses were performed in R version 4.32 [@rcoreteamLanguageEnvironmentStatistical2020].
 To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
+Model fitting was performed with the brms package in R [@burknerBrmsPackageBayesian2017], and descriptive stats and tables were extracted with the BayestestR package [@makowskiBayestestRDescribingEffects2019].
 Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
@@
 To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data in with separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
+Each model was fit to the data with three separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
 We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models to were fit separately to the data of each individual participant.
+It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.
+Models were fit separately to the data of each individual participant.
 The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.

### 2024-04-14 Sections/HTW.qmd
finish up motivation portion of intro

@@
 We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.Models were fit separately to the data of each individual participant.
+It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.
+Models were fit separately to the data of each individual participant.
 The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.

### 2024-04-14 Sections/IGAS.qmd
finish up motivation portion of intro

@@
 subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: last-modified
+#date: last-modified
 #page-layout: full
@@
 
-The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
+The present work examines whether the commonly observed benefits of varied training can be accounted for by a theoretrically motivated measure of the similarity between training throws and the testing solution space.
 We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.

### 2024-04-14 Sections/Introduction.qmd
finish up motivation portion of intro

@@
 
+### Existing Theoretircal Frameworks
+
+A number of theoretical frameworks have been proposed to conceptually explain the effects of varied training on learning and generalization.
+Schema theory (described in more detail above), posts that varied practice leads to the formation of more flexible motor schemas, which then facilitate generalization [@schmidtSchemaTheoryDiscrete1975].
+The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice may impair initial performance but then enhance longer-term retention and transfer.
+Similarily, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
+
+While these frameworks offer valuable conceptual accounts, there has been a limited application of computational modeling efforts aimed at quantitatively assessing and comparing the learning and generalization mechanisms which may be underlying the influence of variability in visuomotor skill learning.
+In contrast, the effects of variability have received more formal computational treatment in other domains, such as category learning [@hahnEffectsCategoryDiversity2005 @huHighvariabilityTrainingDoes2024],  language learning [@jonesDensityDistinctivenessEarly2020], and function learning [@deloshExtrapolationSineQua1997].
+A primary goal of the  current dissertation is to to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
+
 ### The current work

### 2024-04-14 Sections/hold_temp.qmd
finish up motivation portion of intro

@@
 As such, the current research seeks to fill this gap by developing and applying computational models to empirically investigate the effects of training variability in visuomotor tasks, thereby providing a more nuanced understanding of the conditions under which variability facilitates or impedes learning and transfer.
+
+___________
+___________
+
+A number of theoretical frameworks have been proposed to conceptually explain the effects of varied training on learning and generalization, such as the contextual interference effect (Battig, 1972; Shea & Morgan, 1979), the desirable difficulties framework (Bjork, 1994; Soderstrom & Bjork, 2015), and the challenge point hypothesis (Guadagnoli & Lee, 2004).
+While these frameworks offer conceptual accounts of how variability influences skill acquisition and transfer, there has been a relative dearth of computational modeling efforts aimed at precisely specifying the underlying mechanisms, particularly within the domain of visuomotor skill learning.
+
+In contrast, the effects of variability have received more formal computational treatment in other domains.
+For instance, in category learning, researchers have successfully applied exemplar models (e.g., Nosofsky, 1986) and connectionist architectures to capture how the diversity of training instances impacts generalization (Hahn et al., 2005; Hu & Nosofsky, 2024).
+Similarly, neural network models have been used to elucidate the influence of variability on learning and generalization in language acquisition (Jones & Brandt, 2020).
+However, such computational approaches have seen limited application to understanding the role of varied practice in visuomotor skill learning and transfer.
+
+Given the practical relevance of optimizing training for generalization across domains, there is a clear need for formal computational models that can provide a precise, quantitative account of the cognitive processes through which varied practice impacts the acquisition and flexible expression of visuomotor skills.
+Addressing this gap would not only advance theoretical understanding but could also inform the design of more effective training regimens.
+
+___________
+
+Several influential theoretical frameworks, such as the contextual interference effect (Battig, 1972; Shea & Morgan, 1979), the desirable difficulties framework (Bjork, 1994; Soderstrom & Bjork, 2015), and the challenge point hypothesis (Guadagnoli & Lee, 2004), have been proposed to provide conceptual explanations for the effects of training variability on learning and generalization in sensorimotor skill acquisition.
+These frameworks suggest that introducing appropriate levels of variability or difficulty during training can enhance long-term retention and transfer of skills.
+
+However, while these frameworks offer valuable conceptual accounts, there is currently a lack of formal computational modeling approaches that explicitly capture the mechanisms underlying the effects of varied training in the sensorimotor learning domain.
+In contrast, computational models have been developed to account for the influence of variability in other domains, such as category learning (Hahn et al., 2005; Hu & Nosofsky, 2024) and language learning (Jones & Brandt, 2020).
+For example, Hahn et al.
+(2005) used the generalized context model, an exemplar-based model, to explain how category variability affects generalization in a perceptual categorization task.
+Similarly, Jones and Brandt (2020) employed neural network simulations to investigate the role of density and distinctiveness in early word learning.
+
+Given the importance of understanding the cognitive processes involved in sensorimotor learning and generalization, there is a need for computational models that can provide a more precise and quantitative account of how varied practice influences the acquisition and generalization of sensorimotor skills.
+Such models would complement the existing theoretical frameworks by specifying the underlying mechanisms and parameters that give rise to the observed effects of training variability, generating testable predictions, and offering a deeper understanding of the cognitive processes involved in sensorimotor learning and transfer.
+
+___________
+
+Several influential theoretical frameworks have been proposed to account for the effects of training variability on learning and generalization.
+The contextual interference effect (Battig, 1972; Shea & Morgan, 1979) posits that varied practice leads to greater interference during acquisition but enhanced retention and transfer due to increased contextual discrimination and cognitive effort during learning.
+Similarly, the reconceptualized desirable difficulties framework (Bjork, 1994; Soderstrom & Bjork, 2015) suggests that varied practice introduces desirable difficulties that initially impair performance but promote long-term retention and transfer.
+The challenge point hypothesis (Guadagnoli & Lee, 2004) proposes that optimal learning occurs when the difficulty of the task is matched to the learner's skill level, with varied practice serving to increase task difficulty and facilitate learning for more skilled individuals.
+
+While these frameworks offer conceptual explanations for the influence of variability, the sensorimotor skill learning literature has been relatively limited in its application of formal computational modeling approaches to elucidate the underlying cognitive processes.
+In contrast, researchers have made significant progress in developing computational models to account for the effects of variability in other domains, such as category learning (e.g., Hahn et al., 2005; Nosofsky, 1986) and language learning (e.g., Jones & Brandt, 2020).
+The present work seeks to address this gap by implementing and evaluating computational models that can provide a more precise and quantitative account of how varied practice influences the acquisition and generalization of sensorimotor skills.
+
+___________
+
+While several influential frameworks provide conceptual insights into the role of training variability in sensorimotor skill learning, there remains a notable gap in the formal computational modeling of these effects.
+This contrasts sharply with the fields of category learning and language learning, where computational models have been extensively developed and applied.
+For instance, in the realm of category learning, Hahn, Bailey, and Elvin (2005) demonstrate how category diversity influences learning, memory, and generalization through computational modeling approaches that quantify the effects of category structure and exemplar variability.
+Similarly, in language learning, Jones and Brandt (2020) employed neural network simulations to explore how phonological neighborhood density and distinctiveness impact early word learning, providing a computational account of the complex dynamics involved.
+
+In contrast, the sensorimotor domain has largely relied on qualitative frameworks such as the contextual interference effect and the challenge point framework without a corresponding development in computational models that can rigorously test these theories.
+For example, although studies like that of Hu and Nosofsky (2024) investigate the effects of high-variability training in the prototype-distortion paradigm, they primarily focus on empirical evaluations without integrating these findings into a broader computational framework.
+This discrepancy highlights a crucial need for developing computational models that can offer a more precise and mechanistic understanding of how variability affects the acquisition and generalization of sensorimotor skills, akin to the advances seen in category and language learning studies.
+Such efforts would not only bridge the theoretical gaps but also enhance the predictive power and applicability of these models in practical training and rehabilitation settings.
+
+___________
+
+A number of theoretical frameworks have been proposed to conceptually explain the effects of varied training on learning and generalization.
+Schema theory (described in more detail above), posts that varied practice leads to the formation of more flexible motor schemas, which then facilitate generalization [@schmidtSchemaTheoryDiscrete1975].
+The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice may impair initial performance but then enhance longer-term retention and transfer.
+Similarily, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
+
+While these frameworks offer valuable conceptual accounts, there has been a limited application of computational modeling efforts aimed at quantitatively assessing and comparing the learning and generalization mechanisms which may be underlying the influence of variability in visuomotor skill learning.
+In contrast, the effects of variability have received more formal computational treatment in other domains, such as category learning [@hahnEffectsCategoryDiversity2005 @huHighvariabilityTrainingDoes2024],  language learning [@jonesDensityDistinctivenessEarly2020], and function learning [@deloshExtrapolationSineQua1997].
+A primary goal of the  current dissertation is to to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.

### 2024-04-15 Sections/HTW.qmd
fix up htw figure and table captions. Change e1 methods image display function to knitr. bold some p2 e3 table rows.

@@
 The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
 
@@
 
-/
 ```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
@@
 | End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
+| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|band) `` | All Testing trials   |
+| Band Discrimination      | `` brm(vx ~ condit * band +(1 + band|id) ``             | All Testing Trials   |
 \
@@
     theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
+    labs(y = "Absolute Deviation", x="Training Block") 
 #ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
@@
 : **Experiment 1 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
+Comparing final training block accuracy in band common to both groups.
+The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
 A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
 {.sm}
@@
 Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-Larger coefficients  indicate larger deviations from the baselines (Condition=constant & bandType=Trained) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
+extrapolation bands), and the interaction between the two factors.
+The Intercept represents the baseline condition (constant training & trained bands).
+Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.hover .sm}
 :::
@@
 #| label: fig-e1-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
+#| fig-cap: Experiment 1 Testing Accuracy.
+A) Empricial Deviations from target band during testing without feedback stage.
 B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
 Error bars represent 95% credible intervals.
+#| fig-width: 11
+#| fig-height: 7
 
@@
   theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
+  labs(x="Band", y="Absolute Deviation From Target Band")
 
@@
   gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
+ condEffects(bandType) + labs(y="Absolute Deviation From Target Band", x="Band Type")
 
@@
 
-Experiment 1.
+**Experiment 1 Testing Discrimination**.
 Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
 Varied) and Velocity Band.
-Larger coefficients on Band represent greater sensitivity/discrimination.
-{.striped .hover .sm}
+Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
+The interaction between condit and Band indicates the difference between constant and varied slopes.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.hover .sm}
 :::
@@
 See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
+The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, though is not in and of itself useful for assessing discrimination.
 Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
 Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
+The significant negative estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
 This difference is depicted visually in @fig-e1-test-vx.
@@
 #| label: fig-e1-test-vx
-#| fig-cap: Empirical distribution of velocities producing in testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-cap: Experiment 1. Empirical distribution of velocities producing in testing stage. Translucent bands with dashed lines indicate the correct range for each velocity band. 
 #| fig-width: 11
-#| fig-height: 9
+#| fig-height: 8
 
@@
 #| label: tbl-e1-bmm-vx
-#| fig-cap: Experiment 1.
-Conditional effect of training condition and Band.
+#| fig-cap: Experiment 1 Discrimination.
+A) Conditional effect of training condition and Band.
 Ribbons indicate 95% HDI.
 The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
+B) The distribution of slope coefficients for each condition.
+Larger slopes indicates better discrimination.
+C) Individual participant slopes.
+Error bars represent 95% HDI.
+#| fig-height: 7
 #| fig-width: 11
@@
     theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
+    labs(y = "Absolute Deviation", x="Training Block") 
 #ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
@@
 : **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
+The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
 A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
 {.sm}
@@
 extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
+The Intercept represents the baseline condition (constant training & trained bands).
+Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.hover .sm}
 :::
@@
 #| label: fig-e2-test-dev
-#| fig-cap:  A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-#| eval: TRUE
+#| fig-cap: Experiment 2 Testing Accuracy.
+A) Empricial Deviations from target band during testing without feedback stage.
+B) Conditional effect of condition (Constant vs.
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
+Error bars represent 95% credible intervals.
+#| fig-width: 11
+#| fig-height: 7
 
@@
 
-Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band {.striped .hover .sm}
+**Experiment 2 Testing Discrimination**.
+Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
+Varied) and Velocity Band.
+Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
+The interaction between condit and Band indicates the difference between constant and varied slopes.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate) {.hover .sm}
 :::
@@
 #| label: fig-e2-test-vx
-#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-cap: Experiment 2. Empirical distribution of velocities produced in the testing stage. Translucent bands with dash lines indicate the correct range for each velocity band.  
 #| fig-width: 11
-#| fig-height: 9
+#| fig-height: 8
 testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
@@
 #| label: tbl-e2-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
+#| fig-cap: Experiment 2 Discrimination.
+A) Conditional effect of training condition and Band.
 Ribbons indicate 95% HDI.
 The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-height: 9
+B) The distribution of slope coefficients for each condition.
+Larger slopes indicates better discrimination.
+C) Individual participant slopes.
+Error bars represent 95% HDI.
+#| fig-height: 7
 #| fig-width: 11
@@
 : **Experiment 3 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
+The Intercept represents the average of the baseline condition (constant training & original band order), the conditVaried coefficient reflects the difference between the constant and varied groups, and the bandOrderReverse coefficient reflects the difference between original and reverse order.
 A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-{.sm}
+The negative value for the interaction between condit and bandOrder indicates that varied condition with reverse order had significantly lower deviations than the varied condition with the original band order  {.sm}
 
@@
 #| label: fig-e3-train-dev
-#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
+#| fig-cap: Experiment 3 training. Deviations from target band during training. Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2). 
 #| eval: true
@@
     theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block") 
+    labs(y = "Absolute Deviation", x="Training Block") 
 #ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
@@
 | bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
-| conditVaried:bandTypeExtrapolation                  |    52.66 |         14.16 |         90.23 | 1.00 |
+| **conditVaried:bandTypeExtrapolation**                  |    52.66 |         14.16 |         90.23 | 1.00 |
 | conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
@@
 extrapolation), and the interaction between the two factors.
-The Intercept represents the baseline condition, (constant training;  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
-Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.{.striped .hover .sm}
+The Intercept represents the baseline condition, (constant training,   trained bands, & original order), and the remaining coefficients reflect the deviation from that baseline.
+Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
+{.hover .sm}
 :::
@@
 #| fig-cap: Experiment 3 Testing Accuracy.
-A) Deviations from target band during testing without feedback stage.
+A) Empricial Deviations from target band during testing without feedback stage.
 B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (training vs.
-extrapolation) on testing accuracy.
-Error bars represent 95% confidence intervals.
-#| eval: true
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
+Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2).
+Error bars represent 95% credible intervals.
+#| fig-width: 11
+#| fig-height: 8
 
@@
   gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
+ condEffects(bandType) + labs(y="Absolute Deviation From Target Band", x="Band Type") + 
  facet_wrap(~bandOrder,ncol=1)
@@
 | bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
+| **Band**                                 |     0.49 |          0.36 |          0.62 | 1.00 |
+| **conditVaried:bandOrderReverse**         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
 | conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |
-
-Experiment 3.
+| bandOrderReverse:Band              |    -0.10 |         -0.27 |          0.08 | 0.86 |
+| **conditVaried:bandOrderReverse:Band** |     0.42 |          0.17 |          0.70 | 1.00 |
+
+**Experiment 3 testing discrimination**.
 Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs.
 Varied) and Velocity Band.
-The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the linear slope for the baseline condition.
-{.striped .hover .sm}
+The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the  slope for the baseline condition.
+The interaction terms which include condit and Band (e.g.
+conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate the how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
 :::
@@
 Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
-However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating that the varied condition showed a greater slope coefficient on the reverse order bands, compared to the constant condition - this is clearly shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
+However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating a greater slope for the varied condition trained with reverse order bands.
+This interaction is shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
 
@@
 #| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-cap: Experiment 3.
+Empirical distribution of velocities produced in the testing stage.
+Translucent bands with dash lines indicate the correct range for each velocity band.
+Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2).
 #| fig-width: 11
@@
 #| label: fig-e3-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
+#| fig-cap: Experiment 3 Discrimination.
+A) Conditional effect of training condition and Band.
 Ribbons indicate 95% HDI.
 The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
+B) The distribution of slope coefficients for each condition.
+Larger slopes indicates better discrimination.
+C) Individual participant slopes.
+Error bars represent 95% HDI.
 #| fig-height: 10
@@
     heading.subtitle.font.size = 12,
-    table.font.size = 10, 
+    table.font.size = 11, 
     quarto.disable_processing = TRUE
@@
 
-*Experimental Result Summary*
+*Experimental Results Summary*
 

### 2024-04-15 Sections/IGAS.qmd
fix up htw figure and table captions. Change e1 methods image display function to knitr. bold some p2 e3 table rows.

@@
 
-The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library (de Leeuw, 2015).
+The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library [@deleeuwJsPsychJavaScriptLibrary2015].
 The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.

### 2024-04-15 Sections/full.qmd
fix up htw figure and table captions. Change e1 methods image display function to knitr. bold some p2 e3 table rows.

@@
 
-# Abstract
-
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer or generalization to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such generalization challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence generalization, and to develop cognitive models that can predict when generalization is likely to occur.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
-
-This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
-A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
-Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
-To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
-These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
-
-## The study of variability
+## Introduction
 
@@
 
-```{r}
+```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
 #| label: fig-IGAS_Methods
@@
 
-mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
-
+# mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
+# plot_grid(mf,ncol=1)
+knitr::include_graphics(here::here("Assets/methodsFig1.png"))
 ```
@@
 : **Experiment 1 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimate indicates a greater deviation (lower accuracy) for the varied group.
+Comparing final training block accuracy in band common to both groups.
+The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
+A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
 {.sm}
@@
   theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
+  labs(x="Band", y="Deviation From Target Band")
 
@@
 : **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline (constant condition), and the conditVaried coefficient reflects the difference between the constant and varied groups.
+The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
 A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
 {.sm}
-
-:::
 
@@
 extrapolation), and the interaction between the two factors.
-Larger coefficient estimates indicate larger deviations from the baselines (constant & trained bands) - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands {.striped .hover .sm}
+The Intercept represents the baseline condition (constant training & trained bands).
+Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.hover .sm}
 :::
+
 \ \
@@
 extrapolation), and the interaction between the two factors.
-The Intercept represents the baseline condition, (constant training;  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
+The Intercept represents the baseline condition, (constant training,  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
 Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
-{.striped .hover .sm}
+{.hover .sm}
 :::
@@
 | bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| Band                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| conditVaried:bandOrderReverse         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
+| **Band**                                  |     0.49 |          0.36 |          0.62 | 1.00 |
+| **conditVaried:bandOrderReverse**         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
 | conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:bandInt              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| conditVaried:bandOrderReverse:bandInt |     0.42 |          0.17 |          0.70 | 1.00 |
-
-Experiment 3.
+| bandOrderReverse:band              |    -0.10 |         -0.27 |          0.08 | 0.86 |
+| **conditVaried:bandOrderReverse:band** |     0.42 |          0.17 |          0.70 | 1.00 |
+
+**Experiment 3 testing discrimination**.
 Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs.
 Varied) and Velocity Band.
-The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the linear slope for the baseline condition.
-.hover .sm}
+The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the  slope for the baseline condition.
+The interaction terms which include condit and Band (e.g.
+conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate the how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
 :::
@@
 #| label: fig-e3-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
+#| fig-cap: Experiment 3 Discrimination.
+A) Conditional effect of training condition and Band.
 Ribbons indicate 95% HDI.
 The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
+B) The distribution of slope coefficients for each condition.
+Larger slopes indicates better discrimination.
+C) Individual participant slopes.
+Error bars represent 95% HDI.
 #| fig-height: 10
 #| fig-width: 11
-##| eval: FALSE
 # pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")

### 2024-04-15 Manuscript/manuscript.qmd
big re-render of all versions

@@
 toc: false
-toc-depth: 3
+toc-depth: 4
 toc-location: body
+cache: true
 execute: 
@@
   include: true
+  echo: false
 ---
@@
 
-# Abstract
-
-This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
-A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
-Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
-To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
-These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/toc_html.qmd >}}
+
+:::
+
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/toc_pdf.qmd >}}
+
+:::
 
@@
 
-::: {.content-visible when-format="html"}
-
-{{< include pre_sections/toc_html.qmd >}}
-
-:::
-
-::: {.content-visible when-format="pdf"}
-
-{{< include pre_sections/toc_pdf.qmd >}}
-
-:::
+# Introduction
+
+## Varied Training and Generalization
+
+Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
+See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
+
+Research on the effects of varied training typically manipulates variability in one of two ways.
+In the first approach, a high variability group is exposed to a greater number of unique instances during training, while a low variability group receives fewer unique instances with more repetitions.
+Alternatively, both groups may receive the same number of unique instances, but the high variability group's instances are more widely distributed or spread out in the relevant psychological space, while the low variability group's instances are clustered more tightly together.
+Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
+Researchers will usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
+The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
+However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to make it easy to measure how much performance degrades as a function of how far away testing items are from the training items.
+
+The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
+Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
+Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
+an underhand throw).
+When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
+Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer.
+Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
+Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
+For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
+Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
+
+One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
+Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
+The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
+Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
+12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
+Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
+In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
+This result offers a particularly compelling example of the merits of varied practice, given that the varied group was able to outperform the constant group even from the  home turf location where one may have expected the constatn group to have the strongest advantage.
+A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a].
+One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
+Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
+However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperfroms the constant group even from the constants group's home turf has not been consistently replicated.
+One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
+This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
+However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+
+Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
+However, despite its appeal this particular contrast is relatively uncommon in the literature.
+It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
+A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
+@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
+@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
+A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
+Of particular relevance to the current work is the early study of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
+constant training on multiple testing locations of graded distance from the training condition.
+Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
+The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
+Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
+As is often the case, the varied group performed worse during the training phase.
+In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
+
+Benefits of varied training have also been observed in many studies outside of the sensorimotor domain.
+@goodeSuperiorityVariableRepeated2008 trained participants to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
+Although subjects in all conditions were exposed to the same 40 unique words (i.e.
+the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training).
+Two different constant groups were used.
+Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
+LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
+At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had three prior exposures to the word arrangement (i.e.
+the particular permutation of letters) which the varied group had not explicitly seen.
+However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving two more anagrams on average than the constant group.
+This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
+This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.
+
+In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
+typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
+
+Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968].
+A seminal study by @posnerGenesisAbstractIdeas1968 trained participants to categorize artificial dot patterns, manipulating whether learners were trained with low variability examples clustered close to the category prototypes (i.e. low distortion training patterns), or higher-variability patterns spread further away from the prototype (i.e.
+high-distortion patterns).
+Participants that received training on more highly-distorted items showed superior generalization to novel high distortion patterns in the subsequent testing phase.
+It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training rathers, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
+This train-until-criterion procedure led to the high-variability condition participants tending to complete a larger number of training trials before switching to the testing stage.
+More recent work [@huHighvariabilityTrainingDoes2024], also used dot pattern categories, but matched the number of training trials across conditions.
+Under this procedure, higher-variability participants tended to reach lower levels of performance by the end of the training stage.
+The results in the testing phase were the opposite of @posnerGenesisAbstractIdeas1968,  with the low-variability training group showing superior generalization to novel high-distortion patterns (as well as generalization to novel patterns of low or medium distortion levels).
+However, whether this discrepancy is solely a result of the different training procedures is unclear, as the studies also differed in the nature of the prototype patterns used.
+@posnerGenesisAbstractIdeas1968  utilized simpler, recognizable prototypes (e.g., a triangle, the letter M, the letter F), while  @huHighvariabilityTrainingDoes2024 employed random prototype patterns.
+
+Recent studies have also begun utilizing more complex or realistic sitmuli when assessing the influence of variability on category learning.
+@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
+In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
+Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
+higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
+A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyModelguidedSearchOptimal2019].
+For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
+The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
+
+A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g.
+the region between the two categories).
+The general approach is to train participants with examples from a high variability category and a low variability category.
+Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
+@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
+In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
+In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart.
+Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
+Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
+
+Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
+@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002;  @yangCategoryVariabilityEffect2014; and @seitzModelingCategoryVariability2023].
+The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
+They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
+In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial.
+They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
+
+The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present work.
+Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
+During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories.
+The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category.
+Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category.
+Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
+The author compared a variety of similarity-based models based around the Generalized Context Model [@nosofskyAttentionSimilarityIdentificationcategorization1986] to account for their results, manipulating whether a response-bias or similarity-scaling parameter was fit separately between variability conditions.
+No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
+The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
+This model accounted for both the extended generalization gradients of the varied particpants, and also for their poorer performance in a recognition condition.
+
+Variability has also been examined in the learning of higher-order linguistic categories [@perryLearnLocallyThink2010].
+In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
+All infants were introduced to three novel objects of the same category, with participants in the "tight" condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
+Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
+Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
+By the end of the nine weeks, all of the infants had learned the labels of the training objects.
+In the testing phase, the varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category.
+More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
+The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
+
+Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
+Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987; @vanrossumSchmidtSchemaTheory1990], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+
+In an example of a more complex influence of training variation, [@braithwaiteEffectsVariationPrior2015] trained participants on example problems involving the concept of sampling with replacement (SWR).
+Training consisted of examples that were either highly similar in their semantic context (e.g.
+all involving people selecting objects) or in which the surface features were varied between examples (e.g.
+people choosing objects AND objects selected in a sequence).
+The experimenters also surveyed how much prior knowledge each participant had with SWR.
+They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples.
+The authors hypothesized that in order to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
+To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples.
+Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
+Interactions between prior experience and the influence of varied training have also been observed in sensorimotor learning [@guadagnoliRelationshipContextualInterference1999;  @delreyEffectsContextualInterference1982].
+@delreyEffectsContextualInterference1982 recruited participants who self-reported either extensive, or very little experience with athletic activities, and then trained participants on a coincident timing task under with either a single constant training velocity, with one of several varied training procedures.
+Unsurprisingly, athlete participants had superior performance during training, regardless of  condition, and training performance was superior for all subjects in the constant group.
+Of greater interest is the pattern of testing results from novel transfer conditions.
+Among the athlete-participants, transfer performance was best for those who received variable training.
+Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
+
+## Existing Theoretircal Frameworks
+
+A number of theoretical frameworks have been proposed to conceptually explain the effects of varied training on learning and generalization.
+Schema theory (described in more detail above), posts that varied practice leads to the formation of more flexible motor schemas, which then facilitate generalization [@schmidtSchemaTheoryDiscrete1975].
+The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice may impair initial performance but then enhance longer-term retention and transfer.
+Similarily, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
+
+While these frameworks offer valuable conceptual accounts, there has been a limited application of computational modeling efforts aimed at quantitatively assessing and comparing the learning and generalization mechanisms which may be underlying the influence of variability in visuomotor skill learning.
+In contrast, the effects of variability have received more formal computational treatment in other domains, such as category learning [@hahnEffectsCategoryDiversity2005 @huHighvariabilityTrainingDoes2024],  language learning [@jonesDensityDistinctivenessEarly2020], and function learning [@deloshExtrapolationSineQua1997].
+A primary goal of the  current dissertation is to to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
+
+## The current work
+
+The overarching purpose of this dissertation is to investigate the effects of training variability on learning and generalization within visuomotor skill learning and function learning.
+Our investigations is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
+
+In Project 1, we investigated the influence of varied practice in a simple visuomotor projectile launching task.
+Experiments 1 and 2 compared the performance of constant and varied training groups to assess potential benefits of variability on transfer to novel testing conditions.
+To account for the observed empirical effects, we introduced the Instance-based Generalization with Adaptive Similarity (IGAS) model.
+IGAS provides a novel computational approach for quantifying the similarity between training experiences and transfer conditions, while also allowing for variability to influence the generalization gradient itself.
+
+Project 2 shifted focus to the domain of function learning by employing a visuomotor extrapolation task.
+Across three experiments, we examined how constant and varied training regimes affected learning, discrimination between stimuli, and the ability to extrapolate to novel regions of the function's input space.
+To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.
 
@@
 
-# Literature Review
-
-{{< include ../Introduction.qmd >}}
-
-```{r setup}
-
-#| 
-here::set_here(path='..')
-source(here::here("Functions", "packages.R"))
-
-if (is.null(knitr::pandoc_to())) {
-  fmt_out <- "interactive"
-} else {
-  fmt_out <- knitr::pandoc_to()
-}
-
-# knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
-#                       warning = FALSE, message = FALSE, eval=TRUE)
-
-# knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
-#                       fig.width = 6, fig.height = (6 * 0.618),
-#                       out.width = "100%", collapse = TRUE)
-# 
-options(digits = 3, width = 120,
-        dplyr.summarise.inform = FALSE,
-        knitr.kable.NA = "")
-
-```
-
-```{r}
+# Project 1
+
+```{r}
+#| cache: false
+
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
+  ggh4x,htmltools,future,furrr,ez)
+#options(brms.backend="cmdstanr",mc.cores=4)
+#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
+walk(c("brms","dplyr","bayestestR","here","rstanarm"), conflict_prefer_all, quiet = TRUE)
+walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+#conflicts_prefer(tidybayes::rstudent_t)
+
+# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+
+#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
 source(here::here('Functions/IGAS_ProcessFunctions.R'))
 
+#options(brms.backend="cmdstanr",mc.cores=4)
+initial_contrasts <- options("contrasts")$contrasts
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+
+library(tidybayes)
+
+theme_set(theme_classic())
+# load the processed data from experiment 1 and 2
 e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-
-# load the processed data from experiment 1 and 2
-
 e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-
 # load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
@@
 
-options(contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
+# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
+# defaultContrasts = options()$contrasts
+# theme_set(theme_classic())
 
@@
 
-# Project 1
-
 ## Abstract
 
-Exposing learners to variability during training has been demonstrated
-to improve performance in subsequent transfer testing. Such variability
-benefits are often accounted for by assuming that learners are
-developing some general task schema or structure. However much of this
-research has neglected to account for differences in similarity between
-varied and constant training conditions. In a between-groups
-manipulation, we trained participants on a simple projectile launching
-task, with either varied or constant conditions. We replicate previous
-findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to
-account for the benefits of variation, but, if the model is adjusted to
-assume that varied learners are tuned towards a broader generalization
-gradient, then a similarity-based model is sufficient to explain the
-observed benefits of variation. Our results therefore suggest that some
-variability benefits can be accommodated within instance-based models
-without positing the learning of some schemata or structure.
+Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
+Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
+However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
+In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
+We replicate previous findings showing a transfer advantage of varied over constant training.
+Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
+Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
 
@@
 
-The past century of research on human learning has produced ample
-evidence that although learners can improve at almost any task, such
-improvements are often specific to the trained task, with unreliable or
-even nonexistent transfer to novel tasks or conditions
-[@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993]. Such
-transfer challenges are of noteworthy practical relevance, given that
-educators, trainers, and rehabilitators typically intend for their
-students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that
-influence transfer, and to develop cognitive models that can predict
-when transfer is likely to occur. The factor of interest to the present
-investigation is variation during training. Our experiments add to the
-longstanding empirical investigation of the controversial relationship
-between training variation, and subsequent transfer. We also offer a
-novel explanation for such results in the form of an instance-based
-model that accounts for the benefits of variation in simple terms of
-psychological similarity. We first review the relevant concepts and
-literature.
-
 ### Similarity and instance-based approaches to transfer of learning
 
-Notions of similarity have long played a central role in many prominent
-models of generalization of learning, as well as in the longstanding
-theoretical issue of whether learners abstract an aggregate, summary
-representation, or if they simply store individual instances. Early
-models of learning often assumed that discrete experiences with some
-task or category were not stored individually in memory, but instead
-promoted the formation of a summary representation, often referred to as
-a prototype or schema, and that exposure to novel examples would then
-prompt the retrieval of whichever preexisting prototype was most similar
-[@posnerGenesisAbstractIdeas1968]. Prototype
-models were later challenged by the success of instance-based or
-exemplar models -- which were shown to provide an account of
-generalization as good or better than prototype models, with the
-advantage of not assuming the explicit construction of an internal
-prototype [@estesClassificationCognition1994;
-@hintzmanMINERVASimulationModel1984;
-@medinContextTheoryClassification1978;
-@nosofskyAttentionSimilarityIdentificationcategorization1986 ].
-Instance-based models assume that learners encode each experience with a
-task as a separate instance/exemplar/trace, and that each encoded trace
-is in turn compared against novel stimuli. As the number of stored
-instances increases, so does the likelihood that some previously stored
-instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks
-if they are sufficiently similar, thus suggesting that the process of
-computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological
-distance between instances or categories, has provided a successful
-account of generalization across numerous tasks and domains. In an
-influential study demonstrating an ordinal similarity effect,
-experimenters employed a numerosity judgment task in which participants
-quickly report the number of dots flashed on a screen. Performance (in
-terms of response times to new patterns) on novel dot configurations
-varied as an inverse function of their similarity to previously trained
-dot configurations @palmeriExemplarSimilarityDevelopment1997. That is, performance was better on
-novel configurations moderately similar to trained configurations than
-to configurations with low-similarity, and also better on low-similarity
-configurations than to even less similar, unrelated configurations.
-Instance-based approaches have had some success accounting for
-performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017; @crumpEpisodicContributionsSequential2010] trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following
-training, typing speed was tested on previously experienced words
-composed of previously experienced letters; novel words composed of
-letters from the trained letter set; and novel words composed of letters
-from an untrained letter set. Consistent with an instance-based account,
-transfer performance was graded such that participants were fastest at
-typing the words they had previously trained on, followed by novel words
-composed of letters they had trained on, and slowest performance for new
-words composed of untrained letters.
-
-## The effect of training variability on transfer
-
-While similarity-based models account for transfer by the degree of
-similarity between previous and new experiences, a largely separate body
-of research has focused on improving transfer by manipulating
-characteristics of the initial training stage. Such characteristics have
-included training difficulty, spacing, temporal order, feedback
-schedules, and the primary focus of the current work -- variability of
-training examples.
-
-Research on the effects of varied training typically compares
-participants trained under constant, or minimal variability conditions
-to those trained from a variety of examples or conditions [@czyzVariabilityPracticeInformation2021; @soderstromLearningPerformanceIntegrative2015]. Varied training has been shown to influence
-learning in myriad domains including categorization of simple stimuli [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968],
-complex categorization [@nosofskyModelguidedSearchOptimal2018], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory
-extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice
-identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018],
-sports training  [@greenPracticeVariabilityTransfer1995a @northEffectConsistentVaried2019], and training
-on a complex video game [@seowTransferEffectsVaried2019].
-
-Training variation has received a particularly large amount of attention
-within the domain of visuomotor skill learning. Much of this research
-has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a
-schema-based account of motor learning as an attempt to address the
-longstanding problem of how novel movements are produced. According to
-Schema Theory, learners possess general motor programs for classes of
-movements (e.g. throwing a ball with an underhand movement), as well as
-schema rules that determine how a motor program is parameterized or
-scaled for a particular movement. Schema theory predicts that varied
-training results in the formation of a more general schema-rule, which
-can allow for transfer to novel movements within a given movement class.
-Experiments that test this hypothesis are often designed to compare the
-transfer performance of a constant-trained group against that of a
-varied-trained group. Both groups train on the same task, but the varied
-group practices from multiple levels of a task-relevant dimension that
-remains invariant for the constant group. For example, investigators
-might train two groups of participants to throw a projectile at a
-target, with a constant group that throws from a single location, and a
-varied group that throws from multiple locations. Both groups are then
-tested from novel locations. Empirically observed benefits of the
-varied-trained group are then attributed to the variation they received
-during training, a finding observed in numerous studies [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991], and the benefits of this variation are typically
-thought to be mediated by the development of a more general schema for
-the throwing motion.
-
-Of course, the relationship between training variability and transfer is
-unlikely to be a simple function wherein increased variation is always
-beneficial. Numerous studies have found null, or in some cases negative
-effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987], and many more have suggested that the
-benefits of variability may depend on additional factors such as prior
-task experience, the order of training trials, or the type of transfer
-being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
+Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar.
+In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimuli.
+Recall that participants are trained on only on distortions of the category prototypes (e.g.
+low, medium or high distortions), never encountering the exact prototypes during the training stage.
+Then, in the testing phase, participants are tested with the prototype patterns, their old training items, and novel low, medium and high distortions.
+The authors found that participants had the highest testing accuracy for the previously unseen prototype patterns, followed by the old training items, and then the novel low, medium and high distortions.
+The authors interpreted this pattern as evidence that participants had acquired prototype representation of the category, as opposed to storing each individual training instance, and that generalization was based on the similarity of the testing items to the learned prototype representations.
+@posnerGenesisAbstractIdeas1968 has been extremely influential,  and continues to be cited in contemporary research as clear evidence that prototype abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
+However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
+@palmeriCentralTendenciesExtreme2001 demonstrated both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
+These authors conducted a near replication of the @posnerGenesisAbstractIdeas1968 study, but also had participants provide similarity judgements of the dot pattern stimuli after completing the training phase.
+A multidimensional scaling analysis of the similarity judgements revelead that the psychological representations of the prototype stimuli were not located in the middle of the training stimuli, but were instead extreme points in the psychological space.
+The authors also demonstrated the generalization patterns of @posnerGenesisAbstractIdeas1968 could be accounted for by an exemplar-based model, without any need to assume the abstraction of a prototype.
+
+Instance-based, or exemplar-based models generally assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978; @nosofskyAttentionSimilarityIdentificationcategorization1986; @jamiesonInstanceTheoryDomaingeneral2022].
+As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
+Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
+
+Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
+In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
+Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
+That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
+Instance-based similarity approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
+@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
+Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
+Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
 
@@
 
-Although the benefits of training variation in visuomotor skill learning
-have been observed many times, null findings have also been repeatedly
-found, leading some researchers to question the veracity of the
-variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of
-training variability, of the sort described above, often fail to control
-for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of
-freedom (e.g. projectile throwing tasks where participants control the x
-and y velocity of the projectile), varied groups are likely to
-experience a wider range of the task space over the course of their
-training (e.g. more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring
-that the training location(s) of the varied and constant groups are an
-equal distance away from the eventual transfer locations, such that
-their training throws are, on average, equally similar to throws that
-would lead to good performance at the transfer locations. However, even
-this level of experimental control may still be insufficient to rule out
-the effect of similarity on transfer. Given that psychological
-similarity is typically best described as either a Gaussian or
-exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005 ], it is plausible that a subset of the
-most similar training instances could have a disproportionate impact on
-generalization to transfer conditions, even if the average distance
-between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that
-drops off as a Gaussian function of distance from training, as compared
-to a linear drop-off.
+Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
+Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
+For training tasks in which participants have numerous degrees of freedom (e.g.
+projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
+more unique combinations of x and y velocities).
+Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
+However, even this level of experimental control may still be insufficient to rule out the effect of similarity on transfer.
+Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
+@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
 
@@
                   annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=.97,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
                   annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
                   annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=.97,label="Training",size=3.1,fontface="plain"),
+                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
                   theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
@@
 
-In addition to largely overlooking the potential for non-linear
-generalization to confound interpretations of training manipulations,
-the visuomotor skill learning literature also rarely considers
-alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures,
-instance or exemplar-based models have accounted for human behavior
-across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a]. As mentioned above, instance based accounts have been shown to perform well on a
-variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little
-attention within the subdomain of visuomotor skill learning focused on
-the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of
-varied training can be accounted for by between-group differences in
-similarity between training and testing throws. We first attempt to
-replicate previous work finding an advantage of varied training over
-constant training in a projectile launching task. We then examine the
-extent to which this advantage can be explained by an instance-based
-similarity model.
+In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
+Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
+As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
+However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
+
+The present work examines whether the commonly observed benefits of varied training can be accounted for by a theoretrically motivated measure of the similarity between training throws and the testing solution space.
+We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
+We then examine the extent to which this advantage can be explained by an instance-based similarity model.
 
@@
 
-To obtain an independent estimate of effect size, we identified previous
-investigations which included between-subjects contrasts of varied and
-constant conditions following training on an accuracy based projectile
-launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies,
-yielding a Cohens f =.43. The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009],
-2009) was then used to determine that a power of 80% requires a sample
-size of at least 23 participants per condition. All experiments reported
-in the present manuscript exceed this minimum number of participants per
-condition.
+To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
+We then averaged effects across these studies, yielding a Cohen's f =.43.
+The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009] was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
+All experiments reported in the present manuscript exceed this minimum number of participants per condition.
 
@@
 
-Participants were recruited from an undergraduate population that is 63%
-female and consists almost entirely of individuals aged 18-22 years. A
-total of 110 Indiana University psychology students participated in
-Experiment 1. We subsequently excluded 34 participants poor performance
-at one of the dependent measures of the task (2.5-3 standard deviations
-worse than the median subject at the task) or for displaying a pattern
-of responses that was clearly indicative of a lack of engagement with
-the task (e.g. simply dropping the ball on each trial rather than
-throwing it at the target), or for reporting that they completed the
-experiment on a phone or tablet device, despite the instructions not to
-use one of these devices. A total of 74 participants were retained for
-the final analyses, 35 in the varied group and 39 in the constant group.
+Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18 to 22 years.
+A total of 110 Indiana University psychology students participated in Experiment 1.
+We subsequently excluded 34 participants for poor performance on one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
+simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
+A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.
 
@@
 
-The experimental task was programmed in JavaScript, using packages from
-the Phaser physics engine (https://phaser.io) and the jsPsych library
-(de Leeuw, 2015). The stimuli, presented on a black background,
-consisted of a circular blue ball -- controlled by the participant via
-the mouse or trackpad cursor; a rectangular green target; a red
-rectangular barrier located between the ball and the target; and an
-orange square within which the participant could control the ball before
-releasing it in a throw towards the target. Because the task was
-administered online, the absolute distance between stimuli could vary
-depending on the size of the computer monitor being used, but the
-relative distance between the stimuli was held constant. Likewise, the
-distance between the center of the target, and the training and testing
-locations was scaled such that relative distances were preserved
-regardless of screen size. For the sake of brevity, subsequent mentions
-of this relative distance between stimuli, or the position where the
-ball landed in relation to the center of the target, will be referred to
-simply as distance. @fig-igasTask displays the layout of the task, as
-it would appear to a participant at the start of a trial, with the ball
-appearing in the center of the orange square. Using a mouse or trackpad,
-participants click down on the ball to take control of the ball,
-connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the
-confines of the orange square) and then launch the ball by releasing the
-cursor. If the ball does not land on the target, participants are
-presented with feedback in red text at the top right of the screen, on
-how many units away they were from the center of the target. If the ball
-was thrown outside of the boundary of the screen participants are given
-feedback as to how far away from the target center the ball would have
-been if it had continued its trajectory. If the ball strikes the barrier
-(from the side or by landing on top), feedback is presented telling
-participants to avoid hitting the barrier. If participants drag the ball
-outside of the orange square before releasing it, the trial terminates,
-and they are reminded to release the ball within the orange square. If
-the ball lands on the target, feedback is presented in green text,
-confirming that the target was hit, and presenting additional feedback
-on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of
-task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-![The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
+The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library [@deleeuwJsPsychJavaScriptLibrary2015].
+The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
+Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
+Likewise, the distance between the center of the target and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
+For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
+@fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square.
+Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor.
+Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
+If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target.
+If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
+If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier.
+If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square.
+If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
+
+[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+
+```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
+#| label: fig-IGAS_Methods
+#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square](../Assets/methodsFig1.png){#fig-igasTask}
+Participants were constrained to release the ball within the square
+
+# mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
+# plot_grid(mf,ncol=1)
+knitr::include_graphics(here::here("Assets/methodsFig1.png"))
+```
 
@@
 
-To prepare the data, we first removed trials that were not easily
-interpretable as performance indicators in our task. Removed trials
-included: 1) those in which participants dragged the ball outside of the
-orange starting box without releasing it, 2) trials in which
-participants clicked on the ball, and then immediately released it,
-causing the ball to drop straight down, 3) outlier trials in which the
-ball was thrown more than 2.5 standard deviations further than the
-average throw (calculated separately for each throwing position), and 4)
-trials in which the ball struck the barrier. The primary measure of
-performance used in all analyses was the absolute distance away from the
-center of the target. The absolute distance was calculated on every
-trial, and then averaged within each subject to yield a single
-performance score, for each position. A consistent pattern across
-training and testing phases in both experiments was for participants to
-perform worse from throwing positions further away from the target -- a
-pattern which we refer to as the difficulty of the positions. However,
-there were no interactions between throwing position and training
-conditions, allowing us to collapse across positions in cases where
-contrasts for specific positions were not of interest. All data
-processing and statistical analyses were performed in R version 4.03 (R
-Core Team, 2020). ANOVAs for group comparisons were performed using the
-rstatix package (Kassambara, 2021)****.
+To prepare the data, we first removed trials that were not easily interpretable as performance indicators in our task.
+Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier.
+The primary measure of performance used in all analyses was the absolute distance away from the center of the target.
+The absolute distance was calculated on every trial, and then averaged within each subject to yield a single performance score, for each position.
+A consistent pattern across training and testing phases in both experiments was for participants to perform worse from throwing positions further away from the target -- a pattern which we refer to as the difficulty of the positions.
+However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest.
+All data processing and statistical analyses were performed in R version 4.32 [@rcoreteamLanguageEnvironmentStatistical2020].
+ANOVAs for group comparisons were performed using the rstatix package [@kassambaraRstatixPipeFriendlyFramework2021a].
 
@@
 
-@fig-IGAS-Training1 below shows aggregate training performance binned into three
-stages representing the beginning, middle, and end of the training
-phase. Because the two conditions trained from target distances that
-were not equally difficult, it was not possible to directly compare
-performance between conditions in the training phase. Our focus for the
-training data analysis was instead to establish that participants did
-improve their performance over the course of training, and to examine
-whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided
-in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and
-condition as between-group factor. The analysis revealed a significant
-effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17,
-such that performance improved over the course of training There was no
-significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02,
-and no significant interaction between condition and training stage,
-F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
-
-```{r}
-#| label: fig-IGAS-Training1
+@fig-IGAS_Training1 below shows aggregate training performance binned into three stages representing the beginning, middle, and end of the training phase.
+Because the two conditions trained from target distances that were not equally difficult, it was not possible to directly compare performance between conditions in the training phase.
+Our focus for the training data analysis was instead to establish that participants did improve their performance over the course of training, and to examine whether there was any interaction between training stage and condition.
+Descriptive statistics for the intermittent testing phase are provided in the supplementary materials.
+
+We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor.
+The analysis revealed a significant effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training.
+There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02, and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
+
+```{r}
+#| label: fig-IGAS_Training1
 #| fig.cap: Training performance for varied and constant participants binned into three stages.
@@
 
-### Testing Phase
-
-In Experiment 1, a single constant-trained group was compared against a
-single varied-trained group. At the transfer phase, all participants
-were tested from 3 positions: 1) the positions(s) from their own
-training, 2) the training position(s) of the other group, and 3) a
-position novel to both groups. Overall, group performance was compared
-with a mixed type III ANOVA, with condition (varied vs. constant) as a
-between-subject factor and throwing location as a within-subject
-variable. The effect of throwing position was strong, F(3,213) = 56.12,
-p\<.001, η2G = .23. The effect of training condition was significant
-F(1,71)=8.19, p\<.01, η2G = .07. There was no significant interaction
-between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS-Testing1
+#### Testing Phase
+
+In Experiment 1, a single constant-trained group was compared against a single varied-trained group.
+At the transfer phase, all participants were tested from 3 positions: 1) the positions(s) from their own training, 2) the training position(s) of the other group, and 3) a position novel to both groups.
+Overall, group performance was compared with a mixed type III ANOVA, with condition (varied vs.
+constant) as a between-subject factor and throwing location as a within-subject variable.
+The effect of throwing position was strong, F(3,213) = 56.12, p\<.001, η2G = .23.
+The effect of training condition was significant F(1,71)=8.19, p\<.01, η2G = .07.
+There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.
+
+```{r}
+#| label: fig-IGAS_Testing1
 #| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
@@
 ```{r}
-#| label: tbl-IGAS-Table1
+#| label: tbl-IGAS_Table1
 #| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
@@
 
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
-
-#%>% kableExtra::kable_styling(position="left") 
-# %>%   
-#   kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
+kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
 
@@
 
-In Experiment 2, we sought to replicate our findings from Experiment 1
-with a new sample of participants, while also addressing the possibility
-of the pattern of results in Experiment 1 being explained by some
-idiosyncrasy of the particular training location of the constant group
-relative to the varied group. To this end, Experiment 2 employed the
-same basic procedure as Experiment 1, but was designed with six separate
-constant groups each trained from one of six different locations (400,
-500, 625, 675, 800, or 900), and a varied group trained from two
-locations (500 and 800). Participants in all seven groups were then
-tested from each of the 6 unique positions.
-
-## Methods
-
-### Participants
-
-A total of 306 Indiana University psychology students participated in
-Experiment 2, which was also conducted online. As was the case in
-experiment 1, the undergraduate population from which we recruited
-participants was 63% female and primarily composed of 18--22-year-old
-individuals. Using the same procedure as experiment 1, we excluded 98
-participants for exceptionally poor performance at one of the dependent
-measures of the task, or for displaying a pattern of responses
-indicative of a lack of engagement with the task. A total of 208
-participants were included in the final analyses with 31 in the varied
-group and 32, 28, 37, 25, 29, 26 participants in the constant groups
-training from location 400, 500, 625, 675, 800, and 900, respectively.
+In Experiment 2, we sought to replicate our findings from Experiment 1 with a new sample of participants, while also addressing the possibility of the pattern of results in Experiment 1 being explained by some idiosyncrasy of the particular training location of the constant group relative to the varied group.
+To this end, Experiment 2 employed the same basic procedure as Experiment 1, but was designed with six separate constant groups each trained from one of six different locations (400, 500, 625, 675, 800, or 900), and a varied group trained from two locations (500 and 800).
+Participants in all seven groups were then tested from each of the 6 unique positions.
+
+### Methods
+
+#### Participants
+
+A total of 306 Indiana University psychology students participated in Experiment 2, which was also conducted online.
+As was the case in Experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18--22-year-old individuals.
+Using the same procedure as Experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task.
+A total of 208 participants were included in the final analyses with 31 in the varied group and 32, 28, 37, 25, 29, 26 participants in the constant groups training from location 400, 500, 625, 675, 800, and 900, respectively.
 All participants were compensated with course credit.
 
-### Task and Procedure
-
-The task of Experiment 2 was identical to that of Experiment 1, in all
-but some minor adjustments to the height of the barrier, and the
-relative distance between the barrier and the target. Additionally, the
-intermittent testing trials featured in experiment 1 were not utilized
-in experiment 2, and all training and testing trials were presented with
-feedback. An abbreviated demo of the task used for Experiment 2 can be
-found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
-
-The procedure for Experiment 2 was also quite similar to experiment 1.
-Participants completed 140 training trials, all of which were from the
-same position for the constant groups and split evenly (70 trials each -
-randomized) for the varied group. In the testing phase, participants
-completed 30 trials from each of the six locations that had been used
-separately across each of the constant groups during training. Each of
-the constant groups thus experience one trained location and five novel
-throwing locations in the testing phase, while the varied group
-experiences 2 previously trained, and 4 novel locations.
-
-## Results
+#### Task and Procedure
+
+The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target.
+Additionally, the intermittent testing trials featured in experiment 1 were not utilized in Experiment 2.
+An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
+
+The procedure for Experiment 2 was also quite similar to Experiment 1.
+Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group.
+In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training.
+Each of the constant groups thus experienced one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
+
+### Results
 
@@
 
-After confirming that condition and throwing position did not have any
-significant interactions, we standardized performance within each
-position, and then average across position to yield a single performance
-measure per participant. This standardization did not influence our
-pattern of results. As in experiment 1, we performed type III ANOVA's
-due to our unbalanced design, however the pattern of results presented
-below is not altered if type 1 or type III tests are used instead. The
-statistical software for the primary analyses was the same as for
-experiment 1. Individual learning rates in the testing phase, compared
-between groups in the supplementary analyses, were fit using the TEfit
-package in R [@cochraneTEfitsNonlinearRegression2020].
+After confirming that condition and throwing position did not have any significant interactions, we standardized performance within each position, and then average across position to yield a single performance measure per participant.
+This standardization did not influence our pattern of results.
+As in Experiment 1, we performed type III ANOVAs due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.
+The statistical software for the primary analyses was the same as for Experiment 1.
+Individual learning rates in the testing phase, compared between groups in the supplementary analyses, were fit using the TEfit package in R [@cochraneTEfitsNonlinearRegression2020].
 
@@
 transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% convert_as_factor(testHalf)
+  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
 
@@
 transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% convert_as_factor(novel,extrapolate)
+transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
 
@@
 Error bars indicate standard error of the mean.
-#| fig.width: 11
-#| fig.height: 10
+#| fig-width: 11
+#| fig-height: 8
 
@@
 
-e2train1 / e2train2
+e2train1/e2train2
 
@@
 \
+\
+\
 
@@
 
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
-
-#  %>% kableExtra::kable_styling(position="left") %>% 
-#   kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-Next, we compared the testing performance of constant and varied groups
-from only positions that participants had not encountered during
-training. Constant participants each had 5 novel positions, whereas
-varied participants tested from 4 novel positions (400,625,675,900). We
-first standardized performance within in each position, and then
-averaged across positions. Here again, we found a significant effect of
-condition (constant vs. varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ =
-.02 .
+kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+
+```
+
+Next, we compared the testing performance of constant and varied groups from only positions that participants had not encountered during training.
+Constant participants each had 5 novel positions, whereas varied participants tested from 4 novel positions (400,625,675,900).
+We first standardized performance within in each position, and then averaged across positions.
+Here again, we found a significant effect of condition (constant vs.
+varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ = .02 .
 
@@
 
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
-
-# %>% kableExtra::kable_styling(position="left") %>% 
-#   kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
-
-Finally, corresponding to the comparison of position 760 from experiment
-1, we compared the test performance of the varied group against the
-constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis
-omitted two constant groups that trained from positions 500 or 800 as
-those positions were not novel to the varied group). @fig-e2test1 displays
-the particular subset of comparisons utilized for this analysis. Again,
-we standardized performance within each position before performing the
-analyses on the aggregated data. In this case, the effect of condition
-did not reach statistical significance F(1,149)=3.14, p=.079,
-$\eta^{2}_G$ = .02. Table 4 provides descriptive statistics.
+kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+```
+
+Finally, corresponding to the comparison of position 760 from Experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained.
+Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group).
+@fig-e2test1 displays the particular subset of comparisons utilized for this analysis.
+Again, we standardized performance within each position before performing the analyses on the aggregated data.
+In this case, the effect of condition did not reach statistical significance F(1,149)=3.14, p=.079, $\eta^{2}_G$ = .02.
+Table 4 provides descriptive statistics.
 
@@
 \
+\
 
@@
 
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
-
-#  %>% kableExtra::kable_styling(position="left") %>% 
-#   kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-### Discussion
-
-The results of experiment 2 largely conform to the findings of
-experiment 1. Participants in both varied and constant conditions
-improved at the task during the training phase. We did not observe the
-common finding of training under varied conditions producing worse
-performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been
-suggested to relate to the subsequent benefits of varied training in
-retention and generalization testing [@soderstromLearningPerformanceIntegrative2015]. However
-our finding of no difference in training performance between constant
-and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the
-constant conditions in both a general comparison, and in an analysis
-limited to novel throwing positions. The observed benefit of varied over
-constant training echoes the findings of many previous visuomotor skill
-learning studies that have continued to emerge since the introduction of
-Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this
-pattern in a computerized task [@seowTransferEffectsVaried2019]. One departure from
-the experiment 1 findings concerns the pattern wherein the varied group
-outperformed the constant group even from the training position of the
-constant group, which was significant in experiment 1, but did not reach
-significance in experiment 2. Although this pattern has been observed
-elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], 
-the overall evidence for this effect appears to be far weaker than for
-the more general benefit of varied training in conditions novel to all
-training groups.
-
-### Computational Model
-
-Controlling for the similarity between training and testing The primary
-goal of Experiment 2 was to examine whether the benefits of variability
-would persist after accounting for individual differences in the
-similarity between trained and tested throwing locations. To this end,
-we modelled each throw as a two-dimensional point in the space of x and
-y velocities applied to the projectile at the moment of release. For
-each participant, we took each individual training throw, and computed
-the similarity between that throw and the entire population of throws
-within the solution space for each of the 6 testing positions. We
-defined the solution space empirically as the set of all combinations of
-x and y throw velocities that resulted in hitting the target. We then
-summed each of the trial-level similarities to produce a single
-similarity for each testing position score relating how the participant
-threw the ball during training and the solutions that would result in
-target hits from each of the six testing positions -- thus resulting in
-six separate similarity scores for each participant. @fig-taskSpace1
-visualizes the solution space for each location and illustrates how
-different combinations of x and y velocity result in successfully
-striking the target from different launching positions. As illustrated
-in @fig-taskSpace1, the solution throws represent just a small fraction of the
-entire space of velocity combinations used by participants throughout
-the experiment.
-
-```{r}
-#| label: fig-taskSpace1
-#| fig.cap: A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-Figure 8B shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig.height: 10
-#| fig.width: 11
+kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+
+```
+
+### Experiment 2 Discussion
+
+The results of Experiment 2 largely conform to the findings of Experiment 1.
+Participants in both varied and constant conditions improved at the task during the training phase.
+We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing [@soderstromLearningPerformanceIntegrative2015].
+However our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
+
+In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions.
+The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
+We also join a much smaller set of research to observe this pattern in a computerized task [@seowTransferEffectsVaried2019].
+One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
+Although this pattern has been observed elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
+
+## Computational Model
+
+*Controlling for the similarity between training and testing.* The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations.
+To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release.
+For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions.
+We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target.
+We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions -- thus resulting in six separate similarity scores for each participant.
+@fig-taskSpace visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions.
+As illustrated in @fig-taskSpace, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.
+
+```{r}
+#| label: fig-taskSpace
+#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+This empirical solution space was compiled from all of the participants in Experiment 2.
+B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+#| fig-width: 11
+#| fig-height: 9
+#| 
 taskspace <- e2 %>% filter(AbsDistFromCenter<900)
@@
 
-ss / fs
-
-```
-
-For each individual trial, the Euclidean distance (Equation 1) was
-computed between the velocity components (x and y) of that trial and the
-velocity components of each individual solution throw for each of the 6
-positions from which participants would be tested in the final phase of
-the study. The P parameter in Equation 1 is set equal to 2, reflecting a
-Gaussian similarity gradient. Then, as per an instance-based model of
-similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were
-multiplied by a sensitivity parameter, c, and then exponentiated to
-yield a similarity value. The parameter c controls the rate with which
-similarity-based generalization drops off as the Euclidean distance
-between two throws in x- and y-velocity space increases. If c has a
-large value, then even a small difference between two throws' velocities
-greatly decreases the extent of generalization from one to the other. A
-small value for c produces broad generalization from one throw to
-another despite relatively large differences in their velocities. The
-similarity values for each training individual throw made by a given
-participant were then summed to yield a final similarity score, with a
-separate score computed for each of the 6 testing positions. The final
-similarity score is construable as index of how accurate the throws a
-participant made during the training phase would be for each of the
-testing positions.
-
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J}
-(e^{-c^\cdot d^{p}_{i,j}}) $$
+library(patchwork)
+ss/fs
+
+```
+
+For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.
+The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient.
+Then, as per an instance-based model of similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value.
+The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.
+If c has a large value, then even a small difference between two throws' velocities greatly decreases the extent of generalization from one to the other.
+A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities.
+The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions.
+The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.
+
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
 
@@
 
-A simple linear regression revealed that these similarity scores were
-significantly predictive of performance in the transfer stage, t
-=-15.88, p\<.01, $r^2$=.17, such that greater similarity between
-training throws and solution spaces for each of the test locations
-resulted in better performance. We then repeated the group comparisons
-above while including similarity as a covariate in the model. Comparing
-the varied and constant groups in testing performance from all testing
-positions yielded a significant effect of similarity, F(1, 205)=85.66,
-p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition
-(varied vs. constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03. The
-group comparison limited to only novel locations for the varied group
-pit against trained location for the constant group resulted in a
-significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$
-=.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$
-=.07. For all comparisons, the pattern of results was consistent with
-the initial findings from experiment 2, with the varied group still
-performing significantly better than the constant group.
-
-#### Fitting model parameters separately by group
-
-To directly control for similarity in Experiment 2, we developed a
-model-based measure of the similarity between training throws and
-testing conditions. This similarity measure was a significant predictor
-of testing performance, e.g., participants whose training throws were
-more similar to throws that resulted in target hits from the testing
-positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level
-benefits of varied training, which remained significant in our linear
-model predicting testing performance after similarity was added to the
-model. However, previous research has suggested that participants may
-differ in their level of generalization as a function of prior
-experience, and that such differences in generalization gradients can be
-captured by fitting the generalization parameter of an instance-based
-model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization
-will increase when a rational agent encounters a wider variety of
-examples. Following these leads, we assume that in addition to learning
-the task itself, participants are also adjusting how generalizable their
-experience should be. Varied versus constant participants may be
-expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the
-instance-based model (in the present case, the c parameter) can be
-allowed to vary between the two groups to reflect the tendency of
-learners to adaptively tune the extent of their generalization. One
-specific hypothesis is that people adaptively set a value of c to fit
-the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006]. If one's training experience is relatively
-variable, as with the variable training condition, then one might infer
-that future test situations will also be variable, in which case a low
-value of c will allow better generalization because generalization will
-drop off slowly with training-to-testing distance. Conversely, if one's
-training experience has little variability, as found in the constant
-training conditions, then one might adopt a high value of c so that
-generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based
-model of similarity fit against a modified model which separately fits
-the generalization parameter, c, to varied and constant participants. To
-perform this parameter fitting, we used the optim function in R, and fit
-the model to find the c value(s) that maximized the correlation between
-similarity and testing performance.
-
-Both models generate distinct similarity values between training and
-testing locations. Much like the analyses in Experiment 2, these
-similarity values are regressed against testing performance in models of
-the form shown below. As was the case previously, testing performance is
-defined as the mean absolute distance from the center of the target
-(with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant
-predictor of testing performance (p\<.01). Of greater interest is the
-difference between linear model 2, in which similarity is computed from
-a single c value fit from all participants (Similarity1c), with linear
-model 4, which fits the c parameter separately between groups
-(Similarity2c). In linear model 2, the effect of training group remains
-significant when controlling for Similarity1c (p\<.01), with the varied
-group still performing significantly better. However, in linear model 4
-the addition of the Similarity2c predictor results in the effect of
-training group becoming nonsignificant (p=.40), suggesting that the
-effect of varied vs. constant training is accounted for by the
-Similarity2c predictor. Next, to further establish a difference between
-the models, we performed nested model comparisons using ANOVA, to see if
-the addition of the training group parameter led to a significant
-improvement in model performance. In the first comparison, ANOVA(Linear
-Model 1, Linear Model 2), the addition of the training group predictor
-significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear
-Model 4) found no improvement in model performance with the addition of
-the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the
-adjusted Similarity2c model had more predictive power than those
-generated from the original Similarity1c model. Using the BIC function
-in R, we compared BIC values between linear model 1 (BIC=14604.00) and
-linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
-a modest advantage for predicting performance using a similarity measure
-computed with two c values over similarity computed with a single c
-value. When fit with separate c values, the best fitting c parameters
-for the model consistently optimized such that the c value for the
-varied group (c=.00008) was smaller in magnitude than the c value for
-the constant group(c= .00011). Recall that similarity decreases as a
-Gaussian function of distance (equation 1 above), and a smaller value of
-c will result in a more gradual drop-off in similarity as the distance
-between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which
-assumes equivalent generalization gradients between constant and varied
-trained participants is unable to account for the extent of benefits of
-varied over constant training observed at testing. The evidence for this
-in the comparative model fits is that when a varied/constant dummy-coded
-variable for condition is explicitly added to the model, the variable
-adds a significant contribution to the prediction of test performance,
-with the variable condition yielding better performance than the
-constant conditions. However, if the instance-based generalization model
-is modified to assume that the training groups can differ in the
-steepness of their generalization gradient, by incorporating a separate
-generalization parameter for each group, then the instance-based model
-can account for our experimental results without explicitly taking
-training group into account. Henceforth this model will be referred to
-as the Instance-based Generalization with Adaptive Similarity (IGAS)
-model.
-
-### General Discussion
+A simple linear regression revealed that these similarity scores were significantly predictive of performance in the transfer stage, t =-15.88, p\<.01, $r^2$=.17, such that greater similarity between training throws and solution spaces for each of the test locations resulted in better performance.
+We then repeated the group comparisons above while including similarity as a covariate in the model.
+Comparing the varied and constant groups in testing performance from all testing positions yielded a significant effect of similarity, F(1, 205)=85.66, p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition (varied vs.
+constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03.
+The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$ =.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$ =.07.
+For all comparisons, the pattern of results was consistent with the initial findings from Experiment 2, with the varied group still performing significantly better than the constant group.
+
+### Fitting model parameters separately by group
+
+To directly control for similarity in Experiment 2, we developed a model-based measure of the similarity between training throws and testing conditions.
+This similarity measure was a significant predictor of testing performance, e.g., participants whose training throws were more similar to throws that resulted in target hits from the testing positions, tended to perform better during the testing phase.
+Importantly, the similarity measure did not explain away the group-level benefits of varied training, which remained significant in our linear model predicting testing performance after similarity was added to the model.
+However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
+Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
+Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
+Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
+To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
+One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
+If one's training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
+Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+
+To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c, to varied and constant participants.
+To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
+
+Both models generate distinct similarity values between training and testing locations.
+Much like the analyses in Experiment 2, these similarity values are regressed against testing performance in models of the form shown below.
+As was the case previously, testing performance is defined as the mean absolute distance from the center of the target (with a separate score for each participant, from each position).
+
+Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p\<.01).
+Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the c parameter separately between groups (Similarity2c).
+In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p\<.01), with the varied group still performing significantly better.
+However, in linear model 4 the addition of the Similarity2c predictor results in the effect of training group becoming nonsignificant (p=.40), suggesting that the effect of varied vs.
+constant training is accounted for by the Similarity2c predictor.
+Next, to further establish a difference between the models, we performed nested model comparisons using ANOVA, to see if the addition of the training group parameter led to a significant improvement in model performance.
+In the first comparison, ANOVA(Linear Model 1, Linear Model 2), the addition of the training group predictor significantly improved the performance of the model (F=22.07, p\<.01).
+However, in the second model comparison, ANOVA (Linear model 3, Linear Model 4) found no improvement in model performance with the addition of the training group predictor (F=1.61, p=.20).
+
+Finally, we sought to confirm that similarity values generated from the adjusted Similarity2c model had more predictive power than those generated from the original Similarity1c model.
+Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
+The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
+When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
+Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
+
+In summary, our modeling suggests that an instance-based model which assumes equivalent generalization gradients between constant and varied trained participants is unable to account for the extent of benefits of varied over constant training observed at testing.
+The evidence for this in the comparative model fits is that when a varied/constant dummy-coded variable for condition is explicitly added to the model, the variable adds a significant contribution to the prediction of test performance, with the variable condition yielding better performance than the constant conditions.
+However, if the instance-based generalization model is modified to assume that the training groups can differ in the steepness of their generalization gradient, by incorporating a separate generalization parameter for each group, then the instance-based model can account for our experimental results without explicitly taking training group into account.
+Henceforth this model will be referred to as the Instance-based Generalization with Adaptive Similarity (IGAS) model.
+
+## Project 1 General Discussion
 
 Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing
-task. Generalization was observed in both constant and varied
-participants, in that both groups tended to perform better at novel
-positions in the testing phase than did participants who started with
-those positions in the training phase. However, varied trained
-participants consistently performed better than constant trained
-participants, in terms of both the testing phase in general, and in a
-comparison that only included untrained positions. We also found some
-evidence for the less commonly observed pattern wherein varied-trained
-participants outperform constant-trained participants even from
-conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978]. In experiment 1 varied
-participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but
-became significant after controlling for the similarity measure that
-incorporates only a single value for the steepness of similarity-based
-generalization (c). Furthermore, we showed that the general pattern of
-results from Experiment 2 could be parsimoniously accommodated by an
-instance-based similarity model, but only with the assumption that
-constant and varied participants generalize their training experience to
-different degrees. Our results thus suggest that the benefits of
-variation cannot be explained by the varied-trained participants simply
-covering a broader range of the task space. Rather, the modeling
-suggests that varied participants also learn to adaptively tune their
-generalization function such that throwing locations generalize more
-broadly to one another than they do in the constant condition. A
-learning system could end up adopting a higher c value in the constant
-than variable training conditions by monitoring the trial-by-trial
-variability of the training items. The c parameter would be adapted
-downwards when adjacent training items are dissimilar to each other and
-adapted upwards when adjacent training items are the same. In this
-fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation
-has a high amount variability, then the learner should be predisposed
-toward thinking that subsequent test items will also show considerable
-variability, in which case generalization gradients should be broad, as
-is achieved by low values for c.
-
-Also of interest is whether the IGAS model can predict the pattern of
-results wherein the varied condition outperforms the constant condition
-even from the position on which the constant condition trained. Although
-our models were fit using all of the Experiment 2 training and testing
-data, not just that of the identity comparisons, in @fig-Toy-Model2 we
-demonstrate how a simplified version of the IGAS model could in
-principle produce such a pattern. In addition to the assumption of
-differential generalization between varied and constant conditions, our
-simplified model makes explicit an assumption that is incorporated into
-the full IGAS model -- namely that even when being tested from a
-position identical to that which was trained, there are always some
-psychological contextual differences between training and testing
-throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model2
+variability hypothesis in a simple, computerized projectile throwing task.
+Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
+However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions.
+We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978].
+In Experiment 1 varied participants performed significantly better on this identity comparison.
+In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
+Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
+Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
+Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
+A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
+The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
+In this fashion, contextually appropriate c values could be empirically learned.
+This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
+
+Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained.
+Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in @fig-Toy-Model-dis we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern.
+In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model -- namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.
+
+```{r}
+#| label: fig-Toy-Model-dis
 #| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
@@
 
-gtitle="Figure 9."
-title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-
-```
-
-As mentioned above, the idea that learners flexibly adjust their
-generalization gradient based on prior experience does have precedent in
-the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed
-that a simple manipulation of background knowledge during a
-categorization test resulted in participants generalizing their training
-experience more or less broadly, and moreover that such a pattern could
-be captured by allowing the generalization parameter of an
-instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted
-for generalization behavior in cases where participants have been
-trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006]. However, to the best of our
-knowledge, IGAS is the first instance-based similarity model that has
-been put forward to account for the effect of varied training in a
-visuomotor skill task. Although IGAS was inspired by work in the domain
-of category learning, its success in a distinct domain may not be
-surprising in light of the numerous prior observations that at least
-certain aspects of learning and generalization may operate under common
-principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning
-implementations of instance-based models in several ways. One such
-difference is the nature of the training instances that are assumed to
-be stored. In category learning studies, instances are represented as
-points in a multidimensional space of all of the attributes that define
-a category item (e.g. size/color/shape). Rather than defining instances
-in terms of what stimuli learners experience, our approach assumes that
-stored, motor instances reflect how they act, in terms of the velocity
-applied to the ball on each throw. An advantage of many motor learning
-tasks is the relative ease with which task execution variables can be
-directly measured (e.g. movement force, velocity, angle, posture) in
-addition to the decision and response time measures that typically
-exhaust the data generated from more classical cognitive tasks. Of
-course, whether learners actually are storing each individual motor
-instance is a fundamental question beyond the scope of the current work
--- though as described in the introduction there is some evidence in
-support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly
-noteworthy instance-based model of sensory-motor behavior is the
-Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995]. Knowledge II explicitly defines instances as
-postures (joint combinations), and is thus far more detailed than IGAS
-in regards to the contents of stored instances. Knowledge II also
-differs from IGAS in that learning is accounted for by both the
-retrieval of stored postures, and the generation of novel postures via
-the modification of retrieved postures. A promising avenue for future
-research would be to combine the adaptive similarity mechanism of IGAS
-with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on
-the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].  In this task, participants observe a series of lamps
-lighting up consecutively, and attempt to time a button press with the
-onset of the final lamp. The design consisted of four separate constant
-groups, each training from a single lighting velocity, and a single
-varied group training with all four of the lighting velocities used by
-the individual constant groups. Participants were then split into four
-separate testing conditions, each of which were tested from a single
-novel lighting velocity of varying distance from the training
-conditions. The result of primary interest was that all participants
-performed worse as the distance between training and testing velocity
-increased -- a typical generalization decrement. However, varied
-participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in
-a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are
-similar to our own, our work is novel in that we account for our results
-with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their
-separate constant groups together may result in similarity confounds
-between varied and constant conditions that leaves their study open to
-methodological criticisms, especially in light of related work which
-demonstrated that the extent to which varied training may be beneficial
-can depend on whether the constant group they are compared against
-trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987]. Our study alleviates such concerns by explicitly controlling for
-similarity.
-
-## Limitations
-
-A limitation of this study concerns the ordering of the testing/transfer
-trials at the conclusion of both experiments. Participants were tested
-from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
-random, intermixed order. Because the varied group was trained from two
-positions that were also randomly ordered, they may have benefited from
-experience with this type of sequencing, whereas the constant groups had
-no experience with switching between positions trial to trial. This
-concern is somewhat ameliorated by the fact that the testing phase
-performance of the constant groups from their trained position was not
-significantly worse than their level of performance at the end of the
-training phase, suggesting that they were not harmed by random ordering
-of positions during testing. It should also be noted that the
-computerized task utilized in the present work is relatively simple
-compared to many of the real-world tasks utilized in prior research. It
-is thus conceivable that the effect of variability in more complex tasks
-is distinct from the process put forward in the present work. An
-important challenge for future work will be to assess the extent to
-which IGAS can account for generalization in relatively complex tasks
-with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning
-to use an approach such as multidimensional scaling so as to transform
-the stimuli from the physical dimensions used in the particular task
-into the psychological dimensions more reflective of the actual human
-representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987]. Such scaling typically entails having participants rate the similarity between individual items
-and using these similarity judgements to then compute the psychological
-distances between stimuli, which can then be fed into a subsequent
-model. In the present investigation, there was no such way to scale the
-x and y velocity components in terms of the psychological similarity,
-and thus our modelling does rely on the assumption that the
-psychological distances between the different throwing positions are
-proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to
-that between 800 and 900). However, an advantage of our approach is that
-we are measuring similarity in terms of how participants behave
-(applying a velocity to the ball), rather than the metric features of
-the task stimuli.
-
-## Conclusion
-
-Our experiments demonstrate a reliable benefit of varied training in a
-simple projectile launching task. Such results were accounted for by an
-instance-based model that assumes that varied training results in the
-computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable
-approach towards better understanding skill generalization and transfer.
+#gtitle="Figure 9."
+#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
+#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
+p1 <- (ip1+ip2) / (ip3+ip4)
+
+p1
+
+```
+
+As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
+@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
+The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
+However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
+Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
+
+Our modelling approach does differ from category learning implementations of instance-based models in several ways.
+One such difference is the nature of the training instances that are assumed to be stored.
+In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g.
+size/color/shape).
+Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
+An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
+movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
+Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
+A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
+Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
+Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
+A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
+
+Our findings also have some conceptual overlap with an earlier study on the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].
+In this task, participants observe a series of lamps lighting up consecutively, and attempt to time a button press with the onset of the final lamp.
+The design consisted of four separate constant groups, each training from a single lighting velocity, and a single varied group training with all four of the lighting velocities used by the individual constant groups.
+Participants were then split into four separate testing conditions, each of which were tested from a single novel lighting velocity of varying distance from the training conditions.
+The result of primary interest was that all participants performed worse as the distance between training and testing velocity increased -- a typical generalization decrement.
+However, varied participants showed less of a decrement than did constant participants.
+The authors take this result as evidence that varied training results in a less-steep generalization gradient than does constant training.
+Although the experimental conclusions of Catalano and Kleiner are similar to our own, our work is novel in that we account for our results with a cognitive model, and without assuming the formation of a schema.
+Additionally, the way in which Catalano and Kleiner collapse their separate constant groups together may result in similarity confounds between varied and constant conditions that leaves their study open to methodological criticisms, especially in light of related work which demonstrated that the extent to which varied training may be beneficial can depend on whether the constant group they are compared against trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987].
+Our study alleviates such concerns by explicitly controlling for similarity.
+
+### Limitations
+
+A limitation of this study concerns the ordering of the testing/transfer trials at the conclusion of both experiments.
+Participants were tested from each separate position (4 in Experiment 1, 6 in Experiment 2) in a random, intermixed order.
+Because the varied group was trained from two positions that were also randomly ordered, they may have benefited from experience with this type of sequencing, whereas the constant groups had no experience with switching between positions trial to trial.
+This concern is somewhat ameliorated by the fact that the testing phase performance of the constant groups from their trained position was not significantly worse than their level of performance at the end of the training phase, suggesting that they were not harmed by random ordering of positions during testing.
+It should also be noted that the computerized task utilized in the present work is relatively simple compared to many of the real-world tasks utilized in prior research.
+It is thus conceivable that the effect of variability in more complex tasks is distinct from the process put forward in the present work.
+An important challenge for future work will be to assess the extent to which IGAS can account for generalization in relatively complex tasks with far more degrees of freedom.
+
+It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987].
+Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
+In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g.
+the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
+However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
+
+### Conclusion
+
+Our experiments demonstrate a reliable benefit of varied training in a simple projectile launching task.
+Such results were accounted for by an instance-based model that assumes that varied training results in the computation of a broader similarity-based generalization gradient.
+Instance-based models augmented with this assumption may be a valuable approach towards better understanding skill generalization and transfer.
+
+{{< pagebreak >}}
 
@@
 
-```{r}
-test <- readRDS(here::here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
-#options(brms.backend="cmdstanr",mc.cores=4)
-e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
-testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
-  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
-```
-
-# Introduction
-
-In project 1, I applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
-In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-Project 2 also places a greater emphasis on extrapolation performance following training.
-Although varied training has often been purported to be particularly beneficial for generalization or transfer, few experiments have compared varied and constant training in contexts with unambiguous extrapolation testing.
-
-## Function Learning and Extrapolation
+## Introduction
+
+A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
+One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
+The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
+The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022].
+The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
+
+### Function Learning and Extrapolation
 
 The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
 
@@
 
+### Variability and Function Learning
+
+The influence of variability on function learning tasks has received relatively little attention.
+The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
+They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
+
+In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
+The shapes ranged from very spiky to completely circular at the extreme ends of the space.
+Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
+Learning was significantly slower in the higher variation group.
+However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
+The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
+Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
+However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
+
 ```{r}
@@
 #| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
+#| echo: false
 #| fig-width: 10
+#| cache: false 
+# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+#   stringr, here,conflicted, patchwork, knitr)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+
+#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
 source(here::here("Functions","deLosh_data.R"))
+#source(here::here("Functions","Display_Functions.R"))
 
@@
 
-# Methods
-
-## Participants
-
-Data was collected from 647 participants (after exclusions).
-The results shown below consider data from subjects in our initial experiment, which consisted of 196 participants (106 constant, 90 varied).
-The follow-up experiments entailed minor manipulations: 1) reversing the velocity bands that were trained on vs.
-novel during testing; 2) providing ordinal rather than numerical feedback during training (e.g.
-correct, too low, too high).
-The data from these subsequent experiments are largely consistently with our initial results shown below.
-
-## Task
-
-We developed a novel visuomotor extrapolation task, termed the Hit The Wall task, wherein participants learned to launch a projectile such that it hit a rectangle at the far end of the screen with an appropriate amount of force.
-Although the projectile had both x and y velocity components, only the x-dimension was relevant for the task.  [Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}
-
-## Procedure
-
-The HTW task involved launching projectiles to hit a target displayed on the computer screen.
+### Overview Of Present Study
+
+The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
+To the best of our knowledge, this research is the first to employ the classic constant vs.
+varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
+Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
+
+To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
+Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to examine the ability of these influential models of function learning to account for both the group level and individual level data.
+
+## Experiment 1
+
+### Methods
+
+*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
+Participants were randomly assigned to one of two training conditions: varied training or constant training.
+
+*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
+The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
+The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
+band 800-1000).
+During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
+Participants were instructed that only the x velocity component of the ball was relevant to the task.
+The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
+
+```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
+#| label: fig-htw-task
+#| fig-cap: The Hit the wall task.
+Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
+The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
+#| eval: true
+#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
+knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
+
+```
+
+*Procedure.* All participants completed the task online.
+Participants were provided with a description of the experiment and indicated informed consent.
+@fig-design-e1 illustrates the general procedure.
 Participants completed a total of 90 trials during the training stage.
 In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-In contrast, participants in the constant training condition encountered only one velocity band (800-1000).
-
-During the training stage, participants in both conditions also completed "no feedback" trials, where they received no information about their performance.
-These trials were randomly interleaved with the regular training trials.
-
-Following the training stage, participants proceeded to the testing stage, which consisted of three phases.
-In the first phase, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-
-In the second phase of testing, participants completed "no-feedback" testing from the three velocity bands used during the training stage (800-1000, 1000-1200, and 1200-1400).
+Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
+
+Following the training stage, participants proceeded immediately to the testing stage.
+Participants were tested from all six velocity bands, in two separate stages.
+In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
+Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
 In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-
-The third and final phase of testing involved "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 10 trials.
-Participants received feedback on their performance during this phase.
-
-Throughout the experiment, participants' performance was measured by calculating the distance between the produced x-velocity of the projectiles and the closest edge of the current velocity band.
-Lower distances indicated better performance.
-
-After completing the experiment, participants were debriefed and provided with an opportunity to ask questions about the study.
-
+The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
+A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
+
+::: {.content-visible unless-format="markdown"}
 ```{dot}
@@
 //| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 6.0
+//| fig-width: 7.0
 //| fig-height: 2.5
 //| fig-responsive: false
-
+//| echo: false  
+///| eval: !expr out_type 
+/////| column: screen-inset-right
 digraph {
@@
 }
-
-```
-
-## Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.31 @rcoreteamLanguageEnvironmentStatistical2020.
+```
+:::
+
+```{r}
+
+# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+#   stringr, here,conflicted, patchwork, knitr)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+e1 <- readRDS(here("data/e1_08-21-23.rds")) 
+e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
+testE1 <- e1 |> filter(expMode2 == "Test")
+nbins=5
+trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
+    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
+trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
+trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
+```
+
+### Analyses Strategy
+
+All data processing and statistical analyses were performed in R version 4.32 [@rcoreteamLanguageEnvironmentStatistical2020].
 To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
+Model fitting was performed with the brms package in R [@burknerBrmsPackageBayesian2017], and descriptive stats and tables were extracted with the BayestestR package [@makowskiBayestestRDescribingEffects2019].
 Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as circumventing convergence issues common to the frequentist analogues of our mixed models.
-For each model, we report the median values of the posterior distribution, and 95% credible intervals.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 of which were discarded as warmup chains.
-Rhat values were generally within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
+Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
+
+Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
+Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
 We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
-
-We compared varied and constant performance across two measures, deviation and discrimination.
-Deviation was quantified as the absolute deviation from the nearest boundary of the velocity band, or set to 0 if the throw velocity fell anywhere inside the target band.
-Thus, when the target band was 600-800, throws of 400, 650, and 1100 would result in deviation values of 200, 0, and 300, respectively.
-Discrimination was measured by fitting a linear model to the testing throws of each subjects, with the lower end of the target velocity band as the predicted variable, and the x velocity produced by the participants as the predictor variable.
-Participants who reliably discriminated between velocity bands tended to have positive slopes with values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-```{r}
-#| label: tbl-e1-test-nf-deviation
-#| tbl-cap: "Testing Deviation - Empirical Summary"
-#| tbl-subcap:
-#|   - "Full datasets"
-#|   - "Intersection of samples with all labels available"
-#| layout-ncol: 1
-
-result <- test_summary_table(test, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-
-result$constant |>kable(booktabs = TRUE,
-                        linesep = "\\addlinespace[0.5em]",
-                        caption = paste("Summary of Deviation- Constant"))
-# |>
-#   kable_styling(font_size = ifelse(fmt_out == "latex", 8.5, NA))
-
-result$varied |> kable(booktabs = TRUE,
-                        linesep = "\\addlinespace[0.5em]",
-                        caption = paste("Summary of Deviation- Varied"))
-
-```
-
-## Results
-
-### Testing Phase - No feedback.
-
-In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
-
-#### Deviation From Target Band
-
-Descriptive summaries testing deviation data are provided in @tbl-e1-test-nf-deviation and @fig-e1-test-dev.
-To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
-The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
-
-```{=tex}
-\begin{equation}
-dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
-\end{equation}
-```
+For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
+
+::: {#tbl-brms-models}
+| Group Comparison         | Code                                                        | Data                 |
+| ------------------------ | ----------------------------------------------------------- | -------------------- |
+| End of Training Accuracy | `` brm(Abs. Deviation ~ condit) ``                                    | Final Training Block |
+| Test Accuracy            | `` brm(Abs. Deviation ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
+| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
+
+: **Statistical Model Specifications**.
+The specifications for the bayesian regression models used in the analyses of each of the 3 experiments.
+Comparisons of accuracy use abosulte deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
+:::
+\
+
+In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
+extrapolation bands); 3) extent of discrimination between all six testing bands.
+We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
+Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
+The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
+Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
+
+### Results
+
+```{r}
+#| label: fig-e1-train-dev
+#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
+p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
+    stat_summary(geom = "line", fun = mean) +
+    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
+    facet_wrap(~vb)+
+    scale_x_continuous(breaks = seq(1, nbins + 1)) +
+    theme(legend.title=element_blank()) + 
+    labs(y = "Absolute Deviation", x="Training Block") 
+#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
+p1
+```
+
+```{r}
+##| label: tbl-e1-train-dist
+##| tbl-cap: "Experiment 1 - Learning curves. "
+##| output: asis
+
+bmm_e1_train<- trainE1_max %>% 
+  brm(dist ~ condit, 
+      file=here("data/model_cache/e1_train_deviation"),
+      data = .,
+      iter = 2000,
+      chains = 4,
+      control = list(adapt_delta = .94, max_treedepth = 13))
+mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
+colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
+
+# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
+#   tibble::remove_rownames() |> 
+#   mutate(Term = stringr::str_remove(Term, "b_")) |>
+#    kable(booktabs = TRUE)
+
+cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
+```
+
+::: {#tbl-e1-train-dist}
+
+| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
+|:-------------|---------:|--------------:|--------------:|----:|
+| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
+| conditVaried |    79.64 |         57.92 |        101.63 |   1 |
+
+: **Experiment 1 - End of training performance**.
+Comparing final training block accuracy in band common to both groups.
+The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
+A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.sm}
+
+:::
+
+\
+
+*Training*.
+@fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band.
+To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on.
+The full model results are shown in Table 1.
+The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
+
+```{r}
+##| label: tbl-e1-bmm-dist
+##| tbl-cap: "E1. Training vs. Extrapolation"
+#| 
+modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
+bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
+    data=testE1, file=modelFile,
+    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
+
+# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
+# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
+
+# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
+# posterior_summary(bmtd,variable=r_bandInt_params)
+# 
+# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
+# posterior_summary(bmtd,variable=r_bandInt_params)
+
+# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
+#   tibble::remove_rownames() |> 
+#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
+cdted1 <- get_coef_details(bmtd, "conditVaried")
+cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
+cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
+```
+
+::: {#tbl-e1-bmm-dist}
+
+| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
+|:------------------------|-----------:|-----------:|-----------:|-----------:|
+| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
+| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
+| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
+| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |
+
+: **Experiment 1 testing accuracy**.
+Main effects of condition and band type (training vs.
+extrapolation bands), and the interaction between the two factors.
+The Intercept represents the baseline condition (constant training & trained bands).
+Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.hover .sm}
+:::
+
+*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
+constant) and band type (trained vs.
+extrapolation), with random intercepts for participants and bands.
+The model results are shown in @tbl-e1-bmm-dist.
+The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`).
+The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`).
+Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
 
@@
 #| label: fig-e1-test-dev
-#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
-test |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+#| fig-cap: Experiment 1 Testing Accuracy.
+A) Empricial Deviations from target band during testing without feedback stage.
+B) Conditional effect of condition (Constant vs.
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
+Error bars represent 95% credible intervals.
+#| fig-width: 11
+#| fig-height: 7
+
+pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
     stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  labs(x="Band", y="Deviation From Target")
-```
-
-```{r}
-#| label: tbl-e1-bmm-dist
-#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-#| tbl-subcap: ["Constant Testing1 - Deviation", "Varied Testing - Deviation"]
-modelName <- "e1_testDistBand_RF_5K"
-e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
-                      data=test,file=paste0(here::here("data/model_cache",modelName)),
-                      iter=5000,chains=4)
-GetModelStats(e1_distBMM) |> kable(booktabs = TRUE,caption = paste("Coefficients"))
-
-e1_distBMM |> 
-  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
-          epred = TRUE, re_formula = NA) |> 
-  pairs() |> gather_emmeans_draws()  |> 
-   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
-   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
-   mutate(across(where(is.numeric), \(x) round(x, 2)),
-          pd=ifelse(value<0,1-pd,pd)) |> kable(booktabs = TRUE)
-# |> 
-#   kable(caption="Contrasts")
-
-coef_details <- get_coef_details(e1_distBMM, "conditVaried")
-
-```
-
-The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X).
-Overall, the varied training group showed a larger deviation relative to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]).
-Deviation also depended on target velocity band, with lower bands showing less deviation.
-See @tbl-e1-bmm-dist for full model output.
-
-#### Discrimination between bands
-
-In addition to accuracy/deviation, we also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
-responding differently when prompted for band 600-800 than when prompted for band 150-350).
-@tbl-e1-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
-To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants on each testing trial.
-
-```{=tex}
-\begin{equation}
-vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
-\end{equation}
-```
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-
-test %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-test-nf-vx
-#| tbl-cap: "Testing vx - Empirical Summary"
-#| tbl-subcap: ["Constant", "Varied"]
-
-result <- test_summary_table(test, "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-result$constant |> kable(booktabs = TRUE)
-result$varied |> kable(booktabs = TRUE)
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
-#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
+  labs(x="Band", y="Deviation From Target Band")
+
+condEffects <- function(m,xvar){
+  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() + 
+  stat_halfeye(alpha=.1, height=.5) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
+
+}
+
+pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
+  gather_emmeans_draws() |>
+ condEffects(bandType) + labs(y="Absolute Deviation From Target Band", x="Band Type")
+
+p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
+#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
+p2
+
+```
+
+```{r}
+##| label: tbl-e1-bmm-vx
+##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
 e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
@@
                         control=list(adapt_delta=0.94, max_treedepth=13))
-GetModelStats(e1_vxBMM ) |> kable(booktabs=T, caption="Fit to all 6 bands")
+
+#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)
 
@@
 intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-
-modelName <- "e1_extrap_testVxBand"
-e1_extrap_VxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                  data=test |>
-                    filter(expMode=="test-Nf"),file=paste0(here::here("data/model_cache",modelName)),
-                  iter=5000,chains=4)
-GetModelStats(e1_extrap_VxBMM ) |> kable(booktabs=T, caption="Fit to 3 extrapolation bands")
-
-sc2 <- get_coef_details(e1_extrap_VxBMM, "bandInt")
-intCoef2 <- get_coef_details(e1_extrap_VxBMM, "conditVaried:bandInt")
-
-```
-
+```
+
+\
+
+::: {#tbl-e1-bmm-vx}
+
+| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
+|:-------------|---------:|--------------:|--------------:|-----:|
+| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
+| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
+| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
+| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |
+
+**Experiment 1 Testing Discrimination**.
+Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
+Varied) and Velocity Band.
+Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
+The interaction between condit and Band indicates the difference between constant and varied slopes.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.hover .sm}
+:::
+
+Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
 See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($B$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
-Most relevant to the issue of discrimination is the slope on Velocity Band ($B$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
+The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, though is not in and of itself useful for assessing discrimination.
+Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
 Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The estimate for the interaction between slope and condition ($B$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition.
-This difference is depicted visually in @fig-e1-bmm-vx.Slope coefficients are broken down by quartile in @tbl-e1-slope-quartile.
-The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination.
-Figure @fig-e1-bmm-bx2 shows the distributions of slope values for each participant, and the compares the probability density of slope coefficients between training conditions.
-@fig-e1-indv-slopes
-
-The second model, which focused solely on extrapolation bands, revealed similar patterns.
-The Velocity Band term ($B$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]) still demonstrates a high degree of discrimination ability.
-However, the posterior distribution for interaction term ($B$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\] ) does across over 0, suggesting that the evidence for decreased discrimination ability for the varied participants is not as strong when considering only the three extrapolation bands.
-
-```{r}
-#| label: fig-e1-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band.
+The significant negative estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
+This difference is depicted visually in @fig-e1-test-vx.
+
+```{r}
+#| label: fig-e1-test-vx
+#| fig-cap: Experiment 1. Empirical distribution of velocities producing in testing stage. Translucent bands with dashed lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 8
+
+testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e1-bmm-vx
+#| fig-cap: Experiment 1 Discrimination.
+A) Conditional effect of training condition and Band.
 Ribbons indicate 95% HDI.
 The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
-#| layout-ncol: 1
-
-e1_vxBMM |> emmeans( ~condit + bandInt, 
+B) The distribution of slope coefficients for each condition.
+Larger slopes indicates better discrimination.
+C) Individual participant slopes.
+Error bars represent 95% HDI.
+#| fig-height: 7
+#| fig-width: 11
+
+pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                        at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
   gather_emmeans_draws() |> 
-  condEffects() +
+  condEffects(bandInt) +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
   scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(test$vb), 
-                     limits = c(0, 1400))
-
-e1_extrap_VxBMM |> emmeans( ~condit + bandInt, 
-                       at = list(bandInt = c(100, 350, 600))) |>
-  gather_emmeans_draws() |>
-  condEffects() +
-  scale_x_continuous(breaks = c(100, 350, 600), 
-                     labels = levels(test$vb)[1:3], 
-                     limits = c(0, 1000))
-
-```
-
-```{r}
-#| label: tbl-e1-slope-quartile
-#| tbl-cap: "Slope coefficients by quartile, per condition"
-
-new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")]))) |> 
-  dplyr::arrange(id,bandInt) |> 
-  mutate(condit_dummy = ifelse(condit == "Varied", 1, 0))
-
-indv_coefs <- as_tibble(coef(e1_vxBMM)$id, rownames="id")|> 
-  select(id, starts_with("Est")) |>
-  left_join(e1Sbjs, by=join_by(id) )
-
-fixed_effects <- e1_vxBMM |> 
-  spread_draws(`^b_.*`,regex=TRUE) |> arrange(.chain,.draw,.iteration)
-
-random_effects <- e1_vxBMM |> 
-  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
-  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
-  mutate(id = factor(id,levels=levels(test$id))) |> 
-  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)
-
- indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
-  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
-  right_join(new_data_grid, by = join_by("id")) |> 
-  mutate(
-    Slope = bandInt_RF+b_bandInt,
-    Intercept= RF_Intercept + b_Intercept,
-    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
-    SlopeInt = Slope + (`b_conditVaried:bandInt`*condit_dummy)
-  )
-
-  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt, Intercept,b_Intercept,b_bandInt) |>
-  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
-    select(id,condit,Intercept,b_Intercept,starts_with("Slope"),b_bandInt, n) |>
-  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()
-
-  indvSlopes |> mutate(Condition=condit) |>  group_by(Condition) |> 
-    reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
-  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
-  group_by(Condition) |>
-  summarise(across(starts_with("Q"), list(mean = mean))) |> kable()
-
-```
-
-```{r}
-#| label: fig-e1-bmm-bx2
-#| fig-cap: Slope distributions between condition
-#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
-#| layout-ncol: 2
-#| fig-height: 9
-#| fig-width: 10
-
-indvSlopes |> ggplot(aes(y=rankSlope, x=SlopeInt,fill=condit,color=condit)) + 
-  geom_pointrange(aes(xmin=SlopeInt.lower , xmax=SlopeInt.upper)) + 
-  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)
-
-   ggplot(indvSlopes, aes(x = SlopeInt, color = condit)) + 
-  geom_density() + labs(x="Slope Coefficient",y="Density")
-
-```
-
-```{r}
-#| label: fig-e1-indv-slopes
-#| fig-cap: Subset of Varied and Constant Participants with the smallest and largest estimated slope values.
-Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution.
-Black points and intervals at each band represent the estimated median and 95% HDI.
-Blue points are empirical means.
-#| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
-#| fig-height: 6
-#| fig-width: 9
-
-nSbj <- 3
-indvDraws  |> indv_model_plot(indvSlopes, testAvg, SlopeInt,rank_variable=Slope,n_sbj=nSbj,"max")
-indvDraws |> indv_model_plot(indvSlopes, testAvg,SlopeInt, rank_variable=Slope,n_sbj=nSbj,"min")
-
-```
-
-# Experiment 2
-
-```{r setup2b}
-testE2 <- readRDS(here::here("data/e2_08-21-23.rds")) |> filter(expMode2 == "Test") 
-e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
-testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
-  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
-```
-
-@fig-design-e2 illustrates the design of Experiment 2.
-The stages of the experiment (i.e.
-training, testing no-feedback, test with feedback), are identical to that of Experiment 1.
-The only change is that Experiment 2 participants train, and then test, on bands in the reverse order of Experiment 1 (i.e.
-training on the softer bands; and testing on the harder bands).
-
+                     labels = levels(testE1$vb), 
+                     limits = c(0, 1400)) + 
+  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
+  theme(legend.title=element_blank()) + 
+  labs(y="Velcoity", x="Band")
+
+fe <- fixef(e1_vxBMM)[,1]
+fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
+fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
+
+re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
+  rownames_to_column("id") |> 
+  left_join(e1Sbjs,by="id") |>
+  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
+
+pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
+  geom_density(alpha=.5) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
+   theme(legend.title=element_blank()) + 
+  labs(x="Slope Coefficient",y="Density")
+
+pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
+  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
+    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+     theme(legend.title=element_blank(), 
+           axis.text.y = element_text(size=6) ) + 
+    labs(x="Estimated Slope", y="Participant")  + 
+    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
+
+p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
+#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
+p3
+```
+
+### Experiment 1 Summary
+
+In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
+Our findings that training with variable conditions resulted in lower final training performance are consistent with much of the prior research on the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
+
+More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.
+
+## Experiment 2
+
+```{r}
+
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+e2 <- readRDS(here("data/e2_08-04-23.rds")) 
+e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
+testE2 <- e2 |> filter(expMode2 == "Test")
+nbins=5
+trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
+    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
+trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
+
+# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
+```
+
+### Methods & Procedure
+
+The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
+The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800.
+Both groups were tested from all six bands.
+A total of 110 participants completed the experiment (Varied: 55, Constant: 55).
+
+::: {.content-visible unless-format="markdown"}
 ```{dot}
@@
 //| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 6.0
-//| fig-height: 2.5
+//| fig-width: 7.0
+//| fig-height: 2.2
 //| fig-responsive: false
-//| fig-align: left
+//| echo: false 
+//| 
+/////| column: screen-inset-right
 digraph {
   graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
   node [shape = rectangle, style = filled]
-
   data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
@@
   Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
   data1 -> Test1
@@
   }
-
   Test2 -> Test3
 }
-
-```
-
-## E2 Results
-
-### Testing Phase - No feedback.
-
-In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
-
-#### Deviation From Target Band
-
-Descriptive summaries testing deviation data are provided in @tbl-e2-test-nf-deviation and @fig-e2-test-dev. 
-To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
-The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
-
-\begin{equation}
-dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
-\end{equation}
-
-```{r}
-#| label: tbl-e2-test-nf-deviation
-#| tbl-cap: "Testing Deviation - Empirical Summary"
-#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
-
-result <- test_summary_table(testE2, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-result$constant |> kable()
-result$varied |> kable()
-# make kable table with smaller font size
-# result$constant |> kable(caption="Constant Testing - Deviation",booktabs=T,escape=F) |> kable_styling(font_size = 7)
-```
+```
+
+:::
+
+### Results
+
+```{r}
+#| label: fig-e2-train-dev
+#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
+#| eval: TRUE
+p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
+    stat_summary(geom = "line", fun = mean) +
+    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
+    facet_wrap(~vb)+
+    scale_x_continuous(breaks = seq(1, nbins + 1)) +
+    theme(legend.title=element_blank()) + 
+    labs(y = "Absolute Deviation", x="Training Block") 
+#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
+p1
+```
+
+```{r}
+bmm_e2_train <- trainE2_max %>% 
+  brm(dist ~ condit, 
+      file=here("data/model_cache/e2_train_deviation"),
+      data = .,
+      iter = 2000,
+      chains = 4,
+      control = list(adapt_delta = .94, max_treedepth = 13))
+
+mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
+colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
+
+cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
+# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
+#   tibble::remove_rownames() |> 
+#   mutate(Term = stringr::str_remove(Term, "b_")) |>
+#   kable(escape=F,booktabs=T) 
+```
+
+::: {#tbl-e2-train-dist}
+
+| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
+|:-------------|---------:|--------------:|--------------:|----:|
+| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
+| conditVaried |    36.15 |         16.35 |         55.67 |   1 |
+
+: **Experiment 2 - End of training performance**.
+The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
+A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.sm}
+:::
+
+\
+
+*Training*.
+@fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups.
+We again compared training performance on the band common to both groups (600-800).
+The full model results are shown in Table 1.
+The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
+```{r}
+modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
+bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
+    data=testE2, file=modelFile,
+    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
+
+# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
+# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
+# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
+#   tibble::remove_rownames() |> 
+#   mutate(Term = stringr::str_remove(Term, "b_")) |>
+#   kable(booktabs=TRUE)
+
+cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
+cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
+cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
+```
+
+::: {#tbl-e2-bmm-dist}
+
+| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
+|:-----------------------------------|---------:|--------------:|--------------:|-----:|
+| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
+| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
+| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
+| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |
+
+: **Experiment 2 testing accuracy**.
+Main effects of condition and band type (training vs.
+extrapolation), and the interaction between the two factors.
+The Intercept represents the baseline condition (constant training & trained bands).
+Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
+{.hover .sm}
+:::
+
+\ \
+
+*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
+Constant) and band type (training vs.
+extrapolation bands).
+The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`).
+However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).
 
@@
 #| label: fig-e2-test-dev
-#| fig-cap: E2. Deviations from target band during testing without feedback stage. 
-testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+#| fig-cap: Experiment 2 Testing Accuracy.
+A) Empricial Deviations from target band during testing without feedback stage.
+B) Conditional effect of condition (Constant vs.
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
+Error bars represent 95% credible intervals.
+#| fig-width: 11
+#| fig-height: 7
+
+condEffects <- function(m,xvar){
+  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() + 
+  stat_halfeye(alpha=.1, height=.5) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
+
+}
+pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
     stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
   labs(x="Band", y="Deviation From Target")
-```
-
-```{r}
-#| label: tbl-e2-bmm-dist
-#| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-
-modelName <- "e2_testDistBand_RF_5K"
-e2_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
-                      data=testE2,file=paste0(here::here("data/model_cache",modelName)),
-                      iter=5000,chains=4)
-mp2 <- GetModelStats(e2_distBMM) |> kable(booktabs=T)
-mp2
-
-e2_distBMM |> 
-  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
-          epred = TRUE, re_formula = NA) |> 
-  pairs() |> gather_emmeans_draws()  |> 
-   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
-   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
-   mutate(across(where(is.numeric), \(x) round(x, 2)),
-          pd=ifelse(value<0,1-pd,pd)) |>
-   kable(caption="Contrasts")
-
-coef_details <- get_coef_details(e2_distBMM, "conditVaried")
-
-```
-
-The model predicting absolute deviation showed a modest tendency for the varied training group to have lower deviation compared to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]),with 94% of the posterior distribution being less than 0.
-This suggests a potential benefit of training with variation, though the evidence is not definitive.
-
-#### Discrimination between Velocity Bands
-
-In addition to accuracy/deviation.
-We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
-responding differently when prompted for band 600-800 than when prompted for band 150-350).
-@tbl-e2-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
-To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
-
-\begin{equation}
-vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
-\end{equation}
-
-```{r}
-#| label: fig-e2-test-vx
-#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 9
-testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e2-test-nf-vx
-#| tbl-cap: "Testing vx - Empirical Summary"
-#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
-#| layout-ncol: 1
-
-result <- test_summary_table(testE2, "vx","X Velocity" ,mfun = list(mean = mean, median = median, sd = sd))
-result$constant |> kable()
-result$varied |> kable()
-
-```
-
-```{r}
-#| label: tbl-e2-bmm-vx
-#| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+
+pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
+  gather_emmeans_draws() |>
+ condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
+
+p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
+#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
+p2
+```
+
+```{r}
+##| label: tbl-e2-bmm-vx
+##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+
 e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=testE2,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
+                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
                         iter=5000,chains=4,silent=0,
                         control=list(adapt_delta=0.94, max_treedepth=13))
-mt3 <-GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T)
-mt3
-
-cd1 <- get_coef_details(e2_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e2_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
-```
-
-See @tbl-e2-bmm-vx for the full model results.
-
-When examining discrimination ability using the model predicting raw x-velocity, the results were less clear than those of the absolute deviation analysis.
-The slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]) indicates that participants showed good discrimination between bands overall.
-However, the interaction term suggested this effect was not modulated by training condition (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]) Thus, while varied training may provide some advantage for accuracy, both training conditions seem to have similar abilities to discriminate between velocity bands.
-
-```{r}
-#| label: fig-e2-bmm-vx
-#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI.
-
-e2_vxBMM |> emmeans( ~condit + bandInt, 
+
+#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
+
+cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
+sc2 <- get_coef_details(e2_vxBMM, "bandInt")
+intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
+```
+
+::: {#tbl-e2-bmm-vx}
+
+| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
+|:-------------|---------:|--------------:|--------------:|-----:|
+| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
+| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
+| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
+| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
+
+**Experiment 2 Testing Discrimination**.
+Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
+Varied) and Velocity Band.
+Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
+The interaction between condit and Band indicates the difference between constant and varied slopes.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate) {.hover .sm}
+:::
+
+*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
+The full model results are shown in @tbl-e2-bmm-vx.
+The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
+The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).
+
+```{r}
+#| label: fig-e2-test-vx
+#| fig-cap: Experiment 2. Empirical distribution of velocities produced in the testing stage. Translucent bands with dash lines indicate the correct range for each velocity band.  
+#| fig-width: 11
+#| fig-height: 8
+testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e2-bmm-vx
+#| fig-cap: Experiment 2 Discrimination.
+A) Conditional effect of training condition and Band.
+Ribbons indicate 95% HDI.
+The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
+B) The distribution of slope coefficients for each condition.
+Larger slopes indicates better discrimination.
+C) Individual participant slopes.
+Error bars represent 95% HDI.
+#| fig-height: 7
+#| fig-width: 11
+
+condEffects <- function(m,xvar){
+  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() + 
+  stat_halfeye(alpha=.1, height=.5) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+}
+
+pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
                        at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
   gather_emmeans_draws() |> 
-  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() +
+  condEffects(bandInt) +
   stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  ylab("Predicted X Velocity") + xlab("Band")+
   scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
@@
                      limits = c(0, 1400)) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-```
-
-# Experiment 3
-
-```{r setup3b}
-testE3 <- readRDS(here::here("data/e3_08-21-23.rds")) |> filter(expMode2 == "Test") 
-e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
-testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
-  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
-```
-
-The major manipulation adjustment of experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the earlier experiments.
-Ordinal feedback informs participants whether a throw was too soft, too hard, or fell within the target velocity range.
-Experiment 3 participants were randomly assigned to both a training condition (Constant vs.
-Varied) and a Band Order condition (original order used in Experiment 1, or the Reverse order of Experiment 2).
-
-## Results
-
-### Testing Phase - No feedback.
-
-In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
-Note that these no-feedback testing trials are identical to those of Experiment 1 and 2, as the ordinal feedback only occurs during the training phase, and final testing phase, of Experiment 3.
-
-#### Deviation From Target Band
-
-Descriptive summaries testing deviation data are provided in @tbl-e3-test-nf-deviation and @fig-e3-test-dev. 
-To model differences in accuracy between groups, we fit Bayesian mixed effects regression models to the trial level data from the testing phase.
-The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
-
-```{r}
-#| label: tbl-e3-test-nf-deviation
-#| tbl-cap: "Testing Deviation - Empirical Summary"
-#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
-
-resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-resultOrig$constant |> kable()
-resultOrig$varied |> kable()
-
-resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
-resultRev$constant |> kable()
-resultRev$varied |> kable()
-
-```
+scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
+  theme(legend.title=element_blank()) + 
+  labs(y="Velcoity", x="Band")
+
+fe <- fixef(e2_vxBMM)[,1]
+fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
+fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
+
+re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
+  rownames_to_column("id") |> 
+  left_join(e2Sbjs,by="id") |>
+  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
+
+pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
+  geom_density(alpha=.5) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
+   theme(legend.title=element_blank()) + 
+  labs(x="Slope Coefficient",y="Density")
+
+pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
+  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
+    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+      theme(legend.title=element_blank(), 
+        axis.text.y = element_text(size=6) ) + 
+    labs(x="Estimated Slope", y="Participant")  + 
+    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
+
+p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
+#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
+p3
+```
+
+### Experiment 2 Summary
+
+Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands.
+Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
+However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.
+
+## Experiment 3
+
+```{r}
+
+e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
+    mutate(trainCon=case_when(
+    bandOrder=="Original" ~ "800",
+    bandOrder=="Reverse" ~ "600",
+    TRUE ~ NA_character_
+    ), trainCon=as.numeric(trainCon)) 
+e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
+testE3 <- e3 |> filter(expMode2 == "Test")
+nbins=5
+trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
+    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
+trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
+
+```
+
+### Methods & Procedure
+
+The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
+After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.
+within the target velocity range).
+All other aspects of the task and design are identical to Experiments 1 and 2.
+We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied).
+Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
+Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.
+
+### Results
+
+```{r}
+
+bmm_e3_train <- trainE3_max %>% 
+  brm(dist ~ condit*bandOrder, 
+      file=here("data/model_cache/e3_train_deviation"),
+      data = .,
+      iter = 2000,
+      chains = 4,
+      control = list(adapt_delta = .94, max_treedepth = 13))
+
+# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
+# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
+# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
+#   tibble::remove_rownames() |> 
+#   mutate(Term = stringr::str_remove(Term, "b_")) |>
+#   kable(escape=F,booktabs=T)
+
+cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
+cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
+cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
+```
+
+::: {#tbl-e3-train-dist}
+
+| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
+|:------------------------------|---------:|--------------:|--------------:|-----:|
+| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
+| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
+| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
+| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |
+
+: **Experiment 3 - End of training performance**.
+The Intercept represents the average of the baseline condition (constant training & original band order), the conditVaried coefficient reflects the difference between the constant and varied groups, and the bandOrderReverse coefficient reflects the difference between original and reverse order.
+A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
+The negative value for the interaction between condit and bandOrder indicates that varied condition with reverse order had significantly lower deviations than the varied condition with the original band order  {.sm}
+
+:::
+
+*Training*.
+@fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions).
+The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`).
+The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).
+
+```{r}
+#| label: fig-e3-train-dev
+#| fig-cap: Experiment 3 training. Deviations from target band during training. Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2). 
+#| eval: true
+p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
+    stat_summary(geom = "line", fun = mean) +
+    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
+    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
+    scale_x_continuous(breaks = seq(1, nbins + 1)) +
+    theme(legend.title=element_blank()) + 
+    labs(y = "Absolute Deviation", x="Training Block") 
+#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
+p1
+```
+
+```{r}
+#options(brms.backend="cmdstanr",mc.cores=4)
+modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
+bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
+    data=testE3, file=modelFile,
+    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
+
+# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
+# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
+# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
+#   tibble::remove_rownames() |> 
+#   mutate(Term = stringr::str_remove(Term, "b_")) |>
+#   kable(booktabs=TRUE)
+
+#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
+#wrap_plots(ce_bmtd3)
+
+#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")
+
+cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
+cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
+cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
+cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
+cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
+cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
+cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")
+
+```
+
+::: {#tbl-e3-bmm-dist}
+| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
+|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
+| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
+| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
+| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
+| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
+| **conditVaried:bandTypeExtrapolation**                  |    52.66 |         14.16 |         90.23 | 1.00 |
+| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
+| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
+| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |
+
+: **Experiment 3 testing accuracy**.
+Main effects of condition and band type (training vs.
+extrapolation), and the interaction between the two factors.
+The Intercept represents the baseline condition, (constant training,  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
+Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
+{.hover .sm}
+:::
+
+*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
+There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
+However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`.
+The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group.
+There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands.
+No other interactions were significant.
+
+<!-- ::: {#fig-e3-test-condEffect}
+
+![](../Assets/figs/e3_cond_effects_dist.png)
+
+E3.
+A) Deviations from target band during testing without feedback stage.
+B) Estimated marginal means for the interaction between training condition and band type.
+Error bars represent 95% confidence intervals.
+::: -->
 
@@
 #| label: fig-e3-test-dev
-#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
-testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+#| fig-cap: Experiment 3 Testing Accuracy.
+A) Empricial Deviations from target band during testing without feedback stage.
+B) Conditional effect of condition (Constant vs.
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
+Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2).
+Error bars represent 95% credible intervals.
+#| fig-width: 11
+#| fig-height: 8
+
+condEffects <- function(m,xvar){
+  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() + 
+  stat_halfeye(alpha=.1, height=.5) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
+
+}
+
+pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
     stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder) +
-  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-```
-
-```{r}
-#| label: tbl-e3-bmm-dist
-#| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
-
-modelName <- "e3_testDistBand_RF_5K"
-e3_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
-                      data=testE3,file=paste0(here::here("data/model_cache",modelName)),
-                      iter=5000,chains=4)
-mp3 <- GetModelStats(e3_distBMM) |> kable(booktabs=T)
-mp3
-
-cd1 <- get_coef_details(e3_distBMM, "conditVaried")
-sc1 <- get_coef_details(e3_distBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_distBMM, "conditVaried:bandInt")
-```
-
-The effect of training condition in Experiment 3 showed a similar pattern to Experiment 2, with the varied group tending to have lower deviation than the constant group (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0.
-
-```{r}
-#| label: fig-e3-bmm-dist
-#| fig-cap: e3. Conditioinal Effect of Training Condition and Band. Ribbon indicated 95% Credible Intervals.
-
-e3_distBMM |> emmeans( ~condit + bandInt, 
+    facet_wrap(~bandOrder,ncol=1) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
+  labs(x="Band", y="Deviation From Target")
+
+pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
+  gather_emmeans_draws() |>
+ condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
+ facet_wrap(~bandOrder,ncol=1)
+
+p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
+#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
+p2
+```
+
+```{r}
+##| label: tbl-e3-bmm-vx
+##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+
+e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
+                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+
+# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
+# m2 <- fixef(e3_vxBMM)
+# mp3 <- m1[, c(1,2,4,5,6)]
+# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
+# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
+#   tibble::remove_rownames() |> 
+#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
+#   mutate(Term = stringr::str_remove(Term, "b_")) |>
+#   kable(escape=F,booktabs=T)
+
+#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))
+
+cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e3_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
+intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
+coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")
+
+```
+
+::: {#tbl-e3-bmm-vx}
+
+| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
+|:----------------------------------------|---------:|--------------:|--------------:|-----:|
+| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
+| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
+| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
+| **Band**                                  |     0.49 |          0.36 |          0.62 | 1.00 |
+| **conditVaried:bandOrderReverse**         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
+| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
+| bandOrderReverse:band              |    -0.10 |         -0.27 |          0.08 | 0.86 |
+| **conditVaried:bandOrderReverse:band** |     0.42 |          0.17 |          0.70 | 1.00 |
+
+**Experiment 3 testing discrimination**.
+Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs.
+Varied) and Velocity Band.
+The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the  slope for the baseline condition.
+The interaction terms which include condit and Band (e.g.
+conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate the how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
+:::
+
+*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist.
+For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
+The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
+Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
+However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating a greater slope for the varied condition trained with reverse order bands.
+This interaction is shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
+
+```{r}
+#| label: fig-e3-test-vx
+#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 10
+##| column: screen-inset-right
+# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
+# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
+
+testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
+   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
+```
+
+```{r}
+#| label: fig-e3-bmm-vx
+#| fig-cap: Experiment 3 Discrimination.
+A) Conditional effect of training condition and Band.
+Ribbons indicate 95% HDI.
+The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
+B) The distribution of slope coefficients for each condition.
+Larger slopes indicates better discrimination.
+C) Individual participant slopes.
+Error bars represent 95% HDI.
+#| fig-height: 10
+#| fig-width: 11
+# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
+
+condEffects <- function(m,xvar){
+  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() + 
+  stat_halfeye(alpha=.1, height=.5) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
+
+}
+
+pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
                        at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
   gather_emmeans_draws() |> 
-  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() +
+  condEffects(bandInt) +
+  facet_wrap(~bandOrder,ncol=1) +
   stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-    ylab("Predicted Deviation") + xlab("Velocity Band")+
   scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
@@
                      limits = c(0, 1400)) + 
-  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-```
-
-#### Discrimination between Velocity Bands
-
-In addition to accuracy/deviation.
-We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
-responding differently when prompted for band 600-800 than when prompted for band 150-350).
-@tbl-e3-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
-To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
-
-\begin{equation}
-vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
-\end{equation}
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 12
-#| fig-height: 13
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-  facet_wrap(bandOrder~condit,scale="free_x")
-
-```
-
-```{r}
-#| label: tbl-e3-test-nf-vx
-#| tbl-cap: "Testing vx - Empirical Summary"
-#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
-
-resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-resultOrig$constant |> kable()
-resultOrig$varied |> kable()
-
-resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
-resultRev$constant |> kable()
-resultRev$varied |> kable()
-```
-
-```{r}
-#| label: tbl-e3-bmm-vx
-#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-mt4 <-GetModelStats(e3_vxBMM ) |> kable(booktabs=T)
-mt4
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-```
-
-See @tbl-e3-bmm-vx for the full model results.
-
-Slope estimates for experiment 3 suggest that participants were capable of distinguishing between velocity bands even when provided only ordinal feedback during training (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
-Unlike the previous two experiments, the posterior distribution for the interaction between condition and band was consistently positive, suggestive of superior discrimination for the varied participants
-β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\].
-
-### Computational Modelling
-
-{{< include ../Sections/htw_exam.qmd >}}
-
-::: {.content-visible unless-format="pdf"}
+scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
+  theme(legend.title=element_blank()) + 
+  labs(y="Velcoity", x="Band")
+
+fe <- fixef(e3_vxBMM)[,1]
+fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
+fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
+fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
+fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
+
+re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
+  rownames_to_column("id") |> 
+  left_join(e3Sbjs,by="id") |>
+  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
+           fixed_effect_interaction2*(bandOrder=="Reverse") + 
+           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
+  slope = Estimate + adjust )
+
+pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
+  geom_density(alpha=.5) + 
+  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+   theme(legend.title=element_blank()) + 
+  labs(x="Slope Coefficient",y="Density") +
+  facet_wrap(~bandOrder,ncol=1)
+
+pid_slopes3 <- re |>  
+    mutate(id=reorder(id,slope)) |>
+  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
+    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
+    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+    theme(legend.title=element_blank(), 
+      axis.text.y = element_text(size=6) ) + 
+    labs(x="Estimated Slope", y="Participant")  + 
+    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
+
+p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
+
+#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
+p3
+
+```
+
+### Experiment 3 Summary
+
+In Experiment 3, we investigated the effects of training condition (constant vs.
+varied) and band type (training vs.
+extrapolation) on participants' accuracy and discrimination during the testing phase.
+Unlike the previous experiments, participants received ordinal feedback during the training phase.
+Additionally, Experiment 3 included both the original order condition from Experiment 1 and the reverse order condition from Experiment 2.
+The results revealed no significant main effects of training condition on testing accuracy, nor was there a significant difference between groups in band discrimination.
+However, we observed a significant three-way interaction for the discrimination analysis, indicating that the varied condition showed a steeper slope coefficient on the reverse order bands compared to the constant condition.
+This result suggests that varied training enhanced participants' ability to discriminate between velocity bands, but only when the band order was reversed during testing.
+
+## Computational Model
+
+```{r}
+####| cache: false
+# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+```
+
+```{r}
+###| cache: true
+invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
+invisible(list2env(load_e1(), envir = .GlobalEnv))
+e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
+e2_model <- load_e2()
+e3_model <- load_e3()
+options(contrasts = initial_contrasts)
+
+```
+
+```{r}
+#| label: fig-alm-diagram
+#| fig.cap: The Associative Learning Model (ALM).
+The diagram illustrates the basic structure of the ALM model as used in the present work.
+Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
+The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
+The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule.
+alm_plot()
+```
+
+The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997].
+ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.
+
+### ALM & Exam
+
+ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
+The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
+So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
+Depending on the value of the generalization parameter, the nearby units (e.g.
+54 and 56; 53 and 57) may also activate to some degree.
+ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
+The units in the input layer activate as a function of their similarity to a presented stimulus.
+As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
+The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
+The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
+During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
+The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
+The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
+EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
+Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
+EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
+The slope is then used to extrapolate the response to the novel test stimulus.
+Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
+We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
+This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
+
+See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
+
+::: column-page-inset-right
+|                    | **ALM Response Generation**                                        |                                                                                               |
+|------------------|-----------------------------|-------------------------|
+| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
+| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
+| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
+| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
+|                    | **ALM Learning**                                                   |                                                                                               |
+| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
+| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
+| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
+|                    | **EXAM Extrapolation**                                             |                                                                                               |
+| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
+| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
+| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |
+
+: ALM & EXAM Equations {#tbl-alm-exam}
+:::
+
+### Model Fitting
+
+To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
+Each model was fit to the data with three separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
+We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
+It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.
+Models were fit separately to the data of each individual participant.
+The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
+Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.
+
+::: {.callout}
+
+**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
+
+To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
+Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g.
+many neural network models).
+
+The general ABC procedure is to 1) define a prior distribution over model parameters.
+2) sample candidate parameter values, $\theta^*$, from the prior.
+3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
+4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
+5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
+6) Repeat until desired number of posterior samples are obtained.
+
+Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
+For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
+For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
+For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
+After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
+For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
+
+::: column-page-inset-left
+$$
+discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
+$$ {#eq-discrep-test}
+
+$$
+\begin{aligned} \\
+discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
+discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
+\end{aligned}
+$$ {#eq-discrep-train}
+:::
+
+The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
+The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
+Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
+Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
+The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
+Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
+After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
+In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
+To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
+:::
+
+For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution.
+Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant.
+Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs.
+To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.
+
+### Modelling Results
+
+#### Group level Patterns
+
+```{r}
+#| label: tbl-htw-modelError-e1
+#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
+Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
+post_tabs <- abc_tables(post_dat,post_dat_l)
+train_tab <- abc_train_tables(pd_train,pd_train_l)
+
+e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
+
+e1_tab %>%
+  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
+  summarize(ME = mean(mean_error), .groups = "drop") %>%
+  pivot_wider(
+    names_from = c(Model, condit),
+    values_from = ME,
+    names_sep = "_"  # Add this line to specify the separator for column names
+  ) %>%
+  rename("Fit Method" = Fit_Method) %>%
+  gt() %>%
+  cols_move_to_start(columns = c(`Task Stage`)) %>%
+  cols_label(
+    `Task Stage` = "Task Stage"
+  ) %>%
+  fmt_number(
+    columns = starts_with("ALM") | starts_with("EXAM"),
+    decimals = 2
+  ) %>%
+  tab_spanner_delim(delim = "_") %>%
+  tab_style(
+    style = cell_fill(color = "white"),
+     locations = cells_body(columns = everything(), rows = everything())
+  ) %>%
+  tab_style(
+    style = cell_borders(sides = "top", color = "black", weight = px(1)),
+    locations = cells_column_labels()
+  ) %>%
+  tab_options(
+    column_labels.font.size = 10,
+    heading.title.font.size = 14,
+    heading.subtitle.font.size = 12,
+    table.font.size = 10, 
+    quarto.disable_processing = TRUE
+  ) 
+```
+
+```{r}
+#| label: fig-htw-post-dist
+#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters.
+Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
+Note that the y axes of the plots for the c parameter are scaled logarithmically."
+#| fig-height: 6
+#| fig-width: 10
+
+c_post <- post_dat_avg %>%
+    group_by(id, condit, Model, Fit_Method, rank) %>%
+    slice_head(n = 1) |>
+    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
+    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
+  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
+
+lr_post <- post_dat_avg %>%
+    group_by(id, condit, Model, Fit_Method, rank) %>%
+    slice_head(n = 1) |>
+    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
+    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
+  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
+c_post + lr_post
+```
+
+```{r}
+#| label: fig-htw-resid-pred
+#| fig-cap: "Model residuals for each combination of training condition, fit method, and model.
+Residuals reflect the difference between observed and predicted values.
+Lower values indicate better model fit.
+Note that y axes are scaled differently between facets.
+A) Residuals predicting each block of the training data.
+B) Residuals predicting each band during the testing stage.
+Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
+#| fig-height: 14
+#| fig-width: 11
+
+train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
+  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
+  group_by(id,condit,Model,Fit_Method,Block) |>
+  summarise(mean_error=mean(mean_error)) |>
+  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
+  stat_bar + 
+  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
+   scale_x_discrete(guide = "axis_nested") +
+  scale_fill_manual(values=c("gray10","gray50","gray92"))+
+  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
+  theme(legend.position="top")
+
+test_resid <-  post_dat |> 
+   group_by(id,condit,x,Model,Fit_Method,bandType) |>
+    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
+  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
+  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
+  stat_bar + 
+  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
+  scale_color_manual(values = c("black" = "black"), guide = "none") +
+  scale_size_manual(values = c("black" = .5), guide = "none") +
+  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
+  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")
+
+(train_resid / test_resid) +
+  #plot_layout(heights=c(1,1.5)) & 
+  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
+```
+
+The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat.
+There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences.
+The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
+
+We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model.
+Aggregated residuals are displayed in @fig-htw-resid-pred.
+The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method .
+Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms).
+The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models.
+It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task.
+Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories.
+However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data.
+All subsequent analyses and discussion will thus focus on the testing stage.
+
+The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots).
+Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
+The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models.
+Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.
+
+```{r}
+#| label: fig-cm-vx-pat
+#| fig-cap: "Empirical data and Model predictions for mean velocity across target bands.
+Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs.
+Varied) are separated by columns.
+Each facet contains the predictions of ALM and EXAM, alongside the observed data."
+#| fig-height: 10
+#| fig-width: 10
+
+post_dat_l |> 
+  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
+ summarize(vx=median(val)) |> 
+ #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
+ ggplot(aes(x=Resp,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
+  stat_bar + 
+    facet_wrap(~rename_fm(Fit_Method)+condit, ncol=2,strip.position = "top", scales = "free_x") +
+        scale_color_manual(values = c("black" = "black"), guide = "none") +
+  scale_size_manual(values = c("black" = .5), guide = "none") +
+    theme(panel.spacing = unit(0, "lines"), 
+         strip.background = element_blank(),
+         strip.placement = "outside",
+         legend.position = "none",plot.title = element_text(hjust=.50),
+         axis.title.x = element_blank(),
+         plot.margin = unit(c(10,0,0,0), "pt")) + 
+         labs(title="Model Predictions - Experiment 1 Data", y="Vx")
+```
+
+```{r}
+#| label: fig-ee-e1
+#| fig-cap: A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+Varied).
+Lower values on the y axis indicate better model fit.
+D) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs.
+EXAM for the varied group; 3) ALM fits between constant and varied.
+Negative error differences indicate that the term on the left side (e.g.
+EXAM Constant) tended to have smaller model residuals.
+#| fig-height: 8
+#| fig-width: 10
+
+pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+
+pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
+  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
+
+# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
+e1_ee_brm_ae <- brm(data=pdl,
+  aerror ~  Model * condit + (1+bandInt|id), 
+  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
+  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
+
+bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
+  select(1,2,4,5,6) %>%
+  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
+  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
+  tibble::remove_rownames() %>%
+  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
+
+#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
+
+p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
+  ggplot2::xlab("Condition") +ylab("Model Error")
+p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
+  labs(x="Model",y=NULL)
+p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
+  scale_color_manual(values=wes_palette("Darjeeling1")) +
+  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
+
+#p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+
+# plot_custom_effects <- function(model) {
+#   # Extract posterior samples for fixed effects
+#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
+
+#   # Calculate conditional effects
+#   post_samples <- post_samples %>%
+#     mutate(
+#       ALM_Constant = b_Intercept,
+#       EXAM_Constant = b_Intercept + b_ModelEXAM,
+#       ALM_Varied = b_Intercept + b_conditVaried,
+#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
+#     )
+
+#   # Reshape data for plotting
+#   plot_data <- post_samples %>%
+#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
+#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
+#     separate(Condition, into = c("Model", "Condit"), sep = "_")
+
+#   # Plot conditional effects
+#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
+#     geom_boxplot() +
+#     theme_minimal() +
+#     labs(x = "Model", y = "Estimate", color = "Condition")
+# }
+# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
+
+bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
+bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
+bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")
+
+posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
+  select(starts_with("b_")) %>%
+  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))
+
+constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
+varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
+comparison_EXAM <- constant_EXAM - varied_EXAM
+summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
+
+# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
+# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)
+
+# full set of Model x condit contrasts
+# ALM - EXAM
+# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
+#   pluck("contrasts") |> 
+#   gather_emmeans_draws() |> 
+#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
+
+# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()
+
+# Constant - Varied
+# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
+# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
+#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
+# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
+
+p_em_1 <- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
+  pluck("contrasts") |>
+  gather_emmeans_draws() |> 
+  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
+  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
+  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")
+
+#p_ce_1 / p_em_1
+
+(p1 + p2+ p3) /p_em_1 + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+```
+
+To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
+EXAM) and training condition (Constant vs.
+Varied).
+
+Model errors were significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM.
+There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group.
+To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
+The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
+
+```{r}
+#| label: tbl-htw-modelError-e23
+#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
+Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
+
+post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
+train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
+
+pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
+
+e2_tab <- rbind(post_tabs2$agg_pred_full |>
+ mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
+ mutate("Task Stage"="Train")) |> 
+  mutate(Fit_Method=rename_fm(Fit_Method))
+
+post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
+train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
+
+pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
+
+e3_tab <- rbind(post_tabs3$agg_pred_full |> 
+  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
+  mutate(Fit_Method=rename_fm(Fit_Method))
+
+e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3")) 
+gt_table <- e23_tab %>%
+  pivot_wider(
+    names_from = c(Exp, Model, condit),
+    values_from = mean_error,
+    names_glue = "{Exp}_{Model}_{condit}"
+  ) %>%
+  arrange(Fit_Method, `Task Stage`) %>%
+  gt() %>%
+  cols_move_to_start(columns = `Task Stage`) %>%
+  cols_label(`Task Stage` = "Task Stage") %>%
+  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
+  tab_spanner_delim(delim = "_") %>%
+  tab_style(
+    style = list(
+      cell_fill(color = "white"),
+      cell_borders(sides = "top", color = "black", weight = px(1))
+    ),
+    locations = cells_body(columns = everything(), rows = everything())
+  ) %>%
+  tab_options(
+    column_labels.font.size = 10,
+    heading.title.font.size = 14,
+    heading.subtitle.font.size = 12,
+    table.font.size = 10,
+    quarto.disable_processing = TRUE
+  ) 
+gt_table
+```
+
+```{r}
+#| label: fig-cm-vx-pat-e2-e3
+#| fig-height: 8
+#| fig-width: 10
+#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage.
+Observed data is shown on the right.
+Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
+
+rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
+  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
+ summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
+ e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
+  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
+  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
+  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
+  stat_bar + 
+    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
+    scale_color_manual(values = c("black" = "black"), guide = "none") +
+  scale_size_manual(values = c("black" = .7), guide = "none") +
+    theme(panel.spacing = unit(0, "lines"), 
+        #  strip.background = element_blank(),
+        #  strip.placement = "outside",
+         legend.position = "none",plot.title = element_text(hjust=.50),
+         axis.title.x = element_blank(),
+         plot.margin = unit(c(20,0,0,0), "pt")) + 
+         labs(title="Model Predictions Experiment 2 & 3", y="vx")
+```
+
+{{< pagebreak >}}
+
+\scriptsize
+
+```{r}
+#| label: tbl-htw-ee-e23
+#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
+EXAM), Condition (Constant vs.
+Varied), and the interaction between Model and Condition.
+The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
+The intercept reflects the baseline of ALM and Constant.
+The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
+Lower values indicate better model fit."
+
+e2_ee_brm_ae <- brm(data=pdl2,
+  aerror ~  Model * condit + (1+bandInt|id), 
+  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
+  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
+
+bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
+bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
+bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
+
+bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
+  select(1,2,4,5,6) %>%
+  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
+  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
+  tibble::remove_rownames() %>%
+  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
+
+e3_ee_brm_ae <- brm(data=pdl3,
+  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
+  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
+  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
+
+bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
+bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
+bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
+bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
+
+bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
+  select(1,2,4,5,6) %>%
+  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
+  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
+  tibble::remove_rownames() %>%
+  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
+
+bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
+               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
+  relocate(exp, .before=Term)
+
+bct_table <- bct %>%
+  mutate(
+    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
+    pd = round(pd, 2)
+  ) %>%
+  gt() %>%
+  # tab_header(
+  #   title = "Bayesian Model Results",
+  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
+  # ) %>%
+  cols_label(
+    exp = "Experiment",
+    Term = "Term",
+    Estimate = "Estimate",
+    `95% CrI Lower` = "95% CrI Lower",
+    `95% CrI Upper` = "95% CrI Upper",
+    pd = "pd"
+  ) %>%
+  fmt_number(
+    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
+    decimals = 2
+  ) %>%
+  fmt_number(
+    columns = pd,
+    decimals = 2
+  ) %>%
+  tab_spanner(
+    label = "Credible Interval",
+    columns = c(`95% CrI Lower`, `95% CrI Upper`)
+  ) %>%
+  tab_style(
+    style = list(
+      #cell_fill(color = "lightgray"),
+      cell_text(weight = "bold"), 
+      cell_fill(color = "white"),
+      cell_borders(sides = "top", color = "black", weight = px(1))
+    ),
+    locations = cells_body(
+      columns = c(Estimate, pd),
+      rows = Term=="ModelEXAM:conditVaried"
+    )
+  ) %>%
+   tab_row_group(
+    label = "Experiment 3",
+    rows = exp == "Exp 3"
+  ) %>%
+  tab_row_group(
+    label = "Experiment 2",
+    rows = exp == "Exp 2"
+  ) %>%
+  tab_row_group(
+    label = "Experiment 1",
+    rows = exp == "Exp 1"
+  ) %>%
+  tab_options(
+    table.font.size = 10,
+    heading.title.font.size = 14,
+    heading.subtitle.font.size = 12,
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
+    #row_group.background.color = "gray95"
+  )
+bct_table
+
+```
+
+\normalsize
+
+*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
+For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
+The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
+The Bayesian regression models predicting model error as a function of Model (ALM vs.
+EXAM), Condition (Constant vs.
+Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
+The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
+Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
+Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
+We thus also controlled for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
+There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
+
+```{r}
+#| label: fig-e2_e3_ae
+#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+Varied) on Model Error for Experiment 2 and 3 data.
+Experiment 3 also includes a control for the order of training vs.
+testing bands (original order vs.
+reverse order)."
+#| fig-height: 6
+#| fig-width: 9
+
+#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
+p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
+  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
+p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
+  labs(x="Model",y=NULL)
+p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
+  scale_color_manual(values=wes_palette("Darjeeling1")) +
+  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
+
+  p_e2 <- (p1 + p2+ p3) 
+# #wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
+
+p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
+                         effects = "Model:condit", 
+                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
+     points=FALSE,plot=FALSE)$`Model:condit` + 
+     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
+     theme(legend.position="right") + 
+     scale_color_manual(values=wes_palette("Darjeeling1"))
+
+p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
+  ggplot2::xlab("Condition") +ylab("Model Error")
+p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
+  labs(x="Model",y=NULL)
+p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
+  scale_color_manual(values=wes_palette("Darjeeling1")) +
+  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
+
+ p2 <- (p1 + p2+ p3)
+ (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+```
+
+*Computational Model Summary*.
+Across all three experiments, the model fits consistently favored the Extrapolation-Association Model (EXAM) over the Associative Learning Model (ALM).
+This preference for EXAM was particularly pronounced for participants in the constant training conditions (note the positive coefficients on ModelEXAM:conditVaried interaction terms @tbl-htw-ee-e23).
+This pattern is clearly illustrated in @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
+Both varied and constant conditions have a greater proportion of subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly larger for the constant group.
+
+The superior performance of EXAM, especially for the constant training groups, may initially seem counterintuitive.
+One might assume that exposure to multiple, varied examples would be necessary to extract an abstract rule.
+However, EXAM is not a conventional rule-based model; it does not require the explicit abstraction of a rule.
+Instead, rule-based responses emerge during the retrieval process.
+The constant groups' formation of a single, accurate input-output association, combined with the usefulness of the zero point, may have been sufficient for EXAM to capture their performance.
+A potential concern is that the assumption of participants utilizing the zero point essentially transforms the extrapolation problem into an interpolation problem.
+However, this concern is mitigated by the consistency of the results across both the original and reversed order conditions (the testing extrapolation bands fall in between the constant training band and the 0 point in experiment 1, but not in experiment 2).
+
+The fits to the individual participants also reveal a number of interesting cases where the models struggle to capture the data (@fig-htw-indv-pred).
+For example participant 68 exhibits a strong a strong non-monotonicity in the highest velocity band, a pattern which ALM can mimic, but which EXAM cannot capture, given it's to enforce a simple linear relationship between target velocity and response.
+Participant 70 (lower right corner of @fig-htw-indv-pred) had a roughly parabolic response pattern in their observed data, a pattern which neither model can properly reproduce, but which causes EXAM to perform particularly poorly.
+
+*Modeling Limitations.* The present work compared models based on their ability to predict the observed data, without employing conventional model fit indices such as the Akaike Information Criterion (AIC) or the Bayesian Information Criterion (BIC).
+These indices, which penalize models based on their number of free parameters, would have been of limited utility in this case, as both ALM and EXAM have two free parameters.
+However, despite having the same number of free parameters, EXAM could still be considered the more complex model, as it incorporates all the components of ALM plus an additional mechanism for rule-based responding.
+A more comprehensive model comparison approach might involve performing cross-validation with a held-out subset of the data [@mezzadriHoldoutStrategySelecting2022] or penalizing models based on the range of patterns they can produce [@domeGdistanceComparisonModel2023].
+
+{{< pagebreak >}}
+
+```{r}
+#| label: fig-htw-best-model
+#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
+#| fig-height: 12
+#| fig-width: 11
+
+tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
+  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
+  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
+  filter(Fit_Method=="Test_Train") |>
+  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
+    mutate(e2=abs(y-pred)) |> 
+    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
+    group_by(id,condit,Model,Fit_Method,Exp) |> 
+    summarise(mean_error=mean(mean_error)) |> 
+    arrange(id,condit,Fit_Method) |>
+    round_tibble(1)
+
+best_id <- tid1 |> 
+  group_by(id,condit,Fit_Method) |> 
+  mutate(best=ifelse(mean_error==min(mean_error),1,0))
+
+lowest_error_model <- best_id %>%
+  group_by(id, condit,Fit_Method, Exp) %>%
+  summarise(Best_Model = Model[which.min(mean_error)],
+            Lowest_error = min(mean_error),
+            differential = min(mean_error) - max(mean_error)) %>%
+  ungroup()
+
+error_difference<- best_id %>%
+  select(id, condit, Model,Fit_Method, mean_error) %>%
+  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
+  mutate(Error_difference = (ALM - EXAM))
+
+full_comparison <- lowest_error_model |> 
+  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
+  group_by(condit,Fit_Method,Best_Model) |> 
+  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
+  arrange(Fit_Method,-Error_difference)
+
+full_comparison |> 
+  filter(Fit_Method=="Test_Train") |> 
+  ungroup() |>
+  mutate(id = reorder(id, Error_difference)) %>%
+  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
+  geom_col() +
+  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
+  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
+  theme(axis.text.y = element_text(size=8)) +
+  labs(fill="Best Model",
+  x="Mean Model Error Difference (ALM - EXAM)",
+  y="Participant")
+
+```
+
+```{r  fig.width=11, fig.height=10}
+#| label: fig-htw-indv-pred
+#| fig-cap: Model predictions alongside observed data for a subset of individual participants.
+A) 3 constant and 3 varied participants fit to both the test and training data.
+B) 3 constant and 3 varied subjects fit to only the trainign data.
+Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands.
+#| fig-height: 7
+#| fig-width: 10
+
+cId_tr <- c(137, 181, 11)
+vId_tr <- c(14, 193, 47)
+cId_tt <- c(11, 93, 35)
+vId_tt <- c(1,14,74)
+cId_new <- c(175, 68, 93, 74)
+# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")
+
+e1_sbjs <- c(49,68,155, 175,74)
+e3_sbjs <-  c(245, 280, 249)
+e2_sbjs <- c(197, 157, 312, 334)
+cFinal <- c(49, 128,202 )
+vFinal <- c(68,70,245)
+
+indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
+  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
+  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
+  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))
+
+testIndv <- indv_post_l |> 
+#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
+   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
+  group_by(id,condit,Fit_Method,Model,Resp) |>
+   mutate(flab=paste0("Subject: ",id)) |>
+  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
+  stat_bar_sd + 
+  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
+  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
+  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
+  labs(title="Individual Participant fits from Test & Train Fitting Method",
+       y="X Velocity",fill="Target Velocity") +
+   guides(fill = guide_legend(nrow = 1)) + 
+  theme(legend.position = "bottom",axis.title.x = element_blank())
+
+testIndv 
+```
+
+## Project 2 Discussion
+
+Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
+
+In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
+Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
+The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.
+
+Experiment 2 extended these findings by reversing the order of the training and testing bands.
+Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases.
+However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.
+
+In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments.
+Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied).
+The varied condition showed larger deviations at the end of training, consistent with the previous experiments.
+Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition.
+During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands.
+The reverse order conditions showed smaller deviations compared to the original order conditions.
+Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.
+
+All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015].
+The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group.
+Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.
+
+Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
+Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
+A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
+These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study.
+@vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
+However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
+This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
+
+*Limitations*
+
+While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
+First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
+Such a difference may be an unavoidable consequence of varied vs.
+constant design which match the total number of training trials between the two groups.
+However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
+Another limitation is that the testing stage did not include any interpolation items, i.e.
+the participants tested only from the training bands they experienced during training, or from extrapolation bands.
+The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
+Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
+Finally, the task employed in the present study consisted of only a linear, positive function.
+Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
+It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
+
+# General Discussion
+
+To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
+
+## Empirical and Modeling Summary
+
+Across both projects, we investigated the influence of training variability on learning and generalization in computerized visuomotor skill learning, and function learning tasks.
+In project 1 (HTT), experiments 1 and 2 demonstrated that varied training led to superior testing performance compared to constant training.
+In Experiment 1, the varied group even outperformed the constant group even when testing from the constant groups trained position.
+In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of training accuracy, accuracy in extrapolation testing,  and, in a subset of the experiments, the varied group showed a diminished ability to discriminate between bands.
+This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
+
+Both projects also included computational modeling componenents.
+In Project 1, the IGAS model was introduced as a means of addressing the lack of control for similarity between training and testing conditions common to previous work in the "benefits of variability" literature.
+The IGAS model provides a theoretically motivated method of quantifying the similarity between training experience and testing conditions.
+The resulting similarity metric (i.e.
+our 1c-similarity) is shown to be a significant predictor of testing performance on its own, and when added as a covariate to the statistical model used to compare the constant and varied training groups.
+We then showed the group-level effect of training variability on testing performance can be accounted for with the additional assumption that training variability influences the generalization gradient.
+The contribution of the IGAS model was thus twofold:  1) providing a theoretically justifiable method of quantifying/controlling for similarity between training and testing, and 2) demonstrating the viability of a flexible-similarity based generalization account for the empirically observed benefit of variability in our task.
+Although similar approaches have been employed in other domains, both contributions are novel additions to the large body of research assessing the effect of constant vs.
+varied training manipulations in visuomotor skill tasks.
+
+Although theoretically motivated, the IGAS model of Project 1 is best categorized as a descriptive measurement-model.
+Sufficient to account for group differences, but lacking the machinery necessary to provide a full process-level account of how the empirical quantities of interest are generated.
+In contrast, Project 2 (HTW) implemented a more robust computational modeling approach, implementing and comparing full process models (ALM & EXAM), capable of generating predictions for both the learning and testing stages of the experiment.
+ALM and EXAM have been used as models of function learning, cue judgement, and forecasting behavior in numerous studies over the past 25 years [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @brownUnderestimationLinearFunction2017; @kwantesItemOrderMatters2012; @kelleyComparisonModelsLearning2008; @kaneApplicationsBiasVariance2020; @vonhelversenLearningMultiplecueJudgment2010].
+The present work presents the first application of these models to to the study of training variability in a visuomotor function learning task.
+We fit both models to individual participant data, using a form of simulation-based bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
+EXAM provided the best overall account of the testing data, and the advantage of EXAM over ALM was significantly greater for the constant group.
+Notably, EXAM captured the constant groups' ability to extrapolate linearly to novel velocity bands, despite receiving training from only a single input-output pair.
+This finding suggests that EXAM's linear extrapolation mechanism, combined with the assumption of prior knowledge about the origin point (0, 0), was sufficient to account for the constant groups' accurate extrapolation performance.
+Such findings may offer a preliminary suggestion that experience with a more variable set of training examples  may be detrimental to performance in simple extrapolation tasks.
+
+## Differences between the two Projects
+
+The HTT and HTW tasks differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
+
+In HTT, the salient perceptual elements of the task (i.e.
+the launching box, target and barrier) are subject to variation (i.e.
+different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
+Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
+If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
+Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
+the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
+
+The HTT and HTW tasks also differed in terms of general task complexity.
+The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
+Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
+In HTW,the relationship between feedback and optimal behavioral adjustment is also almost perfectly smooth, if participants produce a throw that is 100 units too hard, they'll be told that they were 100 units away from the target band.
+Whereas in HTT, the presence of the barrier in introduces irregularities in the task space.
+Even throws close to the solution space might result in failure, creating a less predictable learning environment.
+
+::: {#tbl-task-diff}
+
+| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
+| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
+| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
+| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
+Only x velocity is relevant.
+|
+| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
+| Simpler: smooth, linear mapping between velocity and feedback.
+|
+| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
+salient differences in distance between launching box and target.
+| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
+|
+| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
+|
+| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
+| Some potential for learning during no-feedback testing by observing ball trajectory.
+|
+| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
+| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
+|
+| Testing Structure                               | Random interleaving of trained/transfer testing distances.
+| Blocked structure, separately testing trained vs extrapolation testing bands.
+|
+
+Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
+:::
+
+### Conclusion
+
+In summary, this dissertation provides a comprehensive examination of the effects of training variability on learning and generalization in visuomotor and function learning tasks.
+The contrasting results obtained from the Hit The Target (HTT) and Hit The Wall (HTW) tasks underscore the complexity inherent to the longstanding pedagogical and scientific goal of identifying training manipulations that consistently benefit learning and generalization.
+Moreover, through the development and application of computational models, we provide novel theoretical accounts for both the beneficial and detrimental effects of training variability observed in our experiments.
+These findings highlight the importance of considering task characteristics when designing experiments intended to assess the influence of training interventions, and demonstrate the value of combining empirical and computational modeling approaches to uncover the cognitive mechanisms that support learning and generalization.
+Future research should continue to investigate the complex interplay between task demands, training manipulations, and individual differences, with the ultimate goal of optimizing educational and training outcomes across a wide range of domains.
+
+\ \
+
+# Appendix
+
+[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html
+
 # References
-
 ::: {#refs}
 :::
-
-:::
-
-# Appendix
-
-### Appendix - Project 1
-
-{{< include ../Appendix/IGAS-Supplemental.qmd >}}
-
-{{< pagebreak >}}
-
-### Appendix - Project 2 - Experiment 1
-
-{{< include ../Appendix/E1_Appendix.qmd >}}
-
-::: {.content-visible when-format="pdf"}
-
-# References
-
-:::

### 2024-04-15 Manuscript/manuscript_old.qmd
big re-render of all versions

--- 2023-10-30 IGAS.qmd
@@
 ---
-title: IGAS Project
-subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
-date: last-modified
-#page-layout: full
-code-fold: true
-code-tools: true
-toc: true
+code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
+toc: false
+toc-depth: 3
 toc-location: body
-toc-title: Contents
 execute: 
   warning: false
-  eval: true
-editor: 
-  markdown: 
-    wrap: 72
+  include: true
 ---
 
-____________________________________________________
-[pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
-
-```{r}
-pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)
-source('Functions/IGAS_ProcessFunctions.R')
-
-theme_set(theme_classic())
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/pre_html.qmd >}}
+
+:::
+
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/pre_pdf.qmd >}}
+
+:::
+
+::: {.content-visible when-format="docx"}
+{{< include pre_sections/pre_docx.qmd >}}
+:::
+
+{{< pagebreak >}}
+
+# Abstract
+
+This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
+A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
+Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
+To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
+These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
+
+{{< pagebreak >}}
+
+::: {.content-visible when-format="html"}
+
+{{< include pre_sections/toc_html.qmd >}}
+
+:::
+
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/toc_pdf.qmd >}}
+
+:::
+
+{{< pagebreak >}}
+
+# Literature Review
+
+{{< include ../Introduction.qmd >}}
+
+```{r setup}
+
+#| 
+here::set_here(path='..')
+source(here::here("Functions", "packages.R"))
+
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
+
+# knitr::opts_chunk$set(echo = FALSE, include =TRUE, 
+#                       warning = FALSE, message = FALSE, eval=TRUE)
+
+# knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
+#                       fig.width = 6, fig.height = (6 * 0.618),
+#                       out.width = "100%", collapse = TRUE)
+# 
+options(digits = 3, width = 120,
+        dplyr.summarise.inform = FALSE,
+        knitr.kable.NA = "")
+
+```
+
+```{r}
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+
 # load the processed data from experiment 1 and 2
-e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
 # load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
 
@@
 
-```{r}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
+![The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
-
-mf <- cowplot::ggdraw()+cowplot::draw_image("Assets/methodsFig1.png",hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
-
-```
-
-## Results
-
-## Data Processing and Statistical Packages
+Participants were constrained to release the ball within the square](Assets/methodsFig1.png){#fig-igasTask}
+
+### Results
+
+#### Data Processing and Statistical Packages
 
@@
 
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>%   
-  kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
+kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
+
+#%>% kableExtra::kable_styling(position="left") 
+# %>%   
+#   kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
+
+```
+
+### Discussion
 
@@
 
-e2train1
-e2train2
-
-```
-
-### Testing Phase
+e2train1 / e2train2
+
+```
+
+#### Testing Phase
 
@@
 
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") %>% 
-  kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-## Discussion
+kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))
+
+#  %>% kableExtra::kable_styling(position="left") %>% 
+#   kable_classic() #%>% footnote(general=captionText,general_title = "")
+
+```
+
+### Discussion
 
@@
 
+# Project 2
+
+```{r}
+test <- readRDS(here::here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
+#options(brms.backend="cmdstanr",mc.cores=4)
+e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
+testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+# Introduction
+
+In project 1, I applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model.
+In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
+Project 2 also places a greater emphasis on extrapolation performance following training.
+Although varied training has often been purported to be particularly beneficial for generalization or transfer, few experiments have compared varied and constant training in contexts with unambiguous extrapolation testing.
+
+## Function Learning and Extrapolation
+
+The study of human function learning investigates how people learn relationships between continuous input and output values.
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021a; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+
+@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
+Input stimuli and output responses were both lines of varying length.
+The correct output response was related to the length of the input line by a linear, quadratic, or random function.
+Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
+Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
+Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
+Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
+@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
+In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
+Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
+
+The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
+In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
+Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
+All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
+Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
+
+The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
+The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
+The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
+
+The authors also introduced two new function-learning models.
+The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
+ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
+ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
+The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
+When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
+ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
+EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
+Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
+
+```{r}
+#| label: fig-delosh-extrap
+#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
+#| fig-width: 10
+source(here::here("Functions","deLosh_data.R"))
+
+extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
+                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
+
+linear_function <- function(x) 2.2 * x + 30
+exponential_function <- function(x) 200 * (1 - exp(-x/25))
+quadratic_function <- function(x) 210 - (x - 50)^2 / 12
+
+linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
+    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
+  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
+
+exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
+  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
+  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
+  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
+  extrapLines +
+  scale_shape_manual(values = c(1)) +
+  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
+  theme(legend.title = element_blank(), legend.position="top") +
+  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
+                                                  linetype = c(0, 1))))
+
+quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
+  geom_point( shape = 1) +
+  stat_function( fun = quadratic_function, geom = "line") +
+  labs(title="Quadratic Function",x="",y="") + extrapLines
+
+linear_plot + exponential_plot + quadratic_plot
+```
+
+# Methods
+
+## Participants
+
+Data was collected from 647 participants (after exclusions).
+The results shown below consider data from subjects in our initial experiment, which consisted of 196 participants (106 constant, 90 varied).
+The follow-up experiments entailed minor manipulations: 1) reversing the velocity bands that were trained on vs.
+novel during testing; 2) providing ordinal rather than numerical feedback during training (e.g.
+correct, too low, too high).
+The data from these subsequent experiments are largely consistently with our initial results shown below.
+
+## Task
+
+We developed a novel visuomotor extrapolation task, termed the Hit The Wall task, wherein participants learned to launch a projectile such that it hit a rectangle at the far end of the screen with an appropriate amount of force.
+Although the projectile had both x and y velocity components, only the x-dimension was relevant for the task.  [Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}
+
+## Procedure
+
+The HTW task involved launching projectiles to hit a target displayed on the computer screen.
+Participants completed a total of 90 trials during the training stage.
+In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
+In contrast, participants in the constant training condition encountered only one velocity band (800-1000).
+
+During the training stage, participants in both conditions also completed "no feedback" trials, where they received no information about their performance.
+These trials were randomly interleaved with the regular training trials.
+
+Following the training stage, participants proceeded to the testing stage, which consisted of three phases.
+In the first phase, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
+
+In the second phase of testing, participants completed "no-feedback" testing from the three velocity bands used during the training stage (800-1000, 1000-1200, and 1200-1400).
+In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
+
+The third and final phase of testing involved "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 10 trials.
+Participants received feedback on their performance during this phase.
+
+Throughout the experiment, participants' performance was measured by calculating the distance between the produced x-velocity of the projectiles and the closest edge of the current velocity band.
+Lower distances indicated better performance.
+
+After completing the experiment, participants were debriefed and provided with an opportunity to ask questions about the study.
+
+```{dot}
+//| label: fig-design-e1
+//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
+//| fig-width: 6.0
+//| fig-height: 2.5
+//| fig-responsive: false
+
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+
+```
+
+## Analyses Strategy
+
+All data processing and statistical analyses were performed in R version 4.31 @rcoreteamLanguageEnvironmentStatistical2020.
+To assess differences between groups, we used Bayesian Mixed Effects Regression.
+Model fitting was performed with the brms package in R @burknerBrmsPackageBayesian2017, and descriptive stats and tables were extracted with the BayestestR package @makowskiBayestestRDescribingEffects2019.
+Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
+Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as circumventing convergence issues common to the frequentist analogues of our mixed models.
+For each model, we report the median values of the posterior distribution, and 95% credible intervals.
+
+Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 of which were discarded as warmup chains.
+Rhat values were generally within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
+We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
+
+We compared varied and constant performance across two measures, deviation and discrimination.
+Deviation was quantified as the absolute deviation from the nearest boundary of the velocity band, or set to 0 if the throw velocity fell anywhere inside the target band.
+Thus, when the target band was 600-800, throws of 400, 650, and 1100 would result in deviation values of 200, 0, and 300, respectively.
+Discrimination was measured by fitting a linear model to the testing throws of each subjects, with the lower end of the target velocity band as the predicted variable, and the x velocity produced by the participants as the predictor variable.
+Participants who reliably discriminated between velocity bands tended to have positive slopes with values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
+
+```{r}
+#| label: tbl-e1-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap:
+#|   - "Full datasets"
+#|   - "Intersection of samples with all labels available"
+#| layout-ncol: 1
+
+result <- test_summary_table(test, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+
+result$constant |>kable(booktabs = TRUE,
+                        linesep = "\\addlinespace[0.5em]",
+                        caption = paste("Summary of Deviation- Constant"))
+# |>
+#   kable_styling(font_size = ifelse(fmt_out == "latex", 8.5, NA))
+
+result$varied |> kable(booktabs = TRUE,
+                        linesep = "\\addlinespace[0.5em]",
+                        caption = paste("Summary of Deviation- Varied"))
+
+```
+
+## Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e1-test-nf-deviation and @fig-e1-test-dev.
+To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+```{=tex}
+\begin{equation}
+dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
+\end{equation}
+```
+
+```{r}
+#| label: fig-e1-test-dev
+#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
+test |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target")
+```
+
+```{r}
+#| label: tbl-e1-bmm-dist
+#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+#| tbl-subcap: ["Constant Testing1 - Deviation", "Varied Testing - Deviation"]
+modelName <- "e1_testDistBand_RF_5K"
+e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=test,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+GetModelStats(e1_distBMM) |> kable(booktabs = TRUE,caption = paste("Coefficients"))
+
+e1_distBMM |> 
+  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
+          epred = TRUE, re_formula = NA) |> 
+  pairs() |> gather_emmeans_draws()  |> 
+   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
+   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
+   mutate(across(where(is.numeric), \(x) round(x, 2)),
+          pd=ifelse(value<0,1-pd,pd)) |> kable(booktabs = TRUE)
+# |> 
+#   kable(caption="Contrasts")
+
+coef_details <- get_coef_details(e1_distBMM, "conditVaried")
+
+```
+
+The model predicting absolute deviation (dist) showed clear effects of both training condition and target velocity band (Table X).
+Overall, the varied training group showed a larger deviation relative to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]).
+Deviation also depended on target velocity band, with lower bands showing less deviation.
+See @tbl-e1-bmm-dist for full model output.
+
+#### Discrimination between bands
+
+In addition to accuracy/deviation, we also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e1-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants on each testing trial.
+
+```{=tex}
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+```
+
+```{r}
+#| label: fig-e1-test-vx
+#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 9
+
+test %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e1-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant", "Varied"]
+
+result <- test_summary_table(test, "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kable(booktabs = TRUE)
+result$varied |> kable(booktabs = TRUE)
+
+```
+
+```{r}
+#| label: tbl-e1-bmm-vx
+#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
+e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+GetModelStats(e1_vxBMM ) |> kable(booktabs=T, caption="Fit to all 6 bands")
+
+cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e1_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
+
+modelName <- "e1_extrap_testVxBand"
+e1_extrap_VxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                  data=test |>
+                    filter(expMode=="test-Nf"),file=paste0(here::here("data/model_cache",modelName)),
+                  iter=5000,chains=4)
+GetModelStats(e1_extrap_VxBMM ) |> kable(booktabs=T, caption="Fit to 3 extrapolation bands")
+
+sc2 <- get_coef_details(e1_extrap_VxBMM, "bandInt")
+intCoef2 <- get_coef_details(e1_extrap_VxBMM, "conditVaried:bandInt")
+
+```
+
+See @tbl-e1-bmm-vx for the full model results.
+The estimated coefficient for training condition ($B$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination.
+Most relevant to the issue of discrimination is the slope on Velocity Band ($B$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
+Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
+The estimate for the interaction between slope and condition ($B$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less senitivity between vands than the constant condition.
+This difference is depicted visually in @fig-e1-bmm-vx.Slope coefficients are broken down by quartile in @tbl-e1-slope-quartile.
+The constant participant participants appear to have larger slopes across quartiles, but the difference between conditions may be less pronounced for the top quartiles of subjects who show the strongest discrimination.
+Figure @fig-e1-bmm-bx2 shows the distributions of slope values for each participant, and the compares the probability density of slope coefficients between training conditions.
+@fig-e1-indv-slopes
+
+The second model, which focused solely on extrapolation bands, revealed similar patterns.
+The Velocity Band term ($B$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]) still demonstrates a high degree of discrimination ability.
+However, the posterior distribution for interaction term ($B$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\] ) does across over 0, suggesting that the evidence for decreased discrimination ability for the varied participants is not as strong when considering only the three extrapolation bands.
+
+```{r}
+#| label: fig-e1-bmm-vx
+#| fig-cap: Conditional effect of training condition and Band.
+Ribbons indicate 95% HDI.
+The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
+#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
+#| layout-ncol: 1
+
+e1_vxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |> 
+  condEffects() +
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(test$vb), 
+                     limits = c(0, 1400))
+
+e1_extrap_VxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600))) |>
+  gather_emmeans_draws() |>
+  condEffects() +
+  scale_x_continuous(breaks = c(100, 350, 600), 
+                     labels = levels(test$vb)[1:3], 
+                     limits = c(0, 1000))
+
+```
+
+```{r}
+#| label: tbl-e1-slope-quartile
+#| tbl-cap: "Slope coefficients by quartile, per condition"
+
+new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")]))) |> 
+  dplyr::arrange(id,bandInt) |> 
+  mutate(condit_dummy = ifelse(condit == "Varied", 1, 0))
+
+indv_coefs <- as_tibble(coef(e1_vxBMM)$id, rownames="id")|> 
+  select(id, starts_with("Est")) |>
+  left_join(e1Sbjs, by=join_by(id) )
+
+fixed_effects <- e1_vxBMM |> 
+  spread_draws(`^b_.*`,regex=TRUE) |> arrange(.chain,.draw,.iteration)
+
+random_effects <- e1_vxBMM |> 
+  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
+  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
+  mutate(id = factor(id,levels=levels(test$id))) |> 
+  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)
+
+ indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
+  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
+  right_join(new_data_grid, by = join_by("id")) |> 
+  mutate(
+    Slope = bandInt_RF+b_bandInt,
+    Intercept= RF_Intercept + b_Intercept,
+    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
+    SlopeInt = Slope + (`b_conditVaried:bandInt`*condit_dummy)
+  )
+
+  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt, Intercept,b_Intercept,b_bandInt) |>
+  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
+    select(id,condit,Intercept,b_Intercept,starts_with("Slope"),b_bandInt, n) |>
+  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()
+
+  indvSlopes |> mutate(Condition=condit) |>  group_by(Condition) |> 
+    reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
+  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
+  group_by(Condition) |>
+  summarise(across(starts_with("Q"), list(mean = mean))) |> kable()
+
+```
+
+```{r}
+#| label: fig-e1-bmm-bx2
+#| fig-cap: Slope distributions between condition
+#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
+#| layout-ncol: 2
+#| fig-height: 9
+#| fig-width: 10
+
+indvSlopes |> ggplot(aes(y=rankSlope, x=SlopeInt,fill=condit,color=condit)) + 
+  geom_pointrange(aes(xmin=SlopeInt.lower , xmax=SlopeInt.upper)) + 
+  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)
+
+   ggplot(indvSlopes, aes(x = SlopeInt, color = condit)) + 
+  geom_density() + labs(x="Slope Coefficient",y="Density")
+
+```
+
+```{r}
+#| label: fig-e1-indv-slopes
+#| fig-cap: Subset of Varied and Constant Participants with the smallest and largest estimated slope values.
+Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution.
+Black points and intervals at each band represent the estimated median and 95% HDI.
+Blue points are empirical means.
+#| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
+#| fig-height: 6
+#| fig-width: 9
+
+nSbj <- 3
+indvDraws  |> indv_model_plot(indvSlopes, testAvg, SlopeInt,rank_variable=Slope,n_sbj=nSbj,"max")
+indvDraws |> indv_model_plot(indvSlopes, testAvg,SlopeInt, rank_variable=Slope,n_sbj=nSbj,"min")
+
+```
+
+# Experiment 2
+
+```{r setup2b}
+testE2 <- readRDS(here::here("data/e2_08-21-23.rds")) |> filter(expMode2 == "Test") 
+e2Sbjs <- testE2 |> group_by(id,condit) |> summarise(n=n())
+testE2Avg <- testE2 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+@fig-design-e2 illustrates the design of Experiment 2.
+The stages of the experiment (i.e.
+training, testing no-feedback, test with feedback), are identical to that of Experiment 1.
+The only change is that Experiment 2 participants train, and then test, on bands in the reverse order of Experiment 1 (i.e.
+training on the softer bands; and testing on the harder bands).
+
+```{dot}
+//| label: fig-design-e2
+//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
+//| fig-width: 6.0
+//| fig-height: 2.5
+//| fig-responsive: false
+//| fig-align: left
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+
+```
+
+## E2 Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e2-test-nf-deviation and @fig-e2-test-dev. 
+To model differences in accuracy between groups, we used Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+\begin{equation}
+dist_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot band_{ij} + \beta_3 \cdot condit_{ij} \cdot band_{ij} + b_{0i} + b_{1i} \cdot band_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: tbl-e2-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
+
+result <- test_summary_table(testE2, "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kable()
+result$varied |> kable()
+# make kable table with smaller font size
+# result$constant |> kable(caption="Constant Testing - Deviation",booktabs=T,escape=F) |> kable_styling(font_size = 7)
+```
+
+```{r}
+#| label: fig-e2-test-dev
+#| fig-cap: E2. Deviations from target band during testing without feedback stage. 
+testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target")
+```
+
+```{r}
+#| label: tbl-e2-bmm-dist
+#| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+
+modelName <- "e2_testDistBand_RF_5K"
+e2_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=testE2,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+mp2 <- GetModelStats(e2_distBMM) |> kable(booktabs=T)
+mp2
+
+e2_distBMM |> 
+  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
+          epred = TRUE, re_formula = NA) |> 
+  pairs() |> gather_emmeans_draws()  |> 
+   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
+   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
+   mutate(across(where(is.numeric), \(x) round(x, 2)),
+          pd=ifelse(value<0,1-pd,pd)) |>
+   kable(caption="Contrasts")
+
+coef_details <- get_coef_details(e2_distBMM, "conditVaried")
+
+```
+
+The model predicting absolute deviation showed a modest tendency for the varied training group to have lower deviation compared to the constant training group (β = `r coef_details$estimate`, 95% CI \[`r coef_details$conf.low`, `r coef_details$conf.high`\]),with 94% of the posterior distribution being less than 0.
+This suggests a potential benefit of training with variation, though the evidence is not definitive.
+
+#### Discrimination between Velocity Bands
+
+In addition to accuracy/deviation.
+We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e2-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
+
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: fig-e2-test-vx
+#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 11
+#| fig-height: 9
+testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
+
+```
+
+```{r}
+#| label: tbl-e2-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
+#| layout-ncol: 1
+
+result <- test_summary_table(testE2, "vx","X Velocity" ,mfun = list(mean = mean, median = median, sd = sd))
+result$constant |> kable()
+result$varied |> kable()
+
+```
+
+```{r}
+#| label: tbl-e2-bmm-vx
+#| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=testE2,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+mt3 <-GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T)
+mt3
+
+cd1 <- get_coef_details(e2_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e2_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
+```
+
+See @tbl-e2-bmm-vx for the full model results.
+
+When examining discrimination ability using the model predicting raw x-velocity, the results were less clear than those of the absolute deviation analysis.
+The slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]) indicates that participants showed good discrimination between bands overall.
+However, the interaction term suggested this effect was not modulated by training condition (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]) Thus, while varied training may provide some advantage for accuracy, both training conditions seem to have similar abilities to discriminate between velocity bands.
+
+```{r}
+#| label: fig-e2-bmm-vx
+#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI.
+
+e2_vxBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |>
+  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+  ylab("Predicted X Velocity") + xlab("Band")+
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE2$vb), 
+                     limits = c(0, 1400)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+```
+
+# Experiment 3
+
+```{r setup3b}
+testE3 <- readRDS(here::here("data/e3_08-21-23.rds")) |> filter(expMode2 == "Test") 
+e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
+testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
+  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
+```
+
+The major manipulation adjustment of experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the earlier experiments.
+Ordinal feedback informs participants whether a throw was too soft, too hard, or fell within the target velocity range.
+Experiment 3 participants were randomly assigned to both a training condition (Constant vs.
+Varied) and a Band Order condition (original order used in Experiment 1, or the Reverse order of Experiment 2).
+
+## Results
+
+### Testing Phase - No feedback.
+
+In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw.
+Note that these no-feedback testing trials are identical to those of Experiment 1 and 2, as the ordinal feedback only occurs during the training phase, and final testing phase, of Experiment 3.
+
+#### Deviation From Target Band
+
+Descriptive summaries testing deviation data are provided in @tbl-e3-test-nf-deviation and @fig-e3-test-dev. 
+To model differences in accuracy between groups, we fit Bayesian mixed effects regression models to the trial level data from the testing phase.
+The primary model predicted the absolute deviation from the target velocity band (dist) as a function of training condition (condit), target velocity band (band), and their interaction, with random intercepts and slopes for each participant (id).
+
+```{r}
+#| label: tbl-e3-test-nf-deviation
+#| tbl-cap: "Testing Deviation - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - Deviation", "Varied Testing - Deviation"]
+
+resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+resultOrig$constant |> kable()
+resultOrig$varied |> kable()
+
+resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
+resultRev$constant |> kable()
+resultRev$varied |> kable()
+
+```
+
+```{r}
+#| label: fig-e3-test-dev
+#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
+testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
+    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+```
+
+```{r}
+#| label: tbl-e3-bmm-dist
+#| tbl-cap: "Experiment 3. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
+
+modelName <- "e3_testDistBand_RF_5K"
+e3_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
+                      data=testE3,file=paste0(here::here("data/model_cache",modelName)),
+                      iter=5000,chains=4)
+mp3 <- GetModelStats(e3_distBMM) |> kable(booktabs=T)
+mp3
+
+cd1 <- get_coef_details(e3_distBMM, "conditVaried")
+sc1 <- get_coef_details(e3_distBMM, "bandInt")
+intCoef1 <- get_coef_details(e3_distBMM, "conditVaried:bandInt")
+```
+
+The effect of training condition in Experiment 3 showed a similar pattern to Experiment 2, with the varied group tending to have lower deviation than the constant group (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0.
+
+```{r}
+#| label: fig-e3-bmm-dist
+#| fig-cap: e3. Conditioinal Effect of Training Condition and Band. Ribbon indicated 95% Credible Intervals.
+
+e3_distBMM |> emmeans( ~condit + bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |>
+  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+    ylab("Predicted Deviation") + xlab("Velocity Band")+
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE3$vb), 
+                     limits = c(0, 1400)) +
+  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
+```
+
+#### Discrimination between Velocity Bands
+
+In addition to accuracy/deviation.
+We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e.
+responding differently when prompted for band 600-800 than when prompted for band 150-350).
+@tbl-e3-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band.
+To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants.
+
+\begin{equation}
+vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
+\end{equation}
+
+```{r}
+#| label: fig-e3-test-vx
+#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-width: 12
+#| fig-height: 13
+# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
+# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
+
+testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
+  facet_wrap(bandOrder~condit,scale="free_x")
+
+```
+
+```{r}
+#| label: tbl-e3-test-nf-vx
+#| tbl-cap: "Testing vx - Empirical Summary"
+#| tbl-subcap: ["Constant Testing - vx", "Varied Testing - vx"]
+
+resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+resultOrig$constant |> kable()
+resultOrig$varied |> kable()
+
+resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
+resultRev$constant |> kable()
+resultRev$varied |> kable()
+```
+
+```{r}
+#| label: tbl-e3-bmm-vx
+#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
+
+e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
+                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
+                        iter=5000,chains=4,silent=0,
+                        control=list(adapt_delta=0.94, max_treedepth=13))
+mt4 <-GetModelStats(e3_vxBMM ) |> kable(booktabs=T)
+mt4
+
+cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
+sc1 <- get_coef_details(e3_vxBMM, "bandInt")
+intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
+```
+
+See @tbl-e3-bmm-vx for the full model results.
+
+Slope estimates for experiment 3 suggest that participants were capable of distinguishing between velocity bands even when provided only ordinal feedback during training (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
+Unlike the previous two experiments, the posterior distribution for the interaction between condition and band was consistently positive, suggestive of superior discrimination for the varied participants
+β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\].
+
+### Computational Modelling
+
+{{< include ../Sections/htw_exam.qmd >}}
+
+::: {.content-visible unless-format="pdf"}
 # References
@@
 
+:::
+
 # Appendix
 
+### Appendix - Project 1
+
 {{< include Appendix/IGAS-Supplemental.qmd >}}
+
+{{< pagebreak >}}
+
+### Appendix - Project 2 - Experiment 1
+
+{{< include ../Appendix/E1_Appendix.qmd >}}
+
+::: {.content-visible when-format="pdf"}
+
+# References
+
+:::

### 2024-04-15 Manuscript/pre_sections/pre_html.qmd
big re-render of all versions

--- 2023-10-19 Manuscript/pre_sections/pre_html.qmd
@@
 <div style="text-align: center; margin-top: 50px; font-size: 24px; font-weight: bold;">
-  The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach
+ The Role of Variability in Learning Generalization: A Computational Modeling Approach
 </div>
@@
 </div>
-
-<!-- Second Page and so on... -->
-<div style="text-align: justify; margin-top: 700px;">
-  Submitted to the faculty of the University Graduate School in partial fulfillment of the
-  requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
-  Sciences and the Cognitive Science Program, Indiana University
-  Indiana University
-</div>
-
-<div style="margin-top: 400px;">
-  <!-- Your page numbering if needed -->
-</div>
-
-<div style="page-break-before: always;"></div>
-
-<!-- Committee Members Page -->
-<div style="text-align: center; margin-top: 300px;">
-  Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
-  requirements for the degree of Doctor of Philosophy.
-</div>
-
-<div style="text-align: center; margin-top: 300px;">
-  _____________________________  Robert L. Goldstone<br><br>
-  _____________________________  Robert Nosofsky<br><br>
-  _____________________________  Peter Todd<br><br>
-  _____________________________  Mike Jones
-</div>
-
-<div style="page-break-before: always;"></div>
-
-<div style="page-break-before: always;"></div>
-
-<!-- Acknowledgements -->
-<div style="text-align: center; font-weight: bold; font-size: 24px;">
-  Acknowledgements
-</div>
-<div style="text-align: center; margin-top: 700px; font-size: 24px;">
-
-</div>
-
-<div style="page-break-before: always;"></div>

### 2024-04-15 Manuscript/pre_sections/pre_html_full.qmd
big re-render of all versions

<div style="text-align: center; margin-top: 50px; font-size: 24px; font-weight: bold;">
 The Role of Variability in Learning Generalization: A Computational Modeling Approach
</div>

<div style="text-align: center; margin-top: 300px; font-size: 32px;">
  Thomas E. Gorman
</div>

Second Page and so on...
<div style="text-align: justify; margin-top: 700px;">
  Submitted to the faculty of the University Graduate School in partial fulfillment of the
  requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
  Sciences and the Cognitive Science Program, Indiana University
  Indiana University
</div>

<div style="margin-top: 400px;">
  <!-- Your page numbering if needed -->
</div>

<div style="page-break-before: always;"></div>

<!-- Committee Members Page -->
<div style="text-align: center; margin-top: 300px;">
  Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
  requirements for the degree of Doctor of Philosophy.
</div>

<div style="text-align: center; margin-top: 300px;">
  _____________________________  Robert L. Goldstone, PhD<br><br>
  _____________________________  Robert Nosofsky, PhD<br><br>
  _____________________________  Peter Todd, PhD<br><br>
  _____________________________  Mike Jones, PhD
</div>

<div style="page-break-before: always;"></div>

<div style="page-break-before: always;"></div>

<!-- Acknowledgements -->
<div style="text-align: center; font-weight: bold; font-size: 24px;">
  Acknowledgements
</div>
<div style="text-align: center; margin-top: 700px; font-size: 24px;">

</div>

<div style="page-break-before: always;"></div>

### 2024-04-15 Manuscript/pre_sections/pre_pdf.qmd
manuscript update
fix docx and html. Update htw with embed
add supplementals
adjust appendices
render full in pdf and markdown
big re-render of all versions

@@
 \LARGE
-{Variability and Generalization - A Similarity-Based Account}
+{The Role of Variability in Learning Generalization: A Computational Modeling Approach}
 
@@
 
-\vspace{11.5cm}
+\vspace{16.5cm}
 
 \end{centering}
-
-Submitted to the faculty of the University Graduate School in partial fulfillment of the
-requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
-Sciences and the Cognitive Science Program, Indiana University
-Indiana University
 
@@
 \newpage
-
-Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
-requirements for the degree of Doctor of Philosophy.
-\vspace{4cm}
-
-\
-\_____________________________  Robert L. Goldstone
-\vspace{2.5cm}
-\
-\
-\_____________________________  Robert Nosofsky
-\vspace{2.5cm}
-\
-\_____________________________  Peter Todd
-\vspace{2.5cm}
-\
-\_____________________________  Mike Jones
-
-\newpage
-
-\begin{centering}
-
-\vspace*{6.5cm}
-
-@2023 \\
-\vspace{1cm}
-
-Thomas E. Gorman
-\vspace{.2cm}
-
-\vspace{5cm}
-
-\end{centering}
-
-\newpage
-\begin{center}
-\textbf{Acknowledgements}
-\end{center}
-\newpage
-
-\tableofcontents
-\newpage
-\listoffigures
-\newpage
-\listoftables
-\newpage

### 2024-04-15 Manuscript/pre_sections/pre_pdf_full.qmd
big re-render of all versions

--- 2023-10-29 Manuscript/igas_e1.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
-%
-\documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
-
-\usepackage{amsmath,amssymb}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else  
-    % xetex/luatex font selection
-  \setmathfont[]{Libertinus Math}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\usepackage[top=1in,bottom=1in,left=1in,right=1in,heightrounded]{geometry}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
-  \fi
-  % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\KOMAoption{captions}{tableheading}
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  colorlinks=true,
-  linkcolor={DarkSlateBlue},
-  filecolor={Maroon},
-  citecolor={DarkSlateBlue},
-  urlcolor={DarkSlateBlue},
-  pdfcreator={LaTeX via pandoc}}
-
-\author{}
-\date{}
-
-\begin{document}
 \begin{centering}
 \LARGE
-{The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach}
+{The Role of Variability in Learning Generalization: A Computational Modeling Approach}
 
@@
 
-Submitted to the faculty of the University Graduate School in partial
-fulfillment of the requirements for the degree Doctor of Philosophy in
-the Department of Psychology and Brain Sciences and the Cognitive
-Science Program, Indiana University Indiana University
+Submitted to the faculty of the University Graduate School in partial fulfillment of the
+requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
+Sciences and the Cognitive Science Program, Indiana University
+Indiana University
 
@@
 
-Accepted by the Graduate Faculty, Indiana University, in partial
-fulfillment of the requirements for the degree of Doctor of Philosophy.
+Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
+requirements for the degree of Doctor of Philosophy.
 \vspace{4cm}
 
-\hfill\break
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Robert L.
-Goldstone, PhD \vspace{2.5cm}\\
-\strut \\
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Robert
-Nosofsky, PhD \vspace{2.5cm}\\
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Peter Todd,
-PhD \vspace{2.5cm}\\
-\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ Mike Jones,
-PhD
+\
+\_____________________________  Robert L. Goldstone, PhD
+\vspace{2.5cm}
+\
+\
+\_____________________________  Robert Nosofsky, PhD
+\vspace{2.5cm}
+\
+\_____________________________  Peter Todd, PhD
+\vspace{2.5cm}
+\
+\_____________________________  Mike Jones, PhD
 
@@
 \newpage
-
-\newpage{}
-
-\section{Abstract}\label{abstract}
-
-This dissertation seeks to explore the cognitive underpinnings that
-govern the generalization of learning, focusing specifically on the role
-of variability during training in shaping subsequent transfer
-performance. A comprehensive review of the existing literature is
-presented, emphasizing the methodological complications associated with
-disentangling the confounding effects of similarity. Through a series of
-experiments involving several novel visuomotor tasks, this work
-investigates whether and how variability in training conditions affects
-performance in novel tasks. To theoretically account for the empirical
-outcomes, I employ both instance-based and connectionist computational
-models, both of which incorporate similarity-based mechanisms. These
-models serve to account for the extent to which variability influences
-the learners' generalization gradient, and also explain how training
-variation can produce both beneficial and deleterious outcomes.
-
-\newpage{}
-
-\tableofcontents
-\newpage
-\listoffigures
-\newpage
-\listoftables
-\newpage
-
-\newpage{}
-
-\subsection{Main body}\label{main-body}
-
-Following the procedure used by Mcdaniel et al.
-(\citeproc{ref-mcdanielPredictingTransferPerformance2009}{2009}), we
-will assess the ability of both ALM and EXAM to account for the
-empirical data when fitting the models to 1) only the training data, and
-2) both training and testing data. Models will be fit directly to the
-trial by trial data of each individual participants, both by minimizing
-the root-mean squared deviation (RMSE), and by maximizing log
-likelihood. Because ALM has been shown to do poorly at accounting for
-human patterns extrapolation
-(\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al., 1997}), we
-will also fit the extended EXAM version of the model, which operates
-identically to ALM during training, but includes a linear extrapolation
-mechanism for generating novel responses during testing.
-
-quarto pandoc --citeproc --pdf-engine xelatex -t pdf\\
---bibliography=../Assets/Bib/Dissertation.bib\\
---standalone\\
--f markdown igas\_e1.pdf.md\\
--o refer-test.pdf
-
-quarto render igas\_e1.qmd --citeproc --pdf-engine xelatex -t pdf\\
---bibliography=../Assets/Bib/Dissertation.bib\\
---standalone\\
--o refer-test.pdf
-
-\section{Appendix}\label{appendix}
-
-\subsubsection{Appendix - Project 2 - Experiment
-1}\label{appendix---project-2---experiment-1}
-
-\subsection{E1 Appendix}\label{e1-appendix}
-
-\subsubsection{Posterior Predictive
-Distributions}\label{posterior-predictive-distributions}
-
-\subsubsection{Empirical vs.~Predicted}\label{empirical-vs.-predicted}
-
-\subsubsection{Different Aggregations}\label{different-aggregations}
-
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
-
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-deloshExtrapolationSineQua1997}
-DeLosh, E. L., McDaniel, M. A., \& Busemeyer, J. R. (1997).
-Extrapolation: {The Sine Qua Non} for {Abstraction} in {Function
-Learning}. \emph{Journal of Experimental Psychology: Learning, Memory,
-and Cognition}, \emph{23}(4), 19.
-\url{https://doi.org/10.1037/0278-7393.23.4.968}
-
-\bibitem[\citeproctext]{ref-mcdanielPredictingTransferPerformance2009}
-Mcdaniel, M. A., Dimperio, E., Griego, J. A., \& Busemeyer, J. R.
-(2009). Predicting transfer performance: {A} comparison of competing
-function learning models. \emph{Journal of Experimental Psychology.
-Learning, Memory, and Cognition}, \emph{35}, 173--195.
-\url{https://doi.org/10.1037/a0013982}
-
-\end{CSLReferences}
-
-\end{document}

### 2024-04-15 Sections/HTW.qmd
big re-render of all versions

@@
 
+::: {#tbl-brms-models}
 | Group Comparison         | Code                                                        | Data                 |
 | ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|band) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + band|id) ``             | All Testing Trials   |
+| End of Training Accuracy | `` brm(Abs. Deviation ~ condit) ``                                    | Final Training Block |
+| Test Accuracy            | `` brm(Abs. Deviation ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
+| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
+
+: **Statistical Model Specifications**.
+The specifications for the bayesian regression models used in the analyses of each of the 3 experiments.
+Comparisons of accuracy use abosulte deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
+:::
 \
@@
 *Computational Model Summary*.
-Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23).
-This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group.
-It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model.
-A subset of these participants are shown in @fig-htw-indv-pred.
+Across all three experiments, the model fits consistently favored the Extrapolation-Association Model (EXAM) over the Associative Learning Model (ALM).
+This preference for EXAM was particularly pronounced for participants in the constant training conditions (note the positive coefficients on ModelEXAM:conditVaried interaction terms @tbl-htw-ee-e23).
+This pattern is clearly illustrated in @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
+Both varied and constant conditions have a greater proportion of subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly larger for the constant group.
+
+The superior performance of EXAM, especially for the constant training groups, may initially seem counterintuitive.
+One might assume that exposure to multiple, varied examples would be necessary to extract an abstract rule.
+However, EXAM is not a conventional rule-based model; it does not require the explicit abstraction of a rule.
+Instead, rule-based responses emerge during the retrieval process.
+The constant groups' formation of a single, accurate input-output association, combined with the usefulness of the zero point, may have been sufficient for EXAM to capture their performance.
+A potential concern is that the assumption of participants utilizing the zero point essentially transforms the extrapolation problem into an interpolation problem.
+However, this concern is mitigated by the consistency of the results across both the original and reversed order conditions (the testing extrapolation bands fall in between the constant training band and the 0 point in experiment 1, but not in experiment 2).
+
+The fits to the individual participants also reveal a number of interesting cases where the models struggle to capture the data (@fig-htw-indv-pred).
+For example participant 68 exhibits a strong a strong non-monotonicity in the highest velocity band, a pattern which ALM can mimic, but which EXAM cannot capture, given it's to enforce a simple linear relationship between target velocity and response.
+Participant 70 (lower right corner of @fig-htw-indv-pred) had a roughly parabolic response pattern in their observed data, a pattern which neither model can properly reproduce, but which causes EXAM to perform particularly poorly.
+
+*Modeling Limitations.* The present work compared models based on their ability to predict the observed data, without employing conventional model fit indices such as the Akaike Information Criterion (AIC) or the Bayesian Information Criterion (BIC).
+These indices, which penalize models based on their number of free parameters, would have been of limited utility in this case, as both ALM and EXAM have two free parameters.
+However, despite having the same number of free parameters, EXAM could still be considered the more complex model, as it incorporates all the components of ALM plus an additional mechanism for rule-based responding.
+A more comprehensive model comparison approach might involve performing cross-validation with a held-out subset of the data [@mezzadriHoldoutStrategySelecting2022] or penalizing models based on the range of patterns they can produce [@domeGdistanceComparisonModel2023].
 
@@
 
-*Modeling Summary*
-EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group.
-May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule.
-But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval.
-The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-
-One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
-
 *Limitations*

### 2024-04-15 Sections/IGAS.qmd
big re-render of all versions

@@
 toc-title: Contents
+toc-depth: 4
 format:

### 2024-04-15 Sections/full.qmd
big re-render of all versions

@@
 ---
-title: Full Dissertation
-subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
+title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
+#subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
 #date: 04/04/24
@@
 toc-title: Contents
+toc-depth: 4
 cache: true
@@
 
-## Introduction
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/toc_pdf.qmd >}}
+
+:::
+
+{{< pagebreak >}}
+
+# Introduction
+
+## Varied Training and Generalization
 
@@
 LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
-At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e.
+At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had three prior exposures to the word arrangement (i.e.
 the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group.
+However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving two more anagrams on average than the constant group.
 This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
@@
 
-### Existing Theoretircal Frameworks
+## Existing Theoretircal Frameworks
 
@@
 
-### The current work
+## The current work
 
@@
 
-# Abstract
+## Abstract
 
@@
 
-## Similarity and instance-based approaches to transfer of learning
+## Introduction
+
+### Similarity and instance-based approaches to transfer of learning
 
@@
 
-## Results
-
-## Data Processing and Statistical Packages
+### Results
+
+#### Data Processing and Statistical Packages
 
@@
 
-## Testing Phase
+#### Testing Phase
 
@@
 
-## Methods
-
-### Participants
+### Methods
+
+#### Participants
 
@@
 
-### Task and Procedure
+#### Task and Procedure
 
@@
 
-## Results
-
-### Data Processing and Statistical Packages
+### Results
+
+#### Data Processing and Statistical Packages
 
@@
 
-## Discussion
+### Experiment 2 Discussion
 
@@
 
-# Computational Model
+## Computational Model
 
@@
 
-## Fitting model parameters separately by group
+### Fitting model parameters separately by group
 
@@
 
-# General Discussion
+## Project 1 General Discussion
 
@@
 
-## Limitations
+### Limitations
 
@@
 However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
-## Conclusion
+
+### Conclusion
 
@@
 
-## Function Learning and Extrapolation
+### Function Learning and Extrapolation
 
@@
 
-## Overview Of Present Study
+### Overview Of Present Study
 
@@
 
-## Methods
+## Experiment 1
+
+### Methods
 
@@
 
+::: {#tbl-brms-models}
 | Group Comparison         | Code                                                        | Data                 |
 | ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(dist ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(dist ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
+| End of Training Accuracy | `` brm(Abs. Deviation ~ condit) ``                                    | Final Training Block |
+| Test Accuracy            | `` brm(Abs. Deviation ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
 | Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
+
+: **Statistical Model Specifications**.
+The specifications for the bayesian regression models used in the analyses of each of the 3 experiments.
+Comparisons of accuracy use abosulte deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
+:::
 \
@@
 
-## E1 Summary
+### Experiment 1 Summary
 
@@
 //| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 8.0
-//| fig-height: 2.5
+//| fig-width: 7.0
+//| fig-height: 2.2
 //| fig-responsive: false
@@
 {.sm}
+:::
 
@@
 
-# Modeling Approach
-
 The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
@@
 
-## ALM & Exam Description
+### ALM & Exam
 
@@
 
-## Model Fitting
+### Model Fitting
 
@@
   tab_options(
-    column_labels.font.size = 10,
+    table.font.size = 12,
     heading.title.font.size = 14,
     heading.subtitle.font.size = 12,
-    table.font.size = 10, 
-    quarto.disable_processing = TRUE
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
   )
@@
 #| label: fig-ee-e1
-#| fig-caption: conditional and marginal effects
+#| fig-cap: A) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+Varied).
+Lower values on the y axis indicate better model fit.
+B) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs.
+EXAM for the varied group; 3) ALM fits between constant and varied.
+Negative error differences indicate that the term on the left side (e.g.
+EXAM Constant) tended to have smaller model residuals.
 #| fig-height: 8
@@
 
-p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+#p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
 
@@
 
-p_ce_1 / p_em_1
+#p_ce_1 / p_em_1
+
+(p1 + p2+ p3) /p_em_1 + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+
 ```
@@
   tab_options(
-    column_labels.font.size = 10,
+    table.font.size = 12,
     heading.title.font.size = 14,
     heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
   )
@@
 ```
+
+\ \ \
 
@@
 ```
+
+{{< pagebreak >}}
+
+\scriptsize
 
@@
     columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
-    decimals = 2
+    decimals = 1
   ) %>%
@@
   tab_options(
-    table.font.size = 10,
-    heading.title.font.size = 16,
-    heading.subtitle.font.size = 14,
-    quarto.disable_processing = TRUE
+    table.font.size = 12,
+    heading.title.font.size = 14,
+    heading.subtitle.font.size = 12,
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
     #row_group.background.color = "gray95"
@@
 ```
+
+\normalsize
 
@@
 Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
-We thus also controleld for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
+We thus also controlled for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
 There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
@@
 *Computational Model Summary*.
-Across the model fits to all three experiments, we found greater support for EXAM over ALM (negative coefficients on the ModelEXAM term in @tbl-htw-ee-e23), and moreover that the constant participants were disproportionately well described by EXAM in comparison to ALM (positive coefficients on ModelEXAM:conditVaried terms in @tbl-htw-ee-e23).
-This pattern is also clearly depicted in  @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a  greater proportion of  subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly greater for the constant group.
-It also bears mention that numerous participants were better fit by ALM, or did not show a clear preference for either model.
-A subset of these participants are shown in @fig-htw-indv-pred.
+Across all three experiments, the model fits consistently favored the Extrapolation-Association Model (EXAM) over the Associative Learning Model (ALM).
+This preference for EXAM was particularly pronounced for participants in the constant training conditions (note the positive coefficients on ModelEXAM:conditVaried interaction terms @tbl-htw-ee-e23).
+This pattern is clearly illustrated in @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
+Both varied and constant conditions have a greater proportion of subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly larger for the constant group.
+
+The superior performance of EXAM, especially for the constant training groups, may initially seem counterintuitive.
+One might assume that exposure to multiple, varied examples would be necessary to extract an abstract rule.
+However, EXAM is not a conventional rule-based model; it does not require the explicit abstraction of a rule.
+Instead, rule-based responses emerge during the retrieval process.
+The constant groups' formation of a single, accurate input-output association, combined with the usefulness of the zero point, may have been sufficient for EXAM to capture their performance.
+A potential concern is that the assumption of participants utilizing the zero point essentially transforms the extrapolation problem into an interpolation problem.
+However, this concern is mitigated by the consistency of the results across both the original and reversed order conditions (the testing extrapolation bands fall in between the constant training band and the 0 point in experiment 1, but not in experiment 2).
+
+The fits to the individual participants also reveal a number of interesting cases where the models struggle to capture the data (@fig-htw-indv-pred).
+For example participant 68 exhibits a strong a strong non-monotonicity in the highest velocity band, a pattern which ALM can mimic, but which EXAM cannot capture, given it's to enforce a simple linear relationship between target velocity and response.
+Participant 70 (lower right corner of @fig-htw-indv-pred) had a roughly parabolic response pattern in their observed data, a pattern which neither model can properly reproduce, but which causes EXAM to perform particularly poorly.
+
+*Modeling Limitations.* The present work compared models based on their ability to predict the observed data, without employing conventional model fit indices such as the Akaike Information Criterion (AIC) or the Bayesian Information Criterion (BIC).
+These indices, which penalize models based on their number of free parameters, would have been of limited utility in this case, as both ALM and EXAM have two free parameters.
+However, despite having the same number of free parameters, EXAM could still be considered the more complex model, as it incorporates all the components of ALM plus an additional mechanism for rule-based responding.
+A more comprehensive model comparison approach might involve performing cross-validation with a held-out subset of the data [@mezzadriHoldoutStrategySelecting2022] or penalizing models based on the range of patterns they can produce [@domeGdistanceComparisonModel2023].
+
+{{< pagebreak >}}
 
@@
 
-*Experimental Result Summary*
-
 Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
@@
 This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
-
-*Modeling Summary*
-EXAM is the best model for both groups, but EXAM does relatively good at accounting for the constant group.
-May have seemed counterintuitive, if one assumed that multiple, varied, examples were necessary to extract a rule.
-But, EXAM is not a conventional rule model - it doesn't require explictly abstract of a rule, but rather the rule-based response occurs during retrieval.
-The constant groups formation of a single, accurate, input-output association, in combination with the usefulness of the zero point, may have been sufficient for EXAM, and the constant group,  to perform well.
-One concern may have been that the assumption of participants making use of the zero point turned the extrapolation problem into an interpolation problem - however this concern is ameliorated by the consistency of the results across both the original and reverse order conditions.
 
@@
 
-### Empirical and Modeling Summary
+## Empirical and Modeling Summary
 
@@
 
-### Differences between the two Projects
+## Differences between the two Projects
 

### 2024-04-15 paper.qmd
big re-render of all versions

@@
 
+    <a class="btn btn-success btn-sm mb-1" href="/Sections/full.html" target="_blank">
+  <iconify-icon inline="" icon="fa6-solid:arrow-up-right-from-square"></iconify-icon> &ensp;HTML <small>(code included)</small>
+  </a>
+
   <a class="btn btn-warning btn-sm mb-1" href="/Manuscript/output/TG_Full_Dissertation.pdf" target="manuscript">
@@
 
-    <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
+    <!-- <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
   <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;DOCX <small>(download)</small>
-  </a>
+  </a> -->
 

### 2024-04-15 Manuscript/manuscript.qmd
fix overflowing table 15

@@
 | bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
-| conditVaried:bandTypeExtrapolation:bandOrderReverse |    30.42 |        -21.00 |         81.65 | 0.87 |
+| conditVaried:bandTypeExtrapolation:bandOrder |    30.42 |        -21.00 |         81.65 | 0.87 |
 

### 2024-04-15 Sections/full.qmd
fix overflowing table 15

@@
 
-\normalsize
+\scriptsize
 

### 2024-04-15 Manuscript/manuscript.qmd
few tweaks

@@
 Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
-@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
+@cohenCategoryVariabilityExemplar2001 conducted two experiments with this basic paradigm.
 In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
@@
 Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
-Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
+Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into the category with greater variation.
 
@@
 The authors interpreted this pattern as evidence that participants had acquired prototype representation of the category, as opposed to storing each individual training instance, and that generalization was based on the similarity of the testing items to the learned prototype representations.
-@posnerGenesisAbstractIdeas1968 has been extremely influential,  and continues to be cited in contemporary research as clear evidence that prototype abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
+@posnerGenesisAbstractIdeas1968 has been extremely influential,  and continues to be cited as evidence that prototype abstraction underlies the benefits of varied training.
+It's also referenced as a key influence in the development of the "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
 However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].

### 2024-04-15 Manuscript/manuscript.qmd
fix page numbers
fix crossref issue

@@
 
-{{< include pre_sections/pre_pdf.qmd >}}
+{{< include pre_sections/pre_pdf2.qmd >}}
 
@@
 #| fig.width: 11
-#| fig.height: 11.5
+#| fig.height: 11.0
 
@@
 Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The significant negative estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition.
-This difference is depicted visually in @fig-e1-test-vx.
+The significant negative estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition (see @fig-e1-test-vx and @fig-e1-bmm-vx).
 
@@
 testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: tbl-e1-bmm-vx
+```
+
+```{r}
+#| label: fig-e1-bmm-vx
 #| fig-cap: Experiment 1 Discrimination.
@@
 Error bars represent 95% HDI.
-#| fig-height: 7
+#| fig-height: 8
 #| fig-width: 11
@@
 The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
-The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx).
+The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx and @fig-e2-bmm-vx).
 
@@
 ```{r}
-#| label: tbl-e2-bmm-vx
+#| label: fig-e2-bmm-vx
 #| fig-cap: Experiment 2 Discrimination.
@@
 
+{{< pagebreak >}}
+
 ```{r}
@@
 Error bars represent 95% HDI.
-#| fig-height: 10
+#| fig-height: 11
 #| fig-width: 11

### 2024-04-15 Sections/full.qmd
make html version a bit nicer. Fix latex issue in alt pdf.

@@
 cache: true
+format-links: [hikmah-manuscript-pdf, gfm]
 execute: 
@@
 
-\scriptsize
+\normalsize
 

### 2024-04-19 Manuscript/manuscript.qmd
fix pdf title; re-render secondary pages; hide into and dis
few tweaks and typos

@@
 
-{{< include pre_sections/pre_pdf2.qmd >}}
+{{< include pre_sections/pre_pdf.qmd >}}
 
@@
 The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
-However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to make it easy to measure how much performance degrades as a function of how far away testing items are from the training items.
+However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to easily measure how much performance degrades as a function of how far away testing items are from the training items.
 
@@
 Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
+For example, studies using a projectile throwing task might assign participants to either constant training that practice throwing from a single location, or to a varied group that throws from multiple locations.
 Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
@@
 Schema theory (described in more detail above), posts that varied practice leads to the formation of more flexible motor schemas, which then facilitate generalization [@schmidtSchemaTheoryDiscrete1975].
-The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice may impair initial performance but then enhance longer-term retention and transfer.
+The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice conditions may impair initial performance but then enhance longer-term retention and transfer.
 Similarily, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
@@
 The overarching purpose of this dissertation is to investigate the effects of training variability on learning and generalization within visuomotor skill learning and function learning.
-Our investigations is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
+Our investigation is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
 
@@
 Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
-However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
+However, much of this research has neglected to account for differences in similarity between varied and constant training conditions.
 In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.

### 2024-04-19 Sections/full.qmd
few tweaks and typos

@@
 Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
+For example, studies using a projectile throwing task might assign participants to either constant training that practice throwing from a single location, or to  a varied group that throws from multiple locations.
 Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].

### 2024-04-19 Manuscript/manuscript.qmd
fix typo; adjust headings

@@
 ### Modelling Results
-
-#### Group level Patterns
 
@@
 The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
-Of course, the nature of the constant training condition makes interpolation teseting impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
+Of course, the nature of the constant training condition makes interpolation testing impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
 Finally, the task employed in the present study consisted of only a linear, positive function.

### 2024-04-21 Manuscript/manuscript.qmd
small typo fixes

@@
 
-Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
+Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
 See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
@@
 Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
-Researchers will usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
+Researchers usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
 The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
@@
 
-The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
+The influence of training variability has received a large amount of attention in the domain of sensorimotor skill learning.
 Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
-an underhand throw).
+Schema theory presumes that learners possess general motor programs for a class of movements (e.g., an underhand throw).
 When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
@@
 
-One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
+One of the earliest and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
 Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
@@
 In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-This result offers a particularly compelling example of the merits of varied practice, given that the varied group was able to outperform the constant group even from the  home turf location where one may have expected the constatn group to have the strongest advantage.
+This result provides particularly strong evidence for the benefits of varied practice, as the varied group outperformed the constant group even when tested at the "home-turf" distance that the constant group had exclusively practiced.
 A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a].
@@
 Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
-LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
+Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g., LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
 At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had three prior exposures to the word arrangement (i.e.
@@
 
-A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g.
-the region between the two categories).
+A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g., the region between the two categories).
 The general approach is to train participants with examples from a high variability category and a low variability category.
@@
 In an example of a more complex influence of training variation, [@braithwaiteEffectsVariationPrior2015] trained participants on example problems involving the concept of sampling with replacement (SWR).
-Training consisted of examples that were either highly similar in their semantic context (e.g.
-all involving people selecting objects) or in which the surface features were varied between examples (e.g.
-people choosing objects AND objects selected in a sequence).
+Training consisted of examples that were either highly similar in their semantic context (e.g., all involving people selecting objects) or in which the surface features were varied between examples (e.g., people choosing objects AND objects selected in a sequence).
 The experimenters also surveyed how much prior knowledge each participant had with SWR.
@@
 The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice conditions may impair initial performance but then enhance longer-term retention and transfer.
-Similarily, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
+Similarly, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
 
@@
 In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimuli.
-Recall that participants are trained on only on distortions of the category prototypes (e.g.
-low, medium or high distortions), never encountering the exact prototypes during the training stage.
+Recall that participants are trained on only on distortions of the category prototypes (e.g.,  low, medium or high distortions), never encountering the exact prototypes during the training stage.
 Then, in the testing phase, participants are tested with the prototype patterns, their old training items, and novel low, medium and high distortions.
@@
 Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g.
-projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
-more unique combinations of x and y velocities).
+For training tasks in which participants have numerous degrees of freedom (e.g., projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g., more unique combinations of x and y velocities).
 Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
@@
 A total of 110 Indiana University psychology students participated in Experiment 1.
-We subsequently excluded 34 participants for poor performance on one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
-simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
+We subsequently excluded 34 participants for poor performance on one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g., simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
 A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.
@@
 #| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g.
-excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
+Includes data only from positions that were not encountered during the training stage (e.g., excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
 Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
@@
 #| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g.
-constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
+#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g., constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
 Error bars indicate standard error of the mean.
@@
 One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g.
-size/color/shape).
+In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g., size/color/shape).
 Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g.
-movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
+An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g., movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
 Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
@@
 Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
-In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g.
-the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
+In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g., the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
 However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
@@
 The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
-band 800-1000).
+The target velocities were given as a range, or band, of acceptable velocity values  (e.g., band 800-1000).
 During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
@@
 The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the  slope for the baseline condition.
-The interaction terms which include condit and Band (e.g.
-conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate the how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
+The interaction terms which include condit and Band (e.g., conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate the how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
 :::
@@
 So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
+Depending on the value of the generalization parameter, the nearby units (e.g., 54 and 56; 53 and 57) may also activate to some degree.
 ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
@@
 ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
-Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g.
-many neural network models).
+Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g., many neural network models).
 
@@
 #| label: fig-ee-e1
-#| fig-cap: A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+#| fig-cap: "A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
 Varied).
@@
 EXAM for the varied group; 3) ALM fits between constant and varied.
-Negative error differences indicate that the term on the left side (e.g.
-EXAM Constant) tended to have smaller model residuals.
+Negative error differences indicate that the term on the left side (e.g., EXAM Constant) tended to have smaller model residuals."
 #| fig-height: 8
@@
 If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
-Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g.
-the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
+Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g., the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
 

### 2024-04-21 Sections/Introduction.qmd
small typo fixes

@@
 
-# Introduction
+## Varied Training and Generalization
 
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer or generalization to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such generalization challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence generalization, and to develop cognitive models that can predict when generalization is likely to occur.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
-
-## The study of variability
-
-Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021],  trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
+Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
 See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
@@
 Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
-Researchers will usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
+Researchers usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
 The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
-However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to make it easy to measure how much performance degrades as a function of how far away testing items are from the training items.
+However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to easily measure how much performance degrades as a function of how far away testing items are from the training items.
 
-The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
+The influence of training variability has received a large amount of attention in the domain of sensorimotor skill learning.
 Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
-an underhand throw).
+Schema theory presumes that learners possess general motor programs for a class of movements (e.g., an underhand throw).
 When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
@@
 Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
+For example, studies using a projectile throwing task might assign participants to either constant training that practice throwing from a single location, or to  a varied group that throws from multiple locations.
 Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
 
-One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
+One of the earliest and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
 Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
@@
 Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
-LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
-At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e.
+Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g., LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
+At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had three prior exposures to the word arrangement (i.e.
 the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group.
+However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving two more anagrams on average than the constant group.
 This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
@@
 
-A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g.
-the region between the two categories).
+A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g., the region between the two categories).
 The general approach is to train participants with examples from a high variability category and a low variability category.
 Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
-@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
+@cohenCategoryVariabilityExemplar2001 conducted two experiments with this basic paradigm.
 In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
@@
 Schema theory (described in more detail above), posts that varied practice leads to the formation of more flexible motor schemas, which then facilitate generalization [@schmidtSchemaTheoryDiscrete1975].
-The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice may impair initial performance but then enhance longer-term retention and transfer.
-Similarily, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
+The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice conditions may impair initial performance but then enhance longer-term retention and transfer.
+Similarly, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
 
@@
 
-### The current work
+## The current work
 
 The overarching purpose of this dissertation is to investigate the effects of training variability on learning and generalization within visuomotor skill learning and function learning.
-Our investigations is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
+Our investigation is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
 

### 2024-04-21 Sections/full.qmd
small typo fixes

@@
 title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
-#subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
-#date: 04/04/24
 author:
@@
 toc-location: body
-toc-title: Contents
+#toc-title: Contents
 toc-depth: 4
@@
 In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimuli.
-Recall that participants are trained on only on distortions of the category prototypes (e.g.
-low, medium or high distortions), never encountering the exact prototypes during the training stage.
+Recall that participants are trained on only on distortions of the category prototypes (e.g., low, medium or high distortions), never encountering the exact prototypes during the training stage.
 Then, in the testing phase, participants are tested with the prototype patterns, their old training items, and novel low, medium and high distortions.
@@
 #| label: fig-ee-e1
-#| fig-cap: A) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+#| fig-cap: "A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
 Varied).
 Lower values on the y axis indicate better model fit.
-B) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs.
+D) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs.
 EXAM for the varied group; 3) ALM fits between constant and varied.
-Negative error differences indicate that the term on the left side (e.g.
-EXAM Constant) tended to have smaller model residuals.
+Negative error differences indicate that the term on the left side (e.g., EXAM Constant) tended to have smaller model residuals."
 #| fig-height: 8

### 2024-04-22 Manuscript/manuscript.qmd
fix few more typos, re-add EXAM description parts that had gotten removed somehow.

@@
 The author compared a variety of similarity-based models based around the Generalized Context Model [@nosofskyAttentionSimilarityIdentificationcategorization1986] to account for their results, manipulating whether a response-bias or similarity-scaling parameter was fit separately between variability conditions.
-No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
+No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improve significantly when the similarity scaling parameter was fit separately.
 The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied particpants, and also for their poorer performance in a recognition condition.
+This model accounted for both the extended generalization gradients of the varied participants, and also for their poorer performance in a recognition condition.
 
@@
 
-## Existing Theoretircal Frameworks
+## Existing Theoretical Frameworks
 
@@
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
+Participants were constrained to release the ball within the square.
 
@@
 The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
+Similar to ALM, the Bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
+However unlike ALM, the Bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
 
@@
 : **Statistical Model Specifications**.
-The specifications for the bayesian regression models used in the analyses of each of the 3 experiments.
+The specifications for the Bayesian regression models used in the analyses of each of the 3 experiments.
 Comparisons of accuracy use abosulte deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
@@
 ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
+The units in the input layer activate as a function of their Gaussian similarity to the input stimulus ( a_i(X) = exp(-c(X - X_i)^2) ).
 So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
 Depending on the value of the generalization parameter, the nearby units (e.g., 54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
 The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
 The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
@@
 The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
+
 The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
 EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
+When a novel test stimulus, $X$, is presented, EXAM first identifies the two nearest training stimuli, $X_1$ and $X_2$, that bracket $X$.
+This is done based on the Gaussian activation of input nodes, similar to ALM, but focuses on identifying the closest known points for extrapolation.
+
+**Slope Calculation**: EXAM calculates a local slope, $S$, using the responses associated with $X_1$ and $X_2$. This is computed as:
+
+   $$
+   S = \frac{m(X_{1}) - m(X_{2})}{X_{1} - X_{2}}
+   $$
+
+where $m(X_1)$ and $m(X_2)$ are the output values from ALM corresponding to the $X_1$ and $X_2$ inputs.
+
+ **Response Generation**: The response for the novel stimulus $X$ is then extrapolated using the slope $S$:
+
+   $$
+   E[Y|X] = m(X_1) + S \cdot |X - X_1|
+   $$
+
+Here, $m(X_1)$ is the ALM response value from the training data for the stimulus closest to $X$, and $(X - X_1)$ represents the distance between the novel stimulus and the nearest training stimulus.
+
 Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
@@
 We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
-This assumption is motivated by previous function learning research (@brownUnderestimationLinearFunction2017), which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
+This assumption is motivated by previous function learning research [@brownUnderestimationLinearFunction2017], which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
 
@@
 | Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | ALM response $m(X_i)$ adjusted by slope.                                                      |
+| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$,  adjusted by local slope $S$.
+|
 
@@
 
-To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+To estimate the  parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
 ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
@@
 #| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
+#| tbl-cap: "Models errors predicting empirical data from Experiment 1 -  aggregated over the full posterior distribution for each participant.
 Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
@@
 Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y axes of the plots for the c parameter are scaled logarithmically."
+Note that the y-axes of the plots for the c parameter are scaled logarithmically."
 #| fig-height: 6
@@
 Lower values indicate better model fit.
-Note that y axes are scaled differently between facets.
+Note that y-axes are scaled differently between facets.
 A) Residuals predicting each block of the training data.
@@
 
-To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
+To quantitatively assess whether the differences in performance between models,  we fit a Bayesian regression predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
 EXAM) and training condition (Constant vs.
@@
 The present work presents the first application of these models to to the study of training variability in a visuomotor function learning task.
-We fit both models to individual participant data, using a form of simulation-based bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
+We fit both models to individual participant data, using a form of simulation-based Bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
 EXAM provided the best overall account of the testing data, and the advantage of EXAM over ALM was significantly greater for the constant group.
@@
 |
-| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.
+| Training Experience                    | Varied group gets half as much experience on any one position as the constant group.
 | Varied group gets 1/3 as much experience on any one velocity band as the constant group.

### 2024-04-22 Manuscript/manuscript.qmd
add docx version; fix igas figure text; re-render everything.

@@
 #| label: fig-IGAS_Training1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
+#| fig-cap: Training performance for varied and constant participants binned into three stages.
 Shorter bars indicate better performance (ball landing closer to the center of the target).
@@
 #| label: fig-IGAS_Testing1
-#| fig.cap: Testing performance for each of the 4 testing positions, compared between training conditions.
+#| fig-cap: Testing performance for each of the 4 testing positions, compared between training conditions.
 Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
@@
 e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)+scale_x_discrete(name="Testing Location",labels=e1Labels)
+  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+
+  guides(fill=guide_legend(title="Training Condition"))+
+  theme(legend.title.align=.25, 
+  axis.text.x = element_text(size = 8.5,angle=0),
+  legend.position="top")+
+  scale_x_discrete(name="Testing Location",labels=e1Labels)
 
@@
 #| label: tbl-IGAS_Table1
-#| tab.cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
+#| tbl-cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
 
@@
 
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
+kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  #%>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
 
@@
 #| label: fig-e2train
-#| fig.cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
+#| fig-cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
 On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
@@
 
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) # %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) #  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
 ```
@@
 #| label: fig-e2test1
-#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g., constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
+#| fig-cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g., constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
 Error bars indicate standard error of the mean.
@@
 
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) # %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+primary=out_type == "html" || out_type == "pdf" || out_type =="latex" || out_type == "docx"
+
 e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
 
+if (primary) {
 e1_tab %>%
@@
   tab_options(
-    column_labels.font.size = 10,
+    table.font.size = 12,
     heading.title.font.size = 14,
     heading.subtitle.font.size = 12,
-    table.font.size = 10, 
-    quarto.disable_processing = TRUE
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
   )
+} else {
+
+  e1_tab %>%
+  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
+  summarize(ME = mean(mean_error), .groups = "drop") %>%
+  pivot_wider(
+    names_from = c(Model, condit),
+    values_from = ME,
+    names_sep = "_"  # Add this line to specify the separator for column names
+  ) %>%
+  rename("Fit Method" = Fit_Method) %>% kable(escape=F,booktabs=T)
+
+  }
 ```
@@
 e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3"))
+
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+primary=out_type == "html" || out_type == "pdf" || out_type =="latex" || out_type == "docx"
+
+if (primary) {
 gt_table <- e23_tab %>%
@@
   tab_options(
-    column_labels.font.size = 10,
+    table.font.size = 12,
     heading.title.font.size = 14,
     heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
   )
 gt_table
+} else {
+  e23_tab %>%
+  pivot_wider(
+    names_from = c(Exp, Model, condit),
+    values_from = mean_error,
+    names_glue = "{Exp}_{Model}_{condit}"
+  ) %>%
+  arrange(Fit_Method, `Task Stage`) %>%
+  kable(escape=F,booktabs=T)
+}
 ```
@@
 
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+primary=out_type == "html" || out_type == "pdf" || out_type =="latex" || out_type == "docx"
+
+if (primary) {
 bct_table <- bct %>%
@@
   tab_options(
-    table.font.size = 10,
+    table.font.size = 12,
     heading.title.font.size = 14,
@@
 bct_table
+} else {
+  bct %>%
+  mutate(
+    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
+    pd = round(pd, 2)
+  ) %>% kable(booktabs = TRUE)
+
+}
 

### 2024-04-22 Manuscript/pre_sections/pre_docx.qmd
fix docx and html. Update htw with embed
add docx version; fix igas figure text; re-render everything.

@@
-# The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach
+# The Role of Variability in Learning Generalization: A Computational Modeling Approach
 
 ## Thomas E. Gorman
-
-Submitted to the faculty of the University Graduate School in partial fulfillment of the
-requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
-Sciences and the Cognitive Science Program, Indiana University.
-
----
-
-Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
-requirements for the degree of Doctor of Philosophy.
-
-- Robert L. Goldstone
-- Robert Nosofsky
-- Peter Todd
-- Mike Jones
-
----
-
-## @2023
-
-### Thomas E. Gorman
-
----
-
-## Acknowledgements
-
----

### 2024-04-22 Manuscript/pre_sections/pre_docx_full.qmd
add docx version; fix igas figure text; re-render everything.

# The Role of Variability in Learning Generalization: A Computational Modeling Approach

## Thomas E. Gorman

Submitted to the faculty of the University Graduate School in partial fulfillment of the
requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
Sciences and the Cognitive Science Program, Indiana University.

---

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.

- Robert L. Goldstone, PhD
- Robert Nosofsky, PhD
- Peter Todd, PhD
- Mike Jones, PhD

---

## @2023

### Thomas E. Gorman

---

## Acknowledgements

---

### 2024-04-22 Sections/docx_test.qmd
add docx version; fix igas figure text; re-render everything.

@@
   eval: false
+  include: false
 format:
-  #html: default
-  hugo-md:
-    echo: false
-    #include: false
-    html-math-method: mathjax
-    output-file: diss_full_hugo22.md
-  gfm:
-    echo: false
-    output: false
-    output-file: diss_full_gfm22.md
-  hikmah-manuscript-pdf:
-    echo: false
-    output-file: "tg_full_disser22.pdf"
-    mainfont: "Linux Libertine O"
-    mainfontoptions:
-      - "Numbers=Proportional"
-      - "Numbers=OldStyle"
-    mathfont: "Libertinus Math"
-  hikmah-manuscript-docx: 
-    output-file: "manuscript-ms2.docx"
+ # html: default
+  # hugo-md:
+  #   echo: false
+  #   #include: false
+  #   html-math-method: mathjax
+  #   output-file: diss_full_hugo22.md
+  # gfm:
+  #   echo: false
+  #   output: false
+  #   output-file: diss_full_gfm22.md
+  # hikmah-manuscript-pdf:
+  #   echo: false
+  #   output-file: "tg_full_disser22.pdf"
+  #   mainfont: "Linux Libertine O"
+  #   mainfontoptions:
+  #     - "Numbers=Proportional"
+  #     - "Numbers=OldStyle"
+  #   mathfont: "Libertinus Math"
+  # hikmah-manuscript-docx: 
+  #   output-file: "manuscript-ms2.docx"
+  #   echo: false
+  #   #prefer-html: true
+  #   toc: false
+  docx:
     echo: false
     prefer-html: true
-    toc: false
+    output-file: "TG_Full_Dissertation3.docx"
+    toc: true
 prefer-html: true
@@
 Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
-
-This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
-A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
-Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
-To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
-These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
-
-## The study of variability
-
-Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
-See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
-
-Research on the effects of varied training typically manipulates variability in one of two ways.
-In the first approach, a high variability group is exposed to a greater number of unique instances during training, while a low variability group receives fewer unique instances with more repetitions.
-Alternatively, both groups may receive the same number of unique instances, but the high variability group's instances are more widely distributed or spread out in the relevant psychological space, while the low variability group's instances are clustered more tightly together.
-Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
-Researchers will usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
-The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
-However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to make it easy to measure how much performance degrades as a function of how far away testing items are from the training items.
-
-The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
-an underhand throw).
-When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
-Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
-Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
-
-One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
-Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
-The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
-Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
-12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
-Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
-In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-This result offers a particularly compelling example of the merits of varied practice, given that the varied group was able to outperform the constant group even from the  home turf location where one may have expected the constatn group to have the strongest advantage.
-A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a].
-One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
-Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperfroms the constant group even from the constants group's home turf has not been consistently replicated.
-One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
-However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-
-Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
-It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
-Of particular relevance to the current work is the early study of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
-constant training on multiple testing locations of graded distance from the training condition.
-Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
-The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
-Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
-As is often the case, the varied group performed worse during the training phase.
-In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
-
-Benefits of varied training have also been observed in many studies outside of the sensorimotor domain.
-@goodeSuperiorityVariableRepeated2008 trained participants to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
-Although subjects in all conditions were exposed to the same 40 unique words (i.e.
-the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training).
-Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
-LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
-At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e.
-the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group.
-This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
-This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.
-
-In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
-typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
-
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968].
-A seminal study by @posnerGenesisAbstractIdeas1968 trained participants to categorize artificial dot patterns, manipulating whether learners were trained with low variability examples clustered close to the category prototypes (i.e. low distortion training patterns), or higher-variability patterns spread further away from the prototype (i.e.
-high-distortion patterns).
-Participants that received training on more highly-distorted items showed superior generalization to novel high distortion patterns in the subsequent testing phase.
-It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training rathers, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
-This train-until-criterion procedure led to the high-variability condition participants tending to complete a larger number of training trials before switching to the testing stage.
-More recent work [@huHighvariabilityTrainingDoes2024], also used dot pattern categories, but matched the number of training trials across conditions.
-Under this procedure, higher-variability participants tended to reach lower levels of performance by the end of the training stage.
-The results in the testing phase were the opposite of @posnerGenesisAbstractIdeas1968,  with the low-variability training group showing superior generalization to novel high-distortion patterns (as well as generalization to novel patterns of low or medium distortion levels).
-However, whether this discrepancy is solely a result of the different training procedures is unclear, as the studies also differed in the nature of the prototype patterns used.
-@posnerGenesisAbstractIdeas1968  utilized simpler, recognizable prototypes (e.g., a triangle, the letter M, the letter F), while  @huHighvariabilityTrainingDoes2024 employed random prototype patterns.
-
-Recent studies have also begun utilizing more complex or realistic sitmuli when assessing the influence of variability on category learning.
-@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
-In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
-Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
-higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyModelguidedSearchOptimal2019].
-For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
-The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
-
-A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g.
-the region between the two categories).
-The general approach is to train participants with examples from a high variability category and a low variability category.
-Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
-@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
-In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
-In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart.
-Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
-Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
-
-Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002;  @yangCategoryVariabilityEffect2014; and @seitzModelingCategoryVariability2023].
-The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
-They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
-In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial.
-They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
-
-The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present work.
-Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
-During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories.
-The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category.
-Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category.
-Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
-The author compared a variety of similarity-based models based around the Generalized Context Model [@nosofskyAttentionSimilarityIdentificationcategorization1986] to account for their results, manipulating whether a response-bias or similarity-scaling parameter was fit separately between variability conditions.
-No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
-The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied particpants, and also for their poorer performance in a recognition condition.
-
-Variability has also been examined in the learning of higher-order linguistic categories [@perryLearnLocallyThink2010].
-In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
-All infants were introduced to three novel objects of the same category, with participants in the "tight" condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
-Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
-Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels of the training objects.
-In the testing phase, the varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category.
-More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
-The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
 
@@
 
-## Similarity and instance-based approaches to transfer of learning
+```{r}
 
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar.
-In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimuli.
-Recall that participants are trained on only on distortions of the category prototypes (e.g.
-low, medium or high distortions), never encountering the exact prototypes during the training stage.
-Then, in the testing phase, participants are tested with the prototype patterns, their old training items, and novel low, medium and high distortions.
-The authors found that participants had the highest testing accuracy for the previously unseen prototype patterns, followed by the old training items, and then the novel low, medium and high distortions.
-The authors interpreted this pattern as evidence that participants had acquired prototype representation of the category, as opposed to storing each individual training instance, and that generalization was based on the similarity of the testing items to the learned prototype representations.
-@posnerGenesisAbstractIdeas1968 has been extremely influential,  and continues to be cited in contemporary research as clear evidence that prototype abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
-However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
-@palmeriCentralTendenciesExtreme2001 demonstrated the both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
-These authors conducted a near replication of the @posnerGenesisAbstractIdeas1968 study, but also had participants provide similarity judgements of the dot pattern stimuli after completing the training phase.
-A multidimensional scaling analysis of the similarity judgements revelead that the psychological representations of the prototype stimuli were not located in the middle of the training stimuli, but were instead extreme points in the psychological space.
-The authors also demonstrated the generalization patterns of @posnerGenesisAbstractIdeas1968 could be accounted for by an exemplar-based model, without any need to assume the abstraction of a prototype.
+e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
 
-Instance-based, or exemplar-based models generally assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978; @nosofskyAttentionSimilarityIdentificationcategorization1986; @jamiesonInstanceTheoryDomaingeneral2022].
-As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
+exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
+  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
 
-Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
-In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
-Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
-That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based similarity approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
-@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
-Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
+exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
+  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
+  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
 
-## Issues with Previous Research
+exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
+  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
 
-Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g.
-projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
-more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
+exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
+  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
+  group_by(sbjCode,Group2,conditType,stage) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
+
+transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
+transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
+
+transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
+  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
+
+variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
+constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
+
+transfer <- rbind(variedTest,constantTest)
+transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
+
+transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
+
+# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
+# novelAll <- novelAll %>% group_by(positionX) %>%
+#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
+
+novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
+novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
+
+constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
+variedTest <- transfer %>% filter(condit==7) # only varied testing
+variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
+
+variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
+constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
+variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
+
+exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
+  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
+
+exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
+  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
+
+exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
+  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
+
+exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
+  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
+
+exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
+  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
+
+```
 
 ```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
+#| label: fig-e2test1
+#| fig.cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g., constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
+Error bars indicate standard error of the mean.
+
+sum.variedVsNovelIden <- variedVsNovelIden  %>%
+  group_by(sbjCode,conditType,positionX) %>% 
+  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
+
+e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
+
+e2Test2
+
+```
+
+\
+\
+
+```{r}
+#| label: tbl-e2tab5
+#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
+Locations 500 and 800 are not included as these were trained by the varied participants.
+Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
+
+tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
+  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
+
+tab4=tab4 %>% group_by(Condition) %>% 
+   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
+
+tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
+ tab4=tab4[,1:3]
+
+kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) # %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+
+```
+
+### Experiment 2 Discussion
+
+The results of Experiment 2 largely conform to the findings of Experiment 1.
+Participants in both varied and constant conditions improved at the task during the training phase.
+We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing [@soderstromLearningPerformanceIntegrative2015].
+However our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
+
+In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions.
+The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
+We also join a much smaller set of research to observe this pattern in a computerized task [@seowTransferEffectsVaried2019].
+One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
+Although this pattern has been observed elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
+
+## Computational Model
+
+*Controlling for the similarity between training and testing.* The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations.
+To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release.
+For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions.
+We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target.
+We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions -- thus resulting in six separate similarity scores for each participant.
+@fig-taskSpace visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions.
+As illustrated in @fig-taskSpace, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.
+
+```{r}
+#| label: fig-taskSpace
+#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+This empirical solution space was compiled from all of the participants in Experiment 2.
+B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+#| fig-width: 11
+#| fig-height: 9
+#| 
+taskspace <- e2 %>% filter(AbsDistFromCenter<900)
+taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
+
+solSpace <- e2 %>% filter(trialType==11)
+#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
+
+solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
+solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
+solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
+
+missSpace <- e2 %>% filter(trialType !=11)
+missSpace$Result = "Missed Target"
+solSpace$Result <- solSpace$Result
+
+# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
+# multiplied velocoties by -1 to make the axes less confusing
+ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
+  geom_point(aes(colour=Result),alpha=0.6) + 
+  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
+  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
+
+fullSpace <- rbind(missSpace,solSpace)
+
+fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
+  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
+  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
+
+library(patchwork)
+ss/fs
+
+```
+
+For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.
+The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient.
+Then, as per an instance-based model of similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value.
+The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.
+If c has a large value, then even a small difference between two throws' velocities greatly decreases the extent of generalization from one to the other.
+A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities.
+The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions.
+The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.
+
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
+
+**Equation 2:**
+$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+
+A simple linear regression revealed that these similarity scores were significantly predictive of performance in the transfer stage, t =-15.88, p\<.01, $r^2$=.17, such that greater similarity between training throws and solution spaces for each of the test locations resulted in better performance.
+We then repeated the group comparisons above while including similarity as a covariate in the model.
+Comparing the varied and constant groups in testing performance from all testing positions yielded a significant effect of similarity, F(1, 205)=85.66, p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition (varied vs.
+constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03.
+The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$ =.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$ =.07.
+For all comparisons, the pattern of results was consistent with the initial findings from Experiment 2, with the varied group still performing significantly better than the constant group.
+
+### Fitting model parameters separately by group
+
+To directly control for similarity in Experiment 2, we developed a model-based measure of the similarity between training throws and testing conditions.
+This similarity measure was a significant predictor of testing performance, e.g., participants whose training throws were more similar to throws that resulted in target hits from the testing positions, tended to perform better during the testing phase.
+Importantly, the similarity measure did not explain away the group-level benefits of varied training, which remained significant in our linear model predicting testing performance after similarity was added to the model.
+However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
+Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
+Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
+Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
+To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
+One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
+If one's training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
+Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+
+To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c, to varied and constant participants.
+To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
+
+Both models generate distinct similarity values between training and testing locations.
+Much like the analyses in Experiment 2, these similarity values are regressed against testing performance in models of the form shown below.
+As was the case previously, testing performance is defined as the mean absolute distance from the center of the target (with a separate score for each participant, from each position).
+
+Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p\<.01).
+Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the c parameter separately between groups (Similarity2c).
+In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p\<.01), with the varied group still performing significantly better.
+However, in linear model 4 the addition of the Similarity2c predictor results in the effect of training group becoming nonsignificant (p=.40), suggesting that the effect of varied vs.
+constant training is accounted for by the Similarity2c predictor.
+Next, to further establish a difference between the models, we performed nested model comparisons using ANOVA, to see if the addition of the training group parameter led to a significant improvement in model performance.
+In the first comparison, ANOVA(Linear Model 1, Linear Model 2), the addition of the training group predictor significantly improved the performance of the model (F=22.07, p\<.01).
+However, in the second model comparison, ANOVA (Linear model 3, Linear Model 4) found no improvement in model performance with the addition of the training group predictor (F=1.61, p=.20).
+
+Finally, we sought to confirm that similarity values generated from the adjusted Similarity2c model had more predictive power than those generated from the original Similarity1c model.
+Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
+The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
+When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
+Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
+
+In summary, our modeling suggests that an instance-based model which assumes equivalent generalization gradients between constant and varied trained participants is unable to account for the extent of benefits of varied over constant training observed at testing.
+The evidence for this in the comparative model fits is that when a varied/constant dummy-coded variable for condition is explicitly added to the model, the variable adds a significant contribution to the prediction of test performance, with the variable condition yielding better performance than the constant conditions.
+However, if the instance-based generalization model is modified to assume that the training groups can differ in the steepness of their generalization gradient, by incorporating a separate generalization parameter for each group, then the instance-based model can account for our experimental results without explicitly taking training group into account.
+Henceforth this model will be referred to as the Instance-based Generalization with Adaptive Similarity (IGAS) model.
+
+## Project 1 General Discussion
+
+Across two experiments, we found evidence in support of the benefits of
+variability hypothesis in a simple, computerized projectile throwing task.
+Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
+However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions.
+We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978].
+In Experiment 1 varied participants performed significantly better on this identity comparison.
+In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
+Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
+Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
+Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
+A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
+The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
+In this fashion, contextually appropriate c values could be empirically learned.
+This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
+
+Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained.
+Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in @fig-Toy-Model-dis we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern.
+In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model -- namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.
+
+```{r}
+#| label: fig-Toy-Model-dis
+#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
+For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
+For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
+The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
+Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
+#| fig.width: 11
+#| fig.height: 11.5
+
+#
 
 p=2
-c<- .0002
+c<- .000002
+
+trainingTestingDifference=2000;
+cvaried=.00002
+cconstant=.0005
 simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
                      train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
+                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
                             genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
+                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
+                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
+                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
+                            ) %>% 
   group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
+  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
+
+#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
+
 colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
+plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
                   geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
@@
                   xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
+                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
+                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
+                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
+                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
+                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
                         legend.position="none"))
 
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
+ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
+ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
+ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
+  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
+ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
+  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
+# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
 
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
+#gtitle="Figure 9."
+#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
+#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
+p1 <- (ip1+ip2) / (ip3+ip4)
+
+p1
 
@@
 
-In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
+# Project 2
 
-The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
-We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
-We then examine the extent to which this advantage can be explained by an instance-based similarity model.
+## Introduction
 
-# Experiment 1
+A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
+One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
+The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
+The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022].
+The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
 
-## Methods
+### Function Learning and Extrapolation
 
-### Sample Size Estimation
+The study of human function learning investigates how people learn relationships between continuous input and output values.
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
 
-To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies, yielding a Cohens f =.43.
-The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009], 2009) was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
-All experiments reported in the present manuscript exceed this minimum number of participants per condition.
+@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
+Input stimuli and output responses were both lines of varying length.
+The correct output response was related to the length of the input line by a linear, quadratic, or random function.
+Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
+Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
+Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
+Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
+@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
+In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
+Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
 
-### Participants
+The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
+In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
+Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
+All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
+Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
 
-Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18-22 years.
-A total of 110 Indiana University psychology students participated in Experiment 1.
-We subsequently excluded 34 participants poor performance at one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
-simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
-A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.
+The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
+The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
+The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
 
-### Task
+The authors also introduced two new function-learning models.
+The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
+ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
+ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
+The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
+When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
+ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
+EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
+Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
 
-The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library (de Leeuw, 2015).
-The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
-Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
-Likewise, the distance between the center of the target, and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
-For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
-@fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square.
-Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
-If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target.
-If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
-If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier.
-If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square.
-If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
+### Variability and Function Learning
 
-[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+The influence of variability on function learning tasks has received relatively little attention.
+The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
+They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
 
-```{r}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
+### Overview Of Present Study
 
-mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
+The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
+To the best of our knowledge, this research is the first to employ the classic constant vs.
+varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
+Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
+
+To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
+Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to examine the ability of these influential models of function learning to account for both the group level and individual level data.
+
+## Experiment 1
+
+### Methods
+
+*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
+Participants were randomly assigned to one of two training conditions: varied training or constant training.
+
+*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
+The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
+The target velocities were given as a range, or band, of acceptable velocity values  (e.g., band 800-1000).
+During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
+Participants were instructed that only the x velocity component of the ball was relevant to the task.
+The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
+
+```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
+#| label: fig-htw-task
+#| fig-cap: The Hit the wall task.
+Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
+The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
+#| eval: true
+#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
+knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
 
@@
 
-## Results
+*Procedure.* All participants completed the task online.
+Participants were provided with a description of the experiment and indicated informed consent.
+@fig-design-e1 illustrates the general procedure.
+Participants completed a total of 90 trials during the training stage.
+In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
+Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
 
-## Data Processing and Statistical Packages
+Following the training stage, participants proceeded immediately to the testing stage.
+Participants were tested from all six velocity bands, in two separate stages.
+In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
+Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
+In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
+The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
+A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
 
-To prepare the data, we first removed trials that were not easily interpretable as performance indicators in our task.
-Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier.
-The primary measure of performance used in all analyses was the absolute distance away from the center of the target.
-The absolute distance was calculated on every trial, and then averaged within each subject to yield a single performance score, for each position.
-A consistent pattern across training and testing phases in both experiments was for participants to perform worse from throwing positions further away from the target -- a pattern which we refer to as the difficulty of the positions.
-However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest.
-All data processing and statistical analyses were performed in R version 4.03 (R Core Team, 2020).
-ANOVAs for group comparisons were performed using the rstatix package (Kassambara, 2021).
+```{dot}
+//| label: fig-design-e1
+//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
+//| fig-width: 7.0
+//| fig-height: 2.5
+//| fig-responsive: false
 
-## Training Phase
+digraph {
+  graph [layout = dot, rankdir = LR]
 
-@fig-IGAS_Training1 below shows aggregate training performance binned into three stages representing the beginning, middle, and end of the training phase.
-Because the two conditions trained from target distances that were not equally difficult, it was not possible to directly compare performance between conditions in the training phase.
-Our focus for the training data analysis was instead to establish that participants did improve their performance over the course of training, and to examine whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided in the supplementary materials.
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
 
-We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor.
-The analysis revealed a significant effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02, and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+```
 
 ```{r}
-#| label: fig-IGAS_Training1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
 
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+#   stringr, here,conflicted, patchwork, knitr)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+e1 <- readRDS(here("data/e1_08-21-23.rds")) 
+e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
+testE1 <- e1 |> filter(expMode2 == "Test")
+nbins=5
+trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
+    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
+trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
+trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
+```
 
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+### Analyses Strategy
 
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+All data processing and statistical analyses were performed in R version 4.32 [@rcoreteamLanguageEnvironmentStatistical2020].
+To assess differences between groups, we used Bayesian Mixed Effects Regression.
+Model fitting was performed with the brms package in R [@burknerBrmsPackageBayesian2017], and descriptive stats and tables were extracted with the BayestestR package [@makowskiBayestestRDescribingEffects2019].
+Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
+Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
 
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
+Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
+We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
+For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
 
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
+::: {#tbl-brms-models}
+| Group Comparison         | Code                                                        | Data                 |
+| ------------------------ | ----------------------------------------------------------- | -------------------- |
+| End of Training Accuracy | `` brm(Abs. Deviation ~ condit) ``                                    | Final Training Block |
+| Test Accuracy            | `` brm(Abs. Deviation ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
+| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
 
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
+: **Statistical Model Specifications**.
+The specifications for the Bayesian regression models used in the analyses of each of the 3 experiments.
+Comparisons of accuracy use abosulte deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
+:::
+\
+
+In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
+extrapolation bands); 3) extent of discrimination between all six testing bands.
+We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
+Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
+The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
+Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
+
+### Results
+
+```{r}
+#| label: fig-e1-train-dev
+#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
+p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
+    stat_summary(geom = "line", fun = mean) +
+    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
+    facet_wrap(~vb)+
+    scale_x_continuous(breaks = seq(1, nbins + 1)) +
+    theme(legend.title=element_blank()) + 
+    labs(y = "Absolute Deviation", x="Training Block") 
+#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
+p1
+```
+
+```{r}
+#| cache: true
+invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
+invisible(list2env(load_e1(), envir = .GlobalEnv))
+e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
+e2_model <- load_e2()
+e3_model <- load_e3()
+options(contrasts = initial_contrasts)
 
@@
 
-## Testing Phase
+### Modelling Results
 
-In Experiment 1, a single constant-trained group was compared against a single varied-trained group.
-At the transfer phase, all participants were tested from 3 positions: 1) the positions(s) from their own training, 2) the training position(s) of the other group, and 3) a position novel to both groups.
-Overall, group performance was compared with a mixed type III ANOVA, with condition (varied vs.
-constant) as a between-subject factor and throwing location as a within-subject variable.
-The effect of throwing position was strong, F(3,213) = 56.12, p\<.001, η2G = .23.
-The effect of training condition was significant F(1,71)=8.19, p\<.01, η2G = .07.
-There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.
+```{r}
+#| label: tbl-htw-modelError-e1
+#| tbl-cap: "Models errors predicting empirical data from Experiment 1 -  aggregated over the full posterior distribution for each participant.
+Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
+#| 
+post_tabs <- abc_tables(post_dat,post_dat_l)
+train_tab <- abc_train_tables(pd_train,pd_train_l)
+
+fmt_out <- knitr::pandoc_to()
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+print(fmt_out)
+
+primary=out_type == "html" || out_type == "pdf"
+
+out_type %in% c("html","pdf")
+
+e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
+
+#if (primary) {
+e1_tab %>%
+  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
+  summarize(ME = mean(mean_error), .groups = "drop") %>%
+  pivot_wider(
+    names_from = c(Model, condit),
+    values_from = ME,
+    names_sep = "_"  # Add this line to specify the separator for column names
+  ) %>%
+  rename("Fit Method" = Fit_Method) %>%
+  gt() %>%
+  cols_move_to_start(columns = c(`Task Stage`)) %>%
+  cols_label(
+    `Task Stage` = "Task Stage"
+  ) %>%
+  fmt_number(
+    columns = starts_with("ALM") | starts_with("EXAM"),
+    decimals = 2
+  ) %>%
+  tab_spanner_delim(delim = "_") %>%
+  tab_style(
+    style = cell_fill(color = "white"),
+     locations = cells_body(columns = everything(), rows = everything())
+  ) %>%
+  tab_style(
+    style = cell_borders(sides = "top", color = "black", weight = px(1)),
+    locations = cells_column_labels()
+  ) %>%
+  tab_options(
+    table.font.size = 12,
+    heading.title.font.size = 14,
+    heading.subtitle.font.size = 12,
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
+  )
+
+  } 
+  # else {
+
+  #   e1_tab %>%
+  # group_by(`Task Stage`, Fit_Method, Model, condit) %>%
+  # summarize(ME = mean(mean_error), .groups = "drop") %>%
+  # pivot_wider(
+  #   names_from = c(Model, condit),
+  #   values_from = ME,
+  #   names_sep = "_"  # Add this line to specify the separator for column names
+  # ) %>%
+  # rename("Fit Method" = Fit_Method) %>% kable(escape=F,booktabs=T)
+
+  # }
+
+```
+
+### table 2
+
+```{r}
+#| label: tbl-htw-modelError-e23
+#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
+Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
+
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+primary=out_type == "html" || out_type == "pdf"
+
+pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+
+pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
+  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
+
+# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
+e1_ee_brm_ae <- brm(data=pdl,
+  aerror ~  Model * condit + (1+bandInt|id), 
+  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
+  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
+
+bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
+  select(1,2,4,5,6) %>%
+  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
+  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
+  tibble::remove_rownames() %>%
+  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
+
+post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
+train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
+
+pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
+
+e2_tab <- rbind(post_tabs2$agg_pred_full |>
+ mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
+ mutate("Task Stage"="Train")) |> 
+  mutate(Fit_Method=rename_fm(Fit_Method))
+
+post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
+train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
+
+pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
+
+e3_tab <- rbind(post_tabs3$agg_pred_full |> 
+  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
+  mutate(Fit_Method=rename_fm(Fit_Method))
+
+e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3"))
+
+if (primary) {
+gt_table <- e23_tab %>%
+  pivot_wider(
+    names_from = c(Exp, Model, condit),
+    values_from = mean_error,
+    names_glue = "{Exp}_{Model}_{condit}"
+  ) %>%
+  arrange(Fit_Method, `Task Stage`) %>%
+  gt() %>%
+  cols_move_to_start(columns = `Task Stage`) %>%
+  cols_label(`Task Stage` = "Task Stage") %>%
+  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
+  tab_spanner_delim(delim = "_") %>%
+  tab_style(
+    style = list(
+      cell_fill(color = "white"),
+      cell_borders(sides = "top", color = "black", weight = px(1))
+    ),
+    locations = cells_body(columns = everything(), rows = everything())
+  ) %>%
+  tab_options(
+    table.font.size = 12,
+    heading.title.font.size = 14,
+    heading.subtitle.font.size = 12,
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
+  )
+gt_table
+} else {
+  e23_tab %>%
+  pivot_wider(
+    names_from = c(Exp, Model, condit),
+    values_from = mean_error,
+    names_glue = "{Exp}_{Model}_{condit}"
+  ) %>%
+  arrange(Fit_Method, `Task Stage`) %>%
+  kable(escape=F,booktabs=T)
+}
+```
+
+```{r}
+#| label: tbl-htw-ee-e23
+#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
+EXAM), Condition (Constant vs.
+Varied), and the interaction between Model and Condition.
+The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
+The intercept reflects the baseline of ALM and Constant.
+The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
+Lower values indicate better model fit."
+
+e2_ee_brm_ae <- brm(data=pdl2,
+  aerror ~  Model * condit + (1+bandInt|id), 
+  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
+  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
+
+bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
+bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
+bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
+
+bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
+  select(1,2,4,5,6) %>%
+  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
+  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
+  tibble::remove_rownames() %>%
+  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
+
+e3_ee_brm_ae <- brm(data=pdl3,
+  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
+  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
+  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
+
+bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
+bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
+bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
+bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
+
+bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
+  select(1,2,4,5,6) %>%
+  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
+  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
+  tibble::remove_rownames() %>%
+  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
+
+bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
+               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
+  relocate(exp, .before=Term)
+
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+primary=out_type == "html" || out_type == "pdf"
+
+if(primary) {
+bct_table <- bct %>%
+  mutate(
+    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
+    pd = round(pd, 2)
+  ) %>%
+  gt() %>%
+  # tab_header(
+  #   title = "Bayesian Model Results",
+  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
+  # ) %>%
+  cols_label(
+    exp = "Experiment",
+    Term = "Term",
+    Estimate = "Estimate",
+    `95% CrI Lower` = "95% CrI Lower",
+    `95% CrI Upper` = "95% CrI Upper",
+    pd = "pd"
+  ) %>%
+  fmt_number(
+    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
+    decimals = 1
+  ) %>%
+  fmt_number(
+    columns = pd,
+    decimals = 2
+  ) %>%
+  tab_spanner(
+    label = "Credible Interval",
+    columns = c(`95% CrI Lower`, `95% CrI Upper`)
+  ) %>%
+  tab_style(
+    style = list(
+      #cell_fill(color = "lightgray"),
+      cell_text(weight = "bold"), 
+      cell_fill(color = "white"),
+      cell_borders(sides = "top", color = "black", weight = px(1))
+    ),
+    locations = cells_body(
+      columns = c(Estimate, pd),
+      rows = Term=="ModelEXAM:conditVaried"
+    )
+  ) %>%
+   tab_row_group(
+    label = "Experiment 3",
+    rows = exp == "Exp 3"
+  ) %>%
+  tab_row_group(
+    label = "Experiment 2",
+    rows = exp == "Exp 2"
+  ) %>%
+  tab_row_group(
+    label = "Experiment 1",
+    rows = exp == "Exp 1"
+  ) %>%
+  tab_options(
+    table.font.size = 12,
+    heading.title.font.size = 14,
+    heading.subtitle.font.size = 12,
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
+    #row_group.background.color = "gray95"
+  )
+bct_table
+} else {
+  bct %>%
+  mutate(
+    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
+    pd = round(pd, 2)
+  ) %>% kable(escape=F,booktabs=T)
+
+}
+
+```
+
+*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
+For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
+The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
+The Bayesian regression models predicting model error as a function of Model (ALM vs.
+EXAM), Condition (Constant vs.
+Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
+The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
+Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
+Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
+We thus also controlled for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
+There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
+
+::: {#tbl-e2-bmm-vx}
+
+| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
+|:-------------|---------:|--------------:|--------------:|-----:|
+| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
+| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
+| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
+| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
+
+**Experiment 2 Testing Discrimination**.
+Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
+Varied) and Velocity Band.
+Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
+The interaction between condit and Band indicates the difference between constant and varied slopes.
+CrI values indicate 95% credible intervals.
+pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate) {.hover .sm}
+:::
+
+Here, $m(X_1)$ is the ALM response value from the training data for the stimulus closest to $X$, and $(X - X_1)$ represents the distance between the novel stimulus and the nearest training stimulus.
+
+Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
+EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
+The slope is then used to extrapolate the response to the novel test stimulus.
+Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
+We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
+This assumption is motivated by previous function learning research [@brownUnderestimationLinearFunction2017], which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
+
+See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
+
+::: column-page-inset-right
+|                    | **ALM Response Generation**                                        |                                                                                               |
+|------------------|-----------------------------|-------------------------|
+| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
+| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
+| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
+| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
+|                    | **ALM Learning**                                                   |                                                                                               |
+| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
+| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
+| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
+|                    | **EXAM Extrapolation**                                             |                                                                                               |
+| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
+| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
+| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$,  adjusted by local slope $S$.
+|
+
+: ALM & EXAM Equations {#tbl-alm-exam}
+:::
+
+::: {.callout}
+
+**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
+
+To estimate the  parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
+Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g., many neural network models).
+
+The general ABC procedure is to 1) define a prior distribution over model parameters.
+2) sample candidate parameter values, $\theta^*$, from the prior.
+3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
+4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
+5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
+6) Repeat until desired number of posterior samples are obtained.
+
+Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
+For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
+For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
+For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
+After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
+For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
+
+::: column-page-inset-left
+$$
+discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
+$$ {#eq-discrep-test}
+
+$$
+\begin{aligned} \\
+discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
+discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
+\end{aligned}
+$$ {#eq-discrep-train}
+:::
+
+The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
+The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
+Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
+Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
+The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
+Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
+After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
+In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
+To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
+:::
+
+# Appendix
+
+[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html
+
+# References

### 2024-04-22 Sections/full.qmd
add docx version; fix igas figure text; re-render everything.

@@
 toc-location: body
-#toc-title: Contents
 toc-depth: 4
 cache: true
-format-links: [hikmah-manuscript-pdf, gfm]
+format-links: [hikmah-manuscript-pdf, gfm, docx]
 execute: 
@@
     echo: false
-    output: false
+    #output: false
     output-file: diss_full_gfm.md
@@
     mathfont: "Libertinus Math"
+  docx:
+    echo: false
+    prefer-html: true
+    output-file: "TG_Full_Dissert.docx"
+    toc: true
 prefer-html: true
@@
 #| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
+#| fig-cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
 On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
@@
 #| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
+#| fig-cap: Testing phase performance from each of the six testing positions.
 The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
@@
 
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  #%>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
 
@@
 
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
+kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) # %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
 ```
@@
 #| label: fig-taskSpace
-#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+#| fig-cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
 This empirical solution space was compiled from all of the participants in Experiment 2.
@@
 #| label: fig-Toy-Model-dis
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
+#| fig-cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
 For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
@@
   )
+} else {
+
+  e1_tab %>%
+  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
+  summarize(ME = mean(mean_error), .groups = "drop") %>%
+  pivot_wider(
+    names_from = c(Model, condit),
+    values_from = ME,
+    names_sep = "_"  # Add this line to specify the separator for column names
+  ) %>%
+  rename("Fit Method" = Fit_Method) %>% kable(escape=F,booktabs=T)
+
+  }
 ```
@@
 
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+primary=out_type == "html" || out_type == "pdf" || out_type =="latex" || out_type == "docx"
+
 post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
@@
 e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3"))
+
+if (primary) {
 gt_table <- e23_tab %>%
@@
 gt_table
+} else {
+  e23_tab %>%
+  pivot_wider(
+    names_from = c(Exp, Model, condit),
+    values_from = mean_error,
+    names_glue = "{Exp}_{Model}_{condit}"
+  ) %>%
+  arrange(Fit_Method, `Task Stage`) %>%
+  kable(escape=F,booktabs=T)
+}
 ```
@@
 Lower values indicate better model fit."
+#| cache: false
 
@@
 bct_table
-
+} else {
+  bct %>%
+  mutate(
+    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
+    pd = round(pd, 2)
+  ) %>% kable(booktabs = TRUE)
+
+}
 ```

### 2024-04-22 Sections/test_types.qmd
add docx version; fix igas figure text; re-render everything.

--- 2024-04-12 Sections/docx_test.qmd
@@
 ---
-title: Full Dissertation2
-subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
-#date: 04/04/24
+title: "test_types"
 author:
@@
   affiliation: Indiana University
-# page-layout: full
-# code-fold: true
-# code-tools: true
-# toc: true
-# toc-location: body
-# toc-title: Contents
-#cache: true
+page-layout: full
+code-fold: true
+code-tools: true
+toc: true
+toc-location: body
+#toc-title: Contents
+toc-depth: 4
+cache: false
+#format-links: [hikmah-manuscript-pdf, gfm]
 execute: 
@@
 format:
-  #html: default
-  hugo-md:
-    echo: false
-    #include: false
-    html-math-method: mathjax
-    output-file: diss_full_hugo22.md
-  gfm:
-    echo: false
-    output: false
-    output-file: diss_full_gfm22.md
-  hikmah-manuscript-pdf:
-    echo: false
-    output-file: "tg_full_disser22.pdf"
-    mainfont: "Linux Libertine O"
-    mainfontoptions:
-      - "Numbers=Proportional"
-      - "Numbers=OldStyle"
-    mathfont: "Libertinus Math"
-  hikmah-manuscript-docx: 
-    output-file: "manuscript-ms2.docx"
+#   html: default
+#   hugo-md:
+#     echo: false
+#     include: true
+#     html-math-method: mathjax
+#     output-file: test_hugo.md
+#   gfm:
+#     echo: false
+#     output: true
+#     output-file: testl_gfm.md
+#   hikmah-manuscript-pdf:
+#     echo: false
+#     output-file: "test.pdf"
+#     mainfont: "Linux Libertine O"
+#     mainfontoptions:
+#       - "Numbers=Proportional"
+#       - "Numbers=OldStyle"
+#     mathfont: "Libertinus Math"
+  docx:
     echo: false
     prefer-html: true
-    toc: false
+    output-file: "teset.docx"
+    toc: true
 prefer-html: true
@@
 
-# Abstract
+**Approximate Bayesian Computation**
 
-The past century of research on human learning has produced ample evidence that although learners can improve at almost any task, such improvements are often specific to the trained task, with unreliable or even nonexistent transfer or generalization to novel tasks or conditions [@barnettWhenWhereWe2002; @dettermanCaseProsecutionTransfer1993].
-Such generalization challenges are of noteworthy practical relevance, given that educators, trainers, and rehabilitators typically intend for their students to be able to apply what they have learned to new situations.
-It is therefore important to better understand the factors that influence generalization, and to develop cognitive models that can predict when generalization is likely to occur.
-Such characteristics have included training difficulty, spacing, temporal order, feedback schedules, and the primary focus of the current work - the variability of training examples.
+To estimate the  parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
+Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g., many neural network models).
 
-This dissertation seeks to explore the cognitive underpinnings that govern the generalization of learning, focusing specifically on the role of variability during training in shaping subsequent transfer performance.
-A comprehensive review of the existing literature is presented, emphasizing the methodological complications associated with disentangling the confounding effects of similarity.
-Through a series of experiments involving several novel visuomotor tasks, this work investigates whether and how variability in training conditions affects performance in novel tasks.
-To theoretically account for the empirical outcomes, I employ both instance-based and connectionist computational models, both of which incorporate similarity-based mechanisms.
-These models serve to account for the extent to which variability influences the learners' generalization gradient, and also explain how training variation can produce both beneficial and deleterious outcomes.
-
-## The study of variability
-
-Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
-See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
-
-Research on the effects of varied training typically manipulates variability in one of two ways.
-In the first approach, a high variability group is exposed to a greater number of unique instances during training, while a low variability group receives fewer unique instances with more repetitions.
-Alternatively, both groups may receive the same number of unique instances, but the high variability group's instances are more widely distributed or spread out in the relevant psychological space, while the low variability group's instances are clustered more tightly together.
-Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
-Researchers will usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
-The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
-However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to make it easy to measure how much performance degrades as a function of how far away testing items are from the training items.
-
-The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes that learners possess general motor programs for a class of movements (e.g.
-an underhand throw).
-When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
-Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations.
-Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
-
-One of the earliest, and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
-Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
-The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
-Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
-12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
-Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
-In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-This result offers a particularly compelling example of the merits of varied practice, given that the varied group was able to outperform the constant group even from the  home turf location where one may have expected the constatn group to have the strongest advantage.
-A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a].
-One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
-Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperfroms the constant group even from the constants group's home turf has not been consistently replicated.
-One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
-However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-
-Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
-It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
-Of particular relevance to the current work is the early study of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
-constant training on multiple testing locations of graded distance from the training condition.
-Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
-The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
-Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
-As is often the case, the varied group performed worse during the training phase.
-In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
-
-Benefits of varied training have also been observed in many studies outside of the sensorimotor domain.
-@goodeSuperiorityVariableRepeated2008 trained participants to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
-Although subjects in all conditions were exposed to the same 40 unique words (i.e.
-the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training).
-Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g.
-LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
-At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had 3 prior exposures to the word arrangement (i.e.
-the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving 2 more anagrams on average than the constant group.
-This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
-This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.
-
-In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
-typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
-
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968].
-A seminal study by @posnerGenesisAbstractIdeas1968 trained participants to categorize artificial dot patterns, manipulating whether learners were trained with low variability examples clustered close to the category prototypes (i.e. low distortion training patterns), or higher-variability patterns spread further away from the prototype (i.e.
-high-distortion patterns).
-Participants that received training on more highly-distorted items showed superior generalization to novel high distortion patterns in the subsequent testing phase.
-It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training rathers, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
-This train-until-criterion procedure led to the high-variability condition participants tending to complete a larger number of training trials before switching to the testing stage.
-More recent work [@huHighvariabilityTrainingDoes2024], also used dot pattern categories, but matched the number of training trials across conditions.
-Under this procedure, higher-variability participants tended to reach lower levels of performance by the end of the training stage.
-The results in the testing phase were the opposite of @posnerGenesisAbstractIdeas1968,  with the low-variability training group showing superior generalization to novel high-distortion patterns (as well as generalization to novel patterns of low or medium distortion levels).
-However, whether this discrepancy is solely a result of the different training procedures is unclear, as the studies also differed in the nature of the prototype patterns used.
-@posnerGenesisAbstractIdeas1968  utilized simpler, recognizable prototypes (e.g., a triangle, the letter M, the letter F), while  @huHighvariabilityTrainingDoes2024 employed random prototype patterns.
-
-Recent studies have also begun utilizing more complex or realistic sitmuli when assessing the influence of variability on category learning.
-@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
-In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
-Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
-higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyModelguidedSearchOptimal2019].
-For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
-The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
-
-A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g.
-the region between the two categories).
-The general approach is to train participants with examples from a high variability category and a low variability category.
-Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
-@cohenCategoryVariabilityExemplar2001 trained subjects on two categories, one with much more variability than the other.
-In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
-In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart.
-Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
-Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into a category with greater variation.
-
-Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002;  @yangCategoryVariabilityEffect2014; and @seitzModelingCategoryVariability2023].
-The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
-They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
-In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial.
-They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
-
-The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present work.
-Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
-During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories.
-The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category.
-Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category.
-Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
-The author compared a variety of similarity-based models based around the Generalized Context Model [@nosofskyAttentionSimilarityIdentificationcategorization1986] to account for their results, manipulating whether a response-bias or similarity-scaling parameter was fit separately between variability conditions.
-No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improvement significantly when the similarity scaling parameter was fit separately.
-The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied particpants, and also for their poorer performance in a recognition condition.
-
-Variability has also been examined in the learning of higher-order linguistic categories [@perryLearnLocallyThink2010].
-In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
-All infants were introduced to three novel objects of the same category, with participants in the "tight" condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
-Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
-Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels of the training objects.
-In the testing phase, the varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category.
-More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
-The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987; @vanrossumSchmidtSchemaTheory1990], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-In an example of a more complex influence of training variation, [@braithwaiteEffectsVariationPrior2015] trained participants on example problems involving the concept of sampling with replacement (SWR).
-Training consisted of examples that were either highly similar in their semantic context (e.g.
-all involving people selecting objects) or in which the surface features were varied between examples (e.g.
-people choosing objects AND objects selected in a sequence).
-The experimenters also surveyed how much prior knowledge each participant had with SWR.
-They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples.
-The authors hypothesized that in order to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
-To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples.
-Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
-Interactions between prior experience and the influence of varied training have also been observed in sensorimotor learning [@guadagnoliRelationshipContextualInterference1999;  @delreyEffectsContextualInterference1982].
-@delreyEffectsContextualInterference1982 recruited participants who self-reported either extensive, or very little experience with athletic activities, and then trained participants on a coincident timing task under with either a single constant training velocity, with one of several varied training procedures.
-Unsurprisingly, athlete participants had superior performance during training, regardless of  condition, and training performance was superior for all subjects in the constant group.
-Of greater interest is the pattern of testing results from novel transfer conditions.
-Among the athlete-participants, transfer performance was best for those who received variable training.
-Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
-
-### The current work
-
-The overarching purpose of this dissertation is to investigate the effects of training variability on learning and generalization within visuomotor skill learning and function learning.
-Our investigations is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
-
-In Project 1, we investigated the influence of varied practice in a simple visuomotor projectile launching task.
-Experiments 1 and 2 compared the performance of constant and varied training groups to assess potential benefits of variability on transfer to novel testing conditions.
-To account for the observed empirical effects, we introduced the Instance-based Generalization with Adaptive Similarity (IGAS) model.
-IGAS provides a novel computational approach for quantifying the similarity between training experiences and transfer conditions, while also allowing for variability to influence the generalization gradient itself.
-
-Project 2 shifted focus to the domain of function learning by employing a visuomotor extrapolation task.
-Across three experiments, we examined how constant and varied training regimes affected learning, discrimination between stimuli, and the ability to extrapolate to novel regions of the function's input space.
-To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.
-
-{{< pagebreak >}}
-
-# Project 1
+The general ABC procedure is to 1) define a prior distribution over model parameters.
+2) sample candidate parameter values, $\theta^*$, from the prior.
+3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
+4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
+5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
+6) Repeat until desired number of posterior samples are obtained.
 
 ```{r}
-#| cache: false
-
+#| echo: false
+#| 
 pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
-  ggh4x,htmltools,future,furrr,ez)
-#options(brms.backend="cmdstanr",mc.cores=4)
-#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
-walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-#conflicts_prefer(tidybayes::rstudent_t)
+  stringr, here,conflicted, patchwork, knitr,gt)
 
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
+out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
+print(out_type)
+primary=out_type == "html" || out_type == "pdf" || out_type =="latex"
 
-#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
+fmt_out <- knitr::pandoc_to()
+print(fmt_out)
 
-#options(brms.backend="cmdstanr",mc.cores=4)
-initial_contrasts <- options("contrasts")$contrasts
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-
-library(tidybayes)
-
-theme_set(theme_classic())
-# load the processed data from experiment 1 and 2
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
-# defaultContrasts = options()$contrasts
-# theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-```
-
-# Abstract
-
-Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
-Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
-However much of this research has neglected to account for differences in similarity between varied and constant training conditions.
-In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
-We replicate previous findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
-Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
-
-## Similarity and instance-based approaches to transfer of learning
-
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar.
-In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimuli.
-Recall that participants are trained on only on distortions of the category prototypes (e.g.
-low, medium or high distortions), never encountering the exact prototypes during the training stage.
-Then, in the testing phase, participants are tested with the prototype patterns, their old training items, and novel low, medium and high distortions.
-The authors found that participants had the highest testing accuracy for the previously unseen prototype patterns, followed by the old training items, and then the novel low, medium and high distortions.
-The authors interpreted this pattern as evidence that participants had acquired prototype representation of the category, as opposed to storing each individual training instance, and that generalization was based on the similarity of the testing items to the learned prototype representations.
-@posnerGenesisAbstractIdeas1968 has been extremely influential,  and continues to be cited in contemporary research as clear evidence that prototype abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
-However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
-@palmeriCentralTendenciesExtreme2001 demonstrated the both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
-These authors conducted a near replication of the @posnerGenesisAbstractIdeas1968 study, but also had participants provide similarity judgements of the dot pattern stimuli after completing the training phase.
-A multidimensional scaling analysis of the similarity judgements revelead that the psychological representations of the prototype stimuli were not located in the middle of the training stimuli, but were instead extreme points in the psychological space.
-The authors also demonstrated the generalization patterns of @posnerGenesisAbstractIdeas1968 could be accounted for by an exemplar-based model, without any need to assume the abstraction of a prototype.
-
-Instance-based, or exemplar-based models generally assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978; @nosofskyAttentionSimilarityIdentificationcategorization1986; @jamiesonInstanceTheoryDomaingeneral2022].
-As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
-In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
-Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
-That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based similarity approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
-@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
-Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
-
-## Issues with Previous Research
-
-Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g.
-projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g.
-more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
-
-```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
-
-p=2
-c<- .0002
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
-  group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
-
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
+out_type %in% c("html","pdf")
+# out_type = "html"
+out_type == "html" || out_type == "pdf" || out_type == "docx"
 
@@
 
-In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
+```{r}
 
-The present work examines whether the commonly observed benefits of varied training can be accounted for by between-group differences in similarity between training and testing throws.
-We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
-We then examine the extent to which this advantage can be explained by an instance-based similarity model.
+# create examples of fancy looking gt tables using cars data
+cars <- cars %>% as_tibble()
 
-# Experiment 1
+# create examples of fancy looking gt tables using flowers data
+# create flowers data
+flowers <- iris %>% as_tibble()
+# flowers
+# # A tibble: 150 × 5
+#    Sepal.Length Sepal.Width Petal.Length Petal.Width Species
+#           <dbl>       <dbl>        <dbl>       <dbl> <fct>  
+#  1          5.1         3.5          1.4         0.2 setosa 
+#  2          4.9         3            1.4         0.2 setosa 
+#  3          4.7         3.2          1.3         0.2 setosa 
+#  4          4.6         3.1          1.5         0.2 setosa 
+#  5          5           3.6          1.4         0.2 setosa 
+#  6          5.4         3.9          1.7         0.4 setosa 
+#  7          4.6         3.4          1.4         0.3 setosa
 
-## Methods
+# create examples of fancy looking gt tables using flowers data
 
-### Sample Size Estimation
-
-To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies, yielding a Cohens f =.43.
-The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009], 2009) was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
-All experiments reported in the present manuscript exceed this minimum number of participants per condition.
-
-### Participants
-
-Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18-22 years.
-A total of 110 Indiana University psychology students participated in Experiment 1.
-We subsequently excluded 34 participants poor performance at one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g.
-simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
-A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.
-
-### Task
-
-The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library (de Leeuw, 2015).
-The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
-Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
-Likewise, the distance between the center of the target, and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
-For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
-@fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square.
-Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
-If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target.
-If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
-If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier.
-If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square.
-If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
-
-[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-```{r}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square
-
-mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-plot_grid(mf,ncol=1)
+if (primary){
+flowers |> gt() |> tab_header(
+  title = "Iris Flower Data",
+  subtitle = "A tibble: 150 × 5"
+) |> fmt_number(
+  columns = c(Sepal.Length, Sepal.Width, Petal.Length, Petal.Width),
+  decimals = 1) |> 
+  tab_spanner(
+    label = "Sepal Characteristics",
+    columns = c(Sepal.Length, Sepal.Width)
+  ) 
+} else {
+    flowers |> kable() }
 
@@
 
-## Results
+See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
 
-## Data Processing and Statistical Packages
+::: column-page-inset-right
+|                    | **ALM Response Generation**                                        |                                                                                               |
+|------------------|-----------------------------|-------------------------|
+| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
+| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
+| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
+| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
+|                    | **ALM Learning**                                                   |                                                                                               |
+| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
+| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
+| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
+|                    | **EXAM Extrapolation**                                             |                                                                                               |
+| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
+| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
+| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$,  adjusted by local slope $S$.
+|
 
-To prepare the data, we first removed trials that were not easily interpretable as performance indicators in our task.
-Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier.
-The primary measure of performance used in all analyses was the absolute distance away from the center of the target.
-The absolute distance was calculated on every trial, and then averaged within each subject to yield a single performance score, for each position.
-A consistent pattern across training and testing phases in both experiments was for participants to perform worse from throwing positions further away from the target -- a pattern which we refer to as the difficulty of the positions.
-However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest.
-All data processing and statistical analyses were performed in R version 4.03 (R Core Team, 2020).
-ANOVAs for group comparisons were performed using the rstatix package (Kassambara, 2021).
+: ALM & EXAM Equations {#tbl-alm-exam}
+:::
 
-## Training Phase
+**Approximate Bayesian Computation**
+To estimate the  parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
+Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g., many neural network models).
 
-@fig-IGAS_Training1 below shows aggregate training performance binned into three stages representing the beginning, middle, and end of the training phase.
-Because the two conditions trained from target distances that were not equally difficult, it was not possible to directly compare performance between conditions in the training phase.
-Our focus for the training data analysis was instead to establish that participants did improve their performance over the course of training, and to examine whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided in the supplementary materials.
+The general ABC procedure is to 1) define a prior distribution over model parameters.
+2) sample candidate parameter values, $\theta^*$, from the prior.
+3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
+4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
+5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
+6) Repeat until desired number of posterior samples are obtained.
 
-We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor.
-The analysis revealed a significant effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02, and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
+Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
+For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
+For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
+For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
+After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
+For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
 
-```{r}
-#| label: fig-IGAS_Training1
-#| fig.cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
+**Approximate Bayesian Computation**
 
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+To estimate the  parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
+Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g., many neural network models).
 
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+The general ABC procedure is to 1) define a prior distribution over model parameters.
+2) sample candidate parameter values, $\theta^*$, from the prior.
+3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
+4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
+5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
+6) Repeat until desired number of posterior samples are obtained.
 
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
+For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
+For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
+For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
+After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
+For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
 
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+::: column-page-inset-left
+$$
+discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
+$$ {#eq-discrep-test}
 
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
+$$
+\begin{aligned} \\
+discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
+discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
+\end{aligned}
+$$ {#eq-discrep-train}
+:::
 
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
+The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
+The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
+Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
+Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
+The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
+Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
+After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
+In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
+To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
 
-```
+# Appendix
 
-## Testing Phase
+[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html
 
-In Experiment 1, a single constant-trained group was compared against a single varied-trained group.
-At the transfer phase, all participants were tested from 3 positions: 1) the positions(s) from their own training, 2) the training position(s) of the other group, and 3) a position novel to both groups.
-Overall, group performance was compared with a mixed type III ANOVA, with condition (varied vs.
-constant) as a between-subject factor and throwing location as a within-subject variable.
-The effect of throwing position was strong, F(3,213) = 56.12, p\<.001, η2G = .23.
-The effect of training condition was significant F(1,71)=8.19, p\<.01, η2G = .07.
-There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.
+# References

### 2024-04-22 paper.qmd
add docx version; fix igas figure text; re-render everything.

@@
 
+<a class="btn btn-warning btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
+  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;docx <small>(download)</small>
+  </a>
     <!-- <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">

### 2024-05-18 Presentation/pres1.qmd
start creating slides

---
title: "The Role of Variability in Learning Generalization"
format: 
  revealjs:
    theme: moon #white
    slideNumber: true
    center: true
    chalkboard: true
author: Thomas Gorman
institute: Indiana University
---

## Introduction
- Investigate effects of training variability on learning and generalization
- Focus areas: visuomotor skill learning and function learning tasks

## Background and Motivation
- Importance of training variability
- Research gaps in visuomotor skill learning
- Previous research in category learning, language learning, and function learning

## Theoretical Frameworks
- Schema Theory (Schmidt, 1975)
- Desirable Difficulties Framework (Bjork & Bjork, 2011)
- Challenge Point Framework (Guadagnoli & Lee, 2004)

## Overview of Current Work
- Project 1: Visuomotor projectile launching task
- Project 2: Visuomotor extrapolation task

## Project 1 - Hit The Target (HTT)
- Influence of varied practice in a projectile launching task
- Experiments 1 & 2:
  - Constant vs. varied training groups
  - Performance metrics and transfer testing

## Project 1 - Methodology
- Task description and experimental design
- Participants and procedures
- IGAS model introduction

## Project 1 - Results and Discussion
- Varied training group's superior performance
- Computational modeling results with IGAS
- Theoretical implications

## Project 2 - Hit The Wall (HTW)
- Influence of varied practice in a function learning task
- Experiments 1, 2, and 3:
  - Training regimes and testing conditions
  - Learning, discrimination, and extrapolation performance metrics

## Project 2 - Methodology
- Task description and experimental design
- Participants and procedures
- Application of ALM and EXAM models

## Project 2 - Results and Discussion
- Training variability's mixed results
- Modeling analysis with ALM and EXAM
- Theoretical implications

## General Discussion
- Compare HTT and HTW
- Empirical findings summary
- Computational modeling contributions

## Theoretical Contributions
- Insights into training variability effects on learning and generalization
- Computational models applications

## Practical Implications
- Training programs design implications
- Future research considerations

## Limitations and Future Directions
- Study limitations
- Future research suggestions

## Conclusion
- Recap of key findings
- Final thoughts on training variability's role in learning

## Questions and Discussion
- Open floor for questions from the committee and audience

### 2024-05-18 Presentation/slides.qmd
update slides - multiple formats and test images

--- 2024-05-18 Presentation/pres1.qmd
@@
 ---
-title: "The Role of Variability in Learning Generalization"
+title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
+subtitle: "Dissertation Defense"
 format: 
-  revealjs:
-    theme: moon #white
+  html: default
+  clean-revealjs:
+    #theme: moon #white
+    output-ext: slide.html
     slideNumber: true
@@
     chalkboard: true
-author: Thomas Gorman
-institute: Indiana University
+  pptx:
+    incremental: true
+author:
+  - name: Thomas Gorman
+    orcid: 0000-0000-0000-0000
+    affiliations: Indiana University
 ---
@@
 
+![](assets/fig-toy-model1-1-1.png)
+
 ## Overview of Current Work
@@
 - IGAS model introduction
+
+![](assets/methodsFig1.png)
 
@@
 
+::: {.content-visible unless-format="markdown"}
+```{dot}
+//| label: fig-design-e1
+//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
+//| fig-width: 7.0
+//| fig-height: 2.5
+//| fig-responsive: false
+//| echo: false  
+///| eval: !expr out_type 
+/////| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+```
+:::
+
 ## Project 2 - Results and Discussion
@@
 - Theoretical implications
+
+## Project 2 - ALM
+
+![](assets/fig-alm-diagram-1-1.png)
 

### 2024-05-18 Presentation/slides.qmd
Add embeded view of slides; re-render major pages.

@@
     #theme: moon #white
-    output-ext: slide.html
+    #output-ext: revealjs.html
+    output-file: slides_revealjs
     slideNumber: true
@@
 ---
+
+::: {.content-visible when-format="html" unless-format="revealjs"}
+
+<div class="ratio ratio-16x9"> <iframe src="/Presentation/slides_revealjs.html"></iframe> </div>
+
+:::
 

### 2024-05-18 Presentation/slides2.qmd
Add embeded view of slides; re-render major pages.

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
subtitle: "Dissertation Defense"
format: 
  html: default
author:
  - name: Thomas Gorman
    orcid: 0000-0000-0000-0000
    affiliations: Indiana University
---

::: {.content-visible when-format="html"}

<div class="ratio ratio-16x9"> <iframe src="/Presentation/slides_revealjs.html"></iframe> </div>

test
:::

### 2024-05-18 Sections/Appendix/IGAS-Supplemental.qmd
start creating slides
try adding alias to appendix

@@
   eval: true
+  echo: false
 ---
@@
 
-Reviewer #2: This study addresses a question that is important both theoretically and practically.
+<!-- Reviewer #2: This study addresses a question that is important both theoretically and practically.
 However, the authors need to rule out the following, less interesting alternative.
@@
 If such disadvantage for the constant group is indeed due to the lack of tryout opportunities, then the authors should verify whether the same results still hold if all groups were provided opportunities to practice, or if pre-training tests across all distances were offered.
+-->
 

### 2024-05-19 Presentation/slides.qmd
some slide updates

--- 2024-05-18 Presentation/slides.qmd
@@
 format: 
-  html: default
+  html: 
+    toc: true
+    #shift-heading-level-by: 1
+    #toc-expand: true
   clean-revealjs:
     #theme: moon #white
-    output-ext: slide.html
+    #output-ext: revealjs.html
+    output-file: slides_revealjs
     slideNumber: true
@@
   - name: Thomas Gorman
-    orcid: 0000-0000-0000-0000
+    url: www.tegorman13.github.io
+    orcid: 0000-0001-5366-5442
     affiliations: Indiana University
@@
 
-## Introduction
+:::: {.content-visible when-format="html" unless-format="revealjs"}
+\
+\
+\
+\
+\
+\
+\
+\
+\
+\
+
+# Slides {visibility="hidden" .unnumbered .unlisted}
+
+Presentation slides are available below.
+You can navigate these sides using the <kbd>←</kbd> and <kbd>→</kbd> keys.
+Press <kbd>m</kbd> to display all commands (e.g., press <kbd>o</kbd> to switch to slide overview)
+
+<p class="buttons" style="text-align:center;">
+
+<a class="btn btn-danger" target="_blank" href="/Presentation/slides_revealjs.html"><i class="fa-solid fa-arrow-up-right-from-square"></i> Open slides in new window </a>
+
+</p>
+
+::::: column-page-inset-right
+::: {.ratio .ratio-16x9}
+<iframe src="/Presentation/slides_revealjs.html"></iframe>
+:::
+:::::
+::::
+
+# Introduction
+
 -   Investigate effects of training variability on learning and generalization
@@
 
+---
+
 ## Background and Motivation
+
 -   Importance of training variability
@@
 
+---
+
 ## Theoretical Frameworks
+
 -   Schema Theory (Schmidt, 1975)
@@
 
+---
+
 ## Overview of Current Work
+
 -   Project 1: Visuomotor projectile launching task
@@
 
-## Project 1 - Hit The Target (HTT)
+---
+
+# Project 1 - Hit The Target (HTT)
+
 -   Influence of varied practice in a projectile launching task
@@
 
+---
+
 ## Project 1 - Methodology
+
 -   Task description and experimental design
@@
 
+---
+
 ## Project 1 - Results and Discussion
+
 -   Varied training group's superior performance
@@
 
-## Project 2 - Hit The Wall (HTW)
+---
+
+## Computational Model
+
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
+
+**Equation 2:**
+$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+
+---
+
+# Project 2 - Hit The Wall (HTW)
+
 -   Influence of varied practice in a function learning task
@@
 
+---
+
 ## Project 2 - Methodology
+
 -   Task description and experimental design
@@
 
+---
+
 ## Project 2 - Results and Discussion
+
 -   Training variability's mixed results
@@
 -   Theoretical implications
+
+---
 
@@
 
-## General Discussion
+---
+
+# General Discussion
+
 -   Compare HTT and HTW
@@
 
+---
+
+## Comparison {.smaller}
+
+| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
+| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
+| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
+| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
+Only x velocity is relevant.
+|
+| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
+| Simpler: smooth, linear mapping between velocity and feedback.
+|
+| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
+salient differences in distance between launching box and target.
+| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
+|
+| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
+|
+| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
+| Some potential for learning during no-feedback testing by observing ball trajectory.
+|
+| Training Experience                    | Varied group gets half as much experience on any one position as the constant group.
+| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
+|
+| Testing Structure                               | Random interleaving of trained/transfer testing distances.
+| Blocked structure, separately testing trained vs extrapolation testing bands.
+|
+
+---
+
 ## Theoretical Contributions
+
 -   Insights into training variability effects on learning and generalization
@@
 
+---
+
 ## Practical Implications
+
 -   Training programs design implications
@@
 
+---
+
 ## Limitations and Future Directions
+
 -   Study limitations
@@
 
+---
+
 ## Conclusion
+
 -   Recap of key findings
@@
 
+---
+
 ## Questions and Discussion
+
 -   Open floor for questions from the committee and audience

### 2024-05-19 Presentation/slides.qmd
tweaks with icons, added iconify

@@
   - name: Thomas Gorman
-    url: www.tegorman13.github.io
+    url: https://tegorman13.github.io
     orcid: 0000-0001-5366-5442
-    affiliations: Indiana University
+    affiliations:
+      - name: Indiana University
+        department: Psychological & Brain Sciences, Cognitive Science
+        address: "55 Park Place NE, #464"
+        city: Bloomington
+        region: IN
+        country: USA
+        postal-code: 47401
 ---
 
-:::: {.content-visible when-format="html" unless-format="revealjs"}
+::::: {.content-visible when-format="html" unless-format="revealjs"}
 \
@@
 
-# Slides {visibility="hidden" .unnumbered .unlisted}
+# Slides {{< fa photo-film size=2xs >}} {.unnumbered .unlisted visibility="hidden"}
 
@@
 
-::::: column-page-inset-right
+:::: column-page-inset-right
 ::: {.ratio .ratio-16x9}
-<iframe src="/Presentation/slides_revealjs.html"></iframe>
+<iframe src="/Presentation/slides_revealjs.html">
+
+</iframe>
 :::
+::::
 :::::
-::::
 
@@
 
----
+------------------------------------------------------------------------
 
@@
 
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
 
----
+------------------------------------------------------------------------
 
@@
 | Dimension | HTT (Project 1) | HTW (Project 2) |
-| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
+|----------------|--------------------------------|------------------------|
 | Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
-| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
-Only x velocity is relevant.
-|
+| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
 | Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
@@
 |
-| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
-|
-| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
-| Some potential for learning during no-feedback testing by observing ball trajectory.
-|
+| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
+| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
 | Training Experience | Varied group gets half as much experience on any one position as the constant group.
@@
 |
-| Testing Structure                               | Random interleaving of trained/transfer testing distances.
-| Blocked structure, separately testing trained vs extrapolation testing bands.
-|
+| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
 
----
+------------------------------------------------------------------------
 

### 2024-05-22 Manuscript/manuscript.qmd
Re-add missing Procedure section; fix appendix link

@@
 The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library [@deleeuwJsPsychJavaScriptLibrary2015].
-The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
+The stimuli, presented on a black background, consisted of a circular blue ball - controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
 Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
@@
 Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
-If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, on how many units away they were from the center of the target.
+If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, specifying how many scaled units away the ball was from the center of the target.
 If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
@@
 
-[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+[Link to abbreviated example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
 
@@
 
+#### Procedure
+
+Participants first electronically consented to participate, and then read instructions for the task which explained how to control the ball, and the goal of throwing the ball as close to the center of the target as possible.
+The training phase was split into 10 blocks of 20 trials, for a total of 200 training trials.
+Participants in the constant condition trained exclusively from a single location (760 scaled units from the target center).
+Participants in the varied condition trained from two locations (610 and 910 scaled units from the target center), encountering each location 100 times.
+The sequence of throwing locations was pseudo-random for the varied group, with the constraint that within every block of 20 training throws both training locations would occur 10 times.
+Participants in both conditions also received intermittent testing trials after every 20 training trials.
+Intermittent testing trials provided no feedback of any kind.
+The ball would disappear from view as soon as it left the orange square, and participants were prompted to start the next trial without receiving any information about the accuracy of the throw.
+Each intermittent testing stage consisted of two trials from each of the three training positions (i.e.
+all participants executed two trials each from Positions 610, 760, and 910 during each of the 10 intermittent testing stages).
+Following training, all participants completed a final testing phase from four positions: 1) their training location, 2) the training location(s) of the other group, 3) a location novel to both groups.
+The testing phase consisted of 15 trials from each of the four locations, presented in a randomized order.
+All trials in the final testing phase included feedback.
+After finishing the final testing portion of the study, participants were queried as to whether they completed the study using a mouse, a trackpad,  or some other device (this information was used in the exclusion process described above).
+Finally, participants were debriefed as to the hypotheses and manipulation of the study.
+
 ### Results
@@
 
-To prepare the data, we first removed trials that were not easily interpretable as performance indicators in our task.
+To prepare the data, we removed trials that were not easily interpretable as performance indicators in our task.
 Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier.
@@
 
-[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html
+[Apppendix](https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html) available at https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html
 

### 2024-05-22 Presentation/slides.qmd
Re-add missing Procedure section; fix appendix link

@@
 format: 
-  html: 
-    toc: true
+  html: default
+    #toc: true
     #shift-heading-level-by: 1
@@
     center: true
-    chalkboard: true
-  pptx:
-    incremental: true
+    chalkboard:
+      theme: whiteboard
+  #   scrollable: true
+  # pptx:
+  #   incremental: true
+  # hugo-md:
+  #   include: false
+  #   html-math-method: mathjax
+  #   output-file: slides_hugo.md
+  gfm:
+    output: false
+    output-file: slides_gfm.md
 author:
@@
         department: Psychological & Brain Sciences, Cognitive Science
-        address: "55 Park Place NE, #464"
-        city: Bloomington
-        region: IN
-        country: USA
-        postal-code: 47401
 ---
 
-::::: {.content-visible when-format="html" unless-format="revealjs"}
+::: {.content-visible when-format="html" unless-format="revealjs"}
 \
+[Click here](../paper.qmd) to open the dissertation manuscript.\
 \
@@
 
-# Slides {{< fa photo-film size=2xs >}} {.unnumbered .unlisted visibility="hidden"}
+## Slides {{< fa photo-film size=2xs >}} {.unnumbered .unlisted visibility="hidden"}
 
@@
 
-:::: column-page-inset-right
+::: column-body-outset-right
 ::: {.ratio .ratio-16x9}
@@
 :::
-::::
-:::::
+:::
 
-# Introduction
+\
+\
+\
+\
+:::
+
+## Introduction
 
@@
 
-# Project 1 - Hit The Target (HTT)
+## Project 1 - Hit The Target (HTT)
 
@@
 
-# Project 2 - Hit The Wall (HTW)
+## Project 2 - Hit The Wall (HTW)
 
@@
 //| fig-height: 2.5
-//| fig-responsive: false
 //| echo: false  
-///| eval: !expr out_type 
-/////| column: screen-inset-right
 digraph {
   graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
   node [shape = rectangle, style = filled]
-
   data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
@@
   Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
   data1 -> Test1
   data2 -> Test1
-
   subgraph cluster {
@@
   }
-
   Test2 -> Test3
@@
 
-# General Discussion
+## General Discussion
 
@@
 
-## Comparison {.smaller}
+## Comparison {.smaller .r-fit-text}
 
 | Dimension                                | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
-|----------------|--------------------------------|------------------------|
+|------------------------------------------|-----------------------------------------------------------------------------------------------------------------------------------------------|----------------------------------------------------------------------------------------------------------------|
 | Task Description                         | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
-| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
+| Task Complexity                          | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
+Only x velocity is relevant.
+|
 | Task Space                               | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
@@
 |
-| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
-| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
+| Testing Feedback                         | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
+|
+| Potential for Learning during Testing    | Limited potential for learning during testing due to feedback.
+| Some potential for learning during no-feedback testing by observing ball trajectory.
+|
 | Training Experience                      | Varied group gets half as much experience on any one position as the constant group.
@@
 |
-| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
+| Testing Structure                        | Random interleaving of trained/transfer testing distances.
+| Blocked structure, separately testing trained vs extrapolation testing bands.
+|
 
@@
 -   Open floor for questions from the committee and audience
+
+<!-- create slide with 2 columns and add text -->
+
+## Future Research Directions {.smaller .r-fit-text}
+
+::: columns
+::: {.column width="50%"}
+### Theoretical Extensions
+
+-   Investigate the role of individual differences in training variability effects.
+-   Explore the impact of different types of feedback on learning and generalization.
+-   Examine the influence of task complexity on the benefits of varied training.
+
+### Methodological Innovations
+
+-   Develop new experimental paradigms to test training variability in more complex tasks.
+-   Utilize advanced computational models to simulate learning processes under varied conditions.
+-   Implement longitudinal studies to assess long-term effects of training variability.
+:::
+
+::: {.column width="50%"}
+### Practical Applications
+
+-   Design adaptive training programs that adjust variability based on learner performance.
+-   Apply findings to educational settings to enhance learning outcomes.
+-   Use insights to improve training protocols in professional skill development.
+
+### Collaborative Opportunities
+
+-   Partner with educational institutions to test training variability in classroom settings.
+-   Collaborate with industry professionals to apply research findings in real-world training programs.
+-   Engage with interdisciplinary teams to explore the broader implications of training variability.
+:::
+:::
+
+------------------------------------------------------------------------

### 2024-05-22 Sections/HTW.qmd
Re-add missing Procedure section; fix appendix link

@@
 date: last-modified
+author:
+- name: Thomas E. Gorman
+  affiliations: 
+   - Department of Psychological and Brain Sciences, Indiana University-Bloomington
+  affiliation-url: https://psych.indiana.edu/
+  url: https://tegorman13.github.io/
+  email: tegorman@iu.edu
+  orcid: 0000-0001-5366-5442
 page-layout: full
@@
 _______________________________________________________________________________
-[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"} \
-
-[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
+{{< fa file-lines >}} [Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \
+
+{{< fa file-pdf >}} [Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
+
+{{< fa brands github >}} [repo](https://github.com/tegorman13/htw) \
 _______________________________________________________________________________
@@
 ```{r}
+#| cache: false 
+#| 
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  data.table, stringr, here,conflicted, gt, ggh4x, patchwork, knitr)
+#options(brms.backend="cmdstanr",mc.cores=4)
+walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+
+walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
+walk(c("Display_Functions","deLosh_data","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+# source(here::here("Functions","deLosh_data.R"))
+# source(here::here("Functions","Display_Functions.R"))
+```
+
+```{r}
 #| label: fig-delosh-extrap
@@
 #| fig-width: 10
-#| cache: false 
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr)
-#options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
-walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-source(here::here("Functions","deLosh_data.R"))
-source(here::here("Functions","Display_Functions.R"))
 
@@
 
+\
 ```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
@@
 Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for the random effects.
+We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
 For each model, we report 1)  the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
@@
     theme(legend.title=element_blank()) + 
-    labs(y = "Absolute Deviation", x="Training Block") 
+    labs(y = "Deviation", x="Training Block") 
 #ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
@@
   theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Absolute Deviation From Target Band")
+  labs(x="Band", y="Deviation From Target Band")
 
@@
 //| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 8.0
-//| fig-height: 2.5
+//| fig-width: 7.0
+//| fig-height: 2.2
 //| fig-responsive: false
-//| 
+//| echo: false 
 //| 
@@
 
+:::
+
 ### Results
@@
     theme(legend.title=element_blank()) + 
-    labs(y = "Absolute Deviation", x="Training Block") 
+    labs(y = "Deviation", x="Training Block") 
 #ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
@@
 {.sm}
-
 :::
@@
 :::
+
 \ \
@@
 extrapolation), and the interaction between the two factors.
-The Intercept represents the baseline condition, (constant training,   trained bands, & original order), and the remaining coefficients reflect the deviation from that baseline.
+The Intercept represents the baseline condition, (constant training,  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
 Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
@@
   theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Absolute Deviation From Target Band")
+  labs(x="Band", y="Deviation From Target")
 
@@
   gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Target Band", x="Band Type") + 
+ condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
  facet_wrap(~bandOrder,ncol=1)
@@
 | conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:Band              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| **conditVaried:bandOrderReverse:Band** |     0.42 |          0.17 |          0.70 | 1.00 |
+| bandOrderReverse:band              |    -0.10 |         -0.27 |          0.08 | 0.86 |
+| **conditVaried:bandOrderReverse:band** |     0.42 |          0.17 |          0.70 | 1.00 |
 
@@
 #| label: fig-e3-test-vx
-#| fig-cap: Experiment 3.
-Empirical distribution of velocities produced in the testing stage.
-Translucent bands with dash lines indicate the correct range for each velocity band.
-Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2).
+#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
 #| fig-width: 11
@@
 ```
+
+{{< pagebreak >}}
 
@@
 Error bars represent 95% HDI.
-#| fig-height: 10
+#| fig-height: 11
 #| fig-width: 11
-##| eval: FALSE
 # pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
@@
 ```{r}
-####| cache: false
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-#walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-#options(brms.backend="cmdstanr",mc.cores=4)
-options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-```
-
-```{r}
-#| cache: true
+###| cache: true
 invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
@@
 e3_model <- load_e3()
+#options(contrasts = initial_contrasts)
+
 ```
@@
 
-## ALM & Exam Description
+### ALM & Exam
 
 ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus.
+The units in the input layer activate as a function of their Gaussian similarity to the input stimulus ( a_i(X) = exp(-c(X - X_i)^2) ).
 So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g.
-54 and 56; 53 and 57) may also activate to some degree.
-ALM is structured with input and output nodes that correspond to regions of the stimulus space, and response space, respectively.
+Depending on the value of the generalization parameter, the nearby units (e.g., 54 and 56; 53 and 57) may also activate to some degree.
 The units in the input layer activate as a function of their similarity to a presented stimulus.
-As was the case with the exemplar-based models, similarity in ALM is exponentially decaying function of distance.
 The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
@@
 
-#### Group level Patterns
-
 ```{r}
 #| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
+#| tbl-cap: "Models errors predicting empirical data from Experiment 1 -  aggregated over the full posterior distribution for each participant.
 Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
@@
   tab_options(
-    column_labels.font.size = 10,
+    table.font.size = 12,
     heading.title.font.size = 14,
     heading.subtitle.font.size = 12,
-    table.font.size = 11, 
-    quarto.disable_processing = TRUE
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
   )
+} else {
+
+  e1_tab %>%
+  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
+  summarize(ME = mean(mean_error), .groups = "drop") %>%
+  pivot_wider(
+    names_from = c(Model, condit),
+    values_from = ME,
+    names_sep = "_"  # Add this line to specify the separator for column names
+  ) %>%
+  rename("Fit Method" = Fit_Method) %>% kable(escape=F,booktabs=T)
+
+  }
 ```
@@
 #| label: fig-ee-e1
-#| fig-caption: conditional and marginal effects
+#| fig-cap: "A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+Varied).
+Lower values on the y axis indicate better model fit.
+D) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs.
+EXAM for the varied group; 3) ALM fits between constant and varied.
+Negative error differences indicate that the term on the left side (e.g., EXAM Constant) tended to have smaller model residuals."
 #| fig-height: 8
 #| fig-width: 10
+###| eval: false
+
+pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
+               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
+               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
 
@@
 
-p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+#p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+
+# plot_custom_effects <- function(model) {
+#   # Extract posterior samples for fixed effects
+#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
+
+#   # Calculate conditional effects
+#   post_samples <- post_samples %>%
+#     mutate(
+#       ALM_Constant = b_Intercept,
+#       EXAM_Constant = b_Intercept + b_ModelEXAM,
+#       ALM_Varied = b_Intercept + b_conditVaried,
+#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
+#     )
+
+#   # Reshape data for plotting
+#   plot_data <- post_samples %>%
+#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
+#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
+#     separate(Condition, into = c("Model", "Condit"), sep = "_")
+
+#   # Plot conditional effects
+#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
+#     geom_boxplot() +
+#     theme_minimal() +
+#     labs(x = "Model", y = "Estimate", color = "Condition")
+# }
+# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
 
@@
 
-p_ce_1 / p_em_1
-```
-
-To quantitatively assess whether the differences in performance between models,  we fit a bayesian regressions predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
+#p_ce_1 / p_em_1
+
+(p1 + p2+ p3) /p_em_1 + plot_annotation(tag_levels = c('A'), tag_suffix=".")
+
+```
+
+To quantitatively assess whether the differences in performance between models,  we fit a Bayesian regression predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
 EXAM) and training condition (Constant vs.
@@
   tab_options(
-    column_labels.font.size = 10,
+    table.font.size = 12,
     heading.title.font.size = 14,
     heading.subtitle.font.size = 12,
-    table.font.size = 10,
-    quarto.disable_processing = TRUE
+    quarto.disable_processing = TRUE,
+    column_labels.padding = 2,
+    data_row.padding = 2
   )
 gt_table
-```
+} else {
+  e23_tab %>%
+  pivot_wider(
+    names_from = c(Exp, Model, condit),
+    values_from = mean_error,
+    names_glue = "{Exp}_{Model}_{condit}"
+  ) %>%
+  arrange(Fit_Method, `Task Stage`) %>%
+  kable(escape=F,booktabs=T)
+}
+```
+
+\ \ \
 
@@
 
+{{< pagebreak >}}
+
+\scriptsize
+
 ```{r}
@@
 bct_table
-
-```
+} else {
+  bct %>%
+  mutate(
+    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
+    pd = round(pd, 2)
+  ) %>% kable(booktabs = TRUE)
+
+}
+```
+
+\normalsize
 
@@
 A more comprehensive model comparison approach might involve performing cross-validation with a held-out subset of the data [@mezzadriHoldoutStrategySelecting2022] or penalizing models based on the range of patterns they can produce [@domeGdistanceComparisonModel2023].
+
+{{< pagebreak >}}
 
@@
 
-*Experimental Results Summary*
-
 Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
+
 In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-
 Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
@@
 It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
+
+# Supplementary
+
+[Apppendix](https://tegorman13.github.io/htw/Analysis/e1_Analysis.html) available at https://tegorman13.github.io/htw/Analysis/e1_Analysis.html
+
+# References
+::: {#refs}
+:::

### 2024-05-22 Sections/IGAS.qmd
Re-add missing Procedure section; fix appendix link

@@
 
-### Task
+#### Task
 
 The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library [@deleeuwJsPsychJavaScriptLibrary2015].
-The stimuli, presented on a black background, consisted of a circular blue ball -- controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
+The stimuli, presented on a black background, consisted of a circular blue ball - controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
 Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
@@
 If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
-[Link to abbrevaited example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
+
+[Link to abbreviated example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
 
@@
 
+#### Procedure
+
+Participants first electronically consented to participate, and then read instructions for the task which explained how to control the ball, and the goal of throwing the ball as close to the center of the target as possible.
+The training phase was split into 10 blocks of 20 trials, for a total of 200 training trials.
+Participants in the constant condition trained exclusively from a single location (760 scaled units from the target center).
+Participants in the varied condition trained from two locations (610 and 910 scaled units from the target center), encountering each location 100 times.
+The sequence of throwing locations was pseudo-random for the varied group, with the constraint that within every block of 20 training throws both training locations would occur 10 times.
+Participants in both conditions also received intermittent testing trials after every 20 training trials.
+Intermittent testing trials provided no feedback of any kind.
+The ball would disappear from view as soon as it left the orange square, and participants were prompted to start the next trial without receiving any information about the accuracy of the throw.
+Each intermittent testing stage consisted of two trials from each of the three training positions (i.e.
+all participants executed two trials each from Positions 610, 760, and 910 during each of the 10 intermittent testing stages).
+Following training, all participants completed a final testing phase from four positions: 1) their training location, 2) the training location(s) of the other group, 3) a location novel to both groups.
+The testing phase consisted of 15 trials from each of the four locations, presented in a randomized order.
+All trials in the final testing phase included feedback.
+After finishing the final testing portion of the study, participants were queried as to whether they completed the study using a mouse, a trackpad,  or some other device (this information was used in the exclusion process described above).
+Finally, participants were debriefed as to the hypotheses and manipulation of the study.
+
 ## Results
@@
 
-{{< include Appendix/IGAS-Supplemental.qmd >}}
+{{< include /Sections/Appendix/IGAS-Supplemental.qmd >}}

### 2024-05-22 Sections/full.qmd
Re-add missing Procedure section; fix appendix link

@@
   affiliation: Indiana University
+  affiliation-url: https://psych.indiana.edu/
+  url: https://tegorman13.github.io/
+  orcid: 0000-0001-5366-5442
 page-layout: full
@@
 
-{{< include pre_sections/toc_pdf.qmd >}}
+{{< include /Sections/pre_sections/toc_pdf.qmd >}}
 
@@
 options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
+#defaultContrasts = options()$contrasts
 
@@
 
-[Apppendix](Appendix/Full_Appendix.qmd) available at tegorman13.github.io/Dissertation/Sections/Appendix.html
+[Apppendix](https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html) available at https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html
 
 # References
+::: {#refs}
+:::

### 2024-05-23 Presentation/_fig_creation.qmd
updates to slides

```{r}
pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,here)
walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))

# Function to simulate exponential learning data
sim_exp <- function(N, alpha, beta, r, t0 = 0, sdlog = .1) {
  t0 + (alpha + (beta-alpha) * exp(-r * N)) + rlnorm(length(N), 0, sdlog)
}

# Parameters for simulation
N <- 1:50  # Number of trials
alpha <- 5  # Initial performance level
beta <- 15  # improvement

# Parameters for two groups
r_fast <- 0.1  # Faster learning rate
r_slow <- 0.05  # Slower learning rate

# Simulate data for two groups
set.seed(123)  # For reproducibility
data_fast <- sim_exp(N, alpha-3, beta, r_fast)
data_slow <- sim_exp(N, alpha, beta, r_slow)

# Combine data into a single dataframe
data <- data.frame(
  Trial = rep(N, 2),
  Performance = c(data_fast, data_slow),
  Group = factor(rep(c("Low Variability", "High Variability"), each = length(N)), levels=c("Low Variability", "High Variability"))
)

# Plot the data using ggplot2
tr_p <- ggplot(data, aes(x = Trial, y = Performance, color = Group)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Learning Curves for Low and High Variability Training",
    x = "Training Trial",
    y = "Error",
    color = "Group"
  ) + ylim(0,20) +  theme(
    #panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

# ggsave(here::here("Presentation/assets/train_pattern.png"), tr_p)
```

```{r}

# Simulate testing data for two groups
set.seed(123)  # For reproducibility
test_data_fast <- rnorm(length(N), mean = 5, sd = 1)
test_data_slow <- rnorm(length(N), mean = 2.5, sd = 1)

# Combine testing data into a single dataframe
test_data <- data.frame(
  Trial = rep(N, 2),
  Performance = c(test_data_fast, test_data_slow),
  Group = factor(rep(c("Low Variability", "High Variability"), each = length(N)), levels=c("Low Variability", "High Variability"))
)

# Plot the testing data using ggplot2
test_p <- ggplot(test_data, aes(x = Group, y = Performance, fill = Group)) +
  stat_summary(fun = mean, geom = "bar", position = "dodge", width = 0.7) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(0.7), width = 0.25) +
  labs(
    title = "Testing Performance for Low and High Variability Training",
    x = "Group",
    y = "Error",
    fill = "Group"
  ) + ylim(0, 10) + theme(
    panel.grid.minor = element_blank()
  )

# ggsave(here::here("Presentation/assets/test_pattern.png"), test_p)
```

### 2024-05-23 Presentation/slides.qmd
updates to slides

@@
     slideNumber: true
+    hash-type: number # Use slide numbers in the URL hash
     center: true
+    scrollable: true
     chalkboard:
       theme: whiteboard
-  #   scrollable: true
-  # pptx:
-  #   incremental: true
+  pptx:
+    incremental: true
   # hugo-md:
@@
         department: Psychological & Brain Sciences, Cognitive Science
+params:
+  start_slide: 0
+#engine: knitr
 ---
 
-::: {.content-visible when-format="html" unless-format="revealjs"}
+::::: {.content-visible when-format="html" unless-format="revealjs"}
 \
@@
 \
-\
-\
-\
-\
-\
+
 \
@@
 
+```{=html}
 <p class="buttons" style="text-align:center;">
+<a class="btn btn-danger" target="_blank" href="/Presentation/slides_revealjs.html#{{< meta params.start_slide >}}"><i class="fa-solid fa-arrow-up-right-from-square"></i> Open slides in new window </a>
+</p>
+```
 
-<a class="btn btn-danger" target="_blank" href="/Presentation/slides_revealjs.html"><i class="fa-solid fa-arrow-up-right-from-square"></i> Open slides in new window </a>
-
-</p>
-
-::: column-body-outset-right
-::: {.ratio .ratio-16x9}
-<iframe src="/Presentation/slides_revealjs.html">
-
+:::: column-body-outset-right
+::: {.ratio .ratio-4x3}
+```{=html}
+<iframe src="/Presentation/slides_revealjs.html#{{< meta params.start_slide >}}">
 </iframe>
+```
 :::
-:::
+::::
 
@@
 \
-\
-:::
+:::::
 
@@
 
+## Common Empirical Patterns
+
+:::::::::  columns
+::: {.column width="60%"}
+### Training
+- Both training conditions complete the same number of training trials.
+- Varied group has worse training performance.
+
+![](assets/train_pattern.png)
+:::
+
+::: {.column width="40%"} 
+::: {.fragment}
+### Testing
+
+- Tested from novel conditions.
+- Varied group has better test performance
+
+![](assets/test_pattern.png)
+:::
+:::
+:::::::::
+
+------------------------------------------------------------------------
+
+## But also plenty of contradictory results and complications
+
+- Cases where varied training makes no difference
+- Cases where more training variation results in worse outcomes
+- Cases where the influence of variation interacts with some other factor
+    - difficulty
+    - prior knowledge
+    - Frequency effects, or amount of training/learning before testing
+
+------------------------------------------------------------------------
+
 ## Theoretical Frameworks
@@
 
-![](assets/fig-toy-model1-1-1.png)
+<!-- ![](assets/fig-toy-model1-1-1.png) -->
 
@@
 
-## Project 1 - Methodology
+## Project 1 - Task & Procedure
 
--   Task description and experimental design
--   Participants and procedures
--   IGAS model introduction
+:::: {.columns}
+::: {.column width="50%"}
+![](assets/methodsFig1.png)
+:::
 
-![](assets/methodsFig1.png)
+::: {.column width="50%"}
+- **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
+- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
+- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
+:::
+
+::::
 
@@
 
-## Project 1 - Results and Discussion
+## Project 1 - Manipulations
+
+:::: {.columns}
+::: {.column width="50%"}
+
+### Experiment 1
+- Train a varied group from 2 positions, and a constant group from 1. Then test both groups, from the training positions and a novel position.
+
+:::
+
+::: {.column width="50%"}
+### Experiment 2
+- 6 constant conditions, each trained from a unique location, and a varied condition trained from 2 locations
+:::
+
+::::
+
+------------------------------------------------------------------------
+
+## Project 1 - Results
+
+:::: {.columns}
+::: {.column width="40%"}
+### Experiment 1
+![](assets/fig-IGAS_Testing1-1-2.png)
+:::
+::: {.column width="60%"}
+### Experiment 2
+![](assets/fig-e2testa-1-2.png)
+:::
+::::
+
+------------------------------------------------------------------------
+
+## Project 1 - Discussion
 
@@
 
-## Computational Model
+## Project 1 Computational Model {.smaller .r-fit-text}
 
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
+### Model of Similarity between training and solutions
 
-**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+![](assets/fig-taskSpace-1-1.png)
 
@@
 
-## Project 2 - Hit The Wall (HTW)
+## Project 1 Computational Model {.smaller .r-fit-text}
+
+ - For each subject, compute similarity between training throws and each of the 6 testing locations
+ - Test whether similarity explains the difference in performance between Constant and Varied conditions
+   - Assuming equivalent generalization (1 c for both groups) - similarity improves model fit, but does not explain group difference
+   - Assume training condition influences generalization gradient (fit c separately) - now similarity does explain the difference between Constant and Varied.
+
+::: footer
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
+**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+:::
+
+## Project 1 General Discussion {.smaller .r-fit-text}
+
+------------------------------------------------------------------------
+
+## Project 2 - Variability and Extrapolation in a Function Learning Task
 
@@
 
+## Project 2 - Questions and Goals
+
+**Empirical**
+- Design a task-space large enough to assess multiple degrees of extrapolation 
+- Compare varied and constant generalization from several distinct distances from their nearest training condition
+
+**Model-based**
+- If variation does influence extrapolation, can a connectionist model with similarity-based activation provide a good account?
+- Can our modelling framework simultaneously account for both training and testing data?
+- Accounting for the full distribution of responses
+
 ## Project 2 - Methodology
 
--   Task description and experimental design
--   Participants and procedures
--   Application of ALM and EXAM models
+-   A total of 156 participants from IU's online subject pool
+-   Varied group trains from 3 "velocity bands", constant group from 1
+
+![](assets/htw_task_fig.png)
+
+## Project 2 - Methodology
 
@@
 
-## Project 2 - Results and Discussion
+## Project 2 - Experiment 1 Results
 
--   Training variability's mixed results
--   Modeling analysis with ALM and EXAM
--   Theoretical implications
+![](assets/fig-e1-train-dev-1-1.png)
+
+## Project 2 - Experiment 1 Results
+
+![](assets/fig-e1-test-dev-1-3.png)
+
+## Project 2 - Experiment 2 Design
+
+![](assets/e2_design.png)
+
+## Project 2 - Experiment 2 Results
+
+![](assets/fig-e2-train-dev-1-1.png)
+
+## Project 2 - Experiment 2 Results
+
+![](assets/fig-e2-test-dev-1-3.png)
+
+## Project 2 - Experiment 2 Results
+
+![](assets/fig-e2-bmm-vx-1-2.png)
+
+## Project 2 - Experiment 3 Design
+
+- Ordinal feedback
+- Include both the original order (E1) and reverse order (E2)
+
+## Project 3 - Experiment 3 Results
+
+![](assets/fig-e3-train-dev-1-1.png)
+
+## Project 3 - Experiment 3 Results
+
+![](assets/fig-e3-test-dev-1-3.png)
+
+## Project 3 - Experiment 3 Results
+
+![](assets/fig-e3-bmm-vx-1-2.png)
 
@@
 ------------------------------------------------------------------------
+
+## ALM
+
+|                    | **ALM Response Generation**                                        |                                                                                               |
+|------------------|-----------------------------|-------------------------|
+| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
+| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
+| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
+| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
+|                    | **ALM Learning**                                                   |                                                                                               |
+| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
+| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
+| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
+
+------------------------------------------------------------------------
+
+## EXAM
+
+|                    | **EXAM Response Generation**                                                                                     |                                                                                                               |
+|--------------------|-----------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------|
+| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                                                 | Novel test stimulus $X$ activates input nodes $X_i$                                                           |
+| Slope Computation  | $S = \frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                                                                     | Slope value, $S$ computed from nearest training instances                                                     |
+| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                                                                         | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$, adjusted by local slope $S$.
+|
+
+------------------------------------------------------------------------
+
+## Project 2 - Model Fitting Procedure
+
+### Approximate Bayesian Computation
+
+## Modelling Results
+
+![](assets/fig-ee-e1-1.png)
 
@@
 | Dimension | HTT (Project 1) | HTW (Project 2) |
-|------------------------------------------|-----------------------------------------------------------------------------------------------------------------------------------------------|----------------------------------------------------------------------------------------------------------------|
+|----------------|--------------------------------|-------------------------|
 | Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
-| Task Complexity                          | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
-Only x velocity is relevant.
-|
+| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
 | Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
@@
 |
-| Testing Feedback                         | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
-|
-| Potential for Learning during Testing    | Limited potential for learning during testing due to feedback.
-| Some potential for learning during no-feedback testing by observing ball trajectory.
-|
+| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
+| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
 | Training Experience | Varied group gets half as much experience on any one position as the constant group.
@@
 |
-| Testing Structure                        | Random interleaving of trained/transfer testing distances.
-| Blocked structure, separately testing trained vs extrapolation testing bands.
-|
+| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
 
@@
 
-::: columns
-::: {.column width="50%"}
+::::::::: columns
+::::: {.column width="50%"}
+::: fragment
 ### Theoretical Extensions
@@
 -   Examine the influence of task complexity on the benefits of varied training.
+:::
 
+::: fragment
 ### Methodological Innovations
@@
 :::
+:::::
 
-::: {.column width="50%"}
+::::: {.column width="50%"}
+::: fragment
 ### Practical Applications
@@
 -   Use insights to improve training protocols in professional skill development.
+:::
 
+::: fragment
 ### Collaborative Opportunities
@@
 :::
-:::
+:::::
+:::::::::
 

### 2024-05-26 Presentation/slides.qmd
add task vids to slides

@@
     incremental: true
-  # hugo-md:
-  #   include: false
-  #   html-math-method: mathjax
-  #   output-file: slides_hugo.md
+  hugo-md:
+    include: false
+    html-math-method: mathjax
+    output-file: slides_hugo.md
   gfm:
@@
 :::: {.columns}
-::: {.column width="50%"}
+::: {.column width="60%"}
+<!-- ![](assets/methodsFig1.png) -->
+
+::: {.content-visible when-format="html"}
+![](assets/htt_vid.mov){height="540" loop="true" autoplay="true"}
+:::
+
+::: {.content-visible unless-format="html"}
 ![](assets/methodsFig1.png)
@@
 
-::: {.column width="50%"}
+:::
+
+::: {.column width="40%"}
 - **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
@@
 - Accounting for the full distribution of responses
+
+------------------------------------------------------------------------
+
+## Task
+
+<!-- {{< video assets/htw_vid.mov width="720" height="540" >}} -->
+
+::: {.content-visible when-format="html"}
+![](assets/htw_vid.mov){height="540" loop="true" autoplay="true"}
+:::
+
+::: {.content-visible unless-format="html"}
+![](assets/htw_task_fig.png)
+:::
+
+------------------------------------------------------------------------
 
@@
 
-<!-- create slide with 2 columns and add text -->
-
 ## Future Research Directions {.smaller .r-fit-text}

### 2024-05-26 Presentation/slides.qmd
slide updates

@@
 subtitle: "Dissertation Defense"
+page-layout: full
+aliases:
+  - /slides.html
 format: 
@@
       theme: whiteboard
-  pptx:
-    incremental: true
-  hugo-md:
-    include: false
-    html-math-method: mathjax
-    output-file: slides_hugo.md
-  gfm:
-    output: false
-    output-file: slides_gfm.md
+  # pptx:
+  #   incremental: false
+  # hugo-md:
+  #   include: false
+  #   html-math-method: mathjax
+  #   output-file: slides_hugo.md
+  # gfm:
+  #   output: false
+  #   output-file: slides_gfm.md
 author:
@@
 \
-
 \
@@
 
-## Introduction
+# Introduction
 
@@
 
-## Project 1 - Hit The Target (HTT)
+# Project 1
 
@@
 
-## Project 1 - Task & Procedure
+## Hit The Target Task
 
-:::: {.columns}
-::: {.column width="60%"}
-<!-- ![](assets/methodsFig1.png) -->
+:::::: column-page-right
+::::: {.columns}
+:::: {.column width="60%"}
 
@@
 
-:::
+::::
 
-::: {.column width="40%"}
+:::: {.column width="40%"}
 - **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
@@
 - **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
-:::
+::::
 
-::::
+:::::
+::::::
 
@@
 
-## Project 2 - Variability and Extrapolation in a Function Learning Task
+# Project 2 - Variability and Extrapolation in a Function Learning Task
 
@@
 
-## Task
+## Hit The Wall Task
 
@@
 
-## Project 2 - ALM
+# Project 2 - ALM
 

### 2024-05-26 Presentation/slides.qmd
some slide tweaks

@@
 title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
-subtitle: "Dissertation Defense"
 page-layout: full
@@
   - /slides.html
+css: /Assets/Style/slides.css
 format: 
-  html: default
+  html: 
+    subtitle: "Dissertation Defense"
     #toc: true
@@
     #output-ext: revealjs.html
+    # template-partials:
+    #   - assets/title-slide.html
     output-file: slides_revealjs
+    date: 05/28/204
     slideNumber: true
@@
 ::: {.content-visible when-format="html"}
-![](assets/htt_vid.mov){height="540" loop="true" autoplay="true"}
+![](assets/htt_vid.mov){height="540" loop="true" autoplay="true" style="max-width: 100%"}
 :::
@@
 ::: {.content-visible when-format="html"}
-![](assets/htw_vid.mov){height="540" loop="true" autoplay="true"}
+![](assets/htw_vid.mov){height="400" loop="true" autoplay="true"}
 :::
+-   A total of 156 participants from IU's online subject pool
+-   Varied group trains from 3 "velocity bands", constant group from 1
 

### 2024-05-27 Presentation/_fig_creation.qmd
slide updates

@@
+# HTW Results
+
+```{r}
+
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  data.table, stringr, here,conflicted, gt, ggh4x, patchwork, knitr)
+#options(brms.backend="cmdstanr",mc.cores=4)
+walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
+options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+
+walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
+walk(c("Display_Functions","deLosh_data","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+
+e1 <- readRDS(here("data/e1_08-21-23.rds")) 
+e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
+testE1 <- e1 |> filter(expMode2 == "Test")
+nbins=5
+trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
+    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
+trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
+trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
+
+condEffects <- function(m,xvar){
+  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() + 
+  stat_halfeye(alpha=.1, height=.5) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
+
+}
+```
+
+## HTW E1
+
+```{r}
+#| label: fig-e1-test-dev
+#| fig-cap: Experiment 1 Testing Accuracy.
+A) Empricial Deviations from target band during testing without feedback stage.
+B) Conditional effect of condition (Constant vs.
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
+Error bars represent 95% credible intervals.
+#| fig-width: 4
+#| fig-height: 4
+
+# pe1td <- testE1 |>  
+#   ggplot(aes(x = vb, y = dist,fill=condit)) +
+#     stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
+#     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
+#   theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
+#   labs(x="Band", y="Deviation From Target Band")
+
+pe1td <- testE1 |> ggplot(aes(x = vb, y = dist,fill=condit,
+                               col=ifelse(bandType=="Trained","black","lightgray"),
+                               size=ifelse(bandType=="Trained",1.0,.5))) +
+  stat_bar + 
+  theme(legend.title.position="top",
+        legend.title = element_text(face = "bold"),
+        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
+  labs(x="Band", y="Deviation", fill="Condition") +
+     # scale_color_manual(values = c("black" = "black"), guide = "legend") +
+  scale_color_manual(values=c("black","lightgray"), 
+                     name= "Band Type",
+                     labels = c("Trained","Extrapolation"),
+                     guide = guide_legend(override.aes = list(fill = NA))
+                     ) +
+  scale_size_continuous(range = c(0.8, 1.0), guide="none")
+
+bmtd <- readRDS(paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2.rds"))
+pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
+  gather_emmeans_draws() |>
+ condEffects(bandType) + labs(y="Deviation", x="Band Type")
+
+#p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
+#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
+#p2
+
+e1_vxBMM <- readRDS(paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k.rds")))
+pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
+                     at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+gather_emmeans_draws() |> 
+condEffects(bandInt) +
+stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+  geom_abline(slope = 1, intercept = 200, linetype = "dashed", color = "gray", size = .5,alpha=.5) +
+scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                   labels = levels(testE1$vb), 
+                   limits = c(100, 1200)) + 
+scale_y_continuous(expand=expansion(add=100),breaks=round(seq(400,1400,by=200),2)) +
+theme(legend.position="none") + 
+  #theme(legend.title=element_blank(),legend.position="right") + 
+labs(y="Velcoity", x="Band")
+
+fe <- fixef(e1_vxBMM)[,1]
+fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
+fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
+
+re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
+  rownames_to_column("id") |> 
+  left_join(e1Sbjs,by="id") |>
+  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
+
+pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
+  geom_density(alpha=.5) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
+   theme(legend.title=element_blank()) + 
+  labs(x="Slope Coefficient",y="Density")
+
+pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
+  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
+    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+     theme(legend.title=element_blank(), 
+           axis.text.y = element_text(size=6) ) + 
+    labs(x="Estimated Slope", y="Participant")  + 
+    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
+
+pe1td
+pe1ce
+
+pe1vce
+pid_den1
+pid_slopes1
+
+ggsave(here::here("Presentation/assets/htw_e1_test1.png"), pe1td, width = 4.0, height = 3, units = "in", dpi = 300)
+ggsave(here::here("Presentation/assets/htw_e1_test2.png"), pe1ce, width = 4.0, height = 3, units = "in", dpi = 300)
+ggsave(here::here("Presentation/assets/htw_e1_test3.png"), pe1vce, width = 4.0, height = 3, units = "in", dpi = 300)
+ggsave(here::here("Presentation/assets/htw_e1_test4.png"), pid_den1, width = 4.0, height = 3, units = "in", dpi = 300)
+ggsave(here::here("Presentation/assets/htw_e1_test5.png"), pid_slopes1, width = 4.0, height = 3, units = "in", dpi = 300)
+```
+
+## HTW Experiment 2
+
+```{r}
+#| label: fig-e2-test-dev
+#| fig-cap: Experiment 2 Testing Accuracy.
+A) Empricial Deviations from target band during testing without feedback stage.
+B) Conditional effect of condition (Constant vs.
+Varied) and testing band type (trained bands vs.
+novel extrapolation bands) on testing accuracy.
+Error bars represent 95% credible intervals.
+#| fig-width: 5
+#| fig-height: 5
+e2 <- readRDS(here("data/e2_08-04-23.rds")) 
+e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
+testE2 <- e2 |> filter(expMode2 == "Test")
+nbins=5
+trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
+    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
+trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
+
+bmtd2 <- readRDS(paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2.rds"))
+
+condEffects <- function(m,xvar){
+  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
+  stat_dist_pointinterval() + 
+  stat_halfeye(alpha=.1, height=.5) +
+  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
+
+}
+
+pe2td <- testE2 |> ggplot(aes(x = vb, y = dist,fill=condit,
+                               col=ifelse(bandType=="Trained","black","lightgray"),
+                               size=ifelse(bandType=="Trained",1.0,.5))) +
+  stat_bar + 
+  theme(legend.title.position="top",
+        legend.title = element_text(face = "bold"),
+        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
+  labs(x="Band", y="Deviation", fill="Condition") +
+  scale_color_manual(values=c("black","lightgray"), 
+                     name= "Band Type",
+                     labels = c("Trained","Extrapolation"),
+                     guide = guide_legend(override.aes = list(fill = NA))
+                     ) +
+  scale_size_continuous(range = c(0.8, 1.0), guide="none")
+
+pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
+  gather_emmeans_draws() |>
+ condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
+
+e2_vxBMM <- readRDS(paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k.rds")))
+
+pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |> 
+  condEffects(bandInt) +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+  geom_abline(slope = 1, intercept = 200, linetype = "dashed", color = "gray", size = .5,alpha=.5) +
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE2$vb), 
+                     limits = c(100, 1200)) + 
+scale_y_continuous(expand=expansion(add=100),breaks=round(seq(200,1400,by=200),2)) +
+  theme(legend.title=element_blank()) + 
+  labs(y="Velcoity", x="Band")
+
+fe <- fixef(e2_vxBMM)[,1]
+fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
+fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
+
+re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
+  rownames_to_column("id") |> 
+  left_join(e2Sbjs,by="id") |>
+  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
+
+pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
+  geom_density(alpha=.5) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
+   theme(legend.title=element_blank()) + 
+  labs(x="Slope Coefficient",y="Density")
+
+pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
+  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
+    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+      theme(legend.title=element_blank(), 
+        axis.text.y = element_text(size=6) ) + 
+    labs(x="Estimated Slope", y="Participant")  + 
+    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
+
+pe2td
+pe2ce
+pe2vce
+pid_den2
+pid_slopes2
+
+ggsave(here::here("Presentation/assets/htw_e2_test1.png"), pe2td, width = 4.0, height = 3, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e2_test2.png"), pe2ce, width = 4.0, height = 3, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e2_test3.png"), pe2vce, width = 4.0, height = 3, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e2_test4.png"), pid_den2, width = 4.0, height = 3, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e2_test5.png"), pid_slopes2, width = 4.0, height = 3, units = "in", dpi = 600)
+
+```
+
+## HTW Exp 3
+
+```{r}
+#| fig-width: 4
+#| fig-height: 6
+e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
+    mutate(trainCon=case_when(
+    bandOrder=="Original" ~ "800",
+    bandOrder=="Reverse" ~ "600",
+    TRUE ~ NA_character_
+    ), trainCon=as.numeric(trainCon)) 
+e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
+testE3 <- e3 |> filter(expMode2 == "Test")
+nbins=5
+trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
+    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
+trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
+
+bmtd3 <- readRDS(paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2.rds"))
+
+pe3td <- testE3 |> ggplot(aes(x = vb, y = dist,fill=condit,
+                               col=ifelse(bandType=="Trained","black","lightgray"),
+                               size=ifelse(bandType=="Trained",1.0,.5))) +
+  stat_bar + 
+  facet_wrap(~bandOrder,ncol=1) +
+  theme(legend.title.position="top",
+        legend.title = element_text(face = "bold"),
+        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
+  labs(x="Band", y="Deviation", fill="Condition") +
+  scale_color_manual(values=c("black","lightgray"), 
+                     name= "Band Type",
+                     labels = c("Trained","Extrapolation"),
+                     guide = guide_legend(override.aes = list(fill = NA))
+                     ) +
+  scale_size_continuous(range = c(0.8, 1.0), guide="none")
+
+pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
+  gather_emmeans_draws() |>
+ condEffects(bandType) + labs(y="Deviation", x="Band Type") + 
+ facet_wrap(~bandOrder,ncol=1)
+
+e3_vxBMM <- readRDS(paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k.rds")))
+
+pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
+                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
+  gather_emmeans_draws() |> 
+  condEffects(bandInt) +
+  facet_wrap(~bandOrder,ncol=1) +
+  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
+  geom_abline(slope = 1, intercept = 200, linetype = "dashed", color = "gray", size = .5,alpha=.5) +
+  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
+                     labels = levels(testE3$vb), 
+                     limits = c(100, 1200)) + 
+scale_y_continuous(expand=expansion(add=100),breaks=round(seq(300,1400,by=200),2)) +
+  theme(legend.title=element_blank()) + 
+  labs(y="Velcoity", x="Band")
+
+fe <- fixef(e3_vxBMM)[,1]
+fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
+fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
+fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
+fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
+
+re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
+  rownames_to_column("id") |> 
+  left_join(e3Sbjs,by="id") |>
+  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
+           fixed_effect_interaction2*(bandOrder=="Reverse") + 
+           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
+  slope = Estimate + adjust )
+
+pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
+  geom_density(alpha=.5) + 
+  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
+  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+   theme(legend.title=element_blank()) + 
+  labs(x="Slope Coefficient",y="Density") +
+  facet_wrap(~bandOrder,ncol=1)
+
+pid_slopes3 <- re |>  
+    mutate(id=reorder(id,slope)) |>
+  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
+    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
+    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
+    theme(legend.title=element_blank(), 
+      axis.text.y = element_text(size=6) ) + 
+    labs(x="Estimated Slope", y="Participant")  + 
+    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
+
+pe3td
+pe3ce
+pe3vce
+pid_den3
+pid_slopes3
+
+ggsave(here::here("Presentation/assets/htw_e3_test1.png"), pe3td, width = 4.0, height = 6, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e3_test2.png"), pe3ce, width = 4.0, height = 6, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e3_test3.png"), pe3vce, width = 4.0, height = 6, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e3_test4.png"), pid_den3, width = 4.0, height = 6, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/htw_e3_test5.png"), pid_slopes3, width = 4.0, height = 6, units = "in", dpi = 600)
+
+```
+
+# Sim Example
+
 ```{r}
@@
 ```
+
+# IGAS Task Space
+
+```{r}
+#| label: fig-taskSpace
+#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
+This empirical solution space was compiled from all of the participants in experiment 2.
+B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
+#| fig-width: 11
+#| fig-height: 9
+
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,here, RColorBrewer, patchwork)
+walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+
+taskspace <- e2 %>% filter(AbsDistFromCenter<900)
+taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
+
+solSpace <- e2 %>% filter(trialType==11)
+#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
+
+solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
+solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
+solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
+solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
+
+missSpace <- e2 %>% filter(trialType !=11, abs(X_Velocity)<1000)
+missSpace$Result = "Missed Target"
+solSpace$Result <- solSpace$Result
+
+# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
+# multiplied velocoties by -1 to make the axes less confusing
+ss= solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
+  geom_point(aes(colour=Result),alpha=0.6) + 
+  scale_color_manual(values =brewer.pal(n=6,name="Set1")) +
+  labs(color="Throw position:", 
+  # title="Empirical Solution Space - Testing Positions",
+  # subtitle="The XY velocity coordinates of all the successful throws", 
+  x="X Release Velocity", 
+  y="Y Release Velocity", )  
+  theme(legend.position="top")
+
+fullSpace <- rbind(missSpace,solSpace)
+
+fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
+  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
+  labs(color=element_blank(),
+  # title="Full Space of Solution Throws and Missed Throws",
+  # subtitle="Colored points represent coordinates of target hits, brown points are coordinates of misses",
+  x="X Release Velocity", 
+  y="Y Release Velocity") + 
+  theme(legend.title = element_blank(), legend.position="top")
+
+ggsave(here::here("Presentation/assets/sol_space.png"),ss)
+ggsave(here::here("Presentation/assets/full_space.png"),fs)
+
+```

### 2024-05-27 Presentation/embed_slides.qmd
slide updates

--- 2024-05-26 Presentation/slides.qmd
@@
----
-title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
-subtitle: "Dissertation Defense"
-format: 
-  html: default
-    #toc: true
-    #shift-heading-level-by: 1
-    #toc-expand: true
-  clean-revealjs:
-    #theme: moon #white
-    #output-ext: revealjs.html
-    output-file: slides_revealjs
-    slideNumber: true
-    hash-type: number # Use slide numbers in the URL hash
-    center: true
-    scrollable: true
-    chalkboard:
-      theme: whiteboard
-  pptx:
-    incremental: true
-  hugo-md:
-    include: false
-    html-math-method: mathjax
-    output-file: slides_hugo.md
-  gfm:
-    output: false
-    output-file: slides_gfm.md
-author:
-  - name: Thomas Gorman
-    url: https://tegorman13.github.io
-    orcid: 0000-0001-5366-5442
-    affiliations:
-      - name: Indiana University
-        department: Psychological & Brain Sciences, Cognitive Science
-params:
-  start_slide: 0
-#engine: knitr
----
-
 ::::: {.content-visible when-format="html" unless-format="revealjs"}
 \
-[Click here](../paper.qmd) to open the dissertation manuscript.\
-\
-\
-\
+[{{< fa file-lines >}} Click here](../paper.qmd) to open the dissertation manuscript.\
 
-\
+<br><br><br><br><br><br>
 
-## Slides {{< fa photo-film size=2xs >}} {.unnumbered .unlisted visibility="hidden"}
+## Slides {{< fa person-chalkboard size=1.0xs >}} {.unnumbered .unlisted visibility="hidden"}
 
@@
 
-\
-\
-\
+<br><br><br><br><br><br>
+
 :::::
-
-## Introduction
-
--   Investigate effects of training variability on learning and generalization
--   Focus areas: visuomotor skill learning and function learning tasks
-
-------------------------------------------------------------------------
-
-## Background and Motivation
-
--   Importance of training variability
--   Research gaps in visuomotor skill learning
--   Previous research in category learning, language learning, and function learning
-
-------------------------------------------------------------------------
-
-## Common Empirical Patterns
-
-:::::::::  columns
-::: {.column width="60%"}
-### Training
-- Both training conditions complete the same number of training trials.
-- Varied group has worse training performance.
-
-![](assets/train_pattern.png)
-:::
-
-::: {.column width="40%"} 
-::: {.fragment}
-### Testing
-
-- Tested from novel conditions.
-- Varied group has better test performance
-
-![](assets/test_pattern.png)
-:::
-:::
-:::::::::
-
-------------------------------------------------------------------------
-
-## But also plenty of contradictory results and complications
-
-- Cases where varied training makes no difference
-- Cases where more training variation results in worse outcomes
-- Cases where the influence of variation interacts with some other factor
-    - difficulty
-    - prior knowledge
-    - Frequency effects, or amount of training/learning before testing
-
-------------------------------------------------------------------------
-
-## Theoretical Frameworks
-
--   Schema Theory (Schmidt, 1975)
--   Desirable Difficulties Framework (Bjork & Bjork, 2011)
--   Challenge Point Framework (Guadagnoli & Lee, 2004)
-
-<!-- ![](assets/fig-toy-model1-1-1.png) -->
-
-------------------------------------------------------------------------
-
-## Overview of Current Work
-
--   Project 1: Visuomotor projectile launching task
--   Project 2: Visuomotor extrapolation task
-
-------------------------------------------------------------------------
-
-## Project 1 - Hit The Target (HTT)
-
--   Influence of varied practice in a projectile launching task
--   Experiments 1 & 2:
-    -   Constant vs. varied training groups
-    -   Performance metrics and transfer testing
-
-------------------------------------------------------------------------
-
-## Project 1 - Task & Procedure
-
-:::: {.columns}
-::: {.column width="60%"}
-<!-- ![](assets/methodsFig1.png) -->
-
-::: {.content-visible when-format="html"}
-![](assets/htt_vid.mov){height="540" loop="true" autoplay="true"}
-:::
-
-::: {.content-visible unless-format="html"}
-![](assets/methodsFig1.png)
-:::
-
-:::
-
-::: {.column width="40%"}
-- **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
-- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
-- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
-:::
-
-::::
-
-------------------------------------------------------------------------
-
-## Project 1 - Manipulations
-
-:::: {.columns}
-::: {.column width="50%"}
-
-### Experiment 1
-- Train a varied group from 2 positions, and a constant group from 1. Then test both groups, from the training positions and a novel position.
-
-:::
-
-::: {.column width="50%"}
-### Experiment 2
-- 6 constant conditions, each trained from a unique location, and a varied condition trained from 2 locations
-:::
-
-::::
-
-------------------------------------------------------------------------
-
-## Project 1 - Results
-
-:::: {.columns}
-::: {.column width="40%"}
-### Experiment 1
-![](assets/fig-IGAS_Testing1-1-2.png)
-:::
-::: {.column width="60%"}
-### Experiment 2
-![](assets/fig-e2testa-1-2.png)
-:::
-::::
-
-------------------------------------------------------------------------
-
-## Project 1 - Discussion
-
--   Varied training group's superior performance
--   Computational modeling results with IGAS
--   Theoretical implications
-
-------------------------------------------------------------------------
-
-## Project 1 Computational Model {.smaller .r-fit-text}
-
-### Model of Similarity between training and solutions
-
-![](assets/fig-taskSpace-1-1.png)
-
-------------------------------------------------------------------------
-
-## Project 1 Computational Model {.smaller .r-fit-text}
-
- - For each subject, compute similarity between training throws and each of the 6 testing locations
- - Test whether similarity explains the difference in performance between Constant and Varied conditions
-   - Assuming equivalent generalization (1 c for both groups) - similarity improves model fit, but does not explain group difference
-   - Assume training condition influences generalization gradient (fit c separately) - now similarity does explain the difference between Constant and Varied.
-
-::: footer
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
-**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-:::
-
-## Project 1 General Discussion {.smaller .r-fit-text}
-
-------------------------------------------------------------------------
-
-## Project 2 - Variability and Extrapolation in a Function Learning Task
-
--   Influence of varied practice in a function learning task
--   Experiments 1, 2, and 3:
-    -   Training regimes and testing conditions
-    -   Learning, discrimination, and extrapolation performance metrics
-
-------------------------------------------------------------------------
-
-## Project 2 - Questions and Goals
-
-**Empirical**
-- Design a task-space large enough to assess multiple degrees of extrapolation 
-- Compare varied and constant generalization from several distinct distances from their nearest training condition
-
-**Model-based**
-- If variation does influence extrapolation, can a connectionist model with similarity-based activation provide a good account?
-- Can our modelling framework simultaneously account for both training and testing data?
-- Accounting for the full distribution of responses
-
-------------------------------------------------------------------------
-
-## Task
-
-<!-- {{< video assets/htw_vid.mov width="720" height="540" >}} -->
-
-::: {.content-visible when-format="html"}
-![](assets/htw_vid.mov){height="540" loop="true" autoplay="true"}
-:::
-
-::: {.content-visible unless-format="html"}
-![](assets/htw_task_fig.png)
-:::
-
-------------------------------------------------------------------------
-
-## Project 2 - Methodology
-
--   A total of 156 participants from IU's online subject pool
--   Varied group trains from 3 "velocity bands", constant group from 1
-
-![](assets/htw_task_fig.png)
-
-## Project 2 - Methodology
-
-::: {.content-visible unless-format="markdown"}
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
-//| echo: false  
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
-:::
-
-------------------------------------------------------------------------
-
-## Project 2 - Experiment 1 Results
-
-![](assets/fig-e1-train-dev-1-1.png)
-
-## Project 2 - Experiment 1 Results
-
-![](assets/fig-e1-test-dev-1-3.png)
-
-## Project 2 - Experiment 2 Design
-
-![](assets/e2_design.png)
-
-## Project 2 - Experiment 2 Results
-
-![](assets/fig-e2-train-dev-1-1.png)
-
-## Project 2 - Experiment 2 Results
-
-![](assets/fig-e2-test-dev-1-3.png)
-
-## Project 2 - Experiment 2 Results
-
-![](assets/fig-e2-bmm-vx-1-2.png)
-
-## Project 2 - Experiment 3 Design
-
-- Ordinal feedback
-- Include both the original order (E1) and reverse order (E2)
-
-## Project 3 - Experiment 3 Results
-
-![](assets/fig-e3-train-dev-1-1.png)
-
-## Project 3 - Experiment 3 Results
-
-![](assets/fig-e3-test-dev-1-3.png)
-
-## Project 3 - Experiment 3 Results
-
-![](assets/fig-e3-bmm-vx-1-2.png)
-
-------------------------------------------------------------------------
-
-## Project 2 - ALM
-
-![](assets/fig-alm-diagram-1-1.png)
-
-------------------------------------------------------------------------
-
-## ALM
-
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-
-------------------------------------------------------------------------
-
-## EXAM
-
-|                    | **EXAM Response Generation**                                                                                     |                                                                                                               |
-|--------------------|-----------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------|
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                                                 | Novel test stimulus $X$ activates input nodes $X_i$                                                           |
-| Slope Computation  | $S = \frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                                                                     | Slope value, $S$ computed from nearest training instances                                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                                                                         | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$, adjusted by local slope $S$.
-|
-
-------------------------------------------------------------------------
-
-## Project 2 - Model Fitting Procedure
-
-### Approximate Bayesian Computation
-
-## Modelling Results
-
-![](assets/fig-ee-e1-1.png)
-
-## General Discussion
-
--   Compare HTT and HTW
--   Empirical findings summary
--   Computational modeling contributions
-
-------------------------------------------------------------------------
-
-## Comparison {.smaller .r-fit-text}
-
-| Dimension | HTT (Project 1) | HTW (Project 2) |
-|----------------|--------------------------------|-------------------------|
-| Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
-| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
-| Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
-| Simpler: smooth, linear mapping between velocity and feedback.
-|
-| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
-salient differences in distance between launching box and target.
-| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
-|
-| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
-| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
-| Training Experience | Varied group gets half as much experience on any one position as the constant group.
-| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
-|
-| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
-
-------------------------------------------------------------------------
-
-## Theoretical Contributions
-
--   Insights into training variability effects on learning and generalization
--   Computational models applications
-
-------------------------------------------------------------------------
-
-## Practical Implications
-
--   Training programs design implications
--   Future research considerations
-
-------------------------------------------------------------------------
-
-## Limitations and Future Directions
-
--   Study limitations
--   Future research suggestions
-
-------------------------------------------------------------------------
-
-## Conclusion
-
--   Recap of key findings
--   Final thoughts on training variability's role in learning
-
-------------------------------------------------------------------------
-
-## Questions and Discussion
-
--   Open floor for questions from the committee and audience
-
-## Future Research Directions {.smaller .r-fit-text}
-
-::::::::: columns
-::::: {.column width="50%"}
-::: fragment
-### Theoretical Extensions
-
--   Investigate the role of individual differences in training variability effects.
--   Explore the impact of different types of feedback on learning and generalization.
--   Examine the influence of task complexity on the benefits of varied training.
-:::
-
-::: fragment
-### Methodological Innovations
-
--   Develop new experimental paradigms to test training variability in more complex tasks.
--   Utilize advanced computational models to simulate learning processes under varied conditions.
--   Implement longitudinal studies to assess long-term effects of training variability.
-:::
-:::::
-
-::::: {.column width="50%"}
-::: fragment
-### Practical Applications
-
--   Design adaptive training programs that adjust variability based on learner performance.
--   Apply findings to educational settings to enhance learning outcomes.
--   Use insights to improve training protocols in professional skill development.
-:::
-
-::: fragment
-### Collaborative Opportunities
-
--   Partner with educational institutions to test training variability in classroom settings.
--   Collaborate with industry professionals to apply research findings in real-world training programs.
--   Engage with interdisciplinary teams to explore the broader implications of training variability.
-:::
-:::::
-:::::::::
-
-------------------------------------------------------------------------

### 2024-05-27 Presentation/slides.qmd
slide updates

@@
     subtitle: "Dissertation Defense"
-    #toc: true
-    #shift-heading-level-by: 1
-    #toc-expand: true
   clean-revealjs:
@@
       theme: whiteboard
-  # pptx:
-  #   incremental: false
-  # hugo-md:
-  #   include: false
-  #   html-math-method: mathjax
-  #   output-file: slides_hugo.md
-  # gfm:
-  #   output: false
-  #   output-file: slides_gfm.md
+  pptx:
+    incremental: false
+  hugo-md:
+    include: false
+    html-math-method: mathjax
+    output-file: slides_hugo.md
+  gfm:
+    output: false
+    output-file: slides_gfm.md
 author:
@@
         department: Psychological & Brain Sciences, Cognitive Science
-params:
-  start_slide: 0
+# params:
+#   start_slide: 
 #engine: knitr
@@
 
-::::: {.content-visible when-format="html" unless-format="revealjs"}
-\
-[Click here](../paper.qmd) to open the dissertation manuscript.\
-\
-\
-\
-\
-
-## Slides {{< fa photo-film size=2xs >}} {.unnumbered .unlisted visibility="hidden"}
-
-Presentation slides are available below.
-You can navigate these sides using the <kbd>←</kbd> and <kbd>→</kbd> keys.
-Press <kbd>m</kbd> to display all commands (e.g., press <kbd>o</kbd> to switch to slide overview)
-
-```{=html}
-<p class="buttons" style="text-align:center;">
-<a class="btn btn-danger" target="_blank" href="/Presentation/slides_revealjs.html#{{< meta params.start_slide >}}"><i class="fa-solid fa-arrow-up-right-from-square"></i> Open slides in new window </a>
-</p>
-```
-
-:::: column-body-outset-right
-::: {.ratio .ratio-4x3}
-```{=html}
-<iframe src="/Presentation/slides_revealjs.html#{{< meta params.start_slide >}}">
-</iframe>
-```
-:::
-::::
-
-\
-\
-\
-:::::
+{{< include /Presentation/embed_slides.qmd >}}
 
@@
 
-### Model of Similarity between training and solutions
+## Model of Similarity between training and solutions
 
-![](assets/fig-taskSpace-1-1.png)
+:::{#fig-solspace}
+![](assets/sol_space.png){fig-align="left" width="500px"}
 
+Solution space
+:::
+
+## Model of Similarity between training and solutions
+
+:::: {.columns}
+::: {.column width="70%"}
+:::{#fig-fullspace}
+![](assets/full_space.png){fig-align="left" width="700px"}
+
+Full Space of Solution Throws and Missed Throws. Colored points represent coordinates of target hits, brown points are coordinates of misses
+:::
+:::
+::: {.column width="30%"}
+some text
+:::
+::::
 ------------------------------------------------------------------------
@@
 //| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
+//| fig-width: 9.5
+//| fig-height: 3.5
 //| echo: false  
@@
   node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#00A08A"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#FF0000"]
   Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
@@
 
-## Project 2 - Experiment 1 Results
+## Project 2 - Experiment 1 Results {.nostretch}
 
-![](assets/fig-e1-train-dev-1-1.png)
+::: {.columns}
+::: {.column width="50%"}
+![Plot 1](assets/htw_e1_test1.png)
+![Plot 3](assets/htw_e1_test3.png)
+:::
 
-## Project 2 - Experiment 1 Results
-
-![](assets/fig-e1-test-dev-1-3.png)
+::: {.column width="50%"}
+![Plot 2](assets/htw_e1_test2.png)
+![Plot 4](assets/htw_e1_test4.png)
+:::
+:::
 
@@
 
-![](assets/e2_design.png)
+::: {.content-visible unless-format="markdown"}
+```{dot}
+//| label: fig-design-e2
+//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
+//| fig-width: 10.0
+//| fig-height: 4
+//| fig-responsive: false
+//| echo: false 
+//| 
+/////| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+  node [shape = rectangle, style = filled]
+  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
+  data2 [label = " Constant Training \n600-800", fillcolor = "#FF0000"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+  data1 -> Test1
+  data2 -> Test1
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+  Test2 -> Test3
+}
+```
+:::
 
-## Project 2 - Experiment 2 Results
+## Project 2 - Experiment 2 Results {.nostretch}
 
-![](assets/fig-e2-train-dev-1-1.png)
+::: {.columns}
+::: {.column width="50%"}
+![Plot 1](assets/htw_e2_test1.png)
+![Plot 3](assets/htw_e2_test3.png)
+:::
 
-## Project 2 - Experiment 2 Results
+::: {.column width="50%"}
+![Plot 2](assets/htw_e2_test2.png)
+![Plot 4](assets/htw_e2_test4.png)
+:::
+:::
 
-![](assets/fig-e2-test-dev-1-3.png)
+## Project 2 - Experiment 3
 
-## Project 2 - Experiment 2 Results
+- Ordinal Feedback
+- Both Reverse and Original Feedback Order
 
-![](assets/fig-e2-bmm-vx-1-2.png)
+## Project 2 - Experiment 3 Results {.nostretch}
 
-## Project 2 - Experiment 3 Design
+## Accuracy
 
-- Ordinal feedback
-- Include both the original order (E1) and reverse order (E2)
+:::: {.columns}
 
-## Project 3 - Experiment 3 Results
+::: {.column width="50%"}
+![Plot 1](assets/htw_e3_test1.png)
+:::
 
-![](assets/fig-e3-train-dev-1-1.png)
+::: {.column width="50%"}
+![Plot 3](assets/htw_e3_test2.png)
+:::
 
-## Project 3 - Experiment 3 Results
+::::
 
-![](assets/fig-e3-test-dev-1-3.png)
+## Discrimination
 
-## Project 3 - Experiment 3 Results
+:::: {.columns}
 
-![](assets/fig-e3-bmm-vx-1-2.png)
+::: {.column width="50%"}
+![Plot 1](assets/htw_e3_test3.png)
+:::
+
+::: {.column width="50%"}
+![Plot 3](assets/htw_e3_test4.png)
+:::
+
+::::
 
@@
 
-# Project 2 - ALM
+# Project 2 - Computational Modeling
+
+## Project 2 - ALM
 
@@
 
-## Project 2 - Model Fitting Procedure
+## Project 2 - Model Fitting Procedure {.r-fit-text}
 
 ### Approximate Bayesian Computation
+
+:::: {.columns}
+
+::: {.column width="60%"}
+![](assets/abc_diagram1.png)
+:::
+
+::: {.column width="40%"}
+
+- simulation based approach
+- approximate likelihood
+- uncertainty in parameter values
+- full distribution of plausible model predictions for each participant
+
+:::
+
+::::
 

### 2024-05-27 Presentation/slides2.qmd
Re-add missing Procedure section; fix appendix link
slide updates

@@
 title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
+page-layout: full
+aliases:
+  - /slides.html
+css: /Assets/Style/slides.css
+format: 
+  html: 
     subtitle: "Dissertation Defense"
-format: 
-  html: default
+  clean-revealjs:
+    #theme: moon #white
+    #output-ext: revealjs.html
+    # template-partials:
+    #   - assets/title-slide.html
+    output-file: slides_revealjs
+    date: 05/28/204
+    slideNumber: true
+    hash-type: number # Use slide numbers in the URL hash
+    center: true
+    scrollable: true
+    chalkboard:
+      theme: whiteboard
+  # pptx:
+  #   incremental: false
+  # hugo-md:
+  #   include: false
+  #   html-math-method: mathjax
+  #   output-file: slides_hugo.md
+  # gfm:
+  #   output: false
+  #   output-file: slides_gfm.md
 author:
   - name: Thomas Gorman
-    orcid: 0000-0000-0000-0000
-    affiliations: Indiana University
+    url: https://tegorman13.github.io
+    orcid: 0000-0001-5366-5442
+    affiliations:
+      - name: Indiana University
+        department: Psychological & Brain Sciences, Cognitive Science
+# params:
+#   start_slide: 5
+#engine: knitr
 ---
-
-::: {.content-visible when-format="html"}
-
-<div class="ratio ratio-16x9"> <iframe src="/Presentation/slides_revealjs.html"></iframe> </div>
-
-test
-:::

### 2024-05-27 Presentation/slides.qmd
fix alm plot

@@
 //| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 9.5
-//| fig-height: 3.5
+//| fig-width: 9.0
+//| fig-height: 3.2
 //| echo: false  
+//| column: screen-inset-right 
 digraph {
@@
 //| echo: false 
+//| column: screen-inset-right
 //| 

### 2024-05-28 Presentation/_fig_creation.qmd
update slides

@@
 
+# Design diagrams
+
+```{r}
+
+library(ggplot2)
+library(dplyr)
+
+# Data preparation
+data <- data.frame(
+  x = c(2, 3, 1, 2, 3),
+  y = c(1, 1, 0.6, 0.6, 0.6),  # Adjusted y values for the bottom segment
+  label = c("Constant-Train\n(100 trials)", "Test", "Varied-Train\n(50 trials)", "Varied-Train\n(50 trials)", "Test"),
+  color = c("blue", "red", "blue", "blue", "red")
+)
+
+segments <- data.frame(
+  x = c(0.5, 1.5, 0.5, 1.5),
+  xend = c(1.5, 3.0, 1.5, 3.0),
+  y = c(1, 1, 0.6, 0.6),  # Adjusted y values for the segments
+  yend = c(1, 1, 0.6, 0.6)
+)
+
+# Plot
+ggplot() +
+  geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend), 
+               linewidth = 1.2, color = "gray40") +
+  geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+  geom_text(data = data %>% filter(color == "blue"), aes(x = x, y = y, label = label), 
+            color = "black", size = 4, vjust = -1, fontface = "bold") +
+  geom_text(data = data %>% filter(color == "red"), aes(x = x, y = y, label = label), 
+            color = "black", size = 4, vjust = -2, fontface = "bold") +
+  scale_color_manual(values = c("blue" = "#3366CC", "red" = "#DC3912")) +
+  xlim(0, 3.5) +
+  ylim(0, 1.5) +  # Adjusted ylim to maintain the overall plot height
+  theme_void() +
+  theme(legend.position = "none",
+        plot.margin = margin(10, 20, 10, 20),
+        plot.background = element_rect(fill = "white", color = NA),
+        panel.background = element_rect(fill = "white", color = NA))
+```
+
+```{r}
+#| fig-width: 10
+#| fig-height: 7
+
+library(ggplot2)
+library(dplyr)
+
+create_data <- function(varied_train, constant_train, both_test, varied_trials, constant_trials) {
+  varied_labels <- paste0("Varied-Train\n(", varied_trials, " trials)")
+  constant_labels <- paste0("Constant-Train\n(", constant_trials, " trials)")
+  test_labels <- "Testing\n(both groups)"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train)), rep(0.3, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("blue", length(varied_train)), rep("blue", length(constant_train)), rep("red", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.7, 1, 0.3),
+    yend = c(0.7, 1, 0.3)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test, varied_trials, constant_trials) {
+  data <- create_data(varied_train, constant_train, both_test, varied_trials, constant_trials)
+  segments <- create_segments(data)
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4, vjust = -0.6, hjust = 0.5, fontface = "bold") +
+    scale_color_manual(values = c("blue" = "#3366CC", "red" = "#DC3912")) +
+    xlim(min(data$x) - 1, max(data$x) + 1) +
+    ylim(0, 1.5) +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+# Example usage
+varied_train <- c(1, 3, 5) # Specify varied training positions
+constant_train <- c(4)     # Specify constant training position
+both_test <- c(2.5, 3.5)        # Specify test position
+varied_trials <- 50        # Specify number of varied trials
+constant_trials <- 100     # Specify number of constant trials
+
+plot <- create_plot(varied_train, constant_train, both_test, varied_trials, constant_trials)
+print(plot)
+
+varied_train <- c(1, 2, 3) # Specify varied training positions
+constant_train <- c(3)     # Specify constant training position
+both_test <- c(1,2,3,4,5,6)        # Specify test position
+varied_trials <- 30        # Specify number of varied trials
+constant_trials <- 90     # Specify number of constant trials
+ create_plot(varied_train, constant_train, both_test, varied_trials, constant_trials)
+
+```
+
+```{r}
+#| fig-width: 10
+#| fig-height: 7
+
+library(ggplot2)
+library(dplyr)
+library(grid)
+
+create_data <- function(varied_train, constant_train, both_test, varied_trials, constant_trials) {
+  varied_labels <- paste0("Varied-Train\n(", varied_trials, " trials)")
+  constant_labels <- paste0("Constant-Train\n(", constant_trials, " trials)")
+  test_labels <- "Testing\n(both groups)"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train)), rep(0.3, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("blue", length(varied_train)), rep("blue", length(constant_train)), rep("red", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.7, 1, 0.3),
+    yend = c(0.7, 1, 0.3)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test, varied_trials, constant_trials) {
+  data <- create_data(varied_train, constant_train, both_test, varied_trials, constant_trials)
+  segments <- create_segments(data)
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4, vjust = -0.6, hjust = 0.5, fontface = "bold") +
+    scale_color_manual(values = c("blue" = "#3366CC", "red" = "#DC3912")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0, 1.5) +
+    theme_void() +
+    annotate("text", x = min(data$x) - .8, y = 1.1, label = "{", color = "black", size = 28, vjust = 1.5) +
+    annotate("text", x = min(data$x) - .8, y = 0.45, label = "{", color = "black", size = 18, vjust = 1.5) +
+    annotate("text", x = min(data$x) - 1.2, y = 0.85, label = "Training", color = "black", size = 5, angle = 90, vjust = 1.5, fontface = "bold") +
+    annotate("text", x = min(data$x) - 1.2, y = 0.35, label = "Testing", color = "black", size = 5, angle = 90, vjust = 1.5, fontface = "bold") +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+# Example usage
+
+varied_train <- c(1, 2, 3) # Specify varied training positions
+constant_train <- c(3)     # Specify constant training position
+both_test <- c(1, 2, 3, 4, 5, 6)        # Specify test position
+varied_trials <- 30        # Specify number of varied trials
+constant_trials <- 90     # Specify number of constant trials
+plot <- create_plot(varied_train, constant_train, both_test, varied_trials, constant_trials)
+print(plot)
+```
+
+```{r}
+#| fig-width: 10
+#| fig-height: 7
+
+library(ggplot2)
+library(dplyr)
+
+create_data <- function(varied_train, constant_train, both_test, varied_trials, constant_trials) {
+  varied_labels <- paste0("Varied-Train\n(", varied_trials, " trials)")
+  constant_labels <- paste0("Constant-Train\n(", constant_trials, " trials)")
+  test_labels <- "Testing\n(both groups)"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train)), rep(0.3, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("blue", length(varied_train)), rep("blue", length(constant_train)), rep("red", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.7, 1, 0.3),
+    yend = c(0.7, 1, 0.3)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test, varied_trials, constant_trials) {
+  data <- create_data(varied_train, constant_train, both_test, varied_trials, constant_trials)
+  segments <- create_segments(data)
+
+  # Variables for Training segment position
+  train_x <- min(data$x) - .5
+  train_y_start <- 0.65
+  train_y_end <- 1.05
+  train_text_y <- 1
+
+  # Variables for Testing segment position
+  test_x <- min(data$x) - .5
+  test_y_start <- 0.25
+  test_y_end <- 0.4
+  test_text_y <- 0.45
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4, vjust = -0.6, hjust = 0.5, fontface = "bold") +
+    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    scale_color_manual(values = c("blue" = "#3366CC", "red" = "#DC3912")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0, 1.5) +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+# Example usage
+
+varied_train <- c(1, 2, 3) # Specify varied training positions
+constant_train <- c(3)     # Specify constant training position
+both_test <- c(1,2,3,4,5,6)        # Specify test position
+varied_trials <- 30        # Specify number of varied trials
+constant_trials <- 90     # Specify number of constant trials
+ create_plot(varied_train, constant_train, both_test, varied_trials, constant_trials)
+
+```
+
+## HTW Exp
+
+```{r}
+#| fig-width: 10
+#| fig-height: 7
+
+library(ggplot2)
+library(dplyr)
+
+create_data <- function(varied_train, constant_train, both_test) {
+  varied_labels <- "Varied-Train"
+  constant_labels <- "Constant-Train"
+  test_labels <- "Testing"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train)), rep(0.3, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+   color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.7, 1, 0.3),
+    yend = c(0.7, 1, 0.3)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test) {
+  data <- create_data(varied_train, constant_train, both_test)
+  segments <- create_segments(data)
+
+  # Variables for Training segment position
+  train_x <- min(data$x) - .5
+  train_y_start <- 0.65
+  train_y_end <- 1.05
+  train_text_y <- 1
+
+  # Variables for Testing segment position
+  test_x <- min(data$x) - .5
+  test_y_start <- 0.25
+  test_y_end <- 0.4
+  test_text_y <- 0.45
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0, 1.5) +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+# Example usage
+
+varied_train <- c(4, 5, 6) # Specify varied training positions
+constant_train <- c(4)     # Specify constant training position
+both_test <- c(1, 2, 3, 4, 5, 6)  # Specify test positions
+htw_e1 <- create_plot(varied_train, constant_train, both_test)
+
+varied_train <- c(1, 2, 3) # Specify varied training positions
+constant_train <- c(3)     # Specify constant training position
+both_test <- c(1, 2, 3, 4, 5, 6)  # Specify test positions
+htw_e2 <- create_plot(varied_train, constant_train, both_test)
+
+htw_e1
+htw_e2
+
+ggsave(here::here("Presentation/assets/htw_e1_manip.png"), htw_e1, width = 9.0, height = 6, units = "in", dpi = 300)
+ggsave(here::here("Presentation/assets/htw_e2_manip.png"), htw_e2, width = 9.0, height = 6, units = "in", dpi = 300)
+
+varied_train <- c(1, 4) # Specify varied training positions
+constant_train <- c(2)     # Specify constant training position
+both_test <- c(1, 2, 3, 4)  # Specify test positions
+igas_e1 <-  create_plot(varied_train, constant_train, both_test)
+igas_e1
+ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 7.0, height = 6, units = "in", dpi = 400)
+
+```
+
+## IGAS - EXP 2
+
+```{r}
+#| fig-width: 10
+#| fig-height: 7
+
+create_data <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test) {
+    varied_labels <- "Varied-Train"
+    constant_labels1 <- "Constant-1-Train"
+    constant_labels2 <- "Constant-2-Train"
+    constant_labels3 <- "Constant-3-Train"
+    constant_labels4 <- "Constant-4-Train"
+    constant_labels5 <- "Constant-5-Train"
+    constant_labels6 <- "Constant-6-Train"
+    test_labels <- "Testing"
+
+    data <- data.frame(
+        x = c(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test),
+        y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train1)), rep(1.3, length(constant_train2)), 
+              rep(1.6, length(constant_train3)), rep(1.9, length(constant_train4)), rep(2.2, length(constant_train5)),
+              rep(2.5, length(constant_train6)), rep(0.3, length(both_test))),
+        label = c(rep(varied_labels, length(varied_train)),
+                  rep(constant_labels1, length(constant_train1)),
+                  rep(constant_labels2, length(constant_train2)),
+                  rep(constant_labels3, length(constant_train3)),
+                  rep(constant_labels4, length(constant_train4)),
+                  rep(constant_labels5, length(constant_train5)),
+                  rep(constant_labels6, length(constant_train6)),
+                  rep(test_labels, length(both_test))),
+        color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train1)), rep("#FF0000", length(constant_train2)),
+                  rep("#FF0000", length(constant_train3)), rep("#FF0000", length(constant_train4)), rep("#FF0000", length(constant_train5)),
+                  rep("#FF0000", length(constant_train6)), rep("#ECCBAE", length(both_test)))
+    )
+
+    data
+}
+
+create_segments <- function(data) {
+    min_x <- min(data$x)
+    max_x <- max(data$x)
+    segments <- data.frame(
+        x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5, min_x - 0.5, min_x - 0.5, min_x - 0.5, min_x - 0.5, min_x - 0.5),
+        xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5, max_x + 0.5, max_x + 0.5, max_x + 0.5, max_x + 0.5, max_x + 0.5),
+        y = c(0.7, 1, 1.3, 1.6, 1.9, 2.2, 2.5, 0.3),
+        yend = c(0.7, 1, 1.3, 1.6, 1.9, 2.2, 2.5, 0.3)
+    )
+    segments
+}
+
+create_plot <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test) {
+    data <- create_data(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test)
+    segments <- create_segments(data)
+
+    # Variables for Training segment position
+    train_x <- min(data$x) - .5
+    train_y_start <- 0.65
+    train_y_end <- 2.55
+    train_text_y <- 2.0
+
+    # Variables for Testing segment position
+    test_x <- min(data$x) - .5
+    test_y_start <- 0.25
+    test_y_end <- 0.4
+    test_text_y <- 0.55
+
+    ggplot() +
+        geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                     linewidth = 1.2, color = "gray40") +
+        geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+        geom_text(data = data, aes(x = x, y = y, label = label),
+                  color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+        geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+        geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+        geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+        geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+        geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+        geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+        geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+        geom_text(aes(x = test_x - .65, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+        scale_color_identity() +
+        xlim(min(data$x) - 2, max(data$x) + 1) +
+        ylim(0, 3.0) +
+        theme_void() +
+        theme(legend.position = "none",
+              plot.margin = margin(10, 20, 10, 20),
+              plot.background = element_rect(fill = "white", color = NA),
+              panel.background = element_rect(fill = "white", color = NA))
+}
+
+# Example usage
+varied_train <- c(3, 5)                   # Specify varied training positions
+constant_train1 <- c(1)                   # Specify constant training position for group 1
+constant_train2 <- c(2)                   # Specify constant training position for group 2
+constant_train3 <- c(3)                   # Specify constant training position for group 3
+constant_train4 <- c(4)                   # Specify constant training position for group 4
+constant_train5 <- c(5) # Specify constant training position for group 5
+constant_train6 <- c(6) # Specify constant training position for group 6
+both_test <- c(1, 2, 3, 4, 5, 6) # Specify test positions
+igas_e2 <- create_plot(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test)
+igas_e2
+
+ggsave(here::here("Presentation/assets/igas_e2_manip.png"), igas_e2, width = 7.5, height = 8, units = "in", dpi = 600)
+
+```
+
 # Sim Example
@@
 
-ggsave(here::here("Presentation/assets/sol_space.png"),ss)
-ggsave(here::here("Presentation/assets/full_space.png"),fs)
+ggsave(here::here("Presentation/assets/sol_space2.png"),ss, width = 5, height = 4, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/full_space2.png"),fs, width = 5, height = 3, units = "in", dpi = 600)
 
 ```
+
+## IGAS Results
+
+```{r}
+pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork,here)
+source(here::here('Functions/IGAS_ProcessFunctions.R'))
+
+theme_set(theme_classic())
+# load the processed data from experiment 1 and 2
+e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
+e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
+# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
+e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
+
+options(contrasts = c("contr.sum", "contr.poly"))
+defaultContrasts = options()$contrasts
+theme_set(theme_classic())
+
+dodge <- position_dodge(width = 0.9)
+e2GrpPos <- c("400","500","625","675","800","900")
+e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
+e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
+                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
+
+e1Pos <- c("610","760","835","910")
+e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
+e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
+
+exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
+  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
+  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
+  group_by(sbjCode,Group,conditType,trainHalf) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
+  group_by(sbjCode,Group,conditType,stage) %>% 
+  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
+
+e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
+  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
+  facet_wrap(~conditType,ncol=2)+
+  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
+  ylab("Mean Distance From Center Of Target")+
+  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
+  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
+
+#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
+plot_grid(e1train2,ncol=1)
+
+walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+
+nbins=5
+
+htt_e1_train <-  e1 %>% filter(stage!="Transfer",mode==1) |> group_by(sbjCode,Group,positionX,conditType) |> 
+    mutate(Trial_Bin = cut(trial, breaks = seq(1, max(trial),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) |>
+ggplot(aes(x = Trial_Bin, y = AbsDistFromCenter, color = conditType)) +
+    stat_summary(geom = "line", fun = mean) +
+    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
+    facet_wrap(~positionX)+
+    scale_x_continuous(breaks = seq(1, nbins + 1)) +
+    theme(legend.title=element_blank()) + 
+    labs(y = "Deviation", x="Training Block",col="Throw Position")
+
+htt_e2_train <- e2 %>% filter(stage!="Transfer",mode==1) |> group_by(sbjCode,Group,positionX,conditType) |> 
+    mutate(Trial_Bin = cut(trial, breaks = seq(1, max(trial),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) |> ggplot(aes(x = Trial_Bin, y = AbsDistFromCenter, color = conditType)) +
+    stat_summary(geom = "line", fun = mean) +
+    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
+    facet_wrap(~positionX)+
+    scale_x_continuous(breaks = seq(1, nbins + 1)) +
+    theme(legend.title=element_blank()) + 
+    labs(y = "Deviation", x="Training Block",col="Throw Position")
+
+ggsave(here::here("Presentation/assets/htt_e1_train.png"),htt_e1_train,width = 5, height = 2, units = "in", dpi = 300)
+ggsave(here::here("Presentation/assets/htt_e2_train.png"),htt_e2_train,width = 5, height = 4, units = "in", dpi = 300)
+
+```
+
+```{r}
+
+exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
+  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% 
+  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
+  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
+summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
+
+#manuscript plot
+e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
+  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+
+  guides(fill=guide_legend(title="Training Condition"))+
+  theme(legend.title.align=.25, 
+  axis.text.x = element_text(size = 8.5,angle=0),
+  legend.position="top")+
+  scale_x_discrete(name="Testing Location",labels=e1Labels)
+
+e1test1
+
+transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
+transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
+  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
+
+transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
+  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
+
+variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
+constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
+
+transfer <- rbind(variedTest,constantTest)
+
+exp2.Test <- filter(e2, stage=="Transfer") %>% group_by(sbjCode,conditType,positionX,ThrowPosition,condit2) %>%
+  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05)) %>%ungroup() %>% as.data.frame()
+
+e2test1<- exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
+  theme(plot.title=element_text(face="bold",size=9),
+        plot.title.position = "plot",
+        legend.title.align=.25)
+
+ggsave(here::here("Presentation/assets/htt_e2_test.png"),e2test1,width = 5, height = 4, units = "in", dpi = 300)
+
+exp2.Test %>% ggplot(aes(x=condit2,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition")) +
+  facet_wrap(~positionX) + 
+  theme(plot.title=element_text(face="bold",size=9),
+        plot.title.position = "plot",
+        legend.title.align=.25) + guides(fill=guide_legend(title="Training Condition"))+
+  theme(plot.title=element_text(face="bold",size=9),
+        plot.title.position = "plot",
+        legend.title.align=.25,
+        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
+  scale_x_discrete(name=" Training Group",labels=e2Labels)
+
+```

### 2024-05-28 Presentation/slides.qmd
update slides

--- 2024-05-27 Presentation/slides.qmd
@@
 css: /Assets/Style/slides.css
+format-links: [clean-revealjs, pptx,gfm]
 format: 
@@
 
-# Introduction
+# Learning Generalization
 
--   Investigate effects of training variability on learning and generalization
--   Focus areas: visuomotor skill learning and function learning tasks
+- Learning is often specific
+- Longstanding scientific interest in how to improve generalization or transfer
 
@@
 
-## Background and Motivation
+## Variability
 
--   Importance of training variability
--   Research gaps in visuomotor skill learning
--   Previous research in category learning, language learning, and function learning
+- Variation during training linked to improved transfer in numerous domains 
+- What does "variability mean in the context of learning interventions?"
+
+## Types of Variability
+
+- The number of unique items/problems experienced
+- How spread out examples are
+
+## My Dissertation Focus
+
+- Number of unique examples
+- Visuomotor skill learning and function learning
+
+- Addressing methodological shortcomings of previous work
+- Adapting cognitive models from other domains to account for results
 
 ------------------------------------------------------------------------
+
+## Common Experimental Manipulations
+
+- Varied vs. Constant
 
@@
 :::::::::  columns
-::: {.column width="60%"}
+::: {.column width="55%"}
 ### Training
@@
 
-::: {.column width="40%"} 
+::: {.column width="45%"} 
 ::: {.fragment}
@@
 
-- Cases where varied training makes no difference
+- Cases where varied training doesn't benefit generalization
 - Cases where more training variation results in worse outcomes
@@
 
+::: footer
+@schmidtSchemaTheoryDiscrete1975 @bjorkMakingThingsHard2011 @guadagnoliChallengePointFramework2004
+:::
+
 <!-- ![](assets/fig-toy-model1-1-1.png) -->
@@
 
--   Project 1: Visuomotor projectile launching task
--   Project 2: Visuomotor extrapolation task
+### Project 1[^1]
 
-------------------------------------------------------------------------
+- Visuomotor projectile launching task
+- two experiments
+- Beneficial effect of variability
+- Instance-based similarity model
 
-# Project 1
+### Project 2
 
--   Influence of varied practice in a projectile launching task
--   Experiments 1 & 2:
-    -   Constant vs. varied training groups
-    -   Performance metrics and transfer testing
+- Visuomotor extrapolation task
+- Three experiments
+- Effect of variability is null or negative
+- Connectionist model (ALM) and hybrid associative & rule model (EXAM)
+
+::: footer
+[^1]: Now published in Cognitive Psychology @gormanInstancebasedModelAccount2022
+:::
+--
+
+# Project 1  - Issues with previous research
+
+- Assumptions about what is encoded
+- Assumptions about the formation of abstractions 
+- Aggregation issues and similarity confounds
+
+---
+
+## designs that seemingly overcome these issues
+
+- Kerr & Booth 1978
+
+::: footer
+@kerrSpecificVariedPractice1978
+:::
+
+## Experiment 1
+
+- Conceptual replication of Kerr & Booth design 
+- Testing classic pattern as well
 
@@
 :::: {.column width="40%"}
-- **Training Stage** - 200 training trials. Constant groups throws from single position. Varied group 60 trials from 2 locations. 
+- **Training Stage** - 200 training trials with feedback. Constant groups trains from single position. Varied group practices from two positions. 
 - **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
@@
 
-## Project 1 - Manipulations
+## Project 1 - Manipulations  {.smaller}
 
@@
 ### Experiment 1
-- Train a varied group from 2 positions, and a constant group from 1. Then test both groups, from the training positions and a novel position.
+- Train varied group from 2 positions, and a constant group from 1.
+- Test both groups from the trained positions - and 1 novel position
+
+![](assets/igas_e1_manip.png)
 
@@
 ### Experiment 2
-- 6 constant conditions, each trained from a unique location, and a varied condition trained from 2 locations
+- 6 distinct constant conditions
+
+![](assets/igas_e2_manip.png)
 :::
@@
 
-## Project 1 - Results
+## Project 1 - Experiment 1 Results
 
@@
 ### Experiment 1
+![](assets/igas_e1_manip.png)
+:::
+::: {.column width="60%"}
+::: fragment
+### Training
+![](assets/htt_e1_train.png)
+:::
+::: fragment
+### Testing
 ![](assets/fig-IGAS_Testing1-1-2.png)
 :::
+:::
+::::
+
+## Project 1 - Experiment 2 Results
+
+:::: {.columns}
+::: {.column width="40%"}
+### Experiment 1
+![](assets/igas_e2_manip.png)
+:::
 ::: {.column width="60%"}
-### Experiment 2
-![](assets/fig-e2testa-1-2.png)
+::: fragment
+### Training
+![](assets/htt_e2_train.png)
+:::
+::: fragment
+### Testing
+![](assets/htt_e2_test.png)
+:::
 :::
@@
 
-## Model of Similarity between training and solutions
+:::: {.columns}
+::: {.column width="50%"}
 
-:::{#fig-solspace}
-![](assets/sol_space.png){fig-align="left" width="500px"}
-
-Solution space
+![](assets/sol_space2.png){width="65%"}
+![](assets/full_space2.png){width="50%"}
 :::
 
-## Model of Similarity between training and solutions
+::: {.column width="50%"}
+
+### Model Steps
+
+- each of the 6 positions has an empirical solution space
+- Compute the summed similarity between training throws, and solution spaces
+  - separately for each participant, and each of the testing positions
+- We now have a measure of how similar training behavior was to testing solutions
+
+### Model Definition
+
+- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
+- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
+
+:::
+::::
+
+## Project 1 Computational Model {.smaller .r-fit-text}
 
@@
 ::: {.column width="70%"}
-:::{#fig-fullspace}
-![](assets/full_space.png){fig-align="left" width="700px"}
+
+![](assets/sol_space.png)
+
+![](assets/full_space.png)
+:::
+::: {.column width="30%"}
+### Model Steps
+
+- each of the 6 positions has an empirical solution space
+- Compute the summed similarity between training throws, and solution spaces
+  - separately for each participant, and each of the testing positions
+- We now have a measure of how similar training behavior was to testing solutions
+
+### Model Definition
+
+- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
+- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
+:::
+::::
+
+## Project 1 Computational Model {.smaller .r-fit-text}
+
+:::: {.columns}
+::: {.column width="60%"}
+### Solution Space
+![](assets/sol_space2.png)
+
+### Full Space
+:::{#fig-fullspace23}
+![](assets/full_space2.png)
 
@@
 :::
+
 :::
-::: {.column width="30%"}
-some text
+
+::: {.column width="40%"}
+
+### Model Steps
+
+- each of the 6 positions has an empirical solution space
+- Compute the summed similarity between training throws, and solution spaces
+  - separately for each participant, and each of the testing positions
+- We now have a measure of how similar training behavior was to testing solutions
+
+### Model Definition
+
+- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
+- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
 :::
 ::::
-------------------------------------------------------------------------
 
-## Project 1 Computational Model {.smaller .r-fit-text}
+## Computational Model - Does Similarity Account for Effect of Variability?
 
-- For each subject, compute similarity between training throws and each of the 6 testing locations
 - Test whether similarity explains the difference in performance between Constant and Varied conditions
@@
 **Model-based**
-- If variation does influence extrapolation, can a connectionist model with similarity-based activation provide a good account?
+- If variation does influence extrapolation, can an associative learning model with similarity-based activation provide a good account?
 - Can our modelling framework simultaneously account for both training and testing data?
@@
 :::
--   A total of 156 participants from IU's online subject pool
--   Varied group trains from 3 "velocity bands", constant group from 1
 
@@
 
+- Target velocity presented at top of screen
+- Participants attempt to "hit the wall" at the correct velocity
+- Feedback during training - how many units above or below the target-band
+- Only the "x velocity" component of the throw is relevant to the task
+
 ------------------------------------------------------------------------
 
-## Project 2 - Methodology
+## Project 2 - Experiment 1 Design {.nostretch .smaller}
 
--   A total of 156 participants from IU's online subject pool
+:::: {.columns}
+::: {.column width="60%"}
+![](assets/htw_e1_manip.png){fig-align="left" fig-align="top" width="65%"}
+
+![](assets/e1_design.png){fig-align="left" fig-align="top" width="70%"}
+:::
+::: {.column width="40%"}
+
+- 156 participants included in final analysis
 - Varied group trains from 3 "velocity bands", constant group from 1
-
-![](assets/htw_task_fig.png)
-
-## Project 2 - Methodology
-
-::: {.content-visible unless-format="markdown"}
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 9.5
-//| fig-height: 3.5
-//| echo: false  
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#00A08A"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#FF0000"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
 :::
+::::
 
@@
 
-## Project 2 - Experiment 2 Design
+## Project 2 - Experiment 2 Design {.smaller}
 
-::: {.content-visible unless-format="markdown"}
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 10.0
-//| fig-height: 4
-//| fig-responsive: false
-//| echo: false 
-//| 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#FF0000"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
+:::: {.columns}
+::: {.column width="60%"}
+![](assets/htw_e2_manip.png){fig-align="left" fig-align="top"}
+
+![](assets/e2_design.png){fig-align="left" fig-align="top"}
 :::
+::: {.column width="40%"}
+
+<br><br><br><br>
+
+- Training and Testing bands are in reversed order, relative to Experiment 1
+- 110 participants included in final analysis
+
+:::
+::::
 
@@
 - Ordinal Feedback
-- Both Reverse and Original Feedback Order
+  - directional feedback indicating too high, too low, or correct
+- Both Original (Experiment 1), and reverse (Experiment 2) orders included
+- 195 participants included in final analysis
 
@@
 
-## Theoretical Contributions
+## Conclusion
 
--   Insights into training variability effects on learning and generalization
--   Computational models applications
+## References
+::: {#refs}
+:::
+
+::: {.content-visible when-format="html"}
+## Manuscript {.scrollable .unnumbered .unlisted}
+
+```{=html}
+<iframe width="800" height="750" src="https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html" title="Webpage example"></iframe>
+```
+:::
 
 ------------------------------------------------------------------------
-
-## Practical Implications
-
--   Training programs design implications
--   Future research considerations
-
-------------------------------------------------------------------------
-
-## Limitations and Future Directions
-
--   Study limitations
--   Future research suggestions
-
-------------------------------------------------------------------------
-
-## Conclusion
-
--   Recap of key findings
--   Final thoughts on training variability's role in learning
-
-------------------------------------------------------------------------
-
-## Questions and Discussion
-
--   Open floor for questions from the committee and audience
-
-## Future Research Directions {.smaller .r-fit-text}
-
-::::::::: columns
-::::: {.column width="50%"}
-::: fragment
-### Theoretical Extensions
-
--   Investigate the role of individual differences in training variability effects.
--   Explore the impact of different types of feedback on learning and generalization.
--   Examine the influence of task complexity on the benefits of varied training.
-:::
-
-::: fragment
-### Methodological Innovations
-
--   Develop new experimental paradigms to test training variability in more complex tasks.
--   Utilize advanced computational models to simulate learning processes under varied conditions.
--   Implement longitudinal studies to assess long-term effects of training variability.
-:::
-:::::
-
-::::: {.column width="50%"}
-::: fragment
-### Practical Applications
-
--   Design adaptive training programs that adjust variability based on learner performance.
--   Apply findings to educational settings to enhance learning outcomes.
--   Use insights to improve training protocols in professional skill development.
-:::
-
-::: fragment
-### Collaborative Opportunities
-
--   Partner with educational institutions to test training variability in classroom settings.
--   Collaborate with industry professionals to apply research findings in real-world training programs.
--   Engage with interdisciplinary teams to explore the broader implications of training variability.
-:::
-:::::
-:::::::::
-
-------------------------------------------------------------------------

### 2024-05-28 Sections/full.qmd
update slides

@@
   node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#00A08A"]
+  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
+  data2 [label = " Constant Training \n600-800", fillcolor = "#FF0000"]
   Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
@@
 ```
-
 :::

### 2024-05-28 Presentation/_fig_creation.qmd
fix slide image displays

@@
+```{r}
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,stringr, here,conflicted, gt, ggh4x, patchwork, knitr)
+walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+
+```
+
 # HTW Results
@@
 igas_e1
-ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 7.0, height = 6, units = "in", dpi = 400)
-
-```
-
-## IGAS - EXP 2
+ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)
+
+```
 
@@
 
-create_data <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test) {
+library(ggplot2)
+library(dplyr)
+
+create_data <- function(varied_train, constant_train, both_test, test_labels_bottom) {
+  varied_labels <- "Varied-Train"
+  constant_labels <- "Constant-Train"
+  test_labels <- "Testing"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train)), rep(0.3, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test))),
+    label_bottom = c(rep(NA, length(varied_train) + length(constant_train)), test_labels_bottom)
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.7, 1, 0.3),
+    yend = c(0.7, 1, 0.3)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test, test_labels_bottom) {
+  data <- create_data(varied_train, constant_train, both_test, test_labels_bottom)
+  segments <- create_segments(data)
+
+  # Variables for Training segment position
+  train_x <- min(data$x) - .5
+  train_y_start <- 0.65
+  train_y_end <- 1.05
+  train_text_y <- 1
+
+  # Variables for Testing segment position
+  test_x <- min(data$x) - .5
+  test_y_start <- 0.25
+  test_y_end <- 0.4
+  test_text_y <- 0.45
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y+.01, label = label),
+              color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+    geom_text(data = data, aes(x = x, y = 0.2, label = label_bottom),
+              color = "black", size = 4, vjust = 1.8, hjust = 0.5, fontface = "italic") +
+    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0, 1.5) +
+    theme_void() +
+    theme(
+          # plot.margin = margin(10, 20, 10, 20),
+          # plot.background = element_rect(fill = "white", color = NA),
+          # panel.background = element_rect(fill = "white", color = NA), 
+          legend.position = "none",)
+}
+
+# Example usage
+
+varied_train <- c(4, 5, 6) # Specify varied training positions
+constant_train <- c(4)     # Specify constant training position
+both_test <- c(1, 2, 3, 4, 5, 6)  # Specify test positions
+test_labels_bottom <- c("100-350", "350-550", "600-800", "800-1000", "1000-1200", "1200-1400") # Labels for bottom of test points
+htw_e1 <- create_plot(varied_train, constant_train, both_test, test_labels_bottom)
+htw_e1
+
+varied_train <- c(1, 2, 3) # Specify varied training positions
+constant_train <- c(3)     # Specify constant training position
+both_test <- c(1, 2, 3, 4, 5, 6)  # Specify test positions
+htw_e2 <- create_plot(varied_train, constant_train, both_test,test_labels_bottom)
+htw_e2
+
+ggsave(here::here("Presentation/assets/htw_e1_manip.png"), htw_e1, width = 9.0, height = 6, units = "in", dpi = 300)
+ggsave(here::here("Presentation/assets/htw_e2_manip.png"), htw_e2, width = 9.0, height = 6, units = "in", dpi = 300)
+
+varied_train <- c(1, 4) # Specify varied training positions
+constant_train <- c(2)     # Specify constant training position
+both_test <- c(1, 2, 3, 4)  # Specify test positions
+test_labels_bottom <- c("610", "760", "835", "910") # Labels for bottom of test points
+igas_e1 <-  create_plot(varied_train, constant_train, both_test,test_labels_bottom)
+igas_e1
+ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)
+
+```
+
+## IGAS - EXP 2
+
+```{r}
+#| fig-width: 10
+#| fig-height: 7
+
+create_data <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom) {
     varied_labels <- "Varied-Train"
@@
                   rep("#FF0000", length(constant_train3)), rep("#FF0000", length(constant_train4)), rep("#FF0000", length(constant_train5)),
-                  rep("#FF0000", length(constant_train6)), rep("#ECCBAE", length(both_test)))
+                  rep("#FF0000", length(constant_train6)), rep("#ECCBAE", length(both_test))),
+        label_bottom = c(rep(NA, length(varied_train) + length(constant_train)*6), test_labels_bottom)
     )
@@
 
-create_plot <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test) {
-    data <- create_data(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test)
+create_plot <- function(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom) {
+    data <- create_data(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom)
     segments <- create_segments(data)
@@
                   color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+      geom_text(data = data, aes(x = x, y = 0.2, label = label_bottom),
+              color = "black", size = 4, vjust = 1.8, hjust = 0.5, fontface = "italic") +
         geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
@@
         theme_void() +
-        theme(legend.position = "none",
-              plot.margin = margin(10, 20, 10, 20),
-              plot.background = element_rect(fill = "white", color = NA),
-              panel.background = element_rect(fill = "white", color = NA))
+        theme(legend.position = "none")
 }
@@
 both_test <- c(1, 2, 3, 4, 5, 6) # Specify test positions
-igas_e2 <- create_plot(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test)
+test_labels_bottom <- c("400", "500", "625","675", "800", "900")
+igas_e2 <- create_plot(varied_train, constant_train1, constant_train2, constant_train3, constant_train4, constant_train5, constant_train6, both_test,test_labels_bottom)
 igas_e2
 
-ggsave(here::here("Presentation/assets/igas_e2_manip.png"), igas_e2, width = 7.5, height = 8, units = "in", dpi = 600)
+ggsave(here::here("Presentation/assets/igas_e2_manip.png"), igas_e2, width = 9, height = 6, units = "in", dpi = 300)
 

### 2024-05-28 Presentation/_hold_slides.qmd
fix slide image displays

--- 2024-05-28 Presentation/slides.qmd
@@
 ---
-title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
-page-layout: full
-aliases:
-  - /slides.html
-css: /Assets/Style/slides.css
-format-links: [clean-revealjs, pptx,gfm]
+title: My Slide Show
 format:
-  html: 
-    subtitle: "Dissertation Defense"
-  clean-revealjs:
-    #theme: moon #white
-    #output-ext: revealjs.html
-    # template-partials:
-    #   - assets/title-slide.html
-    output-file: slides_revealjs
-    date: 05/28/204
-    slideNumber: true
-    hash-type: number # Use slide numbers in the URL hash
-    center: true
-    scrollable: true
-    chalkboard:
-      theme: whiteboard
-  pptx:
-    incremental: false
-  hugo-md:
-    include: false
-    html-math-method: mathjax
-    output-file: slides_hugo.md
-  gfm:
-    output: false
-    output-file: slides_gfm.md
-author:
-  - name: Thomas Gorman
-    url: https://tegorman13.github.io
-    orcid: 0000-0001-5366-5442
-    affiliations:
-      - name: Indiana University
-        department: Psychological & Brain Sciences, Cognitive Science
-# params:
-#   start_slide: 
-#engine: knitr
+  revealjs: default
 ---
 
-{{< include /Presentation/embed_slides.qmd >}}
-
-# Learning Generalization
-
-- Learning is often specific
-- Longstanding scientific interest in how to improve generalization or transfer
-
-------------------------------------------------------------------------
-
-## Variability
-
-- Variation during training linked to improved transfer in numerous domains 
-- What does "variability mean in the context of learning interventions?"
-
-## Types of Variability
-
-- The number of unique items/problems experienced
-- How spread out examples are
-
-## My Dissertation Focus
-
-- Number of unique examples
-- Visuomotor skill learning and function learning
-
-- Addressing methodological shortcomings of previous work
-- Adapting cognitive models from other domains to account for results
-
-------------------------------------------------------------------------
-
-## Common Experimental Manipulations
-
-- Varied vs. Constant
-
-## Common Empirical Patterns
-
-:::::::::  columns
-::: {.column width="55%"}
-### Training
-- Both training conditions complete the same number of training trials.
-- Varied group has worse training performance.
-
-![](assets/train_pattern.png)
-:::
-
-::: {.column width="45%"} 
-::: {.fragment}
-### Testing
-
-- Tested from novel conditions.
-- Varied group has better test performance
-
-![](assets/test_pattern.png)
-:::
-:::
-:::::::::
-
-------------------------------------------------------------------------
-
-## But also plenty of contradictory results and complications
-
-- Cases where varied training doesn't benefit generalization
-- Cases where more training variation results in worse outcomes
-- Cases where the influence of variation interacts with some other factor
-    - difficulty
-    - prior knowledge
-    - Frequency effects, or amount of training/learning before testing
-
-------------------------------------------------------------------------
-
-## Theoretical Frameworks
-
--   Schema Theory (Schmidt, 1975)
--   Desirable Difficulties Framework (Bjork & Bjork, 2011)
--   Challenge Point Framework (Guadagnoli & Lee, 2004)
-
-::: footer
-@schmidtSchemaTheoryDiscrete1975 @bjorkMakingThingsHard2011 @guadagnoliChallengePointFramework2004
-:::
-
-<!-- ![](assets/fig-toy-model1-1-1.png) -->
-
-------------------------------------------------------------------------
-
-## Overview of Current Work
-
-### Project 1[^1]
-
-- Visuomotor projectile launching task
-- two experiments
-- Beneficial effect of variability
-- Instance-based similarity model
-
-### Project 2
-
-- Visuomotor extrapolation task
-- Three experiments
-- Effect of variability is null or negative
-- Connectionist model (ALM) and hybrid associative & rule model (EXAM)
-
-::: footer
-[^1]: Now published in Cognitive Psychology @gormanInstancebasedModelAccount2022
-:::
---
-
-# Project 1  - Issues with previous research
-
-- Assumptions about what is encoded
-- Assumptions about the formation of abstractions 
-- Aggregation issues and similarity confounds
-
----
-
-## designs that seemingly overcome these issues
-
-- Kerr & Booth 1978
-
-::: footer
-@kerrSpecificVariedPractice1978
-:::
-
-## Experiment 1
-
-- Conceptual replication of Kerr & Booth design 
-- Testing classic pattern as well
-
-------------------------------------------------------------------------
-
-## Hit The Target Task
-
-:::::: column-page-right
-::::: {.columns}
-:::: {.column width="60%"}
-
-::: {.content-visible when-format="html"}
-![](assets/htt_vid.mov){height="540" loop="true" autoplay="true" style="max-width: 100%"}
-:::
-
-::: {.content-visible unless-format="html"}
-![](assets/methodsFig1.png)
-:::
-
-::::
-
-:::: {.column width="40%"}
-- **Training Stage** - 200 training trials with feedback. Constant groups trains from single position. Varied group practices from two positions. 
-- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
-- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
-::::
-
-:::::
-::::::
-
-------------------------------------------------------------------------
-
-## Project 1 - Manipulations  {.smaller}
+## Project 1 - Design  {.nostretch .smaller}
 
 :::: {.columns}
-::: {.column width="50%"}
+::: {.column width="40%"}
 
-### Experiment 1
+### Experiment 1222
 - Train varied group from 2 positions, and a constant group from 1.
@@
 
-![](assets/igas_e1_manip.png)
+![](assets/igas_e1_manip.png){.absolute bottom=30 width="50%"}
 
@@
 
-::: {.column width="50%"}
+::: {.column width="60%"}
 ### Experiment 2
+
 - 6 distinct constant conditions
 
-![](assets/igas_e2_manip.png)
+![](assets/igas_e2_manip.png){.absolute bottom=0 width="90%"}
 :::
 
-::::
-
-------------------------------------------------------------------------
-
-## Project 1 - Experiment 1 Results
-
-:::: {.columns}
-::: {.column width="40%"}
-### Experiment 1
-![](assets/igas_e1_manip.png)
-:::
-::: {.column width="60%"}
-::: fragment
-### Training
-![](assets/htt_e1_train.png)
-:::
-::: fragment
-### Testing
-![](assets/fig-IGAS_Testing1-1-2.png)
-:::
-:::
-::::
-
-## Project 1 - Experiment 2 Results
-
-:::: {.columns}
-::: {.column width="40%"}
-### Experiment 1
-![](assets/igas_e2_manip.png)
-:::
-::: {.column width="60%"}
-::: fragment
-### Training
-![](assets/htt_e2_train.png)
-:::
-::: fragment
-### Testing
-![](assets/htt_e2_test.png)
-:::
-:::
-::::
-
-------------------------------------------------------------------------
-
-## Project 1 - Discussion
-
--   Varied training group's superior performance
--   Computational modeling results with IGAS
--   Theoretical implications
-
-------------------------------------------------------------------------
-
-## Project 1 Computational Model {.smaller .r-fit-text}
-
-:::: {.columns}
-::: {.column width="50%"}
-
-![](assets/sol_space2.png){width="65%"}
-![](assets/full_space2.png){width="50%"}
-:::
-
-::: {.column width="50%"}
-
-### Model Steps
-
-- each of the 6 positions has an empirical solution space
-- Compute the summed similarity between training throws, and solution spaces
-  - separately for each participant, and each of the testing positions
-- We now have a measure of how similar training behavior was to testing solutions
-
-### Model Definition
-
-- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
-- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
-
-:::
-::::
-
-## Project 1 Computational Model {.smaller .r-fit-text}
-
-:::: {.columns}
-::: {.column width="70%"}
-
-![](assets/sol_space.png)
-
-![](assets/full_space.png)
-:::
-::: {.column width="30%"}
-### Model Steps
-
-- each of the 6 positions has an empirical solution space
-- Compute the summed similarity between training throws, and solution spaces
-  - separately for each participant, and each of the testing positions
-- We now have a measure of how similar training behavior was to testing solutions
-
-### Model Definition
-
-- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
-- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
-:::
 ::::
@@
 ::::
-
-## Computational Model - Does Similarity Account for Effect of Variability?
-
-- Test whether similarity explains the difference in performance between Constant and Varied conditions
-  - Assuming equivalent generalization (1 c for both groups) - similarity improves model fit, but does not explain group difference
-  - Assume training condition influences generalization gradient (fit c separately) - now similarity does explain the difference between Constant and Varied.
-
-::: footer
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
-**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-:::
-
-## Project 1 General Discussion {.smaller .r-fit-text}
-
-------------------------------------------------------------------------
-
-# Project 2 - Variability and Extrapolation in a Function Learning Task
-
--   Influence of varied practice in a function learning task
--   Experiments 1, 2, and 3:
-    -   Training regimes and testing conditions
-    -   Learning, discrimination, and extrapolation performance metrics
-
-------------------------------------------------------------------------
-
-## Project 2 - Questions and Goals
-
-**Empirical**
-- Design a task-space large enough to assess multiple degrees of extrapolation 
-- Compare varied and constant generalization from several distinct distances from their nearest training condition
-
-**Model-based**
-- If variation does influence extrapolation, can an associative learning model with similarity-based activation provide a good account?
-- Can our modelling framework simultaneously account for both training and testing data?
-- Accounting for the full distribution of responses
-
-------------------------------------------------------------------------
-
-## Hit The Wall Task
-
-<!-- {{< video assets/htw_vid.mov width="720" height="540" >}} -->
-
-::: {.content-visible when-format="html"}
-![](assets/htw_vid.mov){height="400" loop="true" autoplay="true"}
-:::
-
-::: {.content-visible unless-format="html"}
-![](assets/htw_task_fig.png)
-:::
-
-- Target velocity presented at top of screen
-- Participants attempt to "hit the wall" at the correct velocity
-- Feedback during training - how many units above or below the target-band
-- Only the "x velocity" component of the throw is relevant to the task
-
-------------------------------------------------------------------------
-
-## Project 2 - Experiment 1 Design {.nostretch .smaller}
-
-:::: {.columns}
-::: {.column width="60%"}
-![](assets/htw_e1_manip.png){fig-align="left" fig-align="top" width="65%"}
-
-![](assets/e1_design.png){fig-align="left" fig-align="top" width="70%"}
-:::
-::: {.column width="40%"}
-
-- 156 participants included in final analysis
-- Varied group trains from 3 "velocity bands", constant group from 1
-:::
-::::
-
-------------------------------------------------------------------------
-
-## Project 2 - Experiment 1 Results {.nostretch}
-
-::: {.columns}
-::: {.column width="50%"}
-![Plot 1](assets/htw_e1_test1.png)
-![Plot 3](assets/htw_e1_test3.png)
-:::
-
-::: {.column width="50%"}
-![Plot 2](assets/htw_e1_test2.png)
-![Plot 4](assets/htw_e1_test4.png)
-:::
-:::
-
-## Project 2 - Experiment 2 Design {.smaller}
-
-:::: {.columns}
-::: {.column width="60%"}
-![](assets/htw_e2_manip.png){fig-align="left" fig-align="top"}
-
-![](assets/e2_design.png){fig-align="left" fig-align="top"}
-:::
-::: {.column width="40%"}
-
-<br><br><br><br>
-
-- Training and Testing bands are in reversed order, relative to Experiment 1
-- 110 participants included in final analysis
-
-:::
-::::
-
-## Project 2 - Experiment 2 Results {.nostretch}
-
-::: {.columns}
-::: {.column width="50%"}
-![Plot 1](assets/htw_e2_test1.png)
-![Plot 3](assets/htw_e2_test3.png)
-:::
-
-::: {.column width="50%"}
-![Plot 2](assets/htw_e2_test2.png)
-![Plot 4](assets/htw_e2_test4.png)
-:::
-:::
-
-## Project 2 - Experiment 3
-
-- Ordinal Feedback
-  - directional feedback indicating too high, too low, or correct
-- Both Original (Experiment 1), and reverse (Experiment 2) orders included
-- 195 participants included in final analysis
-
-## Project 2 - Experiment 3 Results {.nostretch}
-
-## Accuracy
-
-:::: {.columns}
-
-::: {.column width="50%"}
-![Plot 1](assets/htw_e3_test1.png)
-:::
-
-::: {.column width="50%"}
-![Plot 3](assets/htw_e3_test2.png)
-:::
-
-::::
-
-## Discrimination
-
-:::: {.columns}
-
-::: {.column width="50%"}
-![Plot 1](assets/htw_e3_test3.png)
-:::
-
-::: {.column width="50%"}
-![Plot 3](assets/htw_e3_test4.png)
-:::
-
-::::
-
-------------------------------------------------------------------------
-
-# Project 2 - Computational Modeling
-
-## Project 2 - ALM
-
-![](assets/fig-alm-diagram-1-1.png)
-
-------------------------------------------------------------------------
-
-## ALM
-
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-
-------------------------------------------------------------------------
-
-## EXAM
-
-|                    | **EXAM Response Generation**                                                                                     |                                                                                                               |
-|--------------------|-----------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------|
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                                                 | Novel test stimulus $X$ activates input nodes $X_i$                                                           |
-| Slope Computation  | $S = \frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                                                                     | Slope value, $S$ computed from nearest training instances                                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                                                                         | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$, adjusted by local slope $S$.
-|
-
-------------------------------------------------------------------------
-
-## Project 2 - Model Fitting Procedure {.r-fit-text}
-
-### Approximate Bayesian Computation
-
-:::: {.columns}
-
-::: {.column width="60%"}
-![](assets/abc_diagram1.png)
-:::
-
-::: {.column width="40%"}
-
-- simulation based approach
-- approximate likelihood
-- uncertainty in parameter values
-- full distribution of plausible model predictions for each participant
-
-:::
-
-::::
-
-## Modelling Results
-
-![](assets/fig-ee-e1-1.png)
-
-# General Discussion
-
--   Compare HTT and HTW
--   Empirical findings summary
--   Computational modeling contributions
-
-------------------------------------------------------------------------
-
-## Comparison {.smaller .r-fit-text}
-
-| Dimension | HTT (Project 1) | HTW (Project 2) |
-|----------------|--------------------------------|-------------------------|
-| Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
-| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
-| Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
-| Simpler: smooth, linear mapping between velocity and feedback.
-|
-| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
-salient differences in distance between launching box and target.
-| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
-|
-| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
-| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
-| Training Experience | Varied group gets half as much experience on any one position as the constant group.
-| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
-|
-| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
-
-------------------------------------------------------------------------
-
-## Conclusion
-
-## References
-::: {#refs}
-:::
-
-::: {.content-visible when-format="html"}
-## Manuscript {.scrollable .unnumbered .unlisted}
-
-```{=html}
-<iframe width="800" height="750" src="https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html" title="Webpage example"></iframe>
-```
-:::
-
-------------------------------------------------------------------------

### 2024-05-28 Presentation/slides.qmd
fix slide image displays

@@
 css: /Assets/Style/slides.css
+title-slide-attributes:
+  data-background-image: /Presentation/assets/sol_blank.png
+  data-background-size: 300px #contain
+  data-background-opacity: "0.15"
+  data-background-position: "0% 0%"
 format-links: [clean-revealjs, pptx,gfm]
@@
       theme: whiteboard
-  pptx:
-    incremental: false
-  hugo-md:
-    include: false
-    html-math-method: mathjax
-    output-file: slides_hugo.md
-  gfm:
-    output: false
-    output-file: slides_gfm.md
+  # pptx:
+  #   incremental: false
+  # hugo-md:
+  #   include: false
+  #   html-math-method: mathjax
+  #   output-file: slides_hugo.md
+  # gfm:
+  #   output: false
+  #   output-file: slides_gfm.md
+  # beamer:
+  #   incremental: false
+  #   colortheme: lily 
 author:
@@
 
-## Overview of Current Work
+## Overview of Current Work {.smaller}
 
@@
 ::: footer
-[^1]: Now published in Cognitive Psychology @gormanInstancebasedModelAccount2022
+[^1]: Now published in Cognitive Psychology [@gormanInstancebasedModelAccount2022]
 :::
@@
 
-## Hit The Target Task
+## Hit The Target Task {.smaller}
 
@@
 
-## Project 1 - Manipulations  {.smaller}
+## Experiment 1 Design {.smaller}
+
+![](assets/igas_e1_manip.png){fig-align="left" fig-align="top"}
+
+- Constant trains from one position (760)
+  - 200 trials
+- Varied trains from two positions (610 and 910)
+  - 100 trials per position
+- Both groups are tested from all three training positions, and a new position novel to both groups (835)
+
+------------------------------------------------------------------------
+
+## Project 1 - Experiment 1 Results {.smaller}
 
@@
 ::: {.column width="50%"}
-
-### Experiment 1
-- Train varied group from 2 positions, and a constant group from 1.
-- Test both groups from the trained positions - and 1 novel position
-
-![](assets/igas_e1_manip.png)
-
+::: fragment
+#### Training
+![](assets/htt_e1_train.png){width="95%"}
 :::
-
+:::
 ::: {.column width="50%"}
-### Experiment 2
-- 6 distinct constant conditions
-
-![](assets/igas_e2_manip.png)
-:::
-
-::::
-
-------------------------------------------------------------------------
-
-## Project 1 - Experiment 1 Results
-
-:::: {.columns}
-::: {.column width="40%"}
-### Experiment 1
-![](assets/igas_e1_manip.png)
-:::
-::: {.column width="60%"}
 ::: fragment
-### Training
-![](assets/htt_e1_train.png)
-:::
-::: fragment
-### Testing
-![](assets/fig-IGAS_Testing1-1-2.png)
+#### Testing
+![](assets/fig-IGAS_Testing1-1-2.png){width="95%"}
 :::
@@
 
+___
+
+## Experiment 2 Design
+
+![](assets/igas_e2_manip.png)
+
 ## Project 1 - Experiment 2 Results
@@
 :::: {.columns}
-::: {.column width="40%"}
-### Experiment 1
-![](assets/igas_e2_manip.png)
+::: {.column width="50%"}
+::: fragment
+#### Training {.smaller}
+![](assets/htt_e2_train.png){width="95%"}
 :::
-::: {.column width="60%"}
+:::
+::: {.column width="50%"}
+
 ::: fragment
-### Training
-![](assets/htt_e2_train.png)
-:::
-::: fragment
-### Testing
-![](assets/htt_e2_test.png)
+#### Testing {.smaller}
+![](assets/htt_e2_test.png){width="95%"}
 :::
@@
 ::: {.column width="30%"}
-### Model Steps
-
-- each of the 6 positions has an empirical solution space
-- Compute the summed similarity between training throws, and solution spaces
-  - separately for each participant, and each of the testing positions
-- We now have a measure of how similar training behavior was to testing solutions
-
-### Model Definition
-
-- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
-- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
-:::
-::::
-
-## Project 1 Computational Model {.smaller .r-fit-text}
-
-:::: {.columns}
-::: {.column width="60%"}
-### Solution Space
-![](assets/sol_space2.png)
-
-### Full Space
-:::{#fig-fullspace23}
-![](assets/full_space2.png)
-
-Full Space of Solution Throws and Missed Throws. Colored points represent coordinates of target hits, brown points are coordinates of misses
-:::
-
-:::
-
-::: {.column width="40%"}
-
 ### Model Steps
@@
 ::: {.column width="60%"}
-![](assets/htw_e1_manip.png){fig-align="left" fig-align="top" width="65%"}
+![](assets/htw_e1_manip.png){fig-align="left" fig-align="top"}
 
-![](assets/e1_design.png){fig-align="left" fig-align="top" width="70%"}
+![](assets/e1_design.png){fig-align="left" fig-align="top"}
 :::
@@
 
+<br><br><br>
 - 156 participants included in final analysis
@@
 
-## Project 2 - Experiment 1 Results {.nostretch}
+## Project 2 - Experiment 1 Results
 
@@
 ::: {.column width="50%"}
-![Plot 1](assets/htw_e1_test1.png)
-![Plot 3](assets/htw_e1_test3.png)
+![](assets/htw_e1_test1.png){width="70%"}
+![](assets/htw_e1_test3.png){width="70%"}
 :::
@@
 ::: {.column width="50%"}
-![Plot 2](assets/htw_e1_test2.png)
-![Plot 4](assets/htw_e1_test4.png)
+![](assets/htw_e1_test2.png){width="70%"}
+![](assets/htw_e1_test4.png){width="70%"}
 :::
@@
 
-## Project 2 - Experiment 2 Results {.nostretch}
+## Project 2 - Experiment 2 Results
 
@@
 ::: {.column width="50%"}
-![Plot 1](assets/htw_e2_test1.png)
-![Plot 3](assets/htw_e2_test3.png)
+![](assets/htw_e2_test1.png){width="75%"}
+![](assets/htw_e2_test3.png){width="75%"}
 :::
@@
 ::: {.column width="50%"}
-![Plot 2](assets/htw_e2_test2.png)
-![Plot 4](assets/htw_e2_test4.png)
+![](assets/htw_e2_test2.png){width="75%"}
+![](assets/htw_e2_test4.png){width="75%"}
 :::
@@
 ::: {.column width="50%"}
-![Plot 1](assets/htw_e3_test1.png)
+![](assets/htw_e3_test1.png){width="80%"}
 :::
@@
 ::: {.column width="50%"}
-![Plot 3](assets/htw_e3_test2.png)
+![](assets/htw_e3_test2.png){width="80%"}
 :::
@@
 ::: {.column width="50%"}
-![Plot 1](assets/htw_e3_test3.png)
+![](assets/htw_e3_test3.png){width="80%"}
 :::
@@
 ::: {.column width="50%"}
-![Plot 3](assets/htw_e3_test4.png)
+![](assets/htw_e3_test4.png){width="80%"}
 :::
@@
 ::: {.column width="60%"}
-![](assets/abc_diagram1.png)
+![](assets/abc_diagram1.png){width="80%"}
 :::
@@
 ::::
+
+---
 
@@
 
+___
+
+## Extras
+
+___
+
 ::: {.content-visible when-format="html"}

### 2024-05-28 Presentation/slides2.qmd
fix slide image displays

--- 2024-05-18 Presentation/slides2.qmd
@@
 title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
-subtitle: "Dissertation Defense"
+page-layout: full
+aliases:
+  - /slides.html
+css: /Assets/Style/slides.css
 format: 
-  html: default
+  # html: 
+  #   subtitle: "Dissertation Defense"
+  # clean-revealjs:
+  #   #theme: moon #white
+  #   #output-ext: revealjs.html
+  #   # template-partials:
+  #   #   - assets/title-slide.html
+  #   output-file: slides_revealjs
+  #   date: 05/28/204
+  #   slideNumber: true
+  #   hash-type: number # Use slide numbers in the URL hash
+  #   center: true
+  #   scrollable: true
+  #   chalkboard:
+  #     theme: whiteboard
+  # # pptx:
+  #   incremental: false
+  # hugo-md:
+  #   include: false
+  #   html-math-method: mathjax
+  #   output-file: slides_hugo.md
+  # gfm:
+  #   output: false
+  #   output-file: slides_gfm.md
+  beamer: default
+    # incremental: false
+    # colortheme: lily 
 author:
   - name: Thomas Gorman
-    orcid: 0000-0000-0000-0000
-    affiliations: Indiana University
+    url: https://tegorman13.github.io
+    orcid: 0000-0001-5366-5442
+    affiliations:
+      - name: Indiana University
+        department: Psychological & Brain Sciences, Cognitive Science
+# params:
+#   start_slide: 5
+#engine: knitr
 ---
 
+# Learning Generalization
+
+- Learning is often specific
+- Longstanding scientific interest in how to improve generalization or transfer
+
+------------------------------------------------------------------------
+
+## Variability
+
+- Variation during training linked to improved transfer in numerous domains 
+- What does "variability mean in the context of learning interventions?"
+
+## Types of Variability
+
+- The number of unique items/problems experienced
+- How spread out examples are
+
+## My Dissertation Focus
+
+- Number of unique examples
+- Visuomotor skill learning and function learning
+
+- Addressing methodological shortcomings of previous work
+- Adapting cognitive models from other domains to account for results
+
+------------------------------------------------------------------------
+
+## Common Experimental Manipulations
+
+- Varied vs. Constant
+
+## Common Empirical Patterns
+
+:::::::::  columns
+::: {.column width="55%"}
+### Training
+- Both training conditions complete the same number of training trials.
+- Varied group has worse training performance.
+
+![](assets/train_pattern.png)
+:::
+
+::: {.column width="45%"} 
+::: {.fragment}
+### Testing
+
+- Tested from novel conditions.
+- Varied group has better test performance
+
+![](assets/test_pattern.png)
+:::
+:::
+:::::::::
+
+------------------------------------------------------------------------
+
+## But also plenty of contradictory results and complications
+
+- Cases where varied training doesn't benefit generalization
+- Cases where more training variation results in worse outcomes
+- Cases where the influence of variation interacts with some other factor
+    - difficulty
+    - prior knowledge
+    - Frequency effects, or amount of training/learning before testing
+
+------------------------------------------------------------------------
+
+## Theoretical Frameworks
+
+-   Schema Theory (Schmidt, 1975)
+-   Desirable Difficulties Framework (Bjork & Bjork, 2011)
+-   Challenge Point Framework (Guadagnoli & Lee, 2004)
+
+::: footer
+@schmidtSchemaTheoryDiscrete1975 @bjorkMakingThingsHard2011 @guadagnoliChallengePointFramework2004
+:::
+
+<!-- ![](assets/fig-toy-model1-1-1.png) -->
+
+------------------------------------------------------------------------
+
+## Overview of Current Work
+
+### Project 1[^1]
+
+- Visuomotor projectile launching task
+- two experiments
+- Beneficial effect of variability
+- Instance-based similarity model
+
+### Project 2
+
+- Visuomotor extrapolation task
+- Three experiments
+- Effect of variability is null or negative
+- Connectionist model (ALM) and hybrid associative & rule model (EXAM)
+
+--
+
+# Project 1  - Issues with previous research
+
+- Assumptions about what is encoded
+- Assumptions about the formation of abstractions 
+- Aggregation issues and similarity confounds
+
+---
+
+## designs that seemingly overcome these issues
+
+- Kerr & Booth 1978
+
+## Experiment 1
+
+- Conceptual replication of Kerr & Booth design 
+- Testing classic pattern as well
+
+------------------------------------------------------------------------
+
+## Hit The Target Task
+
+:::::: {column-page-right}
+::::: {.columns}
+:::: {.column width="60%"}
+
 ::: {.content-visible when-format="html"}
+![](assets/htt_vid.mov){height="540" loop="true" autoplay="true" style="max-width: 100%"}
+:::
 
-<div class="ratio ratio-16x9"> <iframe src="/Presentation/slides_revealjs.html"></iframe> </div>
+::: {.content-visible unless-format="html"}
+![](assets/methodsFig1.png)
+:::
 
-test
+::::
+
+:::: {.column width="40%"}
+- **Training Stage** - 200 training trials with feedback. Constant groups trains from single position. Varied group practices from two positions. 
+- **Transfer Stage** - All subjects tested from both positions they were trained, and the positions trained by other group
+- **Data recorded** - For every throw, recorded the X velocity and Y velocity of ball at release
+::::
+
+:::::
+::::::
+
+------------------------------------------------------------------------
+
+------------------------------------------------------------------------
+
+## Project 1 - Experiment 1 Results {.nostretch .smaller}
+
+:::: {.columns}
+::: {.column width="40%"}
+### Experiment 1
+![](assets/igas_e1_manip.png)
 :::
+::: {.column width="60%"}
+::: fragment
+### Training
+![](assets/htt_e1_train.png)
+:::
+::: fragment
+### Testing
+![](assets/fig-IGAS_Testing1-1-2.png)
+:::
+:::
+::::
+
+## Project 1 - Experiment 2 Results
+
+:::: {.columns}
+::: {.column width="40%"}
+### Experiment 1
+![](assets/igas_e2_manip.png)
+:::
+::: {.column width="60%"}
+::: fragment
+### Training
+![](assets/htt_e2_train.png)
+:::
+::: fragment
+### Testing
+![](assets/htt_e2_test.png)
+:::
+:::
+::::
+
+------------------------------------------------------------------------
+
+## Project 1 - Discussion
+
+-   Varied training group's superior performance
+-   Computational modeling results with IGAS
+-   Theoretical implications
+
+------------------------------------------------------------------------
+
+## Project 1 Computational Model {.smaller .r-fit-text}
+
+:::: {.columns}
+::: {.column width="50%"}
+
+![](assets/sol_space2.png){width="65%"}
+![](assets/full_space2.png){width="50%"}
+:::
+
+::: {.column width="50%"}
+
+### Model Steps
+
+- each of the 6 positions has an empirical solution space
+- Compute the summed similarity between training throws, and solution spaces
+  - separately for each participant, and each of the testing positions
+- We now have a measure of how similar training behavior was to testing solutions
+
+### Model Definition
+
+- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
+- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
+
+:::
+::::
+
+## Project 1 Computational Model {.smaller .r-fit-text}
+
+:::: {.columns}
+::: {.column width="70%"}
+
+![](assets/sol_space.png)
+
+![](assets/full_space.png)
+:::
+::: {.column width="30%"}
+### Model Steps
+
+- each of the 6 positions has an empirical solution space
+- Compute the summed similarity between training throws, and solution spaces
+  - separately for each participant, and each of the testing positions
+- We now have a measure of how similar training behavior was to testing solutions
+
+### Model Definition
+
+- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
+- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
+:::
+::::
+
+## Project 1 Computational Model {.smaller .r-fit-text}
+
+:::: {.columns}
+::: {.column width="60%"}
+
+### Solution Space
+![](assets/sol_space2.png)
+
+### Full Space
+
+![](assets/full_space2.png)
+
+:::
+
+::: {.column width="40%"}
+
+### Model Steps
+
+- each of the 6 positions has an empirical solution space
+- Compute the summed similarity between training throws, and solution spaces
+  - separately for each participant, and each of the testing positions
+- We now have a measure of how similar training behavior was to testing solutions
+
+### Model Definition
+
+- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
+- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
+:::
+::::
+
+## Computational Model - Does Similarity Account for Effect of Variability?
+
+- Test whether similarity explains the difference in performance between Constant and Varied conditions
+  - Assuming equivalent generalization (1 c for both groups) - similarity improves model fit, but does not explain group difference
+  - Assume training condition influences generalization gradient (fit c separately) - now similarity does explain the difference between Constant and Varied.
+
+::: footer
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
+**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+:::
+
+## Project 1 General Discussion {.smaller .r-fit-text}
+
+------------------------------------------------------------------------
+
+# Project 2 - Variability and Extrapolation in a Function Learning Task
+
+-   Influence of varied practice in a function learning task
+-   Experiments 1, 2, and 3:
+    -   Training regimes and testing conditions
+    -   Learning, discrimination, and extrapolation performance metrics
+
+------------------------------------------------------------------------
+
+## Project 2 - Questions and Goals
+
+**Empirical**
+- Design a task-space large enough to assess multiple degrees of extrapolation 
+- Compare varied and constant generalization from several distinct distances from their nearest training condition
+
+**Model-based**
+- If variation does influence extrapolation, can an associative learning model with similarity-based activation provide a good account?
+- Can our modelling framework simultaneously account for both training and testing data?
+- Accounting for the full distribution of responses
+
+------------------------------------------------------------------------
+
+## Hit The Wall Task
+
+<!-- {{< video assets/htw_vid.mov width="720" height="540" >}} -->
+
+::: {.content-visible when-format="html"}
+![](assets/htw_vid.mov){height="400" loop="true" autoplay="true"}
+:::
+
+::: {.content-visible unless-format="html"}
+![](assets/htw_task_fig.png)
+:::
+
+- Target velocity presented at top of screen
+- Participants attempt to "hit the wall" at the correct velocity
+- Feedback during training - how many units above or below the target-band
+- Only the "x velocity" component of the throw is relevant to the task
+
+------------------------------------------------------------------------
+
+## Project 2 - Experiment 1 Design {.nostretch .smaller}
+
+:::: {.columns}
+::: {.column width="60%"}
+![](assets/htw_e1_manip.png)
+
+![](assets/e1_design.png)
+:::
+::: {.column width="40%"}
+
+- 156 participants included in final analysis
+- Varied group trains from 3 "velocity bands", constant group from 1
+:::
+::::
+
+------------------------------------------------------------------------
+
+## Project 2 - Experiment 1 Results {.nostretch}
+
+::: {.columns}
+::: {.column width="50%"}
+![Plot 1](assets/htw_e1_test1.png)
+![Plot 3](assets/htw_e1_test3.png)
+:::
+
+::: {.column width="50%"}
+![Plot 2](assets/htw_e1_test2.png)
+![Plot 4](assets/htw_e1_test4.png)
+:::
+:::
+
+## Project 2 - Experiment 2 Design {.smaller}
+
+:::: {.columns}
+::: {.column width="60%"}
+![](assets/htw_e2_manip.png)
+
+![](assets/e2_design.png)
+:::
+::: {.column width="40%"}
+
+<br><br><br><br>
+
+- Training and Testing bands are in reversed order, relative to Experiment 1
+- 110 participants included in final analysis
+
+:::
+::::
+
+## Project 2 - Experiment 2 Results {.nostretch}
+
+::: {.columns}
+::: {.column width="50%"}
+![Plot 1](assets/htw_e2_test1.png)
+![Plot 3](assets/htw_e2_test3.png)
+:::
+
+::: {.column width="50%"}
+![Plot 2](assets/htw_e2_test2.png)
+![Plot 4](assets/htw_e2_test4.png)
+:::
+:::
+
+## Project 2 - Experiment 3
+
+- Ordinal Feedback
+  - directional feedback indicating too high, too low, or correct
+- Both Original (Experiment 1), and reverse (Experiment 2) orders included
+- 195 participants included in final analysis
+
+## Project 2 - Experiment 3 Results {.nostretch}
+
+## Accuracy
+
+:::: {.columns}
+
+::: {.column width="50%"}
+![Plot 1](assets/htw_e3_test1.png)
+:::
+
+::: {.column width="50%"}
+![Plot 3](assets/htw_e3_test2.png)
+:::
+
+::::
+
+## Discrimination
+
+:::: {.columns}
+
+::: {.column width="50%"}
+![Plot 1](assets/htw_e3_test3.png)
+:::
+
+::: {.column width="50%"}
+![Plot 3](assets/htw_e3_test4.png)
+:::
+
+::::
+
+------------------------------------------------------------------------
+
+# Project 2 - Computational Modeling
+
+## Project 2 - ALM
+
+![](assets/fig-alm-diagram-1-1.png)
+
+------------------------------------------------------------------------
+
+## ALM
+
+|                    | **ALM Response Generation**                                        |                                                                                               |
+|------------------|-----------------------------|-------------------------|
+| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
+| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
+| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
+| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
+|                    | **ALM Learning**                                                   |                                                                                               |
+| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
+| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
+| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
+
+------------------------------------------------------------------------
+
+## EXAM
+
+|                    | **EXAM Response Generation**                                                                                     |                                                                                                               |
+|--------------------|-----------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------|
+| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                                                 | Novel test stimulus $X$ activates input nodes $X_i$                                                           |
+| Slope Computation  | $S = \frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                                                                     | Slope value, $S$ computed from nearest training instances                                                     |
+| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                                                                         | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$, adjusted by local slope $S$.
+|
+
+------------------------------------------------------------------------
+
+## Project 2 - Model Fitting Procedure {.r-fit-text}
+
+### Approximate Bayesian Computation
+
+:::: {.columns}
+
+::: {.column width="60%"}
+![](assets/abc_diagram1.png)
+:::
+
+::: {.column width="40%"}
+
+- simulation based approach
+- approximate likelihood
+- uncertainty in parameter values
+- full distribution of plausible model predictions for each participant
+
+:::
+
+::::
+
+----
+
+## Modelling Results
+
+![](assets/fig-ee-e1-1.png)
+
+# General Discussion
+
+-   Compare HTT and HTW
+-   Empirical findings summary
+-   Computational modeling contributions
+
+------------------------------------------------------------------------
+
+## Comparison {.smaller .r-fit-text}
+
+| Dimension | HTT (Project 1) | HTW (Project 2) |
+|----------------|--------------------------------|-------------------------|
+| Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
+| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
+| Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
+| Simpler: smooth, linear mapping between velocity and feedback.
+|
+| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
+salient differences in distance between launching box and target.
+| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
+|
+| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
+| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
+| Training Experience | Varied group gets half as much experience on any one position as the constant group.
+| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
+|
+| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
+
+------------------------------------------------------------------------
+
+## Conclusion
+
+## References
+::: {#refs}
+:::

### 2024-05-28 Presentation/_fig_creation.qmd
update slides

@@
 walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
+
+```
+
+```{r}
+
+library(ggplot2)
+
+# Generate distance values
+distance <- seq(0, 10, length.out = 100)
+
+# Define the c parameter values
+c_values <- c(0.08, 0.5, 1)
+
+# Calculate similarity for each c value
+similarity_data <- data.frame(
+  distance = rep(distance, length(c_values)),
+  c = factor(rep(c_values, each = length(distance))),
+  similarity = exp(-rep(c_values, each = length(distance)) * distance^2)
+)
+
+# Create the faceted plot
+c_example <- ggplot(similarity_data, aes(x = distance, y = similarity)) +
+  geom_line(linewidth = 1) +
+  labs(x = "Distance", y = "Similarity") +
+  #scale_color_manual(values = c("blue", "green", "red")) +
+  facet_wrap(~ c, ncol = 3, labeller = labeller(c = function(x) paste("c =", x))) +
+  theme_minimal() +
+  theme(
+    # plot.title = element_text(hjust = 0.5, size = 14, face = "plain"),
+    # axis.title = element_text(size = 12),
+    legend.position = "none",
+    strip.text = element_text(size = 12)
+  ) +
+  ggtitle("Gaussian Similarity Decay")
+
+ggsave(here::here("Presentation/assets/c_example.png"), c_example, width = 4.0, height = 3, units = "in", dpi = 600)
 

### 2024-05-28 Presentation/_hold_slides.qmd
update slides

@@
 ---
+
+## designs that seemingly overcome these issues
+
+- Kerr & Booth 1978
+
+::: footer
+@kerrSpecificVariedPractice1978
+:::
 
@@
 ::::
+
+## Project 1 Computational Model {.smaller .r-fit-text}
+
+:::: {.columns}
+::: {.column width="70%"}
+
+![](assets/sol_space.png)
+
+![](assets/full_space.png)
+:::
+::: {.column width="30%"}
+### Model Steps
+
+- each of the 6 positions has an empirical solution space
+- Compute the summed similarity between training throws, and solution spaces
+  - separately for each participant, and each of the testing positions
+- We now have a measure of how similar training behavior was to testing solutions
+
+### Model Definition
+
+- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
+- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
+:::
+::::
+
+## Computational Model - Does Similarity Account for Effect of Variability?
+
+- Test whether similarity explains the difference in performance between Constant and Varied conditions
+  - Assuming equivalent generalization (1 c for both groups) - similarity improves model fit, but does not explain group difference
+  - Assume training condition influences generalization gradient (fit c separately) - now similarity does explain the difference between Constant and Varied.
+
+::: footer
+**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
+**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+:::
+
+## Project 1 General Discussion {.smaller .r-fit-text}
+
+------------------------------------------------------------------------

### 2024-05-28 Presentation/slides.qmd
update slides

@@
 
-## Theoretical Frameworks
+## Overview {.smaller}
 
--   Schema Theory (Schmidt, 1975)
--   Desirable Difficulties Framework (Bjork & Bjork, 2011)
--   Challenge Point Framework (Guadagnoli & Lee, 2004)
-
-::: footer
-@schmidtSchemaTheoryDiscrete1975 @bjorkMakingThingsHard2011 @guadagnoliChallengePointFramework2004
-:::
-
-<!-- ![](assets/fig-toy-model1-1-1.png) -->
-
-------------------------------------------------------------------------
-
-## Overview of Current Work {.smaller}
-
-### Project 1[^1]
+### Project 1
 
@@
 
+------------------------------------------------------------------------
+
+---
+
+## Project 1 
+<br>
+
+### An instance-based model account of the benefits of varied practice in visuomotor skill[^1]
+
+<br><br><br>
+
 ::: footer
-[^1]: Now published in Cognitive Psychology [@gormanInstancebasedModelAccount2022]
+[^1]: Now published in Cognitive Psychology -  [@gormanInstancebasedModelAccount2022]
 :::
---
 
-# Project 1  - Issues with previous research
+---
+
+## Theoretical Frameworks
+
+<br>
+
+::: {.fragment .semi-fade-out}
+- Desirable Difficulties Framework (Bjork & Bjork, 2011)
+<br>  
+- Challenge Point Framework (Guadagnoli & Lee, 2004)
+::: 
+- Schema Theory (Schmidt, 1975)
+
+::: footer
+@schmidtSchemaTheoryDiscrete1975 @bjorkMakingThingsHard2011 @guadagnoliChallengePointFramework2004
+:::
+
+::: notes
+Variety of theoretical explanations
+Schema theory in paticular has been extremely influential 
+:::
+
+___
+
+## Issues with previous research
 
@@
 
+::: fragment
+:::: columns
+::: {.column}
+
+![](assets/agg_issues.png)
+:::
+::: {.column}
+<br>
+
+-  If generalization decays exponentially with distance, constant groups 1 and 2 may have far less generalization potential to the testing condition. 
+- performance of individual constant groups often not reported in analyses.
+
+:::
+
+::::
+:::
+::: footnote
+e.g. [@mccrackenTestSchemaTheory1977; @chuaPracticeVariabilityPromotes2019; @delreyEffectsContextualInterference1982]
+:::
+
 ---
 
-## designs that seemingly overcome these issues
+## Designs that avoid similarity issue
 
-- Kerr & Booth 1978
+### Kerr & Booth 1978
 
+:::: columns
+::: {.column}
+![](assets/kerr_booth.png)
+:::
+::: {.column}
+- bean bag throwing task
+- Constant and varied conditions train from distinct positions
+- Both groups are tested from the position where the constant group trained
+- Impressive demonstration of varied training outperforming constant training 
+:::
+::::
 ::: footer
@@
 
+---
+
 ## Experiment 1
@@
 - Conceptual replication of Kerr & Booth design 
-- Testing classic pattern as well
+- Also test positions novel to both groups
+- Validate computerized visuomotor learning task
+
+## Experiment 1 Design {.smaller}
+
+![](assets/igas_e1_manip.png){fig-align="left" fig-align="top"}
+
+- Constant trains from one position (760)
+  - 200 trials
+- Varied trains from two positions (610 and 910)
+  - 100 trials per position
+- Both groups are tested from all three training positions, and a new position novel to both groups (835)
 
@@
 
+::: notes
+- Use mouse to flick the ball towards the target
+- Must release from orange square
+- Subjects have flexibility in terms of trajectory and release point inside the square
+- Nicety of computerized task - we record the precise details easily
+:::
+
 ------------------------------------------------------------------------
-
-## Experiment 1 Design {.smaller}
-
-![](assets/igas_e1_manip.png){fig-align="left" fig-align="top"}
-
-- Constant trains from one position (760)
-  - 200 trials
-- Varied trains from two positions (610 and 910)
-  - 100 trials per position
-- Both groups are tested from all three training positions, and a new position novel to both groups (835)
 
@@
 
+::: notes
+Varied training significantly better at the position that was novel for all subjects. Also better even at the position that the constant group trained at.
+
+4 different positions, the varied group trained from the easiest and the hardest position, they also interpolated the constant group. 
+:::
+
 ___
@@
 ![](assets/igas_e2_manip.png)
+
+::: notes
+task mostly the same - minor adjustments to barrier
+6 different constant groups
+varied group doesn't train on either the easiest or the hardest position
+
+larger design to give us more data to work with for modelling
+:::
 
@@
 
+::: notes
+
+- This time we can compare varied and constant training - by just comparing the varied group to
+the 2 constant groups that trained at the same locations
+- Here we have all 6 of the constant groups collapsed together
+- also did more fine grained grained comparisons
+
+:::
+
 ------------------------------------------------------------------------
 
-## Project 1 - Discussion
+## Project 1 Computational Model {.smaller .r-fit-text}
 
--   Varied training group's superior performance
--   Computational modeling results with IGAS
--   Theoretical implications
+### Instance encoding, and similarity-based generalization assumptions
 
-------------------------------------------------------------------------
+- instances refers to individual throws (x and y velocity)
+- similarity refers to the distance between training throws and the solution space of each of the eventual testing positions.
+
+___
 
@@
 
-### Model Steps
+### Computing Similarity
 
-- each of the 6 positions has an empirical solution space
-- Compute the summed similarity between training throws, and solution spaces
+- Euclidean distance between each training throw, and each solution space
   - separately for each participant, and each of the testing positions
-- We now have a measure of how similar training behavior was to testing solutions
+- Similarity computed as a Gaussian decay function of distance, i.e. larger distances result in lower similarity
+- Each participant gets their own similarity score for each of the 6 testing positions
+  - similarity score for a given testing position is the sum of the similarities between each training throw and the entire empirical solution space
 
@@
 
-## Project 1 Computational Model {.smaller .r-fit-text}
+## Non-linear similarity
 
-:::: {.columns}
-::: {.column width="70%"}
+![](assets/c_example.png)
 
-![](assets/sol_space.png)
+___
 
-![](assets/full_space.png)
-:::
-::: {.column width="30%"}
-### Model Steps
+## Does this similarity metric work?
 
-- each of the 6 positions has an empirical solution space
-- Compute the summed similarity between training throws, and solution spaces
-  - separately for each participant, and each of the testing positions
-- We now have a measure of how similar training behavior was to testing solutions
+- Our similarity measure does is a significant predictor of testing performance. 
+  - Remains significant when controlling for training accuracy, and training condition.
 
-### Model Definition
+___
 
-- $d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 }$
-- $Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}})$
-:::
-::::
+## Accounting for group-level effect {.smaller}
 
-## Computational Model - Does Similarity Account for Effect of Variability?
-
-- Test whether similarity explains the difference in performance between Constant and Varied conditions
-  - Assuming equivalent generalization (1 c for both groups) - similarity improves model fit, but does not explain group difference
-  - Assume training condition influences generalization gradient (fit c separately) - now similarity does explain the difference between Constant and Varied.
-
-::: footer
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
-**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+::: fragment
+- The base version of the model fit a single $c$ parameter 
+  - thus assuming that everyone generalizes to the same degree
 :::
 
-## Project 1 General Discussion {.smaller .r-fit-text}
+::: fragment
+- We next fit a 2-c version, separately optimizing for varied and constant groups, resulting in new 2-c similarity scores for each participant. 
+  - The optimal c value for the varied group is smaller than that of the constant group, indicative of broader generalization. 
+:::
 
-------------------------------------------------------------------------
+::: fragment
+- When 2-c similarity is added to the linear model predicting testing performance as a function of condition, the effect of training condition is no longer significant. 
+  - not the case with the original 1-c similarities. 
+:::
 
-# Project 2 - Variability and Extrapolation in a Function Learning Task
+::: fragment  
+- Thus the influence of varied training can be explained by an instance-based similarity model, IF one assumes flexibility in the generalization gradient. 
+:::
+
+## Conclusions
+
+::: fragment 
+- New empirical support for a benefit of variability in visuomotor skill tasks
+:::
+
+::: fragment 
+- Some support for the less common pattern observed by @kerrSpecificVariedPractice1978
+:::
+
+::: fragment 
+- Demonstrated the utility of a similarity based approach in this domain
+:::
+
+---
+
+# Project 2
+
+---
+
+## Project 2
+
+### Impact of Training Variability on Visuomotor Function Learning and Extrapolation
 
@@
 ::: {.column width="50%"}
-![](assets/htw_e2_test1.png){width="75%"}
-![](assets/htw_e2_test3.png){width="75%"}
+![](assets/htw_e2_test1.png){width="75%" .fragment fragment-index=1}
+![](assets/htw_e2_test3.png){width="75%" .fragment fragment-index=2}
 :::
@@
 ::: {.column width="50%"}
-![](assets/htw_e2_test2.png){width="75%"}
-![](assets/htw_e2_test4.png){width="75%"}
+![](assets/htw_e2_test2.png){width="75%" .fragment fragment-index=1}
+![](assets/htw_e2_test4.png){width="75%" .fragment fragment-index=2}
 :::
@@
 
-## Accuracy
+## Experiment 3 - Accuracy
 
@@
 
-## Discrimination
+## Experiment 3 - Discrimination
 

### 2024-05-28 Presentation/_hold_slides.qmd
update slides

@@
 
-------------------------------------------------------------------------
+---------------------------------------------------------
+
+---------------
+
+## Project 2 - Experiment 2 Results
+
+::: {.columns}
+::: {.column width="50%"}
+![](assets/htw_e2_test1.png){width="75%"}
+![](assets/htw_e2_test3.png){width="75%"}
+:::
+
+::: {.column width="50%"}
+![](assets/htw_e2_test2.png){width="75%"}
+![](assets/htw_e2_test4.png){width="75%"}
+:::
+:::
+
+## Project 2 - Experiment 2 Results {.smaller margin="0"}
+
+::: {.columns}
+::: {.column width="50%"}
+![](assets/htw_e2_test1.png){width=65%"}
+:::
+::: {.column width="50%"}
+![](assets/htw_e2_test2.png){width="65%"}
+:::
+:::
+
+::: fragment
+::: {.columns}
+::: {.column width="50%"}
+
+![](assets/htw_e2_test3.png){width="65%"}
+:::
+::: {.column width="50%"}
+![](assets/htw_e2_test4.png){width="65%"}
+:::
+:::
+:::

### 2024-05-28 Presentation/slides.qmd
update slides

@@
     output-file: slides_revealjs
-    date: 05/28/204
+    date: 05/28/2024
     slideNumber: true
@@
       theme: whiteboard
-  # pptx:
-  #   incremental: false
-  # hugo-md:
-  #   include: false
-  #   html-math-method: mathjax
-  #   output-file: slides_hugo.md
-  # gfm:
-  #   output: false
-  #   output-file: slides_gfm.md
+  pptx:
+    incremental: false
+  hugo-md:
+    include: false
+    html-math-method: mathjax
+    output-file: slides_hugo.md
+  gfm:
+    output: false
+    output-file: slides_gfm.md
   # beamer:
@@
 
-## Issues with previous research
+## Issues with previous research {.smaller}
 
@@
 ::: {.column}
-- bean bag throwing task
+- Bean bag tossing task
 - Constant and varied conditions train from distinct positions
@@
 
-- instances refers to individual throws (x and y velocity)
-- similarity refers to the distance between training throws and the solution space of each of the eventual testing positions.
+- Instances refers to individual throws (x and y velocity)
+- Similarity refers to the distance between training throws and the solution space of each of the eventual testing positions.
 
@@
 
-## Project 1 Computational Model {.smaller .r-fit-text}
+## Project 1 Computational Model {.smaller}
 
@@
 
-### Computing Similarity
+#### Computing Similarity
 
@@
 
-### Model Definition
+#### Model Definition
 
@@
 
-## Hit The Wall Task
+## Hit The Wall Task {.smaller}
 
@@
 <br><br><br>
+
 - 156 participants included in final analysis
 - Varied group trains from 3 "velocity bands", constant group from 1
+- Both groups complete same total number of training trials
 :::
@@
 
-## Project 2 - ALM
+## The Associative Learning Model ALM {.smaller}
 
+:::: {.columns}
+
+::: {.column width="70%"}
 ![](assets/fig-alm-diagram-1-1.png)
-
+:::
+::: {.column width="30%"}
+- Two layer network - adapted from ALCOVE (@kruschkeALCOVEExemplarbasedConnectionist1992)
+- Input layer node for each stimulus, output node for each response 
+- Input nodes activate as a function of their Gaussian similarity to the stimulus
+- Weights udpated via delta rule - error driven learning
+- Provides good account of human learning data, and interpolation performance, but struggles with extrapolation [@deloshExtrapolationSineQua1997]
+:::
+::::
 ------------------------------------------------------------------------
 
-## ALM
+## Extrapolation - Association Model (EXAM) {.smaller}
 
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-
-------------------------------------------------------------------------
-
-## EXAM
+- Extension to ALM to account for human extrapolation behavior 
+- When a novel stimulus is presented, EXAM assumes the nearest 2-3 prior examples are retrieved, and used to compute a slope
+- The slope is used to adjust the ALM response
 
@@
 |--------------------|-----------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------|
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                                                 | Novel test stimulus $X$ activates input nodes $X_i$                                                           |
 | Slope Computation  | $S = \frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                                                                     | Slope value, $S$ computed from nearest training instances                                                     |
@@
 
-## Project 2 - Model Fitting Procedure {.r-fit-text}
+## Project 2 - Model Fitting Procedure {.smaller}
 
-### Approximate Bayesian Computation
+### Approximate Bayesian Computation (ABC)
 
@@
 
-- simulation based approach
-- approximate likelihood
-- uncertainty in parameter values
+- simulation based parameter estimation [@turnerTutorialApproximateBayesian2012; @kangasraasioParameterInferenceComputational2019]
+- Useful for models with unknown likelihood functions (e.g. many neural network and drift diffusion models)
 - full distribution of plausible model predictions for each participant
@@
 
+## Project 2 - Model Fitting Procedure {.smaller}
+
+### Model Fitting Approach
+
+- Two parameters for both ALM and EXAM
+  - generalization parameter: $c$
+  - learning rate parameter: $lr$
+
+- ALM and EXAM fit separately to each individual participant
+- Rejection based ABC used to obtain 200 posterior samples, per participant, per model 
+  - i.e. 200 plausible values of $c$ and $lr$
+
+- All models fit with three different approaches
+    1) Fit to only the training data
+    2) Fit to both training and testing data
+    3) Fit to only testing data
+
 ---
 
-## Modelling Results
+## Modelling Results {.smaller}
 
-![](assets/fig-ee-e1-1.png)
+#### Posterior Predictive Distribution
+
+![](assets/post_pred_e1.png)
+
+::: notes
+ Empirical data and Model predictions for mean velocity across target bands.
+Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs.
+Varied) are separated by columns.
+Each facet contains the predictions of ALM and EXAM, alongside the observed data.
+:::
+
+## Model Comparison - Experiment 1
+
+![](assets/model_reg_e1.png)
+
+::: notes
+Figure 21: A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+Varied).
+Lower values on the y axis indicate better model fit.
+D) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs.
+EXAM for the varied group; 3) ALM fits between constant and varied.
+Negative error differences indicate that the term on the left side (e.g., EXAM Constant) tended to have smaller model residuals.
+:::
+
+## Model Comparison - Experiment 2 and 3
+
+![](assets/fig-e2_e3_ae-1.png)
+
+::: notes
+Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
+Varied) on Model Error for Experiment 2 and 3 data.
+Experiment 3 also includes a control for the order of training vs.
+testing bands (original order vs.
+reverse order).
+:::
+
+___
+
+## Modelling Results {.smaller}
+
+### Best fitting models per participant
+
+![](assets/best_models.png)
+
+::: notes
+Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM
+:::
+
+___
 
@@
 ------------------------------------------------------------------------
+
+## ALM {.scrollable .unnumbered .unlisted}
+
+|                    | **ALM Response Generation**                                        |                                                                                               |
+|------------------|-----------------------------|-------------------------|
+| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
+| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
+| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
+| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
+|                    | **ALM Learning**                                                   |                                                                                               |
+| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
+| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
+| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
+
+------------------------------------------------------------------------
+
+## EXAM {.scrollable .unnumbered .unlisted}
+
+|                    | **EXAM Response Generation**                                                                                     |                                                                                                               |
+|--------------------|-----------------------------------------------------------------------------------------------------------------|---------------------------------------------------------------------------------------------------------------|
+| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                                                                 | Novel test stimulus $X$ activates input nodes $X_i$                                                           |
+| Slope Computation  | $S = \frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                                                                     | Slope value, $S$ computed from nearest training instances                                                     |
+| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                                                                         | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$, adjusted by local slope $S$.
+|
+
+------------------------------------------------------------------------

### 2024-05-28 Presentation/_fig_creation.qmd
update slides again

@@
 ```
+
+Slide 1: Key Points from the General Discussion
+
+Slide 2: Key Points from the General Discussion (cont.)
+
+- HTT and HTW tasks differ in perceptual salience of varied conditions, task complexity, and task space.
+- In HTT, varied conditions (throwing distances) are perceptually distinct, while in HTW, varied conditions (velocity bands) are less salient.
+- HTT has a more complex parabolic trajectory and task space, while HTW has a simpler 1D mapping of force to outcome.
+- The contrasting results highlight the importance of considering task characteristics when designing experiments to assess the influence of training interventions.
+- Combining empirical and computational modeling approaches can help uncover the cognitive mechanisms supporting learning and generalization.
+- Future research should continue to investigate the interplay between task demands, training manipulations, and individual differences to optimize educational and training outcomes.
+
+### Slide 1: Empirical and Modeling Summary
+
+**Bullet Points:**
+
+- **Project Comparison**:
+  - **HTT (Project 1)**: Varied training led to superior testing performance.
+  - **HTW (Project 2)**: Varied training led to poorer performance.
+
+- **Key Findings**:
+  - HTT: Varied group outperformed constant group in both training and testing.
+  - HTW: Varied group exhibited poorer performance across training and testing stages.
+
+- **Modeling Approaches**:
+  - HTT: IGAS model quantifies similarity between training and testing conditions.
+  - HTW: ALM and EXAM models fit to individual participant data.
+
+**Script:**
+
+"In our studies, we explored the impact of training variability on learning and generalization in two projects: Hit The Target (HTT) and Hit The Wall (HTW).
+In HTT, experiments showed that varied training led to superior testing performance compared to constant training.
+Interestingly, the varied group even outperformed the constant group when tested from the constant group's trained position.
+
+In contrast, the HTW project found that varied training resulted in poorer performance than constant training across several metrics, including training accuracy, extrapolation testing accuracy, and the ability to discriminate between bands.
+
+Both projects employed computational modeling to interpret the results.
+In HTT, we introduced the IGAS model to quantify the similarity between training and testing conditions.
+This model helped account for the benefits of varied training by showing how training variability influences the generalization gradient.
+
+In HTW, we implemented the ALM and EXAM models, which have been used in numerous studies on function learning.
+We fit these models to individual participant data using a Bayesian parameter estimation method, allowing us to generate and compare the full posterior predictive distributions of each model.
+The EXAM model provided the best overall account of the testing data, particularly for the constant group."
+
+### Slide 2: Differences between HTT and HTW
+
+**Bullet Points:**
+
+- **Task Differences**:
+  - **HTT**:
+    - Complex parabolic trajectory.
+    - Both x and y velocities relevant.
+    - Perceptually salient varied conditions.
+  - **HTW**:
+    - Simple 1D force mapping.
+    - Only x velocity relevant.
+    - Less perceptually salient varied conditions.
+
+- **Task Complexity**:
+  - HTT: More complex task space with irregularities.
+  - HTW: Smooth, linear mapping between velocity and feedback.
+
+- **Training and Testing Structure**:
+  - HTT: Random interleaving of trained/transfer testing distances.
+  - HTW: Blocked structure, testing trained vs. extrapolation bands separately.
+
+**Script:**
+
+"To understand the differing outcomes between HTT and HTW, it's crucial to consider the differences in their tasks.
+HTT involved a more complex parabolic trajectory where both x and y velocities were relevant, and the varied conditions were perceptually distinct.
+This complexity and perceptual salience likely contributed to the observed benefits of varied training.
+
+In contrast, HTW had a simpler 1D force mapping where only the x velocity was relevant.
+The varied conditions in HTW were less perceptually salient, as they were indicated by numerals rather than distinct visual features.
+This simplicity and lack of perceptual salience might have limited the potential benefits of varied training.
+
+Additionally, the task spaces were different.
+HTT had a more complex task space with irregularities introduced by the barrier, making the learning environment less predictable.
+HTW had a smoother, linear mapping between velocity and feedback, providing a more predictable learning environment.
+
+The structure of training and testing also differed.
+In HTT, testing involved random interleaving of trained and transfer testing distances, while in HTW, testing was blocked, separately testing trained and extrapolation bands.
+These differences highlight the importance of task characteristics in determining the impact of training variability on learning and generalization."

### 2024-05-28 Presentation/_hold_slides.qmd
update slides again

@@
 :::
+
+## Issues with previous research {.smaller}
+
+- Assumptions about what is encoded
+- Assumptions about the formation of abstractions 
+- Aggregation issues and similarity confounds
+
+::: fragment
+:::: columns
+::: {.column}
+
+![](assets/agg_issues.png)
+:::
+::: {.column}
+<br>
+
+-  If generalization decays exponentially with distance, constant groups 1 and 2 may have far less generalization potential to the testing condition. 
+- performance of individual constant groups often not reported in analyses.
+
+:::
+
+::::
+:::
+::: footnote
+e.g. [@mccrackenTestSchemaTheory1977; @chuaPracticeVariabilityPromotes2019; @delreyEffectsContextualInterference1982]
+:::
+
+---

### 2024-05-28 Presentation/slides.qmd
update slides again

@@
     incremental: false
-  hugo-md:
-    include: false
-    html-math-method: mathjax
-    output-file: slides_hugo.md
+  # hugo-md:
+  #   include: false
+  #   html-math-method: mathjax
+  #   output-file: slides_hugo.md
   gfm:
@@
 - Variation during training linked to improved transfer in numerous domains 
-- What does "variability mean in the context of learning interventions?"
+  - sometimes alternatively termed diversity, heterogenity, numerosity etc.
 
-## Types of Variability
-
+- What does variability mean in the context of learning interventions?
+  - How spread out examples are in the task space
   - The number of unique items/problems experienced
-- How spread out examples are
-
-## My Dissertation Focus
-
-- Number of unique examples
-- Visuomotor skill learning and function learning
-
-- Addressing methodological shortcomings of previous work
-- Adapting cognitive models from other domains to account for results
+  - exposure to wider array of contexts/background conditions
 
 ------------------------------------------------------------------------
-
-## Common Experimental Manipulations
-
-- Varied vs. Constant
 
@@
 ::: {.column}
-<br>
-
--  If generalization decays exponentially with distance, constant groups 1 and 2 may have far less generalization potential to the testing condition. 
-- performance of individual constant groups often not reported in analyses.
 
@@
 - Euclidean distance between each training throw, and each solution space
-  - separately for each participant, and each of the testing positions
 - Similarity computed as a Gaussian decay function of distance, i.e. larger distances result in lower similarity
@@
 ::::
+
+::: notes
+each participant has all of their training throws compared to each of the 6 testing positions
+:::
+
+___
 
@@
 
+## Modelling Results {.smaller}
+
+#### Best fitting models per participant
+
+![](assets/best_models.png)
+
+::: notes
+Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM
+:::
+
 ## Model Comparison - Experiment 1
@@
 
-## Modelling Results {.smaller}
-
-### Best fitting models per participant
-
-![](assets/best_models.png)
-
-::: notes
-Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM
-:::
-
 ___
 
-# General Discussion
+## General Discussion
 
--   Compare HTT and HTW
--   Empirical findings summary
--   Computational modeling contributions
+---
+
+## Summary {.smaller}
+
+- **Project Comparison**:
+  - **HTT (Project 1)**: Varied training led to superior testing performance.
+  - **HTW (Project 2)**: Varied training led to poorer performance.
+
+- **Key Findings**:
+  - HTT: Varied group outperformed constant group in both training and testing.
+  - HTW: Varied group exhibited poorer performance across training and testing stages.
+
+- **Modeling Approaches**:
+  - HTT: IGAS model quantifies similarity between training and testing conditions.
+  - HTW: ALM and EXAM models fit to individual participant data.
 
@@
 
-## Comparison {.smaller .r-fit-text}
+## Project Comparison {.smaller}
 
-| Dimension | HTT (Project 1) | HTW (Project 2) |
-|----------------|--------------------------------|-------------------------|
-| Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
-| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
-| Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
-| Simpler: smooth, linear mapping between velocity and feedback.
-|
-| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
-salient differences in distance between launching box and target.
-| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
-|
-| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
-| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
-| Training Experience | Varied group gets half as much experience on any one position as the constant group.
-| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
-|
-| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
+- **Task Differences**:
+  - **HTT**:
+    - Complex parabolic trajectory.
+    - Both x and y velocities relevant.
+    - Perceptually salient varied conditions.
+  - **HTW**:
+    - Simple 1D force mapping.
+    - Only x velocity relevant.
+    - Less perceptually salient varied conditions.
 
-------------------------------------------------------------------------
+- **Task Complexity**:
+  - HTT: More complex task space with irregularities.
+  - HTW: Smooth, linear mapping between velocity and feedback.
+
+::: notes
+
+the task spaces were different.
+HTT had a more complex task space with irregularities introduced by the barrier, making the learning environment less predictable.
+HTW had a smoother, linear mapping between velocity and feedback, providing a more predictable learning environment.
+:::
 
 ## Conclusion
+
+- Task-specific characteristics are crucial in determining the benefits of varied training.
+- Combining empirical research with computational modeling enhances understanding of learning and generalization.
+
+::: notes
+
+- The contrasting results highlight the importance of considering task characteristics when designing experiments to assess the influence of training interventions.
+- Combining empirical and computational modeling approaches can help uncover the cognitive mechanisms supporting learning and generalization.
+- Future research should continue to investigate the interplay between task demands, training manipulations, and individual differences to optimize educational and training outcomes.
+
+:::
 
@@
 ------------------------------------------------------------------------
+
+---
+
+## Comparison {.scrollable .unnumbered .unlisted, .smaller}
+
+| Dimension | HTT (Project 1) | HTW (Project 2) |
+|----------------|--------------------------------|-------------------------|
+| Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
+| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
+| Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
+| Simpler: smooth, linear mapping between velocity and feedback.
+|
+| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
+salient differences in distance between launching box and target.
+| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
+|
+| Testing Feedback | Testing always included feedback | Primary testing stage had no feedback. |
+| Potential for Learning during Testing | Limited potential for learning during testing due to feedback. | Some potential for learning during no-feedback testing by observing ball trajectory. |
+| Training Experience | Varied group gets half as much experience on any one position as the constant group.
+| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
+|
+| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
+
+------------------------------------------------------------------------

### 2024-05-28 Presentation/_hold_slides.qmd
sync again

@@
 ---
+
+### Final Conclusion Slide
+
+**Title: Conclusion**
+
+**Bullet Points:**
+- **Empirical Findings**:
+  - HTT: Varied training led to superior performance.
+  - HTW: Varied training led to poorer performance.
+  - Differences attributed to task characteristics and complexity.
+
+- **Modeling Insights**:
+  - HTT: IGAS model highlighted the importance of similarity between training and testing conditions.
+  - HTW: EXAM model provided the best account of testing data, especially for the constant group.
+
+- **Implications**:
+  - Task-specific characteristics are crucial in determining the benefits of varied training.
+  - Combining empirical research with computational modeling enhances understanding of learning and generalization.
+
+**Script:**
+
+"In summary, our research provided significant insights into the effects of training variability on learning and generalization in different tasks.
+In the HTT project, we found that varied training led to superior performance, consistent with the benefits of variability hypothesis.
+In contrast, the HTW project demonstrated that varied training could be detrimental, particularly in simpler extrapolation tasks.
+
+These opposing patterns highlight the importance of task characteristics and complexity in determining the benefits of training variability.
+The HTT task's complexity and perceptual salience of varied conditions likely contributed to the positive effects, while the simpler, less perceptually salient HTW task showed negative effects.
+
+From a modeling perspective, the IGAS model in HTT emphasized the role of similarity between training and testing conditions, showing that controlling for similarity is crucial for understanding training outcomes.
+The EXAM model in HTW provided a robust account of the data, particularly for the constant training group, suggesting that linear extrapolation mechanisms and prior knowledge can influence performance in simpler tasks.
+
+Overall, our findings underscore the necessity of considering task-specific characteristics when designing training programs.
+The combination of empirical research and computational modeling proved invaluable in uncovering the cognitive mechanisms underlying learning and generalization.
+Future research should continue to explore the interplay between task demands, training manipulations, and individual differences to optimize educational and training outcomes across various domains.
+Thank you."

### 2024-05-28 Presentation/slides.qmd
sync again

@@
 
+::: notes
+thank you all for joining in my defense
+
+Learning is often more specific than we'd like. There has been longstanding scientific interest in trying to understand what factors we might
+be able to control that might have beneficial effects on generalization and transfer.
+
+One such factor, and the topic of my dissertation - is the influence of variability on generalization
+
+Over the next 45 minutes, I will walk through the specific empirical studies and computational modeling work
+
+:::
+
 ------------------------------------------------------------------------
@@
 - Variation during training linked to improved transfer in numerous domains 
+  - Category learning, perceptual learning, education, visuomotor learning
   - sometimes alternatively termed diversity, heterogenity, numerosity etc.
 
+::: {.fragment}
 - What does variability mean in the context of learning interventions?
   - How spread out examples are in the task space
-  - The number of unique items/problems experienced
+  - **The number of unique items/problems experienced**
   - exposure to wider array of contexts/background conditions
+:::
+
+::: notes
+
+- The influence of variability has been studied across many different domains
+- although sometimes referred
+
+variability can refer to many different
+
+:::
 
@@
 
+::: notes
+higher or lower variability can of course vary greatly between domains
+
+One common manipulation in visuomotor learning is to have a group train with the lowest possible variability - constant
+
+This is a fairly common pattern, at least to my reading. But....,
+
+:::
+
 ------------------------------------------------------------------------
@@
     - Frequency effects, or amount of training/learning before testing
+
+::: notes
+Plenty of discrepancy in results, sometimes even for very similar tasks. 
+- and lots of work remains to unravel when exactly variability is or isn't helpful
+:::
 
@@
 
-------------------------------------------------------------------------
+::: notes
+- Dissertations consists of 2 primary projects. 
+- Each within their own subdomain of visuomotor learning
+- and each employing a distinct type of computational modeling
+:::
 
@@
 ::: notes
-Variety of theoretical explanations
-Schema theory in paticular has been extremely influential 
+- Variety of theoretical explanations have been proposed for the commonly observed effects
+- In visuomotor learning and most relevant for my work, Schema theory in paticular has been extremely influential, and seems to have inspired hundreds of studies
 :::
@@
 e.g. [@mccrackenTestSchemaTheory1977; @chuaPracticeVariabilityPromotes2019; @delreyEffectsContextualInterference1982]
+:::
+
+::: notes
+- Schema theory assumes that learners encode abstractions, or parameters, that enable generalization, and that variation is parituiclarly helpful
 :::
@@
 
+::: notes
+- To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
+constant) and band type (trained vs.
+extrapolation), with random intercepts for participants and bands.
+The model results are shown in Table 3.
+The main effect of training condition was not significant (
+ The extrapolation testing items had a significantly greater deviation than the training bands (
+  Most importantly, the interaction between training condition and band type was significant (
+ As shown in Figure 5, the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
+
+ - Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
+
+- on. Most relevant to the issue of discrimination is the coefficient on the Band predictor (
+ Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
+The significant negative estimate for the interaction between slope and condition (
+ suggests that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition 
+:::
+
 ## Project 2 - Experiment 2 Design {.smaller}
@@
 :::
+:::
+
+::: notes
+ The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
+Constant) and band type (training vs.
+extrapolation bands).
+The results, summarized in Table 6, reveal no significant main effect of training condition (
+ However, the interaction between training condition and band type was significant  with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands
+
 :::

### 2024-06-02 Presentation/slides.qmd
final changes pre-presentation

@@
 - In visuomotor learning and most relevant for my work, Schema theory in paticular has been extremely influential, and seems to have inspired hundreds of studies
+- Unlike the models I'll be presenting today, at least to my knowledge none of these have ever been formally specified and actually fit to human data
 :::
@@
 
-::: fragment
-:::: columns
-::: {.column}
-
-![](assets/agg_issues.png)
-:::
-::: {.column}
-
-:::
-
-::::
-:::
-::: footnote
-e.g. [@mccrackenTestSchemaTheory1977; @chuaPracticeVariabilityPromotes2019; @delreyEffectsContextualInterference1982]
-:::
-
 ::: notes
 - Schema theory assumes that learners encode abstractions, or parameters, that enable generalization, and that variation is parituiclarly helpful
+- failures to consider nonlinear effects of learning 
+- failure to consider that, through lieu of being exposed to broader coverage of the task space, varied training manipulations can often 
 :::

### 2024-06-21 index.qmd
re-render
minor changes

@@
 ---
+
+## Project 1
+
+[{{< fa file-lines >}} Project 1 page](https://tegorman13.github.io/Dissertation/Sections/IGAS.html)
+
+[{{< fa file-pdf >}} pdf of the journal
+article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
+[{{< fa scroll >}} Link to online version of journal
+article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
+
+## Project 2
+
+[{{< fa file-lines >}} Link to project 2 page](https://tegorman13.github.io/htw/){target="_blank"} \
+
+[{{< fa file-pdf >}} Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

### 2024-06-21 Sections/HTW.qmd
fix heading on htw page
minor changes
add icons to version links; add igas pdf

@@
 _______________________________________________________________________________
-{{< fa file-lines >}} [Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \
-
-{{< fa file-pdf >}} [Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
-
-{{< fa brands github >}} [repo](https://github.com/tegorman13/htw) \
+
+[{{< fa file-lines >}} Link to project page](https://tegorman13.github.io/htw/){target="_blank"} \
+
+ [{{< fa file-pdf >}} Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
+
+ [{{< fa brands github >}} repo](https://github.com/tegorman13/htw) \
 _______________________________________________________________________________
@@
 
-### Variability and Function Learning
+## Variability and Function Learning
 
@@
 
-## Experiment 1
-
-### Methods
+# Experiment 1
+
+## Methods
 
@@
 
-### Analyses Strategy
+## Analyses Strategy
 
@@
 
-### Results
+## Results
 
@@
 
-## E1 Summary
+## Experiment 1 Summary
 
@@
 
-## Experiment 2
+# Experiment 2
 
@@
 
-### Methods & Procedure
+## Methods & Procedure
 
@@
 
-### Experiment 2 Summary
+## Experiment 2 Summary
 
@@
 
-## Experiment 3
+# Experiment 3
 
@@
 
-### Experiment 3 Summary
+## Experiment 3 Summary
 
@@
 
-## Computational Model
+# Computational Model
 
@@
 
-### ALM & Exam
+## ALM & Exam
 
@@
 
-### Model Fitting
+## Model Fitting
 
@@
 
-### Modelling Results
+## Modelling Results
 
@@
 *Computational Model Summary*.
+
 Across all three experiments, the model fits consistently favored the Extrapolation-Association Model (EXAM) over the Associative Learning Model (ALM).

### 2024-06-21 Sections/IGAS.qmd
add icons to version links; add igas pdf

@@
 subtitle: An instance-based model account of the benefits of varied practice in visuomotor skill
-#date: last-modified
-#page-layout: full
+author:
+- name: Thomas E. Gorman
+  affiliations: 
+  - Department of Psychological and Brain Sciences, Indiana University-Bloomington
+  affiliation-url: https://psych.indiana.edu/
+  url: https://tegorman13.github.io/
+  email: tegorman@iu.edu
+  orcid: 0000-0001-5366-5442
+page-layout: full
 code-fold: true
@@
     output-file: igas_hugo.md
+  hikmah-manuscript-pdf:
+    echo: false
+    output-file: "igas_dis.pdf"
+    mainfont: "Linux Libertine O"
+    mainfontoptions:
+      - "Numbers=Proportional"
+      - "Numbers=OldStyle"
+    mathfont: "Libertinus Math"
 execute: 
@@
     wrap: 72
+prefer-html: true
 ---
 
+::: {.content-visible when-format="html"}
 ____________________________________________________
-[pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
+
+[{{< fa file-pdf >}} pdf of the journal article](https://tegorman13.github.io/pdf/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}
+
+[{{< fa scroll >}} Link to online version of journal article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
+
+[{{< fa brands github >}} repo](https://github.com/tegorman13/IGAS_Variability) \
+
+---
+
+:::
 

### 2024-06-21 index.qmd
add icons to version links; add igas pdf

@@
 
-[{{< fa file-pdf >}} pdf of the journal
-article](Assets/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
-[{{< fa scroll >}} Link to online version of journal
-article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
+[{{< fa file-pdf >}} pdf of the journal article](https://tegorman13.github.io/pdf/Gorman_Goldstone_2022_Instance-based_model_varied_practice.pdf){target="_blank"}\
+
+[{{< fa scroll >}} Link to online version of journal article](https://www.sciencedirect.com/science/article/abs/pii/S0010028522000299){target="_blank"}
 
@@
 [{{< fa file-pdf >}} Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
+
+## Full Manuscript
+
+[{{< fa file-lines >}} Web page version](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html)
+
+[{{< fa file-lines >}} Version with code](https://tegorman13.github.io/Dissertation/Sections/full.html)
+
+[{{< fa file-pdf >}} pdf version](https://tegorman13.github.io/Dissertation/paper.html){target="_blank"}\
+
+## Slides
+
+[{{< fa file-lines >}} Slides overview](https://tegorman13.github.io/Dissertation/Presentation/slides.html)
+
+[{{< fa person-chalkboard size=1.0xs >}} Defense slides](https://tegorman13.github.io/Dissertation/Presentation/slides_revealjs.html#/)

### 2024-06-21 index.qmd
update home page

@@
 title: "Dissertation"
-author: Thomas E. Gorman
+author:
+- name: Thomas E. Gorman
+  affiliation: Indiana University
+  affiliation-url: https://psych.indiana.edu/
+  url: https://tegorman13.github.io/
+  orcid: 0000-0001-5366-5442
 comments: false
@@
 
+[{{< fa brands github >}} repo](https://github.com/tegorman13/IGAS_Variability) \
+
 ## Project 2
@@
 [{{< fa file-pdf >}} Working Draft of Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}
+
+[{{< fa brands github >}} repo](https://github.com/tegorman13/htw) \
 
@@
 
+[{{< fa brands github >}} repo](https://github.com/tegorman13/Dissertation) \
+
 ## Slides

### 2024-06-21 Manuscript/manuscript.qmd
re-render all formats and tweak afiliations

@@
 
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#00A08A"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#FF0000"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
 
@@
 :::
-
 ```{r}

### 2024-06-21 Sections/HTW.qmd
re-render all formats and tweak afiliations

@@
 title: HTW Project
-date: last-modified
 author:
@@
   affiliations: 
-  - Department of Psychological and Brain Sciences, Indiana University-Bloomington
+  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
     affiliation-url: https://psych.indiana.edu/
+  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
+    affiliation-url: https://cogs.indiana.edu/index.html
   url: https://tegorman13.github.io/
   email: tegorman@iu.edu
-  orcid: 0000-0001-5366-5442
+  orcid: "0000-0001-5366-5442"
 page-layout: full
@@
 toc-title: Contents
+format-links: [hikmah-manuscript-pdf, gfm]
+format: 
+  html: 
+    date: last-modified
+  hugo-md:
+    echo: false
+    include: false
+    html-math-method: mathjax
+    output-file: htw_hugo.md
+  gfm:
+    echo: false
+    output-file: htw_gfm.md
+  hikmah-manuscript-pdf:
+    echo: false
+    output-file: "htw_dis.pdf"
+    mainfont: "Linux Libertine O"
+    mainfontoptions:
+      - "Numbers=Proportional"
+      - "Numbers=OldStyle"
+    mathfont: "Libertinus Math"
 execute: 
@@
 
+::: {.content-visible when-format="html"}
 _______________________________________________________________________________
@@
 _______________________________________________________________________________
+:::
 

### 2024-06-21 Sections/IGAS.qmd
re-render all formats and tweak afiliations

@@
 toc-depth: 4
+format-links: [hikmah-manuscript-pdf, gfm]
 format:
@@
     output-file: igas_hugo.md
+  gfm:
+    echo: false
+    output-file: igas_gfm.md
   hikmah-manuscript-pdf:
@@
     mathfont: "Libertinus Math"
+  # hikmah-manuscript-docx: 
+  #   prefer-html: true
+  #   echo: false
 execute: 
@@
 
+# Appendix
+
+{{< include /Sections/Appendix/IGAS-Supplemental.qmd >}}
+
 # References
@@
 :::
-
-# Appendix
-
-{{< include /Sections/Appendix/IGAS-Supplemental.qmd >}}

### 2024-06-21 Sections/full.qmd
re-render all formats and tweak afiliations

@@
 author:
-- name: Thomas Gorman
-  affiliation: Indiana University
+- name: Thomas E. Gorman
+  affiliations: 
+  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
     affiliation-url: https://psych.indiana.edu/
+  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
+    affiliation-url: https://cogs.indiana.edu/index.html
   url: https://tegorman13.github.io/
-  orcid: 0000-0001-5366-5442
+  email: tegorman@iu.edu
+  orcid: "0000-0001-5366-5442"
 page-layout: full

### 2024-06-21 paper.qmd
tweaks with icons, added iconify
re-render all formats and tweak afiliations

@@
 title: Dissertation Manuscript
+subtitle: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
+author:
+- name: Thomas E. Gorman
+  affiliations: 
+  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
+    affiliation-url: https://psych.indiana.edu/
+  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
+    affiliation-url: https://cogs.indiana.edu/index.html
+  url: https://tegorman13.github.io/
+  email: tegorman@iu.edu
+  orcid: "0000-0001-5366-5442"
 toc: false
@@
 ---
+
+{{< iconify <icon> >}}
 

### 2024-06-21 Presentation/slides2.qmd
full site re-render

@@
 page-layout: full
-aliases:
-  - /slides.html
-css: /Assets/Style/slides.css
-format: 
+# aliases:
+#   - /slides.html
+# css: /Assets/Style/slides.css
+#format: 
   # html: 
@@
   #   output-file: slides_gfm.md
-  beamer: default
+  #beamer: default
     # incremental: false

### 2024-06-21 Sections/Discussion.qmd
full site re-render

--- 2024-04-05 Sections/Discussion.qmd
@@
 date: today
+format:
+  html: default
+  hugo-md:
+    #echo: false
+    #output: false
+    html-math-method: mathjax
+    output-file: dissc_hugo.md
+    mermaid-format: png
+  gfm:
+    #echo: false
+    output-file: dissc_gfm.md
+    mermaid-format: png
 ---
+
+# General Discussion
 
@@
 
-\ \ \ \
+\ \
+
+# References
+::: {#refs}
+:::

### 2024-06-21 Sections/Introduction.qmd
full site re-render

@@
     output-file: d_into_gfm.md
-  hikmah-manuscript-pdf:
-    echo: false
-    output-file: "intro_pdf.pdf"
-    mainfont: "Linux Libertine O"
-    mainfontoptions:
-      - "Numbers=Proportional"
-      - "Numbers=OldStyle"
-    mathfont: "Libertinus Math"
+  # hikmah-manuscript-pdf:
+  #   echo: false
+  #   output-file: "intro_pdf.pdf"
+  #   mainfont: "Linux Libertine O"
+  #   mainfontoptions:
+  #     - "Numbers=Proportional"
+  #     - "Numbers=OldStyle"
+  #   mathfont: "Libertinus Math"
 ---
@@
 To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.
+
+{{< pagebreak >}}

### 2024-06-21 Sections/htw_exam.qmd
minor changes
full site re-render

--- 2023-11-14 Sections/htw_exam.qmd
@@
   warning: false
-  eval: true
+  eval: false
 ---

### 2024-06-21 Manuscript/manuscript.qmd
fix mermaid colors

@@
   data2 [label = " Constant Training \n800-1000", fillcolor = "#FF0000"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
 

### 2024-06-22 Manuscript/manuscript.qmd
Rob's edits up through end of htw into

@@
 The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that do not contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021; @schulzCommunicatingCompositionalPatterns2020].
+Studies of function learning often compare the difficulty of learning functions of different underlying forms (e.g.
+linear, bi-linear, power, sinusoidal), and the extent to which participants can accurately respond to novel inputs that fall in-between previously experienced inputs (interpolation testing), or that fall outside the range of previously experienced inputs (extrapolation).
 
@@
 Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
+Carroll argued that these results were best explained by a rule-based model wherein learners form an abstract representation of the underlying function.
+Subsequent work by @brehmerHypothesesRelationsScaled1974, testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
+Brehmer argued that individuals start out assuming a linear function, but given sufficient error will progressively test alternative hypotheses with polynomials of greater degree.
 @kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
-Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
+In this domain, participants performed best when the relation between line length and response duration was determined by a power law, as opposed to linear function.
+Koh and Meyer developed the log-polynomial adaptive-regression model to account for their results.
+
+The first significant challenge to rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
 In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
+Participants approached ceiling performance by the end of training in each function condition, and were able to accurately respond on interpolation testing trials.
 All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
-
-The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
+Extrapolation and interpolation performances are depicted in @fig-delosh-extrap.
+
+The authors evaluated the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
+The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the under and over-estimation biases shown in the human data.
 The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
@@
 ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
-The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
+ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance (see @fig-alm-diagram).
+The EXAM model retains the same similarity-based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
 When presented with novel stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
-
-### Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the Bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the Bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
+ALM was able to provide a good account of participants' training and interpolation data in all three function conditions, however it was unable to extrapolate.
+EXAM, by contrast, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
+Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate a sinusoidal function [@bottNonmonotonicExtrapolationFunction2004] or to scenarios where different functions apply to different regions of the input space [@kalishPopulationLinearExperts2004], though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V-shaped input spaces [@mcdanielPredictingTransferPerformance2009].
 
@@
 #| label: fig-delosh-extrap
-#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
+#| fig-cap: The generalization patterns of human particpiants observed in DeLosh et al.
+(1997) (reproduced from Figure 3 in their manuscript).
+Dots represent the average responses of human participants, and solid lines represent the true functions.
+The dashed vertical lines indicate the lower and upper bounds of the trained examples.
+Stimulii that fall within the dashed lines are interpolations of the training examples, while those that fall outside the dashed lines are extrapolations.
 #| echo: false
@@
 ```
+
+### Variability and Function Learning
+
+The influence of variability on function learning tasks has received relatively little attention.
+The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
+They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
+
+In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
+The shapes ranged from very spiky to completely circular at the extreme ends of the space.
+Participants trained with intermediate shapes having lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower variation condition matching the items used on the extreme ends of the higher variation training space.
+Learning was significantly slower in the higher variation group.
+However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitude to the most similar training item, rather than in accordance with the true linear function.
+The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
+Similar to ALM, the model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
+However, unlike ALM, the Bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
 

### 2024-06-22 Sections/HTW.qmd
Rob's edits up through end of htw into

@@
 toc-title: Contents
-format-links: [hikmah-manuscript-pdf, gfm]
+citeproc: true
+format-links: [hikmah-manuscript-pdf, apaquarto-pdf, gfm]
 format: 
@@
     date: last-modified
+  # apaquarto-pdf: 
+  #   echo: false
+  #   output-file: htw_apaquarto.pdf
   hugo-md:
@@
   eval: true
+# filters: 
+#   - quarto
+#   - apa_and.lua
 ---
@@
 :::
-
-# Introduction
-
-A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
-One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014 ],  language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial  [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022 ].
-The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
-
-## Function Learning and Extrapolation
-
-The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].
-
-@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
-Input stimuli and output responses were both lines of varying length.
-The correct output response was related to the length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a ruled based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974,testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out with an assumption of a linear function, but  given sufficient error will progressively test alternative hypothesis with polynomials of greater degree.
-@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power, as opposed to linear function.
-Koh & Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to the rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
-In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to correctly respond in interpolation testing trials.
-All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performance are depicted in @fig-delosh-extrap.
-
-The authors evaluated both of the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the human data.
-The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the  systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models.
-The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance.
-The EXAM model retains the same similarity based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
-When presented with novel  stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participant training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, on the other hand, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate sinusoidal function @bottNonmonotonicExtrapolationFunction2004 or to scenarios where different functions apply to different regions of the input space @kalishPopulationLinearExperts2004, though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V shaped input spaces @mcdanielPredictingTransferPerformance2009.
-
-## Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes from a lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower varied condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitudes to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the bayesian model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However unlike ALM, the bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
 
@@
 
+# Introduction
+
+A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
+One such aspect, which has received a great deal of research attention, is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
+The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014], language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
+The pattern of results is complex, with numerous studies finding both beneficial [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022].
+The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
+
+## Function Learning and Extrapolation
+
+The study of human function learning investigates how people learn relationships between continuous input and output values.
+Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that do not contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021; @schulzCommunicatingCompositionalPatterns2020].
+Studies of function learning often compare the difficulty of learning functions of different underlying forms (e.g.
+linear, bi-linear, power, sinusoidal), and the extent to which participants can accurately respond to novel inputs that fall in-between previously experienced inputs (interpolation testing), or that fall outside the range of previously experienced inputs (extrapolation).
+
+@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
+Input stimuli and output responses were both lines of varying length.
+The correct output response was related to the length of the input line by a linear, quadratic, or random function.
+Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
+Carroll argued that these results were best explained by a rule-based model wherein learners form an abstract representation of the underlying function.
+Subsequent work by @brehmerHypothesesRelationsScaled1974, testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
+Brehmer argued that individuals start out assuming a linear function, but given sufficient error will progressively test alternative hypotheses with polynomials of greater degree.
+@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
+In this domain, participants performed best when the relation between line length and response duration was determined by a power law, as opposed to linear function.
+Koh and Meyer developed the log-polynomial adaptive-regression model to account for their results.
+
+The first significant challenge to rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
+In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
+Participants approached ceiling performance by the end of training in each function condition, and were able to accurately respond on interpolation testing trials.
+All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
+Extrapolation and interpolation performances are depicted in @fig-delosh-extrap.
+
+The authors evaluated the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
+The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the under and over-estimation biases shown in the human data.
+The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
+
+The authors also introduced two new function-learning models.
+The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
+ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
+ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance (see @fig-alm-diagram).
+The EXAM model retains the same similarity-based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
+When presented with novel stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
+ALM was able to provide a good account of participants' training and interpolation data in all three function conditions, however it was unable to extrapolate.
+EXAM, by contrast, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
+Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate a sinusoidal function [@bottNonmonotonicExtrapolationFunction2004] or to scenarios where different functions apply to different regions of the input space [@kalishPopulationLinearExperts2004], though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V-shaped input spaces [@mcdanielPredictingTransferPerformance2009].
+
 ```{r}
 #| label: fig-delosh-extrap
-#| fig-cap: Generalization reproduced patterns from DeLosh et al. (1997) Figure 3. Stimulii that fall within the dashed lines are interpolations of the training examples. 
+#| fig-cap: The generalization patterns of human particpiants observed in DeLosh et al.
+(1997) (reproduced from Figure 3 in their manuscript).
+Dots represent the average responses of human participants, and solid lines represent the true functions.
+The dashed vertical lines indicate the lower and upper bounds of the trained examples.
+Stimulii that fall within the dashed lines are interpolations of the training examples, while those that fall outside the dashed lines are extrapolations.
 #| echo: false
 #| fig-width: 10
+#| cache: false 
+# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+#   stringr, here,conflicted, patchwork, knitr)
+# #options(brms.backend="cmdstanr",mc.cores=4)
+# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
+# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
+
+#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
+source(here::here("Functions","deLosh_data.R"))
+#source(here::here("Functions","Display_Functions.R"))
 
@@
 ```
+
+## Variability and Function Learning
+
+The influence of variability on function learning tasks has received relatively little attention.
+The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
+They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
+
+In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
+The shapes ranged from very spiky to completely circular at the extreme ends of the space.
+Participants trained with intermediate shapes having lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower variation condition matching the items used on the extreme ends of the higher variation training space.
+Learning was significantly slower in the higher variation group.
+However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitude to the most similar training item, rather than in accordance with the true linear function.
+The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
+Similar to ALM, the model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
+However, unlike ALM, the Bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
 

### 2024-06-22 Sections/full.qmd
Rob's edits up through end of htw into

@@
 ::: {.content-visible when-format="pdf"}
-
 {{< include /Sections/pre_sections/toc_pdf.qmd >}}
-
 :::
@@
 
-In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
-typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
+In the domain of category learning, the constant vs.
+varied comparison is much less suitable.
+Instead, researchers will typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968; @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
 
@@
 
-Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002;  @yangCategoryVariabilityEffect2014; and @seitzModelingCategoryVariability2023].
+Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012; @sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002; @yangCategoryVariabilityEffect2014; and @seitzModelingCategoryVariability2023].
 The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
@@
 Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
+As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010; @gandolfoMotorLearningField1996a; @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
 However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
@@
 
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
+**Equation 2:** $$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
 
@@
 
-Across two experiments, we found evidence in support of the benefits of
-variability hypothesis in a simple, computerized projectile throwing task.
+Across two experiments, we found evidence in support of the benefits of variability hypothesis in a simple, computerized projectile throwing task.
 Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
@@
 | Group Comparison | Code | Data |
-| ------------------------ | ----------------------------------------------------------- | -------------------- |
-| End of Training Accuracy | `` brm(Abs. Deviation ~ condit) ``                                    | Final Training Block |
-| Test Accuracy            | `` brm(Abs. Deviation ~ condit * bandType + (1|id) + (1|bandInt) `` | All Testing trials   |
-| Band Discrimination      | `` brm(vx ~ condit * band +(1 + bandInt|id) ``             | All Testing Trials   |
+|-----------------|---------------------------------------|-----------------|
+| End of Training Accuracy | `brm(Abs. Deviation ~ condit)` | Final Training Block |
+| Test Accuracy | `brm(Abs. Deviation ~ condit * bandType + (1|id) + (1|bandInt)` | All Testing trials |
+| Band Discrimination | `brm(vx ~ condit * band +(1 + bandInt|id)` | All Testing Trials |
 
@@
 :::
+
 \
@@
 ::: {#tbl-e1-train-dist}
-
 | Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
@@
 ::: {#tbl-e1-bmm-dist}
-
 | Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:------------------------|-----------:|-----------:|-----------:|-----------:|
+|:-------------------|------------:|------------:|------------:|------------:|
 | Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
@@
 ::: {#tbl-e1-bmm-vx}
-
 | Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
@@
 ::: {#tbl-e2-train-dist}
-
 | Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
@@
 The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
+
 ```{r}
@@
 ::: {#tbl-e2-bmm-dist}
-
 | Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-----------------------------------|---------:|--------------:|--------------:|-----:|
+|:------------------------|-----------:|-----------:|-----------:|-----------:|
 | Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
@@
 
-\ \
+\
 
@@
 ::: {#tbl-e2-bmm-vx}
-
 | Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
@@
 ::: {#tbl-e3-train-dist}
-
 | Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:------------------------------|---------:|--------------:|--------------:|-----:|
+|:----------------------|------------:|------------:|------------:|------------:|
 | Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
@@
 The negative value for the interaction between condit and bandOrder indicates that varied condition with reverse order had significantly lower deviations than the varied condition with the original band order {.sm}
-
 :::
@@
 | Term | Estimate | 95% CrI Lower | 95% CrI Upper | pd |
-|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
+|:-----------------------------|----------:|----------:|----------:|----------:|
 | Intercept | 288.65 | 199.45 | 374.07 | 1.00 |
@@
 ::: {#tbl-e3-bmm-vx}
-
 | Term | Estimate | 95% CrI Lower | 95% CrI Upper | pd |
-|:----------------------------------------|---------:|--------------:|--------------:|-----:|
+|:-------------------------|-----------:|-----------:|-----------:|-----------:|
 | Intercept | 601.83 | 504.75 | 699.42 | 1.00 |
@@
 ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus ( a_i(X) = exp(-c(X - X_i)^2) ).
+The units in the input layer activate as a function of their Gaussian similarity to the input stimulus ( a_i(X) = exp(-c(X - X_i)\^2) ).
 So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
@@
 | Slope Computation | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$ | Slope value, $S$ computed from nearest training instances |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$,  adjusted by local slope $S$.
-|
+| Response | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$ | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$, adjusted by local slope $S$. |
 
@@
 
-::: {.callout}
-
-**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
+:::: callout
+{{< fa regular lightbulb >}} **Approximate Bayesian Computation**
 
@@
 To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
-:::
+::::
 
@@
 ```
-
-\ \ \
 
@@
 ::: {#tbl-task-diff}
-
 | Dimension | HTT (Project 1) | HTW (Project 2) |
-| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
+|----------------|--------------------------------|------------------------|
 | Task Description | Projectile launching to hit a target | Projectile launching to hit wall at a specific velocity |
-| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
-Only x velocity is relevant.
-|
+| Task Complexity | More complex parabolic trajectory, both x and y velocities relevant to outcome | Simpler 1D mapping of force to outcome. Only x velocity is relevant. |
 | Task Space | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
@@
 |
-| Testing Structure                               | Random interleaving of trained/transfer testing distances.
-| Blocked structure, separately testing trained vs extrapolation testing bands.
-|
+| Testing Structure | Random interleaving of trained/transfer testing distances. | Blocked structure, separately testing trained vs extrapolation testing bands. |
 
@@
 # References
+
 ::: {#refs}

### 2024-06-26 Sections/full.qmd
turn on code show; switch default manuscript to html

@@
 page-layout: full
-code-fold: true
+code-fold: show
 code-tools: true

### 2024-06-26 paper.qmd
turn on code show; switch default manuscript to html

@@
 
-<iframe src="/Manuscript/output/TG_Full_Dissertation.pdf" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
+<iframe src="/Manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
 ```

### 2024-07-02 Manuscript/manuscript.qmd
minor edits

@@
 To the best of our knowledge, this research is the first to employ the classic constant vs.
-varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task.
+varied training manipulation, commonly used in the literature studying the benefits of variability, in the context of a uni-dimensional function learning task.
 Across three experiments, we compare constant and varied training conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.

### 2024-07-09 Manuscript/manuscript.qmd
update with more of Rob's edits, through end of Project 2 modeling results

@@
 
-*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
+*Participants* A total of 156 participants were recruited from Indiana University Introductory Psychology Courses.
 Participants were randomly assigned to one of two training conditions: varied training or constant training.
 
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
+*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in JavaScript, making use of the [phaser.io](https://phaser.io/) game library.
+The HTW task involved launching a projectile such that it would strike the "wall" at the target speed indicated at the top of the screen (see @fig-htw-task).
 The target velocities were given as a range, or band, of acceptable velocity values (e.g., band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
+During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below  the target band.
 Participants were instructed that only the x velocity component of the ball was relevant to the task.
@@
 Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoiding convergence issues common to the frequentist analogues of our mixed models.
+Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoid convergence issues common to the frequentist analogues of our mixed models.
 
@@
 Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for for the random effects.
+We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for the random effects.
 For each model, we report 1) the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
@@
 The specifications for the Bayesian regression models used in the analyses of each of the 3 experiments.
-Comparisons of accuracy use abosulte deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
+Comparisons of accuracy use absolute deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
 :::
@@
 Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
-The degree of discrimination between bands was index by fitting a linear model predicting the response velocity as a function of the target velocity.
-Participants who reliably discriminated between velocity bands tended to haves slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
+The degree of discrimination between bands was measured by fitting a linear model predicting the response velocity as a function of the target velocity.
+Participants who reliably discriminated between velocity bands tended to have slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
 
@@
 #| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
+#| fig-cap: Experiment 1 - Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
 p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
@@
 : **Experiment 1 - End of training performance**.
-Comparing final training block accuracy in band common to both groups.
+Comparing final training block accuracy in the band common to both groups.
 The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
@@
 The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
+The varied group had a significantly greater deviation from the target band than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
 
@@
 #| fig-cap: Experiment 1 Testing Accuracy.
-A) Empricial Deviations from target band during testing without feedback stage.
+A) Empirical Deviations from target band during testing without feedback stage.
 B) Conditional effect of condition (Constant vs.
@@
 See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, though is not in and of itself useful for assessing discrimination.
+The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, though this is not, in and of itself, useful for assessing discrimination.
 Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
 Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The significant negative estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), suggests that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition (see @fig-e1-test-vx and @fig-e1-bmm-vx).
+The significant negative estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), indicates that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition (see @fig-e1-test-vx and @fig-e1-bmm-vx).
 
@@
 #| label: fig-e1-test-vx
-#| fig-cap: Experiment 1. Empirical distribution of velocities producing in testing stage. Translucent bands with dashed lines indicate the correct range for each velocity band. 
+#| fig-cap: Experiment 1. Empirical distribution of velocities produced in the testing stage. Translucent bands with dashed lines indicate the correct range for each velocity band. 
 #| fig-width: 11
@@
 B) The distribution of slope coefficients for each condition.
-Larger slopes indicates better discrimination.
+Larger slopes indicates better discrimination between target bands.
 C) Individual participant slopes.
@@
 
-In Experiment 1, we investigated how variability in training influenced participants' ability learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions resulted in lower final training performance are consistent with much of the prior research on the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and is particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
+In Experiment 1, we investigated how variability in training influenced participants' ability to learn and extrapolate in a visuomotor task.
+Our findings that training with variable conditions resulted in lower final training performance are consistent with much of the prior research on the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and are particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
 
@@
 The Intercept represents the baseline condition (constant training & trained bands).
-Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproporionate deviation for the varied condition on the extrapolation bands.
+Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands.
 CrI values indicate 95% credible intervals.
@@
 #| fig-cap: Experiment 2 Testing Accuracy.
-A) Empricial Deviations from target band during testing without feedback stage.
+A) Empirical Deviations from target band during testing without feedback stage.
 B) Conditional effect of condition (Constant vs.
@@
 Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
-The interaction between condit and Band indicates the difference between constant and varied slopes.
+The interaction between condition and Band indicates the difference between constant and varied slopes.
 CrI values indicate 95% credible intervals.
@@
 Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However unlike experiment 1, the Varied group did not show a significant difference in discrimination between bands.
+However unlike experiment 1, the Varied and Constant groups did not show a significant difference in their discrimination between bands.
 
@@
 #| label: fig-e3-train-dev
-#| fig-cap: Experiment 3 training. Deviations from target band during training. Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2). 
+#| fig-cap: Experiment 3 training. Deviations from target band during training, shown separately for groups trained with the original order (used in E1) and reverse order (used in E2). 
 #| eval: true
@@
 The Intercept represents the baseline condition, (constant training,  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
-Positive coefficients thus represent worse performance relative to the baseline,  - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
+Positive coefficients thus represent worse performance relative to the baseline, and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
 {.hover .sm}
@@
 
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
+*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed effects model predicting absolute deviation from the target band during the testing stage.
 There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
@@
 #| fig-cap: Experiment 3 Testing Accuracy.
-A) Empricial Deviations from target band during testing without feedback stage.
+A) Empirical Deviations from target band during testing without feedback stage.
 B) Conditional effect of condition (Constant vs.
@@
 novel extrapolation bands) on testing accuracy.
-Shown separately for groups trained with the orginal order (used in E1) and reverse order (used in E2).
+Shown separately for groups trained with the original order (used in E1) and reverse order (used in E2).
 Error bars represent 95% credible intervals.
@@
 The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the  slope for the baseline condition.
-The interaction terms which include condit and Band (e.g., conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate the how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
+The interaction terms which include condit and Band (e.g., conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
 :::
@@
 For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
-The baseline effect of band represents the slope cofficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
+The baseline effect of band represents the slope coefficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
 Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
 However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating a greater slope for the varied condition trained with reverse order bands.
-This interaction is shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticably steeper than the other conditions.
+This interaction is shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticeably steeper than the other conditions.
 
@@
 #| label: fig-e3-test-vx
-#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
+#| fig-cap: Experiment 3. Empirical distribution of velocities produced in the testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
 #| fig-width: 11
@@
 extrapolation) on participants' accuracy and discrimination during the testing phase.
-Unlike the previous experiments, participants received ordinal feedback during the training phase.
+Unlike the previous experiments, participants received only ordinal, not continuous valued, feedback during the training phase.
 Additionally, Experiment 3 included both the original order condition from Experiment 1 and the reverse order condition from Experiment 2.
@@
 #| fig.cap: The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model as used in the present work.
+The diagram illustrates the basic structure of the ALM model used in the present work.
 Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
 The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
-The output nodes are activated as a function of the weighted sum of the input nodes - weights are updated via the delta rule.
+The output nodes are activated as a function of the weighted sum of the input nodes.
+During training, when feedback is provided, network weights connecting the input layer to the output layer are updated via the delta rule.
 alm_plot()
@@
 The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
-Parameter estimation was performed using approximate bayesian computation (ABC), which we describe in detail below.
+Parameter estimation was performed using approximate Bayesian computation (ABC), which we describe in detail below.
 
@@
 5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
-6) Repeat until desired number of posterior samples are obtained.
+6) Repeat until the desired number of posterior samples are obtained.
 
@@
 Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
-The initial value of $\epsilon$ was set to the overall standard deviation of each individuals velocity values.
+The initial value of $\epsilon$ was set to the overall standard deviation of each individual's velocity values.
 Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
@@
 #| label: tbl-htw-modelError-e1
-#| tbl-cap: "Models errors predicting empirical data from Experiment 1 -  aggregated over the full posterior distribution for each participant.
+#| tbl-cap: "Model errors predicting empirical data from Experiment 1 -  aggregated over the full posterior distribution for each participant.
 Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
@@
 
-The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) also show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that y axes are scaled different between plots).
+The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that Y-axes are scaled different between plots).
 Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
@@
 
-To quantitatively assess whether the differences in performance between models,  we fit a Bayesian regression predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
+To quantitatively assess the differences in performance between models, we fit a Bayesian regression model predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
 EXAM) and training condition (Constant vs.
@@
 There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group.
-To assess whether EXAM predicts constant performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
+To assess whether EXAM predicts performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
 The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
@@
 Varied), and the interaction between Model and Condition.
-The values represent the estimate coefficient for each term, with 95% credible intervals in brackets.
+The values represent the estimated coefficient for each term, with 95% credible intervals in brackets.
 The intercept reflects the baseline of ALM and Constant.
@@
 
-*Model Fits to Experiment 2 and 3.* Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment1 .
+*Model Fits to Experiment 2 and 3.*  Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment 1.
 For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
@@
 #| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied) on Model Error for Experiment 2 and 3 data.
-Experiment 3 also includes a control for the order of training vs.
+Varied) on Model Error for Experiments 2 and 3 data.
+Experiment 3 also includes a condition for the order of training vs.
 testing bands (original order vs.
@@
 Instead, rule-based responses emerge during the retrieval process.
-The constant groups' formation of a single, accurate input-output association, combined with the usefulness of the zero point, may have been sufficient for EXAM to capture their performance.
+The constant groups' formation of a single, accurate input-output association, combined with the usefulness of the zero point, seem to have been sufficient for EXAM to capture their performance.
 A potential concern is that the assumption of participants utilizing the zero point essentially transforms the extrapolation problem into an interpolation problem.
@@
 The fits to the individual participants also reveal a number of interesting cases where the models struggle to capture the data (@fig-htw-indv-pred).
-For example participant 68 exhibits a strong a strong non-monotonicity in the highest velocity band, a pattern which ALM can mimic, but which EXAM cannot capture, given it's to enforce a simple linear relationship between target velocity and response.
+For example participant 68 exhibits a strong non-monotonicity in the highest velocity band, a pattern which ALM can mimic, but which EXAM cannot capture, given that it enforces a simple linear relationship between target velocity and response.
 Participant 70 (lower right corner of @fig-htw-indv-pred) had a roughly parabolic response pattern in their observed data, a pattern which neither model can properly reproduce, but which causes EXAM to perform particularly poorly.
@@
 *Modeling Limitations.* The present work compared models based on their ability to predict the observed data, without employing conventional model fit indices such as the Akaike Information Criterion (AIC) or the Bayesian Information Criterion (BIC).
-These indices, which penalize models based on their number of free parameters, would have been of limited utility in this case, as both ALM and EXAM have two free parameters.
+These indices, which penalize models based on their number of free parameters, would have been of limited utility in the current case, as both ALM and EXAM have two free parameters.
 However, despite having the same number of free parameters, EXAM could still be considered the more complex model, as it incorporates all the components of ALM plus an additional mechanism for rule-based responding.
-A more comprehensive model comparison approach might involve performing cross-validation with a held-out subset of the data [@mezzadriHoldoutStrategySelecting2022] or penalizing models based on the range of patterns they can produce [@domeGdistanceComparisonModel2023].
+A more comprehensive model comparison approach might involve performing cross-validation with a held-out subset of the data [@mezzadriHoldoutStrategySelecting2022] or penalizing models based on the range of patterns they can produce [@domeGdistanceComparisonModel2023], under the assumption that more constrained models are more impressive when they do adequately fit a given pattern of results.
 

### 2024-07-09 Sections/HTW.qmd
update with more of Rob's edits, through end of Project 2 modeling results

@@
 
-*Participants* A total of 156 participants were recruited from the Indiana University Introductory Psychology Course.
+*Participants* A total of 156 participants were recruited from Indiana University Introductory Psychology Courses.
 Participants were randomly assigned to one of two training conditions: varied training or constant training.
 
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in Javascript, making heavy use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values  (e.g.
-band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below from the target band.
+*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in JavaScript, making use of the [phaser.io](https://phaser.io/) game library.
+The HTW task involved launching a projectile such that it would strike the "wall" at the target speed indicated at the top of the screen (see @fig-htw-task).
+The target velocities were given as a range, or band, of acceptable velocity values (e.g., band 800-1000).
+During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below  the target band.
 Participants were instructed that only the x velocity component of the ball was relevant to the task.
@@
 
-To estimate the  parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+To estimate the parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
 ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].

### 2024-07-09 Sections/full.qmd
update with more of Rob's edits, through end of Project 2 modeling results

@@
 #| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
+#| fig-cap: Experiment 1 -  Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
 p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
@@
 #| fig-cap: Experiment 1 Testing Accuracy.
-A) Empricial Deviations from target band during testing without feedback stage.
+A) Empiricial Deviations from target band during testing without feedback stage.
 B) Conditional effect of condition (Constant vs.
@@
 The Intercept represents the baseline condition, (constant training,  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
-Positive coefficients thus represent worse performance relative to the baseline, - and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
+Positive coefficients thus represent worse performance relative to the baseline, and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
 {.hover .sm}
@@
 
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed efects model predicting absolute deviation from the target band during the testing stage.
+*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed effects model predicting absolute deviation from the target band during the testing stage.
 There was no significant main effect of training condition,$\beta$ = `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ = `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
@@
 The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the slope for the baseline condition.
-The interaction terms which include condit and Band (e.g., conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate the how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
+The interaction terms which include condit and Band (e.g., conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
 :::
@@
 
-To estimate the parameters of ALM and EXAM, we used approximate bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
+To estimate the parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
 ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
@@
 
-To quantitatively assess whether the differences in performance between models, we fit a Bayesian regression predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
+To quantitatively assess the differences in performance between models, we fit a Bayesian regression model predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
 EXAM) and training condition (Constant vs.

### 2024-07-09 Manuscript/manuscript.qmd
add missing cite

@@
 The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014], language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022].
+The pattern of results is complex, with numerous studies finding both beneficial [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001; @gormanInstancebasedModelAccount2022], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022].
 The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.

### 2024-07-09 Manuscript/manuscript.qmd
final edits from Rob's doc

@@
 
-Our findings also diverge from the two previous studies to cleanly manipulate the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
+Our findings also diverge from the two previous studies that cleanly manipulated the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
 Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
 A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
-These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training - may have made it more difficult to observe any between-group differences of training variation in their study.
+These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training, may have made it more difficult to observe any between-group differences of training variation in their study.
 @vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
 However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have preculded any sense of a "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
+This entirely arbitrary mapping also would have precluded any sense sensible "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
 
@@
 First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
-Such a difference may be an unavoidable consequence of varied vs.
-constant design which match the total number of training trials between the two groups.
-However in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
+Such a difference may be an unavoidable consequence of a varied vs.
+constant design which matches the total number of training trials between the two groups.
+However, in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
 Another limitation is that the testing stage did not include any interpolation items, i.e.
-the participants tested only from the training bands they experienced during training, or from extrapolation bands.
+the participants were tested only from the training bands they experienced during training, or from extrapolation bands.
 The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
-Of course, the nature of the constant training condition makes interpolation testing impossible to implement, however future studies might compare a training regimes that each include at least 2 distinct items, but still differ in total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
+Of course, the nature of the constant training condition makes interpolation testing impossible to implement, however future studies might compare training regimes that each include at least 2 distinct items, but still differ in the total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
 Finally, the task employed in the present study consisted of only a linear, positive function.

### 2024-07-09 Manuscript/manuscript.qmd
render after Project 2 discussion edits

@@
 However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have precluded any sense sensible "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
+This entirely arbitrary mapping also would have precluded any sensible "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
 

### 2024-07-09 index.qmd
render after Project 2 discussion edits

@@
 - name: Thomas E. Gorman
-  affiliation: Indiana University
+  affiliations: 
+  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
     affiliation-url: https://psych.indiana.edu/
-  url: https://tegorman13.github.io/
-  orcid: 0000-0001-5366-5442
+  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
+    affiliation-url: https://cogs.indiana.edu/index.html
 comments: false
-date-format: 'MMM YYYY'
+date: today
+#date-format: 'MMM YYYY'
 format:

### 2024-07-13 Manuscript/manuscript.qmd
update with exclusion procedure and counts per experiment

@@
 
-*Participants* A total of 156 participants were recruited from Indiana University Introductory Psychology Courses.
-Participants were randomly assigned to one of two training conditions: varied training or constant training.
+*Participants.* A total of 183 participants were initially recruited from Indiana University Introductory Psychology Courses.
+Of these, 27 participants were excluded from further analysis due to meeting the exclusion criteria, resulting in a final sample of 156 participants.
+The exclusion criteria was defined as performance worse (i.e., larger deviations) than the condition average in either the training or testing stage of the experiment.
+The remaining participants were randomly assigned to one of two training conditions: varied training or constant training.
 
@@
 
+Initially, 131 participants were recruited.
+After applying the same exclusion procedure as in Experiment 1, 21 participants were excluded, resulting in a final sample of 110 participants who completed the experiment (Varied: 55, Constant: 55).
 The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
@@
 Both groups were tested from all six bands.
-A total of 110 participants completed the experiment (Varied: 55, Constant: 55).
 

### 2024-07-13 Sections/HTW.qmd
update with exclusion procedure and counts per experiment

@@
 Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
+227 participants were recruited initially.
 Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.

### 2024-08-02 revisions.qmd
start the revisions page. Updates to main paper files from the HTW updates I did awhile ago.

---
title: Revisions
---

## Primary Issues

1) General Discussion, idea of fitting ALM & EXAM to project 1 - parameter comparison across projects. 
2) Rationale for ordinal feedback in experiment 3. Literature suggesting ordinal is different from continuous. Discussion of how ordinal feedback could be implemented in the model
3) Project 2 discussion - implications of empirical results, and of modeling, take-aways from project
4) More foreshadowing of function learning literature. Show how Projects 1 and 2 are unified in terms of exploring theories of how variability during learning affects generalization.
5) learning c - how how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?
6) Distinction between experienced stimulii and behavioral action

## Distinction between experienced stimulii and behavioral action

- [link 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}

- [link 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\

## Learning c

**How how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?**

- [link 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)

### 2024-08-02 revisions.qmd
update revisions page

@@
 
+#### **Relevant Papers**
+
+- @wifallPerceptualSimilarityAffects2014
+
+- @wifallReachingResponseSelection2017
+
 ## Learning c
@@
 - [link 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)
+
+## Ordinal feedback rationale
+
+> In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
+Specifically, we provided ordinal feedback instead of the continuous feedback used in the previous two experiments.
+Ordinal feedback provides learners with directional information about the results of their throw (e.g., above the target, below the target, or hitting the target) rather than precise numerical deviations.
+This form of feedback resembles many real-world learning scenarios, such as a coach instructing an athlete to perform a movement using "more force" or "less force", or a teacher providing letter grades rather than numeric scores.
+Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
+For example, Cornwall et al., manipulated whether participants received categorical (correct or incorrect) vs.
+numerical feedback (reward points ranging from 50-100).
+
+#### **Relevant Papers**
+
+- @cornwallEffectsCategoricalNumerical2022

### 2024-08-02 revisions.qmd
update revision page

@@
 title: Revisions
+toc: true
 ---
@@
 
-1) General Discussion, idea of fitting ALM & EXAM to project 1 - parameter comparison across projects. 
-2) Rationale for ordinal feedback in experiment 3. Literature suggesting ordinal is different from continuous. Discussion of how ordinal feedback could be implemented in the model
-3) Project 2 discussion - implications of empirical results, and of modeling, take-aways from project
-4) More foreshadowing of function learning literature. Show how Projects 1 and 2 are unified in terms of exploring theories of how variability during learning affects generalization.
-5) learning c - how how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?
-6) Distinction between experienced stimulii and behavioral action
+1) **Plausiblity of fitting ALM & EXAM to project 1** - parameter comparison across projects. \
+
+2) **Rationale for ordinal feedback** in experiment 3. Literature suggesting ordinal is different from continuous. Discussion of how ordinal feedback could be implemented in the model \
+3) **Project 2 take aways** - implications of empirical results, and of modeling \
+4) **More foreshadowing of function learning literature**. Show how Projects 1 and 2 are unified in terms of exploring theories of how variability during learning affects generalization. \
+5) **How c is learned** - how how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii? \
+6) **Similarity spaces of stimuli vs. actions** - important distinctions? \
 
 ## Distinction between experienced stimulii and behavioral action
+<details><summary>
+[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}
+</summary>
+> Our modelling approach does differ from category learning implementations of instance-based models in several ways.
+One such difference is the nature of the training instances that are assumed to be stored.
+In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g., size/color/shape).
+Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
+An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g., movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
+Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work – though as described in the introduction there is some evidence in support of this idea (Chamberlin & Magill, 1992a; Crump & Logan, 2010; Hommel, 1998; Meigh et al., 2018; Poldrack et al., 1999).
+A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues (R.
+G.
+Cohen & Rosenbaum, 2004; Rosenbaum et al., 1995).
+Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
+Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
+A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
+</details>
 
-- [link 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}
-
-- [link 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\
+<details><summary>
+[relevant content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\
+</summary>
+> It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations (Nosofsky, 1992; Shepard, 1987).
+Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
+In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g., the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
+However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
+</details>
 
@@
 
-**How how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?**
-
-- [link 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)
+**How how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?** \
+<details><summary> 
+[relevant content](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)
+</summary>
+>However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group (Hahn et al., 2005; Lamberts, 1994).
+Relatedly, the influential Bayesian generalization model developed by Tenenbaum & Griffiths (2001) predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
+Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
+Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
+To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
+One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience (Nosofsky & Johansen, 2000; Sakamoto et al., 2006).
+If one’s training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
+Conversely, if one’s training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+</details>
 
@@
 
+<details><summary>Addition</summary>
 > In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
@@
 numerical feedback (reward points ranging from 50-100).
+</details>
 
@@
 - @cornwallEffectsCategoricalNumerical2022
+
+## Full Revision Instructions
+
+<details><summary>
+show
+</summary>
+1. Add participant/trial exclusion conditions for Project 2
+
+2.
+Compare parameters values across projects or explain why this isn't possible.  In the General Discussion to both projects, describe the prospects for applying ALM+EXAM to Project 1 (you don't have to actually fit Project 1 with ALM+EXAM).  If ALM+EXAM can likely fit both sets of results, with their opposite generalization patterns vis-a-vis constant vs variable training, then does ALM+EXAM provide a compelling explanation for constant > variable extrapolation in Project 2 or is it too flexible a model?
+
+3.
+Justify why the ordinal feedback in Project 2 Experiment 3 is an interesting manipulation.  Is there a literature suggesting that there would be an important difference between continuous vs ordinal feedback?  How would you incorporate ordinal feedback into ALM+EXAM (you don't have to actually implement this model)?
+
+4.
+In the discussion to Project 2, explain what are the most important implications of the empirical results for theories of human learning and generalization.  Also explain what are the most important implications of the ALM and EXAM modeling are for our understanding of human learning and generalization.  As it currently stands, there is not much of a take-home message from Project 2.
+
+5.
+Somewhere in the introduction to both of the projects, foreshadow the function learning literature that will be relevant to Project 2, and show how Projects 1 and 2 are unified in terms of exploring theories of how variability during learning affects generalization.
+
+6.
+Are there new predictions to make about how the process of c being learned during training would show up in the performance during training, or anywhere else?  For instance, do you propose that c is adjusted on the basis of experienced differences from one trial to the next, or on the basis of running estimates of SD in the data, etc.?
+Could differences in possible learning processes for c account for effects of massed vs.
+distributed presentation of stimuli?
+
+7.
+The distinction between experienced stimuli and behavioral actions  seems like an important factor to explore more in a discussion, given that the similarity space in the two could differ in ways that could affect behavior (and appropriate modeling).
+
+</details>

### 2024-08-13 Manuscript/manuscript.qmd
update after word spellcheck fixes

@@
 Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperfroms the constant group even from the constants group's home turf has not been consistently replicated.
+However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperforms the constant group even from the constants group's home turf has not been consistently replicated.
 One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
@@
 Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
+However, despite its appeal this contrast is relatively uncommon in the literature.
 It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
@@
 Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g., LDOOF), whereas for constant group B, the testing phase consisted of a arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
+Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g., LDOOF), whereas for constant group B, the testing phase consisted of an arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
 At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had three prior exposures to the word arrangement (i.e.
 the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and actually achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving two more anagrams on average than the constant group.
+However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving two more anagrams on average than the constant group.
 This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
@@
 Participants that received training on more highly-distorted items showed superior generalization to novel high distortion patterns in the subsequent testing phase.
-It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training rathers, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
+It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training trials, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
 This train-until-criterion procedure led to the high-variability condition participants tending to complete a larger number of training trials before switching to the testing stage.
-More recent work [@huHighvariabilityTrainingDoes2024], also used dot pattern categories, but matched the number of training trials across conditions.
+More recent work [@huHighvariabilityTrainingDoes2024] also used dot pattern categories, but matched the number of training trials across conditions.
 Under this procedure, higher-variability participants tended to reach lower levels of performance by the end of the training stage.
@@
 
-Recent studies have also begun utilizing more complex or realistic sitmuli when assessing the influence of variability on category learning.
+Recent studies have also begun utilizing more complex or realistic stimuli when assessing the influence of variability on category learning.
 @wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
-In a within-participants design, participants were trained on bird categories with either high repetitions of a few exemplars, or few repetitions of many exemplars.
+In a within-participants design, participants were trained on bird categories with either many repetitions of a few exemplars, or with few repetitions of many exemplars.
 Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
@@
 The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied participants, and also for their poorer performance in a recognition condition.
+This model accounted for both the extended generalization gradients of the varied participants, and for their poorer performance in a recognition condition.
 
@@
 They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples.
-The authors hypothesized that in order to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
+The authors hypothesized that to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
 To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples.
@@
 Interactions between prior experience and the influence of varied training have also been observed in sensorimotor learning [@guadagnoliRelationshipContextualInterference1999;  @delreyEffectsContextualInterference1982].
-@delreyEffectsContextualInterference1982 recruited participants who self-reported either extensive, or very little experience with athletic activities, and then trained participants on a coincident timing task under with either a single constant training velocity, with one of several varied training procedures.
+@delreyEffectsContextualInterference1982 recruited participants who self-reported either extensive, or very little experience with athletic activities, and then trained participants on a coincident timing task with either a single constant training velocity, or with one of several varied training procedures.
 Unsurprisingly, athlete participants had superior performance during training, regardless of  condition, and training performance was superior for all subjects in the constant group.
@@
 
-A number of theoretical frameworks have been proposed to conceptually explain the effects of varied training on learning and generalization.
+Several theoretical frameworks have been proposed to conceptually explain the effects of varied training on learning and generalization.
 Schema theory (described in more detail above), posts that varied practice leads to the formation of more flexible motor schemas, which then facilitate generalization [@schmidtSchemaTheoryDiscrete1975].
@@
 In contrast, the effects of variability have received more formal computational treatment in other domains, such as category learning [@hahnEffectsCategoryDiversity2005 @huHighvariabilityTrainingDoes2024],  language learning [@jonesDensityDistinctivenessEarly2020], and function learning [@deloshExtrapolationSineQua1997].
-A primary goal of the  current dissertation is to to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
+A primary goal of the  current dissertation is to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
 
@@
 Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar.
-In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimuli.
+In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimulus.
 Recall that participants are trained on only on distortions of the category prototypes (e.g.,  low, medium or high distortions), never encountering the exact prototypes during the training stage.
@@
 It's also referenced as a key influence in the development of the "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
-However a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
+However, a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
 @palmeriCentralTendenciesExtreme2001 demonstrated both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
 These authors conducted a near replication of the @posnerGenesisAbstractIdeas1968 study, but also had participants provide similarity judgements of the dot pattern stimuli after completing the training phase.
-A multidimensional scaling analysis of the similarity judgements revelead that the psychological representations of the prototype stimuli were not located in the middle of the training stimuli, but were instead extreme points in the psychological space.
+A multidimensional scaling analysis of the similarity judgements revealed that the psychological representations of the prototype stimuli were not located in the middle of the training stimuli, but were instead extreme points in the psychological space.
 The authors also demonstrated the generalization patterns of @posnerGenesisAbstractIdeas1968 could be accounted for by an exemplar-based model, without any need to assume the abstraction of a prototype.
@@
 
-The present work examines whether the commonly observed benefits of varied training can be accounted for by a theoretrically motivated measure of the similarity between training throws and the testing solution space.
+The present work examines whether the commonly observed benefits of varied training can be accounted for by a theoretically motivated measure of the similarity between training throws and the testing solution space.
 We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
@@
 
-To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
+To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy-based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
 We then averaged effects across these studies, yielding a Cohen's f =.43.
@@
 The superiority of varied training over constant training even at the constant training position is of particular note, given that testing at this position should have been highly similar for participants in the constant condition.
-It should also be noted, though, that testing at the constant trained position is not exactly identical to training from that position, given that the context of testing is different in several ways from that of training, such as the testing trials from the different positions being intermixed, as well as a simple change in context as a function of time.
+It should also be noted, though, that testing at the constant trained position is not identical to training from that position, given that the context of testing is different in several ways from that of training, such as the testing trials from the different positions being intermixed, as well as a simple change in context as a function of time.
 Such contextual differences will be further considered in the General Discussion.
@@
 On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both of the throwing locations trained by the varied group.
+Figure 5b also shows training performance separately for both throwing locations trained by the varied group.
 Error bars indicate standard error of the mean.
@@
 Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group).
-@fig-e2test1 displays the particular subset of comparisons utilized for this analysis.
+@fig-e2test1 displays the subset of comparisons utilized for this analysis.
 Again, we standardized performance within each position before performing the analyses on the aggregated data.
@@
 We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing [@soderstromLearningPerformanceIntegrative2015].
-However our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
+However, our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
 
@@
 The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
+When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group (c= .00011).
 Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
@@
 The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
+ALM is a two-layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
 ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance (see @fig-alm-diagram).
@@
 #| label: fig-delosh-extrap
-#| fig-cap: The generalization patterns of human particpiants observed in DeLosh et al.
+#| fig-cap: The generalization patterns of human participants observed in DeLosh et al.
 (1997) (reproduced from Figure 3 in their manuscript).
@@
 
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task task was programmed in JavaScript, making use of the [phaser.io](https://phaser.io/) game library.
+*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task was programmed in JavaScript, making use of the [phaser.io](https://phaser.io/) game library.
 The HTW task involved launching a projectile such that it would strike the "wall" at the target speed indicated at the top of the screen (see @fig-htw-task).
@@
 The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimates indicates a greater deviation (lower accuracy) for the varied group.
+A larger positive estimate indicates a greater deviation (lower accuracy) for the varied group.
 CrI values indicate 95% credible intervals.
@@
 B) The distribution of slope coefficients for each condition.
-Larger slopes indicates better discrimination between target bands.
+Larger slopes indicate better discrimination between target bands.
 C) Individual participant slopes.
@@
 B) The distribution of slope coefficients for each condition.
-Larger slopes indicates better discrimination.
+Larger slopes indicate better discrimination.
 C) Individual participant slopes.
@@
 Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However unlike experiment 1, the Varied and Constant groups did not show a significant difference in their discrimination between bands.
+However, unlike experiment 1, the Varied and Constant groups did not show a significant difference in their discrimination between bands.
 
@@
 
-To quantitatively assess the differences in performance between models, we fit a Bayesian regression model predicting the errors of the posterior predictions of each models as a function of the Model (ALM vs.
+To quantitatively assess the differences in performance between models, we fit a Bayesian regression model predicting the errors of the posterior predictions of each model as a function of the Model (ALM vs.
 EXAM) and training condition (Constant vs.
@@
 Our findings also diverge from the two previous studies that cleanly manipulated the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
-Like @deloshExtrapolationSineQua1997 , our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
-A noteworthy difference difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
+Like @deloshExtrapolationSineQua1997, our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
+A noteworthy difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
 These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training, may have made it more difficult to observe any between-group differences of training variation in their study.
@@
 While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
-First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had a three times more trials with the nearest velocity band.
+First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had three times more trials with the nearest velocity band.
 Such a difference may be an unavoidable consequence of a varied vs.
@@
 The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
-Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.
-In HTW,the relationship between feedback and optimal behavioral adjustment is also almost perfectly smooth, if participants produce a throw that is 100 units too hard, they'll be told that they were 100 units away from the target band.
+Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output responses are determined by a single input dimension.
+In HTW, the relationship between feedback and optimal behavioral adjustment is also almost perfectly smooth, if participants produce a throw that is 100 units too hard, they'll be told that they were 100 units away from the target band.
 Whereas in HTT, the presence of the barrier in introduces irregularities in the task space.
@@
 These findings highlight the importance of considering task characteristics when designing experiments intended to assess the influence of training interventions, and demonstrate the value of combining empirical and computational modeling approaches to uncover the cognitive mechanisms that support learning and generalization.
-Future research should continue to investigate the complex interplay between task demands, training manipulations, and individual differences, with the ultimate goal of optimizing educational and training outcomes across a wide range of domains.
+Future research should continue to investigate the complex interplay between task demands, training manipulations, and individual differences, with the goal of optimizing educational and training outcomes across a wide range of domains.
 

### 2024-08-13 Sections/full.qmd
update after word spellcheck fixes

@@
 Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperfroms the constant group even from the constants group's home turf has not been consistently replicated.
+However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperforms the constant group even from the constants group's home turf has not been consistently replicated.
 One recent study attempted a near replication of the Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
@@
 In contrast, the effects of variability have received more formal computational treatment in other domains, such as category learning [@hahnEffectsCategoryDiversity2005 @huHighvariabilityTrainingDoes2024], language learning [@jonesDensityDistinctivenessEarly2020], and function learning [@deloshExtrapolationSineQua1997].
-A primary goal of the current dissertation is to to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
+A primary goal of the current dissertation is to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
 

### 2024-08-13 revisions.qmd
revision doc updates
update after word spellcheck fixes

@@
 1) **Plausiblity of fitting ALM & EXAM to project 1** - parameter comparison across projects. \ 
-
 2) **Rationale for ordinal feedback** in experiment 3. Literature suggesting ordinal is different from continuous. Discussion of how ordinal feedback could be implemented in the model \
@@
 - @wifallPerceptualSimilarityAffects2014
-
 - @wifallReachingResponseSelection2017
@@
 <details><summary> 
-[relevant content](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)
+[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)
 </summary>
@@
 Conversely, if one’s training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+</details>
+
+<details><summary> 
+[relevant content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=A%20learning%20system,values%20for%20c.)
+</summary>
+>Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
+Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
+Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
+A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
+The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
+In this fashion, contextually appropriate c values could be empirically learned.
+This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
+
+As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning (Aha & Goldstone, 1992; Briscoe & Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al., 2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013; Taylor & Ivry, 2013; Thoroughman & Taylor, 2005).
+Lamberts (1994) showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
+The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability (Hahn et al., 2005; Sakamoto et al., 2006).
+However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
+Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains (Censor et al., 2012; Hills et al., 2010; Jamieson et al., 2022; Law & Gold, 2010; Roark et al., 2021; Rosenbaum et al., 2001; Vigo et al., 2018; Wall et al., 2021; Wu et al., 2020; J.
+Yang et al., 2020).
 </details>

### 2024-08-14 Manuscript/manuscript.qmd
changes for c-learning and ordinal feedback issues.

@@
 Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
+
 Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
@@
 This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
+@sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).
+In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalization observed around the high variability category when participants were tested with an ambiguous intermediary item.
+In a subsequent work [@sakamotoPuttingPsychologyBack2008], the same authors showed that a similar learning mechanism could account for the pattern wherein participants generalize more broadly around a category when the average distance between the category exemplars is larger (however the only model tested in this work was a prototype model).
 
@@
 
-As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
+As described above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
 @lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
@@
 
+In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
+Specifically, we provided ordinal feedback instead of the continuous feedback used in the previous two experiments.
+Ordinal feedback provides learners with directional information about the results of their throw (e.g., above the target, below the target, or hitting the target) rather than precise numerical deviations.
+This form of feedback resembles many real-world learning scenarios, such as a coach instructing an athlete to perform a movement using "more force" or "less force", or a teacher providing letter grades rather than numeric scores.
+Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
+For example, @cornwallEffectsCategoricalNumerical2022 manipulated whether participants received categorical (correct or incorrect) vs.
+numerical feedback (reward points ranging from 50-100).
+They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
+Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
+
 ### Methods & Procedure
 
-The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
+The only adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
 After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.

### 2024-08-14 Sections/HTW.qmd
changes for c-learning and ordinal feedback issues.

@@
 
+In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
+Specifically, we provided ordinal feedback instead of the continuous feedback used in the previous two experiments.
+Ordinal feedback provides learners with directional information about the results of their throw (e.g., above the target, below the target, or hitting the target) rather than precise numerical deviations.
+This form of feedback resembles many real-world learning scenarios, such as a coach instructing an athlete to perform a movement using "more force" or "less force", or a teacher providing letter grades rather than numeric scores.
+Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
+For example, @cornwallEffectsCategoricalNumerical2022 manipulated whether participants received categorical (correct or incorrect) vs.
+numerical feedback (reward points ranging from 50-100).
+They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
+Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
+
 ## Methods & Procedure
 
-The major adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
+The only adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
 After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.

### 2024-08-14 revisions.qmd
changes for c-learning and ordinal feedback issues.

@@
 
-1) **Plausiblity of fitting ALM & EXAM to project 1** - parameter comparison across projects. \ 
-2) **Rationale for ordinal feedback** in experiment 3. Literature suggesting ordinal is different from continuous. Discussion of how ordinal feedback could be implemented in the model \
-3) **Project 2 take aways** - implications of empirical results, and of modeling \
-4) **More foreshadowing of function learning literature**. Show how Projects 1 and 2 are unified in terms of exploring theories of how variability during learning affects generalization. \
-5) **How c is learned** - how how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii? \
-6) **Similarity spaces of stimuli vs. actions** - important distinctions? \
+1)  **Plausiblity of fitting ALM & EXAM to project 1** - parameter comparison across projects.  
+2)  **Rationale for ordinal feedback** in experiment 3. Literature suggesting ordinal is different from continuous. Discussion of how ordinal feedback could be implemented in the model\
+3)  **Project 2 take aways** - implications of empirical results, and of modeling\
+4)  **More foreshadowing of function learning literature**. Show how Projects 1 and 2 are unified in terms of exploring theories of how variability during learning affects generalization.\
+5)  **How c is learned** - how how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?\
+6)  **Similarity spaces of stimuli vs. actions** - important distinctions?\
 
 ## Distinction between experienced stimulii and behavioral action
-<details><summary>
-[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}
-</summary>
+
+<details>
+
+<summary>[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}</summary>
+
 > Our modelling approach does differ from category learning implementations of instance-based models in several ways.
@@
 A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
+
 </details>
 
-<details><summary>
-[relevant content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\
+<details>
+
+<summary>[relevant content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\
 </summary>
+
 > It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations (Nosofsky, 1992; Shepard, 1987).
@@
 However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
+
 </details>
@@
 
-**How how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?** \
-<details><summary> 
-[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)
-</summary>
->However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group (Hahn et al., 2005; Lamberts, 1994).
+**How how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?**\
+
+<details>
+
+<summary>[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)</summary>
+
+> However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group (Hahn et al., 2005; Lamberts, 1994).
 Relatedly, the influential Bayesian generalization model developed by Tenenbaum & Griffiths (2001) predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
@@
 Conversely, if one’s training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+
 </details>
 
-<details><summary> 
-[relevant content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=A%20learning%20system,values%20for%20c.)
-</summary>
->Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
-Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
+<details>
+
+<summary>[original content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=A%20learning%20system,values%20for%20c.)</summary>
+
+> Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
+>
+> Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
 Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
@@
 This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
-
-As mentioned above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning (Aha & Goldstone, 1992; Briscoe & Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al., 2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013; Taylor & Ivry, 2013; Thoroughman & Taylor, 2005).
+@sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).
+In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalization observed around the high variability category when participants were tested with an ambiguous intermediary item.
+In a subsequent work [@sakamotoPuttingPsychologyBack2008], the same authors showed that a similar learning mechanism could account for the pattern wherein participants generalize more broadly around a category when the average distance between the category exemplars is larger (however the only model tested in this work was a prototype model).
+>
+> As described above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning (Aha & Goldstone, 1992; Briscoe & Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al., 2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013; Taylor & Ivry, 2013; Thoroughman & Taylor, 2005).
 Lamberts (1994) showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
@@
 Yang et al., 2020).
+
 </details>
@@
 
-<details><summary>Addition</summary>
+<details>
+
+<summary>Addition</summary>
+
 > In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
@@
 Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
-For example, Cornwall et al., manipulated whether participants received categorical (correct or incorrect) vs.
+For example, @cornwallEffectsCategoricalNumerical2022 manipulated whether participants received categorical (correct or incorrect) vs.
 numerical feedback (reward points ranging from 50-100).
+They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
+Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
+
 </details>
@@
 
-<details><summary>
-show
-</summary>
+<details>
+
+<summary>show</summary>
+
 1.  Add participant/trial exclusion conditions for Project 2
@@
 2.
-Compare parameters values across projects or explain why this isn't possible.  In the General Discussion to both projects, describe the prospects for applying ALM+EXAM to Project 1 (you don't have to actually fit Project 1 with ALM+EXAM).  If ALM+EXAM can likely fit both sets of results, with their opposite generalization patterns vis-a-vis constant vs variable training, then does ALM+EXAM provide a compelling explanation for constant > variable extrapolation in Project 2 or is it too flexible a model?
+Compare parameters values across projects or explain why this isn't possible.  In the General Discussion to both projects, describe the prospects for applying ALM+EXAM to Project 1 (you don't have to actually fit Project 1 with ALM+EXAM).  If ALM+EXAM can likely fit both sets of results, with their opposite generalization patterns vis-a-vis constant vs variable training, then does ALM+EXAM provide a compelling explanation for constant \> variable extrapolation in Project 2 or is it too flexible a model?
 

### 2024-08-22 Manuscript/manuscript.qmd
foreshadowing and project 2 takeaway issues

@@
 
+To explain our results, we turned to the well established EXAM and ALM models.
+The disproportionate success of EXAM in capturing the performance of participants under the constant training condition suggests that rule-based extrapolation can emerge even from a limited set of training examples.
+This success hinges on the assumption that participants are able to leverage prior knowledge of the zero-point reference [@brownUnderestimationLinearFunction2017; @kwantesWhyPeopleUnderestimate2006].
+The zero-point reference, combined with accurate learning of the single trained velocity band enabled EXAM to capture the extrapolation patterns of the constant participants.
+However, it's important to acknowledge that the ALM model provided a better fit for a subset of participants in each of our three experiment, highlighting the presence of substantial individual differences in generalization patterns.
+
+This finding illustrates the importance of considering task structure when evaluating the effects of training variability on generalization and extrapolation.
+Some tasks, like the one in this study, may permit the use of zero-point knowledge or other prior information, while others may not.
+For example, a zero point may be less relevant in visuomotor tasks with complex rotations [@vanDamMappingShapeVisuomotor2015; @rollerVariablePracticeLenses2001], or in complex sports techniques [@northEffectConsistentVaried2019].
+Future research should systematically investigate how different task structures interact with training variability to influence learning outcomes and generalization abilities, taking into account factors such as the availability of prior knowledge, the complexity of the task, and the specific learning mechanisms involved.
+This approach could help reconcile seemingly contradictory findings in the literature and provide more nuanced guidelines for designing effective training protocols across various domains.
+
 *Limitations*

### 2024-08-22 Sections/full.qmd
foreshadowing and project 2 takeaway issues

@@
 
-Project 2 shifted focus to the domain of function learning by employing a visuomotor extrapolation task.
-Across three experiments, we examined how constant and varied training regimes affected learning, discrimination between stimuli, and the ability to extrapolate to novel regions of the function's input space.
-To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.
+Project 2 will focus on the domain of function learning and in particular the issue of extrapolation.
+Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
+The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997 @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
+Project 2 of this dissertation will address this gap by investigating how constant and varied training regimes affect learning, discrimination, and extrapolation in a novel visuomotor function learning task.
+We will leverage the ALM and EXAM models, fitted to individual participant data using advanced Bayesian techniques, to provide a detailed computational account of the observed empirical patterns.
 

### 2024-08-22 revisions.qmd
foreshadowing and project 2 takeaway issues

@@
 6)  **Similarity spaces of stimuli vs. actions** - important distinctions?\
+
+-----
+
+## Project 2 Takeaways
+
+### Final paragraph on model implications:
+
+To explain our results, we turned to the well established EXAM and ALM models.
+The disproportionate success of EXAM in capturing the performance of participants under the constant training condition suggests that rule-based extrapolation can emerge even from a limited set of training examples.
+This success hinges on the assumption that participants are able to leverage prior knowledge of the zero-point reference [@brownUnderestimationLinearFunction2017; @kwantesWhyPeopleUnderestimate2006].
+The zero-point reference, combined with accurate learning of the single trained velocity band enabled EXAM to capture the extrapolation patterns of the constant participants.
+However, it's important to acknowledge that the ALM model provided a better fit for a subset of participants in each of our three experiment, highlighting the presence of substantial individual differences in generalization patterns.
+
+This finding illustrates the importance of considering task structure when evaluating the effects of training variability on generalization and extrapolation.
+Some tasks, like the one in this study, may permit the use of zero-point knowledge or other prior information, while others may not.
+For example, a zero point may be less relevant in visuomotor tasks with complex rotations [@vanDamMappingShapeVisuomotor2015; @rollerVariablePracticeLenses2001], or in complex sports techniques [@northEffectConsistentVaried2019].
+Future research should systematically investigate how different task structures interact with training variability to influence learning outcomes and generalization abilities, taking into account factors such as the availability of prior knowledge, the complexity of the task, and the specific learning mechanisms involved.
+This approach could help reconcile seemingly contradictory findings in the literature and provide more nuanced guidelines for designing effective training protocols across various domains.
+
+------
 
@@
 @sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).
-In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalization observed around the high variability category when participants were tested with an ambiguous intermediary item.
+In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalione   zation observed around the high variability category when participants were tested with an ambiguous intermediary item.
 In a subsequent work [@sakamotoPuttingPsychologyBack2008], the same authors showed that a similar learning mechanism could account for the pattern wherein participants generalize more broadly around a category when the average distance between the category exemplars is larger (however the only model tested in this work was a prototype model).
@@
 
+## Foreshadowing function learning literature
+
+Project 2 will focus on the domain of function learning and in particular the issue of extrapolation.
+Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
+The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997 @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
+Project 2 of this dissertation will address this gap by investigating how constant and varied training regimes affect learning, discrimination, and extrapolation in a novel visuomotor function learning task.
+We will leverage the ALM and EXAM models, fitted to individual participant data using advanced Bayesian techniques, to provide a detailed computational account of the observed empirical patterns.
+
 ## Full Revision Instructions

### 2024-08-22 Manuscript/manuscript.qmd
re-render after updates

@@
 
-Project 2 shifted focus to the domain of function learning by employing a visuomotor extrapolation task.
-Across three experiments, we examined how constant and varied training regimes affected learning, discrimination between stimuli, and the ability to extrapolate to novel regions of the function's input space.
-To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.
+Project 2 will focus on the domain of function learning and in particular the issue of extrapolation.
+Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
+The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
+Project 2 of this dissertation will address this gap by investigating how constant and varied training regimes affect learning, discrimination, and extrapolation in a novel visuomotor function learning task.
+We will leverage the ALM and EXAM models, fitted to individual participant data using advanced Bayesian techniques, to provide a detailed computational account of the observed empirical patterns.
 
@@
 Some tasks, like the one in this study, may permit the use of zero-point knowledge or other prior information, while others may not.
-For example, a zero point may be less relevant in visuomotor tasks with complex rotations [@vanDamMappingShapeVisuomotor2015; @rollerVariablePracticeLenses2001], or in complex sports techniques [@northEffectConsistentVaried2019].
+For example, a zero point may be less relevant in visuomotor tasks with complex rotations [@vandamMappingShapeVisuomotor2015; @rollerVariablePracticeLenses2001], or in complex sports techniques [@northEffectConsistentVaried2019].
 Future research should systematically investigate how different task structures interact with training variability to influence learning outcomes and generalization abilities, taking into account factors such as the availability of prior knowledge, the complexity of the task, and the specific learning mechanisms involved.

### 2024-08-22 Sections/full.qmd
re-render after updates

@@
 Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
-The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997 @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
 However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.

### 2024-08-22 revisions.qmd
re-render after updates

@@
 
-## Project 2 Takeaways
+## Project Comparison
 
-### Final paragraph on model implications:
+## Project 2 implications:
 

### 2024-08-27 Manuscript/manuscript.qmd
fix minor typo
add discussion of model comparison between projects; and stimuli vs. response issue. Fix $c$ formatting.

@@
 Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
+To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the $c$ parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
 One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
@@
 Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p\<.01).
-Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the c parameter separately between groups (Similarity2c).
+Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the $c$ parameter separately between groups (Similarity2c).
 In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p\<.01), with the varied group still performing significantly better.
@@
 The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group (c= .00011).
+When fit with separate c values, the best fitting $c$ parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group (c= .00011).
 Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
@@
 A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
-The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
+The $c$ parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
 In this fashion, contextually appropriate c values could be empirically learned.
@@
 Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y-axes of the plots for the c parameter are scaled logarithmically."
+Note that the y-axes of the plots for the $c$ parameter are scaled logarithmically."
 #| fig-height: 6
@@
 ALM and EXAM have been used as models of function learning, cue judgement, and forecasting behavior in numerous studies over the past 25 years [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @brownUnderestimationLinearFunction2017; @kwantesItemOrderMatters2012; @kelleyComparisonModelsLearning2008; @kaneApplicationsBiasVariance2020; @vonhelversenLearningMultiplecueJudgment2010].
-The present work presents the first application of these models to to the study of training variability in a visuomotor function learning task.
+The present work presents the first application of these models to the study of training variability in a visuomotor function learning task.
 We fit both models to individual participant data, using a form of simulation-based Bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
@@
 
-The HTT and HTW tasks differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).
+The HTT and HTW tasks differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff for a detailed comparison of the two tasks).
 
@@
 
-### Conclusion
+It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models employed in each project.
+The IGAS model of Project 1 serves as a descriptive measurement model, capturing the similarity between training throws and testing conditions.
+In contrast, the ALM and EXAM models of Project 2 are full process models, capable of generating exact predictions for both learning and testing stages.
+The difference is also reflected in the interpretion of the generalization parameter ($c$) across the models of the two projects.
+In IGAS, $c$ moderates the similarity between executed throws and subsequent testing solutions, while in ALM and EXAM, $c$ governs the extent to which the perceived stimuli activate the input layer nodes.
+Despite these differences, insights from ALM/EXAM, particularly the role of zero-point knowledge, may offer potential explanations for the contrasting empirical results.
+Particularly, EXAM's reliance on zero-point knowledge in the simpler HTW task may explain why constant training was more effective in Project 2, while the lack of a clear zero-point reference in the more complex HTT task of Project 1 may have increased the value of varied training.
+This suggests that the benefits of variability depend critically on how task structure interacts with prior knowledge and the learner's capacity to leverage such knowledge for generalization.
+
+Future work could explore extending ALM and EXAM, which have traditionally been applied to one-dimensional function learning tasks, to more complex motor tasks such as HTT.
+The neural network structure of ALM could be adapted to handle 2D input by utilizing a 2D grid of input nodes, allowing the model to learn mappings between 2D throwing velocities and desired outcomes.
+This would allow the model to process the more complex spatial information inherent in tasks like HTT.
+Furthermore, the output layers of ALM/EXAM could be expanded to express more complex motor outputs in addition to velocity, such as the locations of grabbing and releasing the projectile or other parameters defining the unique trajectories produced.
+In addition to allowing the models to be applied to more complex tasks, these modifications could enable researchers to investigate how perceptual similarity (i.e., the similarity of stimuli) and motoric similarity (i.e., the similarity of behavioral actions) may separately and jointly influence learning and generalization.
+
+## Conclusion
 

### 2024-08-27 Sections/IGAS.qmd
add discussion of model comparison between projects; and stimuli vs. response issue. Fix $c$ formatting.

@@
 The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting c parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
+When fit with separate c values, the best fitting $c$ parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
 Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.

### 2024-08-27 revisions.qmd
add discussion of model comparison between projects; and stimuli vs. response issue. Fix $c$ formatting.

@@
 
-## Project Comparison
+$c$ vs. *c*
+
+## Project Model Comparison/Discussion
+
+It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models employed in each project.
+The IGAS model of Project 1 serves as a descriptive measurement model, capturing the similarity between training throws and testing conditions.
+In contrast, the ALM and EXAM models of Project 2 are full process models, capable of generating exact predictions for both learning and testing stages.
+The difference is also reflected in the interpretion of the generalization parameter ($c$) across the models of the two projects.
+In IGAS, $c$ moderates the similarity between executed throws and subsequent testing solutions, while in ALM and EXAM, $c$ governs the extent to which the perceived stimuli activate the input layer nodes.
+Despite these differences, insights from ALM/EXAM, particularly the role of zero-point knowledge, may offer potential explanations for the contrasting empirical results.
+Particularly, EXAM's reliance on zero-point knowledge in the simpler HTW task may explain why constant training was more effective in Project 2, while the lack of a clear zero-point reference in the more complex HTT task of Project 1 may have increased the value of varied training.
+This suggests that the benefits of variability depend critically on how task structure interacts with prior knowledge and the learner's capacity to leverage such knowledge for generalization.
+
+Future work could explore extending ALM and EXAM, which have traditionally been applied to one-dimensional function learning tasks, to more complex motor tasks such as HTT.
+The neural network structure of ALM could be adapted to handle 2D input by utilizing a 2D grid of input nodes, allowing the model to learn mappings between 2D throwing velocities and desired outcomes.
+This would allow the model to process the more complex spatial information inherent in tasks like HTT.
+Furthermore, the output layers of ALM/EXAM could be expanded to express more complex motor outputs in addition to velocity, such as the locations of grabbing and releasing the projectile or other parameters defining the unique trajectories produced.
+In addition to allowing the models to be applied to more complex tasks, these modifications could enable researchers to investigate how perceptual similarity (i.e., the similarity of stimuli) and motoric similarity (i.e., the similarity of behavioral actions) may separately and jointly influence learning and generalization.
 

### 2024-08-27 Manuscript/manuscript.qmd
re-render with more revision updates

@@
 If one's training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
-Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c, to varied and constant participants.
-To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
+Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of $c$ so that generalization falls off rapidly away from the trained positions.
+
+To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, $c$, to varied and constant participants.
+To perform this parameter fitting, we used the optim function in R, and fit the model to find the $c$ value(s) that maximized the correlation between similarity and testing performance.
 
@@
 Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p\<.01).
-Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the $c$ parameter separately between groups (Similarity2c).
+Of greater interest is the difference between linear model 2, in which similarity is computed from a single $c$ value fit from all participants (Similarity1c), with linear model 4, which fits the $c$ parameter separately between groups (Similarity2c).
 In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p\<.01), with the varied group still performing significantly better.
@@
 Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
-The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting $c$ parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group (c= .00011).
-Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
+The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two $c$ values over similarity computed with a single $c$ value.
+When fit with separate $c$ values, the best fitting $c$ parameters for the model consistently optimized such that the $c$ value for the varied group (c=.00008) was smaller in magnitude than the $c$ value for the constant group (c= .00011).
+Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of $c$ will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
 
@@
 In Experiment 1 varied participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
+In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization ($c$).
 Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
@@
 Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
-A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
+A learning system could end up adopting a higher $c$ value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
 The $c$ parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
-In this fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
+In this fashion, contextually appropriate $c$ values could be empirically learned.
+This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for $c$.
 @sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).

### 2024-08-27 Sections/IGAS.qmd
re-render with more revision updates

@@
 To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the $c$ parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
-One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
+One specific hypothesis is that people adaptively set a value of $c$ to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
 If one's training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
-Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of $c$ so that generalization falls off rapidly away from the trained positions.
 
-To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c, to varied and constant participants.
-To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
+To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, $c$, to varied and constant participants.
+To perform this parameter fitting, we used the optim function in R, and fit the model to find the $c$ value(s) that maximized the correlation between similarity and testing performance.
 
@@
 Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
-The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting $c$ parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group(c= .00011).
-Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
+The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two $c$ values over similarity computed with a single $c$ value.
+When fit with separate $c$ values, the best fitting $c$ parameters for the model consistently optimized such that the $c$ value for the varied group (c=.00008) was smaller in magnitude than the $c$ value for the constant group (c= .00011).
+Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of $c$ will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
 

### 2024-08-27 revisions.qmd
re-render with more revision updates

@@
 
+<style>
+/* Style for Addition callouts */
+.addition-callout summary {
+    background-color: #f0f8ff;
+    padding: 10px;
+    border: 1px solid #ccc;
+    border-radius: 5px;
+}
+
+.addition-callout div {
+    background-color: #f9f9f9;
+    padding: 15px;
+    border: 1px solid #ddd;
+    border-radius: 5px;
+}
+
+/* Style for Relevant Content callouts */
+.relevant-callout summary {
+    background-color: #f5f5f5;
+    padding: 10px;
+    border: 1px solid #bbb;
+    border-radius: 5px;
+}
+
+.relevant-callout div {
+    background-color: #ffffff;
+    padding: 15px;
+    border: 1px solid #ccc;
+    border-radius: 5px;
+}
+</style>
+
 ## Primary Issues
 
-1)  **Plausiblity of fitting ALM & EXAM to project 1** - parameter comparison across projects.  
-2)  **Rationale for ordinal feedback** in experiment 3. Literature suggesting ordinal is different from continuous. Discussion of how ordinal feedback could be implemented in the model\
-3)  **Project 2 take aways** - implications of empirical results, and of modeling\
-4)  **More foreshadowing of function learning literature**. Show how Projects 1 and 2 are unified in terms of exploring theories of how variability during learning affects generalization.\
-5)  **How c is learned** - how how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?\
-6)  **Similarity spaces of stimuli vs. actions** - important distinctions?\
-
------
-
-$c$ vs. *c*
-
-## Project Model Comparison/Discussion
-
-It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models employed in each project.
-The IGAS model of Project 1 serves as a descriptive measurement model, capturing the similarity between training throws and testing conditions.
-In contrast, the ALM and EXAM models of Project 2 are full process models, capable of generating exact predictions for both learning and testing stages.
-The difference is also reflected in the interpretion of the generalization parameter ($c$) across the models of the two projects.
-In IGAS, $c$ moderates the similarity between executed throws and subsequent testing solutions, while in ALM and EXAM, $c$ governs the extent to which the perceived stimuli activate the input layer nodes.
-Despite these differences, insights from ALM/EXAM, particularly the role of zero-point knowledge, may offer potential explanations for the contrasting empirical results.
-Particularly, EXAM's reliance on zero-point knowledge in the simpler HTW task may explain why constant training was more effective in Project 2, while the lack of a clear zero-point reference in the more complex HTT task of Project 1 may have increased the value of varied training.
-This suggests that the benefits of variability depend critically on how task structure interacts with prior knowledge and the learner's capacity to leverage such knowledge for generalization.
-
-Future work could explore extending ALM and EXAM, which have traditionally been applied to one-dimensional function learning tasks, to more complex motor tasks such as HTT.
-The neural network structure of ALM could be adapted to handle 2D input by utilizing a 2D grid of input nodes, allowing the model to learn mappings between 2D throwing velocities and desired outcomes.
-This would allow the model to process the more complex spatial information inherent in tasks like HTT.
-Furthermore, the output layers of ALM/EXAM could be expanded to express more complex motor outputs in addition to velocity, such as the locations of grabbing and releasing the projectile or other parameters defining the unique trajectories produced.
-In addition to allowing the models to be applied to more complex tasks, these modifications could enable researchers to investigate how perceptual similarity (i.e., the similarity of stimuli) and motoric similarity (i.e., the similarity of behavioral actions) may separately and jointly influence learning and generalization.
-
-## Project 2 implications:
-
-To explain our results, we turned to the well established EXAM and ALM models.
-The disproportionate success of EXAM in capturing the performance of participants under the constant training condition suggests that rule-based extrapolation can emerge even from a limited set of training examples.
-This success hinges on the assumption that participants are able to leverage prior knowledge of the zero-point reference [@brownUnderestimationLinearFunction2017; @kwantesWhyPeopleUnderestimate2006].
-The zero-point reference, combined with accurate learning of the single trained velocity band enabled EXAM to capture the extrapolation patterns of the constant participants.
-However, it's important to acknowledge that the ALM model provided a better fit for a subset of participants in each of our three experiment, highlighting the presence of substantial individual differences in generalization patterns.
-
-This finding illustrates the importance of considering task structure when evaluating the effects of training variability on generalization and extrapolation.
-Some tasks, like the one in this study, may permit the use of zero-point knowledge or other prior information, while others may not.
-For example, a zero point may be less relevant in visuomotor tasks with complex rotations [@vandamMappingShapeVisuomotor2015; @rollerVariablePracticeLenses2001], or in complex sports techniques [@northEffectConsistentVaried2019].
-Future research should systematically investigate how different task structures interact with training variability to influence learning outcomes and generalization abilities, taking into account factors such as the availability of prior knowledge, the complexity of the task, and the specific learning mechanisms involved.
-This approach could help reconcile seemingly contradictory findings in the literature and provide more nuanced guidelines for designing effective training protocols across various domains.
-
-------
-
-## Distinction between experienced stimulii and behavioral action
+1)  **Participant/trial exclusion conditions for Project 2** \
+2)  **Plausiblity of fitting ALM & EXAM to project 1**  
+3)  **Rationale for ordinal feedback** 
+4)  **Project 2 take aways** 
+5)  **More foreshadowing of function learning literature**. 
+6)  **How c is learned/updated** 
+7)  **Similarity spaces of stimuli vs. actions**
 
 <details>
-
-<summary>[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}</summary>
-
-> Our modelling approach does differ from category learning implementations of instance-based models in several ways.
-One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g., size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g., movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
-Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work – though as described in the introduction there is some evidence in support of this idea (Chamberlin & Magill, 1992a; Crump & Logan, 2010; Hommel, 1998; Meigh et al., 2018; Poldrack et al., 1999).
-A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues (R.
-G.
-Cohen & Rosenbaum, 2004; Rosenbaum et al., 1995).
-Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
-Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
-A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
-
-</details>
-
-<details>
-
-<summary>[relevant content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\
-</summary>
-
-> It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations (Nosofsky, 1992; Shepard, 1987).
-Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
-In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g., the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
-However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
-
-</details>
-
-#### **Relevant Papers**
-
--   @wifallPerceptualSimilarityAffects2014
--   @wifallReachingResponseSelection2017
-
-## Learning c
-
-**How how does this show up in training data? Process by which c is updated? Can it account for massed vs. distributed presentation of stimulii?**\
-
-<details>
-
-<summary>[relevant content 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.)</summary>
-
-> However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group (Hahn et al., 2005; Lamberts, 1994).
-Relatedly, the influential Bayesian generalization model developed by Tenenbaum & Griffiths (2001) predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
-Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
-Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the c parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
-One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience (Nosofsky & Johansen, 2000; Sakamoto et al., 2006).
-If one’s training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
-Conversely, if one’s training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
-
-</details>
-
-<details>
-
-<summary>[original content 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=A%20learning%20system,values%20for%20c.)</summary>
-
-> Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
->
-> Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
-Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
-A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
-The c parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
-In this fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
-@sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).
-In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalione   zation observed around the high variability category when participants were tested with an ambiguous intermediary item.
-In a subsequent work [@sakamotoPuttingPsychologyBack2008], the same authors showed that a similar learning mechanism could account for the pattern wherein participants generalize more broadly around a category when the average distance between the category exemplars is larger (however the only model tested in this work was a prototype model).
->
-> As described above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning (Aha & Goldstone, 1992; Briscoe & Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al., 2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013; Taylor & Ivry, 2013; Thoroughman & Taylor, 2005).
-Lamberts (1994) showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability (Hahn et al., 2005; Sakamoto et al., 2006).
-However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains (Censor et al., 2012; Hills et al., 2010; Jamieson et al., 2022; Law & Gold, 2010; Roark et al., 2021; Rosenbaum et al., 2001; Vigo et al., 2018; Wall et al., 2021; Wu et al., 2020; J.
-Yang et al., 2020).
-
-</details>
-
-## Ordinal feedback rationale
-
-<details>
-
-<summary>Addition</summary>
-
-> In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
-Specifically, we provided ordinal feedback instead of the continuous feedback used in the previous two experiments.
-Ordinal feedback provides learners with directional information about the results of their throw (e.g., above the target, below the target, or hitting the target) rather than precise numerical deviations.
-This form of feedback resembles many real-world learning scenarios, such as a coach instructing an athlete to perform a movement using "more force" or "less force", or a teacher providing letter grades rather than numeric scores.
-Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
-For example, @cornwallEffectsCategoricalNumerical2022 manipulated whether participants received categorical (correct or incorrect) vs.
-numerical feedback (reward points ranging from 50-100).
-They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
-Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
-
-</details>
-
-#### **Relevant Papers**
-
--   @cornwallEffectsCategoricalNumerical2022
-
-## Foreshadowing function learning literature
-
-Project 2 will focus on the domain of function learning and in particular the issue of extrapolation.
-Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
-The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
-However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
-Project 2 of this dissertation will address this gap by investigating how constant and varied training regimes affect learning, discrimination, and extrapolation in a novel visuomotor function learning task.
-We will leverage the ALM and EXAM models, fitted to individual participant data using advanced Bayesian techniques, to provide a detailed computational account of the observed empirical patterns.
-
-## Full Revision Instructions
-
-<details>
-
-<summary>show</summary>
+<summary>show full revision instructions from Rob</summary>
 
@@
 The distinction between experienced stimuli and behavioral actions  seems like an important factor to explore more in a discussion, given that the similarity space in the two could differ in ways that could affect behavior (and appropriate modeling).
+</details>
 
+-----
+
+**Note.** 
+For each issue - callouts distinguish between novel text that has been added (Additions), and relevant existing content that is also relevant to the issue.
+Each item also includes a link to where the change was implemented in the full manuscript.
+
+----
+
+## 1) Participant/trial exclusion conditions for Project 2
+
+<details open class="addition-callout">
+<summary>Addition [link to context in full manuscript](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#methods-30){target="_blank"}</summary>
+<div>
+*Participants.* A total of 183 participants were initially recruited from Indiana University Introductory Psychology Courses.
+Of these, 27 participants were excluded from further analysis due to meeting the exclusion criteria, resulting in a final sample of 156 participants.
+The exclusion criteria was defined as performance worse (i.e., larger deviations) than the condition average in either the training or testing stage of the experiment.
+The remaining participants were randomly assigned to one of two training conditions: varied training or constant training.
+</div>
 </details>
+
+## 2) IGAS vs. ALM/EXAM Model Comparison/Discussion
+
+<details open class="addition-callout">
+<summary>Addition [link to context in full manuscript](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20important%20to%20note){target="_blank"}</summary>
+
+<div>
+It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models employed in each project.
+The IGAS model of Project 1 serves as a descriptive measurement model, capturing the similarity between training throws and testing conditions.
+In contrast, the ALM and EXAM models of Project 2 are full process models, capable of generating exact predictions for both learning and testing stages.
+The difference is also reflected in the interpretation of the generalization parameter ($c$) across the models of the two projects.
+In IGAS, $c$ moderates the similarity between executed throws and subsequent testing solutions, while in ALM and EXAM, $c$ governs the extent to which the perceived stimuli activate the input layer nodes.
+Despite these differences, insights from ALM/EXAM, particularly the role of zero-point knowledge, may offer potential explanations for the contrasting empirical results.
+Particularly, EXAM's reliance on zero-point knowledge in the simpler HTW task may explain why constant training was more effective in Project 2, while the lack of a clear zero-point reference in the more complex HTT task of Project 1 may have increased the value of varied training.
+This suggests that the benefits of variability depend critically on how task structure interacts with prior knowledge and the learner's capacity to leverage such knowledge for generalization.
+
+Future work could explore extending ALM and EXAM, which have traditionally been applied to one-dimensional function learning tasks, to more complex motor tasks such as HTT.
+The neural network structure of ALM could be adapted to handle 2D input by utilizing a 2D grid of input nodes, allowing the model to learn mappings between 2D throwing velocities and desired outcomes.
+This would allow the model to process the more complex spatial information inherent in tasks like HTT.
+Furthermore, the output layers of ALM/EXAM could be expanded to express more complex motor outputs in addition to velocity, such as the locations of grabbing and releasing the projectile or other parameters defining the unique trajectories produced.
+In addition to allowing the models to be applied to more complex tasks, these modifications could enable researchers to investigate how perceptual similarity (i.e., the similarity of stimuli) and motoric similarity (i.e., the similarity of behavioral actions) may separately and jointly influence learning and generalization.
+</div>
+</details>
+
+## 3) Ordinal feedback rationale
+
+<details open class="addition-callout">
+<summary>Addition [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#experiment-3-38){target="_blank"}</summary>
+<div>
+> In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
+Specifically, we provided ordinal feedback instead of the continuous feedback used in the previous two experiments.
+Ordinal feedback provides learners with directional information about the results of their throw (e.g., above the target, below the target, or hitting the target) rather than precise numerical deviations.
+This form of feedback resembles many real-world learning scenarios, such as a coach instructing an athlete to perform a movement using "more force" or "less force", or a teacher providing letter grades rather than numeric scores.
+Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
+For example, @cornwallEffectsCategoricalNumerical2022 manipulated whether participants received categorical (correct or incorrect) vs.
+numerical feedback (reward points ranging from 50-100).
+They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
+Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
+</div>
+</details>
+
+## 4) Project 2 take-aways:
+
+<details open>
+<summary style="background-color: #f0f8ff; padding: 10px; border: 1px solid #ccc; border-radius: 5px;">Addition [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=we%20turned%20to%20the%20well){target="_blank"}</summary>
+<div style="background-color: #f9f9f9; padding: 15px; border: 1px solid #ddd; border-radius: 5px;">
+To explain our results, we turned to the well established EXAM and ALM models.
+The disproportionate success of EXAM in capturing the performance of participants under the constant training condition suggests that rule-based extrapolation can emerge even from a limited set of training examples.
+This success hinges on the assumption that participants are able to leverage prior knowledge of the zero-point reference [@brownUnderestimationLinearFunction2017; @kwantesWhyPeopleUnderestimate2006].
+The zero-point reference, combined with accurate learning of the single trained velocity band enabled EXAM to capture the extrapolation patterns of the constant participants.
+However, it's important to acknowledge that the ALM model provided a better fit for a subset of participants in each of our three experiment, highlighting the presence of substantial individual differences in generalization patterns.
+
+This finding illustrates the importance of considering task structure when evaluating the effects of training variability on generalization and extrapolation.
+Some tasks, like the one in this study, may permit the use of zero-point knowledge or other prior information, while others may not.
+For example, a zero point may be less relevant in visuomotor tasks with complex rotations [@vandamMappingShapeVisuomotor2015; @rollerVariablePracticeLenses2001], or in complex sports techniques [@northEffectConsistentVaried2019].
+Future research should systematically investigate how different task structures interact with training variability to influence learning outcomes and generalization abilities, taking into account factors such as the availability of prior knowledge, the complexity of the task, and the specific learning mechanisms involved.
+This approach could help reconcile seemingly contradictory findings in the literature and provide more nuanced guidelines for designing effective training protocols across various domains.
+</div>
+</details>
+
+------
+
+## 5) Stimuli vs. Action Similarity
+
+**Note.**  The novel text for this issue overlaps with the novel text for the IGAS vs. ALM/EXAM Model Comparison/Discussion issue.
+
+<details open class="addition-callout">
+<summary>Addition [link to context in full manuscript](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20important%20to%20note){target="_blank"}</summary>
+
+<div>
+Future work could explore extending ALM and EXAM, which have traditionally been applied to one-dimensional function learning tasks, to more complex motor tasks such as HTT.
+The neural network structure of ALM could be adapted to handle 2D input by utilizing a 2D grid of input nodes, allowing the model to learn mappings between 2D throwing velocities and desired outcomes.
+This would allow the model to process the more complex spatial information inherent in tasks like HTT.
+Furthermore, the output layers of ALM/EXAM could be expanded to express more complex motor outputs in addition to velocity, such as the locations of grabbing and releasing the projectile or other parameters defining the unique trajectories produced.
+In addition to allowing the models to be applied to more complex tasks, these modifications could enable researchers to investigate how perceptual similarity (i.e., the similarity of stimuli) and motoric similarity (i.e., the similarity of behavioral actions) may separately and jointly influence learning and generalization.
+</div>
+</details>
+
+<details>
+<summary>relevant existing content 1 [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}</summary>
+> Our modelling approach does differ from category learning implementations of instance-based models in several ways.
+One such difference is the nature of the training instances that are assumed to be stored.
+In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g., size/color/shape).
+Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
+An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g., movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
+Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work – though as described in the introduction there is some evidence in support of this idea (Chamberlin & Magill, 1992a; Crump & Logan, 2010; Hommel, 1998; Meigh et al., 2018; Poldrack et al., 1999).
+A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues (R.
+G.
+Cohen & Rosenbaum, 2004; Rosenbaum et al., 1995).
+Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
+Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
+A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
+</details>
+
+<details>
+<summary>relevant existing content 2 [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\
+</summary>
+
+> It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations (Nosofsky, 1992; Shepard, 1987).
+Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
+In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g., the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
+However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
+</details>
+
+## 6) How c might be learned
+
+<details open class="addition-callout">
+<summary> Addition in context (**new text bolded**) [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20results%20thus%20suggest){target="_blank"}</summary>
+
+> Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
+Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
+A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
+The $c$ parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
+In this fashion, contextually appropriate $c$ values could be empirically learned.
+This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for $c$.
+**@sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).
+In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalione   zation observed around the high variability category when participants were tested with an ambiguous intermediary item.
+In a subsequent work [@sakamotoPuttingPsychologyBack2008], the same authors showed that a similar learning mechanism could account for the pattern wherein participants generalize more broadly around a category when the average distance between the category exemplars is larger (however the only model tested in this work was a prototype model).**
+</details>
+
+<details class="relevant-callout">
+<summary> Relevant existing content [link 1](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=A%20learning%20system,values%20for%20c.){target="_blank"}</summary>
+>
+> As described above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning (Aha & Goldstone, 1992; Briscoe & Feldman, 2011; Hahn et al., 2005; Lamberts, 1994; Op de Beeck et al., 2008), and sensorimotor adaptation (Marongelli & Thoroughman, 2013; Taylor & Ivry, 2013; Thoroughman & Taylor, 2005).
+Lamberts (1994) showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
+The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability (Hahn et al., 2005; Sakamoto et al., 2006).
+However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
+Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains (Censor et al., 2012; Hills et al., 2010; Jamieson et al., 2022; Law & Gold, 2010; Roark et al., 2021; Rosenbaum et al., 2001; Vigo et al., 2018; Wall et al., 2021; Wu et al., 2020; J.
+Yang et al., 2020).
+</details>
+
+<details class="relevant-callout">
+<summary> Relevant existing content [link 2](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=However%2C%20previous%20research,the%20trained%20positions.){target="_blank"}</summary>
+> However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group (Hahn et al., 2005; Lamberts, 1994).
+Relatedly, the influential Bayesian generalization model developed by Tenenbaum & Griffiths (2001) predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
+Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
+Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
+To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the $c$ parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
+One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience (Nosofsky & Johansen, 2000; Sakamoto et al., 2006).
+If one’s training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
+Conversely, if one’s training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
+</details>
+
+## 7) Foreshadowing function learning literature
+
+<details open class="addition-callout">
+<summary>Addition [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Project%202%20will%20focus){target="_blank"}</summary>
+<div>
+Project 2 will focus on the domain of function learning and in particular the issue of extrapolation.
+Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
+The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
+Project 2 of this dissertation will address this gap by investigating how constant and varied training regimes affect learning, discrimination, and extrapolation in a novel visuomotor function learning task.
+We will leverage the ALM and EXAM models, fitted to individual participant data using advanced Bayesian techniques, to provide a detailed computational account of the observed empirical patterns.
+</div>
+</details>

### 2024-08-27 revisions.qmd
tweak callout format

@@
 
-<details>
+<details class="relevant-callout">
 <summary>relevant existing content 1 [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=Our%20modelling%20approach,of%20Knowledge%20II.){target="_blank"}</summary>
@@
 
-<details>
+<details class="relevant-callout">
 <summary>relevant existing content 2 [link](https://tegorman13.github.io/Dissertation/Manuscript/output/manuscript.html#:~:text=It%20is%20common,the%20task%20stimuli.){target="_blank"}\

### 2024-08-27 Manuscript/manuscript.qmd
re-render after a few minor revision text fixes

@@
 Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
-The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+The domain of function learning has yielded influential computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM)[@busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
 However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
@@
 This form of feedback resembles many real-world learning scenarios, such as a coach instructing an athlete to perform a movement using "more force" or "less force", or a teacher providing letter grades rather than numeric scores.
-Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
+Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback is not necessarily detrimental to learning.
 For example, @cornwallEffectsCategoricalNumerical2022 manipulated whether participants received categorical (correct or incorrect) vs.
@@
 They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
-Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
+While we do not make specific predictions about the ordinal condition, this manipulation allows us to explore how different types of feedback might interact with training variability to influence learning and generalization.
 
@@
 
-It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models employed in each project.
+It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models used in each project.
 The IGAS model of Project 1 serves as a descriptive measurement model, capturing the similarity between training throws and testing conditions.

### 2024-08-27 revisions.qmd
re-render after a few minor revision text fixes

@@
 title: Revisions
+author:
+- name: Thomas E. Gorman
+  url: https://tegorman13.github.io/
+page-layout: full
 toc: true
+format:
+  html: default
+  gfm: default
+  docx:
+    prefer-html: true
+    output-file: "tg_revisions.docx"
+    toc: false
 ---
@@
 <div>
-It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models employed in each project.
+It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models used in each project.
 The IGAS model of Project 1 serves as a descriptive measurement model, capturing the similarity between training throws and testing conditions.
@@
 They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
-Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
+While we do not make specific predictions about the ordinal condition, this manipulation allows us to explore how different types of feedback might interact with training variability to influence learning and generalization.
 </div>
@@
 **@sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).
-In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalione   zation observed around the high variability category when participants were tested with an ambiguous intermediary item.
+In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalization observed around the high variability category when participants were tested with an ambiguous intermediary item.
 In a subsequent work [@sakamotoPuttingPsychologyBack2008], the same authors showed that a similar learning mechanism could account for the pattern wherein participants generalize more broadly around a category when the average distance between the category exemplars is larger (however the only model tested in this work was a prototype model).**

### 2024-08-27 revisions.qmd
tweaks

@@
 toc: true
+suppress-bibliography: true
 format:

### 2024-08-31 Functions/fig_creation2.qmd
add design figure to intro

--- 2024-05-28 Presentation/_fig_creation.qmd
@@
 walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-
-```
-
-# HTW Results
-
-```{r}
-
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  data.table, stringr, here,conflicted, gt, ggh4x, patchwork, knitr)
-#options(brms.backend="cmdstanr",mc.cores=4)
-walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-
-walk(c("brms","dplyr","bayestestR","here"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","deLosh_data","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-
-e1 <- readRDS(here("data/e1_08-21-23.rds")) 
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-testE1 <- e1 |> filter(expMode2 == "Test")
-nbins=5
-trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
-trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-```
-
-## HTW E1
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap: Experiment 1 Testing Accuracy.
-A) Empricial Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (trained bands vs.
-novel extrapolation bands) on testing accuracy.
-Error bars represent 95% credible intervals.
-#| fig-width: 4
-#| fig-height: 4
-
-# pe1td <- testE1 |>  
-#   ggplot(aes(x = vb, y = dist,fill=condit)) +
-#     stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-#     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-#   theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-#   labs(x="Band", y="Deviation From Target Band")
-
-pe1td <- testE1 |> ggplot(aes(x = vb, y = dist,fill=condit,
-                               col=ifelse(bandType=="Trained","black","lightgray"),
-                               size=ifelse(bandType=="Trained",1.0,.5))) +
-  stat_bar + 
-  theme(legend.title.position="top",
-        legend.title = element_text(face = "bold"),
-        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation", fill="Condition") +
-     # scale_color_manual(values = c("black" = "black"), guide = "legend") +
-  scale_color_manual(values=c("black","lightgray"), 
-                     name= "Band Type",
-                     labels = c("Trained","Extrapolation"),
-                     guide = guide_legend(override.aes = list(fill = NA))
-                     ) +
-  scale_size_continuous(range = c(0.8, 1.0), guide="none")
-
-bmtd <- readRDS(paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2.rds"))
-pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Deviation", x="Band Type")
-
-#p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
-#p2
-
-e1_vxBMM <- readRDS(paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k.rds")))
-pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                     at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-gather_emmeans_draws() |> 
-condEffects(bandInt) +
-stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  geom_abline(slope = 1, intercept = 200, linetype = "dashed", color = "gray", size = .5,alpha=.5) +
-scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                   labels = levels(testE1$vb), 
-                   limits = c(100, 1200)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(400,1400,by=200),2)) +
-theme(legend.position="none") + 
-  #theme(legend.title=element_blank(),legend.position="right") + 
-labs(y="Velcoity", x="Band")
-
-fe <- fixef(e1_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e1Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-     theme(legend.title=element_blank(), 
-           axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-pe1td
-pe1ce
-
-pe1vce
-pid_den1
-pid_slopes1
-
-ggsave(here::here("Presentation/assets/htw_e1_test1.png"), pe1td, width = 4.0, height = 3, units = "in", dpi = 300)
-ggsave(here::here("Presentation/assets/htw_e1_test2.png"), pe1ce, width = 4.0, height = 3, units = "in", dpi = 300)
-ggsave(here::here("Presentation/assets/htw_e1_test3.png"), pe1vce, width = 4.0, height = 3, units = "in", dpi = 300)
-ggsave(here::here("Presentation/assets/htw_e1_test4.png"), pid_den1, width = 4.0, height = 3, units = "in", dpi = 300)
-ggsave(here::here("Presentation/assets/htw_e1_test5.png"), pid_slopes1, width = 4.0, height = 3, units = "in", dpi = 300)
-```
-
-## HTW Experiment 2
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap: Experiment 2 Testing Accuracy.
-A) Empricial Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (trained bands vs.
-novel extrapolation bands) on testing accuracy.
-Error bars represent 95% credible intervals.
-#| fig-width: 5
-#| fig-height: 5
-e2 <- readRDS(here("data/e2_08-04-23.rds")) 
-e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
-testE2 <- e2 |> filter(expMode2 == "Test")
-nbins=5
-trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
-
-bmtd2 <- readRDS(paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2.rds"))
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe2td <- testE2 |> ggplot(aes(x = vb, y = dist,fill=condit,
-                               col=ifelse(bandType=="Trained","black","lightgray"),
-                               size=ifelse(bandType=="Trained",1.0,.5))) +
-  stat_bar + 
-  theme(legend.title.position="top",
-        legend.title = element_text(face = "bold"),
-        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation", fill="Condition") +
-  scale_color_manual(values=c("black","lightgray"), 
-                     name= "Band Type",
-                     labels = c("Trained","Extrapolation"),
-                     guide = guide_legend(override.aes = list(fill = NA))
-                     ) +
-  scale_size_continuous(range = c(0.8, 1.0), guide="none")
-
-pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-e2_vxBMM <- readRDS(paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k.rds")))
-
-pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  geom_abline(slope = 1, intercept = 200, linetype = "dashed", color = "gray", size = .5,alpha=.5) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE2$vb), 
-                     limits = c(100, 1200)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(200,1400,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e2_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e2Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-      theme(legend.title=element_blank(), 
-        axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-pe2td
-pe2ce
-pe2vce
-pid_den2
-pid_slopes2
-
-ggsave(here::here("Presentation/assets/htw_e2_test1.png"), pe2td, width = 4.0, height = 3, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e2_test2.png"), pe2ce, width = 4.0, height = 3, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e2_test3.png"), pe2vce, width = 4.0, height = 3, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e2_test4.png"), pid_den2, width = 4.0, height = 3, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e2_test5.png"), pid_slopes2, width = 4.0, height = 3, units = "in", dpi = 600)
-
-```
-
-## HTW Exp 3
-
-```{r}
-#| fig-width: 4
-#| fig-height: 6
-e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
-    mutate(trainCon=case_when(
-    bandOrder=="Original" ~ "800",
-    bandOrder=="Reverse" ~ "600",
-    TRUE ~ NA_character_
-    ), trainCon=as.numeric(trainCon)) 
-e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
-testE3 <- e3 |> filter(expMode2 == "Test")
-nbins=5
-trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
-
-bmtd3 <- readRDS(paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2.rds"))
-
-pe3td <- testE3 |> ggplot(aes(x = vb, y = dist,fill=condit,
-                               col=ifelse(bandType=="Trained","black","lightgray"),
-                               size=ifelse(bandType=="Trained",1.0,.5))) +
-  stat_bar + 
-  facet_wrap(~bandOrder,ncol=1) +
-  theme(legend.title.position="top",
-        legend.title = element_text(face = "bold"),
-        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation", fill="Condition") +
-  scale_color_manual(values=c("black","lightgray"), 
-                     name= "Band Type",
-                     labels = c("Trained","Extrapolation"),
-                     guide = guide_legend(override.aes = list(fill = NA))
-                     ) +
-  scale_size_continuous(range = c(0.8, 1.0), guide="none")
-
-pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Deviation", x="Band Type") + 
- facet_wrap(~bandOrder,ncol=1)
-
-e3_vxBMM <- readRDS(paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k.rds")))
-
-pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  facet_wrap(~bandOrder,ncol=1) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  geom_abline(slope = 1, intercept = 200, linetype = "dashed", color = "gray", size = .5,alpha=.5) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(100, 1200)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(300,1400,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e3_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
-fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
-fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
-
-re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e3Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
-           fixed_effect_interaction2*(bandOrder=="Reverse") + 
-           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
-  slope = Estimate + adjust )
-
-pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density") +
-  facet_wrap(~bandOrder,ncol=1)
-
-pid_slopes3 <- re |>  
-    mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-    theme(legend.title=element_blank(), 
-      axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
-
-pe3td
-pe3ce
-pe3vce
-pid_den3
-pid_slopes3
-
-ggsave(here::here("Presentation/assets/htw_e3_test1.png"), pe3td, width = 4.0, height = 6, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e3_test2.png"), pe3ce, width = 4.0, height = 6, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e3_test3.png"), pe3vce, width = 4.0, height = 6, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e3_test4.png"), pid_den3, width = 4.0, height = 6, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/htw_e3_test5.png"), pid_slopes3, width = 4.0, height = 6, units = "in", dpi = 600)
 
@@
 
-## HTW Exp
+## HTW Exp Design
 
@@
 
-ggsave(here::here("Presentation/assets/htw_e1_manip.png"), htw_e1, width = 9.0, height = 6, units = "in", dpi = 300)
-ggsave(here::here("Presentation/assets/htw_e2_manip.png"), htw_e2, width = 9.0, height = 6, units = "in", dpi = 300)
+# ggsave(here::here("Presentation/assets/htw_e1_manip.png"), htw_e1, width = 9.0, height = 6, units = "in", dpi = 300)
+# ggsave(here::here("Presentation/assets/htw_e2_manip.png"), htw_e2, width = 9.0, height = 6, units = "in", dpi = 300)
 
@@
 igas_e1
-ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)
+# ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)
 
+kerr_booth_1978 <- create_plot(varied_train = c(2, 4), constant_train = c(3), both_test = c(3))
+kerr_booth_1978
+
+green_1995 <- create_plot(varied_train = c(1, 2, 3, 4), constant_train = c(1), both_test = c(1, 5, 6)) # 5 and 6 represent novel rackets
+green_1995
+
+catalano_kleiner_1984 <- create_plot(varied_train = c(5, 7, 9, 11), constant_train = c(5), both_test = c(1, 3, 13, 15))
+catalano_kleiner_1984
+
+goode_2008 <- create_plot(varied_train = c(1, 2, 3), constant_train = c(1), both_test = c(4, 5, 6))
+goode_2008
+
+varied_train <- c(5, 9)
+constant_train <- c(7)
+both_test <- c(1, 3, 5, 7, 9, 11)  # Assuming they tested at various distances
+willey_liu <- create_plot(varied_train, constant_train, both_test)
+willey_liu
+```
+
+```{r}
+library(ggplot2)
+library(dplyr)
+
+create_data <- function(varied_train, constant_train, both_test) {
+  varied_labels <- "Varied-Train"
+  constant_labels <- "Constant-Train"
+  test_labels <- "Testing"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.7, length(varied_train)), rep(1, length(constant_train)), rep(0.3, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.7, 1, 0.3),
+    yend = c(0.7, 1, 0.3)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test, title) {
+  data <- create_data(varied_train, constant_train, both_test)
+  segments <- create_segments(data)
+
+  # Variables for Training segment position
+  train_x <- min(data$x) - .5
+  train_y_start <- 0.65
+  train_y_end <- 1.05
+  train_text_y <- 1
+
+  # Variables for Testing segment position
+  test_x <- min(data$x) - .5
+  test_y_start <- 0.25
+  test_y_end <- 0.4
+  test_text_y <- 0.45
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold") +
+    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0, 1.5) +
+    ggtitle(title) +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+# Example usage
+
+# Kerr & Booth (1978) Study
+varied_train <- c(2, 4) # Specify varied training positions
+constant_train <- c(3) # Specify constant training position
+both_test <- c(3) # Specify test positions
+kerr_booth <- create_plot(varied_train, constant_train, both_test, "Kerr & Booth (1978) Study")
+
+# Goode et al. (2008) Study
+varied_train <- c(1, 2, 3) # Specify varied training positions
+constant_train <- c(3) # Specify constant training position
+both_test <- c(1, 2, 3, 4, 5, 6) # Specify test positions
+goode_et_al <- create_plot(varied_train, constant_train, both_test, "Goode et al. (2008) Study")
+
+# Catalano & Kleiner (1984) Study
+varied_train <- c(5, 7, 9, 11) # Specify varied training positions
+constant_train <- c(5, 7, 9, 11) # Specify constant training positions
+both_test <- c(1, 3, 13, 15) # Specify test positions
+catalano_kleiner <- create_plot(varied_train, constant_train, both_test, "Catalano & Kleiner (1984) Study")
+
+# Display plots
+kerr_booth
+goode_et_al
+catalano_kleiner
 ```
@@
 igas_e1
-ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)
+# ggsave(here::here("Presentation/assets/igas_e1_manip.png"), igas_e1, width = 9.0, height = 6, units = "in", dpi = 300)
 
@@
 
-ggsave(here::here("Presentation/assets/igas_e2_manip.png"), igas_e2, width = 9, height = 6, units = "in", dpi = 300)
+# ggsave(here::here("Presentation/assets/igas_e2_manip.png"), igas_e2, width = 9, height = 6, units = "in", dpi = 300)
 
 ```
-
-# Sim Example
-
-```{r}
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,here)
-walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-
-# Function to simulate exponential learning data
-sim_exp <- function(N, alpha, beta, r, t0 = 0, sdlog = .1) {
-  t0 + (alpha + (beta-alpha) * exp(-r * N)) + rlnorm(length(N), 0, sdlog)
-}
-
-# Parameters for simulation
-N <- 1:50  # Number of trials
-alpha <- 5  # Initial performance level
-beta <- 15  # improvement
-
-# Parameters for two groups
-r_fast <- 0.1  # Faster learning rate
-r_slow <- 0.05  # Slower learning rate
-
-# Simulate data for two groups
-set.seed(123)  # For reproducibility
-data_fast <- sim_exp(N, alpha-3, beta, r_fast)
-data_slow <- sim_exp(N, alpha, beta, r_slow)
-
-# Combine data into a single dataframe
-data <- data.frame(
-  Trial = rep(N, 2),
-  Performance = c(data_fast, data_slow),
-  Group = factor(rep(c("Low Variability", "High Variability"), each = length(N)), levels=c("Low Variability", "High Variability"))
-)
-
-# Plot the data using ggplot2
-tr_p <- ggplot(data, aes(x = Trial, y = Performance, color = Group)) +
-  geom_line(size = 1) +
-  geom_point(size = 2) +
-  labs(
-    title = "Learning Curves for Low and High Variability Training",
-    x = "Training Trial",
-    y = "Error",
-    color = "Group"
-  ) + ylim(0,20) +  theme(
-    #panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank()
-  )
-
-# ggsave(here::here("Presentation/assets/train_pattern.png"), tr_p)
-```
-
-```{r}
-
-# Simulate testing data for two groups
-set.seed(123)  # For reproducibility
-test_data_fast <- rnorm(length(N), mean = 5, sd = 1)
-test_data_slow <- rnorm(length(N), mean = 2.5, sd = 1)
-
-# Combine testing data into a single dataframe
-test_data <- data.frame(
-  Trial = rep(N, 2),
-  Performance = c(test_data_fast, test_data_slow),
-  Group = factor(rep(c("Low Variability", "High Variability"), each = length(N)), levels=c("Low Variability", "High Variability"))
-)
-
-# Plot the testing data using ggplot2
-test_p <- ggplot(test_data, aes(x = Group, y = Performance, fill = Group)) +
-  stat_summary(fun = mean, geom = "bar", position = "dodge", width = 0.7) +
-  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(0.7), width = 0.25) +
-  labs(
-    title = "Testing Performance for Low and High Variability Training",
-    x = "Group",
-    y = "Error",
-    fill = "Group"
-  ) + ylim(0, 10) + theme(
-    panel.grid.minor = element_blank()
-  )
-
-# ggsave(here::here("Presentation/assets/test_pattern.png"), test_p)
-```
-
-# IGAS Task Space
-
-```{r}
-#| label: fig-taskSpace
-#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in experiment 2.
-B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig-width: 11
-#| fig-height: 9
-
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,here, RColorBrewer, patchwork)
-walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11, abs(X_Velocity)<1000)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss= solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1")) +
-  labs(color="Throw position:", 
-  # title="Empirical Solution Space - Testing Positions",
-  # subtitle="The XY velocity coordinates of all the successful throws", 
-  x="X Release Velocity", 
-  y="Y Release Velocity", )  
-  theme(legend.position="top")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(color=element_blank(),
-  # title="Full Space of Solution Throws and Missed Throws",
-  # subtitle="Colored points represent coordinates of target hits, brown points are coordinates of misses",
-  x="X Release Velocity", 
-  y="Y Release Velocity") + 
-  theme(legend.title = element_blank(), legend.position="top")
-
-ggsave(here::here("Presentation/assets/sol_space2.png"),ss, width = 5, height = 4, units = "in", dpi = 600)
-ggsave(here::here("Presentation/assets/full_space2.png"),fs, width = 5, height = 3, units = "in", dpi = 600)
-
-```
-
-## IGAS Results
-
-```{r}
-pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork,here)
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-theme_set(theme_classic())
-# load the processed data from experiment 1 and 2
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-options(contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
-
-walk(c("Display_Functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-
-nbins=5
-
-htt_e1_train <-  e1 %>% filter(stage!="Transfer",mode==1) |> group_by(sbjCode,Group,positionX,conditType) |> 
-    mutate(Trial_Bin = cut(trial, breaks = seq(1, max(trial),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) |>
-ggplot(aes(x = Trial_Bin, y = AbsDistFromCenter, color = conditType)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~positionX)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block",col="Throw Position")
-
-htt_e2_train <- e2 %>% filter(stage!="Transfer",mode==1) |> group_by(sbjCode,Group,positionX,conditType) |> 
-    mutate(Trial_Bin = cut(trial, breaks = seq(1, max(trial),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) |> ggplot(aes(x = Trial_Bin, y = AbsDistFromCenter, color = conditType)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~positionX)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Deviation", x="Training Block",col="Throw Position")
-
-ggsave(here::here("Presentation/assets/htt_e1_train.png"),htt_e1_train,width = 5, height = 2, units = "in", dpi = 300)
-ggsave(here::here("Presentation/assets/htt_e2_train.png"),htt_e2_train,width = 5, height = 4, units = "in", dpi = 300)
-
-```
-
-```{r}
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(legend.title.align=.25, 
-  axis.text.x = element_text(size = 8.5,angle=0),
-  legend.position="top")+
-  scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-
-exp2.Test <- filter(e2, stage=="Transfer") %>% group_by(sbjCode,conditType,positionX,ThrowPosition,condit2) %>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-e2test1<- exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)
-
-ggsave(here::here("Presentation/assets/htt_e2_test.png"),e2test1,width = 5, height = 4, units = "in", dpi = 300)
-
-exp2.Test %>% ggplot(aes(x=condit2,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition")) +
-  facet_wrap(~positionX) + 
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25) + guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)
-
-```

### 2024-08-31 Sections/Introduction.qmd
add design figure to intro

@@
 title: Introduction
+author:
+- name: Thomas E. Gorman
+  affiliations: 
+  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
+    affiliation-url: https://psych.indiana.edu/
+  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
+    affiliation-url: https://cogs.indiana.edu/index.html
+  url: https://tegorman13.github.io/
+floatsintext: true
+suppress-author-note: true
 format:
-  html: default
+  apaquarto-html: default
   hugo-md:
@@
   gfm:
-    echo: true
+    echo: false
     output-file: d_into_gfm.md
+  apaquarto-pdf: default
   # hikmah-manuscript-pdf:
@@
 
+```{r}
+#| label: fig-ex-design1
+#| fig-width: 10
+#| fig-height: 6
+#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design.
+The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet).
+Both groups were tested from a distance of 3 feet.
+The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
+pacman::p_load(dplyr, ggplot2, patchwork)
+
+create_data <- function(varied_train, constant_train, both_test) {
+  varied_labels <- "Varied-Train"
+  constant_labels <- "Constant-Train"
+  test_labels <- "Testing"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.55, length(varied_train)), rep(0.75, length(constant_train)), rep(0.4, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.55, 0.75, 0.4),
+    yend = c(0.55, 0.75, 0.4)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test) {
+  data <- create_data(varied_train, constant_train, both_test)
+  segments <- create_segments(data)
+
+  # Variables for Training segment position
+  train_x <- min(data$x) - .5
+  train_y_start <- 0.5
+  train_y_end <- 0.8
+  train_text_y <- 0.75
+
+  # Variables for Testing segment position
+  test_x <- min(data$x) - .5
+  test_y_start <- 0.35
+  test_y_end <- 0.45
+  test_text_y <- 0.48
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4.5, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
+    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
+    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0.3, 1) +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+kerr_booth_1978 <- create_plot(varied_train = c(2, 4), constant_train = c(3), both_test = c(3))
+kerr_booth_1978
+```
+
 Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this particular contrast is relatively uncommon in the literature.
+However, despite its appeal this contrast is relatively uncommon in the literature.
 It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
+A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979; @mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
 A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
@@
 In contrast, the effects of variability have received more formal computational treatment in other domains, such as category learning [@hahnEffectsCategoryDiversity2005 @huHighvariabilityTrainingDoes2024], language learning [@jonesDensityDistinctivenessEarly2020], and function learning [@deloshExtrapolationSineQua1997].
-A primary goal of the  current dissertation is to to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
+A primary goal of the current dissertation is to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
 
@@
 
-Project 2 shifted focus to the domain of function learning by employing a visuomotor extrapolation task.
-Across three experiments, we examined how constant and varied training regimes affected learning, discrimination between stimuli, and the ability to extrapolate to novel regions of the function's input space.
-To model human performance in this task, we fit the influential Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) to individual participant data using advanced Bayesian parameter estimation techniques.
-
-{{< pagebreak >}}
+Project 2 will focus on the domain of function learning and in particular the issue of extrapolation.
+Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
+The domain of function learning has yielded influential computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM)[@busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
+However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
+Project 2 of this dissertation will address this gap by investigating how constant and varied training regimes affect learning, discrimination, and extrapolation in a novel visuomotor function learning task.
+We will leverage the ALM and EXAM models, fitted to individual participant data using advanced Bayesian techniques, to provide a detailed computational account of the observed empirical patterns.

### 2024-09-07 Manuscript/manuscript_full.qmd
formatting tweaks

--- 2024-08-27 Manuscript/manuscript.qmd
@@
 toc-location: body
-cache: true
+#cache: true
+output-dir: output
 execute: 
@@
   echo: false
+format:
+#   docx:
+#     prefer-html: true
+#     output-file: "TG_Full_Dissertation2.docx"
+#     toc: true
+#   html:
+#     toc: true
+#     language: 
+#       title-block-published: "Latest version"
+#     shift-heading-level-by: 0
+#     toc-depth: 4
+#     link-citations: true
+#     page-layout: full
+#     format-links: [pdf, gfm, docx]
+#     theme: 
+#        #- ../Assets/Style/lux-modified.scss 
+#        - cosmo
+#        - custom.scss
+#        - ../Assets/Style/style.scss
+#     css: ../Assets/Style/calloutTG.css
+#     citeproc: false
+#     filters: 
+#       - "_extensions/wordcount/citeproc.lua"
+#       - "_extensions/wordcount/wordcount.lua"
+#     lightbox: auto
+#     knitr:
+#       opts_chunk:
+#         dev: "ragg_png"
+#         dpi: 300
+  pdf:
+    cite-method: citeproc
+    #date: today
+    output-file: "TG_Full_Dissertation2.pdf"
+    mathfont: "Libertinus Math"
+    documentclass: article
+    papersize: letter
+    fontsize: 11pt
+    linestretch: 1.5
+          # Document styling
+    geometry:
+      - top=1in     
+      - bottom=1in  
+      - left=1in    
+      - right=1in  
+      - heightrounded
+
+      # Citations and links
+    # lot: true
+    # lof: true
+    colorlinks: true
+    linkcolor: DarkSlateBlue
+    urlcolor: DarkSlateBlue
+    citecolor: DarkSlateBlue
+    link-citations: true
+    # linestretch: 1.05
+    include-in-header:
+      # The \everydisplay thing makes all math blocks use \small font
+      text: |
+        \usepackage{mathtools}
+        \everydisplay\expandafter{\the\everydisplay\small}
+        \usepackage{float}
+        \floatplacement{figure}{H}
+        \floatplacement{table}{H}
+        \usepackage{setspace}
+        \pagenumbering{arabic}
+        \usepackage{titlesec}
+        \titleformat{\section}{\fontsize{12}{14}\bfseries}{\thesection}{1em}{}
+        \titleformat{\subsection}{\fontsize{11}{14}\bfseries}{\thesubsection}{1em}{}
 ---
@@
 
-{{< include pre_sections/pre_pdf.qmd >}}
+{{< include pre_sections/pre_pdf_full.qmd >}}
 
@@
 
-Research on the effects of varied training typically manipulates variability in one of two ways.
-In the first approach, a high variability group is exposed to a greater number of unique instances during training, while a low variability group receives fewer unique instances with more repetitions.
-Alternatively, both groups may receive the same number of unique instances, but the high variability group's instances are more widely distributed or spread out in the relevant psychological space, while the low variability group's instances are clustered more tightly together.
-Researchers then compare the training groups in terms of their performance during the training phase, as well as their generalization performance during a testing phase.
-Researchers usually compare the performance of the two groups during both the training phase and a subsequent testing phase.
-The primary theoretical interest is often to assess the influence of training variability on generalization to novel testing items or conditions.
-However, the test may also include some or all of the items that were used during the training stage, allowing for an assessment of whether the variability manipulation influenced the learning of the trained items themselves, or to easily measure how much performance degrades as a function of how far away testing items are from the training items.
-
-The influence of training variability has received a large amount of attention in the domain of sensorimotor skill learning.
-Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced.
-Schema theory presumes that learners possess general motor programs for a class of movements (e.g., an underhand throw).
-When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task.
-Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer.
-Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group.
-Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group.
-For example, studies using a projectile throwing task might assign participants to either constant training that practice throwing from a single location, or to a varied group that throws from multiple locations.
-Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].
-
-One of the earliest and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978.
-Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
-The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
-Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
-12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants.
-Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage.
-In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children.
-This result provides particularly strong evidence for the benefits of varied practice, as the varied group outperformed the constant group even when tested at the "home-turf" distance that the constant group had exclusively practiced.
-A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a].
-One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group.
-Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths.
-However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperforms the constant group even from the constants group's home turf has not been consistently replicated.
-One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet).
-This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups.
-However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
-
-Pitting varied against constant practice against each other on the home turf of the constant group provides a compelling argument for the benefits of varied training, as well as an interesting challenge for theoretical accounts that posit generalization to occur as some function of distance.
-However, despite its appeal this contrast is relatively uncommon in the literature.
-It is unclear whether this may be cause for concern over publication bias, or just researchers feeling the design is too risky.
-A far more common design is to have separate constant groups that each train exclusively from each of the conditions that the varied group encounters [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019;
-@newellVariabilityPracticeTransfer1976; @moxleySchemaVariabilityPractice1979;
-@mccrackenTestSchemaTheory1977], or for a single constant group to train from just one of the conditions experienced by the varied participants [@pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @wrisbergTrainingProductionNovel1984; @wrisbergDevelopingCoincidentTiming1983].
-A less common contrast places the constant group training in a region of the task space outside of the range of examples experienced by the varied group, but distinct from the transfer condition [@wrisbergVariabilityPracticeHypothesis1987; @wulfVariabilityPracticeImplicit1997].
-Of particular relevance to the current work is the early study of @catalanoDistantTransferCoincident1984a, as theirs was one of the earliest studies to investigate the influence of varied vs.
-constant training on multiple testing locations of graded distance from the training condition.
-Participants were trained on coincident timing task, in which subjects observe a series of lightbulbs turning on sequentially at a consistent rate and attempt to time a button response with the onset of the final bulb.
-The constant groups trained with a single velocity of either 5,7,9, or 11 mph, while the varied group trained from all 4 of these velocities.
-Participants were then assigned to one of four possible generalization conditions, all of which fell outside of the range of the varied training conditions -- 1, 3, 13 or 15 mph.
-As is often the case, the varied group performed worse during the training phase.
-In the testing phase, the general pattern was for all participants to perform worse as the testing conditions became further away from the training conditions, but since the drop off in performance as a function of distance was far less steep for the varied group, the authors suggested that varied training induced a decremented generalization gradient, such that the varied participants were less affected by the change between training and testing conditions.
-
-Benefits of varied training have also been observed in many studies outside of the sensorimotor domain.
-@goodeSuperiorityVariableRepeated2008 trained participants to solve anagrams of 40 different words ranging in length from 5 to 11 letters, with an anagram of each word repeated 3 times throughout training, for a total of 120 training trials.
-Although subjects in all conditions were exposed to the same 40 unique words (i.e.
-the solution to an anagram), participants in the varied group saw 3 different arrangements for each solution-word, such as DOLOF, FOLOD, and OOFLD for the solution word FLOOD, whereas constant subjects would train on three repetitions of LDOOF (spread evenly across training).
-Two different constant groups were used.
-Both constant groups trained with three repetitions of the same word scramble, but for constant group A, the testing phase consisted of the identical letter arrangement to that seen during training (e.g., LDOOF), whereas for constant group B, the testing phase consisted of an arrangement they had not seen during training, thus presenting them with a testing situation similar situation to the varied group.
-At the testing stage, the varied group outperformed both constant groups, a particularly impressive result, given that constant group A had three prior exposures to the word arrangement (i.e.
-the particular permutation of letters) which the varied group had not explicitly seen.
-However varied subjects in this study did not exhibit the typical decrement in the training phase typical of other varied manipulations in the literature, and achieved higher levels of anagram solving accuracy by the end of training than either of the constant groups -- solving two more anagrams on average than the constant group.
-This might suggest that for tasks of this nature where the learner can simply get stuck with a particular word scramble, repeated exposure to the identical scramble might be less helpful towards finding the solution than being given a different arrangement of the same letters.
-This contention is supported by the fact that constant group A, who was tested on the identical arrangement as they experienced during training, performed no better at testing than did constant group B, who had trained on a different arrangement of the same word solution -- further suggesting that there may not have been a strong identity advantage in this task.
-
-In the domain of category learning, the constant vs. varied comparison is much less suitable. Instead, researchers will 
-typically employ designs where all training groups encounter numerous stimuli, but one group experiences a greater number of unique exemplars [@wahlheimMetacognitiveJudgmentsRepetition2012; @nosofskyModelguidedSearchOptimal2019; @doyleMetacognitiveMonitoringCategory2016; @hoschPriorExperienceVariability2023; @brunsteinPreparingNoveltyDiverse2011], or designs where the number of unique training exemplars is held constant, but one group trains with items that are more dispersed, or spread out across the category space [@posnerGenesisAbstractIdeas1968;  @homaCategoryBreadthAbstraction1976; @huHighvariabilityTrainingDoes2024; @bowmanTrainingSetCoherence2020; @maddoxStimulusRangeDiscontinuity2011].
-
-Much of the earlier work in this sub-area trained subjects on artificial categories, such as dot patterns [@homaCategoryBreadthAbstraction1976; @posnerGenesisAbstractIdeas1968].
-A seminal study by @posnerGenesisAbstractIdeas1968 trained participants to categorize artificial dot patterns, manipulating whether learners were trained with low variability examples clustered close to the category prototypes (i.e. low distortion training patterns), or higher-variability patterns spread further away from the prototype (i.e.
-high-distortion patterns).
-Participants that received training on more highly-distorted items showed superior generalization to novel high distortion patterns in the subsequent testing phase.
-It should be noted that unlike the sensorimotor studies discussed earlier, the @posnerGenesisAbstractIdeas1968 study did not present low-varied and high-varied participants with an equal number of training trials, but instead had participants remain in the training stage of the experiment until they reached a criterion level of performance.
-This train-until-criterion procedure led to the high-variability condition participants tending to complete a larger number of training trials before switching to the testing stage.
-More recent work [@huHighvariabilityTrainingDoes2024] also used dot pattern categories, but matched the number of training trials across conditions.
-Under this procedure, higher-variability participants tended to reach lower levels of performance by the end of the training stage.
-The results in the testing phase were the opposite of @posnerGenesisAbstractIdeas1968,  with the low-variability training group showing superior generalization to novel high-distortion patterns (as well as generalization to novel patterns of low or medium distortion levels).
-However, whether this discrepancy is solely a result of the different training procedures is unclear, as the studies also differed in the nature of the prototype patterns used.
-@posnerGenesisAbstractIdeas1968  utilized simpler, recognizable prototypes (e.g., a triangle, the letter M, the letter F), while  @huHighvariabilityTrainingDoes2024 employed random prototype patterns.
-
-Recent studies have also begun utilizing more complex or realistic stimuli when assessing the influence of variability on category learning.
-@wahlheimMetacognitiveJudgmentsRepetition2012 conducted one such study.
-In a within-participants design, participants were trained on bird categories with either many repetitions of a few exemplars, or with few repetitions of many exemplars.
-Across four different experiments, which were conducted to address an unrelated question on metacognitive judgements, the researchers consistently found that participants generalized better to novel species following training with more unique exemplars (i.e.
-higher variability), while high repetition training produced significantly better performance categorizing the specific species they had trained on.
-A variability advantage was also found in the relatively complex domain of rock categorization [@nosofskyModelguidedSearchOptimal2019].
-For 10 different rock categories, participants were trained with either many repetitions of 3 unique examples of each category, or few repetitions of 9 unique examples, with an equal number of total training trials in each group (the design also included 2 other conditions less amenable to considering the impact of variation).
-The high-variability group, trained with 9 unique examples, showed significantly better generalization performance than the other conditions.
-
-A distinct sub-literature within the category learning domain has examined how the variability or dispersion of the categories themselves influences generalization to ambiguous regions of the category space (e.g., the region between the two categories).
-The general approach is to train participants with examples from a high variability category and a low variability category.
-Participants are then tested with novel items located within ambiguous regions of the category space which allow the experimenters to assess whether the difference in category variability influenced how far participants generalize the category boundaries.
-@cohenCategoryVariabilityExemplar2001 conducted two experiments with this basic paradigm.
-In experiment 1, a low variability category composed of 1 instance was compared against a high-variability category of 2 instances in one condition, and 7 instances in another.
-In experiment 2 both categories were composed of 3 instances, but for the low-variability group the instances were clustered close to each other, whereas the high-variability groups instances were spread much further apart.
-Participants were tested on an ambiguous novel instance that was located in between the two trained categories.
-Both experiments provided evidence that participants were much more likely to categorize the novel middle stimulus into the category with greater variation.
-
-Further observations of widened generalization following varied training have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
-@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; @hoschPriorExperienceVariability2023; but see @stewartEffectCategoryVariability2002;  @yangCategoryVariabilityEffect2014; and @seitzModelingCategoryVariability2023].
-The results of @sakamotoPuttingPsychologyBack2008 are noteworthy.
-They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability.
-In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial.
-They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
-
-The work of @hahnEffectsCategoryDiversity2005, is also of particular interest to the present work.
-Their experimental design was similar to previous studies, but they included a larger set of testing items which were used to assess generalization both between the two training categories as well as novel items located in the outer edges of the training categories.
-During generalization testing, participants were given the option to respond with "neither", in addition to responses to the two training categories.
-The "neither" response was included to test how far away in the stimulus space participants would continue to categorize novel items as belonging to a trained category.
-Consistent with prior findings, high-variability training resulted in an increased probability of categorizing items in between the training categories as belong to the high variability category.
-Additionally, participants trained with higher variability also extended the category boundary further out into the periphery than participants trained with a lower variability category were willing to do.
-The author compared a variety of similarity-based models based around the Generalized Context Model [@nosofskyAttentionSimilarityIdentificationcategorization1986] to account for their results, manipulating whether a response-bias or similarity-scaling parameter was fit separately between variability conditions.
-No improvement in model fit was found by allowing the response-bias parameter to differ between groups, however the model performance did improve significantly when the similarity scaling parameter was fit separately.
-The best fitting similarity-scaling parameters were such that the high-variability group was less sensitive to the distances between stimuli, resulting in greater similarity values between their training items and testing items.
-This model accounted for both the extended generalization gradients of the varied participants, and for their poorer performance in a recognition condition.
-
-Variability has also been examined in the learning of higher-order linguistic categories [@perryLearnLocallyThink2010].
-In nine training sessions spread out over nine weeks infants were trained on object labels in a naturalistic play setting.
-All infants were introduced to three novel objects of the same category, with participants in the "tight" condition being exposed to three similar exemplars of the category, and participants in the varied condition being exposed to three dissimilar objects of the same category.
-Importantly, the similarity of the objects was carefully controlled for by having a separate group of adult subjects provide pairwise similarity judgements of the category objects prior to the study onset.
-Multidimensional scaling was then performed to obtain the coordinates of the objects psychological space, and out of the 10 objects for each category, the 3 most similar objects were selected for the tight group and the three least similar objects for the varied group, with the leftover four objects being retained for testing.
-By the end of the nine weeks, all of the infants had learned the labels of the training objects.
-In the testing phase, the varied group demonstrated superior ability to correctly generalize the object labels to untrained exemplars of the same category.
-More interesting was the superior performance of the varied group on a higher order generalization task -- such that they were able to appropriately generalize the bias they had learned during training for attending to the shape of objects to novel solid objects, but not to non-solids.
-The tight training group, on the other hand, tended to overgeneralize the shape bias, leading the researchers to suggest that the varied training induced a more context-sensitive understanding of when to apply their knowledge.
-
-Of course, the relationship between training variability and transfer is unlikely to be a simple function wherein increased variation is always beneficial.
-Numerous studies have found null, or in some cases negative effects of training variation [@deloshExtrapolationSineQua1997; @sinkeviciuteRoleInputVariability2019; @wrisbergVariabilityPracticeHypothesis1987; @vanrossumSchmidtSchemaTheory1990], and many more have suggested that the benefits of variability may depend on additional factors such as prior task experience, the order of training trials, or the type of transfer being measured [@bernikerEffectsTrainingBreadth2014; @braithwaiteEffectsVariationPrior2015; @hahnEffectsCategoryDiversity2005; @lavanEffectsHighVariability2019; @northEffectConsistentVaried2019; @sadakataIndividualAptitudeMandarin2014; @zamanPerceptualVariabilityImplications2021].
-
-In an example of a more complex influence of training variation, [@braithwaiteEffectsVariationPrior2015] trained participants on example problems involving the concept of sampling with replacement (SWR).
-Training consisted of examples that were either highly similar in their semantic context (e.g., all involving people selecting objects) or in which the surface features were varied between examples (e.g., people choosing objects AND objects selected in a sequence).
-The experimenters also surveyed how much prior knowledge each participant had with SWR.
-They found that whether variation was beneficial depended on the prior knowledge of the participants -- such that participants with some prior knowledge benefited from varied training, whereas participants with minimal prior knowledge performed better after training with similar examples.
-The authors hypothesized that to benefit from varied examples, participants must be able to detect the structure common to the diverse examples, and that participants with prior knowledge are more likely to be sensitive to such structure, and thus to benefit from varied training.
-To test this hypothesis more directly, the authors conducted a 2nd experiment, wherein they controlled prior knowledge by exposing some subjects to a short graphical or verbal pre-training lesson, designed to increase sensitivity to the training examples.
-Consistent with their hypothesis, participants exposed to the structural sensitivity pre-training benefited more from varied training than the controls participants who benefited more from training with similar examples.
-Interactions between prior experience and the influence of varied training have also been observed in sensorimotor learning [@guadagnoliRelationshipContextualInterference1999;  @delreyEffectsContextualInterference1982].
-@delreyEffectsContextualInterference1982 recruited participants who self-reported either extensive, or very little experience with athletic activities, and then trained participants on a coincident timing task with either a single constant training velocity, or with one of several varied training procedures.
-Unsurprisingly, athlete participants had superior performance during training, regardless of  condition, and training performance was superior for all subjects in the constant group.
-Of greater interest is the pattern of testing results from novel transfer conditions.
-Among the athlete-participants, transfer performance was best for those who received variable training.
-Non-athletes showed the opposite pattern, with superior performance for those who had constant training.
-
-## Existing Theoretical Frameworks
-
-Several theoretical frameworks have been proposed to conceptually explain the effects of varied training on learning and generalization.
-Schema theory (described in more detail above), posts that varied practice leads to the formation of more flexible motor schemas, which then facilitate generalization [@schmidtSchemaTheoryDiscrete1975].
-The desirable difficulties framework [@bjorkMakingThingsHard2011; @soderstromLearningPerformanceIntegrative2015] proposes that variable practice conditions may impair initial performance but then enhance longer-term retention and transfer.
-Similarly, the challenge point framework [@guadagnoliChallengePointFramework2004] contends that training variation induces optimal learning occurs insofar as it causes the difficulty of practice tasks to be appropriately matched to the learner's capabilities, but may also be detrimental if the amount of variation causes the task to be too difficult.
-
-While these frameworks offer valuable conceptual accounts, there has been a limited application of computational modeling efforts aimed at quantitatively assessing and comparing the learning and generalization mechanisms which may be underlying the influence of variability in visuomotor skill learning.
-In contrast, the effects of variability have received more formal computational treatment in other domains, such as category learning [@hahnEffectsCategoryDiversity2005 @huHighvariabilityTrainingDoes2024],  language learning [@jonesDensityDistinctivenessEarly2020], and function learning [@deloshExtrapolationSineQua1997].
-A primary goal of the  current dissertation is to address this gap by adapting and applying modeling approaches from these other domains to investigate the effects of training variability in visuomotor skill learning and function learning tasks.
-
-## The current work
-
-The overarching purpose of this dissertation is to investigate the effects of training variability on learning and generalization within visuomotor skill learning and function learning.
-Our investigation is structured into two main projects,  each employing distinct experimental paradigms and computational modeling frameworks to elucidate how and when variability in training enhances or impedes subsequent generalization.
-
-In Project 1, we investigated the influence of varied practice in a simple visuomotor projectile launching task.
-Experiments 1 and 2 compared the performance of constant and varied training groups to assess potential benefits of variability on transfer to novel testing conditions.
-To account for the observed empirical effects, we introduced the Instance-based Generalization with Adaptive Similarity (IGAS) model.
-IGAS provides a novel computational approach for quantifying the similarity between training experiences and transfer conditions, while also allowing for variability to influence the generalization gradient itself.
-
-Project 2 will focus on the domain of function learning and in particular the issue of extrapolation.
-Function learning research examines how people acquire and generalize knowledge about continuous input-output relationships, and the factors influencing extrapolation to novel inputs following an initial learning phase.
-The domain of function learning has yielded influential computational models like the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM) [ @busemeyerLearningFunctionalRelations1997], which have successfully accounted for human learning, interpolation, and extrapolation in numerous investigations[@deloshExtrapolationSineQua1997; @mcdanielConceptualBasisFunction2005; @mcdanielPredictingTransferPerformance2009].
-However, the influence of training variability on function learning, particularly in visuomotor function learning tasks, remains relatively unexplored.
-Project 2 of this dissertation will address this gap by investigating how constant and varied training regimes affect learning, discrimination, and extrapolation in a novel visuomotor function learning task.
-We will leverage the ALM and EXAM models, fitted to individual participant data using advanced Bayesian techniques, to provide a detailed computational account of the observed empirical patterns.
-
 {{< pagebreak >}}
-
-# Project 1
-
-```{r}
-#| cache: false
-
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
-  ggh4x,htmltools,future,furrr,ez)
-#options(brms.backend="cmdstanr",mc.cores=4)
-#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
-walk(c("brms","dplyr","bayestestR","here","rstanarm"), conflict_prefer_all, quiet = TRUE)
-walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-#conflicts_prefer(tidybayes::rstudent_t)
-
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-#pacman::p_load(papaja, tinytex, RColorBrewer, kableExtra, cowplot)
-source(here::here('Functions/IGAS_ProcessFunctions.R'))
-
-#options(brms.backend="cmdstanr",mc.cores=4)
-initial_contrasts <- options("contrasts")$contrasts
-options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, contrasts = c("contr.sum", "contr.poly"))
-defaultContrasts = options()$contrasts
-
-library(tidybayes)
-
-theme_set(theme_classic())
-# load the processed data from experiment 1 and 2
-e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
-e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
-# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
-e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))
-
-# options(contrasts = c("contr.sum", "contr.poly"), kableExtra.auto_format=FALSE)
-# defaultContrasts = options()$contrasts
-# theme_set(theme_classic())
-
-dodge <- position_dodge(width = 0.9)
-e2GrpPos <- c("400","500","625","675","800","900")
-e2Grp <- paste("Constant","Constant", "Constant","Constant","Constant","Constant", "Varied")
-e2Labels <- paste(c("400\n Constant","500\n Constant","625\n Constant","675\n Constant",
-                   "800\n Constant","900\n Constant","500-800\n Varied"),sep="")
-
-e1Pos <- c("610","760","835","910")
-e1Var <- paste("Varied Train Position","Constant Train Position", "Novel Position", "Varied Training Position")
-e1Labels<- paste(c("610\n Varied Trained","760\n Constant Trained","835\n Novel Location","910\n Varied Trained"),sep="")
-```
-
-## Abstract
-
-Exposing learners to variability during training has been demonstrated to improve performance in subsequent transfer testing.
-Such variability benefits are often accounted for by assuming that learners are developing some general task schema or structure.
-However, much of this research has neglected to account for differences in similarity between varied and constant training conditions.
-In a between-groups manipulation, we trained participants on a simple projectile launching task, with either varied or constant conditions.
-We replicate previous findings showing a transfer advantage of varied over constant training.
-Furthermore, we show that a standard similarity model is insufficient to account for the benefits of variation, but, if the model is adjusted to assume that varied learners are tuned towards a broader generalization gradient, then a similarity-based model is sufficient to explain the observed benefits of variation.
-Our results therefore suggest that some variability benefits can be accommodated within instance-based models without positing the learning of some schemata or structure.
-
-## Introduction
-
-### Similarity and instance-based approaches to transfer of learning
-
-Early models of learning often assumed that discrete experiences with some task or category were not stored individually in memory, but instead promoted the formation of a summary representation, often referred to as a prototype or schema, and that exposure to novel examples would then prompt the retrieval of whichever preexisting prototype was most similar.
-In addition to being a landmark study on the influence of training variability, @posnerGenesisAbstractIdeas1968 (described above) also put forward an influential argument concerning the nature of the mental representations acquired during learning - namely that learners tend to abstract a prototype, or aggregate representation of the dot pattern categories, rather than encoding each individual stimulus.
-Recall that participants are trained on only on distortions of the category prototypes (e.g.,  low, medium or high distortions), never encountering the exact prototypes during the training stage.
-Then, in the testing phase, participants are tested with the prototype patterns, their old training items, and novel low, medium and high distortions.
-The authors found that participants had the highest testing accuracy for the previously unseen prototype patterns, followed by the old training items, and then the novel low, medium and high distortions.
-The authors interpreted this pattern as evidence that participants had acquired prototype representation of the category, as opposed to storing each individual training instance, and that generalization was based on the similarity of the testing items to the learned prototype representations.
-@posnerGenesisAbstractIdeas1968 has been extremely influential, and continues to be cited as evidence that prototype abstraction underlies the benefits of varied training.
-It's also referenced as a key influence in the development of the "Schema Theory of Motor Learning" @schmidtSchemaTheoryDiscrete1975, which in turn influenced decades of research on the potential benefits of varied training in motor skill learning.
-However, a number of the core assumptions utilized by @posnerGenesisAbstractIdeas1968 were later called into question both empirically and with competing theoretical accounts [@hintzmanMINERVASimulationModel1984; @hintzmanSchemaAbstractionMultipletrace1986; @palmeriCentralTendenciesExtreme2001; @zakiHighdistortionEnhancementEffect2007; @mcclellandDistributedMemoryRepresentation1985; @nosofskyInvestigationsExemplarBasedConnectionist1992; @knappTheoryCategorizationBased1984].
-@palmeriCentralTendenciesExtreme2001 demonstrated both the dangers of assuming that psychological representations mimic the metric stimulus space, as well the viability of models with simpler representational assumptions.
-These authors conducted a near replication of the @posnerGenesisAbstractIdeas1968 study, but also had participants provide similarity judgements of the dot pattern stimuli after completing the training phase.
-A multidimensional scaling analysis of the similarity judgements revealed that the psychological representations of the prototype stimuli were not located in the middle of the training stimuli, but were instead extreme points in the psychological space.
-The authors also demonstrated the generalization patterns of @posnerGenesisAbstractIdeas1968 could be accounted for by an exemplar-based model, without any need to assume the abstraction of a prototype.
-
-Instance-based, or exemplar-based models generally assume that learners encode each experience with a task as a separate instance/exemplar/trace, and that each encoded trace is in turn compared against novel stimuli [@estesClassificationCognition1994; @hintzmanMINERVASimulationModel1984; @medinContextTheoryClassification1978; @nosofskyAttentionSimilarityIdentificationcategorization1986; @jamiesonInstanceTheoryDomaingeneral2022].
-As the number of stored instances increases, so does the likelihood that some previously stored instance will be retrieved to aid in the performance of a novel task.
-Stored instances are retrieved in the context of novel stimuli or tasks if they are sufficiently similar, thus suggesting that the process of computing similarity is of central importance to generalization.
-
-Similarity, defined in this literature as a function of psychological distance between instances or categories, has provided a successful account of generalization across numerous tasks and domains.
-In an influential study demonstrating an ordinal similarity effect, experimenters employed a numerosity judgment task in which participants quickly report the number of dots flashed on a screen.
-Performance (in terms of response times to new patterns) on novel dot configurations varied as an inverse function of their similarity to previously trained dot configurations @palmeriExemplarSimilarityDevelopment1997.
-That is, performance was better on novel configurations moderately similar to trained configurations than to configurations with low-similarity, and also better on low-similarity configurations than to even less similar, unrelated configurations.
-Instance-based similarity approaches have had some success accounting for performance in certain sub-domains of motor learning [@cohenWhereGraspsAre2004; @crumpEpisodicContributionsSequential2010; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999; @wifallReachingResponseSelection2017].
-@crumpEpisodicContributionsSequential2010 trained participants to type words on an unfamiliar keyboard, while constraining the letters composing the training words to a pre-specified letter set.
-Following training, typing speed was tested on previously experienced words composed of previously experienced letters; novel words composed of letters from the trained letter set; and novel words composed of letters from an untrained letter set.
-Consistent with an instance-based account, transfer performance was graded such that participants were fastest at typing the words they had previously trained on, followed by novel words composed of letters they had trained on, and slowest performance for new words composed of untrained letters.
-
-### Issues with Previous Research
-
-Although the benefits of training variation in visuomotor skill learning have been observed many times, null findings have also been repeatedly found, leading some researchers to question the veracity of the variability of practice hypothesis [@newellSchemaTheory19752003; @vanrossumSchmidtSchemaTheory1990].
-Critics have also pointed out that investigations of the effects of training variability, of the sort described above, often fail to control for the effect of similarity between training and testing conditions.
-For training tasks in which participants have numerous degrees of freedom (e.g., projectile throwing tasks where participants control the x and y velocity of the projectile), varied groups are likely to experience a wider range of the task space over the course of their training (e.g., more unique combinations of x and y velocities).
-Experimenters may attempt to account for this possibility by ensuring that the training location(s) of the varied and constant groups are an equal distance away from the eventual transfer locations, such that their training throws are, on average, equally similar to throws that would lead to good performance at the transfer locations.
-However, even this level of experimental control may still be insufficient to rule out the effect of similarity on transfer.
-Given that psychological similarity is typically best described as either a Gaussian or exponentially decaying function of psychological distance [@ennisMultidimensionalStochasticTheory1988; @ghahramaniGeneralizationLocalRemappings1996; @loganInstanceTheoryAutomatization1988; @nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987; @thoroughmanRapidReshapingHuman2005], it is plausible that a subset of the most similar training instances could have a disproportionate impact on generalization to transfer conditions, even if the average distance between training and transfer conditions is identical between groups.
-@fig-toy-model1 demonstrates the consequences of a generalization gradient that drops off as a Gaussian function of distance from training, as compared to a linear drop-off.
-
-```{r}
-#| label: fig-toy-model1
-#| fig-cap: Left panel- Generalization predicted from a simple model that assumes a linear generalization function.
-A varied group (red vertical lines indicate the 2 training locations) trained from positions 400 and 800, and a constant group (blue vertical line), trained from position 600.
-Right panel- if a Gaussian generalization function is assumed, then varied training (400, 800) is predicted to result in better generalization to positions close to 400 and 800 than does constant training at 600.
-(For interpretation of the references to color in this figure legend, the reader is referred to the web version of this article.)
-
-p=2
-c<- .0002
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(plotjitter=ifelse(condit=="varied",0,7),
-                            linScale=ifelse(condit=="varied",980,1000),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genLinear=1000-abs(x-train.position)+plotjitter) %>% 
-  #group_by(condit) %>% mutate(scaleLinear=(genLinear-min(genLinear))/(max(genLinear)-min(genLinear))) 
-  group_by(x,condit) %>%
-  reframe(genGauss=mean(genGauss),genLinear=mean(genLinear)/linScale,.groups = 'keep')
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7,size=.4),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=447,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=450,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=659,y=1.05,label="Constant",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=657,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=847,y=1.05,label="Varied",size=3.1,fontface="plain"),
-                  annotate(geom="text",x=850,y=1.02,label="Training",size=3.1,fontface="plain"),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, linewidth=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("")
-ip2 <- simdat %>%  ggplot(aes(x,y=genLinear,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")
-
-plot_grid(ip1,ip2,ncol=2,rel_heights=c(1))
-
-```
-
-In addition to largely overlooking the potential for non-linear generalization to confound interpretations of training manipulations, the visuomotor skill learning literature also rarely considers alternatives to schema representations [@chamberlinMemoryRepresentationMotor1992].
-Although schema-theory remains influential within certain literatures, instance or exemplar-based models have accounted for human behavior across myriad domains [@jamiesonInstanceTheoryDomaingeneral2022; @loganInstanceTheoryAttention2002a].
-As mentioned above, instance based accounts have been shown to perform well on a variety of different tasks with motoric components [@crumpEpisodicContributionsSequential2010;@gandolfoMotorLearningField1996a;  @meighWhatMemoryRepresentation2018; @rosenbaumPlanningReachesEvaluating1995; @vandamMappingShapeVisuomotor2015].
-However, such accounts have received little attention within the subdomain of visuomotor skill learning focused on the benefits of varied training.
-
-The present work examines whether the commonly observed benefits of varied training can be accounted for by a theoretically motivated measure of the similarity between training throws and the testing solution space.
-We first attempt to replicate previous work finding an advantage of varied training over constant training in a projectile launching task.
-We then examine the extent to which this advantage can be explained by an instance-based similarity model.
-
-## Experiment 1
-
-### Methods
-
-#### Sample Size Estimation
-
-To obtain an independent estimate of effect size, we identified previous investigations which included between-subjects contrasts of varied and constant conditions following training on an accuracy-based projectile launching task [@chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @kerrSpecificVariedPractice1978; @wulfEffectTypePractice1991].
-We then averaged effects across these studies, yielding a Cohen's f =.43.
-The GPower 3.1 software package [@faulStatisticalPowerAnalyses2009] was then used to determine that a power of 80% requires a sample size of at least 23 participants per condition.
-All experiments reported in the present manuscript exceed this minimum number of participants per condition.
-
-#### Participants
-
-Participants were recruited from an undergraduate population that is 63% female and consists almost entirely of individuals aged 18 to 22 years.
-A total of 110 Indiana University psychology students participated in Experiment 1.
-We subsequently excluded 34 participants for poor performance on one of the dependent measures of the task (2.5-3 standard deviations worse than the median subject at the task) or for displaying a pattern of responses that was clearly indicative of a lack of engagement with the task (e.g., simply dropping the ball on each trial rather than throwing it at the target), or for reporting that they completed the experiment on a phone or tablet device, despite the instructions not to use one of these devices.
-A total of 74 participants were retained for the final analyses, 35 in the varied group and 39 in the constant group.
-
-#### Task
-
-The experimental task was programmed in JavaScript, using packages from the Phaser physics engine (https://phaser.io) and the jsPsych library [@deleeuwJsPsychJavaScriptLibrary2015].
-The stimuli, presented on a black background, consisted of a circular blue ball - controlled by the participant via the mouse or trackpad cursor; a rectangular green target; a red rectangular barrier located between the ball and the target; and an orange square within which the participant could control the ball before releasing it in a throw towards the target.
-Because the task was administered online, the absolute distance between stimuli could vary depending on the size of the computer monitor being used, but the relative distance between the stimuli was held constant.
-Likewise, the distance between the center of the target and the training and testing locations was scaled such that relative distances were preserved regardless of screen size.
-For the sake of brevity, subsequent mentions of this relative distance between stimuli, or the position where the ball landed in relation to the center of the target, will be referred to simply as distance.
-@fig-IGAS_Methods displays the layout of the task, as it would appear to a participant at the start of a trial, with the ball appearing in the center of the orange square.
-Using a mouse or trackpad, participants click down on the ball to take control of the ball, connecting the movement of the ball to the movement of the cursor.
-Participants can then "wind up" the ball by dragging it (within the confines of the orange square) and then launch the ball by releasing the cursor.
-If the ball does not land on the target, participants are presented with feedback in red text at the top right of the screen, specifying how many scaled units away the ball was from the center of the target.
-If the ball was thrown outside of the boundary of the screen participants are given feedback as to how far away from the target center the ball would have been if it had continued its trajectory.
-If the ball strikes the barrier (from the side or by landing on top), feedback is presented telling participants to avoid hitting the barrier.
-If participants drag the ball outside of the orange square before releasing it, the trial terminates, and they are reminded to release the ball within the orange square.
-If the ball lands on the target, feedback is presented in green text, confirming that the target was hit, and presenting additional feedback on how many units away the ball was from the exact center of the target.
-
-[Link to abbreviated example of task](https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html){target="_blank"}.
-
-```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
-#| label: fig-IGAS_Methods
-#| fig.cap: The stimuli of the task consisted of a blue ball, which the participants would launch at the green target, while avoiding the red barrier.
-On each trial, the ball would appear in the center of the orange square, with the position of the orange square varying between experimental conditions.
-Participants were constrained to release the ball within the square.
-
-# mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
-# plot_grid(mf,ncol=1)
-knitr::include_graphics(here::here("Assets/methodsFig1.png"))
-```
-
-#### Procedure
-
-Participants first electronically consented to participate, and then read instructions for the task which explained how to control the ball, and the goal of throwing the ball as close to the center of the target as possible.
-The training phase was split into 10 blocks of 20 trials, for a total of 200 training trials.
-Participants in the constant condition trained exclusively from a single location (760 scaled units from the target center).
-Participants in the varied condition trained from two locations (610 and 910 scaled units from the target center), encountering each location 100 times.
-The sequence of throwing locations was pseudo-random for the varied group, with the constraint that within every block of 20 training throws both training locations would occur 10 times.
-Participants in both conditions also received intermittent testing trials after every 20 training trials.
-Intermittent testing trials provided no feedback of any kind.
-The ball would disappear from view as soon as it left the orange square, and participants were prompted to start the next trial without receiving any information about the accuracy of the throw.
-Each intermittent testing stage consisted of two trials from each of the three training positions (i.e.
-all participants executed two trials each from Positions 610, 760, and 910 during each of the 10 intermittent testing stages).
-Following training, all participants completed a final testing phase from four positions: 1) their training location, 2) the training location(s) of the other group, 3) a location novel to both groups.
-The testing phase consisted of 15 trials from each of the four locations, presented in a randomized order.
-All trials in the final testing phase included feedback.
-After finishing the final testing portion of the study, participants were queried as to whether they completed the study using a mouse, a trackpad,  or some other device (this information was used in the exclusion process described above).
-Finally, participants were debriefed as to the hypotheses and manipulation of the study.
-
-### Results
-
-#### Data Processing and Statistical Packages
-
-To prepare the data, we removed trials that were not easily interpretable as performance indicators in our task.
-Removed trials included: 1) those in which participants dragged the ball outside of the orange starting box without releasing it, 2) trials in which participants clicked on the ball, and then immediately released it, causing the ball to drop straight down, 3) outlier trials in which the ball was thrown more than 2.5 standard deviations further than the average throw (calculated separately for each throwing position), and 4) trials in which the ball struck the barrier.
-The primary measure of performance used in all analyses was the absolute distance away from the center of the target.
-The absolute distance was calculated on every trial, and then averaged within each subject to yield a single performance score, for each position.
-A consistent pattern across training and testing phases in both experiments was for participants to perform worse from throwing positions further away from the target -- a pattern which we refer to as the difficulty of the positions.
-However, there were no interactions between throwing position and training conditions, allowing us to collapse across positions in cases where contrasts for specific positions were not of interest.
-All data processing and statistical analyses were performed in R version 4.32 [@rcoreteamLanguageEnvironmentStatistical2020].
-ANOVAs for group comparisons were performed using the rstatix package [@kassambaraRstatixPipeFriendlyFramework2021a].
-
-#### Training Phase
-
-@fig-IGAS_Training1 below shows aggregate training performance binned into three stages representing the beginning, middle, and end of the training phase.
-Because the two conditions trained from target distances that were not equally difficult, it was not possible to directly compare performance between conditions in the training phase.
-Our focus for the training data analysis was instead to establish that participants did improve their performance over the course of training, and to examine whether there was any interaction between training stage and condition.
-Descriptive statistics for the intermittent testing phase are provided in the supplementary materials.
-
-We performed an ANOVA comparison with stage as a within-group factor and condition as between-group factor.
-The analysis revealed a significant effect of training stage F(2,142)=62.4, p\<.001, $\eta^{2}_G$ = .17, such that performance improved over the course of training.
-There was no significant effect of condition F(1,71)=1.42, p=.24, $\eta^{2}_G$ = .02, and no significant interaction between condition and training stage, F(2,142)=.10, p=.91, $\eta^{2}_G$ \< .01.
-
-```{r}
-#| label: fig-IGAS_Training1
-#| fig-cap: Training performance for varied and constant participants binned into three stages.
-Shorter bars indicate better performance (ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1TrainPosition <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1TrainPosition3 <- e1 %>% filter(stage!="Transfer",mode==1) %>%ungroup() %>% 
-  group_by(sbjCode,Group,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-exp1Train3 <- e1 %>% filter(stage!="Transfer",mode==1)  %>%
-  group_by(sbjCode,Group,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),.groups = 'keep')
-
-e1train2 <- exp1TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",fun=mean,position=dodge)+
-  facet_wrap(~conditType,ncol=2)+
-  stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+
-  ylab("Mean Distance From Center Of Target")+
-  xlab("Training Location(s)")+theme(plot.title = element_text(hjust = 0.5))+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)
-
-#plot_grid(title,e1train2,capt,ncol=1,rel_heights=c(.18,1,.15))
-plot_grid(e1train2,ncol=1)
-
-```
-
-#### Testing Phase
-
-In Experiment 1, a single constant-trained group was compared against a single varied-trained group.
-At the transfer phase, all participants were tested from 3 positions: 1) the positions(s) from their own training, 2) the training position(s) of the other group, and 3) a position novel to both groups.
-Overall, group performance was compared with a mixed type III ANOVA, with condition (varied vs.
-constant) as a between-subject factor and throwing location as a within-subject variable.
-The effect of throwing position was strong, F(3,213) = 56.12, p\<.001, η2G = .23.
-The effect of training condition was significant F(1,71)=8.19, p\<.01, η2G = .07.
-There was no significant interaction between group and position, F(3,213)=1.81, p=.15, η2G = .01.
-
-```{r}
-#| label: fig-IGAS_Testing1
-#| fig-cap: Testing performance for each of the 4 testing positions, compared between training conditions.
-Positions 610 and 910 were trained on by the varied group, and novel for the constant group.
-Position 760 was trained on by the constant group, and novel for the varied group.
-Position 835 was novel for both groups.
-Shorter bars are indicative of better performance (the ball landing closer to the center of the target).
-Error bars indicate standard error of the mean.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-#manuscript plot
-e1test1=exp1.Test %>% ggplot(aes(x=positionX,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",fun=mean,position=dodge)+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(legend.title.align=.25, 
-  axis.text.x = element_text(size = 8.5,angle=0),
-  legend.position="top")+
-  scale_x_discrete(name="Testing Location",labels=e1Labels)
-
-e1test1
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-IGAS_Table1
-#| tbl-cap: Testing performance for varied and constant groups in experiment 1. Mean absolute deviation from the center of the target, with standard deviations in parenthesis.
-
-exp1.Test <- e1 %>% filter(stage=="Transfer") %>% select(-trainHalf)%>% group_by(positionX) %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% 
-  mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%
-  ungroup() %>% group_by(sbjCode,conditType,positionX,ThrowPosition) %>%
-summarise(MeanTargetDeviance = mean(AbsDistFromCenter),MeanScaleDev = mean(scaledDev),.groups="keep")%>% as.data.frame()
-
-test= exp1.Test %>% dplyr::rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- test=test %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- test = test %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- test=test[,1:3]
-
-kable(test,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l"))  #%>% kableExtra::kable_styling(position="left") # %>%  # kable_classic() #%>% kableExtra::footnote(general=captionText,general_title = "")
-
-```
-
-### Discussion
-
-In Experiment 1, we found that varied training resulted in superior testing performance than constant training, from both a position novel to both groups, and from the position at which the constant group was trained, which was novel to the varied condition.
-The superiority of varied training over constant training even at the constant training position is of particular note, given that testing at this position should have been highly similar for participants in the constant condition.
-It should also be noted, though, that testing at the constant trained position is not identical to training from that position, given that the context of testing is different in several ways from that of training, such as the testing trials from the different positions being intermixed, as well as a simple change in context as a function of time.
-Such contextual differences will be further considered in the General Discussion.
-
-In addition to the variation of throwing position during training, the participants in the varied condition of Experiment 1 also received training practice from the closest/easiest position, as well as from the furthest/most difficult position that would later be encountered by all participants during testing.
-The varied condition also had the potential advantage of interpolating both of the novel positions from which they would later be tested.
-Experiment 2 thus sought to address these issues by comparing a varied condition to multiple constant conditions.
-
-## Experiment 2
-
-In Experiment 2, we sought to replicate our findings from Experiment 1 with a new sample of participants, while also addressing the possibility of the pattern of results in Experiment 1 being explained by some idiosyncrasy of the particular training location of the constant group relative to the varied group.
-To this end, Experiment 2 employed the same basic procedure as Experiment 1, but was designed with six separate constant groups each trained from one of six different locations (400, 500, 625, 675, 800, or 900), and a varied group trained from two locations (500 and 800).
-Participants in all seven groups were then tested from each of the 6 unique positions.
-
-### Methods
-
-#### Participants
-
-A total of 306 Indiana University psychology students participated in Experiment 2, which was also conducted online.
-As was the case in Experiment 1, the undergraduate population from which we recruited participants was 63% female and primarily composed of 18--22-year-old individuals.
-Using the same procedure as Experiment 1, we excluded 98 participants for exceptionally poor performance at one of the dependent measures of the task, or for displaying a pattern of responses indicative of a lack of engagement with the task.
-A total of 208 participants were included in the final analyses with 31 in the varied group and 32, 28, 37, 25, 29, 26 participants in the constant groups training from location 400, 500, 625, 675, 800, and 900, respectively.
-All participants were compensated with course credit.
-
-#### Task and Procedure
-
-The task of Experiment 2 was identical to that of Experiment 1, in all but some minor adjustments to the height of the barrier, and the relative distance between the barrier and the target.
-Additionally, the intermittent testing trials featured in experiment 1 were not utilized in Experiment 2.
-An abbreviated demo of the task used for Experiment 2 can be found at (https://pcl.sitehost.iu.edu/tg/demos/igas_expt2_demo.html).
-
-The procedure for Experiment 2 was also quite similar to Experiment 1.
-Participants completed 140 training trials, all of which were from the same position for the constant groups and split evenly (70 trials each - randomized) for the varied group.
-In the testing phase, participants completed 30 trials from each of the six locations that had been used separately across each of the constant groups during training.
-Each of the constant groups thus experienced one trained location and five novel throwing locations in the testing phase, while the varied group experiences 2 previously trained, and 4 novel locations.
-
-### Results
-
-#### Data Processing and Statistical Packages
-
-After confirming that condition and throwing position did not have any significant interactions, we standardized performance within each position, and then average across position to yield a single performance measure per participant.
-This standardization did not influence our pattern of results.
-As in Experiment 1, we performed type III ANOVAs due to our unbalanced design, however the pattern of results presented below is not altered if type 1 or type III tests are used instead.
-The statistical software for the primary analyses was the same as for Experiment 1.
-Individual learning rates in the testing phase, compared between groups in the supplementary analyses, were fit using the TEfit package in R [@cochraneTEfitsNonlinearRegression2020].
-
-#### Training Phase
-
-The different training conditions trained from positions that were not equivalently difficult and are thus not easily amenable to comparison.
-As previously stated, the primary interest of the training data is confirmation that some learning did occur.
-@fig-e2train depicts the training performance of the varied group alongside that of the aggregate of the six constant groups (5a), and each of the 6 separate constant groups (5b).
-An ANOVA comparison with training stage (beginning, middle, end) as a within-group factor and group (the varied condition vs.
-the 6 constant conditions collapsed together) as a between-subject factor revealed no significant effect of group on training performance, F(1,206)=.55,p=.49, $\eta^{2}_G$ \<.01, a significant effect of training stage F(2,412)=77.91, p\<.001, $\eta^{2}_G$ =.05, and no significant interaction between group and training stage, F(2,412)=.489 p=.61, $\eta^{2}_G$ \<.01.
-We also tested for a difference in training performance between the varied group and the two constant groups that trained matching throwing positions (i.e., the constant groups training from position 500, and position 800).
-The results of our ANOVA on this limited dataset mirrors that of the full-group analysis, with no significant effect of group F(1,86)=.48, p=.49, $\eta^{2}_G$ \<.01, a significant effect of training stage F(2,172)=56.29, p\<.001, $\eta^{2}_G$ =.11, and no significant interaction between group and training stage, F(2,172)=.341 p=.71, $\eta^{2}_G$ \<.01.
-
-```{r}
-
-e2$stage <- factor(e2$stage, levels = c("Beginning", "Middle", "End","Transfer"),ordered = TRUE)
-
-exp2TrainPosition <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter))%>% as.data.frame()
-
-exp2TrainPosition3 <- e2  %>% filter(stage!="Transfer") %>%ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage,positionX) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05))%>% as.data.frame()
-
-exp2Train <- e2  %>% filter(stage!="Transfer")  %>% 
-  group_by(sbjCode,Group2,conditType,trainHalf) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter)) %>% as.data.frame()
-
-exp2Train3 <- e2  %>% filter(stage!="Transfer")  %>% ungroup() %>% 
-  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup() %>%
-  group_by(sbjCode,Group2,conditType,stage) %>% 
-  summarise(MeanTargetDistance=mean(AbsDistFromCenter),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-transfer <- filter(e2, stage=="Transfer") %>% droplevels() %>% select(-trainHalf,-initialVelocityY,ThrowPosition2)%>% ungroup()
-transfer <- transfer %>% group_by(positionX) %>% mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-  group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-transfer <- transfer %>% group_by(sbjCode,positionX) %>% mutate(ind=1,testPosIndex=cumsum(ind),posN=max(testPosIndex)) %>%
-  select(-ind) %>% mutate(testHalf = case_when(testPosIndex<15 ~"1st Half",testPosIndex>=15 ~"2nd Half")) %>% rstatix::convert_as_factor(testHalf)
-
-variedTest <- transfer %>% filter(condit==7) %>% mutate(extrapolate=ifelse(positionX=="900" | positionX=="400","extrapolation","interpolation")) 
-constantTest <- transfer %>% filter(condit!=7) %>% mutate(extrapolate=ifelse(distFromTrain==0,"interpolation","extrapolation"))
-
-transfer <- rbind(variedTest,constantTest)
-transfer<- transfer %>% mutate(novel=ifelse(distFromTrain3==0,"trainedLocation","novelLocation"))%>% rstatix::convert_as_factor(novel,extrapolate)
-
-transfer <- transfer %>% relocate(sbjCode,condit2,Group,conditType2,stage,trial,novel,extrapolate,positionX,AbsDistFromCenter,globalAvg,globalSd,scaledDev,distFromTrain3) %>% ungroup()
-
-# novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0) %>% select(-globalAvg,-globalSd,-scaledDev)%>% droplevels() %>% ungroup()
-# novelAll <- novelAll %>% group_by(positionX) %>%
-#  mutate(globalAvg=mean(AbsDistFromCenter),globalSd=sd(AbsDistFromCenter)) %>% 
-#   group_by(sbjCode,positionX) %>% mutate(scaledDev = scaleVar(globalAvg,globalSd,AbsDistFromCenter)) %>%ungroup()
-
-novelAll <- transfer %>% filter(distFromTrain!=0, distFromTrain3!=0)
-novelAllMatched <- novelAll %>% filter(condit!=5,condit!=2)
-
-constantIden <- transfer %>% filter(condit !=7,distFromTrain==0) # only constant groups from their training position
-variedTest <- transfer %>% filter(condit==7) # only varied testing
-variedVsIden <- rbind(constantIden,variedTest) # all varied combined with constant identity
-
-variedNovel <- variedTest %>% filter(distFromTrain3 !=0) # removes 500 and 800 from varied
-constantIden2 <- transfer %>% filter(condit !=7,condit!=5,condit!=2,distFromTrain==0) # only constant groups from training position 400,625,675,900
-variedVsNovelIden <- rbind(constantIden2,variedNovel) # novel positions for varied, trained for constant
-
-exp2.Test <- transfer %>%group_by(sbjCode,conditType,positionX,ThrowPosition)%>%
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test2 <- exp2.Test %>% group_by(sbjCode,conditType)%>%
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>%ungroup() %>% as.data.frame()
-
-exp2.Test7 <- transfer %>%group_by(Group2,sbjCode,positionX,Group,conditType,ThrowPosition4) %>% 
-  summarise(MeanTargetDeviance = mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05)) %>% as.data.frame()
-
-exp2.Test7.agg <- exp2.Test7  %>%group_by(Group2,sbjCode,Group,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-exp2.Test7.agg2 <- exp2.Test7  %>%group_by(sbjCode,conditType) %>% 
-  summarise(MeanTargetDeviance = mean(MeanTargetDeviance),MeanScaledDev=mean(MeanScaledDev)) %>% as.data.frame()
-
-```
-
-```{r}
-#| label: fig-e2train
-#| fig-cap: Training performance for the six constant conditions, and the varied condition, binned into three stages.
-On the left side, the six constant groups are averaged together, as are the two training positions for the varied group.
-On the right side, the six constant groups are shown separately, with each set of bars representing the beginning, middle, and end of training for a single constant group that trained from the position indicated on the x-axis.
-Figure 5b also shows training performance separately for both throwing locations trained by the varied group.
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 8
-
-### New - 3 stage
-e2train1<-exp2TrainPosition3 %>% ggplot(aes(x=stage,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  stat_summary(aes(x=stage,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+facet_wrap(~conditType,ncol=2)+
-  ylab("Mean Distance From Center Of Target") +xlab("Training Stage")+
-  theme(plot.title = element_text(face="bold",hjust = 0.0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("A")
-
-e2train2<-exp2TrainPosition3 %>% ggplot(aes(x=positionX,y=MeanTargetDistance))+
-  geom_bar(aes(group=stage,fill=stage),stat="summary",position=dodge,fun="mean")+
-  facet_wrap(~conditType,ncol=2)+stat_summary(aes(x=positionX,group=stage),fun.data=mean_se,geom="errorbar",position=dodge,width=.8)+ylab("Mean Distance From Center Of Target") +xlab("Training Location(s)")+
-  theme(plot.title = element_text(face="bold",hjust = 0,size=9),
-        plot.title.position = "plot")+
-  guides(fill=guide_legend(title="Training Stage"))+theme(legend.title.align=.25)+ggtitle("B")
-
-#plot_grid(e2train1,e2train2,ncol=1)
-
-e2train1/e2train2
-
-```
-
-#### Testing Phase
-
-In Experiment 2, a single varied condition (trained from two positions, 500 and 800), was compared against six separate constant groups (trained from a single position, 400, 500, 625, 675, 800 or 900).
-For the testing phase, all participants were tested from all six positions, four of which were novel for the varied condition, and five of which were novel for each of the constant groups.
-For a general comparison, we took the absolute deviations for each throwing position and computed standardized scores across all participants, and then averaged across throwing position.
-The six constant groups were then collapsed together allowing us to make a simple comparison between training conditions (constant vs.
-varied).
-A type III between-subjects ANOVA was performed, yielding a significant effect of condition F(1,206)=4.33, p=.039, $\eta^{2}_G$ =.02.
-Descriptive statistics for each condition are shown in table 2.
-In @fig-e2testa visualizes the consistent advantage of the varied condition over the constant groups across the testing positions.
-@fig-e2testa shows performance between the varied condition and the individual constant groups.
-
-```{r}
-#| label: fig-e2testa
-#| fig.cap: Testing phase performance from each of the six testing positions.
-The six constant conditions are averaged together into a single constant group, compared against the single varied-trained group.B) Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-#| fig-width: 11
-#| fig-height: 9
-
-# manuscript plot
-e2test1<-exp2.Test %>% ggplot(aes(x=ThrowPosition,y=MeanTargetDeviance,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25)+
-  ggtitle("A")
-
-e2test2<-exp2.Test7 %>% 
-  ggplot(aes(x=Group,y=MeanTargetDeviance,group=conditType,fill=conditType))+
-  geom_bar(stat="summary",position=position_dodge(),fun="mean")+ 
-  stat_summary(fun.data=mean_se,geom="errorbar",position=position_dodge())+
-  facet_wrap(~ThrowPosition4)+
-  ylab("Mean Distance From Center Of Target")+
-  guides(fill=guide_legend(title="Training Condition"))+
-  theme(plot.title=element_text(face="bold",size=9),
-        plot.title.position = "plot",
-        legend.title.align=.25,
-        axis.text.x = element_text(size = 7,angle=45,hjust=1))+
-  scale_x_discrete(name=" Training Group",labels=e2Labels)+ggtitle("B")
-
-e2test1 / e2test2
-
-```
-
-\
-\
-\
-
-```{r}
-#| label: tbl-e2table1
-#| tbl-cap: Transfer performance from each of the 6 throwing locations from which all participants were tested.
-Each bar represents performance from one of seven distinct training groups (six constant groups in red, one varied group in blue).
-The x axis labels indicate the location(s) from which each group trained.
-Lower values along the y axis reflect better performance at the task (closer distance to target center).
-Error bars indicate standard error of the mean.
-
-tab2= exp2.Test %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-   summarise(Mean=round(mean(MeanTargetDeviance),2),sd=round(sd(MeanTargetDeviance),2),.groups="keep")
- tab2=tab2 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
- tab2 = tab2 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% 
-   select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab2=tab2[,1:3]
-
-kable(tab2,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) # %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-Next, we compared the testing performance of constant and varied groups from only positions that participants had not encountered during training.
-Constant participants each had 5 novel positions, whereas varied participants tested from 4 novel positions (400,625,675,900).
-We first standardized performance within in each position, and then averaged across positions.
-Here again, we found a significant effect of condition (constant vs.
-varied): F(1,206)=4.30, p=.039, $\eta^{2}_G$ = .02 .
-
-```{r}
-#| label: tbl-e2table2
-#| tbl-cap: Testing performance from novel positions.
-Includes data only from positions that were not encountered during the training stage (e.g., excludes positions 500 and 800 for the varied group, and one of the six locations for each of the constant groups).
-Table presents Mean absolute deviations from the center of the target, and standard deviations in parenthesis.
-
-sum.novelAll <- novelAll %>% group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-tab3=sum.novelAll %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
- tab3=tab3 %>% group_by(Condition) %>% mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
- tab3 = tab3 %>% 
-   mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab3=tab3[,1:3]
-
-kable(tab3,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) #  %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-```
-
-Finally, corresponding to the comparison of position 760 from Experiment 1, we compared the test performance of the varied group against the constant group from only the positions that the constant groups trained.
-Such positions were novel to the varied group (thus this analysis omitted two constant groups that trained from positions 500 or 800 as those positions were not novel to the varied group).
-@fig-e2test1 displays the subset of comparisons utilized for this analysis.
-Again, we standardized performance within each position before performing the analyses on the aggregated data.
-In this case, the effect of condition did not reach statistical significance F(1,149)=3.14, p=.079, $\eta^{2}_G$ = .02.
-Table 4 provides descriptive statistics.
-
-```{r}
-#| label: fig-e2test1
-#| fig-cap: A comparison of throwing location that are identical to those trained by the constant participants (e.g., constant participants trained at position 900, tested from position 900), which are also novel to the varied-trained participants (thus excluding positions 500 and 800).
-Error bars indicate standard error of the mean.
-
-sum.variedVsNovelIden <- variedVsNovelIden  %>%
-  group_by(sbjCode,conditType,positionX) %>% 
-  summarise(MeanTargetDev=mean(AbsDistFromCenter,trim=.05),MeanScaledDev=mean(scaledDev,trim=.05),.groups="keep") %>% as.data.frame()
-
-e2Test2 <- sum.variedVsNovelIden %>% ggplot(aes(x=positionX,y=MeanTargetDev,group=conditType,fill=conditType))+geom_bar(stat="summary",position=dodge,fun="mean")+ stat_summary(fun.data=mean_se,geom="errorbar",position=dodge,width=.5)+ylab("Mean Distance From Center Of Target") +xlab("Testing Location")+theme(plot.title = element_text(hjust = 0.5))+guides(fill=guide_legend(title="Training Condition"))+theme(legend.title.align=.25)
-
-e2Test2
-
-```
-
-\
-\
-
-```{r}
-#| label: tbl-e2tab3
-#| tbl-cap:  Testing performance from the locations trained by constant participants and novel to varied participants.
-Locations 500 and 800 are not included as these were trained by the varied participants.
-Table presents Mean absolute deviation from the center of the target, and standard deviations in parenthesis.
-
-tab4=sum.variedVsNovelIden %>% rename(Condition="conditType") %>% group_by(Condition,positionX) %>%
-  summarise(Mean=round(mean(MeanTargetDev),2),sd=round(sd(MeanTargetDev),2),.groups="keep")
-
-tab4=tab4 %>% group_by(Condition) %>% 
-   mutate(GroupAvg=round(mean(Mean),2),groupSd=round(sd(Mean),2))
-
-tab4 = tab4 %>% mutate(msd=paste(Mean,"(",sd,")",sep=""),gsd=paste(GroupAvg,"(",groupSd,")",sep="")) %>% select(positionX,Condition,msd,gsd)%>%pivot_wider(names_from = Condition,values_from=c(msd,gsd))
- tab4=tab4[,1:3]
-
-kable(tab4,escape=FALSE,booktabs=TRUE,col.names=c("Position","Constant","Varied"),align=c("l")) # %>% kableExtra::kable_styling(position="left") #%>% kable_classic() #%>% footnote(general=captionText,general_title = "")
-
-```
-
-### Experiment 2 Discussion
-
-The results of Experiment 2 largely conform to the findings of Experiment 1.
-Participants in both varied and constant conditions improved at the task during the training phase.
-We did not observe the common finding of training under varied conditions producing worse performance during acquisition than training under constant conditions [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987], which has been suggested to relate to the subsequent benefits of varied training in retention and generalization testing [@soderstromLearningPerformanceIntegrative2015].
-However, our finding of no difference in training performance between constant and varied groups has been observed in previous work [@chuaPracticeVariabilityPromotes2019; @moxleySchemaVariabilityPractice1979; @pigottMotorSchemaStructure1984].
-
-In the testing phase, our varied group significantly outperformed the constant conditions in both a general comparison, and in an analysis limited to novel throwing positions.
-The observed benefit of varied over constant training echoes the findings of many previous visuomotor skill learning studies that have continued to emerge since the introduction of Schmidt's influential Schema Theory [@catalanoDistantTransferCoincident1984a; @chuaPracticeVariabilityPromotes2019; @goodwinEffectDifferentQuantities1998; @mccrackenTestSchemaTheory1977; @moxleySchemaVariabilityPractice1979; @newellVariabilityPracticeTransfer1976; @pigottMotorSchemaStructure1984; @rollerVariablePracticeLenses2001; @schmidtSchemaTheoryDiscrete1975; @willeyLongtermMotorLearning2018; @wrisbergVariabilityPracticeHypothesis1987; @wulfEffectTypePractice1991].
-We also join a much smaller set of research to observe this pattern in a computerized task [@seowTransferEffectsVaried2019].
-One departure from the experiment 1 findings concerns the pattern wherein the varied group outperformed the constant group even from the training position of the constant group, which was significant in experiment 1, but did not reach significance in experiment 2.
-Although this pattern has been observed elsewhere in the literature [@goodeSuperiorityVariableRepeated2008; @kerrSpecificVariedPractice1978], the overall evidence for this effect appears to be far weaker than for the more general benefit of varied training in conditions novel to all training groups.
-
-## Computational Model
-
-*Controlling for the similarity between training and testing.* The primary goal of Experiment 2 was to examine whether the benefits of variability would persist after accounting for individual differences in the similarity between trained and tested throwing locations.
-To this end, we modelled each throw as a two-dimensional point in the space of x and y velocities applied to the projectile at the moment of release.
-For each participant, we took each individual training throw, and computed the similarity between that throw and the entire population of throws within the solution space for each of the 6 testing positions.
-We defined the solution space empirically as the set of all combinations of x and y throw velocities that resulted in hitting the target.
-We then summed each of the trial-level similarities to produce a single similarity for each testing position score relating how the participant threw the ball during training and the solutions that would result in target hits from each of the six testing positions -- thus resulting in six separate similarity scores for each participant.
-@fig-taskSpace visualizes the solution space for each location and illustrates how different combinations of x and y velocity result in successfully striking the target from different launching positions.
-As illustrated in @fig-taskSpace, the solution throws represent just a small fraction of the entire space of velocity combinations used by participants throughout the experiment.
-
-```{r}
-#| label: fig-taskSpace
-#| fig.cap: A) A visual representation of the combinations of throw parameters (x and y velocities applied to the ball at launch), which resulted in target hits during the testing phase.
-This empirical solution space was compiled from all of the participants in Experiment 2.
-B) shows the solution space within the context of all of the throws made throughout the testing phase of the experiment.
-#| fig-width: 11
-#| fig-height: 9
-#| 
-taskspace <- e2 %>% filter(AbsDistFromCenter<900)
-taskspace$hitOrMiss <- ifelse(taskspace$trialType==11,"Hit Target","Missed Target")
-
-solSpace <- e2 %>% filter(trialType==11)
-#solSpace %>% ggplot(aes(x=X_Velocity,y=Y_Velocity)) + geom_point(aes(colour=ThrowPosition),alpha=0.58) + ggtitle("")
-
-solSpace$Result = ifelse(solSpace$ThrowPosition==400,"400",solSpace$ThrowPosition)
-solSpace$Result = ifelse(solSpace$ThrowPosition==500,"500",solSpace$Result)
-solSpace$Result= ifelse(solSpace$ThrowPosition==625,"625",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==675,"675",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==800,"800",solSpace$Result)
-solSpace$Result = ifelse(solSpace$ThrowPosition==900,"900",solSpace$Result)
-
-missSpace <- e2 %>% filter(trialType !=11)
-missSpace$Result = "Missed Target"
-solSpace$Result <- solSpace$Result
-
-# the usual method of changing the legend title does not seem to work after the colours are manually scaled. 
-# multiplied velocoties by -1 to make the axes less confusing
-ss=solSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1)) + 
-  geom_point(aes(colour=Result),alpha=0.6) + 
-  scale_color_manual(values =brewer.pal(n=6,name="Set1"))+
-  labs(colour="Target Hit Thrown from Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity")+ggtitle("A")
-
-fullSpace <- rbind(missSpace,solSpace)
-
-fs<- fullSpace %>% ggplot(aes(x=X_Velocity*-1,y=Y_Velocity*-1,colour=Result)) + 
-  geom_point(aes(),alpha=0.6) + scale_color_manual(values =brewer.pal(n=7,name="Set1"))+
-  labs(colour="Target Hit or Miss From Position:") + xlab("X Release Velocity") + ylab("Y Release Velocity") +ggtitle("B")
-
-library(patchwork)
-ss/fs
-
-```
-
-For each individual trial, the Euclidean distance (Equation 1) was computed between the velocity components (x and y) of that trial and the velocity components of each individual solution throw for each of the 6 positions from which participants would be tested in the final phase of the study.
-The P parameter in Equation 1 is set equal to 2, reflecting a Gaussian similarity gradient.
-Then, as per an instance-based model of similarity [@loganInstanceTheoryAttention2002a; @nosofskySimilarityScalingCognitive1992], these distances were multiplied by a sensitivity parameter, c, and then exponentiated to yield a similarity value.
-The parameter c controls the rate with which similarity-based generalization drops off as the Euclidean distance between two throws in x- and y-velocity space increases.
-If c has a large value, then even a small difference between two throws' velocities greatly decreases the extent of generalization from one to the other.
-A small value for c produces broad generalization from one throw to another despite relatively large differences in their velocities.
-The similarity values for each training individual throw made by a given participant were then summed to yield a final similarity score, with a separate score computed for each of the 6 testing positions.
-The final similarity score is construable as index of how accurate the throws a participant made during the training phase would be for each of the testing positions.
-
-**Equation 1:** $$ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) $$
-
-**Equation 2:**
-$$ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } $$
-
-A simple linear regression revealed that these similarity scores were significantly predictive of performance in the transfer stage, t =-15.88, p\<.01, $r^2$=.17, such that greater similarity between training throws and solution spaces for each of the test locations resulted in better performance.
-We then repeated the group comparisons above while including similarity as a covariate in the model.
-Comparing the varied and constant groups in testing performance from all testing positions yielded a significant effect of similarity, F(1, 205)=85.66, p\<.001, $\eta^{2}_G$ =.29, and also a significant effect of condition (varied vs.
-constant), F(1, 205)=6.03, p=.015, $\eta^{2}_G$ =.03.
-The group comparison limited to only novel locations for the varied group pit against trained location for the constant group resulted in a significant effect of similarity, F(1,148)=31.12, p\<.001, $\eta^{2}_G$ =.18 as well as for condition F(1,148)=11.55, p\<.001, $\eta^{2}_G$ =.07.
-For all comparisons, the pattern of results was consistent with the initial findings from Experiment 2, with the varied group still performing significantly better than the constant group.
-
-### Fitting model parameters separately by group
-
-To directly control for similarity in Experiment 2, we developed a model-based measure of the similarity between training throws and testing conditions.
-This similarity measure was a significant predictor of testing performance, e.g., participants whose training throws were more similar to throws that resulted in target hits from the testing positions, tended to perform better during the testing phase.
-Importantly, the similarity measure did not explain away the group-level benefits of varied training, which remained significant in our linear model predicting testing performance after similarity was added to the model.
-However, previous research has suggested that participants may differ in their level of generalization as a function of prior experience, and that such differences in generalization gradients can be captured by fitting the generalization parameter of an instance-based model separately to each group [@hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994].
-Relatedly, the influential Bayesian generalization model developed by @tenenbaumGeneralizationSimilarityBayesian2001a predicts that the breadth of generalization will increase when a rational agent encounters a wider variety of examples.
-Following these leads, we assume that in addition to learning the task itself, participants are also adjusting how generalizable their experience should be.
-Varied versus constant participants may be expected to learn to generalize their experience to different degrees.
-To accommodate this difference, the generalization parameter of the instance-based model (in the present case, the $c$ parameter) can be allowed to vary between the two groups to reflect the tendency of learners to adaptively tune the extent of their generalization.
-One specific hypothesis is that people adaptively set a value of c to fit the variability of their training experience [@nosofskyExemplarbasedAccountsMultiplesystem2000; @sakamotoTrackingVariabilityLearning2006].
-If one's training experience is relatively variable, as with the variable training condition, then one might infer that future test situations will also be variable, in which case a low value of c will allow better generalization because generalization will drop off slowly with training-to-testing distance.
-Conversely, if one's training experience has little variability, as found in the constant training conditions, then one might adopt a high value of c so that generalization falls off rapidly away from the trained positions.
-
-To address this possibility, we compared the original instance-based model of similarity fit against a modified model which separately fits the generalization parameter, c, to varied and constant participants.
-To perform this parameter fitting, we used the optim function in R, and fit the model to find the c value(s) that maximized the correlation between similarity and testing performance.
-
-Both models generate distinct similarity values between training and testing locations.
-Much like the analyses in Experiment 2, these similarity values are regressed against testing performance in models of the form shown below.
-As was the case previously, testing performance is defined as the mean absolute distance from the center of the target (with a separate score for each participant, from each position).
-
-Linear models 1 and 3 both show that similarity is a significant predictor of testing performance (p\<.01).
-Of greater interest is the difference between linear model 2, in which similarity is computed from a single c value fit from all participants (Similarity1c), with linear model 4, which fits the $c$ parameter separately between groups (Similarity2c).
-In linear model 2, the effect of training group remains significant when controlling for Similarity1c (p\<.01), with the varied group still performing significantly better.
-However, in linear model 4 the addition of the Similarity2c predictor results in the effect of training group becoming nonsignificant (p=.40), suggesting that the effect of varied vs.
-constant training is accounted for by the Similarity2c predictor.
-Next, to further establish a difference between the models, we performed nested model comparisons using ANOVA, to see if the addition of the training group parameter led to a significant improvement in model performance.
-In the first comparison, ANOVA(Linear Model 1, Linear Model 2), the addition of the training group predictor significantly improved the performance of the model (F=22.07, p\<.01).
-However, in the second model comparison, ANOVA (Linear model 3, Linear Model 4) found no improvement in model performance with the addition of the training group predictor (F=1.61, p=.20).
-
-Finally, we sought to confirm that similarity values generated from the adjusted Similarity2c model had more predictive power than those generated from the original Similarity1c model.
-Using the BIC function in R, we compared BIC values between linear model 1 (BIC=14604.00) and linear model 3 (BIC = 14587.64).
-The lower BIC value of model 3 suggests a modest advantage for predicting performance using a similarity measure computed with two c values over similarity computed with a single c value.
-When fit with separate c values, the best fitting $c$ parameters for the model consistently optimized such that the c value for the varied group (c=.00008) was smaller in magnitude than the c value for the constant group (c= .00011).
-Recall that similarity decreases as a Gaussian function of distance (equation 1 above), and a smaller value of c will result in a more gradual drop-off in similarity as the distance between training throws and testing solutions increases.
-
-In summary, our modeling suggests that an instance-based model which assumes equivalent generalization gradients between constant and varied trained participants is unable to account for the extent of benefits of varied over constant training observed at testing.
-The evidence for this in the comparative model fits is that when a varied/constant dummy-coded variable for condition is explicitly added to the model, the variable adds a significant contribution to the prediction of test performance, with the variable condition yielding better performance than the constant conditions.
-However, if the instance-based generalization model is modified to assume that the training groups can differ in the steepness of their generalization gradient, by incorporating a separate generalization parameter for each group, then the instance-based model can account for our experimental results without explicitly taking training group into account.
-Henceforth this model will be referred to as the Instance-based Generalization with Adaptive Similarity (IGAS) model.
-
-## Project 1 General Discussion
-
-Across two experiments, we found evidence in support of the benefits of variability hypothesis in a simple, computerized projectile throwing task.
-Generalization was observed in both constant and varied participants, in that both groups tended to perform better at novel positions in the testing phase than did participants who started with those positions in the training phase.
-However, varied trained participants consistently performed better than constant trained participants, in terms of both the testing phase in general, and in a comparison that only included untrained positions.
-We also found some evidence for the less commonly observed pattern wherein varied-trained participants outperform constant-trained participants even from conditions identical to the constant group training [@goodeSuperiorityVariableRepeated2008; @greenPracticeVariabilityTransfer1995a; @kerrSpecificVariedPractice1978].
-In Experiment 1 varied participants performed significantly better on this identity comparison.
-In Experiment 2, the comparison was not significant initially, but became significant after controlling for the similarity measure that incorporates only a single value for the steepness of similarity-based generalization (c).
-Furthermore, we showed that the general pattern of results from Experiment 2 could be parsimoniously accommodated by an instance-based similarity model, but only with the assumption that constant and varied participants generalize their training experience to different degrees.
-
-Our results thus suggest that the benefits of variation cannot be explained by the varied-trained participants simply covering a broader range of the task space.
-Rather, the modeling suggests that varied participants also learn to adaptively tune their generalization function such that throwing locations generalize more broadly to one another than they do in the constant condition.
-A learning system could end up adopting a higher c value in the constant than variable training conditions by monitoring the trial-by-trial variability of the training items.
-The $c$ parameter would be adapted downwards when adjacent training items are dissimilar to each other and adapted upwards when adjacent training items are the same.
-In this fashion, contextually appropriate c values could be empirically learned.
-This learning procedure would capture the insight that if a situation has a high amount variability, then the learner should be predisposed toward thinking that subsequent test items will also show considerable variability, in which case generalization gradients should be broad, as is achieved by low values for c.
-@sakamotoTrackingVariabilityLearning2006 implemented a similar learning mechanism for updating the generalization paramater in an exemplar-based model (although in their model, a separate generalization parameter is assigned to each exemplar).
-In their experiment, participants were trained on a high variability and a low variability category, and the dynamically updated generalization parameter was necessary to account for broader generalization observed around the high variability category when participants were tested with an ambiguous intermediary item.
-In a subsequent work [@sakamotoPuttingPsychologyBack2008], the same authors showed that a similar learning mechanism could account for the pattern wherein participants generalize more broadly around a category when the average distance between the category exemplars is larger (however the only model tested in this work was a prototype model).
-
-Also of interest is whether the IGAS model can predict the pattern of results wherein the varied condition outperforms the constant condition even from the position on which the constant condition trained.
-Although our models were fit using all of the Experiment 2 training and testing data, not just that of the identity comparisons, in @fig-Toy-Model-dis we demonstrate how a simplified version of the IGAS model could in principle produce such a pattern.
-In addition to the assumption of differential generalization between varied and constant conditions, our simplified model makes explicit an assumption that is incorporated into the full IGAS model -- namely that even when being tested from a position identical to that which was trained, there are always some psychological contextual differences between training and testing throws, resulting in a non-zero dissimilarity.
-
-```{r}
-#| label: fig-Toy-Model-dis
-#| fig.cap: A simple model depicting the necessity of both of two separately fit generalization parameters, c, and a positive distance between training and testing contexts, in order for an instance model to predict a pattern of varied training from stimuli 400 and 800 outperforming constant training from position 600 at a test position of 600.
-For the top left panel, in which the generalization model assumes a single c value (-.008) for  both varied and constant conditions, and identical contexts across training and testing, the equation which generates the varied condition is - Amount of Generalization = $e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}$, whereas the constant group generalization is generated from $2\cdot e^{(c\cdot|x-600|)}$.
-For the top right panel, the c constants in the original equations are different for the 2 conditions, with $c=-.002$ for the varied condition, and $c=-.008$ for the constant condition.
-The bottom two panels are generated from identical equations to those immediately above, except for the addition of extra distance (100 units) to reflect the assumption of some change in context between training and testing conditions.
-Thus, the generalization model for the varied condition in the bottom-right panel is of the form - Amount of Generalization = $e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}$ .
-#| fig.width: 11
-#| fig.height: 11.0
-
-#
-
-p=2
-c<- .000002
-
-trainingTestingDifference=2000;
-cvaried=.00002
-cconstant=.0005
-simdat <- data.frame(x=rep(seq(200,1000),3),condit=c(rep("varied",1602),rep("constant",801)),
-                     train.position=c(rep(400,801),rep(800,801),rep(600,801)),c=.0002,p=2) %>%
-                     mutate(c2=ifelse(condit=="varied",cvaried,cconstant),
-                            genGauss=exp(-c*(abs((x-train.position)^p))),
-                            genGaussDist=exp(-c*(trainingTestingDifference+abs((x-train.position)^p))),
-                            genGauss2=exp(-c2*(abs((x-train.position)^p))),
-                            genGaussDist2=exp(-c2*(trainingTestingDifference+abs((x-train.position)^p))),
-                            ) %>% 
-  group_by(x,condit) %>%
-  summarise(genGauss=mean(genGauss),genGauss2=mean(genGauss2),genGaussDist=mean(genGaussDist),genGaussDist2=mean(genGaussDist2),.groups='keep')
-
-#plot(x,exp(c*(trainingTestingDifference+abs(x-800)))+exp(c*(trainingTestingDifference+abs(x-400)))
-
-colorVec=c("darkblue","darkred")
-plotSpecs <- list(geom_line(alpha=.7),scale_color_manual(values=colorVec),
-                  geom_vline(alpha=.55,xintercept = c(400,800),color=colorVec[2]),
-                  geom_vline(alpha=.55,xintercept = c(600),color=colorVec[1]),
-                  ylim(c(0,1.05)),
-                  #xlim(c(250,950)),
-                  scale_x_continuous(breaks=seq(200,1000,by=200)),
-                  xlab("Test Stimulus"),
-                  annotate(geom="text",x=455,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=455,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=662,y=1.05,label="Constant",size=3.0),
-                  annotate(geom="text",x=657,y=.97,label="Training",size=3.0),
-                  annotate(geom="text",x=855,y=1.05,label="Varied",size=3.0),
-                  annotate(geom="text",x=855,y=.97,label="Training",size=3.0),
-                  theme(panel.border = element_rect(colour = "black", fill=NA, size=1),
-                        legend.position="none"))
-
-ip1 <- simdat  %>% ggplot(aes(x,y=genGauss,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+ggtitle("Identical context, 1c")
-ip2 <- simdat %>%  ggplot(aes(x,y=genGauss2,group=condit,col=condit))+plotSpecs+ylab("")+ggtitle("Identical context, 2c")
-ip3 <- simdat  %>% ggplot(aes(x,y=genGaussDist,group=condit,col=condit))+plotSpecs+ylab("Amount of Generalization")+
-  ggtitle("Added distance due to context, 1c")+theme(plot.margin = margin(0, 0, 0, 1))
-ip4 <- simdat %>%  ggplot(aes(x,y=genGaussDist2,group=condit,col=condit))+plotSpecs+ylab("")+
-  ggtitle("Added distance due to context, 2c")+theme(plot.margin = margin(0, 0, 0, 1))
-# gridExtra::grid.arrange(ip1,ip2,ip3,ip4,ncol=2)
-
-#gtitle="Figure 9."
-#title = ggdraw()+draw_label(gtitle,fontface = 'bold',x=0,hjust=0,size=11)+theme(plot.margin = margin(0, 0, 0, 1))
-#p1 <- plot_grid(title,NULL,ip1,ip2,ip3,ip4,ncol=2,rel_heights=c(.1,.8,.8))
-p1 <- (ip1+ip2) / (ip3+ip4)
-
-p1
-
-```
-
-As described above, the idea that learners flexibly adjust their generalization gradient based on prior experience does have precedent in the domains of category learning [@ahaConceptLearningFlexible1992; @briscoeConceptualComplexityBias2011; @hahnEffectsCategoryDiversity2005; @lambertsFlexibleTuningSimilarity1994; @opdebeeckRepresentationPerceivedShape2008], and sensorimotor adaptation [@marongelliAdvantageFlexibleNeuronal2013; @taylorContextdependentGeneralization2013; @thoroughmanRapidReshapingHuman2005].
-@lambertsFlexibleTuningSimilarity1994 showed that a simple manipulation of background knowledge during a categorization test resulted in participants generalizing their training experience more or less broadly, and moreover that such a pattern could be captured by allowing the generalization parameter of an instance-based similarity model to be fit separately between conditions.
-The flexible generalization parameter has also successfully accounted for generalization behavior in cases where participants have been trained on categories that differ in their relative variability [@hahnEffectsCategoryDiversity2005; @sakamotoTrackingVariabilityLearning2006].
-However, to the best of our knowledge, IGAS is the first instance-based similarity model that has been put forward to account for the effect of varied training in a visuomotor skill task.
-Although IGAS was inspired by work in the domain of category learning, its success in a distinct domain may not be surprising in light of the numerous prior observations that at least certain aspects of learning and generalization may operate under common principles across different tasks and domains [@censorCommonMechanismsHuman2012; @hillsCentralExecutiveSearch2010; @jamiesonInstanceTheoryDomaingeneral2022; @lawSharedMechanismsPerceptual2010; @roarkComparingPerceptualCategory2021; @rosenbaumAcquisitionIntellectualPerceptualMotor2001; @vigoLearningDifficultyVisual2018; @wallIdentifyingRelationshipsCognitive2021; @wuSimilaritiesDifferencesSpatial2020; @yangGeneralLearningAbility2020].
-
-Our modelling approach does differ from category learning implementations of instance-based models in several ways.
-One such difference is the nature of the training instances that are assumed to be stored.
-In category learning studies, instances are represented as points in a multidimensional space of all of the attributes that define a category item (e.g., size/color/shape).
-Rather than defining instances in terms of what stimuli learners experience, our approach assumes that stored, motor instances reflect how they act, in terms of the velocity applied to the ball on each throw.
-An advantage of many motor learning tasks is the relative ease with which task execution variables can be directly measured (e.g., movement force, velocity, angle, posture) in addition to the decision and response time measures that typically exhaust the data generated from more classical cognitive tasks.
-Of course, whether learners actually are storing each individual motor instance is a fundamental question beyond the scope of the current work -- though as described in the introduction there is some evidence in support of this idea [@chamberlinNoteSchemaExemplar1992; @crumpEpisodicContributionsSequential2010; @hommelEventFilesEvidence1998; @meighWhatMemoryRepresentation2018; @poldrackRelationshipSkillLearning1999].
-A particularly noteworthy instance-based model of sensory-motor behavior is the Knowledge II model of Rosenbaum and colleagues [@cohenWhereGraspsAre2004; @rosenbaumPlanningReachesEvaluating1995].
-Knowledge II explicitly defines instances as postures (joint combinations), and is thus far more detailed than IGAS in regards to the contents of stored instances.
-Knowledge II also differs from IGAS in that learning is accounted for by both the retrieval of stored postures, and the generation of novel postures via the modification of retrieved postures.
-A promising avenue for future research would be to combine the adaptive similarity mechanism of IGAS with the novel instance generation mechanisms of Knowledge II.
-
-Our findings also have some conceptual overlap with an earlier study on the effects of varied training in a coincident timing task [@catalanoDistantTransferCoincident1984a].
-In this task, participants observe a series of lamps lighting up consecutively, and attempt to time a button press with the onset of the final lamp.
-The design consisted of four separate constant groups, each training from a single lighting velocity, and a single varied group training with all four of the lighting velocities used by the individual constant groups.
-Participants were then split into four separate testing conditions, each of which were tested from a single novel lighting velocity of varying distance from the training conditions.
-The result of primary interest was that all participants performed worse as the distance between training and testing velocity increased -- a typical generalization decrement.
-However, varied participants showed less of a decrement than did constant participants.
-The authors take this result as evidence that varied training results in a less-steep generalization gradient than does constant training.
-Although the experimental conclusions of Catalano and Kleiner are similar to our own, our work is novel in that we account for our results with a cognitive model, and without assuming the formation of a schema.
-Additionally, the way in which Catalano and Kleiner collapse their separate constant groups together may result in similarity confounds between varied and constant conditions that leaves their study open to methodological criticisms, especially in light of related work which demonstrated that the extent to which varied training may be beneficial can depend on whether the constant group they are compared against trained from similar conditions to those later tested [@wrisbergVariabilityPracticeHypothesis1987].
-Our study alleviates such concerns by explicitly controlling for similarity.
-
-### Limitations
-
-A limitation of this study concerns the ordering of the testing/transfer trials at the conclusion of both experiments.
-Participants were tested from each separate position (4 in Experiment 1, 6 in Experiment 2) in a random, intermixed order.
-Because the varied group was trained from two positions that were also randomly ordered, they may have benefited from experience with this type of sequencing, whereas the constant groups had no experience with switching between positions trial to trial.
-This concern is somewhat ameliorated by the fact that the testing phase performance of the constant groups from their trained position was not significantly worse than their level of performance at the end of the training phase, suggesting that they were not harmed by random ordering of positions during testing.
-It should also be noted that the computerized task utilized in the present work is relatively simple compared to many of the real-world tasks utilized in prior research.
-It is thus conceivable that the effect of variability in more complex tasks is distinct from the process put forward in the present work.
-An important challenge for future work will be to assess the extent to which IGAS can account for generalization in relatively complex tasks with far more degrees of freedom.
-
-It is common for psychological process models of categorization learning to use an approach such as multidimensional scaling so as to transform the stimuli from the physical dimensions used in the particular task into the psychological dimensions more reflective of the actual human representations [@nosofskySimilarityScalingCognitive1992; @shepardUniversalLawGeneralization1987].
-Such scaling typically entails having participants rate the similarity between individual items and using these similarity judgements to then compute the psychological distances between stimuli, which can then be fed into a subsequent model.
-In the present investigation, there was no such way to scale the x and y velocity components in terms of the psychological similarity, and thus our modelling does rely on the assumption that the psychological distances between the different throwing positions are proportional to absolute distances in the metric space of the task (e.g., the relative distance between positions 400 and 500 is equivalent to that between 800 and 900).
-However, an advantage of our approach is that we are measuring similarity in terms of how participants behave (applying a velocity to the ball), rather than the metric features of the task stimuli.
-
-### Conclusion
-
-Our experiments demonstrate a reliable benefit of varied training in a simple projectile launching task.
-Such results were accounted for by an instance-based model that assumes that varied training results in the computation of a broader similarity-based generalization gradient.
-Instance-based models augmented with this assumption may be a valuable approach towards better understanding skill generalization and transfer.
-
-{{< pagebreak >}}
-
-# Project 2
-
-## Introduction
-
-A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization.
-One such aspect, which has received a great deal of research attention, is the variability of examples experienced during training [@ravivHowVariabilityShapes2022].
-The influence of training variation has been studied in numerous domains, including category learning [@cohenCategoryVariabilityExemplar2001; @posnerGenesisAbstractIdeas1968], visuomotor learning [@schmidtSchemaTheoryDiscrete1975; @bernikerEffectsTrainingBreadth2014], language learning [@perryLearnLocallyThink2010], and education [@braithwaiteEffectsVariationPrior2015; @guoEffectsExampleVariability2014].
-The pattern of results is complex, with numerous studies finding both beneficial [@catalanoDistantTransferCoincident1984a; @braunMotorTaskVariation2009; @rollerVariablePracticeLenses2001; @gormanInstancebasedModelAccount2022], as well as null or negative effects [@huHighvariabilityTrainingDoes2024; @vanrossumSchmidtSchemaTheory1990; @brekelmansDoesHighVariability2022].
-The present study seeks to contribute to the large body of existing research by examining the influence of variability in visuomotor function learning - a domain in which it has been relatively under-studied.
-
-### Function Learning and Extrapolation
-
-The study of human function learning investigates how people learn relationships between continuous input and output values.
-Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that do not contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021; @schulzCommunicatingCompositionalPatterns2020].
-Studies of function learning often compare the difficulty of learning functions of different underlying forms (e.g.
-linear, bi-linear, power, sinusoidal), and the extent to which participants can accurately respond to novel inputs that fall in-between previously experienced inputs (interpolation testing), or that fall outside the range of previously experienced inputs (extrapolation).
-
-@carrollFunctionalLearningLearning1963 conducted the earliest work on function learning.
-Input stimuli and output responses were both lines of varying length.
-The correct output response was related to the length of the input line by a linear, quadratic, or random function.
-Participants in the linear and quadratic performed above chance levels during extrapolation testing, with those in the linear condition performing the best overall.
-Carroll argued that these results were best explained by a rule-based model wherein learners form an abstract representation of the underlying function.
-Subsequent work by @brehmerHypothesesRelationsScaled1974, testing a wider array of functional forms, provided further evidence for superior extrapolation in tasks with linear functions.
-Brehmer argued that individuals start out assuming a linear function, but given sufficient error will progressively test alternative hypotheses with polynomials of greater degree.
-@kohFunctionLearningInduction1991 employed a visuomotor function learning task, wherein participants were trained on examples from an unknown function relating the length of an input line to the duration of a response (time between keystrokes).
-In this domain, participants performed best when the relation between line length and response duration was determined by a power law, as opposed to linear function.
-Koh and Meyer developed the log-polynomial adaptive-regression model to account for their results.
-
-The first significant challenge to rule-based accounts of function learning was put forth by @deloshExtrapolationSineQua1997 .
-In their task, participants learned to associate stimulus magnitudes with response magnitudes that were related via either linear, exponential, or quadratic function.
-Participants approached ceiling performance by the end of training in each function condition, and were able to accurately respond on interpolation testing trials.
-All three conditions demonstrated some capacity for extrapolation, however participants in the linear condition tended to underestimate the true function, while exponential and quadratic participants reliably overestimated the true function on extrapolation trials.
-Extrapolation and interpolation performances are depicted in @fig-delosh-extrap.
-
-The authors evaluated the rule-based models introduced in earlier research (with some modifications enabling trial-by-trial learning).
-The polynomial hypothesis testing model [@carrollFunctionalLearningLearning1963; @brehmerHypothesesRelationsScaled1974] tended to mimic the true function closely in extrapolation, and thus offered a poor account of the under and over-estimation biases shown in the human data.
-The log-polynomial adaptive regression model [@kohFunctionLearningInduction1991] was able to mimic some of the systematic deviations produced by human subjects, but also predicted overestimation in cases where underestimation occurred.
-
-The authors also introduced two new function-learning models.
-The Associative Learning Model (ALM) and the extrapolation-association model (EXAM).
-ALM is a two-layer connectionist model adapted from the ALCOVE model in the category learning literature [@kruschkeALCOVEExemplarbasedConnectionist1992].
-ALM belongs to the general class of radial-basis function neural networks, and can be considered a similarity-based model in the sense that the nodes in the input layer of the network are activated as a function of distance (see @fig-alm-diagram).
-The EXAM model retains the same similarity-based activation and associative learning mechanisms as ALM, while being augmented with a linear rule response mechanism.
-When presented with novel stimuli, EXAM will retrieve the most similar input-output examples encountered during training, and from those examples compute a local slope.
-ALM was able to provide a good account of participants' training and interpolation data in all three function conditions, however it was unable to extrapolate.
-EXAM, by contrast, was able to reproduce both the extrapolation underestimation, as well as the quadratic and exponential overestimation patterns exhibited by the human participants.
-Subsequent research identified some limitations in EXAM's ability to account for cases where human participants learn and extrapolate a sinusoidal function [@bottNonmonotonicExtrapolationFunction2004] or to scenarios where different functions apply to different regions of the input space [@kalishPopulationLinearExperts2004], though EXAM has been shown to provide a good account of human learning and extrapolation in tasks with bi-linear, V-shaped input spaces [@mcdanielPredictingTransferPerformance2009].
-
-```{r}
-#| label: fig-delosh-extrap
-#| fig-cap: The generalization patterns of human participants observed in DeLosh et al.
-(1997) (reproduced from Figure 3 in their manuscript).
-Dots represent the average responses of human participants, and solid lines represent the true functions.
-The dashed vertical lines indicate the lower and upper bounds of the trained examples.
-Stimulii that fall within the dashed lines are interpolations of the training examples, while those that fall outside the dashed lines are extrapolations.
-#| echo: false
-#| fig-width: 10
-#| cache: false 
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-
-#walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-source(here::here("Functions","deLosh_data.R"))
-#source(here::here("Functions","Display_Functions.R"))
-
-extrapLines <- list(geom_vline(xintercept=30,color="black",alpha=.4,linetype="dashed"),
-                    geom_vline(xintercept=70,color="black",alpha=.4,linetype="dashed"))
-
-linear_function <- function(x) 2.2 * x + 30
-exponential_function <- function(x) 200 * (1 - exp(-x/25))
-quadratic_function <- function(x) 210 - (x - 50)^2 / 12
-
-linear_plot <- ggplot(deLosh_data$human_data_linear, aes(x, y)) +
-    geom_point(shape=1) + stat_function(fun = linear_function, color = "black") +
-  labs(y="Response Magnitude", title="Linear Function",x="") + extrapLines
-
-exponential_plot <- ggplot(deLosh_data$human_data_exp, aes(x, y)) +
-  geom_point(aes(shape = "Observed", color = "Observed"),shape=1) + 
-  stat_function(aes(color = "True Function"),fun = exponential_function, geom="line")+
-  labs(x="Stimulus Magnitude", title="Exponential Function",y="")  +
-  extrapLines +
-  scale_shape_manual(values = c(1)) +
-  scale_color_manual(values = c("Observed" = "black", "True Function" = "black")) +
-  theme(legend.title = element_blank(), legend.position="top") +
-  guides(color = guide_legend(override.aes = list(shape = c(1, NA), 
-                                                  linetype = c(0, 1))))
-
-quadratic_plot <- ggplot(deLosh_data$human_data_quad, aes(x = x, y = y)) +
-  geom_point( shape = 1) +
-  stat_function( fun = quadratic_function, geom = "line") +
-  labs(title="Quadratic Function",x="",y="") + extrapLines
-
-linear_plot + exponential_plot + quadratic_plot
-```
-
-### Variability and Function Learning
-
-The influence of variability on function learning tasks has received relatively little attention.
-The study by @deloshExtrapolationSineQua1997 (described in detail above) did include a variability manipulation (referred to as density in their paper), wherein participants were trained with either 8, 20, or 50 unique input-output pairs, with the total number of training trials held constant.
-They found a minimal influence of variability on training performance, and no difference between groups in interpolation or extrapolation, with all three variability conditions displaying accurate interpolation, and linearly biased extrapolation that was well accounted for by the EXAM model.
-
-In the domain of visuomotor learning, @vandamMappingShapeVisuomotor2015 employed a task which required participants to learn a linear function between the spikiness of shape stimuli and the correct horizontal position to make a rapid pointing response.
-The shapes ranged from very spiky to completely circular at the extreme ends of the space.
-Participants trained with intermediate shapes having lower variation (2 shapes) or higher variation (5 shapes) condition, with the 2 items of the lower variation condition matching the items used on the extreme ends of the higher variation training space.
-Learning was significantly slower in the higher variation group.
-However, the two conditions did not differ when tested with novel shapes, with both groups producing extrapolation responses of comparable magnitude to the most similar training item, rather than in accordance with the true linear function.
-The authors accounted for both learning and extrapolation performance with a Bayesian learning model.
-Similar to ALM, the model assumes that generalization occurs as a Gaussian function of the distance between stimuli.
-However, unlike ALM, the Bayesian learning model utilizes more elaborate probabilistic stimulus representations, with a separate Kalman Filter for each shape stimulus.
-
-### Overview Of Present Study
-
-The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task.
-To the best of our knowledge, this research is the first to employ the classic constant vs.
-varied training manipulation, commonly used in the literature studying the benefits of variability, in the context of a uni-dimensional function learning task.
-Across three experiments, we compare constant and varied training conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.
-
-To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM).
-Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to examine the ability of these influential models of function learning to account for both the group level and individual level data.
-
-## Experiment 1
-
-### Methods
-
-*Participants.* A total of 183 participants were initially recruited from Indiana University Introductory Psychology Courses.
-Of these, 27 participants were excluded from further analysis due to meeting the exclusion criteria, resulting in a final sample of 156 participants.
-The exclusion criteria was defined as performance worse (i.e., larger deviations) than the condition average in either the training or testing stage of the experiment.
-The remaining participants were randomly assigned to one of two training conditions: varied training or constant training.
-
-*Task.* The "Hit The Wall" (HTW) visuomotor extrapolation task was programmed in JavaScript, making use of the [phaser.io](https://phaser.io/) game library.
-The HTW task involved launching a projectile such that it would strike the "wall" at the target speed indicated at the top of the screen (see @fig-htw-task).
-The target velocities were given as a range, or band, of acceptable velocity values (e.g., band 800-1000).
-During the training stage, participants received feedback indicating whether they had hit the wall within the target velocity band, or how many units their throw was above or below  the target band.
-Participants were instructed that only the x velocity component of the ball was relevant to the task.
-The y velocity, or the location at which the ball struck the wall, had no influence on the task feedback.
-
-```{r out.width = "60%", echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
-#| label: fig-htw-task
-#| fig-cap: The Hit the wall task.
-Participants launch the blue ball to hit the red wall at the target velocity band indicated at the top of the screen.
-The ball must be released from within the orange square - but the location of release, and the location at which the ball strikes the wall are both irrelevant to the task feedback.
-#| eval: true
-#knitr::include_graphics(here::here("images/2023-04-19-16-20-55.png"))
-knitr::include_graphics(here::here("Assets/figs/htw_task_fig.png"))
-
-```
-
-*Procedure.* All participants completed the task online.
-Participants were provided with a description of the experiment and indicated informed consent.
-@fig-design-e1 illustrates the general procedure.
-Participants completed a total of 90 trials during the training stage.
-In the varied training condition, participants encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
-Participants in the constant training condition trained on only one velocity band (800-1000) - the closest band to what would be the novel extrapolation bands in the testing stage.
-
-Following the training stage, participants proceeded immediately to the testing stage.
-Participants were tested from all six velocity bands, in two separate stages.
-In the novel extrapolation testing stage, participants completed "no-feedback" testing from three novel extrapolation bands (100-300, 350-550, and 600-800), with each band consisting of 15 trials.
-Participants were also tested from the three velocity bands that were trained by the varied condition (800-1000, 1000-1200, and 1200-1400).
-In the constant training condition, two of these bands were novel, while in the varied training condition, all three bands were encountered during training.
-The order in which participants completed the novel-extrapolation and testing-from-3-varied bands was counterbalanced across participants.
-A final training stage presented participants with "feedback" testing for each of the three extrapolation bands (100-300, 350-550, and 600-800).
-
-::: {.content-visible unless-format="markdown"}
-```{dot}
-//| label: fig-design-e1
-//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
-//| fig-responsive: false
-//| echo: false  
-///| eval: !expr out_type 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-
-  // define the global styles of the nodes
-  node [shape = rectangle, style = filled]
-
-  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#00A08A"]
-  data2 [label = " Constant Training \n800-1000", fillcolor = "#FF0000"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-
-  // edge definitions with the node IDs
-  data1 -> Test1
-  data2 -> Test1
-
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-
-  Test2 -> Test3
-}
-```
-:::
-```{r}
-
-# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-#   stringr, here,conflicted, patchwork, knitr)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=2, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e1 <- readRDS(here("data/e1_08-21-23.rds")) 
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-testE1 <- e1 |> filter(expMode2 == "Test")
-nbins=5
-trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
-trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
-```
-
-### Analyses Strategy
-
-All data processing and statistical analyses were performed in R version 4.32 [@rcoreteamLanguageEnvironmentStatistical2020].
-To assess differences between groups, we used Bayesian Mixed Effects Regression.
-Model fitting was performed with the brms package in R [@burknerBrmsPackageBayesian2017], and descriptive stats and tables were extracted with the BayestestR package [@makowskiBayestestRDescribingEffects2019].
-Mixed effects regression enables us to take advantage of partial pooling, simultaneously estimating parameters at the individual and group level.
-Our use of Bayesian, rather than frequentist methods allows us to directly quantify the uncertainty in our parameter estimates, as well as avoid convergence issues common to the frequentist analogues of our mixed models.
-
-Each model was set to run with 4 chains, 5000 iterations per chain, with the first 2500 discarded as warmup chains.
-Rhat values were within an acceptable range, with values \<=1.02 (see appendix for diagnostic plots).
-We used uninformative priors for the fixed effects of the model (condition and velocity band), and weakly informative Student T distributions for the random effects.
-For each model, we report 1) the mean values of the posterior distribution for the parameters of interest, 2) the lower and upper credible intervals (CrI), and the probability of direction value (pd).
-
-::: {#tbl-brms-models}
-| Group Comparison | Code | Data |
-|-----------------|---------------------------------------|-----------------|
-| End of Training Accuracy | `brm(Abs. Deviation ~ condit)` | Final Training Block |
-| Test Accuracy | `brm(Abs. Deviation ~ condit * bandType + (1|id) + (1|bandInt)` | All Testing trials |
-| Band Discrimination | `brm(vx ~ condit * band +(1 + bandInt|id)` | All Testing Trials |
-
-: **Statistical Model Specifications**.
-The specifications for the Bayesian regression models used in the analyses of each of the 3 experiments.
-Comparisons of accuracy use absolute deviation as the dependent variable, while comparisons of discrimination use the raw velocities produced by participants as the dependent variable.
-:::
-\
-
-In each experiment we compare varied and constant conditions in terms of 1) accuracy in the final training block; 2) testing accuracy as a function of  band type (trained vs.
-extrapolation bands); 3) extent of discrimination between all six testing bands.
-We quantified accuracy as the absolute deviation between the response velocity and the nearest boundary of the target  band.
-Thus, when the target band was velocity 600-800, throws of 400, 650, and 900 would result in deviation values of 200, 0, and 100, respectively.
-The degree of discrimination between bands was measured by fitting a linear model predicting the response velocity as a function of the target velocity.
-Participants who reliably discriminated between velocity bands tended to have slope values \~1, while participants who made throws irrespective of the current target band would have slopes \~0.
-
-### Results
-
-```{r}
-#| label: fig-e1-train-dev
-#| fig-cap: Experiment 1 - Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Absolute Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-##| label: tbl-e1-train-dist
-##| tbl-cap: "Experiment 1 - Learning curves. "
-##| output: asis
-
-bmm_e1_train<- trainE1_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e1_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-mtr1 <- as.data.frame(describe_posterior(bmm_e1_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# mtr1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#    kable(booktabs = TRUE)
-
-cdtr1 <- get_coef_details(bmm_e1_train, "conditVaried")
-```
-
-::: {#tbl-e1-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |   106.34 |         95.46 |        117.25 |   1 |
-| conditVaried |    79.64 |         57.92 |        101.63 |   1 |
-
-: **Experiment 1 - End of training performance**.
-Comparing final training block accuracy in the band common to both groups.
-The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive estimate indicates a greater deviation (lower accuracy) for the varied group.
-CrI values indicate 95% credible intervals.
-pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
-{.sm}
-
-:::
-
-\
-
-*Training*.
-@fig-e1-train-dev displays the average deviations across training blocks for the varied group, which trained on three velocity bands, and the constant group, which trained on one velocity band.
-To compare the training conditions at the end of training, we analyzed performance on the 800-1000 velocity band, which both groups trained on.
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation from the target band than the constant group in the final training block, ($\beta$ = `r cdtr1$estimate`, 95% CrI \[`r cdtr1$conf.low`, `r cdtr1$conf.high`\]; pd = `r cdtr1$pd`).
-
-```{r}
-##| label: tbl-e1-bmm-dist
-##| tbl-cap: "E1. Training vs. Extrapolation"
-#| 
-modelFile <- paste0(here::here("data/model_cache/"), "e1_dist_Cond_Type_RF_2")
-bmtd <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE1, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted1 <- as.data.frame(describe_posterior(bmtd, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted1) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-# 
-# r_bandInt_params <- get_variables(bmtd)[grepl("r_id:bandInt", get_variables(bmtd))]
-# posterior_summary(bmtd,variable=r_bandInt_params)
-
-# mted1 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |> kable(booktabs = TRUE)
-cdted1 <- get_coef_details(bmtd, "conditVaried")
-cdted2 <-get_coef_details(bmtd, "bandTypeExtrapolation")
-cdted3 <-get_coef_details(bmtd, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e1-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:------------------------|-----------:|-----------:|-----------:|-----------:|
-| Intercept                          |   152.55 |         70.63 |        229.85 | 1.0 |
-| conditVaried                       |    39.00 |        -21.10 |        100.81 | 0.9 |
-| bandTypeExtrapolation              |    71.51 |         33.24 |        109.60 | 1.0 |
-| conditVaried:bandTypeExtrapolation |    66.46 |         32.76 |         99.36 | 1.0 |
-
-: **Experiment 1 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation bands), and the interaction between the two factors.
-The Intercept represents the baseline condition (constant training & trained bands).
-Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands.
-CrI values indicate 95% credible intervals.
-pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
-{.hover .sm}
-:::
-
-*Testing.* To compare accuracy between groups in the testing stage, we fit a Bayesian mixed effects model predicting deviation from the target band as a function of training condition (varied vs.
-constant) and band type (trained vs.
-extrapolation), with random intercepts for participants and bands.
-The model results are shown in @tbl-e1-bmm-dist.
-The main effect of training condition was not significant ($\beta$ = `r cdted1$estimate`, 95% CrI \[`r cdted1$conf.low`, `r cdted1$conf.high`\]; pd = `r cdted1$pd`).
-The extrapolation testing items had a significantly greater deviation than the training bands ($\beta$ = `r cdted2$estimate`, 95% CrI \[`r cdted2$conf.low`, `r cdted2$conf.high`\]; pd = `r cdted2$pd`).
-Most importantly, the interaction between training condition and band type was significant ($\beta$ = `r cdted3$estimate`, 95% CrI \[`r cdted3$conf.low`, `r cdted3$conf.high`\]; pd = `r cdted3$pd`), As shown in @fig-e1-test-dev,  the varied group had disproportionately larger deviations compared to the constant group in the extrapolation bands.
-
-```{r}
-#| label: fig-e1-test-dev
-#| fig-cap: Experiment 1 Testing Accuracy.
-A) Empirical Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (trained bands vs.
-novel extrapolation bands) on testing accuracy.
-Error bars represent 95% credible intervals.
-#| fig-width: 11
-#| fig-height: 7
-
-pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target Band")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe1ce <- bmtd |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Target Band", x="Band Type")
-
-p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-
-```
-
-```{r}
-##| label: tbl-e1-bmm-vx
-##| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e1_vxBMM) |> kable(booktabs = TRUE)
-
-cd1 <- get_coef_details(e1_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e1_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e1_vxBMM, "conditVaried:bandInt")
-```
-
-\
-
-::: {#tbl-e1-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   408.55 |        327.00 |        490.61 | 1.00 |
-| conditVaried |   164.05 |         45.50 |        278.85 | 1.00 |
-| Band         |     0.71 |          0.62 |          0.80 | 1.00 |
-| condit\*Band |    -0.14 |         -0.26 |         -0.01 | 0.98 |
-
-**Experiment 1 Testing Discrimination**.
-Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
-Varied) and Velocity Band.
-Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
-The interaction between condit and Band indicates the difference between constant and varied slopes.
-CrI values indicate 95% credible intervals.
-pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
-{.hover .sm}
-:::
-
-Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-See @tbl-e1-bmm-vx for the full model results.
-The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\], pd = `r cd1$pd`) suggests that the varied group tends to produce harder throws than the constant group, though this is not, in and of itself, useful for assessing discrimination.
-Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\], pd = `r sc1$pd`).
-Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands.
-The significant negative estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\], pd = `r intCoef1$pd`), indicates that the discrimination was modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition (see @fig-e1-test-vx and @fig-e1-bmm-vx).
-
-```{r}
-#| label: fig-e1-test-vx
-#| fig-cap: Experiment 1. Empirical distribution of velocities produced in the testing stage. Translucent bands with dashed lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 8
-
-testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()
-```
-
-```{r}
-#| label: fig-e1-bmm-vx
-#| fig-cap: Experiment 1 Discrimination.
-A) Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-B) The distribution of slope coefficients for each condition.
-Larger slopes indicate better discrimination between target bands.
-C) Individual participant slopes.
-Error bars represent 95% HDI.
-#| fig-height: 8
-#| fig-width: 11
-
-pe1vce <- e1_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE1$vb), 
-                     limits = c(0, 1400)) + 
-  scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e1_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e1_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e1_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e1_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e1Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den1 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes1 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-     theme(legend.title=element_blank(), 
-           axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-### Experiment 1 Summary
-
-In Experiment 1, we investigated how variability in training influenced participants' ability to learn and extrapolate in a visuomotor task.
-Our findings that training with variable conditions resulted in lower final training performance are consistent with much of the prior research on the influence of training variability [@ravivHowVariabilityShapes2022; @soderstromLearningPerformanceIntegrative2015], and are particularly unsurprising in the present work, given that the constant group received three times the amount of training on the velocity band common to the two conditions.
-
-More importantly, the varied training group exhibited significantly larger deviations from the target velocity bands during the testing phase, particularly for the extrapolation bands that were not encountered by either condition during training.
-
-## Experiment 2
-
-```{r}
-
-# walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
-# walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
-e2 <- readRDS(here("data/e2_08-04-23.rds")) 
-e2Sbjs <- e2 |> group_by(id,condit) |> summarise(n=n())
-testE2 <- e2 |> filter(expMode2 == "Test")
-nbins=5
-trainE2 <-  e2 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE2_max <- trainE2 |> filter(Trial_Bin == nbins, bandInt==600)
-
-# e2 |> group_by(condit, bandOrder) |> summarise(n_distinct(id))
-```
-
-### Methods & Procedure
-
-Initially, 131 participants were recruited.
-After applying the same exclusion procedure as in Experiment 1, 21 participants were excluded, resulting in a final sample of 110 participants who completed the experiment (Varied: 55, Constant: 55).
-The task and procedure of Experiment 2 was identical to Experiment 1, with the exception that the training and testing bands were reversed (see @fig-design-e2).
-The Varied group trained on bands 100-300, 350-550, 600-800,  and the constant group trained on band 600-800.
-Both groups were tested from all six bands.
-
-::: {.content-visible unless-format="markdown"}
-```{dot}
-//| label: fig-design-e2
-//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 7.0
-//| fig-height: 2.2
-//| fig-responsive: false
-//| echo: false 
-//| 
-/////| column: screen-inset-right
-digraph {
-  graph [layout = dot, rankdir = LR]
-  node [shape = rectangle, style = filled]
-  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
-  data2 [label = " Constant Training \n600-800", fillcolor = "#FF0000"]
-  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-  data1 -> Test1
-  data2 -> Test1
-  subgraph cluster {
-    label = "Test Phase \n(Counterbalanced Order)"
-    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
-    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
-    Test1 -> Test2
-  }
-  Test2 -> Test3
-}
-```
-
-:::
-
-### Results
-
-```{r}
-#| label: fig-e2-train-dev
-#| fig-cap: Experiment 2 Training Stage. Deviations from target band across training blocks. Lower values represent greater accuracy. 
-#| eval: TRUE
-p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    facet_wrap(~vb)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Absolute Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
-p1
-```
-
-```{r}
-bmm_e2_train <- trainE2_max %>% 
-  brm(dist ~ condit, 
-      file=here("data/model_cache/e2_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-mtr2 <- as.data.frame(describe_posterior(bmm_e2_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-colnames(mtr2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-
-cdtr2 <- get_coef_details(bmm_e2_train, "conditVaried")
-# mtr2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T) 
-```
-
-::: {#tbl-e2-train-dist}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |  pd |
-|:-------------|---------:|--------------:|--------------:|----:|
-| Intercept    |    91.01 |         80.67 |        101.26 |   1 |
-| conditVaried |    36.15 |         16.35 |         55.67 |   1 |
-
-: **Experiment 2 - End of training performance**.
-The Intercept represents the average of the baseline condition (constant training), and the conditVaried coefficient reflects the difference between the constant and varied groups.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-CrI values indicate 95% credible intervals.
-pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
-{.sm}
-:::
-
-\
-
-*Training*.
-@fig-e2-train-dev presents the deviations across training blocks for both constant and varied training groups.
-We again compared training performance on the band common to both groups (600-800).
-The full model results are shown in Table 1.
-The varied group had a significantly greater deviation than the constant group in the final training block, ( $\beta$ = `r cdtr2$estimate`, 95% CrI \[`r cdtr2$conf.low`, `r cdtr2$conf.high`\]; pd = `r cdtr2$pd`).
-```{r}
-modelFile <- paste0(here::here("data/model_cache/"), "e2_dist_Cond_Type_RF_2")
-bmtd2 <- brm(dist ~ condit * bandType + (1|bandInt) + (1|id), 
-    data=testE2, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted2 <- as.data.frame(describe_posterior(bmtd2, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted2) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted2 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-cd2ted1 <- get_coef_details(bmtd2, "conditVaried")
-cd2ted2 <-get_coef_details(bmtd2, "bandTypeExtrapolation")
-cd2ted3 <-get_coef_details(bmtd2, "conditVaried:bandTypeExtrapolation")
-```
-
-::: {#tbl-e2-bmm-dist}
-
-| Term                               | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-----------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                          |   190.91 |        125.03 |        259.31 | 1.00 |
-| conditVaried                       |   -20.58 |        -72.94 |         33.08 | 0.78 |
-| bandTypeExtrapolation              |    38.09 |         -6.94 |         83.63 | 0.95 |
-| conditVaried:bandTypeExtrapolation |    82.00 |         41.89 |        121.31 | 1.00 |
-
-: **Experiment 2 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-The Intercept represents the baseline condition (constant training & trained bands).
-Larger coefficients indicate larger deviations from the baselines - and a positive interaction coefficient indicates disproportionate deviation for the varied condition on the extrapolation bands.
-CrI values indicate 95% credible intervals.
-pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate).
-{.hover .sm}
-:::
-
-\ \
-
-*Testing Accuracy.* The analysis of testing accuracy examined deviations from the target band as influenced by training condition (Varied vs.
-Constant) and band type (training vs.
-extrapolation bands).
-The results, summarized in @tbl-e2-bmm-dist, reveal no significant main effect of training condition ($\beta$ = `r cd2ted1$estimate`, 95% CrI \[`r cd2ted1$conf.low`, `r cd2ted1$conf.high`\]; pd = `r cd2ted1$pd`).
-However, the interaction between training condition and band type was significant ($\beta$ = `r cd2ted3$estimate`, 95% CrI \[`r cd2ted3$conf.low`, `r cd2ted3$conf.high`\]; pd = `r cd2ted3$pd`), with the varied group showing disproportionately larger deviations compared to the constant group on the extrapolation bands (see @fig-e2-test-dev).
-
-```{r}
-#| label: fig-e2-test-dev
-#| fig-cap: Experiment 2 Testing Accuracy.
-A) Empirical Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (trained bands vs.
-novel extrapolation bands) on testing accuracy.
-Error bars represent 95% credible intervals.
-#| fig-width: 11
-#| fig-height: 7
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe2ce <- bmtd2 |> emmeans( ~condit + bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type")
-
-p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e2-bmm-vx
-##| tbl-cap: "Experiment 2. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e2_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e2_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-#GetModelStats(e2_vxBMM ) |> kable(escape=F,booktabs=T, caption="Fit to all 6 bands")
-
-cd2 <- get_coef_details(e2_vxBMM, "conditVaried")
-sc2 <- get_coef_details(e2_vxBMM, "bandInt")
-intCoef2 <- get_coef_details(e2_vxBMM, "conditVaried:bandInt")
-```
-
-::: {#tbl-e2-bmm-vx}
-
-| Term         | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:-------------|---------:|--------------:|--------------:|-----:|
-| Intercept    |   362.64 |        274.85 |        450.02 | 1.00 |
-| conditVaried |    -8.56 |       -133.97 |        113.98 | 0.55 |
-| Band         |     0.71 |          0.58 |          0.84 | 1.00 |
-| condit\*Band |    -0.06 |         -0.24 |          0.13 | 0.73 |
-
-**Experiment 2 Testing Discrimination**.
-Bayesian Mixed Model Predicting velocity as a function of condition (Constant vs.
-Varied) and Velocity Band.
-Larger coefficients for the Band term reflect a larger slope, or greater sensitivity/discrimination.
-The interaction between condition and Band indicates the difference between constant and varied slopes.
-CrI values indicate 95% credible intervals.
-pd is the probability of direction (the % of the posterior on the same side of 0 as the coefficient estimate) {.hover .sm}
-:::
-
-*Testing Discrimination.* Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant.
-The full model results are shown in @tbl-e2-bmm-vx.
-The overall slope on target velocity band predictor was significantly positive, ($\beta$ = `r sc2$estimate`, 95% CrI \[`r sc2$conf.low`, `r sc2$conf.high`\]; pd= `r sc2$pd`), indicating that participants exhibited discrimination between bands.
-The interaction between slope and condition was not significant, ($\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd= `r intCoef2$pd`), suggesting that the two conditions did not differ in their ability to discriminate between bands (see @fig-e2-test-vx and @fig-e2-bmm-vx).
-
-```{r}
-#| label: fig-e2-test-vx
-#| fig-cap: Experiment 2. Empirical distribution of velocities produced in the testing stage. Translucent bands with dash lines indicate the correct range for each velocity band.  
-#| fig-width: 11
-#| fig-height: 8
-testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()
-
-```
-
-```{r}
-#| label: fig-e2-bmm-vx
-#| fig-cap: Experiment 2 Discrimination.
-A) Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-B) The distribution of slope coefficients for each condition.
-Larger slopes indicate better discrimination.
-C) Individual participant slopes.
-Error bars represent 95% HDI.
-#| fig-height: 8
-#| fig-width: 11
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
-}
-
-pe2vce <- e2_vxBMM |> emmeans( ~condit + bandInt,re_formula=NA, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE2$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e2_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e2_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction <- fixef(e2_vxBMM)[,1]["conditVaried:bandInt"]
-
-re <- data.frame(ranef(e2_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e2Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction*(condit=="Varied"),slope = Estimate + adjust )
-
-pid_den2 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density")
-
-pid_slopes2 <- re |>  mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-      theme(legend.title=element_blank(), 
-        axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_wrap2(~condit,axes="all",scales="free_y")
-
-p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
-p3
-```
-
-### Experiment 2 Summary
-
-Experiment 2 extended the findings of Experiment 1 by examining the effects of training variability on extrapolation performance in a visuomotor function learning task, but with reversed training and testing bands.
-Similar to Experiment 1, the Varied group exhibited poorer performance during training and testing.
-However, unlike experiment 1, the Varied and Constant groups did not show a significant difference in their discrimination between bands.
-
-## Experiment 3
-
-```{r}
-
-e3 <- readRDS(here("data/e3_08-04-23.rds")) |> 
-    mutate(trainCon=case_when(
-    bandOrder=="Original" ~ "800",
-    bandOrder=="Reverse" ~ "600",
-    TRUE ~ NA_character_
-    ), trainCon=as.numeric(trainCon)) 
-e3Sbjs <- e3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
-testE3 <- e3 |> filter(expMode2 == "Test")
-nbins=5
-trainE3 <-  e3 |> filter(expMode2=="Train") |> group_by(id,condit,bandOrder, vb) |> 
-    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
-trainE3_max <- trainE3 |> filter(Trial_Bin == nbins, bandInt==trainCon)
-
-```
-
-In Experiment 3, we sought to further explore the generality of the findings from the first two experiments by modifying the type of feedback provided during training.
-Specifically, we provided ordinal feedback instead of the continuous feedback used in the previous two experiments.
-Ordinal feedback provides learners with directional information about the results of their throw (e.g., above the target, below the target, or hitting the target) rather than precise numerical deviations.
-This form of feedback resembles many real-world learning scenarios, such as a coach instructing an athlete to perform a movement using "more force" or "less force", or a teacher providing letter grades rather than numeric scores.
-Although ordinal feedback provides less detailed information per trial, prior research has shown that less detailed feedback isn't necessarily detrimental to learning.
-For example, @cornwallEffectsCategoricalNumerical2022 manipulated whether participants received categorical (correct or incorrect) vs.
-numerical feedback (reward points ranging from 50-100).
-They found that the categorical condition produced superior learning, which they explained as arising from larger prediction errors.
-Although we do not make specific predictions about the ordinal condition in our study, it serves as a manipulation that might influence the learning process.
-
-### Methods & Procedure
-
-The only adjustment of Experiment 3 is for participants to receive ordinal feedback during training, in contrast to the continuous feedback of the prior experiments.
-After each training throw, participants are informed whether a throw was too soft, too hard, or correct (i.e.
-within the target velocity range).
-All other aspects of the task and design are identical to Experiments 1 and 2.
-We utilized the order of training and testing bands from both of the prior experiments, thus assigning participants to both an order condition (Original or Reverse) and a training condition (Constant or Varied).
-Participants were once again recruited from the online Indiana University Introductory Psychology Course pool.
-Following exclusions, 195 participants were included in the final analysis, n=51 in the Constant-Original condition, n=59 in the Constant-Reverse condition, n=39 in the Varied-Original condition, and n=46 in the Varied-Reverse condition.
-
-### Results
-
-```{r}
-
-bmm_e3_train <- trainE3_max %>% 
-  brm(dist ~ condit*bandOrder, 
-      file=here("data/model_cache/e3_train_deviation"),
-      data = .,
-      iter = 2000,
-      chains = 4,
-      control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mtr3 <- as.data.frame(describe_posterior(bmm_e3_train, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mtr3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mtr3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-cd3tr1 <- get_coef_details(bmm_e3_train, "conditVaried")
-cd3tr2 <-get_coef_details(bmm_e3_train, "bandOrderReverse")
-cd3tr3 <-get_coef_details(bmm_e3_train, "conditVaried:bandOrderReverse")
-```
-
-::: {#tbl-e3-train-dist}
-
-| Term                          | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                     |   121.86 |        109.24 |        134.60 | 1.00 |
-| conditVaried                  |    64.93 |         36.99 |         90.80 | 1.00 |
-| bandOrderReverse              |     1.11 |        -16.02 |         18.16 | 0.55 |
-| conditVaried:bandOrderReverse |   -77.02 |       -114.16 |        -39.61 | 1.00 |
-
-: **Experiment 3 - End of training performance**.
-The Intercept represents the average of the baseline condition (constant training & original band order), the conditVaried coefficient reflects the difference between the constant and varied groups, and the bandOrderReverse coefficient reflects the difference between original and reverse order.
-A larger positive coefficient indicates a greater deviation (lower accuracy) for the varied group.
-The negative value for the interaction between condit and bandOrder indicates that varied condition with reverse order had significantly lower deviations than the varied condition with the original band order  {.sm}
-
-:::
-
-*Training*.
-@fig-e3-train-dev displays the average deviations from the target band across training blocks, and @tbl-e3-train-dist shows the results of the Bayesian regression model predicting the deviation from the common band at the end of training (600-800 for reversed order, and 800-1000 for original order conditions).
-The main effect of training condition is significant, with the varied condition showing larger deviations ( $\beta$ = `r cd3tr1$estimate`, 95% CrI \[`r cd3tr1$conf.low`, `r cd3tr1$conf.high`\]; pd = `r cd3tr1$pd`).
-The main effect of band order is not significant $\beta$ = `r cd3tr2$estimate`, 95% CrI \[`r cd3tr2$conf.low`, `r cd3tr2$conf.high`\]; pd = `r cd3tr2$pd`, however the interaction between training condition and band order is significant, with the varied condition showing greater accuracy in the reverse order condition ( $\beta$ = `r cd3tr3$estimate`, 95% CrI \[`r cd3tr3$conf.low`, `r cd3tr3$conf.high`\]; pd = `r cd3tr3$pd`).
-
-```{r}
-#| label: fig-e3-train-dev
-#| fig-cap: Experiment 3 training. Deviations from target band during training, shown separately for groups trained with the original order (used in E1) and reverse order (used in E2). 
-#| eval: true
-p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
-    stat_summary(geom = "line", fun = mean) +
-    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
-    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
-    scale_x_continuous(breaks = seq(1, nbins + 1)) +
-    theme(legend.title=element_blank()) + 
-    labs(y = "Absolute Deviation", x="Training Block") 
-#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
-p1
-```
-
-```{r}
-#options(brms.backend="cmdstanr",mc.cores=4)
-modelFile <- paste0(here::here("data/model_cache/"), "e3_dist_Cond_Type_RF_2")
-bmtd3 <- brm(dist ~ condit * bandType*bandOrder + (1|bandInt) + (1|id), 
-    data=testE3, file=modelFile,
-    iter=5000,chains=4, control = list(adapt_delta = .94, max_treedepth = 13))
-
-# mted3 <- as.data.frame(describe_posterior(bmtd3, centrality = "Mean"))[, c(1,2,4,5,6)]
-# colnames(mted3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")
-# mted3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(booktabs=TRUE)
-
-#ce_bmtd3 <- plot(conditional_effects(bmtd3),points=FALSE,plot=FALSE)
-#wrap_plots(ce_bmtd3)
-
-#ggsave(here::here("Assets/figs", "e3_cond_effects_dist.png"), wrap_plots(ce_bmtd3), width=11, height=11, bg="white")
-
-cd3ted1 <- get_coef_details(bmtd3, "conditVaried")
-cd3ted2 <-get_coef_details(bmtd3, "bandTypeExtrapolation")
-cd3ted3 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation")
-cd3ted4 <-get_coef_details(bmtd3, "bandOrderReverse")
-cd3ted5 <-get_coef_details(bmtd3, "conditVaried:bandOrderReverse")
-cd3ted6 <-get_coef_details(bmtd3, "bandTypeExtrapolation:bandOrderReverse")
-cd3ted7 <-get_coef_details(bmtd3, "conditVaried:bandTypeExtrapolation:bandOrderReverse")
-
-```
-
-::: {#tbl-e3-bmm-dist}
-| Term                                                | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                                           |   288.65 |        199.45 |        374.07 | 1.00 |
-| conditVaried                                        |   -40.19 |       -104.68 |         23.13 | 0.89 |
-| bandTypeExtrapolation                               |   -23.35 |        -57.28 |         10.35 | 0.92 |
-| bandOrderReverse                                    |   -73.72 |       -136.69 |        -11.07 | 0.99 |
-| **conditVaried:bandTypeExtrapolation**                  |    52.66 |         14.16 |         90.23 | 1.00 |
-| conditVaried:bandOrderReverse                       |   -37.48 |       -123.28 |         49.37 | 0.80 |
-| bandTypeExtrapolation:bandOrderReverse              |    80.69 |         30.01 |        130.93 | 1.00 |
-| conditVaried:bandTypeExtrapolation:bandOrder |    30.42 |        -21.00 |         81.65 | 0.87 |
-
-: **Experiment 3 testing accuracy**.
-Main effects of condition and band type (training vs.
-extrapolation), and the interaction between the two factors.
-The Intercept represents the baseline condition, (constant training,  trained bands & original order), and the remaining coefficients reflect the deviation from that baseline.
-Positive coefficients thus represent worse performance relative to the baseline, and a positive interaction coefficient indicates disproportionate deviation for the varied condition or reverse order condition.
-{.hover .sm}
-:::
-
-*Testing Accuracy.* @tbl-e3-bmm-dist presents the results of the Bayesian mixed effects model predicting absolute deviation from the target band during the testing stage.
-There was no significant main effect of training condition,$\beta$ =  `r cd3ted1$estimate`, 95% CrI \[`r cd3ted1$conf.low`, `r cd3ted1$conf.high`\]; pd = `r cd3ted1$pd`, or band type,$\beta$ =  `r cd3ted2$estimate`, 95% CrI \[`r cd3ted2$conf.low`, `r cd3ted2$conf.high`\]; pd = `r cd3ted2$pd`.
-However the effect of band order was significant, with the reverse order condition showing lower deviations, $\beta$ =  `r cd3ted4$estimate`, 95% CrI \[`r cd3ted4$conf.low`, `r cd3ted4$conf.high`\]; pd = `r cd3ted4$pd`.
-The interaction between training condition and band type was also significant $\beta$ =  `r cd3ted3$estimate`, 95% CrI \[`r cd3ted3$conf.low`, `r cd3ted3$conf.high`\]; pd = `r cd3ted3$pd`, with the varied condition showing disproprionately large deviations on the extrapolation bands compared to the constant group.
-There was also a significant interaction between band type and band order, $\beta$ =  `r cd3ted6$estimate`, 95% CrI \[`r cd3ted6$conf.low`, `r cd3ted6$conf.high`\]; pd = `r cd3ted6$pd`, such that the reverse order condition showed larger deviations on the extrapolation bands.
-No other interactions were significant.
-
-<!-- ::: {#fig-e3-test-condEffect}
-
-![](../Assets/figs/e3_cond_effects_dist.png)
-
-E3.
-A) Deviations from target band during testing without feedback stage.
-B) Estimated marginal means for the interaction between training condition and band type.
-Error bars represent 95% confidence intervals.
-::: -->
-
-```{r}
-#| label: fig-e3-test-dev
-#| fig-cap: Experiment 3 Testing Accuracy.
-A) Empirical Deviations from target band during testing without feedback stage.
-B) Conditional effect of condition (Constant vs.
-Varied) and testing band type (trained bands vs.
-novel extrapolation bands) on testing accuracy.
-Shown separately for groups trained with the original order (used in E1) and reverse order (used in E2).
-Error bars represent 95% credible intervals.
-#| fig-width: 11
-#| fig-height: 8
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3td <- testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
-    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
-    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
-    facet_wrap(~bandOrder,ncol=1) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
-  labs(x="Band", y="Deviation From Target")
-
-pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
-  gather_emmeans_draws() |>
- condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
- facet_wrap(~bandOrder,ncol=1)
-
-p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
-#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
-p2
-```
-
-```{r}
-##| label: tbl-e3-bmm-vx
-##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
-
-e3_vxBMM <- brm(vx ~ condit * bandOrder * bandInt + (1 + bandInt|id),
-                        data=test,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
-                        iter=5000,chains=4,silent=0,
-                        control=list(adapt_delta=0.94, max_treedepth=13))
-
-# m1 <- as.data.frame(describe_posterior(e3_vxBMM, centrality = "Mean"))
-# m2 <- fixef(e3_vxBMM)
-# mp3 <- m1[, c(1,2,4,5,6)]
-# colnames(mp3) <- c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")                       
-# mp3 |> mutate(across(where(is.numeric), \(x) round(x, 2))) |>
-#   tibble::remove_rownames() |> 
-#   mutate(Term = stringr::str_replace_all(Term, "b_bandInt", "Band")) |>
-#   mutate(Term = stringr::str_remove(Term, "b_")) |>
-#   kable(escape=F,booktabs=T)
-
-#wrap_plots(plot(conditional_effects(e3_vxBMM),points=FALSE,plot=FALSE))
-
-cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
-sc1 <- get_coef_details(e3_vxBMM, "bandInt")
-intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
-intCoef2 <- get_coef_details(e3_vxBMM, "bandOrderReverse:bandInt")
-coef3 <- get_coef_details(e3_vxBMM,"conditVaried:bandOrderReverse:bandInt")
-
-```
-
-::: {#tbl-e3-bmm-vx}
-
-| Term                                    | Estimate | 95% CrI Lower | 95% CrI Upper |   pd |
-|:----------------------------------------|---------:|--------------:|--------------:|-----:|
-| Intercept                             |   601.83 |        504.75 |        699.42 | 1.00 |
-| conditVaried                          |    12.18 |       -134.94 |        162.78 | 0.56 |
-| bandOrderReverse                      |    13.03 |       -123.89 |        144.67 | 0.58 |
-| **Band**                                  |     0.49 |          0.36 |          0.62 | 1.00 |
-| **conditVaried:bandOrderReverse**         |  -338.15 |       -541.44 |       -132.58 | 1.00 |
-| conditVaried:Band                     |    -0.04 |         -0.23 |          0.15 | 0.67 |
-| bandOrderReverse:band              |    -0.10 |         -0.27 |          0.08 | 0.86 |
-| **conditVaried:bandOrderReverse:band** |     0.42 |          0.17 |          0.70 | 1.00 |
-
-**Experiment 3 testing discrimination**.
-Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs.
-Varied) and Velocity Band.
-The Intercept represents the baseline condition (constant training & original order), and the Band coefficient represents the  slope for the baseline condition.
-The interaction terms which include condit and Band (e.g., conditVaried:Band & conditVaried:bandOrderReverse:band) respectively indicate how the slopes of the varied-original condition differed from the baseline condition, and how varied-reverse condition differed from the varied-original condition {.hover .sm}
-:::
-
-*Testing Discrimination.* The full results of the discrimination model are presented in @tbl-e3-bmm-dist.
-For the purposes of assessing group differences in discrimination, only the coefficients including the band variable are of interest.
-The baseline effect of band represents the slope coefficient for the constant training - original order condition, this effect was significant $\beta$ = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]; pd = `r sc1$pd`.
-Neither of the two way interactions reached significance, $\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]; pd = `r intCoef1$pd`, $\beta$ = `r intCoef2$estimate`, 95% CrI \[`r intCoef2$conf.low`, `r intCoef2$conf.high`\]; pd = `r intCoef2$pd`.
-However, the three way interaction between training condition, band order, and target band was significant, $\beta$ = `r coef3$estimate`, 95% CrI \[`r coef3$conf.low`, `r coef3$conf.high`\]; pd = `r coef3$pd` - indicating a greater slope for the varied condition trained with reverse order bands.
-This interaction is shown in @fig-e3-test-vx, where the steepness of the best fitting line for the varied-reversed condition is noticeably steeper than the other conditions.
-
-```{r}
-#| label: fig-e3-test-vx
-#| fig-cap: Experiment 3. Empirical distribution of velocities produced in the testing stage. Translucent bands with dash lines indicate the correct range for each velocity band. 
-#| fig-width: 11
-#| fig-height: 10
-##| column: screen-inset-right
-# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
-# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")
-
-testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
-   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-```
-
-{{< pagebreak >}}
-
-```{r}
-#| label: fig-e3-bmm-vx
-#| fig-cap: Experiment 3 Discrimination.
-A) Conditional effect of training condition and Band.
-Ribbons indicate 95% HDI.
-The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.
-B) The distribution of slope coefficients for each condition.
-Larger slopes indicate better discrimination.
-C) Individual participant slopes.
-Error bars represent 95% HDI.
-#| fig-height: 11
-#| fig-width: 11
-# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
-
-condEffects <- function(m,xvar){
-  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
-  stat_dist_pointinterval() + 
-  stat_halfeye(alpha=.1, height=.5) +
-  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
-
-}
-
-pe3vce <- e3_vxBMM |> emmeans( ~condit* bandOrder* bandInt, 
-                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
-  gather_emmeans_draws() |> 
-  condEffects(bandInt) +
-  facet_wrap(~bandOrder,ncol=1) +
-  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
-  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
-                     labels = levels(testE3$vb), 
-                     limits = c(0, 1400)) + 
-scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
-  theme(legend.title=element_blank()) + 
-  labs(y="Velcoity", x="Band")
-
-fe <- fixef(e3_vxBMM)[,1]
-fixed_effect_bandInt <- fixef(e3_vxBMM)[,1]["bandInt"]
-fixed_effect_interaction1 <- fixef(e3_vxBMM)[,1]["conditVaried:bandInt"]
-fixed_effect_interaction2 <- fixef(e3_vxBMM)[,1]["bandOrderReverse:bandInt"]
-fixed_effect_interaction3 <- fixef(e3_vxBMM)[,1]["conditVaried:bandOrderReverse:bandInt"]
-
-re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) |> 
-  rownames_to_column("id") |> 
-  left_join(e3Sbjs,by="id") |>
-  mutate(adjust= fixed_effect_bandInt + fixed_effect_interaction1*(condit=="Varied") + 
-           fixed_effect_interaction2*(bandOrder=="Reverse") + 
-           fixed_effect_interaction3*(condit=="Varied" & bandOrder=="Reverse"),
-  slope = Estimate + adjust )
-
-pid_den3 <- ggplot(re, aes(x = slope, fill = condit)) + 
-  geom_density(alpha=.5) + 
-  xlim(c(min(re$slope)-.3, max(re$slope)+.3))+
-  geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-   theme(legend.title=element_blank()) + 
-  labs(x="Slope Coefficient",y="Density") +
-  facet_wrap(~bandOrder,ncol=1)
-
-pid_slopes3 <- re |>  
-    mutate(id=reorder(id,slope)) |>
-  ggplot(aes(y=id, x=slope,fill=condit,color=condit)) + 
-    geom_pointrange(aes(xmin=Q2.5+adjust, xmax=Q97.5+adjust)) + 
-    geom_vline(xintercept = 1, linetype="dashed",alpha=.5) +
-    theme(legend.title=element_blank(), 
-      axis.text.y = element_text(size=6) ) + 
-    labs(x="Estimated Slope", y="Participant")  + 
-    ggh4x::facet_nested_wrap(bandOrder~condit,axes="all",scales="free_y")
-
-p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
-
-#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
-p3
-
-```
-
-### Experiment 3 Summary
-
-In Experiment 3, we investigated the effects of training condition (constant vs.
-varied) and band type (training vs.
-extrapolation) on participants' accuracy and discrimination during the testing phase.
-Unlike the previous experiments, participants received only ordinal, not continuous valued, feedback during the training phase.
-Additionally, Experiment 3 included both the original order condition from Experiment 1 and the reverse order condition from Experiment 2.
-The results revealed no significant main effects of training condition on testing accuracy, nor was there a significant difference between groups in band discrimination.
-However, we observed a significant three-way interaction for the discrimination analysis, indicating that the varied condition showed a steeper slope coefficient on the reverse order bands compared to the constant condition.
-This result suggests that varied training enhanced participants' ability to discriminate between velocity bands, but only when the band order was reversed during testing.
-
-## Computational Model
-
-```{r}
-####| cache: false
-# pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-#                stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-#                ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-# #walk(c("dplyr"), conflict_prefer_all, quiet = TRUE)
-# #options(brms.backend="cmdstanr",mc.cores=4)
-# options(digits=3, scipen=999, dplyr.summarise.inform=FALSE)
-# walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
-```
-
-```{r}
-###| cache: true
-invisible(list2env(load_sbj_data(), envir = .GlobalEnv))
-invisible(list2env(load_e1(), envir = .GlobalEnv))
-e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
-e2_model <- load_e2()
-e3_model <- load_e3()
-options(contrasts = initial_contrasts)
-
-```
-
-```{r}
-#| label: fig-alm-diagram
-#| fig.cap: The Associative Learning Model (ALM).
-The diagram illustrates the basic structure of the ALM model used in the present work.
-Input nodes are activated as a function of their similarity to the lower-boundary of the target band.
-The generalization parameter, $c$, determines the degree to which nearby input nodes are activated.
-The output nodes are activated as a function of the weighted sum of the input nodes.
-During training, when feedback is provided, network weights connecting the input layer to the output layer are updated via the delta rule.
-alm_plot()
-```
-
-The modeling goal is to implement a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment.
-For this purpose, we will apply the associative learning model (ALM) and the EXAM model of function learning [@deloshExtrapolationSineQua1997].
-ALM is a simple connectionist learning model which closely resembles Kruschke's ALCOVE model [@kruschkeALCOVEExemplarbasedConnectionist1992], with modifications to allow for the generation of continuous responses.
-
-### ALM & Exam
-
-ALM is a localist neural network model [@pageConnectionistModellingPsychology2000a], with each input node corresponding to a particular stimulus, and each output node corresponding to a particular response value.
-The units in the input layer activate as a function of their Gaussian similarity to the input stimulus ( a_i(X) = exp(-c(X - X_i)^2) ).
-So, for example, an input stimulus of value 55 would induce maximal activation of the input unit tuned to 55.
-Depending on the value of the generalization parameter, the nearby units (e.g., 54 and 56; 53 and 57) may also activate to some degree.
-The units in the input layer activate as a function of their similarity to a presented stimulus.
-The input layer is fully connected to the output layer, and the activation for any particular output node is simply the weighted sum of the connection weights between that node and the input activations.
-The network then produces a response by taking the weighted average of the output units (recall that each output unit has a value corresponding to a particular response).
-During training, the network receives feedback which activates each output unit as a function of its distance from the ideal level of activation necessary to produce the correct response.
-The connection weights between input and output units are then updated via the standard delta learning rule, where the magnitude of weight changes are controlled by a learning rate parameter.
-
-The EXAM model is an extension of ALM, with the same learning rule and representational scheme for input and output units.
-EXAM differs from ALM only in its response rule, as it includes a linear extrapolation mechanism for generating novel responses.
-When a novel test stimulus, $X$, is presented, EXAM first identifies the two nearest training stimuli, $X_1$ and $X_2$, that bracket $X$.
-This is done based on the Gaussian activation of input nodes, similar to ALM, but focuses on identifying the closest known points for extrapolation.
-
-**Slope Calculation**: EXAM calculates a local slope, $S$, using the responses associated with $X_1$ and $X_2$. This is computed as:
-
-   $$
-   S = \frac{m(X_{1}) - m(X_{2})}{X_{1} - X_{2}}
-   $$
-
-where $m(X_1)$ and $m(X_2)$ are the output values from ALM corresponding to the $X_1$ and $X_2$ inputs.
-
- **Response Generation**: The response for the novel stimulus $X$ is then extrapolated using the slope $S$:
-
-   $$
-   E[Y|X] = m(X_1) + S \cdot |X - X_1|
-   $$
-
-Here, $m(X_1)$ is the ALM response value from the training data for the stimulus closest to $X$, and $(X - X_1)$ represents the distance between the novel stimulus and the nearest training stimulus.
-
-Although this extrapolation rule departs from a strictly similarity-based generalization mechanism, EXAM is distinct from pure rule-based models in that it remains constrained by the weights learned during training.
-EXAM retrieves the two nearest training inputs, and the  ALM responses associated with those inputs, and computes the slope between these two points.
-The slope is then used to extrapolate the response to the novel test stimulus.
-Because EXAM requires at least two input-output pairs to generate a response, additional assumptions were required in order for it to generate resposnes for the constant group.
-We assumed that participants come to the task with prior knowledge of the origin point (0,0), which can serve as a reference point necessary for the model to generate responses for the constant group.
-This assumption is motivated by previous function learning research [@brownUnderestimationLinearFunction2017], which through a series of manipulations of the y intercept of the underlying function, found that participants consistently demonstrated knowledge of, or a bias towards, the origin point (see @kwantesWhyPeopleUnderestimate2006 for additional evidence of such a bias in function learning tasks).
-
-See @tbl-alm-exam for a full specification of the equations that define ALM and EXAM, and @fig-alm-diagram for a visual representation of the ALM model.
-
-::: column-page-inset-right
-|                    | **ALM Response Generation**                                        |                                                                                               |
-|------------------|-----------------------------|-------------------------|
-| Input Activation   | $a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}$    | Input nodes activate as a function of Gaussian similarity to stimulus                         |
-| Output Activation  | $O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)$                        | Output unit $O_j$ activation is the weighted sum of input activations and association weights |
-| Output Probability | $P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}$                    | The response, $Y_j$ probabilites computed via Luce's choice rule                              |
-| Mean Output        | $m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}$ | Weighted average of probabilities determines response to X                                    |
-|                    | **ALM Learning**                                                   |                                                                                               |
-| Feedback           | $f_j(Z) = e^{-c(Z-Y_j)^2}$                                         | feedback signal Z computed as similarity between ideal response and observed response         |
-| magnitude of error | $\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)$                          | Delta rule to update weights.                                                                 |
-| Update Weights     | $w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}$                              | Updates scaled by learning rate parameter $\eta$.                                             |
-|                    | **EXAM Extrapolation**                                             |                                                                                               |
-| Instance Retrieval | $P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}$                    | Novel test stimulus $X$ activates input nodes $X_i$                                           |
-| Slope Computation  | $S =$ $\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}$                      | Slope value, $S$ computed from nearest training instances                                     |
-| Response           | $E[Y|X_i] = m(X_i) + S \cdot [X - X_i]$                            | Final EXAM response is the ALM response for the nearest training stimulus, $m(X_i)$,  adjusted by local slope $S$.
-|
-
-: ALM & EXAM Equations {#tbl-alm-exam}
-:::
-
-### Model Fitting
-
-To fit ALM and EXAM to our participant data, we employ a similar method to @mcdanielPredictingTransferPerformance2009, wherein we examine the performance of each model after being fit to various subsets of the data.
-Each model was fit to the data with three separate procedures: 1) fit to maximize predictions of the testing data, 2) fit to maximize predictions of both the training and testing data, 3) fit to maximize predictions of the just the training data.
-We refer to this fitting manipulations as "Fit Method" in the tables and figures below.
-It should be emphasized that for all three fit methods, the ALM and EXAM models behave identically - with weights updating only during the training phase.
-Models were fit separately to the data of each individual participant.
-The free parameters for both models are the generalization ($c$) and learning rate ($lr$) parameters.
-Parameter estimation was performed using approximate Bayesian computation (ABC), which we describe in detail below.
-
-::: {.callout}
-
-**{{< fa regular lightbulb >}} Approximate Bayesian Computation**
-
-To estimate the parameters of ALM and EXAM, we used approximate Bayesian computation (ABC), enabling us to obtain an estimate of the posterior distribution of the generalization and learning rate parameters for each individual.
-ABC belongs to the class of simulation-based inference methods [@cranmerFrontierSimulationbasedInference2020], which have begun being used for parameter estimation in cognitive modeling relatively recently [@turnerTutorialApproximateBayesian2012; @turnerBayesianAnalysisSimulationbased2016; @kangasraasioParameterInferenceComputational2019].
-Although they can be applied to any model from which data can be simulated, ABC methods are most useful for complex models that lack an explicit likelihood function (e.g., many neural network models).
-
-The general ABC procedure is to 1) define a prior distribution over model parameters.
-2) sample candidate parameter values, $\theta^*$, from the prior.
-3) Use $\theta^*$ to generate a simulated dataset, $Data_{sim}$.
-4) Compute a measure of discrepancy between the simulated and observed datasets, $discrep$($Data_{sim}$, $Data_{obs}$).
-5) Accept $\theta^*$ if the discrepancy is less than the tolerance threshold, $\epsilon$, otherwise reject $\theta^*$.
-6) Repeat until the desired number of posterior samples are obtained.
-
-Although simple in the abstract, implementations of ABC require researchers to make a number of non-trivial decisions as to i) the discrepancy function between observed and simulated data, ii) whether to compute the discrepancy between trial level data, or a summary statistic of the datasets, iii) the value of the minimum tolerance $\epsilon$ between simulated and observed data.
-For the present work, we follow the guidelines from previously published ABC tutorials [@turnerTutorialApproximateBayesian2012; @farrellComputationalModelingCognition2018].
-For the test stage, we summarized datasets with mean velocity of each band in the observed dataset as $V_{obs}^{(k)}$ and in the simulated dataset as $V_{sim}^{(k)}$, where $k$ represents each of the six velocity bands.
-For computing the discrepancy between datasets in the training stage, we aggregated training trials into three equally sized blocks (separately for each velocity band in the case of the varied group).
-After obtaining the summary statistics of the simulated and observed datasets, the discrepancy was computed as the mean of the absolute difference between simulated and observed datasets (@eq-discrep-test and @eq-discrep-train).
-For the models fit to both training and testing data, discrepancies were computed for both stages, and then averaged together.
-
-::: column-page-inset-left
-$$
-discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
-$$ {#eq-discrep-test}
-
-$$
-\begin{aligned} \\
-discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
-discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
-\end{aligned}
-$$ {#eq-discrep-train}
-:::
-
-The final component of our ABC implementation is the determination of an appropriate value of $\epsilon$.
-The setting of $\epsilon$ exerts strong influence on the approximated posterior distribution.
-Smaller values of $\epsilon$ increase the rejection rate, and improve the fidelity of the approximated posterior, while larger values result in an ABC sampler that simply reproduces the prior distribution.
-Because the individual participants in our dataset differed substantially in terms of the noisiness of their data, we employed an adaptive tolerance setting strategy to tailor $\epsilon$ to each individual.
-The initial value of $\epsilon$ was set to the overall standard deviation of each individual's velocity values.
-Thus, sampled parameter values that generated simulated data within a standard deviation of the observed data were accepted, while worse performing parameters were rejected.
-After every 300 samples the tolerance was allowed to increase only if the current acceptance rate of the algorithm was less than 1%.
-In such cases, the tolerance was shifted towards the average discrepancy of the 5 best samples obtained thus far.
-To ensure the acceptance rate did not become overly permissive, $\epsilon$ was also allowed to decrease every time a sample was accepted into the posterior.
-:::
-
-For each of the 156 participants from Experiment 1, the ABC algorithm was run until 200 samples of parameters were accepted into the posterior distribution.
-Obtaining this number of posterior samples required an average of 205,000 simulation runs per participant.
-Fitting each combination of participant, Model (EXAM & ALM), and fitting method (Test only, Train only, Test & Train) required a total of 192 million simulation runs.
-To facilitate these intensive computational demands, we used the Future Package in R [@bengtssonUnifyingFrameworkParallel2021], allowing us to parallelize computations across a cluster of ten M1 iMacs, each with 8 cores.
-
-### Modelling Results
-
-```{r}
-#| label: tbl-htw-modelError-e1
-#| tbl-cap: "Model errors predicting empirical data from Experiment 1 -  aggregated over the full posterior distribution for each participant.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-post_tabs <- abc_tables(post_dat,post_dat_l)
-train_tab <- abc_train_tables(pd_train,pd_train_l)
-
-out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
-primary=out_type == "html" || out_type == "pdf" || out_type =="latex" || out_type == "docx"
-
-e1_tab <- rbind(post_tabs$agg_pred_full |> mutate("Task Stage"="Test"), train_tab$agg_pred_full |> mutate("Task Stage"="Train")) |> mutate(Fit_Method=rename_fm(Fit_Method))
-
-if (primary) {
-e1_tab %>%
-  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
-  summarize(ME = mean(mean_error), .groups = "drop") %>%
-  pivot_wider(
-    names_from = c(Model, condit),
-    values_from = ME,
-    names_sep = "_"  # Add this line to specify the separator for column names
-  ) %>%
-  rename("Fit Method" = Fit_Method) %>%
-  gt() %>%
-  cols_move_to_start(columns = c(`Task Stage`)) %>%
-  cols_label(
-    `Task Stage` = "Task Stage"
-  ) %>%
-  fmt_number(
-    columns = starts_with("ALM") | starts_with("EXAM"),
-    decimals = 2
-  ) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = cell_fill(color = "white"),
-     locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_style(
-    style = cell_borders(sides = "top", color = "black", weight = px(1)),
-    locations = cells_column_labels()
-  ) %>%
-  tab_options(
-    table.font.size = 12,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    quarto.disable_processing = TRUE,
-    column_labels.padding = 2,
-    data_row.padding = 2
-  )
-} else {
-
-  e1_tab %>%
-  group_by(`Task Stage`, Fit_Method, Model, condit) %>%
-  summarize(ME = mean(mean_error), .groups = "drop") %>%
-  pivot_wider(
-    names_from = c(Model, condit),
-    values_from = ME,
-    names_sep = "_"  # Add this line to specify the separator for column names
-  ) %>%
-  rename("Fit Method" = Fit_Method) %>% kable(escape=F,booktabs=T)
-
-  }
-```
-
-```{r}
-#| label: fig-htw-post-dist
-#| fig-cap: "Posterior Distributions of $c$ and $lr$ parameters.
-Points represent median values, thicker intervals represent 66% credible intervals and thin intervals represent 95% credible intervals around the median.
-Note that the y-axes of the plots for the $c$ parameter are scaled logarithmically."
-#| fig-height: 6
-#| fig-width: 10
-
-c_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=log(c), x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.2)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="c parameter") +
-  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))
-
-lr_post <- post_dat_avg %>%
-    group_by(id, condit, Model, Fit_Method, rank) %>%
-    slice_head(n = 1) |>
-    ggplot(aes(y=lr, x = Fit_Method,col=condit)) + stat_pointinterval(position=position_dodge(.4)) +
-    ggh4x::facet_nested_wrap(~Model) + labs(title="learning rate parameter") +
-  theme(legend.title = element_blank(), legend.position = "none",plot.title=element_text(hjust=.5))
-c_post + lr_post
-```
-
-```{r}
-#| label: fig-htw-resid-pred
-#| fig-cap: "Model residuals for each combination of training condition, fit method, and model.
-Residuals reflect the difference between observed and predicted values.
-Lower values indicate better model fit.
-Note that y-axes are scaled differently between facets.
-A) Residuals predicting each block of the training data.
-B) Residuals predicting each band during the testing stage.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-#| fig-height: 14
-#| fig-width: 11
-
-train_resid <- pd_train |> group_by(id,condit,Model,Fit_Method, Block,x) |> 
-  summarise(y=mean(y), pred=mean(pred), mean_error=abs(y-pred)) |>
-  group_by(id,condit,Model,Fit_Method,Block) |>
-  summarise(mean_error=mean(mean_error)) |>
-  ggplot(aes(x=interaction(Block,Model), y = mean_error, fill=factor(Block))) + 
-  stat_bar + 
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, scales="free",ncol=2) +
-   scale_x_discrete(guide = "axis_nested") +
-  scale_fill_manual(values=c("gray10","gray50","gray92"))+
-  labs(title="Model Residual Errors - Training Stage", y="RMSE", x= "Model",fill="Training Block") +
-  theme(legend.position="top")
-
-test_resid <-  post_dat |> 
-   group_by(id,condit,x,Model,Fit_Method,bandType) |>
-    summarise(y=mean(y), pred=mean(pred), error=abs(y-pred)) |> 
-  mutate(vbLab = factor(paste0(x,"-",x+200))) |>
-  ggplot(aes(x = Model, y = abs(error), fill=vbLab,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-  #scale_fill_manual(values=wes_palette("AsteroidCity2"))+
-  scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-  ggh4x::facet_nested_wrap(rename_fm(Fit_Method)~condit, axes = "all",ncol=2,scale="free") +
-  labs(title="Model Residual Errors - Testing Stage",y="RMSE", x="Velocity Band")
-
-(train_resid / test_resid) +
-  #plot_layout(heights=c(1,1.5)) & 
-  plot_annotation(tag_levels = list(c('A','B')),tag_suffix = ') ') 
-```
-
-The posterior distributions of the $c$ and $lr$ parameters are shown @fig-htw-post-dist, and model predictions are shown alongside the empirical data in @fig-cm-vx-pat.
-There were substantial individual differences in the posteriors of both parameters, with the within-group individual differences generally swamped any between-group or between-model differences.
-The magnitude of these individual differences remains even if we consider only the single best parameter set for each subject.
-
-We used the posterior distribution of $c$ and $lr$ parameters to generate a posterior predictive distribution of the observed data for each participant, which then allows us to compare the empirical data to the full range of predictions from each model.
-Aggregated residuals are displayed in @fig-htw-resid-pred.
-The pattern of training stage residual errors are unsurprising across the combinations of models and fitting method .
-Differences in training performance between ALM and EXAM  are generally minor (the two models have identical learning mechanisms).
-The differences in the magnitude of residuals across the three fitting methods are also straightforward, with massive errors for the 'fit to Test Only' model, and the smallest errors for the 'fit to train only' models.
-It is also noteworthy that the residual errors are generally larger for the first block of training, which is likely due to the initial values of the ALM weights being unconstrained by whatever initial biases participants tend to bring to the task.
-Future work may explore the ability of the models to capture more fine grained aspects of the learning trajectories.
-However for the present purposes, our primary interest is in the ability of ALM and EXAM to account for the testing patterns while being constrained, or not constrained, by the training data.
-All subsequent analyses and discussion will thus focus on the testing stage.
-
-The residuals of the model predictions for the testing stage (@fig-htw-resid-pred) show an unsurprising pattern across fitting methods - with models fit only to the test data showing the best performance, followed by models fit to both training and test data, and with models fit only to the training data showing the worst performance (note that Y-axes are scaled different between plots).
-Although EXAM tends to perform better for both Constant and Varied participants (see also @fig-ee-e1), the relative advantage of EXAM is generally larger for the Constant group - a pattern consistent across all three fitting methods.
-The primary predictive difference between ALM and EXAM is made clear in @fig-cm-vx-pat, which directly compares the observed data against the posterior predictive distributions for both models.
-Regardless of how the models are fit, only EXAM can capture the pattern where participants are able to discriminate all 6 target bands.
-
-```{r}
-#| label: fig-cm-vx-pat
-#| fig-cap: "Empirical data and Model predictions for mean velocity across target bands.
-Fitting methods (Test Only, Test & Train, Train Only) - are separated across rows, and Training Condition (Constant vs.
-Varied) are separated by columns.
-Each facet contains the predictions of ALM and EXAM, alongside the observed data."
-#| fig-height: 10
-#| fig-width: 10
-
-post_dat_l |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> 
- #left_join(testAvgE1, by=join_by(id,condit,x==bandInt)) |>
- ggplot(aes(x=Resp,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar + 
-    facet_wrap(~rename_fm(Fit_Method)+condit, ncol=2,strip.position = "top", scales = "free_x") +
-        scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .5), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-         strip.background = element_blank(),
-         strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(10,0,0,0), "pt")) + 
-         labs(title="Model Predictions - Experiment 1 Data", y="Vx")
-```
-
-```{r}
-#| label: fig-ee-e1
-#| fig-cap: "A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied).
-Lower values on the y axis indicate better model fit.
-D) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs.
-EXAM for the varied group; 3) ALM fits between constant and varied.
-Negative error differences indicate that the term on the left side (e.g., EXAM Constant) tended to have smaller model residuals."
-#| fig-height: 8
-#| fig-width: 10
-
-pacman::p_load(dplyr,purrr,tidyr,ggplot2, data.table, here, patchwork, conflicted, 
-               stringr,future,furrr, knitr, reactable,ggstance, htmltools,
-               ggdist,ggh4x,brms,tidybayes,emmeans,bayestestR, gt)
-
-pdl <- post_dat_l |> rename("bandInt"=x) |> left_join(testAvgE1,by=c("id","condit","bandInt")) |> 
-  filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-# aerror is model error, which is predicted by Model(ALM vs. EXAM) & condit (Constant vs. Varied)
-e1_ee_brm_ae <- brm(data=pdl,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e1_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bct_e1 <- as.data.frame(bayestestR::describe_posterior(e1_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p1 <- plot(conditional_effects(e1_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e1_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-#p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-
-# plot_custom_effects <- function(model) {
-#   # Extract posterior samples for fixed effects
-#   post_samples <- posterior_samples(model, pars = c("b_Intercept", "b_ModelEXAM", "b_conditVaried", "b_ModelEXAM:conditVaried"))
-
-#   # Calculate conditional effects
-#   post_samples <- post_samples %>%
-#     mutate(
-#       ALM_Constant = b_Intercept,
-#       EXAM_Constant = b_Intercept + b_ModelEXAM,
-#       ALM_Varied = b_Intercept + b_conditVaried,
-#       EXAM_Varied = b_Intercept + b_ModelEXAM + b_conditVaried + `b_ModelEXAM:conditVaried`
-#     )
-
-#   # Reshape data for plotting
-#   plot_data <- post_samples %>%
-#     select(ALM_Constant, EXAM_Constant, ALM_Varied, EXAM_Varied) %>%
-#     pivot_longer(everything(), names_to = "Condition", values_to = "Estimate") %>%
-#     separate(Condition, into = c("Model", "Condit"), sep = "_")
-
-#   # Plot conditional effects
-#   ggplot(plot_data, aes(x = Model, y = Estimate, color = Condit)) +
-#     geom_boxplot() +
-#     theme_minimal() +
-#     labs(x = "Model", y = "Estimate", color = "Condition")
-# }
-# p_ce_1 <- plot_custom_effects(e1_ee_brm_ae)
-
-bm1 <- get_coef_details(e1_ee_brm_ae, "conditVaried")
-bm2 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM")
-bm3 <- get_coef_details(e1_ee_brm_ae, "ModelEXAM:conditVaried")
-
-posterior_estimates <- as.data.frame(e1_ee_brm_ae) %>%
-  select(starts_with("b_")) %>%
-  setNames(c("Intercept", "ModelEXAM", "conditVaried", "ModelEXAM_conditVaried"))
-
-constant_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM
-varied_EXAM <- posterior_estimates$Intercept + posterior_estimates$ModelEXAM + posterior_estimates$conditVaried + posterior_estimates$ModelEXAM_conditVaried
-comparison_EXAM <- constant_EXAM - varied_EXAM
-summary_EXAM <- bayestestR::describe_posterior(comparison_EXAM, centrality = "Mean")
-
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NULL)
-# e1_ee_brm_ae |> emmeans(pairwise ~ Model * condit, re_formula=NA)
-
-# full set of Model x condit contrasts
-# ALM - EXAM
-# btw_model <- e1_ee_brm_ae |> emmeans(pairwise~ Model | condit, re_formula=NULL)  |> 
-#   pluck("contrasts") |> 
-#   gather_emmeans_draws() |> 
-#   group_by(contrast,.draw,condit) |> summarise(value=mean(.value), n=n())
-
-# btw_model |> ggplot(aes(x=value,y=contrast,fill=condit)) +stat_halfeye()
-
-# Constant - Varied
-# emm_condit <- e1_ee_brm_ae |> emmeans(~ condit | Model, re_formula = NULL)
-# btw_con <- emm_condit |>  pairs() |> gather_emmeans_draws() |> 
-#   group_by(contrast,.draw, Model) |> summarise(value=mean(.value), n=n()) 
-# # btw_con |> ggplot(aes(x=value,y=Model,fill=Model)) +stat_halfeye()
-
-p_em_1 <- e1_ee_brm_ae |> emmeans(pairwise~ Model*condit, re_formula=NA)  |> 
-  pluck("contrasts") |>
-  gather_emmeans_draws() |> 
-  group_by(contrast,.draw) |> summarise(value=mean(.value), n=n()) |> 
-  filter(!(contrast %in% c("ALM Constant - EXAM Constant","ALM Constant - EXAM Varied","ALM Varied - EXAM Varied ", "EXAM Constant - ALM Varied" ))) |> 
-  ggplot(aes(x=value,y=contrast,fill=contrast)) +stat_halfeye() + labs(x="Model Error Difference",y="Contrast") + theme(legend.position="none")
-
-#p_ce_1 / p_em_1
-
-(p1 + p2+ p3) /p_em_1 + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-```
-
-To quantitatively assess the differences in performance between models, we fit a Bayesian regression model predicting the errors of the posterior predictions of each model as a function of the Model (ALM vs.
-EXAM) and training condition (Constant vs.
-Varied).
-
-Model errors were significantly lower for EXAM  ($\beta$ = `r bm1$estimate`, 95% CrI \[`r bm1$conf.low`, `r bm1$conf.high`\], pd = `r bm1$pd`)  than ALM.
-There was also a significant interaction between Model and Condition ($\beta$ = `r bm3$estimate`, 95% CrI \[`r bm3$conf.low`, `r bm3$conf.high`\], pd = `r bm3$pd`), indicating that the advantage of EXAM over ALM was significantly greater for the constant group.
-To assess whether EXAM predicts performance significantly better for Constant than for Varied subjects, we calculated the difference in model error between the Constant and Varied conditions specifically for EXAM.
-The results indicated that the model error for EXAM was significantly lower in the Constant condition compared to the Varied condition, with a mean difference of `r summary_EXAM$Mean` (95% CrI \[`r summary_EXAM$CI_low`, `r summary_EXAM$CI_high`\], pd = `r summary_EXAM$pd`).
-
-```{r}
-#| label: tbl-htw-modelError-e23
-#| tbl-cap: "Models errors predicting empirical data -  aggregated over all participants, posterior parameter values,  and velocity bands.
-Note that Fit Method refers to the subset of the data that the model was trained on, while Task Stage refers to the subset of the data that the model was evaluated on."
-
-post_tabs2 <- abc_tables(e2_model$post_dat,e2_model$post_dat_l)
-train_tab2 <- abc_train_tables(e2_model$pd_train,e2_model$pd_train_l)
-
-pdl2 <- e2_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e2_tab <- rbind(post_tabs2$agg_pred_full |>
- mutate("Task Stage"="Test"), train_tab2$agg_pred_full |> 
- mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-post_tabs3 <- abc_tables(e3_model$post_dat,e3_model$post_dat_l)
-train_tab3 <- abc_train_tables(e3_model$pd_train,e3_model$pd_train_l)
-
-pdl3 <- e3_model$post_dat_l |> rename("bandInt"=x) |> filter(rank<=1,Fit_Method=="Test_Train", !(Resp=="Observed")) |> mutate(aerror = abs(error))
-
-e3_tab <- rbind(post_tabs3$agg_pred_full |> 
-  mutate("Task Stage"="Test"), train_tab3$agg_pred_full |> mutate("Task Stage"="Train")) |> 
-  mutate(Fit_Method=rename_fm(Fit_Method))
-
-e23_tab <- rbind(e2_tab |> mutate(Exp="E2"), e3_tab |> mutate(Exp="E3"))
-
-out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
-primary=out_type == "html" || out_type == "pdf" || out_type =="latex" || out_type == "docx"
-
-if (primary) {
-gt_table <- e23_tab %>%
-  pivot_wider(
-    names_from = c(Exp, Model, condit),
-    values_from = mean_error,
-    names_glue = "{Exp}_{Model}_{condit}"
-  ) %>%
-  arrange(Fit_Method, `Task Stage`) %>%
-  gt() %>%
-  cols_move_to_start(columns = `Task Stage`) %>%
-  cols_label(`Task Stage` = "Task Stage") %>%
-  fmt_number(columns = matches("E2|E3"), decimals = 1) %>%
-  tab_spanner_delim(delim = "_") %>%
-  tab_style(
-    style = list(
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(columns = everything(), rows = everything())
-  ) %>%
-  tab_options(
-    table.font.size = 12,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    quarto.disable_processing = TRUE,
-    column_labels.padding = 2,
-    data_row.padding = 2
-  )
-gt_table
-} else {
-  e23_tab %>%
-  pivot_wider(
-    names_from = c(Exp, Model, condit),
-    values_from = mean_error,
-    names_glue = "{Exp}_{Model}_{condit}"
-  ) %>%
-  arrange(Fit_Method, `Task Stage`) %>%
-  kable(escape=F,booktabs=T)
-}
-```
-
-```{r}
-#| label: fig-cm-vx-pat-e2-e3
-#| fig-height: 8
-#| fig-width: 10
-#| fig-cap: "Empirical data and Model predictions from Experiment 2 and 3 for the testing stage.
-Observed data is shown on the right.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-
-rbind(e2_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb) |> 
- summarize(vx=median(val)) |> mutate(Exp="E2",bandOrder="Reverse"), 
- e3_model$post_dat_l |> filter( Fit_Method=="Test_Train") |> 
-  group_by(id,condit, Fit_Method,Resp,bandType,x,vb,bandOrder) |>
-  summarize(vx=median(val)) |> mutate(Exp="E3")) |>
-  ggplot( aes(x=condit,y=vx, fill=vb,col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) +
-  stat_bar + 
-    facet_nested_wrap(~Exp+bandOrder+Resp, strip.position = "top", scales = "free_x") +
-    scale_color_manual(values = c("black" = "black"), guide = "none") +
-  scale_size_manual(values = c("black" = .7), guide = "none") +
-    theme(panel.spacing = unit(0, "lines"), 
-        #  strip.background = element_blank(),
-        #  strip.placement = "outside",
-         legend.position = "none",plot.title = element_text(hjust=.50),
-         axis.title.x = element_blank(),
-         plot.margin = unit(c(20,0,0,0), "pt")) + 
-         labs(title="Model Predictions Experiment 2 & 3", y="vx")
-```
-
-{{< pagebreak >}}
-
-\scriptsize
-
-```{r}
-#| label: tbl-htw-ee-e23
-#| tbl-cap: "Results of Bayesian Regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and the interaction between Model and Condition.
-The values represent the estimated coefficient for each term, with 95% credible intervals in brackets.
-The intercept reflects the baseline of ALM and Constant.
-The other estimates indicate deviations from the baseline for the EXAM mode and varied condition.
-Lower values indicate better model fit."
-
-e2_ee_brm_ae <- brm(data=pdl2,
-  aerror ~  Model * condit + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e2_ae_modelCond_RFint.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e2 <- get_coef_details(e2_ee_brm_ae, "conditVaried")
-bm2_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM")
-bm3_e2 <- get_coef_details(e2_ee_brm_ae, "ModelEXAM:conditVaried")
-
-bct_e2 <- as.data.frame(bayestestR::describe_posterior(e2_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) # %>% kable(booktabs = TRUE)
-
-e3_ee_brm_ae <- brm(data=pdl3,
-  aerror ~  Model * condit*bandOrder + (1+bandInt|id), 
-  file = paste0(here("data/model_cache/e3_ae_modelCondBo_RFint2.rds")),
-  chains=4,silent=1, iter=2000, control=list(adapt_delta=0.92, max_treedepth=11))
-
-bm1_e3 <- get_coef_details(e3_ee_brm_ae, "conditVaried")
-bm2_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM")
-bm3_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried")
-bm4_e3  <- get_coef_details(e3_ee_brm_ae, "ModelEXAM:conditVaried:bandOrderReverse")
-
-bct_e3  <- as.data.frame(bayestestR::describe_posterior(e3_ee_brm_ae, centrality = "Mean")) %>%
-  select(1,2,4,5,6) %>%
-  setNames(c("Term", "Estimate","95% CrI Lower", "95% CrI Upper", "pd")) %>%
-  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
-  tibble::remove_rownames() %>%
-  mutate(Term = stringr::str_remove(Term, "b_")) #%>% kable(booktabs = TRUE)
-
-bct <- rbind(bct_e1 |> mutate(exp="Exp 1"),bct_e2 |> 
-               mutate(exp= "Exp 2"),bct_e3 |> mutate(exp="Exp 3")) |> 
-  relocate(exp, .before=Term)
-
-out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
-primary=out_type == "html" || out_type == "pdf" || out_type =="latex" || out_type == "docx"
-
-if (primary) {
-bct_table <- bct %>%
-  mutate(
-    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
-    pd = round(pd, 2)
-  ) %>%
-  gt() %>%
-  # tab_header(
-  #   title = "Bayesian Model Results",
-  #   subtitle = "Estimates and Credible Intervals for Each Term Across Experiments"
-  # ) %>%
-  cols_label(
-    exp = "Experiment",
-    Term = "Term",
-    Estimate = "Estimate",
-    `95% CrI Lower` = "95% CrI Lower",
-    `95% CrI Upper` = "95% CrI Upper",
-    pd = "pd"
-  ) %>%
-  fmt_number(
-    columns = c(Estimate, `95% CrI Lower`, `95% CrI Upper`),
-    decimals = 1
-  ) %>%
-  fmt_number(
-    columns = pd,
-    decimals = 2
-  ) %>%
-  tab_spanner(
-    label = "Credible Interval",
-    columns = c(`95% CrI Lower`, `95% CrI Upper`)
-  ) %>%
-  tab_style(
-    style = list(
-      #cell_fill(color = "lightgray"),
-      cell_text(weight = "bold"), 
-      cell_fill(color = "white"),
-      cell_borders(sides = "top", color = "black", weight = px(1))
-    ),
-    locations = cells_body(
-      columns = c(Estimate, pd),
-      rows = Term=="ModelEXAM:conditVaried"
-    )
-  ) %>%
-   tab_row_group(
-    label = "Experiment 3",
-    rows = exp == "Exp 3"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 2",
-    rows = exp == "Exp 2"
-  ) %>%
-  tab_row_group(
-    label = "Experiment 1",
-    rows = exp == "Exp 1"
-  ) %>%
-  tab_options(
-    table.font.size = 12,
-    heading.title.font.size = 14,
-    heading.subtitle.font.size = 12,
-    quarto.disable_processing = TRUE,
-    column_labels.padding = 2,
-    data_row.padding = 2
-    #row_group.background.color = "gray95"
-  )
-bct_table
-} else {
-  bct %>%
-  mutate(
-    across(c(Estimate, `95% CrI Lower`, `95% CrI Upper`), ~ round(., 2)),
-    pd = round(pd, 2)
-  ) %>% kable(booktabs = TRUE)
-
-}
-
-```
-
-\normalsize
-
-*Model Fits to Experiment 2 and 3.*  Data from Experiments 2 and 3 were fit to ALM and EXAM in the same manner as Experiment 1.
-For brevity, we only plot and discuss the results of the "fit to training and testing data" models - results from the other fitting methods can be found in the appendix.
-The model fitting results for Experiments 2 and 3 closely mirrored those observed in Experiment 1.
-The Bayesian regression models predicting model error as a function of Model (ALM vs.
-EXAM), Condition (Constant vs.
-Varied), and their interaction (see @tbl-htw-ee-e23) revealed a consistent main effect of Model across all three experiments.
-The negative coefficients for the ModelEXAM term (Exp 2: $\beta$ = `r bm1_e2$estimate`, 95% CrI `r bm1_e2$conf.low`, `r bm1_e2$conf.high`, pd = `r bm1_e2$pd`; Exp 3: $\beta$ = `r bm1_e3$estimate`, 95% CrI `r bm1_e3$conf.low`, `r bm1_e3$conf.high`, pd = `r bm1_e3$pd`) indicate that EXAM outperformed ALM in both experiments.
-Furthermore, the interaction between Model and Condition was significant in both Experiment 2 ($\beta$ = `r bm3_e2$estimate`, 95% CrI `r bm3_e2$conf.low`, `r bm3_e2$conf.high`, pd = `r bm3_e2$pd`) and Experiment 3 ($\beta$ = `r bm3_e3$estimate`, 95% CrI `r bm3_e3$conf.low`, `r bm3_e3$conf.high`, pd = `r bm3_e3$pd`), suggesting that the superiority of EXAM over ALM was more pronounced for the Constant group compared to the Varied group, as was the case in Experiment 1.
-Recall that Experiment 3 included participants in both the original and reverse order conditions - and that this manipulation interacted with the effect of training condition.
-We thus also controlled for band order in our Bayesian Regression assessing the relative performance of EXAM and ALM in Experiment 3.
-There was a significant three way interaction between Model, Training Condition, and Band Order ($\beta$ = `r bm4_e3$estimate`, 95% CrI `r bm4_e3$conf.low`, `r bm4_e3$conf.high`, pd = `r bm4_e3$pd`), indicating that the relative advantage of EXAM over ALM was only more pronounced in the original order condition, and not the reverse order condition (see @fig-e2_e3_ae).
-
-```{r}
-#| label: fig-e2_e3_ae
-#| fig-cap: "Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs.
-Varied) on Model Error for Experiments 2 and 3 data.
-Experiment 3 also includes a condition for the order of training vs.
-testing bands (original order vs.
-reverse order)."
-#| fig-height: 6
-#| fig-width: 9
-
-#wrap_plots(plot(conditional_effects(e1_ee_brm_ae),points=FALSE,plot=FALSE))
-p1 <- plot(conditional_effects(e2_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error") + labs(title="E2. Model Error")
-p2 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e2_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
-  p_e2 <- (p1 + p2+ p3) 
-# #wrap_plots(plot(conditional_effects(e3_ee_brm_ae),points=FALSE,plot=FALSE))
-
-p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
-                         effects = "Model:condit", 
-                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
-     points=FALSE,plot=FALSE)$`Model:condit` + 
-     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
-     theme(legend.position="right") + 
-     scale_color_manual(values=wes_palette("Darjeeling1"))
-
-p1 <- plot(conditional_effects(e3_ee_brm_ae, effects="condit"),points=FALSE, plot=FALSE)$condit + 
-  ggplot2::xlab("Condition") +ylab("Model Error")
-p2 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model"),points=FALSE, plot=FALSE)$Model + 
-  labs(x="Model",y=NULL)
-p3 <- plot(conditional_effects(e3_ee_brm_ae, effects="Model:condit"),points=FALSE, plot=FALSE)$`Model:condit` + 
-  scale_color_manual(values=wes_palette("Darjeeling1")) +
-  labs(x="Model",y=NULL,fill=NULL,col=NULL) + theme(legend.position="right")
-
- p2 <- (p1 + p2+ p3)
- (p_e2 / p_e3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")
-```
-
-*Computational Model Summary*.
-Across all three experiments, the model fits consistently favored the Extrapolation-Association Model (EXAM) over the Associative Learning Model (ALM).
-This preference for EXAM was particularly pronounced for participants in the constant training conditions (note the positive coefficients on ModelEXAM:conditVaried interaction terms @tbl-htw-ee-e23).
-This pattern is clearly illustrated in @fig-htw-best-model, which plots the difference in model errors between ALM and EXAM for each individual participant.
-Both varied and constant conditions have a greater proportion of subjects better fit by EXAM (positive error differences), with the magnitude of EXAM's advantage visibly larger for the constant group.
-
-The superior performance of EXAM, especially for the constant training groups, may initially seem counterintuitive.
-One might assume that exposure to multiple, varied examples would be necessary to extract an abstract rule.
-However, EXAM is not a conventional rule-based model; it does not require the explicit abstraction of a rule.
-Instead, rule-based responses emerge during the retrieval process.
-The constant groups' formation of a single, accurate input-output association, combined with the usefulness of the zero point, seem to have been sufficient for EXAM to capture their performance.
-A potential concern is that the assumption of participants utilizing the zero point essentially transforms the extrapolation problem into an interpolation problem.
-However, this concern is mitigated by the consistency of the results across both the original and reversed order conditions (the testing extrapolation bands fall in between the constant training band and the 0 point in experiment 1, but not in experiment 2).
-
-The fits to the individual participants also reveal a number of interesting cases where the models struggle to capture the data (@fig-htw-indv-pred).
-For example participant 68 exhibits a strong non-monotonicity in the highest velocity band, a pattern which ALM can mimic, but which EXAM cannot capture, given that it enforces a simple linear relationship between target velocity and response.
-Participant 70 (lower right corner of @fig-htw-indv-pred) had a roughly parabolic response pattern in their observed data, a pattern which neither model can properly reproduce, but which causes EXAM to perform particularly poorly.
-
-*Modeling Limitations.* The present work compared models based on their ability to predict the observed data, without employing conventional model fit indices such as the Akaike Information Criterion (AIC) or the Bayesian Information Criterion (BIC).
-These indices, which penalize models based on their number of free parameters, would have been of limited utility in the current case, as both ALM and EXAM have two free parameters.
-However, despite having the same number of free parameters, EXAM could still be considered the more complex model, as it incorporates all the components of ALM plus an additional mechanism for rule-based responding.
-A more comprehensive model comparison approach might involve performing cross-validation with a held-out subset of the data [@mezzadriHoldoutStrategySelecting2022] or penalizing models based on the range of patterns they can produce [@domeGdistanceComparisonModel2023], under the assumption that more constrained models are more impressive when they do adequately fit a given pattern of results.
-
-{{< pagebreak >}}
-
-```{r}
-#| label: fig-htw-best-model
-#| fig-cap: "Difference in model errors for each participant, with models fit to both train and test data. Positive values favor EXAM, while negative values favor ALM." 
-#| fig-height: 12
-#| fig-width: 11
-
-tid1 <- post_dat  |> mutate(Exp="E1",bandOrder="Original") |> select(-pred_dist, -dist) |>
-  rbind(e2_model$post_dat |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat |> mutate(Exp="E3")) |>
-  filter(Fit_Method=="Test_Train") |>
-  group_by(id,condit,Model,Fit_Method,x, Exp) |> 
-    mutate(e2=abs(y-pred)) |> 
-    summarise(y1=median(y), pred1=median(pred),mean_error=abs(y1-pred1)) |>
-    group_by(id,condit,Model,Fit_Method,Exp) |> 
-    summarise(mean_error=mean(mean_error)) |> 
-    arrange(id,condit,Fit_Method) |>
-    round_tibble(1)
-
-best_id <- tid1 |> 
-  group_by(id,condit,Fit_Method) |> 
-  mutate(best=ifelse(mean_error==min(mean_error),1,0))
-
-lowest_error_model <- best_id %>%
-  group_by(id, condit,Fit_Method, Exp) %>%
-  summarise(Best_Model = Model[which.min(mean_error)],
-            Lowest_error = min(mean_error),
-            differential = min(mean_error) - max(mean_error)) %>%
-  ungroup()
-
-error_difference<- best_id %>%
-  select(id, condit, Model,Fit_Method, mean_error) %>%
-  pivot_wider(names_from = Model, values_from = c(mean_error)) %>%
-  mutate(Error_difference = (ALM - EXAM))
-
-full_comparison <- lowest_error_model |> 
-  left_join(error_difference, by=c("id","condit","Fit_Method"))  |> 
-  group_by(condit,Fit_Method,Best_Model) |> 
-  mutate(nGrp=n(), model_rank = nGrp - rank(Error_difference) ) |> 
-  arrange(Fit_Method,-Error_difference)
-
-full_comparison |> 
-  filter(Fit_Method=="Test_Train") |> 
-  ungroup() |>
-  mutate(id = reorder(id, Error_difference)) %>%
-  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
-  geom_col() +
-  #ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
-  ggh4x::facet_nested_wrap(~condit+Exp,scales="free") + 
-  theme(axis.text.y = element_text(size=8)) +
-  labs(fill="Best Model",
-  x="Mean Model Error Difference (ALM - EXAM)",
-  y="Participant")
-
-```
-
-```{r  fig.width=11, fig.height=10}
-#| label: fig-htw-indv-pred
-#| fig-cap: Model predictions alongside observed data for a subset of individual participants.
-A) 3 constant and 3 varied participants fit to both the test and training data.
-B) 3 constant and 3 varied subjects fit to only the trainign data.
-Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands.
-#| fig-height: 7
-#| fig-width: 10
-
-cId_tr <- c(137, 181, 11)
-vId_tr <- c(14, 193, 47)
-cId_tt <- c(11, 93, 35)
-vId_tt <- c(1,14,74)
-cId_new <- c(175, 68, 93, 74)
-# filter(id %in% (filter(bestTestEXAM,group_rank<=9, Fit_Method=="Test")
-
-e1_sbjs <- c(49,68,155, 175,74)
-e3_sbjs <-  c(245, 280, 249)
-e2_sbjs <- c(197, 157, 312, 334)
-cFinal <- c(49, 128,202 )
-vFinal <- c(68,70,245)
-
-indv_post_l <- post_dat_l  |> mutate(Exp="E1",bandOrder="Original") |> select(-signed_dist) |>
-  rbind(e2_model$post_dat_l |> mutate(Exp="E2",bandOrder="Reverse")) |>
-  rbind(e3_model$post_dat_l |> mutate(Exp="E3") |> select(-fb)) |>
-  filter(Fit_Method=="Test_Train", id %in% c(cFinal,vFinal))
-
-testIndv <- indv_post_l |> 
-#filter(id %in% c(cId_tt,vId_tt,cId_new), Fit_Method=="Test_Train") |> 
-   mutate(x=as.factor(x), Resp=as.factor(Resp)) |>
-  group_by(id,condit,Fit_Method,Model,Resp) |>
-   mutate(flab=paste0("Subject: ",id)) |>
-  ggplot(aes(x = Resp, y = val, fill=vb, col=ifelse(bandType=="Trained","black",NA),size=ifelse(bandType=="Trained","black",NA))) + 
-  stat_bar_sd + 
-  ggh4x::facet_nested_wrap(condit~flab, axes = "all",ncol=3) +
-  scale_color_manual(values = c("black" = "black"), guide = FALSE) +
-  scale_size_manual(values = c("black" = .5), guide = FALSE) + 
-  labs(title="Individual Participant fits from Test & Train Fitting Method",
-       y="X Velocity",fill="Target Velocity") +
-   guides(fill = guide_legend(nrow = 1)) + 
-  theme(legend.position = "bottom",axis.title.x = element_blank())
-
-testIndv 
-```
-
-## Project 2 Discussion
-
-Across three experiments, we investigated the impact of training variability on learning and extrapolation in a visuomotor function learning task.
-
-In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition.
-Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training.
-The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.
-
-Experiment 2 extended these findings by reversing the order of the training and testing bands.
-Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases.
-However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.
-
-In Experiment 3, we provided only ordinal feedback  during training, in contrast to the continuous feedback provided in the previous experiments.
-Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied).
-The varied condition showed larger deviations at the end of training, consistent with the previous experiments.
-Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition.
-During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands.
-The reverse order conditions showed smaller deviations compared to the original order conditions.
-Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.
-
-All three of our experiments yielded evidence that varied training conditions produced less learning by the end of training, a pattern consistent with much of the previous research on the influence of training variability [@catalanoDistantTransferCoincident1984a; @wrisbergVariabilityPracticeHypothesis1987; @soderstromLearningPerformanceIntegrative2015].
-The sole exception to this pattern was the reverse order condition in Experiment 3, where the varied group was not significantly worse than the constant group.
-Neither the varied condition trained with the same reverse-order items in Experiment 2, nor the original-order varied condition trained with ordinal feedback in Experiment 3 were able to match the performance of their complementary constant groups by the end of training, suggesting that the relative success of the ordinal-reverse ordered varied group cannot be attributed to item or feedback effects alone.
-
-Our findings also diverge from the two previous studies that cleanly manipulated the variability of training items in a function learning task [@deloshExtrapolationSineQua1997; @vandamMappingShapeVisuomotor2015], although the varied training condition of @vandamMappingShapeVisuomotor2015 also exhibited less learning, neither of these previous studies observed any difference between training conditions in extrapolation to novel items.
-Like @deloshExtrapolationSineQua1997, our participants exhibited above chance extrapolation/discrimination of novel items, however they observed no difference between any of their three training conditions.
-A noteworthy difference between our studies is that @deloshExtrapolationSineQua1997 trained participants with either 8, 20, or 50 unique items (all receiving the same total number of training trials).
-These larger sets of unique items, combined with the fact that participants achieved near ceiling level performance by the end of training, may have made it more difficult to observe any between-group differences of training variation in their study.
-@vandamMappingShapeVisuomotor2015 's variability manipulation was more similar to our own, as they trained participants with either 2 or 5 unique items.
-However, although the mapping between their input stimuli and motor responses was technically linear, the input dimension was more complex than our own, as it was defined by the degree of "spikiness" of the input shape.
-This entirely arbitrary mapping also would have precluded any sensible "0" point, which may partially explain why neither of their training conditions were able to extrapolate linearly in the manner observed in the current study or in @deloshExtrapolationSineQua1997.
-
-To explain our results, we turned to the well established EXAM and ALM models.
-The disproportionate success of EXAM in capturing the performance of participants under the constant training condition suggests that rule-based extrapolation can emerge even from a limited set of training examples.
-This success hinges on the assumption that participants are able to leverage prior knowledge of the zero-point reference [@brownUnderestimationLinearFunction2017; @kwantesWhyPeopleUnderestimate2006].
-The zero-point reference, combined with accurate learning of the single trained velocity band enabled EXAM to capture the extrapolation patterns of the constant participants.
-However, it's important to acknowledge that the ALM model provided a better fit for a subset of participants in each of our three experiment, highlighting the presence of substantial individual differences in generalization patterns.
-
-This finding illustrates the importance of considering task structure when evaluating the effects of training variability on generalization and extrapolation.
-Some tasks, like the one in this study, may permit the use of zero-point knowledge or other prior information, while others may not.
-For example, a zero point may be less relevant in visuomotor tasks with complex rotations [@vandamMappingShapeVisuomotor2015; @rollerVariablePracticeLenses2001], or in complex sports techniques [@northEffectConsistentVaried2019].
-Future research should systematically investigate how different task structures interact with training variability to influence learning outcomes and generalization abilities, taking into account factors such as the availability of prior knowledge, the complexity of the task, and the specific learning mechanisms involved.
-This approach could help reconcile seemingly contradictory findings in the literature and provide more nuanced guidelines for designing effective training protocols across various domains.
-
-*Limitations*
-
-While the present study provides valuable insights into the influence of training variability on visuomotor function learning and extrapolation, there are several limitations that should be flagged. 
-First, although the constant training group never had experience from a velocity band closer to the extrapolation bands than the varied group, they always had three times more trials with the nearest velocity band.
-Such a difference may be an unavoidable consequence of a varied vs.
-constant design which matches the total number of training trials between the two groups.
-However, in order to more carefully tease apart the influence of variability from the influence of frequency/repetition effects, future research could explore alternative designs that maintain the variability manipulation while equating the amount of training on the nearest examples across conditions, such as by increasing the total number of trials for the varied group.
-Another limitation is that the testing stage did not include any interpolation items, i.e.
-the participants were tested only from the training bands they experienced during training, or from extrapolation bands.
-The absence of interpolation testing makes it more difficult to distinguish between the effects of training variability on extrapolation specifically, as opposed to generalization more broadly.
-Of course, the nature of the constant training condition makes interpolation testing impossible to implement, however future studies might compare training regimes that each include at least 2 distinct items, but still differ in the total amount of variability experienced, which would then allow groups to be compared in terms of both interpolation and extrapolation testing.
-Finally, the task employed in the present study consisted of only a linear, positive function.
-Previous work in human function learning has repeatedly shown that such functions are among the easiest to learn, but that humans are nonetheless capable of learning negative, non-linear, or discontinuous functions [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @kalishLearningExtrapolatingPeriodic2013; @busemeyerLearningFunctionalRelations1997].
-It thus remains an open question as to whether the influence of training variability might interact with various components of the to-be-learned function.
-
-# General Discussion
-
-To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).
-
-## Empirical and Modeling Summary
-
-Across both projects, we investigated the influence of training variability on learning and generalization in computerized visuomotor skill learning, and function learning tasks.
-In project 1 (HTT), experiments 1 and 2 demonstrated that varied training led to superior testing performance compared to constant training.
-In Experiment 1, the varied group even outperformed the constant group even when testing from the constant groups trained position.
-In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of training accuracy, accuracy in extrapolation testing,  and, in a subset of the experiments, the varied group showed a diminished ability to discriminate between bands.
-This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.
-
-Both projects also included computational modeling componenents.
-In Project 1, the IGAS model was introduced as a means of addressing the lack of control for similarity between training and testing conditions common to previous work in the "benefits of variability" literature.
-The IGAS model provides a theoretically motivated method of quantifying the similarity between training experience and testing conditions.
-The resulting similarity metric (i.e.
-our 1c-similarity) is shown to be a significant predictor of testing performance on its own, and when added as a covariate to the statistical model used to compare the constant and varied training groups.
-We then showed the group-level effect of training variability on testing performance can be accounted for with the additional assumption that training variability influences the generalization gradient.
-The contribution of the IGAS model was thus twofold:  1) providing a theoretically justifiable method of quantifying/controlling for similarity between training and testing, and 2) demonstrating the viability of a flexible-similarity based generalization account for the empirically observed benefit of variability in our task.
-Although similar approaches have been employed in other domains, both contributions are novel additions to the large body of research assessing the effect of constant vs.
-varied training manipulations in visuomotor skill tasks.
-
-Although theoretically motivated, the IGAS model of Project 1 is best categorized as a descriptive measurement-model.
-Sufficient to account for group differences, but lacking the machinery necessary to provide a full process-level account of how the empirical quantities of interest are generated.
-In contrast, Project 2 (HTW) implemented a more robust computational modeling approach, implementing and comparing full process models (ALM & EXAM), capable of generating predictions for both the learning and testing stages of the experiment.
-ALM and EXAM have been used as models of function learning, cue judgement, and forecasting behavior in numerous studies over the past 25 years [@deloshExtrapolationSineQua1997; @mcdanielPredictingTransferPerformance2009; @brownUnderestimationLinearFunction2017; @kwantesItemOrderMatters2012; @kelleyComparisonModelsLearning2008; @kaneApplicationsBiasVariance2020; @vonhelversenLearningMultiplecueJudgment2010].
-The present work presents the first application of these models to the study of training variability in a visuomotor function learning task.
-We fit both models to individual participant data, using a form of simulation-based Bayesian parameter estimation that allowed us to generate and compare the full posterior predictive distributions of each model.
-EXAM provided the best overall account of the testing data, and the advantage of EXAM over ALM was significantly greater for the constant group.
-Notably, EXAM captured the constant groups' ability to extrapolate linearly to novel velocity bands, despite receiving training from only a single input-output pair.
-This finding suggests that EXAM's linear extrapolation mechanism, combined with the assumption of prior knowledge about the origin point (0, 0), was sufficient to account for the constant groups' accurate extrapolation performance.
-Such findings may offer a preliminary suggestion that experience with a more variable set of training examples  may be detrimental to performance in simple extrapolation tasks.
-
-## Differences between the two Projects
-
-The HTT and HTW tasks differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff for a detailed comparison of the two tasks).
-
-In HTT, the salient perceptual elements of the task (i.e.
-the launching box, target and barrier) are subject to variation (i.e.
-different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target.
-Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen.
-If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability.
-Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g., the color of the wall, or size of the ball), rather than displaying the target velocity numerically.
-
-The HTT and HTW tasks also differed in terms of general task complexity.
-The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released).
-Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output responses are determined by a single input dimension.
-In HTW, the relationship between feedback and optimal behavioral adjustment is also almost perfectly smooth, if participants produce a throw that is 100 units too hard, they'll be told that they were 100 units away from the target band.
-Whereas in HTT, the presence of the barrier in introduces irregularities in the task space.
-Even throws close to the solution space might result in failure, creating a less predictable learning environment.
-
-::: {#tbl-task-diff}
-
-| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
-| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
-| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
-| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome.
-Only x velocity is relevant.
-|
-| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.
-| Simpler: smooth, linear mapping between velocity and feedback.
-|
-| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e.
-salient differences in distance between launching box and target.
-| Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen.
-|
-| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.
-|
-| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.
-| Some potential for learning during no-feedback testing by observing ball trajectory.
-|
-| Training Experience                    | Varied group gets half as much experience on any one position as the constant group.
-| Varied group gets 1/3 as much experience on any one velocity band as the constant group.
-|
-| Testing Structure                               | Random interleaving of trained/transfer testing distances.
-| Blocked structure, separately testing trained vs extrapolation testing bands.
-|
-
-Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
-:::
-
-It is important to note that while both projects utilize computational models, direct comparisons are complicated by the distinct purposes and structures of the models employed in each project.
-The IGAS model of Project 1 serves as a descriptive measurement model, capturing the similarity between training throws and testing conditions.
-In contrast, the ALM and EXAM models of Project 2 are full process models, capable of generating exact predictions for both learning and testing stages.
-The difference is also reflected in the interpretion of the generalization parameter ($c$) across the models of the two projects.
-In IGAS, $c$ moderates the similarity between executed throws and subsequent testing solutions, while in ALM and EXAM, $c$ governs the extent to which the perceived stimuli activate the input layer nodes.
-Despite these differences, insights from ALM/EXAM, particularly the role of zero-point knowledge, may offer potential explanations for the contrasting empirical results.
-Particularly, EXAM's reliance on zero-point knowledge in the simpler HTW task may explain why constant training was more effective in Project 2, while the lack of a clear zero-point reference in the more complex HTT task of Project 1 may have increased the value of varied training.
-This suggests that the benefits of variability depend critically on how task structure interacts with prior knowledge and the learner's capacity to leverage such knowledge for generalization.
-
-Future work could explore extending ALM and EXAM, which have traditionally been applied to one-dimensional function learning tasks, to more complex motor tasks such as HTT.
-The neural network structure of ALM could be adapted to handle 2D input by utilizing a 2D grid of input nodes, allowing the model to learn mappings between 2D throwing velocities and desired outcomes.
-This would allow the model to process the more complex spatial information inherent in tasks like HTT.
-Furthermore, the output layers of ALM/EXAM could be expanded to express more complex motor outputs in addition to velocity, such as the locations of grabbing and releasing the projectile or other parameters defining the unique trajectories produced.
-In addition to allowing the models to be applied to more complex tasks, these modifications could enable researchers to investigate how perceptual similarity (i.e., the similarity of stimuli) and motoric similarity (i.e., the similarity of behavioral actions) may separately and jointly influence learning and generalization.
-
-## Conclusion
-
-In summary, this dissertation provides a comprehensive examination of the effects of training variability on learning and generalization in visuomotor and function learning tasks.
-The contrasting results obtained from the Hit The Target (HTT) and Hit The Wall (HTW) tasks underscore the complexity inherent to the longstanding pedagogical and scientific goal of identifying training manipulations that consistently benefit learning and generalization.
-Moreover, through the development and application of computational models, we provide novel theoretical accounts for both the beneficial and detrimental effects of training variability observed in our experiments.
-These findings highlight the importance of considering task characteristics when designing experiments intended to assess the influence of training interventions, and demonstrate the value of combining empirical and computational modeling approaches to uncover the cognitive mechanisms that support learning and generalization.
-Future research should continue to investigate the complex interplay between task demands, training manipulations, and individual differences, with the goal of optimizing educational and training outcomes across a wide range of domains.
-
-\ \
-
-# Appendix
-
-[Apppendix](https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html) available at https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html
 
@@
 :::
+
+{{< pagebreak >}}
+
+::: {.content-visible when-format="pdf"}
+
+{{< include pre_sections/diss_cv.qmd >}}
+
+:::

### 2024-09-07 Manuscript/pre_sections/diss_cv.qmd
formatting tweaks

\pagenumbering{gobble}

# Curriculum Vitae

## Education {.unnumbered .unlisted}

::: {.content-visible when-format="pdf"}
```{=tex}
\begin{tabular}{p{0.3\textwidth} p{0.7\textwidth}}
2017 - May 2024 & \textbf{Indiana University - Bloomington} \\
& PhD in Psychology and Cognitive Science \\ 
& Dissertation: \textit{The Role of Variability in Learning Generalization: A Computational Modeling Approach}\\
2011 - 2015 & \textbf{University of Wisconsin - Madison} \\
& B.Sc. in Psychology \\
& Thesis: \textit{Short-term mindfulness intervention reduces the negative attentional effects associated with heavy media multitasking} \\
\end{tabular}
```
:::

## Journal Articles and Conference Proceedings {.unnumbered .unlisted}

-   **Gorman**, T. E., & Goldstone, R. L. (2022). An instance-based model account of the benefits of varied practice in visuomotor skill. *Cognitive Psychology*, *137*, 101491.

-   Kattner, F., Cochrane, A., Cox, C. R., **Gorman**, T. E., & Green, C. S. (2017). Perceptual learning generalization from sequential perceptual training as a change in learning rate. *Current Biology*, *27*(6), 840-846.

-   **Gorman**, T.E., & Green, C.S. (2016). Short-term mindfulness intervention reduces the negative attentional effects associated with heavy media multitasking. *Scientific Reports*, *6*.

## Reviews and Book Chapters {.unnumbered .unlisted}

-   **Gorman**, T.E., Gentile, D.A., & Green, C.S. Problem gaming: a short primer (2018). *American Journal of Play*, *10* (3), 309-327

-   **Gorman**, T.E., & Green, C.S. (2017). Young minds on video games. In *Cognitive development in digital contexts*. 121-143. Academic Press.

-   Green, C. S., **Gorman**, T., & Bavelier, D. (2016). Action Video-Game Training and Its Effects on Perception and Attentional Control. In *Cognitive Training* (pp. 107-116). Springer International Publishing.

## Presentations {.unnumbered .unlisted}

-   Half Day Tutorial on Measuring Mindfulness Behaviorally: Onsite/Online Data Col-lection with jsPsych
    -   Cognitive Science Conference – 2018
-   Does interleaving go the distance? Exploring the effect of dissimilarity on interleaved category learning
    -   Math Psych/ICCM 2018
-   Short term mindfulness intervention reduces cognitive deficits in heavy media multi-taskers
    -   Undergraduate Research Symposium – UW-Madison – April 16th, 2015

## Awards {.unnumbered .unlisted}

IU-Bloomington – Development Training Grant – Fall 2019

IU-Bloomington - Steinmetz Summer Research Award - 2018

UW-Madison - Undergraduate Research Scholar Award – 2015

UW-Madison - Hilldale Undergraduate/Faculty Research Fellowship – 2014

## Ad-hoc Reviewer {.unnumbered .unlisted}

Cognitive Science

Journal of Experimental Psychology: General

Journal of Experimental Psychology: Human Perception and Performance

Contemporary Educational Psychology

## Conferences {.unnumbered .unlisted}

Cognitive Science Conference - 2021

Cognitive Science Conference - 2018

Mathematical Psychology & ICCM 2018

Boston Meeting on Methods in Cognitive Training (NSF Sponsored) – May 2017

### 2024-09-07 Manuscript/pre_sections/pre_pdf_full.qmd
formatting tweaks

@@
 \begin{centering}
-\LARGE
-{The Role of Variability in Learning Generalization: A Computational Modeling Approach}
 
-\vspace*{1.5cm}
+{THE ROLE OF VARIABILITY IN LEARNING GENERALIZATION: A COMPUTATIONAL MODELING APPROACH}
 
-\LARGE
+\vspace{5\baselineskip}
+
 {Thomas E. Gorman}
 
-\vspace{16.5cm}
-
-\end{centering}
+\vspace{13.5cm}
 
@@
 Sciences and the Cognitive Science Program, Indiana University
-Indiana University
+Indiana University \\
+September 2024
 
@@
 \pagenumbering{gobble}
+\end{centering}
 
 \newpage
+\pagenumbering{roman}
+\setcounter{page}{2}
+\begin{center}
 
@@
 requirements for the degree of Doctor of Philosophy.
-\vspace{4cm}
+\end{center}
+\vspace{2cm}
+\
+Doctoral Committee
+\vspace{1cm}
+
+\begin{flushright}
+\underline{\hspace{5cm}} \\
+Robert L. Goldstone, Ph.D.
+\vspace{2cm}
+
+\underline{\hspace{5cm}} \\
+Robert M. Nosofsky, Ph.D.
+\vspace{2cm}
+
+\underline{\hspace{5cm}} \\
+Peter M. Todd, Ph.D.
+\vspace{2cm}
+
+\underline{\hspace{5cm}} \\
+Michael N. Jones, Ph.D.
+\end{flushright}
 
 \
-\_____________________________  Robert L. Goldstone, PhD
-\vspace{2.5cm}
-\
-\
-\_____________________________  Robert Nosofsky, PhD
-\vspace{2.5cm}
-\
-\_____________________________  Peter Todd, PhD
-\vspace{2.5cm}
-\
-\_____________________________  Mike Jones, PhD
+May 28th, 2024
 

### 2024-10-11 Manuscript/pre_sections/pre_pdf_full.qmd
cv additions and re-render

@@
 
-\vspace{13.5cm}
+\vspace{10.5cm}
 
-Submitted to the faculty of the University Graduate School in partial fulfillment of the
-requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
-Sciences and the Cognitive Science Program, Indiana University
+Submitted to the faculty of the University Graduate School \\
+in partial fulfillment of the requirements \\
+for the degree \\
+Doctor of Philosophy \\
+in the Cognitive Science Program and \\
+Department of Psychological and Brain Sciences, \\
 Indiana University \\
@@
 \end{center}
-\vspace{2cm}
+\vspace{1cm}
 \

### 2024-10-12 Manuscript/manuscript.qmd
cv additions and re-render
few new references, and a re-render with the intro figure.

@@
 
-{{< include pre_sections/pre_pdf.qmd >}}
+{{< include pre_sections/pre_pdf_full.qmd >}}
+{{< include pre_sections/acknowledgements.qmd >}}
+{{< include pre_sections/abstract.qmd >}}
 
@@
 {{< include pre_sections/pre_docx.qmd >}}
+{{< include pre_sections/acknowledgements.qmd >}}
+{{< include pre_sections/abstract.qmd >}}
 :::
@@
 
-Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
-See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
+Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], pattern and anagram completion tasks [@goodeSuperiorityVariableRepeated2008; @zhangHighVariabilityLearning2024], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019; @ramAnticipatedVariabilityIncreases2024], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015], the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023], simple motor learning [@braunMotorTaskVariation2009; @velazquez-vargasRoleTrainingVariability2024; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
+See @czyzVariabilityPracticeInformation2021 and @ravivHowVariabilityShapes2022 for more detailed reviews.
 
@@
 Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task.
-The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet.
+The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet (see @fig-ex-design1).
 Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial.
@@
 However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+
+```{r}
+#| label: fig-ex-design1
+#| fig-width: 10
+#| fig-height: 6
+#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design.
+The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet).
+Both groups were tested from a distance of 3 feet.
+The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
+#| cache: false
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
+  ggh4x,htmltools,future,furrr,ez)
+
+create_data <- function(varied_train, constant_train, both_test) {
+  varied_labels <- "Varied-Train"
+  constant_labels <- "Constant-Train"
+  test_labels <- "Testing"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.55, length(varied_train)), rep(0.75, length(constant_train)), rep(0.4, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.55, 0.75, 0.4),
+    yend = c(0.55, 0.75, 0.4)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test) {
+  data <- create_data(varied_train, constant_train, both_test)
+  segments <- create_segments(data)
+
+  # Variables for Training segment position
+  train_x <- min(data$x) - .5
+  train_y_start <- 0.5
+  train_y_end <- 0.8
+  train_text_y <- 0.75
+
+  # Variables for Testing segment position
+  test_x <- min(data$x) - .5
+  test_y_start <- 0.35
+  test_y_end <- 0.45
+  test_text_y <- 0.48
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4.5, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
+    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
+    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0.3, 1) +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+kerr_booth_1978 <- create_plot(varied_train = c(2, 4), constant_train = c(3), both_test = c(3))
+kerr_booth_1978
+```
 
@@
 
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
-  ggh4x,htmltools,future,furrr,ez)
 #options(brms.backend="cmdstanr",mc.cores=4)
@@
 ```
+
+This project is based on the following publication:
+
+Gorman, T. E., & Goldstone, R. L. (2022). An instance-based model account of the benefits of varied practice in visuomotor skill. *Cognitive Psychology*, 137, 101491.
 

### 2024-10-12 Manuscript/manuscript_full.qmd
cv additions and re-render
few new references, and a re-render with the intro figure.

@@
 format:
-#   docx:
-#     prefer-html: true
-#     output-file: "TG_Full_Dissertation2.docx"
-#     toc: true
+  docx:
+    prefer-html: true
+    output-file: "TG_Full_Dissertation2.docx"
+    toc: true
 #   html:
@@
 {{< include pre_sections/pre_pdf_full.qmd >}}
+{{< include pre_sections/acknowledgements.qmd >}}
+{{< include pre_sections/abstract.qmd >}}
 
@@
 {{< include pre_sections/pre_docx.qmd >}}
+{{< include pre_sections/acknowledgements.qmd >}}
+{{< include pre_sections/abstract.qmd >}}
 :::
-
 {{< pagebreak >}}

### 2024-10-12 Manuscript/pre_sections/abstract.qmd
few new references, and a re-render with the intro figure.

\begin{centering}

{Thomas E. Gorman}

{THE ROLE OF VARIABILITY IN LEARNING GENERALIZATION: A COMPUTATIONAL MODELING APPROACH}

\end{centering}

Researchers and educators have long been interested in how the variability of training examples experienced
during learning influences subsequent generalization. However, previous studies have reported both beneficial
and detrimental effects, leaving the nature of this relationship unclear. Furthermore, a formal computational
modeling approach to account for the effects of training variability has been largely lacking within the domain of
visuomotor skill learning. The current work presents two projects which shed light on this issue, each consisting of
several experiments which compare varied training (i.e., multiple training items) in comparison to constant
training (training with a single item).
The empirical results, much like those of the broader literature, provide evidence both for and against a benefit of
variable training in visuomotor skill learning, highlighting the complex interplay between training conditions and
generalization performance. To provide a theoretical account of these findings, this dissertation employs both
instance-based and connectionist computational modeling approaches. The instance-based modeling approach
introduced in project 1 provides a theoretically justifiable method of quantifying/controlling for similarity
between training and testing conditions, while also demonstrating that varied training may induce broader
generalization in the similarity function relating training and test items. In project 2, the Extrapolation-
Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
constant groups' ability to extrapolate linearly to novel regions despite limited training experience, while also
revealing potential detriments of varied training for simple extrapolation tasks.
By integrating empirical findings with computational modeling approaches, this dissertation sheds light on the
complex relationship between training variability and generalization performance.

\newpage

### 2024-10-12 Manuscript/pre_sections/acknowledgements.qmd
few new references, and a re-render with the intro figure.

\begin{centering}

\textbf{Acknowledgements}

\end{centering}

My dissertation would not have been possible without the support and guidance of numerous individuals who have shaped my academic and personal growth.

First, I am deeply grateful to my advisor, Rob Goldstone, for his nearly limitless patience, clear thinking, and unwavering guidance. His ability to effortlessly demonstrate the power of so many tools has been awe-inspiring, and I am forever thankful for his mentorship. I also extend my heartfelt thanks to Dr. Rob Nosofsky for his sharp questions and encouragement of model-based thinking, and to Dr. Peter Todd for being a constant source of encouragement.

My foundation in psychological science was laid at the University of Wisconsin-Madison. I am indebted to Dr. Shawn Green, who took a chance on me despite my mediocre grades and lack of experience, introducing me to the world of psychological research. Special thanks to Aaron Cochrane for answering my countless questions, introducing me to R, and advanced data analysis techniques.

I am grateful for the camaraderie and intellectual stimulation provided by my friends at Indiana University, particularly those in the Geolab and Psychology department. Johnathan Avery, Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others have been integral to my graduate school experience. A special mention goes to Jack Avery for introducing me to rock climbing and engaging in fun conversations that often led to unexpected ideas.

The teachers at Pardeeville High School played an essential role in nurturing my curiosity and establishing the educational foundation that shaped my early learning. The professors at UW-Madison and Indiana University further cultivated that curiosity, profoundly influencing my academic development.

I would also like to extend my heartfelt thanks to my family. My parents, Mary and Jim Gorman, have always been a source of love and unwavering belief in my abilities. My brother, Joseph, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed. Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.

\newpage

### 2024-10-12 Manuscript/pre_sections/pre_docx_full.qmd
few new references, and a re-render with the intro figure.

@@
 
+My dissertation would not have been possible without the support and guidance of numerous individuals who have shaped my academic and personal growth.
+
+First, I am deeply grateful to my advisor, Rob Goldstone, for his nearly limitless patience, clear thinking, and unwavering guidance.
+His ability to effortlessly demonstrate the power of so many tools has been awe-inspiring, and I am forever thankful for his mentorship.
+I also extend my heartfelt thanks to Dr.
+Rob Nosofsky for his sharp questions and encouragement of model-based thinking, and to Dr.
+Peter Todd for being a constant source of encouragement.
+
+My foundation in psychological science was laid at the University of Wisconsin-Madison.
+I am indebted to Dr.
+Shawn Green, who took a chance on me despite my mediocre grades and lack of experience, introducing me to the world of psychological research.
+Special thanks to Aaron Cochrane for answering my countless questions, introducing me to R, and advanced data analysis techniques.
+
+I am grateful for the camaraderie and intellectual stimulation provided by my friends at Indiana University, particularly those in the Geolab and Psychology department.
+Johnathan Avery, Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others have been integral to my graduate school experience.
+A special mention goes to Jack Avery for introducing me to rock climbing and engaging in fun conversations that often led to unexpected ideas.
+
+The teachers at Pardeeville High School played an essential role in nurturing my curiosity and establishing the educational foundation that shaped my early learning.
+The professors at UW-Madison and Indiana University further cultivated that curiosity, profoundly influencing my academic development.
+
+I would also like to extend my heartfelt thanks to my family.
+My parents, Mary and Jim Gorman, have always been a source of love and unwavering belief in my abilities.
+My brother, Joseph, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed.
+Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.
+
 ---

### 2024-10-12 Manuscript/pre_sections/pre_pdf_full.qmd
few new references, and a re-render with the intro figure.

@@
 Indiana University \\
-September 2024
+October 2024
 
@@
 \newpage
-\begin{center}
-\textbf{Acknowledgements}
-\end{center}
-\newpage

### 2024-10-12 Sections/Introduction.qmd
few new references, and a re-render with the intro figure.

@@
 
-Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015], the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] , simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
-See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.
+Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], pattern and anagram completion tasks [@goodeSuperiorityVariableRepeated2008; @zhangHighVariabilityLearning2024], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019; @ramAnticipatedVariabilityIncreases2024], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015], the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023], simple motor learning [@braunMotorTaskVariation2009; @velazquez-vargasRoleTrainingVariability2024; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022].
+See @czyzVariabilityPracticeInformation2021 and @ravivHowVariabilityShapes2022 for more detailed reviews.
 

### 2024-10-12 Sections/full.qmd
few new references, and a re-render with the intro figure.

@@
 ::: {.content-visible when-format="pdf"}
-{{< include /Sections/pre_sections/toc_pdf.qmd >}}
+<!-- {{< include /Sections/pre_sections/toc_pdf.qmd >}} -->
 :::
@@
 However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
+
+```{r}
+#| label: fig-ex-design1
+#| fig-width: 10
+#| fig-height: 6
+#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design.
+The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet).
+Both groups were tested from a distance of 3 feet.
+The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
+#| cache: false
+
+pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
+  ggh4x,htmltools,future,furrr,ez)
+
+create_data <- function(varied_train, constant_train, both_test) {
+  varied_labels <- "Varied-Train"
+  constant_labels <- "Constant-Train"
+  test_labels <- "Testing"
+
+  data <- data.frame(
+    x = c(varied_train, constant_train, both_test),
+    y = c(rep(0.55, length(varied_train)), rep(0.75, length(constant_train)), rep(0.4, length(both_test))),
+    label = c(rep(varied_labels, length(varied_train)),
+              rep(constant_labels, length(constant_train)),
+              rep(test_labels, length(both_test))),
+    color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test)))
+  )
+
+  data
+}
+
+create_segments <- function(data) {
+  min_x <- min(data$x)
+  max_x <- max(data$x)
+  segments <- data.frame(
+    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
+    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
+    y = c(0.55, 0.75, 0.4),
+    yend = c(0.55, 0.75, 0.4)
+  )
+  segments
+}
+
+create_plot <- function(varied_train, constant_train, both_test) {
+  data <- create_data(varied_train, constant_train, both_test)
+  segments <- create_segments(data)
+
+  # Variables for Training segment position
+  train_x <- min(data$x) - .5
+  train_y_start <- 0.5
+  train_y_end <- 0.8
+  train_text_y <- 0.75
+
+  # Variables for Testing segment position
+  test_x <- min(data$x) - .5
+  test_y_start <- 0.35
+  test_y_end <- 0.45
+  test_text_y <- 0.48
+
+  ggplot() +
+    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
+                 linewidth = 1.2, color = "gray40") +
+    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
+    geom_text(data = data, aes(x = x, y = y, label = label),
+              color = "black", size = 4.5, vjust = -1.8, hjust = 0.5, fontface = "italic") +
+    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
+    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
+    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
+    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
+    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
+    xlim(min(data$x) - 2, max(data$x) + 1) +
+    ylim(0.3, 1) +
+    theme_void() +
+    theme(legend.position = "none",
+          plot.margin = margin(10, 20, 10, 20),
+          plot.background = element_rect(fill = "white", color = NA),
+          panel.background = element_rect(fill = "white", color = NA))
+}
+
+kerr_booth_1978 <- create_plot(varied_train = c(2, 4), constant_train = c(3), both_test = c(3))
+kerr_booth_1978
+```
 
@@
 
-pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
-  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
-  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
-  ggh4x,htmltools,future,furrr,ez)
+# pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
+#   brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
+#   stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
+#   ggh4x,htmltools,future,furrr,ez)
 #options(brms.backend="cmdstanr",mc.cores=4)

### 2024-10-12 Manuscript/manuscript.qmd
initial re-render with inclusion of acknowledgement and abstract

@@
 #| label: fig-ex-design1
-#| fig-width: 10
-#| fig-height: 6
+#| fig-width: 7
+#| fig-height: 5
 #| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design.

### 2024-10-12 index.qmd
start the revisions page. Updates to main paper files from the HTW updates I did awhile ago.
initial re-render with inclusion of acknowledgement and abstract

--- 2024-06-21 index.qmd
@@
 - name: Thomas E. Gorman
-  affiliation: Indiana University
+  affiliations: 
+  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
     affiliation-url: https://psych.indiana.edu/
+  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
+    affiliation-url: https://cogs.indiana.edu/index.html
   url: https://tegorman13.github.io/
-  orcid: 0000-0001-5366-5442
 comments: false
-date-format: 'MMM YYYY'
+date: today
+#date-format: 'MMM YYYY'
 format:
@@
 [{{< fa person-chalkboard size=1.0xs >}} Defense slides](https://tegorman13.github.io/Dissertation/Presentation/slides_revealjs.html#/)
+
+##
+
+-----
+
+[Revisions](revisions.qmd)

### 2024-10-12 Manuscript/manuscript_full.qmd
fix citation and url colors to be black

@@
     colorlinks: true
-    linkcolor: DarkSlateBlue
-    urlcolor: DarkSlateBlue
-    citecolor: DarkSlateBlue
+    linkcolor: Black
+    urlcolor: Black
+    citecolor: Black
     link-citations: true

### 2024-10-12 Manuscript/manuscript.tex
unnecessary tweaks to html pre-sections

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  11pt,
  letterpaper,
]{article}

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmathfont[]{Libertinus Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=1in,bottom=1in,left=1in,right=1in,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\usepackage{anyfontsize}
\usepackage{multirow}
\usepackage{mathtools}
\everydisplay\expandafter{\the\everydisplay\small}
\usepackage{float}
\floatplacement{figure}{H}
\floatplacement{table}{H}
\usepackage{setspace}
\pagenumbering{arabic}
\usepackage{titlesec}
\titleformat{\section}{\fontsize{12}{14}\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\fontsize{11}{14}\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\fontsize{11}{14}\bfseries}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}{\fontsize{12}{14}\bfseries}{}{0em}{} 
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{sidenotes}{}{\usepackage{sidenotes}}
\@ifpackageloaded{marginnote}{}{\usepackage{marginnote}}
\makeatother
\makeatletter
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  colorlinks=true,
  linkcolor={Black},
  filecolor={Maroon},
  citecolor={Black},
  urlcolor={Black},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{2024-10-12}

\begin{document}

\setstretch{1.5}
\begin{centering}

{THE ROLE OF VARIABILITY IN LEARNING GENERALIZATION: A COMPUTATIONAL MODELING APPROACH}

\vspace{5\baselineskip}

{Thomas E. Gorman}

\vspace{10.5cm}

Submitted to the faculty of the University Graduate School \\
in partial fulfillment of the requirements \\
for the degree \\
Doctor of Philosophy \\
in the Cognitive Science Program and \\
Department of Psychological and Brain Sciences, \\
Indiana University \\
October 2024

\vspace{6cm}

\pagenumbering{gobble}
\end{centering}

\newpage
\pagenumbering{roman}
\setcounter{page}{2}
\begin{center}

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.
\end{center}
\vspace{1cm}

\hfill\break
Doctoral Committee \vspace{1cm}

\begin{flushright}
\underline{\hspace{5cm}} \\
Robert L. Goldstone, Ph.D.
\vspace{2cm}

\underline{\hspace{5cm}} \\
Robert M. Nosofsky, Ph.D.
\vspace{2cm}

\underline{\hspace{5cm}} \\
Peter M. Todd, Ph.D.
\vspace{2cm}

\underline{\hspace{5cm}} \\
Michael N. Jones, Ph.D.
\end{flushright}

\hfill\break
May 28th, 2024

\newpage

\begin{centering}

\vspace*{6.5cm}

@2024 \\
\vspace{1cm}

Thomas E. Gorman
\vspace{.2cm}

\vspace{5cm}

\end{centering}

\newpage

\begin{centering}

\textbf{Acknowledgements}

\end{centering}

My dissertation would not have been possible without the support and
guidance of numerous individuals who have shaped my academic and
personal growth.

First, I am deeply grateful to my advisor, Rob Goldstone, for his nearly
limitless patience, clear thinking, and unwavering guidance. His ability
to effortlessly demonstrate the power of so many tools has been
awe-inspiring, and I am forever thankful for his mentorship. I also
extend my heartfelt thanks to Dr.~Rob Nosofsky for his sharp questions
and encouragement of model-based thinking, and to Dr.~Peter Todd for
being a constant source of encouragement.

My foundation in psychological science was laid at the University of
Wisconsin-Madison. I am indebted to Dr.~Shawn Green, who took a chance
on me despite my mediocre grades and lack of experience, introducing me
to the world of psychological research. Special thanks to Aaron Cochrane
for answering my countless questions, introducing me to R, and advanced
data analysis techniques.

I am grateful for the camaraderie and intellectual stimulation provided
by my friends at Indiana University, particularly those in the Geolab
and Psychology department. Johnathan Avery, Eleanor Schille-Hudson, Mahi
Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan
Hasan, and many others have been integral to my graduate school
experience. A special mention goes to Jack Avery for introducing me to
rock climbing and engaging in fun conversations that often led to
unexpected ideas.

The teachers at Pardeeville High School played an essential role in
nurturing my curiosity and establishing the educational foundation that
shaped my early learning. The professors at UW-Madison and Indiana
University further cultivated that curiosity, profoundly influencing my
academic development.

I would also like to extend my heartfelt thanks to my family. My
parents, Mary and Jim Gorman, have always been a source of love and
unwavering belief in my abilities. My brother, Joseph, played a pivotal
role in helping me through the final stages of my dissertation by
providing a supportive environment and the encouragement I needed. Their
collective support has made this journey not only possible but
meaningful, and I will always be deeply grateful for it.

\newpage

\begin{centering}

{Thomas E. Gorman}

{THE ROLE OF VARIABILITY IN LEARNING GENERALIZATION: A COMPUTATIONAL MODELING APPROACH}

\end{centering}

The impact of training variability on generalization has been a
long-standing topic in the study of human learning, with conflicting
evidence about its potential benefits. This dissertation addresses these
ambiguities by examining the effects of varied versus constant training
in visuomotor skill learning through a combination of experimental and
computational modeling approaches. Across two projects, we
systematically compare varied training (multiple items) to constant
training (single item) in a projectile-throwing task. Empirical findings
reveal both positive and negative impacts of variability, highlighting
the complex interplay between training conditions and generalization
performance. To provide a theoretical account of these findings, this
dissertation employs both instance-based and connectionist computational
modeling approaches. The instance-based modeling approach introduced in
project 1 provides a theoretically justifiable method of
quantifying/controlling for similarity between training and testing
conditions, while also demonstrating that varied training may induce
broader generalization in the similarity function relating training and
test items. In project 2, the Extrapolation-Association Model (EXAM)
provided the best account of the testing data across all experiments,
capturing the constant groups' ability to extrapolate to novel regions
despite limited training experience, while also revealing potential
detriments of varied training for simple extrapolation tasks. These
results challenge simplistic notions about the universality of
variability benefits in training and emphasize the need for tailored
approaches that consider both the structure of the task environment and
the prior knowledge of the learners.

\newpage

\newpage{}

\tableofcontents
\newpage

\clearpage
\pagenumbering{arabic}

\newpage{}

\section{Introduction}\label{introduction}

\subsection{Varied Training and
Generalization}\label{varied-training-and-generalization}

Varied training has been shown to influence learning in a wide array of
different tasks and domains, including categorization
(\citeproc{ref-hahnEffectsCategoryDiversity2005}{Hahn et al., 2005};
\citeproc{ref-maddoxStimulusRangeDiscontinuity2011}{Maddox \& Filoteo,
2011};
\citeproc{ref-morgensternOneshotCategorizationNovel2019}{Morgenstern et
al., 2019}; \citeproc{ref-nosofskyModelguidedSearchOptimal2019}{Nosofsky
et al., 2019};
\citeproc{ref-plebanekEffectsFrequencyVariability2021}{Plebanek \&
James, 2021}; \citeproc{ref-posnerGenesisAbstractIdeas1968}{Posner \&
Keele, 1968}), language learning
(\citeproc{ref-brekelmansDoesHighVariability2022}{Brekelmans et al.,
2022}; \citeproc{ref-jonesDensityDistinctivenessEarly2020}{Jones \&
Brandt, 2020}; \citeproc{ref-perryLearnLocallyThink2010}{Perry et al.,
2010}; \citeproc{ref-twomeyAllRightNoises2018}{Twomey et al., 2018};
\citeproc{ref-wonnacottInputEffectsAcquisition2012}{Wonnacott et al.,
2012}), pattern and anagram completion tasks
(\citeproc{ref-goodeSuperiorityVariableRepeated2008}{Goode et al.,
2008}; \citeproc{ref-zhangHighVariabilityLearning2024}{Zhang \& Fyfe,
2024}), perceptual learning
(\citeproc{ref-lovibondStimulusDiscriminabilityInduction2020}{Lovibond
et al., 2020};
\citeproc{ref-manentiVariabilityTrainingUnlocks2023}{Manenti et al.,
2023}; \citeproc{ref-robsonSpecificVariedPractice2022a}{Robson et al.,
2022}; \citeproc{ref-zamanPerceptualVariabilityImplications2021}{Zaman
et al., 2021}), trajectory extrapolation
(\citeproc{ref-fulvioTaskSpecificResponseStrategy2014}{Fulvio et al.,
2014}), cognitive control tasks
(\citeproc{ref-moshon-cohenStimulusVariabilityImproves2024}{Moshon-Cohen
et al., 2024}; \citeproc{ref-sabahWhenLessMore2019}{Sabah et al.,
2019}), associative learning
(\citeproc{ref-fanStimulusDiversityIncreases2022}{Fan et al., 2022};
\citeproc{ref-leeEvidentialDiversityIncreases2019}{Lee et al., 2019};
\citeproc{ref-liveseyRevisitingPeakShift2019}{Livesey \& McLaren, 2019};
\citeproc{ref-pradaExperiencedCategoryVariability2020}{Prada \&
Garcia-Marques, 2020};
\citeproc{ref-ramAnticipatedVariabilityIncreases2024}{Ram et al., 2024};
\citeproc{ref-reichmannVariabilityAbstractionEvaluative2023}{Reichmann
et al., 2023}), visual search
(\citeproc{ref-georgeStimulusVariabilityTask2021}{George \& Egner,
2021}; \citeproc{ref-gonzalezDiversityTrainingEnhances2011}{Gonzalez \&
Madhavan, 2011}; \citeproc{ref-kelleyLearningAttendEffects2009}{T. A.
Kelley \& Yantis, 2009}), voice identity learning
(\citeproc{ref-lavanEffectsHighVariability2019}{Lavan et al., 2019}),
face recognition
(\citeproc{ref-burtonIdentityVariationRepresentations2016}{Burton et
al., 2016}; \citeproc{ref-honigPerceptualSimilarityModulates2022}{Honig
et al., 2022}; \citeproc{ref-menonVariationPhotosSame2015}{Menon et al.,
2015}), the perception of social group heterogeneity
(\citeproc{ref-gershmanStructureLearningPrinciples2023}{Gershman \&
Cikara, 2023};
\citeproc{ref-konovalovaInformationSamplingExplanation2020}{Konovalova
\& Le Mens, 2020};
\citeproc{ref-linvilleExemplarAbstractionModels1993}{Linville \&
Fischer, 1993};
\citeproc{ref-parkPerceptionVariabilityCategory1987}{Park \& Hastie,
1987}), simple motor learning
(\citeproc{ref-braunMotorTaskVariation2009}{Braun et al., 2009};
\citeproc{ref-rollerVariablePracticeLenses2001}{Roller et al., 2001};
\citeproc{ref-velazquez-vargasRoleTrainingVariability2024}{Velázquez-Vargas
et al., 2024};
\citeproc{ref-willeyLimitedGeneralizationVaried2018}{Willey \& Liu,
2018a}), sports training
(\citeproc{ref-breslinConstantVariablePractice2012}{Breslin et al.,
2012}; \citeproc{ref-greenPracticeVariabilityTransfer1995a}{Green et
al., 1995}; \citeproc{ref-northEffectConsistentVaried2019}{North et al.,
2019}), and complex skill learning
(\citeproc{ref-hacquesVisualControlClimbing2022}{Hacques et al., 2022};
\citeproc{ref-huetEducationAttentionExplanation2011}{Huet et al., 2011};
\citeproc{ref-seowTransferEffectsVaried2019}{Seow et al., 2019}). See
Czyż (\citeproc{ref-czyzVariabilityPracticeInformation2021}{2021}) and
Raviv et al. (\citeproc{ref-ravivHowVariabilityShapes2022}{2022}) for
more detailed reviews.

Research on the effects of varied training typically manipulates
variability in one of two ways. In the first approach, a high
variability group is exposed to a greater number of unique instances
during training, while a low variability group receives fewer unique
instances with more repetitions. Alternatively, both groups may receive
the same number of unique instances, but the high variability group's
instances are more widely distributed or spread out in the relevant
psychological space, while the low variability group's instances are
clustered more tightly together. Researchers then compare the training
groups in terms of their performance during the training phase, as well
as their generalization performance during a testing phase. Researchers
usually compare the performance of the two groups during both the
training phase and a subsequent testing phase. The primary theoretical
interest is often to assess the influence of training variability on
generalization to novel testing items or conditions. However, the test
may also include some or all of the items that were used during the
training stage, allowing for an assessment of whether the variability
manipulation influenced the learning of the trained items themselves, or
to easily measure how much performance degrades as a function of how far
away testing items are from the training items.

The influence of training variability has received a large amount of
attention in the domain of sensorimotor skill learning. Much of this
research has been influenced by the work of Schmidt
(\citeproc{ref-schmidtSchemaTheoryDiscrete1975}{1975}), who proposed a
schema-based account of motor learning as an attempt to address the
longstanding problem of how novel movements are produced. Schema theory
presumes that learners possess general motor programs for a class of
movements (e.g., an underhand throw). When called up for use motor
programs are parameterized by schema rules which determine how the motor
program is parameterized or scaled to the particular demands of the
current task. Schema theory predicts that variable training facilitates
the formation of more robust schemas, which will result in improved
generalization or transfer. Experiments that test this hypothesis are
often designed to compare the transfer performance of a constant-trained
group against that of a varied-trained group. Both groups train on the
same task, but the varied group practices with multiple instances along
some task-relevant dimension that remains invariant for the constant
group. For example, studies using a projectile throwing task might
assign participants to either constant training that practice throwing
from a single location, or to a varied group that throws from multiple
locations. Following training, both groups are then tested from novel
throwing locations
(\citeproc{ref-pachecoLearningSpecificIndividual2018}{Pacheco \& Newell,
2018}; \citeproc{ref-pigottMotorSchemaStructure1984}{Pigott \& Shapiro,
1984}; \citeproc{ref-willeyLimitedGeneralizationVaried2018}{Willey \&
Liu, 2018a}; \citeproc{ref-wulfEffectTypePractice1991}{Wulf, 1991}).

One of the earliest and still often cited investigations of Schmidt's
benefits of variability hypothesis was the work of Kerr \& Booth
(\citeproc{ref-kerrSpecificVariedPractice1978}{1978}). Two groups of
children, aged 8 and 12, were assigned to either constant or varied
training of a bean bag throwing task. The constant group practiced
throwing a bean-bag at a small target placed 3 feet in front of them,
and the varied group practiced throwing from a distance of both 2 feet
and 4 feet (see Figure~\ref{fig-ex-design1}). Participants were
blindfolded and unable to see the target while making each throw but
would receive feedback by looking at where the beanbag had landed in
between each training trial. 12 weeks later, all of the children were
given a final test from a distance of 3 feet which was novel for the
varied participants and repeated for the constant participants.
Participants were also blindfolded for testing and did not receive trial
by trial feedback in this stage. In both age groups, participants
performed significantly better in the varied condition than the constant
condition, though the effect was larger for the younger, 8-year-old
children. This result provides particularly strong evidence for the
benefits of varied practice, as the varied group outperformed the
constant group even when tested at the ``home-turf'' distance that the
constant group had exclusively practiced. A similar pattern of results
was observed in another study wherein varied participants trained with
tennis, squash, badminton, and short-tennis rackets were compared
against constant subjects trained with only a tennis racket
(\citeproc{ref-greenPracticeVariabilityTransfer1995a}{Green et al.,
1995}). One of the testing conditions had subjects repeat the use of the
tennis racket, which had been used on all 128 training trials for the
constant group, and only 32 training trials for the varied group.
Nevertheless, the varied group outperformed the constant group when
using the tennis racket at testing, and also performed better in
conditions with several novel racket lengths. However, as is the case
with many of the patterns commonly observed in the ``benefits of
variability'' literature, the pattern wherein the varied group
outperforms the constant group even from the constants group's home turf
has not been consistently replicated. One recent study attempted a near
replication of the Kerr \& Booth study
(\citeproc{ref-willeyLongtermMotorLearning2018}{Willey \& Liu, 2018b}),
having subjects throw beanbags at a target, with the varied group
training from positions (5 and 9 feet) on either side of the constant
group (7 feet). This study did not find a varied advantage from the
constant training position, though the varied group did perform better
at distances novel to both groups. However, this study diverged from the
original in that the participants were adults; and the amount of
training was much greater (20 sessions with 60 practice trials each,
spread out over 5-7 weeks).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-ex-design1-1.pdf}}

}

\caption{\label{fig-ex-design1}A schematic representation of the Kerr \&
Booth (\citeproc{ref-kerrSpecificVariedPractice1978}{1978}) study
design. The varied group trained from two distances (2 and 4 feet),
while the constant group trained from a single distance (3 feet). Both
groups were tested from a distance of 3 feet. The varied group
outperformed the constant group at testing, despite the constant group
having exclusively practiced from the testing distance.}

\end{figure}%

Pitting varied against constant practice against each other on the home
turf of the constant group provides a compelling argument for the
benefits of varied training, as well as an interesting challenge for
theoretical accounts that posit generalization to occur as some function
of distance. However, despite its appeal this contrast is relatively
uncommon in the literature. It is unclear whether this may be cause for
concern over publication bias, or just researchers feeling the design is
too risky. A far more common design is to have separate constant groups
that each train exclusively from each of the conditions that the varied
group encounters
(\citeproc{ref-catalanoDistantTransferCoincident1984a}{Catalano \&
Kleiner, 1984}; \citeproc{ref-chuaPracticeVariabilityPromotes2019}{Chua
et al., 2019}; \citeproc{ref-mccrackenTestSchemaTheory1977}{McCracken \&
Stelmach, 1977};
\citeproc{ref-moxleySchemaVariabilityPractice1979}{Moxley, 1979};
\citeproc{ref-newellVariabilityPracticeTransfer1976}{Newell \& Shapiro,
1976}), or for a single constant group to train from just one of the
conditions experienced by the varied participants
(\citeproc{ref-pigottMotorSchemaStructure1984}{Pigott \& Shapiro, 1984};
\citeproc{ref-rollerVariablePracticeLenses2001}{Roller et al., 2001};
\citeproc{ref-wrisbergTrainingProductionNovel1984}{Wrisberg \& McLean,
1984}; \citeproc{ref-wrisbergDevelopingCoincidentTiming1983}{Wrisberg \&
Mead, 1983}). A less common contrast places the constant group training
in a region of the task space outside of the range of examples
experienced by the varied group, but distinct from the transfer
condition
(\citeproc{ref-wrisbergVariabilityPracticeHypothesis1987}{Wrisberg et
al., 1987}; \citeproc{ref-wulfVariabilityPracticeImplicit1997}{Wulf \&
Schmidt, 1997}). Of particular relevance to the current work is the
early study of Catalano \& Kleiner
(\citeproc{ref-catalanoDistantTransferCoincident1984a}{1984}), as theirs
was one of the earliest studies to investigate the influence of varied
vs.~constant training on multiple testing locations of graded distance
from the training condition. Participants were trained on coincident
timing task, in which subjects observe a series of lightbulbs turning on
sequentially at a consistent rate and attempt to time a button response
with the onset of the final bulb. The constant groups trained with a
single velocity of either 5,7,9, or 11 mph, while the varied group
trained from all 4 of these velocities. Participants were then assigned
to one of four possible generalization conditions, all of which fell
outside of the range of the varied training conditions -- 1, 3, 13 or 15
mph. As is often the case, the varied group performed worse during the
training phase. In the testing phase, the general pattern was for all
participants to perform worse as the testing conditions became further
away from the training conditions, but since the drop off in performance
as a function of distance was far less steep for the varied group, the
authors suggested that varied training induced a decremented
generalization gradient, such that the varied participants were less
affected by the change between training and testing conditions.

Benefits of varied training have also been observed in many studies
outside of the sensorimotor domain. Goode et al.
(\citeproc{ref-goodeSuperiorityVariableRepeated2008}{2008}) trained
participants to solve anagrams of 40 different words ranging in length
from 5 to 11 letters, with an anagram of each word repeated 3 times
throughout training, for a total of 120 training trials. Although
subjects in all conditions were exposed to the same 40 unique words
(i.e.~the solution to an anagram), participants in the varied group saw
3 different arrangements for each solution-word, such as DOLOF, FOLOD,
and OOFLD for the solution word FLOOD, whereas constant subjects would
train on three repetitions of LDOOF (spread evenly across training). Two
different constant groups were used. Both constant groups trained with
three repetitions of the same word scramble, but for constant group A,
the testing phase consisted of the identical letter arrangement to that
seen during training (e.g., LDOOF), whereas for constant group B, the
testing phase consisted of an arrangement they had not seen during
training, thus presenting them with a testing situation similar
situation to the varied group. At the testing stage, the varied group
outperformed both constant groups, a particularly impressive result,
given that constant group A had three prior exposures to the word
arrangement (i.e.~the particular permutation of letters) which the
varied group had not explicitly seen. However varied subjects in this
study did not exhibit the typical decrement in the training phase
typical of other varied manipulations in the literature, and achieved
higher levels of anagram solving accuracy by the end of training than
either of the constant groups -- solving two more anagrams on average
than the constant group. This might suggest that for tasks of this
nature where the learner can simply get stuck with a particular word
scramble, repeated exposure to the identical scramble might be less
helpful towards finding the solution than being given a different
arrangement of the same letters. This contention is supported by the
fact that constant group A, who was tested on the identical arrangement
as they experienced during training, performed no better at testing than
did constant group B, who had trained on a different arrangement of the
same word solution -- further suggesting that there may not have been a
strong identity advantage in this task.

In the domain of category learning, the constant vs.~varied comparison
is much less suitable. Instead, researchers will typically employ
designs where all training groups encounter numerous stimuli, but one
group experiences a greater number of unique exemplars
(\citeproc{ref-brunsteinPreparingNoveltyDiverse2011}{Brunstein \&
Gonzalez, 2011};
\citeproc{ref-doyleMetacognitiveMonitoringCategory2016}{Doyle \&
Hourihan, 2016};
\citeproc{ref-hoschPriorExperienceVariability2023}{Hosch et al., 2023};
\citeproc{ref-nosofskyModelguidedSearchOptimal2019}{Nosofsky et al.,
2019};
\citeproc{ref-wahlheimMetacognitiveJudgmentsRepetition2012}{Wahlheim et
al., 2012}), or designs where the number of unique training exemplars is
held constant, but one group trains with items that are more dispersed,
or spread out across the category space
(\citeproc{ref-bowmanTrainingSetCoherence2020}{Bowman \& Zeithamova,
2020}; \citeproc{ref-homaCategoryBreadthAbstraction1976}{Homa \&
Vosburgh, 1976}; \citeproc{ref-huHighvariabilityTrainingDoes2024}{Hu \&
Nosofsky, 2024};
\citeproc{ref-maddoxStimulusRangeDiscontinuity2011}{Maddox \& Filoteo,
2011}; \citeproc{ref-posnerGenesisAbstractIdeas1968}{Posner \& Keele,
1968}).

Much of the earlier work in this sub-area trained subjects on artificial
categories, such as dot patterns
(\citeproc{ref-homaCategoryBreadthAbstraction1976}{Homa \& Vosburgh,
1976}; \citeproc{ref-posnerGenesisAbstractIdeas1968}{Posner \& Keele,
1968}). A seminal study by Posner \& Keele
(\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}) trained
participants to categorize artificial dot patterns, manipulating whether
learners were trained with low variability examples clustered close to
the category prototypes (i.e.~low distortion training patterns), or
higher-variability patterns spread further away from the prototype
(i.e.~high-distortion patterns). Participants that received training on
more highly-distorted items showed superior generalization to novel high
distortion patterns in the subsequent testing phase. It should be noted
that unlike the sensorimotor studies discussed earlier, the Posner \&
Keele (\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}) study did
not present low-varied and high-varied participants with an equal number
of training trials, but instead had participants remain in the training
stage of the experiment until they reached a criterion level of
performance. This train-until-criterion procedure led to the
high-variability condition participants tending to complete a larger
number of training trials before switching to the testing stage. More
recent work (\citeproc{ref-huHighvariabilityTrainingDoes2024}{Hu \&
Nosofsky, 2024}) also used dot pattern categories, but matched the
number of training trials across conditions. Under this procedure,
higher-variability participants tended to reach lower levels of
performance by the end of the training stage. The results in the testing
phase were the opposite of Posner \& Keele
(\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}), with the
low-variability training group showing superior generalization to novel
high-distortion patterns (as well as generalization to novel patterns of
low or medium distortion levels). However, whether this discrepancy is
solely a result of the different training procedures is unclear, as the
studies also differed in the nature of the prototype patterns used.
Posner \& Keele (\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968})
utilized simpler, recognizable prototypes (e.g., a triangle, the letter
M, the letter F), while Hu \& Nosofsky
(\citeproc{ref-huHighvariabilityTrainingDoes2024}{2024}) employed random
prototype patterns.

Recent studies have also begun utilizing more complex or realistic
stimuli when assessing the influence of variability on category
learning. Wahlheim et al.
(\citeproc{ref-wahlheimMetacognitiveJudgmentsRepetition2012}{2012})
conducted one such study. In a within-participants design, participants
were trained on bird categories with either many repetitions of a few
exemplars, or with few repetitions of many exemplars. Across four
different experiments, which were conducted to address an unrelated
question on metacognitive judgements, the researchers consistently found
that participants generalized better to novel species following training
with more unique exemplars (i.e.~higher variability), while high
repetition training produced significantly better performance
categorizing the specific species they had trained on. A variability
advantage was also found in the relatively complex domain of rock
categorization
(\citeproc{ref-nosofskyModelguidedSearchOptimal2019}{Nosofsky et al.,
2019}). For 10 different rock categories, participants were trained with
either many repetitions of 3 unique examples of each category, or few
repetitions of 9 unique examples, with an equal number of total training
trials in each group (the design also included 2 other conditions less
amenable to considering the impact of variation). The high-variability
group, trained with 9 unique examples, showed significantly better
generalization performance than the other conditions.

A distinct sub-literature within the category learning domain has
examined how the variability or dispersion of the categories themselves
influences generalization to ambiguous regions of the category space
(e.g., the region between the two categories). The general approach is
to train participants with examples from a high variability category and
a low variability category. Participants are then tested with novel
items located within ambiguous regions of the category space which allow
the experimenters to assess whether the difference in category
variability influenced how far participants generalize the category
boundaries. A. L. Cohen et al.
(\citeproc{ref-cohenCategoryVariabilityExemplar2001}{2001}) conducted
two experiments with this basic paradigm. In experiment 1, a low
variability category composed of 1 instance was compared against a
high-variability category of 2 instances in one condition, and 7
instances in another. In experiment 2 both categories were composed of 3
instances, but for the low-variability group the instances were
clustered close to each other, whereas the high-variability groups
instances were spread much further apart. Participants were tested on an
ambiguous novel instance that was located in between the two trained
categories. Both experiments provided evidence that participants were
much more likely to categorize the novel middle stimulus into the
category with greater variation.

Further observations of widened generalization following varied training
have since been observed in numerous investigations
(\citeproc{ref-hahnEffectsCategoryDiversity2005}{Hahn et al., 2005};
\citeproc{ref-hoschPriorExperienceVariability2023}{Hosch et al., 2023};
\citeproc{ref-hsuEffectsGenerativeDiscriminative2010}{Hsu \& Griffiths,
2010}; \citeproc{ref-perlmanFurtherAttemptsClarify2012}{Perlman et al.,
2012}; \citeproc{ref-sakamotoPuttingPsychologyBack2008}{Sakamoto et al.,
2008}; but see
\citeproc{ref-stewartEffectCategoryVariability2002}{Stewart \& Chater,
2002}; \citeproc{ref-yangCategoryVariabilityEffect2014}{L.-X. Yang \&
Wu, 2014}; and \citeproc{ref-seitzModelingCategoryVariability2023}{Seitz
et al., 2023}). The results of Sakamoto et al.
(\citeproc{ref-sakamotoPuttingPsychologyBack2008}{2008}) are noteworthy.
They first reproduced the basic finding of participants being more
likely to categorize an unknown middle stimulus into a training category
with higher variability. In a second experiment, they held the
variability between the two training categories constant and instead
manipulated the training sequence, such that the examples of one
category appeared in an ordered fashion, with very small changes from
one example to the other (the stimuli were lines that varied only in
length), whereas examples in the alternate category were shown in a
random order and thus included larger jumps in the stimulus space from
trial to trial. They found that the middle stimulus was more likely to
be categorized into the category that had been learned with a random
sequence, which was attributed to an increased perception of variability
which resulted from the larger trial to trial discrepancies.

The work of Hahn et al.
(\citeproc{ref-hahnEffectsCategoryDiversity2005}{2005}), is also of
particular interest to the present work. Their experimental design was
similar to previous studies, but they included a larger set of testing
items which were used to assess generalization both between the two
training categories as well as novel items located in the outer edges of
the training categories. During generalization testing, participants
were given the option to respond with ``neither'', in addition to
responses to the two training categories. The ``neither'' response was
included to test how far away in the stimulus space participants would
continue to categorize novel items as belonging to a trained category.
Consistent with prior findings, high-variability training resulted in an
increased probability of categorizing items in between the training
categories as belong to the high variability category. Additionally,
participants trained with higher variability also extended the category
boundary further out into the periphery than participants trained with a
lower variability category were willing to do. The author compared a
variety of similarity-based models based around the Generalized Context
Model
(\citeproc{ref-nosofskyAttentionSimilarityIdentificationcategorization1986}{Nosofsky,
1986}) to account for their results, manipulating whether a
response-bias or similarity-scaling parameter was fit separately between
variability conditions. No improvement in model fit was found by
allowing the response-bias parameter to differ between groups, however
the model performance did improve significantly when the similarity
scaling parameter was fit separately. The best fitting
similarity-scaling parameters were such that the high-variability group
was less sensitive to the distances between stimuli, resulting in
greater similarity values between their training items and testing
items. This model accounted for both the extended generalization
gradients of the varied participants, and for their poorer performance
in a recognition condition.

Variability has also been examined in the learning of higher-order
linguistic categories (\citeproc{ref-perryLearnLocallyThink2010}{Perry
et al., 2010}). In nine training sessions spread out over nine weeks
infants were trained on object labels in a naturalistic play setting.
All infants were introduced to three novel objects of the same category,
with participants in the ``tight'' condition being exposed to three
similar exemplars of the category, and participants in the varied
condition being exposed to three dissimilar objects of the same
category. Importantly, the similarity of the objects was carefully
controlled for by having a separate group of adult subjects provide
pairwise similarity judgements of the category objects prior to the
study onset. Multidimensional scaling was then performed to obtain the
coordinates of the objects psychological space, and out of the 10
objects for each category, the 3 most similar objects were selected for
the tight group and the three least similar objects for the varied
group, with the leftover four objects being retained for testing. By the
end of the nine weeks, all of the infants had learned the labels of the
training objects. In the testing phase, the varied group demonstrated
superior ability to correctly generalize the object labels to untrained
exemplars of the same category. More interesting was the superior
performance of the varied group on a higher order generalization task --
such that they were able to appropriately generalize the bias they had
learned during training for attending to the shape of objects to novel
solid objects, but not to non-solids. The tight training group, on the
other hand, tended to overgeneralize the shape bias, leading the
researchers to suggest that the varied training induced a more
context-sensitive understanding of when to apply their knowledge.

Of course, the relationship between training variability and transfer is
unlikely to be a simple function wherein increased variation is always
beneficial. Numerous studies have found null, or in some cases negative
effects of training variation
(\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al., 1997};
\citeproc{ref-sinkeviciuteRoleInputVariability2019}{Sinkeviciute et al.,
2019}; \citeproc{ref-vanrossumSchmidtSchemaTheory1990}{Van Rossum,
1990}; \citeproc{ref-wrisbergVariabilityPracticeHypothesis1987}{Wrisberg
et al., 1987}), and many more have suggested that the benefits of
variability may depend on additional factors such as prior task
experience, the order of training trials, or the type of transfer being
measured (\citeproc{ref-bernikerEffectsTrainingBreadth2014}{Berniker et
al., 2014};
\citeproc{ref-braithwaiteEffectsVariationPrior2015}{Braithwaite \&
Goldstone, 2015}; \citeproc{ref-hahnEffectsCategoryDiversity2005}{Hahn
et al., 2005}; \citeproc{ref-lavanEffectsHighVariability2019}{Lavan et
al., 2019}; \citeproc{ref-northEffectConsistentVaried2019}{North et al.,
2019}; \citeproc{ref-sadakataIndividualAptitudeMandarin2014}{Sadakata \&
McQueen, 2014};
\citeproc{ref-zamanPerceptualVariabilityImplications2021}{Zaman et al.,
2021}).

In an example of a more complex influence of training variation,
(\citeproc{ref-braithwaiteEffectsVariationPrior2015}{Braithwaite \&
Goldstone, 2015}) trained participants on example problems involving the
concept of sampling with replacement (SWR). Training consisted of
examples that were either highly similar in their semantic context
(e.g., all involving people selecting objects) or in which the surface
features were varied between examples (e.g., people choosing objects AND
objects selected in a sequence). The experimenters also surveyed how
much prior knowledge each participant had with SWR. They found that
whether variation was beneficial depended on the prior knowledge of the
participants -- such that participants with some prior knowledge
benefited from varied training, whereas participants with minimal prior
knowledge performed better after training with similar examples. The
authors hypothesized that to benefit from varied examples, participants
must be able to detect the structure common to the diverse examples, and
that participants with prior knowledge are more likely to be sensitive
to such structure, and thus to benefit from varied training. To test
this hypothesis more directly, the authors conducted a 2nd experiment,
wherein they controlled prior knowledge by exposing some subjects to a
short graphical or verbal pre-training lesson, designed to increase
sensitivity to the training examples. Consistent with their hypothesis,
participants exposed to the structural sensitivity pre-training
benefited more from varied training than the controls participants who
benefited more from training with similar examples. Interactions between
prior experience and the influence of varied training have also been
observed in sensorimotor learning
(\citeproc{ref-delreyEffectsContextualInterference1982}{Del Rey et al.,
1982};
\citeproc{ref-guadagnoliRelationshipContextualInterference1999}{Guadagnoli
et al., 1999}). Del Rey et al.
(\citeproc{ref-delreyEffectsContextualInterference1982}{1982}) recruited
participants who self-reported either extensive, or very little
experience with athletic activities, and then trained participants on a
coincident timing task with either a single constant training velocity,
or with one of several varied training procedures. Unsurprisingly,
athlete participants had superior performance during training,
regardless of condition, and training performance was superior for all
subjects in the constant group. Of greater interest is the pattern of
testing results from novel transfer conditions. Among the
athlete-participants, transfer performance was best for those who
received variable training. Non-athletes showed the opposite pattern,
with superior performance for those who had constant training.

\subsection{Existing Theoretical
Frameworks}\label{existing-theoretical-frameworks}

Several theoretical frameworks have been proposed to conceptually
explain the effects of varied training on learning and generalization.
Schema theory (described in more detail above), posts that varied
practice leads to the formation of more flexible motor schemas, which
then facilitate generalization
(\citeproc{ref-schmidtSchemaTheoryDiscrete1975}{Schmidt, 1975}). The
desirable difficulties framework
(\citeproc{ref-bjorkMakingThingsHard2011}{Bjork \& Bjork, 2011};
\citeproc{ref-soderstromLearningPerformanceIntegrative2015}{Soderstrom
\& Bjork, 2015}) proposes that variable practice conditions may impair
initial performance but then enhance longer-term retention and transfer.
Similarly, the challenge point framework
(\citeproc{ref-guadagnoliChallengePointFramework2004}{Guadagnoli \& Lee,
2004}) contends that training variation induces optimal learning occurs
insofar as it causes the difficulty of practice tasks to be
appropriately matched to the learner's capabilities, but may also be
detrimental if the amount of variation causes the task to be too
difficult.

While these frameworks offer valuable conceptual accounts, there has
been a limited application of computational modeling efforts aimed at
quantitatively assessing and comparing the learning and generalization
mechanisms which may be underlying the influence of variability in
visuomotor skill learning. In contrast, the effects of variability have
received more formal computational treatment in other domains, such as
category learning Hu \& Nosofsky
(\citeproc{ref-huHighvariabilityTrainingDoes2024}{2024}), language
learning (\citeproc{ref-jonesDensityDistinctivenessEarly2020}{Jones \&
Brandt, 2020}), and function learning
(\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al., 1997}). A
primary goal of the current dissertation is to address this gap by
adapting and applying modeling approaches from these other domains to
investigate the effects of training variability in visuomotor skill
learning and function learning tasks.

\subsection{The current work}\label{the-current-work}

The overarching purpose of this dissertation is to investigate the
effects of training variability on learning and generalization within
visuomotor skill learning and function learning. Our investigation is
structured into two main projects, each employing distinct experimental
paradigms and computational modeling frameworks to elucidate how and
when variability in training enhances or impedes subsequent
generalization.

In Project 1, we investigated the influence of varied practice in a
simple visuomotor projectile launching task. Experiments 1 and 2
compared the performance of constant and varied training groups to
assess potential benefits of variability on transfer to novel testing
conditions. To account for the observed empirical effects, we introduced
the Instance-based Generalization with Adaptive Similarity (IGAS) model.
IGAS provides a novel computational approach for quantifying the
similarity between training experiences and transfer conditions, while
also allowing for variability to influence the generalization gradient
itself.

Project 2 will focus on the domain of function learning and in
particular the issue of extrapolation. Function learning research
examines how people acquire and generalize knowledge about continuous
input-output relationships, and the factors influencing extrapolation to
novel inputs following an initial learning phase. The domain of function
learning has yielded influential computational models, including the
Associative Learning Model (ALM) and the Extrapolation-Association Model
(EXAM)(\citeproc{ref-busemeyerLearningFunctionalRelations1997}{Busemeyer
et al., 1997}), which have successfully accounted for human learning,
interpolation, and extrapolation in numerous
investigations(\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et
al., 1997};
\citeproc{ref-mcdanielPredictingTransferPerformance2009}{McDaniel et
al., 2009}; \citeproc{ref-mcdanielConceptualBasisFunction2005}{McDaniel
\& Busemeyer, 2005}). However, the influence of training variability on
function learning, particularly in visuomotor function learning tasks,
remains relatively unexplored. Project 2 of this dissertation will
address this gap by investigating how constant and varied training
regimes affect learning, discrimination, and extrapolation in a novel
visuomotor function learning task. We will leverage the ALM and EXAM
models, fitted to individual participant data using advanced Bayesian
techniques, to provide a detailed computational account of the observed
empirical patterns.

\newpage{}

\section{Project 1}\label{project-1}

This project is based on the following publication:

Gorman, T. E., \& Goldstone, R. L. (2022). An instance-based model
account of the benefits of varied practice in visuomotor skill.
\emph{Cognitive Psychology}, 137, 101491.

\subsection{Abstract}\label{abstract}

Exposing learners to variability during training has been demonstrated
to improve performance in subsequent transfer testing. Such variability
benefits are often accounted for by assuming that learners are
developing some general task schema or structure. However, much of this
research has neglected to account for differences in similarity between
varied and constant training conditions. In a between-groups
manipulation, we trained participants on a simple projectile launching
task, with either varied or constant conditions. We replicate previous
findings showing a transfer advantage of varied over constant training.
Furthermore, we show that a standard similarity model is insufficient to
account for the benefits of variation, but, if the model is adjusted to
assume that varied learners are tuned towards a broader generalization
gradient, then a similarity-based model is sufficient to explain the
observed benefits of variation. Our results therefore suggest that some
variability benefits can be accommodated within instance-based models
without positing the learning of some schemata or structure.

\subsection{Introduction}\label{introduction-1}

\subsubsection{Similarity and instance-based approaches to transfer of
learning}\label{similarity-and-instance-based-approaches-to-transfer-of-learning}

Early models of learning often assumed that discrete experiences with
some task or category were not stored individually in memory, but
instead promoted the formation of a summary representation, often
referred to as a prototype or schema, and that exposure to novel
examples would then prompt the retrieval of whichever preexisting
prototype was most similar. In addition to being a landmark study on the
influence of training variability, Posner \& Keele
(\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}) (described above)
also put forward an influential argument concerning the nature of the
mental representations acquired during learning - namely that learners
tend to abstract a prototype, or aggregate representation of the dot
pattern categories, rather than encoding each individual stimulus.
Recall that participants are trained on only on distortions of the
category prototypes (e.g., low, medium or high distortions), never
encountering the exact prototypes during the training stage. Then, in
the testing phase, participants are tested with the prototype patterns,
their old training items, and novel low, medium and high distortions.
The authors found that participants had the highest testing accuracy for
the previously unseen prototype patterns, followed by the old training
items, and then the novel low, medium and high distortions. The authors
interpreted this pattern as evidence that participants had acquired
prototype representation of the category, as opposed to storing each
individual training instance, and that generalization was based on the
similarity of the testing items to the learned prototype
representations. Posner \& Keele
(\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}) has been extremely
influential, and continues to be cited as evidence that prototype
abstraction underlies the benefits of varied training. It's also
referenced as a key influence in the development of the ``Schema Theory
of Motor Learning'' Schmidt
(\citeproc{ref-schmidtSchemaTheoryDiscrete1975}{1975}), which in turn
influenced decades of research on the potential benefits of varied
training in motor skill learning. However, a number of the core
assumptions utilized by Posner \& Keele
(\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}) were later called
into question both empirically and with competing theoretical accounts
(\citeproc{ref-hintzmanMINERVASimulationModel1984}{Hintzman, 1984},
\citeproc{ref-hintzmanSchemaAbstractionMultipletrace1986}{1986};
\citeproc{ref-knappTheoryCategorizationBased1984}{Knapp \& Anderson,
1984};
\citeproc{ref-mcclellandDistributedMemoryRepresentation1985}{McClelland
\& Rumelhart, 1985};
\citeproc{ref-nosofskyInvestigationsExemplarBasedConnectionist1992}{Nosofsky
\& Kruschke, 1992};
\citeproc{ref-palmeriCentralTendenciesExtreme2001}{Palmeri \& Nosofsky,
2001}; \citeproc{ref-zakiHighdistortionEnhancementEffect2007}{Zaki \&
Nosofsky, 2007}). Palmeri \& Nosofsky
(\citeproc{ref-palmeriCentralTendenciesExtreme2001}{2001}) demonstrated
both the dangers of assuming that psychological representations mimic
the metric stimulus space, as well the viability of models with simpler
representational assumptions. These authors conducted a near replication
of the Posner \& Keele
(\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}) study, but also
had participants provide similarity judgements of the dot pattern
stimuli after completing the training phase. A multidimensional scaling
analysis of the similarity judgements revealed that the psychological
representations of the prototype stimuli were not located in the middle
of the training stimuli, but were instead extreme points in the
psychological space. The authors also demonstrated the generalization
patterns of Posner \& Keele
(\citeproc{ref-posnerGenesisAbstractIdeas1968}{1968}) could be accounted
for by an exemplar-based model, without any need to assume the
abstraction of a prototype.

Instance-based, or exemplar-based models generally assume that learners
encode each experience with a task as a separate
instance/exemplar/trace, and that each encoded trace is in turn compared
against novel stimuli
(\citeproc{ref-estesClassificationCognition1994}{Estes, 1994};
\citeproc{ref-hintzmanMINERVASimulationModel1984}{Hintzman, 1984};
\citeproc{ref-jamiesonInstanceTheoryDomaingeneral2022}{Jamieson et al.,
2022}; \citeproc{ref-medinContextTheoryClassification1978}{Medin \&
Schaffer, 1978};
\citeproc{ref-nosofskyAttentionSimilarityIdentificationcategorization1986}{Nosofsky,
1986}). As the number of stored instances increases, so does the
likelihood that some previously stored instance will be retrieved to aid
in the performance of a novel task. Stored instances are retrieved in
the context of novel stimuli or tasks if they are sufficiently similar,
thus suggesting that the process of computing similarity is of central
importance to generalization.

Similarity, defined in this literature as a function of psychological
distance between instances or categories, has provided a successful
account of generalization across numerous tasks and domains. In an
influential study demonstrating an ordinal similarity effect,
experimenters employed a numerosity judgment task in which participants
quickly report the number of dots flashed on a screen. Performance (in
terms of response times to new patterns) on novel dot configurations
varied as an inverse function of their similarity to previously trained
dot configurations Palmeri
(\citeproc{ref-palmeriExemplarSimilarityDevelopment1997}{1997}). That
is, performance was better on novel configurations moderately similar to
trained configurations than to configurations with low-similarity, and
also better on low-similarity configurations than to even less similar,
unrelated configurations. Instance-based similarity approaches have had
some success accounting for performance in certain sub-domains of motor
learning (\citeproc{ref-cohenWhereGraspsAre2004}{R. G. Cohen \&
Rosenbaum, 2004};
\citeproc{ref-crumpEpisodicContributionsSequential2010}{Crump \& Logan,
2010}; \citeproc{ref-meighWhatMemoryRepresentation2018}{Meigh et al.,
2018}; \citeproc{ref-poldrackRelationshipSkillLearning1999}{Poldrack et
al., 1999}; \citeproc{ref-wifallReachingResponseSelection2017}{Wifall et
al., 2017}). Crump \& Logan
(\citeproc{ref-crumpEpisodicContributionsSequential2010}{2010}) trained
participants to type words on an unfamiliar keyboard, while constraining
the letters composing the training words to a pre-specified letter set.
Following training, typing speed was tested on previously experienced
words composed of previously experienced letters; novel words composed
of letters from the trained letter set; and novel words composed of
letters from an untrained letter set. Consistent with an instance-based
account, transfer performance was graded such that participants were
fastest at typing the words they had previously trained on, followed by
novel words composed of letters they had trained on, and slowest
performance for new words composed of untrained letters.

\subsubsection{Issues with Previous
Research}\label{issues-with-previous-research}

Although the benefits of training variation in visuomotor skill learning
have been observed many times, null findings have also been repeatedly
found, leading some researchers to question the veracity of the
variability of practice hypothesis
(\citeproc{ref-newellSchemaTheory19752003}{Newell, 2003};
\citeproc{ref-vanrossumSchmidtSchemaTheory1990}{Van Rossum, 1990}).
Critics have also pointed out that investigations of the effects of
training variability, of the sort described above, often fail to control
for the effect of similarity between training and testing conditions.
For training tasks in which participants have numerous degrees of
freedom (e.g., projectile throwing tasks where participants control the
x and y velocity of the projectile), varied groups are likely to
experience a wider range of the task space over the course of their
training (e.g., more unique combinations of x and y velocities).
Experimenters may attempt to account for this possibility by ensuring
that the training location(s) of the varied and constant groups are an
equal distance away from the eventual transfer locations, such that
their training throws are, on average, equally similar to throws that
would lead to good performance at the transfer locations. However, even
this level of experimental control may still be insufficient to rule out
the effect of similarity on transfer. Given that psychological
similarity is typically best described as either a Gaussian or
exponentially decaying function of psychological distance
(\citeproc{ref-ennisMultidimensionalStochasticTheory1988}{Ennis et al.,
1988};
\citeproc{ref-ghahramaniGeneralizationLocalRemappings1996}{Ghahramani et
al., 1996}; \citeproc{ref-loganInstanceTheoryAutomatization1988}{Logan,
1988}; \citeproc{ref-nosofskySimilarityScalingCognitive1992}{Nosofsky,
1992}; \citeproc{ref-shepardUniversalLawGeneralization1987}{Shepard,
1987}; \citeproc{ref-thoroughmanRapidReshapingHuman2005}{Thoroughman \&
Taylor, 2005}), it is plausible that a subset of the most similar
training instances could have a disproportionate impact on
generalization to transfer conditions, even if the average distance
between training and transfer conditions is identical between groups.
Figure~\ref{fig-toy-model1} demonstrates the consequences of a
generalization gradient that drops off as a Gaussian function of
distance from training, as compared to a linear drop-off.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-toy-model1-1.pdf}}

}

\caption{\label{fig-toy-model1}Left panel- Generalization predicted from
a simple model that assumes a linear generalization function. A varied
group (red vertical lines indicate the 2 training locations) trained
from positions 400 and 800, and a constant group (blue vertical line),
trained from position 600. Right panel- if a Gaussian generalization
function is assumed, then varied training (400, 800) is predicted to
result in better generalization to positions close to 400 and 800 than
does constant training at 600. (For interpretation of the references to
color in this figure legend, the reader is referred to the web version
of this article.)}

\end{figure}%

In addition to largely overlooking the potential for non-linear
generalization to confound interpretations of training manipulations,
the visuomotor skill learning literature also rarely considers
alternatives to schema representations
(\citeproc{ref-chamberlinMemoryRepresentationMotor1992}{Chamberlin \&
Magill, 1992b}). Although schema-theory remains influential within
certain literatures, instance or exemplar-based models have accounted
for human behavior across myriad domains
(\citeproc{ref-jamiesonInstanceTheoryDomaingeneral2022}{Jamieson et al.,
2022}; \citeproc{ref-loganInstanceTheoryAttention2002a}{Logan, 2002}).
As mentioned above, instance based accounts have been shown to perform
well on a variety of different tasks with motoric components
(\citeproc{ref-crumpEpisodicContributionsSequential2010}{Crump \& Logan,
2010}; \citeproc{ref-gandolfoMotorLearningField1996a}{Gandolfo et al.,
1996}; \citeproc{ref-meighWhatMemoryRepresentation2018}{Meigh et al.,
2018}; \citeproc{ref-rosenbaumPlanningReachesEvaluating1995}{Rosenbaum
et al., 1995}; \citeproc{ref-vandamMappingShapeVisuomotor2015}{van Dam
\& Ernst, 2015}). However, such accounts have received little attention
within the subdomain of visuomotor skill learning focused on the
benefits of varied training.

The present work examines whether the commonly observed benefits of
varied training can be accounted for by a theoretically motivated
measure of the similarity between training throws and the testing
solution space. We first attempt to replicate previous work finding an
advantage of varied training over constant training in a projectile
launching task. We then examine the extent to which this advantage can
be explained by an instance-based similarity model.

\subsection{Experiment 1}\label{experiment-1}

\subsubsection{Methods}\label{methods}

\paragraph{Sample Size Estimation}\label{sample-size-estimation}

To obtain an independent estimate of effect size, we identified previous
investigations which included between-subjects contrasts of varied and
constant conditions following training on an accuracy-based projectile
launching task (\citeproc{ref-chuaPracticeVariabilityPromotes2019}{Chua
et al., 2019};
\citeproc{ref-goodwinEffectDifferentQuantities1998}{Goodwin et al.,
1998}; \citeproc{ref-kerrSpecificVariedPractice1978}{Kerr \& Booth,
1978}; \citeproc{ref-wulfEffectTypePractice1991}{Wulf, 1991}). We then
averaged effects across these studies, yielding a Cohen's f =.43. The
GPower 3.1 software package
(\citeproc{ref-faulStatisticalPowerAnalyses2009}{Faul et al., 2009}) was
then used to determine that a power of 80\% requires a sample size of at
least 23 participants per condition. All experiments reported in the
present manuscript exceed this minimum number of participants per
condition.

\paragraph{Participants}\label{participants}

Participants were recruited from an undergraduate population that is
63\% female and consists almost entirely of individuals aged 18 to 22
years. A total of 110 Indiana University psychology students
participated in Experiment 1. We subsequently excluded 34 participants
for poor performance on one of the dependent measures of the task (2.5-3
standard deviations worse than the median subject at the task) or for
displaying a pattern of responses that was clearly indicative of a lack
of engagement with the task (e.g., simply dropping the ball on each
trial rather than throwing it at the target), or for reporting that they
completed the experiment on a phone or tablet device, despite the
instructions not to use one of these devices. A total of 74 participants
were retained for the final analyses, 35 in the varied group and 39 in
the constant group.

\paragraph{Task}\label{task}

The experimental task was programmed in JavaScript, using packages from
the Phaser physics engine (https://phaser.io) and the jsPsych library
(\citeproc{ref-deleeuwJsPsychJavaScriptLibrary2015}{de Leeuw, 2015}).
The stimuli, presented on a black background, consisted of a circular
blue ball - controlled by the participant via the mouse or trackpad
cursor; a rectangular green target; a red rectangular barrier located
between the ball and the target; and an orange square within which the
participant could control the ball before releasing it in a throw
towards the target. Because the task was administered online, the
absolute distance between stimuli could vary depending on the size of
the computer monitor being used, but the relative distance between the
stimuli was held constant. Likewise, the distance between the center of
the target and the training and testing locations was scaled such that
relative distances were preserved regardless of screen size. For the
sake of brevity, subsequent mentions of this relative distance between
stimuli, or the position where the ball landed in relation to the center
of the target, will be referred to simply as distance.
Figure~\ref{fig-IGAS_Methods} displays the layout of the task, as it
would appear to a participant at the start of a trial, with the ball
appearing in the center of the orange square. Using a mouse or trackpad,
participants click down on the ball to take control of the ball,
connecting the movement of the ball to the movement of the cursor.
Participants can then ``wind up'' the ball by dragging it (within the
confines of the orange square) and then launch the ball by releasing the
cursor. If the ball does not land on the target, participants are
presented with feedback in red text at the top right of the screen,
specifying how many scaled units away the ball was from the center of
the target. If the ball was thrown outside of the boundary of the screen
participants are given feedback as to how far away from the target
center the ball would have been if it had continued its trajectory. If
the ball strikes the barrier (from the side or by landing on top),
feedback is presented telling participants to avoid hitting the barrier.
If participants drag the ball outside of the orange square before
releasing it, the trial terminates, and they are reminded to release the
ball within the orange square. If the ball lands on the target, feedback
is presented in green text, confirming that the target was hit, and
presenting additional feedback on how many units away the ball was from
the exact center of the target.

\href{https://pcl.sitehost.iu.edu/tg/demos/igas_expt1_demo.html}{Link to
abbreviated example of task}.

\begin{figure}

\centering{

\includegraphics[width=0.6\linewidth,height=\textheight,keepaspectratio]{../Assets/methodsFig1.png}

}

\caption{\label{fig-IGAS_Methods}The stimuli of the task consisted of a
blue ball, which the participants would launch at the green target,
while avoiding the red barrier. On each trial, the ball would appear in
the center of the orange square, with the position of the orange square
varying between experimental conditions. Participants were constrained
to release the ball within the square.}

\end{figure}%

\paragraph{Procedure}\label{procedure}

Participants first electronically consented to participate, and then
read instructions for the task which explained how to control the ball,
and the goal of throwing the ball as close to the center of the target
as possible. The training phase was split into 10 blocks of 20 trials,
for a total of 200 training trials. Participants in the constant
condition trained exclusively from a single location (760 scaled units
from the target center). Participants in the varied condition trained
from two locations (610 and 910 scaled units from the target center),
encountering each location 100 times. The sequence of throwing locations
was pseudo-random for the varied group, with the constraint that within
every block of 20 training throws both training locations would occur 10
times. Participants in both conditions also received intermittent
testing trials after every 20 training trials. Intermittent testing
trials provided no feedback of any kind. The ball would disappear from
view as soon as it left the orange square, and participants were
prompted to start the next trial without receiving any information about
the accuracy of the throw. Each intermittent testing stage consisted of
two trials from each of the three training positions (i.e.~all
participants executed two trials each from Positions 610, 760, and 910
during each of the 10 intermittent testing stages). Following training,
all participants completed a final testing phase from four positions: 1)
their training location, 2) the training location(s) of the other group,
3) a location novel to both groups. The testing phase consisted of 15
trials from each of the four locations, presented in a randomized order.
All trials in the final testing phase included feedback. After finishing
the final testing portion of the study, participants were queried as to
whether they completed the study using a mouse, a trackpad, or some
other device (this information was used in the exclusion process
described above). Finally, participants were debriefed as to the
hypotheses and manipulation of the study.

\subsubsection{Results}\label{results}

\paragraph{Data Processing and Statistical
Packages}\label{data-processing-and-statistical-packages}

To prepare the data, we removed trials that were not easily
interpretable as performance indicators in our task. Removed trials
included: 1) those in which participants dragged the ball outside of the
orange starting box without releasing it, 2) trials in which
participants clicked on the ball, and then immediately released it,
causing the ball to drop straight down, 3) outlier trials in which the
ball was thrown more than 2.5 standard deviations further than the
average throw (calculated separately for each throwing position), and 4)
trials in which the ball struck the barrier. The primary measure of
performance used in all analyses was the absolute distance away from the
center of the target. The absolute distance was calculated on every
trial, and then averaged within each subject to yield a single
performance score, for each position. A consistent pattern across
training and testing phases in both experiments was for participants to
perform worse from throwing positions further away from the target -- a
pattern which we refer to as the difficulty of the positions. However,
there were no interactions between throwing position and training
conditions, allowing us to collapse across positions in cases where
contrasts for specific positions were not of interest. All data
processing and statistical analyses were performed in R version 4.32
(\citeproc{ref-rcoreteamLanguageEnvironmentStatistical2020}{Team,
2020}). ANOVAs for group comparisons were performed using the rstatix
package
(\citeproc{ref-kassambaraRstatixPipeFriendlyFramework2021a}{Kassambara,
2021}).

\paragraph{Training Phase}\label{training-phase}

Figure~\ref{fig-IGAS_Training1} below shows aggregate training
performance binned into three stages representing the beginning, middle,
and end of the training phase. Because the two conditions trained from
target distances that were not equally difficult, it was not possible to
directly compare performance between conditions in the training phase.
Our focus for the training data analysis was instead to establish that
participants did improve their performance over the course of training,
and to examine whether there was any interaction between training stage
and condition. Descriptive statistics for the intermittent testing phase
are provided in the supplementary materials.

We performed an ANOVA comparison with stage as a within-group factor and
condition as between-group factor. The analysis revealed a significant
effect of training stage F(2,142)=62.4, p\textless.001, \(\eta^{2}_G\) =
.17, such that performance improved over the course of training. There
was no significant effect of condition F(1,71)=1.42, p=.24,
\(\eta^{2}_G\) = .02, and no significant interaction between condition
and training stage, F(2,142)=.10, p=.91, \(\eta^{2}_G\) \textless{} .01.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-IGAS_Training1-1.pdf}}

}

\caption{\label{fig-IGAS_Training1}Training performance for varied and
constant participants binned into three stages. Shorter bars indicate
better performance (ball landing closer to the center of the target).
Error bars indicate standard error of the mean.}

\end{figure}%

\paragraph{Testing Phase}\label{testing-phase}

In Experiment 1, a single constant-trained group was compared against a
single varied-trained group. At the transfer phase, all participants
were tested from 3 positions: 1) the positions(s) from their own
training, 2) the training position(s) of the other group, and 3) a
position novel to both groups. Overall, group performance was compared
with a mixed type III ANOVA, with condition (varied vs.~constant) as a
between-subject factor and throwing location as a within-subject
variable. The effect of throwing position was strong, F(3,213) = 56.12,
p\textless.001, η2G = .23. The effect of training condition was
significant F(1,71)=8.19, p\textless.01, η2G = .07. There was no
significant interaction between group and position, F(3,213)=1.81,
p=.15, η2G = .01.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-IGAS_Testing1-1.pdf}}

}

\caption{\label{fig-IGAS_Testing1}Testing performance for each of the 4
testing positions, compared between training conditions. Positions 610
and 910 were trained on by the varied group, and novel for the constant
group. Position 760 was trained on by the constant group, and novel for
the varied group. Position 835 was novel for both groups. Shorter bars
are indicative of better performance (the ball landing closer to the
center of the target). Error bars indicate standard error of the mean.}

\end{figure}%

\hfill\break
\hfill\break

\begin{longtable}[]{@{}lll@{}}

\caption{\label{tbl-IGAS_Table1}Testing performance for varied and
constant groups in experiment 1. Mean absolute deviation from the center
of the target, with standard deviations in parenthesis.}

\tabularnewline

\toprule\noalign{}
Position & Constant & Varied \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
610 & 132.48(50.85) & 104.2(38.92) \\
760 & 207.26(89.19) & 167.12(72.29) \\
835 & 249.13(105.92) & 197.22(109.71) \\
910 & 289.36(122.48) & 212.86(113.93) \\

\end{longtable}

\subsubsection{Discussion}\label{discussion}

In Experiment 1, we found that varied training resulted in superior
testing performance than constant training, from both a position novel
to both groups, and from the position at which the constant group was
trained, which was novel to the varied condition. The superiority of
varied training over constant training even at the constant training
position is of particular note, given that testing at this position
should have been highly similar for participants in the constant
condition. It should also be noted, though, that testing at the constant
trained position is not identical to training from that position, given
that the context of testing is different in several ways from that of
training, such as the testing trials from the different positions being
intermixed, as well as a simple change in context as a function of time.
Such contextual differences will be further considered in the General
Discussion.

In addition to the variation of throwing position during training, the
participants in the varied condition of Experiment 1 also received
training practice from the closest/easiest position, as well as from the
furthest/most difficult position that would later be encountered by all
participants during testing. The varied condition also had the potential
advantage of interpolating both of the novel positions from which they
would later be tested. Experiment 2 thus sought to address these issues
by comparing a varied condition to multiple constant conditions.

\subsection{Experiment 2}\label{experiment-2}

In Experiment 2, we sought to replicate our findings from Experiment 1
with a new sample of participants, while also addressing the possibility
of the pattern of results in Experiment 1 being explained by some
idiosyncrasy of the particular training location of the constant group
relative to the varied group. To this end, Experiment 2 employed the
same basic procedure as Experiment 1, but was designed with six separate
constant groups each trained from one of six different locations (400,
500, 625, 675, 800, or 900), and a varied group trained from two
locations (500 and 800). Participants in all seven groups were then
tested from each of the 6 unique positions.

\subsubsection{Methods}\label{methods-1}

\paragraph{Participants}\label{participants-1}

A total of 306 Indiana University psychology students participated in
Experiment 2, which was also conducted online. As was the case in
Experiment 1, the undergraduate population from which we recruited
participants was 63\% female and primarily composed of 18--22-year-old
individuals. Using the same procedure as Experiment 1, we excluded 98
participants for exceptionally poor performance at one of the dependent
measures of the task, or for displaying a pattern of responses
indicative of a lack of engagement with the task. A total of 208
participants were included in the final analyses with 31 in the varied
group and 32, 28, 37, 25, 29, 26 participants in the constant groups
training from location 400, 500, 625, 675, 800, and 900, respectively.
All participants were compensated with course credit.

\paragraph{Task and Procedure}\label{task-and-procedure}

The task of Experiment 2 was identical to that of Experiment 1, in all
but some minor adjustments to the height of the barrier, and the
relative distance between the barrier and the target. Additionally, the
intermittent testing trials featured in experiment 1 were not utilized
in Experiment 2. An abbreviated demo of the task used for Experiment 2
can be found at
(https://pcl.sitehost.iu.edu/tg/demos/igas\_expt2\_demo.html).

The procedure for Experiment 2 was also quite similar to Experiment 1.
Participants completed 140 training trials, all of which were from the
same position for the constant groups and split evenly (70 trials each -
randomized) for the varied group. In the testing phase, participants
completed 30 trials from each of the six locations that had been used
separately across each of the constant groups during training. Each of
the constant groups thus experienced one trained location and five novel
throwing locations in the testing phase, while the varied group
experiences 2 previously trained, and 4 novel locations.

\subsubsection{Results}\label{results-1}

\paragraph{Data Processing and Statistical
Packages}\label{data-processing-and-statistical-packages-1}

After confirming that condition and throwing position did not have any
significant interactions, we standardized performance within each
position, and then average across position to yield a single performance
measure per participant. This standardization did not influence our
pattern of results. As in Experiment 1, we performed type III ANOVAs due
to our unbalanced design, however the pattern of results presented below
is not altered if type 1 or type III tests are used instead. The
statistical software for the primary analyses was the same as for
Experiment 1. Individual learning rates in the testing phase, compared
between groups in the supplementary analyses, were fit using the TEfit
package in R
(\citeproc{ref-cochraneTEfitsNonlinearRegression2020}{Cochrane, 2020}).

\paragraph{Training Phase}\label{training-phase-1}

The different training conditions trained from positions that were not
equivalently difficult and are thus not easily amenable to comparison.
As previously stated, the primary interest of the training data is
confirmation that some learning did occur. Figure~\ref{fig-e2train}
depicts the training performance of the varied group alongside that of
the aggregate of the six constant groups (5a), and each of the 6
separate constant groups (5b). An ANOVA comparison with training stage
(beginning, middle, end) as a within-group factor and group (the varied
condition vs.~the 6 constant conditions collapsed together) as a
between-subject factor revealed no significant effect of group on
training performance, F(1,206)=.55,p=.49, \(\eta^{2}_G\) \textless.01, a
significant effect of training stage F(2,412)=77.91, p\textless.001,
\(\eta^{2}_G\) =.05, and no significant interaction between group and
training stage, F(2,412)=.489 p=.61, \(\eta^{2}_G\) \textless.01. We
also tested for a difference in training performance between the varied
group and the two constant groups that trained matching throwing
positions (i.e., the constant groups training from position 500, and
position 800). The results of our ANOVA on this limited dataset mirrors
that of the full-group analysis, with no significant effect of group
F(1,86)=.48, p=.49, \(\eta^{2}_G\) \textless.01, a significant effect of
training stage F(2,172)=56.29, p\textless.001, \(\eta^{2}_G\) =.11, and
no significant interaction between group and training stage,
F(2,172)=.341 p=.71, \(\eta^{2}_G\) \textless.01.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2train-1.pdf}}

}

\caption{\label{fig-e2train}Training performance for the six constant
conditions, and the varied condition, binned into three stages. On the
left side, the six constant groups are averaged together, as are the two
training positions for the varied group. On the right side, the six
constant groups are shown separately, with each set of bars representing
the beginning, middle, and end of training for a single constant group
that trained from the position indicated on the x-axis. Figure 5b also
shows training performance separately for both throwing locations
trained by the varied group. Error bars indicate standard error of the
mean.}

\end{figure}%

\paragraph{Testing Phase}\label{testing-phase-1}

In Experiment 2, a single varied condition (trained from two positions,
500 and 800), was compared against six separate constant groups (trained
from a single position, 400, 500, 625, 675, 800 or 900). For the testing
phase, all participants were tested from all six positions, four of
which were novel for the varied condition, and five of which were novel
for each of the constant groups. For a general comparison, we took the
absolute deviations for each throwing position and computed standardized
scores across all participants, and then averaged across throwing
position. The six constant groups were then collapsed together allowing
us to make a simple comparison between training conditions (constant
vs.~varied). A type III between-subjects ANOVA was performed, yielding a
significant effect of condition F(1,206)=4.33, p=.039, \(\eta^{2}_G\)
=.02. Descriptive statistics for each condition are shown in table 2. In
Figure~\ref{fig-e2testa} visualizes the consistent advantage of the
varied condition over the constant groups across the testing positions.
Figure~\ref{fig-e2testa} shows performance between the varied condition
and the individual constant groups.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2testa-1.pdf}}

}

\caption{\label{fig-e2testa}Testing phase performance from each of the
six testing positions. The six constant conditions are averaged together
into a single constant group, compared against the single varied-trained
group.B) Transfer performance from each of the 6 throwing locations from
which all participants were tested. Each bar represents performance from
one of seven distinct training groups (six constant groups in red, one
varied group in blue). The x axis labels indicate the location(s) from
which each group trained. Lower values along the y axis reflect better
performance at the task (closer distance to target center). Error bars
indicate standard error of the mean.}

\end{figure}%

\hfill\break
\hfill\break
\hfill\break

\begin{longtable}[]{@{}lll@{}}

\caption{\label{tbl-e2table1}Transfer performance from each of the 6
throwing locations from which all participants were tested. Each bar
represents performance from one of seven distinct training groups (six
constant groups in red, one varied group in blue). The x axis labels
indicate the location(s) from which each group trained. Lower values
along the y axis reflect better performance at the task (closer distance
to target center). Error bars indicate standard error of the mean.}

\tabularnewline

\toprule\noalign{}
Position & Constant & Varied \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
400 & 100.59(46.3) & 83.92(33.76) \\
500 & 152.28(69.82) & 134.38(61.38) \\
625 & 211.21(90.95) & 183.51(75.92) \\
675 & 233.32(93.35) & 206.32(94.64) \\
800 & 283.24(102.85) & 242.65(89.73) \\
900 & 343.51(114.33) & 289.62(110.07) \\

\end{longtable}

Next, we compared the testing performance of constant and varied groups
from only positions that participants had not encountered during
training. Constant participants each had 5 novel positions, whereas
varied participants tested from 4 novel positions (400,625,675,900). We
first standardized performance within in each position, and then
averaged across positions. Here again, we found a significant effect of
condition (constant vs.~varied): F(1,206)=4.30, p=.039, \(\eta^{2}_G\) =
.02 .

\begin{longtable}[]{@{}lll@{}}

\caption{\label{tbl-e2table2}Testing performance from novel positions.
Includes data only from positions that were not encountered during the
training stage (e.g., excludes positions 500 and 800 for the varied
group, and one of the six locations for each of the constant groups).
Table presents Mean absolute deviations from the center of the target,
and standard deviations in parenthesis.}

\tabularnewline

\toprule\noalign{}
Position & Constant & Varied \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
400 & 98.84(45.31) & 83.92(33.76) \\
500 & 152.12(69.94) & NA \\
625 & 212.91(92.76) & 183.51(75.92) \\
675 & 232.9(95.53) & 206.32(94.64) \\
800 & 285.91(102.81) & NA \\
900 & 346.96(111.35) & 289.62(110.07) \\

\end{longtable}

Finally, corresponding to the comparison of position 760 from Experiment
1, we compared the test performance of the varied group against the
constant group from only the positions that the constant groups trained.
Such positions were novel to the varied group (thus this analysis
omitted two constant groups that trained from positions 500 or 800 as
those positions were not novel to the varied group).
Figure~\ref{fig-e2test1} displays the subset of comparisons utilized for
this analysis. Again, we standardized performance within each position
before performing the analyses on the aggregated data. In this case, the
effect of condition did not reach statistical significance
F(1,149)=3.14, p=.079, \(\eta^{2}_G\) = .02. Table 4 provides
descriptive statistics.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2test1-1.pdf}}

}

\caption{\label{fig-e2test1}A comparison of throwing location that are
identical to those trained by the constant participants (e.g., constant
participants trained at position 900, tested from position 900), which
are also novel to the varied-trained participants (thus excluding
positions 500 and 800). Error bars indicate standard error of the mean.}

\end{figure}%

\hfill\break
\hfill\break

\begin{longtable}[]{@{}lll@{}}

\caption{\label{tbl-e2tab3}Testing performance from the locations
trained by constant participants and novel to varied participants.
Locations 500 and 800 are not included as these were trained by the
varied participants. Table presents Mean absolute deviation from the
center of the target, and standard deviations in parenthesis.}

\tabularnewline

\toprule\noalign{}
Position & Constant & Varied \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
400 & 108.85(50.63) & 83.92(33.76) \\
625 & 204.75(84.66) & 183.51(75.92) \\
675 & 235.75(81.15) & 206.32(94.64) \\
900 & 323.5(130.9) & 289.62(110.07) \\

\end{longtable}

\subsubsection{Experiment 2 Discussion}\label{experiment-2-discussion}

The results of Experiment 2 largely conform to the findings of
Experiment 1. Participants in both varied and constant conditions
improved at the task during the training phase. We did not observe the
common finding of training under varied conditions producing worse
performance during acquisition than training under constant conditions
(\citeproc{ref-catalanoDistantTransferCoincident1984a}{Catalano \&
Kleiner, 1984};
\citeproc{ref-wrisbergVariabilityPracticeHypothesis1987}{Wrisberg et
al., 1987}), which has been suggested to relate to the subsequent
benefits of varied training in retention and generalization testing
(\citeproc{ref-soderstromLearningPerformanceIntegrative2015}{Soderstrom
\& Bjork, 2015}). However, our finding of no difference in training
performance between constant and varied groups has been observed in
previous work (\citeproc{ref-chuaPracticeVariabilityPromotes2019}{Chua
et al., 2019};
\citeproc{ref-moxleySchemaVariabilityPractice1979}{Moxley, 1979};
\citeproc{ref-pigottMotorSchemaStructure1984}{Pigott \& Shapiro, 1984}).

In the testing phase, our varied group significantly outperformed the
constant conditions in both a general comparison, and in an analysis
limited to novel throwing positions. The observed benefit of varied over
constant training echoes the findings of many previous visuomotor skill
learning studies that have continued to emerge since the introduction of
Schmidt's influential Schema Theory
(\citeproc{ref-catalanoDistantTransferCoincident1984a}{Catalano \&
Kleiner, 1984}; \citeproc{ref-chuaPracticeVariabilityPromotes2019}{Chua
et al., 2019};
\citeproc{ref-goodwinEffectDifferentQuantities1998}{Goodwin et al.,
1998}; \citeproc{ref-mccrackenTestSchemaTheory1977}{McCracken \&
Stelmach, 1977};
\citeproc{ref-moxleySchemaVariabilityPractice1979}{Moxley, 1979};
\citeproc{ref-newellVariabilityPracticeTransfer1976}{Newell \& Shapiro,
1976}; \citeproc{ref-pigottMotorSchemaStructure1984}{Pigott \& Shapiro,
1984}; \citeproc{ref-rollerVariablePracticeLenses2001}{Roller et al.,
2001}; \citeproc{ref-schmidtSchemaTheoryDiscrete1975}{Schmidt, 1975};
\citeproc{ref-willeyLongtermMotorLearning2018}{Willey \& Liu, 2018b};
\citeproc{ref-wrisbergVariabilityPracticeHypothesis1987}{Wrisberg et
al., 1987}; \citeproc{ref-wulfEffectTypePractice1991}{Wulf, 1991}). We
also join a much smaller set of research to observe this pattern in a
computerized task (\citeproc{ref-seowTransferEffectsVaried2019}{Seow et
al., 2019}). One departure from the experiment 1 findings concerns the
pattern wherein the varied group outperformed the constant group even
from the training position of the constant group, which was significant
in experiment 1, but did not reach significance in experiment 2.
Although this pattern has been observed elsewhere in the literature
(\citeproc{ref-goodeSuperiorityVariableRepeated2008}{Goode et al.,
2008}; \citeproc{ref-kerrSpecificVariedPractice1978}{Kerr \& Booth,
1978}), the overall evidence for this effect appears to be far weaker
than for the more general benefit of varied training in conditions novel
to all training groups.

\subsection{Computational Model}\label{computational-model}

\emph{Controlling for the similarity between training and testing.} The
primary goal of Experiment 2 was to examine whether the benefits of
variability would persist after accounting for individual differences in
the similarity between trained and tested throwing locations. To this
end, we modelled each throw as a two-dimensional point in the space of x
and y velocities applied to the projectile at the moment of release. For
each participant, we took each individual training throw, and computed
the similarity between that throw and the entire population of throws
within the solution space for each of the 6 testing positions. We
defined the solution space empirically as the set of all combinations of
x and y throw velocities that resulted in hitting the target. We then
summed each of the trial-level similarities to produce a single
similarity for each testing position score relating how the participant
threw the ball during training and the solutions that would result in
target hits from each of the six testing positions -- thus resulting in
six separate similarity scores for each participant.
Figure~\ref{fig-taskSpace} visualizes the solution space for each
location and illustrates how different combinations of x and y velocity
result in successfully striking the target from different launching
positions. As illustrated in Figure~\ref{fig-taskSpace}, the solution
throws represent just a small fraction of the entire space of velocity
combinations used by participants throughout the experiment.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-taskSpace-1.pdf}}

}

\caption{\label{fig-taskSpace}A) A visual representation of the
combinations of throw parameters (x and y velocities applied to the ball
at launch), which resulted in target hits during the testing phase. This
empirical solution space was compiled from all of the participants in
Experiment 2. B) shows the solution space within the context of all of
the throws made throughout the testing phase of the experiment.}

\end{figure}%

For each individual trial, the Euclidean distance (Equation 1) was
computed between the velocity components (x and y) of that trial and the
velocity components of each individual solution throw for each of the 6
positions from which participants would be tested in the final phase of
the study. The P parameter in Equation 1 is set equal to 2, reflecting a
Gaussian similarity gradient. Then, as per an instance-based model of
similarity (\citeproc{ref-loganInstanceTheoryAttention2002a}{Logan,
2002}; \citeproc{ref-nosofskySimilarityScalingCognitive1992}{Nosofsky,
1992}), these distances were multiplied by a sensitivity parameter, c,
and then exponentiated to yield a similarity value. The parameter c
controls the rate with which similarity-based generalization drops off
as the Euclidean distance between two throws in x- and y-velocity space
increases. If c has a large value, then even a small difference between
two throws' velocities greatly decreases the extent of generalization
from one to the other. A small value for c produces broad generalization
from one throw to another despite relatively large differences in their
velocities. The similarity values for each training individual throw
made by a given participant were then summed to yield a final similarity
score, with a separate score computed for each of the 6 testing
positions. The final similarity score is construable as index of how
accurate the throws a participant made during the training phase would
be for each of the testing positions.

\textbf{Equation 1:}
\[ Similarity_{I,J} = \sum_{i=I}\sum_{j=J} (e^{-c^\cdot d^{p}_{i,j}}) \]

\textbf{Equation 2:}
\[ d_{i,j} = \sqrt{(x_{Train_i}-x_{Solution_j})^2 + (y_{Train_i}-y_{Solution_j})^2 } \]

A simple linear regression revealed that these similarity scores were
significantly predictive of performance in the transfer stage, t
=-15.88, p\textless.01, \(r^2\)=.17, such that greater similarity
between training throws and solution spaces for each of the test
locations resulted in better performance. We then repeated the group
comparisons above while including similarity as a covariate in the
model. Comparing the varied and constant groups in testing performance
from all testing positions yielded a significant effect of similarity,
F(1, 205)=85.66, p\textless.001, \(\eta^{2}_G\) =.29, and also a
significant effect of condition (varied vs.~constant), F(1, 205)=6.03,
p=.015, \(\eta^{2}_G\) =.03. The group comparison limited to only novel
locations for the varied group pit against trained location for the
constant group resulted in a significant effect of similarity,
F(1,148)=31.12, p\textless.001, \(\eta^{2}_G\) =.18 as well as for
condition F(1,148)=11.55, p\textless.001, \(\eta^{2}_G\) =.07. For all
comparisons, the pattern of results was consistent with the initial
findings from Experiment 2, with the varied group still performing
significantly better than the constant group.

\subsubsection{Fitting model parameters separately by
group}\label{fitting-model-parameters-separately-by-group}

To directly control for similarity in Experiment 2, we developed a
model-based measure of the similarity between training throws and
testing conditions. This similarity measure was a significant predictor
of testing performance, e.g., participants whose training throws were
more similar to throws that resulted in target hits from the testing
positions, tended to perform better during the testing phase.
Importantly, the similarity measure did not explain away the group-level
benefits of varied training, which remained significant in our linear
model predicting testing performance after similarity was added to the
model. However, previous research has suggested that participants may
differ in their level of generalization as a function of prior
experience, and that such differences in generalization gradients can be
captured by fitting the generalization parameter of an instance-based
model separately to each group
(\citeproc{ref-hahnEffectsCategoryDiversity2005}{Hahn et al., 2005};
\citeproc{ref-lambertsFlexibleTuningSimilarity1994}{Lamberts, 1994}).
Relatedly, the influential Bayesian generalization model developed by
Tenenbaum \& Griffiths
(\citeproc{ref-tenenbaumGeneralizationSimilarityBayesian2001a}{2001})
predicts that the breadth of generalization will increase when a
rational agent encounters a wider variety of examples. Following these
leads, we assume that in addition to learning the task itself,
participants are also adjusting how generalizable their experience
should be. Varied versus constant participants may be expected to learn
to generalize their experience to different degrees. To accommodate this
difference, the generalization parameter of the instance-based model (in
the present case, the \(c\) parameter) can be allowed to vary between
the two groups to reflect the tendency of learners to adaptively tune
the extent of their generalization. One specific hypothesis is that
people adaptively set a value of c to fit the variability of their
training experience
(\citeproc{ref-nosofskyExemplarbasedAccountsMultiplesystem2000}{Nosofsky
\& Johansen, 2000};
\citeproc{ref-sakamotoTrackingVariabilityLearning2006}{Sakamoto et al.,
2006}). If one's training experience is relatively variable, as with the
variable training condition, then one might infer that future test
situations will also be variable, in which case a low value of c will
allow better generalization because generalization will drop off slowly
with training-to-testing distance. Conversely, if one's training
experience has little variability, as found in the constant training
conditions, then one might adopt a high value of \(c\) so that
generalization falls off rapidly away from the trained positions.

To address this possibility, we compared the original instance-based
model of similarity fit against a modified model which separately fits
the generalization parameter, \(c\), to varied and constant
participants. To perform this parameter fitting, we used the optim
function in R, and fit the model to find the \(c\) value(s) that
maximized the correlation between similarity and testing performance.

Both models generate distinct similarity values between training and
testing locations. Much like the analyses in Experiment 2, these
similarity values are regressed against testing performance in models of
the form shown below. As was the case previously, testing performance is
defined as the mean absolute distance from the center of the target
(with a separate score for each participant, from each position).

Linear models 1 and 3 both show that similarity is a significant
predictor of testing performance (p\textless.01). Of greater interest is
the difference between linear model 2, in which similarity is computed
from a single \(c\) value fit from all participants (Similarity1c), with
linear model 4, which fits the \(c\) parameter separately between groups
(Similarity2c). In linear model 2, the effect of training group remains
significant when controlling for Similarity1c (p\textless.01), with the
varied group still performing significantly better. However, in linear
model 4 the addition of the Similarity2c predictor results in the effect
of training group becoming nonsignificant (p=.40), suggesting that the
effect of varied vs.~constant training is accounted for by the
Similarity2c predictor. Next, to further establish a difference between
the models, we performed nested model comparisons using ANOVA, to see if
the addition of the training group parameter led to a significant
improvement in model performance. In the first comparison, ANOVA(Linear
Model 1, Linear Model 2), the addition of the training group predictor
significantly improved the performance of the model (F=22.07,
p\textless.01). However, in the second model comparison, ANOVA (Linear
model 3, Linear Model 4) found no improvement in model performance with
the addition of the training group predictor (F=1.61, p=.20).

Finally, we sought to confirm that similarity values generated from the
adjusted Similarity2c model had more predictive power than those
generated from the original Similarity1c model. Using the BIC function
in R, we compared BIC values between linear model 1 (BIC=14604.00) and
linear model 3 (BIC = 14587.64). The lower BIC value of model 3 suggests
a modest advantage for predicting performance using a similarity measure
computed with two \(c\) values over similarity computed with a single
\(c\) value. When fit with separate \(c\) values, the best fitting \(c\)
parameters for the model consistently optimized such that the \(c\)
value for the varied group (c=.00008) was smaller in magnitude than the
\(c\) value for the constant group (c= .00011). Recall that similarity
decreases as a Gaussian function of distance (equation 1 above), and a
smaller value of \(c\) will result in a more gradual drop-off in
similarity as the distance between training throws and testing solutions
increases.

In summary, our modeling suggests that an instance-based model which
assumes equivalent generalization gradients between constant and varied
trained participants is unable to account for the extent of benefits of
varied over constant training observed at testing. The evidence for this
in the comparative model fits is that when a varied/constant dummy-coded
variable for condition is explicitly added to the model, the variable
adds a significant contribution to the prediction of test performance,
with the variable condition yielding better performance than the
constant conditions. However, if the instance-based generalization model
is modified to assume that the training groups can differ in the
steepness of their generalization gradient, by incorporating a separate
generalization parameter for each group, then the instance-based model
can account for our experimental results without explicitly taking
training group into account. Henceforth this model will be referred to
as the Instance-based Generalization with Adaptive Similarity (IGAS)
model.

\subsection{Project 1 General
Discussion}\label{project-1-general-discussion}

Across two experiments, we found evidence in support of the benefits of
variability hypothesis in a simple, computerized projectile throwing
task. Generalization was observed in both constant and varied
participants, in that both groups tended to perform better at novel
positions in the testing phase than did participants who started with
those positions in the training phase. However, varied trained
participants consistently performed better than constant trained
participants, in terms of both the testing phase in general, and in a
comparison that only included untrained positions. We also found some
evidence for the less commonly observed pattern wherein varied-trained
participants outperform constant-trained participants even from
conditions identical to the constant group training
(\citeproc{ref-goodeSuperiorityVariableRepeated2008}{Goode et al.,
2008}; \citeproc{ref-greenPracticeVariabilityTransfer1995a}{Green et
al., 1995}; \citeproc{ref-kerrSpecificVariedPractice1978}{Kerr \& Booth,
1978}). In Experiment 1 varied participants performed significantly
better on this identity comparison. In Experiment 2, the comparison was
not significant initially, but became significant after controlling for
the similarity measure that incorporates only a single value for the
steepness of similarity-based generalization (\(c\)). Furthermore, we
showed that the general pattern of results from Experiment 2 could be
parsimoniously accommodated by an instance-based similarity model, but
only with the assumption that constant and varied participants
generalize their training experience to different degrees.

Our results thus suggest that the benefits of variation cannot be
explained by the varied-trained participants simply covering a broader
range of the task space. Rather, the modeling suggests that varied
participants also learn to adaptively tune their generalization function
such that throwing locations generalize more broadly to one another than
they do in the constant condition. A learning system could end up
adopting a higher \(c\) value in the constant than variable training
conditions by monitoring the trial-by-trial variability of the training
items. The \(c\) parameter would be adapted downwards when adjacent
training items are dissimilar to each other and adapted upwards when
adjacent training items are the same. In this fashion, contextually
appropriate \(c\) values could be empirically learned. This learning
procedure would capture the insight that if a situation has a high
amount variability, then the learner should be predisposed toward
thinking that subsequent test items will also show considerable
variability, in which case generalization gradients should be broad, as
is achieved by low values for \(c\). Sakamoto et al.
(\citeproc{ref-sakamotoTrackingVariabilityLearning2006}{2006})
implemented a similar learning mechanism for updating the generalization
paramater in an exemplar-based model (although in their model, a
separate generalization parameter is assigned to each exemplar). In
their experiment, participants were trained on a high variability and a
low variability category, and the dynamically updated generalization
parameter was necessary to account for broader generalization observed
around the high variability category when participants were tested with
an ambiguous intermediary item. In a subsequent work
(\citeproc{ref-sakamotoPuttingPsychologyBack2008}{Sakamoto et al.,
2008}), the same authors showed that a similar learning mechanism could
account for the pattern wherein participants generalize more broadly
around a category when the average distance between the category
exemplars is larger (however the only model tested in this work was a
prototype model).

Also of interest is whether the IGAS model can predict the pattern of
results wherein the varied condition outperforms the constant condition
even from the position on which the constant condition trained. Although
our models were fit using all of the Experiment 2 training and testing
data, not just that of the identity comparisons, in
Figure~\ref{fig-Toy-Model-dis} we demonstrate how a simplified version
of the IGAS model could in principle produce such a pattern. In addition
to the assumption of differential generalization between varied and
constant conditions, our simplified model makes explicit an assumption
that is incorporated into the full IGAS model -- namely that even when
being tested from a position identical to that which was trained, there
are always some psychological contextual differences between training
and testing throws, resulting in a non-zero dissimilarity.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-Toy-Model-dis-1.pdf}}

}

\caption{\label{fig-Toy-Model-dis}A simple model depicting the necessity
of both of two separately fit generalization parameters, c, and a
positive distance between training and testing contexts, in order for an
instance model to predict a pattern of varied training from stimuli 400
and 800 outperforming constant training from position 600 at a test
position of 600. For the top left panel, in which the generalization
model assumes a single c value (-.008) for both varied and constant
conditions, and identical contexts across training and testing, the
equation which generates the varied condition is - Amount of
Generalization = \(e^{(c\cdot|x-800|)} + e^{(c\cdot|x-400|)}\), whereas
the constant group generalization is generated from
\(2\cdot e^{(c\cdot|x-600|)}\). For the top right panel, the c constants
in the original equations are different for the 2 conditions, with
\(c=-.002\) for the varied condition, and \(c=-.008\) for the constant
condition. The bottom two panels are generated from identical equations
to those immediately above, except for the addition of extra distance
(100 units) to reflect the assumption of some change in context between
training and testing conditions. Thus, the generalization model for the
varied condition in the bottom-right panel is of the form - Amount of
Generalization =
\(e^{(c_{varied}\cdot|x-800|)}+e^{(c_{varied}\cdot|x-400|)}\) .}

\end{figure}%

As described above, the idea that learners flexibly adjust their
generalization gradient based on prior experience does have precedent in
the domains of category learning
(\citeproc{ref-ahaConceptLearningFlexible1992}{Aha \& Goldstone, 1992};
\citeproc{ref-briscoeConceptualComplexityBias2011}{Briscoe \& Feldman,
2011}; \citeproc{ref-hahnEffectsCategoryDiversity2005}{Hahn et al.,
2005}; \citeproc{ref-lambertsFlexibleTuningSimilarity1994}{Lamberts,
1994}; \citeproc{ref-opdebeeckRepresentationPerceivedShape2008}{Op de
Beeck et al., 2008}), and sensorimotor adaptation
(\citeproc{ref-marongelliAdvantageFlexibleNeuronal2013}{Marongelli \&
Thoroughman, 2013};
\citeproc{ref-taylorContextdependentGeneralization2013}{Taylor \& Ivry,
2013}; \citeproc{ref-thoroughmanRapidReshapingHuman2005}{Thoroughman \&
Taylor, 2005}). Lamberts
(\citeproc{ref-lambertsFlexibleTuningSimilarity1994}{1994}) showed that
a simple manipulation of background knowledge during a categorization
test resulted in participants generalizing their training experience
more or less broadly, and moreover that such a pattern could be captured
by allowing the generalization parameter of an instance-based similarity
model to be fit separately between conditions. The flexible
generalization parameter has also successfully accounted for
generalization behavior in cases where participants have been trained on
categories that differ in their relative variability
(\citeproc{ref-hahnEffectsCategoryDiversity2005}{Hahn et al., 2005};
\citeproc{ref-sakamotoTrackingVariabilityLearning2006}{Sakamoto et al.,
2006}). However, to the best of our knowledge, IGAS is the first
instance-based similarity model that has been put forward to account for
the effect of varied training in a visuomotor skill task. Although IGAS
was inspired by work in the domain of category learning, its success in
a distinct domain may not be surprising in light of the numerous prior
observations that at least certain aspects of learning and
generalization may operate under common principles across different
tasks and domains (\citeproc{ref-censorCommonMechanismsHuman2012}{Censor
et al., 2012}; \citeproc{ref-hillsCentralExecutiveSearch2010}{Hills et
al., 2010};
\citeproc{ref-jamiesonInstanceTheoryDomaingeneral2022}{Jamieson et al.,
2022}; \citeproc{ref-lawSharedMechanismsPerceptual2010}{Law \& Gold,
2010}; \citeproc{ref-roarkComparingPerceptualCategory2021}{Roark et al.,
2021};
\citeproc{ref-rosenbaumAcquisitionIntellectualPerceptualMotor2001}{Rosenbaum
et al., 2001}; \citeproc{ref-vigoLearningDifficultyVisual2018}{Vigo et
al., 2018};
\citeproc{ref-wallIdentifyingRelationshipsCognitive2021}{Wall et al.,
2021}; \citeproc{ref-wuSimilaritiesDifferencesSpatial2020}{Wu et al.,
2020}; \citeproc{ref-yangGeneralLearningAbility2020}{J. Yang et al.,
2020}).

Our modelling approach does differ from category learning
implementations of instance-based models in several ways. One such
difference is the nature of the training instances that are assumed to
be stored. In category learning studies, instances are represented as
points in a multidimensional space of all of the attributes that define
a category item (e.g., size/color/shape). Rather than defining instances
in terms of what stimuli learners experience, our approach assumes that
stored, motor instances reflect how they act, in terms of the velocity
applied to the ball on each throw. An advantage of many motor learning
tasks is the relative ease with which task execution variables can be
directly measured (e.g., movement force, velocity, angle, posture) in
addition to the decision and response time measures that typically
exhaust the data generated from more classical cognitive tasks. Of
course, whether learners actually are storing each individual motor
instance is a fundamental question beyond the scope of the current work
-- though as described in the introduction there is some evidence in
support of this idea
(\citeproc{ref-chamberlinNoteSchemaExemplar1992}{Chamberlin \& Magill,
1992a}; \citeproc{ref-crumpEpisodicContributionsSequential2010}{Crump \&
Logan, 2010}; \citeproc{ref-hommelEventFilesEvidence1998}{Hommel, 1998};
\citeproc{ref-meighWhatMemoryRepresentation2018}{Meigh et al., 2018};
\citeproc{ref-poldrackRelationshipSkillLearning1999}{Poldrack et al.,
1999}). A particularly noteworthy instance-based model of sensory-motor
behavior is the Knowledge II model of Rosenbaum and colleagues
(\citeproc{ref-cohenWhereGraspsAre2004}{R. G. Cohen \& Rosenbaum, 2004};
\citeproc{ref-rosenbaumPlanningReachesEvaluating1995}{Rosenbaum et al.,
1995}). Knowledge II explicitly defines instances as postures (joint
combinations), and is thus far more detailed than IGAS in regards to the
contents of stored instances. Knowledge II also differs from IGAS in
that learning is accounted for by both the retrieval of stored postures,
and the generation of novel postures via the modification of retrieved
postures. A promising avenue for future research would be to combine the
adaptive similarity mechanism of IGAS with the novel instance generation
mechanisms of Knowledge II.

Our findings also have some conceptual overlap with an earlier study on
the effects of varied training in a coincident timing task
(\citeproc{ref-catalanoDistantTransferCoincident1984a}{Catalano \&
Kleiner, 1984}). In this task, participants observe a series of lamps
lighting up consecutively, and attempt to time a button press with the
onset of the final lamp. The design consisted of four separate constant
groups, each training from a single lighting velocity, and a single
varied group training with all four of the lighting velocities used by
the individual constant groups. Participants were then split into four
separate testing conditions, each of which were tested from a single
novel lighting velocity of varying distance from the training
conditions. The result of primary interest was that all participants
performed worse as the distance between training and testing velocity
increased -- a typical generalization decrement. However, varied
participants showed less of a decrement than did constant participants.
The authors take this result as evidence that varied training results in
a less-steep generalization gradient than does constant training.
Although the experimental conclusions of Catalano and Kleiner are
similar to our own, our work is novel in that we account for our results
with a cognitive model, and without assuming the formation of a schema.
Additionally, the way in which Catalano and Kleiner collapse their
separate constant groups together may result in similarity confounds
between varied and constant conditions that leaves their study open to
methodological criticisms, especially in light of related work which
demonstrated that the extent to which varied training may be beneficial
can depend on whether the constant group they are compared against
trained from similar conditions to those later tested
(\citeproc{ref-wrisbergVariabilityPracticeHypothesis1987}{Wrisberg et
al., 1987}). Our study alleviates such concerns by explicitly
controlling for similarity.

\subsubsection{Limitations}\label{limitations}

A limitation of this study concerns the ordering of the testing/transfer
trials at the conclusion of both experiments. Participants were tested
from each separate position (4 in Experiment 1, 6 in Experiment 2) in a
random, intermixed order. Because the varied group was trained from two
positions that were also randomly ordered, they may have benefited from
experience with this type of sequencing, whereas the constant groups had
no experience with switching between positions trial to trial. This
concern is somewhat ameliorated by the fact that the testing phase
performance of the constant groups from their trained position was not
significantly worse than their level of performance at the end of the
training phase, suggesting that they were not harmed by random ordering
of positions during testing. It should also be noted that the
computerized task utilized in the present work is relatively simple
compared to many of the real-world tasks utilized in prior research. It
is thus conceivable that the effect of variability in more complex tasks
is distinct from the process put forward in the present work. An
important challenge for future work will be to assess the extent to
which IGAS can account for generalization in relatively complex tasks
with far more degrees of freedom.

It is common for psychological process models of categorization learning
to use an approach such as multidimensional scaling so as to transform
the stimuli from the physical dimensions used in the particular task
into the psychological dimensions more reflective of the actual human
representations
(\citeproc{ref-nosofskySimilarityScalingCognitive1992}{Nosofsky, 1992};
\citeproc{ref-shepardUniversalLawGeneralization1987}{Shepard, 1987}).
Such scaling typically entails having participants rate the similarity
between individual items and using these similarity judgements to then
compute the psychological distances between stimuli, which can then be
fed into a subsequent model. In the present investigation, there was no
such way to scale the x and y velocity components in terms of the
psychological similarity, and thus our modelling does rely on the
assumption that the psychological distances between the different
throwing positions are proportional to absolute distances in the metric
space of the task (e.g., the relative distance between positions 400 and
500 is equivalent to that between 800 and 900). However, an advantage of
our approach is that we are measuring similarity in terms of how
participants behave (applying a velocity to the ball), rather than the
metric features of the task stimuli.

\subsubsection{Conclusion}\label{conclusion}

Our experiments demonstrate a reliable benefit of varied training in a
simple projectile launching task. Such results were accounted for by an
instance-based model that assumes that varied training results in the
computation of a broader similarity-based generalization gradient.
Instance-based models augmented with this assumption may be a valuable
approach towards better understanding skill generalization and transfer.

\newpage{}

\section{Project 2}\label{project-2}

\subsection{Introduction}\label{introduction-2}

A longstanding issue across both science and instruction has been to
understand how various aspects of an educational curriculum or training
program influence learning acquisition and generalization. One such
aspect, which has received a great deal of research attention, is the
variability of examples experienced during training
(\citeproc{ref-ravivHowVariabilityShapes2022}{Raviv et al., 2022}). The
influence of training variation has been studied in numerous domains,
including category learning
(\citeproc{ref-cohenCategoryVariabilityExemplar2001}{A. L. Cohen et al.,
2001}; \citeproc{ref-posnerGenesisAbstractIdeas1968}{Posner \& Keele,
1968}), visuomotor learning
(\citeproc{ref-bernikerEffectsTrainingBreadth2014}{Berniker et al.,
2014}; \citeproc{ref-schmidtSchemaTheoryDiscrete1975}{Schmidt, 1975}),
language learning (\citeproc{ref-perryLearnLocallyThink2010}{Perry et
al., 2010}), and education
(\citeproc{ref-braithwaiteEffectsVariationPrior2015}{Braithwaite \&
Goldstone, 2015}; \citeproc{ref-guoEffectsExampleVariability2014}{Guo et
al., 2014}). The pattern of results is complex, with numerous studies
finding both beneficial
(\citeproc{ref-braunMotorTaskVariation2009}{Braun et al., 2009};
\citeproc{ref-catalanoDistantTransferCoincident1984a}{Catalano \&
Kleiner, 1984};
\citeproc{ref-gormanInstancebasedModelAccount2022}{Gorman \& Goldstone,
2022}; \citeproc{ref-rollerVariablePracticeLenses2001}{Roller et al.,
2001}), as well as null or negative effects
(\citeproc{ref-brekelmansDoesHighVariability2022}{Brekelmans et al.,
2022}; \citeproc{ref-huHighvariabilityTrainingDoes2024}{Hu \& Nosofsky,
2024}; \citeproc{ref-vanrossumSchmidtSchemaTheory1990}{Van Rossum,
1990}). The present study seeks to contribute to the large body of
existing research by examining the influence of variability in
visuomotor function learning - a domain in which it has been relatively
under-studied.

\subsubsection{Function Learning and
Extrapolation}\label{function-learning-and-extrapolation}

The study of human function learning investigates how people learn
relationships between continuous input and output values. Function
learning is studied both in tasks where individuals are exposed to a
sequence of input/output pairs
(\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al., 1997};
\citeproc{ref-mcdanielEffectsSpacedMassed2013}{McDaniel et al., 2013}),
or situations where observers are presented with an incomplete
scatterplot or line graph and make predictions about regions of the plot
that do not contain data
(\citeproc{ref-ciccioneCanHumansPerform2021}{Ciccione \& Dehaene, 2021};
\citeproc{ref-courrieuQuickApproximationBivariate2012}{Courrieu, 2012};
\citeproc{ref-saidExtrapolationAccuracyUnderestimates2021}{Said \&
Fischer, 2021};
\citeproc{ref-schulzCommunicatingCompositionalPatterns2020}{Schulz et
al., 2020}). Studies of function learning often compare the difficulty
of learning functions of different underlying forms (e.g.~linear,
bi-linear, power, sinusoidal), and the extent to which participants can
accurately respond to novel inputs that fall in-between previously
experienced inputs (interpolation testing), or that fall outside the
range of previously experienced inputs (extrapolation).

Carroll (\citeproc{ref-carrollFunctionalLearningLearning1963}{1963})
conducted the earliest work on function learning. Input stimuli and
output responses were both lines of varying length. The correct output
response was related to the length of the input line by a linear,
quadratic, or random function. Participants in the linear and quadratic
performed above chance levels during extrapolation testing, with those
in the linear condition performing the best overall. Carroll argued that
these results were best explained by a rule-based model wherein learners
form an abstract representation of the underlying function. Subsequent
work by Brehmer
(\citeproc{ref-brehmerHypothesesRelationsScaled1974}{1974}), testing a
wider array of functional forms, provided further evidence for superior
extrapolation in tasks with linear functions. Brehmer argued that
individuals start out assuming a linear function, but given sufficient
error will progressively test alternative hypotheses with polynomials of
greater degree. Koh \& Meyer
(\citeproc{ref-kohFunctionLearningInduction1991}{1991}) employed a
visuomotor function learning task, wherein participants were trained on
examples from an unknown function relating the length of an input line
to the duration of a response (time between keystrokes). In this domain,
participants performed best when the relation between line length and
response duration was determined by a power law, as opposed to linear
function. Koh and Meyer developed the log-polynomial adaptive-regression
model to account for their results.

The first significant challenge to rule-based accounts of function
learning was put forth by DeLosh et al.
(\citeproc{ref-deloshExtrapolationSineQua1997}{1997}) . In their task,
participants learned to associate stimulus magnitudes with response
magnitudes that were related via either linear, exponential, or
quadratic function. Participants approached ceiling performance by the
end of training in each function condition, and were able to accurately
respond on interpolation testing trials. All three conditions
demonstrated some capacity for extrapolation, however participants in
the linear condition tended to underestimate the true function, while
exponential and quadratic participants reliably overestimated the true
function on extrapolation trials. Extrapolation and interpolation
performances are depicted in Figure~\ref{fig-delosh-extrap}.

The authors evaluated the rule-based models introduced in earlier
research (with some modifications enabling trial-by-trial learning). The
polynomial hypothesis testing model
(\citeproc{ref-brehmerHypothesesRelationsScaled1974}{Brehmer, 1974};
\citeproc{ref-carrollFunctionalLearningLearning1963}{Carroll, 1963})
tended to mimic the true function closely in extrapolation, and thus
offered a poor account of the under and over-estimation biases shown in
the human data. The log-polynomial adaptive regression model
(\citeproc{ref-kohFunctionLearningInduction1991}{Koh \& Meyer, 1991})
was able to mimic some of the systematic deviations produced by human
subjects, but also predicted overestimation in cases where
underestimation occurred.

The authors also introduced two new function-learning models. The
Associative Learning Model (ALM) and the extrapolation-association model
(EXAM). ALM is a two-layer connectionist model adapted from the ALCOVE
model in the category learning literature
(\citeproc{ref-kruschkeALCOVEExemplarbasedConnectionist1992}{Kruschke,
1992}). ALM belongs to the general class of radial-basis function neural
networks, and can be considered a similarity-based model in the sense
that the nodes in the input layer of the network are activated as a
function of distance (see Figure~\ref{fig-alm-diagram}). The EXAM model
retains the same similarity-based activation and associative learning
mechanisms as ALM, while being augmented with a linear rule response
mechanism. When presented with novel stimuli, EXAM will retrieve the
most similar input-output examples encountered during training, and from
those examples compute a local slope. ALM was able to provide a good
account of participants' training and interpolation data in all three
function conditions, however it was unable to extrapolate. EXAM, by
contrast, was able to reproduce both the extrapolation underestimation,
as well as the quadratic and exponential overestimation patterns
exhibited by the human participants. Subsequent research identified some
limitations in EXAM's ability to account for cases where human
participants learn and extrapolate a sinusoidal function
(\citeproc{ref-bottNonmonotonicExtrapolationFunction2004}{Bott \& Heit,
2004}) or to scenarios where different functions apply to different
regions of the input space
(\citeproc{ref-kalishPopulationLinearExperts2004}{Kalish et al., 2004}),
though EXAM has been shown to provide a good account of human learning
and extrapolation in tasks with bi-linear, V-shaped input spaces
(\citeproc{ref-mcdanielPredictingTransferPerformance2009}{McDaniel et
al., 2009}).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-delosh-extrap-1.pdf}}

}

\caption{\label{fig-delosh-extrap}The generalization patterns of human
participants observed in DeLosh et al.~(1997) (reproduced from Figure 3
in their manuscript). Dots represent the average responses of human
participants, and solid lines represent the true functions. The dashed
vertical lines indicate the lower and upper bounds of the trained
examples. Stimulii that fall within the dashed lines are interpolations
of the training examples, while those that fall outside the dashed lines
are extrapolations.}

\end{figure}%

\subsubsection{Variability and Function
Learning}\label{variability-and-function-learning}

The influence of variability on function learning tasks has received
relatively little attention. The study by DeLosh et al.
(\citeproc{ref-deloshExtrapolationSineQua1997}{1997}) (described in
detail above) did include a variability manipulation (referred to as
density in their paper), wherein participants were trained with either
8, 20, or 50 unique input-output pairs, with the total number of
training trials held constant. They found a minimal influence of
variability on training performance, and no difference between groups in
interpolation or extrapolation, with all three variability conditions
displaying accurate interpolation, and linearly biased extrapolation
that was well accounted for by the EXAM model.

In the domain of visuomotor learning, van Dam \& Ernst
(\citeproc{ref-vandamMappingShapeVisuomotor2015}{2015}) employed a task
which required participants to learn a linear function between the
spikiness of shape stimuli and the correct horizontal position to make a
rapid pointing response. The shapes ranged from very spiky to completely
circular at the extreme ends of the space. Participants trained with
intermediate shapes having lower variation (2 shapes) or higher
variation (5 shapes) condition, with the 2 items of the lower variation
condition matching the items used on the extreme ends of the higher
variation training space. Learning was significantly slower in the
higher variation group. However, the two conditions did not differ when
tested with novel shapes, with both groups producing extrapolation
responses of comparable magnitude to the most similar training item,
rather than in accordance with the true linear function. The authors
accounted for both learning and extrapolation performance with a
Bayesian learning model. Similar to ALM, the model assumes that
generalization occurs as a Gaussian function of the distance between
stimuli. However, unlike ALM, the Bayesian learning model utilizes more
elaborate probabilistic stimulus representations, with a separate Kalman
Filter for each shape stimulus.

\subsubsection{Overview Of Present
Study}\label{overview-of-present-study}

The present study investigates the influence of training variability on
learning, generalization, and extrapolation in a uni-dimensional
visuomotor function learning task. To the best of our knowledge, this
research is the first to employ the classic constant vs.~varied training
manipulation, commonly used in the literature studying the benefits of
variability, in the context of a uni-dimensional function learning task.
Across three experiments, we compare constant and varied training
conditions in terms of learning performance, extrapolation accuracy, and
the ability to reliably discriminate between stimuli.

To account for the empirical results, we will apply a series of
computational models, including the Associative Learning Model (ALM) and
the Extrapolation-Association Model (EXAM). Notably, this study is the
first to employ approximate Bayesian computation (ABC) to fit these
models to individual subject data, enabling us to thoroughly investigate
the full range of posterior predictions of each model, and to examine
the ability of these influential models of function learning to account
for both the group level and individual level data.

\subsection{Experiment 1}\label{experiment-1-1}

\subsubsection{Methods}\label{methods-2}

\emph{Participants.} A total of 183 participants were initially
recruited from Indiana University Introductory Psychology Courses. Of
these, 27 participants were excluded from further analysis due to
meeting the exclusion criteria, resulting in a final sample of 156
participants. The exclusion criteria was defined as performance worse
(i.e., larger deviations) than the condition average in either the
training or testing stage of the experiment. The remaining participants
were randomly assigned to one of two training conditions: varied
training or constant training.

\emph{Task.} The ``Hit The Wall'' (HTW) visuomotor extrapolation task
was programmed in JavaScript, making use of the
\href{https://phaser.io/}{phaser.io} game library. The HTW task involved
launching a projectile such that it would strike the ``wall'' at the
target speed indicated at the top of the screen (see
Figure~\ref{fig-htw-task}). The target velocities were given as a range,
or band, of acceptable velocity values (e.g., band 800-1000). During the
training stage, participants received feedback indicating whether they
had hit the wall within the target velocity band, or how many units
their throw was above or below the target band. Participants were
instructed that only the x velocity component of the ball was relevant
to the task. The y velocity, or the location at which the ball struck
the wall, had no influence on the task feedback.

\begin{figure}

\centering{

\includegraphics[width=0.6\linewidth,height=\textheight,keepaspectratio]{../Assets/figs/htw_task_fig.png}

}

\caption{\label{fig-htw-task}The Hit the wall task. Participants launch
the blue ball to hit the red wall at the target velocity band indicated
at the top of the screen. The ball must be released from within the
orange square - but the location of release, and the location at which
the ball strikes the wall are both irrelevant to the task feedback.}

\end{figure}%

\emph{Procedure.} All participants completed the task online.
Participants were provided with a description of the experiment and
indicated informed consent. Figure~\ref{fig-design-e1} illustrates the
general procedure. Participants completed a total of 90 trials during
the training stage. In the varied training condition, participants
encountered three velocity bands (800-1000, 1000-1200, and 1200-1400).
Participants in the constant training condition trained on only one
velocity band (800-1000) - the closest band to what would be the novel
extrapolation bands in the testing stage.

Following the training stage, participants proceeded immediately to the
testing stage. Participants were tested from all six velocity bands, in
two separate stages. In the novel extrapolation testing stage,
participants completed ``no-feedback'' testing from three novel
extrapolation bands (100-300, 350-550, and 600-800), with each band
consisting of 15 trials. Participants were also tested from the three
velocity bands that were trained by the varied condition (800-1000,
1000-1200, and 1200-1400). In the constant training condition, two of
these bands were novel, while in the varied training condition, all
three bands were encountered during training. The order in which
participants completed the novel-extrapolation and testing-from-3-varied
bands was counterbalanced across participants. A final training stage
presented participants with ``feedback'' testing for each of the three
extrapolation bands (100-300, 350-550, and 600-800).

\begin{figure}

\centering{

\includegraphics[width=7in,height=2.5in]{manuscript_files/figure-latex/dot-figure-1.png}

}

\caption{\label{fig-design-e1}Experiment 1 Design. Constant and Varied
participants complete different training conditions.}

\end{figure}%

\subsubsection{Analyses Strategy}\label{analyses-strategy}

All data processing and statistical analyses were performed in R version
4.32 (\citeproc{ref-rcoreteamLanguageEnvironmentStatistical2020}{Team,
2020}). To assess differences between groups, we used Bayesian Mixed
Effects Regression. Model fitting was performed with the brms package in
R (\citeproc{ref-burknerBrmsPackageBayesian2017}{Bürkner, 2017}), and
descriptive stats and tables were extracted with the BayestestR package
(\citeproc{ref-makowskiBayestestRDescribingEffects2019}{Makowski et al.,
2019}). Mixed effects regression enables us to take advantage of partial
pooling, simultaneously estimating parameters at the individual and
group level. Our use of Bayesian, rather than frequentist methods allows
us to directly quantify the uncertainty in our parameter estimates, as
well as avoid convergence issues common to the frequentist analogues of
our mixed models.

Each model was set to run with 4 chains, 5000 iterations per chain, with
the first 2500 discarded as warmup chains. Rhat values were within an
acceptable range, with values \textless=1.02 (see appendix for
diagnostic plots). We used uninformative priors for the fixed effects of
the model (condition and velocity band), and weakly informative Student
T distributions for the random effects. For each model, we report 1) the
mean values of the posterior distribution for the parameters of
interest, 2) the lower and upper credible intervals (CrI), and the
probability of direction value (pd).

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2329}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.5342}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2329}}@{}}
\caption{\textbf{Statistical Model Specifications}. The specifications
for the Bayesian regression models used in the analyses of each of the 3
experiments. Comparisons of accuracy use absolute deviation as the
dependent variable, while comparisons of discrimination use the raw
velocities produced by participants as the dependent
variable.}\label{tbl-brms-models}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Group Comparison
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Data
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Group Comparison
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Data
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
End of Training Accuracy &
\texttt{brm(Abs.\ Deviation\ \textasciitilde{}\ condit)} & Final
Training Block \\
Test Accuracy &
\texttt{brm(Abs.\ Deviation\ \textasciitilde{}\ condit\ *\ bandType\ +\ (1\textbar{}id)\ +\ (1\textbar{}bandInt)}
& All Testing trials \\
Band Discrimination &
\texttt{brm(vx\ \textasciitilde{}\ condit\ *\ band\ +(1\ +\ bandInt\textbar{}id)}
& All Testing Trials \\
\end{longtable}

\hfill\break

In each experiment we compare varied and constant conditions in terms of
1) accuracy in the final training block; 2) testing accuracy as a
function of band type (trained vs.~extrapolation bands); 3) extent of
discrimination between all six testing bands. We quantified accuracy as
the absolute deviation between the response velocity and the nearest
boundary of the target band. Thus, when the target band was velocity
600-800, throws of 400, 650, and 900 would result in deviation values of
200, 0, and 100, respectively. The degree of discrimination between
bands was measured by fitting a linear model predicting the response
velocity as a function of the target velocity. Participants who reliably
discriminated between velocity bands tended to have slope values
\textasciitilde1, while participants who made throws irrespective of the
current target band would have slopes \textasciitilde0.

\subsubsection{Results}\label{results-2}

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e1-train-dev-1.pdf}}

}

\caption{\label{fig-e1-train-dev}Experiment 1 - Training Stage.
Deviations from target band across training blocks. Lower values
represent greater accuracy.}

\end{figure}%

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\textbf{Experiment 1 - End of training performance}. Comparing
final training block accuracy in the band common to both groups. The
Intercept represents the average of the baseline condition (constant
training), and the conditVaried coefficient reflects the difference
between the constant and varied groups. A larger positive estimate
indicates a greater deviation (lower accuracy) for the varied group. CrI
values indicate 95\% credible intervals. pd is the probability of
direction (the \% of the posterior on the same side of 0 as the
coefficient estimate).}\label{tbl-e1-train-dist}\tabularnewline
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 106.34 & 95.46 & 117.25 & 1 \\
conditVaried & 79.64 & 57.92 & 101.63 & 1 \\
\end{longtable}

\hfill\break

\emph{Training}. Figure~\ref{fig-e1-train-dev} displays the average
deviations across training blocks for the varied group, which trained on
three velocity bands, and the constant group, which trained on one
velocity band. To compare the training conditions at the end of
training, we analyzed performance on the 800-1000 velocity band, which
both groups trained on. The full model results are shown in Table 1. The
varied group had a significantly greater deviation from the target band
than the constant group in the final training block, (\(\beta\) = 79.64,
95\% CrI {[}57.92, 101.63{]}; pd = 100\%).

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.3425}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1644}}@{}}
\caption{\textbf{Experiment 1 testing accuracy}. Main effects of
condition and band type (training vs.~extrapolation bands), and the
interaction between the two factors. The Intercept represents the
baseline condition (constant training \& trained bands). Larger
coefficients indicate larger deviations from the baselines - and a
positive interaction coefficient indicates disproportionate deviation
for the varied condition on the extrapolation bands. CrI values indicate
95\% credible intervals. pd is the probability of direction (the \% of
the posterior on the same side of 0 as the coefficient
estimate).}\label{tbl-e1-bmm-dist}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 152.55 & 70.63 & 229.85 & 1.0 \\
conditVaried & 39.00 & -21.10 & 100.81 & 0.9 \\
bandTypeExtrapolation & 71.51 & 33.24 & 109.60 & 1.0 \\
conditVaried:bandTypeExtrapolation & 66.46 & 32.76 & 99.36 & 1.0 \\
\end{longtable}

\emph{Testing.} To compare accuracy between groups in the testing stage,
we fit a Bayesian mixed effects model predicting deviation from the
target band as a function of training condition (varied vs.~constant)
and band type (trained vs.~extrapolation), with random intercepts for
participants and bands. The model results are shown in
Table~\ref{tbl-e1-bmm-dist}. The main effect of training condition was
not significant (\(\beta\) = 39, 95\% CrI {[}-21.1, 100.81{]}; pd =
89.93\%). The extrapolation testing items had a significantly greater
deviation than the training bands (\(\beta\) = 71.51, 95\% CrI {[}33.24,
109.6{]}; pd = 99.99\%). Most importantly, the interaction between
training condition and band type was significant (\(\beta\) = 66.46,
95\% CrI {[}32.76, 99.36{]}; pd = 99.99\%), As shown in
Figure~\ref{fig-e1-test-dev}, the varied group had disproportionately
larger deviations compared to the constant group in the extrapolation
bands.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e1-test-dev-1.pdf}}

}

\caption{\label{fig-e1-test-dev}Experiment 1 Testing Accuracy. A)
Empirical Deviations from target band during testing without feedback
stage. B) Conditional effect of condition (Constant vs.~Varied) and
testing band type (trained bands vs.~novel extrapolation bands) on
testing accuracy. Error bars represent 95\% credible intervals.}

\end{figure}%

\hfill\break

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\textbf{Experiment 1 Testing Discrimination}. Bayesian Mixed
Model Predicting velocity as a function of condition (Constant
vs.~Varied) and Velocity Band. Larger coefficients for the Band term
reflect a larger slope, or greater sensitivity/discrimination. The
interaction between condit and Band indicates the difference between
constant and varied slopes. CrI values indicate 95\% credible intervals.
pd is the probability of direction (the \% of the posterior on the same
side of 0 as the coefficient
estimate).}\label{tbl-e1-bmm-vx}\tabularnewline
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 408.55 & 327.00 & 490.61 & 1.00 \\
conditVaried & 164.05 & 45.50 & 278.85 & 1.00 \\
Band & 0.71 & 0.62 & 0.80 & 1.00 \\
condit*Band & -0.14 & -0.26 & -0.01 & 0.98 \\
\end{longtable}

Finally, to assess the ability of both conditions to discriminate
between velocity bands, we fit a model predicting velocity as a function
of training condition and velocity band, with random intercepts and
random slopes for each participant. See Table~\ref{tbl-e1-bmm-vx} for
the full model results. The estimated coefficient for training condition
(\(\beta\) = 164.05, 95\% CrI {[}45.5, 278.85{]}, pd = 99.61\%) suggests
that the varied group tends to produce harder throws than the constant
group, though this is not, in and of itself, useful for assessing
discrimination. Most relevant to the issue of discrimination is the
coefficient on the Band predictor (\(\beta\) = 0.71 95\% CrI {[}0.62,
0.8{]}, pd = 100\%). Although the median slope does fall underneath the
ideal of value of 1, the fact that the 95\% credible interval does not
contain 0 provides strong evidence that participants exhibited some
discrimination between bands. The significant negative estimate for the
interaction between slope and condition (\(\beta\) = -0.14, 95\% CrI
{[}-0.26, -0.01{]}, pd = 98.39\%), indicates that the discrimination was
modulated by training condition, with the varied participants showing
less sensitivity between bands than the constant condition (see
Figure~\ref{fig-e1-test-vx} and Figure~\ref{fig-e1-bmm-vx}).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e1-test-vx-1.pdf}}

}

\caption{\label{fig-e1-test-vx}Experiment 1. Empirical distribution of
velocities produced in the testing stage. Translucent bands with dashed
lines indicate the correct range for each velocity band.}

\end{figure}%

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e1-bmm-vx-1.pdf}}

}

\caption{\label{fig-e1-bmm-vx}Experiment 1 Discrimination. A)
Conditional effect of training condition and Band. Ribbons indicate 95\%
HDI. The steepness of the lines serves as an indicator of how well
participants discriminated between velocity bands. B) The distribution
of slope coefficients for each condition. Larger slopes indicate better
discrimination between target bands. C) Individual participant slopes.
Error bars represent 95\% HDI.}

\end{figure}%

\subsubsection{Experiment 1 Summary}\label{experiment-1-summary}

In Experiment 1, we investigated how variability in training influenced
participants' ability to learn and extrapolate in a visuomotor task. Our
findings that training with variable conditions resulted in lower final
training performance are consistent with much of the prior research on
the influence of training variability
(\citeproc{ref-ravivHowVariabilityShapes2022}{Raviv et al., 2022};
\citeproc{ref-soderstromLearningPerformanceIntegrative2015}{Soderstrom
\& Bjork, 2015}), and are particularly unsurprising in the present work,
given that the constant group received three times the amount of
training on the velocity band common to the two conditions.

More importantly, the varied training group exhibited significantly
larger deviations from the target velocity bands during the testing
phase, particularly for the extrapolation bands that were not
encountered by either condition during training.

\subsection{Experiment 2}\label{experiment-2-1}

\subsubsection{Methods \& Procedure}\label{methods-procedure}

Initially, 131 participants were recruited. After applying the same
exclusion procedure as in Experiment 1, 21 participants were excluded,
resulting in a final sample of 110 participants who completed the
experiment (Varied: 55, Constant: 55). The task and procedure of
Experiment 2 was identical to Experiment 1, with the exception that the
training and testing bands were reversed (see
Figure~\ref{fig-design-e2}). The Varied group trained on bands 100-300,
350-550, 600-800, and the constant group trained on band 600-800. Both
groups were tested from all six bands.

\begin{figure}

\centering{

\includegraphics[width=7in,height=2.2in]{manuscript_files/figure-latex/dot-figure-2.png}

}

\caption{\label{fig-design-e2}Experiment 2 Design. Constant and Varied
participants complete different training conditions. The training and
testing bands are the reverse of Experiment 1.}

\end{figure}%

\subsubsection{Results}\label{results-3}

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2-train-dev-1.pdf}}

}

\caption{\label{fig-e2-train-dev}Experiment 2 Training Stage. Deviations
from target band across training blocks. Lower values represent greater
accuracy.}

\end{figure}%

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\textbf{Experiment 2 - End of training performance}. The
Intercept represents the average of the baseline condition (constant
training), and the conditVaried coefficient reflects the difference
between the constant and varied groups. A larger positive coefficient
indicates a greater deviation (lower accuracy) for the varied group. CrI
values indicate 95\% credible intervals. pd is the probability of
direction (the \% of the posterior on the same side of 0 as the
coefficient estimate).}\label{tbl-e2-train-dist}\tabularnewline
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 91.01 & 80.67 & 101.26 & 1 \\
conditVaried & 36.15 & 16.35 & 55.67 & 1 \\
\end{longtable}

\hfill\break

\emph{Training}. Figure~\ref{fig-e2-train-dev} presents the deviations
across training blocks for both constant and varied training groups. We
again compared training performance on the band common to both groups
(600-800). The full model results are shown in Table 1. The varied group
had a significantly greater deviation than the constant group in the
final training block, ( \(\beta\) = 36.15, 95\% CrI {[}16.35, 55.67{]};
pd = 99.95\%).

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.4390}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1220}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1829}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1829}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.0732}}@{}}
\caption{\textbf{Experiment 2 testing accuracy}. Main effects of
condition and band type (training vs.~extrapolation), and the
interaction between the two factors. The Intercept represents the
baseline condition (constant training \& trained bands). Larger
coefficients indicate larger deviations from the baselines - and a
positive interaction coefficient indicates disproportionate deviation
for the varied condition on the extrapolation bands. CrI values indicate
95\% credible intervals. pd is the probability of direction (the \% of
the posterior on the same side of 0 as the coefficient
estimate).}\label{tbl-e2-bmm-dist}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 190.91 & 125.03 & 259.31 & 1.00 \\
conditVaried & -20.58 & -72.94 & 33.08 & 0.78 \\
bandTypeExtrapolation & 38.09 & -6.94 & 83.63 & 0.95 \\
conditVaried:bandTypeExtrapolation & 82.00 & 41.89 & 121.31 & 1.00 \\
\end{longtable}

~\\

\emph{Testing Accuracy.} The analysis of testing accuracy examined
deviations from the target band as influenced by training condition
(Varied vs.~Constant) and band type (training vs.~extrapolation bands).
The results, summarized in Table~\ref{tbl-e2-bmm-dist}, reveal no
significant main effect of training condition (\(\beta\) = -20.58, 95\%
CrI {[}-72.94, 33.08{]}; pd = 77.81\%). However, the interaction between
training condition and band type was significant (\(\beta\) = 82, 95\%
CrI {[}41.89, 121.31{]}; pd = 100\%), with the varied group showing
disproportionately larger deviations compared to the constant group on
the extrapolation bands (see Figure~\ref{fig-e2-test-dev}).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2-test-dev-1.pdf}}

}

\caption{\label{fig-e2-test-dev}Experiment 2 Testing Accuracy. A)
Empirical Deviations from target band during testing without feedback
stage. B) Conditional effect of condition (Constant vs.~Varied) and
testing band type (trained bands vs.~novel extrapolation bands) on
testing accuracy. Error bars represent 95\% credible intervals.}

\end{figure}%

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\textbf{Experiment 2 Testing Discrimination}. Bayesian Mixed
Model Predicting velocity as a function of condition (Constant
vs.~Varied) and Velocity Band. Larger coefficients for the Band term
reflect a larger slope, or greater sensitivity/discrimination. The
interaction between condition and Band indicates the difference between
constant and varied slopes. CrI values indicate 95\% credible intervals.
pd is the probability of direction (the \% of the posterior on the same
side of 0 as the coefficient
estimate)}\label{tbl-e2-bmm-vx}\tabularnewline
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 362.64 & 274.85 & 450.02 & 1.00 \\
conditVaried & -8.56 & -133.97 & 113.98 & 0.55 \\
Band & 0.71 & 0.58 & 0.84 & 1.00 \\
condit*Band & -0.06 & -0.24 & 0.13 & 0.73 \\
\end{longtable}

\emph{Testing Discrimination.} Finally, to assess the ability of both
conditions to discriminate between velocity bands, we fit a model
predicting velocity as a function of training condition and velocity
band, with random intercepts and random slopes for each participant. The
full model results are shown in Table~\ref{tbl-e2-bmm-vx}. The overall
slope on target velocity band predictor was significantly positive,
(\(\beta\) = 0.71, 95\% CrI {[}0.58, 0.84{]}; pd= 100\%), indicating
that participants exhibited discrimination between bands. The
interaction between slope and condition was not significant, (\(\beta\)
= -0.06, 95\% CrI {[}-0.24, 0.13{]}; pd= 72.67\%), suggesting that the
two conditions did not differ in their ability to discriminate between
bands (see Figure~\ref{fig-e2-test-vx} and Figure~\ref{fig-e2-bmm-vx}).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2-test-vx-1.pdf}}

}

\caption{\label{fig-e2-test-vx}Experiment 2. Empirical distribution of
velocities produced in the testing stage. Translucent bands with dash
lines indicate the correct range for each velocity band.}

\end{figure}%

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2-bmm-vx-1.pdf}}

}

\caption{\label{fig-e2-bmm-vx}Experiment 2 Discrimination. A)
Conditional effect of training condition and Band. Ribbons indicate 95\%
HDI. The steepness of the lines serves as an indicator of how well
participants discriminated between velocity bands. B) The distribution
of slope coefficients for each condition. Larger slopes indicate better
discrimination. C) Individual participant slopes. Error bars represent
95\% HDI.}

\end{figure}%

\subsubsection{Experiment 2 Summary}\label{experiment-2-summary}

Experiment 2 extended the findings of Experiment 1 by examining the
effects of training variability on extrapolation performance in a
visuomotor function learning task, but with reversed training and
testing bands. Similar to Experiment 1, the Varied group exhibited
poorer performance during training and testing. However, unlike
experiment 1, the Varied and Constant groups did not show a significant
difference in their discrimination between bands.

\subsection{Experiment 3}\label{experiment-3}

In Experiment 3, we sought to further explore the generality of the
findings from the first two experiments by modifying the type of
feedback provided during training. Specifically, we provided ordinal
feedback instead of the continuous feedback used in the previous two
experiments. Ordinal feedback provides learners with directional
information about the results of their throw (e.g., above the target,
below the target, or hitting the target) rather than precise numerical
deviations. This form of feedback resembles many real-world learning
scenarios, such as a coach instructing an athlete to perform a movement
using ``more force'' or ``less force'', or a teacher providing letter
grades rather than numeric scores. Although ordinal feedback provides
less detailed information per trial, prior research has shown that less
detailed feedback is not necessarily detrimental to learning. For
example, Cornwall et al.
(\citeproc{ref-cornwallEffectsCategoricalNumerical2022}{2022})
manipulated whether participants received categorical (correct or
incorrect) vs.~numerical feedback (reward points ranging from 50-100).
They found that the categorical condition produced superior learning,
which they explained as arising from larger prediction errors. While we
do not make specific predictions about the ordinal condition, this
manipulation allows us to explore how different types of feedback might
interact with training variability to influence learning and
generalization.

\subsubsection{Methods \& Procedure}\label{methods-procedure-1}

The only adjustment of Experiment 3 is for participants to receive
ordinal feedback during training, in contrast to the continuous feedback
of the prior experiments. After each training throw, participants are
informed whether a throw was too soft, too hard, or correct (i.e.~within
the target velocity range). All other aspects of the task and design are
identical to Experiments 1 and 2. We utilized the order of training and
testing bands from both of the prior experiments, thus assigning
participants to both an order condition (Original or Reverse) and a
training condition (Constant or Varied). Participants were once again
recruited from the online Indiana University Introductory Psychology
Course pool. Following exclusions, 195 participants were included in the
final analysis, n=51 in the Constant-Original condition, n=59 in the
Constant-Reverse condition, n=39 in the Varied-Original condition, and
n=46 in the Varied-Reverse condition.

\subsubsection{Results}\label{results-4}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.4026}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1299}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1948}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1948}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.0779}}@{}}
\caption{\textbf{Experiment 3 - End of training performance}. The
Intercept represents the average of the baseline condition (constant
training \& original band order), the conditVaried coefficient reflects
the difference between the constant and varied groups, and the
bandOrderReverse coefficient reflects the difference between original
and reverse order. A larger positive coefficient indicates a greater
deviation (lower accuracy) for the varied group. The negative value for
the interaction between condit and bandOrder indicates that varied
condition with reverse order had significantly lower deviations than the
varied condition with the original band
order}\label{tbl-e3-train-dist}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 121.86 & 109.24 & 134.60 & 1.00 \\
conditVaried & 64.93 & 36.99 & 90.80 & 1.00 \\
bandOrderReverse & 1.11 & -16.02 & 18.16 & 0.55 \\
conditVaried:bandOrderReverse & -77.02 & -114.16 & -39.61 & 1.00 \\
\end{longtable}

\emph{Training}. Figure~\ref{fig-e3-train-dev} displays the average
deviations from the target band across training blocks, and
Table~\ref{tbl-e3-train-dist} shows the results of the Bayesian
regression model predicting the deviation from the common band at the
end of training (600-800 for reversed order, and 800-1000 for original
order conditions). The main effect of training condition is significant,
with the varied condition showing larger deviations ( \(\beta\) = 64.93,
95\% CrI {[}36.99, 90.8{]}; pd = 100\%). The main effect of band order
is not significant \(\beta\) = 1.11, 95\% CrI {[}-16.02, 18.16{]}; pd =
55.4\%, however the interaction between training condition and band
order is significant, with the varied condition showing greater accuracy
in the reverse order condition ( \(\beta\) = -77.02, 95\% CrI
{[}-114.16, -39.61{]}; pd = 100\%).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e3-train-dev-1.pdf}}

}

\caption{\label{fig-e3-train-dev}Experiment 3 training. Deviations from
target band during training, shown separately for groups trained with
the original order (used in E1) and reverse order (used in E2).}

\end{figure}%

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.5354}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1010}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1515}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1515}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.0606}}@{}}
\caption{\textbf{Experiment 3 testing accuracy}. Main effects of
condition and band type (training vs.~extrapolation), and the
interaction between the two factors. The Intercept represents the
baseline condition, (constant training, trained bands \& original
order), and the remaining coefficients reflect the deviation from that
baseline. Positive coefficients thus represent worse performance
relative to the baseline, and a positive interaction coefficient
indicates disproportionate deviation for the varied condition or reverse
order condition.}\label{tbl-e3-bmm-dist}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 288.65 & 199.45 & 374.07 & 1.00 \\
conditVaried & -40.19 & -104.68 & 23.13 & 0.89 \\
bandTypeExtrapolation & -23.35 & -57.28 & 10.35 & 0.92 \\
bandOrderReverse & -73.72 & -136.69 & -11.07 & 0.99 \\
\textbf{conditVaried:bandTypeExtrapolation} & 52.66 & 14.16 & 90.23 &
1.00 \\
conditVaried:bandOrderReverse & -37.48 & -123.28 & 49.37 & 0.80 \\
bandTypeExtrapolation:bandOrderReverse & 80.69 & 30.01 & 130.93 &
1.00 \\
conditVaried:bandTypeExtrapolation:bandOrder & 30.42 & -21.00 & 81.65 &
0.87 \\
\end{longtable}

\emph{Testing Accuracy.} Table~\ref{tbl-e3-bmm-dist} presents the
results of the Bayesian mixed effects model predicting absolute
deviation from the target band during the testing stage. There was no
significant main effect of training condition,\(\beta\) = -40.19, 95\%
CrI {[}-104.68, 23.13{]}; pd = 89.31\%, or band type,\(\beta\) = -23.35,
95\% CrI {[}-57.28, 10.35{]}; pd = 91.52\%. However the effect of band
order was significant, with the reverse order condition showing lower
deviations, \(\beta\) = -73.72, 95\% CrI {[}-136.69, -11.07{]}; pd =
98.89\%. The interaction between training condition and band type was
also significant \(\beta\) = 52.66, 95\% CrI {[}14.16, 90.23{]}; pd =
99.59\%, with the varied condition showing disproprionately large
deviations on the extrapolation bands compared to the constant group.
There was also a significant interaction between band type and band
order, \(\beta\) = 80.69, 95\% CrI {[}30.01, 130.93{]}; pd = 99.89\%,
such that the reverse order condition showed larger deviations on the
extrapolation bands. No other interactions were significant.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e3-test-dev-1.pdf}}

}

\caption{\label{fig-e3-test-dev}Experiment 3 Testing Accuracy. A)
Empirical Deviations from target band during testing without feedback
stage. B) Conditional effect of condition (Constant vs.~Varied) and
testing band type (trained bands vs.~novel extrapolation bands) on
testing accuracy. Shown separately for groups trained with the original
order (used in E1) and reverse order (used in E2). Error bars represent
95\% credible intervals.}

\end{figure}%

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.4713}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1149}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1724}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.1724}}
  >{\raggedleft\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.0690}}@{}}
\caption{\textbf{Experiment 3 testing discrimination}. Bayesian Mixed
Model Predicting Vx as a function of condition (Constant vs.~Varied) and
Velocity Band. The Intercept represents the baseline condition (constant
training \& original order), and the Band coefficient represents the
slope for the baseline condition. The interaction terms which include
condit and Band (e.g., conditVaried:Band \&
conditVaried:bandOrderReverse:band) respectively indicate how the slopes
of the varied-original condition differed from the baseline condition,
and how varied-reverse condition differed from the varied-original
condition}\label{tbl-e3-bmm-vx}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Term
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Lower
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
95\% CrI Upper
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
pd
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Intercept & 601.83 & 504.75 & 699.42 & 1.00 \\
conditVaried & 12.18 & -134.94 & 162.78 & 0.56 \\
bandOrderReverse & 13.03 & -123.89 & 144.67 & 0.58 \\
\textbf{Band} & 0.49 & 0.36 & 0.62 & 1.00 \\
\textbf{conditVaried:bandOrderReverse} & -338.15 & -541.44 & -132.58 &
1.00 \\
conditVaried:Band & -0.04 & -0.23 & 0.15 & 0.67 \\
bandOrderReverse:band & -0.10 & -0.27 & 0.08 & 0.86 \\
\textbf{conditVaried:bandOrderReverse:band} & 0.42 & 0.17 & 0.70 &
1.00 \\
\end{longtable}

\emph{Testing Discrimination.} The full results of the discrimination
model are presented in Table~\ref{tbl-e3-bmm-dist}. For the purposes of
assessing group differences in discrimination, only the coefficients
including the band variable are of interest. The baseline effect of band
represents the slope coefficient for the constant training - original
order condition, this effect was significant \(\beta\) = 0.49, 95\% CrI
{[}0.36, 0.62{]}; pd = 100\%. Neither of the two way interactions
reached significance, \(\beta\) = -0.04, 95\% CrI {[}-0.23, 0.15{]}; pd
= 66.63\%, \(\beta\) = -0.1, 95\% CrI {[}-0.27, 0.08{]}; pd = 86.35\%.
However, the three way interaction between training condition, band
order, and target band was significant, \(\beta\) = 0.42, 95\% CrI
{[}0.17, 0.7{]}; pd = 99.96\% - indicating a greater slope for the
varied condition trained with reverse order bands. This interaction is
shown in Figure~\ref{fig-e3-test-vx}, where the steepness of the best
fitting line for the varied-reversed condition is noticeably steeper
than the other conditions.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e3-test-vx-1.pdf}}

}

\caption{\label{fig-e3-test-vx}Experiment 3. Empirical distribution of
velocities produced in the testing stage. Translucent bands with dash
lines indicate the correct range for each velocity band.}

\end{figure}%

\newpage{}

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e3-bmm-vx-1.pdf}}

}

\caption{\label{fig-e3-bmm-vx}Experiment 3 Discrimination. A)
Conditional effect of training condition and Band. Ribbons indicate 95\%
HDI. The steepness of the lines serves as an indicator of how well
participants discriminated between velocity bands. B) The distribution
of slope coefficients for each condition. Larger slopes indicate better
discrimination. C) Individual participant slopes. Error bars represent
95\% HDI.}

\end{figure}%

\subsubsection{Experiment 3 Summary}\label{experiment-3-summary}

In Experiment 3, we investigated the effects of training condition
(constant vs.~varied) and band type (training vs.~extrapolation) on
participants' accuracy and discrimination during the testing phase.
Unlike the previous experiments, participants received only ordinal, not
continuous valued, feedback during the training phase. Additionally,
Experiment 3 included both the original order condition from Experiment
1 and the reverse order condition from Experiment 2. The results
revealed no significant main effects of training condition on testing
accuracy, nor was there a significant difference between groups in band
discrimination. However, we observed a significant three-way interaction
for the discrimination analysis, indicating that the varied condition
showed a steeper slope coefficient on the reverse order bands compared
to the constant condition. This result suggests that varied training
enhanced participants' ability to discriminate between velocity bands,
but only when the band order was reversed during testing.

\subsection{Computational Model}\label{computational-model-1}

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-alm-diagram-1.pdf}}

}

\caption{\label{fig-alm-diagram}The Associative Learning Model (ALM).
The diagram illustrates the basic structure of the ALM model used in the
present work. Input nodes are activated as a function of their
similarity to the lower-boundary of the target band. The generalization
parameter, \(c\), determines the degree to which nearby input nodes are
activated. The output nodes are activated as a function of the weighted
sum of the input nodes. During training, when feedback is provided,
network weights connecting the input layer to the output layer are
updated via the delta rule.}

\end{figure}%

The modeling goal is to implement a full process model capable of both
1) producing novel responses and 2) modeling behavior in both the
learning and testing stages of the experiment. For this purpose, we will
apply the associative learning model (ALM) and the EXAM model of
function learning (\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh
et al., 1997}). ALM is a simple connectionist learning model which
closely resembles Kruschke's ALCOVE model
(\citeproc{ref-kruschkeALCOVEExemplarbasedConnectionist1992}{Kruschke,
1992}), with modifications to allow for the generation of continuous
responses.

\subsubsection{ALM \& Exam}\label{alm-exam}

ALM is a localist neural network model
(\citeproc{ref-pageConnectionistModellingPsychology2000a}{Page, 2000}),
with each input node corresponding to a particular stimulus, and each
output node corresponding to a particular response value. The units in
the input layer activate as a function of their Gaussian similarity to
the input stimulus ( a\_i(X) = exp(-c(X - X\_i)\^{}2) ). So, for
example, an input stimulus of value 55 would induce maximal activation
of the input unit tuned to 55. Depending on the value of the
generalization parameter, the nearby units (e.g., 54 and 56; 53 and 57)
may also activate to some degree. The units in the input layer activate
as a function of their similarity to a presented stimulus. The input
layer is fully connected to the output layer, and the activation for any
particular output node is simply the weighted sum of the connection
weights between that node and the input activations. The network then
produces a response by taking the weighted average of the output units
(recall that each output unit has a value corresponding to a particular
response). During training, the network receives feedback which
activates each output unit as a function of its distance from the ideal
level of activation necessary to produce the correct response. The
connection weights between input and output units are then updated via
the standard delta learning rule, where the magnitude of weight changes
are controlled by a learning rate parameter.

The EXAM model is an extension of ALM, with the same learning rule and
representational scheme for input and output units. EXAM differs from
ALM only in its response rule, as it includes a linear extrapolation
mechanism for generating novel responses. When a novel test stimulus,
\(X\), is presented, EXAM first identifies the two nearest training
stimuli, \(X_1\) and \(X_2\), that bracket \(X\). This is done based on
the Gaussian activation of input nodes, similar to ALM, but focuses on
identifying the closest known points for extrapolation.

\textbf{Slope Calculation}: EXAM calculates a local slope, \(S\), using
the responses associated with \(X_1\) and \(X_2\). This is computed as:

\[
   S = \frac{m(X_{1}) - m(X_{2})}{X_{1} - X_{2}}
   \]

where \(m(X_1)\) and \(m(X_2)\) are the output values from ALM
corresponding to the \(X_1\) and \(X_2\) inputs.

\textbf{Response Generation}: The response for the novel stimulus \(X\)
is then extrapolated using the slope \(S\):

\[
   E[Y|X] = m(X_1) + S \cdot |X - X_1|
   \]

Here, \(m(X_1)\) is the ALM response value from the training data for
the stimulus closest to \(X\), and \((X - X_1)\) represents the distance
between the novel stimulus and the nearest training stimulus.

Although this extrapolation rule departs from a strictly
similarity-based generalization mechanism, EXAM is distinct from pure
rule-based models in that it remains constrained by the weights learned
during training. EXAM retrieves the two nearest training inputs, and the
ALM responses associated with those inputs, and computes the slope
between these two points. The slope is then used to extrapolate the
response to the novel test stimulus. Because EXAM requires at least two
input-output pairs to generate a response, additional assumptions were
required in order for it to generate resposnes for the constant group.
We assumed that participants come to the task with prior knowledge of
the origin point (0,0), which can serve as a reference point necessary
for the model to generate responses for the constant group. This
assumption is motivated by previous function learning research
(\citeproc{ref-brownUnderestimationLinearFunction2017}{Brown \& Lacroix,
2017}), which through a series of manipulations of the y intercept of
the underlying function, found that participants consistently
demonstrated knowledge of, or a bias towards, the origin point (see
Kwantes \& Neal (\citeproc{ref-kwantesWhyPeopleUnderestimate2006}{2006})
for additional evidence of such a bias in function learning tasks).

See Table~\ref{tbl-alm-exam} for a full specification of the equations
that define ALM and EXAM, and Figure~\ref{fig-alm-diagram} for a visual
representation of the ALM model.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4028}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3472}}@{}}
\caption{ALM \& EXAM Equations}\label{tbl-alm-exam}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{ALM Response Generation}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{ALM Response Generation}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Input Activation &
\(a_i(X) = \frac{e^{-c(X-X_i)^2}}{\sum_{k=1}^M e^{-c(X-X_k)^2}}\) &
Input nodes activate as a function of Gaussian similarity to stimulus \\
Output Activation & \(O_j(X) = \sum_{k=1}^M w_{ji} \cdot a_i(X)\) &
Output unit \(O_j\) activation is the weighted sum of input activations
and association weights \\
Output Probability & \(P[Y_j|X] = \frac{O_j(X)}{\sum_{k=1}^M O_k(X)}\) &
The response, \(Y_j\) probabilites computed via Luce's choice rule \\
Mean Output &
\(m(X) = \sum_{j=1}^L Y_j \cdot \frac{O_j(x)}{\sum_{k=1}^M O_k(X)}\) &
Weighted average of probabilities determines response to X \\
& \textbf{ALM Learning} & \\
Feedback & \(f_j(Z) = e^{-c(Z-Y_j)^2}\) & feedback signal Z computed as
similarity between ideal response and observed response \\
magnitude of error & \(\Delta_{ji}=(f_{j}(Z)-o_{j}(X))a_{i}(X)\) & Delta
rule to update weights. \\
Update Weights & \(w_{ji}^{new}=w_{ji}+\eta\Delta_{ji}\) & Updates
scaled by learning rate parameter \(\eta\). \\
& \textbf{EXAM Extrapolation} & \\
Instance Retrieval & \(P[X_i|X] = \frac{a_i(X)}{\sum_{k=1}^M a_k(X)}\) &
Novel test stimulus \(X\) activates input nodes \(X_i\) \\
Slope Computation & \(S =\) \(\frac{m(X_{1})-m(X_{2})}{X_{1}-X_{2}}\) &
Slope value, \(S\) computed from nearest training instances \\
Response & \(E[Y|X_i] = m(X_i) + S \cdot [X - X_i]\) & Final EXAM
response is the ALM response for the nearest training stimulus,
\(m(X_i)\), adjusted by local slope \(S\). \\
\end{longtable}

\subsubsection{Model Fitting}\label{model-fitting}

To fit ALM and EXAM to our participant data, we employ a similar method
to McDaniel et al.
(\citeproc{ref-mcdanielPredictingTransferPerformance2009}{2009}),
wherein we examine the performance of each model after being fit to
various subsets of the data. Each model was fit to the data with three
separate procedures: 1) fit to maximize predictions of the testing data,
2) fit to maximize predictions of both the training and testing data, 3)
fit to maximize predictions of the just the training data. We refer to
this fitting manipulations as ``Fit Method'' in the tables and figures
below. It should be emphasized that for all three fit methods, the ALM
and EXAM models behave identically - with weights updating only during
the training phase. Models were fit separately to the data of each
individual participant. The free parameters for both models are the
generalization (\(c\)) and learning rate (\(lr\)) parameters. Parameter
estimation was performed using approximate Bayesian computation (ABC),
which we describe in detail below.

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, left=2mm, colframe=quarto-callout-color-frame, toprule=.15mm, rightrule=.15mm, leftrule=.75mm, bottomrule=.15mm, arc=.35mm, breakable, colback=white]

\textbf{\faIcon{lightbulb} Approximate Bayesian Computation}

To estimate the parameters of ALM and EXAM, we used approximate Bayesian
computation (ABC), enabling us to obtain an estimate of the posterior
distribution of the generalization and learning rate parameters for each
individual. ABC belongs to the class of simulation-based inference
methods
(\citeproc{ref-cranmerFrontierSimulationbasedInference2020}{Cranmer et
al., 2020}), which have begun being used for parameter estimation in
cognitive modeling relatively recently
(\citeproc{ref-kangasraasioParameterInferenceComputational2019}{Kangasrääsiö
et al., 2019};
\citeproc{ref-turnerBayesianAnalysisSimulationbased2016}{Turner et al.,
2016}; \citeproc{ref-turnerTutorialApproximateBayesian2012}{Turner \&
Van Zandt, 2012}). Although they can be applied to any model from which
data can be simulated, ABC methods are most useful for complex models
that lack an explicit likelihood function (e.g., many neural network
models).

The general ABC procedure is to 1) define a prior distribution over
model parameters. 2) sample candidate parameter values, \(\theta^*\),
from the prior. 3) Use \(\theta^*\) to generate a simulated dataset,
\(Data_{sim}\). 4) Compute a measure of discrepancy between the
simulated and observed datasets, \(discrep\)(\(Data_{sim}\),
\(Data_{obs}\)). 5) Accept \(\theta^*\) if the discrepancy is less than
the tolerance threshold, \(\epsilon\), otherwise reject \(\theta^*\). 6)
Repeat until the desired number of posterior samples are obtained.

Although simple in the abstract, implementations of ABC require
researchers to make a number of non-trivial decisions as to i) the
discrepancy function between observed and simulated data, ii) whether to
compute the discrepancy between trial level data, or a summary statistic
of the datasets, iii) the value of the minimum tolerance \(\epsilon\)
between simulated and observed data. For the present work, we follow the
guidelines from previously published ABC tutorials
(\citeproc{ref-farrellComputationalModelingCognition2018}{Farrell \&
Lewandowsky, 2018};
\citeproc{ref-turnerTutorialApproximateBayesian2012}{Turner \& Van
Zandt, 2012}). For the test stage, we summarized datasets with mean
velocity of each band in the observed dataset as \(V_{obs}^{(k)}\) and
in the simulated dataset as \(V_{sim}^{(k)}\), where \(k\) represents
each of the six velocity bands. For computing the discrepancy between
datasets in the training stage, we aggregated training trials into three
equally sized blocks (separately for each velocity band in the case of
the varied group). After obtaining the summary statistics of the
simulated and observed datasets, the discrepancy was computed as the
mean of the absolute difference between simulated and observed datasets
(Equation~\ref{eq-discrep-test} and Equation~\ref{eq-discrep-train}).
For the models fit to both training and testing data, discrepancies were
computed for both stages, and then averaged together.

\begin{equation}\phantomsection\label{eq-discrep-test}{
discrep_{Test}(Data_{sim}, Data_{obs}) = \frac{1}{6} \sum_{k=1}^{6} |V_{obs}^{(k)} - V_{sim}^{(k)}|
}\end{equation}

\begin{equation}\phantomsection\label{eq-discrep-train}{
\begin{aligned} \\
discrep_{Train,constant}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks}} \sum_{j=1}^{N_{blocks}} |V_{obs,constant}^{(j)} - V_{sim,constant}^{(j)}| \\ \\
discrep_{Train,varied}(Data_{sim}, Data_{obs}) = \frac{1}{N_{blocks} \times 3} \sum_{j=1}^{N_{blocks}} \sum_{k=1}^{3} |V_{obs,varied}^{(j,k)} - V_{sim,varied}^{(j,k)}|
\end{aligned}
}\end{equation}

The final component of our ABC implementation is the determination of an
appropriate value of \(\epsilon\). The setting of \(\epsilon\) exerts
strong influence on the approximated posterior distribution. Smaller
values of \(\epsilon\) increase the rejection rate, and improve the
fidelity of the approximated posterior, while larger values result in an
ABC sampler that simply reproduces the prior distribution. Because the
individual participants in our dataset differed substantially in terms
of the noisiness of their data, we employed an adaptive tolerance
setting strategy to tailor \(\epsilon\) to each individual. The initial
value of \(\epsilon\) was set to the overall standard deviation of each
individual's velocity values. Thus, sampled parameter values that
generated simulated data within a standard deviation of the observed
data were accepted, while worse performing parameters were rejected.
After every 300 samples the tolerance was allowed to increase only if
the current acceptance rate of the algorithm was less than 1\%. In such
cases, the tolerance was shifted towards the average discrepancy of the
5 best samples obtained thus far. To ensure the acceptance rate did not
become overly permissive, \(\epsilon\) was also allowed to decrease
every time a sample was accepted into the posterior.

\end{tcolorbox}

For each of the 156 participants from Experiment 1, the ABC algorithm
was run until 200 samples of parameters were accepted into the posterior
distribution. Obtaining this number of posterior samples required an
average of 205,000 simulation runs per participant. Fitting each
combination of participant, Model (EXAM \& ALM), and fitting method
(Test only, Train only, Test \& Train) required a total of 192 million
simulation runs. To facilitate these intensive computational demands, we
used the Future Package in R
(\citeproc{ref-bengtssonUnifyingFrameworkParallel2021}{Bengtsson,
2021}), allowing us to parallelize computations across a cluster of ten
M1 iMacs, each with 8 cores.

\subsubsection{Modelling Results}\label{modelling-results}

\begingroup
\fontsize{9.0pt}{10.8pt}\selectfont

\begin{longtable}{lcrrrr}

\caption{\label{tbl-htw-modelError-e1}Model errors predicting empirical
data from Experiment 1 - aggregated over the full posterior distribution
for each participant. Note that Fit Method refers to the subset of the
data that the model was trained on, while Task Stage refers to the
subset of the data that the model was evaluated on.}

\tabularnewline

\toprule
 &  & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} \\ 
\cmidrule(lr){3-4} \cmidrule(lr){5-6}
{Task Stage} & {Fit Method} & Constant & Varied & Constant & Varied \\ 
\midrule\addlinespace[2.5pt]
{\cellcolor[HTML]{FFFFFF}{Test}} & {\cellcolor[HTML]{FFFFFF}{Fit to Test Data}} & {\cellcolor[HTML]{FFFFFF}{199.93}} & {\cellcolor[HTML]{FFFFFF}{103.36}} & {\cellcolor[HTML]{FFFFFF}{104.01}} & {\cellcolor[HTML]{FFFFFF}{85.68}} \\ 
{\cellcolor[HTML]{FFFFFF}{Test}} & {\cellcolor[HTML]{FFFFFF}{Fit to Test \& Training Data}} & {\cellcolor[HTML]{FFFFFF}{216.97}} & {\cellcolor[HTML]{FFFFFF}{170.28}} & {\cellcolor[HTML]{FFFFFF}{127.94}} & {\cellcolor[HTML]{FFFFFF}{144.86}} \\ 
{\cellcolor[HTML]{FFFFFF}{Test}} & {\cellcolor[HTML]{FFFFFF}{Fit to Training Data}} & {\cellcolor[HTML]{FFFFFF}{467.73}} & {\cellcolor[HTML]{FFFFFF}{291.38}} & {\cellcolor[HTML]{FFFFFF}{273.30}} & {\cellcolor[HTML]{FFFFFF}{297.91}} \\ 
{\cellcolor[HTML]{FFFFFF}{Train}} & {\cellcolor[HTML]{FFFFFF}{Fit to Test Data}} & {\cellcolor[HTML]{FFFFFF}{297.82}} & {\cellcolor[HTML]{FFFFFF}{2,016.01}} & {\cellcolor[HTML]{FFFFFF}{53.90}} & {\cellcolor[HTML]{FFFFFF}{184.00}} \\ 
{\cellcolor[HTML]{FFFFFF}{Train}} & {\cellcolor[HTML]{FFFFFF}{Fit to Test \& Training Data}} & {\cellcolor[HTML]{FFFFFF}{57.40}} & {\cellcolor[HTML]{FFFFFF}{132.32}} & {\cellcolor[HTML]{FFFFFF}{42.92}} & {\cellcolor[HTML]{FFFFFF}{127.90}} \\ 
{\cellcolor[HTML]{FFFFFF}{Train}} & {\cellcolor[HTML]{FFFFFF}{Fit to Training Data}} & {\cellcolor[HTML]{FFFFFF}{51.77}} & {\cellcolor[HTML]{FFFFFF}{103.48}} & {\cellcolor[HTML]{FFFFFF}{51.43}} & {\cellcolor[HTML]{FFFFFF}{107.03}} \\ 
\bottomrule

\end{longtable}

\endgroup

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-htw-post-dist-1.pdf}}

}

\caption{\label{fig-htw-post-dist}Posterior Distributions of \(c\) and
\(lr\) parameters. Points represent median values, thicker intervals
represent 66\% credible intervals and thin intervals represent 95\%
credible intervals around the median. Note that the y-axes of the plots
for the \(c\) parameter are scaled logarithmically.}

\end{figure}%

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-htw-resid-pred-1.pdf}}

}

\caption{\label{fig-htw-resid-pred}Model residuals for each combination
of training condition, fit method, and model. Residuals reflect the
difference between observed and predicted values. Lower values indicate
better model fit. Note that y-axes are scaled differently between
facets. A) Residuals predicting each block of the training data. B)
Residuals predicting each band during the testing stage. Bolded bars
indicate bands that were trained, non-bold bars indicate extrapolation
bands.}

\end{figure}%

The posterior distributions of the \(c\) and \(lr\) parameters are shown
Figure~\ref{fig-htw-post-dist}, and model predictions are shown
alongside the empirical data in Figure~\ref{fig-cm-vx-pat}. There were
substantial individual differences in the posteriors of both parameters,
with the within-group individual differences generally swamped any
between-group or between-model differences. The magnitude of these
individual differences remains even if we consider only the single best
parameter set for each subject.

We used the posterior distribution of \(c\) and \(lr\) parameters to
generate a posterior predictive distribution of the observed data for
each participant, which then allows us to compare the empirical data to
the full range of predictions from each model. Aggregated residuals are
displayed in Figure~\ref{fig-htw-resid-pred}. The pattern of training
stage residual errors are unsurprising across the combinations of models
and fitting method . Differences in training performance between ALM and
EXAM are generally minor (the two models have identical learning
mechanisms). The differences in the magnitude of residuals across the
three fitting methods are also straightforward, with massive errors for
the `fit to Test Only' model, and the smallest errors for the `fit to
train only' models. It is also noteworthy that the residual errors are
generally larger for the first block of training, which is likely due to
the initial values of the ALM weights being unconstrained by whatever
initial biases participants tend to bring to the task. Future work may
explore the ability of the models to capture more fine grained aspects
of the learning trajectories. However for the present purposes, our
primary interest is in the ability of ALM and EXAM to account for the
testing patterns while being constrained, or not constrained, by the
training data. All subsequent analyses and discussion will thus focus on
the testing stage.

The residuals of the model predictions for the testing stage
(Figure~\ref{fig-htw-resid-pred}) show an unsurprising pattern across
fitting methods - with models fit only to the test data showing the best
performance, followed by models fit to both training and test data, and
with models fit only to the training data showing the worst performance
(note that Y-axes are scaled different between plots). Although EXAM
tends to perform better for both Constant and Varied participants (see
also Figure~\ref{fig-ee-e1}), the relative advantage of EXAM is
generally larger for the Constant group - a pattern consistent across
all three fitting methods. The primary predictive difference between ALM
and EXAM is made clear in Figure~\ref{fig-cm-vx-pat}, which directly
compares the observed data against the posterior predictive
distributions for both models. Regardless of how the models are fit,
only EXAM can capture the pattern where participants are able to
discriminate all 6 target bands.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-cm-vx-pat-1.pdf}}

}

\caption{\label{fig-cm-vx-pat}Empirical data and Model predictions for
mean velocity across target bands. Fitting methods (Test Only, Test \&
Train, Train Only) - are separated across rows, and Training Condition
(Constant vs.~Varied) are separated by columns. Each facet contains the
predictions of ALM and EXAM, alongside the observed data.}

\end{figure}%

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-ee-e1-1.pdf}}

}

\caption{\label{fig-ee-e1}A-C) Conditional effects of Model (ALM vs
EXAM) and Condition (Constant vs.~Varied). Lower values on the y axis
indicate better model fit. D) Specific contrasts of model performance
comparing 1) EXAM fits between constant and varied training; 2) ALM
vs.~EXAM for the varied group; 3) ALM fits between constant and varied.
Negative error differences indicate that the term on the left side
(e.g., EXAM Constant) tended to have smaller model residuals.}

\end{figure}%

To quantitatively assess the differences in performance between models,
we fit a Bayesian regression model predicting the errors of the
posterior predictions of each model as a function of the Model (ALM
vs.~EXAM) and training condition (Constant vs.~Varied).

Model errors were significantly lower for EXAM (\(\beta\) = -37.54, 95\%
CrI {[}-60.4, -14.17{]}, pd = 99.85\%) than ALM. There was also a
significant interaction between Model and Condition (\(\beta\) = 60.42,
95\% CrI {[}36.17, 83.85{]}, pd = 100\%), indicating that the advantage
of EXAM over ALM was significantly greater for the constant group. To
assess whether EXAM predicts performance significantly better for
Constant than for Varied subjects, we calculated the difference in model
error between the Constant and Varied conditions specifically for EXAM.
The results indicated that the model error for EXAM was significantly
lower in the Constant condition compared to the Varied condition, with a
mean difference of -22.88 (95\% CrI {[}-46.02, -0.97{]}, pd = 0.98).

\begingroup
\fontsize{9.0pt}{10.8pt}\selectfont

\begin{longtable}{lrrrrrrrr}

\caption{\label{tbl-htw-modelError-e23}Models errors predicting
empirical data - aggregated over all participants, posterior parameter
values, and velocity bands. Note that Fit Method refers to the subset of
the data that the model was trained on, while Task Stage refers to the
subset of the data that the model was evaluated on.}

\tabularnewline

\toprule
 & \multicolumn{4}{c}{E2} & \multicolumn{4}{c}{E3} \\ 
\cmidrule(lr){2-5} \cmidrule(lr){6-9}
 & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} & \multicolumn{2}{c}{ALM} & \multicolumn{2}{c}{EXAM} \\ 
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
Task Stage & Constant & Varied & Constant & Varied & Constant & Varied & Constant & Varied \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{9}{l}{Fit to Test Data} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
{\cellcolor[HTML]{FFFFFF}{Test}} & {\cellcolor[HTML]{FFFFFF}{239.7}} & {\cellcolor[HTML]{FFFFFF}{129.8}} & {\cellcolor[HTML]{FFFFFF}{99.7}} & {\cellcolor[HTML]{FFFFFF}{88.2}} & {\cellcolor[HTML]{FFFFFF}{170.1}} & {\cellcolor[HTML]{FFFFFF}{106.1}} & {\cellcolor[HTML]{FFFFFF}{92.3}} & {\cellcolor[HTML]{FFFFFF}{72.8}} \\ 
{\cellcolor[HTML]{FFFFFF}{Train}} & {\cellcolor[HTML]{FFFFFF}{53.1}} & {\cellcolor[HTML]{FFFFFF}{527.1}} & {\cellcolor[HTML]{FFFFFF}{108.1}} & {\cellcolor[HTML]{FFFFFF}{169.3}} & {\cellcolor[HTML]{FFFFFF}{70.9}} & {\cellcolor[HTML]{FFFFFF}{543.5}} & {\cellcolor[HTML]{FFFFFF}{157.8}} & {\cellcolor[HTML]{FFFFFF}{212.7}} \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{9}{l}{Fit to Test \& Training Data} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
{\cellcolor[HTML]{FFFFFF}{Test}} & {\cellcolor[HTML]{FFFFFF}{266.0}} & {\cellcolor[HTML]{FFFFFF}{208.2}} & {\cellcolor[HTML]{FFFFFF}{125.1}} & {\cellcolor[HTML]{FFFFFF}{126.4}} & {\cellcolor[HTML]{FFFFFF}{197.7}} & {\cellcolor[HTML]{FFFFFF}{189.5}} & {\cellcolor[HTML]{FFFFFF}{130.0}} & {\cellcolor[HTML]{FFFFFF}{128.5}} \\ 
{\cellcolor[HTML]{FFFFFF}{Train}} & {\cellcolor[HTML]{FFFFFF}{40.0}} & {\cellcolor[HTML]{FFFFFF}{35.4}} & {\cellcolor[HTML]{FFFFFF}{30.4}} & {\cellcolor[HTML]{FFFFFF}{23.6}} & {\cellcolor[HTML]{FFFFFF}{49.1}} & {\cellcolor[HTML]{FFFFFF}{85.6}} & {\cellcolor[HTML]{FFFFFF}{49.2}} & {\cellcolor[HTML]{FFFFFF}{78.4}} \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{9}{l}{Fit to Training Data} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
{\cellcolor[HTML]{FFFFFF}{Test}} & {\cellcolor[HTML]{FFFFFF}{357.4}} & {\cellcolor[HTML]{FFFFFF}{295.9}} & {\cellcolor[HTML]{FFFFFF}{305.1}} & {\cellcolor[HTML]{FFFFFF}{234.5}} & {\cellcolor[HTML]{FFFFFF}{415.0}} & {\cellcolor[HTML]{FFFFFF}{298.8}} & {\cellcolor[HTML]{FFFFFF}{295.5}} & {\cellcolor[HTML]{FFFFFF}{243.7}} \\ 
{\cellcolor[HTML]{FFFFFF}{Train}} & {\cellcolor[HTML]{FFFFFF}{42.5}} & {\cellcolor[HTML]{FFFFFF}{23.0}} & {\cellcolor[HTML]{FFFFFF}{43.2}} & {\cellcolor[HTML]{FFFFFF}{22.6}} & {\cellcolor[HTML]{FFFFFF}{51.4}} & {\cellcolor[HTML]{FFFFFF}{63.8}} & {\cellcolor[HTML]{FFFFFF}{51.8}} & {\cellcolor[HTML]{FFFFFF}{65.3}} \\ 
\bottomrule

\end{longtable}

\endgroup

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-cm-vx-pat-e2-e3-1.pdf}}

}

\caption{\label{fig-cm-vx-pat-e2-e3}Empirical data and Model predictions
from Experiment 2 and 3 for the testing stage. Observed data is shown on
the right. Bolded bars indicate bands that were trained, non-bold bars
indicate extrapolation bands.}

\end{figure}%

\newpage{}

\scriptsize

\begingroup
\fontsize{9.0pt}{10.8pt}\selectfont

\begin{longtable}{llrrrr}

\caption{\label{tbl-htw-ee-e23}Results of Bayesian Regression models
predicting model error as a function of Model (ALM vs.~EXAM), Condition
(Constant vs.~Varied), and the interaction between Model and Condition.
The values represent the estimated coefficient for each term, with 95\%
credible intervals in brackets. The intercept reflects the baseline of
ALM and Constant. The other estimates indicate deviations from the
baseline for the EXAM mode and varied condition. Lower values indicate
better model fit.}

\tabularnewline

\toprule
 &  &  & \multicolumn{2}{c}{Credible Interval} &  \\ 
\cmidrule(lr){4-5}
Experiment & Term & Estimate & 95\% CrI Lower & 95\% CrI Upper & pd \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{6}{l}{Experiment 1} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
Exp 1 & Intercept & 176.3 & 156.9 & 194.6 & 1.00 \\ 
Exp 1 & ModelEXAM & -88.4 & -104.5 & -71.8 & 1.00 \\ 
Exp 1 & conditVaried & -37.5 & -60.4 & -14.2 & 1.00 \\ 
Exp 1 & ModelEXAM:conditVaried & {\bfseries \cellcolor[HTML]{FFFFFF}{60.4}} & 36.2 & 83.8 & {\bfseries \cellcolor[HTML]{FFFFFF}{1.00}} \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{6}{l}{Experiment 2} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
Exp 2 & Intercept & 245.9 & 226.2 & 264.5 & 1.00 \\ 
Exp 2 & ModelEXAM & -137.7 & -160.2 & -115.5 & 1.00 \\ 
Exp 2 & conditVaried & -86.4 & -113.5 & -59.3 & 1.00 \\ 
Exp 2 & ModelEXAM:conditVaried & {\bfseries \cellcolor[HTML]{FFFFFF}{56.9}} & 25.3 & 88.0 & {\bfseries \cellcolor[HTML]{FFFFFF}{1.00}} \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{6}{l}{Experiment 3} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
Exp 3 & Intercept & 164.8 & 140.1 & 189.4 & 1.00 \\ 
Exp 3 & ModelEXAM & -65.7 & -86.0 & -46.0 & 1.00 \\ 
Exp 3 & conditVaried & -40.6 & -75.9 & -3.0 & 0.98 \\ 
Exp 3 & bandOrderReverse & 25.5 & -9.3 & 58.7 & 0.93 \\ 
Exp 3 & ModelEXAM:conditVaried & {\bfseries \cellcolor[HTML]{FFFFFF}{41.9}} & 11.2 & 72.5 & {\bfseries \cellcolor[HTML]{FFFFFF}{0.99}} \\ 
Exp 3 & ModelEXAM:bandOrderReverse & -7.3 & -34.5 & 21.1 & 0.70 \\ 
Exp 3 & conditVaried:bandOrderReverse & 30.8 & -19.6 & 83.6 & 0.88 \\ 
Exp 3 & ModelEXAM:conditVaried:bandOrderReverse & -60.6 & -101.8 & -18.7 & 1.00 \\ 
\bottomrule

\end{longtable}

\endgroup

\normalsize

\emph{Model Fits to Experiment 2 and 3.} Data from Experiments 2 and 3
were fit to ALM and EXAM in the same manner as Experiment 1. For
brevity, we only plot and discuss the results of the ``fit to training
and testing data'' models - results from the other fitting methods can
be found in the appendix. The model fitting results for Experiments 2
and 3 closely mirrored those observed in Experiment 1. The Bayesian
regression models predicting model error as a function of Model (ALM
vs.~EXAM), Condition (Constant vs.~Varied), and their interaction (see
Table~\ref{tbl-htw-ee-e23}) revealed a consistent main effect of Model
across all three experiments. The negative coefficients for the
ModelEXAM term (Exp 2: \(\beta\) = -86.39, 95\% CrI -113.52, -59.31, pd
= 100\%; Exp 3: \(\beta\) = -40.61, 95\% CrI -75.9, -3.02, pd = 98.17\%)
indicate that EXAM outperformed ALM in both experiments. Furthermore,
the interaction between Model and Condition was significant in both
Experiment 2 (\(\beta\) = 56.87, 95\% CrI 25.26, 88.04, pd = 99.98\%)
and Experiment 3 (\(\beta\) = 41.9, 95\% CrI 11.2, 72.54, pd = 99.35\%),
suggesting that the superiority of EXAM over ALM was more pronounced for
the Constant group compared to the Varied group, as was the case in
Experiment 1. Recall that Experiment 3 included participants in both the
original and reverse order conditions - and that this manipulation
interacted with the effect of training condition. We thus also
controlled for band order in our Bayesian Regression assessing the
relative performance of EXAM and ALM in Experiment 3. There was a
significant three way interaction between Model, Training Condition, and
Band Order (\(\beta\) = -60.6, 95\% CrI -101.8, -18.66, pd = 99.83\%),
indicating that the relative advantage of EXAM over ALM was only more
pronounced in the original order condition, and not the reverse order
condition (see Figure~\ref{fig-e2_e3_ae}).

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-e2_e3_ae-1.pdf}}

}

\caption{\label{fig-e2_e3_ae}Conditional effects of Model (ALM vs EXAM)
and Condition (Constant vs.~Varied) on Model Error for Experiments 2 and
3 data. Experiment 3 also includes a condition for the order of training
vs.~testing bands (original order vs.~reverse order).}

\end{figure}%

\emph{Computational Model Summary}. Across all three experiments, the
model fits consistently favored the Extrapolation-Association Model
(EXAM) over the Associative Learning Model (ALM). This preference for
EXAM was particularly pronounced for participants in the constant
training conditions (note the positive coefficients on
ModelEXAM:conditVaried interaction terms Table~\ref{tbl-htw-ee-e23}).
This pattern is clearly illustrated in Figure~\ref{fig-htw-best-model},
which plots the difference in model errors between ALM and EXAM for each
individual participant. Both varied and constant conditions have a
greater proportion of subjects better fit by EXAM (positive error
differences), with the magnitude of EXAM's advantage visibly larger for
the constant group.

The superior performance of EXAM, especially for the constant training
groups, may initially seem counterintuitive. One might assume that
exposure to multiple, varied examples would be necessary to extract an
abstract rule. However, EXAM is not a conventional rule-based model; it
does not require the explicit abstraction of a rule. Instead, rule-based
responses emerge during the retrieval process. The constant groups'
formation of a single, accurate input-output association, combined with
the usefulness of the zero point, seem to have been sufficient for EXAM
to capture their performance. A potential concern is that the assumption
of participants utilizing the zero point essentially transforms the
extrapolation problem into an interpolation problem. However, this
concern is mitigated by the consistency of the results across both the
original and reversed order conditions (the testing extrapolation bands
fall in between the constant training band and the 0 point in experiment
1, but not in experiment 2).

The fits to the individual participants also reveal a number of
interesting cases where the models struggle to capture the data
(Figure~\ref{fig-htw-indv-pred}). For example participant 68 exhibits a
strong non-monotonicity in the highest velocity band, a pattern which
ALM can mimic, but which EXAM cannot capture, given that it enforces a
simple linear relationship between target velocity and response.
Participant 70 (lower right corner of Figure~\ref{fig-htw-indv-pred})
had a roughly parabolic response pattern in their observed data, a
pattern which neither model can properly reproduce, but which causes
EXAM to perform particularly poorly.

\emph{Modeling Limitations.} The present work compared models based on
their ability to predict the observed data, without employing
conventional model fit indices such as the Akaike Information Criterion
(AIC) or the Bayesian Information Criterion (BIC). These indices, which
penalize models based on their number of free parameters, would have
been of limited utility in the current case, as both ALM and EXAM have
two free parameters. However, despite having the same number of free
parameters, EXAM could still be considered the more complex model, as it
incorporates all the components of ALM plus an additional mechanism for
rule-based responding. A more comprehensive model comparison approach
might involve performing cross-validation with a held-out subset of the
data (\citeproc{ref-mezzadriHoldoutStrategySelecting2022}{Mezzadri et
al., 2022}) or penalizing models based on the range of patterns they can
produce (\citeproc{ref-domeGdistanceComparisonModel2023}{Dome \& Wills,
2023}), under the assumption that more constrained models are more
impressive when they do adequately fit a given pattern of results.

\newpage{}

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-htw-best-model-1.pdf}}

}

\caption{\label{fig-htw-best-model}Difference in model errors for each
participant, with models fit to both train and test data. Positive
values favor EXAM, while negative values favor ALM.}

\end{figure}%

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-pdf/fig-htw-indv-pred-1.pdf}}

}

\caption{\label{fig-htw-indv-pred}Model predictions alongside observed
data for a subset of individual participants. A) 3 constant and 3 varied
participants fit to both the test and training data. B) 3 constant and 3
varied subjects fit to only the trainign data. Bolded bars indicate
bands that were trained, non-bold bars indicate extrapolation bands.}

\end{figure}%

\subsection{Project 2 Discussion}\label{project-2-discussion}

Across three experiments, we investigated the impact of training
variability on learning and extrapolation in a visuomotor function
learning task.

In Experiment 1, participants in the varied training condition, who
experienced a wider range of velocity bands during training, showed
lower accuracy at the end of training compared to those in the constant
training condition. Crucially, during the testing phase, the varied
group exhibited significantly larger deviations from the target velocity
bands, particularly for the extrapolation bands that were not
encountered during training. The varied group also showed less
discrimination between velocity bands, as evidenced by shallower slopes
when predicting response velocity from target velocity band.

Experiment 2 extended these findings by reversing the order of the
training and testing bands. Similar to Experiment 1, the varied group
demonstrated poorer performance during both training and testing phases.
However, unlike Experiment 1, the varied group did not show a
significant difference in discrimination between bands compared to the
constant group.

In Experiment 3, we provided only ordinal feedback during training, in
contrast to the continuous feedback provided in the previous
experiments. Participants were assigned to both an order condition
(original or reverse) and a training condition (constant or varied). The
varied condition showed larger deviations at the end of training,
consistent with the previous experiments. Interestingly, there was a
significant interaction between training condition and band order, with
the varied condition showing greater accuracy in the reverse order
condition. During testing, the varied group once again exhibited larger
deviations, particularly for the extrapolation bands. The reverse order
conditions showed smaller deviations compared to the original order
conditions. Discrimination between velocity bands was poorer for the
varied group in the original order condition, but not in the reverse
order condition.

All three of our experiments yielded evidence that varied training
conditions produced less learning by the end of training, a pattern
consistent with much of the previous research on the influence of
training variability
(\citeproc{ref-catalanoDistantTransferCoincident1984a}{Catalano \&
Kleiner, 1984};
\citeproc{ref-soderstromLearningPerformanceIntegrative2015}{Soderstrom
\& Bjork, 2015};
\citeproc{ref-wrisbergVariabilityPracticeHypothesis1987}{Wrisberg et
al., 1987}). The sole exception to this pattern was the reverse order
condition in Experiment 3, where the varied group was not significantly
worse than the constant group. Neither the varied condition trained with
the same reverse-order items in Experiment 2, nor the original-order
varied condition trained with ordinal feedback in Experiment 3 were able
to match the performance of their complementary constant groups by the
end of training, suggesting that the relative success of the
ordinal-reverse ordered varied group cannot be attributed to item or
feedback effects alone.

Our findings also diverge from the two previous studies that cleanly
manipulated the variability of training items in a function learning
task (\citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al.,
1997}; \citeproc{ref-vandamMappingShapeVisuomotor2015}{van Dam \& Ernst,
2015}), although the varied training condition of van Dam \& Ernst
(\citeproc{ref-vandamMappingShapeVisuomotor2015}{2015}) also exhibited
less learning, neither of these previous studies observed any difference
between training conditions in extrapolation to novel items. Like DeLosh
et al. (\citeproc{ref-deloshExtrapolationSineQua1997}{1997}), our
participants exhibited above chance extrapolation/discrimination of
novel items, however they observed no difference between any of their
three training conditions. A noteworthy difference between our studies
is that DeLosh et al.
(\citeproc{ref-deloshExtrapolationSineQua1997}{1997}) trained
participants with either 8, 20, or 50 unique items (all receiving the
same total number of training trials). These larger sets of unique
items, combined with the fact that participants achieved near ceiling
level performance by the end of training, may have made it more
difficult to observe any between-group differences of training variation
in their study. van Dam \& Ernst
(\citeproc{ref-vandamMappingShapeVisuomotor2015}{2015}) 's variability
manipulation was more similar to our own, as they trained participants
with either 2 or 5 unique items. However, although the mapping between
their input stimuli and motor responses was technically linear, the
input dimension was more complex than our own, as it was defined by the
degree of ``spikiness'' of the input shape. This entirely arbitrary
mapping also would have precluded any sensible ``0'' point, which may
partially explain why neither of their training conditions were able to
extrapolate linearly in the manner observed in the current study or in
DeLosh et al. (\citeproc{ref-deloshExtrapolationSineQua1997}{1997}).

To explain our results, we turned to the well established EXAM and ALM
models. The disproportionate success of EXAM in capturing the
performance of participants under the constant training condition
suggests that rule-based extrapolation can emerge even from a limited
set of training examples. This success hinges on the assumption that
participants are able to leverage prior knowledge of the zero-point
reference (\citeproc{ref-brownUnderestimationLinearFunction2017}{Brown
\& Lacroix, 2017};
\citeproc{ref-kwantesWhyPeopleUnderestimate2006}{Kwantes \& Neal,
2006}). The zero-point reference, combined with accurate learning of the
single trained velocity band enabled EXAM to capture the extrapolation
patterns of the constant participants. However, it's important to
acknowledge that the ALM model provided a better fit for a subset of
participants in each of our three experiment, highlighting the presence
of substantial individual differences in generalization patterns.

This finding illustrates the importance of considering task structure
when evaluating the effects of training variability on generalization
and extrapolation. Some tasks, like the one in this study, may permit
the use of zero-point knowledge or other prior information, while others
may not. For example, a zero point may be less relevant in visuomotor
tasks with complex rotations
(\citeproc{ref-rollerVariablePracticeLenses2001}{Roller et al., 2001};
\citeproc{ref-vandamMappingShapeVisuomotor2015}{van Dam \& Ernst,
2015}), or in complex sports techniques
(\citeproc{ref-northEffectConsistentVaried2019}{North et al., 2019}).
Future research should systematically investigate how different task
structures interact with training variability to influence learning
outcomes and generalization abilities, taking into account factors such
as the availability of prior knowledge, the complexity of the task, and
the specific learning mechanisms involved. This approach could help
reconcile seemingly contradictory findings in the literature and provide
more nuanced guidelines for designing effective training protocols
across various domains.

\emph{Limitations}

While the present study provides valuable insights into the influence of
training variability on visuomotor function learning and extrapolation,
there are several limitations that should be flagged. First, although
the constant training group never had experience from a velocity band
closer to the extrapolation bands than the varied group, they always had
three times more trials with the nearest velocity band. Such a
difference may be an unavoidable consequence of a varied vs.~constant
design which matches the total number of training trials between the two
groups. However, in order to more carefully tease apart the influence of
variability from the influence of frequency/repetition effects, future
research could explore alternative designs that maintain the variability
manipulation while equating the amount of training on the nearest
examples across conditions, such as by increasing the total number of
trials for the varied group. Another limitation is that the testing
stage did not include any interpolation items, i.e.~the participants
were tested only from the training bands they experienced during
training, or from extrapolation bands. The absence of interpolation
testing makes it more difficult to distinguish between the effects of
training variability on extrapolation specifically, as opposed to
generalization more broadly. Of course, the nature of the constant
training condition makes interpolation testing impossible to implement,
however future studies might compare training regimes that each include
at least 2 distinct items, but still differ in the total amount of
variability experienced, which would then allow groups to be compared in
terms of both interpolation and extrapolation testing. Finally, the task
employed in the present study consisted of only a linear, positive
function. Previous work in human function learning has repeatedly shown
that such functions are among the easiest to learn, but that humans are
nonetheless capable of learning negative, non-linear, or discontinuous
functions
(\citeproc{ref-busemeyerLearningFunctionalRelations1997}{Busemeyer et
al., 1997}; \citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al.,
1997}; \citeproc{ref-kalishLearningExtrapolatingPeriodic2013}{Kalish,
2013}; \citeproc{ref-mcdanielPredictingTransferPerformance2009}{McDaniel
et al., 2009}). It thus remains an open question as to whether the
influence of training variability might interact with various components
of the to-be-learned function.

\section{General Discussion}\label{general-discussion}

To facilitate ease of comparison between the two projects and their
respective tasks, we'll now refer to project 1 as Hit The Target (HTT)
and project 2 as Hit The Wall (HTW).

\subsection{Empirical and Modeling
Summary}\label{empirical-and-modeling-summary}

Across both projects, we investigated the influence of training
variability on learning and generalization in computerized visuomotor
skill learning, and function learning tasks. In project 1 (HTT),
experiments 1 and 2 demonstrated that varied training led to superior
testing performance compared to constant training. In Experiment 1, the
varied group even outperformed the constant group even when testing from
the constant groups trained position. In contrast, Project 2 (HTW) found
the opposite pattern - the varied training groups exhibited poorer
performance than the constant groups, both in terms of training
accuracy, accuracy in extrapolation testing, and, in a subset of the
experiments, the varied group showed a diminished ability to
discriminate between bands. This detrimental effect of variability was
observed across three experiments, with the exception of the reverse
order condition in Experiment 3, where the varied group was able to
match the constant group's performance.

Both projects also included computational modeling componenents. In
Project 1, the IGAS model was introduced as a means of addressing the
lack of control for similarity between training and testing conditions
common to previous work in the ``benefits of variability'' literature.
The IGAS model provides a theoretically motivated method of quantifying
the similarity between training experience and testing conditions. The
resulting similarity metric (i.e.~our 1c-similarity) is shown to be a
significant predictor of testing performance on its own, and when added
as a covariate to the statistical model used to compare the constant and
varied training groups. We then showed the group-level effect of
training variability on testing performance can be accounted for with
the additional assumption that training variability influences the
generalization gradient. The contribution of the IGAS model was thus
twofold:~ 1) providing a theoretically justifiable method of
quantifying/controlling for similarity between training and testing, and
2) demonstrating the viability of a flexible-similarity based
generalization account for the empirically observed benefit of
variability in our task. Although similar approaches have been employed
in other domains, both contributions are novel additions to the large
body of research assessing the effect of constant vs.~varied training
manipulations in visuomotor skill tasks.

Although theoretically motivated, the IGAS model of Project 1 is best
categorized as a descriptive measurement-model. Sufficient to account
for group differences, but lacking the machinery necessary to provide a
full process-level account of how the empirical quantities of interest
are generated. In contrast, Project 2 (HTW) implemented a more robust
computational modeling approach, implementing and comparing full process
models (ALM \& EXAM), capable of generating predictions for both the
learning and testing stages of the experiment. ALM and EXAM have been
used as models of function learning, cue judgement, and forecasting
behavior in numerous studies over the past 25 years
(\citeproc{ref-brownUnderestimationLinearFunction2017}{Brown \& Lacroix,
2017}; \citeproc{ref-deloshExtrapolationSineQua1997}{DeLosh et al.,
1997}; \citeproc{ref-kaneApplicationsBiasVariance2020}{Kane \& Broomell,
2020}; \citeproc{ref-kelleyComparisonModelsLearning2008}{H. Kelley \&
Busemeyer, 2008}; \citeproc{ref-kwantesItemOrderMatters2012}{Kwantes et
al., 2012};
\citeproc{ref-mcdanielPredictingTransferPerformance2009}{McDaniel et
al., 2009};
\citeproc{ref-vonhelversenLearningMultiplecueJudgment2010}{Von Helversen
\& Rieskamp, 2010}). The present work presents the first application of
these models to the study of training variability in a visuomotor
function learning task. We fit both models to individual participant
data, using a form of simulation-based Bayesian parameter estimation
that allowed us to generate and compare the full posterior predictive
distributions of each model. EXAM provided the best overall account of
the testing data, and the advantage of EXAM over ALM was significantly
greater for the constant group. Notably, EXAM captured the constant
groups' ability to extrapolate linearly to novel velocity bands, despite
receiving training from only a single input-output pair. This finding
suggests that EXAM's linear extrapolation mechanism, combined with the
assumption of prior knowledge about the origin point (0, 0), was
sufficient to account for the constant groups' accurate extrapolation
performance. Such findings may offer a preliminary suggestion that
experience with a more variable set of training examples may be
detrimental to performance in simple extrapolation tasks.

\subsection{Differences between the two
Projects}\label{differences-between-the-two-projects}

The HTT and HTW tasks differ across numerous dimensions that may be
relevant to the opposing patterns observed in the two projects (see
Table~\ref{tbl-task-diff} for a detailed comparison of the two tasks).

In HTT, the salient perceptual elements of the task (i.e.~the launching
box, target and barrier) are subject to variation (i.e.~different
distances between the launching box and target), and the spatial layout
of these perceptually variable elements are intrinsically linked to the
task objective of striking the target. Conversely, the perceptual task
elements in HTW are invariant across trials, and the task objective is
specified by the target velocity value specified as a numeral at the top
of the screen. If the benefits of training variation do arise from the
formation and flexible retrieval of distinct memory traces, then the
lack of perceptual salience between training instances in the HTW task
may have limited any potential benefits of variability. Future work
could investigate this possibility further employing a modified version
of the HTW task wherein the correct velocity value is indicated by some
perceptual feature of the task (e.g., the color of the wall, or size of
the ball), rather than displaying the target velocity numerically.

The HTT and HTW tasks also differed in terms of general task complexity.
The HTT task was designed to mimic projectile launching tasks commonly
employed in visuomotor learning studies, and the parabolic trajectories
necessary to strike the target in HTT were sensitive to both the x and y
dimensions of the projectiles velocity (and to a lesser extent, the
position within the launching box at which the ball was released).
Conversely the HTW task was influenced to a greater extent by the tasks
commonly utilized in the function learning literature, wherein the
correct output responses are determined by a single input dimension.
In~HTW, the relationship between feedback and optimal behavioral
adjustment is also almost perfectly smooth, if participants produce a
throw that is 100 units too hard, they'll be told that they were 100
units away from the target band. Whereas in HTT, the presence of the
barrier in introduces irregularities in the task space. Even throws
close to the solution space might result in failure, creating a less
predictable learning environment.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1577}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.4732}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.3691}}@{}}
\caption{Comparison of the tasks in Project 1 (HTT) and Project 2
(HTW).}\label{tbl-task-diff}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Dimension
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
HTT (Project 1)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
HTW (Project 2)
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Dimension
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
HTT (Project 1)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
HTW (Project 2)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Task Description & Projectile launching to hit a target & Projectile
launching to hit wall at a specific velocity \\
Task Complexity & More complex parabolic trajectory, both x and y
velocities relevant to outcome & Simpler 1D mapping of force to outcome.
Only x velocity is relevant. \\
Task Space & More complex: xy velocity combinations closer to the
solution space may still result in worse feedback due to striking the
barrier. & Simpler: smooth, linear mapping between velocity and
feedback. \\
Perceptual salience of Varied Conditions & Varied conditions (\# of
throwing distances) are perceptually distinct, i.e.~salient differences
in distance between launching box and target. & Varied conditions (\# of
velocity bands) are less salient - only difference is the numeral
displayed on screen. \\
Testing Feedback & Testing always included feedback & Primary testing
stage had no feedback. \\
Potential for Learning during Testing & Limited potential for learning
during testing due to feedback. & Some potential for learning during
no-feedback testing by observing ball trajectory. \\
Training Experience & Varied group gets half as much experience on any
one position as the constant group. & Varied group gets 1/3 as much
experience on any one velocity band as the constant group. \\
Testing Structure & Random interleaving of trained/transfer testing
distances. & Blocked structure, separately testing trained vs
extrapolation testing bands. \\
\end{longtable}

It is important to note that while both projects utilize computational
models, direct comparisons are complicated by the distinct purposes and
structures of the models used in each project. The IGAS model of Project
1 serves as a descriptive measurement model, capturing the similarity
between training throws and testing conditions. In contrast, the ALM and
EXAM models of Project 2 are full process models, capable of generating
exact predictions for both learning and testing stages. The difference
is also reflected in the interpretion of the generalization parameter
(\(c\)) across the models of the two projects. In IGAS, \(c\) moderates
the similarity between executed throws and subsequent testing solutions,
while in ALM and EXAM, \(c\) governs the extent to which the perceived
stimuli activate the input layer nodes. Despite these differences,
insights from ALM/EXAM, particularly the role of zero-point knowledge,
may offer potential explanations for the contrasting empirical results.
Particularly, EXAM's reliance on zero-point knowledge in the simpler HTW
task may explain why constant training was more effective in Project 2,
while the lack of a clear zero-point reference in the more complex HTT
task of Project 1 may have increased the value of varied training. This
suggests that the benefits of variability depend critically on how task
structure interacts with prior knowledge and the learner's capacity to
leverage such knowledge for generalization.

Future work could explore extending ALM and EXAM, which have
traditionally been applied to one-dimensional function learning tasks,
to more complex motor tasks such as HTT. The neural network structure of
ALM could be adapted to handle 2D input by utilizing a 2D grid of input
nodes, allowing the model to learn mappings between 2D throwing
velocities and desired outcomes. This would allow the model to process
the more complex spatial information inherent in tasks like HTT.
Furthermore, the output layers of ALM/EXAM could be expanded to express
more complex motor outputs in addition to velocity, such as the
locations of grabbing and releasing the projectile or other parameters
defining the unique trajectories produced. In addition to allowing the
models to be applied to more complex tasks, these modifications could
enable researchers to investigate how perceptual similarity (i.e., the
similarity of stimuli) and motoric similarity (i.e., the similarity of
behavioral actions) may separately and jointly influence learning and
generalization.

\subsection{Conclusion}\label{conclusion-1}

In summary, this dissertation provides a comprehensive examination of
the effects of training variability on learning and generalization in
visuomotor and function learning tasks. The contrasting results obtained
from the Hit The Target (HTT) and Hit The Wall (HTW) tasks underscore
the complexity inherent to the longstanding pedagogical and scientific
goal of identifying training manipulations that consistently benefit
learning and generalization. Moreover, through the development and
application of computational models, we provide novel theoretical
accounts for both the beneficial and detrimental effects of training
variability observed in our experiments. These findings highlight the
importance of considering task characteristics when designing
experiments intended to assess the influence of training interventions,
and demonstrate the value of combining empirical and computational
modeling approaches to uncover the cognitive mechanisms that support
learning and generalization. Future research should continue to
investigate the complex interplay between task demands, training
manipulations, and individual differences, with the goal of optimizing
educational and training outcomes across a wide range of domains.

~\\

\section{Appendix}\label{appendix}

\href{https://tegorman13.github.io/Dissertation/Sections/Appendix/Full_Appendix.html}{Apppendix}
available at
https://tegorman13.github.io/Dissertation/Sections/Appendix/Full\_Appendix.html

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-ahaConceptLearningFlexible1992}
Aha, D. W., \& Goldstone, R. L. (1992). Concept {Learning} and {Flexible
Weighting}. \emph{In {Proceedings} of the {Fourteenth Annual Conference}
of the {Cognitive Science Society}}, 534--539.

\bibitem[\citeproctext]{ref-bengtssonUnifyingFrameworkParallel2021}
Bengtsson, H. (2021). A {Unifying Framework} for {Parallel} and
{Distributed Processing} in {R} using {Futures}. \emph{The R Journal},
\emph{13}(2), 208. \url{https://doi.org/10.32614/RJ-2021-048}

\bibitem[\citeproctext]{ref-bernikerEffectsTrainingBreadth2014}
Berniker, M., Mirzaei, H., \& Kording, K. P. (2014). The effects of
training breadth on motor generalization. \emph{Journal of
Neurophysiology}, \emph{112}(11), 2791--2798.
\url{https://doi.org/10.1152/jn.00615.2013}

\bibitem[\citeproctext]{ref-bjorkMakingThingsHard2011}
Bjork, E. L., \& Bjork, R. A. (2011). Making things hard on yourself,
but in a good way: {Creating} desirable difficulties to enhance
learning. \emph{Psychology and the Real World: Essays Illustrating
Fundamental Contributions to Society}, \emph{2}, 59--68.

\bibitem[\citeproctext]{ref-bottNonmonotonicExtrapolationFunction2004}
Bott, L., \& Heit, E. (2004). Nonmonotonic {Extrapolation} in {Function
Learning}. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{30}(1), 38--50.
\url{https://doi.org/10.1037/0278-7393.30.1.38}

\bibitem[\citeproctext]{ref-bowmanTrainingSetCoherence2020}
Bowman, C. R., \& Zeithamova, D. (2020). Training set coherence and set
size effects on concept generalization and recognition. \emph{Journal of
Experimental Psychology. Learning, Memory, and Cognition}, \emph{46}(8),
1442--1464. \url{https://doi.org/10.1037/xlm0000824}

\bibitem[\citeproctext]{ref-braithwaiteEffectsVariationPrior2015}
Braithwaite, D. W., \& Goldstone, R. L. (2015). Effects of {Variation}
and {Prior Knowledge} on {Abstract Concept Learning}. \emph{Cognition
and Instruction}, \emph{33}(3), 226--256.
\url{https://doi.org/10.1080/07370008.2015.1067215}

\bibitem[\citeproctext]{ref-braunMotorTaskVariation2009}
Braun, D. A., Aertsen, A., Wolpert, D. M., \& Mehring, C. (2009). Motor
{Task Variation Induces Structural Learning}. \emph{Current Biology},
\emph{19}(4), 352--357. \url{https://doi.org/10.1016/j.cub.2009.01.036}

\bibitem[\citeproctext]{ref-brehmerHypothesesRelationsScaled1974}
Brehmer, B. (1974). Hypotheses about relations between scaled variables
in the learning of probabilistic inference tasks. \emph{Organizational
Behavior and Human Performance}, \emph{11}(1), 1--27.
\url{https://doi.org/10.1016/0030-5073(74)90002-6}

\bibitem[\citeproctext]{ref-brekelmansDoesHighVariability2022}
Brekelmans, G., Lavan, N., Saito, H., Clayards, M., \& Wonnacott, E.
(2022). Does high variability training improve the learning of
non-native phoneme contrasts over low variability training? {A}
replication. \emph{Journal of Memory and Language}, \emph{126}, 104352.
\url{https://doi.org/10.1016/j.jml.2022.104352}

\bibitem[\citeproctext]{ref-breslinConstantVariablePractice2012}
Breslin, G., Hodges, N. J., Steenson, A., \& Williams, A. M. (2012).
Constant or variable practice: {Recreating} the especial skill effect.
\emph{Acta Psychologica}, \emph{140}(2), 154--157.
\url{https://doi.org/10.1016/j.actpsy.2012.04.002}

\bibitem[\citeproctext]{ref-briscoeConceptualComplexityBias2011}
Briscoe, E., \& Feldman, J. (2011). Conceptual complexity and the
bias/variance tradeoff. \emph{Cognition}, \emph{118}(1), 2--16.
\url{https://doi.org/10.1016/j.cognition.2010.10.004}

\bibitem[\citeproctext]{ref-brownUnderestimationLinearFunction2017}
Brown, M. A., \& Lacroix, G. (2017). Underestimation in linear function
learning: {Anchoring} to zero or x-y similarity? \emph{Canadian Journal
of Experimental Psychology/Revue Canadienne de Psychologie
Exp{é}rimentale}, \emph{71}(4), 274--282.
\url{https://doi.org/10.1037/cep0000129}

\bibitem[\citeproctext]{ref-brunsteinPreparingNoveltyDiverse2011}
Brunstein, A., \& Gonzalez, C. (2011). Preparing for novelty with
diverse training. \emph{Applied Cognitive Psychology}, \emph{25}(5),
682--691. \url{https://doi.org/10.1002/acp.1739}

\bibitem[\citeproctext]{ref-burknerBrmsPackageBayesian2017}
Bürkner, P.-C. (2017). Brms: {An R Package} for {Bayesian Multilevel
Models Using Stan}. \emph{Journal of Statistical Software}, \emph{80},
1--28. \url{https://doi.org/10.18637/jss.v080.i01}

\bibitem[\citeproctext]{ref-burtonIdentityVariationRepresentations2016}
Burton, A. M., Kramer, R. S. S., Ritchie, K. L., \& Jenkins, R. (2016).
Identity {From Variation}: {Representations} of {Faces Derived From
Multiple Instances}. \emph{Cognitive Science}, \emph{40}(1), 202--223.
\url{https://doi.org/10.1111/cogs.12231}

\bibitem[\citeproctext]{ref-busemeyerLearningFunctionalRelations1997}
Busemeyer, J. R., Byun, E., DeLosh, E. L., \& McDaniel, M. A. (1997).
Learning {Functional Relations Based} on {Experience} with {Input-output
Pairs} by {Humans} and {Artificial Neural Networks}. In \emph{Knowledge
{Concepts} and {Categories}} (pp. 405--437). Psychology Press.

\bibitem[\citeproctext]{ref-carrollFunctionalLearningLearning1963}
Carroll, J. D. (1963). Functional {Learning}: {The Learning} of
{Continuous Functional Mappings Relating Stimulus} and {Response
Continua}. \emph{ETS Research Bulletin Series}, \emph{1963}(2), i--144.
\url{https://doi.org/10.1002/j.2333-8504.1963.tb00958.x}

\bibitem[\citeproctext]{ref-catalanoDistantTransferCoincident1984a}
Catalano, J. F., \& Kleiner, B. M. (1984). Distant {Transfer} in
{Coincident Timing} as a {Function} of {Variability} of {Practice}.
\emph{Perceptual and Motor Skills}, \emph{58}(3), 851--856.
\url{https://doi.org/10.2466/pms.1984.58.3.851}

\bibitem[\citeproctext]{ref-censorCommonMechanismsHuman2012}
Censor, N., Sagi, D., \& Cohen, L. G. (2012). Common mechanisms of human
perceptual and motor learning. \emph{Nature Reviews Neuroscience},
\emph{13}(9), 658--664. \url{https://doi.org/10.1038/nrn3315}

\bibitem[\citeproctext]{ref-chamberlinNoteSchemaExemplar1992}
Chamberlin, C. J., \& Magill, R. A. (1992a). A {Note} on {Schema} and
{Exemplar Approaches} to {Motor Skill Representation} in {Memory}.
\emph{Journal of Motor Behavior}, \emph{24}(2), 221--224.
\url{https://doi.org/10.1080/00222895.1992.9941617}

\bibitem[\citeproctext]{ref-chamberlinMemoryRepresentationMotor1992}
Chamberlin, C. J., \& Magill, R. A. (1992b). The {Memory Representation}
of {Motor Skills}: {A Test} of {Schema Theory}. \emph{Journal of Motor
Behavior}, \emph{24}(4), 309--319.
\url{https://doi.org/10.1080/00222895.1992.9941627}

\bibitem[\citeproctext]{ref-chuaPracticeVariabilityPromotes2019}
Chua, L.-K., Dimapilis, M. K., Iwatsuki, T., Abdollahipour, R.,
Lewthwaite, R., \& Wulf, G. (2019). Practice variability promotes an
external focus of attention and enhances motor skill learning.
\emph{Human Movement Science}, \emph{64}, 307--319.
\url{https://doi.org/10.1016/j.humov.2019.02.015}

\bibitem[\citeproctext]{ref-ciccioneCanHumansPerform2021}
Ciccione, L., \& Dehaene, S. (2021). Can humans perform mental
regression on a graph? {Accuracy} and bias in the perception of
scatterplots. \emph{Cognitive Psychology}, \emph{128}, 101406.
\url{https://doi.org/10.1016/j.cogpsych.2021.101406}

\bibitem[\citeproctext]{ref-cochraneTEfitsNonlinearRegression2020}
Cochrane, A. (2020). {TEfits}: {Nonlinear} regression for time-evolving
indices. \emph{Journal of Open Source Software}, \emph{5}(52), 2535.
\url{https://doi.org/10.21105/joss.02535}

\bibitem[\citeproctext]{ref-cohenCategoryVariabilityExemplar2001}
Cohen, A. L., Nosofsky, R. M., \& Zaki, S. R. (2001). Category
variability, exemplar similarity, and perceptual classification.
\emph{Memory \& Cognition}, \emph{29}(8), 1165--1175.
\url{https://doi.org/10.3758/BF03206386}

\bibitem[\citeproctext]{ref-cohenWhereGraspsAre2004}
Cohen, R. G., \& Rosenbaum, D. A. (2004). Where grasps are made reveals
how grasps are planned: Generation and recall of motor plans.
\emph{Experimental Brain Research}, \emph{157}(4).
\url{https://doi.org/10.1007/s00221-004-1862-9}

\bibitem[\citeproctext]{ref-cornwallEffectsCategoricalNumerical2022}
Cornwall, A. C., Davis, T., Byrne, K. A., \& Worthy, D. A. (2022).
Effects of categorical and numerical feedback on category learning.
\emph{Cognition}, \emph{225}, 105163.
\url{https://doi.org/10.1016/j.cognition.2022.105163}

\bibitem[\citeproctext]{ref-courrieuQuickApproximationBivariate2012}
Courrieu, P. (2012). Quick approximation of bivariate functions.
\emph{British Journal of Mathematical and Statistical Psychology},
\emph{65}(1), 89--121.
\url{https://doi.org/10.1111/j.2044-8317.2011.02016.x}

\bibitem[\citeproctext]{ref-cranmerFrontierSimulationbasedInference2020}
Cranmer, K., Brehmer, J., \& Louppe, G. (2020). The frontier of
simulation-based inference. \emph{Proceedings of the National Academy of
Sciences}, \emph{117}(48), 30055--30062.
\url{https://doi.org/10.1073/pnas.1912789117}

\bibitem[\citeproctext]{ref-crumpEpisodicContributionsSequential2010}
Crump, M. J. C., \& Logan, G. D. (2010). Episodic contributions to
sequential control: {Learning} from a typist's touch. \emph{Journal of
Experimental Psychology: Human Perception and Performance},
\emph{36}(3), 662--672. \url{https://doi.org/10.1037/a0018390}

\bibitem[\citeproctext]{ref-czyzVariabilityPracticeInformation2021}
Czyż, S. H. (2021). Variability of {Practice}, {Information Processing},
and {Decision Making}---{How Much Do We Know}? \emph{Frontiers in
Psychology}, \emph{12}. \url{https://doi.org/10.3389/fpsyg.2021.639131}

\bibitem[\citeproctext]{ref-deleeuwJsPsychJavaScriptLibrary2015}
de Leeuw, J. R. (2015). {jsPsych}: {A JavaScript} library for creating
behavioral experiments in a {Web} browser. \emph{Behavior Research
Methods}, \emph{47}(1), 1--12.
\url{https://doi.org/10.3758/s13428-014-0458-y}

\bibitem[\citeproctext]{ref-delreyEffectsContextualInterference1982}
Del Rey, P., Wughalter, E. H., \& Whitehurst, M. (1982). The {Effects}
of {Contextual Interference} on {Females With Varied Experience} in
{Open Sport Skills}. \emph{Research Quarterly for Exercise and Sport},
\emph{53}(2), 108--115.
\url{https://doi.org/10.1080/02701367.1982.10605236}

\bibitem[\citeproctext]{ref-deloshExtrapolationSineQua1997}
DeLosh, E. L., McDaniel, M. A., \& Busemeyer, J. R. (1997).
Extrapolation: {The Sine Qua Non} for {Abstraction} in {Function
Learning}. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{23}(4), 19.
\url{https://doi.org/10.1037/0278-7393.23.4.968}

\bibitem[\citeproctext]{ref-domeGdistanceComparisonModel2023}
Dome, L., \& Wills, A. (2023). \emph{G-distance: {On} the comparison of
model and human heterogeneity} {[}Preprint{]}. PsyArXiv.
\url{https://doi.org/10.31234/osf.io/ygmcj}

\bibitem[\citeproctext]{ref-doyleMetacognitiveMonitoringCategory2016}
Doyle, M. E., \& Hourihan, K. L. (2016). Metacognitive monitoring during
category learning: How success affects future behaviour: {Memory}.
\emph{Memory}, \emph{24}(9), 1197--1207.
\url{https://doi.org/10.1080/09658211.2015.1086805}

\bibitem[\citeproctext]{ref-ennisMultidimensionalStochasticTheory1988}
Ennis, D. M., Palen, J. J., \& Mullen, K. (1988). A multidimensional
stochastic theory of similarity. \emph{Journal of Mathematical
Psychology}, \emph{32}(4), 449--465.
\url{https://doi.org/10.1016/0022-2496(88)90023-5}

\bibitem[\citeproctext]{ref-estesClassificationCognition1994}
Estes, W. K. (1994). \emph{Classification and {Cognition}}. Oxford
University Press.

\bibitem[\citeproctext]{ref-fanStimulusDiversityIncreases2022}
Fan, M., Zhang, D., Zhao, S., Xie, Q., Chen, W., Jie, J., Wang, Y., \&
Zheng, X. (2022). Stimulus diversity increases category-based fear
generalization and the effect of intolerance of uncertainty.
\emph{Behaviour Research and Therapy}, \emph{159}, 104201.
\url{https://doi.org/10.1016/j.brat.2022.104201}

\bibitem[\citeproctext]{ref-farrellComputationalModelingCognition2018}
Farrell, S., \& Lewandowsky, S. (2018). \emph{Computational {Modeling}
of {Cognition} and {Behavior}:} (1st ed.). Cambridge University Press.
\url{https://doi.org/10.1017/CBO9781316272503}

\bibitem[\citeproctext]{ref-faulStatisticalPowerAnalyses2009}
Faul, F., Erdfelder, E., Buchner, A., \& Lang, A.-G. (2009). Statistical
power analyses using {G}*{Power} 3.1: {Tests} for correlation and
regression analyses. \emph{Behavior Research Methods}, \emph{41}(4),
1149--1160. \url{https://doi.org/10.3758/BRM.41.4.1149}

\bibitem[\citeproctext]{ref-fulvioTaskSpecificResponseStrategy2014}
Fulvio, J. M., Green, C. S., \& Schrater, P. R. (2014). Task-{Specific
Response Strategy Selection} on the {Basis} of {Recent Training
Experience}. \emph{PLOS Computational Biology}, \emph{10}(1), e1003425.
\url{https://doi.org/10.1371/journal.pcbi.1003425}

\bibitem[\citeproctext]{ref-gandolfoMotorLearningField1996a}
Gandolfo, F., Mussa-Ivaldi, F. A., \& Bizzi, E. (1996). Motor learning
by field approximation. \emph{Proceedings of the National Academy of
Sciences}, \emph{93}(9), 3843--3846.
\url{https://doi.org/10.1073/pnas.93.9.3843}

\bibitem[\citeproctext]{ref-georgeStimulusVariabilityTask2021}
George, N., \& Egner, T. (2021). Stimulus variability and task relevance
modulate binding-learning. \emph{Attention, Perception, \&
Psychophysics}. \url{https://doi.org/10.3758/s13414-021-02338-6}

\bibitem[\citeproctext]{ref-gershmanStructureLearningPrinciples2023}
Gershman, S. J., \& Cikara, M. (2023). Structure learning principles of
stereotype change. \emph{Psychonomic Bulletin \& Review}, \emph{30}(4),
1273--1293. \url{https://doi.org/10.3758/s13423-023-02252-y}

\bibitem[\citeproctext]{ref-ghahramaniGeneralizationLocalRemappings1996}
Ghahramani, Z., Wolpert, D. M., \& Jordan, M. I. (1996). Generalization
to {Local Remappings} of the {Visuomotor Coordinate Transformation}.
\emph{Journal of Neuroscience}, \emph{16}(21), 7085--7096.
\url{https://doi.org/10.1523/JNEUROSCI.16-21-07085.1996}

\bibitem[\citeproctext]{ref-gonzalezDiversityTrainingEnhances2011}
Gonzalez, C., \& Madhavan, P. (2011). Diversity during training enhances
detection of novel stimuli. \emph{Journal of Cognitive Psychology},
\emph{23}(3), 342--350.
\url{https://doi.org/10.1080/20445911.2011.507187}

\bibitem[\citeproctext]{ref-goodeSuperiorityVariableRepeated2008}
Goode, M. K., Geraci, L., \& Roediger, H. L. (2008). Superiority of
variable to repeated practice in transfer on anagram solution.
\emph{Psychonomic Bulletin \& Review}, \emph{15}(3), 662--666.
\url{https://doi.org/10.3758/PBR.15.3.662}

\bibitem[\citeproctext]{ref-goodwinEffectDifferentQuantities1998}
Goodwin, J. E., Eckerson, J. M., Grimes, C. R., \& Gordon, P. M. (1998).
Effect of {Different Quantities} of {Variable Practice} on
{Acquisition}, {Retention}, and {Transfer} of {An Applied Motor Skill}.
\emph{Perceptual and Motor Skills}, \emph{87}(1), 147--151.
\url{https://doi.org/10.2466/pms.1998.87.1.147}

\bibitem[\citeproctext]{ref-gormanInstancebasedModelAccount2022}
Gorman, T. E., \& Goldstone, R. L. (2022). An instance-based model
account of the benefits of varied practice in visuomotor skill.
\emph{Cognitive Psychology}, \emph{137}, 101491.
\url{https://doi.org/10.1016/j.cogpsych.2022.101491}

\bibitem[\citeproctext]{ref-greenPracticeVariabilityTransfer1995a}
Green, D. P., Whitehead, J., \& Sugden, D. A. (1995). Practice
{Variability} and {Transfer} of a {Racket Skill}. \emph{Perceptual and
Motor Skills}, \emph{81}(3\_suppl), 1275--1281.
\url{https://doi.org/10.2466/pms.1995.81.3f.1275}

\bibitem[\citeproctext]{ref-guadagnoliRelationshipContextualInterference1999}
Guadagnoli, M. A., Holcomb, W. R., \& Weber, T. J. (1999). The
relationship between contextual interference effects and performer
expertise on the learning of a putting task. \emph{Journal of Human
Movement Studies}, \emph{37}(1), 19--36.

\bibitem[\citeproctext]{ref-guadagnoliChallengePointFramework2004}
Guadagnoli, M. A., \& Lee, T. D. (2004). Challenge {Point}: {A
Framework} for {Conceptualizing} the {Effects} of {Various Practice
Conditions} in {Motor Learning}. \emph{Journal of Motor Behavior},
\emph{36}(2), 212--224. \url{https://doi.org/10.3200/JMBR.36.2.212-224}

\bibitem[\citeproctext]{ref-guoEffectsExampleVariability2014}
Guo, J.-P., Yang, L.-Y., \& Ding, Y. (2014). Effects of example
variability and prior knowledge in how students learn to solve
equations. \emph{European Journal of Psychology of Education},
\emph{29}(1), 21--42. \url{https://www.jstor.org/stable/43551124}

\bibitem[\citeproctext]{ref-hacquesVisualControlClimbing2022}
Hacques, G., Dicks, M., Komar, J., \& Seifert, L. (2022). Visual control
during climbing: {Variability} in practice fosters a proactive gaze
pattern. \emph{PLOS ONE}, \emph{17}(6), e0269794.
\url{https://doi.org/10.1371/journal.pone.0269794}

\bibitem[\citeproctext]{ref-hahnEffectsCategoryDiversity2005}
Hahn, U., Bailey, T. M., \& Elvin, L. B. C. (2005). Effects of category
diversity on learning, memory, and generalization. \emph{Memory \&
Cognition}, \emph{33}(2), 289--302.
\url{https://doi.org/10.3758/BF03195318}

\bibitem[\citeproctext]{ref-hillsCentralExecutiveSearch2010}
Hills, T. T., Todd, P. M., \& Goldstone, R. L. (2010). The central
executive as a search process: {Priming} exploration and exploitation
across domains. \emph{Journal of Experimental Psychology: General},
\emph{139}(4), 590--609. \url{https://doi.org/10.1037/a0020666}

\bibitem[\citeproctext]{ref-hintzmanMINERVASimulationModel1984}
Hintzman, D. L. (1984). {MINERVA} 2: {A} simulation model of human
memory. \emph{Behavior Research Methods, Instruments, \& Computers},
\emph{16}(2), 96--101. \url{https://doi.org/10.3758/BF03202365}

\bibitem[\citeproctext]{ref-hintzmanSchemaAbstractionMultipletrace1986}
Hintzman, D. L. (1986). "{Schema} abstraction" in a multiple-trace
memory model. \emph{Psychological Review}, \emph{93}(4), 411.

\bibitem[\citeproctext]{ref-homaCategoryBreadthAbstraction1976}
Homa, D., \& Vosburgh, R. (1976). Category breadth and the abstraction
of prototypical information. \emph{Journal of Experimental Psychology:
Human Learning and Memory}, \emph{2}(3), 322--330.
\url{https://doi.org/10.1037/0278-7393.2.3.322}

\bibitem[\citeproctext]{ref-hommelEventFilesEvidence1998}
Hommel, B. (1998). Event {Files}: {Evidence} for {Automatic Integration}
of {Stimulus-Response Episodes}. \emph{Visual Cognition}, \emph{5}(1-2),
183--216. \url{https://doi.org/10.1080/713756773}

\bibitem[\citeproctext]{ref-honigPerceptualSimilarityModulates2022}
Honig, T., Shoham, A., \& Yovel, G. (2022). Perceptual similarity
modulates effects of learning from variability on face recognition.
\emph{Vision Research}, \emph{201}, 108128.
\url{https://doi.org/10.1016/j.visres.2022.108128}

\bibitem[\citeproctext]{ref-hoschPriorExperienceVariability2023}
Hosch, A.-K., Wirtz, P., \& von Helversen, B. (2023). Prior {Experience}
of {Variability Influences Generalization} of {Unspecified Categories}.
\emph{Quarterly Journal of Experimental Psychology (2006)},
17470218231210491. \url{https://doi.org/10.1177/17470218231210491}

\bibitem[\citeproctext]{ref-hsuEffectsGenerativeDiscriminative2010}
Hsu, A. S., \& Griffiths, T. L. (2010). Effects of generative and
discriminative learning on use of category variability. \emph{32nd
Annual Conference of the Cognitive Science Society}, 7.

\bibitem[\citeproctext]{ref-huHighvariabilityTrainingDoes2024}
Hu, M., \& Nosofsky, R. M. (2024). High-variability training does not
enhance generalization in the prototype-distortion paradigm.
\emph{Memory \& Cognition}, 1--16.
\url{https://doi.org/10.3758/s13421-023-01516-1}

\bibitem[\citeproctext]{ref-huetEducationAttentionExplanation2011}
Huet, M., Jacobs, D. M., Camachon, C., Missenard, O., Gray, R., \&
Montagne, G. (2011). The education of attention as explanation of
variability of practice effects: {Learning} the final approach phase in
a flight simulator. \emph{Journal of Experimental Psychology: Human
Perception and Performance}, \emph{37}(6), 1841--1854.
\url{https://doi.org/10.1037/a0024386}

\bibitem[\citeproctext]{ref-jamiesonInstanceTheoryDomaingeneral2022}
Jamieson, R. K., Johns, B. T., Vokey, J. R., \& Jones, M. N. (2022).
Instance theory as a domain-general framework for cognitive psychology.
\emph{Nature Reviews Psychology}, \emph{1}(3), 174--183.
\url{https://doi.org/10.1038/s44159-022-00025-3}

\bibitem[\citeproctext]{ref-jonesDensityDistinctivenessEarly2020}
Jones, S. D., \& Brandt, S. (2020). Density and {Distinctiveness} in
{Early Word Learning}: {Evidence From Neural Network Simulations}.
\emph{Cognitive Science}, \emph{44}(1), e12812.
\url{https://doi.org/10.1111/cogs.12812}

\bibitem[\citeproctext]{ref-kalishLearningExtrapolatingPeriodic2013}
Kalish, M. L. (2013). Learning and extrapolating a periodic function.
\emph{Memory \& Cognition}, \emph{41}(6), 886--896.
\url{https://doi.org/10.3758/s13421-013-0306-9}

\bibitem[\citeproctext]{ref-kalishPopulationLinearExperts2004}
Kalish, M. L., Lewandowsky, S., \& Kruschke, J. K. (2004). Population of
{Linear Experts}: {Knowledge Partitioning} and {Function Learning}.
\emph{Psychological Review}, \emph{111}(4), 1072--1099.
\url{https://doi.org/10.1037/0033-295X.111.4.1072}

\bibitem[\citeproctext]{ref-kaneApplicationsBiasVariance2020}
Kane, P. B., \& Broomell, S. B. (2020). Applications of the
bias--variance decomposition to human forecasting. \emph{Journal of
Mathematical Psychology}, \emph{98}, 102417.
\url{https://doi.org/10.1016/j.jmp.2020.102417}

\bibitem[\citeproctext]{ref-kangasraasioParameterInferenceComputational2019}
Kangasrääsiö, A., Jokinen, J. P. P., Oulasvirta, A., Howes, A., \&
Kaski, S. (2019). Parameter {Inference} for {Computational Cognitive
Models} with {Approximate Bayesian Computation}. \emph{Cognitive
Science}, \emph{43}(6), e12738. \url{https://doi.org/10.1111/cogs.12738}

\bibitem[\citeproctext]{ref-kassambaraRstatixPipeFriendlyFramework2021a}
Kassambara, A. (2021). \emph{Rstatix: {Pipe-Friendly Framework} for
{Basic Statistical Tests}}.

\bibitem[\citeproctext]{ref-kelleyComparisonModelsLearning2008}
Kelley, H., \& Busemeyer, J. (2008). A comparison of models for learning
how to dynamically integrate multiple cues in order to forecast
continuous criteria. \emph{Journal of Mathematical Psychology},
\emph{52}(4), 218--240. \url{https://doi.org/10.1016/j.jmp.2008.01.009}

\bibitem[\citeproctext]{ref-kelleyLearningAttendEffects2009}
Kelley, T. A., \& Yantis, S. (2009). Learning to attend: {Effects} of
practice on information selection. \emph{Journal of Vision},
\emph{9}(7), 16. \url{https://doi.org/10.1167/9.7.16}

\bibitem[\citeproctext]{ref-kerrSpecificVariedPractice1978}
Kerr, R., \& Booth, B. (1978). Specific and varied practice of motor
skill. \emph{Perceptual and Motor Skills}, \emph{46}(2), 395--401.
\url{https://doi.org/10.1177/003151257804600201}

\bibitem[\citeproctext]{ref-knappTheoryCategorizationBased1984}
Knapp, A. K., \& Anderson, J. A. (1984). Theory of categorization based
on distributed memory storage. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{10}(4), 616--637.

\bibitem[\citeproctext]{ref-kohFunctionLearningInduction1991}
Koh, K., \& Meyer, D. E. (1991). Function learning: {Induction} of
continuous stimulus-response relations. \emph{Journal of Experimental
Psychology: Learning, Memory, and Cognition}, \emph{17}(5), 811.
\url{https://doi.org/10.1037/0278-7393.17.5.811}

\bibitem[\citeproctext]{ref-konovalovaInformationSamplingExplanation2020}
Konovalova, E., \& Le Mens, G. (2020). An information sampling
explanation for the in-group heterogeneity effect. \emph{Psychological
Review}, \emph{127}(1), 47--73. \url{https://doi.org/10.1037/rev0000160}

\bibitem[\citeproctext]{ref-kruschkeALCOVEExemplarbasedConnectionist1992}
Kruschke, J. K. (1992). {ALCOVE}: {An} exemplar-based connectionist
model of {Category Learning}. \emph{Psychological Review}, \emph{99}(1).
\url{https://doi.org/10.1037/0033-295X.99.1.22}

\bibitem[\citeproctext]{ref-kwantesWhyPeopleUnderestimate2006}
Kwantes, P. J., \& Neal, A. (2006). Why people underestimate y when
extrapolating in linear functions. \emph{Journal of Experimental
Psychology: Learning, Memory, and Cognition}, \emph{32}(5), 1019--1030.
\url{https://doi.org/10.1037/0278-7393.32.5.1019}

\bibitem[\citeproctext]{ref-kwantesItemOrderMatters2012}
Kwantes, P. J., Neal, A., \& Kalish, M. (2012). Item order matters in a
function learning task. \emph{Canadian Journal of Experimental
Psychology/Revue Canadienne de Psychologie Exp{é}rimentale},
\emph{66}(2), 90--97. \url{https://doi.org/10.1037/a0026639}

\bibitem[\citeproctext]{ref-lambertsFlexibleTuningSimilarity1994}
Lamberts, K. (1994). Flexible {Tuning} of {Similarity} in
{Exemplar-Based Categorization}. \emph{Journal of Experimental
Psychology: Learning, Memory, and Cognition}, \emph{20}(5), 1003--1021.
\url{https://doi.org/10.1037/0278-7393.20.5.1003}

\bibitem[\citeproctext]{ref-lavanEffectsHighVariability2019}
Lavan, N., Knight, S., Hazan, V., \& McGettigan, C. (2019). The effects
of high variability training on voice identity learning.
\emph{Cognition}, \emph{193}, 104026.
\url{https://doi.org/10.1016/j.cognition.2019.104026}

\bibitem[\citeproctext]{ref-lawSharedMechanismsPerceptual2010}
Law, C.-T., \& Gold, J. I. (2010). Shared {Mechanisms} of {Perceptual
Learning} and {Decision Making}. \emph{Topics in Cognitive Science},
\emph{2}(2), 226--238.
\url{https://doi.org/10.1111/j.1756-8765.2009.01044.x}

\bibitem[\citeproctext]{ref-leeEvidentialDiversityIncreases2019}
Lee, J. C., Lovibond, P. F., \& Hayes, B. K. (2019). Evidential
diversity increases generalisation in predictive learning.
\emph{Quarterly Journal of Experimental Psychology}, \emph{72}(11),
2647--2657. \url{https://doi.org/10.1177/1747021819857065}

\bibitem[\citeproctext]{ref-linvilleExemplarAbstractionModels1993}
Linville, P. W., \& Fischer, G. W. (1993). Exemplar and {Abstraction
Models} of {Perceived Group Variability} and {Stereotypicality}.
\emph{Social Cognition}, \emph{11}(1), 92--125.
\url{https://doi.org/10.1521/soco.1993.11.1.92}

\bibitem[\citeproctext]{ref-liveseyRevisitingPeakShift2019}
Livesey, E. J., \& McLaren, I. P. (2019). Revisiting peak shift on an
artificial dimension: {Effects} of stimulus variability on
generalisation. \emph{Quarterly Journal of Experimental Psychology},
\emph{72}(2), 132--150. \url{https://doi.org/10.1177/1747021817739832}

\bibitem[\citeproctext]{ref-loganInstanceTheoryAutomatization1988}
Logan, G. D. (1988). Toward an instance theory of automatization.
\emph{Psychological Review}, \emph{95}(4), 492--527.
\url{https://doi.org/10.1037/0033-295X.95.4.492}

\bibitem[\citeproctext]{ref-loganInstanceTheoryAttention2002a}
Logan, G. D. (2002). An instance theory of attention and memory.
\emph{Psychological Review}, \emph{109}(2), 376--400.
\url{https://doi.org/10.1037/0033-295X.109.2.376}

\bibitem[\citeproctext]{ref-lovibondStimulusDiscriminabilityInduction2020}
Lovibond, P. F., Lee, J. C., \& Hayes, B. K. (2020). Stimulus
discriminability and induction as independent components of
generalization. \emph{Journal of Experimental Psychology: Learning,
Memory, and Cognition}, \emph{46}(6), 1106--1120.
\url{https://doi.org/10.1037/xlm0000779}

\bibitem[\citeproctext]{ref-maddoxStimulusRangeDiscontinuity2011}
Maddox, W. T., \& Filoteo, J. V. (2011). Stimulus range and
discontinuity effects on information-integration category learning and
generalization. \emph{Attention, Perception, \& Psychophysics},
\emph{73}(4), 1279--1295.
\url{https://doi.org/10.3758/s13414-011-0101-2}

\bibitem[\citeproctext]{ref-makowskiBayestestRDescribingEffects2019}
Makowski, D., Ben-Shachar, M. S., \& Lüdecke, D. (2019). {bayestestR}:
{Describing Effects} and their {Uncertainty}, {Existence} and
{Significance} within the {Bayesian Framework}. \emph{Journal of Open
Source Software}, \emph{4}(40), 1541.
\url{https://doi.org/10.21105/joss.01541}

\bibitem[\citeproctext]{ref-manentiVariabilityTrainingUnlocks2023}
Manenti, G. L., Dizaji, A. S., \& Schwiedrzik, C. M. (2023). Variability
in training unlocks generalization in visual perceptual learning through
invariant representations. \emph{Current Biology}, \emph{33}(5),
817--826.e3. \url{https://doi.org/10.1016/j.cub.2023.01.011}

\bibitem[\citeproctext]{ref-marongelliAdvantageFlexibleNeuronal2013}
Marongelli, E., \& Thoroughman, K. (2013). The advantage of flexible
neuronal tunings in neural network models for motor learning.
\emph{Frontiers in Computational Neuroscience}, \emph{7}, 100.
\url{https://doi.org/10.3389/fncom.2013.00100}

\bibitem[\citeproctext]{ref-mcclellandDistributedMemoryRepresentation1985}
McClelland, J. L., \& Rumelhart, D. E. (1985). Distributed memory and
the representation of general and specific information. \emph{Journal of
Experimental Psychology: General}, \emph{114}, 159--188.

\bibitem[\citeproctext]{ref-mccrackenTestSchemaTheory1977}
McCracken, H. D., \& Stelmach, G. E. (1977). A {Test} of the {Schema
Theory} of {Discrete Motor Learning}. \emph{Journal of Motor Behavior},
\emph{9}(3), 193--201.
\url{https://doi.org/10.1080/00222895.1977.10735109}

\bibitem[\citeproctext]{ref-mcdanielConceptualBasisFunction2005}
McDaniel, M. A., \& Busemeyer, J. R. (2005). The conceptual basis of
function learning and extrapolation: {Comparison} of rule-based and
associative-based models. \emph{Psychonomic Bulletin \& Review},
\emph{12}(1), 24--42. \url{https://doi.org/10.3758/BF03196347}

\bibitem[\citeproctext]{ref-mcdanielPredictingTransferPerformance2009}
McDaniel, M. A., Dimperio, E., Jacqueline A. Griego, \& Busemeyer, J. R.
(2009). Predicting transfer performance: {A} comparison of competing
function learning models. \emph{Journal of Experimental Psychology.
Learning, Memory, and Cognition}, \emph{35}, 173--195.
\url{https://doi.org/10.1037/a0013982}

\bibitem[\citeproctext]{ref-mcdanielEffectsSpacedMassed2013}
McDaniel, M. A., Fadler, C. L., \& Pashler, H. (2013). Effects of spaced
versus massed training in function learning. \emph{Journal of
Experimental Psychology: Learning, Memory, and Cognition}, \emph{39}(5),
1417--1432. \url{https://doi.org/10.1037/a0032184}

\bibitem[\citeproctext]{ref-medinContextTheoryClassification1978}
Medin, D. L., \& Schaffer, M. M. (1978). Context {Theory} of
{Classification Learning}. \emph{Psychological Review}, \emph{85}(3),
207. \url{https://doi.org/10.1037/0033-295X.85.3.207}

\bibitem[\citeproctext]{ref-meighWhatMemoryRepresentation2018}
Meigh, K. M., Shaiman, S., Tompkins, C. A., Abbott, K. V., \&
Nokes-Malach, T. (2018). What memory representation is acquired during
nonword speech production learning? {The} influence of stimulus features
and training modality on nonword encoding. \emph{Cogent Psychology},
\emph{5}(1), 1493714.
\url{https://doi.org/10.1080/23311908.2018.1493714}

\bibitem[\citeproctext]{ref-menonVariationPhotosSame2015}
Menon, N., White, D., \& Kemp, R. I. (2015). Variation in {Photos} of
the {Same Face Drives Improvements} in {Identity Verification}.
\emph{Perception}, \emph{44}(11), 1332--1341.
\url{https://doi.org/10.1177/0301006615599902}

\bibitem[\citeproctext]{ref-mezzadriHoldoutStrategySelecting2022}
Mezzadri, G., Laloë, T., Mathy, F., \& Reynaud-Bouret, P. (2022).
Hold-out strategy for selecting learning models: {Application} to
categorization subjected to presentation orders. \emph{Journal of
Mathematical Psychology}, \emph{109}, 102691.
\url{https://doi.org/10.1016/j.jmp.2022.102691}

\bibitem[\citeproctext]{ref-morgensternOneshotCategorizationNovel2019}
Morgenstern, Y., Schmidt, F., \& Fleming, R. W. (2019). One-shot
categorization of novel object classes in humans. \emph{Vision
Research}, \emph{165}, 98--108.
\url{https://doi.org/10.1016/j.visres.2019.09.005}

\bibitem[\citeproctext]{ref-moshon-cohenStimulusVariabilityImproves2024}
Moshon-Cohen, T. E., Weinbach, N., \& Bitan, T. (2024). Stimulus
variability improves generalization following response inhibition
training. \emph{Psychological Research}, 1--17.
\url{https://doi.org/10.1007/s00426-023-01913-w}

\bibitem[\citeproctext]{ref-moxleySchemaVariabilityPractice1979}
Moxley, S. E. (1979). Schema: {The Variability} of {Practice
Hypothesis}. \emph{Journal of Motor Behavior}, \emph{11}(1), 65--70.
\url{https://doi.org/10.1080/00222895.1979.10735173}

\bibitem[\citeproctext]{ref-newellSchemaTheory19752003}
Newell, K. M. (2003). Schema {Theory} (1975): {Retrospectives} and
{Prospectives}. \emph{Research Quarterly for Exercise and Sport},
\emph{74}(4), 383--388.
\url{https://doi.org/10.1080/02701367.2003.10609108}

\bibitem[\citeproctext]{ref-newellVariabilityPracticeTransfer1976}
Newell, K. M., \& Shapiro, D. C. (1976). Variability of {Practice} and
{Transfer} of {Training}: {Some Evidence Toward} a {Schema View} of
{Motor Learning}. \emph{Journal of Motor Behavior}, \emph{8}(3),
233--243. \url{https://doi.org/10.1080/00222895.1976.10735077}

\bibitem[\citeproctext]{ref-northEffectConsistentVaried2019}
North, J. S., Bezodis, N. E., Murphy, C. P., Runswick, O. R., Pocock,
C., \& Roca, A. (2019). The effect of consistent and varied
follow-through practice schedules on learning a table tennis backhand.
\emph{Journal of Sports Sciences}, \emph{37}(6), 613--620.
\url{https://doi.org/10.1080/02640414.2018.1522683}

\bibitem[\citeproctext]{ref-nosofskyAttentionSimilarityIdentificationcategorization1986}
Nosofsky, R. M. (1986). Attention, similarity, and the
identification-categorization relationship. \emph{Journal of
Experimental Psychology: General}, \emph{115}(1), 39--57.
\url{https://doi.org/10.1037/0096-3445.115.1.39}

\bibitem[\citeproctext]{ref-nosofskySimilarityScalingCognitive1992}
Nosofsky, R. M. (1992). Similarity scaling and cognitive process models.
\emph{Annual Review of Psychology}, \emph{43}(1), 25--53.
\url{https://doi.org/10.1146/annurev.ps.43.020192.000325}

\bibitem[\citeproctext]{ref-nosofskyExemplarbasedAccountsMultiplesystem2000}
Nosofsky, R. M., \& Johansen, M. K. (2000). Exemplar-based accounts of
"multiple-system" phenomena in perceptual categorization.
\emph{Psychonomic Bulletin \& Review}, \emph{7}(3), 375--402.
\url{https://doi.org/10.1007/BF03543066}

\bibitem[\citeproctext]{ref-nosofskyInvestigationsExemplarBasedConnectionist1992}
Nosofsky, R. M., \& Kruschke, J. K. (1992). Investigations of an
{Exemplar-Based Connectionist Model} of {Category Learning}. In D. L.
Medin (Ed.), \emph{Psychology of {Learning} and {Motivation}} (Vol. 28,
pp. 207--250). Academic Press.
\url{https://doi.org/10.1016/S0079-7421(08)60491-0}

\bibitem[\citeproctext]{ref-nosofskyModelguidedSearchOptimal2019}
Nosofsky, R. M., Sanders, C. A., Zhu, X., \& McDaniel, M. A. (2019).
Model-guided search for optimal natural-science-category training
exemplars: {A} work in progress. \emph{Psychonomic Bulletin \& Review},
\emph{26}(1), 48--76. \url{https://doi.org/10.3758/s13423-018-1508-8}

\bibitem[\citeproctext]{ref-opdebeeckRepresentationPerceivedShape2008}
Op de Beeck, H. P., Wagemans, J., \& Vogels, R. (2008). The
representation of perceived shape similarity and its role for category
learning in monkeys: {A} modeling study. \emph{Vision Research},
\emph{48}(4), 598--610.
\url{https://doi.org/10.1016/j.visres.2007.11.019}

\bibitem[\citeproctext]{ref-pachecoLearningSpecificIndividual2018}
Pacheco, M. M., \& Newell, K. M. (2018). Learning a specific, individual
and generalizable coordination function: Evaluating the variability of
practice hypothesis in motor learning. \emph{Experimental Brain
Research}, \emph{236}(12), 3307--3318.
\url{https://doi.org/10.1007/s00221-018-5383-3}

\bibitem[\citeproctext]{ref-pageConnectionistModellingPsychology2000a}
Page, M. (2000). Connectionist modelling in psychology: {A} localist
manifesto. \emph{Behavioral and Brain Sciences}, \emph{23}(4), 443--467.
\url{https://doi.org/10.1017/S0140525X00003356}

\bibitem[\citeproctext]{ref-palmeriExemplarSimilarityDevelopment1997}
Palmeri, T. J. (1997). Exemplar {Similarity} and the {Development} of
{Automaticity}. \emph{Journal of Experimental Psychology: Human Learning
and Memory}, \emph{23}(2), 324--354.

\bibitem[\citeproctext]{ref-palmeriCentralTendenciesExtreme2001}
Palmeri, T. J., \& Nosofsky, R. M. (2001). Central {Tendencies},
{Extreme Points}, and {Prototype Enhancement Effects} in {Ill-Defined
Perceptual Categorization}. \emph{The Quarterly Journal of Experimental
Psychology Section A}, \emph{54}(1), 197--235.
\url{https://doi.org/10.1080/02724980042000084}

\bibitem[\citeproctext]{ref-parkPerceptionVariabilityCategory1987}
Park, B., \& Hastie, R. (1987). Perception of variability in category
development: {Instance-versus} abstraction-based stereotypes.
\emph{Journal of Personality and Social Psychology}, \emph{53}(4), 621.

\bibitem[\citeproctext]{ref-perlmanFurtherAttemptsClarify2012}
Perlman, A., Hahn, U., Edwards, D. J., \& Pothos, E. M. (2012). Further
attempts to clarify the importance of category variability for
categorisation. \emph{Journal of Cognitive Psychology}, \emph{24}(2),
203--220. \url{https://doi.org/10.1080/20445911.2011.613818}

\bibitem[\citeproctext]{ref-perryLearnLocallyThink2010}
Perry, L. K., Samuelson, L. K., Malloy, L. M., \& Schiffer, R. N.
(2010). Learn {Locally}, {Think Globally}: {Exemplar Variability
Supports Higher-Order Generalization} and {Word Learning}.
\emph{Psychological Science}, \emph{21}(12), 1894--1902.
\url{https://doi.org/10.1177/0956797610389189}

\bibitem[\citeproctext]{ref-pigottMotorSchemaStructure1984}
Pigott, R. E., \& Shapiro, D. C. (1984). Motor {Schema}: {The Structure}
of the {Variability Session}. \emph{Research Quarterly for Exercise and
Sport}, \emph{55}(1), 41--45.
\url{https://doi.org/10.1080/02701367.1984.10605353}

\bibitem[\citeproctext]{ref-plebanekEffectsFrequencyVariability2021}
Plebanek, D. J., \& James, K. H. (2021). The {Effects} of {Frequency},
{Variability}, and {Co-occurrence} on {Category Formation} in {Neural
Systems}. \emph{Journal of Cognitive Neuroscience}, 1--16.
\url{https://doi.org/10.1162/jocn_a_01738}

\bibitem[\citeproctext]{ref-poldrackRelationshipSkillLearning1999}
Poldrack, R. A., Selco, S. L., Field, J. E., \& Cohen, N. J. (1999). The
relationship between skill learning and repetition priming:
{Experimental} and computational analyses. \emph{Journal of Experimental
Psychology: Learning, Memory, and Cognition}, \emph{25}(1), 208--235.
\url{https://doi.org/10.1037/0278-7393.25.1.208}

\bibitem[\citeproctext]{ref-posnerGenesisAbstractIdeas1968}
Posner, M. I., \& Keele, S. W. (1968). On the genesis of abstract ideas.
\emph{Journal of Experimental Psychology}, \emph{77}(3), 353--363.
\url{https://doi.org/10.1037/h0025953}

\bibitem[\citeproctext]{ref-pradaExperiencedCategoryVariability2020}
Prada, M., \& Garcia-Marques, T. (2020). Experienced category
variability modulates the impact of context on evaluative judgments.
\emph{Experimental Psychology}, \emph{67}(1), 5--13.
\url{https://doi.org/10.1027/1618-3169/a000469}

\bibitem[\citeproctext]{ref-ramAnticipatedVariabilityIncreases2024}
Ram, H., Grinfeld, G., \& Liberman, N. (2024). Anticipated variability
increases generalization of predictive learning. \emph{Npj Science of
Learning}, \emph{9}(1), 1--10.
\url{https://doi.org/10.1038/s41539-024-00269-z}

\bibitem[\citeproctext]{ref-ravivHowVariabilityShapes2022}
Raviv, L., Lupyan, G., \& Green, S. C. (2022). How variability shapes
learning and generalization. \emph{Trends in Cognitive Sciences},
S1364661322000651. \url{https://doi.org/10.1016/j.tics.2022.03.007}

\bibitem[\citeproctext]{ref-reichmannVariabilityAbstractionEvaluative2023}
Reichmann, K., Hütter, M., Kaup, B., \& Ramscar, M. (2023). Variability
and abstraction in evaluative conditioning: {Consequences} for the
generalization of likes and dislikes. \emph{Journal of Experimental
Social Psychology}, \emph{108}, 104478.
\url{https://doi.org/10.1016/j.jesp.2023.104478}

\bibitem[\citeproctext]{ref-roarkComparingPerceptualCategory2021}
Roark, C. L., Paulon, G., Sarkar, A., \& Chandrasekaran, B. (2021).
Comparing perceptual category learning across modalities in the same
individuals. \emph{Psychonomic Bulletin \& Review}, \emph{28}(3),
898--909. \url{https://doi.org/10.3758/s13423-021-01878-0}

\bibitem[\citeproctext]{ref-robsonSpecificVariedPractice2022a}
Robson, S. G., Tangen, J. M., \& Searston, R. A. (2022). Specific versus
varied practice in perceptual expertise training. \emph{Journal of
Experimental Psychology: Human Perception and Performance},
\emph{48}(12), 1336--1346. \url{https://doi.org/10.1037/xhp0001057}

\bibitem[\citeproctext]{ref-rollerVariablePracticeLenses2001}
Roller, C. A., Cohen, H. S., Kimball, K. T., \& Bloomberg, J. J. (2001).
Variable practice with lenses improves visuo-motor plasticity.
\emph{Cognitive Brain Research}, \emph{12}(2), 341--352.
\url{https://doi.org/10.1016/S0926-6410(01)00077-5}

\bibitem[\citeproctext]{ref-rosenbaumAcquisitionIntellectualPerceptualMotor2001}
Rosenbaum, D. A., Carlson, R. A., \& Gilmore, R. O. (2001). Acquisition
of {Intellectual} and {Perceptual-Motor Skills}. \emph{Annual Review of
Psychology}, \emph{52}(1), 453--470.
\url{https://doi.org/10.1146/annurev.psych.52.1.453}

\bibitem[\citeproctext]{ref-rosenbaumPlanningReachesEvaluating1995}
Rosenbaum, D. A., Loukopoulos, L. D., Meulenbroek, R. G., Vaughan, J.,
\& Engelbrecht, S. E. (1995). Planning reaches by evaluating stored
postures. \emph{Psychological Review}, \emph{102}(1), 28.
\url{https://doi.org/10.1037/0033-295X.102.1.28}

\bibitem[\citeproctext]{ref-sabahWhenLessMore2019}
Sabah, K., Dolk, T., Meiran, N., \& Dreisbach, G. (2019). When less is
more: Costs and benefits of varied vs. Fixed content and structure in
short-term task switching training. \emph{Psychological Research},
\emph{83}(7), 1531--1542.
\url{https://doi.org/10.1007/s00426-018-1006-7}

\bibitem[\citeproctext]{ref-sadakataIndividualAptitudeMandarin2014}
Sadakata, M., \& McQueen, J. M. (2014). Individual aptitude in
{Mandarin} lexical tone perception predicts effectiveness of
high-variability training. \emph{Frontiers in Psychology}, \emph{5},
1318. \url{https://doi.org/10.3389/fpsyg.2014.01318}

\bibitem[\citeproctext]{ref-saidExtrapolationAccuracyUnderestimates2021}
Said, N., \& Fischer, H. (2021). Extrapolation accuracy underestimates
rule learning: {Evidence} from the function-learning paradigm.
\emph{Acta Psychologica}, \emph{218}, 103356.
\url{https://doi.org/10.1016/j.actpsy.2021.103356}

\bibitem[\citeproctext]{ref-sakamotoPuttingPsychologyBack2008}
Sakamoto, Y., Jones, M., \& Love, B. C. (2008). Putting the psychology
back into psychological models: {Mechanistic} versus rational
approaches. \emph{Memory \& Cognition}, \emph{36}(6), 1057--1065.
\url{https://doi.org/10.3758/MC.36.6.1057}

\bibitem[\citeproctext]{ref-sakamotoTrackingVariabilityLearning2006}
Sakamoto, Y., Love, B. C., \& Jones, M. (2006). Tracking {Variability}
in {Learning}: {Contrasting Statistical} and {Similarity-Based
Accounts}. \emph{Proceedings of the 28th Annual Conference of the
Cognitive Science Society. Vancouver, Canada: Cognitive Science
Society}.

\bibitem[\citeproctext]{ref-schmidtSchemaTheoryDiscrete1975}
Schmidt, R. A. (1975). A schema theory of discrete motor skill learning.
\emph{Psychological Review}, \emph{82}(4), 225--260.
\url{https://doi.org/10.1037/h0076770}

\bibitem[\citeproctext]{ref-schulzCommunicatingCompositionalPatterns2020}
Schulz, E., Quiroga, F., \& Gershman, S. J. (2020). Communicating
{Compositional Patterns}. \emph{Open Mind}, \emph{4}, 25--39.
\url{https://doi.org/10.1162/opmi_a_00032}

\bibitem[\citeproctext]{ref-seitzModelingCategoryVariability2023}
Seitz, F. I., Jarecki, J. B., \& Rieskamp, J. (2023). \emph{Modeling the
{Category Variability Effect} in an {Exemplar-Similarity Framework}}
{[}Preprint{]}. PsyArXiv.

\bibitem[\citeproctext]{ref-seowTransferEffectsVaried2019}
Seow, R. Y. T., Betts, S., \& Anderson, J. R. (2019). Transfer effects
of varied practice and adaptation to changes in complex skill
acquisition. \emph{Proceedings of the 17th International Conference on
Cognitive Modelling}, 222--227.

\bibitem[\citeproctext]{ref-shepardUniversalLawGeneralization1987}
Shepard, R. N. (1987). Toward a universal law of generalization for
psychological science. \emph{Science}, \emph{237}(4820), 1317--1323.
\url{https://doi.org/10.1126/science.3629243}

\bibitem[\citeproctext]{ref-sinkeviciuteRoleInputVariability2019}
Sinkeviciute, R., Brown, H., Brekelmans, G., \& Wonnacott, E. (2019).
The role of input variability and learner age in second language
vocabulary learning. \emph{Studies in Second Language Acquisition},
\emph{41}(04), 795--820. \url{https://doi.org/10.1017/S0272263119000263}

\bibitem[\citeproctext]{ref-soderstromLearningPerformanceIntegrative2015}
Soderstrom, N. C., \& Bjork, R. A. (2015). Learning versus performance:
{An} integrative review. \emph{Perspectives on Psychological Science},
\emph{10}(2), 176--199. \url{https://doi.org/10.1177/1745691615569000}

\bibitem[\citeproctext]{ref-stewartEffectCategoryVariability2002}
Stewart, N., \& Chater, N. (2002). The effect of category variability in
perceptual categorization. \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{28}(5), 893--907.
\url{https://doi.org/10.1037//0278-7393.28.5.893}

\bibitem[\citeproctext]{ref-taylorContextdependentGeneralization2013}
Taylor, J., \& Ivry, R. (2013). Context-dependent generalization.
\emph{Frontiers in Human Neuroscience}, \emph{7}, 171.
\url{https://doi.org/10.3389/fnhum.2013.00171}

\bibitem[\citeproctext]{ref-rcoreteamLanguageEnvironmentStatistical2020}
Team, R. C. (2020). \emph{R: {A Language} and {Environment} for
{Statistical Computing}}. R: A Language and Environment for Statistical
Computing.

\bibitem[\citeproctext]{ref-tenenbaumGeneralizationSimilarityBayesian2001a}
Tenenbaum, J. B., \& Griffiths, T. L. (2001). Generalization,
similarity, and {Bayesian} inference. \emph{Behavioral and Brain
Sciences}, \emph{24}(4), 629--640.
\url{https://doi.org/10.1017/S0140525X01000061}

\bibitem[\citeproctext]{ref-thoroughmanRapidReshapingHuman2005}
Thoroughman, K. A., \& Taylor, J. A. (2005). Rapid {Reshaping} of {Human
Motor Generalization}. \emph{Journal of Neuroscience}, \emph{25}(39),
8948--8953. \url{https://doi.org/10.1523/JNEUROSCI.1771-05.2005}

\bibitem[\citeproctext]{ref-turnerBayesianAnalysisSimulationbased2016}
Turner, B. M., Sederberg, P. B., \& McClelland, J. L. (2016). Bayesian
analysis of simulation-based models. \emph{Journal of Mathematical
Psychology}, \emph{72}, 191--199.
\url{https://doi.org/10.1016/j.jmp.2014.10.001}

\bibitem[\citeproctext]{ref-turnerTutorialApproximateBayesian2012}
Turner, B. M., \& Van Zandt, T. (2012). A tutorial on approximate
{Bayesian} computation. \emph{Journal of Mathematical Psychology},
\emph{56}(2), 69--85. \url{https://doi.org/10.1016/j.jmp.2012.02.005}

\bibitem[\citeproctext]{ref-twomeyAllRightNoises2018}
Twomey, K. E., Ma, L., \& Westermann, G. (2018). All the {Right Noises}:
{Background Variability Helps Early Word Learning}. \emph{Cognitive
Science}, \emph{42}(S2), 413--438.
\url{https://doi.org/10.1111/cogs.12539}

\bibitem[\citeproctext]{ref-vandamMappingShapeVisuomotor2015}
van Dam, L. C. J., \& Ernst, M. O. (2015). Mapping {Shape} to
{Visuomotor Mapping}: {Learning} and {Generalisation} of {Sensorimotor
Behaviour Based} on {Contextual Information}. \emph{PLOS Computational
Biology}, \emph{11}(3), e1004172.
\url{https://doi.org/10.1371/journal.pcbi.1004172}

\bibitem[\citeproctext]{ref-vanrossumSchmidtSchemaTheory1990}
Van Rossum, J. H. A. (1990). Schmidt's schema theory: The empirical base
of the variability of practice hypothesis. \emph{Human Movement
Science}, \emph{9}(3-5), 387--435.
\url{https://doi.org/10.1016/0167-9457(90)90010-B}

\bibitem[\citeproctext]{ref-velazquez-vargasRoleTrainingVariability2024}
Velázquez-Vargas, C. A., Daw, N. D., \& Taylor, J. A. (2024). The role
of training variability for model-based and model-free learning of an
arbitrary visuomotor mapping. \emph{PLOS Computational Biology},
\emph{20}(9), e1012471.
\url{https://doi.org/10.1371/journal.pcbi.1012471}

\bibitem[\citeproctext]{ref-vigoLearningDifficultyVisual2018}
Vigo, R., Doan, K.-M. C., Doan, C. A., \& Pinegar, S. (2018). On the
learning difficulty of visual and auditory modal concepts: {Evidence}
for a single processing system. \emph{Cognitive Processing},
\emph{19}(1), 1--16. \url{https://doi.org/10.1007/s10339-017-0840-7}

\bibitem[\citeproctext]{ref-vonhelversenLearningMultiplecueJudgment2010}
Von Helversen, B., \& Rieskamp, J. (2010). \emph{Learning in
multiple-cue judgment tasks}. \url{https://doi.org/10.5167/UZH-135898}

\bibitem[\citeproctext]{ref-wahlheimMetacognitiveJudgmentsRepetition2012}
Wahlheim, C. N., Finn, B., \& Jacoby, L. L. (2012). Metacognitive
judgments of repetition and variability effects in natural concept
learning: Evidence for variability neglect. \emph{Memory \& Cognition},
\emph{40}(5), 703--716. \url{https://doi.org/10.3758/s13421-011-0180-2}

\bibitem[\citeproctext]{ref-wallIdentifyingRelationshipsCognitive2021}
Wall, L., Gunawan, D., Brown, S. D., Tran, M.-N., Kohn, R., \& Hawkins,
G. E. (2021). Identifying relationships between cognitive processes
across tasks, contexts, and time. \emph{Behavior Research Methods},
\emph{53}(1), 78--95. \url{https://doi.org/10.3758/s13428-020-01405-4}

\bibitem[\citeproctext]{ref-wifallReachingResponseSelection2017}
Wifall, T., Buss, A. T., Farmer, T. A., Spencer, J. P., \& Hazeltine, E.
(2017). Reaching into response selection: {Stimulus} and response
similarity influence central operations. \emph{Journal of Experimental
Psychology: Human Perception and Performance}, \emph{43}(3), 555--568.
\url{https://doi.org/10.1037/xhp0000301}

\bibitem[\citeproctext]{ref-willeyLimitedGeneralizationVaried2018}
Willey, C. R., \& Liu, Z. (2018a). Limited generalization with varied,
as compared to specific, practice in short-term motor learning.
\emph{Acta Psychologica}, \emph{182}, 39--45.
\url{https://doi.org/10.1016/j.actpsy.2017.11.008}

\bibitem[\citeproctext]{ref-willeyLongtermMotorLearning2018}
Willey, C. R., \& Liu, Z. (2018b). Long-term motor learning: {Effects}
of varied and specific practice. \emph{Vision Research}, \emph{152},
10--16. \url{https://doi.org/10.1016/j.visres.2017.03.012}

\bibitem[\citeproctext]{ref-wonnacottInputEffectsAcquisition2012}
Wonnacott, E., Boyd, J. K., Thomson, J., \& Goldberg, A. E. (2012).
Input effects on the acquisition of a novel phrasal construction in
5year olds. \emph{Journal of Memory and Language}, \emph{66}(3),
458--478. \url{https://doi.org/10.1016/j.jml.2011.11.004}

\bibitem[\citeproctext]{ref-wrisbergTrainingProductionNovel1984}
Wrisberg, C. A., \& McLean, E. (1984). Training for the production of
novel timing movements: {Contextual} considerations. \emph{Psychological
Research}, \emph{46}(1-2), 169--176.
\url{https://doi.org/10.1007/BF00308601}

\bibitem[\citeproctext]{ref-wrisbergDevelopingCoincidentTiming1983}
Wrisberg, C. A., \& Mead, B. J. (1983). Developing {Coincident Timing
Skill} in {Children}: {A Comparison} of {Training Methods}.
\emph{Research Quarterly for Exercise and Sport}, \emph{54}(1), 67--74.
\url{https://doi.org/10.1080/02701367.1983.10605274}

\bibitem[\citeproctext]{ref-wrisbergVariabilityPracticeHypothesis1987}
Wrisberg, C. A., Winter, T. P., \& Kuhlman, J. S. (1987). The
{Variability} of {Practice Hypothesis}: {Further Tests} and
{Methodological Discussion}. \emph{Research Quarterly for Exercise and
Sport}, \emph{58}(4), 369--374.
\url{https://doi.org/10.1080/02701367.1987.10608114}

\bibitem[\citeproctext]{ref-wuSimilaritiesDifferencesSpatial2020}
Wu, C. M., Schulz, E., Garvert, M. M., Meder, B., \& Schuck, N. W.
(2020). Similarities and differences in spatial and non-spatial
cognitive maps. \emph{PLOS Computational Biology}, \emph{16}(9).
\url{https://doi.org/10.1101/2020.01.21.914556}

\bibitem[\citeproctext]{ref-wulfEffectTypePractice1991}
Wulf, G. (1991). The effect of type of practice on motor learning in
children. \emph{Applied Cognitive Psychology}, \emph{5}(2), 123--134.
\url{https://doi.org/10.1002/acp.2350050206}

\bibitem[\citeproctext]{ref-wulfVariabilityPracticeImplicit1997}
Wulf, G., \& Schmidt, R. A. (1997). \emph{Variability of {Practice} and
{Implicit Motor Learning}}.

\bibitem[\citeproctext]{ref-yangGeneralLearningAbility2020}
Yang, J., Yan, F.-F., Chen, L., Xi, J., Fan, S., Zhang, P., Lu, Z.-L.,
\& Huang, C.-B. (2020). General learning ability in perceptual learning.
\emph{Proceedings of the National Academy of Sciences}, \emph{117}(32),
19092--19100. \url{https://doi.org/10.1073/pnas.2002903117}

\bibitem[\citeproctext]{ref-yangCategoryVariabilityEffect2014}
Yang, L.-X., \& Wu, Y.-H. (2014). Category variability effect in
category learning with auditory stimuli. \emph{Frontiers in Psychology},
\emph{5}. \url{https://doi.org/10.3389/fpsyg.2014.01122}

\bibitem[\citeproctext]{ref-zakiHighdistortionEnhancementEffect2007}
Zaki, S. R., \& Nosofsky, R. M. (2007). A high-distortion enhancement
effect in the prototype-learning paradigm: {Dramatic} effects of
category learning during test. \emph{Memory \& Cognition}, \emph{35}(8),
2088--2096. \url{https://doi.org/10.3758/BF03192940}

\bibitem[\citeproctext]{ref-zamanPerceptualVariabilityImplications2021}
Zaman, J., Chalkia, A., Zenses, A.-K., Bilgin, A. S., Beckers, T.,
Vervliet, B., \& Boddez, Y. (2021). Perceptual variability:
{Implications} for learning and generalization. \emph{Psychonomic
Bulletin \& Review}, \emph{28}(1), 1--19.
\url{https://doi.org/10.3758/s13423-020-01780-1}

\bibitem[\citeproctext]{ref-zhangHighVariabilityLearning2024}
Zhang, T., \& Fyfe, E. R. (2024). High variability in learning materials
benefits children's pattern practice. \emph{Journal of Experimental
Child Psychology}, \emph{239}, 105829.
\url{https://doi.org/10.1016/j.jecp.2023.105829}

\end{CSLReferences}

\newpage{}

\pagenumbering{gobble}

\section{Curriculum Vitae}\label{curriculum-vitae}

\subsection*{Education}\label{education}

\begin{tabular}{p{0.3\textwidth} p{0.7\textwidth}}
2017 - May 2024 & \textbf{Indiana University - Bloomington} \\
& PhD in Psychology and Cognitive Science \\ 
& Dissertation: \textit{The Role of Variability in Learning Generalization: A Computational Modeling Approach}\\
2011 - 2015 & \textbf{University of Wisconsin - Madison} \\
& B.Sc. in Psychology \\
& Thesis: \textit{Short-term mindfulness intervention reduces the negative attentional effects associated with heavy media multitasking} \\
\end{tabular}

\subsection*{Journal Articles and Conference
Proceedings}\label{journal-articles-and-conference-proceedings}

\begin{itemize}
\item
  \textbf{Gorman}, T. E., \& Goldstone, R. L. (2022). An instance-based
  model account of the benefits of varied practice in visuomotor skill.
  \emph{Cognitive Psychology}, \emph{137}, 101491.
\item
  Kattner, F., Cochrane, A., Cox, C. R., \textbf{Gorman}, T. E., \&
  Green, C. S. (2017). Perceptual learning generalization from
  sequential perceptual training as a change in learning rate.
  \emph{Current Biology}, \emph{27}(6), 840-846.
\item
  \textbf{Gorman}, T.E., \& Green, C.S. (2016). Short-term mindfulness
  intervention reduces the negative attentional effects associated with
  heavy media multitasking. \emph{Scientific Reports}, \emph{6}.
\end{itemize}

\subsection*{Reviews and Book Chapters}\label{reviews-and-book-chapters}

\begin{itemize}
\item
  \textbf{Gorman}, T.E., Gentile, D.A., \& Green, C.S. Problem gaming: a
  short primer (2018). \emph{American Journal of Play}, \emph{10} (3),
  309-327
\item
  \textbf{Gorman}, T.E., \& Green, C.S. (2017). Young minds on video
  games. In \emph{Cognitive development in digital contexts}. 121-143.
  Academic Press.
\item
  Green, C. S., \textbf{Gorman}, T., \& Bavelier, D. (2016). Action
  Video-Game Training and Its Effects on Perception and Attentional
  Control. In \emph{Cognitive Training} (pp.~107-116). Springer
  International Publishing.
\end{itemize}

\subsection*{Presentations}\label{presentations}

\begin{itemize}
\tightlist
\item
  Half Day Tutorial on Measuring Mindfulness Behaviorally: Onsite/Online
  Data Col-lection with jsPsych - Cognitive Science Conference -- 2018
\item
  Does interleaving go the distance? Exploring the effect of
  dissimilarity on interleaved category learning - Math Psych/ICCM 2018
\item
  Short term mindfulness intervention reduces cognitive deficits in
  heavy media multi-taskers - Undergraduate Research Symposium --
  UW-Madison -- April 16th, 2015
\end{itemize}

\subsection*{Awards}\label{awards}

IU-Bloomington -- Development Training Grant -- Fall 2019

IU-Bloomington - Steinmetz Summer Research Award - 2018

UW-Madison - Undergraduate Research Scholar Award -- 2015

UW-Madison - Hilldale Undergraduate/Faculty Research Fellowship -- 2014

\subsection*{Ad-hoc Reviewer}\label{ad-hoc-reviewer}

Cognitive Science

Journal of Experimental Psychology: General

Journal of Experimental Psychology: Human Perception and Performance

\subsection*{Conferences}\label{conferences}

Cognitive Science Conference - 2021

Cognitive Science Conference - 2018

Mathematical Psychology \& ICCM 2018

Boston Meeting on Methods in Cognitive Training (NSF Sponsored) -- May
2017

\end{document}

### 2024-10-12 Manuscript/manuscript_full.qmd
unnecessary tweaks to html pre-sections

@@
     toc: true
-#   html:
-#     toc: true
-#     language: 
-#       title-block-published: "Latest version"
-#     shift-heading-level-by: 0
-#     toc-depth: 4
-#     link-citations: true
-#     page-layout: full
-#     format-links: [pdf, gfm, docx]
-#     theme: 
-#        #- ../Assets/Style/lux-modified.scss 
-#        - cosmo
-#        - custom.scss
-#        - ../Assets/Style/style.scss
-#     css: ../Assets/Style/calloutTG.css
-#     citeproc: false
-#     filters: 
-#       - "_extensions/wordcount/citeproc.lua"
-#       - "_extensions/wordcount/wordcount.lua"
-#     lightbox: auto
-#     knitr:
-#       opts_chunk:
-#         dev: "ragg_png"
-#         dpi: 300
+  html:
+    toc: false
+    language: 
+      title-block-published: "Latest version"
+    shift-heading-level-by: 0
+    toc-depth: 4
+    link-citations: true
+    page-layout: full
+    format-links: [pdf, gfm, docx]
   pdf:
@@
 
-{{< include pre_sections/pre_html.qmd >}}
+{{< include pre_sections/pre_html2.qmd >}}
 
@@
 :::
+
 {{< pagebreak >}}

### 2024-10-12 Manuscript/pre_sections/abstract.qmd
unnecessary tweaks to html pre-sections

@@
 
-Researchers and educators have long been interested in how the variability of training examples experienced
-during learning influences subsequent generalization. However, previous studies have reported both beneficial
-and detrimental effects, leaving the nature of this relationship unclear. Furthermore, a formal computational
-modeling approach to account for the effects of training variability has been largely lacking within the domain of
-visuomotor skill learning. The current work presents two projects which shed light on this issue, each consisting of
-several experiments which compare varied training (i.e., multiple training items) in comparison to constant
-training (training with a single item).
-The empirical results, much like those of the broader literature, provide evidence both for and against a benefit of
-variable training in visuomotor skill learning, highlighting the complex interplay between training conditions and
-generalization performance. To provide a theoretical account of these findings, this dissertation employs both
-instance-based and connectionist computational modeling approaches. The instance-based modeling approach
-introduced in project 1 provides a theoretically justifiable method of quantifying/controlling for similarity
-between training and testing conditions, while also demonstrating that varied training may induce broader
-generalization in the similarity function relating training and test items. In project 2, the Extrapolation-
-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
-constant groups' ability to extrapolate linearly to novel regions despite limited training experience, while also
-revealing potential detriments of varied training for simple extrapolation tasks.
-By integrating empirical findings with computational modeling approaches, this dissertation sheds light on the
-complex relationship between training variability and generalization performance.
+The impact of training variability on generalization has been a long-standing topic in the study of human learning, with conflicting evidence about its potential benefits.
+This dissertation addresses these ambiguities by examining the effects of varied versus constant training in visuomotor skill learning through a combination of experimental and computational modeling approaches.
+Across two projects, we systematically compare varied training (multiple items) to constant training (single item) in a projectile-throwing task.
+Empirical findings reveal both positive and negative impacts of variability, highlighting the complex interplay between training conditions and generalization performance.
+To provide a theoretical account of these findings, this dissertation employs both instance-based and connectionist computational modeling approaches.
+The instance-based modeling approach introduced in project 1 provides a theoretically justifiable method of quantifying/controlling for similarity between training and testing conditions, while also demonstrating that varied training may induce broader generalization in the similarity function relating training and test items.
+In project 2, the Extrapolation-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
+constant groups' ability to extrapolate to novel regions despite limited training experience, while also revealing potential detriments of varied training for simple extrapolation tasks.
+These results challenge simplistic notions about the universality of variability benefits in training and emphasize the need for tailored approaches that consider both the structure of the task environment and the prior knowledge of the learners.
 

### 2024-10-12 Manuscript/pre_sections/pre_html.qmd
unnecessary tweaks to html pre-sections

@@
 </div>
+
+## Acknowledgements
+
+My dissertation would not have been possible without the support and guidance of numerous individuals who have shaped my academic and personal growth.
+
+First, I am deeply grateful to my advisor, Rob Goldstone, for his nearly limitless patience, clear thinking, and unwavering guidance.
+His ability to effortlessly demonstrate the power of so many tools has been awe-inspiring, and I am forever thankful for his mentorship.
+I also extend my heartfelt thanks to Dr.
+Rob Nosofsky for his sharp questions and encouragement of model-based thinking, and to Dr.
+Peter Todd for being a constant source of encouragement.
+
+My foundation in psychological science was laid at the University of Wisconsin-Madison.
+I am indebted to Dr.
+Shawn Green, who took a chance on me despite my mediocre grades and lack of experience, introducing me to the world of psychological research.
+Special thanks to Aaron Cochrane for answering my countless questions, introducing me to R, and advanced data analysis techniques.
+
+I am grateful for the camaraderie and intellectual stimulation provided by my friends at Indiana University, particularly those in the Geolab and Psychology department.
+Johnathan Avery, Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others have been integral to my graduate school experience.
+A special mention goes to Jack Avery for introducing me to rock climbing and engaging in fun conversations that often led to unexpected ideas.
+
+The teachers at Pardeeville High School played an essential role in nurturing my curiosity and establishing the educational foundation that shaped my early learning.
+The professors at UW-Madison and Indiana University further cultivated that curiosity, profoundly influencing my academic development.
+
+I would also like to extend my heartfelt thanks to my family.
+My parents, Mary and Jim Gorman, have always been a source of love and unwavering belief in my abilities.
+My brother, Joseph, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed.
+Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.
+
+<br><br><br>
+
+## Abstract
+
+The impact of training variability on generalization has been a long-standing topic in the study of human learning, with conflicting evidence about its potential benefits.
+This dissertation addresses these ambiguities by examining the effects of varied versus constant training in visuomotor skill learning through a combination of experimental and computational modeling approaches.
+Across two projects, we systematically compare varied training (multiple items) to constant training (single item) in a projectile-throwing task.
+Empirical findings reveal both positive and negative impacts of variability, highlighting the complex interplay between training conditions and generalization performance.
+To provide a theoretical account of these findings, this dissertation employs both instance-based and connectionist computational modeling approaches.
+The instance-based modeling approach introduced in project 1 provides a theoretically justifiable method of quantifying/controlling for similarity between training and testing conditions, while also demonstrating that varied training may induce broader generalization in the similarity function relating training and test items.
+In project 2, the Extrapolation-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
+constant groups' ability to extrapolate to novel regions despite limited training experience, while also revealing potential detriments of varied training for simple extrapolation tasks.
+These results challenge simplistic notions about the universality of variability benefits in training and emphasize the need for tailored approaches that consider both the structure of the task environment and the prior knowledge of the learners.

### 2024-10-12 Manuscript/pre_sections/pre_html2.qmd
unnecessary tweaks to html pre-sections

--- 2024-10-12 Manuscript/pre_sections/pre_html.qmd
@@
-<div style="text-align: center; margin-top: 50px; font-size: 24px; font-weight: bold;">
- The Role of Variability in Learning Generalization: A Computational Modeling Approach
+<style>
+    body {
+        font-family: Times, "Times New Roman", serif;
+        line-height: 1.6;
+    }
+    .title {
+        text-align: center;
+        margin-top: 50px;
+        font-size: 24px;
+        font-weight: bold;
+    }
+    .author {
+        text-align: center;
+        margin-top: 300px;
+        font-size: 32px;
+    }
+    .submitted {
+        text-align: center;
+        margin-top: 200px;
+        font-size: 16px;
+    }
+    .date {
+        text-align: center;
+        margin-top: 200px;
+        font-size: 16px;
+    }
+    .committee {
+        text-align: center;
+        margin-top: 150px;
+        font-size: 16px;
+        width: 60%;
+        margin-left: auto;
+        margin-right: auto;
+    }
+    .signature {
+        display: flex;
+        justify-content: space-between;
+        margin-top: 50px;
+    }
+    .signature div {
+        width: 45%;
+        text-align: center;
+    }
+    .copyright {
+        text-align: center;
+        margin-top: 300px;
+        font-size: 16px;
+        margin-bottom: 200px;
+        }
+</style>
+
+<div class="title">The Role of Variability in Learning Generalization: A Computational Modeling Approach</div>
+
+<div class="author">Thomas E. Gorman</div>
+
+<div class="submitted">
+Submitted to the faculty of the University Graduate School<br>
+in partial fulfillment of the requirements<br>
+for the degree<br>
+Doctor of Philosophy<br><br>
+in the Cognitive Science Program and<br>
+Department of Psychological and Brain Sciences,<br>
+Indiana University<br>
+October 2024
 </div>
 
-<div style="text-align: center; margin-top: 300px; font-size: 32px;">
-  Thomas E. Gorman
+<div class="committee">
+Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the requirements for the degree of Doctor of Philosophy.
 </div>
+
+<div style="text-align: left; margin-top: 50px;">
+Doctoral Committee:
+</div>
+
+<div class="signature">
+<div>_________________________<br>Robert L. Goldstone, Ph.D.</div>
+<div>_________________________<br>Robert M. Nosofsky, Ph.D.</div>
+</div>
+<div class="signature">
+<div>_________________________<br>Peter M. Todd, Ph.D.</div>
+<div>_________________________<br>Michael N. Jones, Ph.D.</div>
+</div>
+
+<div style="text-align: left; margin-top: 50px;">
+May 28th, 2024
+</div>
+
+<br><br><br>
+
+<div class="copyright">&copy; 2024 <br><br> Thomas E. Gorman </div>
 

### 2024-10-12 Sections/Introduction.qmd
unnecessary tweaks to html pre-sections

@@
 ---
+
+The impact of training variability on generalization has been a long-standing topic in the study of human learning, with conflicting evidence about its potential benefits.
+This dissertation addresses these ambiguities by examining the effects of varied versus constant training in visuomotor skill learning through a combination of experimental and computational modeling approaches.
+Across two projects, we systematically compare varied training (multiple items) to constant training (single item) in a projectile-throwing task.
+Empirical findings reveal both positive and negative impacts of variability, highlighting the complex interplay between training conditions and generalization performance.
+To provide a theoretical account of these findings, this dissertation employs both instance-based and connectionist computational modeling approaches.
+The instance-based modeling approach introduced in project 1 provides a theoretically justifiable method of quantifying/controlling for similarity between training and testing conditions, while also demonstrating that varied training may induce broader generalization in the similarity function relating training and test items.
+In project 2, the Extrapolation-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
+constant groups' ability to extrapolate to novel regions despite limited training experience, while also revealing potential detriments of varied training for simple extrapolation tasks.
+These results challenge simplistic notions about the universality of variability benefits in training and emphasize the need for tailored approaches that consider both the structure of the task environment and the prior knowledge of the learners.
 

### 2024-10-12 Sections/full.qmd
unnecessary tweaks to html pre-sections

@@
 {{< pagebreak >}}
+
+# Abstract
+
+The impact of training variability on generalization has been a long-standing topic in the study of human learning, with conflicting evidence about its potential benefits.
+This dissertation addresses these ambiguities by examining the effects of varied versus constant training in visuomotor skill learning through a combination of experimental and computational modeling approaches.
+Across two projects, we systematically compare varied training (multiple items) to constant training (single item) in a projectile-throwing task.
+Empirical findings reveal both positive and negative impacts of variability, highlighting the complex interplay between training conditions and generalization performance.
+To provide a theoretical account of these findings, this dissertation employs both instance-based and connectionist computational modeling approaches.
+The instance-based modeling approach introduced in project 1 provides a theoretically justifiable method of quantifying/controlling for similarity between training and testing conditions, while also demonstrating that varied training may induce broader generalization in the similarity function relating training and test items.
+In project 2, the Extrapolation-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
+constant groups' ability to extrapolate to novel regions despite limited training experience, while also revealing potential detriments of varied training for simple extrapolation tasks.
+These results challenge simplistic notions about the universality of variability benefits in training and emphasize the need for tailored approaches that consider both the structure of the task environment and the prior knowledge of the learners.
 

### 2024-10-12 Manuscript/pre_sections/acknowledgements.qmd
update acknowledgements

@@
 
-First, I am deeply grateful to my advisor, Rob Goldstone, for his nearly limitless patience, clear thinking, and unwavering guidance.
-His ability to effortlessly demonstrate the power of so many tools has been awe-inspiring, and I am forever thankful for his mentorship.
-I also extend my heartfelt thanks to Dr.
-Rob Nosofsky for his sharp questions and encouragement of model-based thinking, and to Dr.
-Peter Todd for being a constant source of encouragement.
+First, I owe immense appreciation to my advisor, Rob Goldstone, for his clear thinking and unwavering support, patiently guiding me throughout my dissertation journey.
+His demonstration of how a single scientist can contribute meaningful work across several distinct areas has been truly awe-inspiring.
 
-My foundation in psychological science was laid at the University of Wisconsin-Madison.
-I am indebted to Dr.
-Shawn Green, who took a chance on me despite my mediocre grades and lack of experience, introducing me to the world of psychological research.
-Special thanks to Aaron Cochrane for answering my countless questions, introducing me to R, and advanced data analysis techniques.
+I also extend my heartfelt thanks to Rob Nosofsky, who always asked sharp questions that challenged my thinking and encouraged model-based approaches, and to Peter Todd, whose encouragement and enthusiasm played an especially important role during the final stages of my work.
 
-I am grateful for the camaraderie and intellectual stimulation provided by my friends at Indiana University, particularly those in the Geolab and Psychology department.
-Johnathan Avery, Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others have been integral to my graduate school experience.
-A special mention goes to Jack Avery for introducing me to rock climbing and engaging in fun conversations that often led to unexpected ideas.
+My journey into the study of the mind began at the Learning and Transfer Lab at the University of Wisconsin-Madison, where I am forever indebted to Dr.
+Shawn Green.
+He gave me my first research job despite my total lack of experience, and through his guidance, I discovered my passion for research.
+It was my time in his lab that made it clear to me that pursuing a career in psychological research was what I wanted to do.
+I also want to thank Aaron Cochrane for investing significant time in answering my many questions, introducing me to R, and humoring my naïve inquiries into advanced data analysis and statistics.
 
-The teachers at Pardeeville High School played an essential role in nurturing my curiosity and establishing the educational foundation that shaped my early learning.
-The professors at UW-Madison and Indiana University further cultivated that curiosity, profoundly influencing my academic development.
+The camaraderie, friendship, and intellectual stimulation I received from my friends at Indiana University have been vital to my graduate school experience.
+I am particularly grateful to Johnathan Avery, who introduced me to bouldering and joined me in bouncing unexpected ideas around in our fun conversations.
+I also want to thank Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others from the Geolab and Psychology department.
+Their support made long hours in front of the computer screen more enjoyable and productive.
+
+I owe much to my teachers at Pardeeville High School for laying the foundation of my education and to the professors at UW-Madison and Indiana University, who continued to foster and build upon that foundation.
+Their dedication helped to instill in me a love of learning and a drive to pursue knowledge that has lasted throughout my academic journey.
 
 I would also like to extend my heartfelt thanks to my family.
-My parents, Mary and Jim Gorman, have always been a source of love and unwavering belief in my abilities.
-My brother, Joseph, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed.
+My parents, Mary and Jim Gorman, have been my unwavering pillars of support.
+My brother, Joseph Gorman, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed.
 Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.

### 2024-10-12 Manuscript/pre_sections/pre_html2.qmd
update acknowledgements

@@
         margin-top: 300px;
-        font-size: 32px;
+        font-size: 21px;
     }
@@
         font-size: 16px;
-        margin-bottom: 200px;
+        margin-bottom: 500px;
         }

### 2024-10-14 Manuscript/pre_sections/abstract.qmd
final render with submitted version

@@
 To provide a theoretical account of these findings, this dissertation employs both instance-based and connectionist computational modeling approaches.
-The instance-based modeling approach introduced in project 1 provides a theoretically justifiable method of quantifying/controlling for similarity between training and testing conditions, while also demonstrating that varied training may induce broader generalization in the similarity function relating training and test items.
-In project 2, the Extrapolation-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
+The instance-based modeling approach introduced in Project 1 provides a theoretically justifiable method of quantifying and controlling for similarity between training and testing conditions, while also demonstrating that varied training may induce broader generalization in the similarity function relating training and test items.
+In Project 2, the Extrapolation-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
 constant groups' ability to extrapolate to novel regions despite limited training experience, while also revealing potential detriments of varied training for simple extrapolation tasks.

### 2024-10-14 Manuscript/pre_sections/acknowledgements.qmd
final render with submitted version

@@
 First, I owe immense appreciation to my advisor, Rob Goldstone, for his clear thinking and unwavering support, patiently guiding me throughout my dissertation journey.
-His demonstration of how a single scientist can contribute meaningful work across several distinct areas has been truly awe-inspiring.
-
-I also extend my heartfelt thanks to Rob Nosofsky, who always asked sharp questions that challenged my thinking and encouraged model-based approaches, and to Peter Todd, whose encouragement and enthusiasm played an especially important role during the final stages of my work.
+His demonstration of how a single scientist can contribute meaningful work across several distinct areas has been nothing short of inspiring.
+I also extend my heartfelt thanks to Rob Nosofsky, who always asked sharp questions that challenged my thinking, and to Peter Todd, whose encouragement and enthusiasm played an especially important role during the final stages of my work.
 
@@
 It was my time in his lab that made it clear to me that pursuing a career in psychological research was what I wanted to do.
-I also want to thank Aaron Cochrane for investing significant time in answering my many questions, introducing me to R, and humoring my naïve inquiries into advanced data analysis and statistics.
+I also want to thank Aaron Cochrane for investing significant time in answering my many research questions, introducing me to R, and patiently humoring my naïve inquiries into statistics.
 
 The camaraderie, friendship, and intellectual stimulation I received from my friends at Indiana University have been vital to my graduate school experience.
-I am particularly grateful to Johnathan Avery, who introduced me to bouldering and joined me in bouncing unexpected ideas around in our fun conversations.
-I also want to thank Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others from the Geolab and Psychology department.
-Their support made long hours in front of the computer screen more enjoyable and productive.
+I am especially grateful to Johnathan Avery for introducing me to bouldering, which became my main source of exercise, and for our many fun and thought-provoking conversations.
+I also want to thank Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others from the Geolab, Cognitive Science program, and Psychology department for their support, which  made the long hours of work much more enjoyable.
 
@@
 
-I would also like to extend my heartfelt thanks to my family.
-My parents, Mary and Jim Gorman, have been my unwavering pillars of support.
-My brother, Joseph Gorman, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed.
-Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.
+Finally, I would also like to extend my heartfelt thanks to my family.
+My parents, Mary and Jim Gorman, have been unwavering pillars of support.
+My brother, Joseph Gorman, played a crucial role in the final stages of my dissertation.
+By hosting me for one of the final months of my work, he provided a novel and structured working environment that helped me overcome some of the most challenging hurdles.
+The support of my family has been instrumental in making this journey possible, and I am forever grateful for their love and encouragement.
 

### 2024-10-19 Manuscript/manuscript.qmd
unnecessary tweaks to html pre-sections
update acknowledgements
changes for ugs revisions

@@
 //| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
-//| fig-width: 7.0
-//| fig-height: 2.5
+//| fig-width: 6.0
+//| fig-height: 1.8
 //| fig-responsive: false
@@
 //| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
-//| fig-width: 7.0
-//| fig-height: 2.2
+//| fig-width: 6.0
+//| fig-height: 1.8
 //| fig-responsive: false

### 2024-10-19 Manuscript/manuscript_full.qmd
changes for ugs revisions

@@
     prefer-html: true
-    output-file: "TG_Full_Dissertation2.docx"
+    output-file: "TG_Diss_Test.docx"
     toc: true
@@
     #date: today
-    output-file: "TG_Full_Dissertation2.pdf"
+    output-file: "TG_Diss_Test.pdf"
     mathfont: "Libertinus Math"
@@
     colorlinks: true
-    linkcolor: Black
-    urlcolor: Black
+    linkcolor: DarkSlateBlue
+    urlcolor: DarkSlateBlue
     citecolor: Black
@@
 
+::: {.content-visible unless-format="markdown"}
+```{dot}
+//| label: fig-design-e1
+//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
+//| fig-width: 6.0
+//| fig-height: 1.9
+//| fig-responsive: false
+//| echo: false  
+///| eval: !expr out_type 
+/////| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+
+  // define the global styles of the nodes
+  node [shape = rectangle, style = filled]
+
+  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#00A08A"]
+  data2 [label = " Constant Training \n800-1000", fillcolor = "#FF0000"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+
+  // edge definitions with the node IDs
+  data1 -> Test1
+  data2 -> Test1
+
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+
+  Test2 -> Test3
+}
+```
+:::
+
+{{< pagebreak >}}
+
+::: {.content-visible unless-format="markdown"}
+```{dot}
+//| label: fig-design-e2
+//| fig-cap: "Experiment 2 Design. Constant and Varied participants complete different training conditions. The training and testing bands are the reverse of Experiment 1. "
+//| fig-width: 6.0
+//| fig-height: 1.8
+//| fig-responsive: false
+//| echo: false 
+//| 
+/////| column: screen-inset-right
+digraph {
+  graph [layout = dot, rankdir = LR]
+  node [shape = rectangle, style = filled]
+  data1 [label = " Varied Training \n100-300\n350-550\n600-800", fillcolor = "#00A08A"]
+  data2 [label = " Constant Training \n600-800", fillcolor = "#FF0000"]
+  Test3 [label = "    Final Test \n  Novel With Feedback  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+  data1 -> Test1
+  data2 -> Test1
+  subgraph cluster {
+    label = "Test Phase \n(Counterbalanced Order)"
+    Test1 [label = "Test  \nNovel Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
+    Test2 [label = "  Test \n  Varied Training Bands  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
+    Test1 -> Test2
+  }
+  Test2 -> Test3
+}
+```
+
+:::
+
+{{< pagebreak >}}
+
 # References

### 2024-10-19 Manuscript/pre_sections/diss_cv.qmd
cv additions and re-render
changes for ugs revisions

@@
 # Curriculum Vitae
+
+# Thomas E. Gorman {.unnumbered .unlisted}
+
+**Email:** tegorman13@gmail.com  <br><br>
+
+**Website:** [tegorman13.github.io](https://tegorman13.github.io/)
 
@@
 \begin{tabular}{p{0.3\textwidth} p{0.7\textwidth}}
-2017 - May 2024 & \textbf{Indiana University - Bloomington} \\
+2017 - October 2024 & \textbf{Indiana University - Bloomington} \\
 & PhD in Psychology and Cognitive Science \\ 
@@
 
--   Half Day Tutorial on Measuring Mindfulness Behaviorally: Onsite/Online Data Col-lection with jsPsych
-    -   Cognitive Science Conference – 2018
--   Does interleaving go the distance? Exploring the effect of dissimilarity on interleaved category learning
-    -   Math Psych/ICCM 2018
--   Short term mindfulness intervention reduces cognitive deficits in heavy media multi-taskers
-    -   Undergraduate Research Symposium – UW-Madison – April 16th, 2015
+-   Half Day Tutorial on Measuring Mindfulness Behaviorally: Onsite/Online Data Col-lection with jsPsych -   Cognitive Science Conference – 2018
+-   Does interleaving go the distance? Exploring the effect of dissimilarity on interleaved category learning -   Math Psych/ICCM 2018
+-   Short term mindfulness intervention reduces cognitive deficits in heavy media multi-taskers -   Undergraduate Research Symposium – UW-Madison – April 16th, 2015
 
@@
 
-Contemporary Educational Psychology
-
 ## Conferences {.unnumbered .unlisted}

### 2024-10-19 Manuscript/pre_sections/pre_html2.qmd
changes for ugs revisions

@@
 <div class="submitted">
-Submitted to the faculty of the University Graduate School<br>
+Submitted to the faculty of the Graduate School<br>
 in partial fulfillment of the requirements<br>

### 2024-10-19 Manuscript/pre_sections/pre_pdf_full.qmd
update acknowledgements
changes for ugs revisions

@@
 
-Submitted to the faculty of the University Graduate School \\
+Submitted to the faculty of the Graduate School \\
 in partial fulfillment of the requirements \\
@@
 @2024 \\
-\vspace{1cm}
+\vspace{.5cm}
 

### 2024-10-19 Sections/pre_sections/pre_pdf.qmd
fix page numbers
changes for ugs revisions

@@
 
-<!-- Submitted to the faculty of the University Graduate School in partial fulfillment of the
+<!-- Submitted to the faculty of the Graduate School in partial fulfillment of the
 requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
@@
 \pagenumbering{gobble}
+
+\newpage
 
@@
 
-\begin{centering}
+<!-- \begin{centering}
 
@@
 
-@2024 \\
-\vspace{1cm}
+@2024 \\ -->
+<!-- \vspace{1cm}
 
@@
 \end{center}
-\newpage
+\newpage -->

### 2024-10-20 Manuscript/pre_sections/pre_docx.qmd
re-render after fixing ugs revision issues

@@
 
+::: {custom-style="Subtitle"}
+
 ## Thomas E. Gorman
+
+Submitted to the faculty of the Graduate School  
+in partial fulfillment of the requirements  
+for the degree  
+Doctor of Philosophy  
+in the Cognitive Science Program and  
+Department of Psychological and Brain Sciences,  
+Indiana University  
+October 2024
+:::
+
+\newpage
+
+# {.unnumbered .unlisted}
+
+::: {custom-style="Subtitle"}
+Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
+requirements for the degree of Doctor of Philosophy.
+
+:::
+
+Doctoral Committee:
+
+Robert L. Goldstone, Ph.D. \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+
+Robert M. Nosofsky, Ph.D. \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+
+Peter M. Todd, Ph.D. \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+
+Michael N. Jones, Ph.D. \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_
+
+May 28th, 2024
+
+\newpage
+
+<!-- Copyright Page -->
+# {.unnumbered .unlisted}
+
+::: {custom-style="Subtitle"}
+© 2024
+
+Thomas E. Gorman
+:::
+
+\newpage
+
+## Acknowledgements
+
+My dissertation would not have been possible without the support and guidance of numerous individuals who have shaped my academic and personal growth.
+
+First, I owe immense appreciation to my advisor, Rob Goldstone, for his clear thinking and unwavering support, patiently guiding me throughout my dissertation journey.
+His demonstration of how a single scientist can contribute meaningful work across several distinct areas has been nothing short of inspiring.
+I also extend my heartfelt thanks to Rob Nosofsky, who always asked sharp questions that challenged my thinking, and to Peter Todd, whose encouragement and enthusiasm played an especially important role during the final stages of my work.
+
+My journey into the study of the mind began at the Learning and Transfer Lab at the University of Wisconsin-Madison, where I am forever indebted to Dr.
+Shawn Green.
+He gave me my first research job despite my total lack of experience, and through his guidance, I discovered my passion for research.
+It was my time in his lab that made it clear to me that pursuing a career in psychological research was what I wanted to do.
+I also want to thank Aaron Cochrane for investing significant time in answering my many research questions, introducing me to R, and patiently humoring my naïve inquiries into statistics.
+
+The camaraderie, friendship, and intellectual stimulation I received from my friends at Indiana University have been vital to my graduate school experience.
+I am especially grateful to Johnathan Avery for introducing me to bouldering, which became my main source of exercise, and for our many fun and thought-provoking conversations.
+I also want to thank Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others from the Geolab, Cognitive Science program, and Psychology department for their support, which  made the long hours of work much more enjoyable.
+
+I owe much to my teachers at Pardeeville High School for laying the foundation of my education and to the professors at UW-Madison and Indiana University, who continued to foster and build upon that foundation.
+Their dedication helped to instill in me a love of learning and a drive to pursue knowledge that has lasted throughout my academic journey.
+
+Finally, I would also like to extend my heartfelt thanks to my family.
+My parents, Mary and Jim Gorman, have been unwavering pillars of support.
+My brother, Joseph Gorman, played a crucial role in the final stages of my dissertation.
+By hosting me for one of the final months of my work, he provided a novel and structured working environment that helped me overcome some of the most challenging hurdles.
+The support of my family has been instrumental in making this journey possible, and I am forever grateful for their love and encouragement.
+
+\newpage
+
+## Abstract
+
+The impact of training variability on generalization has been a long-standing topic in the study of human learning, with conflicting evidence about its potential benefits.
+This dissertation addresses these ambiguities by examining the effects of varied versus constant training in visuomotor skill learning through a combination of experimental and computational modeling approaches.
+Across two projects, we systematically compare varied training (multiple items) to constant training (single item) in a projectile-throwing task.
+Empirical findings reveal both positive and negative impacts of variability, highlighting the complex interplay between training conditions and generalization performance.
+To provide a theoretical account of these findings, this dissertation employs both instance-based and connectionist computational modeling approaches.
+The instance-based modeling approach introduced in Project 1 provides a theoretically justifiable method of quantifying and controlling for similarity between training and testing conditions, while also demonstrating that varied training may induce broader generalization in the similarity function relating training and test items.
+In Project 2, the Extrapolation-Association Model (EXAM) provided the best account of the testing data across all experiments, capturing the
+constant groups' ability to extrapolate to novel regions despite limited training experience, while also revealing potential detriments of varied training for simple extrapolation tasks.
+These results challenge simplistic notions about the universality of variability benefits in training and emphasize the need for tailored approaches that consider both the structure of the task environment and the prior knowledge of the learners.
+
+\newpage

### 2024-10-20 Manuscript/manuscript.qmd
re-render after fixing ugs revision issues
fix issue with figure 28 overlapping with page number

@@
 {{< include pre_sections/pre_docx.qmd >}}
-{{< include pre_sections/acknowledgements.qmd >}}
-{{< include pre_sections/abstract.qmd >}}
 :::
@@
 Bolded bars indicate bands that were trained, non-bold bars indicate extrapolation bands."
-#| fig-height: 14
+#| fig-height: 13.5
 #| fig-width: 11

### 2024-10-20 Manuscript/pre_sections/pre_html2.qmd
re-render after all ugs revision changes again

@@
 for the degree<br>
-Doctor of Philosophy<br><br>
+Doctor of Philosophy<br>
 in the Cognitive Science Program and<br>
@@
 
-<div class="copyright">&copy; 2024 <br><br> Thomas E. Gorman </div>
+<div class="copyright"> Copyright &copy; 2024 <br><br> Thomas E. Gorman </div>
 

### 2024-10-20 Sections/pre_sections/pre_pdf.qmd
re-render after all ugs revision changes again

--- 2023-10-17 Manuscript/pre_sections/pre_pdf.qmd
@@
 \begin{centering}
-\LARGE
-{Variability and Generalization - A Similarity-Based Account}
 
-\vspace*{1.5cm}
+{THE ROLE OF VARIABILITY IN LEARNING GENERALIZATION: A COMPUTATIONAL MODELING APPROACH}
 
-\LARGE
+\vspace{5\baselineskip}
+
 {Thomas E. Gorman}
 
-\vspace{11.5cm}
+\vspace{10.5cm}
 
-\end{centering}
-
-Submitted to the faculty of the University Graduate School in partial fulfillment of the
-requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
-Sciences and the Cognitive Science Program, Indiana University
-Indiana University
+Submitted to the faculty of the Graduate School \\
+in partial fulfillment of the requirements \\
+for the degree \\
+Doctor of Philosophy \\
+in the Cognitive Science Program and \\
+Department of Psychological and Brain Sciences, \\
+Indiana University \\
+October 2024
 
@@
 requirements for the degree of Doctor of Philosophy.
-\vspace{4cm}
+\end{center}
+\vspace{1cm}
+\
+Doctoral Committee
+\vspace{1cm}
+
+\begin{flushright}
+\underline{\hspace{5cm}} \\
+Robert L. Goldstone, Ph.D.
+\vspace{2cm}
+
+\underline{\hspace{5cm}} \\
+Robert M. Nosofsky, Ph.D.
+\vspace{2cm}
+
+\underline{\hspace{5cm}} \\
+Peter M. Todd, Ph.D.
+\vspace{2cm}
+
+\underline{\hspace{5cm}} \\
+Michael N. Jones, Ph.D.
+\end{flushright}
 
 \
-\_____________________________  Robert L. Goldstone
-\vspace{2.5cm}
-\
-\
-\_____________________________  Robert Nosofsky
-\vspace{2.5cm}
-\
-\_____________________________  Peter Todd
-\vspace{2.5cm}
-\
-\_____________________________  Mike Jones
+May 28th, 2024
 
@@
 
-@2023 \\
-\vspace{1cm}
+Copyright @ 2024 \\
+\vspace{.5cm}
 
@@
 \newpage
-\begin{center}
-\textbf{Acknowledgements}
-\end{center}
-\newpage
-
-\tableofcontents
-\newpage
-\listoffigures
-\newpage
-\listoftables
-\newpage
